### 2013-01-24 ABD_results.tex
Initial commit

\documentclass[11pt]{article}

\pdfpagewidth 8.5in
\pdfpageheight 11in

\setlength\topmargin{0in}
\setlength\headheight{0in}
\setlength\headsep{0.2in}
\setlength\textheight{8in}
\setlength\textwidth{6in}
\setlength\oddsidemargin{0in}
\setlength\evensidemargin{0in}
\setlength\parindent{0.25in}
\setlength\parskip{0.1in}

\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{amsthm}

      \theoremstyle{plain}
      \newtheorem{theorem}{Theorem}
      \newtheorem{lemma}[theorem]{Lemma}
      \newtheorem{corollary}[theorem]{Corollary}
      \newtheorem{proposition}[theorem]{Proposition}
      \newtheorem{conjecture}[theorem]{Conjecture}
      \newtheorem{question}[theorem]{Question}
      \newtheorem{example}[theorem]{Example}

      \theoremstyle{definition}
      \newtheorem{definition}[theorem]{Definition}

      \theoremstyle{remark}
      \newtheorem{remark}[theorem]{Remark}

% Strategy uparrow shortcuts
\newcommand{\win}{\uparrow}
\newcommand{\prewin}{\uparrow_{\text{pre}}}
\newcommand{\markwin}{\uparrow_{\text{mark}}}
\newcommand{\tactwin}{\uparrow_{\text{tact}}}
\newcommand{\ktactwin}[1]{\uparrow_{#1\text{-tact}}}
\newcommand{\kmarkwin}[1]{\uparrow_{#1\text{-mark}}}
\newcommand{\codewin}{\uparrow_{\text{code}}}
\newcommand{\limitwin}{\uparrow_{\text{limit}}}

\newcommand{\oneptcomp}[1]{#1^*}

\newcommand{\congame}[2]{Con_{O,P}(#1,#2)}
\newcommand{\clusgame}[2]{Clus_{O,P}(#1,#2)}

\newcommand{\lfkpgame}[1]{LF_{K,P}(#1)}
\newcommand{\lfklgame}[1]{LF_{K,L}(#1)}

\newcommand{\pfgame}[1]{PF_{F,C}(#1)}

\newcommand{\sigmaprodr}[1]{\Sigma\mathbb{R}^{#1}}
\newcommand{\sigmaprodtwo}[1]{\Sigma2^{#1}}

\newcommand{\<}{\langle}
\renewcommand{\>}{\rangle}

\newcommand{\rest}{\restriction}

\newcommand{\largecomment}[1]{}

\begin{document}

%%%%%%%%%
%COMMENT%
%%%%%%%%%
\largecomment{
Assume all spaces are locally compact.

\begin{proposition}
The following are all equivalent winning conditions for $\congame{\oneptcomp{X}}{\infty}$:
\begin{itemize}
\item The points chosen by $P$ converge to $\infty$.
\item All compact subsets of $X$ contain finitely many points chosen by $P$.
\item No compact subset of $X$ contains infinite points chosen by $P$.
\end{itemize}

The following are all equivalent winning conditions for $\clusgame{\oneptcomp{X}}{\infty}$:
\begin{itemize}
\item The points chosen by $P$ cluster about $\infty$.
\item All compact subsets of $X$ miss infinitely many points chosen by $P$.
\item No compact subset of $X$ contains cofinite points chosen by $P$.
\end{itemize}
\end{proposition}

\begin{proposition}
The winning condition for $\congame{\oneptcomp{X}}{\infty}$ is equivalent to the winning condition of $\lfkpgame{X}$.
\end{proposition}

\begin{proof}
First, suppose that the points chosen by $P$ have a limit point $l$, the contradiction of $\lfkpgame{\oneptcomp{X}}$'s winning condition. Every open set about $l$ contains infinitely many points, including a compact neighborhood of $l$. This contradicts the winning condition of $\congame{\oneptcomp{X}}{\infty}$.

Then, suppose that there was a compact subset of $X$ containing infinite points chosen by $P$, the contradiction of $\congame{\oneptcomp{X}}{\infty}$'s winning condition. Every infinite subset of a compact set has a limit point, contradicting $\lfkpgame{\oneptcomp{X}}$'s winning condition.
\end{proof}

\begin{theorem}
The following are all equivalent.
\begin{itemize}
\item $X$ is metacompact.
\item $O\tactwin\congame{\oneptcomp{X}}{\infty}$.
\item $O\tactwin\clusgame{\oneptcomp{X}}{\infty}$.
\end{itemize}
\end{theorem}

\begin{proof}
Gruenhage has shown $X$ is metacompact $\Rightarrow$ $K\tactwin\lfkpgame{X}$ (which is equivalent to $O\tactwin\congame{\oneptcomp{X}}{\infty}$), and obviously $O\tactwin\congame{\oneptcomp{X}}{\infty}$ $\Rightarrow$ $O\tactwin\clusgame{\oneptcomp{X}}{\infty}$. We proceed by modifying Gruenhage's proof that $K\tactwin\lfkpgame{X}$ implies $X$ is metacompact to show $O\tactwin\clusgame{\oneptcomp{X}}{\infty}$ does also.

Let $\mathcal{U}$ be a cover of $X$, and refine it to open $F_\sigma$ sets with compact closures. Let $K:\oneptcomp{X}\to K[X]$ be the complement of a winning clustering strategy for $O$ such that $K(x)$ is a compact neighborhood of $x$ for all $x\in X$.

Let $A(x)=\{p:x\not\in K(p)\}$.

For each $x$, we claim $x$ is not even a limit point of $A(x)$. To see this, suppose there was such an $x$, and choose any compact neighborhood $N$ of $x$. If $x$ was a limit of $A(x)$, then $N\cap A(x)\not=\emptyset$. We choose $x_0\in N\cap A(x)$, and note $x\not\in K(x_0)$ since $x_0\in A(x)$.

This makes $N\setminus K(x_0)$ a neighborhood of $x$, which must then intersect $A(x)$. We may then pick an $x_1$ in $N\cap A(x)\setminus K(x_0)$. By continuing this process inductively we find $x_n$ in $N\cap A(x) \setminus \bigcup_{0\leq i < n} K(x_i)$. Since the $x_n$ are all in the compact set $N$, the winning condition for $\clusgame{\oneptcomp{X}}{\infty}$ is not met for the play $\left<x_0,\oneptcomp{X}\setminus K(x_0),x_1,\oneptcomp{X}\setminus K(x_1),\dots\right>$, contradicting the fact that $K$ is the complement of a winning strategy.

Let $K'(x)=Int(K(x)\setminus A(x))$. We note that $x\in K'(x)$ since $x$ was not a limit point or member of $A(x)$. So for each $K$ let $\{K'(x):x\in K\}$ be an open cover, and take a finite subset $F(K)\subset K$ which yields the subcover $\{K'(x):x\in F(K)\}$.

Enumerate $\mathcal{U}=\{U_\alpha: \alpha < \lambda\}$. We define $\mathcal{U}_\alpha$ for $\alpha<\lambda$ to fulfill the following:

\begin{itemize}
\item $\mathcal{U}_\alpha$ is countable
\item $\{U_\beta: \beta<\alpha\} \subseteq \bigcup_{\beta\leq\alpha} \mathcal{U}_\beta$
\item If \[N_\alpha = \left(\bigcup \mathcal{U}_\alpha\right) \setminus \bigcup_{\beta<\alpha} \left( \bigcup \mathcal{U}_\beta \right)\]

(that is, $N_\alpha$ contains the points covered by $\mathcal{U}_\alpha$ and not covered by a previous $\mathcal{U}_\beta$)

then there exists a countable $S_\alpha\subseteq N_\alpha$ where \[ N_\alpha \subseteq \bigcup_{x\in S_\alpha} K'(x) \subseteq \bigcup_{x\in S_\alpha} K(x) \subseteq \bigcup \mathcal{U}_\alpha\]
\end{itemize}

To start, let $\mathcal{U}_0$ and $\mathcal{U}_\alpha$ for every limit $\alpha$ be the empty set. For the successor ordinal $\alpha+1$, let $\mathcal{U}_{\alpha+1,0}=\{U_\alpha\}$ and $S_{\alpha+1,0}=\emptyset$. Then let $O_{\alpha+1}=\bigcup_{\beta\leq\alpha}\bigcup\mathcal{U}_\beta$, the points covered by previous $\mathcal{U}_\beta$.

We then define \[S_{\alpha+1,n+1}=\bigcup_{U\in\mathcal{U}_{\alpha+1,n}} F(Cl(U)\setminus O_{\alpha+1})\] and let $\mathcal{U}_{\alpha+1,n+1}\subseteq \mathcal{U}$ be a finite cover of $\bigcup_{x \in S_{\alpha+1,n+1}} K(x)$. Note that $S_{\alpha,n}$ and $U_{\alpha,n}$ are finite at every step $n$, so we may define $S_\alpha = \bigcup_{n<\omega} S_{\alpha,n}$ and $U_\alpha=\bigcup_{n<\omega} U_{\alpha,n}$.

Such $\mathcal{U}_\alpha$ may be seen to fulfill the above requirements.

Let $W_\alpha = \bigcup_{x\in S_\alpha} K'(x)$. Note $W_\alpha$ contains everything in $\mathcal{U}_\alpha$ not covered by lower $\mathcal{U}_\beta$.

We now show the collection of $W_\alpha$ is point-finite. Suppose it wasn't: if $x \in W_{\alpha_n}$ for $\alpha_0<\alpha_1<\dots$, then for each $n$ choose some $x_n \in S_{\alpha_n}$ where $x \in K'(x_n)$.

FINISH THIS

\end{proof}

}
%%%%%%%%%%%%
%ENDCOMMENT%
%%%%%%%%%%%%

\begin{example}
Let $X$ be a zero-dimensional, compact L-space (hereditarally Lindeloff and non-separable). It is a fact that there exists a point-countable collection $\mathcal{U}=\{U_\alpha : \alpha<\omega_1\}$ of clopen sets in $X$, and it is also true that any point-finite subcollection of $\mathcal{U}$ is countable. %That is, if we let $A_x = \{\alpha : x \in U_\alpha\}$, then $|A_x|\leq\omega$ for all $x\in X$.

Let $C = \{c_\alpha : \alpha <\omega_1\}$ be any uncountable subset of the Cantor space $2^\omega$. Let $X_s = X \times \{s\}$ for each $s \in 2^{<\omega}$, and $U_{\alpha,s} = U_\alpha \times \{s\}$.

Finally, let \[\mathbb{X} = C \cup \bigcup_{s\in 2^{<\omega}} X_s\] be a tree of $2^{<\omega}$ copies of $X$, and where \[c_\alpha \cup \bigcup_{n < \omega} U_{\alpha, x_\alpha \restriction n}\] is an open set about each $c_\alpha$.
\end{example}

\begin{definition}
Let $S\in[\omega_1]^{<\omega}$ and $m<\omega$. Define 
    \[K_S = \bigcup_{\alpha \in S} \left( c_\alpha \cup \left(\bigcup_{s < c_\alpha} U_{\alpha,s}\right)\right)\] 
    \[ A = \{z^\frown \<1\> : z \in 1^{<\omega}\}\] 
    \[ K^*_S = K_S \setminus \bigcup_{s \in A} X_s \] 
and 
    \[L_m = \bigcup_{s \in 2^{<m}} X_s\] 
and observe that every compact set is dominated by $K^*_S \cup L_m$ for some $S,m$. Intuitively, $K^*_S$ collects the branches of $U_\alpha$ converging up to $c_\alpha$ for each $\alpha \in S$ while avoiding copies $X_s$ of $X$ for each $s$ in an antichain $A$, and $L_m$ collects the copies $X_s$ of $X$ with $|s| < m$ at the base of the tree.
\end{definition}

\begin{proposition}
Without loss of generality, $P$ always plays points in $\bigcup_{s \in 2^{<\omega}} X_s$.
\end{proposition}

\begin{proposition}
$K \win \lfkpgame{\mathbb{X}}$.
\end{proposition}

\begin{proof}
In response to a point $\<x,s\>$, $K$ observes that there are only countably many $\alpha$ such that $U_\alpha \times \{s\}$ contains $\<x,s\>$ (by point-countability of $X$). Enumerate these as $\alpha_n$. $K$ makes a promise that during round $m$, $K$ will forbid some superset of $K_{\{\alpha_n : n\leq m\}}$. Finally, $K$ also always forbids a superset of $L_{|s|+1}$.

Suppose $P$'s moves clustered at some point. Since $K$ forbade $L_{|s|+1}$ during each round, that point must be $c_\alpha$ for some $\alpha$. $P$'s play then must have included a subsequence of points $\<x_0,s_0\>,\<x_1,s_1\>,\<x_2,s_2\>\dots$ such that $x_n \in U_\alpha$ and $s_n \leq s_{n+1} \leq c_\alpha$. However, in response to $\<x_0,s_0\>$, $K$ made a promise to eventually forbid a superset of $K_{\{\alpha\}}$, making every $\<x_n,t_n\>$ illegal after that round.
\end{proof}

%%%%%%%%%
%COMMENT%
%%%%%%%%%
\largecomment{
\begin{lemma}
$K$ lacks a "simple" 2-tactic which is a winning strategy in $\lfkpgame{\mathbb{X}}$.
\end{lemma}

\begin{proof}
Let $a_n = \<0,\dots,0,1\>$ with $n$ zeros We define a simple 2-tactic as one which is dominated by a compact set of the form $K^*_S\cup L_{n+1}$, where $n$ is equal to the height of the highest observable move by $P$, and where $K^*_S = K_S \setminus \bigcup_{n} X_{a_n}$.

Considering a simple 2-tactic $\sigma(\<x,s\>,\<y,t\>)$, we note it is dominated by $K^*_{S(x,y,n(s,t))}\cup L_{n(s,t)+1}$, where $n(s,t)=\max(|s|,|t|)$, and $$S(x,y,n) = \bigcup_{s,t\in 2^{\leq n}} S(\<x,s\>,\<y,t\>)$$ Strengthen $\sigma$ accordingly.

But $K$ could, for fixed $x^*\in X$, define the 1-tactic $\tau(\<x,s\>) = \sigma(\<x,s\>,\<x^*,a_{|s|}\>)$. Since no winning $1$-tactic exists, let $\<x_0,s_0\>,\<x_1,s_1\>,\dots$ be a legal counter to $\tau$ clustering at $c\in C$.

We claim $\<x_0,s_0\>, \<x^*,a_{|s_0|}\>, \<x_1,s_1\>, \<x^*,a_{|s_1|}\>, \dots$ is a counter to the 2-tactic. Since $\<x_0,s_0\>, \<x_1, s_1\>, \dots$ clusters at $c$, we need only show it is legal. By the definition of simple, each $\<x^*, a_{|s_i|}\>$ is a legal move. We note that since $\<x_{i+1},s_{i+1}\>$ was not forbidden by any $\tau(\<x_j,s_j\>)= K^*_{S(x_j,x^*,|s_j|+1)}\cup L_{|s_j|+2}$ for $j\leq i$, it could not be forbidden by $$\sigma(\<x_j,s_j\>,\<x^*,a_{|s_{j-1}|}\>) \subseteq \sigma(\<x_j,s_j\>,\<x^*,a_{|s_j|}\>) = K^*_{S(x_j,x^*,|s_j|+1)}\cup L_{|s_j|+2} $$
\end{proof}

\begin{theorem}
$K\not\ktactwin{2}\lfkpgame{\mathbb{X}}$.
\end{theorem}

\begin{proof}
Take the 2-tactic $\sigma(\<x,s\>,\<y,t\>)$. We define $S(x,y,n)$ and $m(x,y,n)$ so that \[ \bigcup_{s,t \in 2^{\leq n}} \sigma(\<x,s\>,\<y,t\>) \subseteq K_{S(x,y,n)} \cup L_{m(x,y,n)}\] and $|S(x,y,n)|, n < m(x,y,n)$. We've shown that every 2-tactial strategy can be improved so that it only considers $x$, $y$, and $\max(|s|,|t|)$. In addition, as there are $2^{m(x,y,\max(|s|,|t|))}$ copies of $X$ not forbidden by such an improved strategy, and at most \[\sum_{i=1}^{m(x,y,\max(|s|,|t|))-1} i < 2^{m(x,y,\max(|s|,|t|))}\] branches forbidden by this strategy, there is always some copy of $X$ at height $m(x,y,\max(|s|,|t|))$ completely legal to play within by $P$ after each move by $K$ according to this strategy.

Now, define the simple 2-tactic $\tau(\<x,s\>,\<y,t\>)=K^*_{S(x,y,m(x,y,n(s,t))+1)} \cup L_{n(s,t)+1}$. Since there are no winning simple 2-tactics, let $\<x_0,s_0\>,\<x_1,s_1\>,\dots$ be a successful counter to $\tau$ clustering at $c$.

We claim $\<x_0,t_0\>, \<x_1,t_1\>, \dots$ where $t_0=c\rest 0$, $t_1=c\rest 1$, and
$$
t_{i+2} = \left\{
\begin{array}{ll}
\text{arbitrary provided } |t_{i+2}| = m(x_i,x_{i+1},|t_{i+1}|) & x_{i+2}= x^* \text{ and } s_{i+2} \in \{a_n : n < \omega\} \text{ (1) } \\
c\rest m(x_i,x_{i+1},|t_{i+1}|) & \text{otherwise and } s_{i+2} < c  \text{ (2) }\\
\text{arbitrary extension of } s_{i+2} \text{ of length } m(x_i,x_{i+1},|t_{i+1}|) & \text{otherwise} \text{ (3) }
\end{array}
\right.
$$
is a legal counter to $\sigma$. It certainly clusters at $c$, so we need only show it is legal.

Suppose $\<x_{i+2}, t_{i+2}\>$ were an illegal move. Then it must have been forbidden by some $K_{S(x_i,x_{i+1},|t_{i+1}|)}\cup L_{m(x_i,x_{i+1},|t_{i+1}|)}$. In case (1), we strengthened $m$ to ensure that $x^*$ was always legal somewhere on the first level not forbidden by $L_m$. In either case (2) or (3), $s_{i+2}<t_{i+2}$, keeping the move legal.

\end{proof}
}
%%%%%%%%%%%%
%ENDCOMMENT%
%%%%%%%%%%%%

\begin{theorem}
$K\not\tactwin\lfkpgame{\mathbb{X}}$.
\end{theorem}

\begin{proof}
(Vanished somewhere during my editing... looking for it now!)
\end{proof}

\begin{theorem}
$K\not\ktactwin{2}\lfkpgame{\mathbb{X}}$.
\end{theorem}

\begin{proof}
Suppose $\sigma(\<x,s\>,\<y,t\>)$ was a winning 2-tactical strategy. We may define $S(x,y,n)$ and $m(x,y,n)$ such that for each $(x,y)$,
\[
\bigcup_{s,t \in 2^{\leq n}} \sigma(\<x,s\>,\<y,t\>) \subseteq K^*_{S(x,y,n)} \cup L_{m(x,y,n)}
\]

Select an arbitrary point $x' \in X$. We define a tactical strategy 
\[
\tau(x,s) = K^*_{S(x,x',m(x,x',|s|)+1)} \cup L_{m(x,x',m(x,x',|s|)+1)}
\]
We complete the proof by showing $\tau$ is a winning tactical strategy (a contradiction).

Suppose
\[
\<x_0, s_0\>, \<x_1, s_1\>, \<x_2, s_2\>, \dots
\]
successfully countered $\tau$ by clustering at $c\in C$ (the strategy trivially prevents clustering elsewhere). Let $z_n = \<0,\dots,0\>$ with $n$ zeros. We claim
\[
\<x_0, s_0\>, \<x', {z_{m(x_0,x_0,|s_0|)}}^\frown\<1\>\>, \<x_1, s_1\>, \<x', {z_{m(x_1,x',|s_1|)}}^\frown\<1\>\>,  \<x_2, s_2\>, \<x', {z_{m(x_2,x',|s_2|)}}^\frown\<1\>\>, \dots
\]
is a successful counter to $\sigma$.

Obviously it also clusters at $c$, so we need only show that it is a legal counter to $\sigma$. Note that \[\sigma(\<x', {z_{m(x_i,x',|s_i|)}}^\frown\<1\>\>, \<x_{i+1}, s_{i+1}\>) \subseteq \sigma(\<x_{i+1}, s_{i+1}\>, \<x', {z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>\>)\] since the only difference in input is a higher copy of $x'\in X$.

Suppose $\<x_{i}, s_{i}\>$ was an illegal move. Then for some $j<i$, that move was forbidden by 
\[
\sigma(\<x_{j}, s_{j}\>, \<x', {z_{m(x_{j},x',|s_{j}|)}}^\frown\<1\>\>)
\]
\[
\subseteq 
K^*_{S(x_{j},x',m(x_{j},x',|s_{j}|)+1)} \cup L_{m(x_{j},x',m(x_{j},x',|s_{j}|)+1)}
= \tau(x_j,s_j)
\]
which is a contradiction as it was a legal move against $\tau$.

Finally, consider $\<x',{z_{m(x_i,x',|s_i|)}}^\frown\<1\>\>$. Since the length of ${z_{m(x_i,x',|s_i|)}}^\frown\<1\>$ is longer than $m(x_i,x',|s_i|)$, it's not forbidden by any $L_m$ played by $K$. And since ${z_{m(x_i,x',|s_i|)}}^\frown\<1\>$ is on the antichain $A$ avoided by the $K^*_S$s, it could never have been forbidden at all.
\end{proof}

\begin{proposition}
The above proof can be adapted to prove $K\not\ktactwin{k}\lfkpgame{\mathbb{X}}$.
\end{proposition}

\end{document}

### 2013-01-24 menger.tex
Initial commit

\input{./header.tex}

\begin{document}

  \begin{definition}
    $X$ is \textbf{Menger} if for all open covers $\mathcal{U}_0,\mathcal{U}_1,\dots$ there exist finite subcollections $\mathcal{F}_n \subseteq \mathcal{U}_n$ such that $\bigcup_{n<\omega} \mathcal{F}_n$ is a cover of $X$.
  \end{definition}

  \begin{proposition}
    $\sigma$-compact $\Rightarrow$ Menger $\Rightarrow$ Lindelof
  \end{proposition}

  \begin{definition}
    In the two-player game $\mengame{X}$ player $C$ chooses open covers $\mathcal{U}_n$ of $X$, followed by player $S$ choosing a finite subcollection $\mathcal{F}_n\subseteq\mathcal{U}_n$. $S$ wins if $\bigcup_{n<\omega} \mathcal{F}_n$ is a cover of $X$.
  \end{definition}

  \begin{theorem}
    $X$ is Menger if and only if $S \win \mengame{X}$.
  \end{theorem}

  \begin{proof}
    First, suppose $X$ wasn't Menger. Then there would exist open covers $\mathcal{U}_0,\mathcal{U}_1,\dots$ of $X$ such that for any choice of finite subcollections $\mathcal{F}_n\subseteq\mathcal{U}_n$, $\bigcup_{n<\omega} \mathcal{F}_n$ isn't a cover of $X$. Thus $C\prewin\mengame{X} \Rightarrow S \not\win\mengame{X}$.

    The other direction is based upon Gruenhage's topological game presentation. Assume $X$ is Menger, and consider a strategy for $C$ in $\mengame{X}$.

    Since $X$ is Lindelof, we can assume $C$ plays only countable covers of $X$. Then, since $S$ is choosing finite subsets, we may assume $S$ chooses some initial segement of the countable cover. In turn, we can assume $C$ plays an increasing open cover $\{U_0,U_1,\dots\}$ where $U_n\subseteq U_{n+1}$. And in that case, it's suffient to assume $S$ simply chooses a singleton subset of each cover. And finally, since choices made by $S$ are already covered, we can assume that every open set in a cover played by $C$ covers the sets chosen by $S$ previously.

    As a result, we have the following figure of a tree of plays which I need to draw:

    (Insert figure here.)

    Note that for $a,b,c\in\omega^{<\omega}$ and $m\leq n$, we know $U_{a\concat m}\subseteq U_{a\concat n}$ and $U_a \subseteq U_{a\concat b}$. Also, if $a=b\concat n \concat c$, then \[U_{a\concat m} = U_{b\concat n \concat c \concat m} \supseteq U_{b\concat n} \supseteq U_{b\concat m}\] (for example: $U_{48397}\supseteq U_{4837} \supseteq U_{47}$).

    We may observe that if $S$ can find an $f:\omega\to\omega$ such that $\bigcup_{n<\omega}U_{f\rest n} = X$, she can use $\{U_{f\rest 0}\}, \{U_{f\rest 1}\}, \dots$ to counter $C$'s strategy.

    Let $\ds V_k^n = \bigcap_{a\in\omega^{\leq n}} U_{a\concat k}$. We claim that (1) $V_k^n$ is open, (2) $\mathcal{V}^n=\{V_0^n,V_1^n,\dots\}$ is increasing, and (3) $\mathcal{V}^n$ is a cover. Proofs:

    \begin{enumerate}
      \item
      $\ds V_k^n = \bigcap_{a\in\omega^{\leq n}} U_{a\concat k} = \bigcap_{a\in k^{\leq n}} U_{a\concat k}$

      \item
      $\ds V_{k+1}^n = \bigcap_{a\in{k+1}^{\leq n}} U_{a\concat (k+1)} \supseteq \bigcap_{a\in{k+1}^{\leq n}} U_{a\concat k} \supseteq \bigcap_{a\in{k}^{\leq n}} U_{a\concat k} = V_k^n$

      \item
      Let $x\in X$ and pick $l<\omega$ such that $x\in U_l$. Then for $a\in l^{\leq n}$, choose $l_a$ such that $x\in U_{a\concat l_a}$. Then let $k>l_a$ for all $a$. It follows that \[x \in \bigcap_{a\in k^{\leq n}} U_{a\concat l_a} \subseteq \bigcap_{a\in k^{\leq n}} U_{a\concat k} = V_k^n\] THIS ISN'T QUITE RIGHT SHOULD FIX THIS
    \end{enumerate}

    Finally, apply Menger to $\mathcal{V}^n$, resulting in the cover $\{V_{f(0)}^0, V_{f(1)}^1, \dots\}$, noting \[X = \bigcup_{n<\omega}V_{f(n)}^n \subseteq \bigcup_{n<\omega} U_{(f\rest n)\concat f(n)} = \bigcup_{n<\omega} U_{f\rest n+1}\]
  \end{proof}

\end{document}

### 2013-01-24 old_phd_research_results_april_2012.tex
Initial commit

\documentclass[11pt]{article}

\pdfpagewidth 8.5in
\pdfpageheight 11in

\setlength\topmargin{0in}
\setlength\headheight{0in}
\setlength\headsep{0.2in}
\setlength\textheight{8in}
\setlength\textwidth{6in}
\setlength\oddsidemargin{0in}
\setlength\evensidemargin{0in}
\setlength\parindent{0.25in}
\setlength\parskip{0.1in}

\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{amsthm}

      \theoremstyle{plain}
      \newtheorem{theorem}{Theorem}
      \newtheorem{lemma}[theorem]{Lemma}
      \newtheorem{corollary}[theorem]{Corollary}
      \newtheorem{proposition}[theorem]{Proposition}
      \newtheorem{conjecture}[theorem]{Conjecture}
      \newtheorem{question}[theorem]{Question}
      \newtheorem{example}[theorem]{Example}

      \theoremstyle{definition}
      \newtheorem{definition}[theorem]{Definition}

      \theoremstyle{remark}
      \newtheorem{remark}[theorem]{Remark}

% Strategy uparrow shortcuts
\newcommand{\prewin}{\uparrow_{\text{pre}}}
\newcommand{\markwin}{\uparrow_{\text{mark}}}
\newcommand{\tactwin}{\uparrow_{\text{tact}}}
\newcommand{\ktactwin}[1]{\uparrow_{#1\text{-tact}}}
\newcommand{\kmarkwin}[1]{\uparrow_{#1\text{-mark}}}
\newcommand{\codewin}{\uparrow_{\text{code}}}
\newcommand{\limitwin}{\uparrow_{\text{limit}}}

\begin{document}

\centerline{\bf PhD Research Results}
\centerline{Steven Clontz}

\begin{definition} Some notation on games of length $\omega$:

\begin{itemize}
\item A \textbf{game of length $\omega$} consists of two \textbf{Players} I and II. On \textbf{round} $n$ of $\omega$, Player I first takes a \textbf{turn} choosing an element of some set $X$, followed by Player II taking a turn choosing an element from some set $Y$.

\item A \textbf{move} by a player is the selection that player makes during a particular round.

\item A \textbf{rule} for a Player in a game is a condition on that player's move during each round. A move is said to be \textbf{legal} if it doesn't violate the rule.

\item A \textbf{play} by Player I is a sequence $\left<x_0,x_1,\dots\right> \in X^\omega$ (and similar for Player II). It is said to be \textbf{legal} if each move is legal. A finite initial sequence of a play is called a \textbf{partial play}.

\item A \textbf{strategy} for a Player is a function which has all possible partial plays by the opposing player as its domain. It denotes the choice for that Player on each turn. It is said to be \textbf{legal} if it yields only legal moves when the opposing player makes only legal moves.

\item A \textbf{counter} to a legal strategy by a Player is a function which has as its domain the turn number and the other player's strategy. It is said to be \textbf{legal} if it only yields legal moves.

\item A \textbf{winning condition} is some condition on the plays made by both players.

\item At the conclusion of a game, if all moves are legal, then Player I \textbf{wins} the game if the winning condition is satisfied, and Player II wins the game otherwise. (Should any move be illegal, then the first player to make an illegal move loses the game to the other player.)
\end{itemize}
\end{definition}

When the sets $X,Y$ are related to a topological space, it is said to be a \textbf{topological game}. The presence or absense of a ``winning'' strategy for one player or another characterizes a property of the space.

\begin{definition}
A strategy for Player A is said to be a \textbf{winning strategy} if there does not exist a counter which allows the other player to win the game. If Player Z has a winning strategy for the game $G$, this can be denoted $Z \uparrow G$.
\end{definition}

Proofs showing the existance of a winning strategy typically define the winning strategy, and then show that it defeats every possible play by the opponent. Proofs showing the nonexistance of a winning strategy typically define the counter to any arbitrary strategy.

In the mid 1980s, Dr. Gary Gruenhage defined the following topological games.

\begin{definition}
The \textbf{compact-point game on a topological space $X$} is denoted $G_{K,P}(X)$. During round $n$, Player I (called $K$) chooses a compact set $K_n\in K[X]$, and Player II (called $P$) chooses a point $x_n\in X$. $K$ must follow the rule that $K_{n+1}\supseteq K_n$, while $P$ must follow the rule that $x_n\not\in K_n$. The winning condition for $K$ is that the collection of singletons chosen by $P$, $\{\{x_n\} : n<\omega\}$, must be locally finite everywhere in the space. (This is equivalent to the set $\{x_n : n<\omega\}$ lacking a cluster point.)
\end{definition}

\begin{definition}
The \textbf{compact-compact game on a topological space $X$} is denoted $G_{K,L}(X)$. During round $n$, Player I (called $K$) chooses a compact set $K_n\in K[X]$, and Player II (called $L$) also chooses a compact set $L_n\in K[X]$. $K$ must follow the rule that $K_{n+1}\supseteq K_n$, while $P$ must follow the rule that $L_n\cap K_n=\emptyset$. The winning condition for $K$ is that the collection of compact sets chosen by $L$, $\{L_n : n<\omega\}$, must be locally finite everywhere in the space.
\end{definition}

An interesting property of the game $G_{K,L}(X)$ is the following result, proven by Gruenhage in his paper \textit{Games Covering Properties and Eberlein Compacts}.

\begin{theorem}
The following are equivalent for a locally compact space $X$:
    \begin{itemize}
    \item $X$ is paracompact
    \item $K \uparrow G_{K,L}(X)$.
    \end{itemize}
\end{theorem}

However, often it is the presence of ``limited information'' strategies which can characterize interesting properties of a space.

\begin{definition}
A \textbf{limited information strategy} for a game is a function whose domain is restricted to less information than all previous moves by the opposing player.
\end{definition}

In the above mentioned paper, Gruenhage used the following limited information strategies to prove some interesting characterizations based on the game $G_{K,P}(X)$.

\begin{definition}
A \textbf{tactical strategy} considers only the most recent move by the opposing player. If Player $Z$ has a winning tactical strategy for a game $G$, this may be denoted $Z \uparrow_{\text{tact}} G$.
\end{definition}

\begin{definition}
A \textbf{Markov strategy} considers only the most recent move by the opposing player and the turn number. If Player $Z$ has a winning Markov strategy for a game $G$, this may be denoted $Z \uparrow_{\text{mark}} G$.
\end{definition}

\begin{theorem}
The following are equivalent for a locally compact space $X$:
    \begin{itemize}
    \item $X$ is metacompact
    \item $K \uparrow_{\text{tact}}G_{K,P}(X)$.
    \end{itemize}
\end{theorem}

\begin{theorem}
The following are equivalent for a locally compact space $X$:
    \begin{itemize}
    \item $X$ is $\sigma$-metacompact
    \item $K \uparrow_{\text{mark}}G_{K,P}(X)$.
    \end{itemize}
\end{theorem}

Upon learning these results, one might wonder the consequences of the existence of this type of limited information strategy:

\begin{definition}
A \textbf{predetermined strategy} considers only the turn number. If Player $Z$ has a winning predetermined strategy for a game $G$, this may be denoted $Z \prewin G$.
\end{definition}

Intuitively, if a player is using a predetermined strategy, then that player decides every move he or she will make before the game even begins, ignoring the other player's moves.

Consider the following trivial result:

\begin{definition}
A \textbf{button-mashing strategy} is a constant function. If Player $Z$ has a winning button-mashing strategy for a game $G$, this may be denoted $Z \uparrow_{\text{mash}} G$.
\end{definition}

\begin{proposition}
The following are equivalent for any space $X$:
    \begin{itemize}
    \item $X$ is compact
    \item $K \uparrow_{\text{mash}}G_{K,P}(X)$.
    \end{itemize}
\end{proposition}

Observing that giving $K$ the added information of turn number to a tactical strategy (making it Markov) changed the characterization of a metacompact space into a $\sigma$-metacompact space, it would be very convenient if adding that same information to a button-mashing strategy (making it predetermined) would similarly change the characterization of a compact space into $\sigma$-compact.

\begin{proposition}
If $K \prewin G_{K,P}(X)$, then $X$ is $\sigma$-compact.
\end{proposition}

\begin{proof}
Let $K_n$ be the sets given by the winning predetermined strategy. If they did not union to $X$, then the counter play $p_n=p$ for some $p\in X\setminus \bigcup_n K_n$ would defeat the ``winning'' strategy.
\end{proof}

\begin{theorem}
If $Y$ is a locally compact, Lindel\"of space, then $K \prewin G_{K,P}(X)$.
\end{theorem}

\begin{proof}
Let $\mathcal{K}$ be a collection of compact neighborhoods whose interiors cover $X$. By Lindel\"of, let $\{K_n : n<\omega\}$ be a countable subcollection whose interiors cover $X$. We then define the predetermined strategy $\sigma(n)=\bigcup_{m\leq n} K_n$.

Let $p_n$ give a play by $P$. If $p$ is a cluster point of the $p_n$, then every open set about $p$ contains infinitely many $p_n$. Let $K_N$ be some compact neighborhood in $\{K_n : n<\omega\}$ which covers $p$. Then $K_N$ contains infinitely many $p_n$, which means sometime after round $N$, $P$ played in a set already covered by the strategy $\sigma$, which is an illegal move. Thus $\sigma$ is a winning predetermined strategy.
\end{proof}

\begin{corollary}
The following are equivalent for a locally compact space $X$:
    \begin{itemize}
    \item $X$ is $\sigma$-compact
    \item $X$ is Lindel\"of
    \item $K \prewin G_{K,P}(X)$.
    \end{itemize}
\end{corollary}

We now turn our attention to an example of a $\sigma$-compact space for which no predetermined strategy exists (which must, of course, not be locally compact). In fact, $P$ will instead have a winning tactical strategy.

\begin{definition}
Let $M=\omega^2\cup\{\infty\}$ denote the \textbf{metric fan space} with the topology generated by the singletons in $\omega^2$ and sets of the form $((\omega\setminus n)\times\omega) \cup \{\infty\}$ for $n<\omega$.
\end{definition}

\begin{proposition}
For each compact set $C$ in $M$, there exists a minimal dominating function $f_C$ such that for each $(x,y)\in C\setminus\{\infty\}$, $f(x)> y$.
\end{proposition}

\begin{lemma}
$P \markwin G_{K,P}(M)$ where $M$ is the metric fan space. (This implies $K\not\uparrow G_{K,P}(M)$.)
\end{lemma}

\begin{proof}
Let $P$ respond to the move $C\in K[X]$ by $K$ on round $n$ with the point $p=(n,s_C)$ such that $s_C = \min(\{y<\omega : f_C(n) < y\}$. It is easy to see that either $p_n\rightarrow \infty$, so $P$ has a winning tactical strategy.
\end{proof}

Furthermore, by a theorem due to Eric van Douwen...

\begin{theorem}
Every first-countable non-locally countably compact space has the metric fan space $M$ as a closed subspace.
\end{theorem}

... we have the following corollary:

\begin{corollary}
$P \markwin G_{K,P}(X)$ where $X$ is a first-countable non-locally countably compact space. (This implies $K\not\uparrow G_{K,P}(X)$.)
\end{corollary}

(Open question: does $P \tactwin G_{K,P}(X)$?)

\begin{theorem}
$P \not\tactwin D_{K,P}(M)$ where $M$ is the metric fan space.
\end{theorem}

\begin{proof}
Give $P$ the tactic $\sigma$. Suppose that for all $n<\omega$, there is an upper bound $m<\omega$ so that for each $C \in K[M]$, if $\pi_1(\sigma(C))=n$, then $\pi_2(\sigma(C))<m$. We may then define $f(n)=m$, and let $C_f=\{(x,y):f(x)<y\}\in K[M]$. $\sigma(C_f)$ must show a contradiction if $\sigma$ is legal.

So it follows that there is some $n<\omega$ such that there are compact sets $C_i\in K[M]$ with $\pi_1(\sigma(C_i))=n$ and $\pi_2(\sigma(C_i))<\pi_2(\sigma(C_{i+1}))$. The play $\left<C_0,\sigma(C_0),C_1,\sigma(C_1),\dots\right>$ is a counter to $\sigma$.
\end{proof}

While $K\prewin G_{K,P}(X)$ implies $X$ is $\sigma$-compact, it in fact implies something stronger.

\begin{definition}
A space $X$ is \textbf{hemicompact} if there exists a chain of increasing compact sets $K_0\subseteq K_1 \subseteq \dots$ such that every compact set in $X$ is a subset of some $K_n$.
\end{definition}

\begin{lemma}
If $K\prewin G_{K,P}(X)$, then $X$ is hemicompact. Furthermore, any predetermined winning strategy for $K$ witnesses hemicompactness.
\end{lemma}

\begin{proof}
Let $\sigma$ be a predetermined strategy for $K$ in the game $G_{K,P}(Y)$ such that there exists a compact set $C$ with $C \not\subseteq \sigma(n)$ for all $n$. On each turn, have $P$ play some $y_n\in C \setminus \sigma(n)$. Then the $y_n$ are an infinite subset of the compact set $C$ and must have a cluster point in $C$, showing $\sigma$ is not a winning strategy.

Thus if $K$ has a winning predetermined strategy, it witnesses that $Y$ is hemicompact.
\end{proof}

In fact, for locally compact spaces, finding winning predetermined strategies for $G_{K,P}(X)$ and $G_{K,L}(X)$ are equivalent problems.

\begin{theorem}
The following are equivalent for any locally compact space $X$:
  \begin{itemize}
  \item $X$ is hemicompact.
  \item $K \prewin G_{K,L}(X)$.
  \item $K \prewin G_{K,P}(X)$.
  \end{itemize}
\end{theorem}

\begin{proof}
Let $Y$ be hemicompact, witnessed by $K_n=\sigma(n)$. Let $L_0,L_1,\dots$ be a play by $L$ in $G_{K,L}(X)$. Suppose that this play defeats $\sigma$. Then let $x\in X$ be the point such that for all neighborhoods $U$ of $x$, $U$ hits infinite $L_n$. Let $C$ be a compact neighborhood of $x$, which must hit infinite $L_n$. As $K_n$ witnesses hemicompactness, $C \subseteq K_N = \sigma(N)$ for some $N$. But then $C\subset K_N$ intersects infinitely many $L_n$, which shows that the play $L_0,L_1,\dots$ was illegal. Thus $\sigma$ defeats every legal play by $L$ and is thus a winning predetermined strategy for $K$ in $G_{K,L}(X)$.

We conclude by noting that any winning strategy for $G_{K,L}(X)$ is a winning strategy for $G_{K,P}(X)$, and the existence of a winning predetermined strategy for $G_{K,P}(X)$ implies hemicompact by the previous lemma.
\end{proof}

\begin{corollary}
The following are equivalent for any locally compact space $X$:
  \begin{itemize}
  \item $X$ is Lindel\"of.
  \item $X$ is $\sigma$-compact.
  \item $X$ is hemicompact.
  \item $K \prewin G_{K,L}(X)$.
  \item $K \prewin G_{K,P}(X)$.
  \end{itemize}
\end{corollary}

The compact-point and compact-compact games are also useful in inspecting compactly generated ``k''-spaces.

\begin{definition}
A topological space is called a \textbf{$k$-space} if the following condition is satisfied: \[C \subseteq X \text{ is closed in } X\, \Leftrightarrow \, C\cap K \text{ is closed in } K \text{ for all compact sets } K\in K[X]\]
\end{definition}

\begin{definition}
A topological space is called a \textbf{$k_\omega$-space} if there exist $K_0,K_1,\dots \in K[X]$ that satisfy the following condition: \[C \subseteq X \text{ is closed in } X\, \Leftrightarrow \, C \cap K_n \text{ is closed in } K_n \text{ for all } n\]
\end{definition}

\begin{theorem}
The following are equivalent for any Hausdorff $k$-space $X$:
  \begin{itemize}
  \item $X$ is hemicompact.
  \item $X$ is $k_{\omega}$.
  \item $K \prewin G_{K,P}(X)$.
  \end{itemize}
Furthermore, all predetermined strategies for $K$ witness hemicompact and $k_\omega$, and any witness to hemicompact/$k_\omega$ witnesses the other and serves as a predetermined strategy for $K$.
\end{theorem}

\begin{proof}
If $X$ is hemicompact, then let it be witnessed by $K_n$. We claim $K_n$ also witnesses $k_\omega$. Note that the forward implication of $k_\omega$ always holds for $T_1$ spaces as $C\cap K_n$ is closed in $X$, and thus in every $K_n$. So assume $C\cap K_n$ is closed in $K_n$ for all $n$. Let $H$ be any compact set. As $X$ is hemicompact, $H\subseteq K_n$ for some $n$. Note $C\cap H = (C\cap K_n)\cap H$. As both $C \cap K_n$ and $H$ are closed in $K_n$, $C\cap H$ is closed in $K_n$, and thus $C\cap H$ is closed in $H$. As $Y$ is $k$ and $C\cap H$ is closed in $H$ for all compact $H$, $C$ is closed, showing the backwards implication.

Now if $Y$ is $k_\omega$, let it be witnessed by $K_n$. Give $K$ the predeterined strategy $\sigma(n)=K_n$ for the game $G_{K,P}(X)$, and let $p_n$ be the result of a legal counter by $P$. Suppose by way of contradiction that $p$ is a cluster point of the $p_n$. Note $p\in \sigma(N)$ for some $N$. $p$ is a cluster point of $\{p_n : n\geq N\}$ but $p\not\in \{p_n : n \geq N\}$. Also, $\{p_n : n \geq N\} \cap \sigma(m)$ is finite for all $m$, and thus closed, so as $\sigma(n)$ witnesses $k_\omega$, $\{p_n : n\geq N\}$ is closed and must contain its cluster point $p$, which is a contradiction. Thus $\sigma$ is a winning predetermined strategy for $K$ in $G_{K,P}(Y)$.

Finally, if $K \prewin G_{K,P}(X)$, $X$ is hemicompact by the previous lemma.
\end{proof}

For $k$-spaces, it turns out that finding winning predetermined strategies for $G_{K,P}(X)$ and $G_{K,L}(X)$ are also equivalent problems.

\begin{theorem}
For any hemicompact Hausdorff $k$-space $X$, $K \prewin G_{K,L}(X)$.
\end{theorem}

\begin{proof}
Let $X$'s hemicompactness be witnessed by $K_n=\sigma(n)$. Note that this also witnesses $k_\omega$ by the proof of the previous theorem. Let $H_0,H_1,\dots$ be a counter by $H$ for the game $G_{K,L}(X)$ in response to $\sigma$. Suppose by way of contradiction the counter was legal and defeats $\sigma$. Then there is a point $x$ such that every neighborhood of $x$ hits infinitely many of the $H_n$.

Now, $x\in\sigma(N)$ for some $N$, and since the play $H_0,H_1,\dots$ is legal, $x\not\in H_n$ for all $n\geq N$. Consider the set $H_\omega=\bigcup_{n\geq N} H_n$. Note that as the $K_n$ witness $k_\omega$, $H_\omega$ is closed if and only if $H_\omega \cap \sigma(m)$ is closed in $\sigma(m)$ for all $m$. In fact, since every $H_n$ is a subset of some $\sigma(m)$ (by hemicompactness), $H_\omega \cap \sigma(m)$ is a finite union of some $H_n$, and is thus closed in $Y$.

We thus have that $H_\omega$ is a closed set not containing $x$. But since every neighborhood of $x$ intersects $H_\omega$, $x$ is a limit point of the closed set $H_\omega$ and should be included, demonstrating our contradiction. Thus $\sigma$ is a winning predetermined strategy for $K$ in the game $G_{K,L}(X)$.
\end{proof}

\begin{corollary}
The following are equivalent for any Hausdorff $k$-space $X$:
  \begin{itemize}
  \item $X$ is hemicompact.
  \item $X$ is $k_{\omega}$.
  \item $K$ has a winning predetermined strategy in $G_{K,L}(X)$.
  \item $K$ has a winning predetermined strategy in $G_{K,P}(X)$.
  \end{itemize}
\end{corollary}

It's natural to question whethere there is ever any difference between finding winning predetermined strategies for $G_{K,P}(X)$ and $G_{K,L}(X)$. We now look to a (non-locally compact, non-$k$) Hausdorff space where the distinction arises:

\begin{definition}
Given a set $X$, an ultrafilter on $X$ is a collection $\mathcal{F}\subseteq\mathcal{P}(X)$ such that
    \begin{enumerate}
    \item $\emptyset\not\in \mathcal{F}$
    \item $A,B\in\mathcal{F} \Rightarrow A\cap B \in \mathcal{F}$
    \item $A\in\mathcal{F}$ and $A \subseteq B$ $\Rightarrow$ $B\in\mathcal{F}$
    \item $\forall A \subseteq X(A\in\mathcal{F}$ or $X\setminus A \in \mathcal{F})$
    \end{enumerate}
As a result, ultrafilters which contain a finite set contain only one singleton (and are called \textbf{principal}). Otherwise, ultrafilters which contain no finite sets are called \textbf{free}.
\end{definition}

\begin{definition}
The \textbf{Stone-Cech compactification} $\beta\omega$ of $\omega$ is the collection of ultrafilters on $\omega$. The principal ultrafilters containing a singleton $\{n\}$ are each identified with $n$ itself and are isolated. Free ultrafilters $\mathcal{F}$ are given neighborhoods of the form \[\{\mathcal{G} : \mathcal{G} \text{ is an ultrafilter on } \omega \text{ and } A \in \mathcal{G}\} = A \cup \{\mathcal{G}: \mathcal{G} \text{ is a free ultrafilter on } \omega \text{ and } A \in \mathcal{G}\}\] for each $A\in\mathcal{F}$.

Alternately $\beta\omega=\omega\cup\{\mathcal{F} : \mathcal{F}$ is a free ultrafilter on $\omega\}$ where $\omega$ is discrete and the free ultrafilters have the local base described above.
\end{definition}

\begin{definition}
A \textbf{single-ultrafilter space} is a subset of $\beta\omega$ containing all elements of $\omega$ and a single ultrafilter $\mathcal{F}$.
\end{definition}

\begin{proposition}
The compact sets of a single-ultrafilter space are exactly the finite subsets of the space. Thus a single-ultrafilter space is neither locally compact nor $k$.
\end{proposition}

Regardless of the ultrafilter chosen, we can see that $K$ has no hope of having a winning predetermined strategy for $G_{K,L}$ played on a single-ultrafilter space.

\begin{proposition}
If $X$ is any single-ultrafilter space with the ultrafilter $\mathcal{F}$, then $K\not\prewin G_{K,L}(X)$.
\end{proposition}

\begin{proof}
Compact sets are exactly finite sets in this space. Therefore, the difference of any two compact sets is compact.

Give $K$ the predetermined strategy $\sigma(n)$. $H$ counters with \[H_n=(n\cup\sigma(n+1))\setminus\sigma(n)\] on turn $n$. Since any free ultrafilter contains only unbounded sets, every neighborhood $A\cup\{\mathcal{F}\}$ of $\mathcal{F}$ must intersect infinitely many $H_n$, defeating $\sigma$.
\end{proof}

However, while it is consistant that there is an ultrafilter which defies the existance of a predetermined winning strategy for $K$ in $G_{K,P}$...

\begin{proposition} 
If a selective ultrafilter $\mathcal{F}$ exists (this is independent of ZFC), then $K$ has no winning predetermined strategy in the compact-point game $G_{K,P}(Y)$ for the single selective ultrafilter space $Y=\omega \cup \{\mathcal{F}\}$.
\end{proposition}

\begin{proof}
Let $\sigma$ be a predetermined strategy for $K$. By the definition of a selective ultrafilter, for every partition $\{B_n : n < \omega\}$ of subsets of $\omega$ such that $B_n \not\in \mathcal{F}$ for all $n$, there exists $A \in \mathcal{F}$ such that $|A \cap B_n|=1$ for all $n$. So then let \[B_n = \omega \cap \sigma(n) \setminus \sigma(n-1)\]

Note that $B_n$ is finite and thus $B_n \not\in \mathcal{F}$, so there exists $A\in \mathcal{F}$ such that $|A \cap B_n|=1$. Let $p_n$ be the singleton in $A \cap B_{n+1}$, so $\{p_n : n < \omega\}$ is cofinite in $A$, and thus is also a member of $\mathcal{F}$. Thus $p_n$ converges to $\mathcal{F}$, and counters the strategy $\sigma$.
\end{proof}

... in general we can find many ultrafilters for which $K\prewin G_{K,P}$.

\begin{theorem}
Let $a_n$ be a sequence such that the sequence $\frac{a_n}{n}$ is unbounded above. Then there is an ultrafilter $\mathcal{F}$ such that $\sigma(n)=(\sum_{m\leq n} a_m )\cup \{\mathcal{F}\}$ is a winning predetermined strategy for $K$ in $G_{K,P}(\omega\cup\{\mathcal{F}\})$.
\end{theorem}

\begin{proof}
Let $\mathcal{P}$ be the collection of all legal plays by $P$ against the strategy $\sigma$. Consider a finite collection of plays $P_0,\dots,P_{n-1}\in \mathcal{P}$. As $\frac{a_m}{m}$ is unbounded above, we may find infinitely many $m$ such that $\frac{a_m}{m}>n \Rightarrow mn<a_m$. As the $a_m$ partition $\omega$ such that $P$ may only play at most $m$ points in each part, there are infinitely many parts which are not filled, and thus $\bigcup_{m<n} P_m$ is not cofinite.

It then follows that the closure of $\mathcal{P}$ under finite unions and subsets, along with all finite sets, is an ideal. Its dual filter may then be extended to an ultrafilter $\mathcal{F}$ such that every possible play by $P$ is the complement of some member of $\mathcal{F}$.
\end{proof}

So we can see that there are non-$k$ spaces $X$ for which $K\prewin G_{K,P}(X)$. However, we have found no such spaces for the game $G_{K,L}(X)$. So we conclude with this open question:

\begin{question}
$K \prewin G_{K,L}(X) \Rightarrow X$ is a $k$-space?
\end{question}

\centerline{\bf Another game: $Con_{O,P}(X,x)$}

\begin{definition} 
Gruenhage's open-point convergence game $Con_{O,P}(X,x)$ has $O$ choosing nested open sets and $P$ choosing a point within the last chosen open set by $O$. $O$ wins if the points chosen by $P$ converge to $x$.
\end{definition}

\begin{definition}
The one-point compactification of a space $X$ is $X\cup\{\infty\}$, where neighborhoods of points in $X$ are the same as they were originally, and neighborhoods of $\infty$ are sets $X\cup\{\infty\}\setminus K$ for compact $K$. If $X$ is discrete then neighborhoods of $\infty$ are cofinite sets containing $\infty$. 
\end{definition}

\begin{proposition}
$O\not\prewin Con_{O,P}(\kappa\cup\{\infty\},\infty)$, where $\kappa\cup\{\infty\}$ is the one-point compactification of discrete $\kappa\geq\omega_1$.
\end{proposition}

\begin{proof}
Given a predetermined strategy $\sigma(n)$ for $O$, $P$ simply chooses any ordinal in $\bigcap_{n<\omega} \sigma(n)$ to play on every turn.
\end{proof}

\begin{definition}
A \textbf{coding strategy} considers only the most recent move by each player. If Player $Z$ has a winning coding strategy for a game $G$, this may be denoted $Z \codewin G$.
\end{definition}

\begin{proposition}
$O\codewin Con_{O,P}(\kappa\cup\{\infty\},\infty)$ for any cardinal $\kappa$. 
\end{proposition}

\begin{proof}
Define $\sigma(U,p)=U\setminus\{p\}$. A legal play by $P$ must never repeat the same point, so legal plays by $P$ converge to $\infty$.
\end{proof}

\begin{proposition}
$O\not\tactwin Con_{O,P}(\kappa\cup\{\infty\},\infty)$ for $\kappa\geq\omega_1$.
\end{proposition}

\begin{proof}
Let $F(\alpha)$ be the complement of a tactical strategy for $O$. There exists some $n<\omega$ such that we may find an infinite $B\subseteq \omega_1$ with $n\not\in F(\beta)$ for $\beta\in B$ - if not, we may find uncountable ordinals $\alpha$ such that $\omega \subseteq F(\alpha)$, a contradiction. Choose $\beta\in B\setminus F(n)$, and note that repeating $n,\beta$ is a successful counter to $O$'s strategy.
\end{proof}

\begin{definition}
A \textbf{$k$-tactical strategy} considers only the last $k$ moves by the opposing player. If Player $Z$ has a winning $k$-tactical strategy for a game $G$, this may be denoted $Z \ktactwin{k} G$.
\end{definition}

\begin{theorem}
$O\not\ktactwin{k}Con_{O,P}(\kappa\cup\{\infty\},\infty)$ for $\kappa\geq\omega_1$.
\end{theorem}

\begin{proof}
Let $\sigma:[\omega_1]^{\leq k}\to[\omega_1]^{<\omega}$ be a $k$-tactical strategy for $O$ restricted to $\omega_1$ and $F(S)=\omega_1\setminus\sigma(S)$.

Let $W_0=\omega_1$. We define $W_\alpha$ recursively as follows:
    \begin{itemize}
    \item For successor ordinals $\alpha+1$, let $\beta$ be the least element of $W_\alpha$ such that $[\beta+1,\omega_1) \cap \bigcup_{S\leq \beta} F(S)$ is nonempty, where $S \leq \beta$ is shorthand for $\{S \in [\omega_1]^{\leq k} : \forall \gamma \in S(\gamma < \beta)\}$. If no such $\beta$ exists, let $W_{\alpha+1}=W_\alpha$ and otherwise let $W_{\alpha+1}=W_\alpha \setminus \left([\beta+1,\omega_1) \cap \bigcup_{S\leq \beta} F(S)\right)$.
    \item For limit ordinals $\alpha$, let $W_\alpha = \bigcap_{\beta<\alpha} W_\beta$.
    \end{itemize}

Finally let $W=\bigcap_{\alpha<\omega_1}W_\alpha$ and observe that it is unbounded. Let $R$ collect all ordinals $\alpha\in W$ such that there is an ordinal $\beta$ where for all $S\in[W\cap(\beta,\omega_1)]^{\leq k}$, $\alpha \in F(S)$. It is easily seen that $R$ is finite. Let $0^*$ be the least element of $W\setminus R$.

Now, define a strictly increasing sequence of ordinals $\left<\alpha_1,\alpha_2,\alpha_3,\alpha_4,\dots\right>$ such that $\alpha_i \in W$ and $0^* \not\in F(\{\alpha_{2i+1},\dots,\alpha_{2i+k}\})$ for all $i$. The play $\left<0^*,\alpha_1,\dots,\alpha_k,0^*,\alpha_{k+1},\dots,\alpha_{2k},0^*,\dots\right>$ then defeats the strategy $\sigma$.
\end{proof}

Peter J. Nyikos has shown the following:

\begin{theorem}
$O\not\markwin Con_{O,P}(\omega_1\cup\{\infty\},\infty)$.
\end{theorem}

This can be improved:

\begin{theorem}
$O\not\kmarkwin{k} Con_{O,P}(\kappa\cup\{\infty\},\infty)$ for $\kappa\geq\omega_1$.
\end{theorem}

\begin{proof}
Let $F:[\omega_1]^{\leq k}\times\omega\to[\omega_1]^{<\omega}$ be the complement of a $k$-Markov strategy for $O$ restricted to $\omega_1$.

Let $W_0=\omega_1$. We define $W_\alpha$ recursively as follows:
    \begin{itemize}
    \item For successor ordinals $\alpha+1$, let $\beta$ be the least element of $W_\alpha$ such that \[(\beta,\omega_1) \cap \bigcup_{S\in [\beta]^{\leq k}, n<\omega} F(S,n)\] is nonempty. If no such $\beta$ exists, let $W_{\alpha+1}=W_\alpha$ and otherwise let \[W_{\alpha+1}=W_\alpha \setminus \left((\beta,\omega_1) \cap \bigcup_{S\in[\beta]^{\leq k}, n<\omega} F(S,n)\right)\]
    \item For limit ordinals $\alpha$, let $W_\alpha = \bigcap_{\beta<\alpha} W_\beta$.
    \end{itemize}

Finally let $W=\bigcap_{\alpha<\omega_1}W_\alpha$ and observe that it is unbounded. Let $R$ collect all ordinals $\alpha\in W$ such that there is an ordinal $\beta_\alpha$ and number $n_\alpha<\omega$ where for all $S\in[W\cap(\beta_\alpha,\omega_1)]^{\leq k}$, $\alpha \in F(S,n_\alpha)$.

If $R$ was infinite, then there is $\alpha_i\in R$ for each $i<\omega$ and some $N<\omega$ where for all $S\in[W\cap(\beta_{\alpha_i},\omega_1)]^{\leq k}$, $\alpha_i \in F(S,N)$, and thus for all $S\in[W\cap(\sup \beta_{\alpha_i},\omega_1)]^{\leq k}$,  $\{\alpha_i : i<\omega\} \subset F(S,N)$, a contradiction. So let $0^*$ be the least element of $W\setminus R$.

Now, define a strictly increasing sequence of ordinals $\left<\alpha_1,\alpha_2,\alpha_3,\alpha_4,\dots\right>$ such that $\alpha_i \in W$ and $0^* \not\in F(\{\alpha_{2i+1},\dots,\alpha_{2i+k}\})$ for all $i$. The play $\left<0^*,\alpha_1,\dots,\alpha_k,0^*,\alpha_{k+1},\dots,\alpha_{2k},0^*,\dots\right>$ then defeats the Markov strategy.
\end{proof}

While these counters prevent convergence to $\infty$, they do not prohibit clustering, as any sequence of points with infinite range clusters at $\infty$ in this space.

\begin{definition} 
The open-point clustering game $Clus_{O,P}(X,x)$ has $O$ choosing nested open sets and $P$ choosing a point within the last chosen open set by $O$. $O$ wins if the points chosen by $P$ cluster to $x$.
\end{definition}

Any strategy which forces convergence also forces clustering, so a coding strategy exists for player $O$. And since the counter used above to foil any tactical strategy had only finite range...

\begin{proposition}
$O\not\tactwin Clus_{O,P}(X,\infty)$.
\end{proposition}

The other counters only attempt to repeat a point infinitely often, and may have infinite range.

\begin{example}
For $\omega\leq\alpha<\omega_1$ let $\leq_{\alpha}$ be a well-ordering of $\omega_1$ such that its restriction to $\alpha$ is isomorphic to $\omega$ with isomorphism $f(n):\omega\to\alpha$. For $n<\omega$ let $\leq_n$ simply be $\leq$ and $f$ be the identity.

The 2-tactical strategy for $O$ in $Clus_{O,P}(\omega_1\cup\{\infty\}),\infty)$ whose complement is, for $\alpha<\beta$, $F(\alpha,\beta)=\{\gamma : \gamma \leq_\beta \alpha \} \cup \{\beta\}$, forces the point-picker to chose more than three distinct points.
\end{example}

\begin{proof}
Suppose Player $P$ started with $\alpha_0<\alpha_1$. Player $O$ forbids \[F(\alpha_0,\alpha_1) = \{\gamma : \gamma \leq_{\alpha_1}\alpha_0\} \cup \{\alpha_1\}\] so Player $P$ must respond with $\alpha_2$ such that either $\alpha_0<\alpha_1<\alpha_2$ or $\alpha_0<_{\alpha_1}\alpha_2<\alpha_1$.

In the first case that $\alpha_0<\alpha_1<\alpha_2$, Player $O$ now forbids \[F(\alpha_1,\alpha_2) = \{\gamma : \gamma \leq_{\alpha_2}\alpha_1\} \cup \{\alpha_2\}\] If $\alpha_0<_{\alpha_2}\alpha_1$ we're done. Otherwise, Player $P$ chooses $\alpha_0>_{\alpha_2}\alpha_1$ again, and Player $O$ responds with \[F(\alpha_0,\alpha_2)=\{\gamma : \gamma \leq_{\alpha_2} \alpha_0 \} \cup \{\alpha_2\}\] which successfully forbids $\alpha_1$.

In the second case that $\alpha_0<_{\alpha_1}\alpha_2<\alpha_1$, Player $O$ forbids \[F(\alpha_1,\alpha_2) = \{\gamma : \gamma \leq_{\alpha_1}\alpha_2\} \cup \{\alpha_1\}\] which successfully forbids $\alpha_0$.

Thus, a fourth ordinal must be selected.
\end{proof}

But the fourth ordinal is all that is needed.

\begin{theorem}
$O\not\ktactwin{2}Clus_{O,P}(\omega_1\cup\{\infty\},\infty)$.
\end{theorem}

\begin{proof}
Let $F(\alpha,\beta)$ be the complement of a k-tactical strategy for O, and assume without loss of generality that it does not forbid any ordinals larger than its inputs.

Let $n_0=\min(\omega\setminus F(\emptyset)\setminus F(\omega,\omega+1))$ and $n_1 = \min(\omega\setminus F(n_0)\setminus F(n_0,\omega+1))$.

It follows that $\left<n_0,n_1,\omega,\omega+1,n_0,n_1,\omega,\omega+1,\dots\right>$ is a legal counter.
\end{proof}

But, in fact, a similar counter can be used for any $k$-tactical strategy.

\begin{theorem}
$O\not\ktactwin{k}Clus_{O,P}(\omega_1\cup\{\infty\},\infty)$.
\end{theorem}

\begin{proof}
Let $F(\alpha_0,\dots,\alpha_{k-1})$ be the complement of a k-tactical strategy for O, and assume without loss of generality that it does not forbid any ordinals larger than its inputs.

For $0\leq i < k$, we define \[n_i = \min(\omega\setminus F(n_0,\dots,n_{i-1},\omega+i,\dots,\omega+k-1)\setminus F(n_0,\dots,n_{i-1}))\]

It follows that $\left<n_0,\dots,n_{k-1},\omega,\dots,\omega+k-1,n_0,\dots,n_{k-1},\omega,\dots,\omega+k-1,\dots\right>$ is a legal counter.
\end{proof}

However, a Markov strategy is sufficient to defeat $P$ in the clustering game for $\omega_1$.

\begin{theorem}
$O\markwin Clus_{O,P}(\omega_1\cup\{\infty\},\infty)$.
\end{theorem}

\begin{proof}
For $\omega\leq\alpha<\omega_1$ let $\leq_{\alpha}$ be a well-ordering of $\omega_1$ such that its restriction to $\alpha$ is isomorphic to $\omega$ with isomorphism $f(n):\omega\to\alpha$. For $n<\omega$ let $\leq_n$ simply be $\leq$ and $f$ be the identity.

Let $F(\alpha,n)=\{\gamma : \gamma \leq_\alpha f(n)\}$ be the complement of $O$'s Markov strategy in response to move $\alpha$ in round $n$.

If a legal counter by $P$ does not repeat some largest ordinal infinitely often, it does not result in a win for $P$. Otherwise let $\beta$ be largest ordinal repeated infinitely often in some legal counter by $P$. We note that the forbidden sets responded by $O$ are of the form $F(\beta,n)$ where $n$ increases as the game progresses. It is impossible to repeat any ordinal less than $\beta$ infinitely often due to the increasing round number, so the range of the counter is infinite, and does not result in a win for $P$.
\end{proof}

...while it similarly fails for $\kappa>\omega_1$.

\begin{theorem}
$O\not\kmarkwin{k}Clus_{O,P}(\kappa\cup\{\infty\},\infty)$ for $\kappa>\omega_1$.
\end{theorem}

\begin{proof}
Let $F:\omega\times[\kappa]^{\leq k} \to [\kappa]^\omega$ be the complement of a k-Markov strategy for O, and assume without loss of generality that it does not forbid any ordinals larger than its inputs.

For $0\leq i < k$, we define \[\beta_i = \min(\omega\setminus \bigcup_{n<\omega} F(n,\{\beta_0,\dots,\beta_{i-1},\omega_1+i,\dots,\omega_1+k-1\})\setminus\bigcup_{n<\omega} F(n,\{\beta_0,\dots,\beta_{i-1}\}))\]

It follows that $\left<\beta_0,\dots,\beta_{k-1},\omega_1,\dots,\omega_1+k-1,\beta_0,\dots,\beta_{k-1},\omega_1,\dots,\omega_1+k-1,\dots\right>$ is a legal counter.
\end{proof}

\centerline{\bf $Con_{O,P}(X,x)$ for Sigma Product}

\begin{proposition}
The player $O$ has a winning strategy for $Con_{O,P}(X,x)$ where \[X=\Sigma\mathbb{R}^{\omega_1}=\{x\in \mathbb{R}^{\omega_1}: x_\alpha = 0 \text{ for all but countably many } \alpha<\omega_1\}\]
\end{proposition}

\begin{proof}
Without loss of generality we may assume that $x$ is the zero function. Let $y_n$ be the move by $P$ on turn $n$. For each $y_n$, let $l_n\in \omega_1^{\omega}$ enumerate the nonzero coordinates in $y_n$. Give $O$ the strategy $\sigma(y_0,\dots,y_{n-1}) = \prod_{\alpha<\omega_1} O_\alpha$ where if $\alpha$ is listed in the first $n$ coordinates of any term in $\left<l_k\right>_{k<n}$, then $O_\alpha=(-2^{-n},2^{-n})$, and $O_\alpha=\mathbb{R}$ otherwise.
\end{proof}

\begin{theorem}
For all cardinals $\kappa\leq 2^\omega$, the player $O$ has a winning coding strategy for $Con_{O,P}(X,x)$ where \[X=\Sigma\mathbb{R}^{\kappa}=\{x\in \mathbb{R}^{\kappa}: x_\alpha = 0 \text{ for all but countably many } \alpha<\kappa\}\]
\end{theorem}

\begin{proof}
Note that $|\Sigma\mathbb{R}^\kappa| \leq 2^\omega = |\mathbb{R}|$. Define the following:

    \begin{itemize}
    \item Encode every finite sequence $s$ of functions in $\Sigma\mathbb{R}^{\kappa}$ as a real number $0<r(s)<1$. 
    \item Let $\gamma(U)$ be the function which, for basic open sets $U=\prod_{\alpha<\kappa}U_\alpha$ where $U_0=(-\frac{1}{R},\frac{1}{R})$ for some positive noninteger real number $R$, returns the sequence $r^{-1}(R-\lfloor R\rfloor)$.
    \item Let $n(U)$ be the length of $\epsilon^{-1}(\gamma(U))$.
    \item Let $\psi(U,y)=\epsilon^{-1}(\gamma(U))^\frown\left<y\right>$.
    \item Define $\sigma_0(U,y)$ to be $\left(-\frac{1}{n(U)+r(\psi(U,y))},\frac{1}{n(U)+r(\psi(U,y))}\right)$.
    \item For each $0<\alpha<\kappa$, define the interval $\sigma_\alpha(U,y)$ about $0$ as follows:
        \begin{itemize}
        \item If $\alpha$ is listed in the first $n(U)$ coordinates of any term in the finite sequence $\psi(U,y)$, then $\sigma_\alpha(U,y)=(-\frac{1}{n(U)+1},\frac{1}{n(U)+1})$.
        \item Otherwise, then $\sigma_\alpha(U,y)=\mathbb{R}$.
        \end{itemize}
    \end{itemize}

It follows that $\sigma(U,y)=\prod_{\alpha<\kappa} \sigma_\alpha(U,y)$ is a winning coding strategy.
\end{proof}

\begin{theorem}
For all cardinals $\kappa>2^\omega$ such that $\kappa^\omega = \kappa$, the player $O$ has a winning coding strategy for $Con_{O,P}(X,x)$ where \[X=\Sigma\mathbb{R}^{\kappa}=\{x\in \mathbb{R}^{\kappa}: x_\alpha = 0 \text{ for all but countably many } \alpha<\omega_1\}\]
\end{theorem}

\begin{proof}
Note that $|\Sigma\mathbb{R}^\kappa| = \kappa^\omega = \kappa$. Define the following:

    \begin{itemize}
    \item Encode every finite sequence $s$ of functions in $\Sigma\mathbb{R}^{\kappa}$ as an ordinal $\epsilon(s)<\kappa$. 
    \item Let $\gamma(U)$ be the function which, for basic open sets $U=\prod_{\alpha<\kappa}U_\alpha$ with a unique factor $U_{\alpha^*}$, returns $\alpha^*$.
    \item Let $n(U)$ be the length of $\epsilon^{-1}(\gamma(U))$.
    \item Let $\psi(U,y)=\epsilon^{-1}(\gamma(U))^\frown\left<y\right>$.
    \item For each $\alpha<\kappa$, define the interval $\sigma_\alpha(U,y)$ about $0$ as follows:
        \begin{itemize}
        \item If $\alpha$ is listed in the first $n(U)$ coordinates of any term in the finite sequence $\psi(U,y)$ and is not equal to $\epsilon(\psi(U,y))$, then $\sigma_\alpha(U,y)=(-\frac{1}{n(U)+1},\frac{1}{n(U)+1})$.
        \item If $\alpha=\epsilon(\psi(U,y))$, then $\sigma_\alpha(U,y)=(-\frac{1}{n(U)+2},\frac{1}{n(U)+2})$.
        \item Otherwise, then $\sigma_\alpha(U,y)=\mathbb{R}$.
        \end{itemize}
    \end{itemize}

It follows that $\sigma(U,y)=\prod_{\alpha<\kappa} \sigma_\alpha(U,y)$ is a winning coding strategy.
\end{proof}

% NOPE
%\begin{theorem}
%For all cardinals $\kappa$ such that $2^\omega< \kappa < \kappa^\omega$, the player $O\not\codewin Cl_{O,P}(X,x)$ where \[X=\Sigma\mathbb{R}^{\kappa}=\{x\in% \mathbb{R}^{\kappa}: x_\alpha = 0 \text{ for all but countably many } \alpha<\omega_1\}\]
%\end{theorem}
%
%\begin{proof}We begin by noting that $|\tau|=\kappa<\kappa^\omega$, where $\tau$ is the topology of $\Sigma \mathbb{R}^\kappa$.
%
%Suppose that for all $S\subseteq \Sigma\mathbb{R}^\kappa$ such that $\sigma(U,x)=\sigma(V,y)$ for all $x,y\in\Sigma \mathbb{R}^\kappa$ and $U,V\in\tau$, it follows that $|S|<\kappa^\omega$. Then \[\left|\bigcup_{V\in\tau}\sigma^{-1}(V)\right|=\max(\{\lambda : \lambda=|\tau| \,\vee\, \exists V\in\tau(\lambda=|\sigma^{-1}(V)|)\}) < \kappa^\omega \] while $\bigcup_{V\in\tau}\sigma^{-1}(V)=\tau\times \Sigma\mathbb{R}^\kappa$, a contradiction.
%
%It follows that we may find $S\subseteq \Sigma\mathbb{R}^\kappa$ with $|S|=\kappa^\omega$ such that $\sigma(U,x)=\sigma(V,y)$ for all $x,y\in\Sigma \mathbb{R}^\kappa$ and $U,V\in\tau$.
%
%If $P$ only plays sequences in $S$, then $O$ plays the same set in every round following the initial round. As such, $O$ only places restrictions on $\omega$-many coordinates of the sequences chosen by $P$ throughout the game. Call these restricted coordinates $R\subseteq \kappa$. If $x(\alpha)=0$ for all $x\in S$ and $\alpha\not\in R$, then it would follow that $|S|=|\mathbb{R}|^{|R|}=2^\omega<\kappa^\omega$, a contradiction.
%
%So, choose $x\in S$ such that $x(\alpha)\not=0$ for some $\alpha\not\in R$. The play \[\left<U_0,x,U_1=\sigma(U_0,x),x,U_2=\sigma(U_1,x)=U_1,x,U_1,x,\dots\right>\] is a counter to $\sigma$.
%\end{proof}

\centerline{\bf Finite Countable Game}

\begin{theorem}
Let $\kappa$ be a cardinal such that there exists a function $f:\kappa\to[\kappa]^{\leq \omega}$ where for every $W\in[\kappa]^{\leq\omega}$ there exists $\alpha_W<\kappa$ with $W\subseteq f(\alpha_W)$. Then $F \codewin PF_{F,C}(\kappa)$ and $O \codewin Con_{O,P}(\Sigma\mathbb{R}^\kappa)$.
\end{theorem}

\begin{proof}
Long version.

We begin by defining a few helpful tools. Assume $N\in[\kappa]^{<\omega}$ and $W \in [\kappa]^{\leq\omega}$.
    \begin{itemize}
    \item Let $N^* = N \setminus \{\max(N)\}$.
    \item Noting that $\kappa\setminus \alpha$ is order-isomorphic to $\kappa$ for all $\alpha<\kappa$, let $\gamma_N<\kappa$ be the ordinal mapping to $\max(N)$ in $\kappa\setminus(\max(N^*)+1)$ by the appropriate order isomorphism.
    \item Let $s: [\kappa]^{<\omega} \to \kappa$ be a bijection.
    \item Define $W\restriction n \in [\kappa]^{<\omega}$ so that $W\restriction n \subseteq W\restriction (n+1)$ and $\bigcup_{n<\omega}W\restriction n = W$.
    \item Let $t_N=\max(N\cap\omega)+2$.
    \end{itemize}

Let the (non-winning) coding strategy $\sigma'$ be defined as follows: \[\sigma'(N,W)=\bigcup_{\alpha \in s^{-1}(\gamma_N)} f(\alpha) \restriction t_N\]

Let $\left<N_0,N_1,\dots\right>$ be a play by $F$ following the considered strategy in response to the play $\left<W_0,W_1,\dots\right>$ by $C$ in the game $PF_{F,C}(\kappa)$. (For technical reasons, assume $N_0$ contains at least two ordinals.) This coding strategy could have been a winning strategy for $F$ if it had only satisfied two requirements:

    \begin{enumerate}
    \item First, $s^{-1}(\gamma_{N_k})$ provided ordinals $\{\alpha_{W_0},\dots,\alpha_{W_{k-1}}\}$. (Thus $N_{k+1}=\bigcup_{\alpha \in s^{-1}(\gamma_{N_k})} f(\alpha) \restriction t_{N_k} = \bigcup_{0\leq m < k} f(\alpha_{W_m}) \restriction t_{N_k}$.)
    \item In addition, $t_{N_k} \to \infty$. (Thus $\bigcup_{k<\omega} N_{k+1} = \bigcup_{k<\omega}\bigcup_{0\leq m < k-1} f(\alpha_{W_m}) \restriction t_{N_k} = \bigcup_{m<\omega} f(\alpha_{W_m}) \supseteq \bigcup_{m<\omega} W_m$.)
    \end{enumerate}

We shall improve $\sigma'$ so that it does satsify those requirements, beginning with the second.  Define $\sigma^*$: \[\sigma^*(N,W)=t_N \cup \sigma'(N,W)\] Note then that $t_{N_{k+1}}\geq t_{t_{N_k}} = \max(t_{N_k})+2 = t_{N_k}-1+2=t_{N_k}+1$.

Lastly, to cover the first requirement, we define $\sigma$: \[\sigma(N,W) = \sigma^*(N,W) \cup \{ \max(\sigma^*(N,W))+1+s(s^{-1}(\gamma_N)\cup\{\alpha_W\}) \}\] By induction \[s^{-1}(\gamma_{N_{k+1}}) = s^{-1}(s(s^{-1}(\gamma_{N_k})\cup\{\alpha_{W_k}\})) = s^{-1}(\gamma_{N_k})\cup\{\alpha_{W_k}\} = \{\alpha_{W_0},\dots,\alpha_{W_{k-1}}\}\cup\{\alpha_{W_k}\}\] we see the first requirement is satisfied.

Finally, we turn our attention to $Con_{O,P}(\Sigma\mathbb{R}^\kappa)$. We define the winning strategy $\tau(U,p)$ for $O$ as follows: let $N(U)$ be the non-$\mathbb{R}$ coordinates in the basic open set $U$ and $W(p)$ be the non-$0$ coordinates in $p$. Then $\tau(U,p) = \left(\prod_{\alpha<\kappa} U_\alpha\right) \cap \Sigma\mathbb{R}^\kappa$ where if $\alpha \in \sigma(N(U),W(p))$ then $U_\alpha = (-1/t_{N(U)},1/t_{N(U)})$ and $U_\alpha=\mathbb{R}$ otherwise.
\end{proof}

\begin{proof}
Short version, per GG's suggestion.

Let $W\restriction n \in [\kappa]^n$ be a subset of $W\in[\kappa]^\omega$ such that $W\restriction n \subset W \restriction (n+1)$ and $\bigcup_{n<\omega} W\restriction n = W$.

Define \[\sigma(N,W) = N \cup (|N|+1) \cup \{\alpha_W\} \cup \bigcup_{\alpha \in N} f(\alpha) \restriction |N|\]

Consider the play $\left<\emptyset,W_0,N_1,W_1,N_2,W_2,\dots\right>$ with $F$ following the strategy $\sigma$. Let $\gamma \in W_i$, and note $\gamma \in f(\alpha_{W_i})$ (and $\gamma \in f(\alpha_{W_i})\restriction |N_n|$ for sufficiently large $n$). \[N_{i+1} = \sigma(N_i,W_i) \supseteq \{\alpha_{W_i}\}\] and thus \[N_{n+1} = \sigma(N_n,W_n) \supseteq \bigcup_{\alpha \in N_n} f(\alpha) \restriction |N_n| \supseteq \bigcup_{\alpha \in N_{i+1}} f(\alpha) \restriction |N_n| \supseteq f(\alpha_{W_i}) \restriction |N_n|\] showing $\gamma \in N_{n+1}$. Since $\gamma$ is forbidden in round $n+1$, $\gamma$ appears in finitely many sets chosen by $C$.

We turn our attention to $Con_{O,P}(\Sigma\mathbb{R}^\kappa)$. We define the winning strategy $\tau(U,p)$ for $O$ as follows: let $N(U)$ be the non-$\mathbb{R}$ coordinates in the basic open set $U$ and $W(p)$ be the non-$0$ coordinates in $p$. Then $\tau(U,p) = \left(\prod_{\alpha<\kappa} U_\alpha\right) \cap \Sigma\mathbb{R}^\kappa$ where if $\alpha \in \sigma(N(U),W(p))$ then $U_\alpha = (-\frac{1}{|N(U)|},\frac{1}{|N(U)|})$ and $U_\alpha=\mathbb{R}$ otherwise.

Consider the play $\left<\emptyset,p_0,U_1,p_1,U_2,p_2,\dots\right>$ with $O$ following the strategy $\tau$. Observe that $N(\tau(U,p))=\sigma(N(U),W(p))$. Thus $p_i(\gamma)\not=0$ is equivalent to $\gamma \in W(p_i)$, and by the above argument, for sufficiently large $n$, $\gamma \in \sigma(N(U_n),W(p_n))$. Therefore from round $n$ onward the $\gamma$-coordinates of points chosen by $P$ must lay in $(-\frac{1}{|N(U)|},\frac{1}{|N(U)|})$ and converge to $0$.
\end{proof}

%
%\begin{theorem}
%For all cardinals $\kappa \geq \omega$, the player $F \not\tactwin Cov_{F,C}(\kappa)$.
%\end{theorem}
%
%\begin{proof}
%(Based on Scheeper's Meager Nowhere Dense Games I)
%
%Suppose $\sigma$ is a tactical strategy for $F$ such that (without loss of generality) the first move is $\emptyset$. Let $A=\{2n: n<\omega\}$ and $B=\{2n+1:n<\omega\}$.
%
%By Todorcevic's Partition Relations for Partially Ordered Sets, $\mathcal{P}(A)\rightarrow(\omega)^1_B$. That is, for any function $\Phi$ from $\mathcal{P}(A)$ to $B$, there is some $b_\Phi\in B$ and $X_0\subseteq X_1\subseteq \dots \in \mathcal{P}(A)$ such that $\Phi(X_i)=b_\Phi$ for all $i$. Define $\Phi:\mathcal{P}(A)\rightarrow B$ such that $\Phi(X)\in B\setminus(\sigma(B\cup X))$.
%
%Observe the play $\left<\emptyset, B\cup X_0, \sigma(B\cup X_0), B \cup X_1, \sigma(B \cup X_1), B \cup X_2, \dots \right>$. As $b_\Phi \in B \subseteq \bigcup_{i<\omega} B \cup X_i$ but $b_\Phi \not\in \bigcup_{i<\omega} \sigma(B\cup X_i)$, this is a successful counter to any tactic by $F$.
%\end{proof}
%
%\begin{proposition}
%For all cardinals $\kappa \geq \omega_1$, the player $F \not\markwin Cov_{F,C}(\kappa)$.
%\end{proposition}
%
%\begin{proof}
%Suppose $\sigma$ is a Markov strategy for $F$ such that (without loss of generality) the first move is $\emptyset$. Let $A,B\in\mathcal{P}(\kappa)$ be disjoint with $|A|=|B|\geq\omega_1$.
%
%By Todorcevic's Partition Relations for Partially Ordered Sets, $\mathcal{P}(A)\rightarrow(\omega)^1_B$. That is, for any function $\Phi$ from $\mathcal{P}(A)$ to $B$, there is some $b_\Phi\in B$ and $X_0\subseteq X_1\subseteq \dots \in \mathcal{P}(A)$ such that $\Phi(X_i)=b_\Phi$ for all $i$. Define $\Phi:\mathcal{P}(A)\rightarrow B$ such that $\Phi(X)\in B\setminus(\bigcup_{n<\omega}\sigma(B\cup X,n))$.
%
%Observe the play $\left<\emptyset, B\cup X_0, \sigma(B\cup X_0,1), B \cup X_1, \sigma(B \cup X_1,2), B \cup X_2, \dots \right>$. As $b_\Phi \in B \subseteq \bigcup_{i<\omega} B \cup X_i$ but $b_\Phi \in \bigcap_{m<\omega} B \setminus (\bigcup_{n<\omega}\sigma(B\cup X_m,n))$ implying $b_\Phi \not\in \bigcup_{m<\omega}\sigma(B\cup X_m,m+1)$, this is a successful counter to any Markov strategy by $F$.
%\end{proof}

%\begin{theorem}
%If $F\codewin Cov_{F,C}^{**}(\kappa)$ then $O\codewin C_{O,P}(\Sigma\mathbb{R}^\kappa,\vec{0})$.
%\end{theorem}
%
%\begin{proof}
%We begin by comparing
%    \begin{itemize}
%    \item $N\in[\kappa]^{<\omega}$ with the open set $\prod_{\alpha < \kappa} U_\alpha$ in $\Sigma2^\kappa$ where $U_\alpha=\{0\}$ for $\alpha\in N$ and $U_\alpha=\{0,1\}$ otherwise.
%    \item $W\in[\kappa]^{\leq\omega}$ with the point $p\in\Sigma2^\kappa$ defined by $p(\alpha)=1$ for all $\alpha \in W$ and $p(\alpha)=0$ otherwise.
%    \end{itemize}
%
%So if $\sigma$ is a winning coding strategy for $F$ in $Cov_{F,C}^{**}(\kappa)$, we may define $\tau$ to be a corresponding (perfect- or limited-information) winning strategy for $O$ in $C_{O,P}(\Sigma2^\kappa,\vec{0})$ by making the above conversions from finite sets played by $F$ to countable sets played by $C$ to the open sets which may be played by $O$ and points which may be played by $P$. As the legal moves for $C$ correspond to the legal moves for $P$, and as $\sigma$ covers any play by $C$, $\tau$ forces any nonzero coordinate found in a move by $P$ to eventually constrained to $0$.
%
%For the game $C_{O,P}(\Sigma\mathbb{R}^\kappa,\vec{0})$ we must instead use open sets of the form $\prod_{\alpha < \kappa} U_\alpha$ where $U_\alpha=(-1/i,1/i)$ for $\alpha\in N$ and $i$ being the turn number (with $U_\alpha=\mathbb{R}$ for $\alpha\not\in N$). (The turn number is easily encoded and decoded by $O$ by inspecting the non-$\mathbb{R}$ coordinates of her previous move) and associating points $p\in\Sigma\mathbb{R}^\kappa$ with $q\in\Sigma2^\kappa$ by $q(\alpha)=0$ when $|p(\alpha)|<1$ and $q(\alpha)=1$ otherwise.
%\end{proof}

\end{document}

### 2013-01-24 old_phd_research_results_november_2011.tex
Initial commit

\documentclass[11pt]{article}
% \usepackage{aums}       % For Master's papers
% \usepackage{ulem}       % underlining on style-page; see \normalem below

\pdfpagewidth 8.5in
\pdfpageheight 11in

\setlength\topmargin{0in}
\setlength\headheight{0in}
\setlength\headsep{0.2in}
\setlength\textheight{8in}
\setlength\textwidth{6in}
\setlength\oddsidemargin{0in}
\setlength\evensidemargin{0in}
\setlength\parindent{0.25in}
\setlength\parskip{0.1in}

\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{amsthm}

      \theoremstyle{plain}
      \newtheorem{theorem}{Theorem}
      \newtheorem{lemma}[theorem]{Lemma}
      \newtheorem{corollary}[theorem]{Corollary}
      \newtheorem{proposition}[theorem]{Proposition}
      \newtheorem{conjecture}[theorem]{Conjecture}

      \theoremstyle{definition}
      \newtheorem{definition}[theorem]{Definition}

      \theoremstyle{remark}
      \newtheorem{remark}[theorem]{Remark}

% Strategy uparrow shortcuts
\newcommand{\prewin}{\uparrow_{\text{pre}}}
\newcommand{\markwin}{\uparrow_{\text{mark}}}
\newcommand{\tactwin}{\uparrow_{\text{tact}}}
\newcommand{\ktactwin}[1]{\uparrow_{#1\text{-tact}}}
\newcommand{\kmarkwin}[1]{\uparrow_{#1\text{-mark}}}
\newcommand{\codewin}{\uparrow_{\text{code}}}

\begin{document}

%   \author{Steven Clontz}
%   \address{Auburn University}
%   \email{steven.clontz@auburn.edu}

\begin{proposition}
K has a winning strategy in $G_{KP}(Y)$ ($G_{KL}(Y)$) if and only if K has a strictly increasing winning strategy.  The same holds for winning predetermined strategies.
\end{proposition}

\begin{proposition}
For any space $Y$, TFAE
  \begin{itemize}
  \item $Y$ is compact.
  \item $K$ has a winning button-mashing strategy for $G_{KP}(Y)$.
  \end{itemize}
\end{proposition}

\begin{proposition}
If $K$ has a winning predetermined strategy in $G_{KP}(Y)$, then $Y$ is $\sigma$-compact.
\end{proposition}

\begin{theorem}
If $Y$ is a locally compact, $\sigma$-compact space, then $K$ has a winning predetermined strategy for $G_{KP}(Y)$.
\end{theorem}

\begin{proof}
Let $Y_n$ be a compact set for $n<\omega$ such that $Y=\bigcup_{n<\omega}Y_n$. As $Y$ is locally compact, there is a cover of $Y$ by open sets with compact closures. For each $Y_n$, let $\mathcal{U}_n$ be a finite cover of $Y_n$ by open sets with compact closures.

Define a predetermined strategy $\sigma$ for $K$ by \[\sigma(n)=\bigcup \{\overline{U}: U\in \bigcup_{m\leq n} \mathcal{U}_m\}\]

Let $y_n$ give a play by $P$. If $y$ is a cluster point of the $y_n$, then every open set about $y$ contains infinitely many $y_n$. Let $U$ be some open set in $\bigcup_{n<\omega} \mathcal{U}_n$ which covers $y$. Then $\overline{U}$ contains infinitely many $y_n$, which means $P$ played in a set already played by the strategy $\sigma$. Thus $\sigma$ is a winning strategy.
\end{proof}

\begin{corollary}
For any locally compact space $Y$, TFAE
  \begin{itemize}
  \item $Y$ is $\sigma$-compact.
  \item $K$ has a winning predetermined strategy for $G_{KP}(Y)$.
  \end{itemize}
\end{corollary}

\begin{lemma}
$K$ does not have a winning predetermined strategy for $G_{KP}(M)$ where $M$ is the metric fan space.
\end{lemma}

\begin{proof}
Let $\sigma(n)$ be a predetermined strategy for $K$. Note that any compact set cannot contain every point $(a,b)$ for fixed $a$ and every $b\in \omega$, as that would require it be a compact set containing a closed infinite discrete space.

So on turn $n$, let $P$ respond to $\sigma(n)$ with a point $y_n=(a_n,n)$ such that $(a_n,n)$ is not covered by $\bigcup_{m\leq n} \sigma(n)$ (a compact set). It is easy to see that $y_n\rightarrow \infty$, so $P$ beats $\sigma$.
\end{proof}

\begin{corollary}
$K$ does not have a winning predetermined strategy for $G_{KP}(Y)$ where $Y$ is a first-countable non-locally countably compact space.
\end{corollary}

\begin{proof}
By Lemma 8.3 of [E. van Douwen, The integers and Topology, in: K.Kunen, J.E.Vaughan (eds.), Handbook of Set-Theoretic Topology, North-Holland, Amsterdam, 1984, 111-167], the metric fan $M$ is a closed subspace of $Y$.
\end{proof}

\begin{theorem}
For any first-countable \textbf{regular} space $Y$, TFAE
  \begin{itemize}
  \item $Y$ is $\sigma$-compact and locally compact.
  \item $K$ has a winning predetermined strategy for $G_{KP}(Y)$.
  \end{itemize}
\end{theorem}

\begin{proof}
The forward implication was proved earlier.

Suppose $K$ has a winning predetermined strategy. Then $Y$ is certainly $\sigma$-compact, and by the corollary, it must also be locally compact.
\end{proof}

While a winning predetermined strategy for $K$ obviously implies the space is $\sigma$-compact, it further implies that the space is hemicompact (it can be broken into $\omega$ increasing compact portions such that every compact set is a subset of some portion).

\begin{lemma}
If $K$ has a winning predetermined strategy for $G_{KP}(Y)$, then $Y$ is hemicompact.
\end{lemma}

\begin{proof}
Let $\sigma$ be an increasing predetermined strategy for $K$ in the game $G_{KL}(Y)$ such that there exists a compact set $C$ such that $C \not\subseteq \sigma(n)$. On each turn, have $P$ play $y_n\in C \setminus \sigma(n)$. Then the $y_n$ are an infinite subset of the compact set $C$ and must have a cluster point in $C$, showing $\sigma$ is not a winning strategy.

Thus if $K$ has a winning predetermined strategy, it witnesses that $Y$ is hemicompact.
\end{proof}

\begin{theorem}
For any locally compact space $Y$, TFAE
  \begin{itemize}
  \item $Y$ is hemicompact.
  \item $K$ has a winning predetermined strategy in $G_{KL}(Y)$.
  \item $K$ has a winning predetermined strategy in $G_{KP}(Y)$.
  \end{itemize}
\end{theorem}

\begin{proof}
Let $Y$ be hemicompact, witnessed by $K_n=\sigma(n)$. Let $H_0,H_1,\dots$ be a play by $H$ in $G_{KL}(Y)$. Suppose by way of contradiction that this play beats $\sigma$. Then let $y\in Y$ be the point such that for all neighborhoods $U$ of $y$, $U$ hits infinite $H_n$. Let $C$ be a compact neighborhood of $y$. As $K_n$ witnesses hemicompactness, $C \subseteq K_N = \sigma(N)$ for some $N$. But then $H_n$ intersects $\sigma(N)$ for infinitely many $n$, contradiction.

Any winning strategy for $G_{KL}(Y)$ is a winning strategy for $G_{KP}(Y)$, and winning predetermined strategies for $G_{KP}(Y)$ implies hemicompact by the previous lemma.
\end{proof}

\begin{corollary}
For any locally compact space $Y$, TFAE
  \begin{itemize}
  \item $Y$ is $\sigma$-compact.
  \item $Y$ is hemicompact.
  \item $K$ has a winning predetermined strategy in $G_{KL}(Y)$.
  \item $K$ has a winning predetermined strategy in $G_{KP}(Y)$.
  \end{itemize}
\end{corollary}

\begin{theorem}
For any Hausdorff $k$-space $Y$, TFAE
  \begin{itemize}
  \item $Y$ is hemicompact.
  \item $Y$ is $k_{\omega}$.
  \item $K$ has a winning predetermined strategy in $G_{KP}(Y)$.
  \end{itemize}
\end{theorem}

\begin{proof}
If $Y$ is hemicompact, then let it be witnessed by $K_n$. We claim $K_n$ also witnesses $k_{\omega}$, that is, a set $C$ is closed if and only if, $C\cap K_n$ is closed in $K_n$ for all $n$. Note the forward implication always holds for Hausdorff spaces as $C\cap K_n$ is closed in $Y$, and thus in every $K_n$.

Assume $C\cap K_n$ is closed in $K_n$ for all $n$. Let $H$ be any compact set. As $Y$ is hemicompact, $H\subseteq K_n$ for some $n$. Note $C\cap H = (C\cap K_n)\cap H$. As both $C \cap K_n$ and $H$ are closed in $K_n$, $C\cap H$ is closed in $K_n$, and thus $C\cap H$ is closed in $H$. As $Y$ is $k$ and $C\cap H$ is closed in $H$ for all compact $H$, $C$ is closed, showing the backwards implication.

Now if $Y$ is $k_\omega$, let it be witnessed by $K_n$. Give $K$ the strategy $\sigma(n)=K_n$ for the game $G_{KP}(Y)$, and let $y_n$ be a play by $P$ such that $y_n \not\in \sigma(n)$. Suppose by way of contradiction that $y$ is a cluster point of the $y_n$. Note $y\in \sigma(N)$ for some $N$. $y$ is a cluster point of $\{y_n : n\geq N\}$ but $y\not\in \{y_n : n \geq N\}$. Also, $\{y_n : n \geq N\} \cap \sigma(m)$ is finite for all $m$, and thus closed, so as $\sigma(n)$ witnesses $k_\omega$, $\{y_n : n\geq N\}$ is closed and contains its cluster point $y$, contradiction. Thus $\sigma$ is a winning predetermined strategy for $K$ in $G_{KP}(Y)$.

Finally, if $K$ has a winning predetermined strategy for $G_{KP}(Y)$, $Y$ is hemicompact by the previous lemma.
\end{proof}

\begin{theorem}
For any hemicompact Hausdorff k-space $Y$, $K$ has a winning predetermined strategy in $G_{KL}(Y)$.
\end{theorem}

\begin{proof}
Let $Y$'s hemicompactness be witnessed by $K_n=\sigma(n)$ (which also witnesses $k_\omega$ by the previous theorem). Let $H_0,H_1,\dots$ be a play by $H$ in $G_{KL}(Y)$, and suppose this play defeats $\sigma$. Then there is a point $y$ such that every neighborhood of $y$ hits infinitely many of the $H_n$.

Now, $y\in\sigma(N)$ for some $N$, and since $H_0,H_1,\dots$ is a winning play for $H$, $y\not\in H_n$ for all $n\geq N$. Consider the set $H_\omega=\bigcup_{n\geq N} H_n$. Note $H_\omega$ is closed if and only if $H_\omega \cap \sigma(m)$ is closed in $\sigma(m)$ for all $m$ (by $k_\omega$). In fact, since every $H_n$ is a subset of some $\sigma(m)$ (by hemicompactness), $H_\omega \cap \sigma(m)$ is a finite union of some $H_n$, and is thus closed in $Y$.

We thus have that $H_\omega$ is a closed set not containing $y$. But since every neighborhood of $y$ intersects $H_\omega$, we have a contradiction. Thus $\sigma$ is a winning predetermined strategy for $K$ in the game $G_{KL}(Y)$.
\end{proof}

\begin{corollary}
For any Hausdorff $k$-space $Y$, TFAE
  \begin{itemize}
  \item $Y$ is hemicompact.
  \item $Y$ is $k_{\omega}$.
  \item $K$ has a winning predetermined strategy in $G_{KL}(Y)$.
  \item $K$ has a winning predetermined strategy in $G_{KP}(Y)$.
  \end{itemize}
\end{corollary}

We now consider the subspace of $\beta\omega$ consisting of $\omega$ and a single ultrafilter $\mathcal{F}$. (Needs more info on behavior).

\begin{proposition}
$K$ has no predetermined winning strategy in the compact-compact game $G_{K,L}(Y)$ for the single ultrafilter space $Y=\omega \cup \{\mathcal{F}\}$ where $\mathcal{F}\in \beta\omega\setminus\omega$.
\end{proposition}

\begin{proof}
Compact sets are exactly finite sets in this space. Therefore, the difference of any two compact sets is compact.

Give $K$ the predetermined strategy $\sigma(n)$. Have $H$ play \[H_n=(n\cup\sigma(n+1))\setminus\sigma(n)\] on turn $n$. The resulting union of $K$'s play is the cofinite set $Y\setminus\sigma(0)$, for which any ultrafilter would be a limit point.
\end{proof}

\begin{proposition} 
If a selective ultrafilter $\mathcal{F}$ exists, then $K$ has no winning predetermined strategy in the compact-point game $G_{KP}(Y)$ for the single selective ultrafilter space $Y=\omega \cup \{\mathcal{F}\}$.
\end{proposition}

\begin{proof}
Let $\sigma$ be a strictly increasing predetermined strategy for $K$. For every partition $\{B_n : n < \omega\}$ of subsets of $\omega$ such that $B_n \not\in \mathcal{F}$ for all $n$, there exists $A \in \mathcal{F}$ such that $|A \cap B_n|=1$ for all $n$. So then let \[B_n = \omega \cap \sigma(n) \setminus \left(\bigcup_{m<n} \sigma(m)\right)\]

  Note that $B_n$ is finite and thus $B_n \not\in \mathcal{F}$, so there exists $A\in \mathcal{F}$ such that $|A \cap B_n|=1$. Let $y_n$ be the singleton in $A \cap B_{n+1}$, so $\{y_n : n < \omega\}$ is cofinite in $A$, and thus is also in $\mathcal{F}$. Thus $y_n$ has $\mathcal{F}$ as a cluster point, and $\sigma$ is not a  winning predetermined strategy.
\end{proof}

\begin{theorem}
Let $a_n$ be a sequence such that the sequence $\frac{a_n}{n}$ is unbounded above. Then there is an ultrafilter $\mathcal{F}$ such that $\sigma(n)=(\sum_{m\leq n} a_m )\cup \{\mathcal{F}\}$ is a winning predetermined strategy for $K$ in $G_{K,P}(\omega\cup\{\mathcal{F}\})$.
\end{theorem}

\begin{proof}
Let $\mathcal{P}$ be the collection of all legal plays by $P$ against the strategy $\sigma$. Consider a finite collection of plays $P_0,\dots,P_{n-1}\in \mathcal{P}$. As $\frac{a_m}{m}$ is unbounded above, we may find infinitely many $m$ such that $\frac{a_m}{m}>n \Rightarrow mn<a_m$. As the $a_m$ partition $\omega$ such that $P$ may only play at most $m$ points in each part, there are infinitely many parts which are not filled, and thus $\bigcup_{m<n} P_m$ is not cofinite.

It then follows that the closure of $\mathcal{P}$ under finite unions and subsets is an ideal. Its dual filter may then be extended to an ultrafilter $\mathcal{F}$ such that every possible play by $P$ is the complement of some member of $\mathcal{F}$.
\end{proof}

\begin{proposition}
Let $a_n$ be a sequence bounded above by $k$. Then $\sigma(n)=(\sum_{m\leq n} a_m )\cup \{\mathcal{F}\}$ is not a winning predetermined strategy for $K$ in $G_{K,P}(Y)$ for any single ultrafilter space $Y$.
\end{proposition}

\begin{proof}
For any ultrafilter, there exists some $a<k$ such that $P_{a,k}=\{z : a = z\mod k\} \in \mathcal{F}$. Thus for such $\sigma(n)$, have $P$ respond with $y_n = a + (n+1)k$, giving a cofinite subset of $P_{a,k}$ (also in $\mathcal{F}$).
\end{proof}

\begin{conjecture}
If $K$ has a predetermined winning strategy in $G_{K,L}(Y)$ then $Y$ is a $k$-space.
\end{conjecture}

\begin{proof}
Some ideas:

Let $K_n$ be a winning predetermined strategy for $K$. For all sequences $L_n$ of compact sets, if every neighborhood of a point hits infinitely many of the $L_n$, then there is some $N$ such that $L_N \cap K_N \not= \emptyset$.

Aiming for a contradiction, let $C \cap K$ be closed in $K$ for all compact $K$, while for some $l\in C'$, $l \not\in C$. Assume without loss of generality that $l\in K_0$.

For each $n$, there exists an open $U_n$ where $U_n \cap K_n$ is a $K_n$-neighborhood of $l$ but $U_n \cap K_n \cap C = \emptyset$. But since $l\in C'$, each $U_n$ meets $C$ at some point $p_n \not\in K_n$.

There is an open neighborhood $V$ of $l$ which only hits finitely many of the $p_n$. What is $V \cap \bigcup_n U_n$?
\end{proof}

\centerline{\bf $G_{O,P}(X,x)$}

\begin{proposition}
$G_{OP}(X,x)$ is order-inspecific.
\end{proposition}

\centerline{\bf $G_{O,P}(X,x)$ for the one-point comapctification of $\omega_1$}

\begin{proposition}
Let $X=\omega_1\cup\{\infty\}$ be the one-point compactification of discrete $\omega_1$. $O$ has a winning limited-information strategy for $G_{OP}(X,\infty)$ if she may derive a finite superset of all points played so far by $P$.
\end{proposition}

\begin{proposition}
If $O$ has a winning strategy, then $O$ has a winning strategy $\sigma$ which only considers the set of previous moves by $P$ (ignoring order) such that $\sigma(A)\subseteq \sigma(B)$ for $B\subseteq A$.
\end{proposition}

\begin{proposition}
$O$ has no winning predetermined strategy for $G_{OP}(X,\infty)$.
\end{proposition}

\begin{proof}
Given a predetermined strategy $\sigma(n)$ for $O$, $P$ simply chooses any ordinal in $\bigcup_n \sigma(n)$ to play on every turn.
\end{proof}

\begin{proposition}
$O$ has a winning coding strategy for $G_{O,P}(X,\infty)$. 
\end{proposition}

\begin{proof}
Define $\sigma(U,p)=U\setminus\{p\}$. A legal play by $P$ must never repeat the same point, so the play converges to $\infty$.
\end{proof}

%\begin{theorem}
%$O$ has no winning tactical strategy for $G_{OP}(X,\infty)$.
%\end{theorem}

%\begin{proof}
%Let $\sigma(\alpha)$ be a tactical strategy for $O$ and $F(\alpha)=\omega_1\setminus\sigma(\alpha)$. Suppose by way of contradiction that for all% $\alpha_0,\alpha_1<\omega_1$, if $\alpha_1 \not\in F(\alpha_0)$ then it follows that $\alpha_0\in F(\alpha_1)$. Then for all $\alpha<\omega_1$, $\alpha\in F(\beta)$ for all $\beta\not\in F(\alpha)$.

%So $0\in F(\beta)$ for all $\beta\not\in F(0)$, $1\in F(\beta)$ for all $\beta \not\in F(1)$, and so on. Then $0,1,2,\dots\in F(\beta)$ for all $\beta\not\in\bigcup_n F(n)\not=\omega_1$, contradiction.

%Thus there exist a pair $\alpha_0,\alpha_1$ such that $\alpha_1\not\in F(\alpha_0)$ and $\alpha_0\not\in F(\alpha_1)$. $P$ beats $\sigma$ by playing this pair repeatedly.
%\end{proof}

\begin{proposition}
$O \not\markwin{k} G_{O,P}(\omega_1\cup\{\infty\},\infty)$. (Due to P. Nyikos)
\end{proposition}

\begin{proof}
Let $F(\alpha,n)$ be the complement of $O$'s Markov strategy in response to $\alpha$ in round $n$. Let \[ p\in \omega_1 \setminus \bigcup_{(m,n)\in\omega^2} F(m,n)\] and \[q_n \in \omega \setminus F(p,2n+1)\] The play $\left<p,q_0,p,q_1,\dots\right>$ is a counter to $O$'s Markov strategy.
\end{proof}

%\begin{theorem}
%$O$ has no winning $k$-tactical strategy of $G_{O,P}(X,\infty)$.
%\end{theorem}
%
%\begin{proof}
%Let $\sigma:[\omega_1]^{\leq k}\to[\omega_1]^{<\omega}$ be a $k$-tactical strategy for $O$ and $F(S)=\omega_1\setminus\sigma(S)$.
%
%Let $W_0=\omega_1$. We define $W_\alpha$ recursively as follows:
%    \begin{itemize}
%    \item For successor ordinals $\alpha+1$, let $\beta$ be the least element of $W_\alpha$ such that $[\beta+1,\omega_1) \cap \bigcup_{S\in [\beta]^{\leq k}} F(S)$ is nonempty, where $S \leq \beta$ is shorthand for $\{S \in [\omega_1]^{\leq k} : \forall \gamma \in S(\gamma < \beta)\}$. If no such $\beta$ exists, let $W_{\alpha+1}=W_\alpha$ and otherwise let $W_{\alpha+1}=W_\alpha \setminus \left([\beta+1,\omega_1) \cap \bigcup_{S\leq \beta} F(S)\right)$.
%    \item For limit ordinals $\alpha$, let $W_\alpha = \bigcap_{\beta<\alpha} W_\beta$.
%    \end{itemize}
%
%Finally let $W=\bigcap_{\alpha<\omega_1}W_\alpha$ and observe that it is unbounded. Let $R$ collect all ordinals $\alpha\in W$ such that there is an ordinal $\beta$ where for all $S\in[W\cap(\beta,\omega_1)]^{\leq k}$, $\alpha \in F(S)$. It is easily seen that $R$ is finite. Let $0^*$ be the least element of $W\setminus R$.
%
%Now, define a strictly increasing sequence of ordinals $\left<\alpha_1,\alpha_2,\alpha_3,\alpha_4,\dots\right>$ such that $\alpha_i \in W$ and $0^* \not\in F(\{\alpha_{2i+1},\dots,\alpha_{2i+k}\})$ for all $i$. The play $\left<0^*,\alpha_1,\dots,\alpha_k,0^*,\alpha_{k+1},\dots,\alpha_{2k},0^*,\dots\right>$ then defeats the strategy $\sigma$.
%\end{proof}

\begin{theorem}
$O\not\kmarkwin{k}G_{O,P}(\omega_1\cup\{\infty\},\infty)$.
\end{theorem}

\begin{proof}
Let $F:[\omega_1]^{\leq k}\times\omega\to[\omega_1]^{<\omega}$ be the complement of a $k$-Markov strategy for $O$.

Let $W_0=\omega_1$. We define $W_\alpha$ recursively as follows:
    \begin{itemize}
    \item For successor ordinals $\alpha+1$, let $\beta$ be the least element of $W_\alpha$ such that \[(\beta,\omega_1) \cap \bigcup_{S\in [\beta]^{\leq k}, n<\omega} F(S,n)\] is nonempty. If no such $\beta$ exists, let $W_{\alpha+1}=W_\alpha$ and otherwise let \[W_{\alpha+1}=W_\alpha \setminus \left((\beta,\omega_1) \cap \bigcup_{S\in[\beta]^{\leq k}, n<\omega} F(S,n)\right)\]
    \item For limit ordinals $\alpha$, let $W_\alpha = \bigcap_{\beta<\alpha} W_\beta$.
    \end{itemize}

Finally let $W=\bigcap_{\alpha<\omega_1}W_\alpha$ and observe that it is unbounded. Let $R$ collect all ordinals $\alpha\in W$ such that there is an ordinal $\beta_\alpha$ and number $n_\alpha<\omega$ where for all $S\in[W\cap(\beta_\alpha,\omega_1)]^{\leq k}$, $\alpha \in F(S,n_\alpha)$.

If $R$ was infinite, then there is $\alpha_i\in R$ for each $i<\omega$ and some $N<\omega$ where for all $S\in[W\cap(\beta_{\alpha_i},\omega_1)]^{\leq k}$, $\alpha_i \in F(S,N)$, and thus for all $S\in[W\cap(\sup \beta_{\alpha_i},\omega_1)]^{\leq k}$,  $\{\alpha_i : i<\omega\} \subset F(S,N)$, a contradiction. So let $0^*$ be the least element of $W\setminus R$.

Now, define a strictly increasing sequence of ordinals $\left<\alpha_1,\alpha_2,\alpha_3,\alpha_4,\dots\right>$ such that $\alpha_i \in W$ and $0^* \not\in F(\{\alpha_{2i+1},\dots,\alpha_{2i+k}\})$ for all $i$. The play $\left<0^*,\alpha_1,\dots,\alpha_k,0^*,\alpha_{k+1},\dots,\alpha_{2k},0^*,\dots\right>$ then defeats the Markov strategy.
\end{proof}

\centerline{\bf $G_{O,P}(X,x)$ for Sigma Product}

\begin{proposition}
The player $O$ has a winning strategy for $G_{O,P}(X,x)$ where \[X=\{x\in \mathbb{R}^{\omega_1}: x_\alpha = 0 \text{ for all but countably many } \alpha<\omega_1\}\]
\end{proposition}

\begin{proof}
Without loss of generality we may assume that $x$ is the zero function. Let $y_n$ be the move by $P$ on turn $n$. For each $y_n$, let $l_n\in \omega_1^{\omega}$ enumerate the nonzero coordinates in $y_n$. Give $O$ the strategy $\sigma(y_0,\dots,y_{n-1}) = \prod_{\alpha<\omega_1} O_\alpha$ where if $\alpha$ is listed in the first $n$ coordinates of any term in $\left<l_k\right>_{k<n}$, then $O_\alpha=(-2^{-n},2^{-n})$, and $O_\alpha=\mathbb{R}$ otherwise.
\end{proof}

%\begin{theorem}
%The player $O$ has a winning coding (see Open Problems in Topology II) strategy for $G_{O,P}(X,x)$ where \[X=\{x\in \mathbb{R}^{\omega_1}: x_\alpha = 0 %\text{ for all but countably many } \alpha<\omega_1\}\]
%\end{theorem}
%
%\begin{proof}
%Encode every finite sequence $s$ of functions in $\Sigma\mathbb{R}^{\omega_1}$ as a positive real number $E(s)$. Let $L(U)$ be the function which, for each basic open set $O$ in $\mathbb{R}^{\omega_1}$ (besides $\mathbb{R}^{\omega_1}$ itself), returns the last non-$\mathbb{R}$ factor (a bounded open interval) in the product. Then let $D(I)$ be the function which, for each open interval $I=(-\epsilon,\epsilon)$, returns the sequence $E^{-1}(\epsilon)$.
%
%Finally, give $O$ the strategy $\sigma(U,y) = \prod_{\alpha<\omega_1} U_\alpha$ where, letting $n-1$ be the length of $D(L(U))$, if $\alpha$ is listed in the first $n$ coordinates of any term in the finite sequence $D(L(U))^\frown\left<y\right>$, then $U_\alpha=(-2^{-n},2^{-n})$, and if $\alpha$ is the first ordinal greater than all of the first $n$ coordinates of any term in $D(L(U))^\frown\left<y\right>$, then $U_\alpha=(-E(D(L(U))^\frown\left<y\right>),E(D(L(U))^\frown\left<y\right>))$, and $U_\alpha=\mathbb{R}$ otherwise.
%\end{proof}

\begin{theorem}
For all cardinals $\kappa\leq 2^\omega$, the player $O$ has a winning coding strategy for $G_{O,P}(X,x)$ where \[X=\Sigma\mathbb{R}^{\kappa}=\{x\in \mathbb{R}^{\kappa}: x_\alpha = 0 \text{ for all but countably many } \alpha<\omega_1\}\]
\end{theorem}

\begin{proof}
Note that $|\Sigma\mathbb{R}^\kappa| \leq 2^\omega = |\mathbb{R}|$. Define the following:

    \begin{itemize}
    \item Encode every finite sequence $s$ of functions in $\Sigma\mathbb{R}^{\kappa}$ as a real number $0<r(s)<1$. 
    \item Let $\gamma(U)$ be the function which, for basic open sets $U=\prod_{\alpha<\kappa}U_\alpha$ where $U_0=(-\frac{1}{R},\frac{1}{R})$ for some positive noninteger real number $R$, returns the sequence $r^{-1}(R-\lfloor R\rfloor)$.
    \item Let $n(U)$ be the length of $\epsilon^{-1}(\gamma(U))$.
    \item Let $\psi(U,y)=\epsilon^{-1}(\gamma(U))^\frown\left<y\right>$.
    \item Define $\sigma_0(U,y)$ to be $\left(-\frac{1}{n(U)+r(\psi(U,y))},\frac{1}{n(U)+r(\psi(U,y))}\right)$.
    \item For each $0<\alpha<\kappa$, define the interval $\sigma_\alpha(U,y)$ about $0$ as follows:
        \begin{itemize}
        \item If $\alpha$ is listed in the first $n(U)$ coordinates of any term in the finite sequence $\psi(U,y)$, then $\sigma_\alpha(U,y)=(-\frac{1}{n(U)+1},\frac{1}{n(U)+1})$.
        \item Otherwise, then $\sigma_\alpha(U,y)=\mathbb{R}$.
        \end{itemize}
    \end{itemize}

It follows that $\sigma(U,y)=\prod_{\alpha<\kappa} \sigma_\alpha(U,y)$ is a winning coding strategy.
\end{proof}

\begin{theorem}
For all cardinals $\kappa>2^\omega$ such that $\kappa^\omega = \kappa$, the player $O$ has a winning coding strategy for $G_{O,P}(X,x)$ where \[X=\Sigma\mathbb{R}^{\kappa}=\{x\in \mathbb{R}^{\kappa}: x_\alpha = 0 \text{ for all but countably many } \alpha<\omega_1\}\]
\end{theorem}

\begin{proof}
Note that $|\Sigma\mathbb{R}^\kappa| = \kappa^\omega = \kappa$. Define the following:

    \begin{itemize}
    \item Encode every finite sequence $s$ of functions in $\Sigma\mathbb{R}^{\kappa}$ as an ordinal $\epsilon(s)<\kappa$. 
    \item Let $\gamma(U)$ be the function which, for basic open sets $U=\prod_{\alpha<\kappa}U_\alpha$ with a unique factor $U_{\alpha^*}$, returns $\alpha^*$.
    \item Let $n(U)$ be the length of $\epsilon^{-1}(\gamma(U))$.
    \item Let $\psi(U,y)=\epsilon^{-1}(\gamma(U))^\frown\left<y\right>$.
    \item For each $\alpha<\kappa$, define the interval $\sigma_\alpha(U,y)$ about $0$ as follows:
        \begin{itemize}
        \item If $\alpha$ is listed in the first $n(U)$ coordinates of any term in the finite sequence $\psi(U,y)$ and is not equal to $\epsilon(\psi(U,y))$, then $\sigma_\alpha(U,y)=(-\frac{1}{n(U)+1},\frac{1}{n(U)+1})$.
        \item If $\alpha=\epsilon(\psi(U,y))$, then $\sigma_\alpha(U,y)=(-\frac{1}{n(U)+2},\frac{1}{n(U)+2})$.
        \item Otherwise, then $\sigma_\alpha(U,y)=\mathbb{R}$.
        \end{itemize}
    \end{itemize}

It follows that $\sigma(U,y)=\prod_{\alpha<\kappa} \sigma_\alpha(U,y)$ is a winning coding strategy.
\end{proof}

Note: Look at $G_{O,P}(X,x)$ where $x$ has weight $\omega_1$.

Also look at the clustering game $G^{cl}_{O,P}(\omega_1\cup\infty,\infty)$.

\end{document}

### 2013-01-24 phd preliminary oral presentation.tex
Initial commit

% $Header: /home/vedranm/bitbucket/beamer/solutions/generic-talks/generic-ornate-15min-45min.en.tex,v 90e850259b8b 2007/01/28 20:48:30 tantau $

\documentclass{beamer}

% This file is a solution template for:

% - Giving a talk on some subject.
% - The talk is between 15min and 45min long.
% - Style is ornate.

% Copyright 2004 by Till Tantau <tantau@users.sourceforge.net>.
%
% In principle, this file can be redistributed and/or modified under
% the terms of the GNU Public License, version 2.
%
% However, this file is supposed to be a template to be modified
% for your own needs. For this reason, if you use this file as a
% template and not specifically distribute it as part of a another
% package/program, I grant the extra permission to freely copy and
% modify this file as you see fit and even to delete this copyright
% notice.

\mode<presentation>
{
  \usetheme{Warsaw}
  % or ...

  \setbeamercovered{transparent}
  % or whatever (possibly just delete it)
}

\usepackage[english]{babel}
% or whatever

\usepackage[latin1]{inputenc}
% or whatever

\usepackage{times}
\usepackage[T1]{fontenc}
% Or whatever. Note that the encoding and the font should match. If T1
% does not look nice, try deleting the line with the fontenc.

\usepackage{marvosym} % For /Smiley

\title[Limited Information Strategies for Topological Games] % (optional, use only with long paper titles)
{Limited Information Strategies for Topological Games}

\subtitle
{PhD Preliminary Oral Defense} % (optional)

\author%[Author, Another] % (optional, use only with lots of authors)
{Steven~Clontz}%\inst{1} \and S.~Another\inst{2}}
% - Use the \inst{?} command only if the authors have different
%   affiliation.

\institute[Auburn University] % (optional, but mostly needed)
{
  %\inst{1}%
  Department of Mathematics and Statistics\\
  Auburn University}
  %\and
  %\inst{2}%
  %Department of Theoretical Philosophy\\
  %University of Elsewhere}
% - Use the \inst command only if there are several affiliations.
% - Keep it simple, no one is interested in your street address.

\date[5-21-2012] % (optional)
{May 21, 2012}

\subject{Steven Clontz's PhD Preliminary Defense}
% This is only inserted into the PDF information catalog. Can be left
% out.

% If you have a file called "university-logo-filename.xxx", where xxx
% is a graphic format that can be processed by latex or pdflatex,
% resp., then you can add a logo as follows:

% \pgfdeclareimage[height=1cm]{university-logo}{au.gif}
% \logo{\pgfuseimage{university-logo}}

% Delete this, if you do not want the table of contents to pop up at
% the beginning of each subsection:
%\AtBeginSubsection[]
%{
%  \begin{frame}<beamer>{Outline}
%    \tableofcontents[currentsection,currentsubsection]
%  \end{frame}
%}

% If you wish to uncover everything in a step-wise fashion, uncomment
% the following command:

%\beamerdefaultoverlayspecification{<+->}

% Strategy uparrow shortcuts
\newcommand{\win}{\uparrow}
\newcommand{\prewin}{\uparrow_{\text{pre}}}
\newcommand{\markwin}{\uparrow_{\text{mark}}}
\newcommand{\tactwin}{\uparrow_{\text{tact}}}
\newcommand{\ktactwin}[1]{\uparrow_{#1\text{-tact}}}
\newcommand{\kmarkwin}[1]{\uparrow_{#1\text{-mark}}}
\newcommand{\codewin}{\uparrow_{\text{code}}}

%One point compactification
\newcommand{\oneptcomp}[1]{#1^*}

%Open-point convergence/clustering games
\newcommand{\congame}[2]{Con_{O,P}(#1,#2)}
\newcommand{\clusgame}[2]{Clus_{O,P}(#1,#2)}

%Compact-point/compact locally finite games
\newcommand{\lfkpgame}[1]{LF_{K,P}(#1)}
\newcommand{\lfklgame}[1]{LF_{K,L}(#1)}

%Point-finite game on cardinals
\newcommand{\pfgame}[1]{PF_{F,C}(#1)}

%Sigma Product on R and 2
\newcommand{\sigmaprodr}[1]{\Sigma\mathbb{R}^{#1}}
\newcommand{\sigmaprodtwo}[1]{\Sigma2^{#1}}

%Single Ultrafilter Space on \omega
\newcommand{\sus}{\mathcal{F}\omega}
\newcommand{\uF}{\mathcal{F}}

% Vectors are bold
\renewcommand{\vec}[1]{\mathbf{#1}}

%Comments!
\newcommand{\comment}[1]{}

\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}{Table of Contents}
  \tableofcontents
  % You might wish to add the option [pausesections]
\end{frame}

% Since this a solution template for a generic talk, very little can
% be said about how it should be structured. However, the talk length
% of between 15min and 45min and the theme suggest that you stick to
% the following rules:

% - Exactly two or three sections (other than the summary).
% - At *most* three subsections per section.
% - Talk about 30s to 2min per frame. So there should be between about
%   15 and 30 frames, all told.

\section{Introduction}

\begin{frame}
\centerline{Let's get started!}
\end{frame}

\subsection[Definitions and Notation]{Definitions}

\begin{frame}{Definition of a Game of Length $\omega$}%{Subtitles are optional.}
  % - A title should summarize the slide in an understandable fashion
  %   for anyone how does not follow everything on the slide itself.

\begin{itemize}
\item A \textbf{game of length $\omega$} consists of two \textbf{Players} I and II. On \textbf{round} $n$ of $\omega$, Player I first takes a \textbf{turn} choosing an element of some set $X$ (her \textbf{move}), followed by Player II taking a turn choosing an element from some set $Y$.
\pause
\item Example: Gruenhage's open-point convergence game on $\mathbb{R}^2$,$\vec{0}$ with players $O,P$ ($X=\tau$, $Y=\mathbb{R}^2$)
\[
\begin{array}{r|r|l}
\text{Round} & O & P \\\hline\hline
0 & B(1,\vec{0}) & \left<0.5,-0.8\right> \\\hline
1 & B(0.25,\vec{0}) & \left<-0.1,0.1\right> \\\hline
2 & B(0.05,\vec{0}) & \left<-0.01,-0.02\right> \\\hline
\dots & \dots & \dots
\end{array}
\]
\end{itemize}
\end{frame}

\begin{frame}{Definition of a Game of Length $\omega$ (cont)}
\begin{itemize}
\item A \textbf{rule} for a Player in a game is a condition on that player's move during each round. A move is said to be \textbf{legal} if it doesn't violate the rule. (Ex: $P$ must choose a point inside of the set previously chosen by $O$)
\pause
\item A \textbf{play} of the game is a sequence $\left<x_0,y_0,x_1,y_1,\dots\right> \in (X\times Y)^\omega$. It is said to be \textbf{legal} if each move is legal. A finite initial sequence of a play is called a \textbf{partial play}.
\end{itemize}
\end{frame}

\begin{frame}{Definition of a Game of Length $\omega$ (cont)}
\begin{itemize}
\item A \textbf{winning condition} is some condition on the play resulting from the game. (Ex: the points chosen by $P$ converge to $\vec{0}$)
\pause
\item Player I \textbf{wins} a legal play if this condition is satisfied. If not, Player II wins.
\end{itemize}
\end{frame}

\begin{frame}{Definition of a Game of Length $\omega$ (cont)}
\begin{itemize}
\item A \textbf{strategy} for a Player is a function which has all legal partial plays as its domain and yields legal moves for that Player.
\pause
\item A \textbf{counter} to a Player's strategy is a play of the game for which the Player follows her strategy, but the play results in a loss for that Player.
\pause
\item A strategy is called a \textbf{winning strategy} if there does not exist a counter for it.
\pause
\item The notation for player $P$ having a winning strategy for game $G$ is $P\win G$.
\end{itemize}
\end{frame}

\begin{frame}{But why?}
\begin{itemize}
\item For games defined in terms of arbitrary topological spaces, the existence of a winning strategy for a Player characterizes a property of that space.
\pause
\item For example, one of the earliest such games studied was the Banach Mazur game $MB(X)$.
\pause
\item Both players alternate choosing nonempty open sets $W_n,V_n\in\mathcal{W}$, with the rule that $W_n\supseteq V_n\supseteq W_{n+1}$. $I$ wins the game if $\bigcap_{n<\omega}W_n\not=\emptyset$. As it turns out:
\pause
\item \textbf{Theorem:} $II\win MB(X)$ if and only if $X$ is first-category/meager ($X$ is the countable union of nowhere dense subsets). [Oxtoby 1957]
\end{itemize}
\end{frame}

\begin{frame}{Game naming conventions}
For readabily, we adopt the following conventions for naming games.
  \begin{itemize}
  \item
    Games are named according to the following format: \[Clus_{O,P}(X,p)\]
  \pause
  \item
    The subscript letters ($\,_{O,P}$ in the example) name the first and second players based on the moves they make in the game. ($O$ choses open subsets of $X$, $P$ choses points in $X$)
  \pause
  \item
    The leading letters ($Clus$ in the example) refer to the game's winning condition. (The points chosen by $P$ cluster around $p$.)
  \pause
  \item
    The interior of the parentheses ($X,p$ in the example) denotes the topological space and other information about the ``game board''.
  \end{itemize}
\end{frame}

\begin{frame}{Limited Information Strategies}
  \begin{itemize}
  \item
    The presence or absence of a winning strategy characterizes a topological property on the space the game is played on.
  \pause
  \item
    The presence or absence of a winning \textbf{limited information strategy}, a strategy with a restricted domain, also characterizes a property of the space.
  \pause
  \item
    For example, when we consider only locally compact spaces, the presence of a winning strategy for player $K$ in the locally-finite game $LF_{K,L}(X)$ characterizes paracompactness, but the presence of a winning strategy \textit{which only uses the round number} characterizes hemicompactness.
  \end{itemize}
\end{frame}

\begin{frame}{Types of Limited Info Strats}
  \begin{itemize}
  \item
    A \textbf{tactical strategy} (sometimes called a \textit{stationary strategy} or \textit{tactic}) uses only the most recent move by the opponent. (Notation: $P\tactwin G$)
  \pause
  \item
    A \textbf{$k$-tactical strategy} uses only the previous $k$ moves by the opponent. (Notation: $P\ktactwin{k}G$)
  \pause
  \item
    A \textbf{predetermined strategy} uses only the round number. (Notation: $P\prewin G$)
  \end{itemize}
\end{frame}

\begin{frame}{Types of Limited Info Strats (cont)}
  \begin{itemize}
  \item
    A \textbf{Markov strategy} uses only the most recent move of the opponent and the round number (i.e. the current ``state'' of the game). (Notation: $P\markwin G$)
  \pause
  \item
    A \textbf{$k$-Markov strategy} uses only the previous $k$ moves of the opponent and the round number. (Notation: $P\kmarkwin{k}G$)
  \pause
  \item
    A \textbf{coding strategy} uses only the most recent move of the opponent and the player's own most recent move (it ``encodes'' any extra needed information into its own moves). (Notation: $P\codewin G$)
  \end{itemize}
\end{frame}

\begin{frame}{Types of Limited Info Strats (cont)}
\begin{center}
\begin{tabular}{|c|c|c|}\hline
\textbf{Name} & \textbf{Notation} & \textbf{Info Used} \\\hline
tactical & $P\tactwin G$ & \shortstack{most recent move \\ of opponent} \\\hline
$k$-tactical & $P\ktactwin{k} G$ & \shortstack{$k$ most recent moves \\ of opponent} \\\hline
predetermined & $P\prewin G$ & round number \\\hline
Markov & $P\markwin G$ & \shortstack{most recent move of \\ opponent \& round \#} \\\hline
$k$-Markov & $P\kmarkwin{k} G$ & \shortstack{$k$ most recent moves of \\ opponent \& round \#} \\\hline
coding & $P\codewin G$ & \shortstack{most recent moves of \\ both players} \\\hline
\end{tabular}
\end{center}
\end{frame}

\section{Some Results}

\begin{frame}
\centerline{Some Results!}
\end{frame}

\subsection[Compact-Point/Compact Locally Finite Games]{Compact-Point/Compact Locally Finite Games}

\begin{frame}{Compact-Point/Compact Locally Finite Game}
The following two games are due to Gary Gruenhage:
\begin{itemize}
\item $\lfkpgame{X}$ is a game in which $K$ chooses compact subsets of $X$ and $P$ chooses points in $X$ with the rule that chosen points must lay outside of all previously chosen compact sets. $K$ wins if the points chosen by $P$ are locally finite in $X$.
\pause
\item $\lfklgame{X}$ is defined similarly, with $L$ choosing compact sets instead of points.
\end{itemize}
\end{frame}

\begin{frame}{$\lfkpgame{X}$ and $\lfklgame{X}$ for locally compact $X$}
Gruenhage proved the following results in 1985 for locally compact $X$:
\pause
\begin{itemize}
\item $K\tactwin\lfkpgame{X}$ iff $X$ is metacompact
\pause
\item $K\markwin\lfkpgame{X}$ iff $X$ is $\sigma$-metacompact
\pause
\item $K\win\lfklgame{X}$ iff $X$ is paracompact
\end{itemize}
\end{frame}

\begin{frame}{$\lfkpgame{X}$ and $\lfklgame{X}$ for locally compact $X$ (cont)}
Using the idea of a predetermined strategy, I found that the following are all equivalent for locally compact $X$:
\pause
\begin{itemize}
\item $K\prewin\lfkpgame{X}$
\item $K\prewin\lfklgame{X}$
\pause
\item $X$ is Lindelof
\pause
\item $X$ is $\sigma$-compact
\pause
\item $X$ is hemicompact
\end{itemize}
\end{frame}

\begin{frame}{$\lfkpgame{X}$ and $\lfklgame{X}$ for $T_2$ $k$-spaces $X$}
The following equivalancies are found when generalizing locally compact to $k$, provided $X$ is $T_2$:
\pause
\begin{itemize}
\item $K\prewin\lfkpgame{X}$
\item $K\prewin\lfklgame{X}$
\pause
\item $X$ is hemicompact
\pause
\item $X$ is a $k_\omega$ space
\end{itemize}
\end{frame}

\begin{frame}{Single Ultrafilter Space}
We say a \textbf{single ultrafilter space} $\sus$ is a countable subspace of the Stone-Cech compactification $\beta\omega$ consisting of $\omega$ and a single ultrafilter $\uF$. (Any $\sus$ is not a $k$-space.)
\pause
\begin{itemize}
\item $K \not\prewin \lfklgame{\sus}$ for any $\uF$.
\pause
\item It is consistent that there exist ultrafilters $\uF$ such that $K \not\prewin \lfkpgame{\sus}$
\pause
\item There exist ultrafilters $\uF$ such that $K\prewin \lfkpgame{\sus}$
\end{itemize}
\end{frame}

\subsection[Open-Point Convergence/Clustering Games]{Open-Point Convergence/Clustering Games}

\begin{frame}{Open-Point Convergence/Clustering Games}
The following two games are also due to Gary Gruenhage:
\pause
\begin{itemize}
\item $\congame{X}{p}$ is a game in which $O$ chooses neighborhoods of $p$ and $P$ chooses points in $X$ with the rule that chosen points must lay inside of all previously chosen neighborhoods. $O$ wins if the points chosen by $P$ converge to $p$.
\pause
\item $\clusgame{X}{p}$ is defined similarly, but $O$ wins if the points chosen by $P$ just cluster around $p$.
\end{itemize}
\pause
Note that $\congame{\oneptcomp{X}}{\infty}$ is an equivalent game to $\lfkpgame{X}$, where $\oneptcomp{X}=X\cup\{\infty\}$ is the one-point compactification of $X$.
\end{frame}

\begin{frame}{$\congame{\oneptcomp{\kappa}}{\infty}$ and $\clusgame{\oneptcomp{\kappa}}{\infty}$}
For discrete $X$, the existence of winning limited information strategies for $\congame{\oneptcomp{X}}{\infty}$ and $\clusgame{\oneptcomp{X}}{\infty}$ depends on the cardinality of $X$.
\pause
\begin{itemize}
\item For $\kappa<\omega_1$:
    \begin{itemize}
    \item $O\prewin\congame{\oneptcomp{\kappa}}{\infty}$
    \item $O\tactwin\congame{\oneptcomp{\kappa}}{\infty}$
    \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{$\congame{\oneptcomp{\kappa}}{\infty}$ and $\clusgame{\oneptcomp{\kappa}}{\infty}$ (cont)}
\begin{itemize}
\item For $\kappa=\omega_1$:
    \begin{itemize}
    \item $O\not\prewin\clusgame{\oneptcomp{\kappa}}{\infty}$
    \item $O\not\ktactwin{k}\clusgame{\oneptcomp{\kappa}}{\infty}$
    \item $O\markwin\clusgame{\oneptcomp{\kappa}}{\infty}$
    \item $O\not\kmarkwin{k}\congame{\oneptcomp{\kappa}}{\infty}$
    \end{itemize}
\pause
\item For $\kappa>\omega_1$:
    \begin{itemize}
    \item $O\not\kmarkwin{k}\clusgame{\oneptcomp{\kappa}}{\infty}$
    \item $O\codewin\congame{\oneptcomp{\kappa}}{\infty}$
    \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{Proof of No Tactical Strat for Clustering on $\oneptcomp{\omega_1}$}
\begin{itemize}
\item \textbf{Theorem:} $O\not\ktactwin{k}\clusgame{\oneptcomp{\kappa}}{\infty}$ for $\kappa\geq\omega_1$.
\end{itemize}
\pause
\textbf{Proof:} Let $F:[\kappa]^{\leq k} \to [\kappa]^{<\omega}$ be a forbidding strategy by $O$ against $P$ which is downward on $\omega_1$.
\end{frame}

\begin{frame}{Proof of No Tactical Strat for Clustering on $\oneptcomp{\omega_1}$ (cont)}
We define $n_i$ for $0\leq i < k$ to be a finite ordinal such that
\[
n_i \in \omega_1 \setminus F(\{n_0,\dots,n_{i-1}\})
\]
\[
\setminus F(\{n_0,\dots,n_{i-1},\omega+i,\dots,\omega+k-1\})
\]
\pause
and note that
\[
\left<n_0,n_1,\dots,n_{k-1},\omega,\omega+1,\dots,\omega+k-1,\right.
\]
\[
\left.n_0,n_1,\dots,n_{k-1},\omega,\omega+1,\dots,\omega+k-1,\dots\right>
\]
counters $F$. \qed
\end{frame}

\begin{frame}{Proof of Markov Strat for Clustering on $\oneptcomp{\omega_1}$}
While clustering is impossible with a tactic, clustering is possible if you also know the round number:
\begin{itemize}
\item \textbf{Theorem:} $O\markwin \clusgame{\oneptcomp{\omega_1}}{\infty}$.
\end{itemize}
\pause
\textbf{Proof} For $\alpha<\omega_1$ let $A_{\alpha,n}$ be a sequence of finite sets such that $A_{\alpha,n}\subset A_{\alpha,n+1}$ and $\bigcup_{n<\omega}A_{\alpha,n}=\alpha+1$.

\pause\,

Give $O$ the Markov forbidding strategy $F(n,\alpha)=A_{\alpha,n}$ and observe that any sequence of legal moves by $P$ against the strategy $F$ has an image of infinite cardinality.\qed
\end{frame}

\begin{frame}{Sigma Product space $\sigmaprodr{\kappa}$}
The sigma product space of $\mathbb{R}$ is \[\sigmaprodr{\kappa}=\{p\in\mathbb{R}^\kappa:|\{\alpha<\kappa:p(\alpha)\not=0\}|\leq\omega\}\]
\pause
\begin{itemize}
\item Note that $\oneptcomp{\kappa}$ is homeomorphic to the subspace \[\{p\in\mathbb{R}^\kappa:|\{\alpha<\kappa:p(\alpha)\not=0\}|\leq 1\}\subseteq\sigmaprodtwo{\kappa}\]
\pause
\item Thus $O\not\kmarkwin{k}\clusgame{\sigmaprodr{\kappa}}{\vec{0}}$.
\end{itemize}
\end{frame}

\begin{frame}{$\congame{\sigmaprodr{\kappa}}{\vec{0}}$}
The obvious winning strategy for $O$ in $\congame{\sigmaprodr{\kappa}}{\vec{0}}$ uses all the previous moves of the opponent and the turn number.
\begin{itemize}
\item $O\win\congame{\sigmaprodr{\kappa}}{\vec{0}}$
\end{itemize}
\pause
These moves can be encoded so that a coding strategy is sufficient.
\begin{itemize}
\item $O\codewin\congame{\sigmaprodr{\kappa}}{\vec{0}}$
\end{itemize}
\end{frame}

\begin{frame}{Proof of a Winning Strategy for $\congame{\sigmaprodr{\kappa}}{\vec{0}}$}
\begin{itemize}
\item \textbf{Theorem:} $O\win\congame{\sigmaprodr{\kappa}}{\vec{0}}$
\end{itemize}
\pause
\textbf{Proof} The strategy:
\[
\sigma(s_0,\dots,s_{n-1})=\sigmaprodr{\kappa}\cap\prod_{\alpha<\kappa}\sigma_\alpha(s_0,\dots,s_{n-1})
\]
\pause
where
\[
\sigma_\alpha(s_0,\dots,s_{n-1})=\left(-\frac{1}{n},\frac{1}{n}\right)
\]
when $\alpha$ is ``one of the first $n$ nonzero coordinates'' of some $s_i$, and $\sigma_\alpha(s_0,\dots,s_{n-1})=\mathbb{R}$ otherwise.\qed
\end{frame}

\begin{frame}{Proof Sketch of a Winning Coding Strategy for $\congame{\sigmaprodr{\kappa}}{\vec{0}}$}
\begin{itemize}
\item \textbf{Theorem:} $O\codewin\congame{\sigmaprodr{\kappa}}{\vec{0}}$
\end{itemize}
\pause
\textbf{Sketch Proof} by transfinite induction:
\pause
\begin{itemize}
\item Consider $\kappa^+$. For $\alpha<\kappa^+$, $O$ has a coding strategy for $\congame{\sigmaprodr{\alpha}}{\vec{0}}$.
\pause
\item Let $\sigma(U,p)=U \cap \bigcup_{\alpha\in N(U)}\sigma_{\alpha+1}(U\cap(\alpha+1),p\restriction (\alpha+1))$ where $N(U)$ is every coordinate restricted by $U$.\qed
\end{itemize}
\pause
The proof is similar for limit cardinals $\kappa$.
\end{frame}

\section{Questions}

\begin{frame}
\centerline{Things to do...}
\end{frame}

\subsection[Compact-Compact Game and $k$ Property]{Compact-Compact Game and $k$ Property}

\begin{frame}{Question about $K\prewin\lfklgame{X}$}
So far, every examined non-$k$-space examined has failed to reveal a predetermined strategy for $\lfklgame{X}$. Similarly, every examined space which has a predetermined strategy for $\lfklgame{X}$ has been a $k$-space.
\pause
\begin{itemize}
\item Does $K\prewin\lfklgame{X}$ imply $X$ is a $k$-space?
\end{itemize}
\end{frame}

\subsection[Tactical and Markov strategies in $\lfkpgame{X}$]{Tactical and Markov strategies in $\lfkpgame{X}$}

\begin{frame}{Questions about $\lfkpgame{X}$ and $\congame{\oneptcomp{X}}{\infty}$}
For locally compact, $T_2$ $X$: 
\begin{itemize}
\item $K\tactwin\lfkpgame{X}$ iff $O\tactwin\congame{\oneptcomp{X}}{\infty}$ iff $X$ is metacompact
\item $K\markwin\lfkpgame{X}$ iff $O\markwin\congame{\oneptcomp{X}}{\infty}$ iff $X$ is $\sigma$-metacompact
\end{itemize}
\pause
What happens if we make these changes?
\pause
\begin{itemize}
\item Instead of $X$ locally compact, let $X$ be a $k$-space.
\pause
\item Instead of $\congame{\oneptcomp{X}}{\infty}$, consider $\clusgame{\oneptcomp{X}}{\infty}$
\end{itemize}
\end{frame}

\subsection[Convergence Game on Sigma Product and other spaces]{Convergence Game on Sigma Product and other spaces}

\begin{frame}{Questions about $\congame{X}{p}$}
We've seen that $O\codewin\congame{\sigmaprodr{\kappa}}{\vec{0}}$ and $O\not\kmarkwin{k}\clusgame{\sigmaprodr{\kappa}}{\vec{0}}$.
\pause
\begin{itemize}
\item What does the existence of these strategies characterize for an arbitrary space $X$?
\end{itemize}
\end{frame}

\subsection{General Questions}

\begin{frame}{Other ideas...}
\begin{itemize}
\item Investigate other known games (Banach-Mazur, Sierpenski, Menger...)
\pause
\item Anything from the crowd? :-)
\end{itemize}
\end{frame}

\section{Conclusion}

\begin{frame}{Thanks!}
Thanks as always for all your support and instruction.
\pause
\begin{itemize}
\item Questions?
\end{itemize}
\end{frame}

\end{document}

### 2013-01-24 phd_research_results.tex
Initial commit

\documentclass[11pt]{article}

\pdfpagewidth 8.5in
\pdfpageheight 11in

\setlength\topmargin{0in}
\setlength\headheight{0in}
\setlength\headsep{0.2in}
\setlength\textheight{8in}
\setlength\textwidth{6in}
\setlength\oddsidemargin{0in}
\setlength\evensidemargin{0in}
\setlength\parindent{0.25in}
\setlength\parskip{0.1in}

\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{amsthm}

      \theoremstyle{plain}
      \newtheorem{theorem}{Theorem}
      \newtheorem{lemma}[theorem]{Lemma}
      \newtheorem{corollary}[theorem]{Corollary}
      \newtheorem{proposition}[theorem]{Proposition}
      \newtheorem{conjecture}[theorem]{Conjecture}
      \newtheorem{question}[theorem]{Question}
      \newtheorem{example}[theorem]{Example}

      \theoremstyle{definition}
      \newtheorem{definition}[theorem]{Definition}

      \theoremstyle{remark}
      \newtheorem{remark}[theorem]{Remark}

% Strategy uparrow shortcuts
\newcommand{\prewin}{\uparrow_{\text{pre}}}
\newcommand{\markwin}{\uparrow_{\text{mark}}}
\newcommand{\tactwin}{\uparrow_{\text{tact}}}
\newcommand{\ktactwin}[1]{\uparrow_{#1\text{-tact}}}
\newcommand{\kmarkwin}[1]{\uparrow_{#1\text{-mark}}}
\newcommand{\codewin}{\uparrow_{\text{code}}}
\newcommand{\limitwin}{\uparrow_{\text{limit}}}

\newcommand{\oneptcomp}[1]{#1\cup\{\infty\}}

\newcommand{\congame}[2]{Con_{O,P}(#1,#2)}
\newcommand{\clusgame}[2]{Clus_{O,P}(#1,#2)}

\newcommand{\pfgame}[1]{PF_{F,C}(#1)}

\newcommand{\sigmaprodr}[1]{\Sigma\mathbb{R}^{#1}}
\newcommand{\sigmaprodtwo}[1]{\Sigma2^{#1}}

\begin{document}

\centerline{\bf $Con_{O,P}(X,x)$}

\begin{definition} 
Gruenhage's open-point convergence game $\congame{X}{x}$ has $O$ choosing nested open sets and $P$ choosing a point within the last chosen open set by $O$. $O$ wins if the points chosen by $P$ converge to $x$.
\end{definition}

\begin{definition}
The one-point compactification of a space $X$ is $\oneptcomp{X}$, where neighborhoods of points in $X$ are the same as they were originally, and neighborhoods of $\infty$ are sets $\oneptcomp{X}\setminus K$ for compact $K$. If $X$ is discrete then neighborhoods of $\infty$ are cofinite sets containing $\infty$, and the game is equivalent to $O$ choosing finite ``forbidden'' sets and $P$ choosing points not forbidden by $O$.
\end{definition}

\begin{proposition}
$O\codewin \congame{\oneptcomp{\kappa}}{\infty}$ for all cardinals $\kappa$.
\end{proposition}

\begin{proof}
Use $F(N,p)=N\cup\{p\}$.
\end{proof}

\begin{proposition}
$O\prewin \congame{\oneptcomp{\omega}}{\infty}$.
\end{proposition}

\begin{proof}
Use $F(n)=n$.
\end{proof}

\begin{proposition}
$O\not\prewin \clusgame{\oneptcomp{\kappa}}{\infty}$ for $\kappa\geq\omega_1$.
\end{proposition}

\begin{proof}
Let $F(n)$ be $O$'s predetermined forbidding strategy, let $\alpha\in\kappa\setminus\bigcup_{n<\omega}F(n)$, and have $P$ counter with $\left<\alpha,\alpha,\dots\right>$.
\end{proof}

\begin{proposition}
$O\tactwin\congame{\oneptcomp{\omega}}{\infty}$.
\end{proposition}

\begin{proof}
Use $F(n)=n+1$.
\end{proof}

\begin{theorem}
If $\kappa$ is a regular uncountable cardinal, for every function $f:[\kappa]^{<\omega}\to[\kappa]^{<\omega}$ the set $C_f = \{\alpha < \kappa : S\in[\alpha]^{<\omega} \Rightarrow f(S)\in[\alpha]^{<\omega}\}$ is club.
\end{theorem}

\begin{proof}
First assume $\alpha_0<\alpha_1<\dots\in C_f$. It is easily seen that $\sup(\alpha_n)\in C_f$, showing $C_f$ is closed.

Now assume $\gamma_0\in C_f$. Let $\gamma_{n+1}>\gamma_n$ be the least ordinal such that if $S\in[\gamma_n+1]^{<\omega}$ then $f(S)\in[\gamma_{n+1}]^{<\omega}$. We claim $\gamma_\omega = \sup(\gamma_n)\in C_f$. Let $S\in[\gamma_\omega]^{<\omega}$. Then $S\in[\gamma_n+1]^{<\omega}$ for some $n$, and thus $f(S)\in[\gamma_{n+1}]^{<\omega}\subset[\gamma_\omega]^{<\omega}$. Therefore $C_f$ is unbounded.
\end{proof}

We may thus assume, for the purposes of countering a tactical or Markov strategy, that the strategy is \textbf{downward} on some regular uncountable cardinal.

\begin{theorem}
$O\not\ktactwin{k}\clusgame{\oneptcomp{\kappa}}{\infty}$ for $\kappa\geq\omega_1$.
\end{theorem}

\begin{proof}
Let $F:[\kappa]^{\leq k} \to [\kappa]^{<\omega}$ be a forbidding strategy by $O$ against $P$ which is downward on $\omega_1$. We define $n_i$ for $0\leq i < k$ to be a natural number such that \[ n_i \in \omega \setminus(F(n_0,\dots,n_{i-1}) \cup F(n_0,\dots,n_{i-1},\omega+i,\dots,\omega+k-1))\] and note that\[\left<n_0,n_1,\dots,n_{k-1},\omega,\omega+1,\dots,\omega+k-1,n_0,n_1,\dots,n_{k-1},\omega,\omega+1,\dots,\omega+k-1,\dots\right>\] counters $F$.
\end{proof}

\begin{theorem}
$O\markwin \clusgame{\oneptcomp{\omega_1}}{\infty}$.
\end{theorem}

\begin{proof}
For $\alpha<\omega_1$ let $A_{\alpha,n}$ be a sequence of finite sets such that $A_{\alpha,n}\subset A_{\alpha,n+1}$ and $\bigcup_{n<\omega}A_{\alpha,n}=\alpha+1$.

Give $O$ the Markov forbidding strategy $F(n,\alpha)=A_{\alpha,n}$. To observe that any legal play by $P$ against the strategy $F$ has infinite range, we observe that for any $\alpha_0<\dots<\alpha_{k-1}$, there is some round $n$ such that $\{\alpha_0,\dots,\alpha_{k-1}\}\subseteq \bigcup_{0\leq i < k}F(n,\alpha_i)$, and thus $P$ cannot legally play any of these ordinals until another ordinal is played.
\end{proof}

Peter J. Nyikos has shown the following:

\begin{theorem}
$O\not\markwin Con_{O,P}(\omega_1\cup\{\infty\},\infty)$.
\end{theorem}

which improves to:

\begin{theorem}
$O\not\kmarkwin{k}Clus_{O,P}(\kappa\cup\{\infty\},\infty)$ for $\kappa>\omega_1$.
\end{theorem}

\begin{proof}
Let $F:\omega \times [\kappa]^{\leq k} \to [\kappa]^{<\omega}$ be a forbidding strategy by $O$ against $P$ which is downward on $\omega_2$. We define $\alpha_i$ for $0\leq i < k$ to be a countable ordinal such that \[ \alpha_i \in \omega_1 \setminus\bigcup_{n<\omega}\left(F(n,\{\alpha_0,\dots,\alpha_{i-1}\}) \cup F(n,\{\alpha_0,\dots,\alpha_{i-1},\omega_1+i,\dots,\omega_1+k-1\})\right)\] and note that \[\left<\alpha_0,\alpha_1,\dots,\alpha_{k-1},\omega_1,\omega_1+1,\dots,\omega_1+k-1,\alpha_0,\alpha_1,\dots,\alpha_{k-1},\omega_1,\omega_1+1,\dots,\omega_1+k-1,\dots\right>\] counters $F$.
\end{proof}

\centerline{\bf $Con_{O,P}(X,x)$ for Sigma Product}

\begin{proposition}
$O\uparrow\congame{\sigmaprodr{\kappa}}{\vec{0}}$.
\end{proposition}

\begin{proof}
For $s\in\sigmaprodr{\kappa}$ let $C(s)=\{\alpha<\kappa:s(\alpha)\not=0\}$ denote the countable nonzero coordinates of $s$. Let $\Phi:[\kappa]^{\leq\omega}\times\omega\to[\kappa]^{<\omega}$ be such that $\Phi(C,n)\subseteq\Phi(C,n+1)$ and $\bigcup_{n<\omega}\Phi(C,n)=C$.

If $\tau$ is the usual topology on $\mathbb{R}$, let $\sigma_\alpha:(\sigmaprodr{\kappa})^{<\omega}\to\tau$ be such that
\[
U_\alpha(s_0,\dots,s_{n-1})=\left\{
\begin{array}{l}
(-\frac{1}{n},\frac{1}{n}) \text{ if } \alpha\in\bigcup_{i<n}\Phi(C(s_i),n) \\
\mathbb{R} \text{ otherwise}
\end{array}
\right.
\]

Finally, give $O$ the winning strategy $\sigma(s_0,\dots,s_{n-1})=\sigmaprodr{\kappa}\cap\prod_{\alpha<\kappa}U_\alpha(s_0,\dots,s_{n-1})$.
\end{proof}

\begin{theorem}
For all cardinals $\kappa\leq 2^\omega$, $O\codewin\congame{\sigmaprodr{\kappa}}{\vec{0}}$.
\end{theorem}

\begin{proof}
Note that $|\Sigma\mathbb{R}^\kappa| \leq 2^\omega = |\mathbb{R}|$. Define the following:

    \begin{itemize}
    \item Encode every $S \in (\Sigma\mathbb{R}^{\kappa})^{<\omega}$ as a real number $0<r(S)<1$. 
    \item Let $\gamma(U)$ be the function which, for basic open sets $U=\sigmaprodr{\kappa}\cap\prod_{\alpha<\kappa}U_\alpha$ where for all $\alpha<\kappa$ either $U_\alpha=\mathbb{R}$ or $(-\frac{1}{r},\frac{1}{r})$, returns $\lfloor r \rfloor$.
    \item Let $n(U)$ be the number of non-$\mathbb{R}$ components of a basic open set $U$.
    \item Let $\psi(U,s)=r^{-1}(\gamma(U))^\frown\left<y\right>$.
    \item For $s\in\sigmaprodr{\kappa}$ let $C(s)=\{\alpha<\kappa:s(\alpha)\not=0\}$ denote the countable nonzero coordinates of $s$.
    \item Let $\Phi:[\kappa]^{\leq\omega}\times\omega\to[\kappa]^{<\omega}$ be such that $\Phi(C,n)\subseteq\Phi(C,n+1)$ and $\bigcup_{n<\omega}\Phi(C,n)=C$.
    \item For each $\alpha<\kappa$, define the interval $\sigma_\alpha(U,s)$ about $0$ as follows:
        \begin{itemize}
        \item If $\alpha\leq n(U)$ or $\alpha\in\bigcup_{s\in\psi(U,s)}\Phi(C(s),n(U))$ then $\sigma_\alpha(U,s)=(-\frac{1}{n(U)+r(\psi(U,s))},-\frac{1}{n(U)+r(\psi(U,s))})$.
        \item Otherwise, $\sigma_\alpha(U,s)=\mathbb{R}$.
        \end{itemize}
    \end{itemize}

It follows that $\sigma(U,s)=\sigmaprodr{\kappa}\cap\prod_{\alpha<\kappa} \sigma_\alpha(U,s)$ is a winning coding strategy.
\end{proof}

\begin{theorem}
Let $\kappa$ be a cardinal such that there exists a function $f:\kappa\to[\kappa]^{\leq \omega}$ where for every $W\in[\kappa]^{\leq\omega}$ there exists $\alpha_W<\kappa$ with $W\subseteq f(\alpha_W)$. (That is, $\textrm{cf}([\kappa]^{\leq\omega})=\kappa$.) Then $F \codewin PF_{F,C}(\kappa)$ and $O \codewin \congame{\sigmaprodr{\kappa}}{\vec{0}}$.
\end{theorem}

\begin{proof}
Let $W\restriction n \in [\kappa]^n$ be a subset of $W\in[\kappa]^\omega$ such that $W\restriction n \subset W \restriction (n+1)$ and $\bigcup_{n<\omega} W\restriction n = W$.

Define \[\sigma(N,W) = N \cup (|N|+1) \cup \{\alpha_W\} \cup \bigcup_{\alpha \in N} f(\alpha) \restriction |N|\]

Consider the play $\left<\emptyset,W_0,N_1,W_1,N_2,W_2,\dots\right>$ with $F$ following the strategy $\sigma$. Let $\gamma \in W_i$, and note $\gamma \in f(\alpha_{W_i})$ (and $\gamma \in f(\alpha_{W_i})\restriction |N_n|$ for sufficiently large $n$). \[N_{i+1} = \sigma(N_i,W_i) \supseteq \{\alpha_{W_i}\}\] and thus \[N_{n+1} = \sigma(N_n,W_n) \supseteq \bigcup_{\alpha \in N_n} f(\alpha) \restriction |N_n| \supseteq \bigcup_{\alpha \in N_{i+1}} f(\alpha) \restriction |N_n| \supseteq f(\alpha_{W_i}) \restriction |N_n|\] showing $\gamma \in N_{n+1}$. Since $\gamma$ is forbidden in round $n+1$, $\gamma$ appears in finitely many sets chosen by $C$.

We turn our attention to $Con_{O,P}(\Sigma\mathbb{R}^\kappa)$. We define the winning strategy $\tau(U,p)$ for $O$ as follows: let $N(U)$ be the non-$\mathbb{R}$ coordinates in the basic open set $U$ and $W(p)$ be the non-$0$ coordinates in $p$. Then $\tau(U,p) = \left(\prod_{\alpha<\kappa} U_\alpha\right) \cap \Sigma\mathbb{R}^\kappa$ where if $\alpha \in \sigma(N(U),W(p))$ then $U_\alpha = (-\frac{1}{|N(U)|},\frac{1}{|N(U)|})$ and $U_\alpha=\mathbb{R}$ otherwise.

Consider the play $\left<\emptyset,p_0,U_1,p_1,U_2,p_2,\dots\right>$ with $O$ following the strategy $\tau$. Observe that $N(\tau(U,p))=\sigma(N(U),W(p))$. Thus $p_i(\gamma)\not=0$ is equivalent to $\gamma \in W(p_i)$, and by the above argument, for sufficiently large $n$, $\gamma \in \sigma(N(U_n),W(p_n))$. Therefore from round $n$ onward the $\gamma$-coordinates of points chosen by $P$ must lay in $(-\frac{1}{|N(U)|},\frac{1}{|N(U)|})$ and converge to $0$.
\end{proof}

\begin{theorem}
Let $\kappa$ be the limit of cardinals $\kappa_n$ such that $\textrm{cf}([\kappa_n]^{\leq\omega},\subseteq)=\kappa_n$. Then $F \codewin PF_{F,C}(\kappa)$ and $O \codewin \congame{\sigmaprodr{\kappa}}{\vec{0}}$.
\end{theorem}

\begin{proof}
Let $f_n:\kappa_n\to[\kappa_n]^{\leq\omega}$ be such that for every $W\in[\kappa_n]^{\leq\omega}$ there exists $\alpha_{W,n}<\kappa_n$ such that $f_n(\alpha_{W,n})\supseteq W$.

Define \[\sigma(N,W)=N\cup(|N|+1)\cup\{\alpha_{W\cap \kappa_{|N|},|N|}\}\cup\bigcup_{n\leq|N|}\bigcup_{\alpha\in N} f_n(\alpha)\restriction |N|\] We claim that $\sigma$ is a winning coding strategy.

Consider the play $\left<N_0,W_0,N_1,W_1,\dots\right>$ where $O$ follows the strategy $\sigma$. For $\sigma$ to be a winning strategy for $F \codewin PF_{F,C}(\kappa)$, it must follow that for each $\gamma\in\bigcup_{i<\omega}W_i$, $\gamma$ is forbidden by some $\sigma(N_j,W_j)$.

Let $\gamma\in W_i\cap \kappa_{|N_i|}$. For all $j>i$, $\alpha_{W\cap\kappa_{N_i},|N_i|}\in N_j$. Also, $\gamma \in f_{N_i}(\alpha_{W\cap\kappa_{N_i},|N_i|})\restriction|N_j|$ for some sufficiently large $j$. So we observe that $\gamma \in \bigcup_{n\leq|N_j|}\bigcup_{\alpha\in N_j} f_n(\alpha)\restriction |N_j|\subseteq \sigma(N_j,W_j)$.

We turn our attention to $\congame{\sigmaprodr{\kappa}}{\vec{0}}$. We define the winning strategy $\tau(U,p)$ for $O$ as follows: let $N(U)$ be the non-$\mathbb{R}$ coordinates in the basic open set $U$ and $W(p)$ be the non-$0$ coordinates in $p$. Then $\tau(U,p) =\Sigma\mathbb{R}^\kappa \cap \prod_{\alpha<\kappa} U_\alpha$ where if $\alpha \in \sigma(N(U),W(p))$ then $U_\alpha = (-\frac{1}{|N(U)|},\frac{1}{|N(U)|})$ and $U_\alpha=\mathbb{R}$ otherwise.

Consider the play $\left<\sigmaprodr{\kappa},p_0,U_1,p_1,U_2,p_2,\dots\right>$ with $O$ following the strategy $\tau$. Observe that $N(\tau(U,p))=\sigma(N(U),W(p))$. Thus $p_i(\gamma)\not=0$ is equivalent to $\gamma \in W(p_i)$, and by the above argument, for sufficiently large $n$, $\gamma \in \sigma(N(U_n),W(p_n))$. Therefore from round $n$ onward the $\gamma$-coordinates of points chosen by $P$ must lay in $(-\frac{1}{|N(U)|},\frac{1}{|N(U)|})$ and converge to $0$.
\end{proof}

\begin{theorem}
$F\codewin\pfgame{\kappa}$ for all cardinals $\kappa$.
\end{theorem}

\begin{proof}
Let $\kappa$ be the limit of cardinals $\kappa_n$ such that $F\codewin\pfgame{\kappa_n}$ using the strategy $\sigma_n(N,W)$ such that for $M\subseteq N$, $\sigma_n(M,W)\subseteq\sigma_n(N,W)$. Define \[\sigma(N,W)=(|N|+1)\cup\bigcup_{n<|N|}\sigma_n(N\cap\kappa_n,W\cap\kappa_n)\]

Let $\left<N_0,W_0,N_1,W_1,\dots\right>$ be a legal play of the game with $N_{i+1}=\sigma(N_i,W_i)$. Suppose $\gamma\in W_i$ for infinitely-many $i$. $\gamma\in\kappa_n$ for some $n$, so observe the play $\left<M_0,W_0\cap\kappa_n,M_1,W_1\cap\kappa_n,\dots\right>$ with $M_0=N_0\cap\kappa_n$ and $M_{i+1}=\sigma_n(M_i,W_i\cap\kappa_n)\subseteq\sigma_n(N_i\cap\kappa_n,W_i\cap\kappa_n)$ which is $\subseteq\sigma(N_i,W_i)=N_{i+1}$ for sufficiently large $i$.

Since $\sigma_n$ is a winning strategy, $\gamma\in M_{m+1}\subseteq N_{m+1}$ for sufficiently large $i$, making $\left<N_0,W_0,N_1,W_1,\dots\right>$ illegal, contradiction.

Now suppose $F\codewin\pfgame{\kappa}$. For each $\alpha<\kappa^+$, let $\sigma_\alpha(N,W)$ be a winning coding strategy for $\pfgame{\alpha}$ such that for $M\subseteq N$, $\sigma_\alpha(M,W)\subseteq\sigma_\alpha(N,W)$. We define the following strategy for $F$ in $\pfgame{\kappa^+}$: \[\sigma(N,W)=N\cup\bigcup_{\alpha\in N}\sigma_{\alpha+1}(N\cap(\alpha+1),W\cap(\alpha+1))\]

Let $\left<N_0,W_0,N_1,W_1,\dots\right>$ be a legal play of the game with $N_{i+1}=\sigma(N_i,W_i)$. Suppose $\gamma\in W_i$ for infinitely-many $i$. Observe the play $\left<M_0,W_0\cap(\gamma+1),M_1,W_1\cap(\gamma+1),\dots\right>$ with $M_0=N_0\cap(\gamma+1)$ and $M_{i+1}=\sigma_{\gamma+1}(M_i,W_i\cap(\gamma+1))\subseteq\sigma_{\gamma+1}(N_i\cap(\gamma+1),W_i\cap(\gamma+1))$.

Since $\sigma_{\gamma+1}$ is a winning strategy, $\gamma\in M_{m+1}\subseteq\sigma_{\gamma+1}(N_i\cap(\gamma+1),W_i\cap(\gamma+1))\subseteq\sigma(N_i,W_i)=N_{i+1}$ for some sufficiently large $m$, making $\left<N_0,W_0,N_1,W_1,\dots\right>$ illegal, contradiction.
\end{proof}

\begin{corollary}
$O\codewin\congame{\sigmaprodr{\kappa}}{\vec{0}}$ for all cardinals $\kappa$.
\end{corollary}

\begin{proof}
Let $\tau(N,W)$ be the winning coding strategy for $F$ in $\pfgame{\kappa}$, $N(U)\in[\kappa]^{<\omega}$ represent the non-$\mathbb{R}$ coordinates of a basic open set $U$ of $\sigmaprodr{\kappa}$, and $W(p)\in[\kappa]^{\leq\omega}$ represent the non-$0$ coordinates of a point $p$ in $\sigmaprodr{\kappa}$. For each $\alpha<\kappa$, let \[\sigma_\alpha(U,p)=\left\{\begin{array}{ll}(-\frac{1}{|N(U)|},\frac{1}{|N(U)|})&\text{if }\alpha\in\tau(N(U),W(p))\\\mathbb{R}&\text{otherwise}\end{array}\right.\] and $\sigma(U,p)=\sigmaprodr{\kappa}\cap\prod_{\alpha<\kappa}\sigma_\alpha(U,p)$.
\end{proof}

\end{document}

### 2013-01-24 seminar_talk_october_2011.tex
Initial commit

--- 2013-01-24 old_phd_research_results_april_2012.tex
@@
       \newtheorem{question}[theorem]{Question}
-      \newtheorem{example}[theorem]{Example}
 
@@
 \newcommand{\ktactwin}[1]{\uparrow_{#1\text{-tact}}}
-\newcommand{\kmarkwin}[1]{\uparrow_{#1\text{-mark}}}
 \newcommand{\codewin}{\uparrow_{\text{code}}}
-\newcommand{\limitwin}{\uparrow_{\text{limit}}}
 
@@
 
-\centerline{\bf PhD Research Results}
+\centerline{\bf Topology Seminar Talk - Late October / Early Novemeber 2011}
 \centerline{Steven Clontz}
@@
 (Open question: does $P \tactwin G_{K,P}(X)$?)
-
-\begin{theorem}
-$P \not\tactwin D_{K,P}(M)$ where $M$ is the metric fan space.
-\end{theorem}
-
-\begin{proof}
-Give $P$ the tactic $\sigma$.
-Suppose that for all $n<\omega$, there is an upper bound $m<\omega$ so that for each $C \in K[M]$, if $\pi_1(\sigma(C))=n$, then $\pi_2(\sigma(C))<m$.
-We may then define $f(n)=m$, and let $C_f=\{(x,y):f(x)<y\}\in K[M]$.
-$\sigma(C_f)$ must show a contradiction if $\sigma$ is legal.
-
-So it follows that there is some $n<\omega$ such that there are compact sets $C_i\in K[M]$ with $\pi_1(\sigma(C_i))=n$ and $\pi_2(\sigma(C_i))<\pi_2(\sigma(C_{i+1}))$.
-The play $\left<C_0,\sigma(C_0),C_1,\sigma(C_1),\dots\right>$ is a counter to $\sigma$.
-\end{proof}
 
@@
 
-It then follows that the closure of $\mathcal{P}$ under finite unions and subsets, along with all finite sets, is an ideal.
+It then follows that the closure of $\mathcal{P}$ under finite unions and subsets is an ideal.
 Its dual filter may then be extended to an ultrafilter $\mathcal{F}$ such that every possible play by $P$ is the complement of some member of $\mathcal{F}$.
@@
 
-\centerline{\bf Another game: $Con_{O,P}(X,x)$}
+\centerline{\bf Another game: $G_{O,P}(X,x)$}
 
 \begin{definition} 
-Gruenhage's open-point convergence game $Con_{O,P}(X,x)$ has $O$ choosing nested open sets and $P$ choosing a point within the last chosen open set by $O$.
+Gruenhage's open-point convergence game $G_{O,P}(X,x)$ has $O$ choosing nested open sets and $P$ choosing a point within the last chosen open set by $O$.
 $O$ wins if the points chosen by $P$ converge to $x$.
@@
 \begin{proposition}
-$O\not\prewin Con_{O,P}(\kappa\cup\{\infty\},\infty)$, where $\kappa\cup\{\infty\}$ is the one-point compactification of discrete $\kappa\geq\omega_1$.
+$O\not\prewin G_{O,P}(\omega_1\cup\{\infty\},\infty)$, where $\omega_1\cup\{\infty\}$ is the one-point compactification of discrete $\omega_1$.
 \end{proposition}
@@
 \begin{proof}
-Given a predetermined strategy $\sigma(n)$ for $O$, $P$ simply chooses any ordinal in $\bigcap_{n<\omega} \sigma(n)$ to play on every turn.
+Given a predetermined strategy $\sigma(n)$ for $O$, $P$ simply chooses any ordinal in $\bigcup_n \sigma(n)$ to play on every turn.
 \end{proof}
@@
 \begin{proposition}
-$O\codewin Con_{O,P}(\kappa\cup\{\infty\},\infty)$ for any cardinal $\kappa$. 
+$O\codewin G_{O,P}(\omega_1\cup\{\infty\},\infty)$. 
 \end{proposition}
@@
 
-\begin{proposition}
-$O\not\tactwin Con_{O,P}(\kappa\cup\{\infty\},\infty)$ for $\kappa\geq\omega_1$.
-\end{proposition}
+\begin{theorem}
+$O\not\tactwin G_{O,P}(\omega_1\cup\{\infty\},\infty)$.
+\end{theorem}
 
 \begin{proof}
-Let $F(\alpha)$ be the complement of a tactical strategy for $O$.
-There exists some $n<\omega$ such that we may find an infinite $B\subseteq \omega_1$ with $n\not\in F(\beta)$ for $\beta\in B$ - if not, we may find uncountable ordinals $\alpha$ such that $\omega \subseteq F(\alpha)$, a contradiction.
-Choose $\beta\in B\setminus F(n)$, and note that repeating $n,\beta$ is a successful counter to $O$'s strategy.
+Let $\sigma(\alpha)$ be a tactical strategy for $O$ and $F(\alpha)=\omega_1\setminus\sigma(\alpha)$.
+Suppose by way of contradiction that for all $\alpha_0,\alpha_1<\omega_1$, if $\alpha_1 \not\in F(\alpha_0)$ then it follows that $\alpha_0\in F(\alpha_1)$.
+Then for all $\alpha<\omega_1$, $\alpha\in F(\beta)$ for all $\beta\not\in F(\alpha)$.
+
+So $0\in F(\beta)$ for all $\beta\not\in F(0)$, $1\in F(\beta)$ for all $\beta \not\in F(1)$, and so on.
+Then $0,1,2,\dots\in F(\beta)$ for all $\beta\not\in\bigcup_n F(n)\not=\omega_1$, contradiction.
+
+Thus there exist a pair $\alpha_0,\alpha_1$ such that $\alpha_1\not\in F(\alpha_0)$ and $\alpha_0\not\in F(\alpha_1)$. $P$ beats $\sigma$ by playing this pair repeatedly.
 \end{proof}
@@
 \begin{theorem}
-$O\not\ktactwin{k}Con_{O,P}(\kappa\cup\{\infty\},\infty)$ for $\kappa\geq\omega_1$.
+$O\not\ktactwin{k}G_{O,P}(\omega_1\cup\{\infty\},\infty)$.
 \end{theorem}
@@
 \begin{proof}
-Let $\sigma:[\omega_1]^{\leq k}\to[\omega_1]^{<\omega}$ be a $k$-tactical strategy for $O$ restricted to $\omega_1$ and $F(S)=\omega_1\setminus\sigma(S)$.
+Let $\sigma:[\omega_1]^{\leq k}\to[\omega_1]^{<\omega}$ be a $k$-tactical strategy for $O$ and $F(S)=\omega_1\setminus\sigma(S)$.
 
@@
 
-Peter J. Nyikos has shown the following:
+Dr. Gruenhage tells me Peter J. Nyikos has shown the following:
 
 \begin{theorem}
-$O\not\markwin Con_{O,P}(\omega_1\cup\{\infty\},\infty)$.
+$O\not\markwin G_{O,P}(\omega_1\cup\{\infty\},\infty)$.
 \end{theorem}
 
-This can be improved:
+It is natural to ask:
 
-\begin{theorem}
-$O\not\kmarkwin{k} Con_{O,P}(\kappa\cup\{\infty\},\infty)$ for $\kappa\geq\omega_1$.
-\end{theorem}
-
-\begin{proof}
-Let $F:[\omega_1]^{\leq k}\times\omega\to[\omega_1]^{<\omega}$ be the complement of a $k$-Markov strategy for $O$ restricted to $\omega_1$.
-
-Let $W_0=\omega_1$. We define $W_\alpha$ recursively as follows:
-    \begin{itemize}
-    \item For successor ordinals $\alpha+1$, let $\beta$ be the least element of $W_\alpha$ such that \[(\beta,\omega_1) \cap \bigcup_{S\in [\beta]^{\leq k}, n<\omega} F(S,n)\] is nonempty.
-If no such $\beta$ exists, let $W_{\alpha+1}=W_\alpha$ and otherwise let \[W_{\alpha+1}=W_\alpha \setminus \left((\beta,\omega_1) \cap \bigcup_{S\in[\beta]^{\leq k}, n<\omega} F(S,n)\right)\]
-    \item For limit ordinals $\alpha$, let $W_\alpha = \bigcap_{\beta<\alpha} W_\beta$.
-    \end{itemize}
-
-Finally let $W=\bigcap_{\alpha<\omega_1}W_\alpha$ and observe that it is unbounded.
-Let $R$ collect all ordinals $\alpha\in W$ such that there is an ordinal $\beta_\alpha$ and number $n_\alpha<\omega$ where for all $S\in[W\cap(\beta_\alpha,\omega_1)]^{\leq k}$, $\alpha \in F(S,n_\alpha)$.
-
-If $R$ was infinite, then there is $\alpha_i\in R$ for each $i<\omega$ and some $N<\omega$ where for all $S\in[W\cap(\beta_{\alpha_i},\omega_1)]^{\leq k}$, $\alpha_i \in F(S,N)$, and thus for all $S\in[W\cap(\sup \beta_{\alpha_i},\omega_1)]^{\leq k}$,  $\{\alpha_i : i<\omega\} \subset F(S,N)$, a contradiction.
-So let $0^*$ be the least element of $W\setminus R$.
-
-Now, define a strictly increasing sequence of ordinals $\left<\alpha_1,\alpha_2,\alpha_3,\alpha_4,\dots\right>$ such that $\alpha_i \in W$ and $0^* \not\in F(\{\alpha_{2i+1},\dots,\alpha_{2i+k}\})$ for all $i$.
-The play $\left<0^*,\alpha_1,\dots,\alpha_k,0^*,\alpha_{k+1},\dots,\alpha_{2k},0^*,\dots\right>$ then defeats the Markov strategy.
-\end{proof}
-
-While these counters prevent convergence to $\infty$, they do not prohibit clustering, as any sequence of points with infinite range clusters at $\infty$ in this space.
-
-\begin{definition} 
-The open-point clustering game $Clus_{O,P}(X,x)$ has $O$ choosing nested open sets and $P$ choosing a point within the last chosen open set by $O$. $O$ wins if the points chosen by $P$ cluster to $x$.
-\end{definition}
-
-Any strategy which forces convergence also forces clustering, so a coding strategy exists for player $O$. And since the counter used above to foil any tactical strategy had only finite range...
-
-\begin{proposition}
-$O\not\tactwin Clus_{O,P}(X,\infty)$.
-\end{proposition}
-
-The other counters only attempt to repeat a point infinitely often, and may have infinite range.
-
-\begin{example}
-For $\omega\leq\alpha<\omega_1$ let $\leq_{\alpha}$ be a well-ordering of $\omega_1$ such that its restriction to $\alpha$ is isomorphic to $\omega$ with isomorphism $f(n):\omega\to\alpha$.
-For $n<\omega$ let $\leq_n$ simply be $\leq$ and $f$ be the identity.
-
-The 2-tactical strategy for $O$ in $Clus_{O,P}(\omega_1\cup\{\infty\}),\infty)$ whose complement is, for $\alpha<\beta$, $F(\alpha,\beta)=\{\gamma : \gamma \leq_\beta \alpha \} \cup \{\beta\}$, forces the point-picker to chose more than three distinct points.
-\end{example}
-
-\begin{proof}
-Suppose Player $P$ started with $\alpha_0<\alpha_1$.
-Player $O$ forbids \[F(\alpha_0,\alpha_1) = \{\gamma : \gamma \leq_{\alpha_1}\alpha_0\} \cup \{\alpha_1\}\] so Player $P$ must respond with $\alpha_2$ such that either $\alpha_0<\alpha_1<\alpha_2$ or $\alpha_0<_{\alpha_1}\alpha_2<\alpha_1$.
-
-In the first case that $\alpha_0<\alpha_1<\alpha_2$, Player $O$ now forbids \[F(\alpha_1,\alpha_2) = \{\gamma : \gamma \leq_{\alpha_2}\alpha_1\} \cup \{\alpha_2\}\] If $\alpha_0<_{\alpha_2}\alpha_1$ we're done.
-Otherwise, Player $P$ chooses $\alpha_0>_{\alpha_2}\alpha_1$ again, and Player $O$ responds with \[F(\alpha_0,\alpha_2)=\{\gamma : \gamma \leq_{\alpha_2} \alpha_0 \} \cup \{\alpha_2\}\] which successfully forbids $\alpha_1$.
-
-In the second case that $\alpha_0<_{\alpha_1}\alpha_2<\alpha_1$, Player $O$ forbids \[F(\alpha_1,\alpha_2) = \{\gamma : \gamma \leq_{\alpha_1}\alpha_2\} \cup \{\alpha_1\}\] which successfully forbids $\alpha_0$.
-
-Thus, a fourth ordinal must be selected.
-\end{proof}
-
-But the fourth ordinal is all that is needed.
-
-\begin{theorem}
-$O\not\ktactwin{2}Clus_{O,P}(\omega_1\cup\{\infty\},\infty)$.
-\end{theorem}
-
-\begin{proof}
-Let $F(\alpha,\beta)$ be the complement of a k-tactical strategy for O, and assume without loss of generality that it does not forbid any ordinals larger than its inputs.
-
-Let $n_0=\min(\omega\setminus F(\emptyset)\setminus F(\omega,\omega+1))$ and $n_1 = \min(\omega\setminus F(n_0)\setminus F(n_0,\omega+1))$.
-
-It follows that $\left<n_0,n_1,\omega,\omega+1,n_0,n_1,\omega,\omega+1,\dots\right>$ is a legal counter.
-\end{proof}
-
-But, in fact, a similar counter can be used for any $k$-tactical strategy.
-
-\begin{theorem}
-$O\not\ktactwin{k}Clus_{O,P}(\omega_1\cup\{\infty\},\infty)$.
-\end{theorem}
-
-\begin{proof}
-Let $F(\alpha_0,\dots,\alpha_{k-1})$ be the complement of a k-tactical strategy for O, and assume without loss of generality that it does not forbid any ordinals larger than its inputs.
-
-For $0\leq i < k$, we define \[n_i = \min(\omega\setminus F(n_0,\dots,n_{i-1},\omega+i,\dots,\omega+k-1)\setminus F(n_0,\dots,n_{i-1}))\]
-
-It follows that $\left<n_0,\dots,n_{k-1},\omega,\dots,\omega+k-1,n_0,\dots,n_{k-1},\omega,\dots,\omega+k-1,\dots\right>$ is a legal counter.
-\end{proof}
-
-However, a Markov strategy is sufficient to defeat $P$ in the clustering game for $\omega_1$.
-
-\begin{theorem}
-$O\markwin Clus_{O,P}(\omega_1\cup\{\infty\},\infty)$.
-\end{theorem}
-
-\begin{proof}
-For $\omega\leq\alpha<\omega_1$ let $\leq_{\alpha}$ be a well-ordering of $\omega_1$ such that its restriction to $\alpha$ is isomorphic to $\omega$ with isomorphism $f(n):\omega\to\alpha$.
-For $n<\omega$ let $\leq_n$ simply be $\leq$ and $f$ be the identity.
-
-Let $F(\alpha,n)=\{\gamma : \gamma \leq_\alpha f(n)\}$ be the complement of $O$'s Markov strategy in response to move $\alpha$ in round $n$.
-
-If a legal counter by $P$ does not repeat some largest ordinal infinitely often, it does not result in a win for $P$.
-Otherwise let $\beta$ be largest ordinal repeated infinitely often in some legal counter by $P$.
-We note that the forbidden sets responded by $O$ are of the form $F(\beta,n)$ where $n$ increases as the game progresses.
-It is impossible to repeat any ordinal less than $\beta$ infinitely often due to the increasing round number, so the range of the counter is infinite, and does not result in a win for $P$.
-\end{proof}
-
-...while it similarly fails for $\kappa>\omega_1$.
-
-\begin{theorem}
-$O\not\kmarkwin{k}Clus_{O,P}(\kappa\cup\{\infty\},\infty)$ for $\kappa>\omega_1$.
-\end{theorem}
-
-\begin{proof}
-Let $F:\omega\times[\kappa]^{\leq k} \to [\kappa]^\omega$ be the complement of a k-Markov strategy for O, and assume without loss of generality that it does not forbid any ordinals larger than its inputs.
-
-For $0\leq i < k$, we define \[\beta_i = \min(\omega\setminus \bigcup_{n<\omega} F(n,\{\beta_0,\dots,\beta_{i-1},\omega_1+i,\dots,\omega_1+k-1\})\setminus\bigcup_{n<\omega} F(n,\{\beta_0,\dots,\beta_{i-1}\}))\]
-
-It follows that $\left<\beta_0,\dots,\beta_{k-1},\omega_1,\dots,\omega_1+k-1,\beta_0,\dots,\beta_{k-1},\omega_1,\dots,\omega_1+k-1,\dots\right>$ is a legal counter.
-\end{proof}
-
-\centerline{\bf $Con_{O,P}(X,x)$ for Sigma Product}
-
-\begin{proposition}
-The player $O$ has a winning strategy for $Con_{O,P}(X,x)$ where \[X=\Sigma\mathbb{R}^{\omega_1}=\{x\in \mathbb{R}^{\omega_1}: x_\alpha = 0 \text{ for all but countably many } \alpha<\omega_1\}\]
-\end{proposition}
-
-\begin{proof}
-Without loss of generality we may assume that $x$ is the zero function.
-Let $y_n$ be the move by $P$ on turn $n$.
-For each $y_n$, let $l_n\in \omega_1^{\omega}$ enumerate the nonzero coordinates in $y_n$.
-Give $O$ the strategy $\sigma(y_0,\dots,y_{n-1}) = \prod_{\alpha<\omega_1} O_\alpha$ where if $\alpha$ is listed in the first $n$ coordinates of any term in $\left<l_k\right>_{k<n}$, then $O_\alpha=(-2^{-n},2^{-n})$, and $O_\alpha=\mathbb{R}$ otherwise.
-\end{proof}
-
-\begin{theorem}
-For all cardinals $\kappa\leq 2^\omega$, the player $O$ has a winning coding strategy for $Con_{O,P}(X,x)$ where \[X=\Sigma\mathbb{R}^{\kappa}=\{x\in \mathbb{R}^{\kappa}: x_\alpha = 0 \text{ for all but countably many } \alpha<\kappa\}\]
-\end{theorem}
-
-\begin{proof}
-Note that $|\Sigma\mathbb{R}^\kappa| \leq 2^\omega = |\mathbb{R}|$. Define the following:
-
-    \begin{itemize}
-    \item Encode every finite sequence $s$ of functions in $\Sigma\mathbb{R}^{\kappa}$ as a real number $0<r(s)<1$. 
-    \item Let $\gamma(U)$ be the function which, for basic open sets $U=\prod_{\alpha<\kappa}U_\alpha$ where $U_0=(-\frac{1}{R},\frac{1}{R})$ for some positive noninteger real number $R$, returns the sequence $r^{-1}(R-\lfloor R\rfloor)$.
-    \item Let $n(U)$ be the length of $\epsilon^{-1}(\gamma(U))$.
-    \item Let $\psi(U,y)=\epsilon^{-1}(\gamma(U))^\frown\left<y\right>$.
-    \item Define $\sigma_0(U,y)$ to be $\left(-\frac{1}{n(U)+r(\psi(U,y))},\frac{1}{n(U)+r(\psi(U,y))}\right)$.
-    \item For each $0<\alpha<\kappa$, define the interval $\sigma_\alpha(U,y)$ about $0$ as follows:
-        \begin{itemize}
-        \item If $\alpha$ is listed in the first $n(U)$ coordinates of any term in the finite sequence $\psi(U,y)$, then $\sigma_\alpha(U,y)=(-\frac{1}{n(U)+1},\frac{1}{n(U)+1})$.
-        \item Otherwise, then $\sigma_\alpha(U,y)=\mathbb{R}$.
-        \end{itemize}
-    \end{itemize}
-
-It follows that $\sigma(U,y)=\prod_{\alpha<\kappa} \sigma_\alpha(U,y)$ is a winning coding strategy.
-\end{proof}
-
-\begin{theorem}
-For all cardinals $\kappa>2^\omega$ such that $\kappa^\omega = \kappa$, the player $O$ has a winning coding strategy for $Con_{O,P}(X,x)$ where \[X=\Sigma\mathbb{R}^{\kappa}=\{x\in \mathbb{R}^{\kappa}: x_\alpha = 0 \text{ for all but countably many } \alpha<\omega_1\}\]
-\end{theorem}
-
-\begin{proof}
-Note that $|\Sigma\mathbb{R}^\kappa| = \kappa^\omega = \kappa$. Define the following:
-
-    \begin{itemize}
-    \item Encode every finite sequence $s$ of functions in $\Sigma\mathbb{R}^{\kappa}$ as an ordinal $\epsilon(s)<\kappa$. 
-    \item Let $\gamma(U)$ be the function which, for basic open sets $U=\prod_{\alpha<\kappa}U_\alpha$ with a unique factor $U_{\alpha^*}$, returns $\alpha^*$.
-    \item Let $n(U)$ be the length of $\epsilon^{-1}(\gamma(U))$.
-    \item Let $\psi(U,y)=\epsilon^{-1}(\gamma(U))^\frown\left<y\right>$.
-    \item For each $\alpha<\kappa$, define the interval $\sigma_\alpha(U,y)$ about $0$ as follows:
-        \begin{itemize}
-        \item If $\alpha$ is listed in the first $n(U)$ coordinates of any term in the finite sequence $\psi(U,y)$ and is not equal to $\epsilon(\psi(U,y))$, then $\sigma_\alpha(U,y)=(-\frac{1}{n(U)+1},\frac{1}{n(U)+1})$.
-        \item If $\alpha=\epsilon(\psi(U,y))$, then $\sigma_\alpha(U,y)=(-\frac{1}{n(U)+2},\frac{1}{n(U)+2})$.
-        \item Otherwise, then $\sigma_\alpha(U,y)=\mathbb{R}$.
-        \end{itemize}
-    \end{itemize}
-
-It follows that $\sigma(U,y)=\prod_{\alpha<\kappa} \sigma_\alpha(U,y)$ is a winning coding strategy.
-\end{proof}
-
-% NOPE
-%\begin{theorem}
-%For all cardinals $\kappa$ such that $2^\omega< \kappa < \kappa^\omega$, the player $O\not\codewin Cl_{O,P}(X,x)$ where \[X=\Sigma\mathbb{R}^{\kappa}=\{x\in% \mathbb{R}^{\kappa}: x_\alpha = 0 \text{ for all but countably many } \alpha<\omega_1\}\]
-%\end{theorem}
-%
-%\begin{proof}We begin by noting that $|\tau|=\kappa<\kappa^\omega$, where $\tau$ is the topology of $\Sigma \mathbb{R}^\kappa$.
-%
-%Suppose that for all $S\subseteq \Sigma\mathbb{R}^\kappa$ such that $\sigma(U,x)=\sigma(V,y)$ for all $x,y\in\Sigma \mathbb{R}^\kappa$ and $U,V\in\tau$, it follows that $|S|<\kappa^\omega$.
-Then \[\left|\bigcup_{V\in\tau}\sigma^{-1}(V)\right|=\max(\{\lambda : \lambda=|\tau| \,\vee\, \exists V\in\tau(\lambda=|\sigma^{-1}(V)|)\}) < \kappa^\omega \] while $\bigcup_{V\in\tau}\sigma^{-1}(V)=\tau\times \Sigma\mathbb{R}^\kappa$, a contradiction.
-%
-%It follows that we may find $S\subseteq \Sigma\mathbb{R}^\kappa$ with $|S|=\kappa^\omega$ such that $\sigma(U,x)=\sigma(V,y)$ for all $x,y\in\Sigma \mathbb{R}^\kappa$ and $U,V\in\tau$.
-%
-%If $P$ only plays sequences in $S$, then $O$ plays the same set in every round following the initial round.
-As such, $O$ only places restrictions on $\omega$-many coordinates of the sequences chosen by $P$ throughout the game.
-Call these restricted coordinates $R\subseteq \kappa$.
-If $x(\alpha)=0$ for all $x\in S$ and $\alpha\not\in R$, then it would follow that $|S|=|\mathbb{R}|^{|R|}=2^\omega<\kappa^\omega$, a contradiction.
-%
-%So, choose $x\in S$ such that $x(\alpha)\not=0$ for some $\alpha\not\in R$. The play \[\left<U_0,x,U_1=\sigma(U_0,x),x,U_2=\sigma(U_1,x)=U_1,x,U_1,x,\dots\right>\] is a counter to $\sigma$.
-%\end{proof}
-
-\centerline{\bf Finite Countable Game}
-
-\begin{theorem}
-Let $\kappa$ be a cardinal such that there exists a function $f:\kappa\to[\kappa]^{\leq \omega}$ where for every $W\in[\kappa]^{\leq\omega}$ there exists $\alpha_W<\kappa$ with $W\subseteq f(\alpha_W)$.
-Then $F \codewin PF_{F,C}(\kappa)$ and $O \codewin Con_{O,P}(\Sigma\mathbb{R}^\kappa)$.
-\end{theorem}
-
-\begin{proof}
-Long version.
-
-We begin by defining a few helpful tools. Assume $N\in[\kappa]^{<\omega}$ and $W \in [\kappa]^{\leq\omega}$.
-    \begin{itemize}
-    \item Let $N^* = N \setminus \{\max(N)\}$.
-    \item Noting that $\kappa\setminus \alpha$ is order-isomorphic to $\kappa$ for all $\alpha<\kappa$, let $\gamma_N<\kappa$ be the ordinal mapping to $\max(N)$ in $\kappa\setminus(\max(N^*)+1)$ by the appropriate order isomorphism.
-    \item Let $s: [\kappa]^{<\omega} \to \kappa$ be a bijection.
-    \item Define $W\restriction n \in [\kappa]^{<\omega}$ so that $W\restriction n \subseteq W\restriction (n+1)$ and $\bigcup_{n<\omega}W\restriction n = W$.
-    \item Let $t_N=\max(N\cap\omega)+2$.
-    \end{itemize}
-
-Let the (non-winning) coding strategy $\sigma'$ be defined as follows: \[\sigma'(N,W)=\bigcup_{\alpha \in s^{-1}(\gamma_N)} f(\alpha) \restriction t_N\]
-
-Let $\left<N_0,N_1,\dots\right>$ be a play by $F$ following the considered strategy in response to the play $\left<W_0,W_1,\dots\right>$ by $C$ in the game $PF_{F,C}(\kappa)$.
-(For technical reasons, assume $N_0$ contains at least two ordinals.) This coding strategy could have been a winning strategy for $F$ if it had only satisfied two requirements:
-
-    \begin{enumerate}
-    \item First, $s^{-1}(\gamma_{N_k})$ provided ordinals $\{\alpha_{W_0},\dots,\alpha_{W_{k-1}}\}$.
-(Thus $N_{k+1}=\bigcup_{\alpha \in s^{-1}(\gamma_{N_k})} f(\alpha) \restriction t_{N_k} = \bigcup_{0\leq m < k} f(\alpha_{W_m}) \restriction t_{N_k}$.)
-    \item In addition, $t_{N_k} \to \infty$.
-(Thus $\bigcup_{k<\omega} N_{k+1} = \bigcup_{k<\omega}\bigcup_{0\leq m < k-1} f(\alpha_{W_m}) \restriction t_{N_k} = \bigcup_{m<\omega} f(\alpha_{W_m}) \supseteq \bigcup_{m<\omega} W_m$.)
-    \end{enumerate}
-
-We shall improve $\sigma'$ so that it does satsify those requirements, beginning with the second.
-Define $\sigma^*$: \[\sigma^*(N,W)=t_N \cup \sigma'(N,W)\] Note then that $t_{N_{k+1}}\geq t_{t_{N_k}} = \max(t_{N_k})+2 = t_{N_k}-1+2=t_{N_k}+1$.
-
-Lastly, to cover the first requirement, we define $\sigma$: \[\sigma(N,W) = \sigma^*(N,W) \cup \{ \max(\sigma^*(N,W))+1+s(s^{-1}(\gamma_N)\cup\{\alpha_W\}) \}\] By induction \[s^{-1}(\gamma_{N_{k+1}}) = s^{-1}(s(s^{-1}(\gamma_{N_k})\cup\{\alpha_{W_k}\})) = s^{-1}(\gamma_{N_k})\cup\{\alpha_{W_k}\} = \{\alpha_{W_0},\dots,\alpha_{W_{k-1}}\}\cup\{\alpha_{W_k}\}\] we see the first requirement is satisfied.
-
-Finally, we turn our attention to $Con_{O,P}(\Sigma\mathbb{R}^\kappa)$.
-We define the winning strategy $\tau(U,p)$ for $O$ as follows: let $N(U)$ be the non-$\mathbb{R}$ coordinates in the basic open set $U$ and $W(p)$ be the non-$0$ coordinates in $p$.
-Then $\tau(U,p) = \left(\prod_{\alpha<\kappa} U_\alpha\right) \cap \Sigma\mathbb{R}^\kappa$ where if $\alpha \in \sigma(N(U),W(p))$ then $U_\alpha = (-1/t_{N(U)},1/t_{N(U)})$ and $U_\alpha=\mathbb{R}$ otherwise.
-\end{proof}
-
-\begin{proof}
-Short version, per GG's suggestion.
-
-Let $W\restriction n \in [\kappa]^n$ be a subset of $W\in[\kappa]^\omega$ such that $W\restriction n \subset W \restriction (n+1)$ and $\bigcup_{n<\omega} W\restriction n = W$.
-
-Define \[\sigma(N,W) = N \cup (|N|+1) \cup \{\alpha_W\} \cup \bigcup_{\alpha \in N} f(\alpha) \restriction |N|\]
-
-Consider the play $\left<\emptyset,W_0,N_1,W_1,N_2,W_2,\dots\right>$ with $F$ following the strategy $\sigma$.
-Let $\gamma \in W_i$, and note $\gamma \in f(\alpha_{W_i})$ (and $\gamma \in f(\alpha_{W_i})\restriction |N_n|$ for sufficiently large $n$).
-\[N_{i+1} = \sigma(N_i,W_i) \supseteq \{\alpha_{W_i}\}\] and thus \[N_{n+1} = \sigma(N_n,W_n) \supseteq \bigcup_{\alpha \in N_n} f(\alpha) \restriction |N_n| \supseteq \bigcup_{\alpha \in N_{i+1}} f(\alpha) \restriction |N_n| \supseteq f(\alpha_{W_i}) \restriction |N_n|\] showing $\gamma \in N_{n+1}$.
-Since $\gamma$ is forbidden in round $n+1$, $\gamma$ appears in finitely many sets chosen by $C$.
-
-We turn our attention to $Con_{O,P}(\Sigma\mathbb{R}^\kappa)$.
-We define the winning strategy $\tau(U,p)$ for $O$ as follows: let $N(U)$ be the non-$\mathbb{R}$ coordinates in the basic open set $U$ and $W(p)$ be the non-$0$ coordinates in $p$.
-Then $\tau(U,p) = \left(\prod_{\alpha<\kappa} U_\alpha\right) \cap \Sigma\mathbb{R}^\kappa$ where if $\alpha \in \sigma(N(U),W(p))$ then $U_\alpha = (-\frac{1}{|N(U)|},\frac{1}{|N(U)|})$ and $U_\alpha=\mathbb{R}$ otherwise.
-
-Consider the play $\left<\emptyset,p_0,U_1,p_1,U_2,p_2,\dots\right>$ with $O$ following the strategy $\tau$.
-Observe that $N(\tau(U,p))=\sigma(N(U),W(p))$.
-Thus $p_i(\gamma)\not=0$ is equivalent to $\gamma \in W(p_i)$, and by the above argument, for sufficiently large $n$, $\gamma \in \sigma(N(U_n),W(p_n))$.
-Therefore from round $n$ onward the $\gamma$-coordinates of points chosen by $P$ must lay in $(-\frac{1}{|N(U)|},\frac{1}{|N(U)|})$ and converge to $0$.
-\end{proof}
-
-%
-%\begin{theorem}
-%For all cardinals $\kappa \geq \omega$, the player $F \not\tactwin Cov_{F,C}(\kappa)$.
-%\end{theorem}
-%
-%\begin{proof}
-%(Based on Scheeper's Meager Nowhere Dense Games I)
-%
-%Suppose $\sigma$ is a tactical strategy for $F$ such that (without loss of generality) the first move is $\emptyset$. Let $A=\{2n: n<\omega\}$ and $B=\{2n+1:n<\omega\}$.
-%
-%By Todorcevic's Partition Relations for Partially Ordered Sets, $\mathcal{P}(A)\rightarrow(\omega)^1_B$.
-That is, for any function $\Phi$ from $\mathcal{P}(A)$ to $B$, there is some $b_\Phi\in B$ and $X_0\subseteq X_1\subseteq \dots \in \mathcal{P}(A)$ such that $\Phi(X_i)=b_\Phi$ for all $i$.
-Define $\Phi:\mathcal{P}(A)\rightarrow B$ such that $\Phi(X)\in B\setminus(\sigma(B\cup X))$.
-%
-%Observe the play $\left<\emptyset, B\cup X_0, \sigma(B\cup X_0), B \cup X_1, \sigma(B \cup X_1), B \cup X_2, \dots \right>$.
-As $b_\Phi \in B \subseteq \bigcup_{i<\omega} B \cup X_i$ but $b_\Phi \not\in \bigcup_{i<\omega} \sigma(B\cup X_i)$, this is a successful counter to any tactic by $F$.
-%\end{proof}
-%
-%\begin{proposition}
-%For all cardinals $\kappa \geq \omega_1$, the player $F \not\markwin Cov_{F,C}(\kappa)$.
-%\end{proposition}
-%
-%\begin{proof}
-%Suppose $\sigma$ is a Markov strategy for $F$ such that (without loss of generality) the first move is $\emptyset$. Let $A,B\in\mathcal{P}(\kappa)$ be disjoint with $|A|=|B|\geq\omega_1$.
-%
-%By Todorcevic's Partition Relations for Partially Ordered Sets, $\mathcal{P}(A)\rightarrow(\omega)^1_B$.
-That is, for any function $\Phi$ from $\mathcal{P}(A)$ to $B$, there is some $b_\Phi\in B$ and $X_0\subseteq X_1\subseteq \dots \in \mathcal{P}(A)$ such that $\Phi(X_i)=b_\Phi$ for all $i$.
-Define $\Phi:\mathcal{P}(A)\rightarrow B$ such that $\Phi(X)\in B\setminus(\bigcup_{n<\omega}\sigma(B\cup X,n))$.
-%
-%Observe the play $\left<\emptyset, B\cup X_0, \sigma(B\cup X_0,1), B \cup X_1, \sigma(B \cup X_1,2), B \cup X_2, \dots \right>$.
-As $b_\Phi \in B \subseteq \bigcup_{i<\omega} B \cup X_i$ but $b_\Phi \in \bigcap_{m<\omega} B \setminus (\bigcup_{n<\omega}\sigma(B\cup X_m,n))$ implying $b_\Phi \not\in \bigcup_{m<\omega}\sigma(B\cup X_m,m+1)$, this is a successful counter to any Markov strategy by $F$.
-%\end{proof}
-
-%\begin{theorem}
-%If $F\codewin Cov_{F,C}^{**}(\kappa)$ then $O\codewin C_{O,P}(\Sigma\mathbb{R}^\kappa,\vec{0})$.
-%\end{theorem}
-%
-%\begin{proof}
-%We begin by comparing
-%    \begin{itemize}
-%    \item $N\in[\kappa]^{<\omega}$ with the open set $\prod_{\alpha < \kappa} U_\alpha$ in $\Sigma2^\kappa$ where $U_\alpha=\{0\}$ for $\alpha\in N$ and $U_\alpha=\{0,1\}$ otherwise.
-%    \item $W\in[\kappa]^{\leq\omega}$ with the point $p\in\Sigma2^\kappa$ defined by $p(\alpha)=1$ for all $\alpha \in W$ and $p(\alpha)=0$ otherwise.
-%    \end{itemize}
-%
-%So if $\sigma$ is a winning coding strategy for $F$ in $Cov_{F,C}^{**}(\kappa)$, we may define $\tau$ to be a corresponding (perfect- or limited-information) winning strategy for $O$ in $C_{O,P}(\Sigma2^\kappa,\vec{0})$ by making the above conversions from finite sets played by $F$ to countable sets played by $C$ to the open sets which may be played by $O$ and points which may be played by $P$.
-As the legal moves for $C$ correspond to the legal moves for $P$, and as $\sigma$ covers any play by $C$, $\tau$ forces any nonzero coordinate found in a move by $P$ to eventually constrained to $0$.
-%
-%For the game $C_{O,P}(\Sigma\mathbb{R}^\kappa,\vec{0})$ we must instead use open sets of the form $\prod_{\alpha < \kappa} U_\alpha$ where $U_\alpha=(-1/i,1/i)$ for $\alpha\in N$ and $i$ being the turn number (with $U_\alpha=\mathbb{R}$ for $\alpha\not\in N$).
-(The turn number is easily encoded and decoded by $O$ by inspecting the non-$\mathbb{R}$ coordinates of her previous move) and associating points $p\in\Sigma\mathbb{R}^\kappa$ with $q\in\Sigma2^\kappa$ by $q(\alpha)=0$ when $|p(\alpha)|<1$ and $q(\alpha)=1$ otherwise.
-%\end{proof}
+\begin{question}
+Does $O$ have a winning strategy which uses only the turn number and the last $k$ moves of $P$ for the game $G_{O,P}(\omega_1\cup\{\infty\},\infty)$? (Probably not.)
+\end{question}
 

### 2013-01-30 menger.tex
Finished Menger game characterization

@@
 
-    Note that for $a,b,c\in\omega^{<\omega}$ and $m\leq n$, we know $U_{a\concat m}\subseteq U_{a\concat n}$ and $U_a \subseteq U_{a\concat b}$.
-Also, if $a=b\concat n \concat c$, then \[U_{a\concat m} = U_{b\concat n \concat c \concat m} \supseteq U_{b\concat n} \supseteq U_{b\concat m}\] (for example: $U_{48397}\supseteq U_{4837} \supseteq U_{47}$).
+    Note that for $a,b\in\omega^{<\omega}$ and $m\leq n$, we know:
+      \begin{enumerate}[(a)]
+        \item $U_{a\concat m}\subseteq U_{a\concat n}$ \\ (for example, $U_{1627} \subseteq U_{1629}$ - increasing the final digit yields supersets)
+        \item $U_a \subseteq U_{a\concat b}$ \\ (for example, $U_{1627}\subseteq U_{162789}$ - appending any sequence to the end yields supersets)
+        \item $U_{a\concat m} \subseteq U_{a\concat n} \subseteq U_{a\concat n\concat b} \subseteq U_{a\concat n\concat b\concat m}$ \\ (for example: $U_{1627} \subseteq U_{1629283287}$ - injecting a subseqence with initial number larger than the original's final number, prior to the final number, yields supersets)
+      \end{enumerate}
 
-    We may observe that if $S$ can find an $f:\omega\to\omega$ such that $\bigcup_{n<\omega}U_{f\rest n} = X$, she can use $\{U_{f\rest 0}\}, \{U_{f\rest 1}\}, \dots$ to counter $C$'s strategy.
+    We may observe that if $S$ can find an $f:\omega\to\omega$ such that $\bigcup_{n<\omega}U_{f\rest (n+1)} = X$, she can use $\{U_{f\rest 0}\}, \{U_{f\rest 1}\}, \dots$ to counter $C$'s strategy.
 
@@
       \item
-      $\ds V_k^n = \bigcap_{a\in\omega^{\leq n}} U_{a\concat k} = \bigcap_{a\in k^{\leq n}} U_{a\concat k}$
+      Since due to (c) for each $b\in \omega^{\leq n} \setminus k^{\leq n}$, there is an $a\in k^{\leq n}$ with $U_{a\concat k} \subseteq U_{b\concat k}$: \[\ds V_k^n = \bigcap_{a\in\omega^{\leq n}} U_{a\concat k} = \bigcap_{a\in k^{\leq n}} U_{a\concat k} \cap \bigcap_{b\in \omega^{\leq n} \setminus k^{\leq n}} U_{b\concat k} = \bigcap_{a\in k^{\leq n}} U_{a\concat k}\] making $V_k^n$ a finite intersection of open sets.
 
       \item
-      $\ds V_{k+1}^n = \bigcap_{a\in{k+1}^{\leq n}} U_{a\concat (k+1)} \supseteq \bigcap_{a\in{k+1}^{\leq n}} U_{a\concat k} \supseteq \bigcap_{a\in{k}^{\leq n}} U_{a\concat k} = V_k^n$
+      We show $V_k^0\subseteq V_{k+1}^0$:
+      \[
+        V_k^0 = U_k \subseteq U_{k+1} = V_{k+1}^0
+      \]
+      and then assume $V_k^{n}\subseteq V_{k+1}^{n}$:
+      \[
+        V_k^{n+1} = 
+        \bigcap_{a\in{\omega}^{\leq n+1}} U_{a\concat k} = 
+        V_k^{n} \cap \bigcap_{a\in{\omega}^{n+1}} U_{a\concat k} \subseteq
+        V_{k+1}^{n} \cap \bigcap_{a\in{\omega}^{n+1}} U_{a\concat (k+1)} =
+        V_{k+1}^{n+1}
+      \]
 
       \item
-      Let $x\in X$ and pick $l<\omega$ such that $x\in U_l$.
-Then for $a\in l^{\leq n}$, choose $l_a$ such that $x\in U_{a\concat l_a}$.
-Then let $k>l_a$ for all $a$.
-It follows that \[x \in \bigcap_{a\in k^{\leq n}} U_{a\concat l_a} \subseteq \bigcap_{a\in k^{\leq n}} U_{a\concat k} = V_k^n\] THIS ISN'T QUITE RIGHT SHOULD FIX THIS
+      We easily see that $\mathcal{V}^0=\{U_0,U_1,\dots\}$ is a cover, and then assume $\mathcal{V}^n$ is a cover.
+
+      Let $x\in X$ and pick $l<\omega$ such that $x \in V^n_l$. For $a \in l^{n+1}$ choose $l_a$ such that $x\in U_{a\concat l_a}$, giving
+      \[ x \in \bigcap_{a\in l^{n+1}} U_{a\concat l_a} \]
+
+      We will assume $k>l,l_a$ for all $a\in l^{\leq n+1}$.
+
+      For any $a\in k^{n+1}\setminus l^{n+1}$ note that $a = b\concat c$ where $b\in l^{\leq n}$ and $c$ begins with a number $l$ or greater:
+      \[
+        V^n_l \subseteq 
+        U_{b\concat l} \subseteq 
+        U_{b\concat c} \subseteq
+        U_{b\concat c\concat l_a} = 
+        U_{a\concat l_a}
+      \]
+
+      Thus:
+      \[ 
+        x \in 
+        V^n_l \cap \left(\bigcap_{a\in l^{n+1}} U_{a\concat l_a}\right) 
+      \]
+      \[
+        =
+        V^n_l \cap \left(\bigcap_{a\in k^{n+1}\setminus l^{n+1}} U_{a\concat l_a}\right) \cap \left(\bigcap_{a\in l^{n+1}} U_{a\concat l_a}\right)
+      \]
+      \[
+        =
+        V^n_l \cap \left(\bigcap_{a\in k^{n+1}} U_{a\concat l_a}\right)
+      \]
+      \[
+        \subseteq
+        V^n_k \cap \left(\bigcap_{a\in k^{n+1}} U_{a\concat k}\right)
+      \]
+      \[
+        =
+        V^{n+1}_k
+      \]
     \end{enumerate}
 
-    Finally, apply Menger to $\mathcal{V}^n$, resulting in the cover $\{V_{f(0)}^0, V_{f(1)}^1, \dots\}$, noting \[X = \bigcup_{n<\omega}V_{f(n)}^n \subseteq \bigcup_{n<\omega} U_{(f\rest n)\concat f(n)} = \bigcup_{n<\omega} U_{f\rest n+1}\]
+    Finally, apply Menger to $\mathcal{V}^n$, resulting in the cover $\{V_{f(0)}^0, V_{f(1)}^1, \dots\}$, noting \[X = \bigcup_{n<\omega}V_{f(n)}^n \subseteq \bigcup_{n<\omega} U_{(f\rest n)\concat f(n)} = \bigcup_{n<\omega} U_{f\rest (n+1)}\]
   \end{proof}

### 2013-02-04 ABD_results.tex
Finished Menger game characterization
Finished 2-tactic, started k-tactic on Cantor tree of spaces

@@
 \begin{document}
-
-%%%%%%%%%
-%COMMENT%
-%%%%%%%%%
-\largecomment{
 Assume all spaces are locally compact.
@@
 \end{proof}
-
-}
-%%%%%%%%%%%%
-%ENDCOMMENT%
-%%%%%%%%%%%%
 
@@
 \begin{proof}
-Suppose $\sigma(\<x,s\>,\<y,t\>)$ was a winning 2-tactical strategy. We may define $S(x,y,n)$ and $m(x,y,n)$ such that for each $(x,y)$,
+Suppose $\sigma(\<x,s\>,\<y,t\>)$ was a winning 2-tactical strategy. We may define $S(x,y,n)\in [\omega_1]^{<\omega}$ (increasing on $n$) and $n<m(x,y,n)<\omega$ such that for each $(x,y)$,
   \[
-\bigcup_{s,t \in 2^{\leq n}} \sigma(\<x,s\>,\<y,t\>) \subseteq K^*_{S(x,y,n)} \cup L_{m(x,y,n)}
+    \bigcup_{s,t \in 2^{\leq n}} \sigma(\<x,s\>,\<y,t\>) \subseteq 
+    K^*_{S(x,y,n)} \cup L_{m(x,y,n)}
+  \]
+and so we assume
+  \[
+    \sigma(\<x,s\>,\<y,t\>) =
+    K^*_{S(x,y,\max(|s|,|t|))} \cup L_{m(x,y,\max(|s|,|t|))}
   \]
@@
   \[
-\tau(x,s) = K^*_{S(x,x',m(x,x',|s|)+1)} \cup L_{m(x,x',m(x,x',|s|)+1)}
+  \tau(x,s) = 
+  K^*_{S(x,x',m(x,x',|s|)+1)} \cup L_{m(x,x',m(x,x',|s|)+1)}
   \]
@@
 \[
-\<x_0, s_0\>, \<x', {z_{m(x_0,x_0,|s_0|)}}^\frown\<1\>\>, \<x_1, s_1\>, \<x', {z_{m(x_1,x',|s_1|)}}^\frown\<1\>\>,  \<x_2, s_2\>, \<x', {z_{m(x_2,x',|s_2|)}}^\frown\<1\>\>, \dots
+\<x_0, s_0\>, \<x', {z_{m(x_0,x',|s_0|)}}^\frown\<1\>\>, \<x_1, s_1\>, \<x', {z_{m(x_1,x',|s_1|)}}^\frown\<1\>\>,  \<x_2, s_2\>, \<x', {z_{m(x_2,x',|s_2|)}}^\frown\<1\>\>, \dots
 \]
@@
 
-Obviously it also clusters at $c$, so we need only show that it is a legal counter to $\sigma$.
-Note that \[\sigma(\<x', {z_{m(x_i,x',|s_i|)}}^\frown\<1\>\>, \<x_{i+1}, s_{i+1}\>) \subseteq \sigma(\<x_{i+1}, s_{i+1}\>, \<x', {z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>\>)\] since the only difference in input is a higher copy of $x'\in X$.
+We will need the fact that:
+  \[
+    |s_i| <
+    m(x_i,x',|s_i|)+1 =
+    |{z_{m(x_i,x',|s_i|)}}^\frown\<1\>| 
+  \]
+  \[
+    <
+    m(x_i,x',m(x_i,x',|s_i|)+1) =
+    m(x_i,x',|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|) \leq
+    |s_{i+1}|
+  \]
 
-Suppose $\<x_{i}, s_{i}\>$ was an illegal move. Then for some $j<i$, that move was forbidden by 
+Note that $m(x,y,\max(|s|,|t|))$ is increasing throughout this play of the game:
   \[
-\sigma(\<x_{j}, s_{j}\>, \<x', {z_{m(x_{j},x',|s_{j}|)}}^\frown\<1\>\>)
+    m(x_i,x',\max(|s_i|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|))
+    \leq
+    |s_{i+1}| 
+  \]
+  \[
+    <
+    m(x_{i+1},x',\max(|s_{i+1}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|))
+    \leq
+    |{z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>|
+  \]
+  \[
+    <
+    m(x_{i+1},x',\max(|s_{i+1}|,|{z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>|))
+  \]
+
+We turn to showing that $\<x', {z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>\>$ is always a legal move.
+Since ${z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>$ is on the antichain avoided by any $K^*$, the problem is reduced to showing that this move isn't forbidden by
+  \[
+  L_{m(x_{i+1},x',\max(|s_{i+1}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|))}
+  \]
+which we can see here:
+  \[
+    m(x_{i+1},x',\max(|s_{i+1}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|)) =
+    m(x_{i+1},x',|s_{i+1}|) <
+    |{z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>|
+  \]
+
+We can conclude by showing that $\<x_{i+1},s_{i+1}\>$ is always a legal move. We can see it avoids 
+  \[
+  L_{m(x_{i},x',\max(|s_{i}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|))}
+  \]
+since
+  \[
+    m(x_{i},x',\max(|s_{i}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|)) =
+    m(x_{i},x',|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|) \leq
+    |s_{i+1}|
+  \]
+
+Since $\<x_{i+1},s_{i+1}\>$ was legal against $\tau$, it avoided
+  \[
+    K^*_{S(x_j,x',m(x_j,x',|s_j|)+1)} = 
+    K^*_{S(x_j,x',\max(|s_j|,|{z_{m(x_j,x',|s_j|)}}^\frown\<1\>|))}
+  \]
+for $j\leq i$. And when $j<i$,
+  \[
+    K^*_{S(x_{j+1},x',\max(|s_{j+1}|,|{z_{m(x_j,x',|s_j|)}}^\frown\<1\>|))} =
+    K^*_{S(x_{j+1},x',|s_{j+1}|)}
   \]
@@
     \subseteq
-K^*_{S(x_{j},x',m(x_{j},x',|s_{j}|)+1)} \cup L_{m(x_{j},x',m(x_{j},x',|s_{j}|)+1)}
-= \tau(x_j,s_j)
+    K^*_{S(x_{j+1},x',m(x_{j+1},x',|s_{j+1}|)+1)}
   \]
-which is a contradiction as it was a legal move against $\tau$.
 
-Finally, consider $\<x',{z_{m(x_i,x',|s_i|)}}^\frown\<1\>\>$.
-Since the length of ${z_{m(x_i,x',|s_i|)}}^\frown\<1\>$ is longer than $m(x_i,x',|s_i|)$, it's not forbidden by any $L_m$ played by $K$.
-And since ${z_{m(x_i,x',|s_i|)}}^\frown\<1\>$ is on the antichain $A$ avoided by the $K^*_S$s, it could never have been forbidden at all.
+This concludes the proof.
 \end{proof}
 
-\begin{proposition}
-The above proof can be adapted to prove $K\not\ktactwin{k}\lfkpgame{\mathbb{X}}$.
-\end{proposition}
+\begin{theorem}
+$K\not\ktactwin{k}\lfkpgame{\mathbb{X}}$.
+\end{theorem}
+
+\begin{proof}
+The proof proceeds similarly to the proof of $K\not\ktactwin{2}\lfkpgame{\mathbb{X}}$.
+
+Suppose $\sigma(\<\overline{x},\overline{s}\>,\<y,t\>)$ was a winning $k+1$-tactical strategy, where $\<\overline{x},\overline{s}\>$ represents $\<x_0,s_0\>,\dots,\<x_{k-1},s_{k-1}\>$.
+We may define $S(\overline{x},y,n)\in [\omega_1]^{<\omega}$ (increasing on $n$) and $n<m(\overline{x},y,n)<\omega$ such that for each $(\overline{x},y)$,
+  \[
+    \bigcup_{\overline{s},t \in 2^{\leq n}} \sigma(\<\overline{x},\overline{s}\>,\<y,t\>) \subseteq 
+    K^*_{S(\overline{x},y,n)} \cup L_{m(\overline{x},y,n)}
+  \]
+and so we assume
+  \[
+    \sigma(\<x,s\>,\<y,t\>) =
+    K^*_{S(x,y,\max(|s|,|t|))} \cup L_{m(x,y,\max(|s|,|t|))}
+  \]
+
+Select an arbitrary point $x' \in X$. We define a tactical strategy 
+  \[
+  \tau(x,s) = 
+  K^*_{S(x,x',m(x,x',|s|)+1)} \cup L_{m(x,x',m(x,x',|s|)+1)}
+  \]
+We complete the proof by showing $\tau$ is a winning tactical strategy (a contradiction).
+
+Suppose
+\[
+\<x_0, s_0\>, \<x_1, s_1\>, \<x_2, s_2\>, \dots
+\]
+successfully countered $\tau$ by clustering at $c\in C$ (the strategy trivially prevents clustering elsewhere). Let $z_n = \<0,\dots,0\>$ with $n$ zeros. We claim
+\[
+\<x_0, s_0\>, \<x', {z_{m(x_0,x',|s_0|)}}^\frown\<1\>\>, \<x_1, s_1\>, \<x', {z_{m(x_1,x',|s_1|)}}^\frown\<1\>\>,  \<x_2, s_2\>, \<x', {z_{m(x_2,x',|s_2|)}}^\frown\<1\>\>, \dots
+\]
+is a successful counter to $\sigma$.
+
+We will need the fact that:
+  \[
+    |s_i| <
+    m(x_i,x',|s_i|)+1 =
+    |{z_{m(x_i,x',|s_i|)}}^\frown\<1\>| 
+  \]
+  \[
+    <
+    m(x_i,x',m(x_i,x',|s_i|)+1) =
+    m(x_i,x',|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|) \leq
+    |s_{i+1}|
+  \]
+
+Note that $m(x,y,\max(|s|,|t|))$ is increasing throughout this play of the game:
+  \[
+    m(x_i,x',\max(|s_i|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|))
+    \leq
+    |s_{i+1}| 
+  \]
+  \[
+    <
+    m(x_{i+1},x',\max(|s_{i+1}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|))
+    \leq
+    |{z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>|
+  \]
+  \[
+    <
+    m(x_{i+1},x',\max(|s_{i+1}|,|{z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>|))
+  \]
+
+We turn to showing that $\<x', {z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>\>$ is always a legal move.
+Since ${z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>$ is on the antichain avoided by any $K^*$, the problem is reduced to showing that this move isn't forbidden by
+  \[
+  L_{m(x_{i+1},x',\max(|s_{i+1}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|))}
+  \]
+which we can see here:
+  \[
+    m(x_{i+1},x',\max(|s_{i+1}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|)) =
+    m(x_{i+1},x',|s_{i+1}|) <
+    |{z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>|
+  \]
+
+We can conclude by showing that $\<x_{i+1},s_{i+1}\>$ is always a legal move. We can see it avoids 
+  \[
+  L_{m(x_{i},x',\max(|s_{i}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|))}
+  \]
+since
+  \[
+    m(x_{i},x',\max(|s_{i}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|)) =
+    m(x_{i},x',|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|) \leq
+    |s_{i+1}|
+  \]
+
+Since $\<x_{i+1},s_{i+1}\>$ was legal against $\tau$, it avoided
+  \[
+    K^*_{S(x_j,x',m(x_j,x',|s_j|)+1)} = 
+    K^*_{S(x_j,x',\max(|s_j|,|{z_{m(x_j,x',|s_j|)}}^\frown\<1\>|))}
+  \]
+for $j\leq i$. And when $j<i$,
+  \[
+    K^*_{S(x_{j+1},x',\max(|s_{j+1}|,|{z_{m(x_j,x',|s_j|)}}^\frown\<1\>|))} =
+    K^*_{S(x_{j+1},x',|s_{j+1}|)}
+  \]
+  \[
+    \subseteq
+    K^*_{S(x_{j+1},x',m(x_{j+1},x',|s_{j+1}|)+1)}
+  \]
+
+This concludes the proof.
+\end{proof}
 

### 2013-02-04 menger.tex
Finished 2-tactic, started k-tactic on Cantor tree of spaces

@@
   \begin{theorem}
-    $X$ is Menger if and only if $S \win \mengame{X}$.
+    $X$ is Menger if and only if $C \not\win \mengame{X}$.
   \end{theorem}
@@
 
+  \begin{proposition}
+    $X$ is compact if and only if $S \tactwin \mengame{X}$
+  \end{proposition}
+
+  \begin{proof}
+    Assume $X$ is compact. For each open cover played by $C$, pick the finite subcover.
+
+    Assume $S$ has a winning tactical strategy. For any open cover, have $C$ play only it during the entire game. $S$'s only choice must be a finite subcover.
+  \end{proof}
+
+  \begin{proposition}
+    If $X$ is $\sigma$-compact then $S \markwin \mengame{X}$
+  \end{proposition}
+
+  \begin{proof}
+    Let $X=\bigcup_{n<\omega} X_n$ for compact $X_n$. On round $n$, $S$ picks the finite subcover of $C$'s open cover of $X_n$.
+  \end{proof}
+
+  \begin{question}
+    Does $S \markwin \mengame{X}$ imply $X$ is $\sigma$-compact?
+  \end{question}
+
+  Let $\sigma(\mathcal{U},n)$ be $S$'s winning Markov strategy.
+
 \end{document}

### 2013-02-07 ABD_results.tex
Finished k-tactic

@@
 
-We will need the fact that:
+We will need the fact that, as $\<x_{i+1},s_{i+1}\>$ was legal against $\tau$:
   \[
@@
 
-Note that $m(x,y,\max(|s|,|t|))$ is increasing throughout this play of the game:
+Note that $m(x,y,\max(|s|,|t|))$ is increasing throughout this play of the game versus $\sigma$:
   \[
     m(x_i,x',\max(|s_i|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|))
+  \]
+  \[
+    =
+    m(x_i,x',|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|)
+  \]
+  \[
     \leq
@@
     <
+    m(x_{i+1},x',|s_{i+1}|)
+  \]
+  \[
+    =
     m(x_{i+1},x',\max(|s_{i+1}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|))
-    \leq
+  \]
+  \[
+    =
+    |{z_{m(x_{i+1},x',|s_{i+1}|)}}|
+  \]
+  \[
+    <
     |{z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>|
@@
     <
+    m(x_{i+1},x',|{z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>|)
+  \]
+  \[
+    =
     m(x_{i+1},x',\max(|s_{i+1}|,|{z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>|))
@@
   \[
-    K^*_{S(x_j,x',m(x_j,x',|s_j|)+1)} = 
-    K^*_{S(x_j,x',\max(|s_j|,|{z_{m(x_j,x',|s_j|)}}^\frown\<1\>|))}
+    K^*_{S(x_h,x',m(x_h,x',|s_h|)+1)} = 
+    K^*_{S(x_h,x',\max(|s_h|,|{z_{m(x_h,x',|s_h|)}}^\frown\<1\>|))}
   \]
-for $j\leq i$. And when $j<i$,
+for $h\leq i$. And when $h<i$, we see it avoids:
   \[
-    K^*_{S(x_{j+1},x',\max(|s_{j+1}|,|{z_{m(x_j,x',|s_j|)}}^\frown\<1\>|))} =
-    K^*_{S(x_{j+1},x',|s_{j+1}|)}
+    K^*_{S(x_{h+1},x',\max(|s_{h+1}|,|{z_{m(x_h,x',|s_h|)}}^\frown\<1\>|))} =
+    K^*_{S(x_{h+1},x',|s_{h+1}|)}
   \]
@@
     \subseteq
-    K^*_{S(x_{j+1},x',m(x_{j+1},x',|s_{j+1}|)+1)}
+    K^*_{S(x_{h+1},x',m(x_{h+1},x',|s_{h+1}|)+1)}
   \]
@@
 \begin{proof}
-The proof proceeds similarly to the proof of $K\not\ktactwin{2}\lfkpgame{\mathbb{X}}$.
+The proof proceeds in parallel to the proof of $K\not\ktactwin{2}\lfkpgame{\mathbb{X}}$.
 
-Suppose $\sigma(\<\overline{x},\overline{s}\>,\<y,t\>)$ was a winning $k+1$-tactical strategy, where $\<\overline{x},\overline{s}\>$ represents $\<x_0,s_0\>,\dots,\<x_{k-1},s_{k-1}\>$.
-We may define $S(\overline{x},y,n)\in [\omega_1]^{<\omega}$ (increasing on $n$) and $n<m(\overline{x},y,n)<\omega$ such that for each $(\overline{x},y)$,
+Suppose $\sigma(\<x_0,s_0\>,\dots,\<x_{k},s_{k}\>)$ was a winning $(k+1)$-tactical strategy.
+We may define $S(x_0,\dots,x_{k},n)\in [\omega_1]^{<\omega}$ (increasing on $n$) and $n<m(x_0,\dots,x_{k},n)<\omega$ such that for each $(x_0,\dots,x_{k})$,
   \[
-    \bigcup_{\overline{s},t \in 2^{\leq n}} \sigma(\<\overline{x},\overline{s}\>,\<y,t\>) \subseteq 
-    K^*_{S(\overline{x},y,n)} \cup L_{m(\overline{x},y,n)}
+    \bigcup_{s_0,\dots,s_k \in 2^{\leq n}} \sigma(\<x_0,s_0\>,\dots,\<x_{k},s_{k}\>) \subseteq 
+    K^*_{S(x_0,\dots,x_{k},n)} \cup L_{m(x_0,\dots,x_{k},n)}
   \]
@@
   \[
-    \sigma(\<x,s\>,\<y,t\>) =
-    K^*_{S(x,y,\max(|s|,|t|))} \cup L_{m(x,y,\max(|s|,|t|))}
+    \sigma(\<x_0,s_0\>,\dots,\<x_{k},s_{k}\>) =
+    K^*_{S(x_0,\dots,x_{k},\max(|s_0|,\dots,|s_k|))} \cup L_{m(x_0,\dots,x_{k},\max(|s_0|,\dots,|s_k|))}
   \]
 
-Select an arbitrary point $x' \in X$. We define a tactical strategy 
+Select an arbitrary point $x' \in X$. Let $M^0(x,n)=m(x,x',\dots,x',n)$ and $M^{i+1}(x,n)=M^0(x,M^i(x,n)+1)$. We define a tactical strategy 
   \[
-  \tau(x,s) = 
-  K^*_{S(x,x',m(x,x',|s|)+1)} \cup L_{m(x,x',m(x,x',|s|)+1)}
+  \tau(x,s) = K^*_{S(x,x',\dots,x',M^{k-1}(x,|s|)+1)} \cup L_{m(x,x',\dots,x',M^{k-1}(x,|s|)+1)}
   \]
@@
 \[
-\<x_0, s_0\>, \<x', {z_{m(x_0,x',|s_0|)}}^\frown\<1\>\>, \<x_1, s_1\>, \<x', {z_{m(x_1,x',|s_1|)}}^\frown\<1\>\>,  \<x_2, s_2\>, \<x', {z_{m(x_2,x',|s_2|)}}^\frown\<1\>\>, \dots
+  \<x_0, s_0\>, 
+  \<x', {z_{M^0(x_0,|s_0|)}}^\frown\<1\>\>,
+  \<x', {z_{M^1(x_0,|s_0|)}}^\frown\<1\>\>, 
+  \dots, 
+  \<x', {z_{M^{k-1}(x_0,|s_0|)}}^\frown\<1\>\>,
+\]
+\[
+  \<x_1, s_1\>, 
+  \<x', {z_{M^0(x_1,|s_1|)}}^\frown\<1\>\>, 
+  \<x', {z_{M^1(x_1,|s_1|)}}^\frown\<1\>\>, 
+  \dots, 
+  \<x', {z_{M^{k-1}(x_1,|s_1|)}}^\frown\<1\>\>, 
+  \dots
 \]
@@
 
-We will need the fact that:
+We will need the fact that, as $\<x_{i+1},s_{i+1}\>$ was legal against $\tau$:
   \[
     |s_i| <
-    m(x_i,x',|s_i|)+1 =
-    |{z_{m(x_i,x',|s_i|)}}^\frown\<1\>| 
+    M^0(x_i,|s_i|)+1 =
+    |{z_{M^0(x_i,|s_i|)}}^\frown\<1\>| <
+    M^0(x_i,M^0(x_i,|s_i|)+1)+1 
   \]
   \[
-    <
-    m(x_i,x',m(x_i,x',|s_i|)+1) =
-    m(x_i,x',|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|) \leq
+    =
+    M^1(x_i,|s_i|)+1 =
+    |{z_{M^1(x_i,|s_i|)}}^\frown\<1\>| <
+    \dots <
+    |{z_{M^{k-1}(x_i,|s_i|)}}^\frown\<1\>| 
+  \]
+  \[
+    =
+    M^{k-1}(x_i,|s_i|) + 1 <
+    m(x_i,x',\dots,x',M^{k-1}(x_i,|s_i|)+1) \leq
     |s_{i+1}|
@@
 
-Note that $m(x,y,\max(|s|,|t|))$ is increasing throughout this play of the game:
+Note that $m(x_0,\dots,x_{k},\max(|s_0|,\dots,|s_k|))$ is increasing throughout this play of the game versus $\sigma$:
   \[
-    m(x_i,x',\max(|s_i|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|))
+    m(x_i,x',\dots,x',\max(|s_i|,|{z_{M^0(x_i,|s_i|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_i,|s_i|)}}^\frown\<1\>|))
+  \]
+  \[
+    =
+    m(x_i,x',\dots,x',|{z_{M^{k-1}(x_i,|s_i|)}}^\frown\<1\>|)
+  \]
+  \[
+    =
+    m(x_i,x',\dots,x',M^{k-1}(x_i,|s_i|)+1)
+  \]
+  \[
     \leq
@@
     <
-    m(x_{i+1},x',\max(|s_{i+1}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|))
-    \leq
-    |{z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>|
+    M^0(x_{i+1},|s_{i+1}|)
+  \]
+  \[
+    =
+    m(x_{i+1},x',\dots,x',|s_{i+1}|)
+  \]
+  \[
+    =
+    m(x_{i+1},x',\dots,x',\max(|s_{i+1}|,|{z_{M^0(x_i,|s_i|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_i,|s_i|)}}^\frown\<1\>|))
+  \]
+  \[
+    =
+    |{z_{m(x_{i+1},x',\dots,x',|s_{i+1}|)}}|
+  \]
+  \[
+    =
+    |{z_{M^0(x_{i+1},|s_{i+1}|)}}|
   \]
@@
     <
-    m(x_{i+1},x',\max(|s_{i+1}|,|{z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>|))
+    |{z_{M^0(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|
+  \]
+  \[
+    <
+    m(x_{i+1},x',\dots,x',|{z_{M^0(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|)
+  \]
+  \[
+    =
+    m(x_{i+1},x',\dots,x',\max(|s_{i+1}|,|{z_{M^0(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|,|{z_{M^1(x_{i},|s_{i}|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_{i},|s_{i}|)}}^\frown\<1\>|))
+  \]
+  \[
+    \vdots
+  \]
+  \[
+    <
+    m(x_{i+1},x',\dots,x',\max(|s_{i+1}|,|{z_{M^0(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|))
   \]
 
-We turn to showing that $\<x', {z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>\>$ is always a legal move.
-Since ${z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>$ is on the antichain avoided by any $K^*$, the problem is reduced to showing that this move isn't forbidden by
+We turn to showing that $\<x', {z_{M^j(x_{i+1},|s_{i+1}|)}}^\frown\<1\>\>$ is always a legal move.
+Since ${z_{M^j(x_{i+1},|s_{i+1}|)}}^\frown\<1\>$ is on the antichain avoided by any $K^*$, the problem is reduced to showing that this move isn't forbidden by
   \[
-  L_{m(x_{i+1},x',\max(|s_{i+1}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|))}
+    L_{m(x_{i+1},x',\dots,x',\max(|s_{i+1}|,|{z_{M^0(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|,\dots,|{z_{M^{j-1}(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|,|{z_{M^{j}(x_{i},|s_{i}|)}}^\frown\<1\>|,\dots,|{z_{M^{k}(x_{i},|s_{i}|)}}^\frown\<1\>|))}
+  \]
+  \[
+    =
+    L_{m(x_{i+1},x',\dots,x',|{z_{M^{j-1}(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|)}
   \]
@@
   \[
-    m(x_{i+1},x',\max(|s_{i+1}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|)) =
-    m(x_{i+1},x',|s_{i+1}|) <
-    |{z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>|
+    m(x_{i+1},x',\dots,x',|{z_{M^{j-1}(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|)
+  \]
+  \[
+    =
+    m(x_{i+1},x',\dots,x',M^{j-1}(x_{i+1},|s_{i+1}|)+1)
+  \]
+  \[
+    =
+    M^0(x_{i+1},M^{j-1}(x_{i+1},|s_{i+1}|)+1)
+  \]
+  \[
+    =
+    M^j(x_{i+1},s_{i+1})
+  \]
+  \[
+    <
+    |{z_{M^j(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|
   \]
@@
   \[
-  L_{m(x_{i},x',\max(|s_{i}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|))}
+  L_{m(x_{i},x',\dots,x',\max(|s_{i}|,|{z_{M^0(x_i,|s_i|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_i,|s_i|)}}^\frown\<1\>|))}
   \]
@@
   \[
-    m(x_{i},x',\max(|s_{i}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|)) =
-    m(x_{i},x',|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|) \leq
+    m(x_{i},x',\dots,x',\max(|s_{i}|,|{z_{M^0(x_i,|s_i|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_i,|s_i|)}}^\frown\<1\>|))
+  \]
+  \[
+    =
+    m(x_{i},x',\dots,x',|{z_{M^{k-1}(x_i,|s_i|)}}^\frown\<1\>|)
+  \]
+  \[
+    =
+    m(x_{i},x',\dots,x',M^{k-1}(x_i,|s_i|)+1)
+  \]
+  \[
+    \leq
     |s_{i+1}|
@@
   \[
-    K^*_{S(x_j,x',m(x_j,x',|s_j|)+1)} = 
-    K^*_{S(x_j,x',\max(|s_j|,|{z_{m(x_j,x',|s_j|)}}^\frown\<1\>|))}
+    K^*_{S(x_h,x',\dots,x',M^{k-1}(x_h,|s_h|)+1)} 
   \]
-for $j\leq i$. And when $j<i$,
   \[
-    K^*_{S(x_{j+1},x',\max(|s_{j+1}|,|{z_{m(x_j,x',|s_j|)}}^\frown\<1\>|))} =
-    K^*_{S(x_{j+1},x',|s_{j+1}|)}
+    = 
+    K^*_{S(x_h,x',\dots,x',\max(|s_h|,|{z_{M^{0}(x_h,|s_h|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_h,|s_h|)}}^\frown\<1\>|))}
+  \]
+for $h\leq i$. And when $h<i$, we see it avoids both:
+  \[
+    K^*_{S(x_{h+1},x',\dots,x',\max(|s_{h+1}|,|{z_{M^0(x_{h+1},|s_{h+1}|)}}^\frown\<1\>|,\dots,|{z_{M^{j-1}(x_{h+1},|s_{h+1}|)}}^\frown\<1\>|,|{z_{M^{j}(x_{h},|s_{h}|)}}^\frown\<1\>|,\dots,|{z_{M^{k}(x_{h},|s_{h}|)}}^\frown\<1\>|))}
+  \]
+  \[
+    =
+    K^*_{S(x_{h+1},x',\dots,x',|{z_{M^{j-1}(x_{h+1},|s_{h+1}|)}}^\frown\<1\>|)}
+  \]
+  \[
+    =
+    K^*_{S(x_{h+1},x',\dots,x',M^{j-1}(x_{h+1},|s_{h+1}|)+1)}
   \]
@@
     \subseteq
-    K^*_{S(x_{j+1},x',m(x_{j+1},x',|s_{j+1}|)+1)}
+    K^*_{S(x_{h+1},x',\dots,x',M^{k-1}(x_{h+1},|s_{h+1}|)+1)}
+  \]
+and:
+  \[
+    K^*_{S(x_{h+1},x',\dots,x',\max(|s_{h+1}|,|{z_{M^0(x_{h},|s_{h}|)}}^\frown\<1\>|,\dots,|{z_{M^{k}(x_{h},|s_{h}|)}}^\frown\<1\>|))} 
+  \]
+  \[
+    =
+    K^*_{S(x_{h+1},x',\dots,x',|s_{k+1}|)}
+  \]
+  \[
+    \subseteq
+    K^*_{S(x_{h+1},x',\dots,x',M^{k-1}(x_{h+1},|s_{h+1}|)+1)}
   \]

### 2013-02-12 au_topology_seminar_talk_2013_02_18.tex
Added seminar talk

--- 2013-02-07 ABD_results.tex
@@
 \begin{document}
-Assume all spaces are locally compact.
-
-\begin{proposition}
-The following are all equivalent winning conditions for $\congame{\oneptcomp{X}}{\infty}$:
-\begin{itemize}
-\item The points chosen by $P$ converge to $\infty$.
-\item All compact subsets of $X$ contain finitely many points chosen by $P$.
-\item No compact subset of $X$ contains infinite points chosen by $P$.
-\end{itemize}
-
-The following are all equivalent winning conditions for $\clusgame{\oneptcomp{X}}{\infty}$:
-\begin{itemize}
-\item The points chosen by $P$ cluster about $\infty$.
-\item All compact subsets of $X$ miss infinitely many points chosen by $P$.
-\item No compact subset of $X$ contains cofinite points chosen by $P$.
-\end{itemize}
-\end{proposition}
-
-\begin{proposition}
-The winning condition for $\congame{\oneptcomp{X}}{\infty}$ is equivalent to the winning condition of $\lfkpgame{X}$.
-\end{proposition}
-
-\begin{proof}
-First, suppose that the points chosen by $P$ have a limit point $l$, the contradiction of $\lfkpgame{\oneptcomp{X}}$'s winning condition.
-Every open set about $l$ contains infinitely many points, including a compact neighborhood of $l$.
-This contradicts the winning condition of $\congame{\oneptcomp{X}}{\infty}$.
-
-Then, suppose that there was a compact subset of $X$ containing infinite points chosen by $P$, the contradiction of $\congame{\oneptcomp{X}}{\infty}$'s winning condition.
-Every infinite subset of a compact set has a limit point, contradicting $\lfkpgame{\oneptcomp{X}}$'s winning condition.
-\end{proof}
-
-\begin{theorem}
-The following are all equivalent.
-\begin{itemize}
-\item $X$ is metacompact.
-\item $O\tactwin\congame{\oneptcomp{X}}{\infty}$.
-\item $O\tactwin\clusgame{\oneptcomp{X}}{\infty}$.
-\end{itemize}
-\end{theorem}
-
-\begin{proof}
-Gruenhage has shown $X$ is metacompact $\Rightarrow$ $K\tactwin\lfkpgame{X}$ (which is equivalent to $O\tactwin\congame{\oneptcomp{X}}{\infty}$), and obviously $O\tactwin\congame{\oneptcomp{X}}{\infty}$ $\Rightarrow$ $O\tactwin\clusgame{\oneptcomp{X}}{\infty}$.
-We proceed by modifying Gruenhage's proof that $K\tactwin\lfkpgame{X}$ implies $X$ is metacompact to show $O\tactwin\clusgame{\oneptcomp{X}}{\infty}$ does also.
-
-Let $\mathcal{U}$ be a cover of $X$, and refine it to open $F_\sigma$ sets with compact closures.
-Let $K:\oneptcomp{X}\to K[X]$ be the complement of a winning clustering strategy for $O$ such that $K(x)$ is a compact neighborhood of $x$ for all $x\in X$.
-
-Let $A(x)=\{p:x\not\in K(p)\}$.
-
-For each $x$, we claim $x$ is not even a limit point of $A(x)$.
-To see this, suppose there was such an $x$, and choose any compact neighborhood $N$ of $x$.
-If $x$ was a limit of $A(x)$, then $N\cap A(x)\not=\emptyset$.
-We choose $x_0\in N\cap A(x)$, and note $x\not\in K(x_0)$ since $x_0\in A(x)$.
-
-This makes $N\setminus K(x_0)$ a neighborhood of $x$, which must then intersect $A(x)$.
-We may then pick an $x_1$ in $N\cap A(x)\setminus K(x_0)$.
-By continuing this process inductively we find $x_n$ in $N\cap A(x) \setminus \bigcup_{0\leq i < n} K(x_i)$.
-Since the $x_n$ are all in the compact set $N$, the winning condition for $\clusgame{\oneptcomp{X}}{\infty}$ is not met for the play $\left<x_0,\oneptcomp{X}\setminus K(x_0),x_1,\oneptcomp{X}\setminus K(x_1),\dots\right>$, contradicting the fact that $K$ is the complement of a winning strategy.
-
-Let $K'(x)=Int(K(x)\setminus A(x))$.
-We note that $x\in K'(x)$ since $x$ was not a limit point or member of $A(x)$.
-So for each $K$ let $\{K'(x):x\in K\}$ be an open cover, and take a finite subset $F(K)\subset K$ which yields the subcover $\{K'(x):x\in F(K)\}$.
-
-Enumerate $\mathcal{U}=\{U_\alpha: \alpha < \lambda\}$. We define $\mathcal{U}_\alpha$ for $\alpha<\lambda$ to fulfill the following:
-
-\begin{itemize}
-\item $\mathcal{U}_\alpha$ is countable
-\item $\{U_\beta: \beta<\alpha\} \subseteq \bigcup_{\beta\leq\alpha} \mathcal{U}_\beta$
-\item If \[N_\alpha = \left(\bigcup \mathcal{U}_\alpha\right) \setminus \bigcup_{\beta<\alpha} \left( \bigcup \mathcal{U}_\beta \right)\]
-
-(that is, $N_\alpha$ contains the points covered by $\mathcal{U}_\alpha$ and not covered by a previous $\mathcal{U}_\beta$)
-
-then there exists a countable $S_\alpha\subseteq N_\alpha$ where \[ N_\alpha \subseteq \bigcup_{x\in S_\alpha} K'(x) \subseteq \bigcup_{x\in S_\alpha} K(x) \subseteq \bigcup \mathcal{U}_\alpha\]
-\end{itemize}
-
-To start, let $\mathcal{U}_0$ and $\mathcal{U}_\alpha$ for every limit $\alpha$ be the empty set.
-For the successor ordinal $\alpha+1$, let $\mathcal{U}_{\alpha+1,0}=\{U_\alpha\}$ and $S_{\alpha+1,0}=\emptyset$.
-Then let $O_{\alpha+1}=\bigcup_{\beta\leq\alpha}\bigcup\mathcal{U}_\beta$, the points covered by previous $\mathcal{U}_\beta$.
-
-We then define \[S_{\alpha+1,n+1}=\bigcup_{U\in\mathcal{U}_{\alpha+1,n}} F(Cl(U)\setminus O_{\alpha+1})\] and let $\mathcal{U}_{\alpha+1,n+1}\subseteq \mathcal{U}$ be a finite cover of $\bigcup_{x \in S_{\alpha+1,n+1}} K(x)$.
-Note that $S_{\alpha,n}$ and $U_{\alpha,n}$ are finite at every step $n$, so we may define $S_\alpha = \bigcup_{n<\omega} S_{\alpha,n}$ and $U_\alpha=\bigcup_{n<\omega} U_{\alpha,n}$.
-
-Such $\mathcal{U}_\alpha$ may be seen to fulfill the above requirements.
-
-Let $W_\alpha = \bigcup_{x\in S_\alpha} K'(x)$. Note $W_\alpha$ contains everything in $\mathcal{U}_\alpha$ not covered by lower $\mathcal{U}_\beta$.
-
-We now show the collection of $W_\alpha$ is point-finite.
-Suppose it wasn't: if $x \in W_{\alpha_n}$ for $\alpha_0<\alpha_1<\dots$, then for each $n$ choose some $x_n \in S_{\alpha_n}$ where $x \in K'(x_n)$.
-
-FINISH THIS
-
-\end{proof}
 
@@
 
-%%%%%%%%%
-%COMMENT%
-%%%%%%%%%
-\largecomment{
-\begin{lemma}
-$K$ lacks a "simple" 2-tactic which is a winning strategy in $\lfkpgame{\mathbb{X}}$.
-\end{lemma}
-
-\begin{proof}
-Let $a_n = \<0,\dots,0,1\>$ with $n$ zeros We define a simple 2-tactic as one which is dominated by a compact set of the form $K^*_S\cup L_{n+1}$, where $n$ is equal to the height of the highest observable move by $P$, and where $K^*_S = K_S \setminus \bigcup_{n} X_{a_n}$.
-
-Considering a simple 2-tactic $\sigma(\<x,s\>,\<y,t\>)$, we note it is dominated by $K^*_{S(x,y,n(s,t))}\cup L_{n(s,t)+1}$, where $n(s,t)=\max(|s|,|t|)$, and $$S(x,y,n) = \bigcup_{s,t\in 2^{\leq n}} S(\<x,s\>,\<y,t\>)$$ Strengthen $\sigma$ accordingly.
-
-But $K$ could, for fixed $x^*\in X$, define the 1-tactic $\tau(\<x,s\>) = \sigma(\<x,s\>,\<x^*,a_{|s|}\>)$.
-Since no winning $1$-tactic exists, let $\<x_0,s_0\>,\<x_1,s_1\>,\dots$ be a legal counter to $\tau$ clustering at $c\in C$.
-
-We claim $\<x_0,s_0\>, \<x^*,a_{|s_0|}\>, \<x_1,s_1\>, \<x^*,a_{|s_1|}\>, \dots$ is a counter to the 2-tactic.
-Since $\<x_0,s_0\>, \<x_1, s_1\>, \dots$ clusters at $c$, we need only show it is legal.
-By the definition of simple, each $\<x^*, a_{|s_i|}\>$ is a legal move.
-We note that since $\<x_{i+1},s_{i+1}\>$ was not forbidden by any $\tau(\<x_j,s_j\>)= K^*_{S(x_j,x^*,|s_j|+1)}\cup L_{|s_j|+2}$ for $j\leq i$, it could not be forbidden by $$\sigma(\<x_j,s_j\>,\<x^*,a_{|s_{j-1}|}\>) \subseteq \sigma(\<x_j,s_j\>,\<x^*,a_{|s_j|}\>) = K^*_{S(x_j,x^*,|s_j|+1)}\cup L_{|s_j|+2} $$
-\end{proof}
-
-\begin{theorem}
-$K\not\ktactwin{2}\lfkpgame{\mathbb{X}}$.
-\end{theorem}
-
-\begin{proof}
-Take the 2-tactic $\sigma(\<x,s\>,\<y,t\>)$.
-We define $S(x,y,n)$ and $m(x,y,n)$ so that \[ \bigcup_{s,t \in 2^{\leq n}} \sigma(\<x,s\>,\<y,t\>) \subseteq K_{S(x,y,n)} \cup L_{m(x,y,n)}\] and $|S(x,y,n)|, n < m(x,y,n)$.
-We've shown that every 2-tactial strategy can be improved so that it only considers $x$, $y$, and $\max(|s|,|t|)$.
-In addition, as there are $2^{m(x,y,\max(|s|,|t|))}$ copies of $X$ not forbidden by such an improved strategy, and at most \[\sum_{i=1}^{m(x,y,\max(|s|,|t|))-1} i < 2^{m(x,y,\max(|s|,|t|))}\] branches forbidden by this strategy, there is always some copy of $X$ at height $m(x,y,\max(|s|,|t|))$ completely legal to play within by $P$ after each move by $K$ according to this strategy.
-
-Now, define the simple 2-tactic $\tau(\<x,s\>,\<y,t\>)=K^*_{S(x,y,m(x,y,n(s,t))+1)} \cup L_{n(s,t)+1}$.
-Since there are no winning simple 2-tactics, let $\<x_0,s_0\>,\<x_1,s_1\>,\dots$ be a successful counter to $\tau$ clustering at $c$.
-
-We claim $\<x_0,t_0\>, \<x_1,t_1\>, \dots$ where $t_0=c\rest 0$, $t_1=c\rest 1$, and
-$$
-t_{i+2} = \left\{
-\begin{array}{ll}
-\text{arbitrary provided } |t_{i+2}| = m(x_i,x_{i+1},|t_{i+1}|) & x_{i+2}= x^* \text{ and } s_{i+2} \in \{a_n : n < \omega\} \text{ (1) } \\
-c\rest m(x_i,x_{i+1},|t_{i+1}|) & \text{otherwise and } s_{i+2} < c  \text{ (2) }\\
-\text{arbitrary extension of } s_{i+2} \text{ of length } m(x_i,x_{i+1},|t_{i+1}|) & \text{otherwise} \text{ (3) }
-\end{array}
-\right.
-$$
-is a legal counter to $\sigma$. It certainly clusters at $c$, so we need only show it is legal.
-
-Suppose $\<x_{i+2}, t_{i+2}\>$ were an illegal move.
-Then it must have been forbidden by some $K_{S(x_i,x_{i+1},|t_{i+1}|)}\cup L_{m(x_i,x_{i+1},|t_{i+1}|)}$.
-In case (1), we strengthened $m$ to ensure that $x^*$ was always legal somewhere on the first level not forbidden by $L_m$.
-In either case (2) or (3), $s_{i+2}<t_{i+2}$, keeping the move legal.
-
-\end{proof}
-}
-%%%%%%%%%%%%
-%ENDCOMMENT%
-%%%%%%%%%%%%
-
 \begin{theorem}
@@
 \begin{proof}
-(Vanished somewhere during my editing... looking for it now!)
+This is actually a corollary of G's theorem in [?]. The following is a direct game-theoretic proof.
+
+Suppose that $\sigma(\<x,s\>)$ was a winning strategy for $K$ and assume 
+  \[
+    \sigma(\<x,s\>) = \bigcup_{|t|\leq |s|} \sigma(\<x,t\>) = \sigma'(x,|s|)
+  \]
+Thus there exists some $f: \omega_1 \to \omega$ such that $\sigma'(x,f(\alpha))$ covers every neighborhood of $c_\alpha$ for all $x\in U_\alpha$.
+(If not, $P$ wins by taking the $\alpha$ for which $f$ is not defined, and may always play $\<x,s\>$ in a neighborhood of $c_\alpha$ for which $\sigma'(x,|s|)$ doesn't cover a neighborhood of $c_\alpha$.) Fix $n$ for which $f(\alpha)=n$ for $\alpha$ in an uncountable set $A$.
+
+Since the collection $\{U_\alpha : \alpha \in A\}$ is uncountable, it is not point-finite.
+Fix $x$ so that $x$ belongs to $U_\alpha$ for all $\alpha$ in an infinite $B \subseteq A$.
+Finally, consider $\sigma'(x,n)$.
+For each $\alpha\in B$, $\sigma'(x,f(\alpha))=\sigma'(x,n)$ covers $c_\alpha$.
+Since $\{c_\alpha : \alpha \in B\}$ is a closed infinite discrete set, we have a contradiction to the compactness of $\sigma'(x,n)$.
 \end{proof}

### 2013-02-15 au_topology_seminar_talk_2013_02_18.tex
Updated seminar talk with pictures and ZFC example

@@
 \usepackage{amsthm}
+
+\usepackage{graphicx}
 
@@
 
+\centerline{\bf An Example of Gruenhage's Compact-Point Game for which $K$ has }
+\centerline{\bf a winning strategy, but no winning $k$-tactical strategy}
+
+We construct a ZFC example given by Gary Gruenhage, inpsired by a ZFC+$\lnot$SH example due to Stephen Watson \cite{Watson}.
+
+\begin{theorem}\label{basic_x}
+There exists a compact, zero-dimensional topological space $X$ which has a point-countable cover $\mathcal{U} = \{U_c : c \in 2^\omega\}$ which is not the union of countably-many point-finite collections.
+\end{theorem}
+
+\begin{proof}
+Take a zero-dimensional Corson compact $Y$ of weight $2^\omega$, which is not Eberlein compact.
+It follows by \cite{G1} that $Y^2 \setminus \Delta = \{(y_1,y_2): y_1,y_2 \in Y, y_1\not=y_2\}$ is metalindelof, but not $\sigma$-metacompact.
+So every cover has a point-countable refinement of cardinality $2^\omega$, but no open refinement composed of the union of countably-many point-finite collections.
+\end{proof}
+
 \begin{example}
-Let $X$ be a zero-dimensional, compact L-space (hereditarally Lindeloff and non-separable).
-It is a fact that there exists a point-countable collection $\mathcal{U}=\{U_\alpha : \alpha<\omega_1\}$ of clopen sets in $X$, and it is also true that any point-finite subcollection of $\mathcal{U}$ is countable.
-%That is, if we let $A_x = \{\alpha : x \in U_\alpha\}$, then $|A_x|\leq\omega$ for all $x\in X$.
-
-Let $C = \{c_\alpha : \alpha <\omega_1\}$ be any uncountable subset of the Cantor space $2^\omega$. Let $X_s = X \times \{s\}$ for each $s \in 2^{<\omega}$, and $U_{\alpha,s} = U_\alpha \times \{s\}$.
-
-Finally, let \[\mathbb{X} = C \cup \bigcup_{s\in 2^{<\omega}} X_s\] be a tree of $2^{<\omega}$ copies of $X$, and where \[c_\alpha \cup \bigcup_{n < \omega} U_{\alpha, x_\alpha \restriction n}\] is an open set about each $c_\alpha$.
+Using the $X$ from Theorem \ref{basic_x}, let \[\mathbb{X} = (X \times 2^{<\omega}) \cup 2^\omega\] compose a disjoint union of $2^{<\omega}$ copies of $X$ along with a discrete copy of the Cantor Set $2^\omega$, and add open neighborhoods of the form:
+  \[
+    B_c = c \cup (U_c \times \{c\rest n : n < \omega\})
+  \]
+as seen in Figure \ref{fig:cantor_tree}.
 \end{example}
 
+\begin{figure}[p]
+  \centering
+  \includegraphics[width=6in]{cantor_tree_open.pdf}
+  \caption{The Cantor Tree space $\mathbb{X}$}
+  \label{fig:cantor_tree}
+\end{figure}
+
 \begin{definition}
-Let $S\in[\omega_1]^{<\omega}$ and $m<\omega$. Define 
-    \[K_S = \bigcup_{\alpha \in S} \left( c_\alpha \cup \left(\bigcup_{s < c_\alpha} U_{\alpha,s}\right)\right)\] 
-    \[ A = \{z^\frown \<1\> : z \in 1^{<\omega}\}\] 
-    \[ K^*_S = K_S \setminus \bigcup_{s \in A} X_s \] 
-and 
-    \[L_m = \bigcup_{s \in 2^{<m}} X_s\] 
+Let $S\in[2^\omega]^{<\omega}$ and $m<\omega$. Define 
+  \[
+    K_S = \bigcup_{c \in S} B_c
+  \] 
+  \[ 
+    A = \{z^\frown \<1\> : z \in 1^{<\omega}\}
+  \] 
+  \[ 
+    K^*_S = K_S \setminus (X \times A)
+  \] 
+  \[
+    L_m = X \times 2^{<m}
+  \] 
 and observe that every compact set is dominated by $K^*_S \cup L_m$ for some $S,m$.
-Intuitively, $K^*_S$ collects the branches of $U_\alpha$ converging up to $c_\alpha$ for each $\alpha \in S$ while avoiding copies $X_s$ of $X$ for each $s$ in an antichain $A$, and $L_m$ collects the copies $X_s$ of $X$ with $|s| < m$ at the base of the tree.
+
+Intuitively, $K^*_S$ collects the branches of $U_c$ converging up to each $c \in S$ while avoiding the copy of $X$ for each $s$ in an antichain $A$, and $L_m$ collects the copies of $X$ with $|s| < m$ at the base of the tree.
+(See Figure \ref{fig:cantor_tree_compact})
+\end{definition}
+
+\begin{figure}[p]
+  \centering
+  \includegraphics[width=6in]{cantor_tree_compact.pdf}
+  \caption{$K^*_S$ and $L_m$}
+  \label{fig:cantor_tree_compact}
+\end{figure}
+
+\begin{definition}
+$\lfkpgame{\mathbb{X}}$ is a topological game consisting of players $K$ and $P$.
+During each round, $K$ chooses a compact subset of $\mathbb{X}$, and $P$ chooses a point outside of any compact set previously played by $K$.
+$K$ wins the game if the set of points chosen by $P$ throughout all rounds of the game are locally finite in the space.
 \end{definition}
@@
 \begin{proposition}
-Without loss of generality, $P$ always plays points in $\bigcup_{s \in 2^{<\omega}} X_s$.
+Without loss of generality, we may assume $P$ always plays points in $X \times 2^{<\omega}$ throughout $\lfkpgame{\mathbb{X}}$.
 \end{proposition}
@@
 \begin{proposition}
-$K \win \lfkpgame{\mathbb{X}}$.
+$K \win \lfkpgame{\mathbb{X}}$
 \end{proposition}
@@
 \begin{proof}
-In response to a point $\<x,s\>$, $K$ observes that there are only countably many $\alpha$ such that $U_\alpha \times \{s\}$ contains $\<x,s\>$ (by point-countability of $X$).
-Enumerate these as $\alpha_n$.
-$K$ makes a promise that during round $m$, $K$ will forbid some superset of $K_{\{\alpha_n : n\leq m\}}$.
-Finally, $K$ also always forbids a superset of $L_{|s|+1}$.
+Let $x\in X$. $C^x = \{c \in C : x \in U_c\}$ is a countable collection by the point-countability of $\mathcal{U}$, so label its elements as $\{c^x_n: n<\omega\}$.
 
-Suppose $P$'s moves clustered at some point.
-Since $K$ forbade $L_{|s|+1}$ during each round, that point must be $c_\alpha$ for some $\alpha$.
-$P$'s play then must have included a subsequence of points $\<x_0,s_0\>,\<x_1,s_1\>,\<x_2,s_2\>\dots$ such that $x_n \in U_\alpha$ and $s_n \leq s_{n+1} \leq c_\alpha$.
-However, in response to $\<x_0,s_0\>$, $K$ made a promise to eventually forbid a superset of $K_{\{\alpha\}}$, making every $\<x_n,t_n\>$ illegal after that round.
+$K$ may use the strategy 
+  \[
+    \sigma(\<x_0,s_0\>,\dots,\<x_{n-1},s_{n-1}\>) = 
+    \bigcup_{i < n} K_{\{c^{x_i}_0,\dots,c^{x_i}_{n-1}\}} \cup L_{|s_i|+1}
+  \]
+
+This is a winning strategy because each point $\<x_i,s_i\>$ played by $P$ cannot be a part of a sequence converging to some $c^{x_i}_n$, since a $K_{\{c^{x_i}_0,\dots,c^{x_i}_n\}} \supseteq B_{c^{x_i}_n}$ was forbidden during round $n$.
 \end{proof}
@@
 \begin{proof}
-This is actually a corollary of G's theorem in [?]. The following is a direct game-theoretic proof.
+This is actually a corollary of Gruenhage's theorem in \cite{G2} by proving $\mathbb{X}$ is not metacompact. The following is a direct game-theoretic proof.
 
-Suppose that $\sigma(\<x,s\>)$ was a winning strategy for $K$ and assume 
+Suppose that $\sigma(\<x,s\>)$ was a winning tactical strategy for $K$ and define the compact set 
   \[
-    \sigma(\<x,s\>) = \bigcup_{|t|\leq |s|} \sigma(\<x,t\>) = \sigma'(x,|s|)
+    \sigma'(x,n) = \bigcup_{|s|\leq n} \sigma(\<x,s\>)
   \]
-Thus there exists some $f: \omega_1 \to \omega$ such that $\sigma'(x,f(\alpha))$ covers every neighborhood of $c_\alpha$ for all $x\in U_\alpha$.
-(If not, $P$ wins by taking the $\alpha$ for which $f$ is not defined, and may always play $\<x,s\>$ in a neighborhood of $c_\alpha$ for which $\sigma'(x,|s|)$ doesn't cover a neighborhood of $c_\alpha$.) Fix $n$ for which $f(\alpha)=n$ for $\alpha$ in an uncountable set $A$.
 
-Since the collection $\{U_\alpha : \alpha \in A\}$ is uncountable, it is not point-finite.
-Fix $x$ so that $x$ belongs to $U_\alpha$ for all $\alpha$ in an infinite $B \subseteq A$.
-Finally, consider $\sigma'(x,n)$.
-For each $\alpha\in B$, $\sigma'(x,f(\alpha))=\sigma'(x,n)$ covers $c_\alpha$.
-Since $\{c_\alpha : \alpha \in B\}$ is a closed infinite discrete set, we have a contradiction to the compactness of $\sigma'(x,n)$.
+There exists some $f: 2^\omega \to \omega$ such that for all $x\in U_c$, $\sigma'(x,f(c))$ covers some $B_c \setminus L_m$. (If not, $P$ counters by simply always playing in $B_c \setminus L_m$.)
+
+Recall that $\mathcal{U}$ is not the union of the countably-many point-finite collections, and 
+  \[
+    \mathcal{U} = \bigcup_{n<\omega} \{U_c : f(c) = n\}
+  \]
+so we may find choose $n$ where $\mathcal{U}_n = \{U_c : f(c) = n\}$ is not point-finite. Fix $x$ so that $x$ belongs to each of $\{U_{c_0},U_{c_1},\dots\} \subseteq \mathcal{U}_n$.
+
+For each $c_i$, $\sigma'(x,f(c_i))=\sigma'(x,n)$ covers $c_i$. Thus $\sigma'(x,n) \supseteq \{c_0,c_1,\dots\}$ is not compact, a contradiction.
 \end{proof}
+
+\newpage
 
@@
 \begin{proof}
-Suppose $\sigma(\<x,s\>,\<y,t\>)$ was a winning 2-tactical strategy. We may define $S(x,y,n)\in [\omega_1]^{<\omega}$ (increasing on $n$) and $n<m(x,y,n)<\omega$ such that for each $(x,y)$,
+Suppose $\sigma(\<x,s\>,\<y,t\>)$ was a winning 2-tactical strategy.
+Without loss of generality we assume it ignores order.
+We may define $S(x,y,n)\in [2^\omega]^{<\omega}$ (increasing on $n$) and $n<m(x,y,n)<\omega$ such that for each $(x,y)$,
   \[
@@
 \]
-successfully countered $\tau$ by clustering at $c\in C$ (the strategy trivially prevents clustering elsewhere). Let $z_n = \<0,\dots,0\>$ with $n$ zeros. We claim
+successfully countered $\tau$ by clustering at $c\in 2^\omega$ (the strategy trivially prevents clustering elsewhere). Let $z_n = \<0,\dots,0\>$ with $n$ zeros. We claim
 \[
@@
 \begin{proof}
-The proof proceeds in parallel to the proof of $K\not\ktactwin{2}\lfkpgame{\mathbb{X}}$.
+The proof proceeds in parallel to the proof of $K\not\ktactwin{2}\lfkpgame{\mathbb{X}}$, and in fact is just a generalization of said proof (at the cost of simplicity).
 
 Suppose $\sigma(\<x_0,s_0\>,\dots,\<x_{k},s_{k}\>)$ was a winning $(k+1)$-tactical strategy.
-We may define $S(x_0,\dots,x_{k},n)\in [\omega_1]^{<\omega}$ (increasing on $n$) and $n<m(x_0,\dots,x_{k},n)<\omega$ such that for each $(x_0,\dots,x_{k})$,
+Without loss of generality we assume it ignores order.
+We may define $S(x_0,\dots,x_{k},n)\in [2^\omega]^{<\omega}$ (increasing on $n$) and $n<m(x_0,\dots,x_{k},n)<\omega$ such that for each $(x_0,\dots,x_{k})$,
   \[
@@
 
+\begin{thebibliography}{9}
+
+\bibitem{G1}
+  G. Gruenhage,
+  \emph{Covering Properties on $X^2\setminus\Delta$, $W$-sets, and Compact Subsets of $\Sigma$-Products}.
+  Topology Appl. 17 (1984), 287-304
+
+\bibitem{G2}
+  G. Gruenhage,
+  \emph{Games, Covering Properites, and Eberlein Compacts}.
+  Topology Appl. 23 (1986), 291-297
+
+\bibitem{Watson}
+  S. Watson,
+  \emph{Locally compact normal meta-Lindelöf spaces may not be paracompact: 
+  an application of uniformization and Suslin lines}. 
+  Proc. Amer. Math. Soc. 98 (1986), no. 4, 676–680.
+
+\end{thebibliography}
+
 \end{document}

### 2013-02-18 au_topology_seminar_talk_2013_02_18.tex
Final touches to seminar talk feb 2013

@@
 \centerline{\bf An Example of Gruenhage's Compact-Point Game for which $K$ has }
-\centerline{\bf a winning strategy, but no winning $k$-tactical strategy}
+\centerline{\bf a winning strategy, but no winning $k$-Markov strategy}
 
@@
 \begin{theorem}\label{basic_x}
-There exists a compact, zero-dimensional topological space $X$ which has a point-countable cover $\mathcal{U} = \{U_c : c \in 2^\omega\}$ which is not the union of countably-many point-finite collections.
+There exists a compact, zero-dimensional topological space $X$ which has a point-countable cover $\mathcal{U} = \{U_c : c \in 2^\omega\}$ of clopen sets which is not the union of countably-many point-finite collections.
 \end{theorem}
@@
 Take a zero-dimensional Corson compact $Y$ of weight $2^\omega$, which is not Eberlein compact.
-It follows by \cite{G1} that $Y^2 \setminus \Delta = \{(y_1,y_2): y_1,y_2 \in Y, y_1\not=y_2\}$ is metalindelof, but not $\sigma$-metacompact.
-So every cover has a point-countable refinement of cardinality $2^\omega$, but no open refinement composed of the union of countably-many point-finite collections.
+It follows by \cite{G1} that $Y^2 \setminus \Delta = \{(y_1,y_2): y_1,y_2 \in Y, y_1\not=y_2\}$ is metalindel\"of, but not $\sigma$-metacompact.
+
+Let $X = Y^2$, and let $\mathcal{V}$ be an open cover of $X$ by $2^\omega$ clopen sets.
+Since $Y^2 \setminus \Delta$ is metalindel\"of and $\Delta$ is compact, let $\mathcal{V}'$ be a refinement of $\mathcal{U}$ such that it is a point-countable cover of $Y^2 \setminus \Delta$, and let $\mathcal{V}''$ be a refinement of $\mathcal{U}$ such that it is finite cover of $\Delta$.
+Then $\mathcal{U} = \mathcal{V}'\cup\mathcal{V}''$ is point-countable on $Y^2$, and if it was the union of countably-many point-finite collections, so would $\mathcal{V}'$ (making $Y^2\setminus \Delta$ $\sigma$-metacompact, contradiction).
 \end{proof}
 
-\begin{example}
-Using the $X$ from Theorem \ref{basic_x}, let \[\mathbb{X} = (X \times 2^{<\omega}) \cup 2^\omega\] compose a disjoint union of $2^{<\omega}$ copies of $X$ along with a discrete copy of the Cantor Set $2^\omega$, and add open neighborhoods of the form:
+\begin{definition}
+Using the $X$ from Theorem \ref{basic_x}, let \[\mathbb{X} = (X \times 2^{<\omega}) \cup 2^\omega\] compose a topological sum of $2^{<\omega}$ copies of $X$ along with a discrete copy of the Cantor Set $2^\omega$, and add open (in fact, compact) neighborhoods of the form:
   \[
@@
 as seen in Figure \ref{fig:cantor_tree}.
-\end{example}
+\end{definition}
 
@@
   \] 
-and observe that every compact set is dominated by $K^*_S \cup L_m$ for some $S,m$.
+and observe that every compact set is dominated by the compact set $K^*_S \cup L_m$ for some $S,m$.
 
@@
 $K$ wins the game if the set of points chosen by $P$ throughout all rounds of the game are locally finite in the space.
+\end{definition}
+
+\begin{definition}
+We say $I \win G$ if Player $I$ has a winning strategy in the game $G$.
+
+We say $I \tactwin G$ (resp.
+$I \ktactwin{k} G$) if Player $I$ has a winning tactical (resp.
+$k$-tactical) strategy in the game $G$, a strategy depending on only the ($k$) most recent move(s) of the opponent.
+
+We say $I \markwin G$ (resp.
+$I \kmarkwin{k} G$) if Player $I$ has a winning Markov (resp.
+$k$-Markov) strategy in the game $G$, a strategy depending on only the ($k$) most recent move(s) of the opponent and the current round number.
 \end{definition}
@@
 
-This is a winning strategy because each point $\<x_i,s_i\>$ played by $P$ cannot be a part of a sequence converging to some $c^{x_i}_n$, since a $K_{\{c^{x_i}_0,\dots,c^{x_i}_n\}} \supseteq B_{c^{x_i}_n}$ was forbidden during round $n$.
+This is a winning strategy because each move $\<x_i,s_i\>$ by $P$ cannot be a part of a subsequence of the play converging to any $c^{x_i}_n$, since $K_{\{c^{x_i}_0,\dots,c^{x_i}_n\}} \supseteq B_{c^{x_i}_n}$ was forbidden during round $n$.
 \end{proof}
@@
 \begin{proof}
-This is actually a corollary of Gruenhage's theorem in \cite{G2} by proving $\mathbb{X}$ is not metacompact. The following is a direct game-theoretic proof.
+This is actually a corollary of Gruenhage's theorem in \cite{G2}: $\mathbb{X}$ is locally compact (each point is either in some $X$ or in some $B_c$) but not metacompact (any cover of $2^\omega$ necessarily will have infinite overlap at some $X \times \{s\}$).
+However, we proceed with a direct game-theoretic proof.
 
@@
   \]
-so we may find choose $n$ where $\mathcal{U}_n = \{U_c : f(c) = n\}$ is not point-finite. Fix $x$ so that $x$ belongs to each of $\{U_{c_0},U_{c_1},\dots\} \subseteq \mathcal{U}_n$.
+so we may choose $n$ where $\mathcal{U}_n = \{U_c : f(c) = n\}$ is not point-finite. Fix $x$ so that $x$ belongs to each of $\{U_{c_0},U_{c_1},\dots\} \subseteq \mathcal{U}_n$.
 
-For each $c_i$, $\sigma'(x,f(c_i))=\sigma'(x,n)$ covers $c_i$. Thus $\sigma'(x,n) \supseteq \{c_0,c_1,\dots\}$ is not compact, a contradiction.
+For each $c_i$, $\sigma'(x,f(c_i))=\sigma'(x,n)$ covers $c_i$. Thus $\sigma'(x,n) \supseteq \{c_0,c_1,\dots\}$ is a compact set covering a closed discrete subset, a contradiction.
 \end{proof}
-
-\newpage
 
@@
 
-Since $\<x_{i+1},s_{i+1}\>$ was legal against $\tau$, it avoided
+Since $\<x_{i+1},s_{i+1}\>$ was legal against $\tau$, for $h\leq i$ it avoided
   \[
@@
   \]
-for $h\leq i$. And when $h<i$, we see it avoids:
+and when $h<i$, we see it avoids:
   \[
@@
 \end{proof}
+
+\newpage
 
@@
   \]
-for $h\leq i$. And when $h<i$, we see it avoids both:
+and when $h<i$, we see it avoids both:
   \[
@@
 
+\begin{corollary}
+$K\not\kmarkwin{k}\lfkpgame{\mathbb{X}}$.
+\end{corollary}
+
+\begin{proof}
+Let $\sigma(\<x_0,s_0\>,\dots,\<x_{k-1},s_{k-1}\>,n)$ be a winning $k$-Markov strategy for $K$ increasing on $n$. We define a $k$-tactical strategy
+  \[
+    \tau(\<x_0,s_0\>,\dots,\<x_{k-1},s_{k-1}\>) = \sigma(\<x_0,s_0\>,\dots,\<x_{k-1},s_{k-1}\>,\max_{i<k}(|s_i|)) \cup L_{\max_{i<k}(|s_i|)+1}
+  \]
+and observe that since for any legal play of the game, the round number $n \leq \max_{i<k}(|s_i|)$, we know $\tau$ always yields supersets of $\sigma$, and is thus also a winning strategy, contradiction.
+\end{proof}
+
 \begin{thebibliography}{9}
@@
   S. Watson,
-  \emph{Locally compact normal meta-Lindelöf spaces may not be paracompact: 
+  \emph{Locally compact normal meta-Lindel\"of spaces may not be paracompact: 
   an application of uniformization and Suslin lines}. 

### 2013-03-14 au_topology_seminar_talk_2013_02_18.tex
Added readme, working on ZFC example for k-Markov result in LFKP

@@
-\documentclass[11pt]{article}
-
-\pdfpagewidth 8.5in
-\pdfpageheight 11in
-
-\setlength\topmargin{0in}
-\setlength\headheight{0in}
-\setlength\headsep{0.2in}
-\setlength\textheight{8in}
-\setlength\textwidth{6in}
-\setlength\oddsidemargin{0in}
-\setlength\evensidemargin{0in}
-\setlength\parindent{0.25in}
-\setlength\parskip{0.1in}
-
-\usepackage{amssymb}
-\usepackage{amsfonts}
-\usepackage{amsmath}
-\usepackage{mathtools}
-\usepackage{amsthm}
-
-\usepackage{graphicx}
-
-      \theoremstyle{plain}
-      \newtheorem{theorem}{Theorem}
-      \newtheorem{lemma}[theorem]{Lemma}
-      \newtheorem{corollary}[theorem]{Corollary}
-      \newtheorem{proposition}[theorem]{Proposition}
-      \newtheorem{conjecture}[theorem]{Conjecture}
-      \newtheorem{question}[theorem]{Question}
-      \newtheorem{example}[theorem]{Example}
-
-      \theoremstyle{definition}
-      \newtheorem{definition}[theorem]{Definition}
-
-      \theoremstyle{remark}
-      \newtheorem{remark}[theorem]{Remark}
-
-% Strategy uparrow shortcuts
-\newcommand{\win}{\uparrow}
-\newcommand{\prewin}{\uparrow_{\text{pre}}}
-\newcommand{\markwin}{\uparrow_{\text{mark}}}
-\newcommand{\tactwin}{\uparrow_{\text{tact}}}
-\newcommand{\ktactwin}[1]{\uparrow_{#1\text{-tact}}}
-\newcommand{\kmarkwin}[1]{\uparrow_{#1\text{-mark}}}
-\newcommand{\codewin}{\uparrow_{\text{code}}}
-\newcommand{\limitwin}{\uparrow_{\text{limit}}}
-
-\newcommand{\oneptcomp}[1]{#1^*}
-
-\newcommand{\congame}[2]{Con_{O,P}(#1,#2)}
-\newcommand{\clusgame}[2]{Clus_{O,P}(#1,#2)}
-
-\newcommand{\lfkpgame}[1]{LF_{K,P}(#1)}
-\newcommand{\lfklgame}[1]{LF_{K,L}(#1)}
-
-\newcommand{\pfgame}[1]{PF_{F,C}(#1)}
-
-\newcommand{\sigmaprodr}[1]{\Sigma\mathbb{R}^{#1}}
-\newcommand{\sigmaprodtwo}[1]{\Sigma2^{#1}}
-
-\newcommand{\<}{\langle}
-\renewcommand{\>}{\rangle}
-
-\newcommand{\rest}{\restriction}
-
-\newcommand{\largecomment}[1]{}
+\input{./header.tex}
 
@@
 We construct a ZFC example given by Gary Gruenhage, inpsired by a ZFC+$\lnot$SH example due to Stephen Watson \cite{Watson}.
+We require a slight modification of a result of Gruenhage and Michael \cite{Michael}:
+
+\begin{theorem}\label{michael}
+Let $X$ be a meta-Lindel\"of, locally Lindel\"of regular space, and let $\mc{B}$ be a base of cardinality $\kappa$ for $X$.
+Then $X$ has a cover $\mc{B}'\subseteq\mc{B}$ of cardinality $\kappa$ such that $\{\close{B}:B\in\mc{B}'\}$ is point-countable.
+\end{theorem}
+
+\begin{proof}
+asdf?
+\end{proof}
 
 \begin{theorem}\label{basic_x}
-There exists a compact, zero-dimensional topological space $X$ which has a point-countable cover $\mathcal{U} = \{U_c : c \in 2^\omega\}$ of clopen sets which is not the union of countably-many point-finite collections.
+There exists a compact, zero-dimensional topological space $X$ which has a point-countable cover $\mc{U} = \{U_c : c \in 2^\omega\}$ of clopen sets which is not $\sigma$-point-finite (the union of countably-many point-finite collections).
 \end{theorem}
@@
 Take a zero-dimensional Corson compact $Y$ of weight $2^\omega$, which is not Eberlein compact.
-It follows by \cite{G1} that $Y^2 \setminus \Delta = \{(y_1,y_2): y_1,y_2 \in Y, y_1\not=y_2\}$ is metalindel\"of, but not $\sigma$-metacompact.
+(See Todercevic \cite{Todercevic} for an example.) It follows by \cite{G1} that $Y^2$ is hereditarily metaLindel\"of, but not hereditarily $\sigma$-metacompact.
+Let $X$ be a non-$\sigma$-metacompact subset of $Y^2$, and let $\mc{V}$ be an open cover of $X$ such that no $\sigma$-point-finite open refinement exists.
 
-Let $X = Y^2$, and let $\mathcal{V}$ be an open cover of $X$ by $2^\omega$ clopen sets.
-Since $Y^2 \setminus \Delta$ is metalindel\"of and $\Delta$ is compact, let $\mathcal{V}'$ be a refinement of $\mathcal{U}$ such that it is a point-countable cover of $Y^2 \setminus \Delta$, and let $\mathcal{V}''$ be a refinement of $\mathcal{U}$ such that it is finite cover of $\Delta$.
-Then $\mathcal{U} = \mathcal{V}'\cup\mathcal{V}''$ is point-countable on $Y^2$, and if it was the union of countably-many point-finite collections, so would $\mathcal{V}'$ (making $Y^2\setminus \Delta$ $\sigma$-metacompact, contradiction).
+Let $\mc{B}$ be a clopen base for $X$ of cardinality $2^\omega$ which is a refinement of $\mc{V}$.
+Then as $X$ is metaLindel\"of, locally Lindel\"of, and regular, by Thm \ref{michael}, let $\mc{U}\subseteq \mc{B}$ be a point-countable clopen refinement of $\mc{V}$ of cardinality $2^\omega$, which cannot be $\sigma$-point-finite.
 \end{proof}
@@
 \begin{proof}
-Let $x\in X$. $C^x = \{c \in C : x \in U_c\}$ is a countable collection by the point-countability of $\mathcal{U}$, so label its elements as $\{c^x_n: n<\omega\}$.
+Let $x\in X$. $C^x = \{c \in C : x \in U_c\}$ is a countable collection by the point-countability of $\mc{U}$, so label its elements as $\{c^x_n: n<\omega\}$.
 
@@
 
-Recall that $\mathcal{U}$ is not the union of the countably-many point-finite collections, and 
+Recall that $\mc{U}$ is not the union of the countably-many point-finite collections, and 
   \[
-    \mathcal{U} = \bigcup_{n<\omega} \{U_c : f(c) = n\}
+    \mc{U} = \bigcup_{n<\omega} \{U_c : f(c) = n\}
   \]
-so we may choose $n$ where $\mathcal{U}_n = \{U_c : f(c) = n\}$ is not point-finite. Fix $x$ so that $x$ belongs to each of $\{U_{c_0},U_{c_1},\dots\} \subseteq \mathcal{U}_n$.
+so we may choose $n$ where $\mc{U}_n = \{U_c : f(c) = n\}$ is not point-finite. Fix $x$ so that $x$ belongs to each of $\{U_{c_0},U_{c_1},\dots\} \subseteq \mc{U}_n$.
 
@@
 
+\bibitem{Michael}
+  G. Gruenhage and E. Michael, 
+  \emph{A result on shrinkable open covers}.
+  Proceedings of the 1983 topology conference (Houston, Tex., 1983), 1983, pp. 37–43.
+
+\bibitem{Todercevic}
+  S. Todercevic,
+  \emph{Trees and linearly ordered sets}.
+  Handbook of Set-theoretic Topology (North-Holland, Amsterdam, 1984), pp. 235-293
+
 \bibitem{Watson}

### 2013-03-14 au_topology_seminar_talk_2013_02_18.tex
updated todos

@@
 (See Todercevic \cite{Todercevic} for an example.) It follows by \cite{G1} that $Y^2$ is hereditarily metaLindel\"of, but not hereditarily $\sigma$-metacompact.
-Let $X$ be a non-$\sigma$-metacompact subset of $Y^2$, and let $\mc{V}$ be an open cover of $X$ such that no $\sigma$-point-finite open refinement exists.
+Note $X=Y^2\setminus \Delta$ is an open non-$\sigma$-metacompact subspace of $Y^2$, and thus locally compact, and let $\mc{V}$ be an open cover of $X$ such that no $\sigma$-point-finite open refinement exists.
 
-Let $\mc{B}$ be a clopen base for $X$ of cardinality $2^\omega$ which is a refinement of $\mc{V}$.
+Let $\mc{B}$ be a clopen base for $X$ of cardinality $\leq 2^\omega$ which is a refinement of $\mc{V}$.
 Then as $X$ is metaLindel\"of, locally Lindel\"of, and regular, by Thm \ref{michael}, let $\mc{U}\subseteq \mc{B}$ be a point-countable clopen refinement of $\mc{V}$ of cardinality $2^\omega$, which cannot be $\sigma$-point-finite.
+
+% TODO finish this for \leq 2^\omega
 \end{proof}
@@
 \begin{definition}
-Using the $X$ from Theorem \ref{basic_x}, let \[\mathbb{X} = (X \times 2^{<\omega}) \cup 2^\omega\] compose a topological sum of $2^{<\omega}$ copies of $X$ along with a discrete copy of the Cantor Set $2^\omega$, and add open (in fact, compact) neighborhoods of the form:
+Using the $X$ from Theorem \ref{basic_x}, let \[\mathbb{X} = (X \times 2^{<\omega}) \cup 2^\omega\] compose a topological sum of $2^{<\omega}$ copies of $X$ along with a discrete copy of the Cantor Set $\leq 2^\omega$, and add open (in fact, compact) neighborhoods of the form:
   \[

### 2013-03-28 menger.tex
Added example of markov menger game

--- 2013-01-30 menger.tex
@@
   \begin{definition}
-    In the two-player game $\mengame{X}$ player $C$ chooses open covers $\mathcal{U}_n$ of $X$, followed by player $S$ choosing a finite subcollection $\mathcal{F}_n\subseteq\mathcal{U}_n$.
-$S$ wins if $\bigcup_{n<\omega} \mathcal{F}_n$ is a cover of $X$.
+    In the two-player game $\mengame{X}$ player $C$ chooses open covers $\mathcal{U}_n$ of $X$, followed by player $F$ choosing a finite subcollection $\mathcal{F}_n\subseteq\mathcal{U}_n$.
+$F$ wins if $\bigcup_{n<\omega} \mathcal{F}_n$ is a cover of $X$.
   \end{definition}
@@
     Since $X$ is Lindelof, we can assume $C$ plays only countable covers of $X$.
-Then, since $S$ is choosing finite subsets, we may assume $S$ chooses some initial segement of the countable cover.
+Then, since $F$ is choosing finite subsets, we may assume $F$ chooses some initial segement of the countable cover.
 In turn, we can assume $C$ plays an increasing open cover $\{U_0,U_1,\dots\}$ where $U_n\subseteq U_{n+1}$.
-And in that case, it's suffient to assume $S$ simply chooses a singleton subset of each cover.
-And finally, since choices made by $S$ are already covered, we can assume that every open set in a cover played by $C$ covers the sets chosen by $S$ previously.
+And in that case, it's suffient to assume $F$ simply chooses a singleton subset of each cover.
+And finally, since choices made by $F$ are already covered, we can assume that every open set in a cover played by $C$ covers the sets chosen by $F$ previously.
 
@@
 
-    We may observe that if $S$ can find an $f:\omega\to\omega$ such that $\bigcup_{n<\omega}U_{f\rest (n+1)} = X$, she can use $\{U_{f\rest 0}\}, \{U_{f\rest 1}\}, \dots$ to counter $C$'s strategy.
+    We may observe that if $F$ can find an $f:\omega\to\omega$ such that $\bigcup_{n<\omega}U_{f\rest (n+1)} = X$, she can use $\{U_{f\rest 0}\}, \{U_{f\rest 1}\}, \dots$ to counter $C$'s strategy.
 
@@
 
+  \begin{proposition}
+    $X$ is compact if and only if $F \tactwin \mengame{X}$
+  \end{proposition}
+
+  \begin{proof}
+    Assume $X$ is compact. For each open cover played by $C$, pick the finite subcover.
+
+    Assume $F$ has a winning tactical strategy. For any open cover, have $C$ play only it during the entire game. $F$'s only choice must be a finite subcover.
+  \end{proof}
+
+  \begin{proposition}
+    If $X$ is $\sigma$-compact then $F \markwin \mengame{X}$
+  \end{proposition}
+
+  \begin{proof}
+    Let $X=\bigcup_{n<\omega} X_n$ for compact $X_n$. On round $n$, $F$ picks the finite subcover of $C$'s open cover of $X_n$.
+  \end{proof}
+
+  Due to Telgarski in ``On Games of Topsoe'':
+
+  \begin{theorem}
+    For metrizable $X$, $X$ is $\sigma$-compact if and only if $F \win \mengame{X}$.
+  \end{theorem}
+
+  In a question I posed to G, he answered:
+
+  \begin{lemma}
+    For all $\alpha_0, \alpha_1, \dots < \omega_1$ and functions $\tau:\omega_1\times\omega \rightarrow [\omega_1]^{<\omega}$, $\{\tau(\alpha_n,n): n<\omega\}$ is not a cover for $\{\beta:\forall n<\omega (\beta < \alpha_n)\}$.
+  \end{lemma}
+
+  \begin{proof}
+    Let $P_n = \{\beta: \beta < \alpha \Rightarrow \beta \in \tau(\alpha, n)\}$.
+Observe that each $P_n$ is finite; else there is some $\alpha$ larger than every member of $P_n$ such that $P_n \subseteq \tau(\alpha, n)$.
+
+    Choose $\beta \not\in \bigcup_{n<\omega} P_n$. Then for each $n<\omega$, pick $\alpha_n>\beta$ such that $\beta \not\in \tau(\alpha_n, n)$.
+  \end{proof}
+
+  Note that the one-point Lindel\"ofication of discrete $\omega_1$, $\oneptlind{\omega_1}$, is not $\sigma$-compact. With the above lemma, we may see that:
+
+  \begin{example}
+    $F \win \mengame{\oneptlind{\omega_1}}$ but $F \not\markwin \mengame{\oneptlind{\omega_1}}$.
+  \end{example}
+
+  \begin{proof}
+    First, we see $F$ has a simple perfect information strategy: in response to the initial cover of $\oneptlind{\omega_1}$, $F$ chooses a co-countable neighborhood of $\infty$.
+On successive turns she may pick a single set from $C$'s covers to cover the countable remainder.
+
+    Now, suppose that $\sigma(\mc{U}, n)$ was a winning Markov strategy and aim for a contradiction.
+Consider the covers \[\mc{U}(\alpha) = \{[\alpha,\omega_1)\cup\{\infty\}\} \cup \{\{\beta\}:\beta < \alpha\}\] and define $\tau(\alpha,n)$ to be the union of singletons chosen by $\sigma(\mathcal{U}(\alpha),n)$.
+As $\sigma$ was a winning strategy, for all $\alpha_0, \alpha_1, \dots < \omega_1$, $\{\sigma(\mathcal{U}(\alpha_n),n): n<\omega\}$ must cover $\oneptlind{\omega_1}$, and thus $\{\tau(\alpha_n,n): n<\omega\}$ must cover $\{\beta:\forall n<\omega (\beta < \alpha_n)\}$, contradiction.
+  \end{proof}
+
+  The question remains:
+
+  \begin{question}
+    Does $F \markwin \mengame{X}$ imply $X$ is $\sigma$-compact?
+  \end{question}
+
+  % Let $\sigma(\mathcal{U},n)$ be $F$'s winning Markov strategy.
+
 \end{document}

### 2013-03-28 au_topology_seminar_talk_2013_02_18.tex
Updated TODOs and fixed seminar talk

@@
 
-We construct a ZFC example given by Gary Gruenhage, inpsired by a ZFC+$\lnot$SH example due to Stephen Watson \cite{Watson}.
-We require a slight modification of a result of Gruenhage and Michael \cite{Michael}:
+We construct a ZFC example given by Gary Gruenhage, inpsired by a ZFC+$\lnot$SH example due to Stephen Watson \cite{Watson}. We require a result of Gruenhage and Michael \cite{Michael}:
 
 \begin{theorem}\label{michael}
-Let $X$ be a meta-Lindel\"of, locally Lindel\"of regular space, and let $\mc{B}$ be a base of cardinality $\kappa$ for $X$.
-Then $X$ has a cover $\mc{B}'\subseteq\mc{B}$ of cardinality $\kappa$ such that $\{\close{B}:B\in\mc{B}'\}$ is point-countable.
+Let $X$ be a meta-Lindel\"of, locally Lindel\"of regular space, and let $\mc{B}$ be a base for $X$.
+Then $X$ has a cover $\mc{B}'\subseteq\mc{B}$ such that $\{\close{B}:B\in\mc{B}'\}$ is point-countable.
 \end{theorem}
 
-\begin{proof}
-asdf?
-\end{proof}
-
 \begin{theorem}\label{basic_x}
-There exists a compact, zero-dimensional topological space $X$ which has a point-countable cover $\mc{U} = \{U_c : c \in 2^\omega\}$ of clopen sets which is not $\sigma$-point-finite (the union of countably-many point-finite collections).
+There exists a compact, zero-dimensional topological space $X$ and an uncountable subspace $C\subseteq 2^\omega$ of the Cantor Set, such that $X$ has a point-countable cover $\mc{U} = \{U_c : c \in C\}$ of clopen sets which is not $\sigma$-point-finite (the union of countably-many point-finite collections).
 \end{theorem}
@@
 
-Let $\mc{B}$ be a clopen base for $X$ of cardinality $\leq 2^\omega$ which is a refinement of $\mc{V}$.
-Then as $X$ is metaLindel\"of, locally Lindel\"of, and regular, by Thm \ref{michael}, let $\mc{U}\subseteq \mc{B}$ be a point-countable clopen refinement of $\mc{V}$ of cardinality $2^\omega$, which cannot be $\sigma$-point-finite.
-
-% TODO finish this for \leq 2^\omega
+Let $\mc{B}$ be a clopen base for $X$ of cardinality $2^\omega$ which is a refinement of $\mc{V}$.
+Then as $X$ is metaLindel\"of, locally Lindel\"of, and regular, by Thm \ref{michael}, let $\mc{U}\subseteq \mc{B}$ be a point-countable clopen refinement of $\mc{V}$ of cardinality $\leq 2^\omega$, which cannot be $\sigma$-point-finite (and is thus uncountable).
 \end{proof}
@@
 \begin{definition}
-Using the $X$ from Theorem \ref{basic_x}, let \[\mathbb{X} = (X \times 2^{<\omega}) \cup 2^\omega\] compose a topological sum of $2^{<\omega}$ copies of $X$ along with a discrete copy of the Cantor Set $\leq 2^\omega$, and add open (in fact, compact) neighborhoods of the form:
+Using the $X$ from Theorem \ref{basic_x}, let \[\mathbb{X} = (X \times 2^{<\omega}) \cup 2^\omega\] compose a topological sum of $2^{<\omega}$ copies of $X$ along with a discrete copy of a subspace $C \subseteq 2^\omega$ of the Cantor Set, and add open (in fact, compact) neighborhoods of the form:
   \[
@@
 \begin{definition}
-Let $S\in[2^\omega]^{<\omega}$ and $m<\omega$. Define 
+Let $S\in[C]^{<\omega}$ and $m<\omega$. Define 
   \[
@@
 \begin{proof}
-This is actually a corollary of Gruenhage's theorem in \cite{G2}: $\mathbb{X}$ is locally compact (each point is either in some $X$ or in some $B_c$) but not metacompact (any cover of $2^\omega$ necessarily will have infinite overlap at some $X \times \{s\}$).
+This is actually a corollary of Gruenhage's theorem in \cite{G2}: $\mathbb{X}$ is locally compact (each point is either in some $X$ or in some $B_c$) but not metacompact (any cover of $C$ necessarily will have infinite overlap at some $X \times \{s\}$).
 However, we proceed with a direct game-theoretic proof.
@@
 
-There exists some $f: 2^\omega \to \omega$ such that for all $x\in U_c$, $\sigma'(x,f(c))$ covers some $B_c \setminus L_m$. (If not, $P$ counters by simply always playing in $B_c \setminus L_m$.)
+There exists some $f: C \to \omega$ such that for all $x\in U_c$, $\sigma'(x,f(c))$ covers some $B_c \setminus L_m$. (If not, $P$ counters by simply always playing in $B_c \setminus L_m$.)
 
@@
 Without loss of generality we assume it ignores order.
-We may define $S(x,y,n)\in [2^\omega]^{<\omega}$ (increasing on $n$) and $n<m(x,y,n)<\omega$ such that for each $(x,y)$,
+We may define $S(x,y,n)\in [C]^{<\omega}$ (increasing on $n$) and $n<m(x,y,n)<\omega$ such that for each $(x,y)$,
   \[
@@
 \]
-successfully countered $\tau$ by clustering at $c\in 2^\omega$ (the strategy trivially prevents clustering elsewhere). Let $z_n = \<0,\dots,0\>$ with $n$ zeros. We claim
+successfully countered $\tau$ by clustering at $c\in C$ (the strategy trivially prevents clustering elsewhere). Let $z_n = \<0,\dots,0\>$ with $n$ zeros. We claim
 \[
@@
 Without loss of generality we assume it ignores order.
-We may define $S(x_0,\dots,x_{k},n)\in [2^\omega]^{<\omega}$ (increasing on $n$) and $n<m(x_0,\dots,x_{k},n)<\omega$ such that for each $(x_0,\dots,x_{k})$,
+We may define $S(x_0,\dots,x_{k},n)\in [C]^{<\omega}$ (increasing on $n$) and $n<m(x_0,\dots,x_{k},n)<\omega$ such that for each $(x_0,\dots,x_{k})$,
   \[

### 2013-04-02 menger.tex
2-mark = k-mark for Menger Game finite player

@@
 
+  \begin{lemma}
+    Let $\sigma(\mc{U}, n)$ be a winning Markov strategy for $F$ in $\mengame{X}$, and $\mathfrak{C}$ collect all open covers of $X$. Then for
+      \[
+        C_n = \bigcap_{\mc{U}\in\mathfrak{C}} \overline{\bigcup\sigma(\mc{U},n)}
+      \]
+    and
+      \[
+        D_n = \bigcap_{\mc{U}\in\mathfrak{C}} \bigcup\sigma(\mc{U},n)
+      \]
+    it follows that $\bigcup_{n<\omega} C_n = \bigcup_{n<\omega} D_n = X$.
+  \end{lemma}
+
+  \begin{proof}
+    Observe $D_n \subseteq C_n$.
+Suppose that $x \not\in D_n = \bigcap_{\mc{U}\in\mathfrak{C}} \bigcup\sigma(\mc{U},n)$ for any $n<\omega$.
+Then for each $n$, pick $\mc{U}_n\in\mathfrak{C}$ such that $x\not\in \bigcup\sigma(\mc{U}_n,n)$.
+Then $\sigma$ does not defeat the play $\mc{U}_0,\mc{U}_1,\dots$ since the $\sigma(\mc{U}_n,n)$ do not cover $x$, contradiction.
+  \end{proof}
+
+  \begin{theorem}
+    For regular spaces $X$, $F \markwin \mengame{X}$ if and only if $X$ is $\sigma$-compact.
+  \end{theorem}
+
+  \begin{proof}
+    The reverse implication has already been shown. To complete the proof, we look to Scheepers for inspiration.
+
+    Let $\sigma(\mathcal{U},n)$ be a winning Markov strategy for $F$ in $\mengame{X}$. Let $\mathfrak{C}$ collect all open covers of $X$. Define
+      \[
+        C_n = \bigcap_{\mc{U}\in\mathfrak{C}} \overline{\bigcup\sigma(\mc{U},n)}
+      \]
+    as in the previous lemma. Note that $\bigcup_{n<\omega} C_n = X$, and we will show each $C_n$ is compact as it is $H$-closed.
+
+    Let $\mc{U}$ be an open cover of $C_n$, and $\mc{V}$ be a cover of $X\setminus C_n$ by open sets whose closures are disjoint from $C_n$ (possible by regularity).
+
+    Since $\mc{U}\cup\mc{V}$ covers $X$, $\overline{\bigcup\sigma(\mc{U}\cup\mc{V},n)} \supseteq C_n$.
+Furthermore, if $\mc{F} = \sigma(\mc{U}\cup\mc{V},n)\setminus \mc{V}$, then $\overline{\bigcup\mc{F}} \supseteq C_n$ (the closures of sets in $\mc{V}$ missed $C_n$).
+Thus $\mc{F}$ witnesses that $C_n$ is $H$-closed.
+  \end{proof}
+
+  \begin{example}
+  Let $R$ be given the topology from example 63 from Counterexamples in Topology, the topology generated by open intervals with countable sets removed.
+This space is non-regular, non-$\sigma$-compact, and Lindel\"of.
+It is also Menger as $F \win \mengame{R}$, but $F \not\markwin \mengame{R}$.
+  \end{example}
+
+  \begin{proof}
+  From Counterexamples: The irrationals are open, but contain no closed neighborhood, showing non-regular. Compact subsets are exactly finite subsets, showing non-$\sigma$-compact.
+
+  Take open covers $\mc{U}_0,\mc{U}_1,\dots$.
+Define $\sigma(\mc{U}_0,\dots,\mc{U}_{2n})$ to be a finite subcover of $[-n,n]\setminus C_n$ for some countable $C_n=\{c_{n,0}, c_{n,1}, \dots\}$.
+For $\sigma(\mc{U}_0,\dots,\mc{U}_{2n+1})$, use any subcover of $\{c_{i,j} : i,j < n\}$.
+It is easily seen that $\sigma$ is a winning perfect information strategy.
+
+  There cannot be a winning Markov strategy $\sigma(\mc{U},n)$, however. Define 
+      \[
+        D_n = \bigcap_{\mc{U}\in\mathfrak{C}} \bigcup\sigma(\mc{U},n)
+      \]
+  where $\mathfrak{C}$ is the collection of open covers of $R$.
+For any $x_0,x_1,\dots \in R$, we may define the open cover $\mc{U} = \{R \setminus \{x_i: i \not= n\} : n < \omega \}$, and observe that $\bigcup \sigma(\mc{U},n) \supseteq D_n$ cannot contain every $x_i$.
+Thus $D_n$ is finite, but since the previous lemma requires $\bigcup_{n<\omega} D_n = R$ if $\sigma$ is a winning strategy, there exists a counter to $\sigma$.
+  \end{proof}
+
+  \begin{theorem}
+  For any topological space $X$ and all $k \geq 2$, $F \kmarkwin{k} \mengame{X}$ if and only if $F \kmarkwin{2} \mengame{X}$.
+  \end{theorem}
+
+  \begin{proof}
+  Assume $\sigma(\mc{U}_0,\dots,\mc{U}_{k-1},n)$ is a winning $k$-Markov strategy.
+Define the $2$-Markov strategy $\tau(\mc{U},\mc{V},n)$ so that it contains $\sigma(\mc{W}_0,\dots,\mc{W}_{k-1},m)$ for the following conditions on $(\mc{W}_0,\dots,\mc{W}_{k-1},m)$:
+    \begin{itemize}
+    \item Each $\mc{W}_i \in \{\mc{U},\mc{V}\}$
+    \item $m \leq (n+1)k$; in particular, for $i<k$, 
+      \[
+        \sigma(\mc{W}_0,\dots,\mc{W}_{k-1},(n+1)k+i)
+        \subseteq 
+        \tau(\mc{U},\mc{V},n+1) 
+      \]
+    \end{itemize}
+
+  Considering an arbitrary play $\mc{U}_0, \mc{U}_1, \dots$ by $C$ versus $\tau$, we note that $\sigma$ defeats the play 
+  \[
+    \underbrace{\mc{U}_0,\mc{U}_0,\dots,\mc{U}_0}_{k},
+    \underbrace{\mc{U}_1,\mc{U}_1,\dots,\mc{U}_1}_{k}
+    \dots
+  \]
+
+  So we have that
+    \[
+      \bigcup_{i<k, n<\omega} \sigma(
+      \underbrace{\mc{U}_n,\dots,\mc{U}_n}_{k-i-1},
+      \underbrace{\mc{U}_{n+1},\dots,\mc{U}_{n+1}}_{i+1},
+      (n+1)k+i)
+    \]
+  is a cover for $X$, and as 
+    \[
+      \sigma(
+      \underbrace{\mc{U}_n,\dots,\mc{U}_n}_{k-i-1},
+      \underbrace{\mc{U}_{n+1},\dots,\mc{U}_{n+1}}_{i+1},
+      (n+1)k+i)
+      \subseteq 
+      \tau(\mc{U}_n,\mc{U}_{n+1},n+1)
+    \]
+  $\tau$ defeats the play $\mc{U}_0, \mc{U}_1, \dots$.
+  \end{proof}
+
   The question remains:
@@
   \begin{question}
-    Does $F \markwin \mengame{X}$ imply $X$ is $\sigma$-compact?
+    In general, does $F \markwin \mengame{X}$ imply $X$ is $\sigma$-compact?
   \end{question}

### 2013-04-04 metalindelof_not_metacompact.tex
Lots of uncategorized changes

\input{./header.tex}

\begin{document}

\begin{example}
  Let $X$ be a compact, zero-dimensional space with a point-countable cover $\{U_\alpha : \alpha \in \Lim(\omega_1)\}$ which is not $\sigma$-point-finite. (Can we change this to, every uncountable subcollection is not point-finite, or every stationary subset $S$ of $\Lim(\omega_1)$ doesn't yield a point-finite subcollection?)

  For $\alpha \in \Lim(\omega_1)$, pick $\beta_{\alpha,n}$ such that $\ds\lim_{n\to\infty}\beta_{\alpha,n}=\alpha$. Assume every $\beta\in\Suc(\omega_1)$ is $\beta_{\alpha,n}$ for some $\alpha,n$. Let $\mc{B}_\alpha = \{\beta_{\alpha,0},\beta_{\alpha,1},\dots\}$

  Let $\mathbb{X} = \Lim(\omega_1) \cup (X \times \Suc(\omega_1))$, with the topology induced by $X\times\{\beta\}$ being open and a topological copy of $X$, and each $\alpha$ given the open neighborhood $B_\alpha = \{\alpha\}\cup(U_\alpha \times \mc{B}_\alpha)$.
\end{example}

\begin{theorem}
  $K\win\lfkpgame{\mathbb{X}}$.
\end{theorem}

\begin{proof}
  Idea: Seeing $\<x_i,\beta_i\>$, $K$ forbids $X\times \{\beta_i\}$, and promises to eventually forbid $B_\alpha$ for each $\alpha$ where $x_i \in U_\alpha$.
\end{proof}

\begin{theorem}
  $K\not\tactwin\lfkpgame{\mathbb{X}}$.
\end{theorem}

\begin{proof}
  Locally compact, not metacompact.

  Game idea: Suppose there exists $\alpha\in\Lim(\omega_1)$ such that one may find arbitrarily large $n<\omega$ and $x\in U_\alpha$ such that $\sigma(x,\beta_{\alpha,n})$ does not forbid a branch for $\alpha$. Then $P$ has a counter converging to $\alpha$.

  Otherwise define $f:\Lim(\omega_1)\to\omega$ such that for $n\geq f(\alpha)$, $\sigma(x,\beta_{\alpha,n})$ forbids a branch for $\alpha$ for all $x\in U_\alpha$. Then $g(\alpha) = \beta_{\alpha,f(\alpha)}$ is a downward function, and there exists a stationary subset $S\subseteq \Lim_{\omega_1}$ and some $\beta\in\Suc(\omega_1)$ such that $\beta = \beta_{\alpha,f(\alpha)}$ for all $\alpha\in S$.

  Observing that $\{U_\alpha : \alpha \in S\}$ is dfggreat
\end{proof}

% \begin{thebibliography}{9}

% \bibitem{G1}
%   G. Gruenhage,
%   \emph{Covering Properties on $X^2\setminus\Delta$, $W$-sets, and Compact Subsets of $\Sigma$-Products}.
%   Topology Appl. 17 (1984), 287-304

% \bibitem{G2}
%   G. Gruenhage,
%   \emph{Games, Covering Properites, and Eberlein Compacts}.
%   Topology Appl. 23 (1986), 291-297

% \bibitem{Michael}
%   G. Gruenhage and E. Michael, 
%   \emph{A result on shrinkable open covers}.
%   Proceedings of the 1983 topology conference (Houston, Tex., 1983), 1983, pp. 37–43.

% \bibitem{Todercevic}
%   S. Todercevic,
%   \emph{Trees and linearly ordered sets}.
%   Handbook of Set-theoretic Topology (North-Holland, Amsterdam, 1984), pp. 235-293

% \bibitem{Watson}
%   S. Watson,
%   \emph{Locally compact normal meta-Lindel\"of spaces may not be paracompact: 
%   an application of uniformization and Suslin lines}. 
%   Proc. Amer. Math. Soc. 98 (1986), no. 4, 676–680.

% \end{thebibliography}

\end{document}

### 2013-04-11 metacompact game characterization.tex
broke off metacompact stuff from seminar talk paper

--- 2013-03-28 au_topology_seminar_talk_2013_02_18.tex
@@
 
+\newpage
+
+\centerline{\bf Ladder Space Stuff}
+
+\begin{proposition}
+It is consistant that there exists a compact, zero-dimensional topological space $X$ such that $X$ has a point-countable cover $\mc{U} = \{U_\alpha : \alpha\in\omega_1^L\}$ of clopen sets such that no uncountable subset of $\mc{U}$ is point-finite.
+\end{proposition}
+
+\begin{definition}
+For each $\alpha\in\omega_1^L$, define successor ordinals $\alpha_0<\alpha_1<\dots\to\alpha$ such that each successor ordinal $\beta$ equals $\alpha_n$ for some $\alpha, n$.
+Using the $X$ from the previous lemma, let \[\mathbb{X} = (X \times \omega_1^S) \cup \omega_1^L\] compose a topological sum of copies of $X$ for each countable successor ordinal, along with a discrete copy of the countable limit ordinals, and add open (in fact, compact) neighborhoods of the form:
+  \[
+    B(\alpha) = \{\alpha\} \cup (U_\alpha \times \{\alpha_n : n < \omega\})
+  \]
+\end{definition}
+
+\begin{definition}
+Define these things as I need them:
+\end{definition}
+
+\begin{proposition}
+Without loss of generality, we may assume $P$ always plays points in $X \times \omega_1^S$ throughout $\lfkpgame{\mathbb{X}}$.
+\end{proposition}
+
+\begin{proposition}
+$K \win \lfkpgame{\mathbb{X}}$
+\end{proposition}
+
+\begin{proof}
+Sketch of proof: For each point $\<x,\beta\>$ played by $P$, $K$ makes a promise to eventually cover $B(\alpha)$ for each of the countably-many $\alpha$ where $x\in U_\alpha$.
+\end{proof}
+
+\begin{theorem}
+$K \not\tactwin \lfkpgame{\mathbb{X}}$
+\end{theorem}
+
+\begin{proof}
+Follows from G: $\mathbb{X}$ is locally compact, but not metacompact. A game-theoretic proof follows.
+
+Suppose $\sigma(x,\beta)$ was a winning strategy for $K$.
+We claim that for each $\alpha\in\omega_1^L$, there exists some $f(\alpha)<\omega$ such that $\bigcap_{x\in U_\alpha} \sigma(x,\alpha_{f(\alpha)}) \supseteq B(\alpha)$.
+If not, choose $\alpha$ for which $f(\alpha)$ cannot exist.
+Then there exists some $x_0\in U_\alpha$ where $\sigma(x,\alpha_{m_0})$ misses $B(\alpha)$ for sufficiently large $m_0$.
+In general, choose $x_n\in U_\alpha$ in round $n$ where $\sigma(x,\alpha_{m_n})$ misses $B(\alpha)$ for sufficiently large $m_n$, and the play
+  \[
+    \<x_0,\alpha_{m_0}\>, \<x_1,\alpha_{m_1}\>, \<x_2,\alpha_{m_2}\>, \dots
+  \]
+counters $\sigma$ by converging to $\alpha$, contradiction.
+
+So, define a function $f:\omega_1^L\to\omega$ where $\bigcap_{x\in U_\alpha} \sigma(x,\alpha_{f(\alpha)}) \supseteq B(\alpha)$, and let $g:\omega_1^L\to\omega_1^S$ be defined such that $g(\alpha)=\alpha_{f(\alpha)}$.
+By the pressing down lemma, there exists an uncountable $A\subseteq\omega_1^L$ and $\beta\in\omega_1^S$ such that $g(\alpha)=\alpha_{f(\alpha)}=\beta$ for all $\alpha \in A$.
+
+Since no uncountable subset of $\mc{U}=\{U_\alpha : \alpha \in \omega_1^L\}$ is point-finite, there exists a point $x\in X$ such that $x$ belongs to $U_\alpha$ for each $\alpha$ in some infinite $A'\subseteq A$.
+Then note that $\sigma(x,g(\alpha))=\sigma(x,\beta)\supseteq B(\alpha)$ for each $\alpha\in A'$, and thus $\sigma(x,\beta)$ is not compact, contradiction.
+\end{proof}
+
+\newpage
+
 \begin{thebibliography}{9}

### 2013-05-03 menger.tex
2-Markov doesn't imply Markov in Mneger game

@@
   \begin{proof}
+    Result due to (???)
+
     First, suppose $X$ wasn't Menger.
@@
   \begin{lemma}
-    For all $\alpha_0, \alpha_1, \dots < \omega_1$ and functions $\tau:\omega_1\times\omega \rightarrow [\omega_1]^{<\omega}$, $\{\tau(\alpha_n,n): n<\omega\}$ is not a cover for $\{\beta:\forall n<\omega (\beta < \alpha_n)\}$.
+    For all functions $\tau:\omega_1\times\omega \rightarrow [\omega_1]^{<\omega}$, there exists a sequence $\alpha_0, \alpha_1, \dots < \omega_1$ such that $\{\tau(\alpha_n,n): n<\omega\}$ is not a cover for $\{\beta:\forall n<\omega (\beta < \alpha_n)\}$.
   \end{lemma}
@@
     Let $P_n = \{\beta: \beta < \alpha \Rightarrow \beta \in \tau(\alpha, n)\}$.
-Observe that each $P_n$ is finite; else there is some $\alpha$ larger than every member of $P_n$ such that $P_n \subseteq \tau(\alpha, n)$.
+Observe that each $P_n$ is finite; else there is some $\alpha$ larger than every member of some countably infinite $P_n^*\subseteq P_n$ such that $P_n^* \subseteq \tau(\alpha, n)$.
 
@@
 Consider the covers \[\mc{U}(\alpha) = \{[\alpha,\omega_1)\cup\{\infty\}\} \cup \{\{\beta\}:\beta < \alpha\}\] and define $\tau(\alpha,n)$ to be the union of singletons chosen by $\sigma(\mathcal{U}(\alpha),n)$.
-As $\sigma$ was a winning strategy, for all $\alpha_0, \alpha_1, \dots < \omega_1$, $\{\sigma(\mathcal{U}(\alpha_n),n): n<\omega\}$ must cover $\oneptlind{\omega_1}$, and thus $\{\tau(\alpha_n,n): n<\omega\}$ must cover $\{\beta:\forall n<\omega (\beta < \alpha_n)\}$, contradiction.
+
+    Using the sequence $\alpha_0, \alpha_1,\dots<\omega_1$ from the previous lemma, we consider the play $\mc{U}(\alpha_0),\mc{U}(\alpha_1),\dots$.
+
+    As $\sigma$ was a winning strategy, $\{\sigma(\mathcal{U}(\alpha_n),n): n<\omega\}$ must cover $\oneptlind{\omega_1}$, and thus $\{\tau(\alpha_n,n): n<\omega\}$ must cover $\{\beta:\forall n<\omega (\beta < \alpha_n)\}$, contradiction.
+  \end{proof}
+
+  We require a lemma.
+
+  \begin{lemma}
+    There exist injective functions $f_\alpha:\alpha\to\omega$ such that if $\alpha<\beta$, then \[f_\beta\rest\alpha =^* f_\alpha\] that is, $f_\beta\rest\alpha$ and $f_\alpha$ agree on all but finitely many ordinals.
+  \end{lemma}
+
+  \begin{example}
+    $F \kmarkwin{2} \mengame{\oneptlind{\omega_1}}$
+  \end{example}
+
+  \begin{proof}
+    Using the functions $f_\alpha$ from the previous lemma, let \[\tau(\alpha_n,\alpha_{n+1},n+1)=f_{\alpha_n}^{-1}([0,n]) \cup \{\beta<\alpha_n,\alpha_{n+1} : f_{\alpha_n}(\beta)\not=f_{\alpha_{n+1}}(\beta)\}\]
+
+    For any sequence $\alpha_n$, suppose that $\beta<\alpha_n$ for all $n$, and $\beta$ is not covered by \[\{\tau(\alpha_n,\alpha_{n+1},n+1): n<\omega\}\] Then we see first that $f_{\alpha_n}(\beta)=f_{\alpha_{n+1}}(\beta)$ for all $n$.
+However, $f_{n}(\beta)>n$ for all $n$ as well, which is a contradiction.
+
+    Finally, for each open cover $\mc{U}$, assign arbirtary $\alpha(\mc{U})$, $U(\mc{U})$ such that $[\alpha(\mc{U}),\omega_1)\cup\{\infty\}$ is a subset of $U(\mc{U})\in\mc{U}$.
+Then a $2$-Markov strategy $\sigma(\mc{U}_n,\mc{U}_{n+1},n+1)$ which chooses $U(\mc{U}_n)$ and covers the finite set $\tau(\alpha(\mc{U}_n),\alpha(\mc{U}_{n+1}),n+1)$ is a winning strategy for $F$.
   \end{proof}

### 2013-05-08 menger.tex
starting sorgenfrey side project

@@
   \begin{proposition}
-    $X$ is compact if and only if $F \tactwin \mengame{X}$
+    $X$ is compact if and only if $F \tactwin \mengame{X}$ if and only if $F \ktactwin{k} \mengame{X}$
   \end{proposition}
@@
   \begin{proof}
-    Assume $X$ is compact. For each open cover played by $C$, pick the finite subcover.
+    Assume $X$ is compact. For each open cover played by $C$, pick a finite subcover, and this yields a winning tactical strategy.
 
-    Assume $F$ has a winning tactical strategy. For any open cover, have $C$ play only it during the entire game. $F$'s only choice must be a finite subcover.
+    Assume $F$ has a winning $k$-tactical strategy. For any open cover, have $C$ play only it during the entire game. $F$'s only choice must be a finite subcover.
   \end{proof}
@@
 
-  Due to Telgarski in ``On Games of Topsoe'':
+  For Menger's game, there is no useful distinction between a $k$-Markov strategy for $F$, and a $2$-Markov strategy.
 
   \begin{theorem}
-    For metrizable $X$, $X$ is $\sigma$-compact if and only if $F \win \mengame{X}$.
+  For any topological space $X$ and all $k \geq 2$, $F \kmarkwin{k} \mengame{X}$ if and only if $F \kmarkwin{2} \mengame{X}$.
   \end{theorem}
+
+  \begin{proof}
+  Assume $\sigma(\mc{U}_0,\dots,\mc{U}_{k-1},n)$ is a winning $k$-Markov strategy.
+Define the $2$-Markov strategy $\tau(\mc{U},\mc{V},n)$ so that it contains $\sigma(\mc{W}_0,\dots,\mc{W}_{k-1},m)$ for the following conditions on $(\mc{W}_0,\dots,\mc{W}_{k-1},m)$:
+    \begin{itemize}
+    \item Each $\mc{W}_i \in \{\mc{U},\mc{V}\}$
+    \item $m \leq (n+1)k$; in particular, for $i<k$, 
+      \[
+        \sigma(\mc{W}_0,\dots,\mc{W}_{k-1},(n+1)k+i)
+        \subseteq 
+        \tau(\mc{U},\mc{V},n+1) 
+      \]
+    \end{itemize}
+
+  Considering an arbitrary play $\mc{U}_0, \mc{U}_1, \dots$ by $C$ versus $\tau$, we note that $\sigma$ defeats the play 
+  \[
+    \underbrace{\mc{U}_0,\mc{U}_0,\dots,\mc{U}_0}_{k},
+    \underbrace{\mc{U}_1,\mc{U}_1,\dots,\mc{U}_1}_{k}
+    \dots
+  \]
+
+  So we have that
+    \[
+      \bigcup_{i<k, n<\omega} \sigma(
+      \underbrace{\mc{U}_n,\dots,\mc{U}_n}_{k-i-1},
+      \underbrace{\mc{U}_{n+1},\dots,\mc{U}_{n+1}}_{i+1},
+      (n+1)k+i)
+    \]
+  is a cover for $X$, and as 
+    \[
+      \sigma(
+      \underbrace{\mc{U}_n,\dots,\mc{U}_n}_{k-i-1},
+      \underbrace{\mc{U}_{n+1},\dots,\mc{U}_{n+1}}_{i+1},
+      (n+1)k+i)
+      \subseteq 
+      \tau(\mc{U}_n,\mc{U}_{n+1},n+1)
+    \]
+  $\tau$ defeats the play $\mc{U}_0, \mc{U}_1, \dots$.
+  \end{proof}
+
+  But there are spaces for which there is no Markov strategy, but there is a $2$-Markov strategy.
 
@@
 
-  We require a lemma.
-
   \begin{lemma}
     There exist injective functions $f_\alpha:\alpha\to\omega$ such that if $\alpha<\beta$, then \[f_\beta\rest\alpha =^* f_\alpha\] that is, $f_\beta\rest\alpha$ and $f_\alpha$ agree on all but finitely many ordinals.
+(In addition, the range of each $f_\alpha$ is co-infinite.)
   \end{lemma}
+
+  \begin{proof}
+    Taken from Kunen (used for the construction of an $\omega_1$-Aronszajn tree).
+
+    We begin with the empty function $f_0:0\to\omega_1$ which satisfies the hypothesis, and assume $f_\alpha$ is defined by induction.
+Let $f_{\alpha+1} = f_\alpha \cup \{\<\alpha,n\>\}$ where $n$ is not defined for $f_\alpha$, and this satisfies the hypothesis.
+
+    Finally, suppose $\gamma$ is the limit of $\alpha_0,\alpha_1,\dots$, and $f_\alpha$ is defined for $\alpha<\gamma$.
+Let $g_0=f_{\alpha_0}$, and define $g_n : \alpha_n \to \omega$ to be injective, $g_n=^* f_{\alpha_n}$, and $g_{n+1} \rest \alpha_n = g_n$.
+$g = \bigcup_{n<\omega} g_n$ is an injective function from $\gamma \to \omega$ and $g =^* f_\alpha$ for $\alpha <\gamma$, but the range need not be coinfinte.
+So let
+    \[
+      f_\gamma(\beta) = \left\{
+      \begin{array}{ll}
+        g(\alpha_{2n}) & \beta = \alpha_n \\
+        g(\beta) & \text{otherwise}
+      \end{array}
+      \right.
+    \]
+    which frees up $\{g(\alpha_{2n+1}):n<\omega\}$ from the range of $f_\gamma$, but still agrees with all but finitely many points compared to previous $f$'s.
+  \end{proof}
 
@@
   \end{proof}
+
+  Due to Telgarski in ``On Games of Topsoe'':
+
+  \begin{theorem}
+    For metrizable $X$, $X$ is $\sigma$-compact if and only if $F \win \mengame{X}$.
+  \end{theorem}
+
+  We adapt this result for regular spaces.
 
@@
 
-  \begin{theorem}
-  For any topological space $X$ and all $k \geq 2$, $F \kmarkwin{k} \mengame{X}$ if and only if $F \kmarkwin{2} \mengame{X}$.
-  \end{theorem}
+  \begin{example}
+  Let $R$ be given the topology from example 67 from Counterexamples in Topology, the topology generated by open intervals with or without the rationals removed.
+This space is non-regular, non-$\sigma$-compact, and Lindel\"of.
+  \end{example}
 
   \begin{proof}
-  Assume $\sigma(\mc{U}_0,\dots,\mc{U}_{k-1},n)$ is a winning $k$-Markov strategy.
-Define the $2$-Markov strategy $\tau(\mc{U},\mc{V},n)$ so that it contains $\sigma(\mc{W}_0,\dots,\mc{W}_{k-1},m)$ for the following conditions on $(\mc{W}_0,\dots,\mc{W}_{k-1},m)$:
-    \begin{itemize}
-    \item Each $\mc{W}_i \in \{\mc{U},\mc{V}\}$
-    \item $m \leq (n+1)k$; in particular, for $i<k$, 
-      \[
-        \sigma(\mc{W}_0,\dots,\mc{W}_{k-1},(n+1)k+i)
-        \subseteq 
-        \tau(\mc{U},\mc{V},n+1) 
-      \]
-    \end{itemize}
-
-  Considering an arbitrary play $\mc{U}_0, \mc{U}_1, \dots$ by $C$ versus $\tau$, we note that $\sigma$ defeats the play 
-  \[
-    \underbrace{\mc{U}_0,\mc{U}_0,\dots,\mc{U}_0}_{k},
-    \underbrace{\mc{U}_1,\mc{U}_1,\dots,\mc{U}_1}_{k}
-    \dots
-  \]
-
-  So we have that
-    \[
-      \bigcup_{i<k, n<\omega} \sigma(
-      \underbrace{\mc{U}_n,\dots,\mc{U}_n}_{k-i-1},
-      \underbrace{\mc{U}_{n+1},\dots,\mc{U}_{n+1}}_{i+1},
-      (n+1)k+i)
-    \]
-  is a cover for $X$, and as 
-    \[
-      \sigma(
-      \underbrace{\mc{U}_n,\dots,\mc{U}_n}_{k-i-1},
-      \underbrace{\mc{U}_{n+1},\dots,\mc{U}_{n+1}}_{i+1},
-      (n+1)k+i)
-      \subseteq 
-      \tau(\mc{U}_n,\mc{U}_{n+1},n+1)
-    \]
-  $\tau$ defeats the play $\mc{U}_0, \mc{U}_1, \dots$.
+  From Counterexamples: The rationals are closed, but the closure of any open neighborhood is the whole real line, so they cannot be separated from any irrational point.
+Compact sets in this topology are nowhere dense in the Euclidean topology, so there cannot be countably many which union to the whole space.
+$\{(a,b)\setminus D : a,b\in\mathbb{Q},D\in\{\emptyset,\mathbb{Q}\}\}$ is a countable base for the space, and second-countability implies Lindel\"of.
   \end{proof}
 
-  The question remains:
-
-  \begin{question}
-    In general, does $F \markwin \mengame{X}$ imply $X$ is $\sigma$-compact?
-  \end{question}
-
-  % Let $\sigma(\mathcal{U},n)$ be $F$'s winning Markov strategy.
-
 \end{document}

### 2013-05-08 sorgenfrey/sorgenfrey.tex
added simple result to sorgenfrey

\input{../header.tex}

\begin{document}

In this paper we investigate an open question posed to us by Gruenhage:

\begin{question}
Let $P$ be the subspace of the Sorgenfrey line containing only irrational numbers. Does there exist a base $\mc{B}$ for $P$ such that for every $\mc{C}\subseteq\mc{B}$ which is also a base for $X$, there exists a locally finite subcover $\mc{C}'\subseteq\mc{C}$?
\end{question}

We begin by tackling a simpler (solved) problem:

\begin{proposition}
Let $R$ be the Sorgenfrey line, the set of real numbers with the topology generated by the base $\mc{B} = \{[a,b): a<b\in R\}$ (where $[a,b) = \{x : a\leq x < b\}$).

For every $\mc{C}\subseteq\mc{B}$ which is also a base for $R$, there exists a pairwise disjoint subcover $\mc{C}'\subseteq\mc{C}$ (and thus a locally finite subcover).
\end{proposition}

\begin{proof}
We begin by letting $b_{n,0}=n$ for each $n<\omega$, and if $b_{n,\alpha}$ is defined for some ordinal $\alpha<\omega_1$ and $b_{n,\alpha}<n+1$, we define its successor $b_{n,\alpha+1}$ as follows:
  \begin{itemize}
    \item $b_{n,\alpha} < b_{n,\alpha+1} \leq n+1$
    \item $[b_{n,\alpha},b_{n,\alpha+1})\in \mathcal{C}$

    (This is possible as $\mc C$ is a base, and there must be some element of $\mc C$ which contains $b_{n,\alpha}$ and is a subset of $[b_{n,\alpha},n+1)$.)
  \end{itemize}
(If $b_{n,\alpha}=n+1$, then let $b_{n,\alpha+1}=n+1$ as well.) Finally, if $\alpha<\omega_1$ is a limit ordinal, let $\ds b_{n,\alpha} = \lim_{\beta\to\alpha}b_{n,\beta}$.

Let $C_{n,\alpha} = [b_{n,\alpha},b_{n,\alpha+1})$. We claim $\mc{C}' = \{C_{n,\alpha} : n<\omega,\alpha<\omega_1\}$ is a pairwise disjoint cover of $R$. Pairwise disjoint is evident by definition. To see that it is a cover, suppose it wasn't and missed some $x\in[n,n+1)$. Then we have an uncountable increasing sequence of numbers $\{b_{n,\alpha}:\alpha<\omega_1\}$, which contradicts the countable chain condition on the real line.
\end{proof}

\end{document}

### 2013-05-17 menger.tex
added simple result to sorgenfrey
Proved irrational sorgenfrey result for any dense subset

@@
 
-  Due to Telgarski in ``On Games of Topsoe'':
+  Due to Telgarski in ``On Games of Topsoe'' (along with $\sigma$-compact implying $F\markwin \mengame{X}$).
 
   \begin{theorem}
-    For metrizable $X$, $X$ is $\sigma$-compact if and only if $F \win \mengame{X}$.
+    For metrizable $X$, $X$ is $\sigma$-compact if and only if $F \win \mengame{X}$ if and only if $F\markwin \mengame{X}$.
   \end{theorem}
@@
   \begin{theorem}
-    For regular spaces $X$, $F \markwin \mengame{X}$ if and only if $X$ is $\sigma$-compact.
+    For regular spaces $X$, $X$ is $\sigma$-compact if and only if $F \markwin \mengame{X}$.
   \end{theorem}
@@
 This space is non-regular, non-$\sigma$-compact, and Lindel\"of.
+
+  This space is an example of non-$\sigma$-compact but $F \markwin \mengame{R}$ (and is thus also Menger).
   \end{example}
@@
 $\{(a,b)\setminus D : a,b\in\mathbb{Q},D\in\{\emptyset,\mathbb{Q}\}\}$ is a countable base for the space, and second-countability implies Lindel\"of.
+
+  % To see Menger, let $\mc{U}_0,\mc{U}_1,\dots$ be a sequence of open covers, and choose open sets $U_{2n}\in\mc{U}_{2n}$ which cover $q_n$ for each $q_n\in\mathbb{Q}$ (which in turn are open in the Euclidean line).
+Since the complement of the union $\bigcup_{n<\omega} U_{2n}$ must be closed discrete in the Euclidean line, it is countable, so open sets $U_{2n+1}\in\mc{U}_{2n+1}$ may be found to cover the remainder.
+
+  To see $F \markwin \mengame{R}$, we define $\sigma(\mc{U}_{2n},2n)$ to be a finite cover of $[-n,n]\setminus\mathbb{Q}$, and $\sigma(\mc{U}_{2n+1},2n+1)$ to be a finite cover of $\{q_n\}$ for each $q_n\in\mathbb{Q}$.
   \end{proof}

### 2013-05-17 sorgenfrey/sorgenfrey.tex
Proved irrational sorgenfrey result for any dense subset

@@
 \begin{proposition}
-Let $R$ be the Sorgenfrey line, the set of real numbers with the topology generated by the base $\mc{B} = \{[a,b): a<b\in R\}$ (where $[a,b) = \{x : a\leq x < b\}$).
+Let $R$ be the Sorgenfrey line, the set of real numbers with the topology generated by the base $\mc{B} = \{[a,b): a<b\}$ (where $[a,b) = \{x : a\leq x < b\}$).
 
@@
 
+This idea can be generalized for the irrationals, but it takes some machinery:
+
+\begin{theorem}
+Let $P$ be a dense subspace of the Sorgenfrey line with the induced topology, which has the base $\mc{B} = \{[a,b) : a<b, a\in P\}$.
+
+For every $\mc{C}\subseteq\mc{B}$ which is also a base for $P$, there exists a pairwise disjoint subcover $\mc{C}'\subseteq\mc{C}$ (and thus a locally finite subcover).
+\end{theorem}
+\newpage
+\begin{proof}
+It suffices to show for $[0,1)\cap P$. We begin by constructing a collection of functions $S\subseteq \omega^{\omega_1}$ and numbers $c_s$, $d_s$ defined by those functions as follows:
+  \begin{itemize}
+    \item Let $S_0 = \{\emptyset\}$. Let $d_{\emptyset}=0$ and $c_{\<-1\>}=1$.
+    \item Suppose $S_\alpha$ has been defined, as well as $d_s\leq c_{s\concat\<-1\>}$. For $s\in S$, consider the following:
+      \begin{itemize}
+        \item If $d_s = c_{s\concat\<-1\>}$, do nothing.
+        \item If $d_s < c_{s\concat\<-1\>}$ and $d_s\in P$, let $S_{\alpha+1}$ contain $s\concat\<0\>$ and define $c_{s\concat\<0\>}$, $d_{s\concat\<0\>}$, $c_{s\concat\<0,-1\>}$ such that 
+          \[
+            d_s = c_{s\concat\<0\>} < d_{s\concat\<0\>} \leq c_{s\concat\<0,-1\>} = c_{s\concat\<-1\>}
+          \]
+        where $[c_{s\concat\<0\>}, d_{s\concat\<0\>})\in \mc{C}$.
+        \item If $d_s < c_{s\concat\<-1\>}$ and $d_s\in P$, let $S_{\alpha+1}$ contain $s\concat\<n\>$ for all $n<\omega$ and define $c_{s\concat\<n\>}$, $d_{s\concat\<n\>}$, $c_{s\concat\<n,-1\>}$ for all $n<\omega$ such that
+          \[
+            d_s < \dots \leq c_{s\concat\<2,-1\>} = c_{s\concat\<1\>} < d_{s\concat\<1\>} \leq c_{s\concat\<1,-1\>} = c_{s\concat\<0\>} < d_{s\concat\<0\>} \leq c_{s\concat\<0,-1\>} = c_{s\concat\<-1\>}
+          \]
+        where $[c_{s\concat\<n\>}, d_{s\concat\<n\>})\in \mc{C}$ for all $n<\omega$ and $c_{s\concat\<n\>} \rightarrow d_s$.
+      \end{itemize}
+    \item Suppose $\alpha$ is a limit ordinal and $S_\beta$ has been defined for all $\beta<\alpha$.
+If $s\in\omega^\alpha$ and $t\in \bigcup_{\beta<\alpha}S_\beta$ for all $t<s$, let $S_\alpha$ contain $s$ and define $d_s = \lim_{t<s}d_t$ and $c_{s\concat\<-1\>} = \lim_{t<s} c_{t\concat\<-1\>}$.
+  \end{itemize}
+
+  By construction, $\mc{C}' = \{[c_s,d_s) : s\in S\}$ is a disjoint subcollection of $\mc{C}$. We claim it also must cover $[0,1)\cap P$.
+
+  Suppose not: $x\in[0,1)\cap P$ is not contained in $[c_s,d_s)$ for any $s\in S$.
+Note that $d_\emptyset<x$ (or else $x\in[c_{\<0\>},d_{\<1\>}$)).
+Assume $n_\beta<\omega$ is defined for all $\beta<\alpha$, and consider $s\in\omega^\alpha$ where $s(\beta)=n_\beta$.
+If $d_s<x$, we claim there is a minimal $n_\alpha<\omega$ where $d_{s\concat\<n_\alpha\>}<x$.
+    \begin{itemize}
+      \item This possible when $d_s\not\in P$ since $d_{s\concat\<n\>}\to d_s$.
+      \item This is also possible when $d_s\in P$ since $[c_{s\concat\<0\>},d_{s\concat\<0\>})$ does not contain $x$, and thus $d_s=c_{s\concat\<0\>}<d_{s\concat\<0\>}\leq x$.
+If $d_{s\concat\<0\>} = x$ then $d_{s\concat\<0\>}\in P$ and $[d_{s\concat\<0\>},d_{s\concat\<0,0\>})=[c_{s\concat\<0,0\>},d_{s\concat\<0,0\>})$ contains $x$, which is a contradiction.
+    \end{itemize}
+
+  Finally, we notice that by defining $f\in\omega^\omega_1$ such that $f(\alpha)=n_\alpha$, then $d_{f(\alpha)}$ is an increasing sequence defined for all $\alpha<\omega_1$, which is a contradiction.
+\end{proof}
+
 \end{document}

### 2013-05-22 menger.tex
added sufficient condition for 2-Markov in Menger game

@@
 
+  We define a new property ``\scish'' to describe a sufficient condition for $F \kmarkwin{2}\mengame{X}$.
+
+  \begin{definition}
+    Let $\mathfrak{C}$ collect all the open covers of $X$. We say $X$ is \scish if there exists a fuction $f:\mathfrak{C}\times\omega\to\mc{P}(X)$, such that:
+      \begin{itemize}
+        \item $f(\mc{V},n)\subseteq f(\mc{V},n+1)$
+        \item $f(\mc{V},n)$ may be covered by a finite subset of $\mc{U}$
+        \item $\bigcup_{n<\omega}f(\mc{V},n)=X$
+        \item The set
+          \[
+            g(\mc{U},\mc{V},n) = \bigcup_{m\geq n}\left(f(\mc{U},m)\setminus f(\mc{V},m)\right)
+          \]
+         may be covered by a finite subset of $\mc{V}$
+      \end{itemize}
+  \end{definition}
+
+  Obviously $\sigma$-compact implies \scish implies Lindel\"of. Note that the non-$\sigma$-compact space $\omega_1^\dagger$ is \scish.
+
+  \begin{theorem}
+    If $X$ is \scish, then $F \kmarkwin{2}\mengame{X}$.
+  \end{theorem}
+
+  \begin{proof}
+    Let $\sigma(\mc{U}_n,\mc{U}_{n+1},n+1)$ cover $f(\mc{U}_{n+1},n+1)$ and $g(\mc{U}_n,\mc{U}_{n+1},n+1)$.
+If $\mc{U}_0,\mc{U}_1,\dots$ is any play by $C$, then for each $x\in X$, we note that $x\in f(\mc{U}_0,N)$ for some $N$.
+So either $x\in \bigcap_{m\leq N} f(\mc{U}_m,N)$ and is covered by the strategy during round $N$, or for some $m\leq N$, $x \in f(\mc{U}_m,N)\setminus f(\mc{U}_{m+1},N)$ and is covered by the strategy during round $m+1$.
+  \end{proof}
+
 \end{document}

### 2013-05-26 menger.tex
Fixed sorgenfrey typos
edited some menger stuff

--- 2013-05-17 menger.tex
@@
 
-  \begin{lemma}
-    There exist injective functions $f_\alpha:\alpha\to\omega$ such that if $\alpha<\beta$, then \[f_\beta\rest\alpha =^* f_\alpha\] that is, $f_\beta\rest\alpha$ and $f_\alpha$ agree on all but finitely many ordinals.
-(In addition, the range of each $f_\alpha$ is co-infinite.)
-  \end{lemma}
-
-  \begin{proof}
-    Taken from Kunen (used for the construction of an $\omega_1$-Aronszajn tree).
-
-    We begin with the empty function $f_0:0\to\omega_1$ which satisfies the hypothesis, and assume $f_\alpha$ is defined by induction.
-Let $f_{\alpha+1} = f_\alpha \cup \{\<\alpha,n\>\}$ where $n$ is not defined for $f_\alpha$, and this satisfies the hypothesis.
-
-    Finally, suppose $\gamma$ is the limit of $\alpha_0,\alpha_1,\dots$, and $f_\alpha$ is defined for $\alpha<\gamma$.
-Let $g_0=f_{\alpha_0}$, and define $g_n : \alpha_n \to \omega$ to be injective, $g_n=^* f_{\alpha_n}$, and $g_{n+1} \rest \alpha_n = g_n$.
-$g = \bigcup_{n<\omega} g_n$ is an injective function from $\gamma \to \omega$ and $g =^* f_\alpha$ for $\alpha <\gamma$, but the range need not be coinfinte.
-So let
-    \[
-      f_\gamma(\beta) = \left\{
-      \begin{array}{ll}
-        g(\alpha_{2n}) & \beta = \alpha_n \\
-        g(\beta) & \text{otherwise}
-      \end{array}
-      \right.
-    \]
-    which frees up $\{g(\alpha_{2n+1}):n<\omega\}$ from the range of $f_\gamma$, but still agrees with all but finitely many points compared to previous $f$'s.
-  \end{proof}
-
-  \begin{example}
-    $F \kmarkwin{2} \mengame{\oneptlind{\omega_1}}$
-  \end{example}
-
-  \begin{proof}
-    Using the functions $f_\alpha$ from the previous lemma, let \[\tau(\alpha_n,\alpha_{n+1},n+1)=f_{\alpha_n}^{-1}([0,n]) \cup \{\beta<\alpha_n,\alpha_{n+1} : f_{\alpha_n}(\beta)\not=f_{\alpha_{n+1}}(\beta)\}\]
-
-    For any sequence $\alpha_n$, suppose that $\beta<\alpha_n$ for all $n$, and $\beta$ is not covered by \[\{\tau(\alpha_n,\alpha_{n+1},n+1): n<\omega\}\] Then we see first that $f_{\alpha_n}(\beta)=f_{\alpha_{n+1}}(\beta)$ for all $n$.
-However, $f_{n}(\beta)>n$ for all $n$ as well, which is a contradiction.
-
-    Finally, for each open cover $\mc{U}$, assign arbirtary $\alpha(\mc{U})$, $U(\mc{U})$ such that $[\alpha(\mc{U}),\omega_1)\cup\{\infty\}$ is a subset of $U(\mc{U})\in\mc{U}$.
-Then a $2$-Markov strategy $\sigma(\mc{U}_n,\mc{U}_{n+1},n+1)$ which chooses $U(\mc{U}_n)$ and covers the finite set $\tau(\alpha(\mc{U}_n),\alpha(\mc{U}_{n+1}),n+1)$ is a winning strategy for $F$.
-  \end{proof}
-
   Due to Telgarski in ``On Games of Topsoe'' (along with $\sigma$-compact implying $F\markwin \mengame{X}$).
@@
 
+  We define a new property ``\scish'' to describe a sufficient condition for $F \kmarkwin{2}\mengame{X}$.
+
+  \begin{definition}
+    Let $\mc U$ be a cover of $X$. We say $C\subseteq X$ is $\mc U$-compact if there exists a finite subcover of $\mc U$ which covers $C$.
+
+    Let $\mathfrak{C}$ collect all the open covers of $X$. We say $X$ is \scish if there exists a fuction $f:\mathfrak{C}\times\omega\to\mc{P}(X)$ such that:
+      \begin{itemize}
+        \item $f(\mc{V},n)$ is $\mc{V}$-compact
+        \item $f(\mc{V},n)\subseteq f(\mc{V},n+1)$
+        \item $\bigcup_{n<\omega}f(\mc{V},n)=X$
+        \item The set
+          \[
+            g(\mc{U},\mc{V},n) = \bigcup_{m\geq n} f(\mc{U},m)\setminus ( f(\mc{U},m-1)\cup f(\mc{V},m))
+          \]
+         is $\mc{V}$-compact
+      \end{itemize}
+  \end{definition}
+
+  Obviously $\sigma$-compact implies \scish implies Lindel\"of. We shall see that the non-$\sigma$-compact space $\omega_1^\dagger$ is \scish.
+
+   \begin{lemma}
+    There exist injective functions $f_\alpha:\alpha\to\omega$ such that if $\alpha<\beta$, then \[f_\beta\rest\alpha =^* f_\alpha\] that is, $f_\beta\rest\alpha$ and $f_\alpha$ agree on all but finitely many ordinals.
+(In addition, the range of each $f_\alpha$ is co-infinite.)
+  \end{lemma}
+
+  \begin{proof}
+    Taken from Kunen (used for the construction of an $\omega_1$-Aronszajn tree).
+
+    We begin with the empty function $f_0:0\to\omega_1$ which satisfies the hypothesis, and assume $f_\alpha$ is defined by induction.
+Let $f_{\alpha+1} = f_\alpha \cup \{\<\alpha,n\>\}$ where $n$ is not defined for $f_\alpha$, and this satisfies the hypothesis.
+
+    Finally, suppose $\gamma$ is the limit of $\alpha_0,\alpha_1,\dots$, and $f_\alpha$ is defined for $\alpha<\gamma$.
+Let $g_0=f_{\alpha_0}$, and define $g_n : \alpha_n \to \omega$ to be injective, $g_n=^* f_{\alpha_n}$, and $g_{n+1} \rest \alpha_n = g_n$.
+$g = \bigcup_{n<\omega} g_n$ is an injective function from $\gamma \to \omega$ and $g =^* f_\alpha$ for $\alpha <\gamma$, but the range need not be coinfinte.
+So let
+    \[
+      f_\gamma(\beta) = \left\{
+      \begin{array}{ll}
+        g(\alpha_{2n}) & \beta = \alpha_n \\
+        g(\beta) & \text{otherwise}
+      \end{array}
+      \right.
+    \]
+    which frees up $\{g(\alpha_{2n+1}):n<\omega\}$ from the range of $f_\gamma$, but still agrees with all but finitely many points compared to previous $f$'s.
+  \end{proof}
+
+  \begin{theorem}
+    The one-point Lindel\"ofication of the uncountable discrete space, $\oneptlind{\omega_1}$, is \scish.
+  \end{theorem}
+
+  \begin{proof}
+    Take the injective funcions $f_\alpha$ from Kunen's lemma such that $f_\alpha\rest\beta =^* f_\beta$.
+Let $\gamma(\mc U)$ identify the least ordinal such that $[\gamma(\mc U),\omega_1)\cup\{\infty\}$ is in a refinement of $\mc U$.
+Then $f(\mc U,n)=f^{-1}_{\gamma(\mc U)}([0,n]) \cup [\gamma(\mc U),\omega_1)\cup\{\infty\}$ is easily seen to witness the property.
+  \end{proof}
+
+  \begin{theorem}
+    If $X$ is \scish, then $F \kmarkwin{2}\mengame{X}$.
+  \end{theorem}
+
+  \begin{proof}
+    Let $\sigma(\mc{U}_n,\mc{U}_{n+1},n+1)$ cover $f(\mc{U}_{n+1},n+1)$ and $g(\mc{U}_n,\mc{U}_{n+1},n+1)$.
+If $\mc{U}_0,\mc{U}_1,\dots$ is any play by $C$, then for each $x\in X$, we note that $x\in f(\mc{U}_0,N)$ for some $N$.
+So either $x\in \bigcap_{m\leq N} f(\mc{U}_m,N)$ and is covered by the strategy during round $N$, or for some $m< N$, $x \in f(\mc{U}_m,N)\setminus (f(\mc{U}_{m},N-1)\cup f(\mc{U}_{m+1},N))$ and is covered by the strategy during round $m+1$.
+  \end{proof}
+
+  \begin{corollary}
+    $F\kmarkwin{2}\mengame{\oneptlind{\omega_1}}$
+  \end{corollary}
+
 \end{document}

### 2013-06-06 menger.tex
Relatively compact results

@@
   Assume $\sigma(\mc{U}_0,\dots,\mc{U}_{k-1},n)$ is a winning $k$-Markov strategy.
-Define the $2$-Markov strategy $\tau(\mc{U},\mc{V},n)$ so that it contains $\sigma(\mc{W}_0,\dots,\mc{W}_{k-1},m)$ for the following conditions on $(\mc{W}_0,\dots,\mc{W}_{k-1},m)$:
+Define the $2$-Markov strategy $\tau(\mc{U},\mc{V},n)$ so that it contains $\sigma(\mc{W}_0,\dots,\mc{W}_{k-2},\mc{V},m)$ for the following conditions on $\mc{W}_0,\dots,\mc{W}_{k-2},m$:
     \begin{itemize}
@@
       \[
-        \sigma(\mc{W}_0,\dots,\mc{W}_{k-1},(n+1)k+i)
+        \sigma(\mc{W}_0,\dots,\mc{W}_{k-2},\mc{V},(n+1)k+i)
         \subseteq 
@@
 
-  Due to Telgarski in ``On Games of Topsoe'' (along with $\sigma$-compact implying $F\markwin \mengame{X}$).
+  Telgarski showed in ``On Games of Topsoe'' that a metrizable space is $\sigma$-compact if and only if there exists a winning strategy for $F$ in the Menger game, and Scheepers gave a more direct proof later.
+We slightly generalize Scheeper's proof.
+
+  \begin{definition}
+    A space $X$ is $H$-closed if for every open cover of $X$, there exists a finite subset of the cover whose union is dense in $X$.
+  \end{definition}
+
+  \begin{proposition}
+    For regular spaces, $X$ is $H$-closed if and only if $X$ is compact.
+  \end{proposition}
+
+  \begin{proof}
+    TODO: this
+  \end{proof}
+
+  \begin{definition}
+    A set $R\subseteq X$ is relatively compact to the topological space $X$ if for every open cover of the entire space $X$, there is a finite subcover of the set $R$.
+  \end{definition}
+
+  \begin{proposition}
+    Every subset of a compact set is relatively compact to the entire space.
+  \end{proposition}
+
+  \begin{proposition}
+    If $X$ is regular, then $Y$ is relatively compact if and only if $\cl{Y}$ is compact.
+  \end{proposition}
+
+  \begin{proof}
+    The reverse implication is trivial.
+
+    Assume $Y$ is relatively compact, let $\mc U$ be an open cover of $\cl Y$, and let $\mc V$ be an open cover of $X\setminus\cl Y$ such that the closure of each member also misses $\cl Y$ (possible by regularity).
+
+    Let $\mc W\subseteq \mc U \cup \mc V$ be a finite subcover of $Y$, and note $\cl{\bigcup\mc W} \supseteq \cl Y$.
+If $\mc F = \mc W \setminus \mc V$, then $\cl{\bigcup\mc F} \supseteq \cl Y$ as well.
+Thus $\bigcup\mc F$ is dense in $\cl Y$, showing $\cl Y$ is $H$-closed and thus compact.
+  \end{proof}
 
   \begin{theorem}
-    For metrizable $X$, $X$ is $\sigma$-compact if and only if $F \win \mengame{X}$ if and only if $F\markwin \mengame{X}$.
+    For metrizable $X$, the following are equivalent:
+      \begin{enumerate}[(a)]
+        \item $X$ is $\sigma$-compact
+        \item $X$ is $\sigma$-(relatively compact)
+        \item $F \win \mengame{X}$
+        \item $F\markwin \mengame{X}$
+      \end{enumerate}
   \end{theorem}
 
-  We adapt this result for regular spaces.
+  \begin{proof}
+    We've seen $(a) \Rightarrow (d)$, and $(d)\Rightarrow(c)$ is trivial. We may see $(b)\Rightarrow(a)$ since for regular spaces, the closure of a relatively compact set is compact.
+
+    To prove $(c)\Rightarrow(b)$, let $\sigma(\mc{U}_0,\dots,\mc{U}_{n-1})$ be a winning strategy for $F$, and observe that since $X$ is second-countable, we may assume all covers are countable.
+Let $\mathfrak{C}$ be the collection of all countable covers of $X$.
+We define $R_s,\mc{U}_s$ for $s\in\omega^{<\omega}$ as follows:
+      \begin{itemize}
+        \item $\ds R_\emptyset = \bigcap_{\mc{U}\in\mathfrak{C}} \left(\bigcup \sigma(\mc{U})\right)$
+        \item Note that there are only countably many distinct finite subsets $\sigma(\mc{U})$ of the countable collection $\mathfrak{C}$. Thus define each $\mc U_{\<n\>}$ so that
+          \[
+            R_\emptyset = 
+            \bigcap_{n<\omega}\left(\bigcup\sigma(\mc{U}_{\<n\>})\right)
+          \]
+        \item $\ds R_s = \bigcap_{\mc{U}\in\mathfrak{C}} \left(\bigcup \sigma(\mc{U}_{s\rest1},\mc{U}_{s\rest2},\dots,\mc{U}_s,\mc{U})\right)$
+        \item Again, note that there are only countably many distinct finite subsets $\sigma(\mc{U}_{s\rest1},\mc{U}_{s\rest2},\dots,\mc{U}_s,\mc{U})$ of the countable collection $\mathfrak{C}$.
+Thus define each $\mc U_{s\concat\<n\>}$ so that
+          \[
+            R_s = 
+            \bigcap_{n<\omega} \left(\bigcup \sigma(\mc{U}_{s\rest1},\mc{U}_{s\rest2},\dots,\mc{U}_s,\mc{U}_{s\concat\<n\>})\right)
+          \]
+      \end{itemize}
+
+    We quickly confirm that each $R_s$ is relatively compact as for each open cover $\mc{U}$ of $X$ we have the finite subcover $\sigma(\mc{U}_{s\rest1},\mc{U}_{s\rest2},\dots,\mc{U}_s,\mc{U})$ of $R_s$.
+
+    Finally, we claim that $X = \bigcup_{s\in\omega^{<\omega}} R_s$.
+If not, let $x$ be missed by every $R_s$, and define $f\in\omega^\omega$ such that $x\not\in \bigcup\sigma(\mc{U}_{f\rest1},\dots,\mc{U}_{f\rest n})$ for any $n$.
+Then $\mc{U}_{f\rest1},\mc{U}_{f\rest2},\dots$ is a counter to the winning strategy $\sigma$, a contradiction.
+  \end{proof}
+
+  We generalize this result for non-metric spaces.
 
@@
       \[
-        C_n = \bigcap_{\mc{U}\in\mathfrak{C}} \overline{\bigcup\sigma(\mc{U},n)}
+        R_n = \bigcap_{\mc{U}\in\mathfrak{C}} \bigcup\sigma(\mc{U},n)
       \]
-    and
-      \[
-        D_n = \bigcap_{\mc{U}\in\mathfrak{C}} \bigcup\sigma(\mc{U},n)
-      \]
-    it follows that $\bigcup_{n<\omega} C_n = \bigcup_{n<\omega} D_n = X$.
+    it follows that $R_n$ is relatively compact to $X$, and $\bigcup_{n<\omega} R_n = X$.
   \end{lemma}
@@
   \begin{proof}
-    Observe $D_n \subseteq C_n$.
-Suppose that $x \not\in D_n = \bigcap_{\mc{U}\in\mathfrak{C}} \bigcup\sigma(\mc{U},n)$ for any $n<\omega$.
+    First, we see that $\sigma(\mc{U},n)$ witnesses the relative compactness of $R_n$.
+Suppose that $x \not\in R_n = \bigcap_{\mc{U}\in\mathfrak{C}} \bigcup\sigma(\mc{U},n)$ for any $n<\omega$.
 Then for each $n$, pick $\mc{U}_n\in\mathfrak{C}$ such that $x\not\in \bigcup\sigma(\mc{U}_n,n)$.
-Then $\sigma$ does not defeat the play $\mc{U}_0,\mc{U}_1,\dots$ since the $\sigma(\mc{U}_n,n)$ do not cover $x$, contradiction.
+Then $\sigma$ does not defeat the play $\mc{U}_0,\mc{U}_1,\dots$ since the $\sigma(\mc{U}_n,n)$ do not cover $x$.
   \end{proof}
@@
   \begin{theorem}
-    For regular spaces $X$, $X$ is $\sigma$-compact if and only if $F \markwin \mengame{X}$.
+    A space $X$ is $\sigma$-(relatively compact) if and only if $F \markwin \mengame{X}$.
   \end{theorem}
@@
   \begin{proof}
-    The reverse implication has already been shown. To complete the proof, we look to Scheepers for inspiration.
+    For the forward implication, let $X=\bigcup_{n<\omega}R_n$ for $R_n$ relatively compact, and define $\sigma(\mc U,n)$ to be a finite subcover of $R_n$.
+The previous lemma proves the other direction.
+  \end{proof}
 
-    Let $\sigma(\mathcal{U},n)$ be a winning Markov strategy for $F$ in $\mengame{X}$. Let $\mathfrak{C}$ collect all open covers of $X$. Define
-      \[
-        C_n = \bigcap_{\mc{U}\in\mathfrak{C}} \overline{\bigcup\sigma(\mc{U},n)}
-      \]
-    as in the previous lemma. Note that $\bigcup_{n<\omega} C_n = X$, and we will show each $C_n$ is compact as it is $H$-closed.
-
-    Let $\mc{U}$ be an open cover of $C_n$, and $\mc{V}$ be a cover of $X\setminus C_n$ by open sets whose closures are disjoint from $C_n$ (possible by regularity).
-
-    Since $\mc{U}\cup\mc{V}$ covers $X$, $\overline{\bigcup\sigma(\mc{U}\cup\mc{V},n)} \supseteq C_n$.
-Furthermore, if $\mc{F} = \sigma(\mc{U}\cup\mc{V},n)\setminus \mc{V}$, then $\overline{\bigcup\mc{F}} \supseteq C_n$ (the closures of sets in $\mc{V}$ missed $C_n$).
-Thus $\mc{F}$ witnesses that $C_n$ is $H$-closed.
-  \end{proof}
+  \begin{corollary}
+    For regular spaces $X$, the following are equivalent:
+      \begin{enumerate}[(a)]
+        \item $X$ is $\sigma$-compact
+        \item $X$ is $\sigma$-(relatively compact)
+        \item $F \markwin \mengame{X}$
+      \end{enumerate}
+  \end{corollary}
 
@@
       \[
-        D_n = \bigcap_{\mc{U}\in\mathfrak{C}} \bigcup\sigma(\mc{U},n)
+        R_n = \bigcap_{\mc{U}\in\mathfrak{C}} \bigcup\sigma(\mc{U},n)
       \]
   where $\mathfrak{C}$ is the collection of open covers of $R$.
-For any $x_0,x_1,\dots \in R$, we may define the open cover $\mc{U} = \{R \setminus \{x_i: i \not= n\} : n < \omega \}$, and observe that $\bigcup \sigma(\mc{U},n) \supseteq D_n$ cannot contain every $x_i$.
-Thus $D_n$ is finite, but since the previous lemma requires $\bigcup_{n<\omega} D_n = R$ if $\sigma$ is a winning strategy, there exists a counter to $\sigma$.
+For any $x_0,x_1,\dots \in R$, we may define the open cover $\mc{U} = \{R \setminus \{x_i: i \not= n\} : n < \omega \}$, and observe that $\bigcup \sigma(\mc{U},n) \supseteq R_n$ contains only finitely many $x_i$.
+Thus $R_n$ is finite, but since the previous lemma requires $\bigcup_{n<\omega} R_n = R$ if $\sigma$ is a winning strategy, there exists a counter to $\sigma$.
   \end{proof}
@@
 
-    Let $\mathfrak{C}$ collect all the open covers of $X$. We say $X$ is \scish if there exists a fuction $f:\mathfrak{C}\times\omega\to\mc{P}(X)$ such that:
+    Let $\mathfrak{C}$ collect all the open covers of $X$. We say $X$ is \scish if there exists a function $f:\mathfrak{C}\times\omega\to\mc{P}(X)$ such that:
       \begin{itemize}
@@
 
+  \newpage
+
+  \begin{definition}
+    $X$ is \textbf{Rothberger} if for all open covers $\mathcal{U}_0,\mathcal{U}_1,\dots$ there exist open sets $U_n\in \mathcal{U}_n$ such that $\{U_n:n<\omega\}$ is a cover of $X$.
+  \end{definition}
+
+  \begin{proposition}
+    Rothberger $\Rightarrow$ Menger
+  \end{proposition}
+
+  \begin{definition}
+    In the two-player game $\rothgame{X}$ player $C$ chooses open covers $\mathcal{U}_n$ of $X$, followed by player $O$ choosing an open set $U_n\in\mathcal{U}_n$.
+$O$ wins if $\{U_n:n<\omega\}$ is a cover of $X$.
+  \end{definition}
+
+  \begin{theorem}
+    $X$ is Rothberger if and only if $C\not\win\rothgame{X}$.
+  \end{theorem}
+
+  \begin{proof}
+    Due to Pawlikowski
+  \end{proof}
+
 \end{document}

### 2013-06-06 menger.tex
added H-closed proof

@@
   \begin{proof}
-    TODO: this
+    The backward implication is trivial, so let $X$ be $H$-closed.
+For any open cover $\mc U$ of $X$ and point $x\in X$, choose $x\in V_x\subseteq \cl{V_x}\subseteq U_x\in \mc U$.
+Then if $\mc F = \{V_{x_i}:i<n\}$ is a finite subset of $\mc V=\{V_x:x\in X\}$ with dense union in $X$, then $\mc G = \{U_{x_i}:i<n\}\subseteq \mc U$ is a finite subcover of $X$.
   \end{proof}
@@
   \end{definition}
-
-  \begin{proposition}
-    Every subset of a compact set is relatively compact to the entire space.
-  \end{proposition}
 
@@
   \begin{proof}
-    We've seen $(a) \Rightarrow (d)$, and $(d)\Rightarrow(c)$ is trivial. We may see $(b)\Rightarrow(a)$ since for regular spaces, the closure of a relatively compact set is compact.
+    We've seen $(a) \Rightarrow (d)$, and $(d)\Rightarrow(c)$, $(b)\Rightarrow(a)$ are trivial.
 
@@
         \item $\ds R_\emptyset = \bigcap_{\mc{U}\in\mathfrak{C}} \left(\bigcup \sigma(\mc{U})\right)$
-        \item Note that there are only countably many distinct finite subsets $\sigma(\mc{U})$ of the countable collection $\mathfrak{C}$. Thus define each $\mc U_{\<n\>}$ so that
+        \item Note that there are only countably many distinct finite subsets $\sigma(\mc{U})$ of the countable collection $\mc U$. Thus define each $\mc U_{\<n\>}$ so that
           \[
@@
         \item $\ds R_s = \bigcap_{\mc{U}\in\mathfrak{C}} \left(\bigcup \sigma(\mc{U}_{s\rest1},\mc{U}_{s\rest2},\dots,\mc{U}_s,\mc{U})\right)$
-        \item Again, note that there are only countably many distinct finite subsets $\sigma(\mc{U}_{s\rest1},\mc{U}_{s\rest2},\dots,\mc{U}_s,\mc{U})$ of the countable collection $\mathfrak{C}$.
+        \item Again, note that there are only countably many distinct finite subsets $\sigma(\mc{U}_{s\rest1},\mc{U}_{s\rest2},\dots,\mc{U}_s,\mc{U})$ of the countable collection $\mc U$.
 Thus define each $\mc U_{s\concat\<n\>}$ so that
@@
   \end{proof}
-
-  We generalize this result for non-metric spaces.
 

### 2013-06-07 menger.tex
minor updates

@@
   Telgarski showed in ``On Games of Topsoe'' that a metrizable space is $\sigma$-compact if and only if there exists a winning strategy for $F$ in the Menger game, and Scheepers gave a more direct proof later.
-We slightly generalize Scheeper's proof.
+We generalize Scheeper's proof to handle a number of cases.
 
-  \begin{definition}
-    A space $X$ is $H$-closed if for every open cover of $X$, there exists a finite subset of the cover whose union is dense in $X$.
-  \end{definition}
+  % \begin{definition}
+  %   A space $X$ is $H$-closed if for every open cover of $X$, there exists a finite subset of the cover whose union is dense in $X$.
+  % \end{definition}
 
-  \begin{proposition}
-    For regular spaces, $X$ is $H$-closed if and only if $X$ is compact.
-  \end{proposition}
+  % \begin{proposition}
+  %   For regular spaces, $X$ is $H$-closed if and only if $X$ is compact.
+  % \end{proposition}
 
-  \begin{proof}
-    The backward implication is trivial, so let $X$ be $H$-closed.
+  % \begin{proof}
+  %   The backward implication is trivial, so let $X$ be $H$-closed.
 For any open cover $\mc U$ of $X$ and point $x\in X$, choose $x\in V_x\subseteq \cl{V_x}\subseteq U_x\in \mc U$.
 Then if $\mc F = \{V_{x_i}:i<n\}$ is a finite subset of $\mc V=\{V_x:x\in X\}$ with dense union in $X$, then $\mc G = \{U_{x_i}:i<n\}\subseteq \mc U$ is a finite subcover of $X$.
-  \end{proof}
+  % \end{proof}
 
@@
 
-    Assume $Y$ is relatively compact, let $\mc U$ be an open cover of $\cl Y$, and let $\mc V$ be an open cover of $X\setminus\cl Y$ such that the closure of each member also misses $\cl Y$ (possible by regularity).
+    Assume $Y$ is relatively compact, let $\mc U$ be an open cover of $\cl Y$, and define $x\in V_x\subseteq \cl{V_x}\subseteq U_x \in \mc U$ for each $x\in X$.
+Then if we take a cover $\mc F = \{V_{x_i} : i<n\}$ of $Y$ by relative compactness, then $\{U_{x_i}:i<n\}$ is a finite cover of $\cl Y$, showing compactness.
+  \end{proof}
 
-    Let $\mc W\subseteq \mc U \cup \mc V$ be a finite subcover of $Y$, and note $\cl{\bigcup\mc W} \supseteq \cl Y$.
-If $\mc F = \mc W \setminus \mc V$, then $\cl{\bigcup\mc F} \supseteq \cl Y$ as well.
-Thus $\bigcup\mc F$ is dense in $\cl Y$, showing $\cl Y$ is $H$-closed and thus compact.
+  \begin{lemma}
+    Let $\sigma(\mc{U}, n)$ be a winning Markov strategy for $F$ in $\mengame{X}$, and $\mathfrak{C}$ collect all open covers of $X$. Then for
+      \[
+        R_n = \bigcap_{\mc{U}\in\mathfrak{C}} \bigcup\sigma(\mc{U},n)
+      \]
+    it follows that $R_n$ is relatively compact to $X$, and $\bigcup_{n<\omega} R_n = X$.
+  \end{lemma}
+
+  \begin{proof}
+    First, we see that $\sigma(\mc{U},n)$ witnesses the relative compactness of $R_n$.
+Suppose that $x \not\in R_n = \bigcap_{\mc{U}\in\mathfrak{C}} \bigcup\sigma(\mc{U},n)$ for any $n<\omega$.
+Then for each $n$, pick $\mc{U}_n\in\mathfrak{C}$ such that $x\not\in \bigcup\sigma(\mc{U}_n,n)$.
+Then $\sigma$ does not defeat the play $\mc{U}_0,\mc{U}_1,\dots$
   \end{proof}
@@
   \begin{theorem}
-    For metrizable $X$, the following are equivalent:
+    A space $X$ is $\sigma$-(relatively compact) if and only if $F \markwin \mengame{X}$.
+  \end{theorem}
+
+  \begin{proof}
+    For the forward implication, let $X=\bigcup_{n<\omega}R_n$ for $R_n$ relatively compact, and define $\sigma(\mc U,n)$ to be a finite subcover of $R_n$.
+The previous lemma proves the other direction.
+  \end{proof}
+
+  \begin{corollary}
+    For regular spaces $X$, the following are equivalent:
       \begin{enumerate}[(a)]
         \item $X$ is $\sigma$-compact
+        \item $X$ is $\sigma$-(relatively compact)
+        \item $F \markwin \mengame{X}$
+      \end{enumerate}
+  \end{corollary}
+
+  \begin{theorem}
+    For second-countable $X$, the following are equivalent:
+      \begin{enumerate}[(a)]
         \item $X$ is $\sigma$-(relatively compact)
@@
 
-  \begin{proof}
-    We've seen $(a) \Rightarrow (d)$, and $(d)\Rightarrow(c)$, $(b)\Rightarrow(a)$ are trivial.
-
-    To prove $(c)\Rightarrow(b)$, let $\sigma(\mc{U}_0,\dots,\mc{U}_{n-1})$ be a winning strategy for $F$, and observe that since $X$ is second-countable, we may assume all covers are countable.
+  \begin{proof}.
+    We need only show $(b)\Rightarrow(a)$, so let $\sigma(\mc{U}_0,\dots,\mc{U}_{n-1})$ be a winning strategy for $F$, and observe that since $X$ is second-countable, we may assume all covers are countable.
 Let $\mathfrak{C}$ be the collection of all countable covers of $X$.
@@
 
-  \begin{lemma}
-    Let $\sigma(\mc{U}, n)$ be a winning Markov strategy for $F$ in $\mengame{X}$, and $\mathfrak{C}$ collect all open covers of $X$. Then for
-      \[
-        R_n = \bigcap_{\mc{U}\in\mathfrak{C}} \bigcup\sigma(\mc{U},n)
-      \]
-    it follows that $R_n$ is relatively compact to $X$, and $\bigcup_{n<\omega} R_n = X$.
-  \end{lemma}
-
-  \begin{proof}
-    First, we see that $\sigma(\mc{U},n)$ witnesses the relative compactness of $R_n$.
-Suppose that $x \not\in R_n = \bigcap_{\mc{U}\in\mathfrak{C}} \bigcup\sigma(\mc{U},n)$ for any $n<\omega$.
-Then for each $n$, pick $\mc{U}_n\in\mathfrak{C}$ such that $x\not\in \bigcup\sigma(\mc{U}_n,n)$.
-Then $\sigma$ does not defeat the play $\mc{U}_0,\mc{U}_1,\dots$ since the $\sigma(\mc{U}_n,n)$ do not cover $x$.
-  \end{proof}
-
-  \begin{theorem}
-    A space $X$ is $\sigma$-(relatively compact) if and only if $F \markwin \mengame{X}$.
-  \end{theorem}
-
-  \begin{proof}
-    For the forward implication, let $X=\bigcup_{n<\omega}R_n$ for $R_n$ relatively compact, and define $\sigma(\mc U,n)$ to be a finite subcover of $R_n$.
-The previous lemma proves the other direction.
-  \end{proof}
-
   \begin{corollary}
-    For regular spaces $X$, the following are equivalent:
+    For metric spaces $X$, the following are equivalent:
       \begin{enumerate}[(a)]
@@
         \item $X$ is $\sigma$-(relatively compact)
+        \item $F \win \mengame{X}$
         \item $F \markwin \mengame{X}$

### 2013-06-10 menger.tex
Lots of rothberger stuff, in middle of silly proof

@@
 
+  \begin{definition}
+    A space $X$ is scattered if every subspace contains an isolated point.
+By convention, $\ds X = \bigcup_{\alpha<\rank(X)}X^\alpha$ where $X^\alpha$ is the set of isolated points of $\ds X\setminus\bigcup_{\beta<\alpha}X^\beta$.
+  \end{definition}
+
+  \begin{proposition}
+    A space $X$ is scattered if and only if every closed subspace contains an isolated point.
+  \end{proposition}
+
+  \begin{proposition}
+    The rank of a compact scattered $T_1$ space is a successor ordinal, and $X^{\rank(X)-1}$ is finite.
+  \end{proposition}
+
+  \begin{proof}
+    Suppose that the rank of $X$ was a limit ordinal $\beta$.
+Then by choosing $\beta_n\to\beta$, we may pick a point $x_n\in X^{\beta_n}$, and $\{x_n: n<\omega\}$ may be shown to be a closed discrete subspace of $X$.
+
+    It's easily seen that $X^{\rank(X)-1}$ must be finite - it is a closed discrete subspace of compact $X$.
+  \end{proof}
+
+  \begin{theorem}
+    The following are equivalent for compact $T_2$ $X$:
+      \begin{enumerate}[(a)]
+        \item $X$ is Rothberger
+        \item $X$ is scattered
+        \item $O\win\rothgame{X}$
+      \end{enumerate}
+  \end{theorem}
+
+  \begin{proof}
+    To show $(a)\Rightarrow(b)$, we use Aurichi's proof in \textit{D-Spaces}: suppose $X$ has a closed subspace without isolated points.
+Then it is compact and contains a closed copy of the Cantor set, which is not Rothberger, contradiction.
+
+    To show $(b)\Rightarrow(c)$, if $X$ is scattered, suppose during a particular round $n$, player $O$ observes that the uncovered subspace $Y \subseteq X$ is nonempty.
+Then as $Y$ is also compact scattered,  select one of the finite points in $Y^{\rank(Y)-1}$, label it $x_n$, and choose an open set containing $x_n$ from the given cover.
+
+    We claim that if $O$ follows this strategy, player $O$ will observe that the uncovered subspace $Y\subseteq X$ is empty during some round.
+If not, consider the $x_n$ chosen by $Y$ by the end of the game - the rank of each point within $X$ is nonincreasing, and does not contain a constant final sequence, contradiction.
+
+    Of course, $(c)\Rightarrow(a)$ is trivial.
+  \end{proof}
+
+  \begin{theorem}
+    The following are equivalent for points-$G_\delta$ $X$:
+      \begin{enumerate}[(a)]
+        \item $O\win\rothgame{X}$
+        \item $O\markwin\rothgame{X}$
+        \item $|X|=\omega$
+      \end{enumerate}
+  \end{theorem}
+
+  \begin{proof}
+    $(c)\Rightarrow(b)\Rightarrow(a)$ are all trivial. Galvin has shown $(a)\Rightarrow(c)$ in \textit{Indeterminacy}, but a direct proof follows.
+
+    Suppose $X$ is uncountable: define open sets $G_{x,m}$ for $x\in X$ and $m<\omega$ such that $\{x\}=\bigcap_{m<\omega} G_{x,m}$. Let $\mc{U}_m = \{G_{x,m} : x\in X \}$.
+      \[
+        A = \{ x \in X : \exists \<m_0,\dots,m_{n-1}\>\in\omega^{<\omega} ( 
+          \sigma(\mc{U}_{m_0},\dots,\mc{U}_{m_{n-1}})=G_{x,m_{n-1}} )\}
+      \]
+    Since $|A|=\omega$, choose $x\in X\setminus A$, and during round $n$, playasdf. TODO finish
+  \end{proof}
+
 \end{document}

### 2013-06-12 menger.tex
Proved Galvin's result, for Cov_CS

@@
   \begin{definition}
-    In the two-player game $\rothgame{X}$ player $C$ chooses open covers $\mathcal{U}_n$ of $X$, followed by player $O$ choosing an open set $U_n\in\mathcal{U}_n$.
-$O$ wins if $\{U_n:n<\omega\}$ is a cover of $X$.
+    In the two-player game $\rothgame{X}$ player $C$ chooses open covers $\mathcal{U}_n$ of $X$, followed by player $S$ choosing an open set $U_n\in\mathcal{U}_n$.
+$S$ wins if $\{U_n:n<\omega\}$ is a cover of $X$.
   \end{definition}
@@
 
-    To show $(b)\Rightarrow(c)$, if $X$ is scattered, suppose during a particular round $n$, player $O$ observes that the uncovered subspace $Y \subseteq X$ is nonempty.
+    To show $(b)\Rightarrow(c)$, if $X$ is scattered, suppose during a particular round $n$, player $S$ observes that the uncovered subspace $Y \subseteq X$ is nonempty.
 Then as $Y$ is also compact scattered,  select one of the finite points in $Y^{\rank(Y)-1}$, label it $x_n$, and choose an open set containing $x_n$ from the given cover.
 
-    We claim that if $O$ follows this strategy, player $O$ will observe that the uncovered subspace $Y\subseteq X$ is empty during some round.
+    We claim that if $S$ follows this strategy, player $S$ will observe that the uncovered subspace $Y\subseteq X$ is empty during some round.
 If not, consider the $x_n$ chosen by $Y$ by the end of the game - the rank of each point within $X$ is nonincreasing, and does not contain a constant final sequence, contradiction.
@@
 
+  \begin{definition}
+    In the two-player game $\altrothgame{X}$ player $P$ chooses points $x_n\in X$, followed by player $O$ choosing an open neighborhood $U_n$ of $x_n$.
+$P$ wins if $\{U_n:n<\omega\}$ is a cover of $X$.
+  \end{definition}
+
+  \begin{theorem} $\altrothgame{X}$ is equivalent to $\rothgame{X}$. That is:
+
+    \begin{itemize}
+      \item $P\win\altrothgame{X}$ if and only if $S\win\rothgame{X}$
+      \item $O\win\altrothgame{X}$ if and only if $C\win\rothgame{X}$.
+    \end{itemize}
+  \end{theorem}
+
+  \begin{proof}
+    Due to Galvin.
+
+    \begin{itemize}
+      \item
+      Let $\sigma$ be a strategy for $S$ in $\rothgame{X}$.
+
+      We define a strategy for $P$ in $\altrothgame{X}$ as follows: during round $0$, $P$ chooses a point $x_0$ for which every open neighborhood is of the form $U_0 = \sigma(\mc{U}_0)$ for some open cover $\mc{U}_0$.
+(If not, let $U_x$ witness for every $x\in X$, and note that $\sigma(\{U_x:x\in X\})$ is a contradiction.)
+
+      During round $n+1$, $P$ chooses point $x_{n+1}$ for which every open neighborhood is of the form $U_{n+1}=\sigma(\mc{U}_0,\dots,\mc{U}_n,\mc{U}_{n+1})$ for some open cover $\mc{U}_{n+1}$.
+(If not, let $U_x$ witness for every $x\in X$, and note that $\sigma(\mc{U}_0,\dots,\mc{U}_n,\{U_x:x\in X\})$ is a contradiction.)
+
+      If $\sigma$ was a winning strategy for $S$, then the open sets chosen by $P$ are of the form $\{\sigma(\mc U_0),\sigma(\mc U_0,\mc U_1),\dots\}$ and are an open cover of $X$.
+
+      \item
+      Let $\sigma$ be a strategy for $P$ in $\altrothgame{X}$.
+
+      We define a strategy for $S$ in $\rothgame{X}$ as follows: during round $n$, if $S$ has chosen $U_0,\dots,U_{n-1}$ in previous rounds, $S$ chooses an open set covering the point $\sigma(U_0,\dots,U_{n-1})$.
+If $\sigma$ was a winning strategy for $P$, then for any open sets $U_0,U_1,\dots$ containing $\sigma(\cdot),\sigma(U_0),\dots$, the collection $\{U_0,U_1,\dots\}$ is a cover for $X$.
+
+      \item
+      Let $\sigma$ be a strategy for $C$ in $\rothgame{X}$.
+
+      We define a strategy for $O$ in $\altrothgame{X}$ as follows: during round $n$, if $O$ has chosen $U_0,\dots,U_{n-1}$ in previous rounds, $O$ chooses an open set from the cover $\sigma(U_0,\dots,U_{n-1})$ containing the point chosen by $P$ that round.
+If $\sigma$ was a winning strategy for $C$, then for any open sets $U_0,U_1,\dots$ from the covers $\sigma(\cdot),\sigma(U_0),\dots$, the collection $\{U_0,U_1,\dots\}$ is not a cover for $X$.
+
+      \item
+      Let $\sigma$ be a strategy for $O$ in $\altrothgame{X}$.
+
+      We define a strategy for $C$ in $\rothgame{X}$ as follows: during round $0$, $C$ chooses $\mc{U}_0 = \{\sigma(x) : x\in X\}$.
+In response, $S$ chooses some $\sigma(x_0)$.
+During round $n+1$, if $S$ has chosen $\sigma(x_0),\dots,\sigma(x_0,\dots,x_n)$ in previous rounds, $C$ chooses $\mc{U}_{n+1} = \{\sigma(x_0,\dots,x_n,x) : x\in X\}$.
+If $\sigma$ was a winning strategy for $O$, then $\{\sigma(x_0),\sigma(x_0,x_1),\dots\}$ is not a cover for $X$.
+
+    \end{itemize}
+  \end{proof}
+
   \begin{theorem}
@@
       \begin{enumerate}[(a)]
-        \item $O\win\rothgame{X}$
-        \item $O\markwin\rothgame{X}$
+        \item $S\win\rothgame{X}$
+        \item $S\markwin\rothgame{X}$
         \item $|X|=\omega$
@@
   \begin{proof}
-    $(c)\Rightarrow(b)\Rightarrow(a)$ are all trivial. Galvin has shown $(a)\Rightarrow(c)$ in \textit{Indeterminacy}, but a direct proof follows.
+    $(c)\Rightarrow(b)\Rightarrow(a)$ are all trivial. Galvin has shown $(a)\Rightarrow(c)$ in \textit{Indeterminacy}, but a direct proof follows. Let $\sigma$ be a strategy for $S$ in $\rothgame{X}$.
 
-    Suppose $X$ is uncountable: define open sets $G_{x,m}$ for $x\in X$ and $m<\omega$ such that $\{x\}=\bigcap_{m<\omega} G_{x,m}$. Let $\mc{U}_m = \{G_{x,m} : x\in X \}$.
+    Let $G_{x,m}$ designate open sets such that $\{x\}=\bigcap_{m<\omega}G_{x,m}$ for all $x\in X$.
+
+    Suppose for $s\in\omega^{<\omega}$, $\mc U_t$ is defined for each $t\leq s$.
+Then $C$ may find a point $x_s$ such that for each $m<\omega$, there exists an open cover $\mc U_{s\concat\<m\>}$ where $\sigma(\mc U_{s\rest1},\dots,\mc U_{s},\mc U_{s\concat\<m\>})=G_{x_s,m}$.
+(If not, let $m(x)$ witness the contrary for each $x$, and consider $\sigma(\mc U_{s\rest0},\dots,\mc U_s,\{G_{x,m(x)}:x\in X\})$ to see the contradiction.)
+
+    If $x\not\in\{x_s:s\in\omega^{<\omega}\}$, then $C$ may counter the strategy $\sigma$ by choosing $f\in\omega^\omega$ where $x\not\in G_{x_{f\rest n},f(n)}$, and playing $\mc U_{f\rest1},\mc U_{f\rest2},\dots$, for which
       \[
-        A = \{ x \in X : \exists \<m_0,\dots,m_{n-1}\>\in\omega^{<\omega} ( 
-          \sigma(\mc{U}_{m_0},\dots,\mc{U}_{m_{n-1}})=G_{x,m_{n-1}} )\}
+        x\not\in 
+        \bigcup_{n<\omega} G_{x_{f\rest n},f(n)}=
+        \bigcup_{n<\omega} \sigma(\mc U_{f\rest1},\dots,\mc U_{f\rest n+1})
       \]
-    Since $|A|=\omega$, choose $x\in X\setminus A$, and during round $n$, playasdf. TODO finish
+
+    Thus if $\sigma$ is a winning strategy, then $X=\{x_s:s\in\omega^{<\omega}\}$ is countable.
   \end{proof}

### 2013-07-04 menger.tex
menger/rothberger updates
menger updates, added inverse limit seminar folder

@@
 
-  \begin{theorem} $\altrothgame{X}$ is equivalent to $\rothgame{X}$. That is:
+  \begin{theorem} $\altrothgame{X}$ is ``perfect information equivalent'' to $\rothgame{X}$. That is:
 
@@
 
-      We define a strategy for $P$ in $\altrothgame{X}$ as follows: during round $0$, $P$ chooses a point $x_0$ for which every open neighborhood is of the form $U_0 = \sigma(\mc{U}_0)$ for some open cover $\mc{U}_0$.
-(If not, let $U_x$ witness for every $x\in X$, and note that $\sigma(\{U_x:x\in X\})$ is a contradiction.)
+      Let $n<\omega$, and consider open covers $\mc{U}_m$ for each $m<n$.
+Suppose that for each $x\in X$, there was an open neighborhood $U_x$ of $x$ where for every open cover $\mc U$, $\sigma(\mc U_0,\dots,\mc U_{n-1},\mc U)\not=U_x$.
+The open cover $\{U_x : x\in X\}$ demonstrates the contradiction.
 
-      During round $n+1$, $P$ chooses point $x_{n+1}$ for which every open neighborhood is of the form $U_{n+1}=\sigma(\mc{U}_0,\dots,\mc{U}_n,\mc{U}_{n+1})$ for some open cover $\mc{U}_{n+1}$.
-(If not, let $U_x$ witness for every $x\in X$, and note that $\sigma(\mc{U}_0,\dots,\mc{U}_n,\{U_x:x\in X\})$ is a contradiction.)
+      We define a strategy for $P$ in $\altrothgame{X}$ as follows: during round $n$, $P$ chooses a point $x_n$ for which every open neighborhood is of the form $U_n = \sigma(\mc U_0,\dots,\mc U_{n-1},\mc{U}_n)$ for some open cover $\mc{U}_0$.
 
-      If $\sigma$ was a winning strategy for $S$, then the open sets chosen by $P$ are of the form $\{\sigma(\mc U_0),\sigma(\mc U_0,\mc U_1),\dots\}$ and are an open cover of $X$.
+      If $\sigma$ was a winning strategy for $S$ in $\rothgame{X}$, then the open sets chosen by $O$ in response to $P$'s strategy for $\altrothgame{X}$ are of the form $\{\sigma(\mc U_0),\sigma(\mc U_0,\mc U_1),\dots\}$ and are an open cover of $X$.
 
@@
 
+  % \begin{theorem}
+  % For any $T_1$ space $X$, the following are equivalent:
+  %   \begin{itemize}
+  %     \item $S\markwin\rothgame{X}$
+  %     \item $|X|=\omega$
+  %   \end{itemize}
+  % \end{theorem}
+
+  % \begin{proof}
+  %   If $|X|=\omega$ then the winning Markov strategy is obvious, so let $\sigma(\mc U,n)$ be a Markov strategy.
+
+  %   Let $n<\omega$.
+Suppose that for each $x\in X$, there was an open neighborhood $U_x$ of $x$ where for every open cover $\mc U$, $\sigma(\mc U,n)\not=U_x$.
+The open cover $\{U_x : x\in X\}$ demonstrates the contradiction.
+
+  %   So let $x_n\in X$ be chosen such that for each open neighborhood $U$ of $x_n$, there is an open cover $\mc U$ such that $\sigma(\mc U,n)=U$.
+Then if $x\not=\{x_n : n<\omega\}$, $C$ may counter $\sigma$ as follows: during round $n$, choose $U_n$ which contains $x_n$ but not $x$, and then choose $\mc U_n$ such that $\sigma(\mc U_n,n)=U_n$.
+  % \end{proof}
+
+  \begin{theorem}
+  For any $T_1$ space $X$, the following are equivalent:
+    \begin{itemize}
+      \item $S\markwin\rothgame{X}$
+      \item $|X|=\omega$
+    \end{itemize}
+  \end{theorem}
+
+  \begin{proof}
+    If $|X|=\omega$ then the winning Markov strategy is obvious, so let $\sigma(\mc U,n)$ be a Markov strategy.
+
+    Let $n<\omega$.
+Suppose that for each $x\in X$, there was an open neighborhood $U_x$ of $x$ where for every open cover $\mc U$, $\sigma(\mc U,n) \not= U_x$.
+The open cover $\{U_x : x\in X\}$ demonstrates the contradiction.
+
+    So let $x_n\in X$ be chosen such that for each open neighborhood $U$ of $x_n$, there is an open cover $\mc U$ such that $\sigma(\mc U,n)=U$.
+Then if $x\not=\{x_n : n<\omega\}$, $C$ may counter $\sigma$ as follows: during round $n$, choose $U_n$ which contains $x_n$ but not $x$, and then choose $\mc U_n$ such that $\sigma(\mc U_n,n)=U_n$.
+  \end{proof}
+
+  % \begin{example}
+  %   For the one-point Lindel\"ofication $\oneptlind{\omega_1}$ (a $T_2$ space), $S\win\rothgame{\oneptlind{\omega}}$, but $S\not\kmarkwin{k}\rothgame{X}$ for any $k$.
+  % \end{example}
+
+  \begin{example}
+    Let $X=\omega_1\cup\{\infty\}$ be a ``weak Lindel\"ofication'' of $\omega_1$ such that open neighborhoods of $\infty$ contain the complement of $\omega$.
+This space is $T_0$ (provided the topology on $\omega_1$ is) but not $T_1$, and note that $S\markwin\rothgame{X}$ and $|X|>\omega$.
+  \end{example}
+
   \begin{theorem}
@@
         \item $S\win\rothgame{X}$
-        \item $S\markwin\rothgame{X}$
+        \item $S\kmarkwin{k}\rothgame{X}$
         \item $|X|=\omega$
@@
 
-    Suppose for $s\in\omega^{<\omega}$, $\mc U_t$ is defined for each $t\leq s$.
-Then $C$ may find a point $x_s$ such that for each $m<\omega$, there exists an open cover $\mc U_{s\concat\<m\>}$ where $\sigma(\mc U_{s\rest1},\dots,\mc U_{s},\mc U_{s\concat\<m\>})=G_{x_s,m}$.
-(If not, let $m(x)$ witness the contrary for each $x$, and consider $\sigma(\mc U_{s\rest0},\dots,\mc U_s,\{G_{x,m(x)}:x\in X\})$ to see the contradiction.)
+    Let $n<\omega$, $s\in\omega^{n}$, and consider open covers $\mc{U}_t$ for each $t\leq s$.
+Suppose that for each $x\in X$, there was an open neighborhood $U_x$ of $x$ where for every open cover $\mc U$, $\sigma(\mc U_{s\rest 1},\dots,\mc U_{s},\mc U)\not=U_x$.
+The open cover $\{U_x : x\in X\}$ demonstrates the contradiction.
 
-    If $x\not\in\{x_s:s\in\omega^{<\omega}\}$, then $C$ may counter the strategy $\sigma$ by choosing $f\in\omega^\omega$ where $x\not\in G_{x_{f\rest n},f(n)}$, and playing $\mc U_{f\rest1},\mc U_{f\rest2},\dots$, for which
-      \[
-        x\not\in 
-        \bigcup_{n<\omega} G_{x_{f\rest n},f(n)}=
-        \bigcup_{n<\omega} \sigma(\mc U_{f\rest1},\dots,\mc U_{f\rest n+1})
-      \]
-
-    Thus if $\sigma$ is a winning strategy, then $X=\{x_s:s\in\omega^{<\omega}\}$ is countable.
+    Thus $C$ may find points $x_s$ such that for each $m<\omega$, there exists an open cover $\mc U_{s\concat\<m\>}$ where $\sigma(\mc U_{s\rest 1},\dots,\mc U_{s},\mc U_{s\concat\<m\>})=G_{x_s,m}$.
+Then if $x\not=\{x_s : s\in\omega^{<\omega}\}$, $C$ may counter $\sigma$ as follows: during round $n$, choose $f(n)$ so that $x\not\in G_{x_{f\rest n},f(n)}$, and then choose $\mc U_{f\rest n\concat\<f(n)\>}$ such that $\sigma(\mc U_{f\rest 1},\dots,\mc U_{f\rest n},\mc U_{f\rest n\concat\<f(n)\>})=G_{x_{f\rest n},f(n)}$.
   \end{proof}
 
+  \begin{question}
+    $S\kmarkwin{2}\rothgame{\oneptcomp{\omega_1}}$ or $S\kmarkwin{2}\rothgame{\oneptlind{\omega_1}}$?
+  \end{question}
+
+  \begin{question}
+    $S\kmarkwin{2}\rothgame{X}\Leftrightarrow S\kmarkwin{k}\rothgame{X}$?
+  \end{question}
+
 \end{document}

### 2013-07-04 miscellaneous/inverse-limit-seminar-summer-2013/results.tex
Refactored file system

\input{../header.tex}

\begin{document}

\begin{example}
Let $L\subseteq \prod_{i=1}^\infty [0,1]$ be the inverse limit space with bonding functions all equal to
\[
  f(x) = \left\{
     \begin{array}{lr}
       2x & : x \leq 0.5 \\
       2-2x & : x \geq 0.5
     \end{array}
   \right.
\]
Then the following hold:
  \begin{enumerate}
    \item The subspaces $C_t = \{\alpha\in L : \alpha(1)=t\}$ are each homeomorphic to the Cantor Set.
    \item All proper subcontinuua are homeomorphic to the unit interval $[0,1]$
    \item All proper subcontinuua are nowhere dense in the space.
  \end{enumerate}
\end{example}

\begin{proof}
For (1), consider that for each number $t\in(0,1)$, there are exactly two preimages under $f$ inside $(0,1)$, giving a natural corespondance with the Cantor tree with branches given by points in the Cantor set $2^\omega$. The arguments for $t=0,1$ are similar.

For (2), we first claim that all basic open sets are of the form $L\cap\prod_{n=1}^\infty B_n$ where $B_n=[0,1]$ for all $n\not=N$. By definition all basic open sets are of the form $L\cap\prod_{n=1}^\infty A_n$ where $A_n=[0,1]$ for all $n\not=N_1,\dots,N_m$. It's easily seen that if $N=N_m$ and $B_N = \bigcap_{i=1}^m (f^{-1})^{(N_m-N_i)}(A_{N_i})$ and $B_n=[0,1]$ otherwise, then $L\cap\prod_{n=1}^\infty A_n = L\cap\prod_{n=1}^\infty B_n$.

Using this fact, we can argue that each proper subcontinuum $K$ is of the form $L \cap \prod_{n=1}^\infty [a_n,b_n]$ where $0\leq a_N < b_N < 1$ for some $N$.

First note that every maximal basic open set missed by $K$ must be of the form $L\cap\prod_{n=1}^\infty B_n$ here $B_n=[0,1]$ for all $n\not=N$ and $[0,1] \setminus B_N$ is connected, that is, $B_N=[0,a)\cup(b,1]$. (If not, then the disconnection of $[0,1]\setminus B_N$ yields a disconnection for $K$.) Thus $K = \prod_{n=1}^\infty [0,1]\setminus ([0,a_n)\cup(b_n,1]) = \prod_{n=1}^\infty [a_n,b_n]$.

We can see that $a_n<b_n$ always; otherwise the continuum is a single point. Suppose $b_n = 1$ for all $n$, then either $a_n=0$ for all $n$ (contradiction since $K$ is a proper subcontinuum), or $a_N>0$, and $b_{N+1}\leq 1-\frac{a_N}{2}$ (contradition).

Finally, considering $[a_N,b_N]$ where $0\leq a_N<b_n<1$, we note that as only a single sequence $\alpha$ in $K$ may satisfy $\alpha(N)=t$ for each $t\in [a_N,b_N]$, the projection from $K$ onto the $N^{th}$ coordinate is a homeomorphism onto $[a_N,b_N]$.

For (3), we need only observe that for any sequence $\alpha\in K$, an open neighborhood of $\alpha$ would contain infinte sequences $\beta$ such that $\alpha(N)=\beta(N)$.

\end{proof}

\end{document}

### 2013-07-04 miscellaneous/sorgenfrey/sorgenfrey.tex
Refactored file system

--- 2013-05-17 sorgenfrey/sorgenfrey.tex
@@
 
-This idea can be generalized for the irrationals, but it takes some machinery:
+This idea can actually be generalized for any dense subspace, but it takes some machinery:
 
@@
 \begin{proof}
-It suffices to show for $[0,1)\cap P$. We begin by constructing a collection of functions $S\subseteq \omega^{\omega_1}$ and numbers $c_s$, $d_s$ defined by those functions as follows:
+It suffices to show for $[0,1)\cap P$.
+We begin by constructing a collection of functions $S\subseteq \omega^{\omega_1}$ and numbers $c_s$, $d_s$, $c_{s\concat\<-1\>}$ defined by those functions as follows:
   \begin{itemize}
     \item Let $S_0 = \{\emptyset\}$. Let $d_{\emptyset}=0$ and $c_{\<-1\>}=1$.
-    \item Suppose $S_\alpha$ has been defined, as well as $d_s\leq c_{s\concat\<-1\>}$. For $s\in S$, consider the following:
+    \item Suppose $S_\alpha$ has been defined, as well as $d_s\leq c_{s\concat\<-1\>}$ for each $s\in S_\alpha$. For $s\in S_\alpha$, consider the following:
       \begin{itemize}
@@
         where $[c_{s\concat\<0\>}, d_{s\concat\<0\>})\in \mc{C}$.
-        \item If $d_s < c_{s\concat\<-1\>}$ and $d_s\in P$, let $S_{\alpha+1}$ contain $s\concat\<n\>$ for all $n<\omega$ and define $c_{s\concat\<n\>}$, $d_{s\concat\<n\>}$, $c_{s\concat\<n,-1\>}$ for all $n<\omega$ such that
+        \item If $d_s < c_{s\concat\<-1\>}$ and $d_s\not\in P$, let $S_{\alpha+1}$ contain $s\concat\<n\>$ for all $n<\omega$ and define $c_{s\concat\<n\>}$, $d_{s\concat\<n\>}$, $c_{s\concat\<n,-1\>}$ for all $n<\omega$ such that
           \[
@@
 If $s\in\omega^\alpha$ and $t\in \bigcup_{\beta<\alpha}S_\beta$ for all $t<s$, let $S_\alpha$ contain $s$ and define $d_s = \lim_{t<s}d_t$ and $c_{s\concat\<-1\>} = \lim_{t<s} c_{t\concat\<-1\>}$.
+      \item Let $S=\bigcup_{n<\omega} S_\alpha$.
   \end{itemize}
 
-  By construction, $\mc{C}' = \{[c_s,d_s) : s\in S\}$ is a disjoint subcollection of $\mc{C}$. We claim it also must cover $[0,1)\cap P$.
+  Let $S = \bigcup_{\alpha<\omega_1} S_\alpha$. By construction, $\mc{C}' = \{[c_s,d_s) : s\in S\}$ is a disjoint subcollection of $\mc{C}$. We claim it also must cover $[0,1)\cap P$.
 
@@
 
-  Finally, we notice that by defining $f\in\omega^\omega_1$ such that $f(\alpha)=n_\alpha$, then $d_{f(\alpha)}$ is an increasing sequence defined for all $\alpha<\omega_1$, which is a contradiction.
+  Finally, we notice that by defining $f\in\omega^\omega_1$ such that $f(\alpha)=n_\alpha$, then $d_{f\rest\alpha}$ is an increasing uncountable sequence defined for all $\alpha<\omega_1$, which is a contradiction.
 \end{proof}

### 2013-07-04 phd/menger.tex
Refactored file system

--- 2013-07-04 menger.tex
@@
-\input{./header.tex}
+\input{../header.tex}
 
@@
           \[
-            g(\mc{U},\mc{V},n) = \bigcup_{m\geq n} f(\mc{U},m)\setminus ( f(\mc{U},m-1)\cup f(\mc{V},m))
+            g(\mc{U},\mc{V},m+1) = \left(\bigcup_{n\geq m} f(\mc{U},n+1)\setminus f(\mc{V},n+1))\right)\setminus f(\mc{U},0)
           \]
@@
   \begin{proof}
-    Let $\sigma(\mc{U}_n,\mc{U}_{n+1},n+1)$ cover $f(\mc{U}_{n+1},n+1)$ and $g(\mc{U}_n,\mc{U}_{n+1},n+1)$.
-If $\mc{U}_0,\mc{U}_1,\dots$ is any play by $C$, then for each $x\in X$, we note that $x\in f(\mc{U}_0,N)$ for some $N$.
-So either $x\in \bigcap_{m\leq N} f(\mc{U}_m,N)$ and is covered by the strategy during round $N$, or for some $m< N$, $x \in f(\mc{U}_m,N)\setminus (f(\mc{U}_{m},N-1)\cup f(\mc{U}_{m+1},N))$ and is covered by the strategy during round $m+1$.
+    Let $\sigma(\mc{U}_0,0)$ cover $f(\mc{U}_0,0)$, and let $\sigma(\mc{U}_n,\mc{U}_{n+1},n+1)$ cover $f(\mc{U}_{n+1},n+1)$ and $g(\mc{U}_n,\mc{U}_{n+1},n+1)$.
+If $\mc{U}_0,\mc{U}_1,\dots$ is any play by $C$, then for each $x\in X$, we note that either $x\in f(\mc{U}_0,0)$ and is covered in the initial round, or $x\in f(\mc{U}_0,N+1)$ for some minimal $N$.
+So one of the following must occur:
+      \begin{itemize}
+        \item $x\in \bigcup_{m\leq N} f(\mc{U}_{m},0)$ and is covered by the strategy during some round $m\leq N$.
+        \item $x\in \bigcap_{m\leq N} f(\mc{U}_{m+1},N+1)$ and is covered by the strategy during round $N+1$.
+        \item For some $m \leq N$, 
+          \[x \in \Big( f(\mc{U}_{m},N+1)\setminus f(\mc{U}_{m+1},N+1) \Big)\setminus f(\mc{U}_m,0) \subseteq g(\mc{U}_m,\mc{U}_{m+1},m+1)\]
+         and is covered during round $m+1$.
+      \end{itemize}
   \end{proof}

### 2013-07-11 miscellaneous/inverse-limit-seminar-summer-2013/results.tex
Updated inverse limits

@@
-\input{../header.tex}
+\input{../../header.tex}
 
@@
 
-For (3), we need only observe that for any sequence $\alpha\in K$, an open neighborhood of $\alpha$ would contain infinte sequences $\beta$ such that $\alpha(N)=\beta(N)$.
+For (3), it is easy to show that for any sequence $\alpha\in L \cap \prod_{n=1}^\infty [a_n,b_n]$ where $0\leq a_N < b_N < 1$ for some $N$, an open neighborhood of $\alpha$ would contain infinte sequences $\beta$ with $\alpha(N)=\beta(N)$ and $\beta(p)>b_p$ for some number $p$.
 

### 2013-07-11 phd/menger.tex
menger updates

--- 2013-07-04 menger.tex
@@
         \item $f(\mc{V},n)$ is $\mc{V}$-compact
-        \item $f(\mc{V},n)\subseteq f(\mc{V},n+1)$
+        \item $f(\mc{V},n)\cap f(\mc{V},n+1) = \emptyset$
         \item $\bigcup_{n<\omega}f(\mc{V},n)=X$
@@
           \[
-            g(\mc{U},\mc{V},n) = \bigcup_{m\geq n} f(\mc{U},m)\setminus ( f(\mc{U},m-1)\cup f(\mc{V},m))
+            g(\mc{U},\mc{V},n+1) = \bigcup_{p\geq n} \Big(f(\mc{U},p+1)\setminus f(\mc{V},p+1)\Big)\setminus \bigcup_{m\leq n}f(\mc{U},m+1)
           \]
@@
     Take the injective funcions $f_\alpha$ from Kunen's lemma such that $f_\alpha\rest\beta =^* f_\beta$.
-Let $\gamma(\mc U)$ identify the least ordinal such that $[\gamma(\mc U),\omega_1)\cup\{\infty\}$ is in a refinement of $\mc U$.
-Then $f(\mc U,n)=f^{-1}_{\gamma(\mc U)}([0,n]) \cup [\gamma(\mc U),\omega_1)\cup\{\infty\}$ is easily seen to witness the property.
+Let $\gamma(\mc V)$ identify the least ordinal such that $[\gamma(\mc V),\omega_1)\cup\{\infty\}$ is in a refinement of $\mc U$.
+Then $f$ defined by $f(\mc V,0)=[\gamma(\mc V),\omega_1)\cup\{\infty\}$ and $f(\mc{V},n+1) = f_{\gamma(\mc V)}^{-1}(\{n\})$ is easily seen to witness the property.
   \end{proof}
@@
   \begin{proof}
-    Let $\sigma(\mc{U}_n,\mc{U}_{n+1},n+1)$ cover $f(\mc{U}_{n+1},n+1)$ and $g(\mc{U}_n,\mc{U}_{n+1},n+1)$.
-If $\mc{U}_0,\mc{U}_1,\dots$ is any play by $C$, then for each $x\in X$, we note that $x\in f(\mc{U}_0,N)$ for some $N$.
-So either $x\in \bigcap_{m\leq N} f(\mc{U}_m,N)$ and is covered by the strategy during round $N$, or for some $m< N$, $x \in f(\mc{U}_m,N)\setminus (f(\mc{U}_{m},N-1)\cup f(\mc{U}_{m+1},N))$ and is covered by the strategy during round $m+1$.
+    Let $\sigma(\mc{U}_0,0)$ cover $f(\mc{U}_0,0)$, and let $\sigma(\mc{U}_n,\mc{U}_{n+1},n+1)$ cover $\bigcup_{m\leq n+1}f(\mc{U}_{n+1},m)$ and $g(\mc{U}_n,\mc{U}_{n+1},n+1)$.
+If $\mc{U}_0,\mc{U}_1,\dots$ is any play by $C$, then for each $x\in X$, we note that one of the following must occur:
+      \begin{itemize}
+        \item $x \in f(\mc U_0,0)$ and is covered in the initial round.
+        \item $x \in f(\mc U_0,P+1)$ for some $P\geq 0$ and:
+        \begin{itemize}
+          \item $x\in \bigcup_{m\leq n\leq P} f(\mc{U}_{n+1},m+1)$ and is covered by the strategy by round $P+1$.
+          \item $x\in \bigcap_{n\leq P} f(\mc{U}_{n+1},P+1)$ and is covered by the strategy during round $P+1$.
+          \item For some $n \leq P$, 
+            \[x \in \Big( f(\mc{U}_{n},P+1)\setminus f(\mc{U}_{n+1},P+1) \Big)\setminus \bigcup_{m\leq n} f(\mc{U}_{n+1},m+1) \subseteq g(\mc{U}_m,\mc{U}_{m+1},m+1)\]
+           and is covered during round $n+1$.
+         \end{itemize}
+      \end{itemize}
   \end{proof}

### 2013-07-11 miscellaneous/unorganized/2013-07-11-gameTheoryTalk.tex
Added game theory talk

\input{../../header.tex}

\begin{document}

\centerline{\bf 2013-07-11 talk on Game Theory for Auburn REU program}

Let's start by discussing a few games. For this talk, I'll roughly define a \textbf{game} as a two-player competition, where at the end of the game, exactly one player has won the game.

\begin{game}{(Tic-Tac-Toe-ish)}\label{tictactoe}
Players $X$ and $O$ are playing Tic-Tac-Toe, but in the case of a ``tie'', player $O$ wins.
\end{game}

\begin{question}
Which player has a \textbf{winning strategy} for Game \ref{tictactoe}? (A winning strategy is a strategy where no matter what the opponent does, the strategy guarantees that player will win.)
\end{question}

\begin{game}{(Pick-a-Number)}\label{pickanum}
Players I and II alternate removing numbers from the set $\{1,2,\dots,9\}$. The game ends when once a player has removed three different numbers which sum to $15$ (not every number removed must be used), or when all numbers have been removed. Player I wins if she has removed three different numbers which sum to $15$, and Player II wins otherwise.
\end{game}

\begin{question}
Which player has a winning strategy for Game \ref{pickanum}?
\end{question}

\begin{question}
Can you find a relationship between Game \ref{tictactoe} and Game \ref{pickanum}?
\end{question}

\begin{game}{(Take One-or-Two)}\label{taketwo}
Let the game $G_{\ref{taketwo}}(n)$ be defined as follows: a total of $n$ tokens are played on the table. Players I and II alternate removing one or two tokens from the table each turn. The game ends once all tokens are removed from the table, and the player who removed the final token wins.
\end{game}

\begin{question}
For which values of $n$ does Player I have a winning strategy for $G_{\ref{taketwo}}(n)$? For which values of $n$ does Player II have a winning strategy?
\end{question}

\begin{game}{(Take One-or-Two-or-Three)}\label{takethree}
Same as Game \ref{taketwo}, except players may remove up to three tokens.
\end{game}

\begin{question}
For which values of $n$ does Player I have a winning strategy for $G_{\ref{takethree}}(n)$? For which values of $n$ does Player II have a winning strategy?
\end{question}

\begin{question}
Generalize Games \ref{taketwo} and \ref{takethree} so that players may take up to $m$ tokens, and describe the winning strategies for a player for each value of $n$.
\end{question}

\begin{game}{(Nim)}\label{nim}
Let the game $G_{\ref{nim}}(r,f)$ be defined as follows: $r$ rows of tokens are placed on the table, each with $f(r)$ tokens. Players I and II alternate removing as many tokens as they wish from a particular row each turn. The game ends once all tokens are removed from the table, and the player who removed the final token wins.
\end{game}

\begin{question}
Consider the game of Nim with three rows, containing $x$, $y$, and $x$ objects each. Which player has a winning strategy?
\end{question}

If you're interested in learning more, Nim is a very famous game within Game Theory - in fact, it's provable that any ``finite'' game is equivalent to a game of Nim.

So far, we've taken on faith that for any game, one player or another must have a winning strategy. To see that this is the case (for finite games, anyway), we'll want to model the game mathematically.

\begin{definition}
We model a finite two-player game as follows: a game is defined as a triple $\<V,E,s\>$ where $\<V,E\>$ form a directed graph, and $s\in V$. We call $s$ the starting position for the game. Each $v\in V$ represents a ``game state'' with $s$ representing the starting game state, and each $e\in E$ represents a legal move for a player from one game state to another. A player wins the game if they can force the other player into a game state for which there are no legal moves.
\end{definition}

\begin{definition}
A strategy can be defined as a function $\sigma:V\to V$ where $\sigma(v)$ is always an out-vertex from $v$. Then, a winning strategy for Player $A$ is a strategy where no matter what strategy their opponent Player $B$ uses, the winning strategy results in a win for Player $A$.
\end{definition}

\begin{question}
What criteria must be placed on $\<V,E,s\>$ such that $\<V,E,s\>$ represents a game which must always end in finitely many turns, and exactly one player has a winning strategy for the game?
\end{question}

\begin{question}
Design a game which must terminate in finitely many moves, but cannot be modeled by $\<V,E,s\>$ where $V$ is finite.
\end{question}

Although such games can never be played out in reality, considering games which can possibly extend for infinitely many turns (called infinite games or $\omega$-length games) is often useful in set theory and topology. However, these games have to be modeled differently.

\begin{definition}
We say an $\omega$-length game is a triple $\<M,N,W\>$ such that $W$ contains infinite-length sequences of elements alternating between $M$ and $N$. The sets $M$ and $N$ represent the possible moves of Player I and Player II respectively. The set $W$ represents the ``plays'' of the game where Player I wins.
\end{definition}

\begin{game}\label{eighteen}
An example of an infinte game is as follows: Players I and II alternate choosing integers between $2$ and $9$. If at any point during the game, the numbers chosen so far by both players have a product which is a multiple of 18, then Player I wins. If the game never ends, then Player II wins. This game is modeled by $M=N=\{2,\dots,9\}$ and $W$ is the set of sequences such that there exists an initial sequence of odd length whose product is a multiple of 18, and there doesn't exist a shorter even-length initial sequence whose product is a multiple of 18.
\end{game}

\begin{question}
Prove that Player II has a winning strategy in Game \ref{eighteen}.
\end{question}

\begin{question}
Define an $\omega$-length game $\<M,N,W\>$ to be basically equivalent to a finite game with a digraph model $\<V,E,s\>$.
\end{question}

A simple example of how such games can be used follows:

\begin{game}\label{converge}
Let the game $G_{\ref{converge}}(S)$ for $S\subseteq \mathbb{R}$ be defined as follows: during the initial round, Player I chooses $a_0\in \mathbb{R}$, and Player II responds with $b_0\in \mathbb{R}$ where $a_0<b_0$. During round $n+1$, Player I chooses $a_{n+1}\in \mathbb{R}$ where $a_0<\dots<a_{n+1}<b_n<\dots<b_0$, and Player II responds with $b_{n+1}\in \mathbb{R}$ where $a_0<\dots<a_{n+1}<b_{n+1}<\dots<b_0$. The game cannot end in finitely many turns, but Player I wins the game if $\lim_{n\to\infty} a_n \in S$, and Player II wins otherwise.
\end{game}

Obviously, Player I wins $G_{\ref{converge}}(\mathbb{R})$.

\begin{question}
Prove that Player II wins $G_{\ref{converge}}(S)$ when $S$ is a countable subset of $\mathbb{R}$.
\end{question}

There's a cute consequence to this.

\begin{theorem}
$\mathbb{R}$ is an uncountable set.
\end{theorem}

\end{document}

### 2013-07-19 miscellaneous/inverse-limit-seminar-summer-2013/inverse-limit-results.tex
renamed inverse limit papers, changed header

 \input{../../header.tex}

\begin{document}

% \begin{example}
% Let $L\subseteq \prod_{i=1}^\infty [0,1]$ be the inverse limit space with bonding functions all equal to
% \[
%   f(x) = \left\{
%      \begin{array}{lr}
%        2x & : x \leq 0.5 \\
%        2-2x & : x \geq 0.5
%      \end{array}
%    \right.
% \]
% Then the following hold:
%   \begin{enumerate}
%     \item The subspaces $C_t = \{\alpha\in L : \alpha(1)=t\}$ are each homeomorphic to the Cantor Set.
%     \item All proper subcontinuua are homeomorphic to the unit interval $[0,1]$
%     \item All proper subcontinuua are nowhere dense in the space.
%   \end{enumerate}
% \end{example}

% \begin{proof}
% For (1), consider that for each number $t\in(0,1)$, there are exactly two preimages under $f$ inside $(0,1)$, giving a natural corespondance with the Cantor tree with branches given by points in the Cantor set $2^\omega$. The arguments for $t=0,1$ are similar.

% For (2), we first claim that all basic open sets are of the form $L\cap\prod_{n=1}^\infty B_n$ where $B_n=[0,1]$ for all $n\not=N$. By definition all basic open sets are of the form $L\cap\prod_{n=1}^\infty A_n$ where $A_n=[0,1]$ for all $n\not=N_1,\dots,N_m$. It's easily seen that if $N=N_m$ and $B_N = \bigcap_{i=1}^m (f^{-1})^{(N_m-N_i)}(A_{N_i})$ and $B_n=[0,1]$ otherwise, then $L\cap\prod_{n=1}^\infty A_n = L\cap\prod_{n=1}^\infty B_n$.

% Using this fact, we can argue that each proper subcontinuum $K$ is of the form $L \cap \prod_{n=1}^\infty [a_n,b_n]$ where $0\leq a_N < b_N < 1$ for some $N$.

% First note that every maximal basic open set missed by $K$ must be of the form $L\cap\prod_{n=1}^\infty B_n$ here $B_n=[0,1]$ for all $n\not=N$ and $[0,1] \setminus B_N$ is connected, that is, $B_N=[0,a)\cup(b,1]$. (If not, then the disconnection of $[0,1]\setminus B_N$ yields a disconnection for $K$.) Thus $K = \prod_{n=1}^\infty [0,1]\setminus ([0,a_n)\cup(b_n,1]) = \prod_{n=1}^\infty [a_n,b_n]$.

% We can see that $a_n<b_n$ always; otherwise the continuum is a single point. Suppose $b_n = 1$ for all $n$, then either $a_n=0$ for all $n$ (contradiction since $K$ is a proper subcontinuum), or $a_N>0$, and $b_{N+1}\leq 1-\frac{a_N}{2}$ (contradition).

% Finally, considering $[a_N,b_N]$ where $0\leq a_N<b_n<1$, we note that as only a single sequence $\alpha$ in $K$ may satisfy $\alpha(N)=t$ for each $t\in [a_N,b_N]$, the projection from $K$ onto the $N^{th}$ coordinate is a homeomorphism onto $[a_N,b_N]$.

% For (3), it is easy to show that for any sequence $\alpha\in L \cap \prod_{n=1}^\infty [a_n,b_n]$ where $0\leq a_N < b_N < 1$ for some $N$, an open neighborhood of $\alpha$ would contain infinte sequences $\beta$ with $\alpha(N)=\beta(N)$ and $\beta(p)>b_p$ for some number $p$.

% \end{proof}

Let $X_n$ be a continuum for each $n<\omega$, and $f_n:X_{n+1}\to X_n$ be a continuous function for each $n<\omega$, and $\ds L=\lim_{\leftarrow}(X_n,f_n)$ be the inverse limit space induced by the spaces $X_n$ and bonding maps $f_n$.

\begin{lemma}\label{basis}
  Let 
    \[
      \mc{B}_N = 
      \{L\cap \prod_{n<\omega} B_n : B_n=X_n \text{ for all } n\not= N \text{ and } B_N \text{ is open in } X_N\}
    \]

  Then $\mc{B} = \bigcup_{N<\omega} \mc{B}_N$ is a basis for $L$.
\end{lemma}

\begin{proof}
  Let $\alpha$ be a member of a basic open set induced by the product topology:
    \[
      L \cap \prod_{n<\omega} A_n
    \]
  where $A_n=X_n$ for all $n\not=N_i$ where $i<m$ and $N_i<N_{i+1}$, and $A_{N_i}$ is open in $X_{N_i}$.

  Let $g_{a\to b}: 2^{X_a}\to 2^{X_b}$ for $a\leq b$ be defined by
  \[
    g_{a\to a} = id_{X_a}
  \]
  \[
    g_{a\to (b+1)} =
    \underbrace{ f^{-1}_{b} \circ \dots \circ f^{-1}_{a+1} \circ f^{-1}_a}_{b-a+1 \text{ times}},
  \]

  Let $N=N_{m-1}$ and
    \[
      B_N = \bigcap_{i<m} g_{N_i\to N} (A_{N_i})
    \]
  noting that $B_N$ is open. Note that $\alpha(N_i)\in A_i$ for all $i<m$ implies $\alpha(N)\in B_N$, and thus $\alpha\in L \cap \prod_{n<\omega} B_n$ where $B_n=X_n$ for all $n\not=N$.

  Finally, let $\beta\in L \cap \prod_{n<\omega} B_n$. Since $\beta(N)\in B_N = \bigcap_{i<m} g_{N_i\to N} (A_{N_i})$, we may easily see that $\beta(N_i)\in A_{N_i}$ for each $i<m$ and thus $\beta\in L\cap\prod_{n<\omega} A_n$.
\end{proof}

\begin{lemma}\label{subcontinuua}
  For each subcontinuum $K\subseteq L$, there are minimal subcontinuua $K_n\subseteq X_n$ such that
    \[
      K = L \cap \prod_{n<\omega} K_n
    \]
\end{lemma}

\begin{proof}
  For each $N<\omega$, let $\mc{B}'_N$ contain all basic open sets in $\mc{B}_N$ whose intersection with $K$ is empty. Then let 
    \[
      K_N = X_N \setminus \bigcup_{B\in\mc{B}'_N} \pi_N(B)
    \]

  $K_N$ is a closed subset of a compact space, and is trivially compact. It is also connected: suppose $K_N\subseteq G\cup H$ with $G,H$ disjoint open in $X_N$. Then $K\subseteq \pi_N^{-1}(G)\cup\pi_N^{-1}(H)$ with $\pi_N^{-1}(G)$,$\pi_N^{-1}(H)$ disjoint open, disconnecting $K$ and showing the contradiction.

  Let $\alpha\in K$. Then as $\alpha\not\in \bigcup_{B\in\mc{B}'_N} B$, we know $\alpha(N)\not\in \bigcup_{B\in\mc{B}'_N} \pi_N(B)$ for any $N<\omega$, so $\alpha \in L \cap \prod_{n<\omega} K_n$.

  Let $\alpha\in L\setminus K$. Then $\alpha\in B \in \mc{B}_N$ for some $N$, and thus $\alpha(N)\in \bigcup_{B\in\mc{B}'_N} \pi_N(B)$. This shows $\alpha(N)\not\in K_N$ and thus $\alpha \not\in L \cap \prod_{n<\omega} K_n$.

  This shows $K = L \cap \prod_{n<\omega} K_n$. To see that minimal candidates for $K_n$ exist, observe that that if
    \[
      K = L \cap \prod_{n<\omega} K_{n,\lambda}
    \]
  for all $\lambda$ in some indexing set $I$, then if $K^*_n = \bigcap_{\lambda\in I} K_{n,\lambda}$ we may see
    \[
      K = L \cap \prod_{n<\omega} \left(\bigcap_{\lambda\in I} K_{n,\lambda}\right)
    \]
  and thus $K^*_n$ is the minimal subcontinuum for each $n$. ($K^*_n$ is obviously compact, and observe that if it weren't connected, $K$ wouldn't be connected either.)
\end{proof}

\begin{example}
Let $L$ be the inverse limit space induced by $X_n=[0,1]$ and $f_n=f$ where
\[
  f(x) = \left\{
     \begin{array}{lr}
       2x & : x \leq 0.5 \\
       2-2x & : x \geq 0.5
     \end{array}
   \right.
\]
Then the following hold:
  \begin{enumerate}
    \item The subspaces $C_t = \{\alpha\in L : \alpha(0)=t\}$ are each homeomorphic to the Cantor Set.
    \item All proper subcontinuua $K$ are homeomorphic to the unit interval.
    \item All proper subcontinuua $K$ are nowhere dense in the space.
  \end{enumerate}
\end{example}

\begin{proof}
The reader may easily prove the first item by considering the Cantor tree produced by the branching sequences with a fixed initial coordinate.

By Lemma \ref{subcontinuua}, we may write any proper subcontinuum $K$ as
  \[
    K = L \cap \prod_{n<\omega} [a_n,b_n] 
  \]
for $0\leq a_n \leq b_n \leq 1$ with $[a_n,b_n]$ minimal.

It's easily seen that $a_n < b_n$ must actually be strict (otherwise $K$ is a single point).

We proceed to show that if each $[a_n,b_n]$ is minimal, then there must exist some $N$ such that $0\leq a_N < b_N < 1$.

If $a_n=0$ and $b_n=1$ always, then $K=L$ and is not a proper subcontinuum, so either:
  \begin{itemize}
    \item We assume $0< a_N < b_N \leq 1$ and observe by the minimality of $[a_{N+1},b_{N+1}]$ and $f(1-\frac{a_N}{2})=a_N$ that $[a_{N+1},b_{N+1}]\subseteq[a_{N+1},1-\frac{a_N}{2}]$, which implies $0\leq a_{N+1} < b_{N+1} \leq 1 - \frac{a_N}{2} < 1$.
    \item We get $0\leq a_N < b_N < 1$ for free.
  \end{itemize}

Then one of the following occurs:
  \begin{itemize}
    \item We may find $N$ such that $0<a_N<b_N<1$.
  \end{itemize}
\end{proof}

\end{document}

### 2013-07-19 phd/menger.tex
Added limited info theorem on Rothberger game

@@
 
-      We define a strategy for $S$ in $\rothgame{X}$ as follows: during round $n$, if $S$ has chosen $U_0,\dots,U_{n-1}$ in previous rounds, $S$ chooses an open set covering the point $\sigma(U_0,\dots,U_{n-1})$.
+      We define a strategy for $S$ in $\rothgame{X}$ as follows: during round $n$, if $S$ has chosen $U_0,\dots,U_{n-1}$ in previous rounds, $S$ chooses any open set in $C$'s latest cover containing the point $\sigma(U_0,\dots,U_{n-1})$.
 If $\sigma$ was a winning strategy for $P$, then for any open sets $U_0,U_1,\dots$ containing $\sigma(\cdot),\sigma(U_0),\dots$, the collection $\{U_0,U_1,\dots\}$ is a cover for $X$.
@@
 
-  % \begin{theorem}
-  % For any $T_1$ space $X$, the following are equivalent:
-  %   \begin{itemize}
-  %     \item $S\markwin\rothgame{X}$
-  %     \item $|X|=\omega$
-  %   \end{itemize}
-  % \end{theorem}
+  A similar theorem exists for limited information strategies.
 
-  % \begin{proof}
-  %   If $|X|=\omega$ then the winning Markov strategy is obvious, so let $\sigma(\mc U,n)$ be a Markov strategy.
+  \begin{theorem}
+    \begin{itemize}
+      \item $P\prewin\altrothgame{X}$ if and only if $S\markwin\rothgame{X}$
+      \item $O\markwin\altrothgame{X}$ if and only if $C\prewin\rothgame{X}$.
+    \end{itemize}
+  \end{theorem}
 
-  %   Let $n<\omega$.
+  \begin{proof}
+
+    \begin{itemize}
+      \item
+      Let $\sigma(\mc U_n,n)$ be a Markov strategy for $S$ in $\rothgame{X}$.
+
+      Let $n<\omega$.
 Suppose that for each $x\in X$, there was an open neighborhood $U_x$ of $x$ where for every open cover $\mc U$, $\sigma(\mc U,n)\not=U_x$.
@@
 
-  %   So let $x_n\in X$ be chosen such that for each open neighborhood $U$ of $x_n$, there is an open cover $\mc U$ such that $\sigma(\mc U,n)=U$.
-Then if $x\not=\{x_n : n<\omega\}$, $C$ may counter $\sigma$ as follows: during round $n$, choose $U_n$ which contains $x_n$ but not $x$, and then choose $\mc U_n$ such that $\sigma(\mc U_n,n)=U_n$.
-  % \end{proof}
+      We define a predetermined strategy for $P$ in $\altrothgame{X}$ as follows: during round $n$, $P$ chooses a point $x_n$ for which every open neighborhood is of the form $U_n = \sigma(\mc U,n)$ for some open cover $\mc{U}$.
+
+      If $\sigma$ was a winning strategy for $S$ in $\rothgame{X}$, then the open sets chosen by $O$ in response to $P$'s strategy for $\altrothgame{X}$ are of the form $\{\sigma(\mc U_0,0),\sigma(\mc U_1,1),\dots\}$ and are an open cover of $X$.
+
+      \item
+      Let $\sigma(n)$ be a predetermined strategy for $P$ in $\altrothgame{X}$.
+
+      We define a Markov strategy for $S$ in $\rothgame{X}$ as follows: during round $n$, $S$ chooses any open set in $C$'s cover containing the point $\sigma(n)$.
+If $\sigma$ was a winning strategy for $P$, then for any open sets $U_0,U_1,\dots$ containing $\sigma(0),\sigma(1),\dots$, the collection $\{U_0,U_1,\dots\}$ is a cover for $X$.
+
+      \item
+      Let $\sigma(n)$ be a predetermined strategy for $C$ in $\rothgame{X}$.
+
+      We define a Markov strategy for $O$ in $\altrothgame{X}$ as follows: during round $n$, $O$ chooses an open set from the cover $\sigma(n)$ containing the point chosen by $P$ that round.
+If $\sigma$ was a winning strategy for $C$, then for any open sets $U_0,U_1,\dots$ from the covers $\sigma(0),\sigma(1),\dots$, the collection $\{U_0,U_1,\dots\}$ is not a cover for $X$.
+
+      \item
+      Let $\sigma(x_n,n)$ be a Markov strategy for $O$ in $\altrothgame{X}$.
+
+      We define a predetermined strategy for $C$ in $\rothgame{X}$ as follows: during round $n$, $C$ chooses $\mc{U}_n = \{\sigma(x,n) : x\in X\}$.
+If $\sigma$ was a winning strategy for $O$, we observe any play $\{\sigma(x_0,0),\sigma(x_1,1),\dots\}$ by $S$ is not a cover for $X$.
+
+    \end{itemize}
+
+  \end{proof}
 
@@
       \item $S\markwin\rothgame{X}$
-      \item $|X|=\omega$
+      \item $|X|\leq\omega$
     \end{itemize}
@@
         \item $S\kmarkwin{k}\rothgame{X}$
-        \item $|X|=\omega$
+        \item $|X|\leq\omega$
       \end{enumerate}
@@
   \begin{proof}
-    $(c)\Rightarrow(b)\Rightarrow(a)$ are all trivial. Galvin has shown $(a)\Rightarrow(c)$ in \textit{Indeterminacy}, but a direct proof follows. Let $\sigma$ be a strategy for $S$ in $\rothgame{X}$.
+    $(c)\Rightarrow(b)\Rightarrow(a)$ are all trivial.
+Galvin has shown $(a) \Leftrightarrow P\win\altrothgame{X} \Rightarrow (c)$ in \textit{Indeterminacy}, but a direct proof of $(a)\Rightarrow(c)$ follows.
+Let $\sigma$ be a strategy for $S$ in $\rothgame{X}$.
 

### 2013-07-23 miscellaneous/inverse-limit-seminar-summer-2013/inverse-limit-results.tex
Finished wedge inverse limit example

@@
     \[
-      K = L \cap \prod_{n<\omega} \left(\bigcap_{\lambda\in I} K_{n,\lambda}\right)
+      K = L \cap \prod_{n<\omega} K^*_n
     \]
@@
     \item We assume $0< a_N < b_N \leq 1$ and observe by the minimality of $[a_{N+1},b_{N+1}]$ and $f(1-\frac{a_N}{2})=a_N$ that $[a_{N+1},b_{N+1}]\subseteq[a_{N+1},1-\frac{a_N}{2}]$, which implies $0\leq a_{N+1} < b_{N+1} \leq 1 - \frac{a_N}{2} < 1$.
-    \item We get $0\leq a_N < b_N < 1$ for free.
+    \item We have $0\leq a_N < b_N < 1$ for free.
+  \end{itemize}
+Then one of the following occurs:
+  \begin{itemize}
+    \item Suppose $b_{N+1}=1$; then $a_{N+2}>0$.
+In this case, the reader may check that each sequence in $K$ has a unique value in the $(N+2)^{th}$ coordinate - if not, then the sequences must ``branch'' in some $M>N+2$ coordinate, but either $b_M<\frac{1}{2}$ or $a_M>\frac{1}{2}$ prevents such branching.
+    \item It may be that $0=a_n$ for all $n<\omega$.
+Then the reader may again check that each sequence in $K$ has a unique value in the $(N+2)^{th}$ coordinate where $0=a_{N+2}<b_{N+2}<1$, as $M>N+2 \Rightarrow b_M<\frac{1}{2}$ prevents branching.
   \end{itemize}
 
-Then one of the following occurs:
-  \begin{itemize}
-    \item We may find $N$ such that $0<a_N<b_N<1$.
-  \end{itemize}
+It may be easily verified then that the projection $\pi_{N+2}$ is a homeomorphism from $K$ to $[a_{N+2},b_{N+2}]$.
 \end{proof}

### 2013-08-22 phd/menger.tex
Added initial filling game results, factored out todos to TeX

@@
 \begin{document}
+
+  \centerline{Menger}
 
@@
 
+  \centerline{Filling Games}
+
+  \begin{definition}
+    The \textbf{filling game} $\fillgame{X}$ proceeds as follows: player $C$ chooses $C_0\in[X]^{\leq\omega}$ in the initial round, followed by $F$ choosing $F_0\in[C_0]^{<\omega}$.
+In round $n+1$, player $C$ chooses $C_{n+1}$ where $C_n\subseteq C_{n+1}\in[X]^{\leq\omega}$, and player $F$ replies with $F_{n+1}\in[C_{n+1}]^{<\omega}$.
+Player $F$ wins the game if $\bigcup_{n<\omega} F_n = \bigcup_{n<\omega} C_n$.
+
+    The \textbf{strict filling game} $\sfillgame{X}$ proceeds analogously, with the added requirement that $C_n\subsetneq C_{n+1}$.
+  \end{definition}
+
+  \begin{theorem}
+    $F\ktactwin{2}\sfillgame{\kappa} \Rightarrow F\kmarkwin{2}\fillgame{\kappa}$
+  \end{theorem}
+
+  \begin{proof}
+    Let $\sigma$ be a winning $2$-tactical strategy for $F$ in $\sfillgame{\kappa}$.
+
+    For $C\in [\omega_1]^{\leq\omega}$ and $n<\omega$, let $C+n$ denote the superset of $C$ which also contains the $n$ least elements of $\omega_1\setminus C$, and let $C+\omega = \bigcup_{n<\omega} C + n$.
+
+    We define a $2$-Markov strategy $\tau$ for $F$ in $\fillgame{\kappa}$ as follows:
+
+      \[
+        \tau(C_0,0) = \sigma(C_0)
+      \]
+      \[
+        \tau(C_n,C_{n+1},n+1) = \left\{
+      \begin{array}{ll}
+        \sigma(C_n)\cup \sigma(C_n,C_{n+1}) & C_n\subsetneq C_{n+1} \\
+        C_n \cap \left(\sigma(C_n) \cup \bigcup_{m<n} \sigma(C_n+m,C_n+m+1) \right) & C_n=C_{n+1}
+      \end{array}
+      \right.
+      \]
+
+    Let $C_0 \subseteq C_1 \subseteq \dots$ be an attack by $C$ against $\tau$. There are two possible cases:
+
+      \begin{itemize}
+        \item
+          Assume $C_n=C_N$ for all $n\geq N$.
+
+          The collection produced by $\sigma$ versus the attack
+            \[
+              C_N+0 \subsetneq C_N+1 \subsetneq \dots
+            \] 
+          is 
+            \[
+              \{\sigma(C_N)\}\cup\{\sigma(C_N+m,C_N+m+1) : m<\omega\}
+            \]
+          and must cover $C_N$ as $\sigma$ is a winning strategy.
+
+          Let $\alpha \in C_N$.
+Then if $\alpha \in \sigma(C_N)$, we observe that $\alpha$ must be covered by $\tau$ in round $N+1$.
+Otherwise $\alpha \in \sigma(C_N+m,C_N+m+1)$ for some $m$, and $\alpha$ must be covered by $\tau$ in round $N+m+1$.
+
+        \item
+          Assume we may find $f(0)<f(1)<\dots$ such that $C_{f(m)}\subsetneq C_{f(m)+1}$ and $C_{f(m)+1}=C_{f(m+1)}$.
+
+          Then the collection produced by $\sigma$ versus the attack 
+            \[
+              C_{f(0)}\subsetneq C_{f(1)} \subsetneq C_{f(2)} \dots
+            \]
+          is 
+            \[
+              \{\sigma(C_{f(0)})\}\cup\{\sigma(C_{f(m)},C_{f(m+1)}):m<\omega\}
+            \]
+          and must cover $C_N$ as $\sigma$ is a winning strategy.
+
+          Let $\alpha \in C_N$.
+Then if $\alpha \in \sigma(C_{f(0)})$, we observe that $\alpha$ must be covered by $\tau$ in round $f(0)+1$.
+Otherwise $\alpha \in \sigma(C_{f(m)},C_{f(m+1)})=\sigma(C_{f(m)},C_{f(m)+1})$ for some $m$, and $\alpha$ must be covered by $\tau$ in round $f(m)+1$
+      \end{itemize}
+
+      Thus $\tau$ is a winning strategy.
+  \end{proof}
+
+\newpage
+
+  \centerline{Rothberger}
+
   \begin{definition}

### 2013-08-22 todo.tex
Added initial filling game results, factored out todos to TeX

\input{header.tex}

\begin{document}
\centerline{\bf Research TODOs}

  \begin{itemize}
    \item Menger-related properties and games results
      \begin{itemize}
        \item Is there a slick characterization of $F\kmarkwin{2}\mengame{X}$ for regular/general spaces?
        \item Is $F\uparrow_{?}\mengame{X}$ or $F\uparrow_{?}\rothgame{X}$ a hereditary property under closed subsets for any type of limited information? (The Menger property is. Is Rothberger?)
      \end{itemize}
    \item Search for a class of spaces where $K\ktactwin{2}\lfkpgame{X}$ characterizes metacompact (aka implies $K\tactwin\lfkpgame{X}$)
      \begin{itemize}
        \item Investigate the ladder space suggested by G.
        \item Try zero-dimensional.
      \end{itemize}
  \end{itemize}
\end{document}

### 2013-09-22 miscellaneous/unorganized/algebraic-topology-week3.tex
added alg top result, working on meager-nwd game

\input{../../header.tex}

\begin{document}

  \begin{question}
    Week 3 (1b)

    Show that there is no no-trivial chain $\gamma\in C_2(\mc{S}(E),\mathbb{Z})$ whose boundary is in $A$.
  \end{question}

  \centerline{\includegraphics[width=0.7\linewidth]{alg-top-2013-09-18.pdf}}

  \begin{proof}
    Assume $\gamma$ has boundary completely in $A$. Then $\partial(\gamma)=\sum_{i<4} k_i[v_i,v_{i+1(\text{mod}4)}]$.

    We claim $\gamma(\sigma_i) = 0$ for $4\leq i<8$. This can be verified by observing that giving the faces $\sigma_4,\dots,\sigma_7$ nonzero value in $\gamma$ results in non-zero boundary values for the edges on the inner square.

    Next, we observe that since the values for the $45^\circ$ degree diagonals $[v_i,v_{i+4}]$ ($i<4$) in the boundary of $\gamma$ are each $0$, that the two faces at each edge, $\sigma_0$:$\sigma_7$, $\sigma_1$:$\sigma_3$, etc., must be inversely included in $\gamma$. Thus $\gamma(\sigma_0)=-\gamma(\sigma_7)=0$, $\gamma(\sigma_1)=-\gamma(\sigma_4)=0$, etc.

    Therefore $\gamma(\sigma_i)=0$ for $0\leq i<8$.
  \end{proof}

\end{document}

### 2013-09-22 phd/menger.tex
added alg top result, working on meager-nwd game

--- 2013-07-19 phd/menger.tex
@@
 
+  \centerline{Filling Games}
+
+  \begin{definition}
+    The \textbf{filling game} $\fillgame{J}$ on an ideal $J$ proceeds as follows: player $M$ chooses $M_0 \in \<J\>$, the $\sigma$-completion of $J$, in the initial round, followed by $N$ choosing $N_0\in J$.
+In round $n+1$, player $M$ chooses $M_{n+1}$ where $M_n\subseteq M_{n+1}\in\<J\>$, and player $N$ replies with $N_{n+1}\in J$.
+Player $N$ wins the game if $\bigcup_{n<\omega} N_n \supseteq \bigcup_{n<\omega} M_n$.
+(The sets in $J$ and $\<J\>$ are thought of as nowhere-dense and meager sets, respectively.)
+
+    The \textbf{strict filling game} $\sfillgame{J}$ proceeds analogously, with the added requirement that $M_n\subsetneq M_{n+1}$.
+  \end{definition}
+
+  \begin{theorem}
+    $F\ktactwin{2}\sfillgame{J} \Rightarrow F\kmarkwin{2}\fillgame{J}$
+  \end{theorem}
+
+  \begin{proof}
+    Enumerate the sets in $J$ as $A_\alpha$ for $\alpha<|J|$. For $M\in \<J\>$ and $n<\omega$, let $M+0=M$ and $M+n+1$ be the union of $M+n$ and the least $A_\alpha$ not contained in $M+n$.
+
+    Let $\sigma$ be a winning $2$-tactical strategy for $N$ in $\sfillgame{\kappa}$, and assume $\sigma(M)\cup\sigma(M')\subseteq\sigma(M,M')$.
+
+    We define a $2$-Markov strategy $\tau$ for $F$ in $\fillgame{\kappa}$ as follows:
+
+      \[
+        \tau(M_0,0) = \sigma(M_0)
+      \]
+      \[
+        \tau(M_{n},M_{n+1},n+1) = \left\{
+          \begin{array}{ll}
+            \sigma(M_{n},M_{n+1}) & \text{if } M_n\subsetneq M_{n+1} \\
+            \bigcup_{m\leq n}\sigma(M_n+m,M_{n+1}+m+1) & \text{otherwise}
+          \end{array}
+        \right.
+      \]
+
+    Let $M_0 \subseteq M_1 \subseteq \dots$ be an attack by $C$ against $\tau$. There are two possible cases:
+
+      \begin{itemize}
+        \item
+          Assume $M_n=M_N$ for all $n\geq N$.
+
+          The collection produced by $\sigma$ versus the attack
+            \[
+              M_N+0 \subsetneq M_N+1 \subsetneq \dots
+            \] 
+          must cover $M_N$ as $\sigma$ is a winning strategy.
+
+          Let $x \in M_N$. If $x\in\sigma(M_N+0)$, then $x$ will be covered in round $N+1$ by 
+            \[
+              \tau(M_N,M_N,N+1)
+              \supseteq \sigma(M_N+0,M_N+1)
+              \supseteq \sigma(M_N+0)
+            \]
+
+          Otherwise, $x\in\sigma(M_N+n,M_N+n+1)$, and $x$ will be covered in round $N+n+1$ by 
+            \[
+              \tau(M_N,M_N,N+n+1)
+              \supseteq \sigma(M_N+n,M_N+n+1)
+            \]
+
+        \item
+          Otherwise we may find $0<f(0)<f(1)<\dots$ such that $M_{f(n)}\subsetneq M_{f(n)+1}=M_{f(n+1)}$.
+
+          Then the collection produced by $\sigma$ versus the attack 
+            \[
+              M_{f(0)}\subsetneq M_{f(1)} \subsetneq M_{f(2)} \dots
+            \]
+          must cover $\bigcup_{n<\omega}M_n$ as $\sigma$ is a winning strategy.
+
+          Let $x \in \bigcup_{n<\omega}M_n$. If $x\in\sigma(M_{f(0)})$, then $x$ will be covered by $\tau$ in round $f(0)+1$ by
+            \[
+              \tau(M_{f(0)},M_{f(0)+1},f(0)+1)
+              = \sigma(M_{f(0)},M_{f(0)+1})
+              \supseteq \sigma(M_{f(0)})
+            \]
+
+          Otherwise, $x\in\sigma(M_{f(n)},M_{f(n+1)})$, and $x$ will be covered by $\tau$ in round $f(n)+1$ by
+            \[
+              \tau(M_{f(n)},M_{f(n)+1},f(n)+1)
+              = \sigma(M_{f(n)},M_{f(n)+1})
+              = \sigma(M_{f(n)},M_{f(n+1)})
+            \]
+      \end{itemize}
+
+      Thus $\tau$ is a winning strategy.
+  \end{proof}
+
+\newpage
+
+  \centerline{Rothberger}
+
   \begin{definition}

### 2013-09-22 phd/menger.tex
found counter example for strict and nonstrict filling games

@@
 
-    The \textbf{strict filling game} $\sfillgame{J}$ proceeds analogously, with the added requirement that $M_n\subsetneq M_{n+1}$.
+    The \textbf{strict filling game} $\sfillgame{J}$ proceeds analogously, with the added requirement that $M_n\subsetneq M_{n+1}$. This game has been studied by Scheepers.
   \end{definition}
@@
   \begin{theorem}
-    $F\ktactwin{2}\sfillgame{J} \Rightarrow F\kmarkwin{2}\fillgame{J}$
+    $N\ktactwin{2}\sfillgame{J} \Rightarrow N\kmarkwin{2}\fillgame{J}$
   \end{theorem}
@@
       Thus $\tau$ is a winning strategy.
+  \end{proof}
+
+  \begin{example}
+    There is a free ideal $J$ such that $N\not\ktactwin{2}\sfillgame{J}$ but $N\kmarkwin{2}\fillgame{J}$.
+  \end{example}
+
+  \begin{proof}
+    Result based on ``Meager nowhere dense games'' Prop 9 by Scheepers. Assume $\mathbb{R}$ has the usual Euclidean topology.
+
+    Choose $A\subseteq\mathbb{R}$ such that $|A|=\omega$ and $A$ is meager but not nowhere dense.
+Then choose $V\subseteq\mathbb{R}$ such that $|V|=2^\omega$, $V$ is meager, and $V$ is disjoint from $A$.
+Assume $A=\{a_n:n<\omega\}$.
+
+    Certainly, if $J$ is the collection of nowhere dense subsets of $A\cup V$, then $F\kmarkwin{2}\fillgame{J}$. In fact, since $A\cup V$ is meager, $F\prewin\fillgame{J}$.
+
+    However, we may show that $F\not\ktactwin{2}\sfillgame{J}$ | let $\sigma$ be a $2$-tactical strategy such that $\sigma(M)\subseteq\sigma(M,M')$.
+
+    We may define $K_n$ to be the collection of pairs of comparable sets $\{B,C\}$ such that $B\subsetneq C$ and $n$ is the least integer where $a_n \in A \setminus \sigma(A\cup B,A\cup C)$.
+
+    By Cor 28 of Scheeper's ``A partition relation for partially ordered sets'', for every partition $\{K_n:n<\omega\}$ of the comparable pairs in $[\pow{V}]^2$ there is some $n'<\omega$ and branch $C_0\subsetneq C_1\subsetneq \dots\subsetneq V$ where $\{C_m,C_{m+1}\}\in K_{n'}$ for all $m<\omega$.
+
+    Then $\sigma$ may be countered by the attack $A\cup C_0, A\cup C_1, \dots$, since $a_{n'} \in A \setminus \sigma(A\cup C_m,A\cup C_{m+1})$ for all $m<\omega$ and thus is never covered.
   \end{proof}

### 2013-09-24 phd/menger.tex
Updated filling results and todos

@@
 
-    However, we may show that $F\not\ktactwin{2}\sfillgame{J}$ | let $\sigma$ be a $2$-tactical strategy such that $\sigma(M)\subseteq\sigma(M,M')$.
+    By Prop 9 in Scheeper's paper, $F\not\ktactwin{2}\sfillgame{J}$ immediately. A proof follows: let $\sigma$ be a $2$-tactical strategy such that $\sigma(M)\subseteq\sigma(M,M')$.
 
@@
     Then $\sigma$ may be countered by the attack $A\cup C_0, A\cup C_1, \dots$, since $a_{n'} \in A \setminus \sigma(A\cup C_m,A\cup C_{m+1})$ for all $m<\omega$ and thus is never covered.
+  \end{proof}
+
+  \begin{theorem}
+    $F\kmarkwin{k}\kfillgame{\kappa} \Rightarrow F\kmarkwin{k}\mengame{\oneptlind{\kappa}}$
+  \end{theorem}
+
+  \begin{proof}
+    Assume $\sigma$ is a winning $k$-Mark\"ov strategy for $F\kmarkwin{k}\kfillgame{\kappa}$, where 
+      \[
+        \sigma(C_0,0)\subseteq
+        \dots \subseteq
+        \sigma(\mc C_0,\dots,\mc C_{k-2},k-2) \subseteq
+        \sigma(C_0,C_1,\dots,C_{k-1},k-1)
+      \]
+    for all $n<\omega$.
+
+    For each open cover $\mc U$ of $\oneptlind{\kappa}$, let $C(\mc U)$ be a countable set such that $\oneptlind{\kappa}\setminus C(\mc U)$ is in a refinement of $\mc U$.
+We define $\tau^*$ as follows:
+
+      \[
+        \tau^*(\mc U_0,0) =
+        \oneptlind{\kappa}\setminus C(\mc U_0)
+      \]
+      \[
+        \tau^*(\mc U_0,\mc U_1,1) =
+        \dots =
+        \tau^*(\mc U_0,\dots,\mc U_{k-2},k-2) =
+        \emptyset
+      \]
+      \[
+        \tau^*(\mc U_0,\dots,\mc U_{k-1},n+k-1) = 
+        \sigma(C(\mc U_0),\dots,C(\mc U_{k-1}),n+k-1)
+      \]
+
+    If $\tau$ yields legal open sets covering $\tau^*$, then we claim $\tau$ is a winning strategy.
+Note that for any attack $\mc U_0,\mc U_1,\dots$ that $\tau$ covers $\oneptlind{\kappa}\setminus C(\mc U_0)$ in the initial round, and also covers
+      \[
+        \bigcup_{n<\omega}\sigma(C(\mc U_n),\dots,C(\mc U_{n+k-1}),n+k-1) \supseteq
+        \bigcup_{n<\omega} C(\mc U_n) \supseteq
+        C(\mc U_0)
+      \]
+    by the game's end.
   \end{proof}

### 2013-10-15 phd/menger.tex
Added forcing argument

--- 2013-09-22 phd/menger.tex
@@
 
-    Let $\mathfrak{C}$ collect all the open covers of $X$. We say $X$ is \scish if there exists a function $f:\mathfrak{C}\times\omega\to\mc{P}(X)$ such that:
+    Let $\mathfrak{C}$ collect all the open covers of $X$. We say $X$ is \scish~if there exists a function $f:\mathfrak{C}\times\omega\to\mc{P}(X)$ such that:
       \begin{itemize}
@@
 
-  Obviously $\sigma$-compact implies \scish implies Lindel\"of. We shall see that the non-$\sigma$-compact space $\omega_1^\dagger$ is \scish.
+  Obviously $\sigma$-(relatively compact) implies \scish~implies Lindel\"of. We shall see that the non-$\sigma$-(relatively compact) space $\omega_1^\dagger$ is \scish.
 
-   \begin{lemma}
-    There exist injective functions $f_\alpha:\alpha\to\omega$ such that if $\alpha<\beta$, then \[f_\beta\rest\alpha =^* f_\alpha\] that is, $f_\beta\rest\alpha$ and $f_\alpha$ agree on all but finitely many ordinals.
-(In addition, the range of each $f_\alpha$ is co-infinite.)
+  \begin{definition}
+    For two functions $f,g$ we say $f$ is \textbf{$\mu$-almost compatible} with $g$ ($f\al\perp_\mu g$) if $|\{x\in\dom(f)\cap\dom(g):f(x)\not=g(x)\}|<\mu$.
+If $\mu=\omega$ then we say $f,g$ are \textbf{almost compatible} ($f\al\perp g$).
+  \end{definition}
+
+  \begin{lemma}\label{kunlem}
+    For each $\alpha<\omega_1$, there exist injective functions $f_\alpha:\alpha\to\omega$ such that if $\alpha<\beta$, then \[f_\alpha \al\perp f_\beta\] that is, $f_\alpha$ and $f_\beta\rest\alpha$ agree on all but finitely many ordinals.
+In addition, the range of each $f_\alpha$ is co-infinite.
   \end{lemma}
@@
     Finally, suppose $\gamma$ is the limit of $\alpha_0,\alpha_1,\dots$, and $f_\alpha$ is defined for $\alpha<\gamma$.
-Let $g_0=f_{\alpha_0}$, and define $g_n : \alpha_n \to \omega$ to be injective, $g_n=^* f_{\alpha_n}$, and $g_{n+1} \rest \alpha_n = g_n$.
-$g = \bigcup_{n<\omega} g_n$ is an injective function from $\gamma \to \omega$ and $g =^* f_\alpha$ for $\alpha <\gamma$, but the range need not be coinfinte.
+Let $g_0=f_{\alpha_0}$, and assuming $g_n\al\perp f_{\alpha_n}$ with coinfinite range, define $g_{n+1}:\alpha_{n+1}\to\omega$ so that $g_{n+1}\rest\alpha_n=g_n$ and $g_{n+1}\rest(\alpha_{n+1}\setminus\alpha_n)\al\perp f_{\alpha_{n+1}}$ with coinfinite range.
+Then $g=\bigcup_{n<\omega} g_n$ is an injective function from $\gamma \to \omega$ and $g \al\perp f_\alpha$ for $\alpha <\gamma$, but the range need not be coinfinite.
 So let
@@
     \]
-    which frees up $\{g(\alpha_{2n+1}):n<\omega\}$ from the range of $f_\gamma$, but still agrees with all but finitely many points compared to previous $f$'s.
+    which frees up $\{g(\alpha_{2n+1}):n<\omega\}$ from the range of $f_\gamma$, and allows $f_\gamma\al\perp f_\alpha$.
   \end{proof}
@@
   \begin{proof}
-    Take the injective funcions $f_\alpha$ from Kunen's lemma such that $f_\alpha\rest\beta =^* f_\beta$.
-Let $\gamma(\mc V)$ identify the least ordinal such that $[\gamma(\mc V),\omega_1)\cup\{\infty\}$ is in a refinement of $\mc U$.
+    Take the injective funcions $f_\alpha$ from Kunen's lemma such that $f_\alpha \al\perp f_\beta$.
+For each open cover $\mc V$ of $\oneptlind{\omega_1}$ let $\gamma(\mc V)$ identify the least ordinal such that $[\gamma(\mc V),\omega_1)\cup\{\infty\}$ is in a refinement of $\mc V$.
 Then $f$ defined by $f(\mc V,0)=[\gamma(\mc V),\omega_1)\cup\{\infty\}$ and $f(\mc{V},n+1) = f_{\gamma(\mc V)}^{-1}(\{n\})$ is easily seen to witness the property.
@@
     $F\kmarkwin{2}\mengame{\oneptlind{\omega_1}}$
+  \end{corollary}
+
+  \begin{definition} 
+    The statement $S(\kappa,\mu,\lambda)$ due to Scheepers is shorthand for the following: there exist injective functions $f_A:A\to\lambda$ for each $A\in[\kappa]^\mu$ such that $f_A\al\perp_\mu f_B$ for all $A,B\in[\kappa]^\mu$.
+  \end{definition}
+
+  \begin{theorem}
+    $S(\kappa,\omega,\omega)$ implies $\oneptlind{\kappa}$ is \scish.
+  \end{theorem}
+
+  \begin{proof}
+    Take the injective funcions $f_A:A\to\omega$ witnessing $S(\kappa,\omega,\omega)$.
+For each cover $\mc V$ of $\oneptlind{\kappa}$ let $A(\mc V)$ define a set such that $\oneptlind{\kappa}\setminus A(\mc V)$ is in a refinement of $\mc V$.
+Then define $f$ by $f(\mc V,0)=\oneptlind{\kappa}\setminus A(\mc V)$ and $f(\mc{V},n+1) = f_{A(\mc V)}^{-1}(\{n\})$.
+
+    \begin{itemize}
+      \item $f(\mc{V},n)$ is $\mc{V}$-compact by definition.
+      \item $f(\mc{V},n)\cap f(\mc{V},n+1) = \emptyset$ by definition.
+      \item $\bigcup_{n<\omega}f(\mc{V},n)=X$ by definition.
+      \item Note that as $f(\mc{U},p+1)=f^{-1}_{A(\mc U)}(\{p\})$, $f(\mc{V},p+1)=f^{-1}_{A(\mc V)}(\{p\})$, and $f_{A(\mc U)}\al\perp f_{A(\mc V)}$, the set
+          \[
+            \left(\bigcup_{p<\omega} \Big(f(\mc{U},p+1)\setminus f(\mc{V},p+1)\Big) 
+            \setminus A(\mc{U})\right)
+            \setminus A(\mc{V})
+          \] 
+        is finite.
+
+        Thus the set
+          \[
+            g(\mc{U},\mc{V},n+1) = \bigcup_{p\geq n} \Big(f(\mc{U},p+1)\setminus f(\mc{V},p+1)\Big)\setminus \bigcup_{m\leq n}f(\mc{U},m+1)
+          \]
+        is $\mc{V}$-compact.
+    \end{itemize}
+  \end{proof}
+
+  \begin{corollary}
+    $S(\kappa,\omega,\omega)$ implies $F\kmarkwin{2}\mengame{\oneptlind{\kappa}}$.
+  \end{corollary}
+
+  \begin{definition}
+    A finite partial function $p$ from $A$ to $B$ has a domain which is a finite subset of $A$ and a range which is a finite subset of $B$.
+Let the set of all finite partial functions from $A$ to $B$ be denoted by $Fn(A,B)$.
+
+    Then let $Fn^2(\mc A,B)\subset Fn(\mc A,Fn(\bigcup \mc A,B))$ such that for each $p\in Fn^2(\mc A,B)$, $p(A)=p_A\in Fn(A,B)$.
+  \end{definition}
+
+  \begin{definition}
+    Let $\pok\subset Fn^2([\kappa]^\omega,\omega)$ be such that each $p_A$ is injective, and give it the partial order $\leq$ defined by $q\leq p$ if and only if:
+          \begin{itemize}
+            \item $\dom(q)\supseteq\dom(p)$
+            \item For each $A\in\dom(p)$, $q_A\supseteq p_A$
+            \item For each $A,B\in\dom(p)$, if $p_A$ and $p_B$ are not defined for some $\alpha\in A\cap B$, but $q_A$ is, then $q_B$ is also defined for $\alpha$ and $q_A(\alpha)=q_B(x)$. That is, 
+              \[
+                \alpha\in\dom(q_A)\setminus(\dom(p_A)\cup\dom(p_B))
+                \Rightarrow
+                \alpha\in\dom(q_B) \text{ and } q_A(x)=q_B(x)
+              \]
+          \end{itemize}
+  \end{definition}
+
+  \begin{lemma}
+    $\pok$ has property $K$ (and thus is c.c.c.). That is, let $P\subseteq\pok$ be uncountable: there is an uncountable $Q\subseteq P$ such that points in $Q$ are pairwise compatible.
+  \end{lemma}
+
+  \begin{proof}
+    If $|\{\dom(p):p\in P\}|>\omega$, we will use the $\Delta$-system lemma to find an uncountable $P'\subseteq P$ such that for $p,q\in P'$, $\dom(p)\cap\dom(q)=\mc R$.
+Otherwise, we may fix an uncountable $P'\subseteq P$ such that for $p,q\in P'$, $\dom(p)=\dom(q)=\mc R$.
+
+    Similarly, for each $A\in\mc{R}$ we may find that $|\{\dom(p_A):p\in P'\}|>\omega$, and we can use the $\Delta$-system lemma to find an uncountable $P''\subseteq P'$ where $\dom(p_A)\cap\dom(q_A)=A'$ for all $p,q\in P''$, or otherwise we may find $P''\subseteq P'$ where $\dom(p_A)=\dom(q_A)=A'$ for all $p,q\in P''$.
+
+    Finally, for each $A\in\mc R$ and $\alpha\in A'$, we may find $n_{A,\alpha}$ such that there are uncountable $p\in P''$ with $p_A(\alpha)=n_{A,\alpha}$, and thus we may choose $Q\subseteq P''$ to be an uncountable collection such that for $p,q\in Q$, $p_A=q_A$ for $A\in\mc R$.
+
+    Then it is easily verified that $p\cup q\in\pok$ and $p\cup q\leq p,q$ for all $p,q\in Q$.
+  \end{proof}
+
+  \begin{proposition}
+    For $A\in[\kappa]^\omega$ and $\alpha\in A$, the sets 
+      \[
+        D_A = \{p\in\pok: A\in\dom(p)\}
+      \]
+      \[
+        D_{A,\alpha} = \{p\in\pok: A\in\dom(p), \alpha\in\dom(p_A)\}
+      \]
+    are dense in $\pok$.
+  \end{proposition}
+
+  \begin{proof}
+    Let $A\in[\kappa]^\omega$ and $p\in\pok$. Either $p'=p\in D_A$, or $p'=p\cup\{\<A,\emptyset\>\}\in D_A$ with $p'\leq p$.
+
+    Let $\alpha\in A$.
+Either $p''=p'\in D_{A,\alpha}$, or we may find $n<\omega$ not in the range of $p'_A$, and then $p''=p'\setminus\{\<A,p'_A\>\}\cup\{\<A,p'_A\cup\{\<\alpha,n\>\}\>\} \in D_{A,\alpha}$ with $p''\leq p'\leq p$.
+  \end{proof}
+
+  \begin{theorem}
+    $S(\kappa,\omega,\omega)$ is consistent with ZFC for any cardinal $\kappa$.
+  \end{theorem}
+
+  \begin{proof}
+    If $\kappa\leq\omega_1$, then $S(\kappa,\omega,\omega)$ is a theorem of ZFC - use Lemma \ref{kunlem}.
+
+    Assume $\kappa>\omega_1$; we adapt a forcing argument due to Scheepers.
+Let $M$ be a countable transitive submodel of ZFC.
+Consider the c.c.c.
+poset $\pok$ realized in the model $M$.
+Let $G$ be a $\pok$-generic filter over $M$.
+
+    We now work in the smallest model $M[G]$ extending $M$ and containing $G$. Observe that by (Kunen), $M[G]$ preserves cofinalities and cardinals.
+
+    For each $A\in [\kappa]^\omega$, note $[\kappa]^\omega\cap M$ is cofinal in $[\kappa]^\omega$, so let $A'\supseteq A$ be in $[\kappa]^\omega\cap M$ and let $f_A=\bigcup_{p\in G}p_{A'}\rest A$.
+Since $G$ is a $\pok$-generic filter over $M$, it is easily verified (considering the dense sets $D_{A,\alpha}$) that $f_A$ is an injective function from $A$ into $\omega$.
+
+    In addition, for $A,B\in [\kappa]^\omega\cap M$, let $p\in G\cap D_A\cap D_B$.
+For all $q\leq p$ it follows that $\{\alpha\in \dom(q_A)\cap \dom(q_B): q_A(\alpha)\not= q_B(\alpha)\} \subseteq \dom(p_A)\cup\dom(p_B)$.
+Thus $|\{\alpha\in A\cap B: f_A(\alpha)\not= f_B(\alpha)\}|<\omega$ and $f_A\al\perp f_B$ for $A,B\in [\kappa]^\omega\cap M$, and it's immediate that $f_A\al\perp f_B$ for $A,B\in[\kappa]^\omega$ as well.
+
+    The $f_A$ witness $S(\kappa,\omega,\omega)$ relativized to $M[G]$.
+  \end{proof}
+
+  As a result of this forcing for $\kappa>\omega_1$, $CH$ cannot hold in $M[G]$ (Scheepers points out that $\omega_1<\kappa\leq 2^\omega$).
+It is an open question whether $S(\kappa,\omega,\omega)$ is a theorem of ZFC+CH or ZFC.
+Nonetheless,
+
+  \begin{corollary}
+    $F\kmarkwin{2}\mengame{\oneptlind{\kappa}}$ is consistent with ZFC.
   \end{corollary}
@@
   \end{proof}
+
+  % I am error
+  % \begin{theorem}
+  %   $F\kmarkwin{k}\kfillgame{\kappa} \Rightarrow F\kmarkwin{k}\mengame{\oneptlind{\kappa}}$
+  % \end{theorem}
+
+  % \begin{proof}
+  %   Assume $\sigma$ is a winning $k$-Mark\"ov strategy for $F\kmarkwin{k}\kfillgame{\kappa}$, where 
+  %     \[
+  %       \sigma(C_0,0)\subseteq
+  %       \dots \subseteq
+  %       \sigma(\mc C_0,\dots,\mc C_{k-2},k-2) \subseteq
+  %       \sigma(C_0,C_1,\dots,C_{k-1},k-1)
+  %     \]
+  %   for all $n<\omega$.
+
+  %   For each open cover $\mc U$ of $\oneptlind{\kappa}$, let $C(\mc U)$ be a countable set such that $\oneptlind{\kappa}\setminus C(\mc U)$ is in a refinement of $\mc U$.
+We define $\tau^*$ as follows:
+
+  %     \[
+  %       \tau^*(\mc U_0,0) =
+  %       \oneptlind{\kappa}\setminus C(\mc U_0)
+  %     \]
+  %     \[
+  %       \tau^*(\mc U_0,\mc U_1,1) =
+  %       \dots =
+  %       \tau^*(\mc U_0,\dots,\mc U_{k-2},k-2) =
+  %       \emptyset
+  %     \]
+  %     \[
+  %       \tau^*(\mc U_0,\dots,\mc U_{k-1},n+k-1) = 
+  %       \sigma(C(\mc U_0),\dots,C(\mc U_{k-1}),n+k-1)
+  %     \]
+
+  %   If $\tau$ yields legal open sets covering $\tau^*$, then we claim $\tau$ is a winning strategy.
+Note that for any attack $\mc U_0,\mc U_1,\dots$ that $\tau$ covers $\oneptlind{\kappa}\setminus C(\mc U_0)$ in the initial round, and also covers
+  %     \[
+  %       \bigcup_{n<\omega}\sigma(C(\mc U_n),\dots,C(\mc U_{n+k-1}),n+k-1) \supseteq
+  %       \bigcup_{n<\omega} C(\mc U_n) \supseteq
+  %       C(\mc U_0)
+  %     \]
+  %   by the game's end.
+  % \end{proof}
 
@@
         \item $X$ is scattered
-        \item $O\win\rothgame{X}$
+        \item $S\win\rothgame{X}$
+        \item $C\not\win\rothgame{X}$
       \end{enumerate}
@@
 
-    Of course, $(c)\Rightarrow(a)$ is trivial.
+    Of course, $(c)\Rightarrow(a)$ is trivial, and $(a)\Leftrightarrow(d)$.
   \end{proof}
@@
 
+  \begin{definition}
+    Let $\mc{N}(x)$ be the $\textbf{neighborhood network}$ of $x$, that is, the collection of all neighborhoods of $x$.
+  \end{definition}
+
+  \begin{definition}
+    A topological space $X$ is \textbf{almost countable} if there exist $x_n\in X$ for each $n<\omega$ such that $X=\bigcup_{n<\omega}\bigcap\mc{N}(x_n)$.
+  \end{definition}
+
+  \begin{theorem}
+    For any space $X$, the following are equivalent:
+    \begin{itemize}
+      \item $S\markwin\rothgame{X}$ 
+      \item $P\prewin\altrothgame{X}$
+      \item $X$ is almost countable
+    \end{itemize}
+  \end{theorem}
+
+  \begin{proof}
+    If there exist $x_n\in X$ for each $n<\omega$ such that $X=\bigcup_{n<\omega}\bigcap\mc{N}(x_n)$, then let $\sigma(n)=x_n$ be a predetermined strategy for $P$ in $\altrothgame{X}$.
+For any neighborhoods $O_n$ of $x_n$ chosen by $O$ to attack $\sigma$, note that $\bigcup_{n<\omega}O_n\supseteq\bigcup_{n<\omega}\bigcap\mc{N}(x_n)=X$ results in a win for $P$.
+
+    Likewise, if for each sequence $x_n \in X$ there is $x\in X$ with $x\not\in \bigcup_{n<\omega}\bigcap\mc{N}(x_n)$, then for a fixed strategy $\sigma(n)$ for $P$, $O$ may counter $\sigma$ by choosing $O_n\in\mc{N}(x_n)$ which misses $x$ during each round, causing $\sigma$ to lose.
+  \end{proof}
+
   \begin{theorem}
@@
       \item $S\markwin\rothgame{X}$
+      \item $P\prewin\altrothgame{X}$
+      \item $X$ is almost countable
       \item $|X|\leq\omega$
@@
 
-  % \begin{example}
-  %   For the one-point Lindel\"ofication $\oneptlind{\omega_1}$ (a $T_2$ space), $S\win\rothgame{\oneptlind{\omega}}$, but $S\not\kmarkwin{k}\rothgame{X}$ for any $k$.
-  % \end{example}
-
   \begin{example}
-    Let $X=\omega_1\cup\{\infty\}$ be a ``weak Lindel\"ofication'' of $\omega_1$ such that open neighborhoods of $\infty$ contain the complement of $\omega$.
-This space is $T_0$ (provided the topology on $\omega_1$ is) but not $T_1$, and note that $S\markwin\rothgame{X}$ and $|X|>\omega$.
+    Let $X=\omega_1\cup\{\infty\}$ be a ``weak Lindel\"ofication'' of discrete $\omega_1$ such that open neighborhoods of $\infty$ contain $\omega_1\setminus\omega$.
+This space is $T_0$ but not $T_1$, and note that $S\markwin\rothgame{X}$ and $|X|>\omega$.
   \end{example}
@@
         \item $S\win\rothgame{X}$
-        \item $S\kmarkwin{k}\rothgame{X}$
+        \item $P\win\altrothgame{X}$
+        \item $S\kmarkwin{k}\rothgame{X}$ for some $k\geq 1$
+        \item $S\markwin\rothgame{X}$
+        \item $P\prewin\altrothgame{X}$
+        \item $X$ is almost countable
         \item $|X|\leq\omega$
@@
   \begin{proof}
-    $(c)\Rightarrow(b)\Rightarrow(a)$ are all trivial.
+    % $(c)\Rightarrow(b)\Rightarrow(a)$ are all trivial.
 Galvin has shown $(a) \Leftrightarrow P\win\altrothgame{X} \Rightarrow (c)$ in \textit{Indeterminacy}, but a direct proof of $(a)\Rightarrow(c)$ follows.
-Let $\sigma$ be a strategy for $S$ in $\rothgame{X}$.
+
+    Due to Galvin. Let $\sigma$ be a strategy for $S$ in $\rothgame{X}$.
 
@@
 
-  \begin{question}
-    $S\kmarkwin{2}\rothgame{\oneptcomp{\omega_1}}$ or $S\kmarkwin{2}\rothgame{\oneptlind{\omega_1}}$?
-  \end{question}
+  \begin{corollary}
+    The following are equivalent for compact points-$G_\delta$ $X$:
+      \begin{enumerate}[(a)]
+        \item $S\win\rothgame{X}$
+        \item $P\win\altrothgame{X}$
+        \item $S\kmarkwin{k}\rothgame{X}$ for some $k\geq 1$
+        \item $S\markwin\rothgame{X}$
+        \item $P\prewin\altrothgame{X}$
+        \item $X$ is almost countable
+        \item $|X|\leq\omega$
+        \item $C\not\win\rothgame{X}$
+        \item $O\not\win\altrothgame{X}$
+        \item $X$ is Rothberger
+        \item $X$ is scattered
+      \end{enumerate}
+  \end{corollary}
 
-  \begin{question}
-    $S\kmarkwin{2}\rothgame{X}\Leftrightarrow S\kmarkwin{k}\rothgame{X}$?
-  \end{question}
+  \begin{definition}
+    The game $\recallgame{m}{\kappa}$ proceeds as follows: during round $0$, player $F$ chooses $F_0\in[\kappa]^m$, followed by player $S$ choosing $x_0\in F_0\cup\{\infty\}$.
+During round $n+1$, $F$ chooses $F_{n+1}\in[\kappa]^{m^{n+2}}$ such that $F_{n+1}\supset F_n$, followed by $S$ choosing $x_{n+1}\in F_{n+1}\cup\{\infty\}$.
+
+    $S$ wins the game if $\{x_n : n<\omega\}\supseteq F_0\cup\{\infty\}$, and $F$ wins otherwise.
+  \end{definition}
+
+  \begin{proposition}
+    $S\limitwin\rothgame{\oneptlind{\kappa}} \Rightarrow S\limitwin\recallgame{m}{\kappa}$
+  \end{proposition}
+
+  \begin{proof}
+    Let $\sigma$ be a limited information strategy for $S$ in $\rothgame{\oneptlind{\kappa}}$.
+
+    Suppose $C(\cdot)$ converts any finite set $G$ played by $F$ in $\recallgame{m}{\kappa}$ into the open cover $\mc{U}_G=[G]^1\cup\{\oneptcomp{\kappa}\setminus G\}$.
+Then we may define a strategy $\tau$ using the same type of information as $\sigma$ by setting $\tau(\cdot)\in\sigma(C(\cdot))$.
+
+    Suppose that the attack $F_0, F_1, \dots$ countered $\tau$. Let $x_n$ be the point given by $\tau$ during round $n$, and choose $\alpha\in (F_0\cup\{\infty\})\setminus \{x_n : n<\omega \}$.
+
+    If $\alpha=\infty$, then $\sigma$ may be countered by the attack $\mc{U}_{F_0}, \mc{U}_{F_1}, \dots$ since no neighborhood of $\infty$ is ever chosen.
+
+    Similarly, if $\alpha\in F_0$, then $\sigma$ may also be countered by the attack $\mc{U}_{F_0}, \mc{U}_{F_1}, \dots$ since the singleton $\{\alpha\}$ is never chosen.
+  \end{proof}
+
+  \begin{proposition}
+    $S\kmarkwin{k}\recallgame{m}{\kappa} \Leftrightarrow S\ktactwin{k}\recallgame{m}{\kappa}$
+  \end{proposition}
+
+  \begin{proof}
+    The round number is deterimined by the size of the sets played by $C$.
+  \end{proof}
 

### 2013-10-28 phd/menger.tex
Finished presentation, cleaned up some asrc stuff as well as forcing argument

@@
   \begin{proof}
-    Result due to (???)
+    Result due to Hurewicz.
 
@@
 
-    The other direction is based upon Gruenhage's topological game presentation. Assume $X$ is Menger, and consider a strategy for $C$ in $\mengame{X}$.
+    Now, assume $X$ is Menger, and consider a strategy for $C$ in $\mengame{X}$.
 
@@
 
-  \begin{theorem}
+  \begin{corollary}
     A space $X$ is $\sigma$-(relatively compact) if and only if $F \markwin \mengame{X}$.
-  \end{theorem}
-
-  \begin{proof}
-    For the forward implication, let $X=\bigcup_{n<\omega}R_n$ for $R_n$ relatively compact, and define $\sigma(\mc U,n)$ to be a finite subcover of $R_n$.
-The previous lemma proves the other direction.
-  \end{proof}
+  \end{corollary}
 
@@
   Let $R$ be given the topology from example 63 from Counterexamples in Topology, the topology generated by open intervals with countable sets removed.
-This space is non-regular, non-$\sigma$-compact, and Lindel\"of.
-It is also Menger as $F \win \mengame{R}$, but $F \not\markwin \mengame{R}$.
+This space is a non-regular example where $F \win \mengame{R}$, but $F \not\markwin \mengame{R}$, that is, $R$ is not $\sigma$-(relatively compact).
   \end{example}
@@
   \begin{proof}
-  From Counterexamples: The irrationals are open, but contain no closed neighborhood, showing non-regular. Compact subsets are exactly finite subsets, showing non-$\sigma$-compact.
+  From Counterexamples: The irrationals are open, but contain no closed neighborhood, showing non-regular.
 
@@
 
-  There cannot be a winning Markov strategy $\sigma(\mc{U},n)$, however. Define 
-      \[
-        R_n = \bigcap_{\mc{U}\in\mathfrak{C}} \bigcup\sigma(\mc{U},n)
-      \]
-  where $\mathfrak{C}$ is the collection of open covers of $R$.
-For any $x_0,x_1,\dots \in R$, we may define the open cover $\mc{U} = \{R \setminus \{x_i: i \not= n\} : n < \omega \}$, and observe that $\bigcup \sigma(\mc{U},n) \supseteq R_n$ contains only finitely many $x_i$.
-Thus $R_n$ is finite, but since the previous lemma requires $\bigcup_{n<\omega} R_n = R$ if $\sigma$ is a winning strategy, there exists a counter to $\sigma$.
+  For any $A=\{x_n:n<\omega\} \in [R]^\omega$, we may choose the open cover $\mc{U} = \{R \setminus \{x_i: i \not= n\} : n < \omega \}$ of $R$ with no finite subcover.
+Thus all relatively compact sets are finite, and the countable union of finite sets cannot contain $R$, making $R$ not $\sigma$-(relatively compact).
   \end{proof}
@@
   Let $R$ be given the topology from example 67 from Counterexamples in Topology, the topology generated by open intervals with or without the rationals removed.
-This space is non-regular, non-$\sigma$-compact, and Lindel\"of.
-
-  This space is an example of non-$\sigma$-compact but $F \markwin \mengame{R}$ (and is thus also Menger).
+This space is non-regular, and non-$\sigma$-compact, but is second-countable and $\sigma$-(relatively compact).
   \end{example}
@@
 Compact sets in this topology are nowhere dense in the Euclidean topology, so there cannot be countably many which union to the whole space.
-$\{(a,b)\setminus D : a,b\in\mathbb{Q},D\in\{\emptyset,\mathbb{Q}\}\}$ is a countable base for the space, and second-countability implies Lindel\"of.
+$\{(a,b)\setminus D : a,b\in\mathbb{Q},D\in\{\emptyset,\mathbb{Q}\}\}$ is a countable base for the space.
 
-  % To see Menger, let $\mc{U}_0,\mc{U}_1,\dots$ be a sequence of open covers, and choose open sets $U_{2n}\in\mc{U}_{2n}$ which cover $q_n$ for each $q_n\in\mathbb{Q}$ (which in turn are open in the Euclidean line).
-Since the complement of the union $\bigcup_{n<\omega} U_{2n}$ must be closed discrete in the Euclidean line, it is countable, so open sets $U_{2n+1}\in\mc{U}_{2n+1}$ may be found to cover the remainder.
-
-  To see $F \markwin \mengame{R}$, we define $\sigma(\mc{U}_{2n},2n)$ to be a finite cover of $[-n,n]\setminus\mathbb{Q}$, and $\sigma(\mc{U}_{2n+1},2n+1)$ to be a finite cover of $\{q_n\}$ for each $q_n\in\mathbb{Q}$.
+  To see that $R$ is $\sigma$-relatively compact, it suffices to show that $[a,b]\setminus\mathbb{Q}$ is relatively compact.
+Let $\mc U$ be a cover of $R$, and let $\mc U'$ fill in the missing rationals for any open set in $\mc U$.
+There is a finite subcover $\mc V'\subseteq \mc U'$ for $[a,b]$ since $\mc U'$ contains open sets from the Euclidean topology.
+Let $\mc V= \{V\setminus\mathbb{Q}:V\in V'\}$: this is a finite refinment of $\mc U$ covering $[a,b]\setminus\mathbb{Q}$, so $[a,b]\setminus\mathbb{Q}$ is relatively compact.
   \end{proof}
@@
 
-    Let $\mathfrak{C}$ collect all the open covers of $X$. We say $X$ is \scish~if there exists a function $f:\mathfrak{C}\times\omega\to\mc{P}(X)$ such that:
-      \begin{itemize}
-        \item $f(\mc{V},n)$ is $\mc{V}$-compact
-        \item $f(\mc{V},n)\cap f(\mc{V},n+1) = \emptyset$
-        \item $\bigcup_{n<\omega}f(\mc{V},n)=X$
-        \item The set
+    We say $X$ is \scish~if there exist functions $r_{\mc V}:X\to\omega$ for each open cover $\mc V$ of $X$ such that both of the following sets are $\mc V$-compact for all open covers $\mc U$, $\mc V$ and $n<\omega$:
       \[
-            g(\mc{U},\mc{V},n+1) = \bigcup_{p\geq n} \Big(f(\mc{U},p+1)\setminus f(\mc{V},p+1)\Big)\setminus \bigcup_{m\leq n}f(\mc{U},m+1)
+        c(\mc V,n)=\{ x\in X : r_{\mc V}(x)\leq n\}
       \]
-         is $\mc{V}$-compact
-      \end{itemize}
+      \[
+        p(\mc U,\mc V)=\{ x\in X : 0<r_{\mc U}(x)<r_{\mc V}(x)\}
+      \]
   \end{definition}
 
-  Obviously $\sigma$-(relatively compact) implies \scish~implies Lindel\"of. We shall see that the non-$\sigma$-(relatively compact) space $\omega_1^\dagger$ is \scish.
-
   \begin{definition}
-    For two functions $f,g$ we say $f$ is \textbf{$\mu$-almost compatible} with $g$ ($f\al\perp_\mu g$) if $|\{x\in\dom(f)\cap\dom(g):f(x)\not=g(x)\}|<\mu$.
-If $\mu=\omega$ then we say $f,g$ are \textbf{almost compatible} ($f\al\perp g$).
+    For two functions $f,g$ we say $f$ is \textbf{$\mu$-almost compatible} with $g$ ($f\alcomp_\mu g$) if $|\{x\in\dom(f)\cap\dom(g):f(x)\not=g(x)\}|<\mu$.
+If $\mu=\omega$ then we say $f,g$ are \textbf{almost compatible} ($f\alcomp g$).
   \end{definition}
@@
   \begin{lemma}\label{kunlem}
-    For each $\alpha<\omega_1$, there exist injective functions $f_\alpha:\alpha\to\omega$ such that if $\alpha<\beta$, then \[f_\alpha \al\perp f_\beta\] that is, $f_\alpha$ and $f_\beta\rest\alpha$ agree on all but finitely many ordinals.
+    For each $\alpha<\omega_1$, there exist injective functions $f_\alpha:\alpha\to\omega$ such that if $\alpha<\beta$, then \[f_\alpha \alcomp f_\beta\] that is, $f_\alpha$ and $f_\beta\rest\alpha$ agree on all but finitely many ordinals.
 In addition, the range of each $f_\alpha$ is co-infinite.
@@
     Finally, suppose $\gamma$ is the limit of $\alpha_0,\alpha_1,\dots$, and $f_\alpha$ is defined for $\alpha<\gamma$.
-Let $g_0=f_{\alpha_0}$, and assuming $g_n\al\perp f_{\alpha_n}$ with coinfinite range, define $g_{n+1}:\alpha_{n+1}\to\omega$ so that $g_{n+1}\rest\alpha_n=g_n$ and $g_{n+1}\rest(\alpha_{n+1}\setminus\alpha_n)\al\perp f_{\alpha_{n+1}}$ with coinfinite range.
-Then $g=\bigcup_{n<\omega} g_n$ is an injective function from $\gamma \to \omega$ and $g \al\perp f_\alpha$ for $\alpha <\gamma$, but the range need not be coinfinite.
+Let $g_0=f_{\alpha_0}$, and assuming $g_n\alcomp f_{\alpha_n}$ with coinfinite range, define $g_{n+1}:\alpha_{n+1}\to\omega$ so that $g_{n+1}\rest\alpha_n=g_n$ and $g_{n+1}\rest(\alpha_{n+1}\setminus\alpha_n)\alcomp f_{\alpha_{n+1}}$ with coinfinite range.
+Then $g=\bigcup_{n<\omega} g_n$ is an injective function from $\gamma \to \omega$ and $g \alcomp f_\alpha$ for $\alpha <\gamma$, but the range need not be coinfinite.
 So let
@@
     \]
-    which frees up $\{g(\alpha_{2n+1}):n<\omega\}$ from the range of $f_\gamma$, and allows $f_\gamma\al\perp f_\alpha$.
+    which frees up $\{g(\alpha_{2n+1}):n<\omega\}$ from the range of $f_\gamma$, and allows $f_\gamma\alcomp f_\alpha$.
   \end{proof}
@@
   \begin{proof}
-    Take the injective funcions $f_\alpha$ from Kunen's lemma such that $f_\alpha \al\perp f_\beta$.
-For each open cover $\mc V$ of $\oneptlind{\omega_1}$ let $\gamma(\mc V)$ identify the least ordinal such that $[\gamma(\mc V),\omega_1)\cup\{\infty\}$ is in a refinement of $\mc V$.
-Then $f$ defined by $f(\mc V,0)=[\gamma(\mc V),\omega_1)\cup\{\infty\}$ and $f(\mc{V},n+1) = f_{\gamma(\mc V)}^{-1}(\{n\})$ is easily seen to witness the property.
+    Take the injective funcions $f_\alpha$ from Kunen's lemma such that $f_\alpha \alcomp f_\beta$.
+For each open cover $\mc V$ of $\oneptlind{\omega_1}$ let $\gamma(\mc V)$ identify the least ordinal such that $\oneptlind{\omega_1}\setminus\gamma(\mc U)$ is in a refinement of $\mc V$.
+Then $r_{\mc V}$ defined by
+      \[
+        r_{\mc V}(x) = \left\{
+      \begin{array}{ll}
+        0 & x\in\oneptlind{\omega_1}\setminus\gamma(\mc V) \\
+        f_{\gamma(\mc V)}(x)+1 & x\in\gamma(\mc V)
+      \end{array}
+      \right.
+      \] 
+    witnesses the property as $c(\mc V,0)$ is contained in a single open set in $\mc V$, $c(\mc V,n+1)$ is a singleton or empty set, and
+      \[
+        p(\mc U,\mc V) = \{\alpha<\min(\gamma(\mc U),\gamma(\mc V)) : f_{\gamma(\mc U)}(\alpha)<f_{\gamma(\mc V)}(\alpha)\}
+      \]
+    is finite.
   \end{proof}
@@
   \begin{proof}
-    Let $\sigma(\mc{U}_0,0)$ cover $f(\mc{U}_0,0)$, and let $\sigma(\mc{U}_n,\mc{U}_{n+1},n+1)$ cover $\bigcup_{m\leq n+1}f(\mc{U}_{n+1},m)$ and $g(\mc{U}_n,\mc{U}_{n+1},n+1)$.
+    Let $\sigma(\mc{U}_0,0)$ cover $c(\mc{U}_0,0)$, and let $\sigma(\mc{U}_n,\mc{U}_{n+1},n+1)$ cover both $c(\mc{U}_{n+1},n+1)$ and $p(\mc{U}_n,\mc{U}_{n+1})$.
 If $\mc{U}_0,\mc{U}_1,\dots$ is any play by $C$, then for each $x\in X$, we note that one of the following must occur:
       \begin{itemize}
-        \item $x \in f(\mc U_0,0)$ and is covered in the initial round.
-        \item $x \in f(\mc U_0,P+1)$ for some $P\geq 0$ and:
+        \item $r_{\mc U_0}(x)=0$ and thus $x\in c(\mc U_0,0)\subseteq \bigcup \sigma(\mc{U}_0,0)$.
+        \item $r_{\mc U_0}(x)=N+1$ for some $N\geq 0$ and:
         \begin{itemize}
-          \item $x\in \bigcup_{m\leq n\leq P} f(\mc{U}_{n+1},m+1)$ and is covered by the strategy by round $P+1$.
-          \item $x\in \bigcap_{n\leq P} f(\mc{U}_{n+1},P+1)$ and is covered by the strategy during round $P+1$.
-          \item For some $n \leq P$, 
-            \[x \in \Big( f(\mc{U}_{n},P+1)\setminus f(\mc{U}_{n+1},P+1) \Big)\setminus \bigcup_{m\leq n} f(\mc{U}_{n+1},m+1) \subseteq g(\mc{U}_m,\mc{U}_{m+1},m+1)\]
-           and is covered during round $n+1$.
+          \item For all $n\leq N$, 
+            \[
+              n+1< r_{\mc U_{n+1}}(x)\leq N+1
+            \] 
+            and thus $x\in c(\mc U_{N+1},r_{\mc U_{n+1}}(x))=c(\mc U_{N+1},N+1)$.
+          \item For some $n \leq N$,
+            \[
+              r_{\mc U_{n+1}}(x)< n+1 \leq r_{\mc U_n}(x)< N+1
+            \]
+            and thus $x\in c(\mc U_{n+1},r_{\mc U_{n+1}}(x))\subseteq c(\mc U_{n+1},n+1)$.
+          \item For some $n \leq N$, 
+            \[
+              n+1 \leq r_{\mc U_n}(x)< N+1 < r_{\mc U_{n+1}}(x)
+            \]
+           and thus $x\in p(\mc U_n,\mc U_{n+1})$
          \end{itemize}
@@
   \begin{definition} 
-    The statement $S(\kappa,\mu,\lambda)$ due to Scheepers is shorthand for the following: there exist injective functions $f_A:A\to\lambda$ for each $A\in[\kappa]^\mu$ such that $f_A\al\perp_\mu f_B$ for all $A,B\in[\kappa]^\mu$.
+    The statement $S(\kappa,\mu,\lambda)$ due to Scheepers is shorthand for the following: there exist injective functions $f_A:A\to\lambda$ for each $A\in[\kappa]^\mu$ such that $f_A\alcomp_\mu f_B$ for all $A,B\in[\kappa]^\mu$.
   \end{definition}
+
+  \begin{proposition}
+    $\neg S(\kappa,\omega,\omega)$ for $\kappa>2^\omega$
+  \end{proposition}
+
+  \begin{proof}
+    Let $A_\alpha=\{\alpha\cdot\omega+n:n<\omega\}\in[\kappa]^\omega$ and $f_{A_\alpha}:A_\alpha\to\omega$ be injective for $\alpha<\kappa$.
+Since there are $\kappa>|[\omega]^\omega|$ different $A_\alpha$, there must be $\alpha,\beta$ where $\text{ran}(f_{A_\alpha})=\text{ran}(f_{A_\beta})$.
+Then there is no way to define $f_{A_\alpha\cup A_\beta}$ so that it is almost compatible with both $f_{A_\alpha}$ and $f_{A_\beta}$.
+  \end{proof}
 
@@
 For each cover $\mc V$ of $\oneptlind{\kappa}$ let $A(\mc V)$ define a set such that $\oneptlind{\kappa}\setminus A(\mc V)$ is in a refinement of $\mc V$.
-Then define $f$ by $f(\mc V,0)=\oneptlind{\kappa}\setminus A(\mc V)$ and $f(\mc{V},n+1) = f_{A(\mc V)}^{-1}(\{n\})$.
+Then $r_{\mc V}$ defined by
+      \[
+        r_{\mc V}(x) = \left\{
+      \begin{array}{ll}
+        0 & x\in\oneptlind{\kappa}\setminus A(\mc V) \\
+        f_{A(\mc V)}(x)+1 & x\in A(\mc V)
+      \end{array}
+      \right.
+      \]
 
-    \begin{itemize}
-      \item $f(\mc{V},n)$ is $\mc{V}$-compact by definition.
-      \item $f(\mc{V},n)\cap f(\mc{V},n+1) = \emptyset$ by definition.
-      \item $\bigcup_{n<\omega}f(\mc{V},n)=X$ by definition.
-      \item Note that as $f(\mc{U},p+1)=f^{-1}_{A(\mc U)}(\{p\})$, $f(\mc{V},p+1)=f^{-1}_{A(\mc V)}(\{p\})$, and $f_{A(\mc U)}\al\perp f_{A(\mc V)}$, the set
+    witnesses the property as $c(\mc V,0)$ is contained in a single open set in $\mc V$, $c(\mc V,n+1)$ is a singleton or empty set, and
       \[
-            \left(\bigcup_{p<\omega} \Big(f(\mc{U},p+1)\setminus f(\mc{V},p+1)\Big) 
-            \setminus A(\mc{U})\right)
-            \setminus A(\mc{V})
+        p(\mc U,\mc V) = \{\alpha\in A(\mc U)\cap A(\mc V) : f_{A(\mc U)}(\alpha)<f_{A(\mc V)}(\alpha)\}
       \]
     is finite.
-
-        Thus the set
-          \[
-            g(\mc{U},\mc{V},n+1) = \bigcup_{p\geq n} \Big(f(\mc{U},p+1)\setminus f(\mc{V},p+1)\Big)\setminus \bigcup_{m\leq n}f(\mc{U},m+1)
-          \]
-        is $\mc{V}$-compact.
-    \end{itemize}
   \end{proof}
@@
             \item For each $A\in\dom(p)$, $q_A\supseteq p_A$
-            \item For each $A,B\in\dom(p)$, if $p_A$ and $p_B$ are not defined for some $\alpha\in A\cap B$, but $q_A$ is, then $q_B$ is also defined for $\alpha$ and $q_A(\alpha)=q_B(x)$. That is, 
+            \item For each $A,B\in\dom(p)$, if $p_A$ and $p_B$ are not defined for some $\alpha\in A\cap B$, but $q_A$ is, then $q_B$ is also defined for $\alpha$ and $q_A(\alpha)=q_B(x)$.
+That is, for $\alpha\in A\cap B$
               \[
@@
   \begin{theorem}
-    $S(\kappa,\omega,\omega)$ is consistent with ZFC for any cardinal $\kappa$.
+    $S(\kappa,\omega,\omega)+(\kappa=2^\omega)$ is consistent with ZFC for any cardinal $\kappa$ with $cf(\kappa)>\omega$.
   \end{theorem}
@@
   \begin{proof}
-    If $\kappa\leq\omega_1$, then $S(\kappa,\omega,\omega)$ is a theorem of ZFC - use Lemma \ref{kunlem}.
-
-    Assume $\kappa>\omega_1$; we adapt a forcing argument due to Scheepers.
+    We adapt a forcing argument due to Scheepers.
 Let $M$ be a countable transitive submodel of ZFC.
@@
 
-    For each $A\in [\kappa]^\omega$, note $[\kappa]^\omega\cap M$ is cofinal in $[\kappa]^\omega$, so let $A'\supseteq A$ be in $[\kappa]^\omega\cap M$ and let $f_A=\bigcup_{p\in G}p_{A'}\rest A$.
+    For each $A\in [\kappa]^\omega$, note $[\kappa]^\omega\cap M$ is cofinal in $[\kappa]^\omega$, so let $A'\supseteq A$ be in $[\kappa]^\omega\cap M$ and let $f_A=\bigcup_{p\in G\cap D_{A'}}p_{A'}\rest A$.
 Since $G$ is a $\pok$-generic filter over $M$, it is easily verified (considering the dense sets $D_{A,\alpha}$) that $f_A$ is an injective function from $A$ into $\omega$.
@@
 For all $q\leq p$ it follows that $\{\alpha\in \dom(q_A)\cap \dom(q_B): q_A(\alpha)\not= q_B(\alpha)\} \subseteq \dom(p_A)\cup\dom(p_B)$.
-Thus $|\{\alpha\in A\cap B: f_A(\alpha)\not= f_B(\alpha)\}|<\omega$ and $f_A\al\perp f_B$ for $A,B\in [\kappa]^\omega\cap M$, and it's immediate that $f_A\al\perp f_B$ for $A,B\in[\kappa]^\omega$ as well.
+Thus $|\{\alpha\in A\cap B: f_A(\alpha)\not= f_B(\alpha)\}|<\omega$ and $f_A\alcomp f_B$ for $A,B\in [\kappa]^\omega\cap M$, and it's immediate that $f_A\alcomp f_B$ for $A,B\in[\kappa]^\omega$ as well.
 
-    The $f_A$ witness $S(\kappa,\omega,\omega)$ relativized to $M[G]$.
+    The $f_A$ witness $S(\kappa,\omega,\omega)$. Since $\kappa\geq 2^\omega$ by $\pok$ c.c.c., and $S(\kappa,\omega,\omega)$ is a contradiction for $\kappa>2^\omega$, we know $\kappa=2^\omega$. 
   \end{proof}
 
-  As a result of this forcing for $\kappa>\omega_1$, $CH$ cannot hold in $M[G]$ (Scheepers points out that $\omega_1<\kappa\leq 2^\omega$).
-It is an open question whether $S(\kappa,\omega,\omega)$ is a theorem of ZFC+CH or ZFC.
-Nonetheless,
-
   \begin{corollary}
-    $F\kmarkwin{2}\mengame{\oneptlind{\kappa}}$ is consistent with ZFC.
+    For each $\kappa$, $F\kmarkwin{2}\mengame{\oneptlind{\kappa}}$ is consistent with ZFC.
   \end{corollary}
@@
   \end{proof}
-
-  % I am error
-  % \begin{theorem}
-  %   $F\kmarkwin{k}\kfillgame{\kappa} \Rightarrow F\kmarkwin{k}\mengame{\oneptlind{\kappa}}$
-  % \end{theorem}
-
-  % \begin{proof}
-  %   Assume $\sigma$ is a winning $k$-Mark\"ov strategy for $F\kmarkwin{k}\kfillgame{\kappa}$, where 
-  %     \[
-  %       \sigma(C_0,0)\subseteq
-  %       \dots \subseteq
-  %       \sigma(\mc C_0,\dots,\mc C_{k-2},k-2) \subseteq
-  %       \sigma(C_0,C_1,\dots,C_{k-1},k-1)
-  %     \]
-  %   for all $n<\omega$.
-
-  %   For each open cover $\mc U$ of $\oneptlind{\kappa}$, let $C(\mc U)$ be a countable set such that $\oneptlind{\kappa}\setminus C(\mc U)$ is in a refinement of $\mc U$.
-We define $\tau^*$ as follows:
-
-  %     \[
-  %       \tau^*(\mc U_0,0) =
-  %       \oneptlind{\kappa}\setminus C(\mc U_0)
-  %     \]
-  %     \[
-  %       \tau^*(\mc U_0,\mc U_1,1) =
-  %       \dots =
-  %       \tau^*(\mc U_0,\dots,\mc U_{k-2},k-2) =
-  %       \emptyset
-  %     \]
-  %     \[
-  %       \tau^*(\mc U_0,\dots,\mc U_{k-1},n+k-1) = 
-  %       \sigma(C(\mc U_0),\dots,C(\mc U_{k-1}),n+k-1)
-  %     \]
-
-  %   If $\tau$ yields legal open sets covering $\tau^*$, then we claim $\tau$ is a winning strategy.
-Note that for any attack $\mc U_0,\mc U_1,\dots$ that $\tau$ covers $\oneptlind{\kappa}\setminus C(\mc U_0)$ in the initial round, and also covers
-  %     \[
-  %       \bigcup_{n<\omega}\sigma(C(\mc U_n),\dots,C(\mc U_{n+k-1}),n+k-1) \supseteq
-  %       \bigcup_{n<\omega} C(\mc U_n) \supseteq
-  %       C(\mc U_0)
-  %     \]
-  %   by the game's end.
-  % \end{proof}
 

### 2013-10-29 phd/2013-10-22_seminar_presentation.tex
Added pauses to presentation

% $Header: /home/vedranm/bitbucket/beamer/solutions/generic-talks/generic-ornate-15min-45min.en.tex,v 90e850259b8b 2007/01/28 20:48:30 tantau $

\documentclass{beamer}

% This file is a solution template for:

% - Giving a talk on some subject.
% - The talk is between 15min and 45min long.
% - Style is ornate.

% Copyright 2004 by Till Tantau <tantau@users.sourceforge.net>.
%
% In principle, this file can be redistributed and/or modified under
% the terms of the GNU Public License, version 2.
%
% However, this file is supposed to be a template to be modified
% for your own needs. For this reason, if you use this file as a
% template and not specifically distribute it as part of a another
% package/program, I grant the extra permission to freely copy and
% modify this file as you see fit and even to delete this copyright
% notice.

\mode<presentation>
{
  \usetheme{Warsaw}
  % or ...

  \setbeamercovered{transparent}
  % or whatever (possibly just delete it)
}

      \theoremstyle{theorem}
      \newtheorem{proposition}[theorem]{Proposition}
      \theoremstyle{definition}
      \newtheorem{game}[theorem]{Game}
      \newtheorem{question}[theorem]{Question}

\usepackage[english]{babel}
% or whatever

\usepackage[latin1]{inputenc}
% or whatever

\usepackage{times}
\usepackage[T1]{fontenc}
% Or whatever. Note that the encoding and the font should match. If T1
% does not look nice, try deleting the line with the fontenc.

\usepackage{marvosym} % For \Smiley
\usepackage{verbatim} % for \verbatiminput

\title
{Scheeper's Meager-NWD Game and the Menger Game}

\subtitle
{AU Topology Seminar} % (optional)

\author%[Author, Another] % (optional, use only with lots of authors)
{Steven~Clontz}%\inst{1} \and S.~Another\inst{2}}
% - Use the \inst{?} command only if the authors have different
%   affiliation.

\institute[Auburn University] % (optional, but mostly needed)
{
  %\inst{1}%
  Department of Mathematics and Statistics\\
  Auburn University}
  %\and
  %\inst{2}%
  %Department of Theoretical Philosophy\\
  %University of Elsewhere}
% - Use the \inst command only if there are several affiliations.
% - Keep it simple, no one is interested in your street address.

\date[13-10-22] % (optional)
{October 22, 2013}

% If you have a file called "university-logo-filename.xxx", where xxx
% is a graphic format that can be processed by latex or pdflatex,
% resp., then you can add a logo as follows:

 \pgfdeclareimage[height=1cm]{university-logo}{auburn_logo.png}
 \logo{\pgfuseimage{university-logo}}

% Delete this, if you do not want the table of contents to pop up at
% the beginning of each subsection:
%\AtBeginSubsection[]
%{
%  \begin{frame}<beamer>{Outline}
%    \tableofcontents[currentsection,currentsubsection]
%  \end{frame}
%}

% If you wish to uncover everything in a step-wise fashion, uncomment
% the following command:

%\beamerdefaultoverlayspecification{<+->}

% My game notational definitions
\newcommand{\win}{\uparrow}
\newcommand{\prewin}{\uparrow_{\text{pre}}}
\newcommand{\markwin}{\uparrow_{\text{mark}}}
\newcommand{\tactwin}{\uparrow_{\text{tact}}}
\newcommand{\ktactwin}[1]{\uparrow_{#1\text{-tact}}}
\newcommand{\kmarkwin}[1]{\uparrow_{#1\text{-mark}}}
\newcommand{\codewin}{\uparrow_{\text{code}}}
\newcommand{\limitwin}{\uparrow_{\text{limit}}}
\newcommand{\oneptcomp}[1]{#1^*}
\newcommand{\oneptlind}[1]{#1^\dagger}
\newcommand{\congame}[2]{Con_{\pl O\pl P}(#1,#2)}
\newcommand{\clusgame}[2]{Clus_{\pl O\pl P}(#1,#2)}
\newcommand{\lfkpgame}[1]{LF_{\pl K\pl P}(#1)}
\newcommand{\lfklgame}[1]{LF_{\pl K\pl L}(#1)}
\newcommand{\pfgame}[1]{PF_{\pl F\pl C}(#1)}
\newcommand{\mengame}[1]{Cov_{\pl C\pl F}(#1)}
\newcommand{\rothgame}[1]{Cov_{\pl C\pl S}(#1)}
\newcommand{\altrothgame}[1]{Cov_{\pl P\pl O}(#1)}
\newcommand{\fillgame}[1]{Fill^{\subseteq}_{\pl M\pl N}(#1)}
\newcommand{\sfillgame}[1]{Fill^{\subsetneq}_{\pl M\pl N}(#1)}
\newcommand{\kfillgame}[1]{Fill^{\subseteq}_{\pl C\pl F}(#1)}
\newcommand{\ksfillgame}[1]{Fill^{\subsetneq}_{\pl C\pl F}(#1)}
\newcommand{\recallgame}[2]{Rec^{#1}_{\pl F\pl S}(#2)}
\newcommand{\sigmaprodr}[1]{\Sigma\mathbb{R}^{#1}}
\newcommand{\sigmaprodtwo}[1]{\Sigma2^{#1}}
\newcommand{\concat}{^\frown}
\newcommand{\rest}{\restriction}
\newcommand{\cl}[1]{\overline{#1}}
\newcommand{\pow}[1]{\mc{P}(#1)}
\newcommand{\<}{\langle}
\renewcommand{\>}{\rangle}
\newcommand{\al}[1]{{#1}^*}
\newcommand{\mc}[1]{\mathcal{#1}}
\newcommand{\po}{\mathbb{P}}
\newcommand{\pok}{\po_\kappa}
\newcommand{\Lim}{\mathrm{Lim}}
\newcommand{\Suc}{\mathrm{Suc}}
\newcommand{\ds}{\displaystyle}
\newcommand{\alcomp}{\al\parallel}
\newcommand{\rank}{\textrm{rank}}
\newcommand{\dom}{\textrm{dom}}
\newcommand{\scish}{almost-$\sigma$-(relatively compact)}

\usepackage{mathrsfs}
\newcommand{\pl}[1]{\mathscr{#1}}

\begin{document}
% \renewcommand{\pause}{}

\begin{frame}
  \titlepage
\end{frame}

% \begin{frame}{Table of Contents}
%   \tableofcontents
%   % You might wish to add the option [pausesections]
% \end{frame}

\section{Introduction}

\subsection{Abstract}

\begin{frame}{Abstract}%{Subtitles are optional.}

    Marion Scheepers designed the Meager-NWD game $\sfillgame{J}$ in the 80s to study the existence of $k$-tactics in set-theoretic and topological games.

    \pause
    \vspace{12pt}

    There are strong similarities between Dr. Scheeper's game and the special case of the Menger game $\mengame{\oneptlind{\kappa}}$ played upon the one-point ``Lindel\"ofication'' of a discrete cardinal $\kappa$.

    \pause
    \vspace{12pt}

    We will explore the relationship between $k$-tactical stratgies in $\sfillgame{J}$ and $k$-Mark\"ov strategies in $\fillgame{J}$ or $\mengame{\oneptlind{\kappa}}$, as well as a sentence $S(\kappa,\omega,\omega)$ which is consistent with ZFC.
\end{frame}

\subsection{Motivation}

\begin{frame}{Menger Game}
  \begin{game}
    The two-player Menger Game $\mengame{X}$ proceeds as follows:
    \begin{itemize}
      \item Round $n$: player $\pl C$ chooses an open cover $\mathcal{U}_n$ of $X$
      \item Round $n$: player $\pl F$ chooses finite $\mathcal{F}_n\subseteq\mathcal{U}_n$.
    \end{itemize}
    $\pl F$ wins if $\bigcup_{n<\omega} \mathcal{F}_n$ is a cover of $X$.
  \end{game}
  \pause

  \begin{itemize}
  \item Easy to see that $\pl F$ can win for any $\sigma$-compact space.
  \pause
  \item
    The existence or non-existence of various limited info strategies in this game characterize covering properties of $X$.
  \end{itemize}
\end{frame}

\begin{frame}{$\mengame{X}$ characterizations}

{\tiny
  \begin{tabular}{ccccccc}
  $\pl F\markwin\mengame{X}$ & $\Rightarrow$ &
  $\pl F\kmarkwin{2}\mengame{X}$ & $\Rightarrow$ &
  $\pl F\win\mengame{X}$ & $\Rightarrow$ &
  $\pl C\not\win\mengame{X}$ \\
  $\Updownarrow$ &&
  $\Updownarrow$ &&
  $\Updownarrow$ &&
  $\Updownarrow$ \\
  $X$ is $\sigma$-(rel. compact) & $\Rightarrow$ &
  ??? & $\Rightarrow$ &
  ??? & $\Rightarrow$ &
  $X$ is Menger
  \end{tabular}
}
{\small
\begin{itemize}
  \item $\win$ denotes a player with a \textbf{winning strategy}
  \item $\markwin$ denotes a player with a winning \textbf{Mark\"ov} strategy (using only the round number and most recent move of opponent)
  \item $\kmarkwin{k}$ denotes a player with a winning $k$-\textbf{Mark\"ov} strategy (using only the round number and $k$ most recent moves of opponent)
\end{itemize}
}
\pause
\begin{theorem}
Assume $k\geq 2$. $\pl F\kmarkwin{k}\mengame{X} \Leftrightarrow \pl F\kmarkwin{2}\mengame{X}$
\end{theorem}
\begin{theorem}
For $X$ second-countable, $\pl F\markwin\mengame{X} \Leftrightarrow \pl F\win\mengame{X}$
\end{theorem}

\end{frame}

\begin{frame}{$\mengame{X}$ characterizations}
Here are a couple properties between $\sigma$-compact and Menger:
  \begin{itemize}
    \item Alster
    \item Hurewicz
  \end{itemize}

\pause

An example of a Menger space which doesn't yield a Markov strategy for $\pl F$ in the Menger game is $\oneptlind{\omega_1}$.

{\tiny ($\oneptlind{\kappa}=\kappa\cup\{\infty\}$ is the one-point ``Lindel\"ofication'' of discrete $\kappa$.)}

\begin{theorem}
$\pl F\not\markwin\mengame{\oneptlind{\omega_1}}$ but $\pl F\kmarkwin{2}\mengame{\oneptlind{\omega_1}}$
\end{theorem}
\end{frame}

\begin{frame}{What about $\mengame{\oneptlind{\kappa}}$?}
  \begin{itemize}
    \item The direct proof of $\pl F\kmarkwin{2}\mengame{\oneptlind{\omega_1}}$ uses injective functions $f_\alpha:\alpha\to\omega$ for each $\alpha<\omega_1$ such that for $\alpha<\beta$:
      \[
        |\{\gamma<\alpha: f_\alpha(\gamma)\not=f_\beta(\gamma)\}|<\omega
      \]
      (Proof in Kunen's set theory text, used for construction of an Aronszajn tree)
    \pause
    \item Would like to extend this idea for $\kappa>\omega_1$ to show $\pl F\kmarkwin{2}\mengame{\oneptlind{\kappa}}$...
  \end{itemize}
\end{frame}

\section{Filling Games}

\subsection{Scheeper's Strict Filling Game}

\begin{frame}{$\sfillgame{J}$}
  \begin{game} 
      The \textbf{strict filling game} $\sfillgame{J}$ on an ideal $J$ proceeds as follows:
        \begin{itemize}
          \item Round 0: player $\pl M$ chooses $M_0 \in \<J\>$, the $\sigma$-completion of $J$ (closure under countable unions)
          \item Round 0: player $\pl N$ chooses $N_0\in J$. 
          \item Round $n+1$: player $\pl M$ chooses $M_{n+1}$ where $M_n\subsetneq M_{n+1}\in\<J\>$
          \item Round $n+1$: player $\pl N$ replies with $N_{n+1}\in J$. 
        \end{itemize}
      Player $\pl N$ wins the game if $\bigcup_{n<\omega} N_n \supseteq \bigcup_{n<\omega} M_n$. 
  \end{game}
\end{frame}

\begin{frame}
  \begin{itemize}
    \item
      The sets in $\<J\>$ and $J$ are referred to as meager and nowhere-dense sets, respectively.
      \begin{itemize}
        \item For any topological space, the set of nowhere dense sets $J$ forms an ideal. 
        \item For every ideal $J$, there is a topological space where $J$ is the set of nowhere dense sets.
      \end{itemize}
    \pause
    \item
      This game was defined and studied by Marion Scheepers. Here's some facts.
  \end{itemize}
  \begin{proposition}
    \[\pl N\win\sfillgame{J}\]
  \end{proposition}
\end{frame}

\begin{frame}

  \begin{theorem}
    \[\pl N\tactwin\sfillgame{J} \Leftrightarrow J=\<J\>\]
  \end{theorem}

{\small
\begin{itemize}
  \item $\tactwin$ denotes a player with a winning \textbf{tactical} strategy (using only the most recent move of opponent)
  \item $\ktactwin{k}$ denotes a player with a winning $k$-\textbf{tactical} strategy (using only the $k$ most recent moves of opponent)
\end{itemize}
}
\end{frame}

\begin{frame}
  \begin{theorem}
    Assume $cf(\<J\>)=\omega_1$. Let $J_X = \{N\cap X : N\in J\}$.

    $\pl N\ktactwin{k}\sfillgame{J} \Leftrightarrow \pl N\ktactwin{k}\sfillgame{J_X}$ for each $X\in\<J\>\setminus J$
  \end{theorem}

  \pause

  \textbf{Proof:} 
    $\Rightarrow$ is straight-forward.

  \pause

    \vspace{12pt}

    Sketch of $\Leftarrow$: Let $S_\alpha$ for $\alpha<\omega_1$ enumerate a cofinal set of $\<J\>$, with $\beta\leq\alpha\Rightarrow S_\beta\subseteq S_\alpha$. Assume the latest move by $\pl M$ is contained by $S_\alpha$. There are two types of attacks that $\pl N$ must defeat.

  \pause

    \begin{enumerate}\small
      \item $\pl M$'s attack may never go outside $S_\alpha$, so $\pl N$ can cover according to the strategy for $\pl N\ktactwin{k}\sfillgame{S_\alpha}$.
      \pause
      \item $\pl M$'s attack may eventually exceed $S_\alpha$, but by using tree arrangments $<_n$ of $\omega_1$ of finite height approximating $<$, $\pl N$ can cover according to the \textit{winning perfect information strategy} as though $\pl M$ had played sets $S_\beta$ for $\beta\leq_n \alpha$ instead.
    \end{enumerate}
\end{frame}

\begin{frame}
  \begin{corollary}
    If $|\bigcup J| \leq \omega_1$ and $|M|\leq \omega$ for $M\in\<J\>$, then $\pl N\ktactwin{2}\sfillgame{J}$.
  \end{corollary}

  \pause

  \textbf{Proof:}
    Assume $\omega\in\<J\>$ and assume the two latest moves of $\pl M$ are $M\subsetneq M'\subseteq \omega$. Let $n=\min(M'\setminus M)$, and have $\pl N$ cover $\{0,\dots,n\}$. It follows that the generated $n$ must be unbounded for any legal attack by $\pl M$, making it a winning $2$-tactic for $\sfillgame{J_\omega}$.
    \pause

    \vspace{12pt}

    Apply the previous theorem to finish the result. \qed

\end{frame}

\begin{frame}{Countable Finite Game}

  \begin{game}
    The special case of $\sfillgame{J}$ where $J=[\kappa]^{<\omega}$ is the Countable-Finite game $\ksfillgame{\kappa}$.
  \end{game}

  \pause

  \begin{corollary}
    \[\pl F\ktactwin{2}\ksfillgame{\omega_1}\]
  \end{corollary}

  \pause

  So $\pl F\ktactwin{2}\ksfillgame{\omega_1}$ and $\pl F\kmarkwin{2}\mengame{\oneptlind{\omega_1}}$. In addition, the basic goal of $\pl F$ in $\mengame{\oneptlind{\omega_1}}$ is similar to the goal of $\pl F$ in $\ksfillgame{\omega_1}$: $\pl F$ can cover a co-countable neighborhood of $\infty$ in the initial round, and is trying to cover the countable remainder in the following rounds (most likely using finitely many singletons from $\pl C$'s covers).
\end{frame}

\subsection{A game to connect $\ksfillgame{\kappa}$ and $\mengame{\oneptlind{\kappa}}$}

\begin{frame}

  \begin{itemize}
    \item Question: why does $\pl F$ need the round number in $\mengame{\oneptlind{\omega_1}}$ and not $\ksfillgame{\omega_1}$?
  \end{itemize}

  \pause

  \begin{proposition}
    $\pl F \ktactwin{k} \mengame{X} \Leftrightarrow X$ is compact
  \end{proposition}

  \textbf{Proof:}
    If $X$ isn't compact, and $\pl C$ constantly chooses an open cover $\mc U$ without a finite subcover for $X$ throughout the entire game, then $\pl F$ only chooses $k$ different finite subcollections of $\mc U$ by the game's end, which cannot cover $X$.

    \vspace{12pt}

    If $X$ is compact, $\pl F \tactwin \mengame{X}$ trivially. \qed

    \pause

    \begin{itemize}
      \item Answer: $\pl C$ cannot choose a constant strategy in $\ksfillgame{\kappa}$, but $\pl C$ can in $\mengame{\oneptlind{\kappa}}$.
    \end{itemize}

\end{frame}

\begin{frame}

  This provides the motivation to change the rules of Scheeper's game to bring it more in line with the Menger game.
  \pause

  \begin{game}
    The game $\fillgame{J}$ is identical to $\sfillgame{J}$, except that $\pl M$ may choose the same set in successive rounds.
  \end{game}

  \begin{game}
    $\kfillgame{\kappa}$ is identical to $\fillgame{[\kappa]^{<\omega}}$
  \end{game}

  \pause

  It seems reasonable to ask if $k$-tactics in $\sfillgame{J}$ correspond to $k$-Mark\"ov strategies in $\fillgame{J}$.

\end{frame}

\begin{frame}
  \begin{theorem}
    \[\pl N\ktactwin{2}\sfillgame{J} \Rightarrow \pl N\kmarkwin{2}\fillgame{J}\]
  \end{theorem}

  \pause

  \textbf{Proof:}
    Enumerate the sets in $J$ as $A_\alpha$ for $\alpha<|J|$. For $M\in \<J\>$ and $n<\omega$, let $M+0=M$ and $M+n+1$ be the union of $M+n$ and the least $A_\alpha$ not contained in $M+n$.

    \pause\vspace{12pt}

    Let $\sigma$ be a winning $2$-tactical strategy for $N$ in $\sfillgame{\kappa}$, and assume $\sigma(M)\cup\sigma(M')\subseteq\sigma(M,M')$.

    \pause\vspace{12pt}

    We define a $2$-Markov strategy $\tau$ for $F$ in $\fillgame{\kappa}$ as follows:
\end{frame}

\begin{frame}{}

{\small
      \[
        \tau(M_0,0) = \sigma(M_0)
      \]
      \[
        \tau(M_{n},M_{n+1},n+1) = \left\{
          \begin{array}{ll}
            \sigma(M_{n},M_{n+1}) & \text{if } M_n\subsetneq M_{n+1} \\
            \bigcup_{m\leq n}\sigma(M_n+m,M_{n+1}+m+1) & \text{otherwise}
          \end{array}
        \right.
      \]
}

\pause
\begin{itemize}
\item (Essentially, if $\pl M$ tries to be tricky and not increase the size of her meager set, $\pl N$ can pretend she added a few extra nowhere dense sets based on the round number.)
\end{itemize}
\end{frame}

\begin{frame}
Let $M_0 \subseteq M_1 \subseteq \dots$ be an attack by $\pl M$ against $\tau$. There are two possible cases:

      \begin{itemize}\small
        \item
          Assume $M_n=M_N$ for all $n\geq N$.\pause

          The collection produced by $\sigma$ versus the attack
            \[
              M_N+0 \subsetneq M_N+1 \subsetneq \dots
            \] 
          must cover $M_N$ as $\sigma$ is a winning strategy.\pause

          Let $x \in M_N$. If $x\in\sigma(M_N+0)$, then $x$ will be covered in round $N+1$ by 
            \[
              \tau(M_N,M_N,N+1)
              \supseteq \sigma(M_N+0,M_N+1)
              \supseteq \sigma(M_N+0)
            \]\pause

          Otherwise, $x\in\sigma(M_N+n,M_N+n+1)$, and $x$ will be covered in round $N+n+1$ by 
            \[
              \tau(M_N,M_N,N+n+1)
              \supseteq \sigma(M_N+n,M_N+n+1)
            \]
      \end{itemize}
\end{frame}
\begin{frame}
      \begin{itemize}\small
        \item
          Otherwise we may find $0<f(0)<f(1)<\dots$ such that $M_{f(n)}\subsetneq M_{f(n)+1}=M_{f(n+1)}$.\pause

          Then the collection produced by $\sigma$ versus the attack 
            \[
              M_{f(0)}\subsetneq M_{f(1)} \subsetneq M_{f(2)} \dots
            \]
          must cover $\bigcup_{n<\omega}M_n$ as $\sigma$ is a winning strategy.\pause

          Let $x \in \bigcup_{n<\omega}M_n$. If $x\in\sigma(M_{f(0)})$, then $x$ will be covered by $\tau$ in round $f(0)+1$ by
            \[
              \tau(M_{f(0)},M_{f(0)+1},f(0)+1)
              = \sigma(M_{f(0)},M_{f(0)+1})
              \supseteq \sigma(M_{f(0)})
            \]\pause

          Otherwise, $x\in\sigma(M_{f(n)},M_{f(n+1)})$, and $x$ will be covered by $\tau$ in round $f(n)+1$ by
            \[
              \tau(M_{f(n)},M_{f(n)+1},f(n)+1)
              = \sigma(M_{f(n)},M_{f(n)+1})
              = \sigma(M_{f(n)},M_{f(n+1)})
            \]
      \end{itemize}\pause

      Thus $\tau$ is a winning strategy. \qed
\end{frame}

\begin{frame}
But the converse need not hold.\pause

  \begin{theorem}
    There is a free ideal $J$ such that $\pl N\not\ktactwin{2}\sfillgame{J}$ but $\pl N\kmarkwin{2}\fillgame{J}$.
  \end{theorem}
  {\small
  \textbf{Proof:}
    This counterexample was constructed by Scheepers for another purpose, but works for us as well. Assume $\mathbb{R}$ has the usual Euclidean topology.\vspace{12pt}

    Choose $A\subseteq\mathbb{R}$ such that $|A|=\omega$ and $A$ is meager but not nowhere dense. Then choose $V\subseteq\mathbb{R}$ such that $|V|=2^\omega$, $V$ is meager, and $V$ is disjoint from $A$. Assume $A=\{a_n:n<\omega\}$.\pause\vspace{12pt}

    Certainly, if $J$ is the collection of nowhere dense subsets of $A\cup V$, then $F\kmarkwin{2}\fillgame{J}$. In fact, since $A\cup V$ is meager, $F\prewin\fillgame{J}$ ($\pl F$ has a \textbf{predetermined strategy} using only the round number). 
    }
\end{frame}
\begin{frame}

    Let $\sigma$ be a $2$-tactical strategy for $\pl N$ in $\sfillgame{J}$.\pause\vspace{12pt}

    By Cor 28 of Scheepers' ``Partition relation for partially ordered sets'', for every partition $\{K_n:n<\omega\}$ of the comparable pairs in $[\pow{V}]^2$ there is some $n'<\omega$ and sequence $C_0\subsetneq C_1\subsetneq \dots\subsetneq V$ where $\{C_m,C_{m+1}\}\in K_{n'}$ for all $m<\omega$.\pause\vspace{12pt}

    Define $K_n$ to be the collection of pairs of sets $\{B,C\}$ such that $B\subsetneq C$ and $n$ is the least integer where $a_n \in A \setminus \sigma(A\cup B,A\cup C)$.\pause\vspace{12pt}

    Then $\sigma$ may be countered by the attack $A\cup C_0, A\cup C_1, \dots$, since $a_{n'} \in A \setminus \sigma(A\cup C_m,A\cup C_{m+1})$ for all $m<\omega$ and thus is never covered. \qed\pause

    \begin{question}
      $\pl N\kmarkwin{2}\kfillgame{\kappa}\Rightarrow \pl N\ktactwin{2}\ksfillgame{\kappa}$?
    \end{question}
\end{frame}

\subsection{$S(\kappa,\omega,\omega)$}

\begin{frame}{$S(\kappa,\omega,\omega)$}

Scheepers introduced the sentence $S(\kappa,\omega,\omega)$ (or rather, a sentence equivalent to the one I use below).\pause

  \begin{definition}
    For two functions $f,g$ we say $f$ is \textbf{almost compatible} with $g$ ($f\alcomp g$) if $|\{x\in\dom(f)\cap\dom(g):f(x)\not=g(x)\}|<\omega$.
  \end{definition}\pause

\begin{definition}
  $S(\kappa,\omega,\omega)$ is shorthand for the sentence: there exist injective functions $f_A:A\to\omega$ for each $A\in[\kappa]^\omega$ such that $f_A\alcomp f_B$ for all $A,B\in[\kappa]^\omega$.
\end{definition}

\end{frame}

\begin{frame}
  \begin{theorem}
    $S(\omega_1,\omega,\omega)$
  \end{theorem}

  \textbf{Proof:}
    Use Kunen's $f_\alpha$ mentioned earlier. \qed

  \pause\vspace{12pt}

  \begin{theorem}
    $\neg S(\kappa,\omega,\omega)$ for $\kappa>2^\omega$
  \end{theorem}

  \textbf{Proof:}
    Let $A_\alpha=\{\alpha\cdot\omega+n:n<\omega\}\in[\kappa]^\omega$ and $f_{A_\alpha}:A_\alpha\to\omega$ be injective for $\alpha<\kappa$. Since there are $\kappa>|[\omega]^\omega|$ different $A_\alpha$, there must be $\alpha,\beta$ where $\text{ran}(f_{A_\alpha})=\text{ran}(f_{A_\beta})$. Then there is no way to define $f_{A_\alpha\cup A_\beta}$ so that it is almost compatible with both $f_{A_\alpha}$ and $f_{A_\beta}$. \qed\pause

  \begin{corollary}
    $S(\omega_2,\omega,\omega) \Rightarrow \neg CH$
  \end{corollary}
\end{frame}

\begin{frame}
  So what about the consistency of $\neg CH + S(\omega_2,\omega,\omega)$? It turns out that's fine (to be shown later).

  \pause

  \begin{theorem}
    $S(\kappa,\omega,\omega) \Rightarrow \pl F \ktactwin{2} \ksfillgame{\kappa}$
  \end{theorem}\pause

  \textbf{Proof:} Due to Todorcevic. Let $f_A:A\to\omega$ for $A\in[\kappa]^\omega$ witness $S(\kappa,\omega,\omega)$, and let $g_A(\alpha)$ be the number of ordinals ``skipped'' by $f_A$ below $f_A(\alpha)$, that is, $f_A(\alpha)-|\{\beta\in A:f_A(\beta)<f_A(\alpha)\}|$.
  \pause\vspace{6pt}

  Note that for $A\subsetneq B$, $|\{\alpha\in A:g_A(\alpha)\leq g_B(\alpha)\}|<\omega$ since the difference in $f_A$ and $f_B\rest A$ is finite, and $f_B$ has to map at least one more ordinal than $f_A$.
  \pause\vspace{6pt}

  Let $\sigma(C,C')=\{\alpha\in C: g_C(\alpha)\leq g_{C'}(\alpha)\}$. If $C_0\subsetneq C_1\subsetneq\dots$ was an attack defeating $\sigma$, then let $\alpha\in C_N\setminus\bigcup_{n<\omega}\sigma(C_n,C_{n+1})$.
  \pause\vspace{6pt}

  Observe that $g_{C_N}(\alpha)>g_{C_{N+1}}(\alpha)>g_{C_{N+2}}(\alpha)>\dots$, contradiction.\qed

\end{frame}

\begin{frame}

  \begin{theorem}
    $S(\kappa,\omega,\omega) \Rightarrow \pl F \kmarkwin{2} \kfillgame{\kappa}$
  \end{theorem}

  \textbf{Proof:} 
    Corollary of the previous theorem. Alternatively, $\pl F$ can use the winning strategy
      \[
        \sigma(C,C',n+1)=f_C^{-1}(\{0,\dots,n-1\}) \cup \{\alpha\in C: f_C(\alpha)\not= f_{C'}(\alpha)\}
      \]

\end{frame}

\section{Menger Game}

\subsection{Almost-$\sigma$-(Relatively Compact)}

\begin{frame}{Back to $\mengame{\oneptlind{\kappa}}$}
  While a proof $\pl F \kmarkwin{2} \kfillgame{\kappa}\Rightarrow \pl F \kmarkwin{2} \mengame{\oneptlind{\kappa}}$ has eluded me, the techniques used previously are very useful for dealing with $\mengame{\oneptlind{\kappa}}$ directly.

  \pause\vspace{12pt}

  It will be useful to define a sufficient property for $\pl F \kmarkwin{2} \mengame{X}$, which I've called \scish{}.
\end{frame}

\begin{frame}
  \begin{definition}
    Let $\mc U$ be a cover of $X$. We say $C\subseteq X$ is $\mc U$-compact if there exists a finite subcover of $\mc U$ which covers $C$.\vspace{6pt}

    We say $X$ is \scish~if there exist functions $r_{\mc V}:X\to\omega$ for each open cover $\mc V$ of $X$ such that both of the following sets are $\mc V$-compact for all open covers $\mc U$, $\mc V$ and $n<\omega$:
      \[
        c(\mc V,n)=\{ x\in X : r_{\mc V}(x)\leq n\}
      \]
      \[
        p(\mc U,\mc V)=\{ x\in X : 0<r_{\mc U}(x)<r_{\mc V}(x)\}
      \]

  \end{definition}\pause

  \begin{proposition}
    $X$ $\sigma$-(relatively compact) $\Rightarrow$ $X$ \scish
  \end{proposition}
\end{frame}

\begin{frame}

  \begin{theorem}
    If $X$ is \scish, then $\pl F \kmarkwin{2} \mengame{X}$.
  \end{theorem}\pause

  \textbf{Proof:}
    Let $\sigma(\mc{U}_0,0)$ cover $c(\mc{U}_0,0)$, and let $\sigma(\mc{U}_n,\mc{U}_{n+1},n+1)$ cover both $c(\mc{U}_{n+1},n+1)$ and $p(\mc{U}_n,\mc{U}_{n+1})$. If $\mc{U}_0,\mc{U}_1,\dots$ is any play by $C$, then for each $x\in X$, we note that one of the following must occur:\pause
      \begin{itemize}
        \item $r_{\mc U_0}(x)=0$ and thus $x\in c(\mc U_0,0)$.\pause
        \item $r_{\mc U_0}(x)=N+1$ for some $N\geq 0$ and:\pause
        \begin{itemize}
          \item For all $n\leq N$, 
            \[
              n+1< r_{\mc U_{n+1}}(x)\leq N+1
            \] 
            and thus $x\in c(\mc U_{N+1},r_{\mc U_{n+1}}(x))=c(\mc U_{N+1},N+1)$.
        \end{itemize}
      \end{itemize}
\end{frame}
\begin{frame}
      \begin{itemize}
      \item $r_{\mc U_0}(x)=N+1$ for some $N\geq 0$ and: (cont.)
        \begin{itemize}
          \item For some $n \leq N$,
            \[
              r_{\mc U_{n+1}}(x)< n+1 \leq r_{\mc U_n}(x)< N+1
            \]
            and thus $x\in c(\mc U_{n+1},r_{\mc U_{n+1}}(x))\subseteq c(\mc U_{n+1},n+1)$.\pause
          \item For some $n \leq N$, 
            \[
              n+1 \leq r_{\mc U_n}(x)< N+1 < r_{\mc U_{n+1}}(x)
            \]
           and thus $x\in p(\mc U_n,\mc U_{n+1})$\qed
         \end{itemize}
      \end{itemize}\pause

  \begin{corollary}
    $X$ \scish~ $\Rightarrow$ $X$ Menger
  \end{corollary}\pause

  \begin{question}
    $\pl F \kmarkwin{2} \mengame{X} \Rightarrow X$ \scish? (Or can I slightly adjust the definition to get this result?)
  \end{question}
\end{frame}

\begin{frame}

  \begin{theorem}
    If $S(\kappa,\omega,\omega)$, then $\oneptlind{\kappa}$ is \scish.
  \end{theorem}\pause

  \textbf{Proof:}
    Take the injective funcions $f_A:A\to\omega$ witnessing $S(\kappa,\omega,\omega)$. For each cover $\mc V$ of $\oneptlind{\kappa}$ let $A(\mc V)$ define a set such that $\oneptlind{\kappa}\setminus A(\mc V)$ is in a refinement of $\mc V$. \pause

    Then $r_{\mc V}$ defined by 
      \[
        r_{\mc V}(x) = \left\{
      \begin{array}{ll}
        0 & x\in\oneptlind{\kappa}\setminus A(\mc V) \\
        f_{A(\mc V)}(x)+1 & x\in A(\mc V)
      \end{array}
      \right.
      \]

    witnesses the property as $c(\mc V,0)$ is contained in a single open set in $\mc V$, $c(\mc V,n+1)$ is a singleton or empty set, and
      \[
        p(\mc U,\mc V) = \{\alpha\in A(\mc U)\cap A(\mc V) : f_{A(\mc U)}(\alpha)<f_{A(\mc V)}(\alpha)\}
      \]
    is finite.\qed
\end{frame}

\subsection{Consistency of $S(\kappa,\omega,\omega)$}

\begin{frame}
  \begin{corollary}
    If $S(\kappa,\omega,\omega)$, then $\pl F\kmarkwin{2}\mengame{\oneptlind{\kappa}}$
  \end{corollary}
  This result becomes more interesting if we can show $S(\kappa,\omega,\omega)$ is consistent for $\kappa>\omega_1$.\pause

  \begin{definition}
    A finite partial function $p$ from $A$ to $B$ has a domain which is a finite subset of $A$ and a range which is a finite subset of $B$. Let the set of all finite partial functions from $A$ to $B$ be denoted by $Fn(A,B)$.
  \end{definition}\pause
  \begin{definition}
    Let $Fn^2(\mc A,B)\subset Fn(\mc A,Fn(\bigcup \mc A,B))$ such that for each $p\in Fn^2(\mc A,B)$, $p(A)=p_A\in Fn(A,B)$.
  \end{definition}
\end{frame}

\begin{frame}
  \begin{definition}
    For $\kappa>\omega_1$, let $\pok\subset Fn^2([\kappa]^\omega,\omega)$ be such that each $p_A$ is injective, and give it the partial order $\leq$ defined by $q\leq p$ if and only if:
          \begin{itemize}
            \item $\dom(q)\supseteq\dom(p)$
            \item For each $A\in\dom(p)$, $q_A\supseteq p_A$
            \item For each $A,B\in\dom(p)$, if $p_A$ and $p_B$ are not defined for some $\alpha\in A\cap B$, but $q_A$ is, then $q_B$ is also defined for $\alpha$ and $q_A(\alpha)=q_B(x)$. That is, for $\alpha\in A\cap B$
              \[
                \alpha\in \dom(q_A)\setminus(\dom(p_A)\cup\dom(p_B))
              \]
              \[
                \Downarrow
              \]
              \[
                \alpha\in\dom(q_B) \text{ and } q_A(x)=q_B(x)
              \]
          \end{itemize}
  \end{definition}
\end{frame}

\begin{frame}
  \begin{lemma}
    $\pok$ has property $K$ (and thus is c.c.c.). That is, let $P\subseteq\pok$ be uncountable: there is an uncountable $Q\subseteq P$ such that points in $Q$ are pairwise compatible.
  \end{lemma}\pause

  \textbf{Proof:}
    If $|\{\dom(p):p\in P\}|>\omega$, we will use the $\Delta$-system lemma to find an uncountable $P'\subseteq P$ such that for $p,q\in P'$, $\dom(p)\cap\dom(q)=\mc R$. Otherwise, we may fix an uncountable $P'\subseteq P$ such that for $p,q\in P'$, $\dom(p)=\dom(q)=\mc R$.\pause\vspace{6pt}

    Similarly, for each $A\in\mc{R}$ we may find that $|\{\dom(p_A):p\in P'\}|>\omega$, and we can use the $\Delta$-system lemma to find an uncountable $P''\subseteq P'$ where $\dom(p_A)\cap\dom(q_A)=A'$ for all $p,q\in P''$, or otherwise we may find $P''\subseteq P'$ where $\dom(p_A)=\dom(q_A)=A'$ for all $p,q\in P''$.
\end{frame}
\begin{frame}
    Finally, for each $A\in\mc R$ and $\alpha\in A'$, we may find $n_{A,\alpha}$ such that there are uncountable $p\in P''$ with $p_A(\alpha)=n_{A,\alpha}$, and thus we may choose $Q\subseteq P''$ to be an uncountable collection such that for $p,q\in Q$, $p_A=q_A$ for $A\in\mc R$.\pause\vspace{6pt}

    Then it is easily verified that $p\cup q\in\pok$ and $p\cup q\leq p,q$ for all $p,q\in Q$.\qed\pause\vspace{12pt}

    Since $\pok$ is c.c.c.:

    \begin{corollary}
      Any forcing using a $\pok$-generic filter preserves cardinals and cofinalities.
    \end{corollary}

    \begin{corollary}
      If $cf(\kappa)>\omega$, any forcing using a $\pok$-generic filter results in $2^\omega\leq\kappa$.
    \end{corollary}
\end{frame}

\begin{frame}
  \begin{proposition}
    For $A\in[\kappa]^\omega$ and $\alpha\in A$, the sets 
      \[
        D_A = \{p\in\pok: A\in\dom(p)\}
      \]
      \[
        D_{A,\alpha} = \{p\in\pok: A\in\dom(p), \alpha\in\dom(p_A)\}
      \]
    are dense in $\pok$.
  \end{proposition}

  \begin{theorem}
    If $cf(\kappa)>\omega$, $S(\kappa,\omega,\omega)+(\kappa=2^\omega)$ is consistent with $ZFC$.
  \end{theorem}\pause

  \textbf{Proof:}
    We adapt a forcing argument due to Scheepers (which used a slightly different poset). Let $M$ be a countable transitive submodel of ZFC. Consider the c.c.c. poset $\pok$ realized in the model $M$. Let $G$ be a $\pok$-generic filter over $M$.
\end{frame}
\begin{frame}
    We now work in the smallest model $M[G]$ extending $M$ and containing $G$.\vspace{6pt}

    For each $A\in [\kappa]^\omega$, note $[\kappa]^\omega\cap M$ is cofinal in $[\kappa]^\omega$, so let $A'\supseteq A$ be in $[\kappa]^\omega\cap M$ and let $f_A=\bigcup_{p\in G\cap D_{A'}}p_{A'}\rest A$. Since $G$ is a $\pok$-generic filter over $M$, it is easily verified (considering the dense sets $D_{A,\alpha}$) that $f_A$ is an injective function from $A$ into $\omega$.\pause\vspace{6pt}

    In addition, for $A,B\in [\kappa]^\omega\cap M$, let $p\in G\cap D_A\cap D_B$. For all $q\leq p$ it follows that 
      \[
        \{\alpha\in \dom(q_A)\cap \dom(q_B): q_A(\alpha)\not= q_B(\alpha)\} \subseteq \dom(p_A)\cup\dom(p_B)
      \] 
    Thus $|\{\alpha\in A\cap B: f_A(\alpha)\not= f_B(\alpha)\}|<\omega$ and $f_A\alcomp f_B$ for $A,B\in [\kappa]^\omega\cap M$, and it's immediate that $f_A\alcomp f_B$ for $A,B\in[\kappa]^\omega$ as well.\pause\vspace{6pt}

    The $f_A$ witness $S(\kappa,\omega,\omega)$. Since $\kappa\geq 2^\omega$ and $S(\kappa,\omega,\omega)$ is a contradiction for $\kappa>2^\omega$, we know $\kappa=2^\omega$. \qed
\end{frame}

\begin{frame}
  \begin{corollary}
    For all $\kappa$, $\pl F\kmarkwin{2}\mengame{\oneptlind{\kappa}}$ is consistent with $ZFC$.
  \end{corollary}

  \begin{question}
    Is $\pl F\kmarkwin{2}\mengame{\oneptlind{\omega_2}}$ a theorem of ZFC?
  \end{question}
\end{frame}

\end{document}

### 2013-11-24 phd/archive/LF_KP on various spaces.tex
housecleaning, added proximal game results

\documentclass[11pt]{article}

\pdfpagewidth 8.5in
\pdfpageheight 11in

\setlength\topmargin{0in}
\setlength\headheight{0in}
\setlength\headsep{0.2in}
\setlength\textheight{8in}
\setlength\textwidth{6in}
\setlength\oddsidemargin{0in}
\setlength\evensidemargin{0in}
\setlength\parindent{0.25in}
\setlength\parskip{0.1in}

\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{amsthm}

      \theoremstyle{plain}
      \newtheorem{theorem}{Theorem}
      \newtheorem{lemma}[theorem]{Lemma}
      \newtheorem{corollary}[theorem]{Corollary}
      \newtheorem{proposition}[theorem]{Proposition}
      \newtheorem{conjecture}[theorem]{Conjecture}
      \newtheorem{question}[theorem]{Question}
      \newtheorem{example}[theorem]{Example}

      \theoremstyle{definition}
      \newtheorem{definition}[theorem]{Definition}

      \theoremstyle{remark}
      \newtheorem{remark}[theorem]{Remark}

% Strategy uparrow shortcuts
\newcommand{\win}{\uparrow}
\newcommand{\prewin}{\uparrow_{\text{pre}}}
\newcommand{\markwin}{\uparrow_{\text{mark}}}
\newcommand{\tactwin}{\uparrow_{\text{tact}}}
\newcommand{\ktactwin}[1]{\uparrow_{#1\text{-tact}}}
\newcommand{\kmarkwin}[1]{\uparrow_{#1\text{-mark}}}
\newcommand{\codewin}{\uparrow_{\text{code}}}
\newcommand{\limitwin}{\uparrow_{\text{limit}}}

\newcommand{\oneptcomp}[1]{#1^*}

\newcommand{\congame}[2]{Con_{O,P}(#1,#2)}
\newcommand{\clusgame}[2]{Clus_{O,P}(#1,#2)}

\newcommand{\lfkpgame}[1]{LF_{K,P}(#1)}
\newcommand{\lfklgame}[1]{LF_{K,L}(#1)}

\newcommand{\pfgame}[1]{PF_{F,C}(#1)}

\newcommand{\sigmaprodr}[1]{\Sigma\mathbb{R}^{#1}}
\newcommand{\sigmaprodtwo}[1]{\Sigma2^{#1}}

\newcommand{\<}{\langle}
\renewcommand{\>}{\rangle}

\begin{document}

\begin{example}
If $\mathcal{F}$ is a free ultrafilter on $\omega$, let $L(\mathcal{F})=\omega \cup \{\mathcal{F}\}$ as a subspace of the Stone-Cech compactification $\beta\omega$ be the \textbf{single ultrafilter line}. There is some ultrafilter $\mathcal{F}$ such that $K \prewin \lfkpgame{L(\mathcal{F})}$ and $K \tactwin \lfkpgame{L(\mathcal{F})}$.

($L(\mathcal{F})$ is not compactly generated, and thus not locally compact.)
\end{example}

\begin{proof}
Let $a_n$ be a sequence such that the sequence $\frac{a_n}{n}$ is unbounded above. Then there is an ultrafilter $\mathcal{F}$ such that $\sigma(n)=(\sum_{m\leq n} a_m )\cup \{\mathcal{F}\}$ is a winning predetermined strategy for $K$ in $\lfkpgame{L(\mathcal{F})}$.

Let $\mathcal{P}$ be the collection of all legal plays by $P$ against the strategy $\sigma$. Consider a finite collection of plays $P_0,\dots,P_{n-1}\in \mathcal{P}$. As $\frac{a_m}{m}$ is unbounded above, we may find infinitely many $m$ such that $\frac{a_m}{m}>n \Rightarrow mn<a_m$. As the $a_m$ partition $\omega$ such that $P$ may only play at most $m$ points in each part, there are infinitely many parts which are not filled, and thus $\bigcup_{m<n} P_m$ is not cofinite.

It then follows that the closure of $\mathcal{P}$ under finite unions and subsets, along with all finite sets, is an ideal. Its dual filter may then be extended to an ultrafilter $\mathcal{F}$ such that every possible play by $P$ is the complement of some member of $\mathcal{F}$, making $\sigma$ a winning predetermined strategy.

A winning tactic can then be easily constructed by using the moves by $P$ as the round number in the predetermined strategy.
\end{proof}

\begin{example}
Let $T(\mathcal{F}) = 2^{\leq\omega}$ where $2^{<\omega}$ is discrete and for each $c\in 2^\omega$, $\{c \restriction \alpha : \alpha \leq \omega\}$ is homeomorphic to $L(\mathcal{F})$. This is called the \textbf{single ultrafilter tree}. There is some ultrafilter $\mathcal{F}$ such that $K \prewin \lfkpgame{L(\mathcal{F})}$ and $K \tactwin \lfkpgame{L(\mathcal{F})}$.

($T(\mathcal{F})$ is not compactly generated, and thus not locally compact.)
\end{example}

\begin{proof}
Assume without loss of generality that $P$ does not play points in $2^\omega$.

We use a winning predetermined strategy $\sigma^*(n)$ for $L(\mathcal{F})$ and let $\sigma(n) = \bigcup_{m \in \sigma^*(n)} 2^m$. Note that if $P$ has a counter which converges to some $c\in \,^\omega2$, then $P$ would have a counter within a single branch. Since each branch is homeomorphic to $L(\mathcal{F})$; this is impossible.

A winning tactic can then be easily constructed by using the moves by $P$, taking the level of the tree played upon as the round number in the predetermined strategy.
\end{proof}

\begin{example}
Let $M = \omega^2 \cup \{\infty\}$ be the \textbf{metric fan} where $\omega^2$ is discrete and $\infty$ has neighborhoods of the form $M \setminus (n\times\omega)$ for any $n<\omega$. Then $K \not\win \lfkpgame{M}$. (In fact, $P \markwin \lfkpgame{M}$.)

($M$ is not locally compact, but is compactly generated.)
\end{example}

\begin{proof}
For each compact set $C$ in $M$, there exists a minimal dominating function $f_C$ such that for each $(x,y)\in C\setminus\{\infty\}$, $f(x)> y$.

So let $P$ respond to the move $C\in K[X]$ by $K$ on round $n$ with the point $p=(n,s_C)$ such that $s_C = \min(\{y<\omega : f_C(n) < y\}$. It is easy to see that $p_n\rightarrow \infty$, so $P$ has a winning Markov strategy.
\end{proof}

\begin{example}
Let $S = \omega^2 \cup \{\infty\}$ be the \textbf{sequential fan} where $\omega^2$ is discrete and $\infty$ has neighborhoods of the form $M \setminus \{(x,y) : x<f(y)\}$ for any $f:\omega\to\omega$. Then $K \prewin \lfkpgame{S}$ and $K\tactwin \lfkpgame{S}$.

($S$ is not locally compact, but is compactly generated.)

\end{example}

\begin{proof}
Let $\sigma(n)=\omega\times(n+1) \cup \{\infty\}$. By defining $f(y)$ to be greater than the $x$-coordinate of all $P$'s plays through round $y$, we see that $M\setminus\{(x,y): x<f(y)\}$ misses every move by $P$, so $P$ cannot converge to $\infty$.

A winning tactic can be easily constructed by using the $y$-coordinate of $P$'s moves as the round number in the predetermined strategy.
\end{proof}

\end{document}

### 2013-11-24 phd/menger.tex
Minor tweaks to asrc implies 2-mark proof
housecleaning, added proximal game results

@@
             \[
-              n+1< r_{\mc U_{n+1}}(x)\leq N+1
-            \] 
-            and thus $x\in c(\mc U_{N+1},r_{\mc U_{n+1}}(x))=c(\mc U_{N+1},N+1)$.
+              r_{\mc U_{n+1}}(x)\leq N+1
+            \] 
+            and thus $x\in c(\mc U_{N+1},N+1)$.
           \item For some $n \leq N$, 
             \[
-              r_{\mc U_{n+1}}(x)< n+1 \leq r_{\mc U_n}(x)< N+1
-            \]
-            and thus $x\in c(\mc U_{n+1},r_{\mc U_{n+1}}(x))\subseteq c(\mc U_{n+1},n+1)$.
-          \item For some $n \leq N$, 
-            \[
-              n+1 \leq r_{\mc U_n}(x)< N+1 < r_{\mc U_{n+1}}(x)
+              r_{\mc U_n}(x)\leq N+1 < r_{\mc U_{n+1}}(x)
             \]
@@
   \end{corollary}
+
+  \begin{definition}
+    A space suggested by G: Give $\kappa^\sharp=(\kappa\times\oneptlind\kappa)\cup\{\infty\}$ the topology where $\{\alpha\}\times\kappa^\sharp$ is an open copy of $\oneptlind{\kappa}$, and neighborhoods of $\infty$ contain a set of the form $\kappa^\sharp\setminus(A\times\oneptlind\kappa)$ for some $A\in[\kappa]^\omega$.
+  \end{definition}
+
+  \begin{theorem}
+    $F\kmarkwin{2}\mengame{\omega_1^\sharp}$
+  \end{theorem}
+
+  \begin{proof}
+    Let $f_\alpha:\alpha\to\omega$ witness $S(\omega_1,\omega,\omega)$ for limit ordinals $\alpha<\omega_1$.
+Also note that there is a bijection $e:\omega_1\to[\omega_1]^{<\omega}$ such that $e\rest\alpha:\alpha\to[\alpha]^{<\omega}$ is also a bijection for each limit ordinal $\alpha<\omega_1$.
+
+    We define the finite set $F(\alpha_n,\alpha_{n+1},n+1)$ to contain $e(\beta)$ for each $\beta<\alpha_n\cap\alpha_{n+1}$ such that either $f_{\alpha_{n+1}}(\beta)\leq n$ or $f_{\alpha_{n}}(\beta)\not=f_{\alpha_{n+1}}(\beta)$.
+
+    If $\alpha_n<\omega_1$ for all $n<\omega$ with $\alpha=\min\{\alpha_{n+1}:n<\omega\}$ and $G\in[\alpha]^{<\omega}$, note that for each $\beta<\alpha$, either $f_{\alpha_n}(\beta)=N$ always, or $f_{\alpha_n}(\beta)\not=f_{\alpha_{n+1}}(\beta)$ for some $n$.
+Either way, $e(\beta)\subseteq F(\alpha_n,\alpha_{n+1},n+1)$ for some $n$, and thus every finite subset of $\alpha$ is contained in some $F(\alpha_n,\alpha_{n+1},n+1)$.
+
+    If we let $R(\alpha)=\omega_1^\sharp\setminus(A\times\oneptlind\omega_1)$ and $U(\gamma,\alpha)=\{\gamma\}\times(\oneptlind\omega_1\setminus\alpha)$, then any open cover of $\omega_1^\sharp$ may be refined to be of the form $\mc U_\alpha = \{R(\alpha)\}\cup\{U(\gamma,\alpha):\gamma<\alpha\}\cup\{\{(\gamma,\beta)\}:\gamma,\beta<\alpha\}$ for some limit $\alpha$.
+
+    Without loss of generality assume $\pl C$ plays only covers of the form $\mc U_\alpha$ for limit $\alpha$.
+Then we may define the $2$-Markov strategy $\sigma(\mc U_{\alpha_n},\mc U_{\alpha_{n+1}},n+1)$ to cover the sets:
+      \[
+        R(\alpha_{n+1})
+      \]
+      \[
+        \bigcup \{U(\gamma,\alpha_{n+1}) : \gamma \in F(\alpha_n,\alpha_{n+1},n+1) \}
+      \]
+      \[
+        \{(\gamma,\delta): \gamma,\delta\in F(\alpha_n,\alpha_{n+1},n+1)\}
+      \]
+
+    Let $\mc U_{\alpha_0},\mc U_{\alpha_1},\dots$ be an attack by $\pl C$, $\alpha=\min\{\alpha_{n+1}:n<\omega\}$ and $\alpha'=\sup\{\alpha_{n+1}:n<\omega\}$.
+Since $\infty\in R(\alpha_0)$ always, first consider $(\gamma,\infty)$ for $\gamma<\omega_1$.
+If $\gamma\geq\alpha_{n+1}$ for some $n$, then $(\gamma,\infty)\in R(\alpha_{n+1})$.
+Otherwise, $\gamma<\alpha$, but then $\gamma\in F(\alpha_n,\alpha_{n+1},n+1)$ for some $n$ and $(\gamma,\infty)\in U(\gamma,\alpha_{n+1})$.
+
+    Lastly consider $(\gamma,\delta)$ for $\gamma,\delta<\omega_1$. If $\gamma\geq\alpha_{n+1}$ for some $n$, then $(\gamma,\delta)\in R(\alpha_{n+1})$.
+
+    Otherwise, $\gamma<\alpha$.
+If $\delta\geq \alpha'$, then as $\gamma\in F(\alpha_n,\alpha_{n+1},n+1)$ for some $n$ we see $(\gamma,\delta)\in U(\gamma,\alpha_{n+1})$.
+If $\delta<\alpha$, then $\{\gamma,\delta\}\subseteq F(\alpha_n,\alpha_{n+1},n+1)$ for some $n$ and $(\gamma,\delta)$ is covered.
+The final case is when $\alpha\leq\delta<\alpha'$.
+
+    (STILL MISSING STUFF)
+
+    % If $\alpha_{n+1}=\beta$ is fixed for $n\in W\in[\omega]^\omega$, observe that $f_{\alpha_{n+1}}(\gamma)=f_\beta(\gamma)=N$ for all $n\in W$, and thus $\gamma\in F(\alpha_n,\alpha_{n+1},n+1)$ for some $n\in W\setminus N$.
+Thus $(\gamma,\delta)\in U(\gamma,\alpha)$ is covered.
+  \end{proof}
+
+  % \begin{lemma}
+  %   For each infinite cardinal $\kappa$, the sentence $S(\kappa,\omega,\omega)$ implies there exists a function $F:[\kappa]^\omega\times[\kappa]^\omega\times\omega\to [\kappa]^{<\omega}$ such that for any choice of $A_n\in[\omega]^\omega$ and $G\in[\bigcap_{m<\omega}\bigcup_{m\leq n<\omega} A_{n+1}]^{<\omega}$, there exists an $n<\omega$ with $G\subseteq F(A_n,A_{n+1},n+1)$.
+  % \end{lemma}
+
+  % \begin{proof}
+  %   Let $\Lim([\kappa]^\omega)\subseteq[\kappa]^\omega$ denote the countable subsets of $\kappa$ for which if a set contains $\alpha+n$, then it contains $\alpha+m$ for all $m<\omega$.
+
+  %   Let $e:[\kappa]^{<\omega}\to\kappa$ be a bijection such that for every $A\in\Lim([\kappa]^\omega)$, $e\rest [A]^{<\omega}:[A]^{<\omega}\to A$ is a bijection.
+
+  %   Then for $A,B\in\Lim([\kappa]^\omega)$ let $F(A,B,n+1)$ contain all $G\in[B]^{<\omega}$ satsifying $f_{B}(e(G))\leq n$, and also contain all $G\in[A\cap B]^{<\omega}$ satisfying $f_{A}(e(G))\not= f_{B}(e(G))$.
+
+  %   Fix arbitrary $A_n\in[\omega]^\omega$ and $G\in[\bigcap_{m<\omega}\bigcup_{m\leq n<\omega} A_{n+1}]^{<\omega}$.
+  % \end{proof}
+
+  % \begin{theorem}
+  %   $F\kmarkwin{2}\mengame{\omega_1^\sharp}$
+  % \end{theorem}
+
+  % \begin{proof}
+  %   Let $f_A$ witness $S(\kappa,\omega,\omega)$ for each $A<[\kappa]^{\omega}$.
+
+  %   Let $R(A)=\kappa^\sharp\setminus(A\times\oneptlind\kappa)$.
+Let $U(\gamma,A)=\{\gamma\}\times(\oneptlind{\kappa}\setminus A)$.
+Then note that every open cover has a pairwise disjoint open refinement of the form
+  %     \[
+  %       \mc U_A = 
+  %       \{R(A)\}\cup\{U(\gamma,A):\gamma\in A\}\cup\{\{(\gamma,\beta)\}:\gamma,\beta\in A\}
+  %     \]
+  %   Assume without loss of generality that all covers are of the form $\mc U_A$.
+
+  %   % Rough idea: Let $\mc U_\alpha$ cover...
+
+  %   % Let $\sigma(\mc U,\mc V,n+1)$ be a $2$-mark.
+
+  %   % Let $F(\alpha_n,\alpha_{n+1},n+1) = \{\alpha<\alpha_n\cap\alpha_{n+1}:\sigma(\mc U_{\alpha_n},\mc U_{\alpha_{n+1}},n+1)$ covers $(\alpha,\beta)$ or $(\beta,\alpha)$ for some $\beta\}$.
+
+  %   % Claim: It is not true that for all $\alpha,\beta<\alpha_0<\alpha_1<\dots$ there exists $n<\omega$ with $\alpha,\beta\in F(\alpha_n,\alpha_{n+1},n+1)$.
+
+  %   % If so, then choose $\alpha,\beta<\alpha_0<\alpha_1<\dots$ such that $\alpha,\beta\not\in\bigcap_{n<\omega}F(\alpha_n,\alpha_{n+1},n+1)$.
+Then $\sigma$ covers neither $(\alpha,\beta)$ or $(\beta,\alpha)$ in response to the attack $\mc U_{\alpha_0},\mc U_{\alpha_1},\dots$
+  % \end{proof}
+
+\newpage
+
+  \centerline{Alster, Hurewicz}
+
+  Besides various limited information characterizations of $\mengame{X}$, there are other interesting covering properties between $\sigma$-(relatively compact) and Menger.
+
+  \begin{definition}
+    A colleciton of subsets of a space $X$ is (\textbf{really}) \textbf{ample} if has a finite subcover for each (relatively) compact subset of $X$.
+  \end{definition}
+
+  \begin{proposition}
+    Every ample cover of a regular space $X$ is really ample.
+  \end{proposition}
+
+  \begin{proof}
+    Every relatively compact set $R$ is a subset of the compact set $\overline{R}$.
+  \end{proof}
+
+  \begin{definition}
+    A space $X$ is (\textbf{relatively}) \textbf{Alster} if there exists a countable subcover for each (really) ample cover of $X$ by $G_\delta$ sets.
+  \end{definition}
+
+  \begin{proposition}
+    Every regular relatively Alster space is Alster.
+  \end{proposition}
+
+  \begin{theorem}
+    $X$ $\sigma$-compact $\Rightarrow$ $X$ Alster $\Rightarrow$ $X$ Menger
+  \end{theorem}
+
+  \begin{proof}
+    Due to Leandro F. Aurichi and Franklin D. Tall in ``Lindel\"of spaces which are indestructible, productive, or D''.
+  \end{proof}
+
+  \begin{proposition}
+    $X$ $\sigma$-(relatively compact) $\Rightarrow$ $X$ relatively Alster $\Rightarrow$ $X$ Menger
+  \end{proposition}
+
+  \begin{proof}
+    If $X$ is $\sigma$-(relatively compact), then there exists a countable subcover for every really ample cover of $X$ by arbitrary sets.
+
+    If $X$ is relatively Alster, we adapt Aurichi and Tall's argument for the previous theorem.
+
+    Since relatively Alster implies Lindel\"of (all open covers of $X$ are relatively ample by definition of relatively compact), it is sufficient to consider open covers $\mc U_n = \{ U_n^m : m<\omega\}$ such that $U_n^m\subseteq U_n^{m+1}$.
+Then $\mc G=\{\bigcap_{n<\omega} U_n^{f(n)} : f\in \omega^\omega\}$ is a $G_\delta$ cover.
+To see that $\mc G$ is relatively ample, note for each relatively compact $K$ in $X$, $K$ is covered by something in each $\mc U_n$, and thus there is $f_K(n)\in\omega^\omega$ such that $K\subseteq \bigcap_{n<\omega} U_n^{f_K(n)}$.
+
+    By relatively Alster, let $f_m\in\omega^\omega$ for $m<\omega$ so that $\mc G'=\{\bigcap_{n<\omega} U_n^{f_m(n)}:m<\omega\}$ covers $X$.
+
+    Then let $\mc F_n = \{U_n^{f_m(n)}:m\leq n\}\in[\mc U_n]^{<\omega}$.
+Note that if $x\in X$, then $x\in \bigcap_{n<\omega} U_n^{f_{m_x}(n)}$ for some $m_x<\omega$ as $\mc G'$ is a cover.
+Thus $x\in U_{m_x}^{f_{m_x}(m_x)}$ and is covered by $\mc F_{m_x}$.
+  \end{proof}
+
+  \begin{example}
+    Let the real numbers $R$ be given the topology generated by open intervals with countable sets removed.
+$R$ is not relatively Alster and $F\win\mengame{R}$.
+If $S(2^\omega,\omega,\omega)$ holds, then $F\kmarkwin{2}\mengame{R}$.
+  \end{example}
+
+  \begin{proof}
+    Since points are $G_\delta$ and its relatively compact sets are all finite, a cover by singletons is really ample and has no countable subcover, showing $R$ is not relatively Alster.
+
+    It was proven earlier that $F\win\mengame{R}$. Assuming $S(2^\omega,\omega,\omega)$, we construct a $2$-Mark\"ov strategy by first defining the following:
+      \begin{itemize}
+        \item Let $z_n$ enumerate the integers for $n<\omega$.
+        \item For each open cover $\mc V$ of $R$, let $A(\mc V)$ be a countable set such that $[z_n,z_n+1)\setminus A(V)$ is $\mc V$-compact for each $n<\omega$.
+        \item Let $f_A:A\to\omega$ for $A\subseteq R$ witness $S(2^\omega,\omega,\omega)$.
+      \end{itemize}
+
+    Then we may define $\sigma(\mc U_0,0)=\emptyset$ and define $\sigma(\mc U_n,\mc U_{n+1},n+1)$ such that it covers each of the following:
+      \[
+        \left(\bigcup_{m\leq n} [z_m,z_m+1)\right) \setminus A(\mc U_{n+1})
+      \]
+      \[
+        \{f_{A(\mc U_{n+1})}^{-1}(m) : m\leq n\}
+      \]
+      \[
+        \{x \in A(\mc U_n)\cap A(\mc U_{n+1}) : f_{A(\mc U_{n})}(x)\not= f_{A(\mc U_{n+1})}(x)\}
+      \]
+
+    For any attack $\mc U_0,\mc U_1,\dots$ on $\sigma$, let $x\in[z_n,z_n+1)$. 
+      \begin{itemize}
+        \item If $x\not\in A(\mc U_{n+1})$, then $x$ is covered in round $n+1$.
+        \item If $x\in A(\mc U_{n+1})$, let $N=f_{A(\mc U_{n+1})}(x)$. 
+        \begin{itemize}
+          \item If $N\leq n$, then $x$ is covered in round $n+1$.
+          \item If $N>n$ and $N=f_{A(\mc U_{p+1})}(x)$ for all $p\geq n$, then $x$ is covered in round $N$.
+          \item If $N>n$ and $N\not=f_{A(\mc U_{p+1})}(x)$ for some $p>n$, then $x$ is covered in round $p+1$.
+        \end{itemize}
+      \end{itemize}
+  \end{proof}
+
+  \begin{definition}
+    A space $X$ is \textbf{Hurewicz} if for each sequence of open covers $\mc U_n$, there are $\mc F_n \in [\mc U_n]^{<\omega}$ such that $X=\bigcup_{m<\omega}\bigcap_{m\leq n<\omega}\cup\mc F_n$.
+  \end{definition}
+
+  % Probably no good.
+  % \begin{definition}
+  %   A $\gamma$-cover $\mc U$ of $X$ is a countable cover such that each $x\in X$ is contained in all but finite members of $\mc U$.
+
+  %   A $\gamma_\infty$-cover is an infinite $\gamma$-cover. 
+  % \end{definition}
+
+  % \begin{definition}
+  %   A space $X$ is \textbf{Hurewicz} if and only if for each sequence $\mc U_n$ of $\gamma_\infty$-covers, there are $\mc F_n\in[\mc U_n]^{<\omega}$ such that either $\bigcup_{n<\omega} \mc F_n$ is a $\gamma_\infty$-cover, or $\mc F_N$ is a cover for some $N$.
+  % \end{definition}
+
+  % \begin{proposition}
+  %   A space $X$ is Hurewicz if and only if for each sequence $\mc U_n$ of $\gamma$-covers, there are $\mc F_n\in[\mc U_n]^{<\omega}$ such that $\bigcup_{n<\omega} \mc F_n$ is a $\gamma$-cover.
+  % \end{proposition}
+
+  % \begin{proof}
+  %   Suppose $X$ is Hurewicz. For each sequence $\mc U_n$ of $\gamma$-covers, either:
+  %     \begin{itemize}
+  %       \item Each $\mc U_n$ is a $\gamma_\infty$-cover as well.
+Apply Hurewicz to find $\mc F_n$ such that either $\bigcup_{n<\omega} \mc F_n$ is a $\gamma_\infty$-cover (and thus a $\gamma$-cover) or else $\mc F_N$ is a cover for some $N$, so letting $\mc F_n'=\emptyset$ for $n\not=N$ and $\mc F_N'=\mc F_N$ yields the $\gamma$-cover $\bigcup_{n<\omega} \mc F_n'=\mc F_n$.
+  %       \item Some $U_N$ is not a $\gamma_\infty$-cover as it is finite.
+Let $\mc F_n'=\emptyset$ for $n\not=N$ and $\mc F_N=\mc U_N$ to yield the $\gamma$-cover $\bigcup_{n<\omega} \mc F_n=\mc U_n$.
+  %     \end{itemize}
+
+  %   Suppose for each sequence $\mc U_n$ of $\gamma$-covers, there are $\mc F_n\in[\mc U_n]^{<\omega}$ such that $\bigcup_{n<\omega} \mc F_n$ is a $\gamma$-cover.
+Then for each sequence $\mc U_n$ of $\gamma_\infty$-covers, let $\mc F_n\in[\mc U_n]^{<\omega}$ such that $\bigcup_{n<\omega} \mc F_n$ is a $\gamma$-cover.
+We are now done, unless $\bigcup_{n<\omega} \mc F_n$ is finite.
+  % \end{proof}
 
@@
         \item $S\kmarkwin{k}\rothgame{X}$ for some $k\geq 1$
+        \item $P\kmarkwin{k}\altrothgame{X}$ for some $k\geq 1$
         \item $S\markwin\rothgame{X}$

### 2013-11-24 todo.tex
added alg top result, working on meager-nwd game
Updated filling results and todos
Updated todos
Added forcing argument
housecleaning, added proximal game results

@@
   \begin{itemize}
-    \item Menger-related properties and games results
+    \item Menger/Rothberger properties and games results
       \begin{itemize}
         \item Is there a slick characterization of $F\kmarkwin{2}\mengame{X}$ for regular/general spaces?
-        \item Is $F\uparrow_{?}\mengame{X}$ or $F\uparrow_{?}\rothgame{X}$ a hereditary property under closed subsets for any type of limited information? (The Menger property is. Is Rothberger?)
+        \item Is $F\uparrow_{?}\mengame{X}$ or $F\uparrow_{?}\rothgame{X}$ a hereditary property under closed subsets for any type of limited information? (The Menger property is; is Rothberger?)
+        \item Investigate Markov strategies for $S$ in $\rothgame{X}$ or $P$ in $\altrothgame{X}$.
+        \item $S\kmarkwin{2}\rothgame{X}\Leftrightarrow S\kmarkwin{k}\rothgame{X}$?
+        \item $S\kmarkwin{2}\rothgame{\oneptcomp{\omega_1}}$ or $S\kmarkwin{2}\rothgame{\oneptlind{\omega_1}}$?
+        \item $F\kmarkwin{k}\kfillgame{\kappa} \Rightarrow F\kmarkwin{k}\mengame{\oneptlind{\kappa}}$?
+        \item Would Lindelof scattered spaces have a $2$-Markov strategy in the Menger game?
+      \end{itemize}
+    \item Filling games
+      \begin{itemize}
+        \item Show/disprove $F\ktactwin{3}\sfillgame{J}$ implies $F\kmarkwin{3}\fillgame{J}$.
+        \item Show/disprove $F\kmarkwin{2}\mengame{\oneptlind{\kappa}}$ implies $F\kmarkwin{2}\kfillgame{\kappa}$.
       \end{itemize}
@@
       \end{itemize}
+    \item Proximity Game
+      \begin{itemize}
+        \item Read paper by Bell
+        \item Investigate k-tacts and k-Mark for one-point compactifications
+      \end{itemize}
   \end{itemize}

### 2013-12-18 articles/proximity-corson/proximity-corson.tex
begin writing article on proximal compacts

\documentclass{amsart}

\newtheorem{thm}{Theorem}[section]
\newtheorem{prop}[thm]{Proposition}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{cor}[thm]{Corollary}

\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition}
\newtheorem{ex}[thm]{Example}

\theoremstyle{remark}

\newtheorem{remark}[thm]{Remark}

\newcommand{\oneptcomp}[1]{{#1}^*}

\newcommand{\mc}{\mathcal}

\newcommand{\<}{\langle}
\renewcommand{\>}{\rangle}

\renewcommand{\int}[1]{\text{int}(#1)}
\newcommand{\cl}[1]{\overline{#1}}

\begin{document}

\title{Equivalency of Proximal Compact and Corson Compact in Uniform Spaces}

\author{Gary Gruenhage}
\address{Department of Mathematics, Auburn University, 
Auburn, AL 36830}
\email{gruengf@auburn.edu}
\urladdr{www.auburn.edu/$\sim$gruengf}

\author{Steven Clontz}
\address{Department of Mathematics, Auburn University, 
Auburn, AL 36830}
\email{steven.clontz@auburn.edu}
\urladdr{www.stevenclontz.com}

\begin{abstract}
A common generalization of metric spaces is the idea of a uniform space, determined by a uniformity of entourages on the diagonal of the square. Proximal uniform spaces are those for which the first player has a winning strategy in this $\omega$-length game due to Bell: the first player chooses an entourage of the space, and her opponent chooses a point close to the point chosen in the previous round, with respect to the entourage chosen in the previous round. As proximal spaces are preserved under $\Sigma$-products, Nyikos has observed that every Corson compact space, a compact space embeddable in the $\Sigma$-product of real lines, must then be proximal. He asked if that implication may also be reversed. We answer his question postively, by way of defining a stronger version of the proximal game which is perfect-information equivalent to Bell's original game for uniformly locally compact spaces.
\end{abstract}

\maketitle

Jocelyn Bell introduced the concept of proximal spaces in her doctoral dissertation while working on the so-called uniform box product problems, due to her advisor Scott Williams: is the uniform box product of compact spaces normal, collectionwise normal, or paracompact? Proximal spaces, such as the one-point compactification $\oneptcomp\omega_1=\omega_1\cup\{\infty\}$ of the discrete space of cardinality $\omega_1$, are defined to be the spaces for which the first player in the proximal game played on that space has a winning strategy. Bell has shown that proximal spaces have strong preservation properties, particularly, the $\Sigma$-product of proximal spaces is itself proximal \cite{b}. This mirrors the analogous theorem for metric spaces; in fact, every metric space is easily seen to be proximal.

In \cite{n}, Peter Nyikos observed that compact subspaces of the $\Sigma$-product of real lines, known as Corson compacts, must be proximal, since the proximal property is preserved under $\Sigma$-products. He left open the question as to whether any proximal compact must then be Corson compact. Using a characterization of Corson compact due to Gruenhage in \cite{g}, we can answer that question in the affirmative.

\section{Definitions and Properites of Uniform Spaces}

In this paper, all spaces are assumed to be topological spaces induced by a uniformity. We relate some definitions and properties of uniform spaces.

\begin{defn}
  A \textbf{uniform space} is a pair $\<X,\mc{D}\>$ where $X$ is a set, and $\mc{D}$ is a \textbf{uniformity}. A uniformity is a filter on subsets of $X^2$, called \textbf{entourages}, such that for each entourage $D\in \mc D$:
  \begin{itemize}
      \item $D$ is reflexive, i.e., the diagonal $\Delta=\{\<x,x\>:x\in X\}\subseteq D$.
      \item Its inverse $D^{-1}=\{\<y,x\>:\<x,y\>\in D\}\in \mc D$.
      \item There exists $\frac{1}{2}D\in\mc D$ such that 
        \[
          2\left(\frac{1}{2}D\right)=\frac{1}{2}D\circ \frac{1}{2}D=\left\{\<x,z\>:\exists y\left(\<x,y\>,\<y,z\>\in \frac{1}{2}D\right)\right\}\subseteq D
        \]
      (Let $\frac{1}{2^{n+1}}D$ be shorthand for $\frac{1}{2}(\frac{1}{2^{n}}D)$. Without loss of generality, assume that $\frac{1}{2}D$ is always symmetric, that is, $\<x,y\>\in \frac{1}{2} D\Leftrightarrow \<y,x\>\in\frac{1}{2}D$.)
    \end{itemize}
\end{defn}

\begin{defn}
  The \textbf{uniform topology} induced by a uniformity declares a set $U$ to be open if for every $x\in U$, there is some $D\in\mc D$ with $x\in D[x]=\{y: \<x,y\>\in D\}\subseteq U$.
\end{defn}

\begin{thm}
  Every completely regular topology may be induced by a uniformity, and every uniform topology is completely regular.
\end{thm}

\begin{thm}
  For every entourage $D$, there is an open symmetric entourage $E\subseteq D$. That is, $\<x,y\>\in E \Leftrightarrow \<y,x\> \in E$, and $E$ is open in $X^2$ with the usual product topology induced by the uniform topology on $X$.
\end{thm}

\begin{prop}
  If $D$ is an open entourage, then for all $x\in X$, $D[x]$ is an open neighborhood of $x$.
\end{prop}

\begin{proof}
  For the proofs of these, see \cite{e}.
\end{proof}

\begin{prop}
  If $X$ is a uniform space, then for all $x\in X$ and open symmetric entourages $D$:
    \[
      \frac{1}{2}D[x]\subseteq \cl{\frac{1}{2}D[x]}\subseteq D[x]
    \]
\end{prop}

\begin{thebibliography}{99}
\bibitem{b}
  Bell, Jocelyn.
  \emph{An Infinite Game with Topological Consequences}.
  etc.
\bibitem{e}
  Engelking, Ryszard.
  \emph{General Topology}.
  etc.
\bibitem{g}
  Gruenhage, Gary.
  \emph{Covering properties on $X^2\setminus\Delta$, $W$-sets, and compact subsets of $\Sigma$-products}. 
  Topology Appl. 17 (1984), no. 3, 287–304. 
\bibitem{n}
  Nyikos, Peter.
  \emph{Proximal and Semi-Proximal Spaces}.
  etc.
\end{thebibliography}

\end{document}

### 2013-12-19 articles/proximity-corson/proximity-corson.tex
first draft finished

@@
 \documentclass{amsart}
+\usepackage{amssymb}
 
@@
 \newtheorem{ex}[thm]{Example}
+\newtheorem{ques}[thm]{Question}
 
@@
 \newcommand{\cl}[1]{\overline{#1}}
+
+\newcommand{\proxgame}[1]{Prox_{D,P}(#1)}
+\newcommand{\sproxgame}[1]{sProx_{D,P}(#1)}
+\newcommand{\congame}[2]{Con_{O,P}(#1,#2)}
+\newcommand{\clusgame}[2]{Clus_{O,P}(#1,#2)}
+
+\usepackage{mathrsfs}
+\newcommand{\pl}[1]{\mathscr{#1}}
+
+\newcommand{\win}{\uparrow}
+\newcommand{\markwin}{\win_{\textrm{mark}}}
+
+\newcommand{\rest}{\restriction}
+\newcommand{\concat}{^\frown}
 
@@
 
-Jocelyn Bell introduced the concept of proximal spaces in her doctoral dissertation while working on the so-called uniform box product problems, due to her advisor Scott Williams: is the uniform box product of compact spaces normal, collectionwise normal, or paracompact?
-Proximal spaces, such as the one-point compactification $\oneptcomp\omega_1=\omega_1\cup\{\infty\}$ of the discrete space of cardinality $\omega_1$, are defined to be the spaces for which the first player in the proximal game played on that space has a winning strategy.
+Jocelyn Bell introduced the concept of proximal spaces in her doctoral dissertation while working on the following uniform box product problems due to her advisor Scott Williams: is the uniform box product of compact spaces normal, collectionwise normal, or paracompact?
+Proximal spaces are defined to be the spaces for which the first player in the proximal game played on that space has a winning strategy.
 Bell has shown that proximal spaces have strong preservation properties, particularly, the $\Sigma$-product of proximal spaces is itself proximal \cite{b}.
@@
 
-In \cite{n}, Peter Nyikos observed that compact subspaces of the $\Sigma$-product of real lines, known as Corson compacts, must be proximal, since the proximal property is preserved under $\Sigma$-products.
+In \cite{nproximal}, Peter Nyikos observed that compact subspaces of the $\Sigma$-product of real lines, known as Corson compacts, must be proximal, since the proximal property is preserved under $\Sigma$-products.
 He left open the question as to whether any proximal compact must then be Corson compact.
-Using a characterization of Corson compact due to Gruenhage in \cite{g}, we can answer that question in the affirmative.
+Using a characterization of Corson compact due to Gruenhage in \cite{gcovering}, we can answer that question in the affirmative.
 
@@
         \]
-      (Let $\frac{1}{2^{n+1}}D$ be shorthand for $\frac{1}{2}(\frac{1}{2^{n}}D)$.
-Without loss of generality, assume that $\frac{1}{2}D$ is always symmetric, that is, $\<x,y\>\in \frac{1}{2} D\Leftrightarrow \<y,x\>\in\frac{1}{2}D$.)
+      (Let $\frac{1}{2^{n+1}}D$ be shorthand for $\frac{1}{2}(\frac{1}{2^{n}}D)$.)
     \end{itemize}
@@
 
+(For convenience, we assume that $\frac{1}{2}D$ is always open symmetric.)
+
 \begin{prop}
@@
 
+We quickly note a couple properites of $\frac{1}{2}D$.
+
 \begin{prop}
-  If $X$ is a uniform space, then for all $x\in X$ and open symmetric entourages $D$:
+  If $x\in \frac{1}{2}D[y]$ and $y\in \frac{1}{2}D[z]$, then $x\in D[z]$
+\end{prop}
+
+\begin{proof}
+  Directly from the definition of $\frac{1}{2}D$.
+Note that the same result holds if we assumed instead that $y\in \frac{1}{2}D[x]$ or $z\in \frac{1}{2}D[y]$, since $\frac{1}{2}D$ is assumed to be symmetric.
+\end{proof}
+
+\begin{prop}
+  If $X$ is a uniform space, then for all $x\in X$ and symmetric entourages $D$:
     \[
@@
 
+\begin{proof}
+  If $y$ is a limit point of $\frac{1}{2}D[x]$, then $\frac{1}{2}D[y]$ must intersect $\frac{1}{2}D[x]$ at some $z$. It follows then that $z\in D[x]$.
+\end{proof}
+
+\subsection{The Proximal Game}
+
+The theory of proximal uniform spaces relies on an $\omega$-length game, which proceeds as follows:
+
+\begin{defn}
+  The \textbf{proximal game} $\proxgame{X}$ of length $\omega$ played on a uniform space $X$ with two players $\pl D$, $\pl P$ proceeds as follows:
+    \begin{itemize}
+      \item In the initial round $0$, $\pl D$ chooses an open symmetric entourage $D_0$, followed by $\pl P$ choosing a point $p_0\in X$.
+      \item In round $n+1$, $\pl D$ chooses an open symmetric entourage $D_{n+1}\subseteq \frac{1}{4}D_n$, followed by $\pl P$ choosing a point $p_{n+1}\in D_n[p_n]$.
+    \end{itemize}
+  At the conclusion of the game, $\pl D$ wins if either $\bigcap_{n<\omega}D_n[p_n]=\emptyset$ or $\<p_0,p_1,\dots\>$ converges, and $\pl P$ wins otherwise.
+\end{defn}
+
+The reader familiar with proximal spaces may note that this definition is different than the original formulation of the game (see \cite{b}); however, it is easily verified that $\pl D$ has a winning strategy in the original game if and only if $\pl D$ has a winning strategy in our version.
+
+\begin{defn}
+  If a player $\pl P$ has a winning strategy in a game $G$, we write $\pl P\win G$. Otherwise, we write $\pl P\not\win G$.
+\end{defn}
+
+\begin{defn}
+  A uniform space $X$ is said to be \textbf{proximal} if and only if $\pl D\win\proxgame{X}$.
+\end{defn}
+
+\section{Proximal Games and $W$ Games}
+
+The first author introduced the following game in \cite{ginfinite}.
+
+\begin{defn}
+  The \textbf{$W$-convergence game} $\congame{X}{H}$ of length $\omega$ played on a topological space $X$ and set $H\subseteq X$ with two players $\pl O$, $\pl P$ proceeds as follows:
+    \begin{itemize}
+      \item In the initial round $0$, $\pl O$ chooses an open neighborhood $O_0$ of $H$, followed by $\pl P$ choosing a point $p_0\in O_0$.
+      \item In round $n+1$, $\pl O$ chooses an open neigborhood $O_{n+1}\subseteq O_n$ of $H$, followed by $\pl P$ choosing a point $p_{n+1}\in O_{n+1}$.
+    \end{itemize}
+  At the conclusion of the game, $\pl O$ wins if $\<p_0,p_1,\dots\>$ converges to $H$ (every open neighborhood of $H$ contains all but finitely many points of the sequence), and $\pl P$ wins otherwise.
+
+  In the case of $H=\{x\}$, we abuse notation and write $\congame{X}{x}$.
+\end{defn}
+
+\begin{defn}
+  A topological space $X$ is said to be a $W$ space if and only if for every $x\in X$, $\pl O\win \congame{X}{x}$.
+\end{defn}
+
+We find it useful to consider a (seemingly) weaker version of this game.
+
+\begin{defn}
+  The \textbf{$W$-clustering game} $\clusgame{X}{H}$ proceeds identically to $\congame{X}{H}$, except that $\pl O$ need only force $p$ to cluster at $H$ (every open neighborhood of $H$ contains infinitely many points of the sequence).
+\end{defn}
+
+\begin{thm}
+  $\pl O\win\congame{X}{H}$ if and only if $\pl O \win\clusgame{X}{H}$
+\end{thm}
+
+\begin{proof}
+  Shown for $H=\{x\}$ in \cite{ginfinite}, but the analogous proof works for arbitrary $H$.
+The forward implication is immediate.
+Let $\sigma$ be a strategy for $\pl O$ witnessing $\pl O\win \clusgame{X}{H}$.
+Note $\sigma$ is a function whose domain is all possible partial attacks by $\pl P$ (finite sequences of points in $X$), and whose range is the open neighborhoods of $H$, such that for any legal attack $p=\<p_0,p_1,\dots\>$ against $\sigma$, it follows that $p$ must cluster at $H$.
+
+  For every partial attack $a$, let $S(a)$ contain all subsequences of $a$.
+We then define $\tau(p\rest n)=\bigcap_{b\in S(p\rest n)}\sigma(b)$.
+If $p$ attacks the strategy $\tau$ for $\congame{X}{H}$, then it also is a legal attack against $\sigma$ in $\clusgame{X}{H}$, so $p$ clusters at $H$.
+
+  But not only that: let $q$ be a subsequence of $p$.
+If $q\rest n$ is a legal partial attack against $\sigma$ and $q\rest n$ is a subsequence of $p\rest m$ with $q(n)=p(m)$, then since $q(n)=p(m)\in\tau(p\rest m)\subseteq\sigma(q\rest n)$, $q\rest n+1$ is a legal partial attack against $\sigma$ as well.
+Thus $q$ is a legal attack against $\sigma$ in $\clusgame{X}{H}$, so $q$ clusters at $H$.
+
+  Since no infinite subsequence of $p$ can be completely missed by an open neighborhood of $H$, it follows that $p$ converges to $H$.
+\end{proof}
+
+\begin{thm}
+  All proximal spaces are $W$ spaces.
+\end{thm}
+
+\begin{proof}
+  Due to Bell, see \cite{b}.
+The idea of the proof is to consider the result of an attack on the winning strategy for $\pl D$ in $\proxgame{X}$ which alternates between points chosen by $\pl P$ in $\congame{X}{x}$ and the particular point $x$ itself.
+Since the intersection $\bigcap_{n<\omega} D_n[p_n]$ must contain $x$, the sequence must converge, and since the sequence contains $x$ infinitely often, it must converge to $x$.
+\end{proof}
+
+While there is not much trouble in ensuring the nonempty intersection of\\ $\bigcap_{n<\omega} D_n[p_n]$ for this particular proof, we turned to a stronger version of $\proxgame{X}$ which avoids the issue entirely.
+
+\begin{defn}
+  The \textbf{strong proximal game} $\sproxgame{X}$ proceeds identially to $\proxgame{X}$, except that $\pl D$ may only win in the case that $\<p_0,p_1,\dots\>$ converges.
+\end{defn}
+
+Certainly, if $\pl D\win \sproxgame{X}$, then $\pl D\win \proxgame{X}$, so all ``strongly proximal'' spaces are proximal. We are interested in the case that both games are equivalent for $\pl D$.
+
+\begin{defn}
+  A uniform space is uniformly locally compact if there exists an open symmetric entourage $L$ such that $\cl{L[x]}$ is a compact neighborhood of $x$ for all $x\in X$.
+\end{defn}
+
+\begin{thm}
+  A uniformly locally compact space $X$ is proximal if and only if $\pl D\win \sproxgame{X}$.
+\end{thm}
+
+\begin{proof}
+  Let $L$ be a uniformly locally compact entourage.
+Let $\sigma$ be a strategy for $\pl D$ witnessing $\pl D\win \proxgame{X}$.
+Without loss of generality, we may assume such that $\sigma(p\rest n)\subseteq L$ for all partial attacks $p\rest n$ (so $\cl{\sigma(p\rest n)[x]}\subseteq\cl{L[x]}$ is compact), since $\sigma(p\rest n)\cap L$ is itself an open symmetric entourage, and any legal attack against these refined entourages is also a legal attack against the original.
+
+  Let $\tau(p\rest n)=\frac{1}{2}\sigma(p\rest n)$. If $p$ attacks $\tau$ in $\sproxgame{X}$, then
+    \[
+      p(n+1)
+        \in
+      \tau(p\rest n)[p(n)]
+        =
+      \frac{1}{2}\sigma(p\rest n)[p(n)]
+    \]
+
+    and for
+
+    \[
+      x
+        \in
+      \cl{\sigma(p\rest (n+1))[p(n+1)]}
+        \subseteq
+      \cl{\frac{1}{4}\sigma(p\rest n)[p(n+1)]}
+        \subseteq
+      \frac{1}{2}\sigma(p\rest n)[p(n+1)]
+    \]
+
+  we can conclude $x\in\sigma(p\rest n)[p(n)]$. Thus
+
+    \[
+      \sigma(p\rest (n+1))[p(n+1)]
+        \subseteq
+      \cl{\sigma(p\rest (n+1))[p(n+1)]}
+        \subseteq
+      \sigma(p\rest n)[p(n)]
+    \]
+
+  Finally, note that since $\tau$ yields refinements of $\sigma$, then $p$ attacks the winning strategy $\sigma$ in $\proxgame{X}$, but since the intersection of a descending chain of nonempty compact sets is nonempty:
+
+    \[
+      \bigcap_{n<\omega} \sigma(p\rest n)[p(n)]
+        =
+      \bigcap_{n<\omega} \cl{\sigma(p\rest n)[p(n)]}
+        \not=
+      \emptyset
+    \]
+
+  We conclude that $p$ converges.
+\end{proof}
+
+To wrap up this section, we cite a few required results due to Bell, also from \cite{b}.
+
+\begin{thm}
+  The $\Sigma$-product of proximal spaces is proximal. In particular, if $X$ is proximal, then $X^2$ is proximal.
+\end{thm}
+
+\begin{thm}
+  Every closed subspace of a proximal space is proximal.
+\end{thm}
+
+\begin{thm}
+  Every metrizable space is proximal.
+\end{thm}
+
+\section{Corson Compacts and Proximal Compacts}
+
+We recall from \cite{gcovering} the definition of Corson compact.
+
+\begin{defn}
+  A space is said to be Corson compact if and only if it is homeomorphic to a compact set within the $\Sigma$-product $\Sigma\mathbb{R}^\kappa$ of $\kappa$-many real lines, that is:
+    \[
+      \Sigma\mathbb{R}^\kappa
+        =
+      \{x\in \mathbb{R}^\kappa: |\{\alpha:x(\alpha)\not=0\}|<\omega\}
+    \]
+\end{defn}
+
+\begin{prop}
+  Every Corson compact is proximal.
+\end{prop}
+
+\begin{proof}
+  As observed by Nyikos in \cite{nproximal}.
+Any Corson compact is a $\Sigma$-product of compact subsets of the real line.
+Since closed subsets of metrizable spaces are proximal, and the $\Sigma$-product of proximal spaces is proximal, the result follows.
+\end{proof}
+
+However, this characterization of Corson compact is less useful when proving the other direction.
+
+\begin{thm}
+  A space $X$ is Corson compact if and only if $X$ is compact and $\pl O\win\congame{X^2}{\Delta}$.
+\end{thm}
+
+\begin{proof}
+  See \cite{gcovering}.
+\end{proof}
+
+The reverse implication also relies upon a non-trivial lemma.
+
+\begin{thm}
+  For any uniformly locally compact proximal space $X$, $\pl O\win \congame{X}{H}$ for all compact $H\subseteq X$.
+\end{thm}
+
+\begin{proof}
+  Let $\sigma$ witness $\pl D \win \sproxgame{X}$. Let $o(t)$ be the subsequence of $t$ consisting of its odd-indexed terms.
+
+  We define $T(\emptyset)$, etc. as follows:
+
+  \begin{itemize}
+    \item Let $\emptyset\in T(\emptyset)$.
+    \item Choose $m_\emptyset<\omega$, $h_{\emptyset,i}\in H$ for $i<m_\emptyset$, and $h_{\emptyset,i,j}\in H\cap\cl{\frac{1}{4}\sigma(\emptyset)[h_{\emptyset,i}]}$ for $i,j<m_\emptyset$ such that
+      \[
+        \{\frac{1}{4}\sigma(\emptyset)[h_{\emptyset,i}]:i<m_\emptyset\}
+      \]
+    is a cover for $H$ and such that for each $i<m_\emptyset$
+      \[
+        \{\frac{1}{4}\sigma(\<h_{\emptyset,i}\>)[h_{\emptyset,i,j}]:j<m_\emptyset\}
+      \]
+    is a cover for $H\cap\cl{\frac{1}{4}\sigma(\emptyset)[h_{\emptyset,i}]}$.
+    \item Let $\<i\>\in T(\emptyset)$, $\<i,h_{\emptyset,i}\>\in T(\emptyset)$, and $\<i,h_{\emptyset,i},j\>\in T(\emptyset)$ for $i,j<m_\emptyset$.
+  \end{itemize}
+
+  Suppose $T(a)$, etc. are defined. We then define $T(a\concat\<x\>)$, etc. for
+    \[
+      x\in \bigcup_{s\concat\<i,h_{s,i},j\>\in\max(T(a))} \frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]
+    \]
+  as follows:
+
+  \begin{itemize}
+    \item Let $T(a)\subseteq T(a\concat\<x\>)$.
+    \item Choose $t=s\concat\<i,h_{s,i},j,x\>$ such that $s\concat\<i,h_{s,i},j\>\in\max(T(a))$ and $x\in \frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]$. 
+    \item Note that, assuming $o(s)\concat\<h_{s,i}\>$ is a legal partial attack against $\sigma$, then
+      \[
+        x
+          \in 
+        \frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]
+          \subseteq
+        \frac{1}{4}\sigma(o(s))[h_{s,i,j}]
+      \]
+    and
+      \[
+        h_{s,i,j}
+          \in 
+        \cl{\frac{1}{4}\sigma(o(s))[h_{s,i}]}
+          \subseteq 
+        \frac{1}{2}\sigma(o(s))[h_{s,i}]
+      \]
+    implies
+      \[
+        x
+          \in 
+        \sigma(o(s))[h_{s,i}]
+      \]
+    and thus $o(s)\concat\<h_{s,i},x\>=o(t)$ is a legal partial attack against $\sigma$.
+    \item Choose $m_t<\omega$, $h_{t,k}\in H\cap \cl{\frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]}$ for $k<m_t$, and $h_{t,k,l}\in H\cap\cl{\frac{1}{4}\sigma(t)[h_{t,k}]}$ for $k,l<m_t$ such that
+      \[
+        \{\frac{1}{4}\sigma(o(t))[h_{t,k}]:k<m_t\}
+      \]
+    is a cover for $H\cap \cl{\frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]}$ and such that for each $k<m_t$
+      \[
+        \{\frac{1}{4}\sigma(o(t)\concat\<h_{t,k}\>)[h_{t,i,j}]:l<m_t\}
+      \]
+    is a cover for $H\cap\cl{\frac{1}{4}\sigma(o(t))[h_{t,k}]}$.
+    \item Note that, assuming $o(t)$ is a legal partial attack against $\sigma$, then
+      \[
+        h_{t,k}
+          \in 
+        \cl{\frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]}
+          \subseteq
+        \frac{1}{2}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]
+      \]
+    and
+      \[
+        x
+          \in 
+        \frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]
+      \]
+    implies
+      \[
+        h_{t,k}
+          \in
+        \sigma(o(s)\concat\<h_{s,i}\>)[x]
+      \]
+    and thus $o(t)\concat\<h_{t,k}\>$ is a legal partial attack against $\sigma$.
+    \item Let $t\in T(a\concat\<x\>)$, $t\concat\<k\>\in T(a\concat\<x\>)$, $t\concat\<k,h_{t,k}\>\in T(a\concat\<x\>)$, and $t\concat\<k,h_{t,k},l\>\in T(a\concat\<x\>)$ for $k,l<m_t$.
+    \item Note that assuming
+      \[
+        \{\frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}] : s\concat\<i,h_{s,i},j\>\in\max(T(a))\}
+      \]
+    covers $H$, then since
+      \[
+        \{\frac{1}{4}\sigma(o(t)\concat\<h_{t,k}\>)[h_{t,k,l}] : s\concat\<i,h_{s,i},j,x,k,h_{t,k},l\>\in\max(T(a\concat\<x\>))\setminus\max(T(a))\}
+      \]
+    covers $H\cap \frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]$, we have that
+      \[
+        \{\frac{1}{4}\sigma(o(t)\concat\<h_{t,k}\>)[h_{t,k,l}] : t\concat\<k,h_{t,k},l\>\in\max(T(a\concat\<x\>))\}
+      \]
+    covers $H$.
+  \end{itemize}
+
+  With this we may define the strategy $\tau$ for $\pl O$ in $\clusgame{X}{H}$ such that:
+  \[
+    \tau(p\rest n) = \bigcup_{s\concat\<i,h_{s,i},j\>\in\max(T(p\rest n))} \frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]
+  \]
+
+  If $p$ attacks $\tau$, then it follows that $T(p\rest n)$ is defined for all $n<\omega$, so let $T(p)=\bigcup_{n<\omega} T(p\rest n)$. We note $T(p)$ is an infinite tree with finite levels:
+    \begin{itemize}
+      \item $\emptyset$ has exactly $m_\emptyset$ successors $\<i\>$.
+      \item $s\concat\<i\>$ has exactly one successor $t\concat\<i,h_{s,i}\>$
+      \item $s\concat\<i,h_{s,i}\>$ has exactly $m_s$ successors $t\concat\<i,h_{s,i},j\>$
+      \item $s\concat\<i,h_{s,i},j\>$ has either no successors or exactly one successor $t\concat\<i,h_{s,i},j,x\>$
+      \item $t=s\concat\<i,h_{s,i},j,x\>$ has exactly $m_t$ successors $t\concat\<k\>$
+    \end{itemize}
+
+  Let $q'=\<i_0,h_0,j_0,x_0,i_1,h_1,j_1,x_1,\dots\>$ correspond to this infinite branch in $T(p)$, and let $q=o(q')=\<h_0,x_0,h_1,x_1,\dots\>$.
+Note that by the construction of $T(p)$, $q$ is an attack on the winning strategy $\sigma$ in $\sproxgame{X}$, so it must converge.
+Since every other term of $q$ is in $H$, it must converge to $H$.
+Then since $q$ is a subsequence of $p$, $p$ must cluster at $H$.
+
+  Since $\pl O\win\clusgame{X}{H}$ if and only if $\pl O\win\congame{X}{H}$, the result follows.
+\end{proof}
+
+The equivalency result follows as a quick corollary.
+
+\begin{cor}
+  For any compact uniform space $X$, $X$ is proximal if and only if $X$ is Corson compact.
+\end{cor}
+
+\begin{proof}
+  The reverse implication was shown earlier. If $X$ is compact proximal, then so is $X^2$. By the previous theorem, $\pl O\win\congame{X^2}{\Delta}$, which is a characterization of Corson compact.
+\end{proof}
+
+% Commented out...
+I just realized that my old results concerning \congame did not assume that the point picker must pick in the intersection of all the sets chosen by O!
+In fact, O has an easy tactic for the game used in this paper on a one-point compactification of any space: just forbid the last point played, and it can never be repeated.
+So there is some hope to show that $\pl O \markwin \congame{X}{x}$ if and only if $\pl O \markwin \clusgame{X}{x}$.
+
+% \section{Further possibilities}
+
+% Note a similar characterization of \textbf{Eberlein compacts}.
+
+% \begin{thm}
+%   A space $X$ is Eberlein compact if and only if $X$ is compact and $\pl O \markwin \congame{X^2}{\Delta}$ (that is, $\pl O$ has a \textbf{Mark\"ov} winning strategy depending on only the round number and must recent move of $\pl P$).
+% \end{thm}
+
+% One might suspect a positive result to the following question.
+
+% \begin{ques}
+%   Is it true that for any compact uniform space $X$, $\pl D\markwin\proxgame{X}$ if and only if $X$ is Eberlein compact?
+% \end{ques}
+
+% A difficulty in approaching this problem arises upon realizing that $\congame{X}{H}$ and $\clusgame{X}{H}$ are not equivalent for $\pl O$ in the case of limited-information strategies, even when considering just compact spaces $X$ with $H$ being a singleton.
+
+% \begin{ex}
+% Let $\oneptcomp{\omega_1}=\omega_1\cup\{\infty\}$ be the one-point compactification of discrete $\omega_1$ by declaring complements of finite subsets of $\omega_1$ to be open.
+(Such spaces are also known as \textbf{Fort spaces}.) Then $\pl O\win\congame{\oneptcomp\omega_1}{\infty}$ and $\pl O\markwin\clusgame{\oneptcomp\omega_1}{\infty}$, but $\pl O\not\markwin\congame{\oneptcomp\omega_1}{\infty}$.
+% \end{ex}
+
+% \begin{proof}
+%   The perfect information winning strategy for $\pl O$ in $\congame{\oneptcomp\omega_1}{\infty}$ is evident: each round, $\pl O$ chooses the complement of all non-$\infty$ points chosen by $\pl P$.
+Since any legal attack by $\pl P$ cannot reside in a finite subset of $\omega_1$, any open neighborhood of $\infty$ contains all but finitely many points chosen by $\pl P$.
+
+%   To see that $\pl O\markwin\clusgame{\oneptcomp\omega_1}{\infty}$, let $A_{\alpha,n}$ be a finite set such that $A_{\alpha,n}\subseteq A_{\alpha,n+1}$ and $\bigcup_{n<\omega}A_{\alpha,n}=\alpha+1$ for each $\alpha<\omega_1$.
+We define the Mark\"ov strategy $\sigma$ for $\pl O$ in $\clusgame{\oneptcomp\omega_1}{\infty}$ by letting $\sigma(\alpha,n)=\oneptcomp{\omega_1}\setminus \bigcup_{m\leq n}A_{\alpha,m}$.
+Note that for any arbitrary $\{\alpha_0,\dots,\alpha_{k-1}\}\in [\omega_1]^{<\omega}$, there is some round $n$ such that $\{\alpha_0,\dots,\alpha_{k-1}\}\setminus \bigcup_{m\leq n,i<k}A_{\alpha_i,m}=\emptyset$, and thus no legal attack by $P$ can keep its range completely within $\{\alpha_0,\dots,\alpha_{k-1}\}$.
+
+%   Finally, $\pl O\not\markwin\congame{\oneptcomp\omega_1}{\infty}$ was shown by Nyikos in \cite{nclasses}.
+% \end{proof}
+
+\newpage
 \begin{thebibliography}{99}
@@
   Bell, Jocelyn.
-  \emph{An Infinite Game with Topological Consequences}.
+  \emph{An infinite game with topological consequences}.
   etc.
@@
   Engelking, Ryszard.
-  \emph{General Topology}.
+  \emph{General topology}.
   etc.
-\bibitem{g}
+\bibitem{gcovering}
   Gruenhage, Gary.
@@
   Topology Appl. 17 (1984), no. 3, 287–304.
-\bibitem{n}
+\bibitem{ginfinite}
+  Gruenhage, Gary.
+  \emph{Infinite games and generalizations of first-countable spaces}. 
+  etc.
+\bibitem{nproximal}
   Nyikos, Peter.
-  \emph{Proximal and Semi-Proximal Spaces}.
+  \emph{Proximal and semi-proximal spaces}.
   etc.
+% \bibitem{nclasses}
+%   Nyikos, Peter.
+%   \emph{Classes of compact sequential spaces}.
+%   etc.
 \end{thebibliography}

### 2013-12-19 articles/proximity-corson/proximity-corson.tex
noted Bells' usage of strong proximal game

@@
 He asked if that implication may also be reversed.
-We answer his question postively, by way of defining a stronger version of the proximal game which is perfect-information equivalent to Bell's original game for uniformly locally compact spaces.
+We answer his question postively, by way of a stronger version of the proximal game which is perfect-information equivalent to Bell's original game for uniformly locally compact spaces.
 \end{abstract}
@@
 
-While there is not much trouble in ensuring the nonempty intersection of\\ $\bigcap_{n<\omega} D_n[p_n]$ for this particular proof, we turned to a stronger version of $\proxgame{X}$ which avoids the issue entirely.
+While there is not much trouble in ensuring the nonempty intersection of\\ $\bigcap_{n<\omega} D_n[p_n]$ for this particular proof, we turned to a stronger version of $\proxgame{X}$ discussed briefly by Bell which avoids the issue entirely.
 

### 2013-12-27 articles/proximity-corson/proximity-corson.tex
G's revision.

--- 2013-12-19 articles/proximity-corson/proximity-corson.tex
@@
 
-\title{Equivalency of Proximal Compact and Corson Compact in Uniform Spaces}
+\title{Proximal compact spaces are Corson compact}
+
+\author{Steven Clontz}
+\address{Department of Mathematics, Auburn University,
+Auburn, AL 36830}
+\email{steven.clontz@auburn.edu}
+\urladdr{www.stevenclontz.com}
 
@@
 
-\author{Steven Clontz}
-\address{Department of Mathematics, Auburn University, 
-Auburn, AL 36830}
-\email{steven.clontz@auburn.edu}
-\urladdr{www.stevenclontz.com}
+\keywords{Proximal, absolutely proximal, Corson compact, uniform space, $W$-space}
+
+\subjclass[2010]{54E15, 54D30, 54A20}
 
 \begin{abstract}
-A common generalization of metric spaces is the idea of a uniform space, determined by a uniformity of entourages on the diagonal of the square.
+
+J.
+Bell defined a topological space $X$ to be {\it proximal} if $X$ has a compatible uniformity with respect to which the first player has a winning strategy in a certain $\omega$-length game.
+As noted by P.J.
+Nyikos, it follows easily from Bell's results that Corson compact spaces are proximal.
+We answer a question of Nyikos by showing that a compact space is proximal iff it is Corson compact.
+
+%A common generalization of metric spaces is the idea of a uniform space, determined by a uniformity of entourages on the diagonal of the square.
 Proximal uniform spaces are those for which the first player has a winning strategy in this $\omega$-length game due to Bell: the first player chooses an entourage of the space, and her opponent chooses a point close to the point chosen in the previous round, with respect to the entourage chosen in the previous round.
@@
 He asked if that implication may also be reversed.
-We answer his question postively, by way of defining a stronger version of the proximal game which is perfect-information equivalent to Bell's original game for uniformly locally compact spaces.
+We answer his question positively, by way of defining a stronger version of the proximal game which is perfect-information equivalent to Bell's original game for uniformly locally compact spaces.
 \end{abstract}
@@
 
-Jocelyn Bell introduced the concept of proximal spaces in her doctoral dissertation while working on the following uniform box product problems due to her advisor Scott Williams: is the uniform box product of compact spaces normal, collectionwise normal, or paracompact?
-Proximal spaces are defined to be the spaces for which the first player in the proximal game played on that space has a winning strategy.
-Bell has shown that proximal spaces have strong preservation properties, particularly, the $\Sigma$-product of proximal spaces is itself proximal \cite{b}.
-This mirrors the analogous theorem for metric spaces; in fact, every metric space is easily seen to be proximal.
+A common generalization of metric spaces is the idea of a {\it uniform space}.
+A uniform space is a determined by a collection of supersets of the diagonal in the square (called ``entourages")  satisfying certain conditions.
+A uniformity induces in a natural way a topology on $X$, called the {\it uniform topology}.
+A topological space $X$ is {\it uniformizable} if there is  a uniformity on $X$ which generates its topology.
+Any completely regular space is uniformizable.
+See the next section for more complete definitions of these concepts and some of their basic properties.
 
-In \cite{nproximal}, Peter Nyikos observed that compact subspaces of the $\Sigma$-product of real lines, known as Corson compacts, must be proximal, since the proximal property is preserved under $\Sigma$-products.
-He left open the question as to whether any proximal compact must then be Corson compact.
-Using a characterization of Corson compact due to Gruenhage in \cite{gcovering}, we can answer that question in the affirmative.
+Jocelyn Bell introduced the concept of proximal spaces in her doctoral dissertation while working on some uniform box product problems due to her advisor Scott Williams.
+Proximal spaces are defined to be the spaces $X$ for which there is a compatible uniformity on $X$ such that the entourage picker has a winning strategy in a certain $\omega$-length game.
+Every metric space is easily seen to be proximal.
+Bell has shown that proximal spaces are collectionwise normal, countably paracompact, and have strong preservation properties, particularly, closed subpaces and  $\Sigma$-products of proximal spaces are  proximal \cite{b}.
+
+In \cite{nproximal}, Peter Nyikos observed that Bell's results imply that compact subspaces of the $\Sigma$-product of real lines, known as Corson compacts, must be proximal.
+He asked the natural question as to whether any proximal compact must then be Corson compact.
+Using a characterization of Corson compact due to the second author in \cite{gcovering}, we  answer that question in the affirmative.
+
+In this paper, all topological spaces are assumed to be completely regular.
 
 \section{Definitions and Properites of Uniform Spaces}
-
-In this paper, all spaces are assumed to be topological spaces induced by a uniformity. We relate some definitions and properties of uniform spaces.
+ We relate some definitions and properties of uniform spaces.
 
 \begin{defn}
-  A \textbf{uniform space} is a pair $\<X,\mc{D}\>$ where $X$ is a set, and $\mc{D}$ is a \textbf{uniformity}.
-A uniformity is a filter on subsets of $X^2$, called \textbf{entourages}, such that for each entourage $D\in \mc D$:
+  A \textit{uniform space} is a pair $\<X,\mc{D}\>$ where $X$ is a set, and $\mc{D}$ is a uniformity.
+A {\it uniformity} is a filter on subsets of $X^2$, called \textit{entourages}, such that for each entourage $D\in \mc D$:
   \begin{itemize}
@@
         \[
-          2\left(\frac{1}{2}D\right)=\frac{1}{2}D\circ \frac{1}{2}D=\left\{\<x,z\>:\exists y\left(\<x,y\>,\<y,z\>\in \frac{1}{2}D\right)\right\}\subseteq D
+          2\left(\frac{1}{2}D\right)=\frac{1}{2}D\circ \frac{1}{2}D=\left\{\<x,z\>:\exists y\left(\<x,y\>,\<y,z\>\in \frac{1}{2}D\right)\right\}\subseteq D.
         \]
-      (Let $\frac{1}{2^{n+1}}D$ be shorthand for $\frac{1}{2}(\frac{1}{2^{n}}D)$.)
+      %(Let $\frac{1}{2^{n+1}}D$ be shorthand for $\frac{1}{2}(\frac{1}{2^{n}}D)$.)
     \end{itemize}
@@
 \begin{defn}
-  The \textbf{uniform topology} induced by a uniformity declares a set $U$ to be open if for every $x\in U$, there is some $D\in\mc D$ with $x\in D[x]=\{y: \<x,y\>\in D\}\subseteq U$.
+  The \textit{uniform topology} induced by a uniformity declares a set $U$ to be open if for every $x\in U$, there is some $D\in\mc D$ with $x\in D[x]=\{y: \<x,y\>\in D\}\subseteq U$.
+A topological space $X$ is said to be \textit{uniformizable} if there is a uniformity $D$ on $X$ which induces its topology.
 \end{defn}
 
-\begin{thm}
-  Every completely regular topology may be induced by a uniformity, and every uniform topology is completely regular.
-\end{thm}
+We now list some basic results about uniformities and uniform spaces.  One may  see \cite{e}, for example, for proofs.
 
-\begin{thm}
-  For every entourage $D$, there is an open symmetric entourage $E\subseteq D$.
+\begin{itemize}
+ \item Every uniform topology is completely regular, and every completely regular space is uniformizable.
+\item  For every entourage $D$, there is an open symmetric entourage $E\subseteq D$.
 That is, $\<x,y\>\in E \Leftrightarrow \<y,x\> \in E$, and $E$ is open in $X^2$ with the usual product topology induced by the uniform topology on $X$.
-\end{thm}
+\item  If $D$ is an open entourage, then for all $x\in X$, $D[x]$ is an open neighborhood of $x$.
+\end{itemize}
 
-(For convenience, we assume that $\frac{1}{2}D$ is always open symmetric.)
-
-\begin{prop}
-  If $D$ is an open entourage, then for all $x\in X$, $D[x]$ is an open neighborhood of $x$.
-\end{prop}
-
-\begin{proof}
-  For the proofs of these, see \cite{e}.
-\end{proof}
+We will make frequent use of $\frac{1}{2}D$ in this paper.
+Of course, $\frac{1}{2}D$ is not unique, but for convenience we will assume that for each $D\in \mathcal D$, a unique $\frac{1}{2}D$ has been chosen, which  by the second item above may be assumed to be open and symmetric.
+Then we define $\frac{1}{4}D=\frac{1}{2}(\frac{1}{2}D)$,
+$\frac{1}{8}D=\frac{1}{2}(\frac{1}{4}D)$, and so on.
 
@@
 \begin{proof}
-  If $y$ is a limit point of $\frac{1}{2}D[x]$, then $\frac{1}{2}D[y]$ must intersect $\frac{1}{2}D[x]$ at some $z$. It follows then that $z\in D[x]$.
+  If $y$ is a limit point of $\frac{1}{2}D[x]$, then $\frac{1}{2}D[y]$ must intersect $\frac{1}{2}D[x]$ at some $z$. It follows then that $y\in D[x]$.
 \end{proof}
@@
 
-The theory of proximal uniform spaces relies on an $\omega$-length game, which proceeds as follows:
+The theory of proximal uniform spaces relies on the following $\omega$-length game:
 
@@
       \item In the initial round $0$, $\pl D$ chooses an open symmetric entourage $D_0$, followed by $\pl P$ choosing a point $p_0\in X$.
-      \item In round $n+1$, $\pl D$ chooses an open symmetric entourage $D_{n+1}\subseteq \frac{1}{4}D_n$, followed by $\pl P$ choosing a point $p_{n+1}\in D_n[p_n]$.
+      \item In round $n+1$, $\pl D$ chooses an open symmetric entourage $D_{n+1}\subseteq D_n$, followed by $\pl P$ choosing a point $p_{n+1}\in D_n[p_n]$.
     \end{itemize}
@@
 The reader familiar with proximal spaces may note that this definition is different than the original formulation of the game (see \cite{b}); however, it is easily verified that $\pl D$ has a winning strategy in the original game if and only if $\pl D$ has a winning strategy in our version.
+Also, if we wish we may assume that if $\sigma$ is a winning strategy for $\pl D$, then $D_{n+1}=\sigma (x_0,x_1,...,x_n)$ is contained in something smaller than $D_n$, e.g., $\frac{1}{4}D_n$.
+That is because a sequence of legal moves by $\pl P$ with $\pl D$ using the refined strategy is also a legal sequence of moves with $\pl D$ using the original strategy.
 
@@
 \begin{defn}
-  A uniform space $X$ is said to be \textbf{proximal} if and only if $\pl D\win\proxgame{X}$.
+  A uniform space $(X,\mathcal D)$ is said to be \textit{proximal} if and only if $\pl D\win\proxgame{X}$.
+A topological space is \textit{proximal} iff it admits  a compatible uniformity (i.e., one which induces its topology) which is proximal.
 \end{defn}
@@
 
-The first author introduced the following game in \cite{ginfinite}.
+The second author introduced the following game in \cite{ginfinite}.
 
@@
 \begin{defn}
-  A topological space $X$ is said to be a $W$ space if and only if for every $x\in X$, $\pl O\win \congame{X}{x}$.
+  A topological space $X$ is said to be a {\it $W$-space} if and only if for every $x\in X$, $\pl O\win \congame{X}{x}$.
 \end{defn}
@@
 
-\begin{thm}
-  All proximal spaces are $W$ spaces.
+\begin{thm}\cite{b}
+  All proximal spaces are $W$-spaces.
 \end{thm}
 
-\begin{proof}
-  Due to Bell, see \cite{b}.
-The idea of the proof is to consider the result of an attack on the winning strategy for $\pl D$ in $\proxgame{X}$ which alternates between points chosen by $\pl P$ in $\congame{X}{x}$ and the particular point $x$ itself.
+   The idea of Bell's proof of the above result is to consider the result of an attack on the winning strategy for $\pl D$ in $\proxgame{X}$ which alternates between points chosen by $\pl P$ in $\congame{X}{x}$ and the particular point $x$ itself.
 Since the intersection $\bigcap_{n<\omega} D_n[p_n]$ must contain $x$, the sequence must converge, and since the sequence contains $x$ infinitely often, it must converge to $x$.
-\end{proof}
 
-While there is not much trouble in ensuring the nonempty intersection of\\ $\bigcap_{n<\omega} D_n[p_n]$ for this particular proof, we turned to a stronger version of $\proxgame{X}$ which avoids the issue entirely.
+While there is not much trouble in ensuring the nonempty intersection of\\ $\bigcap_{n<\omega} D_n[p_n]$ for this particular proof, we turn to a stronger version of $\proxgame{X}$, also introduced by Bell, which avoids the issue entirely.
 
 \begin{defn}
-  The \textbf{strong proximal game} $\sproxgame{X}$ proceeds identially to $\proxgame{X}$, except that $\pl D$ may only win in the case that $\<p_0,p_1,\dots\>$ converges.
+  The \textit{absolutely proximal game}  proceeds identially to $\proxgame{X}$, except that $\pl D$ may only win in the case that $\<p_0,p_1,\dots\>$ converges.
 \end{defn}
 
-Certainly, if $\pl D\win \sproxgame{X}$, then $\pl D\win \proxgame{X}$, so all ``strongly proximal'' spaces are proximal. We are interested in the case that both games are equivalent for $\pl D$.
+Obviously, all absolutely proximal spaces are proximal. We are interested in when we have equivalence.
 
 \begin{defn}
-  A uniform space is uniformly locally compact if there exists an open symmetric entourage $L$ such that $\cl{L[x]}$ is a compact neighborhood of $x$ for all $x\in X$.
+  A uniform space is {\it uniformly locally compact} if there exists an open symmetric entourage $L$ such that $\cl{L[x]}$ is a compact neighborhood of $x$ for all $x\in X$.
+A topological space is uniformly locally compact if it admits a compatible uniformly locally compact uniformity.
 \end{defn}
 
+Obviously every compact space is uniformly locally compact, but not every locally compact space is uniformly locally compact.
+For example, the space of countable ordinals is locally compact, but does not admit a compatible uniformly locally compact uniformity.
+
 \begin{thm}
-  A uniformly locally compact space $X$ is proximal if and only if $\pl D\win \sproxgame{X}$.
+  A uniformly locally compact space $X$ is proximal if and only if it is absolutely proximal.
 \end{thm}
@@
 Let $\sigma$ be a strategy for $\pl D$ witnessing $\pl D\win \proxgame{X}$.
-Without loss of generality, we may assume such that $\sigma(p\rest n)\subseteq L$ for all partial attacks $p\rest n$ (so $\cl{\sigma(p\rest n)[x]}\subseteq\cl{L[x]}$ is compact), since $\sigma(p\rest n)\cap L$ is itself an open symmetric entourage, and any legal attack against these refined entourages is also a legal attack against the original.
+Without loss of generality, we may assume such that $\sigma(p\rest n)\subseteq L$ for all partial attacks $p\rest n$ (so $\cl{\sigma(p\rest n)[x]}\subseteq\cl{L[x]}$ is compact), and that $n > m$ implies $\sigma(p\rest n)\subset \frac{1}{4}\sigma(p\rest m)$.
 
-  Let $\tau(p\rest n)=\frac{1}{2}\sigma(p\rest n)$. If $p$ attacks $\tau$ in $\sproxgame{X}$, then
+  Let $\tau(p\rest n)=\frac{1}{2}\sigma(p\rest n)$. If $p$ attacks $\tau$, then
     \[
@@
 
-  Finally, note that since $\tau$ yields refinements of $\sigma$, then $p$ attacks the winning strategy $\sigma$ in $\proxgame{X}$, but since the intersection of a descending chain of nonempty compact sets is nonempty:
+  Finally, note that since $\tau$ yields refinements of $\sigma$, then $p$ attacks the winning strategy $\sigma$ in $\proxgame{X}$, but since the intersection of a descending chain of nonempty compact sets is nonempty, we have
 
@@
         \not=
-      \emptyset
+      \emptyset.
     \]
@@
 
-To wrap up this section, we cite a few required results due to Bell, also from \cite{b}.
-
-\begin{thm}
-  The $\Sigma$-product of proximal spaces is proximal. In particular, if $X$ is proximal, then $X^2$ is proximal.
-\end{thm}
-
-\begin{thm}
-  Every closed subspace of a proximal space is proximal.
-\end{thm}
-
-\begin{thm}
-  Every metrizable space is proximal.
-\end{thm}
-
 \section{Corson Compacts and Proximal Compacts}
 
-We recall from \cite{gcovering} the definition of Corson compact.
+We recall  the definition of Corson compact.
 
 \begin{defn}
-  A space is said to be Corson compact if and only if it is homeomorphic to a compact set within the $\Sigma$-product $\Sigma\mathbb{R}^\kappa$ of $\kappa$-many real lines, that is:
+  A space is said to be {\it Corson compact} if and only if it is homeomorphic to a compact set within the $\Sigma$-product $\Sigma\mathbb{R}^\kappa$ of $\kappa$-many real lines, that is:
     \[
@@
 
-\begin{prop}
-  Every Corson compact is proximal.
-\end{prop}
+Since proximal spaces are closed under closed subsets and $\Sigma$-products, it follows (as noted by Nyikos) that
+every Corson compact is proximal.
 
-\begin{proof}
-  As observed by Nyikos in \cite{nproximal}.
-Any Corson compact is a $\Sigma$-product of compact subsets of the real line.
-Since closed subsets of metrizable spaces are proximal, and the $\Sigma$-product of proximal spaces is proximal, the result follows.
-\end{proof}
+However, the given characterization of Corson compact is less useful when proving the other direction.  Instead we use the following game characterization due to the second author.
 
-However, this characterization of Corson compact is less useful when proving the other direction.
-
-\begin{thm}
+\begin{thm}\cite{gcovering}
   A space $X$ is Corson compact if and only if $X$ is compact and $\pl O\win\congame{X^2}{\Delta}$.
@@
 
-\begin{proof}
-  See \cite{gcovering}.
-\end{proof}
-
-The reverse implication also relies upon a non-trivial lemma.
+The following contains the meat of our proof of the title result.
 
 \begin{thm}
-  For any uniformly locally compact proximal space $X$, $\pl O\win \congame{X}{H}$ for all compact $H\subseteq X$.
+  For any absolutely proximal space $X$, $\pl O\win \congame{X}{H}$ for all compact $H\subseteq X$.
 \end{thm}
@@
 \begin{proof}
-  Let $\sigma$ witness $\pl D \win \sproxgame{X}$. Let $o(t)$ be the subsequence of $t$ consisting of its odd-indexed terms.
+  Let $\sigma$ be a winning strategy for $\pl D$ in the absolutely proximal game such that $p\supsetneq q$ implies $\sigma(p)\subset \frac{1}{4}\sigma(q)$.
+  For any sequence $t=\<t_0,t_1,\dots\>$, let $o(t)$ be the subsequence of $t$ consisting of its odd-indexed terms.
 
-  We define $T(\emptyset)$, etc. as follows:
+  For certain finite sequences $s$ in $X$, we will define by induction a tree $T(s)$ of finite height such that $t\supset s$ implies $T(s)$ is a subtree of $T(t)$, and if $u$ is a node of $T(s)$ having successors in $T(s)$, then $u$ has no new successors in $T(t)$.
+We let $\max(T)$ denote the nodes of $T$ that have no successors in $T$.
+
+  \bigskip
+
+First we define $T(\emptyset)$.
 
@@
     is a cover for $H\cap\cl{\frac{1}{4}\sigma(\emptyset)[h_{\emptyset,i}]}$.
-    \item Let $\<i\>\in T(\emptyset)$, $\<i,h_{\emptyset,i}\>\in T(\emptyset)$, and $\<i,h_{\emptyset,i},j\>\in T(\emptyset)$ for $i,j<m_\emptyset$.
+    \item Let $\<i\>, \<i,h_{\emptyset,i}\>$, and $\<i,h_{\emptyset,i},j\>$ be in $T(\emptyset)$ for $i,j<m_\emptyset$.
   \end{itemize}
+This ends the construction of $T(\emptyset)$.   We remark that the indexings $i\mapsto h_{\emptyset,i}$ and $(i,j)\mapsto h_{\emptyset,i, j}$ need not be one-to-one; repetition of points is allowed.
 
-  Suppose $T(a)$, etc. are defined. We then define $T(a\concat\<x\>)$, etc. for
+\bigskip
+
+  Now suppose $T(a)$ is defined. We then define $T(a\concat\<x\>)$, etc., for
     \[
@@
     \item Choose $t=s\concat\<i,h_{s,i},j,x\>$ such that $s\concat\<i,h_{s,i},j\>\in\max(T(a))$ and $x\in \frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]$.
+Then $s\concat\<i,h_{s,i},j\>$ is the only node of $T(a)$ that will be extended in this step.
     \item Note that, assuming $o(s)\concat\<h_{s,i}\>$ is a legal partial attack against $\sigma$, then
@@
     and thus $o(s)\concat\<h_{s,i},x\>=o(t)$ is a legal partial attack against $\sigma$.
-    \item Choose $m_t<\omega$, $h_{t,k}\in H\cap \cl{\frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]}$ for $k<m_t$, and $h_{t,k,l}\in H\cap\cl{\frac{1}{4}\sigma(t)[h_{t,k}]}$ for $k,l<m_t$ such that
+    \item Choose $m_t<\omega$, $h_{t,k}\in H\cap \cl{\frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]}$ for $k<m_t$, and $h_{t,k,l}\in H\cap\cl{\frac{1}{4}\sigma(o(t))[h_{t,k}]}$ for $k,l<m_t$ such that
       \[
@@
       \[
-        \{\frac{1}{4}\sigma(o(t)\concat\<h_{t,k}\>)[h_{t,i,j}]:l<m_t\}
+        \{\frac{1}{4}\sigma(o(t)\concat\<h_{t,k}\>)[h_{t,k,l}]:l<m_t\}
       \]
@@
     and thus $o(t)\concat\<h_{t,k}\>$ is a legal partial attack against $\sigma$.
-    \item Let $t\in T(a\concat\<x\>)$, $t\concat\<k\>\in T(a\concat\<x\>)$, $t\concat\<k,h_{t,k}\>\in T(a\concat\<x\>)$, and $t\concat\<k,h_{t,k},l\>\in T(a\concat\<x\>)$ for $k,l<m_t$.
+    \item For each $k,l<m_t$, put $t\concat\<k,h_{t,k},l\>$ and all of its initial segments in $ T(a\concat\<x\>)$.   This completes the construction of  $ T(a\concat\<x\>)$.
+
+    \bigskip
+
     \item Note that assuming
@@
 
-  With this we may define the strategy $\tau$ for $\pl O$ in $\clusgame{X}{H}$ such that:
+  Hence we may define the strategy $\tau$ for $\pl O$ in $\clusgame{X}{H}$ such that:
   \[
@@
       \item $\emptyset$ has exactly $m_\emptyset$ successors $\<i\>$.
-      \item $s\concat\<i\>$ has exactly one successor $t\concat\<i,h_{s,i}\>$
-      \item $s\concat\<i,h_{s,i}\>$ has exactly $m_s$ successors $t\concat\<i,h_{s,i},j\>$
-      \item $s\concat\<i,h_{s,i},j\>$ has either no successors or exactly one successor $t\concat\<i,h_{s,i},j,x\>$
+      \item $s\concat\<i\>$ has exactly one successor $s\concat\<i,h_{s,i}\>$
+      \item $s\concat\<i,h_{s,i}\>$ has exactly $m_s$ successors $s\concat\<i,h_{s,i},j\>$
+      \item $s\concat\<i,h_{s,i},j\>$ has either no successors or exactly one successor $s\concat\<i,h_{s,i},j,x\>$
       \item $t=s\concat\<i,h_{s,i},j,x\>$ has exactly $m_t$ successors $t\concat\<k\>$
@@
 
-  Let $q'=\<i_0,h_0,j_0,x_0,i_1,h_1,j_1,x_1,\dots\>$ correspond to this infinite branch in $T(p)$, and let $q=o(q')=\<h_0,x_0,h_1,x_1,\dots\>$.
-Note that by the construction of $T(p)$, $q$ is an attack on the winning strategy $\sigma$ in $\sproxgame{X}$, so it must converge.
+  Hence $T(p)$ has an infinite branch $q'=\<i_0,h_0,j_0,x_0,i_1,h_1,j_1,x_1,\dots\>$.
+Let $q=o(q')=\<h_0,x_0,h_1,x_1,\dots\>$.
+Note that by the construction of $T(p)$, $q$ is an attack on the winning strategy $\sigma$ in the absolutely proximal game, so it must converge.
 Since every other term of $q$ is in $H$, it must converge to $H$.
-Then since $q$ is a subsequence of $p$, $p$ must cluster at $H$.
+Then since $o(q)$ is a subsequence of $p$, $p$ must cluster at $H$.
 
@@
 \begin{cor}
-  For any compact uniform space $X$, $X$ is proximal if and only if $X$ is Corson compact.
+  For any compact space $X$, $X$ is proximal if and only if $X$ is Corson compact.
 \end{cor}
@@
 \begin{proof}
-  The reverse implication was shown earlier. If $X$ is compact proximal, then so is $X^2$. By the previous theorem, $\pl O\win\congame{X^2}{\Delta}$, which is a characterization of Corson compact.
+  The reverse implication was noted earlier. If $X$ is compact proximal, then so is $X^2$. By the previous theorem, $\pl O\win\congame{X^2}{\Delta}$, which is a characterization of Corson compact.
 \end{proof}
@@
 
-\newpage
 \begin{thebibliography}{99}
 \bibitem{b}
-  Bell, Jocelyn.
-  \emph{An infinite game with topological consequences}.
-  etc.
+ J. Bell,
+  \emph{An infinite game with topological consequences}, preprint.
 \bibitem{e}
-  Engelking, Ryszard.
-  \emph{General topology}.
-  etc.
+  R. Engelking,
+  \emph{General topology}, Revised and completed edition, Heldermann Verlag, Berlin, 1989.
+
+  \bibitem{ginfinite}
+ G. Gruenhage,
+  \emph{Infinite games and generalizations of first-countable spaces}, Gen. Top. Appl. 6(1976), 339-352.
+
 \bibitem{gcovering}
-  Gruenhage, Gary.
-  \emph{Covering properties on $X^2\setminus\Delta$, $W$-sets, and compact subsets of $\Sigma$-products}. 
-  Topology Appl. 17 (1984), no. 3, 287–304.
-\bibitem{ginfinite}
-  Gruenhage, Gary.
-  \emph{Infinite games and generalizations of first-countable spaces}. 
-  etc.
+  G. Gruenhage,
+  \emph{Covering properties on $X^2\setminus\Delta$, $W$-sets, and compact subsets of $\Sigma$-products},
+  Topology Appl. 17 (1984), no. 3, 287–-304.
+
 \bibitem{nproximal}
-  Nyikos, Peter.
-  \emph{Proximal and semi-proximal spaces}.
-  etc.
+  P.J. Nyikos,
+  \emph{Proximal and semi-proximal spaces}, preprint.
 % \bibitem{nclasses}

### 2013-12-27 articles/proximity-corson/proximity-corson.tex
cleanup, slight revisions

@@
 \newcommand{\proxgame}[1]{Prox_{D,P}(#1)}
-\newcommand{\sproxgame}[1]{sProx_{D,P}(#1)}
 \newcommand{\congame}[2]{Con_{O,P}(#1,#2)}
@@
 \newcommand{\concat}{^\frown}
+
+\newcommand{\term}{\textit}
 
@@
 J.
-Bell defined a topological space $X$ to be {\it proximal} if $X$ has a compatible uniformity with respect to which the first player has a winning strategy in a certain $\omega$-length game.
+Bell defined a topological space $X$ to be \term{proximal} if $X$ has a compatible uniformity with respect to which the first player has a winning strategy in a certain $\omega$-length game.
 As noted by P.J.
@@
 We answer a question of Nyikos by showing that a compact space is proximal iff it is Corson compact.
-
-%A common generalization of metric spaces is the idea of a uniform space, determined by a uniformity of entourages on the diagonal of the square.
-Proximal uniform spaces are those for which the first player has a winning strategy in this $\omega$-length game due to Bell: the first player chooses an entourage of the space, and her opponent chooses a point close to the point chosen in the previous round, with respect to the entourage chosen in the previous round.
-As proximal spaces are preserved under $\Sigma$-products, Nyikos has observed that every Corson compact space, a compact space embeddable in the $\Sigma$-product of real lines, must then be proximal.
-He asked if that implication may also be reversed.
-We answer his question positively, by way of defining a stronger version of the proximal game which is perfect-information equivalent to Bell's original game for uniformly locally compact spaces.
 \end{abstract}
@@
 
-A common generalization of metric spaces is the idea of a {\it uniform space}.
+A common generalization of metric spaces is the idea of a \term{uniform space}.
 A uniform space is a determined by a collection of supersets of the diagonal in the square (called ``entourages")  satisfying certain conditions.
-A uniformity induces in a natural way a topology on $X$, called the {\it uniform topology}.
-A topological space $X$ is {\it uniformizable} if there is  a uniformity on $X$ which generates its topology.
+A uniformity induces in a natural way a topology on $X$, called the \term{uniform topology}.
+A topological space $X$ is \term{uniformizable} if there is  a uniformity on $X$ which generates its topology.
 Any completely regular space is uniformizable.
@@
 \begin{defn}
-  A \textit{uniform space} is a pair $\<X,\mc{D}\>$ where $X$ is a set, and $\mc{D}$ is a uniformity.
-A {\it uniformity} is a filter on subsets of $X^2$, called \textit{entourages}, such that for each entourage $D\in \mc D$:
+  A \term{uniform space} is a pair $\<X,\mc{D}\>$ where $X$ is a set, and $\mc{D}$ is a uniformity.
+A \term{uniformity} is a filter on subsets of $X^2$, called \term{entourages}, such that for each entourage $D\in \mc D$:
   \begin{itemize}
@@
         \]
-      %(Let $\frac{1}{2^{n+1}}D$ be shorthand for $\frac{1}{2}(\frac{1}{2^{n}}D)$.)
     \end{itemize}
@@
 \begin{defn}
-  The \textit{uniform topology} induced by a uniformity declares a set $U$ to be open if for every $x\in U$, there is some $D\in\mc D$ with $x\in D[x]=\{y: \<x,y\>\in D\}\subseteq U$.
-A topological space $X$ is said to be \textit{uniformizable} if there is a uniformity $D$ on $X$ which induces its topology.
+  The \term{uniform topology} induced by a uniformity declares a set $U$ to be open if for every $x\in U$, there is some $D\in\mc D$ with $x\in D[x]=\{y: \<x,y\>\in D\}\subseteq U$.
+A topological space $X$ is said to be \term{uniformizable} if there is a uniformity $D$ on $X$ which induces its topology.
 \end{defn}
@@
 \begin{defn}
-  A uniform space $(X,\mathcal D)$ is said to be \textit{proximal} if and only if $\pl D\win\proxgame{X}$.
-A topological space is \textit{proximal} iff it admits  a compatible uniformity (i.e., one which induces its topology) which is proximal.
+  A uniform space $(X,\mathcal D)$ is said to be \term{proximal} if and only if $\pl D\win\proxgame{X}$.
+A topological space is \term{proximal} iff it admits  a compatible uniformity (i.e., one which induces its topology) which is proximal.
 \end{defn}
@@
 \begin{defn}
-  A topological space $X$ is said to be a {\it $W$-space} if and only if for every $x\in X$, $\pl O\win \congame{X}{x}$.
+  A topological space $X$ is said to be a \term{$W$-space} if and only if for every $x\in X$, $\pl O\win \congame{X}{x}$.
 \end{defn}
@@
 \begin{defn}
-  The \textit{absolutely proximal game}  proceeds identially to $\proxgame{X}$, except that $\pl D$ may only win in the case that $\<p_0,p_1,\dots\>$ converges.
+  The \term{absolutely proximal game}  proceeds identially to $\proxgame{X}$, except that $\pl D$ may only win in the case that $\<p_0,p_1,\dots\>$ converges.
 \end{defn}
@@
 \begin{defn}
-  A uniform space is {\it uniformly locally compact} if there exists an open symmetric entourage $L$ such that $\cl{L[x]}$ is a compact neighborhood of $x$ for all $x\in X$.
+  A uniform space is \term{uniformly locally compact} if there exists an open symmetric entourage $L$ such that $\cl{L[x]}$ is a compact neighborhood of $x$ for all $x\in X$.
 A topological space is uniformly locally compact if it admits a compatible uniformly locally compact uniformity.
@@
 Let $\sigma$ be a strategy for $\pl D$ witnessing $\pl D\win \proxgame{X}$.
-Without loss of generality, we may assume such that $\sigma(p\rest n)\subseteq L$ for all partial attacks $p\rest n$ (so $\cl{\sigma(p\rest n)[x]}\subseteq\cl{L[x]}$ is compact), and that $n > m$ implies $\sigma(p\rest n)\subset \frac{1}{4}\sigma(p\rest m)$.
+Without loss of generality, we may assume such that $\sigma(p\rest n)\subseteq L$ for all partial attacks $p\rest n$ (so $\cl{\sigma(p\rest n)[x]}\subseteq\cl{L[x]}$ is compact), and that $n > m$ implies $\sigma(p\rest n)\subseteq \frac{1}{4}\sigma(p\rest m)$.
 
@@
 
-  Finally, note that since $\tau$ yields refinements of $\sigma$, then $p$ attacks the winning strategy $\sigma$ in $\proxgame{X}$, but since the intersection of a descending chain of nonempty compact sets is nonempty, we have
+  Finally, note that since $\tau$ yields subsets of $\sigma$, then $p$ attacks the winning strategy $\sigma$ in $\proxgame{X}$, but since the intersection of a descending chain of nonempty compact sets is nonempty, we have
 
@@
 \begin{defn}
-  A space is said to be {\it Corson compact} if and only if it is homeomorphic to a compact set within the $\Sigma$-product $\Sigma\mathbb{R}^\kappa$ of $\kappa$-many real lines, that is:
+  A space is said to be \term{Corson compact} if and only if it is homeomorphic to a compact set within the $\Sigma$-product $\Sigma\mathbb{R}^\kappa$ of $\kappa$-many real lines, that is:
     \[
@@
       \[
-        \{\frac{1}{4}\sigma(\emptyset)[h_{\emptyset,i}]:i<m_\emptyset\}
+        \left\{\frac{1}{4}\sigma(\emptyset)[h_{\emptyset,i}]:i<m_\emptyset\right\}
       \]
@@
       \[
-        \{\frac{1}{4}\sigma(\<h_{\emptyset,i}\>)[h_{\emptyset,i,j}]:j<m_\emptyset\}
+        \left\{\frac{1}{4}\sigma(\<h_{\emptyset,i}\>)[h_{\emptyset,i,j}]:j<m_\emptyset\right\}
       \]
@@
   \end{itemize}
-This ends the construction of $T(\emptyset)$.   We remark that the indexings $i\mapsto h_{\emptyset,i}$ and $(i,j)\mapsto h_{\emptyset,i, j}$ need not be one-to-one; repetition of points is allowed.
+This ends the construction of $T(\emptyset)$.   We remark that the indexings $i\mapsto h_{\emptyset,i}$ and $\<i,j\>\mapsto h_{\emptyset,i, j}$ need not be one-to-one; repetition of points is allowed.
 
@@
       \[
-        \{\frac{1}{4}\sigma(o(t))[h_{t,k}]:k<m_t\}
+        \left\{\frac{1}{4}\sigma(o(t))[h_{t,k}]:k<m_t\right\}
       \]
@@
       \[
-        \{\frac{1}{4}\sigma(o(t)\concat\<h_{t,k}\>)[h_{t,k,l}]:l<m_t\}
+        \left\{\frac{1}{4}\sigma(o(t)\concat\<h_{t,k}\>)[h_{t,k,l}]:l<m_t\right\}
       \]
@@
       \[
-        \{\frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}] : s\concat\<i,h_{s,i},j\>\in\max(T(a))\}
+        \left\{\frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}] : s\concat\<i,h_{s,i},j\>\in\max(T(a))\right\}
       \]
@@
       \[
-        \{\frac{1}{4}\sigma(o(t)\concat\<h_{t,k}\>)[h_{t,k,l}] : s\concat\<i,h_{s,i},j,x,k,h_{t,k},l\>\in\max(T(a\concat\<x\>))\setminus\max(T(a))\}
+        \left\{\frac{1}{4}\sigma(o(t)\concat\<h_{t,k}\>)[h_{t,k,l}] : s\concat\<i,h_{s,i},j,x,k,h_{t,k},l\>\in\max(T(a\concat\<x\>))\setminus\max(T(a))\right\}
       \]
@@
       \[
-        \{\frac{1}{4}\sigma(o(t)\concat\<h_{t,k}\>)[h_{t,k,l}] : t\concat\<k,h_{t,k},l\>\in\max(T(a\concat\<x\>))\}
+        \left\{\frac{1}{4}\sigma(o(t)\concat\<h_{t,k}\>)[h_{t,k,l}] : t\concat\<k,h_{t,k},l\>\in\max(T(a\concat\<x\>))\right\}
       \]
@@
 
-% Commented out...
-I just realized that my old results concerning \congame did not assume that the point picker must pick in the intersection of all the sets chosen by O!
-In fact, O has an easy tactic for the game used in this paper on a one-point compactification of any space: just forbid the last point played, and it can never be repeated.
-So there is some hope to show that $\pl O \markwin \congame{X}{x}$ if and only if $\pl O \markwin \clusgame{X}{x}$.
-
-% \section{Further possibilities}
-
-% Note a similar characterization of \textbf{Eberlein compacts}.
-
-% \begin{thm}
-%   A space $X$ is Eberlein compact if and only if $X$ is compact and $\pl O \markwin \congame{X^2}{\Delta}$ (that is, $\pl O$ has a \textbf{Mark\"ov} winning strategy depending on only the round number and must recent move of $\pl P$).
-% \end{thm}
-
-% One might suspect a positive result to the following question.
-
-% \begin{ques}
-%   Is it true that for any compact uniform space $X$, $\pl D\markwin\proxgame{X}$ if and only if $X$ is Eberlein compact?
-% \end{ques}
-
-% A difficulty in approaching this problem arises upon realizing that $\congame{X}{H}$ and $\clusgame{X}{H}$ are not equivalent for $\pl O$ in the case of limited-information strategies, even when considering just compact spaces $X$ with $H$ being a singleton.
-
-% \begin{ex}
-% Let $\oneptcomp{\omega_1}=\omega_1\cup\{\infty\}$ be the one-point compactification of discrete $\omega_1$ by declaring complements of finite subsets of $\omega_1$ to be open.
-(Such spaces are also known as \textbf{Fort spaces}.) Then $\pl O\win\congame{\oneptcomp\omega_1}{\infty}$ and $\pl O\markwin\clusgame{\oneptcomp\omega_1}{\infty}$, but $\pl O\not\markwin\congame{\oneptcomp\omega_1}{\infty}$.
-% \end{ex}
-
-% \begin{proof}
-%   The perfect information winning strategy for $\pl O$ in $\congame{\oneptcomp\omega_1}{\infty}$ is evident: each round, $\pl O$ chooses the complement of all non-$\infty$ points chosen by $\pl P$.
-Since any legal attack by $\pl P$ cannot reside in a finite subset of $\omega_1$, any open neighborhood of $\infty$ contains all but finitely many points chosen by $\pl P$.
-
-%   To see that $\pl O\markwin\clusgame{\oneptcomp\omega_1}{\infty}$, let $A_{\alpha,n}$ be a finite set such that $A_{\alpha,n}\subseteq A_{\alpha,n+1}$ and $\bigcup_{n<\omega}A_{\alpha,n}=\alpha+1$ for each $\alpha<\omega_1$.
-We define the Mark\"ov strategy $\sigma$ for $\pl O$ in $\clusgame{\oneptcomp\omega_1}{\infty}$ by letting $\sigma(\alpha,n)=\oneptcomp{\omega_1}\setminus \bigcup_{m\leq n}A_{\alpha,m}$.
-Note that for any arbitrary $\{\alpha_0,\dots,\alpha_{k-1}\}\in [\omega_1]^{<\omega}$, there is some round $n$ such that $\{\alpha_0,\dots,\alpha_{k-1}\}\setminus \bigcup_{m\leq n,i<k}A_{\alpha_i,m}=\emptyset$, and thus no legal attack by $P$ can keep its range completely within $\{\alpha_0,\dots,\alpha_{k-1}\}$.
-
-%   Finally, $\pl O\not\markwin\congame{\oneptcomp\omega_1}{\infty}$ was shown by Nyikos in \cite{nclasses}.
-% \end{proof}
-
 \begin{thebibliography}{99}
@@
   \emph{Proximal and semi-proximal spaces}, preprint.
-% \bibitem{nclasses}
-%   Nyikos, Peter.
-%   \emph{Classes of compact sequential spaces}.
-%   etc.
 \end{thebibliography}

### 2014-01-08 articles/proximity-corson/proximity-corson.tex
G update to paper
Final tweaks to article

@@
 \documentclass{amsart}
+% \documentclass[preprint]{elsarticle}
+\usepackage{amsmath}
+\usepackage{amsthm}
 \usepackage{amssymb}
@@
 
+% \title{Proximal compact spaces are Corson compact\tnoteref{t1}}
+% \tnotetext[t1]{2010 Mathematics Subject Classification. 54E15, 54D30, 54A20.}
 \title{Proximal compact spaces are Corson compact}
+
+% \author[aub]{S.~Clontz\fnref{fn1}}
+% \ead{steven.clontz@auburn.edu}
+% \author[aub]{G.~Gruenhage\fnref{fn2}}
+% \ead{gruengf@auburn.edu}
+
+% \address[aub]{Department of Mathematics, Auburn University,
+%  Auburn, AL 36830}
 
@@
 \keywords{Proximal, absolutely proximal, Corson compact, uniform space, $W$-space}
+% \begin{keyword}
+%   Proximal\sep absolutely proximal\sep Corson compact\sep uniform space\sep $W$-space
+% \end{keyword}
 
@@
 A common generalization of metric spaces is the idea of a \term{uniform space}.
-A uniform space is a determined by a collection of supersets of the diagonal in the square (called ``entourages")  satisfying certain conditions.
+A uniform space is a determined by a collection of supersets of the diagonal in the square (called \term{entourages})  satisfying certain conditions.
 A uniformity induces in a natural way a topology on $X$, called the \term{uniform topology}.
@@
 Bell has shown that proximal spaces are collectionwise normal, countably paracompact, and have strong preservation properties, particularly, closed subpaces and  $\Sigma$-products of proximal spaces are  proximal \cite{b}.
+The power of these results is illustrated by the fact that the difficult result, due independently to M.E.
+Rudin \cite{ru} and S.P.
+Gul'ko \cite{gu}, that $\Sigma$-products of metrizable spaces are normal, follows as an immediate corollary.
 
@@
   A \term{uniform space} is a pair $\<X,\mc{D}\>$ where $X$ is a set, and $\mc{D}$ is a uniformity.
-A \term{uniformity} is a filter on subsets of $X^2$, called \term{entourages}, such that for each entourage $D\in \mc D$:
+A \term{uniformity} is a filter (see e.g.
+\cite{k}) on subsets of $X^2$, called \term{entourages}, such that for each entourage $D\in \mc D$:
   \begin{itemize}
@@
 \begin{defn}
-  A uniform space $(X,\mathcal D)$ is said to be \term{proximal} if and only if $\pl D\win\proxgame{X}$.
+  A uniform space $\<X,\mathcal D\>$ is said to be \term{proximal} if and only if $\pl D\win\proxgame{X}$.
 A topological space is \term{proximal} iff it admits  a compatible uniformity (i.e., one which induces its topology) which is proximal.
@@
 
-Since proximal spaces are closed under closed subsets and $\Sigma$-products, it follows (as noted by Nyikos) that
+Since proximal spaces are closed under closed subsets and $\Sigma$-products \cite{b}, it follows (as noted by Nyikos) that
 every Corson compact is proximal.
@@
   \emph{An infinite game with topological consequences}, preprint.
+
 \bibitem{e}
@@
 
+\bibitem{gu} S.P. Gul'ko, \emph{On properties of sets lying in $\Sigma$-products}, Dokl. Akad. Nauk. SSSR 237(1977), 505--508, Soviet Math. Dokl. 18(1977), 1438--1442.
+
+\bibitem{k}
+K. Kunen,
+\emph{Set theory. An introduction to independence proofs.},
+Studies in Logic and the Foundations of Mathematics, 102, North-Holland Publishing Co., Amsterdam, 1983.
+
 \bibitem{nproximal}
@@
   \emph{Proximal and semi-proximal spaces}, preprint.
+
+\bibitem{ru} M.E. Rudin, \emph{The shrinking property}, Canad. Math. Bull. 26(1983), no. 4, 385-388.
+
 \end{thebibliography}

### 2014-01-08 articles/proximity-corson/proximity-corson.tex
remove filter reference to kunen

@@
   A \term{uniform space} is a pair $\<X,\mc{D}\>$ where $X$ is a set, and $\mc{D}$ is a uniformity.
-A \term{uniformity} is a filter (see e.g.
-\cite{k}) on subsets of $X^2$, called \term{entourages}, such that for each entourage $D\in \mc D$:
+A \term{uniformity} is a filter on subsets of $X^2$, called \term{entourages}, such that for each entourage $D\in \mc D$:
   \begin{itemize}
@@
 
-Since proximal spaces are closed under closed subsets and $\Sigma$-products \cite{b}, it follows (as noted by Nyikos) that
-every Corson compact is proximal.
+Since proximal spaces are closed under closed subsets and $\Sigma$-products \cite{b}, it follows (as noted by Nyikos) that every Corson compact is proximal.
 
@@
 
-\bibitem{k}
-K. Kunen,
-\emph{Set theory. An introduction to independence proofs.},
-Studies in Logic and the Foundations of Mathematics, 102, North-Holland Publishing Co., Amsterdam, 1983.
+% \bibitem{k}
+% K. Kunen,
+% \emph{Set theory. An introduction to independence proofs.},
+% Studies in Logic and the Foundations of Mathematics, 102, North-Holland Publishing Co., Amsterdam, 1983.
 

### 2014-01-20 todo.tex
Updated todos

@@
       \begin{itemize}
-        \item Read paper by Bell
-        \item Investigate k-tacts and k-Mark for one-point compactifications
+        \item Question: predetermined strategy for D on abs. proxmial space, does that imply predetermined strategy for O in con(X,H) for H compact.
+        \item Is proximal game properties preserved under perfect maps? Or, compact proximal preserved under continuous.
+        \item Alexandrof duplicate of unit interval: EC, not metrizable, what about Markov proximal?
       \end{itemize}

### 2014-02-27 todo.tex
Update todo, fix strong => absolute

--- 2013-11-24 todo.tex
@@
       \begin{itemize}
-        \item Read paper by Bell
-        \item Investigate k-tacts and k-Mark for one-point compactifications
+        \item Does predetermined strategy for D on abs. proxmial space, imply predetermined strategy for O in con(X,H) for H compact?
+        \item Is proximal game properties preserved under perfect maps? Or, compact proximal preserved under continuous.
+        \item Does the one-point compactification of ladder omega_1 space have Markov strategy? (Try ladder space where
+              nth rung is limit+n => is a Moore space and has G_delta diagonal)
+        \item Does the Michael line have a predetermined/Markov strategy?
+        \item Uniformly locally compact plus predtermiend implies metrizable unifomrity.
       \end{itemize}

### 2014-04-22 articles/proximity-corson/proximity-corson.tex
first round of revisions

@@
 
-We quickly note a couple properites of $\frac{1}{2}D$.
+We quickly note two properites of $\frac{1}{2}D$.
 
 \begin{prop}
-  If $x\in \frac{1}{2}D[y]$ and $y\in \frac{1}{2}D[z]$, then $x\in D[z]$
+  If $x\in \frac{1}{2}D[y]$ and $y\in \frac{1}{2}D[z]$, then $x\in D[z]$.
 \end{prop}
@@
 
-The theory of proximal uniform spaces relies on the following $\omega$-length game:
+The theory of proximal uniform spaces relies on the following $\omega$-length 
+game introduced in \cite{b}:
 
@@
   At the conclusion of the game, $\pl D$ wins if either $\bigcap_{n<\omega}D_n[p_n]=\emptyset$ or $\<p_0,p_1,\dots\>$ converges, and $\pl P$ wins otherwise.
+  \footnote{It's worth noting that a widely distributed preprint of Bell's 
+  paper considered $4D_n$ in place of $D_n$ for the winning
+  condition; however, it's easily verified that player $\pl D$
+  has a winning strategy in one if and only if she has a winning strategy in
+  the other.}
 \end{defn}
 
-The reader familiar with proximal spaces may note that this definition is different than the original formulation of the game (see \cite{b}); however, it is easily verified that $\pl D$ has a winning strategy in the original game if and only if $\pl D$ has a winning strategy in our version.
-Also, if we wish we may assume that if $\sigma$ is a winning strategy for $\pl D$, then $D_{n+1}=\sigma (x_0,x_1,...,x_n)$ is contained in something smaller than $D_n$, e.g., $\frac{1}{4}D_n$.
+We may assume that if $\sigma$ is a winning strategy for $\pl D$, then $D_{n+1}=\sigma (x_0,x_1,...,x_n)$ is contained in something smaller than $D_n$, e.g., $\frac{1}{4}D_n$.
 That is because a sequence of legal moves by $\pl P$ with $\pl D$ using the refined strategy is also a legal sequence of moves with $\pl D$ using the original strategy.
@@
 \begin{defn}
-  If a player $\pl P$ has a winning strategy in a game $G$, we write $\pl P\win G$. Otherwise, we write $\pl P\not\win G$.
+  If a player $\pl A$ has a winning strategy in a game $G$, we write $\pl A\win G$. Otherwise, we write $\pl A\not\win G$.
 \end{defn}
@@
         =
-      \{x\in \mathbb{R}^\kappa: |\{\alpha:x(\alpha)\not=0\}|<\omega\}
+      \{x\in \mathbb{R}^\kappa: |\{\alpha:x(\alpha)\not=0\}|\leq\omega\}
     \]
@@
 \begin{proof}
-  Let $\sigma$ be a winning strategy for $\pl D$ in the absolutely proximal game such that $p\supsetneq q$ implies $\sigma(p)\subset \frac{1}{4}\sigma(q)$.
-  For any sequence $t=\<t_0,t_1,\dots\>$, let $o(t)$ be the subsequence of $t$ consisting of its odd-indexed terms.
-
-  For certain finite sequences $s$ in $X$, we will define by induction a tree $T(s)$ of finite height such that $t\supset s$ implies $T(s)$ is a subtree of $T(t)$, and if $u$ is a node of $T(s)$ having successors in $T(s)$, then $u$ has no new successors in $T(t)$.
-We let $\max(T)$ denote the nodes of $T$ that have no successors in $T$.
+  Let $\sigma$ be a winning strategy for $\pl D$ in the absolutely proximal 
+  game such that $p\supsetneq q$ implies $\sigma(p)\subseteq \frac{1}{4}\sigma(q)$.
+  For any sequence $t=\<t_0,t_1,\dots\>$, let $o(t)=\<t_1,t_3,\dots\>$ 
+  be the subsequence of $t$ 
+  consisting of its odd-indexed terms. We proceed by constructing a winning
+  strategy for $\pl O$ in $\clusgame{X}{H}$. Since $\pl O\win\clusgame{X}{H}$ 
+  if and only if $\pl O\win\congame{X}{H}$, the result will follow.
 
@@
 
-First we define $T(\emptyset)$.
+First we define a tree $T(\emptyset)$. Our aim is to define an open set
+  \[
+    \bigcup_{i,j<m_\emptyset}
+      \frac{1}{4}\sigma(\<h_{\emptyset,i}\>)[h_{\emptyset,i,j}]
+    =
+    \bigcup_{\<i,h_{\emptyset,i},j\>\in\max(T(\emptyset))} 
+      \frac{1}{4}\sigma(o(\emptyset)\concat\<h_{\emptyset,i}\>)[h_{\emptyset,i,j}]
+  \]
+which contains $H$, and $\pl O$ will use this as the inital move in her winning 
+strategy for $\clusgame{X}{H}$.
 
   \begin{itemize}
-    \item Let $\emptyset\in T(\emptyset)$.
     \item Choose $m_\emptyset<\omega$, $h_{\emptyset,i}\in H$ for $i<m_\emptyset$, and $h_{\emptyset,i,j}\in H\cap\cl{\frac{1}{4}\sigma(\emptyset)[h_{\emptyset,i}]}$ for $i,j<m_\emptyset$ such that
@@
     is a cover for $H\cap\cl{\frac{1}{4}\sigma(\emptyset)[h_{\emptyset,i}]}$.
-    \item Let $\<i\>, \<i,h_{\emptyset,i}\>$, and $\<i,h_{\emptyset,i},j\>$ be in $T(\emptyset)$ for $i,j<m_\emptyset$.
+
+    (The indexings $i\mapsto h_{\emptyset,i}$ and 
+    $\<i,j\>\mapsto h_{\emptyset,i, j}$ need not be 
+    one-to-one; repetition of points is allowed.)
+    \item Let $\<i,h_{\emptyset,i},j\>$ and its initial segments be in 
+    $T(\emptyset)$ for $i,j<m_\emptyset$.
   \end{itemize}
-This ends the construction of $T(\emptyset)$.   We remark that the indexings $i\mapsto h_{\emptyset,i}$ and $\<i,j\>\mapsto h_{\emptyset,i, j}$ need not be one-to-one; repetition of points is allowed.
 
@@
 
-  Now suppose $T(a)$ is defined. We then define $T(a\concat\<x\>)$, etc., for
+Now suppose that $a$ is a finite 
+sequence of moves by $\pl P$ in $\clusgame{X}{H}$ for which $\pl O$ replied with
   \[
-      x\in \bigcup_{s\concat\<i,h_{s,i},j\>\in\max(T(a))} \frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]
+    \bigcup_{s\concat\<i,h_{s,i},j\>\in\max(T(a))} 
+      \frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]
   \]
-  as follows:
+as a part of her winning strategy for some tree $T(a)\supseteq T(\emptyset)$. 
+As we will soon guarantee, any nonempty $s$ will be of the form 
+$\<i_0,h_0,j_0,x_0,\dots\>$ so that 
+$o(s)\concat\<h_{s,i}\> = \<h_0,x_0,\dots,h_{s,i}\>\in X^{<\omega}$ 
+corresponds to a partial attack against $\sigma$ by the proximal game's $\pl P$. 
+We then define $T(a\concat\<x\>)$ for each of the legal responses
+  \[
+    x\in 
+      \bigcup_{s\concat\<i,h_{s,i},j\>\in\max(T(a))} 
+      \frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]
+  \]
+by the clustering game's $\pl P$ as follows:
 
   \begin{itemize}
-    \item Let $T(a)\subseteq T(a\concat\<x\>)$.
-    \item Choose $t=s\concat\<i,h_{s,i},j,x\>$ such that $s\concat\<i,h_{s,i},j\>\in\max(T(a))$ and $x\in \frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]$.
-Then $s\concat\<i,h_{s,i},j\>$ is the only node of $T(a)$ that will be extended in this step.
+    \item Fix $s\concat\<i,h_{s,i},j\>\in\max(T(a))$ such that 
+      $x\in \frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]$.  
+      Then $s\concat\<i,h_{s,i},j\>$ is the only node of $T(a)$ that will be 
+      extended in this step. Let $t=s\concat\<i,h_{s,i},j,x\>$.
     \item Note that, assuming $o(s)\concat\<h_{s,i}\>$ is a legal partial attack against $\sigma$, then
@@
     and thus $o(t)\concat\<h_{t,k}\>$ is a legal partial attack against $\sigma$.
-    \item For each $k,l<m_t$, put $t\concat\<k,h_{t,k},l\>$ and all of its initial segments in $ T(a\concat\<x\>)$.   This completes the construction of  $ T(a\concat\<x\>)$.
+
+    \item Let $T(a\concat\<x\>)\supseteq T(a)$, and for each $k,l<m_t$, 
+    also let $t\concat\<k,h_{t,k},l\>$ and all of its initial segments be in 
+    $T(a\concat\<x\>)$.
+  \end{itemize}
 
@@
 
-    \item Note that assuming
+ This completes the construction of  $ T(a\concat\<x\>)$. Note that assuming
     \[
@@
   covers $H$.
-  \end{itemize}
 
@@
 
-  If $p$ attacks $\tau$, then it follows that $T(p\rest n)$ is defined for all $n<\omega$, so let $T(p)=\bigcup_{n<\omega} T(p\rest n)$. We note $T(p)$ is an infinite tree with finite levels:
+  If $p$ is an attack by $\pl P$ against $\tau$, then it follows that $T(p\rest n)$ is defined for all $n<\omega$, so let $T(p)=\bigcup_{n<\omega} T(p\rest n)$.
+We note $T(p)$ is an infinite tree with finite levels:
     \begin{itemize}
@@
 Then since $o(q)$ is a subsequence of $p$, $p$ must cluster at $H$.
-
-  Since $\pl O\win\clusgame{X}{H}$ if and only if $\pl O\win\congame{X}{H}$, the result follows.
 \end{proof}

### 2014-04-28 phd/dissertation/appendix1.tex
Initial dissertation commit

%!TEX root = dissertation.tex
% ^ leave for LaTeXTools build functionality

\appendix
\chapter*{Appendices\addcontentsline{toc}{chapter}{Appendices}}

\chapter{Notes on the style-file project}

\begin{singlespace}
These style-files have been modified by Christopher Wilson to support the new Electronic Thesis and Dissertation process. The following was written before the ETD guidelines update on Fall 2009. Changes to the original appendix have been shown in italics.

These style-files for use with \LaTeX{} {\it were} maintained by Darrel
Hankerson\footnote{Mathematics and Statistics, 221 Parker Hall,
844-3641, {\tt hankedr@auburn.edu}} and Ed
Slaminka\footnote{Mathematics and Statistics, 218 Parker,
{\tt slamiee@auburn.edu}}.

In 1990, department heads and other representatives met with Dean Doorenbos
and Judy Bush-Crofton (then responsible for manuscript approval). This
meeting was prompted by a memorandum\footnote{Originally, the memorandum
was presented to Professor Larry Wit. A copy is available on request.} from
members of the mathematics departments concerning the {\em Thesis and
Dissertation Guide\/} and the approval process. There was wide agreement
among the participants (including Dean Doorenbos) to support the basic
recommendations outlined in the memorandum. The revised {\em Guide\/}
reflected some (but not all) of the agreements of the meeting.

Ms Bush-Crofton was supportive of the plan to obtain ``official approval''
of these style files.\footnote{Followup memoranda gave a definition of
``official approval.'' Copies will be sent on request.}  Unfortunately, Ms
Bush-Crofton left the Graduate School before the process was completed. In
1994, we were revisiting some of the same problems which were
resolved at the 1990 meeting.

In Summer 1994, I sent several memoranda to Ms Ilga Trend of the Graduate
School, reminding her of the agreements made at the 1990 meeting.
Professors A. Scottedward Hodel and Stan Reeves provided additional
support.  In short, it is essential that the Graduate School honor its
commitments of the 1990 meeting. It should be emphasized that Dean
Doorenbos is to thank for the success of that meeting.

Maintaining these \LaTeX{} files has been more work than expected, in
part due to continuing changes in requirement by the graduate school.
The Graduate School occasionally has complete memory loss about the
agreements of the 1990 meeting. If the Graduate School rejects your
manuscript based on items controlled by the style-files, ask
your advisor to contact the Graduate school (and copy to me) to urge
cooperation.

Finally, there have been several requests for additions to the package
(mostly formatting changes for figures, etc.). While such changes are not
really part of the thesis-style package, it could be beneficial to collect
these options and distribute with the package (making it easier on the next
student).  I'm especially interested in changes needed by various
departments.
\end{singlespace}

### 2014-04-28 phd/dissertation/bibliography.tex
Initial dissertation commit

%!TEX root = dissertation.tex
% ^ leave for LaTeXTools build functionality

%%%%%%%%Two options for having a bibliography. If you use a separate file or multiple files:
%\bibliography{./robotics,./imageprocessing,./thesis}
%%%%% where the files are robotics.bib, imageprocessing.bib and/or thesis.bib.

%Or you can include the bibliography entries directly:

\begin{thebibliography}{99}

\bibitem{hahn} Jane Hahn, ``\LaTeX{} For Everyone,'' Personal TeX Inc., 
  12 Madrona Street, Mill Valley, California.

\bibitem{goossens} Frank Mittelbach and Michel Goossens (with
Johannes Braams, David Carlisle, and Chris Rowley),
  ``The \LaTeX{} Companion,'' second edition, Addison-Wesley, 2004.

\bibitem{GRM:LaTeXGraphicsCompanion} 
Michal Goossens, Sabastian Rahtz, and Frank Mittelbach, ``The \LaTeX{} 
Graphics Companion,'' Addison-Wesley, 1997.

\bibitem{Gra:MathIntoLaTeX} George Gr\"atzer, ``Math into \LaTeX: An 
introduction to \LaTeX{} and \mbox{\AmS-\LaTeX},'' Birkh\"auser, 1996.

\bibitem{hoenig} Alan Hoenig, ``\TeX{} Unbound: \LaTeX{} and \TeX{} strategies
for Fonts, Graphics, and More,'' Oxford University Press, 1997. Includes
practical advice and numerous exammples for a wide range of topics,
includeing virtual fonts, graphics, and resources for the internet and
multimedia.

\bibitem{KH} Helmut Kopka and Patrick W. Daly, ``A Guide to \LaTeXe:
  Document Preparation for Beginners and Advanced Users,'' 2nd ed.,
  Addison-Wesley, 1995.

\bibitem{lamport} Leslie Lamport, ``\LaTeX: A Document Preparation
  System,'' 2nd ed., Addison-Wesley, 1994.

\bibitem{walsh} Norman Walsh, ``Making \TeX{} Work,'' O'Reilly and
  Associates, 1994.

\end{thebibliography}

### 2014-04-28 phd/dissertation/chapter1.tex
Initial dissertation commit

%!TEX root = dissertation.tex
% ^ leave for LaTeXTools build functionality

\chapter{Introduction}

Basic overview of combinatorial games, topological games, limited info strategies,
and applications in topology.

% \section{heading}

% \subsection{other heading}

### 2014-04-28 phd/dissertation/chapter2.tex
Initial dissertation commit

%!TEX root = dissertation.tex
% ^ leave for LaTeXTools build functionality

\chapter{Toplogical Games and Strategies\\ of Perfect and Limited Information}

Definitions and conventions for dealing with topological games and strategies.

### 2014-04-28 phd/dissertation/chapter5.tex
Initial dissertation commit

--- 2013-10-28 phd/menger.tex
@@
-\input{../header.tex}
-
-\begin{document}
-
-  \centerline{Menger}
+%!TEX root = dissertation.tex
+% ^ leave for LaTeXTools build functionality
+
+\chapter{Menger Game}
+
+Results pertaining to the Menger game characterizing the Menger property.
+
+\section{cut-and-paste}
 
@@
 We generalize Scheeper's proof to handle a number of cases.
-
-  % \begin{definition}
-  %   A space $X$ is $H$-closed if for every open cover of $X$, there exists a finite subset of the cover whose union is dense in $X$.
-  % \end{definition}
-
-  % \begin{proposition}
-  %   For regular spaces, $X$ is $H$-closed if and only if $X$ is compact.
-  % \end{proposition}
-
-  % \begin{proof}
-  %   The backward implication is trivial, so let $X$ be $H$-closed.
-For any open cover $\mc U$ of $X$ and point $x\in X$, choose $x\in V_x\subseteq \cl{V_x}\subseteq U_x\in \mc U$.
-Then if $\mc F = \{V_{x_i}:i<n\}$ is a finite subset of $\mc V=\{V_x:x\in X\}$ with dense union in $X$, then $\mc G = \{U_{x_i}:i<n\}\subseteq \mc U$ is a finite subcover of $X$.
-  % \end{proof}
 
@@
   \end{corollary}
+
+\newpage
+
+  \centerline{Alster, Hurewicz}
+
+  Besides various limited information characterizations of $\mengame{X}$, there are other interesting covering properties between $\sigma$-(relatively compact) and Menger.
+
+  \begin{definition}
+    A colleciton of subsets of a space $X$ is (\textbf{really}) \textbf{ample} if has a finite subcover for each (relatively) compact subset of $X$.
+  \end{definition}
+
+  \begin{proposition}
+    Every ample cover of a regular space $X$ is really ample.
+  \end{proposition}
+
+  \begin{proof}
+    Every relatively compact set $R$ is a subset of the compact set $\overline{R}$.
+  \end{proof}
+
+  \begin{definition}
+    A space $X$ is (\textbf{relatively}) \textbf{Alster} if there exists a countable subcover for each (really) ample cover of $X$ by $G_\delta$ sets.
+  \end{definition}
+
+  \begin{proposition}
+    Every regular relatively Alster space is Alster.
+  \end{proposition}
+
+  \begin{theorem}
+    $X$ $\sigma$-compact $\Rightarrow$ $X$ Alster $\Rightarrow$ $X$ Menger
+  \end{theorem}
+
+  \begin{proof}
+    Due to Leandro F. Aurichi and Franklin D. Tall in ``Lindel\"of spaces which are indestructible, productive, or D''.
+  \end{proof}
+
+  \begin{proposition}
+    $X$ $\sigma$-(relatively compact) $\Rightarrow$ $X$ relatively Alster $\Rightarrow$ $X$ Menger
+  \end{proposition}
+
+  \begin{proof}
+    If $X$ is $\sigma$-(relatively compact), then there exists a countable subcover for every really ample cover of $X$ by arbitrary sets.
+
+    If $X$ is relatively Alster, we adapt Aurichi and Tall's argument for the previous theorem.
+
+    Since relatively Alster implies Lindel\"of (all open covers of $X$ are relatively ample by definition of relatively compact), it is sufficient to consider open covers $\mc U_n = \{ U_n^m : m<\omega\}$ such that $U_n^m\subseteq U_n^{m+1}$.
+Then $\mc G=\{\bigcap_{n<\omega} U_n^{f(n)} : f\in \omega^\omega\}$ is a $G_\delta$ cover.
+To see that $\mc G$ is relatively ample, note for each relatively compact $K$ in $X$, $K$ is covered by something in each $\mc U_n$, and thus there is $f_K(n)\in\omega^\omega$ such that $K\subseteq \bigcap_{n<\omega} U_n^{f_K(n)}$.
+
+    By relatively Alster, let $f_m\in\omega^\omega$ for $m<\omega$ so that $\mc G'=\{\bigcap_{n<\omega} U_n^{f_m(n)}:m<\omega\}$ covers $X$.
+
+    Then let $\mc F_n = \{U_n^{f_m(n)}:m\leq n\}\in[\mc U_n]^{<\omega}$.
+Note that if $x\in X$, then $x\in \bigcap_{n<\omega} U_n^{f_{m_x}(n)}$ for some $m_x<\omega$ as $\mc G'$ is a cover.
+Thus $x\in U_{m_x}^{f_{m_x}(m_x)}$ and is covered by $\mc F_{m_x}$.
+  \end{proof}
+
+  \begin{example}
+    Let the real numbers $R$ be given the topology generated by open intervals with countable sets removed.
+$R$ is not relatively Alster and $F\win\mengame{R}$.
+If $S(2^\omega,\omega,\omega)$ holds, then $F\kmarkwin{2}\mengame{R}$.
+  \end{example}
+
+  \begin{proof}
+    Since points are $G_\delta$ and its relatively compact sets are all finite, a cover by singletons is really ample and has no countable subcover, showing $R$ is not relatively Alster.
+
+    It was proven earlier that $F\win\mengame{R}$. Assuming $S(2^\omega,\omega,\omega)$, we construct a $2$-Mark\"ov strategy by first defining the following:
+      \begin{itemize}
+        \item Let $z_n$ enumerate the integers for $n<\omega$.
+        \item For each open cover $\mc V$ of $R$, let $A(\mc V)$ be a countable set such that $[z_n,z_n+1)\setminus A(V)$ is $\mc V$-compact for each $n<\omega$.
+        \item Let $f_A:A\to\omega$ for $A\subseteq R$ witness $S(2^\omega,\omega,\omega)$.
+      \end{itemize}
+
+    Then we may define $\sigma(\mc U_0,0)=\emptyset$ and define $\sigma(\mc U_n,\mc U_{n+1},n+1)$ such that it covers each of the following:
+      \[
+        \left(\bigcup_{m\leq n} [z_m,z_m+1)\right) \setminus A(\mc U_{n+1})
+      \]
+      \[
+        \{f_{A(\mc U_{n+1})}^{-1}(m) : m\leq n\}
+      \]
+      \[
+        \{x \in A(\mc U_n)\cap A(\mc U_{n+1}) : f_{A(\mc U_{n})}(x)\not= f_{A(\mc U_{n+1})}(x)\}
+      \]
+
+    For any attack $\mc U_0,\mc U_1,\dots$ on $\sigma$, let $x\in[z_n,z_n+1)$. 
+      \begin{itemize}
+        \item If $x\not\in A(\mc U_{n+1})$, then $x$ is covered in round $n+1$.
+        \item If $x\in A(\mc U_{n+1})$, let $N=f_{A(\mc U_{n+1})}(x)$. 
+        \begin{itemize}
+          \item If $N\leq n$, then $x$ is covered in round $n+1$.
+          \item If $N>n$ and $N=f_{A(\mc U_{p+1})}(x)$ for all $p\geq n$, then $x$ is covered in round $N$.
+          \item If $N>n$ and $N\not=f_{A(\mc U_{p+1})}(x)$ for some $p>n$, then $x$ is covered in round $p+1$.
+        \end{itemize}
+      \end{itemize}
+  \end{proof}
+
+  \begin{definition}
+    A space $X$ is \textbf{Hurewicz} if for each sequence of open covers $\mc U_n$, there are $\mc F_n \in [\mc U_n]^{<\omega}$ such that $X=\bigcup_{m<\omega}\bigcap_{m\leq n<\omega}\cup\mc F_n$.
+  \end{definition}
 
@@
   \end{proof}
-
-\end{document}

### 2014-04-30 phd/dissertation/chapter2.tex
outline of games chapter
Begun work on chapter 2

@@
 
-Definitions and conventions for dealing with topological games and strategies.
+The goal of this paper is to explore the applications of limited information
+strategies in existing topological games. (TODO: History of combinatorical
+and topological games?)
+
+\section{Games}
+
+Intuitively, the games studied in this paper are two-player games for which
+each player takes turns making a choice from a set of possible moves. At
+the conclusion of the game, the choices made by both players are examined,
+and one of the players is declared the winner of that playthrough, with
+no ties allowed.
+
+Games may be modeled mathematically in various ways (TODO: cite digraph model)
+but we will find it convenient to think of them as follows.
+
+\begin{defn}
+  A \term{game} is a tuple $\<M,W\>$ such that 
+  $W\subseteq (M^{\omega})^2$. $M$ is set of \term{moves} for
+  the game, and $(M^{\omega})^2$ is the set of all possible 
+  \term{playthroughs} of the game.
+
+  $W$ is the set of \term{winning} playthroughs for the 
+  first player, and $(M^{\omega})^2\setminus W$ is the set of winning
+  playthroughs for the second player.
+\end{defn}
+
+To illustrate this definition, we may formally model the well-known game 
+Tic-Tac-Toe. Imagine that the game board is labeled as a ``magic square''
+of the numbers $0$ through $8$. (TODO: image) Then writing $X$ or $O$ on
+the game board is equivalent to choosing a number $0$ through $8$, and 
+getting a ``tic-tac-toe'' is equivalent to having chosen three numbers which 
+sum to $12$.
+
+\begin{game}
+  Let $\tttgame$ denote the game \term{Tic-Tac-Toe}, with players $\pl X$ 
+  and $\pl O$.
+
+  The moves $M$ for the game are the first nine non-negative 
+  integers $\{0,\dots,8\}$. The winning playthroughs $W$ for $\pl X$ 
+  consist of pairs of sequences $\<X,O\>$ such that $X\geq\<X_0,\dots,X_4\>$,
+  $O\geq\<O_0,\dots,O_3\>$, and any of the following hold:
+    \begin{itemize}
+      \item There exists some $k<4$ such that $\<X_0,O_0,\dots,X_k\>$ contains
+            no repeated integers, but $\<X_0,O_0,\dots,X_k,O_k\>$ does.
+
+            ($\pl O$ drew her mark on a space already occupied.)
+      \item There exists $i<j<k<5$ such that $\<X_0,O_0,\dots,X_4\>$ contains 
+            no repeated integers and $X_i+X_j+X_k=12$, and for all
+            $i'<j'<k'<k$ it follows that $O_{i'}+O_{j'}+O_{k'}\not=12$.
+
+            ($\pl X$ did not draw her mark on a space that was already occupied,
+            and was able to secure a ``tic-tac-toe'' before $\pl O$.)
+            \footnote{
+              The observant reader will note that in this formulation of 
+              Tic-Tac-Toe, player $\pl O$ wins ``cat's games'' where neither 
+              player secures a ``tic-tac-toe'' (since no ties are allowed).
+            }
+    \end{itemize}
+\end{game}
+
+Due to the tedium of defining games explicitly from the definition, we 
+typically define games by declaring the \term{rules} that each player must 
+follow (e.g. players may not make a mark on a space which was already marked)
+and the \term{winning condition} for the first player (e.g. $\pl X$ secures
+a ``tic-tac-toe'' before $\pl O$). Then a playthrough is in $W$ if either 
+the first player made only \term{legal moves} which observed the game's rules
+and the playthrough satisifies the winning condition, or the second player
+made an \term{illegal move} which contradicted the game's rules.
+
+Often, players should not be able to choose from the same set of moves
+(e.g. player Black cannot move White's pieces in chess), in which case $M$ may
+be partitioned into two sets $M_0,M_1$ and the rules for the game may be defined
+such that each player may only choose from one of those sets 
+(e.g. Black will automatically lose if she moves one of White's pieces).
+
+An artifact of this game model is that games never technically end, since 
+playthroughs of the game are infinite sequences. Nonetheless, Tic-Tac-Toe
+is always decided by $\pl X$'s fifth move, and in chess, there is also an
+upper bound for the length of a game due to the finite number of ways pieces
+may be positioned on the chessboard (and the ``threefold rule''
+which declares the game finished if the same position is repeated three times).
+
+But a two-player game need not have a bounded number of rounds, as is
+demonstrated by this game due to John Conway:
+
+\begin{game}
+  The game ...
+\end{game}
+
+\subsection{Infinite Games}
+
+\subsection{Topological Games}
+
+\section{Strategies}
+
+\subsection{Perfect Information}
+
+\subsection{Limited Information}
+
+\section{Examples of Topological Games}

### 2014-04-30 phd/dissertation/chapter3.tex
Initial dissertation commit
Begun work on chapter 2

--- 2013-01-24 phd_research_results.tex
@@
-\documentclass[11pt]{article}
+%!TEX root = dissertation.tex
+% ^ leave for LaTeXTools build functionality
 
-\pdfpagewidth 8.5in
-\pdfpageheight 11in
+\chapter{Convergence/clustering games}
 
-\setlength\topmargin{0in}
-\setlength\headheight{0in}
-\setlength\headsep{0.2in}
-\setlength\textheight{8in}
-\setlength\textwidth{6in}
-\setlength\oddsidemargin{0in}
-\setlength\evensidemargin{0in}
-\setlength\parindent{0.25in}
-\setlength\parskip{0.1in}
+Results related to Gruenhage's ``W''-convergence game and variants.
 
-\usepackage{amssymb}
-\usepackage{amsfonts}
-\usepackage{amsmath}
-\usepackage{mathtools}
-\usepackage{amsthm}
+\section{Basic game}
 
-      \theoremstyle{plain}
-      \newtheorem{theorem}{Theorem}
-      \newtheorem{lemma}[theorem]{Lemma}
-      \newtheorem{corollary}[theorem]{Corollary}
-      \newtheorem{proposition}[theorem]{Proposition}
-      \newtheorem{conjecture}[theorem]{Conjecture}
-      \newtheorem{question}[theorem]{Question}
-      \newtheorem{example}[theorem]{Example}
-
-      \theoremstyle{definition}
-      \newtheorem{definition}[theorem]{Definition}
-
-      \theoremstyle{remark}
-      \newtheorem{remark}[theorem]{Remark}
-
-% Strategy uparrow shortcuts
-\newcommand{\prewin}{\uparrow_{\text{pre}}}
-\newcommand{\markwin}{\uparrow_{\text{mark}}}
-\newcommand{\tactwin}{\uparrow_{\text{tact}}}
-\newcommand{\ktactwin}[1]{\uparrow_{#1\text{-tact}}}
-\newcommand{\kmarkwin}[1]{\uparrow_{#1\text{-mark}}}
-\newcommand{\codewin}{\uparrow_{\text{code}}}
-\newcommand{\limitwin}{\uparrow_{\text{limit}}}
-
-\newcommand{\oneptcomp}[1]{#1\cup\{\infty\}}
-
-\newcommand{\congame}[2]{Con_{O,P}(#1,#2)}
-\newcommand{\clusgame}[2]{Clus_{O,P}(#1,#2)}
-
-\newcommand{\pfgame}[1]{PF_{F,C}(#1)}
-
-\newcommand{\sigmaprodr}[1]{\Sigma\mathbb{R}^{#1}}
-\newcommand{\sigmaprodtwo}[1]{\Sigma2^{#1}}
-
-\begin{document}
-
-\centerline{\bf $Con_{O,P}(X,x)$}
-
-\begin{definition} 
+\begin{defn} 
 Gruenhage's open-point convergence game $\congame{X}{x}$ has $O$ choosing nested open sets and $P$ choosing a point within the last chosen open set by $O$.
 $O$ wins if the points chosen by $P$ converge to $x$.
-\end{definition}
+\end{defn}
 
-\begin{definition}
+TODO: This version of the game (where $\pl P$ need not play within all 
+previously chosen open sets) is more difficult for $\pl O$. Need to 
+differientiate these two versions somehow...
+
+\begin{defn}
 The one-point compactification of a space $X$ is $\oneptcomp{X}$, where neighborhoods of points in $X$ are the same as they were originally, and neighborhoods of $\infty$ are sets $\oneptcomp{X}\setminus K$ for compact $K$.
 If $X$ is discrete then neighborhoods of $\infty$ are cofinite sets containing $\infty$, and the game is equivalent to $O$ choosing finite ``forbidden'' sets and $P$ choosing points not forbidden by $O$.
-\end{definition}
+\end{defn}
 
-\begin{proposition}
+\begin{prop}
 $O\codewin \congame{\oneptcomp{\kappa}}{\infty}$ for all cardinals $\kappa$.
-\end{proposition}
+\end{prop}
 
@@
 
-\begin{proposition}
+\begin{prop}
 $O\prewin \congame{\oneptcomp{\omega}}{\infty}$.
-\end{proposition}
+\end{prop}
 
@@
 
-\begin{proposition}
+\begin{prop}
 $O\not\prewin \clusgame{\oneptcomp{\kappa}}{\infty}$ for $\kappa\geq\omega_1$.
-\end{proposition}
+\end{prop}
 
@@
 
-\begin{proposition}
+\begin{prop}
 $O\tactwin\congame{\oneptcomp{\omega}}{\infty}$.
-\end{proposition}
+\end{prop}
 
@@
 
-\begin{theorem}
+\begin{thm}
 If $\kappa$ is a regular uncountable cardinal, for every function $f:[\kappa]^{<\omega}\to[\kappa]^{<\omega}$ the set $C_f = \{\alpha < \kappa : S\in[\alpha]^{<\omega} \Rightarrow f(S)\in[\alpha]^{<\omega}\}$ is club.
-\end{theorem}
+\end{thm}
 
@@
 
-\begin{theorem}
+\begin{thm}
 $O\not\ktactwin{k}\clusgame{\oneptcomp{\kappa}}{\infty}$ for $\kappa\geq\omega_1$.
-\end{theorem}
+\end{thm}
 
@@
 
-\begin{theorem}
+\begin{thm}
 $O\markwin \clusgame{\oneptcomp{\omega_1}}{\infty}$.
-\end{theorem}
+\end{thm}
 
@@
 
-\begin{theorem}
+\begin{thm}
 $O\not\markwin Con_{O,P}(\omega_1\cup\{\infty\},\infty)$.
-\end{theorem}
+\end{thm}
 
@@
 
-\begin{theorem}
+\begin{thm}
 $O\not\kmarkwin{k}Clus_{O,P}(\kappa\cup\{\infty\},\infty)$ for $\kappa>\omega_1$.
-\end{theorem}
+\end{thm}
 
@@
 
-\centerline{\bf $Con_{O,P}(X,x)$ for Sigma Product}
+\section{$Con_{O,P}(X,x)$ for Sigma Product}
 
-\begin{proposition}
+\begin{prop}
 $O\uparrow\congame{\sigmaprodr{\kappa}}{\vec{0}}$.
-\end{proposition}
+\end{prop}
 
@@
 
-\begin{theorem}
+\begin{thm}
 For all cardinals $\kappa\leq 2^\omega$, $O\codewin\congame{\sigmaprodr{\kappa}}{\vec{0}}$.
-\end{theorem}
+\end{thm}
 
@@
 
-\begin{theorem}
+\begin{thm}
 Let $\kappa$ be a cardinal such that there exists a function $f:\kappa\to[\kappa]^{\leq \omega}$ where for every $W\in[\kappa]^{\leq\omega}$ there exists $\alpha_W<\kappa$ with $W\subseteq f(\alpha_W)$.
 (That is, $\textrm{cf}([\kappa]^{\leq\omega})=\kappa$.) Then $F \codewin PF_{F,C}(\kappa)$ and $O \codewin \congame{\sigmaprodr{\kappa}}{\vec{0}}$.
-\end{theorem}
+\end{thm}
 
@@
 
-\begin{theorem}
+\begin{thm}
 Let $\kappa$ be the limit of cardinals $\kappa_n$ such that $\textrm{cf}([\kappa_n]^{\leq\omega},\subseteq)=\kappa_n$.
 Then $F \codewin PF_{F,C}(\kappa)$ and $O \codewin \congame{\sigmaprodr{\kappa}}{\vec{0}}$.
-\end{theorem}
+\end{thm}
 
@@
 
-\begin{theorem}
+\begin{thm}
 $F\codewin\pfgame{\kappa}$ for all cardinals $\kappa$.
-\end{theorem}
+\end{thm}
 
@@
 
-\begin{corollary}
+\begin{cor}
 $O\codewin\congame{\sigmaprodr{\kappa}}{\vec{0}}$ for all cardinals $\kappa$.
-\end{corollary}
+\end{cor}
 
@@
 \end{proof}
-
-\end{document}

### 2014-04-30 phd/dissertation/chapter5.tex
Begun work on chapter 2

@@
 
-  \begin{definition}
+  \begin{defn}
     $X$ is \textbf{Menger} if for all open covers $\mathcal{U}_0,\mathcal{U}_1,\dots$ there exist finite subcollections $\mathcal{F}_n \subseteq \mathcal{U}_n$ such that $\bigcup_{n<\omega} \mathcal{F}_n$ is a cover of $X$.
-  \end{definition}
-
-  \begin{proposition}
+  \end{defn}
+
+  \begin{prop}
     $\sigma$-compact $\Rightarrow$ Menger $\Rightarrow$ Lindelof
-  \end{proposition}
-
-  \begin{definition}
+  \end{prop}
+
+  \begin{defn}
     In the two-player game $\mengame{X}$ player $C$ chooses open covers $\mathcal{U}_n$ of $X$, followed by player $F$ choosing a finite subcollection $\mathcal{F}_n\subseteq\mathcal{U}_n$.
 $F$ wins if $\bigcup_{n<\omega} \mathcal{F}_n$ is a cover of $X$.
-  \end{definition}
-
-  \begin{theorem}
+  \end{defn}
+
+  \begin{thm}
     $X$ is Menger if and only if $C \not\win \mengame{X}$.
-  \end{theorem}
+  \end{thm}
 
@@
 
-  \begin{proposition}
+  \begin{prop}
     $X$ is compact if and only if $F \tactwin \mengame{X}$ if and only if $F \ktactwin{k} \mengame{X}$
-  \end{proposition}
+  \end{prop}
 
@@
 
-  \begin{proposition}
+  \begin{prop}
     If $X$ is $\sigma$-compact then $F \markwin \mengame{X}$
-  \end{proposition}
+  \end{prop}
 
@@
 
-  \begin{theorem}
+  \begin{thm}
   For any topological space $X$ and all $k \geq 2$, $F \kmarkwin{k} \mengame{X}$ if and only if $F \kmarkwin{2} \mengame{X}$.
-  \end{theorem}
+  \end{thm}
 
@@
 
-  \begin{lemma}
+  \begin{lem}
     For all functions $\tau:\omega_1\times\omega \rightarrow [\omega_1]^{<\omega}$, there exists a sequence $\alpha_0, \alpha_1, \dots < \omega_1$ such that $\{\tau(\alpha_n,n): n<\omega\}$ is not a cover for $\{\beta:\forall n<\omega (\beta < \alpha_n)\}$.
-  \end{lemma}
+  \end{lem}
 
@@
 
-  \begin{example}
+  \begin{ex}
     $F \win \mengame{\oneptlind{\omega_1}}$ but $F \not\markwin \mengame{\oneptlind{\omega_1}}$.
-  \end{example}
+  \end{ex}
 
@@
 
-  \begin{definition}
+  \begin{defn}
     A set $R\subseteq X$ is relatively compact to the topological space $X$ if for every open cover of the entire space $X$, there is a finite subcover of the set $R$.
-  \end{definition}
-
-  \begin{proposition}
+  \end{defn}
+
+  \begin{prop}
     If $X$ is regular, then $Y$ is relatively compact if and only if $\cl{Y}$ is compact.
-  \end{proposition}
+  \end{prop}
 
@@
 
-  \begin{lemma}
+  \begin{lem}
     Let $\sigma(\mc{U}, n)$ be a winning Markov strategy for $F$ in $\mengame{X}$, and $\mathfrak{C}$ collect all open covers of $X$. Then for
@@
     it follows that $R_n$ is relatively compact to $X$, and $\bigcup_{n<\omega} R_n = X$.
-  \end{lemma}
+  \end{lem}
 
@@
 
-  \begin{corollary}
+  \begin{cor}
     A space $X$ is $\sigma$-(relatively compact) if and only if $F \markwin \mengame{X}$.
-  \end{corollary}
-
-  \begin{corollary}
+  \end{cor}
+
+  \begin{cor}
     For regular spaces $X$, the following are equivalent:
@@
       \end{enumerate}
-  \end{corollary}
-
-  \begin{theorem}
+  \end{cor}
+
+  \begin{thm}
     For second-countable $X$, the following are equivalent:
@@
       \end{enumerate}
-  \end{theorem}
+  \end{thm}
 
@@
 
-  \begin{corollary}
+  \begin{cor}
     For metric spaces $X$, the following are equivalent:
@@
       \end{enumerate}
-  \end{corollary}
-
-  \begin{example}
+  \end{cor}
+
+  \begin{ex}
   Let $R$ be given the topology from example 63 from Counterexamples in Topology, the topology generated by open intervals with countable sets removed.
 This space is a non-regular example where $F \win \mengame{R}$, but $F \not\markwin \mengame{R}$, that is, $R$ is not $\sigma$-(relatively compact).
-  \end{example}
+  \end{ex}
 
@@
 
-  \begin{example}
+  \begin{ex}
   Let $R$ be given the topology from example 67 from Counterexamples in Topology, the topology generated by open intervals with or without the rationals removed.
 This space is non-regular, and non-$\sigma$-compact, but is second-countable and $\sigma$-(relatively compact).
-  \end{example}
+  \end{ex}
 
@@
 
-  \begin{definition}
+  \begin{defn}
     Let $\mc U$ be a cover of $X$. We say $C\subseteq X$ is $\mc U$-compact if there exists a finite subcover of $\mc U$ which covers $C$.
@@
       \]
-  \end{definition}
-
-  \begin{definition}
+  \end{defn}
+
+  \begin{defn}
     For two functions $f,g$ we say $f$ is \textbf{$\mu$-almost compatible} with $g$ ($f\alcomp_\mu g$) if $|\{x\in\dom(f)\cap\dom(g):f(x)\not=g(x)\}|<\mu$.
 If $\mu=\omega$ then we say $f,g$ are \textbf{almost compatible} ($f\alcomp g$).
-  \end{definition}
-
-  \begin{lemma}\label{kunlem}
+  \end{defn}
+
+  \begin{lem}\label{kunlem}
     For each $\alpha<\omega_1$, there exist injective functions $f_\alpha:\alpha\to\omega$ such that if $\alpha<\beta$, then \[f_\alpha \alcomp f_\beta\] that is, $f_\alpha$ and $f_\beta\rest\alpha$ agree on all but finitely many ordinals.
 In addition, the range of each $f_\alpha$ is co-infinite.
-  \end{lemma}
+  \end{lem}
 
@@
 
-  \begin{theorem}
+  \begin{thm}
     The one-point Lindel\"ofication of the uncountable discrete space, $\oneptlind{\omega_1}$, is \scish.
-  \end{theorem}
+  \end{thm}
 
@@
 
-  \begin{theorem}
+  \begin{thm}
     If $X$ is \scish, then $F \kmarkwin{2}\mengame{X}$.
-  \end{theorem}
+  \end{thm}
 
@@
 
-  \begin{corollary}
+  \begin{cor}
     $F\kmarkwin{2}\mengame{\oneptlind{\omega_1}}$
-  \end{corollary}
-
-  \begin{definition} 
+  \end{cor}
+
+  \begin{defn} 
     The statement $S(\kappa,\mu,\lambda)$ due to Scheepers is shorthand for the following: there exist injective functions $f_A:A\to\lambda$ for each $A\in[\kappa]^\mu$ such that $f_A\alcomp_\mu f_B$ for all $A,B\in[\kappa]^\mu$.
-  \end{definition}
-
-  \begin{proposition}
+  \end{defn}
+
+  \begin{prop}
     $\neg S(\kappa,\omega,\omega)$ for $\kappa>2^\omega$
-  \end{proposition}
+  \end{prop}
 
@@
 
-  \begin{theorem}
+  \begin{thm}
     $S(\kappa,\omega,\omega)$ implies $\oneptlind{\kappa}$ is \scish.
-  \end{theorem}
+  \end{thm}
 
@@
 
-  \begin{corollary}
+  \begin{cor}
     $S(\kappa,\omega,\omega)$ implies $F\kmarkwin{2}\mengame{\oneptlind{\kappa}}$.
-  \end{corollary}
-
-  \begin{definition}
+  \end{cor}
+
+  \begin{defn}
     A finite partial function $p$ from $A$ to $B$ has a domain which is a finite subset of $A$ and a range which is a finite subset of $B$.
@@
     Then let $Fn^2(\mc A,B)\subset Fn(\mc A,Fn(\bigcup \mc A,B))$ such that for each $p\in Fn^2(\mc A,B)$, $p(A)=p_A\in Fn(A,B)$.
-  \end{definition}
-
-  \begin{definition}
+  \end{defn}
+
+  \begin{defn}
     Let $\pok\subset Fn^2([\kappa]^\omega,\omega)$ be such that each $p_A$ is injective, and give it the partial order $\leq$ defined by $q\leq p$ if and only if:
@@
           \end{itemize}
-  \end{definition}
-
-  \begin{lemma}
+  \end{defn}
+
+  \begin{lem}
     $\pok$ has property $K$ (and thus is c.c.c.). That is, let $P\subseteq\pok$ be uncountable: there is an uncountable $Q\subseteq P$ such that points in $Q$ are pairwise compatible.
-  \end{lemma}
+  \end{lem}
 
@@
 
-  \begin{proposition}
+  \begin{prop}
     For $A\in[\kappa]^\omega$ and $\alpha\in A$, the sets 
@@
     are dense in $\pok$.
-  \end{proposition}
+  \end{prop}
 
@@
 
-  \begin{theorem}
+  \begin{thm}
     $S(\kappa,\omega,\omega)+(\kappa=2^\omega)$ is consistent with ZFC for any cardinal $\kappa$ with $cf(\kappa)>\omega$.
-  \end{theorem}
+  \end{thm}
 
@@
 
-  \begin{corollary}
+  \begin{cor}
     For each $\kappa$, $F\kmarkwin{2}\mengame{\oneptlind{\kappa}}$ is consistent with ZFC.
-  \end{corollary}
+  \end{cor}
 
@@
 
-  \begin{definition}
+  \begin{defn}
     A colleciton of subsets of a space $X$ is (\textbf{really}) \textbf{ample} if has a finite subcover for each (relatively) compact subset of $X$.
-  \end{definition}
-
-  \begin{proposition}
+  \end{defn}
+
+  \begin{prop}
     Every ample cover of a regular space $X$ is really ample.
-  \end{proposition}
+  \end{prop}
 
@@
 
-  \begin{definition}
+  \begin{defn}
     A space $X$ is (\textbf{relatively}) \textbf{Alster} if there exists a countable subcover for each (really) ample cover of $X$ by $G_\delta$ sets.
-  \end{definition}
-
-  \begin{proposition}
+  \end{defn}
+
+  \begin{prop}
     Every regular relatively Alster space is Alster.
-  \end{proposition}
-
-  \begin{theorem}
+  \end{prop}
+
+  \begin{thm}
     $X$ $\sigma$-compact $\Rightarrow$ $X$ Alster $\Rightarrow$ $X$ Menger
-  \end{theorem}
+  \end{thm}
 
@@
 
-  \begin{proposition}
+  \begin{prop}
     $X$ $\sigma$-(relatively compact) $\Rightarrow$ $X$ relatively Alster $\Rightarrow$ $X$ Menger
-  \end{proposition}
+  \end{prop}
 
@@
 
-  \begin{example}
+  \begin{ex}
     Let the real numbers $R$ be given the topology generated by open intervals with countable sets removed.
@@
 If $S(2^\omega,\omega,\omega)$ holds, then $F\kmarkwin{2}\mengame{R}$.
-  \end{example}
+  \end{ex}
 
@@
 
-  \begin{definition}
+  \begin{defn}
     A space $X$ is \textbf{Hurewicz} if for each sequence of open covers $\mc U_n$, there are $\mc F_n \in [\mc U_n]^{<\omega}$ such that $X=\bigcup_{m<\omega}\bigcap_{m\leq n<\omega}\cup\mc F_n$.
-  \end{definition}
+  \end{defn}
 
@@
 
-  \begin{definition}
+  \begin{defn}
     The \textbf{filling game} $\fillgame{J}$ on an ideal $J$ proceeds as follows: player $M$ chooses $M_0 \in \<J\>$, the $\sigma$-completion of $J$, in the initial round, followed by $N$ choosing $N_0\in J$.
@@
     The \textbf{strict filling game} $\sfillgame{J}$ proceeds analogously, with the added requirement that $M_n\subsetneq M_{n+1}$. This game has been studied by Scheepers.
-  \end{definition}
-
-  \begin{theorem}
+  \end{defn}
+
+  \begin{thm}
     $N\ktactwin{2}\sfillgame{J} \Rightarrow N\kmarkwin{2}\fillgame{J}$
-  \end{theorem}
+  \end{thm}
 
@@
 
-  \begin{example}
+  \begin{ex}
     There is a free ideal $J$ such that $N\not\ktactwin{2}\sfillgame{J}$ but $N\kmarkwin{2}\fillgame{J}$.
-  \end{example}
+  \end{ex}
 
@@
 
-  \begin{definition}
+  \begin{defn}
     $X$ is \textbf{Rothberger} if for all open covers $\mathcal{U}_0,\mathcal{U}_1,\dots$ there exist open sets $U_n\in \mathcal{U}_n$ such that $\{U_n:n<\omega\}$ is a cover of $X$.
-  \end{definition}
-
-  \begin{proposition}
+  \end{defn}
+
+  \begin{prop}
     Rothberger $\Rightarrow$ Menger
-  \end{proposition}
-
-  \begin{definition}
+  \end{prop}
+
+  \begin{defn}
     In the two-player game $\rothgame{X}$ player $C$ chooses open covers $\mathcal{U}_n$ of $X$, followed by player $S$ choosing an open set $U_n\in\mathcal{U}_n$.
 $S$ wins if $\{U_n:n<\omega\}$ is a cover of $X$.
-  \end{definition}
-
-  \begin{theorem}
+  \end{defn}
+
+  \begin{thm}
     $X$ is Rothberger if and only if $C\not\win\rothgame{X}$.
-  \end{theorem}
+  \end{thm}
 
@@
 
-  \begin{definition}
+  \begin{defn}
     A space $X$ is scattered if every subspace contains an isolated point.
 By convention, $\ds X = \bigcup_{\alpha<\rank(X)}X^\alpha$ where $X^\alpha$ is the set of isolated points of $\ds X\setminus\bigcup_{\beta<\alpha}X^\beta$.
-  \end{definition}
-
-  \begin{proposition}
+  \end{defn}
+
+  \begin{prop}
     A space $X$ is scattered if and only if every closed subspace contains an isolated point.
-  \end{proposition}
-
-  \begin{proposition}
+  \end{prop}
+
+  \begin{prop}
     The rank of a compact scattered $T_1$ space is a successor ordinal, and $X^{\rank(X)-1}$ is finite.
-  \end{proposition}
+  \end{prop}
 
@@
 
-  \begin{theorem}
+  \begin{thm}
     The following are equivalent for compact $T_2$ $X$:
@@
 
-  \begin{definition}
+  \begin{defn}
     In the two-player game $\altrothgame{X}$ player $P$ chooses points $x_n\in X$, followed by player $O$ choosing an open neighborhood $U_n$ of $x_n$.
 $P$ wins if $\{U_n:n<\omega\}$ is a cover of $X$.
-  \end{definition}
-
-  \begin{theorem} $\altrothgame{X}$ is ``perfect information equivalent'' to $\rothgame{X}$. That is:
+  \end{defn}
+
+  \begin{thm} $\altrothgame{X}$ is ``perfect information equivalent'' to $\rothgame{X}$. That is:
 
@@
     \end{itemize}
-  \end{theorem}
+  \end{thm}
 
@@
 
-  \begin{theorem}
+  \begin{thm}
     \begin{itemize}
@@
 
-  \begin{definition}
+  \begin{defn}
     Let $\mc{N}(x)$ be the $\textbf{neighborhood network}$ of $x$, that is, the collection of all neighborhoods of $x$.
-  \end{definition}
-
-  \begin{definition}
+  \end{defn}
+
+  \begin{defn}
     A topological space $X$ is \textbf{almost countable} if there exist $x_n\in X$ for each $n<\omega$ such that $X=\bigcup_{n<\omega}\bigcap\mc{N}(x_n)$.
-  \end{definition}
-
-  \begin{theorem}
+  \end{defn}
+
+  \begin{thm}
     For any space $X$, the following are equivalent:
@@
 
-  \begin{theorem}
+  \begin{thm}
     For any $T_1$ space $X$, the following are equivalent:
@@
 
-  \begin{example}
+  \begin{ex}
     Let $X=\omega_1\cup\{\infty\}$ be a ``weak Lindel\"ofication'' of discrete $\omega_1$ such that open neighborhoods of $\infty$ contain $\omega_1\setminus\omega$.
 This space is $T_0$ but not $T_1$, and note that $S\markwin\rothgame{X}$ and $|X|>\omega$.
-  \end{example}
-
-  \begin{theorem}
+  \end{ex}
+
+  \begin{thm}
     The following are equivalent for points-$G_\delta$ $X$:
@@
 
-  \begin{corollary}
+  \begin{cor}
     The following are equivalent for compact points-$G_\delta$ $X$:
@@
       \end{enumerate}
-  \end{corollary}
-
-  \begin{definition}
+  \end{cor}
+
+  \begin{defn}
     The game $\recallgame{m}{\kappa}$ proceeds as follows: during round $0$, player $F$ chooses $F_0\in[\kappa]^m$, followed by player $S$ choosing $x_0\in F_0\cup\{\infty\}$.
@@
     $S$ wins the game if $\{x_n : n<\omega\}\supseteq F_0\cup\{\infty\}$, and $F$ wins otherwise.
-  \end{definition}
-
-  \begin{proposition}
+  \end{defn}
+
+  \begin{prop}
     $S\limitwin\rothgame{\oneptlind{\kappa}} \Rightarrow S\limitwin\recallgame{m}{\kappa}$
-  \end{proposition}
+  \end{prop}
 
@@
 
-  \begin{proposition}
+  \begin{prop}
     $S\kmarkwin{k}\recallgame{m}{\kappa} \Leftrightarrow S\ktactwin{k}\recallgame{m}{\kappa}$
-  \end{proposition}
+  \end{prop}
 

### 2014-05-02 phd/dissertation/chapter2.tex
Expanded chapter 2 overview of games

@@
 Games may be modeled mathematically in various ways (TODO: cite digraph model)
-but we will find it convenient to think of them as follows.
+but we will find it convenient to think of them in terms defined by
+Gale and Stewart. (TODO: cite)
 
@@
   A \term{game} is a tuple $\<M,W\>$ such that 
-  $W\subseteq (M^{\omega})^2$. $M$ is set of \term{moves} for
-  the game, and $(M^{\omega})^2$ is the set of all possible 
+  $W\subseteq M^{\omega}$. $M$ is set of \term{moves} for
+  the game, and $M^{\omega}$ is the set of all possible 
   \term{playthroughs} of the game.
 
-  $W$ is the set of \term{winning} playthroughs for the 
-  first player, and $(M^{\omega})^2\setminus W$ is the set of winning
-  playthroughs for the second player.
+  $W$ is the set of \term{winning playthroughs} or \term{victories} for the 
+  first player, and $M^{\omega}\setminus W$ is the set of victories for the 
+  second player. ($W$ is often called the \term{payoff set} for the
+  first player.)
 \end{defn}
@@
 To illustrate this definition, we may formally model the well-known game 
-Tic-Tac-Toe. Imagine that the game board is labeled as a ``magic square''
-of the numbers $0$ through $8$. (TODO: image) Then writing $X$ or $O$ on
+Tic-Tac-Toe. For convenince, we may label the game board as a ``magic square''
+of the numbers $0$ through $8$ such that the combinations of three integers
+which sum to $12$ are exactly the rows, columns, and diagonals of the
+grid.
+
+(TODO: image)
+
+Then writing $X$ or $O$ on
 the game board is equivalent to choosing a number $0$ through $8$, and 
@@
   The moves $M$ for the game are the first nine non-negative 
-  integers $\{0,\dots,8\}$. The winning playthroughs $W$ for $\pl X$ 
-  consist of pairs of sequences $\<X,O\>$ such that $X\geq\<X_0,\dots,X_4\>$,
-  $O\geq\<O_0,\dots,O_3\>$, and any of the following hold:
+  integers $\{0,\dots,8\}$. The victories $W$ for $\pl X$ 
+  consist of sequences $\<X_0,O_0,X_1,O_1,\dots\>$ such that either of the 
+  following hold:
     \begin{itemize}
@@
 demonstrated by this game due to John Conway:
+\cite{winning_ways}
 
 \begin{game}
-  The game ...
+  Let $\coingame$ denote the game \term{Sylver Coinage} with players 
+  $\pl A$ and $\pl B$. During round $n$, $\pl A$ chooses an integer $a_n>0$,
+  followed by $\pl B$ choosing another integer $b_n>0$, with the rule that
+  neither player may choose an integer which is the sum of nonnegative integer 
+  multiples of previously chosen integers. $\pl A$ wins the game if $\pl B$
+  ever chooses the number $1$, and $\pl B$ wins otherwise.
 \end{game}
 
-\subsection{Infinite Games}
+After some thought, the reader may confirm that there will be no 
+legal moves except $1$ remaining after a finite number of rounds. 
+Specifically, if $\pl A$
+chooses $a_0$ in the initial round, then all following legal moves must be
+of the form $i \mod\, a_0$ for $0<i<a_0$. $i \mod\, a_0$ may be repeated,
+but all following repetitions must be strictly less than the previous
+iterations, which may only be done finitely many times. Thus after a finite 
+number of moves, there will only be finitely many legal moves remaining. 
+\footnote{
+  A more involved
+  argument due to Sylvester (for whom the game is named)
+  shows that the number of legal moves 
+  is finite as soon as two coprime numbers have been played. \cite{sylvester}
+}
 
-\subsection{Topological Games}
+Sylver Coinage was defined as an example of an ``unboundedly unboundedly 
+bounded'' game, the maximum length of which is not decided until at least
+the second move.
+
+\subsection{Infinite and Topological Games}
+
+(TODO: History of infinite games in topology / descriptive set theory)
+
+\begin{defn}
+  A game is said to be an \term{infinite game} if there exists a playthrough
+  $p\in M^\omega$ of the game such that for all $n<\omega$,
+    $ 
+      \{q : q\geq p\rest n \}
+    $
+  is not a subset of either $W$ or $M^\omega\setminus W$.
+\end{defn}
+
+Put another way, an infinite game need not be decided after a finite number
+of rounds. Games which are not infinite are of course called
+\term{finite games}.
+
+As an illustration, we may consider an example due to 
+Baker \cite{baker}.
+
+\begin{game}
+  Let $\bakergame{A}$ denote a game with players $\pl A$ and $\pl B$,
+  defined for each subset $A\subset \mathbb{R}$.
+  In round $0$, $\pl A$ chooses a number $a_0$, followed by $\pl B$ choosing
+  a number $b_0$ such that $a_0<b_0$.
+  In round $n+1$, $\pl A$ chooses a number $a_{n+1}$ such that 
+  $a_n<a_{n+1}<b_n$, followed by $\pl B$ choosing a number $b_{n+1}$ such that
+  $a_{n+1}<b_{n+1}<b_n$.
+
+  $\pl A$ wins the game if the sequence $\<a_n:n<\omega\>$ converges to a 
+  point in $A$, and $\pl B$ wins otherwise.
+\end{game}
+
+Certainly, $\pl A$ and $\pl B$ will never be in
+a position without (infinitely many) legal moves available, so this is
+an infinite game. While the game could never be ``completed'' in reality,
+the winning condition considers the infinite sequence of moves made by the
+players and declares a victor at the ``end'' of the game.
+
+As a simple example, if $A=\mathbb{R}$, then $W=M^\omega$. That is,
+all playthroughs of the game are victories for $\pl A$, since every
+bounded increasing sequence converges to some real number.
+
+\begin{defn}
+  A \term{topological game} is a game defined in terms of an arbitrary
+  topological space.
+\end{defn}
+
+Topological games are usually infinite games. One of the earliest examples
+of a topological game is the Banach Mazur game, proposed by Stanislaw Mazur
+as Problem 43 in Stefan Banach's Scottish Book (1935). We give a more
+general definition here.
+
+\begin{game}
+  Let $\bmgame{X}$ denote the \term{Banach-Mazur game} with players $\pl E$,
+  $\pl N$ defined for each topological space $X$.
+  In round $0$, $\pl E$ chooses a nonempty open set $E_0\subseteq X$, followed
+  by $\pl N$ choosing a nonempty open subset $N_0\subseteq E_0$.
+  In round $n+1$, $\pl E$ chooses a nonempty open subset $E_{n+1}\subseteq N_n$, 
+  followed by $\pl N$ choosing a nonempty open subset 
+  $N_{n+1}\subseteq E_{n+1}$.
+
+  $\pl E$ wins the game if $\bigcap_{n<\omega} E_n = \emptyset$, 
+  and $\pl N$ wins otherwise.
+\end{game}
+
+For example, if $X$ is a locally compact Hausdorff space, $\pl N$ can ``force'' 
+a win by choosing $N_0$ such that $\cl{N_0}$ is compact, and choosing 
+$N_{n+1}$ such that 
+$N_{n+1}\subseteq\cl{N_{n+1}}\subseteq O_{n+1}\subseteq N_n$ 
+(possible since $N_n$ is a compact Hausdorff $\Rightarrow$ normal space). 
+Since $\bigcap_{n<\omega} E_n = \bigcap_{n<\omega} N_n$ is the decreasing 
+intersection of compact sets, it cannot be empty.
+
+This concept of when (and how) a player can ``force'' a win in certain
+topological games is the focus of this manuscript.
 
@@
 
-\subsection{Perfect Information}
+We shall make the notion of forcing a win in a game rigorous by introducing
+``strategies'' and ``attacks'' for games.
 
-\subsection{Limited Information}
+\begin{defn}
+  A \term{strategy} for a game $G=\<M,W\>$ is a function 
+  from $M^{<\omega}$ to $M$.
+\end{defn}
+
+\begin{defn}
+  An \term{attack} for a game $G=\<M,W\>$ is a function 
+  from $\omega$ to $M$.
+\end{defn}
+
+Intuitively, a strategy is a rule for one of the players on how to play
+the game based upon the previous moves of her opponent, while an attack is
+a fixed strike by an opponent.
+
+\begin{defn}
+  The \term{result} of a game for a strategy $\sigma$ for the first player and 
+  attack $\<a_0,a_1,\dots\>$ for  the second player is the playthrough
+    \[
+      \<\sigma(\emptyset),a_0,\sigma(\<a_0\>), a_1, \sigma(\<a_0,a_1\>),\dots\>
+    \]
+  Likewise, if $\sigma$ is a strategy for the second player, and 
+  $\<a_0,a_1,\dots\>$ is an attack by the first player, then the result is
+  the playthrough
+    \[
+      \<a_0,\sigma(\<a_0\>), a_1, \sigma(\<a_0,a_1\>),\dots\>
+    \]
+\end{defn}
+
+We now may rigorously define the notion of ``forcing'' a win in a game.
+
+\begin{defn}
+  A strategy $\sigma$ is a \term{winning strategy} for a player if for
+  every attack by the opponent, the result of the game is a victory 
+  for that player.
+
+  If a winning strategy exists for player $\pl A$ in the game $G$, then we
+  write $\pl A \win G$. Otherwise, we write $\pl A \not\win G$.
+\end{defn}
+
+Of course, a strategy $\sigma$ is not a winning strategy for a player if there 
+exists some \term{counter-attack} by the opponent for which the result is 
+a victory for the opponent. Typically this counter-attack is defined in
+terms of the strategy $\sigma$; else, the counter-attack is itself a
+winning strategy depending on only the round number (which we will
+investigate further in a later section).
+
+\begin{defn}
+  A game $G$ with players $\pl A$, $\pl B$ is said to be \term{determined}
+  if either $\pl A \win G$ or $\pl B \win G$.
+\end{defn}
+
+(TODO: cite Gale and Stewart)
+% http://en.wikipedia.org/wiki/Borel_determinacy_theorem
+
+\begin{thm}
+  If the move set $M$ for a game $G=\<M,W\>$ is given the discrete topology
+  and $W$ is either an open or closed subset of $M^\omega$ with the
+  usual product topology, then $G$ is determined.
+\end{thm}
+
+(TODO: outline proof?)
+
+We get this important corollary:
+
+\begin{cor}
+  Finite games are determined.
+\end{cor}
+
+\begin{proof} 
+  For every victory $p\in W$ for the first player, there was some 
+  round $n<\omega$ for which that partial playthrough was guaranteed to
+  result in a victory for the first player.
+
+  Put another way, there exists $n<\omega$ such that
+    $ 
+      \{q : q\geq p\rest n \}
+    $
+  (a neighborhood of $p$) is contained in $W$. Thus $W$ is open.
+\end{proof}
+
+(TODO: find combinatorial proof and cite it)
+
+(TODO: Cover Martin's Borel determinacy theorem?)
+
+\subsection{Applications of Strategies}
+
+\subsection{Limited Information Strategies}
 

### 2014-05-07 phd/dissertation/chapter2.tex
More work on expository chapter

@@
 Topological games are usually infinite games. One of the earliest examples
-of a topological game is the Banach Mazur game, proposed by Stanislaw Mazur
-as Problem 43 in Stefan Banach's Scottish Book (1935). We give a more
-general definition here.
+of a topological game is the Banach-Mazur game, proposed by Stanislaw Mazur
+as Problem 43 in Stefan Banach's Scottish Book (1935). A more comprehensive
+history of the Banacy-Mazur and other topological games may be found in 
+Telgarsky's survey on the subject \cite{telgarsky}.
+
+The original game was defined for subsets of the real line; however, 
+we give a more general definition here.
 
@@
 
+Non-trivial topological games are infinite, however, and many are indetermined
+for certain spaces.
+
+\begin{ex}
+  Let $B$ be a Bernstein subset of the real line. Then $\bmgame{B}$ is
+  undetermined.
+\end{ex}
+
+\begin{proof}
+  It can be shown that $B$ is a Baire space, and we will soon see that 
+  $\pl E\not\win \bmgame{X}$ characterizes Baire spaces. Also, if $\sigma$
+  is a winning strategy for $\pl N$ in $\bmgame{Y}$ for $Y\subseteq X$, it can 
+  be shown that $Y$ contains a closed uncountable set in $X$. 
+  Thus $\pl N\not\win \bmgame{B}$.
+\end{proof}
+
 \subsection{Applications of Strategies}
+
+The presence or absence of a winning strategie for a player in a topological
+game characterizes a property of the topological space in question.
+
+A classical result follows.
+
+\begin{thm}
+$\pl E\not\win \bmgame{X}$ if and only if $X$ is a Baire space. \cite{haworth}
+\end{thm}
 
@@
 \section{Examples of Topological Games}
+
+(TODO: )

### 2014-05-07 miscellaneous/unorganized/_sylver_coinage.tex
cleaning up ch 2 todos

--- 2014-04-30 phd/dissertation/chapter2.tex
@@
-%!TEX root = dissertation.tex
-% ^ leave for LaTeXTools build functionality
-
-\chapter{Toplogical Games and Strategies\\ of Perfect and Limited Information}
-
-The goal of this paper is to explore the applications of limited information
-strategies in existing topological games. (TODO: History of combinatorical
-and topological games?)
-
-\section{Games}
-
-Intuitively, the games studied in this paper are two-player games for which
-each player takes turns making a choice from a set of possible moves. At
-the conclusion of the game, the choices made by both players are examined,
-and one of the players is declared the winner of that playthrough, with
-no ties allowed.
-
-Games may be modeled mathematically in various ways (TODO: cite digraph model)
-but we will find it convenient to think of them as follows.
-
-\begin{defn}
-  A \term{game} is a tuple $\<M,W\>$ such that 
-  $W\subseteq (M^{\omega})^2$. $M$ is set of \term{moves} for
-  the game, and $(M^{\omega})^2$ is the set of all possible 
-  \term{playthroughs} of the game.
-
-  $W$ is the set of \term{winning} playthroughs for the 
-  first player, and $(M^{\omega})^2\setminus W$ is the set of winning
-  playthroughs for the second player.
-\end{defn}
-
-To illustrate this definition, we may formally model the well-known game 
-Tic-Tac-Toe. Imagine that the game board is labeled as a ``magic square''
-of the numbers $0$ through $8$. (TODO: image) Then writing $X$ or $O$ on
-the game board is equivalent to choosing a number $0$ through $8$, and 
-getting a ``tic-tac-toe'' is equivalent to having chosen three numbers which 
-sum to $12$.
+But a two-player game need not have a bounded number of rounds, as is
+demonstrated by this game due to John Conway:
+\cite{winning_ways}
 
 \begin{game}
-  Let $\tttgame$ denote the game \term{Tic-Tac-Toe}, with players $\pl X$ 
-  and $\pl O$.
-
-  The moves $M$ for the game are the first nine non-negative 
-  integers $\{0,\dots,8\}$. The winning playthroughs $W$ for $\pl X$ 
-  consist of pairs of sequences $\<X,O\>$ such that $X\geq\<X_0,\dots,X_4\>$,
-  $O\geq\<O_0,\dots,O_3\>$, and any of the following hold:
-    \begin{itemize}
-      \item There exists some $k<4$ such that $\<X_0,O_0,\dots,X_k\>$ contains
-            no repeated integers, but $\<X_0,O_0,\dots,X_k,O_k\>$ does.
-
-            ($\pl O$ drew her mark on a space already occupied.)
-      \item There exists $i<j<k<5$ such that $\<X_0,O_0,\dots,X_4\>$ contains 
-            no repeated integers and $X_i+X_j+X_k=12$, and for all
-            $i'<j'<k'<k$ it follows that $O_{i'}+O_{j'}+O_{k'}\not=12$.
-
-            ($\pl X$ did not draw her mark on a space that was already occupied,
-            and was able to secure a ``tic-tac-toe'' before $\pl O$.)
-            \footnote{
-              The observant reader will note that in this formulation of 
-              Tic-Tac-Toe, player $\pl O$ wins ``cat's games'' where neither 
-              player secures a ``tic-tac-toe'' (since no ties are allowed).
-            }
-    \end{itemize}
+  Let $\coingame$ denote the game \term{Sylver Coinage} with players 
+  $\pl A$ and $\pl B$. During round $n$, $\pl A$ chooses an integer $a_n>0$,
+  followed by $\pl B$ choosing another integer $b_n>0$, with the rule that
+  neither player may choose an integer which is the sum of nonnegative integer 
+  multiples of previously chosen integers. $\pl A$ wins the game if $\pl B$
+  ever chooses the number $1$, and $\pl B$ wins otherwise.
 \end{game}
 
-Due to the tedium of defining games explicitly from the definition, we 
-typically define games by declaring the \term{rules} that each player must 
-follow (e.g. players may not make a mark on a space which was already marked)
-and the \term{winning condition} for the first player (e.g. $\pl X$ secures
-a ``tic-tac-toe'' before $\pl O$). Then a playthrough is in $W$ if either 
-the first player made only \term{legal moves} which observed the game's rules
-and the playthrough satisifies the winning condition, or the second player
-made an \term{illegal move} which contradicted the game's rules.
+After some thought, the reader may confirm that there will be no 
+legal moves except $1$ remaining after a finite number of rounds. 
+Specifically, if $\pl A$
+chooses $a_0$ in the initial round, then all following legal moves must be
+of the form $i \mod\, a_0$ for $0<i<a_0$. $i \mod\, a_0$ may be repeated,
+but all following repetitions must be strictly less than the previous
+iterations, which may only be done finitely many times. Thus after a finite 
+number of moves, there will only be finitely many legal moves remaining. 
+\footnote{
+  A more involved
+  argument due to Sylvester (for whom the game is named)
+  shows that the number of legal moves 
+  is finite as soon as two coprime numbers have been played. \cite{sylvester}
+}
 
-Often, players should not be able to choose from the same set of moves
-(e.g. player Black cannot move White's pieces in chess), in which case $M$ may
-be partitioned into two sets $M_0,M_1$ and the rules for the game may be defined
-such that each player may only choose from one of those sets 
-(e.g. Black will automatically lose if she moves one of White's pieces).
-
-An artifact of this game model is that games never technically end, since 
-playthroughs of the game are infinite sequences. Nonetheless, Tic-Tac-Toe
-is always decided by $\pl X$'s fifth move, and in chess, there is also an
-upper bound for the length of a game due to the finite number of ways pieces
-may be positioned on the chessboard (and the ``threefold rule''
-which declares the game finished if the same position is repeated three times).
-
-But a two-player game need not have a bounded number of rounds, as is
-demonstrated by this game due to John Conway:
-
-\begin{game}
-  The game ...
-\end{game}
-
-\subsection{Infinite Games}
-
-\subsection{Topological Games}
-
-\section{Strategies}
-
-\subsection{Perfect Information}
-
-\subsection{Limited Information}
-
-\section{Examples of Topological Games}
+Sylver Coinage was defined as an example of an ``unboundedly unboundedly 
+bounded'' game, the maximum length of which is not decided until at least
+the second move.

### 2014-05-07 miscellaneous/unorganized/_tic-tac-toe.tex
cleaning up ch 2 todos

--- 2014-04-30 phd/dissertation/chapter2.tex
@@
-%!TEX root = dissertation.tex
-% ^ leave for LaTeXTools build functionality
+To illustrate this definition, we may formally model the well-known game 
+Tic-Tac-Toe. For convenince, we may label the game board as a ``magic square''
+of the numbers $0$ through $8$ such that the combinations of three integers
+which sum to $12$ are exactly the rows, columns, and diagonals of the
+grid.
 
-\chapter{Toplogical Games and Strategies\\ of Perfect and Limited Information}
+(TODO: image)
 
-The goal of this paper is to explore the applications of limited information
-strategies in existing topological games. (TODO: History of combinatorical
-and topological games?)
-
-\section{Games}
-
-Intuitively, the games studied in this paper are two-player games for which
-each player takes turns making a choice from a set of possible moves. At
-the conclusion of the game, the choices made by both players are examined,
-and one of the players is declared the winner of that playthrough, with
-no ties allowed.
-
-Games may be modeled mathematically in various ways (TODO: cite digraph model)
-but we will find it convenient to think of them as follows.
-
-\begin{defn}
-  A \term{game} is a tuple $\<M,W\>$ such that 
-  $W\subseteq (M^{\omega})^2$. $M$ is set of \term{moves} for
-  the game, and $(M^{\omega})^2$ is the set of all possible 
-  \term{playthroughs} of the game.
-
-  $W$ is the set of \term{winning} playthroughs for the 
-  first player, and $(M^{\omega})^2\setminus W$ is the set of winning
-  playthroughs for the second player.
-\end{defn}
-
-To illustrate this definition, we may formally model the well-known game 
-Tic-Tac-Toe. Imagine that the game board is labeled as a ``magic square''
-of the numbers $0$ through $8$. (TODO: image) Then writing $X$ or $O$ on
+Then writing $X$ or $O$ on
 the game board is equivalent to choosing a number $0$ through $8$, and 
@@
 \end{game}
-
-Due to the tedium of defining games explicitly from the definition, we 
-typically define games by declaring the \term{rules} that each player must 
-follow (e.g. players may not make a mark on a space which was already marked)
-and the \term{winning condition} for the first player (e.g. $\pl X$ secures
-a ``tic-tac-toe'' before $\pl O$). Then a playthrough is in $W$ if either 
-the first player made only \term{legal moves} which observed the game's rules
-and the playthrough satisifies the winning condition, or the second player
-made an \term{illegal move} which contradicted the game's rules.
-
-Often, players should not be able to choose from the same set of moves
-(e.g. player Black cannot move White's pieces in chess), in which case $M$ may
-be partitioned into two sets $M_0,M_1$ and the rules for the game may be defined
-such that each player may only choose from one of those sets 
-(e.g. Black will automatically lose if she moves one of White's pieces).
-
-An artifact of this game model is that games never technically end, since 
-playthroughs of the game are infinite sequences. Nonetheless, Tic-Tac-Toe
-is always decided by $\pl X$'s fifth move, and in chess, there is also an
-upper bound for the length of a game due to the finite number of ways pieces
-may be positioned on the chessboard (and the ``threefold rule''
-which declares the game finished if the same position is repeated three times).
-
-But a two-player game need not have a bounded number of rounds, as is
-demonstrated by this game due to John Conway:
-
-\begin{game}
-  The game ...
-\end{game}
-
-\subsection{Infinite Games}
-
-\subsection{Topological Games}
-
-\section{Strategies}
-
-\subsection{Perfect Information}
-
-\subsection{Limited Information}
-
-\section{Examples of Topological Games}

### 2014-05-07 phd/dissertation/chapter2.tex
cleaning up ch 2 todos

@@
 The goal of this paper is to explore the applications of limited information
-strategies in existing topological games. (TODO: History of combinatorical
-and topological games?)
+strategies in existing topological games. There are a variety of frameworks
+for modeling such games, so we establish one within this chapter which we 
+will use for this manuscript.
 
@@
 the conclusion of the game, the choices made by both players are examined,
-and one of the players is declared the winner of that playthrough, with
-no ties allowed.
+and one of the players is declared the winner of that playthrough.
 
-Games may be modeled mathematically in various ways (TODO: cite digraph model)
+Games may be modeled mathematically in various ways,
 but we will find it convenient to think of them in terms defined by
-Gale and Stewart. (TODO: cite)
+Gale and Stewart. \cite{gale}
 
@@
 
-To illustrate this definition, we may formally model the well-known game 
-Tic-Tac-Toe. For convenince, we may label the game board as a ``magic square''
-of the numbers $0$ through $8$ such that the combinations of three integers
-which sum to $12$ are exactly the rows, columns, and diagonals of the
-grid.
+Within this model, we may imagine two players $\pl A$ and $\pl B$ playing a 
+game which consists of \term{rounds} enumerated for each $n<\omega$.
+During round $n$, $\pl A$ chooses $a_n\in M$, followed by $\pl B$ choosing
+$b_n\in M$. The playthrough corresponding to those choices would be
+the sequence $p = \<a_0,b_0,a_1,b_1,\dots\>$. If $p\in W$, then $\pl A$
+is the winner of that playthrough, and if $p\not\in W$, then $\pl B$ is
+the winner. (No ties are allowed.)
 
-(TODO: image)
-
-Then writing $X$ or $O$ on
-the game board is equivalent to choosing a number $0$ through $8$, and 
-getting a ``tic-tac-toe'' is equivalent to having chosen three numbers which 
-sum to $12$.
-
-\begin{game}
-  Let $\tttgame$ denote the game \term{Tic-Tac-Toe}, with players $\pl X$ 
-  and $\pl O$.
-
-  The moves $M$ for the game are the first nine non-negative 
-  integers $\{0,\dots,8\}$. The victories $W$ for $\pl X$ 
-  consist of sequences $\<X_0,O_0,X_1,O_1,\dots\>$ such that either of the 
-  following hold:
-    \begin{itemize}
-      \item There exists some $k<4$ such that $\<X_0,O_0,\dots,X_k\>$ contains
-            no repeated integers, but $\<X_0,O_0,\dots,X_k,O_k\>$ does.
-
-            ($\pl O$ drew her mark on a space already occupied.)
-      \item There exists $i<j<k<5$ such that $\<X_0,O_0,\dots,X_4\>$ contains 
-            no repeated integers and $X_i+X_j+X_k=12$, and for all
-            $i'<j'<k'<k$ it follows that $O_{i'}+O_{j'}+O_{k'}\not=12$.
-
-            ($\pl X$ did not draw her mark on a space that was already occupied,
-            and was able to secure a ``tic-tac-toe'' before $\pl O$.)
-            \footnote{
-              The observant reader will note that in this formulation of 
-              Tic-Tac-Toe, player $\pl O$ wins ``cat's games'' where neither 
-              player secures a ``tic-tac-toe'' (since no ties are allowed).
-            }
-    \end{itemize}
-\end{game}
-
-Due to the tedium of defining games explicitly from the definition, we 
+Rather than explicitly defining $W$, we 
 typically define games by declaring the \term{rules} that each player must 
-follow (e.g. players may not make a mark on a space which was already marked)
-and the \term{winning condition} for the first player (e.g. $\pl X$ secures
-a ``tic-tac-toe'' before $\pl O$). Then a playthrough is in $W$ if either 
+follow and the \term{winning condition} for the first player. 
+Then a playthrough is in $W$ if either 
 the first player made only \term{legal moves} which observed the game's rules
-and the playthrough satisifies the winning condition, or the second player
+and the playthrough satisified the winning condition, or the second player
 made an \term{illegal move} which contradicted the game's rules.
 
-Often, players should not be able to choose from the same set of moves
-(e.g. player Black cannot move White's pieces in chess), in which case $M$ may
-be partitioned into two sets $M_0,M_1$ and the rules for the game may be defined
-such that each player may only choose from one of those sets 
-(e.g. Black will automatically lose if she moves one of White's pieces).
-
-An artifact of this game model is that games never technically end, since 
-playthroughs of the game are infinite sequences. Nonetheless, Tic-Tac-Toe
-is always decided by $\pl X$'s fifth move, and in chess, there is also an
-upper bound for the length of a game due to the finite number of ways pieces
-may be positioned on the chessboard (and the ``threefold rule''
-which declares the game finished if the same position is repeated three times).
-
-But a two-player game need not have a bounded number of rounds, as is
-demonstrated by this game due to John Conway:
-\cite{winning_ways}
-
-\begin{game}
-  Let $\coingame$ denote the game \term{Sylver Coinage} with players 
-  $\pl A$ and $\pl B$. During round $n$, $\pl A$ chooses an integer $a_n>0$,
-  followed by $\pl B$ choosing another integer $b_n>0$, with the rule that
-  neither player may choose an integer which is the sum of nonnegative integer 
-  multiples of previously chosen integers. $\pl A$ wins the game if $\pl B$
-  ever chooses the number $1$, and $\pl B$ wins otherwise.
-\end{game}
-
-After some thought, the reader may confirm that there will be no 
-legal moves except $1$ remaining after a finite number of rounds. 
-Specifically, if $\pl A$
-chooses $a_0$ in the initial round, then all following legal moves must be
-of the form $i \mod\, a_0$ for $0<i<a_0$. $i \mod\, a_0$ may be repeated,
-but all following repetitions must be strictly less than the previous
-iterations, which may only be done finitely many times. Thus after a finite 
-number of moves, there will only be finitely many legal moves remaining. 
+As an illustration, we could model a game of chess (ignoring stalemates) 
+by letting
+\[
+  M = \{\<p,s\>: p \text{ is a chess piece and } 
+                 s \text{ is a space on the board } \}
+\]
+representing moving a piece $p$ to the space $s$ on the board. Then the
+rules of chess restict White from moving pieces which belong to
+Black, or moving a piece to an illegal space on the board. 
 \footnote{
-  A more involved
-  argument due to Sylvester (for whom the game is named)
-  shows that the number of legal moves 
-  is finite as soon as two coprime numbers have been played. \cite{sylvester}
+  In practice, $M$ is often defined as the union of two sets, such
+  as white pieces and black pieces in chess. For example,
+  the first player may choose open sets in a topology, while the second player
+  chooses points within the topological space.
 }
-
-Sylver Coinage was defined as an example of an ``unboundedly unboundedly 
-bounded'' game, the maximum length of which is not decided until at least
-the second move.
+The winning condition could then
+``inspect'' the resulting positions of pieces on the board after each move 
+to see if White attained a
+checkmate. This winning condition along with the rules implicitly define the 
+set $W$ of winning playthroughs for White.
 
@@
 
-(TODO: History of infinite games in topology / descriptive set theory)
+Games never technically end within this model, since 
+playthroughs of the game are infinite sequences. However, for all practical
+purposes many games end after a finite number of turns.
 
 \begin{defn}
-  A game is said to be an \term{infinite game} if there exists a playthrough
-  $p\in M^\omega$ of the game such that for all $n<\omega$,
+  A game is said to be an \term{finite game} if for every playthrough
+  $p\in M^\omega$ there exists a round $n<\omega$ such that
     $ 
-      \{q : q\geq p\rest n \}
+      [p\rest n] = \{q\in M^\omega : q\supseteq p\rest n \}
     $
-  is not a subset of either $W$ or $M^\omega\setminus W$.
+  is a subset of either $W$ or $M^\omega\setminus W$.
 \end{defn}
 
-Put another way, an infinite game need not be decided after a finite number
-of rounds. Games which are not infinite are of course called
-\term{finite games}.
+Put another way, a finite game is decided after a finite number
+of rounds, after which the game's winner could not change even if further
+rounds were played.
+Games which are not finite are called \term{infinite games}.
 
-As an illustration, we may consider an example due to 
+As an illustration of an infinite game, we may consider a simple example due to 
 Baker \cite{baker}.
@@
 Certainly, $\pl A$ and $\pl B$ will never be in
-a position without (infinitely many) legal moves available, so this is
-an infinite game. While the game could never be ``completed'' in reality,
-the winning condition considers the infinite sequence of moves made by the
+a position without (infinitely many) legal moves available, and provided that
+$A$ is non-trivial, there is a playthrough such that for all $n<\omega$,
+the segment $(a_n,b_n)$ intersects both $A$ and $\mathbb{R}\setminus A$. 
+Such a playthrough could never be decided in a finite number of moves,
+so the winning condition considers the infinite sequence of moves made by the
 players and declares a victor at the ``end'' of the game.
-
-As a simple example, if $A=\mathbb{R}$, then $W=M^\omega$. That is,
-all playthroughs of the game are victories for $\pl A$, since every
-bounded increasing sequence converges to some real number.
 
@@
 
-Topological games are usually infinite games. One of the earliest examples
+Topological games are usually infinite games for non-trivial spaces.
+(The meaning of trivial here depends on the game played.)
+One of the earliest examples
 of a topological game is the Banach-Mazur game, proposed by Stanislaw Mazur
@@
 Intuitively, a strategy is a rule for one of the players on how to play
-the game based upon the previous moves of her opponent, while an attack is
-a fixed strike by an opponent.
+the game based upon the previous (finite) moves of her opponent, while an 
+attack is a fixed strike by an opponent indexed by round number.
 
 \begin{defn}
-  The \term{result} of a game for a strategy $\sigma$ for the first player and 
-  attack $\<a_0,a_1,\dots\>$ for  the second player is the playthrough
+  The \term{result} of a game given a strategy $\sigma$ for the first player 
+  and an attack $\<a_0,a_1,\dots\>$ by the second player is the playthrough
     \[
-      \<\sigma(\emptyset),a_0,\sigma(\<a_0\>), a_1, \sigma(\<a_0,a_1\>),\dots\>
+      \<
+        \sigma(\emptyset), 
+        a_0,
+        \sigma(\<a_0\>), 
+        a_1, 
+        \sigma(\<a_0,a_1\>),
+        \dots
+      \>
     \]
@@
     \[
-      \<a_0,\sigma(\<a_0\>), a_1, \sigma(\<a_0,a_1\>),\dots\>
+      \< 
+        a_0,
+        \sigma(\<a_0\>), 
+        a_1, 
+        \sigma(\<a_0,a_1\>),
+        \dots
+      \>
     \]
@@
   if either $\pl A \win G$ or $\pl B \win G$.
+  Otherwise, the game is \term{indetermined}.
 \end{defn}
 
-(TODO: cite Gale and Stewart)
-% http://en.wikipedia.org/wiki/Borel_determinacy_theorem
-
-\begin{thm}
+\begin{thm}\cite{gale}
   If the move set $M$ for a game $G=\<M,W\>$ is given the discrete topology
@@
 
-(TODO: outline proof?)
+This is actually a special case of the powerful Borel Determinacy theorem 
+which states that $G=\<M,W\>$ is determined whenever $W$ is a Borel subset
+of $M^\omega$. \cite{martin}
 
-We get this important corollary:
-
-\begin{cor}
-  Finite games are determined.
-\end{cor}
-
-\begin{proof} 
-  For every victory $p\in W$ for the first player, there was some 
-  round $n<\omega$ for which that partial playthrough was guaranteed to
-  result in a victory for the first player.
-
-  Put another way, there exists $n<\omega$ such that
-    $ 
-      \{q : q\geq p\rest n \}
-    $
-  (a neighborhood of $p$) is contained in $W$. Thus $W$ is open.
-\end{proof}
-
-(TODO: find combinatorial proof and cite it)
-
-(TODO: Cover Martin's Borel determinacy theorem?)
-
-Non-trivial topological games are infinite, however, and many are indetermined
-for certain spaces.
+It's an easy corollary that all finite games are determined
+($W$ must be clopen). As stated earlier, most topological games are infinite,
+and many are indetermined for certain spaces constructed using the Axiom of
+Choice.
+\footnote{
+  The Axiom of Choice is required, as the Axiom of Determinacy stating
+  that all Gale-Stewart games are determined is another axiom independent
+  of ZF. \cite{MR0140430}
+}
 

### 2014-05-12 phd/dissertation/chapter2.tex
almost finished chapter 2 draft

@@
 is the winner of that playthrough, and if $p\not\in W$, then $\pl B$ is
-the winner. (No ties are allowed.)
+the winner. Note that no ties are allowed.
 
@@
 rules of chess restict White from moving pieces which belong to
-Black, or moving a piece to an illegal space on the board. 
-\footnote{
+Black, or moving a piece to an illegal space on the board.\footnote{
   In practice, $M$ is often defined as the union of two sets, such
@@
 \begin{game}
-  Let $\bakergame{A}$ denote a game with players $\pl A$ and $\pl B$,
+  Let $\bakergame{X}$ denote a game with players $\pl A$ and $\pl B$,
   defined for each subset $A\subset \mathbb{R}$.
@@
 
-  $\pl A$ wins the game if the sequence $\<a_n:n<\omega\>$ converges to a 
-  point in $A$, and $\pl B$ wins otherwise.
+  $\pl A$ wins the game if the sequence $\<a_n:n<\omega\>$ limits to a
+  point in $X$, and $\pl B$ wins otherwise.
 \end{game}
@@
 
-Topological games are usually infinite games for non-trivial spaces.
-(The meaning of trivial here depends on the game played.)
+Topological games are usually infinite games, ignoring trivial examples.
 One of the earliest examples
@@
 
-  If a winning strategy exists for player $\pl A$ in the game $G$, then we
+  If a winning strategy exists for a player $\pl A$ in the game $G$, then we
   write $\pl A \win G$. Otherwise, we write $\pl A \not\win G$.
@@
 
-Of course, a strategy $\sigma$ is not a winning strategy for a player if there 
-exists some \term{counter-attack} by the opponent for which the result is 
-a victory for the opponent. Typically this counter-attack is defined in
-terms of the strategy $\sigma$; else, the counter-attack is itself a
-winning strategy depending on only the round number (which we will
-investigate further in a later section).
+To show that a winning strategy exists for a player (i.e. $\pl A\win G$),
+we typically begin by
+defining it and showing that it is \term{legal}: it only yields moves which are
+legal according to the rules of the game. Then, we consider an arbitrary
+legal attack, and prove that the result of the game is a victory for that
+player.
+
+If we wish to show that a winning strategy does not exist for a player
+(i.e. $\pl A\not\win G$), we
+often consider an arbitrary legal strategy, and use it to define a legal
+\term{counter-attack} for the opponent. If we can prove that the result of
+the game for that strategy and counter-attack is a victory for the opponent,
+then a winning strategy does not exist.
+
+Unlike finite games, is not the case that a winning strategy must exist for
+one of the players in an infinite game.
 
@@
   if either $\pl A \win G$ or $\pl B \win G$.
-  Otherwise, the game is \term{indetermined}.
+  Otherwise, the game is \term{undetermined}.
 \end{defn}
 
-\begin{thm}\cite{gale}
-  If the move set $M$ for a game $G=\<M,W\>$ is given the discrete topology
-  and $W$ is either an open or closed subset of $M^\omega$ with the
-  usual product topology, then $G$ is determined.
-\end{thm}
+The Borel Determinacy Theorem states that $G=\<M,W\>$ is determined whenever
+$W$ is a Borel subset of $M^\omega$ \cite{martin}. It's an easy corollary that
+all finite games are determined; $W$ must be clopen.
 
-This is actually a special case of the powerful Borel Determinacy theorem 
-which states that $G=\<M,W\>$ is determined whenever $W$ is a Borel subset
-of $M^\omega$. \cite{martin}
-
-It's an easy corollary that all finite games are determined
-($W$ must be clopen). As stated earlier, most topological games are infinite,
-and many are indetermined for certain spaces constructed using the Axiom of
-Choice.
-\footnote{
-  The Axiom of Choice is required, as the Axiom of Determinacy stating
-  that all Gale-Stewart games are determined is another axiom independent
-  of ZF. \cite{MR0140430}
+However, as stated earlier, most topological games are infinite,
+and many are undetermined for certain spaces constructed using the Axiom of
+Choice.\footnote{
+  These spaces cannot be constructed just only the axioms of ZF. In fact,
+  mathematicians have studied an Axiom of Determinacy which declares that
+  that all Gale-Stewart games are determined (and implies that the Axiom
+  of Choice is false). \cite{MR0140430}
 }
-
-\begin{ex}
-  Let $B$ be a Bernstein subset of the real line. Then $\bmgame{B}$ is
-  undetermined.
-\end{ex}
-
-\begin{proof}
-  It can be shown that $B$ is a Baire space, and we will soon see that 
-  $\pl E\not\win \bmgame{X}$ characterizes Baire spaces. Also, if $\sigma$
-  is a winning strategy for $\pl N$ in $\bmgame{Y}$ for $Y\subseteq X$, it can 
-  be shown that $Y$ contains a closed uncountable set in $X$. 
-  Thus $\pl N\not\win \bmgame{B}$.
-\end{proof}
 
@@
 
-The presence or absence of a winning strategie for a player in a topological
-game characterizes a property of the topological space in question.
+The power of studying these infinite-length games can be illustrated by
+considering the following proposition.
 
-A classical result follows.
+\begin{prop}
+  If $X$ is countable, then $\pl B \win \bakergame{X}$.
+\end{prop}
+
+\begin{proof}
+  Adapted from \cite{baker}.
+  Let $X=\{x_0,x_1,\dots\}$. Let $i(a,b)$ be the least integer such that
+  $a<x_{i(x,y)}<b$, if it exists. We define a strategy $\sigma$ for $\pl B$
+  such that:
+  \begin{itemize}
+    \item $\sigma(\<a_0\>)=x_{i(a_0,\infty)}$.
+          If $i(a_0,\infty)$ does not exist, then the choice of $\sigma(\<a_0\>)$
+          is arbitary, say, $a_0+1$.
+    \item $\sigma(\<a_0,...,a_{n+1}\>)=x_{i(a_{n+1},b_n)}$, where
+          $b_n=\sigma(\<a_0,\dots,a_n\>)$.
+          If $i(a_{n+1},b_n)$ does not exist, then the choice of
+          $\sigma(\<a_0,...,a_{n+1}\>)$ is arbitrary, say,
+          $
+            \sigma(\<a_0,...,a_{n+1}\>)
+              =
+            \frac{a_{n+1}+b_n}{2}
+          $.
+  \end{itemize}
+
+  Observe that $\sigma$ is a legal strategy according to the rules of the game
+  since $a_0<\sigma(\<a_0\>)$ and $a_{n+1}<\sigma(\<a_0,\dots,a_{n+1}\>)<b_n$.
+  We claim this is a winning strategy for $\pl B$. Let $a=\<a_0,a_1,\dots\>$
+  be a legal attack by $\pl A$ against $\sigma$: we will show that the
+  resulting playthrough is a victory for $\pl B$, that is,
+  $\lim_{n\to\infty} a_n\not\in X$. Let $b_n=\sigma(\<a_0,\dots,a_n\>)$.
+  Note that
+    \[
+      a_0<a_1<\dots<\lim_{n\to\infty}a_n<\dots<b_1<b_0
+    \]
+
+  If $i(a_0,\infty)$ does not exist, then $a_0$ is greater than every element
+  of $X$, and thus
+  $\lim_{n\to\infty} a_n \not\in X$. A similar argument follows if some
+  $i(a_{n+1},b_n)$ does not exist.
+
+  Otherwise,
+    \[
+      i(a_0,\infty)<i(a_1,b_0)<i(a_2,b_1)<\dots
+    \]
+  and for each $i<\omega$, one of the following must hold.
+    \begin{itemize}
+      \item $i<i(a_0,\infty)$. Then $x_i\leq a_0<\lim_{n\to\infty}a_n$.
+      \item $i = i(a_0,\infty)$. Then $x_i=b_0>\lim_{n\to\infty}a_n$.
+      \item $i(a_0,\infty)<i<i(a_1,b_0)$.
+            Then $x_i\leq a_1<\lim_{n\to\infty}a_n$ or
+            $x_i\geq b_0>\lim_{n\to\infty}a_n$.
+      \item $i = i(a_{n+1},b_n)$ for some $n<\omega$.
+            Then $x_i=b_{n+1}>\lim_{n\to\infty}a_n$.
+      \item $i(a_{n+1},b_n)<i<i(a_{n+2},b_{n+1})$ for some $n<\omega$.
+            Then $x_i\leq a_{n+2}<\lim_{n\to\infty}a_n$ or
+            $x_i\geq b_{n+1}>\lim_{n\to\infty}a_n$.
+    \end{itemize}
+  In any case, $x_i\not=\lim_{n\to\infty}a_n$, and thus
+  $\lim_{n\to\infty}a_n\not\in X$.
+\end{proof}
+
+This yields a classical result.
+
+\begin{cor}
+  $\mathbb{R}$ is uncountable.
+\end{cor}
+
+\begin{proof}
+  $\pl A\win \bakergame{\mathbb{R}}$, since $a_n$ must converge to some
+  real number. This implies $\pl B\not\win \bakergame{\mathbb{R}}$, and thus
+  $\mathbb{R}$ is not countable.
+\end{proof}
+
+Infinite games thus provide a rich framework for considering questions in
+set theory and topology. In general, the presence or absence of a winning
+strategy for a player in a topological game characterizes a property of the
+topological space in question.
 
@@
 
-\section{Examples of Topological Games}
+So far we have assumed both players enjoy \term{perfect information}, and
+may develop strategies which use all of the previous moves of the opponent
+as input.
 
-(TODO: )
+\begin{defn}
+  For a game $G=\<M,W\>$, the \term{$k$-tactical fog-of-war} is the function
+  $\nu_k:M^{<\omega}\to M^{\leq k}$ defined by
+    \[
+      \nu_k(\<m_0,\dots,m_{n-1}\>)=\<m_{n-k},\dots,m_{n-1}\>
+    \]
+  and the \term{$k$-Mark\"ov fog-of-war} is the function
+  $\mu_k:M^{<\omega}\to (M^{\leq k}\times\omega)$ defined by
+    \[
+      \mu_k(\<m_0,\dots,m_{n-1}\>)=\<\<m_{n-k},\dots,m_{n-1}\>,n\>
+    \]
+\end{defn}
+
+Essentially, these fogs-of-war represent a limited memory: $\nu_k$ filters out
+all but the last $k$ moves of the opponent, and $\mu_k$ filters out all but
+the last $k$ moves of the opponent and the round number.
+
+We call strategies which do not require full recollection of the opponent's
+moves \term{limited information strategies}.
+
+\begin{defn}
+  A \term{$k$-tactical strategy} or \term{$k$-tactic} is a limited information
+  strategy of the form $\sigma\circ\nu_k$.
+
+  A \term{$k$-Mark\"ov strategy} or \term{$k$-mark} is a limited information
+  strategy of the form $\sigma\circ\mu_k$.
+\end{defn}
+
+$k$-tactics and $k$-marks may then only use the last $k$ moves of the opponent,
+and in the latter case, also the round number.
+
+The $k$ is usually omitted when $k=1$. A ($1$-)tactic is
+called a \term{stationary strategy} by some authors. $0$-tactics are not
+usually interesting (such strategies would be constant functions); however,
+we will discuss $0$-Mark\"ov strategies, called
+\term{predetermined strategies} since such a strategy only uses the round
+number and does not rely on knowing which moves the opponent will make.
+
+\begin{defn}
+  If a winning $k$-tactical strategy exists for a player $\pl A$ in the game
+  $G$, then we write $\pl A \ktactwin{k} G$. If $k=1$, then $\pl A \tactwin G$.
+
+  If a winning $k$-Mark\"ov strategy exists for a player $\pl A$ in the game
+  $G$, then we write $\pl A \kmarkwin{k} G$. If $k=1$, then $\pl A \markwin G$,
+  and if $k=0$, then $\pl A \prewin G$.
+\end{defn}
+
+The existence of a winning limited information strategy can characterize a
+stronger property than the property characterized by a perfect information
+strategy.
+
+\begin{defn}
+  $X$ is an \term{$\alpha$-favorable space}
+  when $\pl N \tactwin \bmgame{X}$.
+  $X$ is a \term{weakly $\alpha$-favorable space}
+  when $\pl N \win \bmgame{X}$.
+\end{defn}
+
+\begin{obs}
+  $X$ is $\alpha$-favorable
+    $\Rightarrow$
+  $X$ is weakly $\alpha$-favorable
+    $\Rightarrow$
+  $X$ is Baire
+\end{obs}
+
+Those arrows may not be reversed. A Bernstein subset of the real line is an
+example of a Baire space which is not weakly $\alpha$-favorable, and

### 2014-05-14 phd/dissertation/_raw_chapter4.tex
Finish ch 2 draft, outline of results for ch 3, ch 6

--- 2013-01-24 old_phd_research_results_april_2012.tex
@@
-\documentclass[11pt]{article}
+%!TEX root = dissertation.tex
+% ^ leave for LaTeXTools build functionality
 
-\pdfpagewidth 8.5in
-\pdfpageheight 11in
+\chapter{Locally Finite Games}
 
-\setlength\topmargin{0in}
-\setlength\headheight{0in}
-\setlength\headsep{0.2in}
-\setlength\textheight{8in}
-\setlength\textwidth{6in}
-\setlength\oddsidemargin{0in}
-\setlength\evensidemargin{0in}
-\setlength\parindent{0.25in}
-\setlength\parskip{0.1in}
+Results pertaining to the Locally Finite game related to the W games.
 
-\usepackage{amssymb}
-\usepackage{amsfonts}
-\usepackage{amsmath}
-\usepackage{mathtools}
-\usepackage{amsthm}
+\section{basic results}
 
-      \theoremstyle{plain}
-      \newtheorem{theorem}{Theorem}
-      \newtheorem{lemma}[theorem]{Lemma}
-      \newtheorem{corollary}[theorem]{Corollary}
-      \newtheorem{proposition}[theorem]{Proposition}
-      \newtheorem{conjecture}[theorem]{Conjecture}
-      \newtheorem{question}[theorem]{Question}
-      \newtheorem{example}[theorem]{Example}
-
-      \theoremstyle{definition}
-      \newtheorem{definition}[theorem]{Definition}
-
-      \theoremstyle{remark}
-      \newtheorem{remark}[theorem]{Remark}
-
-% Strategy uparrow shortcuts
-\newcommand{\prewin}{\uparrow_{\text{pre}}}
-\newcommand{\markwin}{\uparrow_{\text{mark}}}
-\newcommand{\tactwin}{\uparrow_{\text{tact}}}
-\newcommand{\ktactwin}[1]{\uparrow_{#1\text{-tact}}}
-\newcommand{\kmarkwin}[1]{\uparrow_{#1\text{-mark}}}
-\newcommand{\codewin}{\uparrow_{\text{code}}}
-\newcommand{\limitwin}{\uparrow_{\text{limit}}}
-
-\begin{document}
-
-\centerline{\bf PhD Research Results}
-\centerline{Steven Clontz}
-
-\begin{definition} Some notation on games of length $\omega$:
-
-\begin{itemize}
-\item A \textbf{game of length $\omega$} consists of two \textbf{Players} I and II.
-On \textbf{round} $n$ of $\omega$, Player I first takes a \textbf{turn} choosing an element of some set $X$, followed by Player II taking a turn choosing an element from some set $Y$.
-
-\item A \textbf{move} by a player is the selection that player makes during a particular round.
-
-\item A \textbf{rule} for a Player in a game is a condition on that player's move during each round. A move is said to be \textbf{legal} if it doesn't violate the rule.
-
-\item A \textbf{play} by Player I is a sequence $\left<x_0,x_1,\dots\right> \in X^\omega$ (and similar for Player II).
-It is said to be \textbf{legal} if each move is legal.
-A finite initial sequence of a play is called a \textbf{partial play}.
-
-\item A \textbf{strategy} for a Player is a function which has all possible partial plays by the opposing player as its domain.
-It denotes the choice for that Player on each turn.
-It is said to be \textbf{legal} if it yields only legal moves when the opposing player makes only legal moves.
-
-\item A \textbf{counter} to a legal strategy by a Player is a function which has as its domain the turn number and the other player's strategy.
-It is said to be \textbf{legal} if it only yields legal moves.
-
-\item A \textbf{winning condition} is some condition on the plays made by both players.
-
-\item At the conclusion of a game, if all moves are legal, then Player I \textbf{wins} the game if the winning condition is satisfied, and Player II wins the game otherwise.
-(Should any move be illegal, then the first player to make an illegal move loses the game to the other player.)
-\end{itemize}
-\end{definition}
-
-When the sets $X,Y$ are related to a topological space, it is said to be a \textbf{topological game}.
-The presence or absense of a ``winning'' strategy for one player or another characterizes a property of the space.
-
-\begin{definition}
-A strategy for Player A is said to be a \textbf{winning strategy} if there does not exist a counter which allows the other player to win the game.
-If Player Z has a winning strategy for the game $G$, this can be denoted $Z \uparrow G$.
-\end{definition}
-
-Proofs showing the existance of a winning strategy typically define the winning strategy, and then show that it defeats every possible play by the opponent.
-Proofs showing the nonexistance of a winning strategy typically define the counter to any arbitrary strategy.
-
-In the mid 1980s, Dr. Gary Gruenhage defined the following topological games.
-
-\begin{definition}
-The \textbf{compact-point game on a topological space $X$} is denoted $G_{K,P}(X)$.
-During round $n$, Player I (called $K$) chooses a compact set $K_n\in K[X]$, and Player II (called $P$) chooses a point $x_n\in X$.
-$K$ must follow the rule that $K_{n+1}\supseteq K_n$, while $P$ must follow the rule that $x_n\not\in K_n$.
-The winning condition for $K$ is that the collection of singletons chosen by $P$, $\{\{x_n\} : n<\omega\}$, must be locally finite everywhere in the space.
-(This is equivalent to the set $\{x_n : n<\omega\}$ lacking a cluster point.)
-\end{definition}
-
-\begin{definition}
-The \textbf{compact-compact game on a topological space $X$} is denoted $G_{K,L}(X)$.
-During round $n$, Player I (called $K$) chooses a compact set $K_n\in K[X]$, and Player II (called $L$) also chooses a compact set $L_n\in K[X]$.
-$K$ must follow the rule that $K_{n+1}\supseteq K_n$, while $P$ must follow the rule that $L_n\cap K_n=\emptyset$.
-The winning condition for $K$ is that the collection of compact sets chosen by $L$, $\{L_n : n<\omega\}$, must be locally finite everywhere in the space.
-\end{definition}
-
-An interesting property of the game $G_{K,L}(X)$ is the following result, proven by Gruenhage in his paper \textit{Games Covering Properties and Eberlein Compacts}.
-
-\begin{theorem}
+\begin{thm}
 The following are equivalent for a locally compact space $X$:
@@
     \end{itemize}
-\end{theorem}
+\end{thm}
 
@@
 
-\begin{definition}
+\begin{defn}
 A \textbf{limited information strategy} for a game is a function whose domain is restricted to less information than all previous moves by the opposing player.
-\end{definition}
+\end{defn}
 
@@
 
-\begin{definition}
+\begin{defn}
 A \textbf{tactical strategy} considers only the most recent move by the opposing player. If Player $Z$ has a winning tactical strategy for a game $G$, this may be denoted $Z \uparrow_{\text{tact}} G$.
-\end{definition}
+\end{defn}
 
-\begin{definition}
+\begin{defn}
 A \textbf{Markov strategy} considers only the most recent move by the opposing player and the turn number.
 If Player $Z$ has a winning Markov strategy for a game $G$, this may be denoted $Z \uparrow_{\text{mark}} G$.
-\end{definition}
+\end{defn}
 
-\begin{theorem}
+\begin{thm}
 The following are equivalent for a locally compact space $X$:
@@
     \end{itemize}
-\end{theorem}
+\end{thm}
 
-\begin{theorem}
+\begin{thm}
 The following are equivalent for a locally compact space $X$:
@@
 
-\begin{definition}
+\begin{defn}
 A \textbf{predetermined strategy} considers only the turn number. If Player $Z$ has a winning predetermined strategy for a game $G$, this may be denoted $Z \prewin G$.
-\end{definition}
+\end{defn}
 
@@
 
-\begin{definition}
+\begin{defn}
 A \textbf{button-mashing strategy} is a constant function. If Player $Z$ has a winning button-mashing strategy for a game $G$, this may be denoted $Z \uparrow_{\text{mash}} G$.
-\end{definition}
+\end{defn}
 
-\begin{proposition}
+\begin{prop}
 The following are equivalent for any space $X$:
@@
     \end{itemize}
-\end{proposition}
+\end{prop}
 
@@
 
-\begin{proposition}
+\begin{prop}
 If $K \prewin G_{K,P}(X)$, then $X$ is $\sigma$-compact.
-\end{proposition}
+\end{prop}
 
@@
 
-\begin{theorem}
+\begin{thm}
 If $Y$ is a locally compact, Lindel\"of space, then $K \prewin G_{K,P}(X)$.
-\end{theorem}
+\end{thm}
 
@@
 
-\begin{corollary}
+\begin{cor}
 The following are equivalent for a locally compact space $X$:
@@
     \end{itemize}
-\end{corollary}
+\end{cor}
 
@@
 
-\begin{definition}
+\begin{defn}
 Let $M=\omega^2\cup\{\infty\}$ denote the \textbf{metric fan space} with the topology generated by the singletons in $\omega^2$ and sets of the form $((\omega\setminus n)\times\omega) \cup \{\infty\}$ for $n<\omega$.
-\end{definition}
+\end{defn}
 
-\begin{proposition}
+\begin{prop}
 For each compact set $C$ in $M$, there exists a minimal dominating function $f_C$ such that for each $(x,y)\in C\setminus\{\infty\}$, $f(x)> y$.
-\end{proposition}
+\end{prop}
 
-\begin{lemma}
+\begin{lem}
 $P \markwin G_{K,P}(M)$ where $M$ is the metric fan space. (This implies $K\not\uparrow G_{K,P}(M)$.)
-\end{lemma}
+\end{lem}
 
@@
 
-\begin{theorem}
+\begin{thm}
 Every first-countable non-locally countably compact space has the metric fan space $M$ as a closed subspace.
-\end{theorem}
+\end{thm}
 
@@
 
-\begin{corollary}
+\begin{cor}
 $P \markwin G_{K,P}(X)$ where $X$ is a first-countable non-locally countably compact space. (This implies $K\not\uparrow G_{K,P}(X)$.)
-\end{corollary}
+\end{cor}
 
@@
 
-\begin{theorem}
+\begin{thm}
 $P \not\tactwin D_{K,P}(M)$ where $M$ is the metric fan space.
-\end{theorem}
+\end{thm}
 
@@
 
-\begin{definition}
+\begin{defn}
 A space $X$ is \textbf{hemicompact} if there exists a chain of increasing compact sets $K_0\subseteq K_1 \subseteq \dots$ such that every compact set in $X$ is a subset of some $K_n$.
-\end{definition}
+\end{defn}
 
-\begin{lemma}
+\begin{lem}
 If $K\prewin G_{K,P}(X)$, then $X$ is hemicompact. Furthermore, any predetermined winning strategy for $K$ witnesses hemicompactness.
-\end{lemma}
+\end{lem}
 
@@
 
-\begin{theorem}
+\begin{thm}
 The following are equivalent for any locally compact space $X$:
@@
   \end{itemize}
-\end{theorem}
+\end{thm}
 
@@
 
-\begin{corollary}
+\begin{cor}
 The following are equivalent for any locally compact space $X$:
@@
   \end{itemize}
-\end{corollary}
+\end{cor}
 
@@
 
-\begin{definition}
+\begin{defn}
 A topological space is called a \textbf{$k$-space} if the following condition is satisfied: \[C \subseteq X \text{ is closed in } X\, \Leftrightarrow \, C\cap K \text{ is closed in } K \text{ for all compact sets } K\in K[X]\]
-\end{definition}
+\end{defn}
 
-\begin{definition}
+\begin{defn}
 A topological space is called a \textbf{$k_\omega$-space} if there exist $K_0,K_1,\dots \in K[X]$ that satisfy the following condition: \[C \subseteq X \text{ is closed in } X\, \Leftrightarrow \, C \cap K_n \text{ is closed in } K_n \text{ for all } n\]
-\end{definition}
+\end{defn}
 
-\begin{theorem}
+\begin{thm}
 The following are equivalent for any Hausdorff $k$-space $X$:
@@
 Furthermore, all predetermined strategies for $K$ witness hemicompact and $k_\omega$, and any witness to hemicompact/$k_\omega$ witnesses the other and serves as a predetermined strategy for $K$.
-\end{theorem}
+\end{thm}
 
@@
 
-\begin{theorem}
+\begin{thm}
 For any hemicompact Hausdorff $k$-space $X$, $K \prewin G_{K,L}(X)$.
-\end{theorem}
+\end{thm}
 
@@
 
-\begin{corollary}
+\begin{cor}
 The following are equivalent for any Hausdorff $k$-space $X$:
@@
 
-\begin{definition}
+\begin{defn}
 Given a set $X$, an ultrafilter on $X$ is a collection $\mathcal{F}\subseteq\mathcal{P}(X)$ such that
@@
 As a result, ultrafilters which contain a finite set contain only one singleton (and are called \textbf{principal}). Otherwise, ultrafilters which contain no finite sets are called \textbf{free}.
-\end{definition}
+\end{defn}
 
-\begin{definition}
+\begin{defn}
 The \textbf{Stone-Cech compactification} $\beta\omega$ of $\omega$ is the collection of ultrafilters on $\omega$.
@@
 Alternately $\beta\omega=\omega\cup\{\mathcal{F} : \mathcal{F}$ is a free ultrafilter on $\omega\}$ where $\omega$ is discrete and the free ultrafilters have the local base described above.
-\end{definition}
+\end{defn}
 
-\begin{definition}
+\begin{defn}
 A \textbf{single-ultrafilter space} is a subset of $\beta\omega$ containing all elements of $\omega$ and a single ultrafilter $\mathcal{F}$.
-\end{definition}
+\end{defn}
 
-\begin{proposition}
+\begin{prop}
 The compact sets of a single-ultrafilter space are exactly the finite subsets of the space. Thus a single-ultrafilter space is neither locally compact nor $k$.
-\end{proposition}
+\end{prop}
 
@@
 
-\begin{proposition}
+\begin{prop}
 If $X$ is any single-ultrafilter space with the ultrafilter $\mathcal{F}$, then $K\not\prewin G_{K,L}(X)$.
-\end{proposition}
+\end{prop}
 
@@
 
-\begin{proposition} 
+\begin{prop} 
 If a selective ultrafilter $\mathcal{F}$ exists (this is independent of ZFC), then $K$ has no winning predetermined strategy in the compact-point game $G_{K,P}(Y)$ for the single selective ultrafilter space $Y=\omega \cup \{\mathcal{F}\}$.
-\end{proposition}
+\end{prop}
 
@@
 
-\begin{theorem}
+\begin{thm}
 Let $a_n$ be a sequence such that the sequence $\frac{a_n}{n}$ is unbounded above.
 Then there is an ultrafilter $\mathcal{F}$ such that $\sigma(n)=(\sum_{m\leq n} a_m )\cup \{\mathcal{F}\}$ is a winning predetermined strategy for $K$ in $G_{K,P}(\omega\cup\{\mathcal{F}\})$.
-\end{theorem}
+\end{thm}
 
@@
 
-\begin{question}
+\begin{ques}
 $K \prewin G_{K,L}(X) \Rightarrow X$ is a $k$-space?
-\end{question}
+\end{ques}
 
-\centerline{\bf Another game: $Con_{O,P}(X,x)$}
+\section{Cantor space example}
 
-\begin{definition} 
-Gruenhage's open-point convergence game $Con_{O,P}(X,x)$ has $O$ choosing nested open sets and $P$ choosing a point within the last chosen open set by $O$.
-$O$ wins if the points chosen by $P$ converge to $x$.
-\end{definition}
+\begin{ex}
+Let $X$ be a zero-dimensional, compact L-space (hereditarally Lindeloff and non-separable).
+It is a fact that there exists a point-countable collection $\mathcal{U}=\{U_\alpha : \alpha<\omega_1\}$ of clopen sets in $X$, and it is also true that any point-finite subcollection of $\mathcal{U}$ is countable.
+%That is, if we let $A_x = \{\alpha : x \in U_\alpha\}$, then $|A_x|\leq\omega$ for all $x\in X$.
 
-\begin{definition}
-The one-point compactification of a space $X$ is $X\cup\{\infty\}$, where neighborhoods of points in $X$ are the same as they were originally, and neighborhoods of $\infty$ are sets $X\cup\{\infty\}\setminus K$ for compact $K$.
-If $X$ is discrete then neighborhoods of $\infty$ are cofinite sets containing $\infty$.
-\end{definition}
+Let $C = \{c_\alpha : \alpha <\omega_1\}$ be any uncountable subset of the Cantor space $2^\omega$. Let $X_s = X \times \{s\}$ for each $s \in 2^{<\omega}$, and $U_{\alpha,s} = U_\alpha \times \{s\}$.
 
-\begin{proposition}
-$O\not\prewin Con_{O,P}(\kappa\cup\{\infty\},\infty)$, where $\kappa\cup\{\infty\}$ is the one-point compactification of discrete $\kappa\geq\omega_1$.
-\end{proposition}
+Finally, let \[\mathbb{X} = C \cup \bigcup_{s\in 2^{<\omega}} X_s\] be a tree of $2^{<\omega}$ copies of $X$, and where \[c_\alpha \cup \bigcup_{n < \omega} U_{\alpha, x_\alpha \restriction n}\] is an open set about each $c_\alpha$.
+\end{ex}
+
+\begin{defn}
+Let $S\in[\omega_1]^{<\omega}$ and $m<\omega$. Define 
+    \[K_S = \bigcup_{\alpha \in S} \left( c_\alpha \cup \left(\bigcup_{s < c_\alpha} U_{\alpha,s}\right)\right)\] 
+    \[ A = \{z^\frown \<1\> : z \in 1^{<\omega}\}\] 
+    \[ K^*_S = K_S \setminus \bigcup_{s \in A} X_s \] 
+and 
+    \[L_m = \bigcup_{s \in 2^{<m}} X_s\] 
+and observe that every compact set is dominated by $K^*_S \cup L_m$ for some $S,m$.
+Intuitively, $K^*_S$ collects the branches of $U_\alpha$ converging up to $c_\alpha$ for each $\alpha \in S$ while avoiding copies $X_s$ of $X$ for each $s$ in an antichain $A$, and $L_m$ collects the copies $X_s$ of $X$ with $|s| < m$ at the base of the tree.
+\end{defn}
+
+\begin{prop}
+Without loss of generality, $P$ always plays points in $\bigcup_{s \in 2^{<\omega}} X_s$.
+\end{prop}
+
+\begin{prop}
+$K \win \lfkpgame{\mathbb{X}}$.
+\end{prop}
 
 \begin{proof}
-Given a predetermined strategy $\sigma(n)$ for $O$, $P$ simply chooses any ordinal in $\bigcap_{n<\omega} \sigma(n)$ to play on every turn.
+In response to a point $\<x,s\>$, $K$ observes that there are only countably many $\alpha$ such that $U_\alpha \times \{s\}$ contains $\<x,s\>$ (by point-countability of $X$).
+Enumerate these as $\alpha_n$.
+$K$ makes a promise that during round $m$, $K$ will forbid some superset of $K_{\{\alpha_n : n\leq m\}}$.
+Finally, $K$ also always forbids a superset of $L_{|s|+1}$.
+
+Suppose $P$'s moves clustered at some point.
+Since $K$ forbade $L_{|s|+1}$ during each round, that point must be $c_\alpha$ for some $\alpha$.
+$P$'s play then must have included a subsequence of points $\<x_0,s_0\>,\<x_1,s_1\>,\<x_2,s_2\>\dots$ such that $x_n \in U_\alpha$ and $s_n \leq s_{n+1} \leq c_\alpha$.
+However, in response to $\<x_0,s_0\>$, $K$ made a promise to eventually forbid a superset of $K_{\{\alpha\}}$, making every $\<x_n,t_n\>$ illegal after that round.
 \end{proof}
 
-\begin{definition}
-A \textbf{coding strategy} considers only the most recent move by each player. If Player $Z$ has a winning coding strategy for a game $G$, this may be denoted $Z \codewin G$.
-\end{definition}
-
-\begin{proposition}
-$O\codewin Con_{O,P}(\kappa\cup\{\infty\},\infty)$ for any cardinal $\kappa$. 
-\end{proposition}
+\begin{thm}
+$K\not\tactwin\lfkpgame{\mathbb{X}}$.
+\end{thm}
 
 \begin{proof}
-Define $\sigma(U,p)=U\setminus\{p\}$. A legal play by $P$ must never repeat the same point, so legal plays by $P$ converge to $\infty$.
+This is actually a corollary of G's theorem in [?]. The following is a direct game-theoretic proof.
+
+Suppose that $\sigma(\<x,s\>)$ was a winning strategy for $K$ and assume 
+  \[
+    \sigma(\<x,s\>) = \bigcup_{|t|\leq |s|} \sigma(\<x,t\>) = \sigma'(x,|s|)
+  \]
+Thus there exists some $f: \omega_1 \to \omega$ such that $\sigma'(x,f(\alpha))$ covers every neighborhood of $c_\alpha$ for all $x\in U_\alpha$.
+(If not, $P$ wins by taking the $\alpha$ for which $f$ is not defined, and may always play $\<x,s\>$ in a neighborhood of $c_\alpha$ for which $\sigma'(x,|s|)$ doesn't cover a neighborhood of $c_\alpha$.) Fix $n$ for which $f(\alpha)=n$ for $\alpha$ in an uncountable set $A$.
+
+Since the collection $\{U_\alpha : \alpha \in A\}$ is uncountable, it is not point-finite.
+Fix $x$ so that $x$ belongs to $U_\alpha$ for all $\alpha$ in an infinite $B \subseteq A$.
+Finally, consider $\sigma'(x,n)$.
+For each $\alpha\in B$, $\sigma'(x,f(\alpha))=\sigma'(x,n)$ covers $c_\alpha$.
+Since $\{c_\alpha : \alpha \in B\}$ is a closed infinite discrete set, we have a contradiction to the compactness of $\sigma'(x,n)$.
 \end{proof}
 
-\begin{proposition}
-$O\not\tactwin Con_{O,P}(\kappa\cup\{\infty\},\infty)$ for $\kappa\geq\omega_1$.
-\end{proposition}
+\begin{thm}
+$K\not\ktactwin{2}\lfkpgame{\mathbb{X}}$.
+\end{thm}
 
 \begin{proof}
-Let $F(\alpha)$ be the complement of a tactical strategy for $O$.
-There exists some $n<\omega$ such that we may find an infinite $B\subseteq \omega_1$ with $n\not\in F(\beta)$ for $\beta\in B$ - if not, we may find uncountable ordinals $\alpha$ such that $\omega \subseteq F(\alpha)$, a contradiction.
-Choose $\beta\in B\setminus F(n)$, and note that repeating $n,\beta$ is a successful counter to $O$'s strategy.
+Suppose $\sigma(\<x,s\>,\<y,t\>)$ was a winning 2-tactical strategy. We may define $S(x,y,n)\in [\omega_1]^{<\omega}$ (increasing on $n$) and $n<m(x,y,n)<\omega$ such that for each $(x,y)$,
+  \[
+    \bigcup_{s,t \in 2^{\leq n}} \sigma(\<x,s\>,\<y,t\>) \subseteq 
+    K^*_{S(x,y,n)} \cup L_{m(x,y,n)}
+  \]
+and so we assume
+  \[
+    \sigma(\<x,s\>,\<y,t\>) =
+    K^*_{S(x,y,\max(|s|,|t|))} \cup L_{m(x,y,\max(|s|,|t|))}
+  \]
+
+Select an arbitrary point $x' \in X$. We define a tactical strategy 
+  \[
+  \tau(x,s) = 
+  K^*_{S(x,x',m(x,x',|s|)+1)} \cup L_{m(x,x',m(x,x',|s|)+1)}
+  \]
+We complete the proof by showing $\tau$ is a winning tactical strategy (a contradiction).
+
+Suppose
+\[
+\<x_0, s_0\>, \<x_1, s_1\>, \<x_2, s_2\>, \dots
+\]
+successfully countered $\tau$ by clustering at $c\in C$ (the strategy trivially prevents clustering elsewhere). Let $z_n = \<0,\dots,0\>$ with $n$ zeros. We claim
+\[
+\<x_0, s_0\>, \<x', {z_{m(x_0,x',|s_0|)}}^\frown\<1\>\>, \<x_1, s_1\>, \<x', {z_{m(x_1,x',|s_1|)}}^\frown\<1\>\>,  \<x_2, s_2\>, \<x', {z_{m(x_2,x',|s_2|)}}^\frown\<1\>\>, \dots
+\]
+is a successful counter to $\sigma$.
+
+We will need the fact that, as $\<x_{i+1},s_{i+1}\>$ was legal against $\tau$:
+  \[
+    |s_i| <
+    m(x_i,x',|s_i|)+1 =
+    |{z_{m(x_i,x',|s_i|)}}^\frown\<1\>| 
+  \]
+  \[
+    <
+    m(x_i,x',m(x_i,x',|s_i|)+1) =
+    m(x_i,x',|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|) \leq
+    |s_{i+1}|
+  \]
+
+Note that $m(x,y,\max(|s|,|t|))$ is increasing throughout this play of the game versus $\sigma$:
+  \[
+    m(x_i,x',\max(|s_i|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|))
+  \]
+  \[
+    =
+    m(x_i,x',|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|)
+  \]
+  \[
+    \leq
+    |s_{i+1}| 
+  \]
+  \[
+    <
+    m(x_{i+1},x',|s_{i+1}|)
+  \]
+  \[
+    =
+    m(x_{i+1},x',\max(|s_{i+1}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|))
+  \]
+  \[
+    =
+    |{z_{m(x_{i+1},x',|s_{i+1}|)}}|
+  \]
+  \[
+    <
+    |{z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>|
+  \]
+  \[
+    <
+    m(x_{i+1},x',|{z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>|)
+  \]
+  \[
+    =
+    m(x_{i+1},x',\max(|s_{i+1}|,|{z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>|))
+  \]
+
+We turn to showing that $\<x', {z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>\>$ is always a legal move.
+Since ${z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>$ is on the antichain avoided by any $K^*$, the problem is reduced to showing that this move isn't forbidden by
+  \[
+  L_{m(x_{i+1},x',\max(|s_{i+1}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|))}
+  \]
+which we can see here:
+  \[
+    m(x_{i+1},x',\max(|s_{i+1}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|)) =
+    m(x_{i+1},x',|s_{i+1}|) <
+    |{z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>|
+  \]
+
+We can conclude by showing that $\<x_{i+1},s_{i+1}\>$ is always a legal move. We can see it avoids 
+  \[
+  L_{m(x_{i},x',\max(|s_{i}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|))}
+  \]
+since
+  \[
+    m(x_{i},x',\max(|s_{i}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|)) =
+    m(x_{i},x',|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|) \leq
+    |s_{i+1}|
+  \]
+
+Since $\<x_{i+1},s_{i+1}\>$ was legal against $\tau$, it avoided
+  \[
+    K^*_{S(x_h,x',m(x_h,x',|s_h|)+1)} = 
+    K^*_{S(x_h,x',\max(|s_h|,|{z_{m(x_h,x',|s_h|)}}^\frown\<1\>|))}
+  \]
+for $h\leq i$. And when $h<i$, we see it avoids:
+  \[
+    K^*_{S(x_{h+1},x',\max(|s_{h+1}|,|{z_{m(x_h,x',|s_h|)}}^\frown\<1\>|))} =
+    K^*_{S(x_{h+1},x',|s_{h+1}|)}
+  \]
+  \[
+    \subseteq
+    K^*_{S(x_{h+1},x',m(x_{h+1},x',|s_{h+1}|)+1)}
+  \]
+
+This concludes the proof.
 \end{proof}
 
-\begin{definition}
-A \textbf{$k$-tactical strategy} considers only the last $k$ moves by the opposing player. If Player $Z$ has a winning $k$-tactical strategy for a game $G$, this may be denoted $Z \ktactwin{k} G$.
-\end{definition}
-
-\begin{theorem}
-$O\not\ktactwin{k}Con_{O,P}(\kappa\cup\{\infty\},\infty)$ for $\kappa\geq\omega_1$.
-\end{theorem}
+\begin{thm}
+$K\not\ktactwin{k}\lfkpgame{\mathbb{X}}$.
+\end{thm}
 
 \begin{proof}
-Let $\sigma:[\omega_1]^{\leq k}\to[\omega_1]^{<\omega}$ be a $k$-tactical strategy for $O$ restricted to $\omega_1$ and $F(S)=\omega_1\setminus\sigma(S)$.
+The proof proceeds in parallel to the proof of $K\not\ktactwin{2}\lfkpgame{\mathbb{X}}$.
 
-Let $W_0=\omega_1$. We define $W_\alpha$ recursively as follows:
-    \begin{itemize}
-    \item For successor ordinals $\alpha+1$, let $\beta$ be the least element of $W_\alpha$ such that $[\beta+1,\omega_1) \cap \bigcup_{S\leq \beta} F(S)$ is nonempty, where $S \leq \beta$ is shorthand for $\{S \in [\omega_1]^{\leq k} : \forall \gamma \in S(\gamma < \beta)\}$.
-If no such $\beta$ exists, let $W_{\alpha+1}=W_\alpha$ and otherwise let $W_{\alpha+1}=W_\alpha \setminus \left([\beta+1,\omega_1) \cap \bigcup_{S\leq \beta} F(S)\right)$.
-    \item For limit ordinals $\alpha$, let $W_\alpha = \bigcap_{\beta<\alpha} W_\beta$.
-    \end{itemize}
+Suppose $\sigma(\<x_0,s_0\>,\dots,\<x_{k},s_{k}\>)$ was a winning $(k+1)$-tactical strategy.
+We may define $S(x_0,\dots,x_{k},n)\in [\omega_1]^{<\omega}$ (increasing on $n$) and $n<m(x_0,\dots,x_{k},n)<\omega$ such that for each $(x_0,\dots,x_{k})$,
+  \[
+    \bigcup_{s_0,\dots,s_k \in 2^{\leq n}} \sigma(\<x_0,s_0\>,\dots,\<x_{k},s_{k}\>) \subseteq 
+    K^*_{S(x_0,\dots,x_{k},n)} \cup L_{m(x_0,\dots,x_{k},n)}
+  \]
+and so we assume
+  \[
+    \sigma(\<x_0,s_0\>,\dots,\<x_{k},s_{k}\>) =
+    K^*_{S(x_0,\dots,x_{k},\max(|s_0|,\dots,|s_k|))} \cup L_{m(x_0,\dots,x_{k},\max(|s_0|,\dots,|s_k|))}
+  \]
 
-Finally let $W=\bigcap_{\alpha<\omega_1}W_\alpha$ and observe that it is unbounded.
-Let $R$ collect all ordinals $\alpha\in W$ such that there is an ordinal $\beta$ where for all $S\in[W\cap(\beta,\omega_1)]^{\leq k}$, $\alpha \in F(S)$.
-It is easily seen that $R$ is finite.
-Let $0^*$ be the least element of $W\setminus R$.
+Select an arbitrary point $x' \in X$. Let $M^0(x,n)=m(x,x',\dots,x',n)$ and $M^{i+1}(x,n)=M^0(x,M^i(x,n)+1)$. We define a tactical strategy 
+  \[
+  \tau(x,s) = K^*_{S(x,x',\dots,x',M^{k-1}(x,|s|)+1)} \cup L_{m(x,x',\dots,x',M^{k-1}(x,|s|)+1)}
+  \]
+We complete the proof by showing $\tau$ is a winning tactical strategy (a contradiction).
 
-Now, define a strictly increasing sequence of ordinals $\left<\alpha_1,\alpha_2,\alpha_3,\alpha_4,\dots\right>$ such that $\alpha_i \in W$ and $0^* \not\in F(\{\alpha_{2i+1},\dots,\alpha_{2i+k}\})$ for all $i$.
-The play $\left<0^*,\alpha_1,\dots,\alpha_k,0^*,\alpha_{k+1},\dots,\alpha_{2k},0^*,\dots\right>$ then defeats the strategy $\sigma$.
+Suppose
+\[
+\<x_0, s_0\>, \<x_1, s_1\>, \<x_2, s_2\>, \dots
+\]
+successfully countered $\tau$ by clustering at $c\in C$ (the strategy trivially prevents clustering elsewhere). Let $z_n = \<0,\dots,0\>$ with $n$ zeros. We claim
+\[
+  \<x_0, s_0\>, 
+  \<x', {z_{M^0(x_0,|s_0|)}}^\frown\<1\>\>,
+  \<x', {z_{M^1(x_0,|s_0|)}}^\frown\<1\>\>, 
+  \dots, 
+  \<x', {z_{M^{k-1}(x_0,|s_0|)}}^\frown\<1\>\>,
+\]
+\[
+  \<x_1, s_1\>, 
+  \<x', {z_{M^0(x_1,|s_1|)}}^\frown\<1\>\>, 
+  \<x', {z_{M^1(x_1,|s_1|)}}^\frown\<1\>\>, 
+  \dots, 
+  \<x', {z_{M^{k-1}(x_1,|s_1|)}}^\frown\<1\>\>, 
+  \dots
+\]
+is a successful counter to $\sigma$.
+
+We will need the fact that, as $\<x_{i+1},s_{i+1}\>$ was legal against $\tau$:
+  \[
+    |s_i| <
+    M^0(x_i,|s_i|)+1 =
+    |{z_{M^0(x_i,|s_i|)}}^\frown\<1\>| <
+    M^0(x_i,M^0(x_i,|s_i|)+1)+1 
+  \]
+  \[
+    =
+    M^1(x_i,|s_i|)+1 =
+    |{z_{M^1(x_i,|s_i|)}}^\frown\<1\>| <
+    \dots <
+    |{z_{M^{k-1}(x_i,|s_i|)}}^\frown\<1\>| 
+  \]
+  \[
+    =
+    M^{k-1}(x_i,|s_i|) + 1 <
+    m(x_i,x',\dots,x',M^{k-1}(x_i,|s_i|)+1) \leq
+    |s_{i+1}|
+  \]
+
+Note that $m(x_0,\dots,x_{k},\max(|s_0|,\dots,|s_k|))$ is increasing throughout this play of the game versus $\sigma$:
+  \[
+    m(x_i,x',\dots,x',\max(|s_i|,|{z_{M^0(x_i,|s_i|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_i,|s_i|)}}^\frown\<1\>|))
+  \]
+  \[
+    =
+    m(x_i,x',\dots,x',|{z_{M^{k-1}(x_i,|s_i|)}}^\frown\<1\>|)
+  \]
+  \[
+    =
+    m(x_i,x',\dots,x',M^{k-1}(x_i,|s_i|)+1)
+  \]
+  \[
+    \leq
+    |s_{i+1}| 
+  \]
+  \[
+    <
+    M^0(x_{i+1},|s_{i+1}|)
+  \]
+  \[
+    =
+    m(x_{i+1},x',\dots,x',|s_{i+1}|)
+  \]
+  \[
+    =
+    m(x_{i+1},x',\dots,x',\max(|s_{i+1}|,|{z_{M^0(x_i,|s_i|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_i,|s_i|)}}^\frown\<1\>|))
+  \]
+  \[
+    =
+    |{z_{m(x_{i+1},x',\dots,x',|s_{i+1}|)}}|
+  \]
+  \[
+    =
+    |{z_{M^0(x_{i+1},|s_{i+1}|)}}|
+  \]
+  \[
+    <
+    |{z_{M^0(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|
+  \]
+  \[
+    <
+    m(x_{i+1},x',\dots,x',|{z_{M^0(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|)
+  \]
+  \[
+    =
+    m(x_{i+1},x',\dots,x',\max(|s_{i+1}|,|{z_{M^0(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|,|{z_{M^1(x_{i},|s_{i}|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_{i},|s_{i}|)}}^\frown\<1\>|))
+  \]
+  \[
+    \vdots
+  \]
+  \[
+    <
+    m(x_{i+1},x',\dots,x',\max(|s_{i+1}|,|{z_{M^0(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|))
+  \]
+
+We turn to showing that $\<x', {z_{M^j(x_{i+1},|s_{i+1}|)}}^\frown\<1\>\>$ is always a legal move.
+Since ${z_{M^j(x_{i+1},|s_{i+1}|)}}^\frown\<1\>$ is on the antichain avoided by any $K^*$, the problem is reduced to showing that this move isn't forbidden by
+  \[
+    L_{m(x_{i+1},x',\dots,x',\max(|s_{i+1}|,|{z_{M^0(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|,\dots,|{z_{M^{j-1}(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|,|{z_{M^{j}(x_{i},|s_{i}|)}}^\frown\<1\>|,\dots,|{z_{M^{k}(x_{i},|s_{i}|)}}^\frown\<1\>|))}
+  \]
+  \[
+    =
+    L_{m(x_{i+1},x',\dots,x',|{z_{M^{j-1}(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|)}
+  \]
+which we can see here:
+  \[
+    m(x_{i+1},x',\dots,x',|{z_{M^{j-1}(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|)
+  \]
+  \[
+    =
+    m(x_{i+1},x',\dots,x',M^{j-1}(x_{i+1},|s_{i+1}|)+1)
+  \]
+  \[
+    =
+    M^0(x_{i+1},M^{j-1}(x_{i+1},|s_{i+1}|)+1)
+  \]
+  \[
+    =
+    M^j(x_{i+1},s_{i+1})
+  \]
+  \[
+    <
+    |{z_{M^j(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|
+  \]
+
+We can conclude by showing that $\<x_{i+1},s_{i+1}\>$ is always a legal move. We can see it avoids 
+  \[
+  L_{m(x_{i},x',\dots,x',\max(|s_{i}|,|{z_{M^0(x_i,|s_i|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_i,|s_i|)}}^\frown\<1\>|))}
+  \]
+since
+  \[
+    m(x_{i},x',\dots,x',\max(|s_{i}|,|{z_{M^0(x_i,|s_i|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_i,|s_i|)}}^\frown\<1\>|))
+  \]
+  \[
+    =
+    m(x_{i},x',\dots,x',|{z_{M^{k-1}(x_i,|s_i|)}}^\frown\<1\>|)
+  \]
+  \[
+    =
+    m(x_{i},x',\dots,x',M^{k-1}(x_i,|s_i|)+1)
+  \]
+  \[
+    \leq
+    |s_{i+1}|
+  \]
+
+Since $\<x_{i+1},s_{i+1}\>$ was legal against $\tau$, it avoided
+  \[
+    K^*_{S(x_h,x',\dots,x',M^{k-1}(x_h,|s_h|)+1)} 
+  \]
+  \[
+    = 
+    K^*_{S(x_h,x',\dots,x',\max(|s_h|,|{z_{M^{0}(x_h,|s_h|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_h,|s_h|)}}^\frown\<1\>|))}
+  \]
+for $h\leq i$. And when $h<i$, we see it avoids both:
+  \[
+    K^*_{S(x_{h+1},x',\dots,x',\max(|s_{h+1}|,|{z_{M^0(x_{h+1},|s_{h+1}|)}}^\frown\<1\>|,\dots,|{z_{M^{j-1}(x_{h+1},|s_{h+1}|)}}^\frown\<1\>|,|{z_{M^{j}(x_{h},|s_{h}|)}}^\frown\<1\>|,\dots,|{z_{M^{k}(x_{h},|s_{h}|)}}^\frown\<1\>|))}
+  \]
+  \[
+    =
+    K^*_{S(x_{h+1},x',\dots,x',|{z_{M^{j-1}(x_{h+1},|s_{h+1}|)}}^\frown\<1\>|)}
+  \]
+  \[
+    =
+    K^*_{S(x_{h+1},x',\dots,x',M^{j-1}(x_{h+1},|s_{h+1}|)+1)}
+  \]
+  \[
+    \subseteq
+    K^*_{S(x_{h+1},x',\dots,x',M^{k-1}(x_{h+1},|s_{h+1}|)+1)}
+  \]
+and:
+  \[
+    K^*_{S(x_{h+1},x',\dots,x',\max(|s_{h+1}|,|{z_{M^0(x_{h},|s_{h}|)}}^\frown\<1\>|,\dots,|{z_{M^{k}(x_{h},|s_{h}|)}}^\frown\<1\>|))} 
+  \]
+  \[
+    =
+    K^*_{S(x_{h+1},x',\dots,x',|s_{k+1}|)}
+  \]
+  \[
+    \subseteq
+    K^*_{S(x_{h+1},x',\dots,x',M^{k-1}(x_{h+1},|s_{h+1}|)+1)}
+  \]
+
+This concludes the proof.
 \end{proof}
 
-Peter J. Nyikos has shown the following:
+\section{various examples}
 
-\begin{theorem}
-$O\not\markwin Con_{O,P}(\omega_1\cup\{\infty\},\infty)$.
-\end{theorem}
+\begin{ex}
+If $\mathcal{F}$ is a free ultrafilter on $\omega$, let $L(\mathcal{F})=\omega \cup \{\mathcal{F}\}$ as a subspace of the Stone-Cech compactification $\beta\omega$ be the \textbf{single ultrafilter line}.
+There is some ultrafilter $\mathcal{F}$ such that $K \prewin \lfkpgame{L(\mathcal{F})}$ and $K \tactwin \lfkpgame{L(\mathcal{F})}$.
 
-This can be improved:
-
-\begin{theorem}
-$O\not\kmarkwin{k} Con_{O,P}(\kappa\cup\{\infty\},\infty)$ for $\kappa\geq\omega_1$.
-\end{theorem}
+($L(\mathcal{F})$ is not compactly generated, and thus not locally compact.)
+\end{ex}
 
 \begin{proof}
-Let $F:[\omega_1]^{\leq k}\times\omega\to[\omega_1]^{<\omega}$ be the complement of a $k$-Markov strategy for $O$ restricted to $\omega_1$.
+Let $a_n$ be a sequence such that the sequence $\frac{a_n}{n}$ is unbounded above.
+Then there is an ultrafilter $\mathcal{F}$ such that $\sigma(n)=(\sum_{m\leq n} a_m )\cup \{\mathcal{F}\}$ is a winning predetermined strategy for $K$ in $\lfkpgame{L(\mathcal{F})}$.
 
-Let $W_0=\omega_1$. We define $W_\alpha$ recursively as follows:
-    \begin{itemize}
-    \item For successor ordinals $\alpha+1$, let $\beta$ be the least element of $W_\alpha$ such that \[(\beta,\omega_1) \cap \bigcup_{S\in [\beta]^{\leq k}, n<\omega} F(S,n)\] is nonempty.
-If no such $\beta$ exists, let $W_{\alpha+1}=W_\alpha$ and otherwise let \[W_{\alpha+1}=W_\alpha \setminus \left((\beta,\omega_1) \cap \bigcup_{S\in[\beta]^{\leq k}, n<\omega} F(S,n)\right)\]
-    \item For limit ordinals $\alpha$, let $W_\alpha = \bigcap_{\beta<\alpha} W_\beta$.
-    \end{itemize}
+Let $\mathcal{P}$ be the collection of all legal plays by $P$ against the strategy $\sigma$.
+Consider a finite collection of plays $P_0,\dots,P_{n-1}\in \mathcal{P}$.
+As $\frac{a_m}{m}$ is unbounded above, we may find infinitely many $m$ such that $\frac{a_m}{m}>n \Rightarrow mn<a_m$.
+As the $a_m$ partition $\omega$ such that $P$ may only play at most $m$ points in each part, there are infinitely many parts which are not filled, and thus $\bigcup_{m<n} P_m$ is not cofinite.
 
-Finally let $W=\bigcap_{\alpha<\omega_1}W_\alpha$ and observe that it is unbounded.
-Let $R$ collect all ordinals $\alpha\in W$ such that there is an ordinal $\beta_\alpha$ and number $n_\alpha<\omega$ where for all $S\in[W\cap(\beta_\alpha,\omega_1)]^{\leq k}$, $\alpha \in F(S,n_\alpha)$.
+It then follows that the closure of $\mathcal{P}$ under finite unions and subsets, along with all finite sets, is an ideal.
+Its dual filter may then be extended to an ultrafilter $\mathcal{F}$ such that every possible play by $P$ is the complement of some member of $\mathcal{F}$, making $\sigma$ a winning predetermined strategy.
 
-If $R$ was infinite, then there is $\alpha_i\in R$ for each $i<\omega$ and some $N<\omega$ where for all $S\in[W\cap(\beta_{\alpha_i},\omega_1)]^{\leq k}$, $\alpha_i \in F(S,N)$, and thus for all $S\in[W\cap(\sup \beta_{\alpha_i},\omega_1)]^{\leq k}$,  $\{\alpha_i : i<\omega\} \subset F(S,N)$, a contradiction.
-So let $0^*$ be the least element of $W\setminus R$.
-
-Now, define a strictly increasing sequence of ordinals $\left<\alpha_1,\alpha_2,\alpha_3,\alpha_4,\dots\right>$ such that $\alpha_i \in W$ and $0^* \not\in F(\{\alpha_{2i+1},\dots,\alpha_{2i+k}\})$ for all $i$.
-The play $\left<0^*,\alpha_1,\dots,\alpha_k,0^*,\alpha_{k+1},\dots,\alpha_{2k},0^*,\dots\right>$ then defeats the Markov strategy.
+A winning tactic can then be easily constructed by using the moves by $P$ as the round number in the predetermined strategy.
 \end{proof}
 
-While these counters prevent convergence to $\infty$, they do not prohibit clustering, as any sequence of points with infinite range clusters at $\infty$ in this space.
+\begin{ex}
+Let $T(\mathcal{F}) = 2^{\leq\omega}$ where $2^{<\omega}$ is discrete and for each $c\in 2^\omega$, $\{c \restriction \alpha : \alpha \leq \omega\}$ is homeomorphic to $L(\mathcal{F})$.
+This is called the \textbf{single ultrafilter tree}.
+There is some ultrafilter $\mathcal{F}$ such that $K \prewin \lfkpgame{L(\mathcal{F})}$ and $K \tactwin \lfkpgame{L(\mathcal{F})}$.
 
-\begin{definition} 
-The open-point clustering game $Clus_{O,P}(X,x)$ has $O$ choosing nested open sets and $P$ choosing a point within the last chosen open set by $O$. $O$ wins if the points chosen by $P$ cluster to $x$.
-\end{definition}
-
-Any strategy which forces convergence also forces clustering, so a coding strategy exists for player $O$. And since the counter used above to foil any tactical strategy had only finite range...
-
-\begin{proposition}
-$O\not\tactwin Clus_{O,P}(X,\infty)$.
-\end{proposition}
-
-The other counters only attempt to repeat a point infinitely often, and may have infinite range.
-
-\begin{example}
-For $\omega\leq\alpha<\omega_1$ let $\leq_{\alpha}$ be a well-ordering of $\omega_1$ such that its restriction to $\alpha$ is isomorphic to $\omega$ with isomorphism $f(n):\omega\to\alpha$.
-For $n<\omega$ let $\leq_n$ simply be $\leq$ and $f$ be the identity.
-
-The 2-tactical strategy for $O$ in $Clus_{O,P}(\omega_1\cup\{\infty\}),\infty)$ whose complement is, for $\alpha<\beta$, $F(\alpha,\beta)=\{\gamma : \gamma \leq_\beta \alpha \} \cup \{\beta\}$, forces the point-picker to chose more than three distinct points.
-\end{example}
+($T(\mathcal{F})$ is not compactly generated, and thus not locally compact.)
+\end{ex}
 
 \begin{proof}
-Suppose Player $P$ started with $\alpha_0<\alpha_1$.
-Player $O$ forbids \[F(\alpha_0,\alpha_1) = \{\gamma : \gamma \leq_{\alpha_1}\alpha_0\} \cup \{\alpha_1\}\] so Player $P$ must respond with $\alpha_2$ such that either $\alpha_0<\alpha_1<\alpha_2$ or $\alpha_0<_{\alpha_1}\alpha_2<\alpha_1$.
+Assume without loss of generality that $P$ does not play points in $2^\omega$.
 
-In the first case that $\alpha_0<\alpha_1<\alpha_2$, Player $O$ now forbids \[F(\alpha_1,\alpha_2) = \{\gamma : \gamma \leq_{\alpha_2}\alpha_1\} \cup \{\alpha_2\}\] If $\alpha_0<_{\alpha_2}\alpha_1$ we're done.
-Otherwise, Player $P$ chooses $\alpha_0>_{\alpha_2}\alpha_1$ again, and Player $O$ responds with \[F(\alpha_0,\alpha_2)=\{\gamma : \gamma \leq_{\alpha_2} \alpha_0 \} \cup \{\alpha_2\}\] which successfully forbids $\alpha_1$.
+We use a winning predetermined strategy $\sigma^*(n)$ for $L(\mathcal{F})$ and let $\sigma(n) = \bigcup_{m \in \sigma^*(n)} 2^m$.
+Note that if $P$ has a counter which converges to some $c\in \,^\omega2$, then $P$ would have a counter within a single branch.
+Since each branch is homeomorphic to $L(\mathcal{F})$; this is impossible.
 
-In the second case that $\alpha_0<_{\alpha_1}\alpha_2<\alpha_1$, Player $O$ forbids \[F(\alpha_1,\alpha_2) = \{\gamma : \gamma \leq_{\alpha_1}\alpha_2\} \cup \{\alpha_1\}\] which successfully forbids $\alpha_0$.
-
-Thus, a fourth ordinal must be selected.
+A winning tactic can then be easily constructed by using the moves by $P$, taking the level of the tree played upon as the round number in the predetermined strategy.
 \end{proof}
 
-But the fourth ordinal is all that is needed.
+\begin{ex}
+Let $M = \omega^2 \cup \{\infty\}$ be the \textbf{metric fan} where $\omega^2$ is discrete and $\infty$ has neighborhoods of the form $M \setminus (n\times\omega)$ for any $n<\omega$.
+Then $K \not\win \lfkpgame{M}$.
+(In fact, $P \markwin \lfkpgame{M}$.)
 
-\begin{theorem}
-$O\not\ktactwin{2}Clus_{O,P}(\omega_1\cup\{\infty\},\infty)$.
-\end{theorem}
+($M$ is not locally compact, but is compactly generated.)
+\end{ex}
 
 \begin{proof}
-Let $F(\alpha,\beta)$ be the complement of a k-tactical strategy for O, and assume without loss of generality that it does not forbid any ordinals larger than its inputs.
+For each compact set $C$ in $M$, there exists a minimal dominating function $f_C$ such that for each $(x,y)\in C\setminus\{\infty\}$, $f(x)> y$.
 
-Let $n_0=\min(\omega\setminus F(\emptyset)\setminus F(\omega,\omega+1))$ and $n_1 = \min(\omega\setminus F(n_0)\setminus F(n_0,\omega+1))$.
-
-It follows that $\left<n_0,n_1,\omega,\omega+1,n_0,n_1,\omega,\omega+1,\dots\right>$ is a legal counter.
+So let $P$ respond to the move $C\in K[X]$ by $K$ on round $n$ with the point $p=(n,s_C)$ such that $s_C = \min(\{y<\omega : f_C(n) < y\}$.
+It is easy to see that $p_n\rightarrow \infty$, so $P$ has a winning Markov strategy.
 \end{proof}
 
-But, in fact, a similar counter can be used for any $k$-tactical strategy.
+\begin{ex}
+Let $S = \omega^2 \cup \{\infty\}$ be the \textbf{sequential fan} where $\omega^2$ is discrete and $\infty$ has neighborhoods of the form $M \setminus \{(x,y) : x<f(y)\}$ for any $f:\omega\to\omega$.
+Then $K \prewin \lfkpgame{S}$ and $K\tactwin \lfkpgame{S}$.
 
-\begin{theorem}
-$O\not\ktactwin{k}Clus_{O,P}(\omega_1\cup\{\infty\},\infty)$.
-\end{theorem}
+($S$ is not locally compact, but is compactly generated.)
+
+\end{ex}
 
 \begin{proof}
-Let $F(\alpha_0,\dots,\alpha_{k-1})$ be the complement of a k-tactical strategy for O, and assume without loss of generality that it does not forbid any ordinals larger than its inputs.
+Let $\sigma(n)=\omega\times(n+1) \cup \{\infty\}$.
+By defining $f(y)$ to be greater than the $x$-coordinate of all $P$'s plays through round $y$, we see that $M\setminus\{(x,y): x<f(y)\}$ misses every move by $P$, so $P$ cannot converge to $\infty$.
 
-For $0\leq i < k$, we define \[n_i = \min(\omega\setminus F(n_0,\dots,n_{i-1},\omega+i,\dots,\omega+k-1)\setminus F(n_0,\dots,n_{i-1}))\]
-
-It follows that $\left<n_0,\dots,n_{k-1},\omega,\dots,\omega+k-1,n_0,\dots,n_{k-1},\omega,\dots,\omega+k-1,\dots\right>$ is a legal counter.
+A winning tactic can be easily constructed by using the $y$-coordinate of $P$'s moves as the round number in the predetermined strategy.
 \end{proof}
-
-However, a Markov strategy is sufficient to defeat $P$ in the clustering game for $\omega_1$.
-
-\begin{theorem}
-$O\markwin Clus_{O,P}(\omega_1\cup\{\infty\},\infty)$.
-\end{theorem}
-
-\begin{proof}
-For $\omega\leq\alpha<\omega_1$ let $\leq_{\alpha}$ be a well-ordering of $\omega_1$ such that its restriction to $\alpha$ is isomorphic to $\omega$ with isomorphism $f(n):\omega\to\alpha$.
-For $n<\omega$ let $\leq_n$ simply be $\leq$ and $f$ be the identity.
-
-Let $F(\alpha,n)=\{\gamma : \gamma \leq_\alpha f(n)\}$ be the complement of $O$'s Markov strategy in response to move $\alpha$ in round $n$.
-
-If a legal counter by $P$ does not repeat some largest ordinal infinitely often, it does not result in a win for $P$.
-Otherwise let $\beta$ be largest ordinal repeated infinitely often in some legal counter by $P$.
-We note that the forbidden sets responded by $O$ are of the form $F(\beta,n)$ where $n$ increases as the game progresses.
-It is impossible to repeat any ordinal less than $\beta$ infinitely often due to the increasing round number, so the range of the counter is infinite, and does not result in a win for $P$.
-\end{proof}
-
-...while it similarly fails for $\kappa>\omega_1$.
-
-\begin{theorem}
-$O\not\kmarkwin{k}Clus_{O,P}(\kappa\cup\{\infty\},\infty)$ for $\kappa>\omega_1$.
-\end{theorem}
-
-\begin{proof}
-Let $F:\omega\times[\kappa]^{\leq k} \to [\kappa]^\omega$ be the complement of a k-Markov strategy for O, and assume without loss of generality that it does not forbid any ordinals larger than its inputs.
-
-For $0\leq i < k$, we define \[\beta_i = \min(\omega\setminus \bigcup_{n<\omega} F(n,\{\beta_0,\dots,\beta_{i-1},\omega_1+i,\dots,\omega_1+k-1\})\setminus\bigcup_{n<\omega} F(n,\{\beta_0,\dots,\beta_{i-1}\}))\]
-
-It follows that $\left<\beta_0,\dots,\beta_{k-1},\omega_1,\dots,\omega_1+k-1,\beta_0,\dots,\beta_{k-1},\omega_1,\dots,\omega_1+k-1,\dots\right>$ is a legal counter.
-\end{proof}
-
-\centerline{\bf $Con_{O,P}(X,x)$ for Sigma Product}
-
-\begin{proposition}
-The player $O$ has a winning strategy for $Con_{O,P}(X,x)$ where \[X=\Sigma\mathbb{R}^{\omega_1}=\{x\in \mathbb{R}^{\omega_1}: x_\alpha = 0 \text{ for all but countably many } \alpha<\omega_1\}\]
-\end{proposition}
-
-\begin{proof}
-Without loss of generality we may assume that $x$ is the zero function.
-Let $y_n$ be the move by $P$ on turn $n$.
-For each $y_n$, let $l_n\in \omega_1^{\omega}$ enumerate the nonzero coordinates in $y_n$.
-Give $O$ the strategy $\sigma(y_0,\dots,y_{n-1}) = \prod_{\alpha<\omega_1} O_\alpha$ where if $\alpha$ is listed in the first $n$ coordinates of any term in $\left<l_k\right>_{k<n}$, then $O_\alpha=(-2^{-n},2^{-n})$, and $O_\alpha=\mathbb{R}$ otherwise.
-\end{proof}
-
-\begin{theorem}
-For all cardinals $\kappa\leq 2^\omega$, the player $O$ has a winning coding strategy for $Con_{O,P}(X,x)$ where \[X=\Sigma\mathbb{R}^{\kappa}=\{x\in \mathbb{R}^{\kappa}: x_\alpha = 0 \text{ for all but countably many } \alpha<\kappa\}\]
-\end{theorem}
-
-\begin{proof}
-Note that $|\Sigma\mathbb{R}^\kappa| \leq 2^\omega = |\mathbb{R}|$. Define the following:
-
-    \begin{itemize}
-    \item Encode every finite sequence $s$ of functions in $\Sigma\mathbb{R}^{\kappa}$ as a real number $0<r(s)<1$. 
-    \item Let $\gamma(U)$ be the function which, for basic open sets $U=\prod_{\alpha<\kappa}U_\alpha$ where $U_0=(-\frac{1}{R},\frac{1}{R})$ for some positive noninteger real number $R$, returns the sequence $r^{-1}(R-\lfloor R\rfloor)$.
-    \item Let $n(U)$ be the length of $\epsilon^{-1}(\gamma(U))$.
-    \item Let $\psi(U,y)=\epsilon^{-1}(\gamma(U))^\frown\left<y\right>$.
-    \item Define $\sigma_0(U,y)$ to be $\left(-\frac{1}{n(U)+r(\psi(U,y))},\frac{1}{n(U)+r(\psi(U,y))}\right)$.
-    \item For each $0<\alpha<\kappa$, define the interval $\sigma_\alpha(U,y)$ about $0$ as follows:
-        \begin{itemize}
-        \item If $\alpha$ is listed in the first $n(U)$ coordinates of any term in the finite sequence $\psi(U,y)$, then $\sigma_\alpha(U,y)=(-\frac{1}{n(U)+1},\frac{1}{n(U)+1})$.
-        \item Otherwise, then $\sigma_\alpha(U,y)=\mathbb{R}$.
-        \end{itemize}
-    \end{itemize}
-
-It follows that $\sigma(U,y)=\prod_{\alpha<\kappa} \sigma_\alpha(U,y)$ is a winning coding strategy.
-\end{proof}
-
-\begin{theorem}
-For all cardinals $\kappa>2^\omega$ such that $\kappa^\omega = \kappa$, the player $O$ has a winning coding strategy for $Con_{O,P}(X,x)$ where \[X=\Sigma\mathbb{R}^{\kappa}=\{x\in \mathbb{R}^{\kappa}: x_\alpha = 0 \text{ for all but countably many } \alpha<\omega_1\}\]
-\end{theorem}
-
-\begin{proof}
-Note that $|\Sigma\mathbb{R}^\kappa| = \kappa^\omega = \kappa$. Define the following:
-
-    \begin{itemize}
-    \item Encode every finite sequence $s$ of functions in $\Sigma\mathbb{R}^{\kappa}$ as an ordinal $\epsilon(s)<\kappa$. 
-    \item Let $\gamma(U)$ be the function which, for basic open sets $U=\prod_{\alpha<\kappa}U_\alpha$ with a unique factor $U_{\alpha^*}$, returns $\alpha^*$.
-    \item Let $n(U)$ be the length of $\epsilon^{-1}(\gamma(U))$.
-    \item Let $\psi(U,y)=\epsilon^{-1}(\gamma(U))^\frown\left<y\right>$.
-    \item For each $\alpha<\kappa$, define the interval $\sigma_\alpha(U,y)$ about $0$ as follows:
-        \begin{itemize}
-        \item If $\alpha$ is listed in the first $n(U)$ coordinates of any term in the finite sequence $\psi(U,y)$ and is not equal to $\epsilon(\psi(U,y))$, then $\sigma_\alpha(U,y)=(-\frac{1}{n(U)+1},\frac{1}{n(U)+1})$.
-        \item If $\alpha=\epsilon(\psi(U,y))$, then $\sigma_\alpha(U,y)=(-\frac{1}{n(U)+2},\frac{1}{n(U)+2})$.
-        \item Otherwise, then $\sigma_\alpha(U,y)=\mathbb{R}$.
-        \end{itemize}
-    \end{itemize}
-
-It follows that $\sigma(U,y)=\prod_{\alpha<\kappa} \sigma_\alpha(U,y)$ is a winning coding strategy.
-\end{proof}
-
-% NOPE
-%\begin{theorem}
-%For all cardinals $\kappa$ such that $2^\omega< \kappa < \kappa^\omega$, the player $O\not\codewin Cl_{O,P}(X,x)$ where \[X=\Sigma\mathbb{R}^{\kappa}=\{x\in% \mathbb{R}^{\kappa}: x_\alpha = 0 \text{ for all but countably many } \alpha<\omega_1\}\]
-%\end{theorem}
-%
-%\begin{proof}We begin by noting that $|\tau|=\kappa<\kappa^\omega$, where $\tau$ is the topology of $\Sigma \mathbb{R}^\kappa$.
-%
-%Suppose that for all $S\subseteq \Sigma\mathbb{R}^\kappa$ such that $\sigma(U,x)=\sigma(V,y)$ for all $x,y\in\Sigma \mathbb{R}^\kappa$ and $U,V\in\tau$, it follows that $|S|<\kappa^\omega$.
-Then \[\left|\bigcup_{V\in\tau}\sigma^{-1}(V)\right|=\max(\{\lambda : \lambda=|\tau| \,\vee\, \exists V\in\tau(\lambda=|\sigma^{-1}(V)|)\}) < \kappa^\omega \] while $\bigcup_{V\in\tau}\sigma^{-1}(V)=\tau\times \Sigma\mathbb{R}^\kappa$, a contradiction.
-%
-%It follows that we may find $S\subseteq \Sigma\mathbb{R}^\kappa$ with $|S|=\kappa^\omega$ such that $\sigma(U,x)=\sigma(V,y)$ for all $x,y\in\Sigma \mathbb{R}^\kappa$ and $U,V\in\tau$.
-%
-%If $P$ only plays sequences in $S$, then $O$ plays the same set in every round following the initial round.
-As such, $O$ only places restrictions on $\omega$-many coordinates of the sequences chosen by $P$ throughout the game.
-Call these restricted coordinates $R\subseteq \kappa$.
-If $x(\alpha)=0$ for all $x\in S$ and $\alpha\not\in R$, then it would follow that $|S|=|\mathbb{R}|^{|R|}=2^\omega<\kappa^\omega$, a contradiction.
-%
-%So, choose $x\in S$ such that $x(\alpha)\not=0$ for some $\alpha\not\in R$. The play \[\left<U_0,x,U_1=\sigma(U_0,x),x,U_2=\sigma(U_1,x)=U_1,x,U_1,x,\dots\right>\] is a counter to $\sigma$.
-%\end{proof}
-
-\centerline{\bf Finite Countable Game}
-
-\begin{theorem}
-Let $\kappa$ be a cardinal such that there exists a function $f:\kappa\to[\kappa]^{\leq \omega}$ where for every $W\in[\kappa]^{\leq\omega}$ there exists $\alpha_W<\kappa$ with $W\subseteq f(\alpha_W)$.
-Then $F \codewin PF_{F,C}(\kappa)$ and $O \codewin Con_{O,P}(\Sigma\mathbb{R}^\kappa)$.
-\end{theorem}
-
-\begin{proof}
-Long version.
-
-We begin by defining a few helpful tools. Assume $N\in[\kappa]^{<\omega}$ and $W \in [\kappa]^{\leq\omega}$.
-    \begin{itemize}
-    \item Let $N^* = N \setminus \{\max(N)\}$.
-    \item Noting that $\kappa\setminus \alpha$ is order-isomorphic to $\kappa$ for all $\alpha<\kappa$, let $\gamma_N<\kappa$ be the ordinal mapping to $\max(N)$ in $\kappa\setminus(\max(N^*)+1)$ by the appropriate order isomorphism.
-    \item Let $s: [\kappa]^{<\omega} \to \kappa$ be a bijection.
-    \item Define $W\restriction n \in [\kappa]^{<\omega}$ so that $W\restriction n \subseteq W\restriction (n+1)$ and $\bigcup_{n<\omega}W\restriction n = W$.
-    \item Let $t_N=\max(N\cap\omega)+2$.
-    \end{itemize}
-
-Let the (non-winning) coding strategy $\sigma'$ be defined as follows: \[\sigma'(N,W)=\bigcup_{\alpha \in s^{-1}(\gamma_N)} f(\alpha) \restriction t_N\]
-
-Let $\left<N_0,N_1,\dots\right>$ be a play by $F$ following the considered strategy in response to the play $\left<W_0,W_1,\dots\right>$ by $C$ in the game $PF_{F,C}(\kappa)$.
-(For technical reasons, assume $N_0$ contains at least two ordinals.) This coding strategy could have been a winning strategy for $F$ if it had only satisfied two requirements:
-
-    \begin{enumerate}
-    \item First, $s^{-1}(\gamma_{N_k})$ provided ordinals $\{\alpha_{W_0},\dots,\alpha_{W_{k-1}}\}$.
-(Thus $N_{k+1}=\bigcup_{\alpha \in s^{-1}(\gamma_{N_k})} f(\alpha) \restriction t_{N_k} = \bigcup_{0\leq m < k} f(\alpha_{W_m}) \restriction t_{N_k}$.)
-    \item In addition, $t_{N_k} \to \infty$.
-(Thus $\bigcup_{k<\omega} N_{k+1} = \bigcup_{k<\omega}\bigcup_{0\leq m < k-1} f(\alpha_{W_m}) \restriction t_{N_k} = \bigcup_{m<\omega} f(\alpha_{W_m}) \supseteq \bigcup_{m<\omega} W_m$.)
-    \end{enumerate}
-
-We shall improve $\sigma'$ so that it does satsify those requirements, beginning with the second.
-Define $\sigma^*$: \[\sigma^*(N,W)=t_N \cup \sigma'(N,W)\] Note then that $t_{N_{k+1}}\geq t_{t_{N_k}} = \max(t_{N_k})+2 = t_{N_k}-1+2=t_{N_k}+1$.
-
-Lastly, to cover the first requirement, we define $\sigma$: \[\sigma(N,W) = \sigma^*(N,W) \cup \{ \max(\sigma^*(N,W))+1+s(s^{-1}(\gamma_N)\cup\{\alpha_W\}) \}\] By induction \[s^{-1}(\gamma_{N_{k+1}}) = s^{-1}(s(s^{-1}(\gamma_{N_k})\cup\{\alpha_{W_k}\})) = s^{-1}(\gamma_{N_k})\cup\{\alpha_{W_k}\} = \{\alpha_{W_0},\dots,\alpha_{W_{k-1}}\}\cup\{\alpha_{W_k}\}\] we see the first requirement is satisfied.
-
-Finally, we turn our attention to $Con_{O,P}(\Sigma\mathbb{R}^\kappa)$.
-We define the winning strategy $\tau(U,p)$ for $O$ as follows: let $N(U)$ be the non-$\mathbb{R}$ coordinates in the basic open set $U$ and $W(p)$ be the non-$0$ coordinates in $p$.
-Then $\tau(U,p) = \left(\prod_{\alpha<\kappa} U_\alpha\right) \cap \Sigma\mathbb{R}^\kappa$ where if $\alpha \in \sigma(N(U),W(p))$ then $U_\alpha = (-1/t_{N(U)},1/t_{N(U)})$ and $U_\alpha=\mathbb{R}$ otherwise.
-\end{proof}
-
-\begin{proof}
-Short version, per GG's suggestion.
-
-Let $W\restriction n \in [\kappa]^n$ be a subset of $W\in[\kappa]^\omega$ such that $W\restriction n \subset W \restriction (n+1)$ and $\bigcup_{n<\omega} W\restriction n = W$.
-
-Define \[\sigma(N,W) = N \cup (|N|+1) \cup \{\alpha_W\} \cup \bigcup_{\alpha \in N} f(\alpha) \restriction |N|\]
-
-Consider the play $\left<\emptyset,W_0,N_1,W_1,N_2,W_2,\dots\right>$ with $F$ following the strategy $\sigma$.
-Let $\gamma \in W_i$, and note $\gamma \in f(\alpha_{W_i})$ (and $\gamma \in f(\alpha_{W_i})\restriction |N_n|$ for sufficiently large $n$).
-\[N_{i+1} = \sigma(N_i,W_i) \supseteq \{\alpha_{W_i}\}\] and thus \[N_{n+1} = \sigma(N_n,W_n) \supseteq \bigcup_{\alpha \in N_n} f(\alpha) \restriction |N_n| \supseteq \bigcup_{\alpha \in N_{i+1}} f(\alpha) \restriction |N_n| \supseteq f(\alpha_{W_i}) \restriction |N_n|\] showing $\gamma \in N_{n+1}$.
-Since $\gamma$ is forbidden in round $n+1$, $\gamma$ appears in finitely many sets chosen by $C$.
-
-We turn our attention to $Con_{O,P}(\Sigma\mathbb{R}^\kappa)$.
-We define the winning strategy $\tau(U,p)$ for $O$ as follows: let $N(U)$ be the non-$\mathbb{R}$ coordinates in the basic open set $U$ and $W(p)$ be the non-$0$ coordinates in $p$.
-Then $\tau(U,p) = \left(\prod_{\alpha<\kappa} U_\alpha\right) \cap \Sigma\mathbb{R}^\kappa$ where if $\alpha \in \sigma(N(U),W(p))$ then $U_\alpha = (-\frac{1}{|N(U)|},\frac{1}{|N(U)|})$ and $U_\alpha=\mathbb{R}$ otherwise.
-
-Consider the play $\left<\emptyset,p_0,U_1,p_1,U_2,p_2,\dots\right>$ with $O$ following the strategy $\tau$.
-Observe that $N(\tau(U,p))=\sigma(N(U),W(p))$.
-Thus $p_i(\gamma)\not=0$ is equivalent to $\gamma \in W(p_i)$, and by the above argument, for sufficiently large $n$, $\gamma \in \sigma(N(U_n),W(p_n))$.
-Therefore from round $n$ onward the $\gamma$-coordinates of points chosen by $P$ must lay in $(-\frac{1}{|N(U)|},\frac{1}{|N(U)|})$ and converge to $0$.
-\end{proof}
-
-%
-%\begin{theorem}
-%For all cardinals $\kappa \geq \omega$, the player $F \not\tactwin Cov_{F,C}(\kappa)$.
-%\end{theorem}
-%
-%\begin{proof}
-%(Based on Scheeper's Meager Nowhere Dense Games I)
-%
-%Suppose $\sigma$ is a tactical strategy for $F$ such that (without loss of generality) the first move is $\emptyset$. Let $A=\{2n: n<\omega\}$ and $B=\{2n+1:n<\omega\}$.
-%
-%By Todorcevic's Partition Relations for Partially Ordered Sets, $\mathcal{P}(A)\rightarrow(\omega)^1_B$.
-That is, for any function $\Phi$ from $\mathcal{P}(A)$ to $B$, there is some $b_\Phi\in B$ and $X_0\subseteq X_1\subseteq \dots \in \mathcal{P}(A)$ such that $\Phi(X_i)=b_\Phi$ for all $i$.
-Define $\Phi:\mathcal{P}(A)\rightarrow B$ such that $\Phi(X)\in B\setminus(\sigma(B\cup X))$.
-%
-%Observe the play $\left<\emptyset, B\cup X_0, \sigma(B\cup X_0), B \cup X_1, \sigma(B \cup X_1), B \cup X_2, \dots \right>$.
-As $b_\Phi \in B \subseteq \bigcup_{i<\omega} B \cup X_i$ but $b_\Phi \not\in \bigcup_{i<\omega} \sigma(B\cup X_i)$, this is a successful counter to any tactic by $F$.
-%\end{proof}
-%
-%\begin{proposition}
-%For all cardinals $\kappa \geq \omega_1$, the player $F \not\markwin Cov_{F,C}(\kappa)$.
-%\end{proposition}
-%
-%\begin{proof}
-%Suppose $\sigma$ is a Markov strategy for $F$ such that (without loss of generality) the first move is $\emptyset$. Let $A,B\in\mathcal{P}(\kappa)$ be disjoint with $|A|=|B|\geq\omega_1$.
-%
-%By Todorcevic's Partition Relations for Partially Ordered Sets, $\mathcal{P}(A)\rightarrow(\omega)^1_B$.
-That is, for any function $\Phi$ from $\mathcal{P}(A)$ to $B$, there is some $b_\Phi\in B$ and $X_0\subseteq X_1\subseteq \dots \in \mathcal{P}(A)$ such that $\Phi(X_i)=b_\Phi$ for all $i$.
-Define $\Phi:\mathcal{P}(A)\rightarrow B$ such that $\Phi(X)\in B\setminus(\bigcup_{n<\omega}\sigma(B\cup X,n))$.
-%
-%Observe the play $\left<\emptyset, B\cup X_0, \sigma(B\cup X_0,1), B \cup X_1, \sigma(B \cup X_1,2), B \cup X_2, \dots \right>$.
-As $b_\Phi \in B \subseteq \bigcup_{i<\omega} B \cup X_i$ but $b_\Phi \in \bigcap_{m<\omega} B \setminus (\bigcup_{n<\omega}\sigma(B\cup X_m,n))$ implying $b_\Phi \not\in \bigcup_{m<\omega}\sigma(B\cup X_m,m+1)$, this is a successful counter to any Markov strategy by $F$.
-%\end{proof}
-
-%\begin{theorem}
-%If $F\codewin Cov_{F,C}^{**}(\kappa)$ then $O\codewin C_{O,P}(\Sigma\mathbb{R}^\kappa,\vec{0})$.
-%\end{theorem}
-%
-%\begin{proof}
-%We begin by comparing
-%    \begin{itemize}
-%    \item $N\in[\kappa]^{<\omega}$ with the open set $\prod_{\alpha < \kappa} U_\alpha$ in $\Sigma2^\kappa$ where $U_\alpha=\{0\}$ for $\alpha\in N$ and $U_\alpha=\{0,1\}$ otherwise.
-%    \item $W\in[\kappa]^{\leq\omega}$ with the point $p\in\Sigma2^\kappa$ defined by $p(\alpha)=1$ for all $\alpha \in W$ and $p(\alpha)=0$ otherwise.
-%    \end{itemize}
-%
-%So if $\sigma$ is a winning coding strategy for $F$ in $Cov_{F,C}^{**}(\kappa)$, we may define $\tau$ to be a corresponding (perfect- or limited-information) winning strategy for $O$ in $C_{O,P}(\Sigma2^\kappa,\vec{0})$ by making the above conversions from finite sets played by $F$ to countable sets played by $C$ to the open sets which may be played by $O$ and points which may be played by $P$.
-As the legal moves for $C$ correspond to the legal moves for $P$, and as $\sigma$ covers any play by $C$, $\tau$ forces any nonzero coordinate found in a move by $P$ to eventually constrained to $0$.
-%
-%For the game $C_{O,P}(\Sigma\mathbb{R}^\kappa,\vec{0})$ we must instead use open sets of the form $\prod_{\alpha < \kappa} U_\alpha$ where $U_\alpha=(-1/i,1/i)$ for $\alpha\in N$ and $i$ being the turn number (with $U_\alpha=\mathbb{R}$ for $\alpha\not\in N$).
-(The turn number is easily encoded and decoded by $O$ by inspecting the non-$\mathbb{R}$ coordinates of her previous move) and associating points $p\in\Sigma\mathbb{R}^\kappa$ with $q\in\Sigma2^\kappa$ by $q(\alpha)=0$ when $|p(\alpha)|<1$ and $q(\alpha)=1$ otherwise.
-%\end{proof}
-
-\end{document}

### 2014-05-14 phd/dissertation/chapter3.tex
Finish ch 2 draft, outline of results for ch 3, ch 6

@@
 
-\chapter{Convergence/clustering games}
+\chapter{$W$ convergence and clustering games}
 
@@
 
-\section{Basic game}
+(these are related to the ``hard'' version for $\pl O$ where $\pl P$
+need only play within the most recent open set)
 
-\begin{defn} 
-Gruenhage's open-point convergence game $\congame{X}{x}$ has $O$ choosing nested open sets and $P$ choosing a point within the last chosen open set by $O$.
-$O$ wins if the points chosen by $P$ converge to $x$.
-\end{defn}
-
-TODO: This version of the game (where $\pl P$ need not play within all 
-previously chosen open sets) is more difficult for $\pl O$. Need to 
-differientiate these two versions somehow...
-
-\begin{defn}
-The one-point compactification of a space $X$ is $\oneptcomp{X}$, where neighborhoods of points in $X$ are the same as they were originally, and neighborhoods of $\infty$ are sets $\oneptcomp{X}\setminus K$ for compact $K$.
-If $X$ is discrete then neighborhoods of $\infty$ are cofinite sets containing $\infty$, and the game is equivalent to $O$ choosing finite ``forbidden'' sets and $P$ choosing points not forbidden by $O$.
-\end{defn}
-
-\begin{prop}
-$O\codewin \congame{\oneptcomp{\kappa}}{\infty}$ for all cardinals $\kappa$.
-\end{prop}
-
-\begin{proof}
-Use $F(N,p)=N\cup\{p\}$.
-\end{proof}
-
-\begin{prop}
-$O\prewin \congame{\oneptcomp{\omega}}{\infty}$.
-\end{prop}
-
-\begin{proof}
-Use $F(n)=n$.
-\end{proof}
-
-\begin{prop}
-$O\not\prewin \clusgame{\oneptcomp{\kappa}}{\infty}$ for $\kappa\geq\omega_1$.
-\end{prop}
-
-\begin{proof}
-Let $F(n)$ be $O$'s predetermined forbidding strategy, let $\alpha\in\kappa\setminus\bigcup_{n<\omega}F(n)$, and have $P$ counter with $\left<\alpha,\alpha,\dots\right>$.
-\end{proof}
-
-\begin{prop}
-$O\tactwin\congame{\oneptcomp{\omega}}{\infty}$.
-\end{prop}
-
-\begin{proof}
-Use $F(n)=n+1$.
-\end{proof}
+\section{Fort spaces}
 
 \begin{thm}
-If $\kappa$ is a regular uncountable cardinal, for every function $f:[\kappa]^{<\omega}\to[\kappa]^{<\omega}$ the set $C_f = \{\alpha < \kappa : S\in[\alpha]^{<\omega} \Rightarrow f(S)\in[\alpha]^{<\omega}\}$ is club.
+$O\not\ktactwin{k}\clusgame{\oneptcomp{\omega_1}}{\infty}$.
 \end{thm}
-
-\begin{proof}
-First assume $\alpha_0<\alpha_1<\dots\in C_f$. It is easily seen that $\sup(\alpha_n)\in C_f$, showing $C_f$ is closed.
-
-Now assume $\gamma_0\in C_f$.
-Let $\gamma_{n+1}>\gamma_n$ be the least ordinal such that if $S\in[\gamma_n+1]^{<\omega}$ then $f(S)\in[\gamma_{n+1}]^{<\omega}$.
-We claim $\gamma_\omega = \sup(\gamma_n)\in C_f$.
-Let $S\in[\gamma_\omega]^{<\omega}$.
-Then $S\in[\gamma_n+1]^{<\omega}$ for some $n$, and thus $f(S)\in[\gamma_{n+1}]^{<\omega}\subset[\gamma_\omega]^{<\omega}$.
-Therefore $C_f$ is unbounded.
-\end{proof}
-
-We may thus assume, for the purposes of countering a tactical or Markov strategy, that the strategy is \textbf{downward} on some regular uncountable cardinal.
-
-\begin{thm}
-$O\not\ktactwin{k}\clusgame{\oneptcomp{\kappa}}{\infty}$ for $\kappa\geq\omega_1$.
-\end{thm}
-
-\begin{proof}
-Let $F:[\kappa]^{\leq k} \to [\kappa]^{<\omega}$ be a forbidding strategy by $O$ against $P$ which is downward on $\omega_1$.
-We define $n_i$ for $0\leq i < k$ to be a natural number such that \[ n_i \in \omega \setminus(F(n_0,\dots,n_{i-1}) \cup F(n_0,\dots,n_{i-1},\omega+i,\dots,\omega+k-1))\] and note that\[\left<n_0,n_1,\dots,n_{k-1},\omega,\omega+1,\dots,\omega+k-1,n_0,n_1,\dots,n_{k-1},\omega,\omega+1,\dots,\omega+k-1,\dots\right>\] counters $F$.
-\end{proof}
 
@@
 
-\begin{proof}
-For $\alpha<\omega_1$ let $A_{\alpha,n}$ be a sequence of finite sets such that $A_{\alpha,n}\subset A_{\alpha,n+1}$ and $\bigcup_{n<\omega}A_{\alpha,n}=\alpha+1$.
-
-Give $O$ the Markov forbidding strategy $F(n,\alpha)=A_{\alpha,n}$.
-To observe that any legal play by $P$ against the strategy $F$ has infinite range, we observe that for any $\alpha_0<\dots<\alpha_{k-1}$, there is some round $n$ such that $\{\alpha_0,\dots,\alpha_{k-1}\}\subseteq \bigcup_{0\leq i < k}F(n,\alpha_i)$, and thus $P$ cannot legally play any of these ordinals until another ordinal is played.
-\end{proof}
-
-Peter J. Nyikos has shown the following:
+\begin{thm}(Nyikos)
+$O\not\markwin \congame{\oneptcomp{\omega_1}}{\infty}$.
+\end{thm}
 
 \begin{thm}
-$O\not\markwin Con_{O,P}(\omega_1\cup\{\infty\},\infty)$.
+$O\not\kmarkwin{k}\clusgame{\oneptcomp{\kappa}}{\infty}$ for $\kappa>\omega_1$.
 \end{thm}
 
-which improves to:
+(TODO: It's feasible that $k$-limit $\Leftrightarrow$ $1$-limit.)
+
+\section{Sigma-products}
 
 \begin{thm}
-$O\not\kmarkwin{k}Clus_{O,P}(\kappa\cup\{\infty\},\infty)$ for $\kappa>\omega_1$.
+  Let $\textrm{cf}([\kappa]^{\leq\omega})=\kappa$.
+  Then $F \codewin PF_{F,C}(\kappa)$.
 \end{thm}
 
-\begin{proof}
-Let $F:\omega \times [\kappa]^{\leq k} \to [\kappa]^{<\omega}$ be a forbidding strategy by $O$ against $P$ which is downward on $\omega_2$.
-We define $\alpha_i$ for $0\leq i < k$ to be a countable ordinal such that \[ \alpha_i \in \omega_1 \setminus\bigcup_{n<\omega}\left(F(n,\{\alpha_0,\dots,\alpha_{i-1}\}) \cup F(n,\{\alpha_0,\dots,\alpha_{i-1},\omega_1+i,\dots,\omega_1+k-1\})\right)\] and note that \[\left<\alpha_0,\alpha_1,\dots,\alpha_{k-1},\omega_1,\omega_1+1,\dots,\omega_1+k-1,\alpha_0,\alpha_1,\dots,\alpha_{k-1},\omega_1,\omega_1+1,\dots,\omega_1+k-1,\dots\right>\] counters $F$.
-\end{proof}
-
-\section{$Con_{O,P}(X,x)$ for Sigma Product}
-
-\begin{prop}
-$O\uparrow\congame{\sigmaprodr{\kappa}}{\vec{0}}$.
-\end{prop}
-
-\begin{proof}
-For $s\in\sigmaprodr{\kappa}$ let $C(s)=\{\alpha<\kappa:s(\alpha)\not=0\}$ denote the countable nonzero coordinates of $s$.
-Let $\Phi:[\kappa]^{\leq\omega}\times\omega\to[\kappa]^{<\omega}$ be such that $\Phi(C,n)\subseteq\Phi(C,n+1)$ and $\bigcup_{n<\omega}\Phi(C,n)=C$.
-
-If $\tau$ is the usual topology on $\mathbb{R}$, let $\sigma_\alpha:(\sigmaprodr{\kappa})^{<\omega}\to\tau$ be such that
-\[
-U_\alpha(s_0,\dots,s_{n-1})=\left\{
-\begin{array}{l}
-(-\frac{1}{n},\frac{1}{n}) \text{ if } \alpha\in\bigcup_{i<n}\Phi(C(s_i),n) \\
-\mathbb{R} \text{ otherwise}
-\end{array}
-\right.
-\]
-
-Finally, give $O$ the winning strategy $\sigma(s_0,\dots,s_{n-1})=\sigmaprodr{\kappa}\cap\prod_{\alpha<\kappa}U_\alpha(s_0,\dots,s_{n-1})$.
-\end{proof}
-
 \begin{thm}
-For all cardinals $\kappa\leq 2^\omega$, $O\codewin\congame{\sigmaprodr{\kappa}}{\vec{0}}$.
+  Let $\kappa$ be the limit of cardinals $\kappa_n$ such that
+  $\textrm{cf}([\kappa_n]^{\leq\omega},\subseteq)=\kappa_n$.
+  Then $F \codewin \pfgame{\kappa}$.
 \end{thm}
-
-\begin{proof}
-Note that $|\Sigma\mathbb{R}^\kappa| \leq 2^\omega = |\mathbb{R}|$. Define the following:
-
-    \begin{itemize}
-    \item Encode every $S \in (\Sigma\mathbb{R}^{\kappa})^{<\omega}$ as a real number $0<r(S)<1$. 
-    \item Let $\gamma(U)$ be the function which, for basic open sets $U=\sigmaprodr{\kappa}\cap\prod_{\alpha<\kappa}U_\alpha$ where for all $\alpha<\kappa$ either $U_\alpha=\mathbb{R}$ or $(-\frac{1}{r},\frac{1}{r})$, returns $\lfloor r \rfloor$.
-    \item Let $n(U)$ be the number of non-$\mathbb{R}$ components of a basic open set $U$.
-    \item Let $\psi(U,s)=r^{-1}(\gamma(U))^\frown\left<y\right>$.
-    \item For $s\in\sigmaprodr{\kappa}$ let $C(s)=\{\alpha<\kappa:s(\alpha)\not=0\}$ denote the countable nonzero coordinates of $s$.
-    \item Let $\Phi:[\kappa]^{\leq\omega}\times\omega\to[\kappa]^{<\omega}$ be such that $\Phi(C,n)\subseteq\Phi(C,n+1)$ and $\bigcup_{n<\omega}\Phi(C,n)=C$.
-    \item For each $\alpha<\kappa$, define the interval $\sigma_\alpha(U,s)$ about $0$ as follows:
-        \begin{itemize}
-        \item If $\alpha\leq n(U)$ or $\alpha\in\bigcup_{s\in\psi(U,s)}\Phi(C(s),n(U))$ then $\sigma_\alpha(U,s)=(-\frac{1}{n(U)+r(\psi(U,s))},-\frac{1}{n(U)+r(\psi(U,s))})$.
-        \item Otherwise, $\sigma_\alpha(U,s)=\mathbb{R}$.
-        \end{itemize}
-    \end{itemize}
-
-It follows that $\sigma(U,s)=\sigmaprodr{\kappa}\cap\prod_{\alpha<\kappa} \sigma_\alpha(U,s)$ is a winning coding strategy.
-\end{proof}
-
-\begin{thm}
-Let $\kappa$ be a cardinal such that there exists a function $f:\kappa\to[\kappa]^{\leq \omega}$ where for every $W\in[\kappa]^{\leq\omega}$ there exists $\alpha_W<\kappa$ with $W\subseteq f(\alpha_W)$.
-(That is, $\textrm{cf}([\kappa]^{\leq\omega})=\kappa$.) Then $F \codewin PF_{F,C}(\kappa)$ and $O \codewin \congame{\sigmaprodr{\kappa}}{\vec{0}}$.
-\end{thm}
-
-\begin{proof}
-Let $W\restriction n \in [\kappa]^n$ be a subset of $W\in[\kappa]^\omega$ such that $W\restriction n \subset W \restriction (n+1)$ and $\bigcup_{n<\omega} W\restriction n = W$.
-
-Define \[\sigma(N,W) = N \cup (|N|+1) \cup \{\alpha_W\} \cup \bigcup_{\alpha \in N} f(\alpha) \restriction |N|\]
-
-Consider the play $\left<\emptyset,W_0,N_1,W_1,N_2,W_2,\dots\right>$ with $F$ following the strategy $\sigma$.
-Let $\gamma \in W_i$, and note $\gamma \in f(\alpha_{W_i})$ (and $\gamma \in f(\alpha_{W_i})\restriction |N_n|$ for sufficiently large $n$).
-\[N_{i+1} = \sigma(N_i,W_i) \supseteq \{\alpha_{W_i}\}\] and thus \[N_{n+1} = \sigma(N_n,W_n) \supseteq \bigcup_{\alpha \in N_n} f(\alpha) \restriction |N_n| \supseteq \bigcup_{\alpha \in N_{i+1}} f(\alpha) \restriction |N_n| \supseteq f(\alpha_{W_i}) \restriction |N_n|\] showing $\gamma \in N_{n+1}$.
-Since $\gamma$ is forbidden in round $n+1$, $\gamma$ appears in finitely many sets chosen by $C$.
-
-We turn our attention to $Con_{O,P}(\Sigma\mathbb{R}^\kappa)$.
-We define the winning strategy $\tau(U,p)$ for $O$ as follows: let $N(U)$ be the non-$\mathbb{R}$ coordinates in the basic open set $U$ and $W(p)$ be the non-$0$ coordinates in $p$.
-Then $\tau(U,p) = \left(\prod_{\alpha<\kappa} U_\alpha\right) \cap \Sigma\mathbb{R}^\kappa$ where if $\alpha \in \sigma(N(U),W(p))$ then $U_\alpha = (-\frac{1}{|N(U)|},\frac{1}{|N(U)|})$ and $U_\alpha=\mathbb{R}$ otherwise.
-
-Consider the play $\left<\emptyset,p_0,U_1,p_1,U_2,p_2,\dots\right>$ with $O$ following the strategy $\tau$.
-Observe that $N(\tau(U,p))=\sigma(N(U),W(p))$.
-Thus $p_i(\gamma)\not=0$ is equivalent to $\gamma \in W(p_i)$, and by the above argument, for sufficiently large $n$, $\gamma \in \sigma(N(U_n),W(p_n))$.
-Therefore from round $n$ onward the $\gamma$-coordinates of points chosen by $P$ must lay in $(-\frac{1}{|N(U)|},\frac{1}{|N(U)|})$ and converge to $0$.
-\end{proof}
-
-\begin{thm}
-Let $\kappa$ be the limit of cardinals $\kappa_n$ such that $\textrm{cf}([\kappa_n]^{\leq\omega},\subseteq)=\kappa_n$.
-Then $F \codewin PF_{F,C}(\kappa)$ and $O \codewin \congame{\sigmaprodr{\kappa}}{\vec{0}}$.
-\end{thm}
-
-\begin{proof}
-Let $f_n:\kappa_n\to[\kappa_n]^{\leq\omega}$ be such that for every $W\in[\kappa_n]^{\leq\omega}$ there exists $\alpha_{W,n}<\kappa_n$ such that $f_n(\alpha_{W,n})\supseteq W$.
-
-Define \[\sigma(N,W)=N\cup(|N|+1)\cup\{\alpha_{W\cap \kappa_{|N|},|N|}\}\cup\bigcup_{n\leq|N|}\bigcup_{\alpha\in N} f_n(\alpha)\restriction |N|\] We claim that $\sigma$ is a winning coding strategy.
-
-Consider the play $\left<N_0,W_0,N_1,W_1,\dots\right>$ where $O$ follows the strategy $\sigma$.
-For $\sigma$ to be a winning strategy for $F \codewin PF_{F,C}(\kappa)$, it must follow that for each $\gamma\in\bigcup_{i<\omega}W_i$, $\gamma$ is forbidden by some $\sigma(N_j,W_j)$.
-
-Let $\gamma\in W_i\cap \kappa_{|N_i|}$.
-For all $j>i$, $\alpha_{W\cap\kappa_{N_i},|N_i|}\in N_j$.
-Also, $\gamma \in f_{N_i}(\alpha_{W\cap\kappa_{N_i},|N_i|})\restriction|N_j|$ for some sufficiently large $j$.
-So we observe that $\gamma \in \bigcup_{n\leq|N_j|}\bigcup_{\alpha\in N_j} f_n(\alpha)\restriction |N_j|\subseteq \sigma(N_j,W_j)$.
-
-We turn our attention to $\congame{\sigmaprodr{\kappa}}{\vec{0}}$.
-We define the winning strategy $\tau(U,p)$ for $O$ as follows: let $N(U)$ be the non-$\mathbb{R}$ coordinates in the basic open set $U$ and $W(p)$ be the non-$0$ coordinates in $p$.
-Then $\tau(U,p) =\Sigma\mathbb{R}^\kappa \cap \prod_{\alpha<\kappa} U_\alpha$ where if $\alpha \in \sigma(N(U),W(p))$ then $U_\alpha = (-\frac{1}{|N(U)|},\frac{1}{|N(U)|})$ and $U_\alpha=\mathbb{R}$ otherwise.
-
-Consider the play $\left<\sigmaprodr{\kappa},p_0,U_1,p_1,U_2,p_2,\dots\right>$ with $O$ following the strategy $\tau$.
-Observe that $N(\tau(U,p))=\sigma(N(U),W(p))$.
-Thus $p_i(\gamma)\not=0$ is equivalent to $\gamma \in W(p_i)$, and by the above argument, for sufficiently large $n$, $\gamma \in \sigma(N(U_n),W(p_n))$.
-Therefore from round $n$ onward the $\gamma$-coordinates of points chosen by $P$ must lay in $(-\frac{1}{|N(U)|},\frac{1}{|N(U)|})$ and converge to $0$.
-\end{proof}
 
@@
 
-\begin{proof}
-Let $\kappa$ be the limit of cardinals $\kappa_n$ such that $F\codewin\pfgame{\kappa_n}$ using the strategy $\sigma_n(N,W)$ such that for $M\subseteq N$, $\sigma_n(M,W)\subseteq\sigma_n(N,W)$.
-Define \[\sigma(N,W)=(|N|+1)\cup\bigcup_{n<|N|}\sigma_n(N\cap\kappa_n,W\cap\kappa_n)\]
-
-Let $\left<N_0,W_0,N_1,W_1,\dots\right>$ be a legal play of the game with $N_{i+1}=\sigma(N_i,W_i)$.
-Suppose $\gamma\in W_i$ for infinitely-many $i$.
-$\gamma\in\kappa_n$ for some $n$, so observe the play $\left<M_0,W_0\cap\kappa_n,M_1,W_1\cap\kappa_n,\dots\right>$ with $M_0=N_0\cap\kappa_n$ and $M_{i+1}=\sigma_n(M_i,W_i\cap\kappa_n)\subseteq\sigma_n(N_i\cap\kappa_n,W_i\cap\kappa_n)$ which is $\subseteq\sigma(N_i,W_i)=N_{i+1}$ for sufficiently large $i$.
-
-Since $\sigma_n$ is a winning strategy, $\gamma\in M_{m+1}\subseteq N_{m+1}$ for sufficiently large $i$, making $\left<N_0,W_0,N_1,W_1,\dots\right>$ illegal, contradiction.
-
-Now suppose $F\codewin\pfgame{\kappa}$.
-For each $\alpha<\kappa^+$, let $\sigma_\alpha(N,W)$ be a winning coding strategy for $\pfgame{\alpha}$ such that for $M\subseteq N$, $\sigma_\alpha(M,W)\subseteq\sigma_\alpha(N,W)$.
-We define the following strategy for $F$ in $\pfgame{\kappa^+}$: \[\sigma(N,W)=N\cup\bigcup_{\alpha\in N}\sigma_{\alpha+1}(N\cap(\alpha+1),W\cap(\alpha+1))\]
-
-Let $\left<N_0,W_0,N_1,W_1,\dots\right>$ be a legal play of the game with $N_{i+1}=\sigma(N_i,W_i)$.
-Suppose $\gamma\in W_i$ for infinitely-many $i$.
-Observe the play $\left<M_0,W_0\cap(\gamma+1),M_1,W_1\cap(\gamma+1),\dots\right>$ with $M_0=N_0\cap(\gamma+1)$ and $M_{i+1}=\sigma_{\gamma+1}(M_i,W_i\cap(\gamma+1))\subseteq\sigma_{\gamma+1}(N_i\cap(\gamma+1),W_i\cap(\gamma+1))$.
-
-Since $\sigma_{\gamma+1}$ is a winning strategy, $\gamma\in M_{m+1}\subseteq\sigma_{\gamma+1}(N_i\cap(\gamma+1),W_i\cap(\gamma+1))\subseteq\sigma(N_i,W_i)=N_{i+1}$ for some sufficiently large $m$, making $\left<N_0,W_0,N_1,W_1,\dots\right>$ illegal, contradiction.
-\end{proof}
-
 \begin{cor}
-$O\codewin\congame{\sigmaprodr{\kappa}}{\vec{0}}$ for all cardinals $\kappa$.
+  $O\codewin\congame{\sigmaprodr{\kappa}}{\vec{0}}$
+  for all cardinals $\kappa$.
 \end{cor}
-
-\begin{proof}
-Let $\tau(N,W)$ be the winning coding strategy for $F$ in $\pfgame{\kappa}$, $N(U)\in[\kappa]^{<\omega}$ represent the non-$\mathbb{R}$ coordinates of a basic open set $U$ of $\sigmaprodr{\kappa}$, and $W(p)\in[\kappa]^{\leq\omega}$ represent the non-$0$ coordinates of a point $p$ in $\sigmaprodr{\kappa}$.
-For each $\alpha<\kappa$, let \[\sigma_\alpha(U,p)=\left\{\begin{array}{ll}(-\frac{1}{|N(U)|},\frac{1}{|N(U)|})&\text{if }\alpha\in\tau(N(U),W(p))\\\mathbb{R}&\text{otherwise}\end{array}\right.\] and $\sigma(U,p)=\sigmaprodr{\kappa}\cap\prod_{\alpha<\kappa}\sigma_\alpha(U,p)$.
-\end{proof}

### 2014-05-14 phd/dissertation/chapter5.tex
Renumber chapters

@@
 
-\chapter{Menger Game}
+\chapter{Locally Finite Games}
 
-Results pertaining to the Menger game characterizing the Menger property.
+Results pertaining to the Locally Finite games related to $W$ games.
 
-\section{cut-and-paste}
+\section{Characterizations using $\lfkpgame{X}$, $\lfklgame{X}$}
 
-  \begin{defn}
-    $X$ is \textbf{Menger} if for all open covers $\mathcal{U}_0,\mathcal{U}_1,\dots$ there exist finite subcollections $\mathcal{F}_n \subseteq \mathcal{U}_n$ such that $\bigcup_{n<\omega} \mathcal{F}_n$ is a cover of $X$.
-  \end{defn}
+\begin{thm}(G)
+  The following are equivalent for a locally compact space $X$:
+    \begin{itemize}
+      \item $X$ is paracompact
+      \item $\pl K \uparrow \lfklgame{X}$.
+    \end{itemize}
+\end{thm}
+
+\begin{thm}(G)
+  The following are equivalent for a locally compact space $X$:
+    \begin{itemize}
+      \item $X$ is metacompact
+      \item $\pl K \tactwin \lfkpgame{X}$.
+    \end{itemize}
+\end{thm}
+
+\begin{thm}(G)
+  The following are equivalent for a locally compact space $X$:
+    \begin{itemize}
+      \item $X$ is $\sigma$-metacompact
+      \item $\pl K \markwin \lfkpgame{X}$.
+    \end{itemize}
+\end{thm}
+
+\begin{obs}
+  The following are equivalent for any space $X$:
+    \begin{itemize}
+      \item $X$ is compact
+      \item $\pl K \ktactwin{0} \lfkpgame{X}$.
+    \end{itemize}
+\end{obs}
+
+\begin{thm}
+  $P \markwin G_{K,P}(X)$ where $X$ is a first-countable non-locally
+  countably compact space.
+\end{thm}
+
+\begin{thm}
+  $P \not\tactwin G_{K,P}(M)$ where $M$ is the metric fan space.
+\end{thm}
+
+\begin{thm}
+  The following are equivalent for any locally compact space $X$:
+    \begin{itemize}
+      \item $X$ is Lindel\"of.
+      \item $X$ is $\sigma$-compact.
+      \item $X$ is hemicompact.
+      \item $\pl K \prewin G_{K,L}(X)$.
+      \item $\pl K \prewin G_{K,P}(X)$.
+    \end{itemize}
+\end{thm}
+
+\begin{thm}
+  The following are equivalent for any Hausdorff $k$-space $X$:
+    \begin{itemize}
+      \item $X$ is hemicompact.
+      \item $X$ is $k_{\omega}$.
+      \item $\pl K \prewin \lfklgame{X}$.
+      \item $\pl K \prewin \lfkpgame{X}$.
+    \end{itemize}
+\end{thm}
+
+\section{Non-locally compact spaces}
 
 \begin{prop}
-    $\sigma$-compact $\Rightarrow$ Menger $\Rightarrow$ Lindelof
+  If $X=\omega\cup\mathcal{F}\subset\beta\omega$ (a non-$k$ space),
+  then $K\not\prewin \lfklgame{X}$.
 \end{prop}
 
-  \begin{defn}
-    In the two-player game $\mengame{X}$ player $C$ chooses open covers $\mathcal{U}_n$ of $X$, followed by player $F$ choosing a finite subcollection $\mathcal{F}_n\subseteq\mathcal{U}_n$.
-$F$ wins if $\bigcup_{n<\omega} \mathcal{F}_n$ is a cover of $X$.
-  \end{defn}
-
-  \begin{thm}
-    $X$ is Menger if and only if $C \not\win \mengame{X}$.
-  \end{thm}
-
-  \begin{proof}
-    Result due to Hurewicz.
-
-    First, suppose $X$ wasn't Menger.
-Then there would exist open covers $\mathcal{U}_0,\mathcal{U}_1,\dots$ of $X$ such that for any choice of finite subcollections $\mathcal{F}_n\subseteq\mathcal{U}_n$, $\bigcup_{n<\omega} \mathcal{F}_n$ isn't a cover of $X$.
-Thus $C\prewin\mengame{X} \Rightarrow S \not\win\mengame{X}$.
-
-    Now, assume $X$ is Menger, and consider a strategy for $C$ in $\mengame{X}$.
-
-    Since $X$ is Lindelof, we can assume $C$ plays only countable covers of $X$.
-Then, since $F$ is choosing finite subsets, we may assume $F$ chooses some initial segement of the countable cover.
-In turn, we can assume $C$ plays an increasing open cover $\{U_0,U_1,\dots\}$ where $U_n\subseteq U_{n+1}$.
-And in that case, it's suffient to assume $F$ simply chooses a singleton subset of each cover.
-And finally, since choices made by $F$ are already covered, we can assume that every open set in a cover played by $C$ covers the sets chosen by $F$ previously.
-
-    As a result, we have the following figure of a tree of plays which I need to draw:
-
-    (Insert figure here.)
-
-    Note that for $a,b\in\omega^{<\omega}$ and $m\leq n$, we know:
-      \begin{enumerate}[(a)]
-        \item $U_{a\concat m}\subseteq U_{a\concat n}$ \\ (for example, $U_{1627} \subseteq U_{1629}$ - increasing the final digit yields supersets)
-        \item $U_a \subseteq U_{a\concat b}$ \\ (for example, $U_{1627}\subseteq U_{162789}$ - appending any sequence to the end yields supersets)
-        \item $U_{a\concat m} \subseteq U_{a\concat n} \subseteq U_{a\concat n\concat b} \subseteq U_{a\concat n\concat b\concat m}$ \\ (for example: $U_{1627} \subseteq U_{1629283287}$ - injecting a subseqence with initial number larger than the original's final number, prior to the final number, yields supersets)
-      \end{enumerate}
-
-    We may observe that if $F$ can find an $f:\omega\to\omega$ such that $\bigcup_{n<\omega}U_{f\rest (n+1)} = X$, she can use $\{U_{f\rest 0}\}, \{U_{f\rest 1}\}, \dots$ to counter $C$'s strategy.
-
-    Let $\ds V_k^n = \bigcap_{a\in\omega^{\leq n}} U_{a\concat k}$.
-We claim that (1) $V_k^n$ is open, (2) $\mathcal{V}^n=\{V_0^n,V_1^n,\dots\}$ is increasing, and (3) $\mathcal{V}^n$ is a cover.
-Proofs:
-
-    \begin{enumerate}
-      \item
-      Since due to (c) for each $b\in \omega^{\leq n} \setminus k^{\leq n}$, there is an $a\in k^{\leq n}$ with $U_{a\concat k} \subseteq U_{b\concat k}$: \[\ds V_k^n = \bigcap_{a\in\omega^{\leq n}} U_{a\concat k} = \bigcap_{a\in k^{\leq n}} U_{a\concat k} \cap \bigcap_{b\in \omega^{\leq n} \setminus k^{\leq n}} U_{b\concat k} = \bigcap_{a\in k^{\leq n}} U_{a\concat k}\] making $V_k^n$ a finite intersection of open sets.
-
-      \item
-      We show $V_k^0\subseteq V_{k+1}^0$:
-      \[
-        V_k^0 = U_k \subseteq U_{k+1} = V_{k+1}^0
-      \]
-      and then assume $V_k^{n}\subseteq V_{k+1}^{n}$:
-      \[
-        V_k^{n+1} = 
-        \bigcap_{a\in{\omega}^{\leq n+1}} U_{a\concat k} = 
-        V_k^{n} \cap \bigcap_{a\in{\omega}^{n+1}} U_{a\concat k} \subseteq
-        V_{k+1}^{n} \cap \bigcap_{a\in{\omega}^{n+1}} U_{a\concat (k+1)} =
-        V_{k+1}^{n+1}
-      \]
-
-      \item
-      We easily see that $\mathcal{V}^0=\{U_0,U_1,\dots\}$ is a cover, and then assume $\mathcal{V}^n$ is a cover.
-
-      Let $x\in X$ and pick $l<\omega$ such that $x \in V^n_l$. For $a \in l^{n+1}$ choose $l_a$ such that $x\in U_{a\concat l_a}$, giving
-      \[ x \in \bigcap_{a\in l^{n+1}} U_{a\concat l_a} \]
-
-      We will assume $k>l,l_a$ for all $a\in l^{\leq n+1}$.
-
-      For any $a\in k^{n+1}\setminus l^{n+1}$ note that $a = b\concat c$ where $b\in l^{\leq n}$ and $c$ begins with a number $l$ or greater:
-      \[
-        V^n_l \subseteq 
-        U_{b\concat l} \subseteq 
-        U_{b\concat c} \subseteq
-        U_{b\concat c\concat l_a} = 
-        U_{a\concat l_a}
-      \]
-
-      Thus:
-      \[ 
-        x \in 
-        V^n_l \cap \left(\bigcap_{a\in l^{n+1}} U_{a\concat l_a}\right) 
-      \]
-      \[
-        =
-        V^n_l \cap \left(\bigcap_{a\in k^{n+1}\setminus l^{n+1}} U_{a\concat l_a}\right) \cap \left(\bigcap_{a\in l^{n+1}} U_{a\concat l_a}\right)
-      \]
-      \[
-        =
-        V^n_l \cap \left(\bigcap_{a\in k^{n+1}} U_{a\concat l_a}\right)
-      \]
-      \[
-        \subseteq
-        V^n_k \cap \left(\bigcap_{a\in k^{n+1}} U_{a\concat k}\right)
-      \]
-      \[
-        =
-        V^{n+1}_k
-      \]
-    \end{enumerate}
-
-    Finally, apply Menger to $\mathcal{V}^n$, resulting in the cover $\{V_{f(0)}^0, V_{f(1)}^1, \dots\}$, noting \[X = \bigcup_{n<\omega}V_{f(n)}^n \subseteq \bigcup_{n<\omega} U_{(f\rest n)\concat f(n)} = \bigcup_{n<\omega} U_{f\rest (n+1)}\]
-  \end{proof}
-
 \begin{prop}
-    $X$ is compact if and only if $F \tactwin \mengame{X}$ if and only if $F \ktactwin{k} \mengame{X}$
-  \end{prop}
-
-  \begin{proof}
-    Assume $X$ is compact. For each open cover played by $C$, pick a finite subcover, and this yields a winning tactical strategy.
-
-    Assume $F$ has a winning $k$-tactical strategy. For any open cover, have $C$ play only it during the entire game. $F$'s only choice must be a finite subcover.
-  \end{proof}
-
-  \begin{prop}
-    If $X$ is $\sigma$-compact then $F \markwin \mengame{X}$
-  \end{prop}
-
-  \begin{proof}
-    Let $X=\bigcup_{n<\omega} X_n$ for compact $X_n$. On round $n$, $F$ picks the finite subcover of $C$'s open cover of $X_n$.
-  \end{proof}
-
-  For Menger's game, there is no useful distinction between a $k$-Markov strategy for $F$, and a $2$-Markov strategy.
-
-  \begin{thm}
-  For any topological space $X$ and all $k \geq 2$, $F \kmarkwin{k} \mengame{X}$ if and only if $F \kmarkwin{2} \mengame{X}$.
-  \end{thm}
-
-  \begin{proof}
-  Assume $\sigma(\mc{U}_0,\dots,\mc{U}_{k-1},n)$ is a winning $k$-Markov strategy.
-Define the $2$-Markov strategy $\tau(\mc{U},\mc{V},n)$ so that it contains $\sigma(\mc{W}_0,\dots,\mc{W}_{k-2},\mc{V},m)$ for the following conditions on $\mc{W}_0,\dots,\mc{W}_{k-2},m$:
-    \begin{itemize}
-    \item Each $\mc{W}_i \in \{\mc{U},\mc{V}\}$
-    \item $m \leq (n+1)k$; in particular, for $i<k$, 
-      \[
-        \sigma(\mc{W}_0,\dots,\mc{W}_{k-2},\mc{V},(n+1)k+i)
-        \subseteq 
-        \tau(\mc{U},\mc{V},n+1) 
-      \]
-    \end{itemize}
-
-  Considering an arbitrary play $\mc{U}_0, \mc{U}_1, \dots$ by $C$ versus $\tau$, we note that $\sigma$ defeats the play 
-  \[
-    \underbrace{\mc{U}_0,\mc{U}_0,\dots,\mc{U}_0}_{k},
-    \underbrace{\mc{U}_1,\mc{U}_1,\dots,\mc{U}_1}_{k}
-    \dots
-  \]
-
-  So we have that
-    \[
-      \bigcup_{i<k, n<\omega} \sigma(
-      \underbrace{\mc{U}_n,\dots,\mc{U}_n}_{k-i-1},
-      \underbrace{\mc{U}_{n+1},\dots,\mc{U}_{n+1}}_{i+1},
-      (n+1)k+i)
-    \]
-  is a cover for $X$, and as 
-    \[
-      \sigma(
-      \underbrace{\mc{U}_n,\dots,\mc{U}_n}_{k-i-1},
-      \underbrace{\mc{U}_{n+1},\dots,\mc{U}_{n+1}}_{i+1},
-      (n+1)k+i)
-      \subseteq 
-      \tau(\mc{U}_n,\mc{U}_{n+1},n+1)
-    \]
-  $\tau$ defeats the play $\mc{U}_0, \mc{U}_1, \dots$.
-  \end{proof}
-
-  But there are spaces for which there is no Markov strategy, but there is a $2$-Markov strategy.
-
-  In a question I posed to G, he answered:
-
-  \begin{lem}
-    For all functions $\tau:\omega_1\times\omega \rightarrow [\omega_1]^{<\omega}$, there exists a sequence $\alpha_0, \alpha_1, \dots < \omega_1$ such that $\{\tau(\alpha_n,n): n<\omega\}$ is not a cover for $\{\beta:\forall n<\omega (\beta < \alpha_n)\}$.
-  \end{lem}
-
-  \begin{proof}
-    Let $P_n = \{\beta: \beta < \alpha \Rightarrow \beta \in \tau(\alpha, n)\}$.
-Observe that each $P_n$ is finite; else there is some $\alpha$ larger than every member of some countably infinite $P_n^*\subseteq P_n$ such that $P_n^* \subseteq \tau(\alpha, n)$.
-
-    Choose $\beta \not\in \bigcup_{n<\omega} P_n$. Then for each $n<\omega$, pick $\alpha_n>\beta$ such that $\beta \not\in \tau(\alpha_n, n)$.
-  \end{proof}
-
-  Note that the one-point Lindel\"ofication of discrete $\omega_1$, $\oneptlind{\omega_1}$, is not $\sigma$-compact. With the above lemma, we may see that:
-
-  \begin{ex}
-    $F \win \mengame{\oneptlind{\omega_1}}$ but $F \not\markwin \mengame{\oneptlind{\omega_1}}$.
-  \end{ex}
-
-  \begin{proof}
-    First, we see $F$ has a simple perfect information strategy: in response to the initial cover of $\oneptlind{\omega_1}$, $F$ chooses a co-countable neighborhood of $\infty$.
-On successive turns she may pick a single set from $C$'s covers to cover the countable remainder.
-
-    Now, suppose that $\sigma(\mc{U}, n)$ was a winning Markov strategy and aim for a contradiction.
-Consider the covers \[\mc{U}(\alpha) = \{[\alpha,\omega_1)\cup\{\infty\}\} \cup \{\{\beta\}:\beta < \alpha\}\] and define $\tau(\alpha,n)$ to be the union of singletons chosen by $\sigma(\mathcal{U}(\alpha),n)$.
-
-    Using the sequence $\alpha_0, \alpha_1,\dots<\omega_1$ from the previous lemma, we consider the play $\mc{U}(\alpha_0),\mc{U}(\alpha_1),\dots$.
-
-    As $\sigma$ was a winning strategy, $\{\sigma(\mathcal{U}(\alpha_n),n): n<\omega\}$ must cover $\oneptlind{\omega_1}$, and thus $\{\tau(\alpha_n,n): n<\omega\}$ must cover $\{\beta:\forall n<\omega (\beta < \alpha_n)\}$, contradiction.
-  \end{proof}
-
-  Telgarski showed in ``On Games of Topsoe'' that a metrizable space is $\sigma$-compact if and only if there exists a winning strategy for $F$ in the Menger game, and Scheepers gave a more direct proof later.
-We generalize Scheeper's proof to handle a number of cases.
-
-  \begin{defn}
-    A set $R\subseteq X$ is relatively compact to the topological space $X$ if for every open cover of the entire space $X$, there is a finite subcover of the set $R$.
-  \end{defn}
-
-  \begin{prop}
-    If $X$ is regular, then $Y$ is relatively compact if and only if $\cl{Y}$ is compact.
-  \end{prop}
-
-  \begin{proof}
-    The reverse implication is trivial.
-
-    Assume $Y$ is relatively compact, let $\mc U$ be an open cover of $\cl Y$, and define $x\in V_x\subseteq \cl{V_x}\subseteq U_x \in \mc U$ for each $x\in X$.
-Then if we take a cover $\mc F = \{V_{x_i} : i<n\}$ of $Y$ by relative compactness, then $\{U_{x_i}:i<n\}$ is a finite cover of $\cl Y$, showing compactness.
-  \end{proof}
-
-  \begin{lem}
-    Let $\sigma(\mc{U}, n)$ be a winning Markov strategy for $F$ in $\mengame{X}$, and $\mathfrak{C}$ collect all open covers of $X$. Then for
-      \[
-        R_n = \bigcap_{\mc{U}\in\mathfrak{C}} \bigcup\sigma(\mc{U},n)
-      \]
-    it follows that $R_n$ is relatively compact to $X$, and $\bigcup_{n<\omega} R_n = X$.
-  \end{lem}
-
-  \begin{proof}
-    First, we see that $\sigma(\mc{U},n)$ witnesses the relative compactness of $R_n$.
-Suppose that $x \not\in R_n = \bigcap_{\mc{U}\in\mathfrak{C}} \bigcup\sigma(\mc{U},n)$ for any $n<\omega$.
-Then for each $n$, pick $\mc{U}_n\in\mathfrak{C}$ such that $x\not\in \bigcup\sigma(\mc{U}_n,n)$.
-Then $\sigma$ does not defeat the play $\mc{U}_0,\mc{U}_1,\dots$
-  \end{proof}
-
-  \begin{cor}
-    A space $X$ is $\sigma$-(relatively compact) if and only if $F \markwin \mengame{X}$.
-  \end{cor}
-
-  \begin{cor}
-    For regular spaces $X$, the following are equivalent:
-      \begin{enumerate}[(a)]
-        \item $X$ is $\sigma$-compact
-        \item $X$ is $\sigma$-(relatively compact)
-        \item $F \markwin \mengame{X}$
-      \end{enumerate}
-  \end{cor}
-
-  \begin{thm}
-    For second-countable $X$, the following are equivalent:
-      \begin{enumerate}[(a)]
-        \item $X$ is $\sigma$-(relatively compact)
-        \item $F \win \mengame{X}$
-        \item $F\markwin \mengame{X}$
-      \end{enumerate}
-  \end{thm}
-
-  \begin{proof}.
-    We need only show $(b)\Rightarrow(a)$, so let $\sigma(\mc{U}_0,\dots,\mc{U}_{n-1})$ be a winning strategy for $F$, and observe that since $X$ is second-countable, we may assume all covers are countable.
-Let $\mathfrak{C}$ be the collection of all countable covers of $X$.
-We define $R_s,\mc{U}_s$ for $s\in\omega^{<\omega}$ as follows:
-      \begin{itemize}
-        \item $\ds R_\emptyset = \bigcap_{\mc{U}\in\mathfrak{C}} \left(\bigcup \sigma(\mc{U})\right)$
-        \item Note that there are only countably many distinct finite subsets $\sigma(\mc{U})$ of the countable collection $\mc U$. Thus define each $\mc U_{\<n\>}$ so that
-          \[
-            R_\emptyset = 
-            \bigcap_{n<\omega}\left(\bigcup\sigma(\mc{U}_{\<n\>})\right)
-          \]
-        \item $\ds R_s = \bigcap_{\mc{U}\in\mathfrak{C}} \left(\bigcup \sigma(\mc{U}_{s\rest1},\mc{U}_{s\rest2},\dots,\mc{U}_s,\mc{U})\right)$
-        \item Again, note that there are only countably many distinct finite subsets $\sigma(\mc{U}_{s\rest1},\mc{U}_{s\rest2},\dots,\mc{U}_s,\mc{U})$ of the countable collection $\mc U$.
-Thus define each $\mc U_{s\concat\<n\>}$ so that
-          \[
-            R_s = 
-            \bigcap_{n<\omega} \left(\bigcup \sigma(\mc{U}_{s\rest1},\mc{U}_{s\rest2},\dots,\mc{U}_s,\mc{U}_{s\concat\<n\>})\right)
-          \]
-      \end{itemize}
-
-    We quickly confirm that each $R_s$ is relatively compact as for each open cover $\mc{U}$ of $X$ we have the finite subcover $\sigma(\mc{U}_{s\rest1},\mc{U}_{s\rest2},\dots,\mc{U}_s,\mc{U})$ of $R_s$.
-
-    Finally, we claim that $X = \bigcup_{s\in\omega^{<\omega}} R_s$.
-If not, let $x$ be missed by every $R_s$, and define $f\in\omega^\omega$ such that $x\not\in \bigcup\sigma(\mc{U}_{f\rest1},\dots,\mc{U}_{f\rest n})$ for any $n$.
-Then $\mc{U}_{f\rest1},\mc{U}_{f\rest2},\dots$ is a counter to the winning strategy $\sigma$, a contradiction.
-  \end{proof}
-
-  \begin{cor}
-    For metric spaces $X$, the following are equivalent:
-      \begin{enumerate}[(a)]
-        \item $X$ is $\sigma$-compact
-        \item $X$ is $\sigma$-(relatively compact)
-        \item $F \win \mengame{X}$
-        \item $F \markwin \mengame{X}$
-      \end{enumerate}
-  \end{cor}
-
-  \begin{ex}
-  Let $R$ be given the topology from example 63 from Counterexamples in Topology, the topology generated by open intervals with countable sets removed.
-This space is a non-regular example where $F \win \mengame{R}$, but $F \not\markwin \mengame{R}$, that is, $R$ is not $\sigma$-(relatively compact).
-  \end{ex}
-
-  \begin{proof}
-  From Counterexamples: The irrationals are open, but contain no closed neighborhood, showing non-regular.
-
-  Take open covers $\mc{U}_0,\mc{U}_1,\dots$.
-Define $\sigma(\mc{U}_0,\dots,\mc{U}_{2n})$ to be a finite subcover of $[-n,n]\setminus C_n$ for some countable $C_n=\{c_{n,0}, c_{n,1}, \dots\}$.
-For $\sigma(\mc{U}_0,\dots,\mc{U}_{2n+1})$, use any subcover of $\{c_{i,j} : i,j < n\}$.
-It is easily seen that $\sigma$ is a winning perfect information strategy.
-
-  For any $A=\{x_n:n<\omega\} \in [R]^\omega$, we may choose the open cover $\mc{U} = \{R \setminus \{x_i: i \not= n\} : n < \omega \}$ of $R$ with no finite subcover.
-Thus all relatively compact sets are finite, and the countable union of finite sets cannot contain $R$, making $R$ not $\sigma$-(relatively compact).
-  \end{proof}
-
-  \begin{ex}
-  Let $R$ be given the topology from example 67 from Counterexamples in Topology, the topology generated by open intervals with or without the rationals removed.
-This space is non-regular, and non-$\sigma$-compact, but is second-countable and $\sigma$-(relatively compact).
-  \end{ex}
-
-  \begin{proof}
-  From Counterexamples: The rationals are closed, but the closure of any open neighborhood is the whole real line, so they cannot be separated from any irrational point.
-Compact sets in this topology are nowhere dense in the Euclidean topology, so there cannot be countably many which union to the whole space.
-$\{(a,b)\setminus D : a,b\in\mathbb{Q},D\in\{\emptyset,\mathbb{Q}\}\}$ is a countable base for the space.
-
-  To see that $R$ is $\sigma$-relatively compact, it suffices to show that $[a,b]\setminus\mathbb{Q}$ is relatively compact.
-Let $\mc U$ be a cover of $R$, and let $\mc U'$ fill in the missing rationals for any open set in $\mc U$.
-There is a finite subcover $\mc V'\subseteq \mc U'$ for $[a,b]$ since $\mc U'$ contains open sets from the Euclidean topology.
-Let $\mc V= \{V\setminus\mathbb{Q}:V\in V'\}$: this is a finite refinment of $\mc U$ covering $[a,b]\setminus\mathbb{Q}$, so $[a,b]\setminus\mathbb{Q}$ is relatively compact.
-  \end{proof}
-
-  We define a new property ``\scish'' to describe a sufficient condition for $F \kmarkwin{2}\mengame{X}$.
-
-  \begin{defn}
-    Let $\mc U$ be a cover of $X$. We say $C\subseteq X$ is $\mc U$-compact if there exists a finite subcover of $\mc U$ which covers $C$.
-
-    We say $X$ is \scish~if there exist functions $r_{\mc V}:X\to\omega$ for each open cover $\mc V$ of $X$ such that both of the following sets are $\mc V$-compact for all open covers $\mc U$, $\mc V$ and $n<\omega$:
-      \[
-        c(\mc V,n)=\{ x\in X : r_{\mc V}(x)\leq n\}
-      \]
-      \[
-        p(\mc U,\mc V)=\{ x\in X : 0<r_{\mc U}(x)<r_{\mc V}(x)\}
-      \]
-  \end{defn}
-
-  \begin{defn}
-    For two functions $f,g$ we say $f$ is \textbf{$\mu$-almost compatible} with $g$ ($f\alcomp_\mu g$) if $|\{x\in\dom(f)\cap\dom(g):f(x)\not=g(x)\}|<\mu$.
-If $\mu=\omega$ then we say $f,g$ are \textbf{almost compatible} ($f\alcomp g$).
-  \end{defn}
-
-  \begin{lem}\label{kunlem}
-    For each $\alpha<\omega_1$, there exist injective functions $f_\alpha:\alpha\to\omega$ such that if $\alpha<\beta$, then \[f_\alpha \alcomp f_\beta\] that is, $f_\alpha$ and $f_\beta\rest\alpha$ agree on all but finitely many ordinals.
-In addition, the range of each $f_\alpha$ is co-infinite.
-  \end{lem}
-
-  \begin{proof}
-    Taken from Kunen (used for the construction of an $\omega_1$-Aronszajn tree).
-
-    We begin with the empty function $f_0:0\to\omega_1$ which satisfies the hypothesis, and assume $f_\alpha$ is defined by induction.
-Let $f_{\alpha+1} = f_\alpha \cup \{\<\alpha,n\>\}$ where $n$ is not defined for $f_\alpha$, and this satisfies the hypothesis.
-
-    Finally, suppose $\gamma$ is the limit of $\alpha_0,\alpha_1,\dots$, and $f_\alpha$ is defined for $\alpha<\gamma$.
-Let $g_0=f_{\alpha_0}$, and assuming $g_n\alcomp f_{\alpha_n}$ with coinfinite range, define $g_{n+1}:\alpha_{n+1}\to\omega$ so that $g_{n+1}\rest\alpha_n=g_n$ and $g_{n+1}\rest(\alpha_{n+1}\setminus\alpha_n)\alcomp f_{\alpha_{n+1}}$ with coinfinite range.
-Then $g=\bigcup_{n<\omega} g_n$ is an injective function from $\gamma \to \omega$ and $g \alcomp f_\alpha$ for $\alpha <\gamma$, but the range need not be coinfinite.
-So let
-    \[
-      f_\gamma(\beta) = \left\{
-      \begin{array}{ll}
-        g(\alpha_{2n}) & \beta = \alpha_n \\
-        g(\beta) & \text{otherwise}
-      \end{array}
-      \right.
-    \]
-    which frees up $\{g(\alpha_{2n+1}):n<\omega\}$ from the range of $f_\gamma$, and allows $f_\gamma\alcomp f_\alpha$.
-  \end{proof}
-
-  \begin{thm}
-    The one-point Lindel\"ofication of the uncountable discrete space, $\oneptlind{\omega_1}$, is \scish.
-  \end{thm}
-
-  \begin{proof}
-    Take the injective funcions $f_\alpha$ from Kunen's lemma such that $f_\alpha \alcomp f_\beta$.
-For each open cover $\mc V$ of $\oneptlind{\omega_1}$ let $\gamma(\mc V)$ identify the least ordinal such that $\oneptlind{\omega_1}\setminus\gamma(\mc U)$ is in a refinement of $\mc V$.
-Then $r_{\mc V}$ defined by
-      \[
-        r_{\mc V}(x) = \left\{
-      \begin{array}{ll}
-        0 & x\in\oneptlind{\omega_1}\setminus\gamma(\mc V) \\
-        f_{\gamma(\mc V)}(x)+1 & x\in\gamma(\mc V)
-      \end{array}
-      \right.
-      \] 
-    witnesses the property as $c(\mc V,0)$ is contained in a single open set in $\mc V$, $c(\mc V,n+1)$ is a singleton or empty set, and
-      \[
-        p(\mc U,\mc V) = \{\alpha<\min(\gamma(\mc U),\gamma(\mc V)) : f_{\gamma(\mc U)}(\alpha)<f_{\gamma(\mc V)}(\alpha)\}
-      \]
-    is finite.
-  \end{proof}
-
-  \begin{thm}
-    If $X$ is \scish, then $F \kmarkwin{2}\mengame{X}$.
-  \end{thm}
-
-  \begin{proof}
-    Let $\sigma(\mc{U}_0,0)$ cover $c(\mc{U}_0,0)$, and let $\sigma(\mc{U}_n,\mc{U}_{n+1},n+1)$ cover both $c(\mc{U}_{n+1},n+1)$ and $p(\mc{U}_n,\mc{U}_{n+1})$.
-If $\mc{U}_0,\mc{U}_1,\dots$ is any play by $C$, then for each $x\in X$, we note that one of the following must occur:
-      \begin{itemize}
-        \item $r_{\mc U_0}(x)=0$ and thus $x\in c(\mc U_0,0)\subseteq \bigcup \sigma(\mc{U}_0,0)$.
-        \item $r_{\mc U_0}(x)=N+1$ for some $N\geq 0$ and:
-        \begin{itemize}
-          \item For all $n\leq N$, 
-            \[
-              r_{\mc U_{n+1}}(x)\leq N+1
-            \] 
-            and thus $x\in c(\mc U_{N+1},N+1)$.
-          \item For some $n \leq N$, 
-            \[
-              r_{\mc U_n}(x)\leq N+1 < r_{\mc U_{n+1}}(x)
-            \]
-           and thus $x\in p(\mc U_n,\mc U_{n+1})$
-         \end{itemize}
-      \end{itemize}
-  \end{proof}
-
-  \begin{cor}
-    $F\kmarkwin{2}\mengame{\oneptlind{\omega_1}}$
-  \end{cor}
-
-  \begin{defn} 
-    The statement $S(\kappa,\mu,\lambda)$ due to Scheepers is shorthand for the following: there exist injective functions $f_A:A\to\lambda$ for each $A\in[\kappa]^\mu$ such that $f_A\alcomp_\mu f_B$ for all $A,B\in[\kappa]^\mu$.
-  \end{defn}
-
-  \begin{prop}
-    $\neg S(\kappa,\omega,\omega)$ for $\kappa>2^\omega$
-  \end{prop}
-
-  \begin{proof}
-    Let $A_\alpha=\{\alpha\cdot\omega+n:n<\omega\}\in[\kappa]^\omega$ and $f_{A_\alpha}:A_\alpha\to\omega$ be injective for $\alpha<\kappa$.
-Since there are $\kappa>|[\omega]^\omega|$ different $A_\alpha$, there must be $\alpha,\beta$ where $\text{ran}(f_{A_\alpha})=\text{ran}(f_{A_\beta})$.
-Then there is no way to define $f_{A_\alpha\cup A_\beta}$ so that it is almost compatible with both $f_{A_\alpha}$ and $f_{A_\beta}$.
-  \end{proof}
-
-  \begin{thm}
-    $S(\kappa,\omega,\omega)$ implies $\oneptlind{\kappa}$ is \scish.
-  \end{thm}
-
-  \begin{proof}
-    Take the injective funcions $f_A:A\to\omega$ witnessing $S(\kappa,\omega,\omega)$.
-For each cover $\mc V$ of $\oneptlind{\kappa}$ let $A(\mc V)$ define a set such that $\oneptlind{\kappa}\setminus A(\mc V)$ is in a refinement of $\mc V$.
-Then $r_{\mc V}$ defined by
-      \[
-        r_{\mc V}(x) = \left\{
-      \begin{array}{ll}
-        0 & x\in\oneptlind{\kappa}\setminus A(\mc V) \\
-        f_{A(\mc V)}(x)+1 & x\in A(\mc V)
-      \end{array}
-      \right.
-      \]
-
-    witnesses the property as $c(\mc V,0)$ is contained in a single open set in $\mc V$, $c(\mc V,n+1)$ is a singleton or empty set, and
-      \[
-        p(\mc U,\mc V) = \{\alpha\in A(\mc U)\cap A(\mc V) : f_{A(\mc U)}(\alpha)<f_{A(\mc V)}(\alpha)\}
-      \]
-    is finite.
-  \end{proof}
-
-  \begin{cor}
-    $S(\kappa,\omega,\omega)$ implies $F\kmarkwin{2}\mengame{\oneptlind{\kappa}}$.
-  \end{cor}
-
-  \begin{defn}
-    A finite partial function $p$ from $A$ to $B$ has a domain which is a finite subset of $A$ and a range which is a finite subset of $B$.
-Let the set of all finite partial functions from $A$ to $B$ be denoted by $Fn(A,B)$.
-
-    Then let $Fn^2(\mc A,B)\subset Fn(\mc A,Fn(\bigcup \mc A,B))$ such that for each $p\in Fn^2(\mc A,B)$, $p(A)=p_A\in Fn(A,B)$.
-  \end{defn}
-
-  \begin{defn}
-    Let $\pok\subset Fn^2([\kappa]^\omega,\omega)$ be such that each $p_A$ is injective, and give it the partial order $\leq$ defined by $q\leq p$ if and only if:
-          \begin{itemize}
-            \item $\dom(q)\supseteq\dom(p)$
-            \item For each $A\in\dom(p)$, $q_A\supseteq p_A$
-            \item For each $A,B\in\dom(p)$, if $p_A$ and $p_B$ are not defined for some $\alpha\in A\cap B$, but $q_A$ is, then $q_B$ is also defined for $\alpha$ and $q_A(\alpha)=q_B(x)$.
-That is, for $\alpha\in A\cap B$
-              \[
-                \alpha\in\dom(q_A)\setminus(\dom(p_A)\cup\dom(p_B))
-                \Rightarrow
-                \alpha\in\dom(q_B) \text{ and } q_A(x)=q_B(x)
-              \]
-          \end{itemize}
-  \end{defn}
-
-  \begin{lem}
-    $\pok$ has property $K$ (and thus is c.c.c.). That is, let $P\subseteq\pok$ be uncountable: there is an uncountable $Q\subseteq P$ such that points in $Q$ are pairwise compatible.
-  \end{lem}
-
-  \begin{proof}
-    If $|\{\dom(p):p\in P\}|>\omega$, we will use the $\Delta$-system lemma to find an uncountable $P'\subseteq P$ such that for $p,q\in P'$, $\dom(p)\cap\dom(q)=\mc R$.
-Otherwise, we may fix an uncountable $P'\subseteq P$ such that for $p,q\in P'$, $\dom(p)=\dom(q)=\mc R$.
-
-    Similarly, for each $A\in\mc{R}$ we may find that $|\{\dom(p_A):p\in P'\}|>\omega$, and we can use the $\Delta$-system lemma to find an uncountable $P''\subseteq P'$ where $\dom(p_A)\cap\dom(q_A)=A'$ for all $p,q\in P''$, or otherwise we may find $P''\subseteq P'$ where $\dom(p_A)=\dom(q_A)=A'$ for all $p,q\in P''$.
-
-    Finally, for each $A\in\mc R$ and $\alpha\in A'$, we may find $n_{A,\alpha}$ such that there are uncountable $p\in P''$ with $p_A(\alpha)=n_{A,\alpha}$, and thus we may choose $Q\subseteq P''$ to be an uncountable collection such that for $p,q\in Q$, $p_A=q_A$ for $A\in\mc R$.
-
-    Then it is easily verified that $p\cup q\in\pok$ and $p\cup q\leq p,q$ for all $p,q\in Q$.
-  \end{proof}
-
-  \begin{prop}
-    For $A\in[\kappa]^\omega$ and $\alpha\in A$, the sets 
-      \[
-        D_A = \{p\in\pok: A\in\dom(p)\}
-      \]
-      \[
-        D_{A,\alpha} = \{p\in\pok: A\in\dom(p), \alpha\in\dom(p_A)\}
-      \]
-    are dense in $\pok$.
-  \end{prop}
-
-  \begin{proof}
-    Let $A\in[\kappa]^\omega$ and $p\in\pok$. Either $p'=p\in D_A$, or $p'=p\cup\{\<A,\emptyset\>\}\in D_A$ with $p'\leq p$.
-
-    Let $\alpha\in A$.
-Either $p''=p'\in D_{A,\alpha}$, or we may find $n<\omega$ not in the range of $p'_A$, and then $p''=p'\setminus\{\<A,p'_A\>\}\cup\{\<A,p'_A\cup\{\<\alpha,n\>\}\>\} \in D_{A,\alpha}$ with $p''\leq p'\leq p$.
-  \end{proof}
-
-  \begin{thm}
-    $S(\kappa,\omega,\omega)+(\kappa=2^\omega)$ is consistent with ZFC for any cardinal $\kappa$ with $cf(\kappa)>\omega$.
-  \end{thm}
-
-  \begin{proof}
-    We adapt a forcing argument due to Scheepers.
-Let $M$ be a countable transitive submodel of ZFC.
-Consider the c.c.c.
-poset $\pok$ realized in the model $M$.
-Let $G$ be a $\pok$-generic filter over $M$.
-
-    We now work in the smallest model $M[G]$ extending $M$ and containing $G$. Observe that by (Kunen), $M[G]$ preserves cofinalities and cardinals.
-
-    For each $A\in [\kappa]^\omega$, note $[\kappa]^\omega\cap M$ is cofinal in $[\kappa]^\omega$, so let $A'\supseteq A$ be in $[\kappa]^\omega\cap M$ and let $f_A=\bigcup_{p\in G\cap D_{A'}}p_{A'}\rest A$.
-Since $G$ is a $\pok$-generic filter over $M$, it is easily verified (considering the dense sets $D_{A,\alpha}$) that $f_A$ is an injective function from $A$ into $\omega$.
-
-    In addition, for $A,B\in [\kappa]^\omega\cap M$, let $p\in G\cap D_A\cap D_B$.
-For all $q\leq p$ it follows that $\{\alpha\in \dom(q_A)\cap \dom(q_B): q_A(\alpha)\not= q_B(\alpha)\} \subseteq \dom(p_A)\cup\dom(p_B)$.
-Thus $|\{\alpha\in A\cap B: f_A(\alpha)\not= f_B(\alpha)\}|<\omega$ and $f_A\alcomp f_B$ for $A,B\in [\kappa]^\omega\cap M$, and it's immediate that $f_A\alcomp f_B$ for $A,B\in[\kappa]^\omega$ as well.
-
-    The $f_A$ witness $S(\kappa,\omega,\omega)$. Since $\kappa\geq 2^\omega$ by $\pok$ c.c.c., and $S(\kappa,\omega,\omega)$ is a contradiction for $\kappa>2^\omega$, we know $\kappa=2^\omega$. 
-  \end{proof}
-
-  \begin{cor}
-    For each $\kappa$, $F\kmarkwin{2}\mengame{\oneptlind{\kappa}}$ is consistent with ZFC.
-  \end{cor}
-
-\newpage
-
-  \centerline{Alster, Hurewicz}
-
-  Besides various limited information characterizations of $\mengame{X}$, there are other interesting covering properties between $\sigma$-(relatively compact) and Menger.
-
-  \begin{defn}
-    A colleciton of subsets of a space $X$ is (\textbf{really}) \textbf{ample} if has a finite subcover for each (relatively) compact subset of $X$.
-  \end{defn}
-
-  \begin{prop}
-    Every ample cover of a regular space $X$ is really ample.
-  \end{prop}
-
-  \begin{proof}
-    Every relatively compact set $R$ is a subset of the compact set $\overline{R}$.
-  \end{proof}
-
-  \begin{defn}
-    A space $X$ is (\textbf{relatively}) \textbf{Alster} if there exists a countable subcover for each (really) ample cover of $X$ by $G_\delta$ sets.
-  \end{defn}
-
-  \begin{prop}
-    Every regular relatively Alster space is Alster.
+  If a selective ultrafilter $\mathcal{F}$ exists (independent of ZFC),
+  then $K \not\prewin \lfkpgame{X}$
+  for $X=\omega \cup \{\mathcal{F}\}\subset \beta\omega$.
 \end{prop}
@@
 \begin{thm}
-    $X$ $\sigma$-compact $\Rightarrow$ $X$ Alster $\Rightarrow$ $X$ Menger
+  Then there is an ultrafilter $\mathcal{F}$ such that
+  then $K \prewin \lfkpgame{X}$ and $K \tactwin \lfkpgame{X}$
+  for $X=\omega \cup \{\mathcal{F}\}\subset \beta\omega$.
 \end{thm}
 
-  \begin{proof}
-    Due to Leandro F. Aurichi and Franklin D. Tall in ``Lindel\"of spaces which are indestructible, productive, or D''.
-  \end{proof}
+\begin{thm}
+  Let $M$ be the \term{metric fan}, a non-locally compact $k$ space.
+  Then $P \win \lfkpgame{M}$.
+\end{thm}
+
+\begin{thm}
+  Let $S$ be the \term{sequential fan}, a non-locally compact $k$ space.
+  Then $K \prewin \lfkpgame{S}$ and $K\tactwin \lfkpgame{S}$.
+\end{thm}
+
+(TODO: Maybe consider claim
+$K \prewin \lfkpgame{X}$ $\Rightarrow$ $X$ is a $k$-space)
+
+\section{Cantor tree space example}
+
+\begin{ex}
+  Let $X$ be a zero-dimensional, compact L-space
+  (hereditarally Lindeloff and non-separable).
+  It is a fact that there exists a point-countable collection
+  $\mathcal{U}=\{U_\alpha : \alpha<\omega_1\}$ of clopen sets in $X$, and it is
+  also true that any point-finite subcollection of $\mathcal{U}$ is countable.
+
+  Let $C = \{c_\alpha : \alpha <\omega_1\}$ be any uncountable subset of the
+  Cantor space $2^\omega$. Let $X_s = X \times \{s\}$ for each
+  $s \in 2^{<\omega}$, and $U_{\alpha,s} = U_\alpha \times \{s\}$.
+
+  Finally, let \[\mathbb{X} = C \cup \bigcup_{s\in 2^{<\omega}} X_s\] be a
+  tree of $2^{<\omega}$ copies of $X$, and where
+  \[c_\alpha \cup \bigcup_{n < \omega} U_{\alpha, x_\alpha \restriction n}\]
+  is an open set about each $c_\alpha$.
+\end{ex}
 
 \begin{prop}
-    $X$ $\sigma$-(relatively compact) $\Rightarrow$ $X$ relatively Alster $\Rightarrow$ $X$ Menger
+$K \win \lfkpgame{\mathbb{X}}$.
 \end{prop}
 
-  \begin{proof}
-    If $X$ is $\sigma$-(relatively compact), then there exists a countable subcover for every really ample cover of $X$ by arbitrary sets.
-
-    If $X$ is relatively Alster, we adapt Aurichi and Tall's argument for the previous theorem.
-
-    Since relatively Alster implies Lindel\"of (all open covers of $X$ are relatively ample by definition of relatively compact), it is sufficient to consider open covers $\mc U_n = \{ U_n^m : m<\omega\}$ such that $U_n^m\subseteq U_n^{m+1}$.
-Then $\mc G=\{\bigcap_{n<\omega} U_n^{f(n)} : f\in \omega^\omega\}$ is a $G_\delta$ cover.
-To see that $\mc G$ is relatively ample, note for each relatively compact $K$ in $X$, $K$ is covered by something in each $\mc U_n$, and thus there is $f_K(n)\in\omega^\omega$ such that $K\subseteq \bigcap_{n<\omega} U_n^{f_K(n)}$.
-
-    By relatively Alster, let $f_m\in\omega^\omega$ for $m<\omega$ so that $\mc G'=\{\bigcap_{n<\omega} U_n^{f_m(n)}:m<\omega\}$ covers $X$.
-
-    Then let $\mc F_n = \{U_n^{f_m(n)}:m\leq n\}\in[\mc U_n]^{<\omega}$.
-Note that if $x\in X$, then $x\in \bigcap_{n<\omega} U_n^{f_{m_x}(n)}$ for some $m_x<\omega$ as $\mc G'$ is a cover.
-Thus $x\in U_{m_x}^{f_{m_x}(m_x)}$ and is covered by $\mc F_{m_x}$.
-  \end{proof}
-
-  \begin{ex}
-    Let the real numbers $R$ be given the topology generated by open intervals with countable sets removed.
-$R$ is not relatively Alster and $F\win\mengame{R}$.
-If $S(2^\omega,\omega,\omega)$ holds, then $F\kmarkwin{2}\mengame{R}$.
-  \end{ex}
-
-  \begin{proof}
-    Since points are $G_\delta$ and its relatively compact sets are all finite, a cover by singletons is really ample and has no countable subcover, showing $R$ is not relatively Alster.
-
-    It was proven earlier that $F\win\mengame{R}$. Assuming $S(2^\omega,\omega,\omega)$, we construct a $2$-Mark\"ov strategy by first defining the following:
-      \begin{itemize}
-        \item Let $z_n$ enumerate the integers for $n<\omega$.
-        \item For each open cover $\mc V$ of $R$, let $A(\mc V)$ be a countable set such that $[z_n,z_n+1)\setminus A(V)$ is $\mc V$-compact for each $n<\omega$.
-        \item Let $f_A:A\to\omega$ for $A\subseteq R$ witness $S(2^\omega,\omega,\omega)$.
-      \end{itemize}
-
-    Then we may define $\sigma(\mc U_0,0)=\emptyset$ and define $\sigma(\mc U_n,\mc U_{n+1},n+1)$ such that it covers each of the following:
-      \[
-        \left(\bigcup_{m\leq n} [z_m,z_m+1)\right) \setminus A(\mc U_{n+1})
-      \]
-      \[
-        \{f_{A(\mc U_{n+1})}^{-1}(m) : m\leq n\}
-      \]
-      \[
-        \{x \in A(\mc U_n)\cap A(\mc U_{n+1}) : f_{A(\mc U_{n})}(x)\not= f_{A(\mc U_{n+1})}(x)\}
-      \]
-
-    For any attack $\mc U_0,\mc U_1,\dots$ on $\sigma$, let $x\in[z_n,z_n+1)$. 
-      \begin{itemize}
-        \item If $x\not\in A(\mc U_{n+1})$, then $x$ is covered in round $n+1$.
-        \item If $x\in A(\mc U_{n+1})$, let $N=f_{A(\mc U_{n+1})}(x)$. 
-        \begin{itemize}
-          \item If $N\leq n$, then $x$ is covered in round $n+1$.
-          \item If $N>n$ and $N=f_{A(\mc U_{p+1})}(x)$ for all $p\geq n$, then $x$ is covered in round $N$.
-          \item If $N>n$ and $N\not=f_{A(\mc U_{p+1})}(x)$ for some $p>n$, then $x$ is covered in round $p+1$.
-        \end{itemize}
-      \end{itemize}
-  \end{proof}
-
-  \begin{defn}
-    A space $X$ is \textbf{Hurewicz} if for each sequence of open covers $\mc U_n$, there are $\mc F_n \in [\mc U_n]^{<\omega}$ such that $X=\bigcup_{m<\omega}\bigcap_{m\leq n<\omega}\cup\mc F_n$.
-  \end{defn}
-
-\newpage
-
-  \centerline{Filling Games}
-
-  \begin{defn}
-    The \textbf{filling game} $\fillgame{J}$ on an ideal $J$ proceeds as follows: player $M$ chooses $M_0 \in \<J\>$, the $\sigma$-completion of $J$, in the initial round, followed by $N$ choosing $N_0\in J$.
-In round $n+1$, player $M$ chooses $M_{n+1}$ where $M_n\subseteq M_{n+1}\in\<J\>$, and player $N$ replies with $N_{n+1}\in J$.
-Player $N$ wins the game if $\bigcup_{n<\omega} N_n \supseteq \bigcup_{n<\omega} M_n$.
-(The sets in $J$ and $\<J\>$ are thought of as nowhere-dense and meager sets, respectively.)
-
-    The \textbf{strict filling game} $\sfillgame{J}$ proceeds analogously, with the added requirement that $M_n\subsetneq M_{n+1}$. This game has been studied by Scheepers.
-  \end{defn}
+\begin{thm}(cor of G, game-theoretic proof by me)
+$K\not\tactwin\lfkpgame{\mathbb{X}}$.
+\end{thm}
 
 \begin{thm}
-    $N\ktactwin{2}\sfillgame{J} \Rightarrow N\kmarkwin{2}\fillgame{J}$
+$K\not\ktactwin{k}\lfkpgame{\mathbb{X}}$.
 \end{thm}
-
-  \begin{proof}
-    Enumerate the sets in $J$ as $A_\alpha$ for $\alpha<|J|$. For $M\in \<J\>$ and $n<\omega$, let $M+0=M$ and $M+n+1$ be the union of $M+n$ and the least $A_\alpha$ not contained in $M+n$.
-
-    Let $\sigma$ be a winning $2$-tactical strategy for $N$ in $\sfillgame{\kappa}$, and assume $\sigma(M)\cup\sigma(M')\subseteq\sigma(M,M')$.
-
-    We define a $2$-Markov strategy $\tau$ for $F$ in $\fillgame{\kappa}$ as follows:
-
-      \[
-        \tau(M_0,0) = \sigma(M_0)
-      \]
-      \[
-        \tau(M_{n},M_{n+1},n+1) = \left\{
-          \begin{array}{ll}
-            \sigma(M_{n},M_{n+1}) & \text{if } M_n\subsetneq M_{n+1} \\
-            \bigcup_{m\leq n}\sigma(M_n+m,M_{n+1}+m+1) & \text{otherwise}
-          \end{array}
-        \right.
-      \]
-
-    Let $M_0 \subseteq M_1 \subseteq \dots$ be an attack by $C$ against $\tau$. There are two possible cases:
-
-      \begin{itemize}
-        \item
-          Assume $M_n=M_N$ for all $n\geq N$.
-
-          The collection produced by $\sigma$ versus the attack
-            \[
-              M_N+0 \subsetneq M_N+1 \subsetneq \dots
-            \] 
-          must cover $M_N$ as $\sigma$ is a winning strategy.
-
-          Let $x \in M_N$. If $x\in\sigma(M_N+0)$, then $x$ will be covered in round $N+1$ by 
-            \[
-              \tau(M_N,M_N,N+1)
-              \supseteq \sigma(M_N+0,M_N+1)
-              \supseteq \sigma(M_N+0)
-            \]
-
-          Otherwise, $x\in\sigma(M_N+n,M_N+n+1)$, and $x$ will be covered in round $N+n+1$ by 
-            \[
-              \tau(M_N,M_N,N+n+1)
-              \supseteq \sigma(M_N+n,M_N+n+1)
-            \]
-
-        \item
-          Otherwise we may find $0<f(0)<f(1)<\dots$ such that $M_{f(n)}\subsetneq M_{f(n)+1}=M_{f(n+1)}$.
-
-          Then the collection produced by $\sigma$ versus the attack 
-            \[
-              M_{f(0)}\subsetneq M_{f(1)} \subsetneq M_{f(2)} \dots
-            \]
-          must cover $\bigcup_{n<\omega}M_n$ as $\sigma$ is a winning strategy.
-
-          Let $x \in \bigcup_{n<\omega}M_n$. If $x\in\sigma(M_{f(0)})$, then $x$ will be covered by $\tau$ in round $f(0)+1$ by
-            \[
-              \tau(M_{f(0)},M_{f(0)+1},f(0)+1)
-              = \sigma(M_{f(0)},M_{f(0)+1})
-              \supseteq \sigma(M_{f(0)})
-            \]
-
-          Otherwise, $x\in\sigma(M_{f(n)},M_{f(n+1)})$, and $x$ will be covered by $\tau$ in round $f(n)+1$ by
-            \[
-              \tau(M_{f(n)},M_{f(n)+1},f(n)+1)
-              = \sigma(M_{f(n)},M_{f(n)+1})
-              = \sigma(M_{f(n)},M_{f(n+1)})
-            \]
-      \end{itemize}
-
-      Thus $\tau$ is a winning strategy.
-  \end{proof}
-
-  \begin{ex}
-    There is a free ideal $J$ such that $N\not\ktactwin{2}\sfillgame{J}$ but $N\kmarkwin{2}\fillgame{J}$.
-  \end{ex}
-
-  \begin{proof}
-    Result based on ``Meager nowhere dense games'' Prop 9 by Scheepers. Assume $\mathbb{R}$ has the usual Euclidean topology.
-
-    Choose $A\subseteq\mathbb{R}$ such that $|A|=\omega$ and $A$ is meager but not nowhere dense.
-Then choose $V\subseteq\mathbb{R}$ such that $|V|=2^\omega$, $V$ is meager, and $V$ is disjoint from $A$.
-Assume $A=\{a_n:n<\omega\}$.
-
-    Certainly, if $J$ is the collection of nowhere dense subsets of $A\cup V$, then $F\kmarkwin{2}\fillgame{J}$. In fact, since $A\cup V$ is meager, $F\prewin\fillgame{J}$.
-
-    By Prop 9 in Scheeper's paper, $F\not\ktactwin{2}\sfillgame{J}$ immediately. A proof follows: let $\sigma$ be a $2$-tactical strategy such that $\sigma(M)\subseteq\sigma(M,M')$.
-
-    We may define $K_n$ to be the collection of pairs of comparable sets $\{B,C\}$ such that $B\subsetneq C$ and $n$ is the least integer where $a_n \in A \setminus \sigma(A\cup B,A\cup C)$.
-
-    By Cor 28 of Scheeper's ``A partition relation for partially ordered sets'', for every partition $\{K_n:n<\omega\}$ of the comparable pairs in $[\pow{V}]^2$ there is some $n'<\omega$ and branch $C_0\subsetneq C_1\subsetneq \dots\subsetneq V$ where $\{C_m,C_{m+1}\}\in K_{n'}$ for all $m<\omega$.
-
-    Then $\sigma$ may be countered by the attack $A\cup C_0, A\cup C_1, \dots$, since $a_{n'} \in A \setminus \sigma(A\cup C_m,A\cup C_{m+1})$ for all $m<\omega$ and thus is never covered.
-  \end{proof}
-
-\newpage
-
-  \centerline{Rothberger}
-
-  \begin{defn}
-    $X$ is \textbf{Rothberger} if for all open covers $\mathcal{U}_0,\mathcal{U}_1,\dots$ there exist open sets $U_n\in \mathcal{U}_n$ such that $\{U_n:n<\omega\}$ is a cover of $X$.
-  \end{defn}
-
-  \begin{prop}
-    Rothberger $\Rightarrow$ Menger
-  \end{prop}
-
-  \begin{defn}
-    In the two-player game $\rothgame{X}$ player $C$ chooses open covers $\mathcal{U}_n$ of $X$, followed by player $S$ choosing an open set $U_n\in\mathcal{U}_n$.
-$S$ wins if $\{U_n:n<\omega\}$ is a cover of $X$.
-  \end{defn}
-
-  \begin{thm}
-    $X$ is Rothberger if and only if $C\not\win\rothgame{X}$.
-  \end{thm}
-
-  \begin{proof}
-    Due to Pawlikowski
-  \end{proof}
-
-  \begin{defn}
-    A space $X$ is scattered if every subspace contains an isolated point.
-By convention, $\ds X = \bigcup_{\alpha<\rank(X)}X^\alpha$ where $X^\alpha$ is the set of isolated points of $\ds X\setminus\bigcup_{\beta<\alpha}X^\beta$.
-  \end{defn}
-
-  \begin{prop}
-    A space $X$ is scattered if and only if every closed subspace contains an isolated point.
-  \end{prop}
-
-  \begin{prop}
-    The rank of a compact scattered $T_1$ space is a successor ordinal, and $X^{\rank(X)-1}$ is finite.
-  \end{prop}
-
-  \begin{proof}
-    Suppose that the rank of $X$ was a limit ordinal $\beta$.
-Then by choosing $\beta_n\to\beta$, we may pick a point $x_n\in X^{\beta_n}$, and $\{x_n: n<\omega\}$ may be shown to be a closed discrete subspace of $X$.
-
-    It's easily seen that $X^{\rank(X)-1}$ must be finite - it is a closed discrete subspace of compact $X$.
-  \end{proof}
-
-  \begin{thm}
-    The following are equivalent for compact $T_2$ $X$:
-      \begin{enumerate}[(a)]
-        \item $X$ is Rothberger
-        \item $X$ is scattered
-        \item $S\win\rothgame{X}$
-        \item $C\not\win\rothgame{X}$
-      \end{enumerate}
-  \end{thm}
-
-  \begin{proof}
-    To show $(a)\Rightarrow(b)$, we use Aurichi's proof in \textit{D-Spaces}: suppose $X$ has a closed subspace without isolated points.
-Then it is compact and contains a closed copy of the Cantor set, which is not Rothberger, contradiction.
-
-    To show $(b)\Rightarrow(c)$, if $X$ is scattered, suppose during a particular round $n$, player $S$ observes that the uncovered subspace $Y \subseteq X$ is nonempty.
-Then as $Y$ is also compact scattered,  select one of the finite points in $Y^{\rank(Y)-1}$, label it $x_n$, and choose an open set containing $x_n$ from the given cover.
-
-    We claim that if $S$ follows this strategy, player $S$ will observe that the uncovered subspace $Y\subseteq X$ is empty during some round.
-If not, consider the $x_n$ chosen by $Y$ by the end of the game - the rank of each point within $X$ is nonincreasing, and does not contain a constant final sequence, contradiction.
-
-    Of course, $(c)\Rightarrow(a)$ is trivial, and $(a)\Leftrightarrow(d)$.
-  \end{proof}
-
-  \begin{defn}
-    In the two-player game $\altrothgame{X}$ player $P$ chooses points $x_n\in X$, followed by player $O$ choosing an open neighborhood $U_n$ of $x_n$.
-$P$ wins if $\{U_n:n<\omega\}$ is a cover of $X$.
-  \end{defn}
-
-  \begin{thm} $\altrothgame{X}$ is ``perfect information equivalent'' to $\rothgame{X}$. That is:
-
-    \begin{itemize}
-      \item $P\win\altrothgame{X}$ if and only if $S\win\rothgame{X}$
-      \item $O\win\altrothgame{X}$ if and only if $C\win\rothgame{X}$.
-    \end{itemize}
-  \end{thm}
-
-  \begin{proof}
-    Due to Galvin.
-
-    \begin{itemize}
-      \item
-      Let $\sigma$ be a strategy for $S$ in $\rothgame{X}$.
-
-      Let $n<\omega$, and consider open covers $\mc{U}_m$ for each $m<n$.
-Suppose that for each $x\in X$, there was an open neighborhood $U_x$ of $x$ where for every open cover $\mc U$, $\sigma(\mc U_0,\dots,\mc U_{n-1},\mc U)\not=U_x$.
-The open cover $\{U_x : x\in X\}$ demonstrates the contradiction.
-
-      We define a strategy for $P$ in $\altrothgame{X}$ as follows: during round $n$, $P$ chooses a point $x_n$ for which every open neighborhood is of the form $U_n = \sigma(\mc U_0,\dots,\mc U_{n-1},\mc{U}_n)$ for some open cover $\mc{U}_0$.
-
-      If $\sigma$ was a winning strategy for $S$ in $\rothgame{X}$, then the open sets chosen by $O$ in response to $P$'s strategy for $\altrothgame{X}$ are of the form $\{\sigma(\mc U_0),\sigma(\mc U_0,\mc U_1),\dots\}$ and are an open cover of $X$.
-
-      \item
-      Let $\sigma$ be a strategy for $P$ in $\altrothgame{X}$.
-
-      We define a strategy for $S$ in $\rothgame{X}$ as follows: during round $n$, if $S$ has chosen $U_0,\dots,U_{n-1}$ in previous rounds, $S$ chooses any open set in $C$'s latest cover containing the point $\sigma(U_0,\dots,U_{n-1})$.
-If $\sigma$ was a winning strategy for $P$, then for any open sets $U_0,U_1,\dots$ containing $\sigma(\cdot),\sigma(U_0),\dots$, the collection $\{U_0,U_1,\dots\}$ is a cover for $X$.
-
-      \item
-      Let $\sigma$ be a strategy for $C$ in $\rothgame{X}$.
-
-      We define a strategy for $O$ in $\altrothgame{X}$ as follows: during round $n$, if $O$ has chosen $U_0,\dots,U_{n-1}$ in previous rounds, $O$ chooses an open set from the cover $\sigma(U_0,\dots,U_{n-1})$ containing the point chosen by $P$ that round.
-If $\sigma$ was a winning strategy for $C$, then for any open sets $U_0,U_1,\dots$ from the covers $\sigma(\cdot),\sigma(U_0),\dots$, the collection $\{U_0,U_1,\dots\}$ is not a cover for $X$.
-
-      \item
-      Let $\sigma$ be a strategy for $O$ in $\altrothgame{X}$.
-
-      We define a strategy for $C$ in $\rothgame{X}$ as follows: during round $0$, $C$ chooses $\mc{U}_0 = \{\sigma(x) : x\in X\}$.
-In response, $S$ chooses some $\sigma(x_0)$.
-During round $n+1$, if $S$ has chosen $\sigma(x_0),\dots,\sigma(x_0,\dots,x_n)$ in previous rounds, $C$ chooses $\mc{U}_{n+1} = \{\sigma(x_0,\dots,x_n,x) : x\in X\}$.
-If $\sigma$ was a winning strategy for $O$, then $\{\sigma(x_0),\sigma(x_0,x_1),\dots\}$ is not a cover for $X$.
-
-    \end{itemize}
-  \end{proof}
-
-  A similar theorem exists for limited information strategies.
-
-  \begin{thm}
-    \begin{itemize}
-      \item $P\prewin\altrothgame{X}$ if and only if $S\markwin\rothgame{X}$
-      \item $O\markwin\altrothgame{X}$ if and only if $C\prewin\rothgame{X}$.
-    \end{itemize}
-  \end{thm}
-
-  \begin{proof}
-
-    \begin{itemize}
-      \item
-      Let $\sigma(\mc U_n,n)$ be a Markov strategy for $S$ in $\rothgame{X}$.
-
-      Let $n<\omega$.
-Suppose that for each $x\in X$, there was an open neighborhood $U_x$ of $x$ where for every open cover $\mc U$, $\sigma(\mc U,n)\not=U_x$.
-The open cover $\{U_x : x\in X\}$ demonstrates the contradiction.
-
-      We define a predetermined strategy for $P$ in $\altrothgame{X}$ as follows: during round $n$, $P$ chooses a point $x_n$ for which every open neighborhood is of the form $U_n = \sigma(\mc U,n)$ for some open cover $\mc{U}$.
-
-      If $\sigma$ was a winning strategy for $S$ in $\rothgame{X}$, then the open sets chosen by $O$ in response to $P$'s strategy for $\altrothgame{X}$ are of the form $\{\sigma(\mc U_0,0),\sigma(\mc U_1,1),\dots\}$ and are an open cover of $X$.
-
-      \item
-      Let $\sigma(n)$ be a predetermined strategy for $P$ in $\altrothgame{X}$.
-
-      We define a Markov strategy for $S$ in $\rothgame{X}$ as follows: during round $n$, $S$ chooses any open set in $C$'s cover containing the point $\sigma(n)$.
-If $\sigma$ was a winning strategy for $P$, then for any open sets $U_0,U_1,\dots$ containing $\sigma(0),\sigma(1),\dots$, the collection $\{U_0,U_1,\dots\}$ is a cover for $X$.
-
-      \item
-      Let $\sigma(n)$ be a predetermined strategy for $C$ in $\rothgame{X}$.
-
-      We define a Markov strategy for $O$ in $\altrothgame{X}$ as follows: during round $n$, $O$ chooses an open set from the cover $\sigma(n)$ containing the point chosen by $P$ that round.
-If $\sigma$ was a winning strategy for $C$, then for any open sets $U_0,U_1,\dots$ from the covers $\sigma(0),\sigma(1),\dots$, the collection $\{U_0,U_1,\dots\}$ is not a cover for $X$.
-
-      \item
-      Let $\sigma(x_n,n)$ be a Markov strategy for $O$ in $\altrothgame{X}$.
-
-      We define a predetermined strategy for $C$ in $\rothgame{X}$ as follows: during round $n$, $C$ chooses $\mc{U}_n = \{\sigma(x,n) : x\in X\}$.
-If $\sigma$ was a winning strategy for $O$, we observe any play $\{\sigma(x_0,0),\sigma(x_1,1),\dots\}$ by $S$ is not a cover for $X$.
-
-    \end{itemize}
-
-  \end{proof}
-
-  \begin{defn}
-    Let $\mc{N}(x)$ be the $\textbf{neighborhood network}$ of $x$, that is, the collection of all neighborhoods of $x$.
-  \end{defn}
-
-  \begin{defn}
-    A topological space $X$ is \textbf{almost countable} if there exist $x_n\in X$ for each $n<\omega$ such that $X=\bigcup_{n<\omega}\bigcap\mc{N}(x_n)$.
-  \end{defn}
-
-  \begin{thm}
-    For any space $X$, the following are equivalent:
-    \begin{itemize}
-      \item $S\markwin\rothgame{X}$ 
-      \item $P\prewin\altrothgame{X}$
-      \item $X$ is almost countable
-    \end{itemize}
-  \end{thm}
-
-  \begin{proof}
-    If there exist $x_n\in X$ for each $n<\omega$ such that $X=\bigcup_{n<\omega}\bigcap\mc{N}(x_n)$, then let $\sigma(n)=x_n$ be a predetermined strategy for $P$ in $\altrothgame{X}$.
-For any neighborhoods $O_n$ of $x_n$ chosen by $O$ to attack $\sigma$, note that $\bigcup_{n<\omega}O_n\supseteq\bigcup_{n<\omega}\bigcap\mc{N}(x_n)=X$ results in a win for $P$.
-
-    Likewise, if for each sequence $x_n \in X$ there is $x\in X$ with $x\not\in \bigcup_{n<\omega}\bigcap\mc{N}(x_n)$, then for a fixed strategy $\sigma(n)$ for $P$, $O$ may counter $\sigma$ by choosing $O_n\in\mc{N}(x_n)$ which misses $x$ during each round, causing $\sigma$ to lose.
-  \end{proof}
-
-  \begin{thm}
-    For any $T_1$ space $X$, the following are equivalent:
-    \begin{itemize}
-      \item $S\markwin\rothgame{X}$
-      \item $P\prewin\altrothgame{X}$
-      \item $X$ is almost countable
-      \item $|X|\leq\omega$
-    \end{itemize}
-  \end{thm}
-
-  \begin{proof}
-    If $|X|=\omega$ then the winning Markov strategy is obvious, so let $\sigma(\mc U,n)$ be a Markov strategy.
-
-    Let $n<\omega$.
-Suppose that for each $x\in X$, there was an open neighborhood $U_x$ of $x$ where for every open cover $\mc U$, $\sigma(\mc U,n) \not= U_x$.
-The open cover $\{U_x : x\in X\}$ demonstrates the contradiction.
-
-    So let $x_n\in X$ be chosen such that for each open neighborhood $U$ of $x_n$, there is an open cover $\mc U$ such that $\sigma(\mc U,n)=U$.
-Then if $x\not=\{x_n : n<\omega\}$, $C$ may counter $\sigma$ as follows: during round $n$, choose $U_n$ which contains $x_n$ but not $x$, and then choose $\mc U_n$ such that $\sigma(\mc U_n,n)=U_n$.
-  \end{proof}
-
-  \begin{ex}
-    Let $X=\omega_1\cup\{\infty\}$ be a ``weak Lindel\"ofication'' of discrete $\omega_1$ such that open neighborhoods of $\infty$ contain $\omega_1\setminus\omega$.
-This space is $T_0$ but not $T_1$, and note that $S\markwin\rothgame{X}$ and $|X|>\omega$.
-  \end{ex}
-
-  \begin{thm}
-    The following are equivalent for points-$G_\delta$ $X$:
-      \begin{enumerate}[(a)]
-        \item $S\win\rothgame{X}$
-        \item $P\win\altrothgame{X}$
-        \item $S\kmarkwin{k}\rothgame{X}$ for some $k\geq 1$
-        \item $P\kmarkwin{k}\altrothgame{X}$ for some $k\geq 1$
-        \item $S\markwin\rothgame{X}$
-        \item $P\prewin\altrothgame{X}$
-        \item $X$ is almost countable
-        \item $|X|\leq\omega$
-      \end{enumerate}
-  \end{thm}
-
-  \begin{proof}
-    % $(c)\Rightarrow(b)\Rightarrow(a)$ are all trivial.
-Galvin has shown $(a) \Leftrightarrow P\win\altrothgame{X} \Rightarrow (c)$ in \textit{Indeterminacy}, but a direct proof of $(a)\Rightarrow(c)$ follows.
-
-    Due to Galvin. Let $\sigma$ be a strategy for $S$ in $\rothgame{X}$.
-
-    Let $G_{x,m}$ designate open sets such that $\{x\}=\bigcap_{m<\omega}G_{x,m}$ for all $x\in X$.
-
-    Let $n<\omega$, $s\in\omega^{n}$, and consider open covers $\mc{U}_t$ for each $t\leq s$.
-Suppose that for each $x\in X$, there was an open neighborhood $U_x$ of $x$ where for every open cover $\mc U$, $\sigma(\mc U_{s\rest 1},\dots,\mc U_{s},\mc U)\not=U_x$.
-The open cover $\{U_x : x\in X\}$ demonstrates the contradiction.
-
-    Thus $C$ may find points $x_s$ such that for each $m<\omega$, there exists an open cover $\mc U_{s\concat\<m\>}$ where $\sigma(\mc U_{s\rest 1},\dots,\mc U_{s},\mc U_{s\concat\<m\>})=G_{x_s,m}$.
-Then if $x\not=\{x_s : s\in\omega^{<\omega}\}$, $C$ may counter $\sigma$ as follows: during round $n$, choose $f(n)$ so that $x\not\in G_{x_{f\rest n},f(n)}$, and then choose $\mc U_{f\rest n\concat\<f(n)\>}$ such that $\sigma(\mc U_{f\rest 1},\dots,\mc U_{f\rest n},\mc U_{f\rest n\concat\<f(n)\>})=G_{x_{f\rest n},f(n)}$.
-  \end{proof}
-
-  \begin{cor}
-    The following are equivalent for compact points-$G_\delta$ $X$:
-      \begin{enumerate}[(a)]
-        \item $S\win\rothgame{X}$
-        \item $P\win\altrothgame{X}$
-        \item $S\kmarkwin{k}\rothgame{X}$ for some $k\geq 1$
-        \item $P\kmarkwin{k}\altrothgame{X}$ for some $k\geq 1$
-        \item $S\markwin\rothgame{X}$
-        \item $P\prewin\altrothgame{X}$
-        \item $X$ is almost countable
-        \item $|X|\leq\omega$
-        \item $C\not\win\rothgame{X}$
-        \item $O\not\win\altrothgame{X}$
-        \item $X$ is Rothberger
-        \item $X$ is scattered
-      \end{enumerate}
-  \end{cor}
-
-  \begin{defn}
-    The game $\recallgame{m}{\kappa}$ proceeds as follows: during round $0$, player $F$ chooses $F_0\in[\kappa]^m$, followed by player $S$ choosing $x_0\in F_0\cup\{\infty\}$.
-During round $n+1$, $F$ chooses $F_{n+1}\in[\kappa]^{m^{n+2}}$ such that $F_{n+1}\supset F_n$, followed by $S$ choosing $x_{n+1}\in F_{n+1}\cup\{\infty\}$.
-
-    $S$ wins the game if $\{x_n : n<\omega\}\supseteq F_0\cup\{\infty\}$, and $F$ wins otherwise.
-  \end{defn}
-
-  \begin{prop}
-    $S\limitwin\rothgame{\oneptlind{\kappa}} \Rightarrow S\limitwin\recallgame{m}{\kappa}$
-  \end{prop}
-
-  \begin{proof}
-    Let $\sigma$ be a limited information strategy for $S$ in $\rothgame{\oneptlind{\kappa}}$.
-
-    Suppose $C(\cdot)$ converts any finite set $G$ played by $F$ in $\recallgame{m}{\kappa}$ into the open cover $\mc{U}_G=[G]^1\cup\{\oneptcomp{\kappa}\setminus G\}$.
-Then we may define a strategy $\tau$ using the same type of information as $\sigma$ by setting $\tau(\cdot)\in\sigma(C(\cdot))$.
-
-    Suppose that the attack $F_0, F_1, \dots$ countered $\tau$. Let $x_n$ be the point given by $\tau$ during round $n$, and choose $\alpha\in (F_0\cup\{\infty\})\setminus \{x_n : n<\omega \}$.
-
-    If $\alpha=\infty$, then $\sigma$ may be countered by the attack $\mc{U}_{F_0}, \mc{U}_{F_1}, \dots$ since no neighborhood of $\infty$ is ever chosen.
-
-    Similarly, if $\alpha\in F_0$, then $\sigma$ may also be countered by the attack $\mc{U}_{F_0}, \mc{U}_{F_1}, \dots$ since the singleton $\{\alpha\}$ is never chosen.
-  \end{proof}
-
-  \begin{prop}
-    $S\kmarkwin{k}\recallgame{m}{\kappa} \Leftrightarrow S\ktactwin{k}\recallgame{m}{\kappa}$
-  \end{prop}
-
-  \begin{proof}
-    The round number is deterimined by the size of the sets played by $C$.
-  \end{proof}

### 2014-05-14 miscellaneous/unorganized/baker_game.tex
Baker game notes

\input{../../header.tex}

\usepackage{hyperref}

\begin{document}

\textbf{Notes on an example due to Baker}

In \cite{baker}, the author defines a game played on the unit interval.

\begin{game}
  Let $G(X,J)$ denote a game with players $\pl A$ and $\pl B$.

  In round 0, $\pl A$ chooses a number $a_0$ such that $0\leq a_0\leq 1$, 
  followed by $\pl B$ choosing a number $b_0$ such that $a_0<b_0\leq 1$.

  In round $n+1$, $\pl A$ chooses a number $a_{n+1}$ such that 
  $a_n<a_{n+1}< b_n$, followed by $\pl B$ choosing a number $b_{n+1}$ such
  that $a_{n+1}< b_{n+1}<b_n$.

  $\pl A$ wins the game if $\lim_{n\to\infty}a_n\in X$, and $\pl B$ wins
  otherwise.
\end{game}

The game is strongly related to one formulation of the Banach-Mazur game
played upon the unit interval, which has been extensively studied
\cite{telgarsky}.

\begin{game}
  Let $M(X,J)$ denote the Banach-Mazur interval game with players $\pl A$ and
  $\pl B$.

  In round 0, $\pl A$ chooses a closed interval $I_0\subseteq J=[0,1]$,
  followed by $\pl B$ choosing a closed interval $J_0\subseteq I_0$.

  In round $n+1$, $\pl A$ chooses a closed interval $I_{n+1}\subseteq J_n$,
  followed by $\pl B$ choosing a closed interval $J_{n+1}\subseteq I_{n+1}$.
\end{game}

The author of \cite{baker} asks if there is a set $X$ such that $G(X,J)$ is
indetermined: neither $\pl A$ nor $\pl B$ have a winning strategy.

We show that such a set would also make $MB(X,J)$ indeteremined.

\begin{theorem}
  $\pl A\win MB(X,J) \Rightarrow \pl A\win G(X,J)$ and
  $\pl B\win MB(X,J) \Rightarrow \pl B\win G(X,J)$.
  (Thus if $MB(X,J)$ is determined, then $G(X,J)$ is determined.)
\end{theorem}

\begin{proof}
  First let $\sigma$ witness $\pl A\win MB(X,J)$. We define the strategy $\tau$
  for $\pl A$ in $G(X,J)$ like so:
    \[
      a_0 = \tau(\emptyset) = \inf(\sigma(\emptyset))
    \]
    \[
      a_{n+1} = \tau(\<b_0,\dots,b_n\>) 
        = 
      \inf\left(\sigma\left(\left\<
        \left[\frac{2a_0+b_0}{3},\frac{a_0+2b_0}{3}\right],
        \dots,
        \left[\frac{2a_n+b_n}{3},\frac{a_n+2b_n}{3}\right]
      \right\>\right)\right)
    \]

  It is easily seen that
    $
      \bigcap_{n<\omega}
      [\frac{2a_n+b_n}{3},\frac{a_n+2b_n}{3}]
        =
      \{x\}
    $
  and $x\in X$ since $\sigma$ is a winning strategy.
  Thus $\lim_{n\to\infty}a_n=x$ and $\pl A\win G(X,J)$.

  If $\sigma$ now witnesses $\pl B\win MB(X,J)$, then a similar argument shows
  that
    \[
      b_n = \tau(\<b_0,\dots,b_n\>) 
        = 
      \inf\left(\sigma\left(\left\<
        \left[\frac{2a_0+b_0}{3},\frac{a_0+2b_0}{3}\right],
        \dots,
        \left[\frac{2a_n+b_n}{3},\frac{a_n+2b_n}{3}\right]
      \right\>\right)\right)
    \]
  defines a winning strategy for $\pl B$ in $G(X,J)$.
\end{proof}

\begin{corollary}
  If $X$ is Baire, then $G(X,J)$ is determined.
\end{corollary}

\begin{proof}
  If $X$ is a Baire subset of a Polish space, then $MB(X,J)$ is determined.
\end{proof}

\newpage

\begin{thebibliography}{9}

\bibitem{baker}
  Baker, M. H.,
  \emph{Uncountable sets and an inﬁnite real number game}.
  \url{http://arxiv.org/pdf/math/0606253.pdf}
  2006.

\bibitem{telgarsky}
  Telgarksy, R.,
  \emph{Topological games: On the 50th anniversary of the Banach-Mazur game}.
  \url{http://www.telgarsky.com/1987-RMJM-Telgarsky-Topological-Games.pdf}
  1987.

\end{thebibliography}

\end{document}

### 2014-05-14 phd/dissertation/_raw_chapter4.tex

@@
 
-\chapter{Locally Finite Games}
+\chapter{Proximal Game}
 
-Results pertaining to the Locally Finite game related to the W games.
+Results pertaining to Bell's proximal game for uniform spaces.
 
-\section{basic results}
+\section{cut-and-paste}
+
+\begin{defn}
+  A \textbf{uniform space} $\<X,\mc D\>$ is a set $X$ paired with a filter $\mc D$ (called its \textbf{uniformity}) of relations (called \textbf{entourages}) on $X$ such that for each entourage $D\in \mc D$:
+    \begin{itemize}
+      \item $D$ is reflexive, i.e., the diagonal $\Delta\subseteq D$.
+      \item Its inverse $D^{-1}=\{\<y,x\>:\<x,y\>\in D\}\in \mc D$.
+      \item There exists $\frac{1}{2}D\in\mc D$ such that 
+        \[
+          2(\frac{1}{2}D)=\frac{1}{2}D\circ\frac{1}{2}D=\{\<x,z\>:\exists y(\<x,y\>,\<y,z\>\in\frac{1}{2}D)\}\subseteq D
+        \]
+    \end{itemize}
+  Note that since $\mc D$ is a filter, for each $D\in\mc D$, the symmetric relation $D\cap D^{-1}\in \mc D$.
+\end{defn}
+
+\begin{prop}
+For each $D\in\mc D$ and $n<\omega$ there exists $\frac{1}{2^{n+1}}D\in\mc D$ such that 
+  \[2(\frac{1}{2^{n+1}}D)=\frac{1}{2^{n+1}}D\circ \frac{1}{2^{n+1}}D\subseteq \frac{1}{2^{n}}D\]
+and if $2E\subseteq \frac{1}{2^{n}}D$, then $E\subseteq \frac{1}{2^{n+1}}D$.
+\end{prop}
+
+\begin{defn}
+  For an entourage $D\in\mc D$, let $D[x]=\{y:(x,y)\in D\}$ be the \textbf{$D$-neighborhood} of $x$.
+The \text{uniform topology} for a uniform space $\<X,\mc D\>$ is generated by the base $\{D[x]:x\in X,D\in\mc D\}$.
+\end{defn}
 
 \begin{thm}
-The following are equivalent for a locally compact space $X$:
-    \begin{itemize}
-    \item $X$ is paracompact
-    \item $K \uparrow G_{K,L}(X)$.
-    \end{itemize}
+  A space $X$ is uniformizable (its topology is the uniform topology for some uniformity) if and only if $X$ is completely regular ($T_{3\frac{1}{2}}$).
 \end{thm}
 
-However, often it is the presence of ``limited information'' strategies which can characterize interesting properties of a space.
+\begin{prop}
+  If $X$ is a uniform space, then for all $x\in X$ and symmetric entourages $D$:
+    \[
+      x\in \frac{1}{2}D[y]\text{ and } y\in\frac{1}{2}D[z] \Rightarrow x\in D[z]
+    \]
+  and
+    \[
+      \frac{1}{2}D[x]\subseteq \cl{\frac{1}{2}D[x]}\subseteq D[x]
+    \]
+\end{prop}
+
+\begin{proof}
+  The first is by definition of $\frac{1}{2}D$.
+
+  If $z\in \cl{\frac{1}{2}D[x]}$, it follows that there is $y\in \frac{1}{2}D[x]\cap\frac{1}{2}D[z]$ since $\frac{1}{2}D[z]$ is an open neighborhood of $z$.
+Thus $(x,z)\in D \Rightarrow z\in D[x] \Rightarrow \cl{\frac{1}{2}D[x]}\subseteq D[x]$.
+\end{proof}
 
 \begin{defn}
-A \textbf{limited information strategy} for a game is a function whose domain is restricted to less information than all previous moves by the opposing player.
-\end{defn}
+  For a uniform space $X$, Bell's proximity game proceeds as follows.
 
-In the above mentioned paper, Gruenhage used the following limited information strategies to prove some interesting characterizations based on the game $G_{K,P}(X)$.
+  In round $0$, $\pl D$ chooses an entourage $D_0$, followed by $\pl P$ choosing a point $p_0\in X$.
 
-\begin{defn}
-A \textbf{tactical strategy} considers only the most recent move by the opposing player. If Player $Z$ has a winning tactical strategy for a game $G$, this may be denoted $Z \uparrow_{\text{tact}} G$.
+  In round $n+1$, $\pl D$ chooses an entourage $D_{n+1}\subseteq D_n$, followed by $\pl P$ choosing a point $p_{n+1}\in 4D_n[p_n]$.
+
+  Player $\pl D$ wins if either $\bigcap_{n<\omega} 4D_n[p_n] = \emptyset$ or $\<p_0,p_1,\dots\>$ converges.
 \end{defn}
@@
 \begin{defn}
-A \textbf{Markov strategy} considers only the most recent move by the opposing player and the turn number.
-If Player $Z$ has a winning Markov strategy for a game $G$, this may be denoted $Z \uparrow_{\text{mark}} G$.
+  For a uniform space $X$, the simplified proximal game $\proxgame{X}$ can be defined as follows:
+
+  In round $0$, $\pl D$ chooses a symmetric entourage $D_0$, followed by $\pl P$ choosing a point $p_0\in X$.
+
+  In round $n+1$, $\pl D$ chooses a symmetric entourage $D_{n+1}$, followed by $\pl P$ choosing a point $p_{n+1}\in\left(\bigcap_{m\leq n}D_m\right)[p_n]$.
+
+  Player $\pl D$ wins if either $\bigcap_{n<\omega}\left(\bigcap_{m\leq n} D_m\right)[p_n]=\emptyset$ or $\<p_0,p_1,\dots\>$ converges.
 \end{defn}
@@
 \begin{thm}
-The following are equivalent for a locally compact space $X$:
-    \begin{itemize}
-    \item $X$ is metacompact
-    \item $K \uparrow_{\text{tact}}G_{K,P}(X)$.
-    \end{itemize}
+  $\pl D$ has a winning perfect-information strategy in Bell's game if and only if $\pl D\win\proxgame{X}$.
 \end{thm}
 
-\begin{thm}
-The following are equivalent for a locally compact space $X$:
-    \begin{itemize}
-    \item $X$ is $\sigma$-metacompact
-    \item $K \uparrow_{\text{mark}}G_{K,P}(X)$.
-    \end{itemize}
-\end{thm}
+\begin{proof}
+  Let $\sigma$ be a winning perfect information strategy for $\pl D$ in Bell's game.
+We define a perfect information strategy $\tau$ in the simplified game to yield symmetric entourages $\tau(p\rest n)=\sigma(p\rest n)\cap(\sigma(p\rest n))^{-1}$ for all partial attacks $p\rest n$.
+Note that $\tau(p\rest n)=\bigcap_{m\leq n}\tau(p\rest m)$.
 
-Upon learning these results, one might wonder the consequences of the existence of this type of limited information strategy:
+  If $p$ attacks $\tau$ in the simplified game, $p(n+1)\in\left(\bigcap_{m\leq n}\tau(p\rest m)\right)[p(n)]=\tau(p\rest n)[p(n)]\subseteq\sigma(p\rest n)[p(n)]\subseteq 4\sigma(p\rest n)[p(n)]$, so $p$ attacks $\sigma$ in Bell's game.
+Thus either $p$ converges, or
+    \[
+      \emptyset
+        =
+      \bigcap_{n<\omega} 4\sigma(p\rest n)[p(n)]
+        \supseteq 
+      \bigcap_{n<\omega}\tau(p\rest n)[p(n)]
+        =
+      \bigcap_{n<\omega}\left(\bigcap_{m\leq n}\tau(p\rest n)\right)[p(n)]
+    \]
 
-\begin{defn}
-A \textbf{predetermined strategy} considers only the turn number. If Player $Z$ has a winning predetermined strategy for a game $G$, this may be denoted $Z \prewin G$.
-\end{defn}
+  For the other direction, let $\sigma$ be a winning perfect information strategy for $\pl D$ in the simplified game such that $\sigma(p\rest n)=\bigcap_{m\leq n}\sigma(p\rest m)$.
+Define the perfect information strategy $\tau$ in Bell's Game such that $4\tau(p\rest n)\subseteq \sigma(p\rest n)$ and $\tau(p\rest n)=\bigcap_{m\leq n}\tau(p\rest m)$ for all partial attacks $p\rest n$.
 
-Intuitively, if a player is using a predetermined strategy, then that player decides every move he or she will make before the game even begins, ignoring the other player's moves.
-
-Consider the following trivial result:
-
-\begin{defn}
-A \textbf{button-mashing strategy} is a constant function. If Player $Z$ has a winning button-mashing strategy for a game $G$, this may be denoted $Z \uparrow_{\text{mash}} G$.
-\end{defn}
+  If $p$ attacks $\tau$ in Bell's game, $p(n)\in 4\tau(p\rest n)\subseteq\sigma(p\rest n)=\bigcap_{m\leq n}\sigma(p\rest m)$, so $p$ attacks $\sigma$ in the simplified game.
+Thus either $p$ converges, or
+    \[
+      \emptyset
+        =
+      \bigcap_{n<\omega}\left(\bigcap_{m\leq n}\sigma(p\rest n)\right)[p(n)]
+        =
+      \bigcap_{n<\omega}\sigma(p\rest n)[p(n)]
+        \supseteq
+      \bigcap_{n<\omega}4\tau(p\rest n)[p(n)]
+        \supseteq
+      \bigcap_{n<\omega}\tau(p\rest n)[p(n)]
+    \]
+\end{proof}
 
 \begin{prop}
-The following are equivalent for any space $X$:
-    \begin{itemize}
-    \item $X$ is compact
-    \item $K \uparrow_{\text{mash}}G_{K,P}(X)$.
-    \end{itemize}
-\end{prop}
-
-Observing that giving $K$ the added information of turn number to a tactical strategy (making it Markov) changed the characterization of a metacompact space into a $\sigma$-metacompact space, it would be very convenient if adding that same information to a button-mashing strategy (making it predetermined) would similarly change the characterization of a compact space into $\sigma$-compact.
-
-\begin{prop}
-If $K \prewin G_{K,P}(X)$, then $X$ is $\sigma$-compact.
+$\pl P$ has a winning perfect-information strategy in Bell's game if and only if $\pl P \win \proxgame{X}$.
 \end{prop}
@@
 \begin{proof}
-Let $K_n$ be the sets given by the winning predetermined strategy.
-If they did not union to $X$, then the counter play $p_n=p$ for some $p\in X\setminus \bigcup_n K_n$ would defeat the ``winning'' strategy.
+  Similar to the previous.
 \end{proof}
 
-\begin{thm}
-If $Y$ is a locally compact, Lindel\"of space, then $K \prewin G_{K,P}(X)$.
-\end{thm}
-
-\begin{proof}
-Let $\mathcal{K}$ be a collection of compact neighborhoods whose interiors cover $X$.
-By Lindel\"of, let $\{K_n : n<\omega\}$ be a countable subcollection whose interiors cover $X$.
-We then define the predetermined strategy $\sigma(n)=\bigcup_{m\leq n} K_n$.
-
-Let $p_n$ give a play by $P$.
-If $p$ is a cluster point of the $p_n$, then every open set about $p$ contains infinitely many $p_n$.
-Let $K_N$ be some compact neighborhood in $\{K_n : n<\omega\}$ which covers $p$.
-Then $K_N$ contains infinitely many $p_n$, which means sometime after round $N$, $P$ played in a set already covered by the strategy $\sigma$, which is an illegal move.
-Thus $\sigma$ is a winning predetermined strategy.
-\end{proof}
-
-\begin{cor}
-The following are equivalent for a locally compact space $X$:
-    \begin{itemize}
-    \item $X$ is $\sigma$-compact
-    \item $X$ is Lindel\"of
-    \item $K \prewin G_{K,P}(X)$.
-    \end{itemize}
-\end{cor}
-
-We now turn our attention to an example of a $\sigma$-compact space for which no predetermined strategy exists (which must, of course, not be locally compact).
-In fact, $P$ will instead have a winning tactical strategy.
+\begin{defn}
+  A uniform space is \textbf{proximal} if $\pl D \win \proxgame{X}$.
+\end{defn}
 
 \begin{defn}
-Let $M=\omega^2\cup\{\infty\}$ denote the \textbf{metric fan space} with the topology generated by the singletons in $\omega^2$ and sets of the form $((\omega\setminus n)\times\omega) \cup \{\infty\}$ for $n<\omega$.
+  For a space $X$ and a point $x\in X$, the \textbf{$W$-convergence-game} $\congame{X}{x}$ proceeds as follows.
+
+  In round $0$, $\pl O$ chooses a neighborhood $U_n$ of $x$, followed by $\pl P$ choosing a point $p_n\in \bigcap_{m\leq n}U_m$.
+
+  Player $\pl O$ wins if $\<p_0,p_1,\dots\>$ converges.
 \end{defn}
 
-\begin{prop}
-For each compact set $C$ in $M$, there exists a minimal dominating function $f_C$ such that for each $(x,y)\in C\setminus\{\infty\}$, $f(x)> y$.
-\end{prop}
+\begin{defn}
+  A space is \textbf{$W$} if $\pl O \win \congame{X}{x}$ for all $x\in X$.
+\end{defn}
 
-\begin{lem}
-$P \markwin G_{K,P}(M)$ where $M$ is the metric fan space. (This implies $K\not\uparrow G_{K,P}(M)$.)
-\end{lem}
+\begin{defn}
+  For each finite tuple $(m_0,\dots,m_{n-1})$, we define the \textbf{$k$-tactical fog-of-war}
+    \[
+      T_k(\<m_0,\dots,m_{n-1}\>)=\<m_{n-k},\dots,m_{n-1}\>
+    \]
+  and the \textbf{$k$-Mark\"ov fog-of-war}
+    \[
+      M_k(\<m_0,\dots,m_{n-1}\>)=\<\<m_{n-k},\dots,m_{n-1}\>,n\>
+    \]
 
-\begin{proof}
-Let $P$ respond to the move $C\in K[X]$ by $K$ on round $n$ with the point $p=(n,s_C)$ such that $s_C = \min(\{y<\omega : f_C(n) < y\}$.
-It is easy to see that either $p_n\rightarrow \infty$, so $P$ has a winning tactical strategy.
-\end{proof}
-
-Furthermore, by a theorem due to Eric van Douwen...
+  So $P\ktactwin{k}G$ if and only if there exists a winning strategy for $P$ of the form $\sigma\circ T_k$, and $P\kmarkwin{k}G$ if and only if there exists a winning strategy of the form $\sigma\circ M_k$.
+\end{defn}
 
 \begin{thm}
-Every first-countable non-locally countably compact space has the metric fan space $M$ as a closed subspace.
-\end{thm}
-
-... we have the following corollary:
-
-\begin{cor}
-$P \markwin G_{K,P}(X)$ where $X$ is a first-countable non-locally countably compact space. (This implies $K\not\uparrow G_{K,P}(X)$.)
-\end{cor}
-
-(Open question: does $P \tactwin G_{K,P}(X)$?)
-
-\begin{thm}
-$P \not\tactwin D_{K,P}(M)$ where $M$ is the metric fan space.
-\end{thm}
-
-\begin{proof}
-Give $P$ the tactic $\sigma$.
-Suppose that for all $n<\omega$, there is an upper bound $m<\omega$ so that for each $C \in K[M]$, if $\pi_1(\sigma(C))=n$, then $\pi_2(\sigma(C))<m$.
-We may then define $f(n)=m$, and let $C_f=\{(x,y):f(x)<y\}\in K[M]$.
-$\sigma(C_f)$ must show a contradiction if $\sigma$ is legal.
-
-So it follows that there is some $n<\omega$ such that there are compact sets $C_i\in K[M]$ with $\pi_1(\sigma(C_i))=n$ and $\pi_2(\sigma(C_i))<\pi_2(\sigma(C_{i+1}))$.
-The play $\left<C_0,\sigma(C_0),C_1,\sigma(C_1),\dots\right>$ is a counter to $\sigma$.
-\end{proof}
-
-While $K\prewin G_{K,P}(X)$ implies $X$ is $\sigma$-compact, it in fact implies something stronger.
-
-\begin{defn}
-A space $X$ is \textbf{hemicompact} if there exists a chain of increasing compact sets $K_0\subseteq K_1 \subseteq \dots$ such that every compact set in $X$ is a subset of some $K_n$.
-\end{defn}
-
-\begin{lem}
-If $K\prewin G_{K,P}(X)$, then $X$ is hemicompact. Furthermore, any predetermined winning strategy for $K$ witnesses hemicompactness.
-\end{lem}
-
-\begin{proof}
-Let $\sigma$ be a predetermined strategy for $K$ in the game $G_{K,P}(Y)$ such that there exists a compact set $C$ with $C \not\subseteq \sigma(n)$ for all $n$.
-On each turn, have $P$ play some $y_n\in C \setminus \sigma(n)$.
-Then the $y_n$ are an infinite subset of the compact set $C$ and must have a cluster point in $C$, showing $\sigma$ is not a winning strategy.
-
-Thus if $K$ has a winning predetermined strategy, it witnesses that $Y$ is hemicompact.
-\end{proof}
-
-In fact, for locally compact spaces, finding winning predetermined strategies for $G_{K,P}(X)$ and $G_{K,L}(X)$ are equivalent problems.
-
-\begin{thm}
-The following are equivalent for any locally compact space $X$:
+For all $x\in X$:
   \begin{itemize}
-  \item $X$ is hemicompact.
-  \item $K \prewin G_{K,L}(X)$.
-  \item $K \prewin G_{K,P}(X)$.
+    \item
+      $\pl D\win \proxgame{X} \Rightarrow \pl O \win \congame{X}{x}$
+    \item
+      $\pl D\ktactwin{2k} \proxgame{X} \Rightarrow \pl O \ktactwin{k} \congame{X}{x}$
+    \item
+      $\pl D\kmarkwin{2k} \proxgame{X} \Rightarrow \pl O \kmarkwin{k} \congame{X}{x}$
   \end{itemize}
@@
 \begin{proof}
-Let $Y$ be hemicompact, witnessed by $K_n=\sigma(n)$.
-Let $L_0,L_1,\dots$ be a play by $L$ in $G_{K,L}(X)$.
-Suppose that this play defeats $\sigma$.
-Then let $x\in X$ be the point such that for all neighborhoods $U$ of $x$, $U$ hits infinite $L_n$.
-Let $C$ be a compact neighborhood of $x$, which must hit infinite $L_n$.
-As $K_n$ witnesses hemicompactness, $C \subseteq K_N = \sigma(N)$ for some $N$.
-But then $C\subset K_N$ intersects infinitely many $L_n$, which shows that the play $L_0,L_1,\dots$ was illegal.
-Thus $\sigma$ defeats every legal play by $L$ and is thus a winning predetermined strategy for $K$ in $G_{K,L}(X)$.
+Let $\sigma$ witness $\pl D \ktactwin{2k}\proxgame{X}$ (resp.
+$\pl D \kmarkwin{2k}\proxgame{X}$, $\pl D\win\proxgame{X}$).
+We define the $k$-tactical (resp.
+$k$-Mark\"ov, perfect info) strategy $\tau$ such that
+  \[
+    \tau\circ L_k(p)
+      =
+    \sigma\circ L_{2k}(\<x,p(0),\dots,x,p(|p|-1)\>)[x]
+      \cap
+    \sigma\circ L_{2k}(\<x,p(0),\dots,x,p(|p|-1),x\>)[x]
+  \]
+where $L_{2k}$ is the $2k$-tactical fog-of-war (resp. $2k$-Mark\"ov fog-of-war, identity) and $L_{k}$ is the $k$-tactical fog-of-war (resp. $k$-Mark\"ov fog-of-war, identity).
 
-We conclude by noting that any winning strategy for $G_{K,L}(X)$ is a winning strategy for $G_{K,P}(X)$, and the existence of a winning predetermined strategy for $G_{K,P}(X)$ implies hemicompact by the previous lemma.
+Let $p$ attack $\tau$. Consider the attack $q$ against the winning strategy $\sigma$ such that $q(2n)=x$ and $q(2n+1)=p(n)$, and let $D_n=\sigma\circ L_{2k}(q)$ and $E_n=\bigcap_{m\leq n}D_n$.
+
+Certainly, $x\in E_{2n}[x]= E_{2n}[q(2n)]$ for any $n<\omega$. Note also for any $n<\omega$ that 
+    \[
+      p(n) \in 
+      \bigcap_{m\leq n}\tau\circ L_k(p\rest n)
+    \]
+    \[
+      =
+      \bigcap_{m\leq n}\left(
+        \sigma\circ L_{2k}(\<x,p(0),\dots,x,p(m-1)\>)[x]\cap
+        \sigma\circ L_{2k}(\<x,p(0),\dots,x,p(m-1),x\>)[x]
+      \right)
+    \]
+    \[
+      =
+      \bigcap_{m\leq n}\left(
+        D_{2m}[x]\cap
+        D_{2m+1}[x]
+      \right) =
+      \bigcap_{m\leq 2n+1} D_m[x]=E_{2n+1}[x]
+    \]
+so by the symmetry of $E_{2n+1}$, $x\in E_{2n+1}[p(n)]= E_{2n+1}[q(2n+1)]$.
+Thus $x\in \bigcap_{n<\omega} E_n[q(n)]\not=\emptyset$, and since $\sigma$ is a winning strategy, the attack $q$ converges.
+Since $q(2n)=x$, $q$ must converge to $x$.
+Thus its subsequence $p$ converges to $x$, and $\tau$ is a winning strategy in $\congame{X}{x}$.
 \end{proof}
@@
 \begin{cor}
-The following are equivalent for any locally compact space $X$:
+For all $x\in X$:
   \begin{itemize}
-  \item $X$ is Lindel\"of.
-  \item $X$ is $\sigma$-compact.
-  \item $X$ is hemicompact.
-  \item $K \prewin G_{K,L}(X)$.
-  \item $K \prewin G_{K,P}(X)$.
+    \item
+      $\pl D\ktactwin{k} \proxgame{X} \Rightarrow \pl O \ktactwin{k} \congame{X}{x}$
+    \item
+      $\pl D\kmarkwin{k} \proxgame{X} \Rightarrow \pl O \kmarkwin{k} \congame{X}{x}$
   \end{itemize}
@@
 
-The compact-point and compact-compact games are also useful in inspecting compactly generated ``k''-spaces.
+\begin{cor}
+  All proximal spaces are $W$-spaces.
+\end{cor}
+
+\begin{thm}
+  Let $X\cup\{\infty\}$ be a uniformizable space such that $X$ is discrete. Then
+  \begin{itemize}
+    \item
+      $\pl O\win \congame{X\cup\{\infty\}}{\infty} \Rightarrow \pl D \win \proxgame{X\cup\{\infty\}}$
+    \item
+      $\pl O\ktactwin{k} \congame{X\cup\{\infty\}}{\infty} \Rightarrow \pl D \ktactwin{k} \proxgame{X\cup\{\infty\}}$
+    \item
+      $\pl O\kmarkwin{k} \congame{X\cup\{\infty\}}{\infty} \Rightarrow \pl D \kmarkwin{k} \proxgame{X\cup\{\infty\}}$
+  \end{itemize}
+\end{thm}
+
+\begin{proof}
+  Note that the topology on $X\cup\{\infty\}$ is induced by the uniformity with equivalence relation entourages $D(U)=\Delta\cup U^2$ for each open neighborhood $U$ of $\infty$.
+
+  Let $\sigma$ witness $\pl D \ktactwin{k}\congame{X\cap\{\infty\}}{\infty}$ (resp.
+$\pl D \kmarkwin{k}\congame{X\cap\{\infty\}}{\infty}$, $\pl D\win\congame{X\cap\{\infty\}}{\infty}$).
+We define the $k$-tactical (resp.
+$k$-Mark\"ov, perfect info) strategy $\tau$ such that
+    \[
+      \tau\circ L(p)
+        =
+      D(\sigma\circ L(p))
+    \]
+  where $L$ is the $k$-tactical fog-of-war (resp. $k$-Mark\"ov fog-of-war, identity).
+
+  Let $p\in (X\cup\{\infty\})^\omega$ attack $\tau$ such that $\bigcap_{n<\omega}\tau(p\rest n)[p(n)]\not=\emptyset$.
+
+  If $\infty\in\bigcap_{n<\omega}\tau(p\rest n)[p(n)]$, it follows that $p$ is an attack on $\sigma$.
+Since $\sigma$ is a winning strategy, it follows that $q$ and its subsequence $p$ must coverge to $\infty$.
+
+  Otherwise, $\infty\not\in\tau(p\rest N)[p(N)]$ for some $N<\omega$, and then $\tau(p\rest N)[p(N)]=\{p(N)\}$ implies $p\to p(N)$.
+
+  Thus $\tau\circ L$ is a winning strategy.
+\end{proof}
+
+\begin{cor}
+  Let $X\cup\{\infty\}$ be a uniformizable space such that $X$ is discrete. Then
+  \begin{itemize}
+    \item
+      $\pl O\win \congame{X\cup\{\infty\}}{\infty} \Leftrightarrow \pl D \win \proxgame{X\cup\{\infty\}}$
+    \item
+      $\pl O\ktactwin{k} \congame{X\cup\{\infty\}}{\infty} \Leftrightarrow \pl D \ktactwin{k} \proxgame{X\cup\{\infty\}}$
+    \item
+      $\pl O\kmarkwin{k} \congame{X\cup\{\infty\}}{\infty} \Leftrightarrow \pl D \kmarkwin{k} \proxgame{X\cup\{\infty\}}$
+  \end{itemize}
+\end{cor}
+
+\begin{prop} For any $x\in X$ and $k\geq 1$,
+  \begin{itemize}
+    \item
+      $\pl O\ktactwin{k}\congame{X}{x} \Leftrightarrow \pl O\tactwin\congame{X}{x}$
+    \item
+      $\pl O\kmarkwin{k}\congame{X}{x} \Leftrightarrow \pl O\markwin\congame{X}{x}$
+  \end{itemize}
+\end{prop}
+
+\begin{proof}
+  If $\sigma$ witnesses $\pl O\ktactwin{k}\congame{X}{x}$, let $\tau(\emptyset)=\sigma(\emptyset)$ and
+    \[
+      \tau(\<q\>)
+        =
+      \bigcap_{i< k}
+      \sigma(\<\underbrace{x,\dots,x}_{k-i-1},q,\underbrace{x,\dots,x}_{i}\>)
+    \]
+
+  This is easily verified to be a winning strategy. The proof for $\pl O\kmarkwin{k}\congame{X}{x}$ is analogous.
+\end{proof}
+
+\begin{cor}
+  Let $X\cup\{\infty\}$ be a uniformizable space such that $X$ is discrete, and $k\geq 1$. Then
+  \begin{itemize}
+    \item
+      $\pl D\ktactwin{k}\proxgame{X\cup\{\infty\}} \Leftrightarrow O\tactwin\proxgame{X\cup\{\infty\}}$
+    \item
+      $\pl D\kmarkwin{k}\proxgame{X\cup\{\infty\}} \Leftrightarrow O\markwin\proxgame{X\cup\{\infty\}}$
+  \end{itemize}
+\end{cor}
+
+\begin{prop} For any uniform space $X$,
+  \begin{itemize}
+    \item
+      $\pl O\ktactwin{k}\proxgame{X} \Leftrightarrow \pl O\ktactwin{2}\proxgame{X}$
+    \item
+      $\pl O\kmarkwin{k}\proxgame{X} \Leftrightarrow \pl O\kmarkwin{2}\proxgame{X}$
+  \end{itemize}
+\end{prop}
+
+\begin{proof}
+  If $\sigma$ witnesses $\pl O\ktactwin{k}\congame{X}{x}$, let $\tau(\emptyset)=\sigma(\emptyset)$ and
+    \[
+      \tau(\<q\>)
+        =
+      \bigcap_{i<k}
+      \sigma(\<\underbrace{q,\dots,q}_{i}\>)
+    \]
+    \[
+      \tau(\<q,q'\>)
+        =
+      \bigcap_{i< k}
+      \sigma(\<\underbrace{q,\dots,q}_{k-i},\underbrace{q',\dots,q'}_{i}\>)
+    \]
+
+  This is easily verified to be a winning strategy. The proof for $\pl O\kmarkwin{k}\congame{X}{x}$ is analogous.
+\end{proof}
+
+\newpage
 
 \begin{defn}
-A topological space is called a \textbf{$k$-space} if the following condition is satisfied: \[C \subseteq X \text{ is closed in } X\, \Leftrightarrow \, C\cap K \text{ is closed in } K \text{ for all compact sets } K\in K[X]\]
+  The absolute proximal game $\aproxgame{X}$ is analogous to $\proxgame{X}$, except $\pl D$ may only win if $p$ converges.
 \end{defn}
@@
 \begin{defn}
-A topological space is called a \textbf{$k_\omega$-space} if there exist $K_0,K_1,\dots \in K[X]$ that satisfy the following condition: \[C \subseteq X \text{ is closed in } X\, \Leftrightarrow \, C \cap K_n \text{ is closed in } K_n \text{ for all } n\]
+  A \textbf{uniformly locally compact} space is a uniformizable space with a \textbf{uniformly compact entourage} $M$ where $\cl{M[x]}$ is compact for all $x$.
 \end{defn}
@@
 \begin{thm}
-The following are equivalent for any Hausdorff $k$-space $X$:
-  \begin{itemize}
-  \item $X$ is hemicompact.
-  \item $X$ is $k_{\omega}$.
-  \item $K \prewin G_{K,P}(X)$.
-  \end{itemize}
-Furthermore, all predetermined strategies for $K$ witness hemicompact and $k_\omega$, and any witness to hemicompact/$k_\omega$ witnesses the other and serves as a predetermined strategy for $K$.
+  For any uniformly locally compact space $X$,
+      $\pl D\win \proxgame{X} \Leftrightarrow \pl D\win \aproxgame{X}$
 \end{thm}
@@
 \begin{proof}
-If $X$ is hemicompact, then let it be witnessed by $K_n$.
-We claim $K_n$ also witnesses $k_\omega$.
-Note that the forward implication of $k_\omega$ always holds for $T_1$ spaces as $C\cap K_n$ is closed in $X$, and thus in every $K_n$.
-So assume $C\cap K_n$ is closed in $K_n$ for all $n$.
-Let $H$ be any compact set.
-As $X$ is hemicompact, $H\subseteq K_n$ for some $n$.
-Note $C\cap H = (C\cap K_n)\cap H$.
-As both $C \cap K_n$ and $H$ are closed in $K_n$, $C\cap H$ is closed in $K_n$, and thus $C\cap H$ is closed in $H$.
-As $Y$ is $k$ and $C\cap H$ is closed in $H$ for all compact $H$, $C$ is closed, showing the backwards implication.
+  Let $M$ be a uniformly locally compact entourage.
+Let $\sigma$ witness $\pl D\win \proxgame{X}$ such that $\sigma(a)\subseteq M$ always (so $\cl{\sigma(a)[x]}\subseteq\cl{M[x]}$ is compact), and $a\supseteq b$  implies $\sigma(a)\subseteq\frac{1}{4}\sigma(b)$.
 
-Now if $Y$ is $k_\omega$, let it be witnessed by $K_n$.
-Give $K$ the predeterined strategy $\sigma(n)=K_n$ for the game $G_{K,P}(X)$, and let $p_n$ be the result of a legal counter by $P$.
-Suppose by way of contradiction that $p$ is a cluster point of the $p_n$.
-Note $p\in \sigma(N)$ for some $N$.
-$p$ is a cluster point of $\{p_n : n\geq N\}$ but $p\not\in \{p_n : n \geq N\}$.
-Also, $\{p_n : n \geq N\} \cap \sigma(m)$ is finite for all $m$, and thus closed, so as $\sigma(n)$ witnesses $k_\omega$, $\{p_n : n\geq N\}$ is closed and must contain its cluster point $p$, which is a contradiction.
-Thus $\sigma$ is a winning predetermined strategy for $K$ in $G_{K,P}(Y)$.
+  Let $\tau(p\rest n)=\frac{1}{2}\sigma(p\rest n)$. If $p$ attacks $\tau$ in $\aproxgame{X}$, then
+    \[
+      p(n+1)
+        \in
+      \tau(p\rest n)[p(n)]
+        =
+      \frac{1}{2}\sigma(p\rest n)[p(n)]
+    \]
 
-Finally, if $K \prewin G_{K,P}(X)$, $X$ is hemicompact by the previous lemma.
+    and for
+
+    \[
+      x
+        \in
+      \cl{\sigma(p\rest (n+1))[p(n+1)]}
+        \subseteq
+      \cl{\frac{1}{4}\sigma(p\rest n)[p(n+1)]}
+        \subseteq
+      \frac{1}{2}\sigma(p\rest n)[p(n+1)]
+    \]
+
+  we can conclude $x\in\sigma(p\rest n)[p(n)]$. Thus
+
+    \[
+      \sigma(p\rest (n+1))[p(n+1)]
+        \subseteq
+      \cl{\sigma(p\rest (n+1))[p(n+1)]}
+        \subseteq
+      \sigma(p\rest n)[p(n)]
+    \]
+
+  Finally, note that $p$ attacks the winning strategy $\sigma$ in $\proxgame{X}$, but since the intersection of a chain of nonempty compact sets is nonempty:
+
+    \[
+      \bigcap_{n<\omega} \sigma(p\rest n)[p(n)]
+        =
+      \bigcap_{n<\omega} \cl{\sigma(p\rest n)[p(n)]}
+        \not=
+      \emptyset
+    \]
+
+  We conclude that $p$ converges.
 \end{proof}
 
-For $k$-spaces, it turns out that finding winning predetermined strategies for $G_{K,P}(X)$ and $G_{K,L}(X)$ are also equivalent problems.
+\begin{cor}
+  A uniformaly locally compact space $X$ is proximal if and only if $\pl D \win \aproxgame{X}$.
+\end{cor}
 
 \begin{thm}
-For any hemicompact Hausdorff $k$-space $X$, $K \prewin G_{K,L}(X)$.
+  For any uniformly locally compact proximal space $X$, $\pl O\win \clusgame{X}{H}$ for all compact $H\subseteq X$.
 \end{thm}
@@
 \begin{proof}
-Let $X$'s hemicompactness be witnessed by $K_n=\sigma(n)$.
-Note that this also witnesses $k_\omega$ by the proof of the previous theorem.
-Let $H_0,H_1,\dots$ be a counter by $H$ for the game $G_{K,L}(X)$ in response to $\sigma$.
-Suppose by way of contradiction the counter was legal and defeats $\sigma$.
-Then there is a point $x$ such that every neighborhood of $x$ hits infinitely many of the $H_n$.
+  Let $\sigma$ witness $\pl D \win \aproxgame{X}$ such that $p\supseteq q$ implies $\sigma(p)\subseteq \frac{1}{4}\sigma(q)$.
 
-Now, $x\in\sigma(N)$ for some $N$, and since the play $H_0,H_1,\dots$ is legal, $x\not\in H_n$ for all $n\geq N$.
-Consider the set $H_\omega=\bigcup_{n\geq N} H_n$.
-Note that as the $K_n$ witness $k_\omega$, $H_\omega$ is closed if and only if $H_\omega \cap \sigma(m)$ is closed in $\sigma(m)$ for all $m$.
-In fact, since every $H_n$ is a subset of some $\sigma(m)$ (by hemicompactness), $H_\omega \cap \sigma(m)$ is a finite union of some $H_n$, and is thus closed in $Y$.
+  Let $o(t)$ be the subsequence of $t$ consisting of its odd-indexed terms.
 
-We thus have that $H_\omega$ is a closed set not containing $x$.
-But since every neighborhood of $x$ intersects $H_\omega$, $x$ is a limit point of the closed set $H_\omega$ and should be included, demonstrating our contradiction.
-Thus $\sigma$ is a winning predetermined strategy for $K$ in the game $G_{K,L}(X)$.
+  We define $T(\emptyset)$, etc. as follows:
+
+  \begin{itemize}
+    \item Let $\emptyset\in T(\emptyset)$.
+    \item Choose $m_\emptyset<\omega$, $h_{\emptyset,i}\in H$ for $i<m_\emptyset$, and $h_{\emptyset,i,j}\in H\cap\cl{\frac{1}{4}\sigma(\emptyset)[h_{\emptyset,i}]}$ for $i,j<m_\emptyset$ such that
+      \[
+        \{\frac{1}{4}\sigma(\emptyset)[h_{\emptyset,i}]:i<m_\emptyset\}
+      \]
+    is a cover for $H$ and such that for each $i<m_\emptyset$
+      \[
+        \{\frac{1}{4}\sigma(\<h_{\emptyset,i}\>)[h_{\emptyset,i,j}]:j<m_\emptyset\}
+      \]
+    is a cover for $H\cap\cl{\frac{1}{4}\sigma(\emptyset)[h_{\emptyset,i}]}$.
+    \item Let $\<i\>\in T(\emptyset)$, $\<i,h_{\emptyset,i}\>\in T(\emptyset)$, and $\<i,h_{\emptyset,i},j\>\in T(\emptyset)$ for $i,j<m_\emptyset$.
+  \end{itemize}
+
+  Suppose $T(a)$, etc. are defined. We then define $T(a\concat\<x\>)$, etc. for
+    \[
+      x\in \bigcup_{s\concat\<i,h_{s,i},j\>\in\max(T(a))} \frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]
+    \]
+  as follows:
+
+  \begin{itemize}
+    \item Let $T(a)\subseteq T(a\concat\<x\>)$.
+    \item Choose $t=s\concat\<i,h_{s,i},j,x\>$ such that $s\concat\<i,h_{s,i},j\>\in\max(T(a))$ and $x\in \frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]$. 
+    \item Note that, assuming $o(s)\concat\<h_{s,i}\>$ is a legal partial attack against $\sigma$, then
+      \[
+        x
+          \in 
+        \frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]
+          \subseteq
+        \frac{1}{4}\sigma(o(s))[h_{s,i,j}]
+      \]
+    and
+      \[
+        h_{s,i,j}
+          \in 
+        \cl{\frac{1}{4}\sigma(o(s))[h_{s,i}]}
+          \subseteq 
+        \frac{1}{2}\sigma(o(s))[h_{s,i}]
+      \]
+    implies
+      \[
+        x
+          \in 
+        \sigma(o(s))[h_{s,i}]
+      \]
+    and thus $o(s)\concat\<h_{s,i},x\>=o(t)$ is a legal partial attack against $\sigma$.
+    \item Choose $m_t<\omega$, $h_{t,k}\in H\cap \cl{\frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]}$ for $k<m_t$, and $h_{t,k,l}\in H\cap\cl{\frac{1}{4}\sigma(t)[h_{t,k}]}$ for $k,l<m_t$ such that
+      \[
+        \{\frac{1}{4}\sigma(o(t))[h_{t,k}]:k<m_t\}
+      \]
+    is a cover for $H\cap \cl{\frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]}$ and such that for each $k<m_t$
+      \[
+        \{\frac{1}{4}\sigma(o(t)\concat\<h_{t,k}\>)[h_{t,i,j}]:l<m_t\}
+      \]
+    is a cover for $H\cap\cl{\frac{1}{4}\sigma(o(t))[h_{t,k}]}$.
+    \item Note that, assuming $o(t)$ is a legal partial attack against $\sigma$, then
+      \[
+        h_{t,k}
+          \in 
+        \cl{\frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]}
+          \subseteq
+        \frac{1}{2}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]
+      \]
+    and
+      \[
+        x
+          \in 
+        \frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]
+      \]
+    implies
+      \[
+        h_{t,k}
+          \in
+        \sigma(o(s)\concat\<h_{s,i}\>)[x]
+      \]
+    and thus $o(t)\concat\<h_{t,k}\>$ is a legal partial attack against $\sigma$.
+    \item Let $t\in T(a\concat\<x\>)$, $t\concat\<k\>\in T(a\concat\<x\>)$, $t\concat\<k,h_{t,k}\>\in T(a\concat\<x\>)$, and $t\concat\<k,h_{t,k},l\>\in T(a\concat\<x\>)$ for $k,l<m_t$.
+    \item Note that assuming
+      \[
+        \{\frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}] : s\concat\<i,h_{s,i},j\>\in\max(T(a))\}
+      \]
+    covers $H$, then since
+      \[
+        \{\frac{1}{4}\sigma(o(t)\concat\<h_{t,k}\>)[h_{t,k,l}] : s\concat\<i,h_{s,i},j,x,k,h_{t,k},l\>\in\max(T(a\concat\<x\>))\setminus\max(T(a))\}
+      \]
+    covers $H\cap \frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]$, we have that
+      \[
+        \{\frac{1}{4}\sigma(o(t)\concat\<h_{t,k}\>)[h_{t,k,l}] : t\concat\<k,h_{t,k},l\>\in\max(T(a\concat\<x\>))\}
+      \]
+    covers $H$.
+  \end{itemize}
+
+  With this we may define the perfect information strategy $\tau$ for $\pl O$ in $\congame{X}{H}$ such that:
+  \[
+    \tau(p\rest n) = \bigcup_{s\concat\<i,h_{s,i},j\>\in\max(T(p\rest n))} \frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]
+  \]
+
+  If $p$ attacks $\tau$, then it follows that $T(p\rest n)$ is defined for all $n<\omega$, so let $T(p)=\bigcup_{n<\omega} T(p\rest n)$. We note $T(p)$ is an infinite tree with finite levels:
+    \begin{itemize}
+      \item $\emptyset$ has exactly $m_\emptyset$ successors $\<i\>$.
+      \item $s\concat\<i\>$ has exactly one successor $t\concat\<i,h_{s,i}\>$
+      \item $s\concat\<i,h_{s,i}\>$ has exactly $m_s$ successors $t\concat\<i,h_{s,i},j\>$
+      \item $s\concat\<i,h_{s,i},j\>$ has either no successors or exactly one successor $t\concat\<i,h_{s,i},j,x\>$
+      \item $t=s\concat\<i,h_{s,i},j,x\>$ has exactly $m_t$ successors $t\concat\<k\>$
+    \end{itemize}
+
+  Let $q'=\<i_0,h_0,j_0,x_0,i_1,h_1,j_1,x_1,\dots\>$ correspond to this infinite branch in $T(p)$, and let $q=o(q')=\<h_0,x_0,h_1,x_1,\dots\>$.
+Note that by the construction of $T(p)$, $q$ is an attack on the winning strategy $\sigma$ in $\aproxgame{X}$, so it must converge.
+Since every other term of $q$ is in $H$, it must converge to $H$.
+Then since $q$ is a subsequence of $p$, $p$ must cluster at $H$.
 \end{proof}
@@
 \begin{cor}
-The following are equivalent for any Hausdorff $k$-space $X$:
-  \begin{itemize}
-  \item $X$ is hemicompact.
-  \item $X$ is $k_{\omega}$.
-  \item $K$ has a winning predetermined strategy in $G_{K,L}(X)$.
-  \item $K$ has a winning predetermined strategy in $G_{K,P}(X)$.
-  \end{itemize}
+  For any uniformly locally compact proximal space, $\pl O\win \congame{X}{H}$ for all compact $H\subseteq X$.
 \end{cor}
 
-It's natural to question whethere there is ever any difference between finding winning predetermined strategies for $G_{K,P}(X)$ and $G_{K,L}(X)$.
-We now look to a (non-locally compact, non-$k$) Hausdorff space where the distinction arises:
+\begin{proof}
+  $\pl O \win \congame{X}{H}$ if and only if $\pl O \win \clusgame{X}{H}$.
+\end{proof}
+
+\begin{cor}
+  A compact uniform space $X$ is Corson compact if and only if it is proximal.
+\end{cor}
+
+\begin{proof}
+  A characterization of Corson compact is having a $W$-set diagonal. If $X$ is proximal compact, then $X^2$ is proximal compact, and its compact diagonal is a $W$-set.
+\end{proof}
+
+\newpage
+
+\begin{thm}
+  $\pl O \prewin \congame{X}{H}$ if and only if there exists a countable base 
+  around $H$.
+\end{thm}
+
+\begin{proof}
+  Let $\{U_n:n<\omega\}$ be a countable base around $H$. We define the 
+  predetermined strategy $\sigma(n)=\bigcap_{m\leq n}U_m$. Let $p$ attack 
+  $\sigma(n)$ - then if $U$ is any neighborhood of $H$, we may choose 
+  $H\subseteq U_m\subseteq U$, and note that $\sigma(n)\subseteq U_m$ for 
+  $n\geq m$, and thus $p(n)\in U_m\subseteq U$ for all $n\geq m$. Thus 
+  $\sigma$ is a winning strategy.
+
+  For the other direction, suppose there does not exist a countable base 
+  around $H$, and let $\sigma(n)$ be an arbitrary predetermined strategy. 
+  Since $\{\bigcap_{m\leq n}\sigma(m):n<\omega\}$ is not a countable base 
+  around $H$, we may choose an open set $U$ around $H$ such that 
+  $\bigcap_{m\leq n}\sigma(m)\not\subseteq U$ for all $n<\omega$. We may 
+  easily verify that if $p(n)\in\bigcap_{m\leq n}\sigma(m)\setminus U$ for 
+  all $n<\omega$, then $p$ is a successful counterattack to $\sigma$.
+\end{proof}
+
+\begin{cor}
+  $X$ is first countable if and only if $\pl O \prewin \congame{X}{x}$ for 
+  all $x\in X$
+\end{cor}
+
+\begin{cor}
+  $\pl D \prewin \proxgame{X}$ implies $X$ is first countable.
+\end{cor}
 
 \begin{defn}
-Given a set $X$, an ultrafilter on $X$ is a collection $\mathcal{F}\subseteq\mathcal{P}(X)$ such that
-    \begin{enumerate}
-    \item $\emptyset\not\in \mathcal{F}$
-    \item $A,B\in\mathcal{F} \Rightarrow A\cap B \in \mathcal{F}$
-    \item $A\in\mathcal{F}$ and $A \subseteq B$ $\Rightarrow$ $B\in\mathcal{F}$
-    \item $\forall A \subseteq X(A\in\mathcal{F}$ or $X\setminus A \in \mathcal{F})$
-    \end{enumerate}
-As a result, ultrafilters which contain a finite set contain only one singleton (and are called \textbf{principal}). Otherwise, ultrafilters which contain no finite sets are called \textbf{free}.
+  Scattered Eberlein compact spaces are known as \term{strong Eberlein 
+  compact} spaces.
 \end{defn}
 
-\begin{defn}
-The \textbf{Stone-Cech compactification} $\beta\omega$ of $\omega$ is the collection of ultrafilters on $\omega$.
-The principal ultrafilters containing a singleton $\{n\}$ are each identified with $n$ itself and are isolated.
-Free ultrafilters $\mathcal{F}$ are given neighborhoods of the form \[\{\mathcal{G} : \mathcal{G} \text{ is an ultrafilter on } \omega \text{ and } A \in \mathcal{G}\} = A \cup \{\mathcal{G}: \mathcal{G} \text{ is a free ultrafilter on } \omega \text{ and } A \in \mathcal{G}\}\] for each $A\in\mathcal{F}$.
+\begin{thm}[folklore]
+  Scattered compact first-countable spaces are metrizable.
+\end{thm}
 
-Alternately $\beta\omega=\omega\cup\{\mathcal{F} : \mathcal{F}$ is a free ultrafilter on $\omega\}$ where $\omega$ is discrete and the free ultrafilters have the local base described above.
-\end{defn}
+\begin{cor}
+  If $X$ is scattered compact and $\pl O \prewin\congame{X}{x}$ for all
+  $x\in X$ (or $\pl D \prewin\proxgame{X}$), then $X$ is metrizable.
+\end{cor}
 
-\begin{defn}
-A \textbf{single-ultrafilter space} is a subset of $\beta\omega$ containing all elements of $\omega$ and a single ultrafilter $\mathcal{F}$.
-\end{defn}
+\begin{ex}
+  $\pl D \not\prewin \proxgame{\oneptcomp\omega_1}$
+\end{ex}
+
+\begin{proof}
+  There does not exist a countable base around $\infty$, so 
+    $\pl O \not\prewin \congame{X}{\omega_1}$.
+\end{proof}
+
+\begin{ex}
+  $\pl O \tactwin \congame{\oneptcomp\kappa}{\infty}$ and 
+  $\pl D \tactwin \proxgame{\oneptcomp\kappa}$ for all cardinals $\kappa$
+\end{ex}
+
+\begin{proof}
+  For $\congame{\oneptcomp\kappa}{\infty}$, let 
+    $\sigma()=\sigma(\infty)=\oneptcomp\kappa$ 
+  and 
+    $\sigma(x)=\oneptcomp\kappa\setminus\{x\}$ 
+  otherwise.
+\end{proof}
+
+\newpage
+
+\begin{thm}
+  If $H$ is a closed subset of $X$, then 
+    $
+      \pl D \limitwin \proxgame{X}
+        \Rightarrow
+      \pl D \limitwin \proxgame{H}
+    $
+  where $\limitwin$ is any of $\win$, $\ktactwin{k}$, or $\kmarkwin{k}$.
+\end{thm}
+
+\begin{proof}
+  Let $\sigma\circ L$ witness $\pl D \limitwin \proxgame{X}$. We define
+  $\tau\circ L$ for $\pl D$ in $\proxgame{H}$ as follows:
+    \[
+      \tau\circ L(p\rest n)
+        =
+      \sigma\circ L(p\rest n)
+        \cap
+      H^2
+    \]
+
+  Let $p$ attack $\tau\circ L$. $p$ also attacks the winning strategy 
+  $\sigma\circ L$, so either 
+    \[
+      \bigcap_{n<\omega}
+      \left(\bigcap_{m\leq n}\tau\circ L(p\rest n)\right)
+      [p(n)]
+        \subseteq
+      \bigcap_{n<\omega}
+      \left(\bigcap_{m\leq n}\sigma\circ L(p\rest n)\right)
+      [p(n)]
+        =
+      \emptyset
+    \]
+  or $p$ converges in $X$, and thus converges in $H$.
+\end{proof}
+
+\begin{thm}
+  If $\pl D\limitwin \proxgame{X_i}$ for $i<\omega$, then
+  $\pl D\limitwin \proxgame{\prod_{i<\omega}X_i}$, where $\limitwin$ is either
+  $\win$ or $\kmarkwin{k}$.
+\end{thm}
+
+\begin{proof}
+  A subbase for $\prod_{i<\omega}X_i$ is
+    \[
+      \{\pi_i^{-1}(D):i<\omega, D\in\mc D_i\}
+    \]
+  where $\pi_i$ is the natural projection from 
+  $\left(\prod_{i<\omega}X_i\right)^2$ onto $X_i^2$. (See Bell.)
+
+  For $p\in \left(\prod_{i<\omega}X_i\right)^\omega$, let $p_i\in X_i^\omega$
+  such that $p_i(n)=p(n)(i)$.
+
+  Let $\sigma_i\circ L$ witness $\pl D\limitwin \proxgame{X_i}$ for
+  $i<\omega$, and assume without loss of generality that 
+  $\sigma_i\circ L$ always yields $X_i^2$ before round $i$.
+
+  Then we define the strategy $\tau\circ L$ for $\pl D$ in
+  $\proxgame{\prod_{i<\omega}X_i}$ as follows:
+    \[
+      \tau\circ L(p\rest n)
+        =
+      \bigcap_{i\leq n} \pi_i^{-1}(\sigma_i\circ L(p_i\rest n))
+    \]
+
+  Let $p$ attack $\tau\circ L$. If
+    $
+      \bigcap_{n<\omega}
+      \left(\bigcap_{m\leq n}\sigma_i(p_i\rest n)\right)[p_i(n)]
+      = \emptyset
+    $
+  for any $i<\omega$, it easily follows that 
+    $
+      \bigcap_{n<\omega}
+      \left(\bigcap_{m\leq n}\tau(p\rest n)\right)[p(n)]
+      = \emptyset
+    $.
+
+  Otherwise, we assume that for each $i<\omega$, $p_i$ converges to some
+  $x_i\in X_i$. Thus $p$ converges to $x=\<x_0,x_1,\dots\>$.
+\end{proof}
+
+Note: I expect I should be able to do some clever things 
+assuming $S(\kappa,\omega,\omega)$ to get a similar result for sigma
+products of dimension $\kappa$.
+
+\begin{ex}
+  $\pl D \markwin \proxgame{(\oneptcomp\kappa)^\omega}$
+\end{ex}
+
+\begin{proof}
+  $\pl D \tactwin \proxgame{\oneptcomp\kappa}$ + previous result
+\end{proof}
+
+\newpage
+
+\begin{lem}
+  $\pl O\prewin\clusgame{X}{S}$ if and only if $\pl O\prewin\congame{X}{S}$.
+\end{lem}
+
+\begin{proof}
+  Suppose that $\sigma$ is a predetermined winning strategy for 
+  $\clusgame{X}{S}$. Let $p$ attack $\sigma$, and $q$ be a subsequence of $p$.
+  It follows that $q$ also attacks $\sigma$, so $q$ clusters at $S$. Thus $p$
+  conveges to $S$, and $\sigma$ is a predetermined winning strategy for 
+  $\congame{X}{S}$.
+\end{proof}
+
+\begin{thm}
+  For any predetermined absolutely proximal space $X$, 
+  $\pl O\prewin \congame{X}{H}$ for all compact $H\subseteq X$.
+\end{thm}
+
+\begin{proof}
+  Let $\sigma(n)$ be a winning predetermined strategy for $\pl D$ in the 
+  absolutely proximal game such that 
+  $\sigma(n+1)\subseteq \sigma(n)$.
+  For a given tree $T$, let $\max(T)$ denote its maximal nodes.
+
+  \bigskip
+
+  First we define $T(0)\subseteq \omega^{\leq 2}$.
+
+  \begin{itemize}
+    \item Let $\emptyset\in T(0)$.
+    \item Choose 
+      \[
+        m_{\emptyset}<\omega
+      \]
+      and for $i<m_{\emptyset}$ choose
+      \[
+        h_{\<i\>}\in H
+      \]
+      and for $i,j<m_{\emptyset}$ choose
+      \[
+        h_{\<i,j\>}
+          \in 
+        H\cap\cl{\frac{1}{4}\sigma(0)[h_{\<i\>}]}
+      \]
+      such that
+        \[
+          \left\{\frac{1}{4}\sigma(0)[h_{\<i\>}]:i<m_{\emptyset}\right\}
+        \]
+      is a cover for $H$ and such that for each $i<m_{\emptyset}$
+        \[
+          \left\{\frac{1}{4}\sigma(1)[h_{\<i,j\>}]:j<m_{\emptyset}\right\}
+        \]
+      is a cover for 
+      $H\cap\cl{\frac{1}{4}\sigma(0)[h_{\<i\>}]}$.
+    \item Let $\<i\>$ and $\<i,j\>$ be in $T(0)$ for $i,j<m_{\emptyset}$.
+  \end{itemize}
+
+  \bigskip
+
+  Now suppose $T(n)\subseteq \omega^{\leq 2n+2}$ is defined. 
+  We then define $T(n+1)\subseteq \omega^{\leq 2n+4}$ as follows:
+
+  \begin{itemize}
+    \item Let $T(n)\subseteq T(n+1)$.
+    \item For each $t\concat\<i,j\>\in\max(T(n))$, choose 
+        \[m_{t\concat\<i,j\>}<\omega\]
+        and for $k<m_{t\concat\<i,j\>}$ choose 
+          \[
+            h_{t\concat\<i,j,k\>}
+              \in 
+            H\cap \cl{\frac{1}{4}\sigma(2n+2)[h_{t\concat\<i,j\>}]}
+          \]
+        and for $k,l<m_{t\concat\<i,j\>}$ choose
+          \[
+            h_{t\concat\<i,j,k,l\>} 
+              \in 
+            H\cap\cl{\frac{1}{4}\sigma(2n+3)[h_{t\concat\<i,j,k\>}]}
+          \]
+        such that
+      \[
+        \left\{\frac{1}{4}\sigma(2n+2)[h_{t\concat\<i,j,k\>}]
+          :
+        k<m_{t\concat\<i,j\>}\right\}
+      \]
+    is a cover for $H\cap \cl{\frac{1}{4}\sigma(2n+1)[h_{t\concat\<i,j\>}]}$, 
+    and such that for each $k<m_{t\concat\<i,j\>}$
+      \[
+        \left\{\frac{1}{4}\sigma(2n+3)[h_{t\concat\<i,j,k\>}]:l<m_t\right\}
+      \]
+    is a cover for $H\cap\cl{\frac{1}{4}\sigma(2n+2)[h_{t\concat\<i,j,k\>}]}$.
+    \item For each $t\in\max(T(n))$ and each $i,j<m_t$, put $t\concat\<i\>$
+      and $t\concat\<i,j\>$ in $T(n+1)$.
+  \end{itemize}
+
+  \bigskip
+
+  We now define the predetermined strategy $\tau$ for $\pl O$ in 
+  $\clusgame{X}{H}$ such that:
+  \[
+    \tau(n) 
+      = 
+    \bigcup_{t\in\max(T(n))} 
+      \bigcap_{m<2n+2}
+        \frac{1}{4}\sigma(m)[h_{t\rest m+1}]
+  \]
+  noting that $\tau(n)=\bigcap_{m\leq n}\tau(m)$ by definition.
+
+  Since 
+  $\left\{\frac{1}{4}\sigma(2n+2)[h_{t\concat\<i\>}]:i<m_{t}\right\}$ is a cover
+  for $H\cap \frac{1}{4}\sigma(2n+1)[h_{t}]$, since \\
+  $\left\{\frac{1}{4}\sigma(2n+1)[h_{t\concat\<i,j\>}]:j<m_{t}\right\}$ is 
+  a cover for $H\cap \frac{1}{4}\sigma(2n)[h_{t\concat\<i\>}]$, and since
+  $\left\{\frac{1}{4}\sigma(0)[h_{\<i\>}]:i<m_{\emptyset}\right\}$ is a 
+  cover for $H$, it follows that $\tau(n)$ contains $H$ and is $\tau$ is
+  a legal strategy.
+
+  Let $p$ be an attack against $\tau$ such that 
+  $p(n)\in \tau(n)$. If we can construct an attack $q$ 
+  against $\sigma$ which shares a subsequence of $p$, then $p$ must cluster
+  since $q$ must converge.
+  To find such a $q$, we construct a subtree $T'\subseteq T$.
+
+  We begin by setting $T'(0)=T(0)$.
+
+  For $n<\omega$, suppose $T'(n)\subseteq T(n)$ is defined such that:
+    \begin{itemize}
+      \item If $t'\concat\<i,j\>\in T'(n)$, then $|t'|\leq 2n$
+      \item If $s'\leq t'\in T'(n)$, then $s\in T'(n)$.
+      \item If $t'\in T'(n)\setminus\max(T'(n))$ and $|t'|$ is even,
+            then $t'\concat\<i,j\>\in T'(n)$ for $i,j<m_{t'}$.
+    \end{itemize}
+
+  Since $p(n)\in\tau(n)$, there exists some $t_n\in\max(T(n))$ such that
+  \[
+    p(n) 
+      \in
+    \bigcap_{m<2n+2}
+    \frac{1}{4}\sigma(m)[h_{t_n\rest m+1}]
+  \]
+  and in turn, there exists $t_n'\concat\<i,j\>\in\max(T'(n))$ 
+  with $t_n'\concat\<i,j\>\leq t_n$ and
+  \[
+    p(n)
+      \in
+    \bigcap_{m<|t_n'|+2}
+    \frac{1}{4}\sigma(m)[h_{t_n'\concat\<i,j\>\rest m+1}]
+  \]
+  since $|t_n'|\leq 2n$.
+
+  Let $p_{t_n'\concat\<i,j\>}=p(n)$
+
+  Take note that, in particular,
+  \[
+    p_{t_n'\concat\<i,j\>}
+      \in
+    \sigma(|t_n'|)[h_{t_n'\concat\<i\>}]
+  \]
+  and
+  \[
+    p_{t_n'\concat\<i,j\>}
+      \in
+    \frac{1}{4}\sigma(|t_n'|+1)[h_{t_n'\concat\<i,j\>}]
+  \]
+
+  We then define 
+  \[
+    T'(n+1)
+      =
+    T'(n)
+      \cup
+    \{t_n'\concat\<i,j,k\>: k\leq m_{t_n'\concat\<i,j\>}\}
+      \cup
+    \{t_n'\concat\<i,j,k,l\>: k,l\leq m_{t_n'\concat\<i,j\>}\}
+  \]
+  while noting that for all $k\leq m_{t_n'\concat\<i,j\>}$,
+  \[
+    h_{t_n'\concat\<i,j,k\>}
+      \in 
+    H\cap \cl{\frac{1}{4}\sigma(|t_n'|+2)[h_{t_n'\concat\<i,j\>}]}
+      \subseteq 
+    \frac{1}{2}\sigma(|t_n'|+1)[h_{t_n'\concat\<i,j\>}]
+  \]
+  and thus
+  \[
+    h_{t_n'\concat\<i,j,k\>}\in\sigma(|t_n'|+1)[p_{t_n'\concat\<i,j\>}]
+  \]
+
+  Finally, we let $T'=\bigcup_{n<\omega}T'(n)$. Since 
+  $T'$ is an infinite tree with finite levels, we may
+  pick an infinite branch $b$. From $b$, we construct the sequence
+  \[
+    q=\<h_{b\rest 1}, p_{b\rest 2}, h_{b\rest 3}, p_{b\rest 4}, \dots\>
+  \]
+  and claim it attacks $\sigma$ and thus must converge. If so, since 
+  $\<p_{b\rest2},p_{b\rest4},\dots\>$ is a subsequence of $p$, $p$ must
+  cluster. To see this, recall that for some $t_n'$:
+  \[
+    p_{b\rest2n+2} 
+      =
+    p_{t_n'\concat\<i,j\>}
+      \in
+    \sigma(|t_n'|)[h_{t_n'\concat\<i\>}]
+  \]
+  and
+  \[
+    h_{b\rest2n+3}
+      =
+    h_{t_n'\concat\<i,j,k\>}
+      \in
+    \sigma(|t_n'|+1)[p_{t_n'\concat\<i,j\>}]
+  \]
+
+  We have thus proven $\pl O\prewin\clusgame{X}{H}$, and thus
+  $\pl O\prewin\congame{X}{H}$.
+\end{proof}
+
+\newpage
+
+\begin{ex}
+  Let $X=I\times 2$ be the Alexandrov double interval. Then 
+  $\pl D \not\prewin \proxgame{X}$, but $\pl D \markwin \proxgame{X}$.
+\end{ex}
+
+\begin{proof}
+  We assume that the uniformity on $X$ is given by entourages 
+  \[
+    D(\epsilon,F) = 
+    \{\<x,0\>,\<y,0\>: |x-y|<\epsilon \}
+      \cup
+    \{\<x,1\>,\<y,0\>: |x-y|<\epsilon \vee x\not\in F\}
+  \]
+  \[
+      \cup
+    \{\<x,0\>,\<y,1\>: |x-y|<\epsilon \vee y\not\in F\}
+      \cup
+    \{\<x,1\>,\<y,1\>: x=y\}
+  \]
+
+  That is, points are $D(\epsilon,F)$-close if they are the same point, or 
+  the first coordinates are within $\epsilon$ of each other while neither 
+  second coordinate is in $F$.
+
+  Suppose $\pl D$ had a predetermined winning strategy 
+  $\sigma(n)=D(\epsilon_n,F_n)$. Then 
+  $\pl P$ can choose $x\not\in \bigcup_{n<\omega} F_n$, and play $\<x,1\>$ 
+  during even rounds, and $\<x_{2n+1},0\>$ where $|x-x_{2n+1}|<\epsilon_{2n}$
+  during odd rounds, preventing convergence.
+
+  However, assume $\pl D$ uses the Mark\"ov strategy 
+  $\sigma(x,n)=D(2^{-n},\{x\})$.
+  If $\pl P$ repeats a point of the form $\<x,1\>$, then since 
+  $D(2^{-n},\{x\})[\<x,1\>]=\{\<x,1\>\}$, $\pl P$ must repeat $\<x,1\>$ for
+  the rest of the game, and $\pl D$ wins. Otherwise, $\pl P$ cannot repeat 
+  points played in $I\times\{1\}$, and as the first
+  coordinates form a Cauchy sequence and converge to some $z$, any open set
+  about $\<z,0\>$ contains all but finitely many points of $\pl P$'s sequence,
+  and $\pl D$ wins.
+\end{proof}
+
+\begin{thm}
+  For any uniformly locally compact space $X$,
+      $\pl D\prewin \proxgame{X} \Leftrightarrow \pl D\prewin \aproxgame{X}$
+\end{thm}
+
+\begin{proof}
+  Let $M$ be a uniformly locally compact entourage. 
+  Let $\sigma$ witness $\pl D\prewin \proxgame{X}$ such that 
+  $\sigma(n)\subseteq M$ always 
+  (so $\cl{\sigma(a)[x]}\subseteq\cl{M[x]}$ is compact), 
+  $\sigma(n+1)\subseteq\frac{1}{4}\sigma(n)$.
+
+  Let $\tau(n)=\frac{1}{2}\sigma(n)$. If $p$ attacks $\tau$ in 
+  $\aproxgame{X}$, then
+    \[
+      p(n+1)
+        \in
+      \tau(n)[p(n)]
+        =
+      \frac{1}{2}\sigma(n)[p(n)]
+    \]
+
+    and for
+
+    \[
+      x
+        \in
+      \cl{\sigma(n+1)[p(n+1)]}
+        \subseteq
+      \cl{\frac{1}{4}\sigma(n)[p(n+1)]}
+        \subseteq
+      \frac{1}{2}\sigma(n)[p(n+1)]
+    \]
+
+  we can conclude $x\in\sigma(n)[p(n)]$. Thus
+
+    \[
+      \sigma(n+1)[p(n+1)]
+        \subseteq
+      \cl{\sigma(n+1)[p(n+1)]}
+        \subseteq
+      \sigma(n)[p(n)]
+    \]
+
+  Finally, note that $p$ attacks the winning strategy $\sigma$ in 
+  $\proxgame{X}$, but since the intersection of a chain of nonempty compact 
+  sets is nonempty:
+
+    \[
+      \bigcap_{n<\omega} \sigma(n)[p(n)]
+        =
+      \bigcap_{n<\omega} \cl{\sigma(n)[p(n)]}
+        \not=
+      \emptyset
+    \]
+
+  We conclude that $p$ converges.
+\end{proof}
 
 \begin{prop}
-The compact sets of a single-ultrafilter space are exactly the finite subsets of the space. Thus a single-ultrafilter space is neither locally compact nor $k$.
-\end{prop}
-
-Regardless of the ultrafilter chosen, we can see that $K$ has no hope of having a winning predetermined strategy for $G_{K,L}$ played on a single-ultrafilter space.
-
-\begin{prop}
-If $X$ is any single-ultrafilter space with the ultrafilter $\mathcal{F}$, then $K\not\prewin G_{K,L}(X)$.
+If $\pl D \prewin \proxgame{X}$, then $X$ has a $G_\delta$ diagonal.
 \end{prop}
@@
 \begin{proof}
-Compact sets are exactly finite sets in this space. Therefore, the difference of any two compact sets is compact.
-
-Give $K$ the predetermined strategy $\sigma(n)$.
-$H$ counters with \[H_n=(n\cup\sigma(n+1))\setminus\sigma(n)\] on turn $n$.
-Since any free ultrafilter contains only unbounded sets, every neighborhood $A\cup\{\mathcal{F}\}$ of $\mathcal{F}$ must intersect infinitely many $H_n$, defeating $\sigma$.
+  If $\pl D \prewin \proxgame{X}$ with strategy $\sigma$, then consider 
+  $\<x,y\>\in \bigcap_{n<\omega} \sigma(n)$. It follows that 
+  $\<x,y,x,y,\dots\>$ attacks $\sigma$, and 
+    $
+      \{x,y\}\subseteq \bigcap_{n<\omega} 
+      \sigma(n)[x]\cap\bigcap_{n<\omega}\sigma(n)[y]
+      \not=0
+    $ 
+  so it must converge, and $x=y$. Thus
+  $\bigcap_{n<\omega}\sigma(n) = \Delta$ is $G_\delta$.
 \end{proof}
 
-However, while it is consistant that there is an ultrafilter which defies the existance of a predetermined winning strategy for $K$ in $G_{K,P}$...
+\begin{ex}
+The Sorgenfrey line $S$ has a $G_\delta$ diagonal but $\pl P\win\proxgame{S}$.
+\end{ex}
 
-\begin{prop} 
-If a selective ultrafilter $\mathcal{F}$ exists (this is independent of ZFC), then $K$ has no winning predetermined strategy in the compact-point game $G_{K,P}(Y)$ for the single selective ultrafilter space $Y=\omega \cup \{\mathcal{F}\}$.
-\end{prop}
+\begin{cor}
+  For $X$ with uniformity $\mathbb{D}$ inducing the compact Hausdorff topology 
+  $\tau$, the following are equivalent:
+    \begin{enumerate}[(a)]
+      \item $\pl D \prewin \proxgame{X}$
+      \item $\pl D \prewin \aproxgame{X}$
+      \item $X$ has a $G_\delta$ diagonal
+      \item $\mathbb{D}$ is metrizable
+      \item $\tau$ is metrizable
+    \end{enumerate}
+\end{cor}
 
 \begin{proof}
-Let $\sigma$ be a predetermined strategy for $K$.
-By the definition of a selective ultrafilter, for every partition $\{B_n : n < \omega\}$ of subsets of $\omega$ such that $B_n \not\in \mathcal{F}$ for all $n$, there exists $A \in \mathcal{F}$ such that $|A \cap B_n|=1$ for all $n$.
-So then let \[B_n = \omega \cap \sigma(n) \setminus \sigma(n-1)\]
-
-Note that $B_n$ is finite and thus $B_n \not\in \mathcal{F}$, so there exists $A\in \mathcal{F}$ such that $|A \cap B_n|=1$.
-Let $p_n$ be the singleton in $A \cap B_{n+1}$, so $\{p_n : n < \omega\}$ is cofinite in $A$, and thus is also a member of $\mathcal{F}$.
-Thus $p_n$ converges to $\mathcal{F}$, and counters the strategy $\sigma$.
+  For compact Hausdorff spaces, it is well known that there is exactly one
+  uniformity inducing the topology. Thus $(d)\Leftrightarrow(e)$. Since $X$
+  is uniformly locally compact, $(a)\Leftrightarrow(b)$. Also, compact spaces
+  with a $G_\delta$ diagonal are metrizable, so $(c)\Rightarrow(e)$. 
+  Bell noted $(d)\Rightarrow(a)$ 
+  for arbitrary uniform spaces, and the previous proposition shows
+  $(a)\Rightarrow(c)$.
 \end{proof}
 
-... in general we can find many ultrafilters for which $K\prewin G_{K,P}$.
-
 \begin{thm}
-Let $a_n$ be a sequence such that the sequence $\frac{a_n}{n}$ is unbounded above.
-Then there is an ultrafilter $\mathcal{F}$ such that $\sigma(n)=(\sum_{m\leq n} a_m )\cup \{\mathcal{F}\}$ is a winning predetermined strategy for $K$ in $G_{K,P}(\omega\cup\{\mathcal{F}\})$.
+  A uniformly locally compact space with a $G_\delta$ diagonal is metrizable.
 \end{thm}
@@
 \begin{proof}
-Let $\mathcal{P}$ be the collection of all legal plays by $P$ against the strategy $\sigma$.
-Consider a finite collection of plays $P_0,\dots,P_{n-1}\in \mathcal{P}$.
-As $\frac{a_m}{m}$ is unbounded above, we may find infinitely many $m$ such that $\frac{a_m}{m}>n \Rightarrow mn<a_m$.
-As the $a_m$ partition $\omega$ such that $P$ may only play at most $m$ points in each part, there are infinitely many parts which are not filled, and thus $\bigcup_{m<n} P_m$ is not cofinite.
+  Based on several folklore results.
 
-It then follows that the closure of $\mathcal{P}$ under finite unions and subsets, along with all finite sets, is an ideal.
-Its dual filter may then be extended to an ultrafilter $\mathcal{F}$ such that every possible play by $P$ is the complement of some member of $\mathcal{F}$.
+  Uniformly locally compact implies the topological sum of $\sigma$-compact
+  spaces implies paracompact. Locally compact plus $G_\delta$ diagonal implies
+  locally metrizable. Locally metrizable plus paracompact characterizes
+  metrizable.
 \end{proof}
 
-So we can see that there are non-$k$ spaces $X$ for which $K\prewin G_{K,P}(X)$. However, we have found no such spaces for the game $G_{K,L}(X)$. So we conclude with this open question:
+\begin{cor}
+  If $X$ is uniformly locally compact, then $\pl D \prewin \proxgame{X}$ 
+  implies $X$'s topology is metrizable.
+\end{cor}
 
-\begin{ques}
-$K \prewin G_{K,L}(X) \Rightarrow X$ is a $k$-space?
-\end{ques}
-
-\section{Cantor space example}
+\newpage
 
 \begin{ex}
-Let $X$ be a zero-dimensional, compact L-space (hereditarally Lindeloff and non-separable).
-It is a fact that there exists a point-countable collection $\mathcal{U}=\{U_\alpha : \alpha<\omega_1\}$ of clopen sets in $X$, and it is also true that any point-finite subcollection of $\mathcal{U}$ is countable.
-%That is, if we let $A_x = \{\alpha : x \in U_\alpha\}$, then $|A_x|\leq\omega$ for all $x\in X$.
-
-Let $C = \{c_\alpha : \alpha <\omega_1\}$ be any uncountable subset of the Cantor space $2^\omega$. Let $X_s = X \times \{s\}$ for each $s \in 2^{<\omega}$, and $U_{\alpha,s} = U_\alpha \times \{s\}$.
-
-Finally, let \[\mathbb{X} = C \cup \bigcup_{s\in 2^{<\omega}} X_s\] be a tree of $2^{<\omega}$ copies of $X$, and where \[c_\alpha \cup \bigcup_{n < \omega} U_{\alpha, x_\alpha \restriction n}\] is an open set about each $c_\alpha$.
-\end{ex}
-
-\begin{defn}
-Let $S\in[\omega_1]^{<\omega}$ and $m<\omega$. Define 
-    \[K_S = \bigcup_{\alpha \in S} \left( c_\alpha \cup \left(\bigcup_{s < c_\alpha} U_{\alpha,s}\right)\right)\] 
-    \[ A = \{z^\frown \<1\> : z \in 1^{<\omega}\}\] 
-    \[ K^*_S = K_S \setminus \bigcup_{s \in A} X_s \] 
-and 
-    \[L_m = \bigcup_{s \in 2^{<m}} X_s\] 
-and observe that every compact set is dominated by $K^*_S \cup L_m$ for some $S,m$.
-Intuitively, $K^*_S$ collects the branches of $U_\alpha$ converging up to $c_\alpha$ for each $\alpha \in S$ while avoiding copies $X_s$ of $X$ for each $s$ in an antichain $A$, and $L_m$ collects the copies $X_s$ of $X$ with $|s| < m$ at the base of the tree.
-\end{defn}
-
-\begin{prop}
-Without loss of generality, $P$ always plays points in $\bigcup_{s \in 2^{<\omega}} X_s$.
-\end{prop}
-
-\begin{prop}
-$K \win \lfkpgame{\mathbb{X}}$.
-\end{prop}
-
-\begin{proof}
-In response to a point $\<x,s\>$, $K$ observes that there are only countably many $\alpha$ such that $U_\alpha \times \{s\}$ contains $\<x,s\>$ (by point-countability of $X$).
-Enumerate these as $\alpha_n$.
-$K$ makes a promise that during round $m$, $K$ will forbid some superset of $K_{\{\alpha_n : n\leq m\}}$.
-Finally, $K$ also always forbids a superset of $L_{|s|+1}$.
-
-Suppose $P$'s moves clustered at some point.
-Since $K$ forbade $L_{|s|+1}$ during each round, that point must be $c_\alpha$ for some $\alpha$.
-$P$'s play then must have included a subsequence of points $\<x_0,s_0\>,\<x_1,s_1\>,\<x_2,s_2\>\dots$ such that $x_n \in U_\alpha$ and $s_n \leq s_{n+1} \leq c_\alpha$.
-However, in response to $\<x_0,s_0\>$, $K$ made a promise to eventually forbid a superset of $K_{\{\alpha\}}$, making every $\<x_n,t_n\>$ illegal after that round.
-\end{proof}
-
-\begin{thm}
-$K\not\tactwin\lfkpgame{\mathbb{X}}$.
-\end{thm}
-
-\begin{proof}
-This is actually a corollary of G's theorem in [?]. The following is a direct game-theoretic proof.
-
-Suppose that $\sigma(\<x,s\>)$ was a winning strategy for $K$ and assume 
-  \[
-    \sigma(\<x,s\>) = \bigcup_{|t|\leq |s|} \sigma(\<x,t\>) = \sigma'(x,|s|)
-  \]
-Thus there exists some $f: \omega_1 \to \omega$ such that $\sigma'(x,f(\alpha))$ covers every neighborhood of $c_\alpha$ for all $x\in U_\alpha$.
-(If not, $P$ wins by taking the $\alpha$ for which $f$ is not defined, and may always play $\<x,s\>$ in a neighborhood of $c_\alpha$ for which $\sigma'(x,|s|)$ doesn't cover a neighborhood of $c_\alpha$.) Fix $n$ for which $f(\alpha)=n$ for $\alpha$ in an uncountable set $A$.
-
-Since the collection $\{U_\alpha : \alpha \in A\}$ is uncountable, it is not point-finite.
-Fix $x$ so that $x$ belongs to $U_\alpha$ for all $\alpha$ in an infinite $B \subseteq A$.
-Finally, consider $\sigma'(x,n)$.
-For each $\alpha\in B$, $\sigma'(x,f(\alpha))=\sigma'(x,n)$ covers $c_\alpha$.
-Since $\{c_\alpha : \alpha \in B\}$ is a closed infinite discrete set, we have a contradiction to the compactness of $\sigma'(x,n)$.
-\end{proof}
-
-\begin{thm}
-$K\not\ktactwin{2}\lfkpgame{\mathbb{X}}$.
-\end{thm}
-
-\begin{proof}
-Suppose $\sigma(\<x,s\>,\<y,t\>)$ was a winning 2-tactical strategy. We may define $S(x,y,n)\in [\omega_1]^{<\omega}$ (increasing on $n$) and $n<m(x,y,n)<\omega$ such that for each $(x,y)$,
-  \[
-    \bigcup_{s,t \in 2^{\leq n}} \sigma(\<x,s\>,\<y,t\>) \subseteq 
-    K^*_{S(x,y,n)} \cup L_{m(x,y,n)}
-  \]
-and so we assume
-  \[
-    \sigma(\<x,s\>,\<y,t\>) =
-    K^*_{S(x,y,\max(|s|,|t|))} \cup L_{m(x,y,\max(|s|,|t|))}
-  \]
-
-Select an arbitrary point $x' \in X$. We define a tactical strategy 
-  \[
-  \tau(x,s) = 
-  K^*_{S(x,x',m(x,x',|s|)+1)} \cup L_{m(x,x',m(x,x',|s|)+1)}
-  \]
-We complete the proof by showing $\tau$ is a winning tactical strategy (a contradiction).
-
-Suppose
-\[
-\<x_0, s_0\>, \<x_1, s_1\>, \<x_2, s_2\>, \dots
-\]
-successfully countered $\tau$ by clustering at $c\in C$ (the strategy trivially prevents clustering elsewhere). Let $z_n = \<0,\dots,0\>$ with $n$ zeros. We claim
-\[
-\<x_0, s_0\>, \<x', {z_{m(x_0,x',|s_0|)}}^\frown\<1\>\>, \<x_1, s_1\>, \<x', {z_{m(x_1,x',|s_1|)}}^\frown\<1\>\>,  \<x_2, s_2\>, \<x', {z_{m(x_2,x',|s_2|)}}^\frown\<1\>\>, \dots
-\]
-is a successful counter to $\sigma$.
-
-We will need the fact that, as $\<x_{i+1},s_{i+1}\>$ was legal against $\tau$:
-  \[
-    |s_i| <
-    m(x_i,x',|s_i|)+1 =
-    |{z_{m(x_i,x',|s_i|)}}^\frown\<1\>| 
-  \]
-  \[
-    <
-    m(x_i,x',m(x_i,x',|s_i|)+1) =
-    m(x_i,x',|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|) \leq
-    |s_{i+1}|
-  \]
-
-Note that $m(x,y,\max(|s|,|t|))$ is increasing throughout this play of the game versus $\sigma$:
-  \[
-    m(x_i,x',\max(|s_i|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|))
-  \]
-  \[
-    =
-    m(x_i,x',|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|)
-  \]
-  \[
-    \leq
-    |s_{i+1}| 
-  \]
-  \[
-    <
-    m(x_{i+1},x',|s_{i+1}|)
-  \]
-  \[
-    =
-    m(x_{i+1},x',\max(|s_{i+1}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|))
-  \]
-  \[
-    =
-    |{z_{m(x_{i+1},x',|s_{i+1}|)}}|
-  \]
-  \[
-    <
-    |{z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>|
-  \]
-  \[
-    <
-    m(x_{i+1},x',|{z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>|)
-  \]
-  \[
-    =
-    m(x_{i+1},x',\max(|s_{i+1}|,|{z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>|))
-  \]
-
-We turn to showing that $\<x', {z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>\>$ is always a legal move.
-Since ${z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>$ is on the antichain avoided by any $K^*$, the problem is reduced to showing that this move isn't forbidden by
-  \[
-  L_{m(x_{i+1},x',\max(|s_{i+1}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|))}
-  \]
-which we can see here:
-  \[
-    m(x_{i+1},x',\max(|s_{i+1}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|)) =
-    m(x_{i+1},x',|s_{i+1}|) <
-    |{z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>|
-  \]
-
-We can conclude by showing that $\<x_{i+1},s_{i+1}\>$ is always a legal move. We can see it avoids 
-  \[
-  L_{m(x_{i},x',\max(|s_{i}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|))}
-  \]
-since
-  \[
-    m(x_{i},x',\max(|s_{i}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|)) =
-    m(x_{i},x',|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|) \leq
-    |s_{i+1}|
-  \]
-
-Since $\<x_{i+1},s_{i+1}\>$ was legal against $\tau$, it avoided
-  \[
-    K^*_{S(x_h,x',m(x_h,x',|s_h|)+1)} = 
-    K^*_{S(x_h,x',\max(|s_h|,|{z_{m(x_h,x',|s_h|)}}^\frown\<1\>|))}
-  \]
-for $h\leq i$. And when $h<i$, we see it avoids:
-  \[
-    K^*_{S(x_{h+1},x',\max(|s_{h+1}|,|{z_{m(x_h,x',|s_h|)}}^\frown\<1\>|))} =
-    K^*_{S(x_{h+1},x',|s_{h+1}|)}
-  \]
-  \[
-    \subseteq
-    K^*_{S(x_{h+1},x',m(x_{h+1},x',|s_{h+1}|)+1)}
-  \]
-
-This concludes the proof.
-\end{proof}
-
-\begin{thm}
-$K\not\ktactwin{k}\lfkpgame{\mathbb{X}}$.
-\end{thm}
-
-\begin{proof}
-The proof proceeds in parallel to the proof of $K\not\ktactwin{2}\lfkpgame{\mathbb{X}}$.
-
-Suppose $\sigma(\<x_0,s_0\>,\dots,\<x_{k},s_{k}\>)$ was a winning $(k+1)$-tactical strategy.
-We may define $S(x_0,\dots,x_{k},n)\in [\omega_1]^{<\omega}$ (increasing on $n$) and $n<m(x_0,\dots,x_{k},n)<\omega$ such that for each $(x_0,\dots,x_{k})$,
-  \[
-    \bigcup_{s_0,\dots,s_k \in 2^{\leq n}} \sigma(\<x_0,s_0\>,\dots,\<x_{k},s_{k}\>) \subseteq 
-    K^*_{S(x_0,\dots,x_{k},n)} \cup L_{m(x_0,\dots,x_{k},n)}
-  \]
-and so we assume
-  \[
-    \sigma(\<x_0,s_0\>,\dots,\<x_{k},s_{k}\>) =
-    K^*_{S(x_0,\dots,x_{k},\max(|s_0|,\dots,|s_k|))} \cup L_{m(x_0,\dots,x_{k},\max(|s_0|,\dots,|s_k|))}
-  \]
-
-Select an arbitrary point $x' \in X$. Let $M^0(x,n)=m(x,x',\dots,x',n)$ and $M^{i+1}(x,n)=M^0(x,M^i(x,n)+1)$. We define a tactical strategy 
-  \[
-  \tau(x,s) = K^*_{S(x,x',\dots,x',M^{k-1}(x,|s|)+1)} \cup L_{m(x,x',\dots,x',M^{k-1}(x,|s|)+1)}
-  \]
-We complete the proof by showing $\tau$ is a winning tactical strategy (a contradiction).
-
-Suppose
-\[
-\<x_0, s_0\>, \<x_1, s_1\>, \<x_2, s_2\>, \dots
-\]
-successfully countered $\tau$ by clustering at $c\in C$ (the strategy trivially prevents clustering elsewhere). Let $z_n = \<0,\dots,0\>$ with $n$ zeros. We claim
-\[
-  \<x_0, s_0\>, 
-  \<x', {z_{M^0(x_0,|s_0|)}}^\frown\<1\>\>,
-  \<x', {z_{M^1(x_0,|s_0|)}}^\frown\<1\>\>, 
-  \dots, 
-  \<x', {z_{M^{k-1}(x_0,|s_0|)}}^\frown\<1\>\>,
-\]
-\[
-  \<x_1, s_1\>, 
-  \<x', {z_{M^0(x_1,|s_1|)}}^\frown\<1\>\>, 
-  \<x', {z_{M^1(x_1,|s_1|)}}^\frown\<1\>\>, 
-  \dots, 
-  \<x', {z_{M^{k-1}(x_1,|s_1|)}}^\frown\<1\>\>, 
-  \dots
-\]
-is a successful counter to $\sigma$.
-
-We will need the fact that, as $\<x_{i+1},s_{i+1}\>$ was legal against $\tau$:
-  \[
-    |s_i| <
-    M^0(x_i,|s_i|)+1 =
-    |{z_{M^0(x_i,|s_i|)}}^\frown\<1\>| <
-    M^0(x_i,M^0(x_i,|s_i|)+1)+1 
-  \]
-  \[
-    =
-    M^1(x_i,|s_i|)+1 =
-    |{z_{M^1(x_i,|s_i|)}}^\frown\<1\>| <
-    \dots <
-    |{z_{M^{k-1}(x_i,|s_i|)}}^\frown\<1\>| 
-  \]
-  \[
-    =
-    M^{k-1}(x_i,|s_i|) + 1 <
-    m(x_i,x',\dots,x',M^{k-1}(x_i,|s_i|)+1) \leq
-    |s_{i+1}|
-  \]
-
-Note that $m(x_0,\dots,x_{k},\max(|s_0|,\dots,|s_k|))$ is increasing throughout this play of the game versus $\sigma$:
-  \[
-    m(x_i,x',\dots,x',\max(|s_i|,|{z_{M^0(x_i,|s_i|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_i,|s_i|)}}^\frown\<1\>|))
-  \]
-  \[
-    =
-    m(x_i,x',\dots,x',|{z_{M^{k-1}(x_i,|s_i|)}}^\frown\<1\>|)
-  \]
-  \[
-    =
-    m(x_i,x',\dots,x',M^{k-1}(x_i,|s_i|)+1)
-  \]
-  \[
-    \leq
-    |s_{i+1}| 
-  \]
-  \[
-    <
-    M^0(x_{i+1},|s_{i+1}|)
-  \]
-  \[
-    =
-    m(x_{i+1},x',\dots,x',|s_{i+1}|)
-  \]
-  \[
-    =
-    m(x_{i+1},x',\dots,x',\max(|s_{i+1}|,|{z_{M^0(x_i,|s_i|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_i,|s_i|)}}^\frown\<1\>|))
-  \]
-  \[
-    =
-    |{z_{m(x_{i+1},x',\dots,x',|s_{i+1}|)}}|
-  \]
-  \[
-    =
-    |{z_{M^0(x_{i+1},|s_{i+1}|)}}|
-  \]
-  \[
-    <
-    |{z_{M^0(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|
-  \]
-  \[
-    <
-    m(x_{i+1},x',\dots,x',|{z_{M^0(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|)
-  \]
-  \[
-    =
-    m(x_{i+1},x',\dots,x',\max(|s_{i+1}|,|{z_{M^0(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|,|{z_{M^1(x_{i},|s_{i}|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_{i},|s_{i}|)}}^\frown\<1\>|))
-  \]
-  \[
-    \vdots
-  \]
-  \[
-    <
-    m(x_{i+1},x',\dots,x',\max(|s_{i+1}|,|{z_{M^0(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|))
-  \]
-
-We turn to showing that $\<x', {z_{M^j(x_{i+1},|s_{i+1}|)}}^\frown\<1\>\>$ is always a legal move.
-Since ${z_{M^j(x_{i+1},|s_{i+1}|)}}^\frown\<1\>$ is on the antichain avoided by any $K^*$, the problem is reduced to showing that this move isn't forbidden by
-  \[
-    L_{m(x_{i+1},x',\dots,x',\max(|s_{i+1}|,|{z_{M^0(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|,\dots,|{z_{M^{j-1}(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|,|{z_{M^{j}(x_{i},|s_{i}|)}}^\frown\<1\>|,\dots,|{z_{M^{k}(x_{i},|s_{i}|)}}^\frown\<1\>|))}
-  \]
-  \[
-    =
-    L_{m(x_{i+1},x',\dots,x',|{z_{M^{j-1}(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|)}
-  \]
-which we can see here:
-  \[
-    m(x_{i+1},x',\dots,x',|{z_{M^{j-1}(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|)
-  \]
-  \[
-    =
-    m(x_{i+1},x',\dots,x',M^{j-1}(x_{i+1},|s_{i+1}|)+1)
-  \]
-  \[
-    =
-    M^0(x_{i+1},M^{j-1}(x_{i+1},|s_{i+1}|)+1)
-  \]
-  \[
-    =
-    M^j(x_{i+1},s_{i+1})
-  \]
-  \[
-    <
-    |{z_{M^j(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|
-  \]
-
-We can conclude by showing that $\<x_{i+1},s_{i+1}\>$ is always a legal move. We can see it avoids 
-  \[
-  L_{m(x_{i},x',\dots,x',\max(|s_{i}|,|{z_{M^0(x_i,|s_i|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_i,|s_i|)}}^\frown\<1\>|))}
-  \]
-since
-  \[
-    m(x_{i},x',\dots,x',\max(|s_{i}|,|{z_{M^0(x_i,|s_i|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_i,|s_i|)}}^\frown\<1\>|))
-  \]
-  \[
-    =
-    m(x_{i},x',\dots,x',|{z_{M^{k-1}(x_i,|s_i|)}}^\frown\<1\>|)
-  \]
-  \[
-    =
-    m(x_{i},x',\dots,x',M^{k-1}(x_i,|s_i|)+1)
-  \]
-  \[
-    \leq
-    |s_{i+1}|
-  \]
-
-Since $\<x_{i+1},s_{i+1}\>$ was legal against $\tau$, it avoided
-  \[
-    K^*_{S(x_h,x',\dots,x',M^{k-1}(x_h,|s_h|)+1)} 
-  \]
-  \[
-    = 
-    K^*_{S(x_h,x',\dots,x',\max(|s_h|,|{z_{M^{0}(x_h,|s_h|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_h,|s_h|)}}^\frown\<1\>|))}
-  \]
-for $h\leq i$. And when $h<i$, we see it avoids both:
-  \[
-    K^*_{S(x_{h+1},x',\dots,x',\max(|s_{h+1}|,|{z_{M^0(x_{h+1},|s_{h+1}|)}}^\frown\<1\>|,\dots,|{z_{M^{j-1}(x_{h+1},|s_{h+1}|)}}^\frown\<1\>|,|{z_{M^{j}(x_{h},|s_{h}|)}}^\frown\<1\>|,\dots,|{z_{M^{k}(x_{h},|s_{h}|)}}^\frown\<1\>|))}
-  \]
-  \[
-    =
-    K^*_{S(x_{h+1},x',\dots,x',|{z_{M^{j-1}(x_{h+1},|s_{h+1}|)}}^\frown\<1\>|)}
-  \]
-  \[
-    =
-    K^*_{S(x_{h+1},x',\dots,x',M^{j-1}(x_{h+1},|s_{h+1}|)+1)}
-  \]
-  \[
-    \subseteq
-    K^*_{S(x_{h+1},x',\dots,x',M^{k-1}(x_{h+1},|s_{h+1}|)+1)}
-  \]
-and:
-  \[
-    K^*_{S(x_{h+1},x',\dots,x',\max(|s_{h+1}|,|{z_{M^0(x_{h},|s_{h}|)}}^\frown\<1\>|,\dots,|{z_{M^{k}(x_{h},|s_{h}|)}}^\frown\<1\>|))} 
-  \]
-  \[
-    =
-    K^*_{S(x_{h+1},x',\dots,x',|s_{k+1}|)}
-  \]
-  \[
-    \subseteq
-    K^*_{S(x_{h+1},x',\dots,x',M^{k-1}(x_{h+1},|s_{h+1}|)+1)}
-  \]
-
-This concludes the proof.
-\end{proof}
-
-\section{various examples}
-
-\begin{ex}
-If $\mathcal{F}$ is a free ultrafilter on $\omega$, let $L(\mathcal{F})=\omega \cup \{\mathcal{F}\}$ as a subspace of the Stone-Cech compactification $\beta\omega$ be the \textbf{single ultrafilter line}.
-There is some ultrafilter $\mathcal{F}$ such that $K \prewin \lfkpgame{L(\mathcal{F})}$ and $K \tactwin \lfkpgame{L(\mathcal{F})}$.
-
-($L(\mathcal{F})$ is not compactly generated, and thus not locally compact.)
+  Let $R$ be the Michael Line. Then $\pl P\win \proxgame{X}$.
 \end{ex}
@@
 \begin{proof}
-Let $a_n$ be a sequence such that the sequence $\frac{a_n}{n}$ is unbounded above.
-Then there is an ultrafilter $\mathcal{F}$ such that $\sigma(n)=(\sum_{m\leq n} a_m )\cup \{\mathcal{F}\}$ is a winning predetermined strategy for $K$ in $\lfkpgame{L(\mathcal{F})}$.
+  During round $0$, $\pl P$ may choose $m(0)=0$ and $p(0)=1$, 
+  and during round $n+1$,
+  $\pl P$ may choose $m(n+1)>m(n)$ and
+  $p(n+1)=p(n)+\frac{1}{10^{m(n+1)}}$ such that $p$ is a legal attack.
 
-Let $\mathcal{P}$ be the collection of all legal plays by $P$ against the strategy $\sigma$.
-Consider a finite collection of plays $P_0,\dots,P_{n-1}\in \mathcal{P}$.
-As $\frac{a_m}{m}$ is unbounded above, we may find infinitely many $m$ such that $\frac{a_m}{m}>n \Rightarrow mn<a_m$.
-As the $a_m$ partition $\omega$ such that $P$ may only play at most $m$ points in each part, there are infinitely many parts which are not filled, and thus $\bigcup_{m<n} P_m$ is not cofinite.
-
-It then follows that the closure of $\mathcal{P}$ under finite unions and subsets, along with all finite sets, is an ideal.
-Its dual filter may then be extended to an ultrafilter $\mathcal{F}$ such that every possible play by $P$ is the complement of some member of $\mathcal{F}$, making $\sigma$ a winning predetermined strategy.
-
-A winning tactic can then be easily constructed by using the moves by $P$ as the round number in the predetermined strategy.
+  It follows that $p$ ``converges'' to 
+  $x=\sum_{n<\omega}\frac{1}{10^{m(n)}}$, except $x$ is an irrational
+  number composed of $1$s separated by strings of $0$s of strictly
+  increasing size.
 \end{proof}
@@
 \begin{ex}
-Let $T(\mathcal{F}) = 2^{\leq\omega}$ where $2^{<\omega}$ is discrete and for each $c\in 2^\omega$, $\{c \restriction \alpha : \alpha \leq \omega\}$ is homeomorphic to $L(\mathcal{F})$.
-This is called the \textbf{single ultrafilter tree}.
-There is some ultrafilter $\mathcal{F}$ such that $K \prewin \lfkpgame{L(\mathcal{F})}$ and $K \tactwin \lfkpgame{L(\mathcal{F})}$.
+  Let $\omega_1$ be given a ladder topology:
+    \begin{itemize}
+      \item All successor ordinals are isolated.
+      \item Strictly increasing sequences (ladders) $L_\alpha:\omega\to\alpha$ 
+            are defined for each limit ordinal $\alpha$ such that $L_\alpha$ converges to $\alpha$ in the order topology, and each limit
+            $\alpha$ is given neighborhoods of the form
+            $L(\alpha,m)=\{\alpha\}\cup\{L_\alpha(n):n\geq m\}$. 
+      \item $\omega_1=\bigcup_{\alpha\in\omega_1^L} L(\alpha,0)$
+    \end{itemize}
 
-($T(\mathcal{F})$ is not compactly generated, and thus not locally compact.)
+  Let 
+    \[
+      A(\alpha,n)
+        =
+      [L(\alpha,0)\setminus L(\alpha,n)]^1 
+        \cup
+      \{\oneptcomp\omega_1 \setminus (L(\alpha,0)\setminus L(\alpha,n))\}
+    \]
+    \[
+      B(\alpha)
+        =
+      \{L(\alpha,0), \oneptcomp\omega_1 \setminus L(\alpha,0)\}
+    \]
+
+  Finite refinements of $A(\alpha,n)$ and $B(\alpha)$ give partitions
+  witnessing a uniformization of the ladder topology.
+
+  Then $\proxgame{\oneptcomp\omega_1}$ is indetermined.
 \end{ex}
@@
 \begin{proof}
-Assume without loss of generality that $P$ does not play points in $2^\omega$.
+  $\pl D\not\win\proxgame{\oneptcomp\omega_1}$ since $\oneptcomp\omega_1$
+  isn't Corson compact.
 
-We use a winning predetermined strategy $\sigma^*(n)$ for $L(\mathcal{F})$ and let $\sigma(n) = \bigcup_{m \in \sigma^*(n)} 2^m$.
-Note that if $P$ has a counter which converges to some $c\in \,^\omega2$, then $P$ would have a counter within a single branch.
-Since each branch is homeomorphic to $L(\mathcal{F})$; this is impossible.
+  Let $\sigma$ be a perfect information strategy for $\pl P$.
 
-A winning tactic can then be easily constructed by using the moves by $P$, taking the level of the tree played upon as the round number in the predetermined strategy.
+  Let
+  \[
+    C(\sigma) 
+      = 
+    \{
+      \delta\in\omega_1^L
+        : 
+      \omega_1\setminus D[\infty] \subseteq \delta
+        \Rightarrow
+      \sigma(D) < \delta
+    \}
+  \]
+  and note that by the closing up lemma, $C(\sigma)$ is always club.
+
+  We define a counterattack for $\pl D$ with $D_0=D(F_0,0)$ and
+  $F_0=\emptyset$ as her 
+  initial move, and let $p_0=\sigma(D_0)$ be the initial move of $\pl P$. 
+  We fix $p_0<\delta_0<\delta_1<\dots\in C(\sigma)$ such that 
+  $\lim_{n\to\infty}\delta_n=\delta_\infty\in C$. Enumerate all the
+  limit ordinals $<\delta_n$ as $\alpha_{n,m}$ for $m<\omega$. Let
+  $i_n<\omega$ be the least integer such that 
+  $L_{\delta_\infty}(i_n)>\delta_n$.
+
+  If $D_0,\dots,D_n$ are the first $n$ moves of $\pl D$, and 
+  $p_0,\dots,p_n$ are the first $n$ moves of $\pl P$ determined by $\sigma$,
+  then we define
+    \[
+      D_{n+1} 
+        =
+      \bigwedge_{j\leq n}
+      \left(
+        A(\delta_j,n)
+          \wedge
+        B(\delta_j)
+      \right)
+        \wedge
+      \bigwedge_{j,k\leq n}
+      \left(
+        A(\alpha_{j,k},n)
+          \wedge
+        B(\alpha_{j,k})
+      \right)
+        \wedge
+      A(\delta_\infty,i_n)
+    \]
+
+  (TODO: show this is a winning counterattack)
 \end{proof}
-
-\begin{ex}
-Let $M = \omega^2 \cup \{\infty\}$ be the \textbf{metric fan} where $\omega^2$ is discrete and $\infty$ has neighborhoods of the form $M \setminus (n\times\omega)$ for any $n<\omega$.
-Then $K \not\win \lfkpgame{M}$.
-(In fact, $P \markwin \lfkpgame{M}$.)
-
-($M$ is not locally compact, but is compactly generated.)
-\end{ex}
-
-\begin{proof}
-For each compact set $C$ in $M$, there exists a minimal dominating function $f_C$ such that for each $(x,y)\in C\setminus\{\infty\}$, $f(x)> y$.
-
-So let $P$ respond to the move $C\in K[X]$ by $K$ on round $n$ with the point $p=(n,s_C)$ such that $s_C = \min(\{y<\omega : f_C(n) < y\}$.
-It is easy to see that $p_n\rightarrow \infty$, so $P$ has a winning Markov strategy.
-\end{proof}
-
-\begin{ex}
-Let $S = \omega^2 \cup \{\infty\}$ be the \textbf{sequential fan} where $\omega^2$ is discrete and $\infty$ has neighborhoods of the form $M \setminus \{(x,y) : x<f(y)\}$ for any $f:\omega\to\omega$.
-Then $K \prewin \lfkpgame{S}$ and $K\tactwin \lfkpgame{S}$.
-
-($S$ is not locally compact, but is compactly generated.)
-
-\end{ex}
-
-\begin{proof}
-Let $\sigma(n)=\omega\times(n+1) \cup \{\infty\}$.
-By defining $f(y)$ to be greater than the $x$-coordinate of all $P$'s plays through round $y$, we see that $M\setminus\{(x,y): x<f(y)\}$ misses every move by $P$, so $P$ cannot converge to $\infty$.
-
-A winning tactic can be easily constructed by using the $y$-coordinate of $P$'s moves as the round number in the predetermined strategy.
-\end{proof}

### 2014-05-14 phd/dissertation/chapter2.tex

@@
 but we will find it convenient to think of them in terms defined by
-Gale and Stewart. \cite{gale}
+Gale and Stewart. \cite{MR0054922}
 
@@
 As an illustration of an infinite game, we may consider a simple example due to
-Baker \cite{baker}.
+Baker \cite{noMRbaker}.
 
@@
 history of the Banacy-Mazur and other topological games may be found in
-Telgarsky's survey on the subject \cite{telgarsky}.
+Telgarsky's survey on the subject \cite{MR892457}.
 
@@
 The Borel Determinacy Theorem states that $G=\<M,W\>$ is determined whenever
-$W$ is a Borel subset of $M^\omega$ \cite{martin}. It's an easy corollary that
+$W$ is a Borel subset of $M^\omega$ \cite{MR0403976}. It's an easy corollary that
 all finite games are determined; $W$ must be clopen.
@@
 \begin{proof}
-  Adapted from \cite{baker}.
+  Adapted from \cite{noMRbaker}.
   Let $X=\{x_0,x_1,\dots\}$. Let $i(a,b)$ be the least integer such that
@@
 
+More informally, $\pl B$ can force a win by enumerating the countable set
+$X$ and playing every legal choice by the end of the game.
 This yields a classical result.
@@
 \begin{thm}
-$\pl E\not\win \bmgame{X}$ if and only if $X$ is a Baire space. \cite{haworth}
+$\pl E\not\win \bmgame{X}$ if and only if $X$ is a Baire space.
+\cite{MR0431104}
 \end{thm}
@@
 Those arrows may not be reversed. A Bernstein subset of the real line is an
-example of a Baire space which is not weakly $\alpha$-favorable, and
+example of a Baire space which is not weakly $\alpha$-favorable, and Gabriel
+Debs constructed an example of a completely regular space for which $\pl N$
+has a winning $2$-tactic, but lacks a winning $1$-tactic. \cite{MR817083}

### 2014-05-20 phd/dissertation/chapter2.tex
work on ch 3 intro

@@
 made an \term{illegal move} which contradicted the game's rules.
+Often, we will consider \term{legal playthoughs} where both players only
+made legal moves, in which case only the winning condition need be considered.
 
@@
 
+Often, we will build new strategies based on others.
+
+\begin{defn}
+  A strategy $\tau$ is a \term{strengthening} of another strategy $\sigma$
+  for a player if whenever the result of the game for $\sigma$ and an attack
+  $a$ by the opponent is a victory for the player, then the result of the game
+  for $\tau$ and $a$ is also a victory for the player.
+\end{defn}
+
+\begin{prop}
+  If $\sigma$ is a winning strategy, and $\tau$ strengthens $\sigma$,
+  then $\tau$ is also a winning strategy.
+\end{prop}
+
 \subsection{Applications of Strategies}
@@
 \begin{defn}
-  A \term{$k$-tactical strategy} or \term{$k$-tactic} is a limited information
-  strategy of the form $\sigma\circ\nu_k$.
+  A \term{$k$-tactical strategy} or \term{$k$-tactic} is a function
+  $\sigma:M^{\leq k}\to M$ yielding a corresponding strategy
+  $\sigma\circ\nu_k:M^{<\omega}\to M$.
 
-  A \term{$k$-Mark\"ov strategy} or \term{$k$-mark} is a limited information
-  strategy of the form $\sigma\circ\mu_k$.
+  A \term{$k$-Mark\"ov strategy} or \term{$k$-mark} is a function
+  $\sigma:M^{\leq k}\times\omega\to M$ yielding a corresponding strategy
+  $\sigma\circ\mu_k:M^{<\omega}\to M$.
 \end{defn}
@@
 number and does not rely on knowing which moves the opponent will make.
+Of course, a limited information strategy $\sigma$ is \term{winning} for a
+player if its corresponding strategy $\sigma\circ\nu_k$ or $\sigma\circ\mu_k$
+is winning for that player.
 
@@
 
-\begin{obs}
+\begin{prop}
   $X$ is $\alpha$-favorable
@@
   $X$ is Baire
-\end{obs}
+\end{prop}
 

### 2014-05-20 phd/dissertation/chapter3.tex
work on ch 3 intro

@@
 
-Results related to Gruenhage's ``W''-convergence game and variants.
+We begin by investigating a game due to Gary Gruenhage.
 
-(these are related to the ``hard'' version for $\pl O$ where $\pl P$
-need only play within the most recent open set)
+\begin{game}
+  Let $\congame{X}{S}$ denote the \term{$W$-convergence game} with
+  players $\pl O$, $\pl P$, for a topological space $X$ and $S\subseteq X$.
+
+  In round $n$, $\pl O$ chooses an open neighborhood $O_n\supseteq S$, followed
+  by $\pl P$ choosing a point $x_n\in \bigcap_{m\leq n}O_m$.
+
+  $\pl O$ wins the game if the points $x_n$ converge to the set $S$; that is,
+  for every open neighborhood $U\supseteq S$, $x_n\in U$ for
+  all but finite $n<\omega$.
+
+  If $S=\{x\}$ then we write $\congamehard{X}{x}$ for short.
+\end{game}
+
+(TODO: Any reason for the ``W''?)
+
+Gruenhage defined this game in his doctoral dissertation to define a class
+of spaces generalizing first-countability. \cite{MR0413049}
+
+\begin{defn}
+  The spaces $X$ for which $\pl O \win \congamehard{X}{x}$ for all $x\in X$ are
+  called \term{$W$-spaces}.
+\end{defn}
+
+In fact, using limited information strategies, one may characterize the
+first-countable spaces using this game.
+
+\begin{prop}
+  $X$ is first countable
+    if and only if
+  $\pl O \prewin \congamehard{X}{x}$ for all $x\in X$.
+\end{prop}
+
+\begin{proof}
+  The forward implication shows that all $W$ spaces are first-countable spaces,
+  and was proven in \cite{MR0413049}: if $\{U_n:n<\omega\}$ is a countable
+  base at $x$, let $\sigma(n)=\bigcap_{m\leq n} U_m$. $\sigma$ is easily seen
+  to be a winning predetermined strategy.
+
+  If $X$ is not first countable at some $x$, let $\sigma$ be a
+  predetermined strategy for $\pl O$ in $\congamehard{X}{x}$. There exists
+  an open neighborhood $U$ such that $U$ is not a subset of any $\sigma(n)$
+  (otherwise $\{\sigma(n):n<\omega\}$ would be a countable base at $x$).
+  Let $x_n$ be an element of $\sigma(n)\setminus U$ for all $n<\omega$.
+  Then $\<x_0,x_1,\dots\>$ is a winning counter-attack to $\sigma$ for $\pl P$,
+  so $\pl O$ lacks a winning predetermined strategy.
+\end{proof}
+
+At first glance, the difficulty of $\congame{X}{S}$ could be increased for
+$\pl O$ by only restricting the choices for $\pl P$ to be within the most
+recent open set played by $\pl O$, rather than all the previously played
+open sets.
+
+\begin{defn}
+  Let $\congame{X}{S}$ denote the \term{hard $W$-convergence game} which proceeds
+  as $\congamehard{X}{S}$, except that $\pl P$ need only play within $O_n$
+  rather than $\bigcap_{m\leq n}O_n$.
+\end{defn}
+
+Of course, this is normally easily circumvented.
+
+\begin{prop}
+  $\pl O \limitwin \congame{X}{S}$
+    if and only if
+  $\pl O \limitwin \congamehard{X}{S}$,
+  where $\limitwin$ is either $\win$ or $\prewin$.
+\end{prop}
+
+\begin{proof}
+  The backwards implication is immediate.
+
+  For the forward implication, let $\sigma$ be a winning predetermined
+  (perfect information) strategy, and $\lambda$ be $\mu_0$ (the identity).
+
+  We define a new predetermined (perfect information) strategy $\tau$ by
+    \[
+      \tau\circ\lambda(\<x_0,\dots,x_{n-1}\>)
+        =
+      \bigcap_{m\leq n}\sigma\circ\lambda(\<x_0,\dots,x_{m-1}\>)
+    \]
+  so that each move by $\pl O$ according to $\tau$ is the intersection of
+  $\pl O$'s previous moves. Then any attack against $\tau$ is an attack
+  against $\sigma$, and since $\sigma$ is a winning strategy, so is $\tau$.
+\end{proof}
+
+It's important to note that $\tau$ is only well-defined in the case
+$\lambda=\mu_0$ because the value of
+$\sigma\circ\lambda(\<x_0,\dots,x_{m-1}\>)$ does not rely on knowledge of the
+points $\<x_0,\dots,x_{m-1}\>$ for any $m\leq n$.
+The proof would be invalid if $\lambda$ was required to be, say,
+$\nu_{k+1}$, since the value of
+$\sigma\circ\nu_{k+1}(\<x_0,\dots,x_k\>)=\sigma(\<x_0,\dots,x_k\>)$
+could not be uniquely determined from
+$\nu_{k+1}(\<x_0,\dots,x_{k+1}\>)=\<x_1,\dots,x_{k+1}\>$.
+
+Due to the equivalency of the ``hard'' and ``normal'' variations of the
+convergence game in the perfect information case, most authors use them
+interchangibly. However, it is easy to find spaces for which the games are
+not equivalent when considering $k+1$-tactics and $k+1$-marks.
+
+In addition to the $W$-convergence games, we will also investigate
+``clustering'' analogs to both variations.
+
+\begin{game}
+  Let $\clusgame{X}{S}$ (resp. $\clusgamehard{X}{S}$) be a variation of
+  $\congame{X}{S}$ (resp. $\congamehard{X}{S}$) such that $x_n$ need only
+  cluster at $S$, that is, for every open neighborhood $U$ of $S$, $x_n\in U$
+  for infinitely many $n<\omega$.
+\end{game}
+
+Gruenhage noted that the clustering game is
+perfect-information equivalent to the convergence game for $\pl O$. This
+can easily be extended for some limited information cases as well.
+
+\begin{prop}
+  $\pl O \limitwin \congame{X}{S}$
+    if and only if
+  $\pl O \limitwin \clusgame{X}{S}$
+  where $\limitwin$ is any of $\win$, $\prewin$, $\tactwin$, or $\markwin$.
+\end{prop}
+
+\begin{proof}
+  For the perfect information case we refer to \cite{MR0413049}.
+
+  In the predetermined (resp. tactical) case, suppose that $\sigma$ is a
+  winning predetermined (resp. tactical) strategy for $\pl O$ in
+  $\clusgame{X}{S}$. Let $p$ be a legal attack against $\sigma$, and $q$ be a
+  subsequence of $p$. It's easily seen that $q$ is also a legal attack against
+  $\sigma$, so $q$ clusters at $S$. Since every subsequence of $p$ clusters
+  at $S$, $p$ converges to $S$, and $\sigma$ is a winning predetermined
+  (resp. tactical) strategy for $\pl O$ in $\congame{X}{S}$ as well.
+
+  In the final case, note that any Mark\"ov strategy $\sigma$ for $\pl O$ may be
+  strengthened by setting $\sigma'(x,n)=\bigcap_{m\leq n}\sigma(x,m)$.
+  So, suppose that $\sigma$ is a winning Mark\"ov strategy for $\pl O$ in
+  $\clusgame{X}{S}$ such that $\sigma(x,m)\supseteq\sigma(x,n)$ for all
+  $m\leq n$.
+
+  Let $p$ be a legal attack against $\sigma$, and $q$ be a subsequence of $p$.
+  For $m<\omega$, there exists $f(m)\leq m$ such that $q(m)=p(f(m))$. It follows
+  that
+    \[
+      q(n+1)
+        \in
+      \bigcap_{m\leq n}\sigma(q(m),m+1)
+        =
+      \bigcap_{m\leq n}\sigma(p(f(m)),m+1)
+    \]
+    \[
+        \subseteq
+      \bigcap_{m\leq n}\sigma(p(f(m)),f(m)+1)
+        \subseteq
+      \bigcap_{m\leq f(n)}\sigma(p(m),m+1)
+    \]
+  so $q$ is also a legal attack against $\sigma$. Since $\sigma$ is a winning
+  strategy, $q$ clusters at $S$, and since every subsequence of $p$ clusters
+  at $S$, $p$ must converge to $S$. Thus $\sigma$ is also a winning Mark\"ov
+  strategy for $\pl O$ in $\congame{X}{S}$ as well.
+\end{proof}
+
+(TODO: Maybe $k+2$ tacts/marks as well, but not as obvious if so.)
 
 \section{Fort spaces}
+
+Gruenhage suggested the one-point-compactification of a discrete space as
+an example of a $W$-space which is not first-countable.
+
+\begin{defn}
+  A \term{Fort space} $\oneptcomp\kappa=\kappa\cup\{\infty\}$ is defined
+  for each cardinal $\kappa$. Its subspace $\kappa$ is discrete, and the
+  neighborhoods of $\infty$ are of the form $\oneptcomp\kappa\setminus F$
+  for each $F\in[\kappa]^{<\omega}$.
+\end{defn}
 

### 2014-05-20 phd/dissertation/chapter3.tex
drafts for 3.0 and 3.1

@@
 
-  If $S=\{x\}$ then we write $\congamehard{X}{x}$ for short.
+  If $S=\{x\}$ then we write $\congame{X}{x}$ for short.
 \end{game}
@@
   predetermined strategy for $\pl O$ in $\congamehard{X}{x}$. There exists
-  an open neighborhood $U$ such that $U$ is not a subset of any $\sigma(n)$
+  an open neighborhood $U$ of $x$ which does not contain any $\sigma(n)$
   (otherwise $\{\sigma(n):n<\omega\}$ would be a countable base at $x$).
@@
 \begin{defn}
-  Let $\congame{X}{S}$ denote the \term{hard $W$-convergence game} which proceeds
-  as $\congamehard{X}{S}$, except that $\pl P$ need only play within $O_n$
-  rather than $\bigcap_{m\leq n}O_n$.
+  Let $\congamehard{X}{S}$ denote the \term{hard $W$-convergence game} which
+  proceeds as $\congame{X}{S}$, except that $\pl P$ need only choose
+  $x_n\in O_n$ rather than $x_n\in \bigcap_{m\leq n}O_m$ during each round.
 \end{defn}
 
-Of course, this is normally easily circumvented.
+This seemingly more difficult game for $\pl O$ is Gruenhage's original
+formulation. But with perfect information, there is no real difference for
+$\pl O$.
 
-\begin{prop}
+\begin{prop}\label{propNormalHardCon}
   $\pl O \limitwin \congame{X}{S}$
@@
   For the forward implication, let $\sigma$ be a winning predetermined
-  (perfect information) strategy, and $\lambda$ be $\mu_0$ (the identity).
+  (perfect information) strategy, and $\lambda$ be the $0$-Mark\"ov
+  fog-of-war $\mu_0$ (the identity).
 
@@
     \]
-  so that each move by $\pl O$ according to $\tau$ is the intersection of
-  $\pl O$'s previous moves. Then any attack against $\tau$ is an attack
-  against $\sigma$, and since $\sigma$ is a winning strategy, so is $\tau$.
+  so that each move by $\pl O$ according to $\tau\circ\lambda$ is the
+  intersection of $\pl O$'s previous moves. Then any attack against
+  $\tau\circ\lambda$ is an attack against $\sigma\circ\lambda$, and since
+  $\sigma\circ\lambda$ is a winning strategy, so is $\tau\circ\lambda$.
 \end{proof}
 
-It's important to note that $\tau$ is only well-defined in the case
-$\lambda=\mu_0$ because the value of
-$\sigma\circ\lambda(\<x_0,\dots,x_{m-1}\>)$ does not rely on knowledge of the
-points $\<x_0,\dots,x_{m-1}\>$ for any $m\leq n$.
-The proof would be invalid if $\lambda$ was required to be, say,
-$\nu_{k+1}$, since the value of
-$\sigma\circ\nu_{k+1}(\<x_0,\dots,x_k\>)=\sigma(\<x_0,\dots,x_k\>)$
-could not be uniquely determined from
-$\nu_{k+1}(\<x_0,\dots,x_{k+1}\>)=\<x_1,\dots,x_{k+1}\>$.
+Put another way, $\tau(n)=\bigcap_{m\leq n}\sigma(m)$ in the predetermined
+case, and
+$\tau(\<x_0,\dots,x_{n-1}\>)=\bigcap_{m\leq n}\sigma(\<x_0,\dots,x_{m-1}\>)$
+in the perfect information case.
+The original proof would have been invalid if $\lambda$ was required to be, say,
+the tactical fog-of-war $\nu_1$, since the value of $\pl O$'s own second move
+$\sigma\circ\nu_1(\<x_0\>)=\sigma(\<x_0\>)$
+could not be determined from the information she has during round
+$2$: $\nu_1(\<x_0,x_1\>)=\<x_1\>$.
 
 Due to the equivalency of the ``hard'' and ``normal'' variations of the
-convergence game in the perfect information case, most authors use them
-interchangibly. However, it is easy to find spaces for which the games are
-not equivalent when considering $k+1$-tactics and $k+1$-marks.
+convergence game in the perfect information case, many authors use them
+interchangibly. However, it is possible to find spaces for which the games are
+not equivalent when considering $k+1$-tactics and $k+1$-marks, as we will
+soon see.
 
@@
 \begin{game}
-  Let $\clusgame{X}{S}$ (resp. $\clusgamehard{X}{S}$) be a variation of
-  $\congame{X}{S}$ (resp. $\congamehard{X}{S}$) such that $x_n$ need only
+  Let $\clusgame{X}{S}$ ($\clusgamehard{X}{S}$) be a variation of
+  $\congame{X}{S}$ ($\congamehard{X}{S}$) such that $x_n$ need only
   cluster at $S$, that is, for every open neighborhood $U$ of $S$, $x_n\in U$
@@
 
-Gruenhage noted that the clustering game is
-perfect-information equivalent to the convergence game for $\pl O$. This
-can easily be extended for some limited information cases as well.
+This variation seems to make $\pl O$'s job easier, but Gruenhage noted that
+the clustering game is perfect-information equivalent to the convergence game
+for $\pl O$. This can easily be extended for some limited information cases
+as well.
 
@@
 
-  In the final case, note that any Mark\"ov strategy $\sigma$ for $\pl O$ may be
-  strengthened by setting $\sigma'(x,n)=\bigcap_{m\leq n}\sigma(x,m)$.
+  In the final case, note that any Mark\"ov strategy $\sigma'$ for $\pl O$ may
+  be strengthened to $\sigma$ defined by
+  $\sigma(x,n)=\bigcap_{m\leq n}\sigma'(x,m)$.
   So, suppose that $\sigma$ is a winning Mark\"ov strategy for $\pl O$ in
@@
   Let $p$ be a legal attack against $\sigma$, and $q$ be a subsequence of $p$.
-  For $m<\omega$, there exists $f(m)\leq m$ such that $q(m)=p(f(m))$. It follows
+  For $m<\omega$, there exists $f(m)\geq m$ such that $q(m)=p(f(m))$. It follows
   that
+    $
+      q(0)=p(f(0))
+        \in
+      \sigma(\emptyset,0)\cap \bigcap_{m\leq f(0)}\sigma(\<p(m)\>,m)
+        \subseteq
+      \sigma(\emptyset,0)
+    $
+  and
     \[
-      q(n+1)
-        \in
-      \bigcap_{m\leq n}\sigma(q(m),m+1)
-        =
-      \bigcap_{m\leq n}\sigma(p(f(m)),m+1)
-    \]
-    \[
-        \subseteq
-      \bigcap_{m\leq n}\sigma(p(f(m)),f(m)+1)
-        \subseteq
-      \bigcap_{m\leq f(n)}\sigma(p(m),m+1)
+      \begin{array}{rcl}
+        q(n+1)=p(f(n+1)) &
+          \in &
+        \displaystyle
+        \sigma(\emptyset,0)\cap \bigcap_{m<f(n+1)}\sigma(\<p(m)\>,m+1) \\ &
+          \subseteq &
+        \displaystyle
+        \sigma(\emptyset,0)\cap \bigcap_{m<n+1}\sigma(\<p(f(m))\>,f(m)+1) \\ &
+          = &
+        \displaystyle
+        \sigma(\emptyset,0)\cap \bigcap_{m<n+1}\sigma(\<q(m)\>,f(m)+1) \\ &
+          \subseteq &
+        \displaystyle
+        \sigma(\emptyset,0)\cap \bigcap_{m<n+1}\sigma(\<q(m)\>,m+1)
+      \end{array}
     \]
@@
 
+(TODO: It's feasible that $k$-limit $\Leftrightarrow$ $1$-limit for
+one variation or another.)
+
 \section{Fort spaces}
 
-Gruenhage suggested the one-point-compactification of a discrete space as
-an example of a $W$-space which is not first-countable.
+In his original paper, Gruenhage suggested the one-point-compactification of a
+discrete space as an example of a $W$-space which is not first-countable.
 
@@
 
+\begin{prop}\label{propFortTact}
+  $\pl O \tactwin \congame{\oneptcomp\kappa}{\infty}$ for all cardinals $\kappa$
+\end{prop}
+
+\begin{proof}
+  Let $\sigma(\emptyset)=\sigma(\<\infty\>)=\oneptcomp\kappa$ and
+  $\sigma(\<\alpha\>)=\oneptcomp\kappa\setminus\{\alpha\}$. Any legal attack
+  against the tactic $\sigma$ could not repeat non-$\infty$ points, so
+  it must converge to $\infty$.
+\end{proof}
+
+\begin{cor}
+  $\pl O \win \congamehard{\oneptcomp\kappa}{\infty}$ for all cardinals $\kappa$
+\end{cor}
+
+\begin{proof}
+  Propositions \ref{propNormalHardCon} and \ref{propFortTact}.
+\end{proof}
+
+Since it's trivial to show that $\pl O\prewin\congame{\oneptcomp\kappa}$ if and
+only if $\kappa\leq\omega$, this closes the question on limited information
+strategies for $\congame{\oneptcomp\kappa}{\infty}$. However, limited
+information analysis of the harder $\congamehard{\oneptcomp\kappa}{\infty}$
+is more interesting.
+
+Peter Nyikos noted Proposition \ref{propFortTact} and the following in
+\cite{MR1031771}.
+
 \begin{thm}
-$O\not\ktactwin{k}\clusgame{\oneptcomp{\omega_1}}{\infty}$.
+  $\pl O \not\markwin \congamehard{\oneptcomp\omega_1}{\infty}$.
 \end{thm}
 
+This actually can be generalized to any $k$-Mark\"ov strategy with just
+a little more bookkeeping.
+
 \begin{thm}
-$O\markwin \clusgame{\oneptcomp{\omega_1}}{\infty}$.
+  $\pl O \not\kmarkwin{k} \congamehard{\oneptcomp\omega_1}{\infty}$.
 \end{thm}
 
-\begin{thm}(Nyikos)
-$O\not\markwin \congame{\oneptcomp{\omega_1}}{\infty}$.
+\begin{proof}
+  Let $\sigma$ be a $k$-mark for $\pl O$. Since the set
+    \[
+      D_\sigma
+        =
+      \bigcap_{n<\omega,s\in \omega^{\leq k}}
+      \sigma(s,n)
+    \]
+  is co-countable, we may choose $\alpha_\sigma\in D_\sigma\cap\omega_1$.
+  Thus, we may choose $n_0<n_1<\dots<\omega$ such that
+    \[
+      \<n_0,\dots,n_{k-1},\alpha_\sigma,
+        n_k,\dots,n_{2k-1},\alpha_\sigma,
+        \dots\>
+    \]
+  is a legal counterattack, which fails to converge to $\infty$ since
+  $\alpha_\sigma$ is repeated infinitely often.
+\end{proof}
+
+However, while the clustering and convergence variants are equivalent
+for Mark\"ov strategies in the ``normal'' version of the $W$ game, they are
+\textit{not} equivalent in the ``hard'' version.
+
+\begin{thm}
+  $\pl O\markwin \clusgamehard{\oneptcomp\omega_1}{\infty}$.
 \end{thm}
 
+\begin{proof}
+  For each $\alpha<\omega_1$ let $A_\alpha=\<A_\alpha(0),A_\alpha(1),\dots\>$
+  be a countable sequence of finite sets such that
+  $A_\alpha(n)\subset A_\alpha(n+1)$ and
+  $\bigcup_{n<\omega}A_\alpha(n)=\alpha+1$.
+
+  We define the Mark\"ov strategy $\sigma$ by setting
+    \[
+      \sigma(\emptyset,0) = \sigma(\<\infty\>,n) = \oneptcomp\omega_1
+    \]
+  and for all $\alpha<\omega_1$ setting
+    \[
+      \sigma(\<\alpha\>,n) = \oneptcomp\omega_1 \setminus A_\alpha(n)
+    \]
+
+  Note that for any $\alpha_0<\dots<\alpha_{k-1}$, there is some $n<\omega$
+  such that
+  $\{\alpha_0,\dots,\alpha_{k-1}\}\subseteq A_{\alpha_i}(n)$ for all $i<k$.
+  Thus for any legal attack $p$ against $\sigma$, the range of $p$ cannot
+  be finite. Since the range of $p$ is infinite, every open neighborhood of
+  $\infty$ contains infinitely many points of $p$, so $p$ clusters at $\infty$.
+\end{proof}
+
+However, knowledge of the round number is critical.
+
 \begin{thm}
-$O\not\kmarkwin{k}\clusgame{\oneptcomp{\kappa}}{\infty}$ for $\kappa>\omega_1$.
+  $O\not\ktactwin{k}\clusgamehard{\oneptcomp\omega_1}{\infty}$.
 \end{thm}
 
-(TODO: It's feasible that $k$-limit $\Leftrightarrow$ $1$-limit.)
+\begin{proof}
+  Let $\sigma$ be a $k$-tactic for $\pl O$ in
+  $\clusgame{\oneptcomp\omega_1}{\infty}$. By the closing-up lemma, the set
+    \[
+      C_\sigma
+        =
+      \{
+        \alpha<\omega_1
+          :
+        s\in\alpha^{\leq k}
+          \Rightarrow
+        \oneptcomp\omega_1\setminus\sigma(s)
+        \subset \alpha
+      \}
+    \]
+  is closed and unbounded. Let $a_\sigma:\omega_1\to C_\sigma$ be an order
+  isomorphism.
 
-\section{Sigma-products}
+  Choose $n_0<\dots<n_{k-1}<\omega$ such that for each $i<k$:
+    \[
+      a_\sigma(n_i)
+        \in
+      \sigma(
+        \<a_\sigma(n_0),\dots,a_\sigma(n_{i-1}),
+          a_\sigma(\omega+i),\dots,a_\sigma(\omega+k-1)\>
+      )
+    \]
+
+  Finally, observe that the legal counterattack
+    \[
+      \<a_\sigma(n_0),\dots,a_\sigma(n_{k-1}),
+        a_\sigma(\omega),\dots,a_\sigma(\omega+k-1),
+        a_\sigma(n_0),\dots,a_\sigma(n_{k-1}),
+        a_\sigma(\omega),\dots,a_\sigma(\omega+k-1),
+        \dots\>
+    \]
+  has a range outside the open neighborhood
+    \[
+      \oneptcomp\omega_1
+        \setminus
+      \{a_\sigma(n_0),\dots,a_\sigma(n_{k-1}),
+        a_\sigma(\omega),\dots,a_\sigma(\omega+k-1)\}
+    \]
+  of $\infty$. Thus $\sigma$ is not a winning $k$-tactic.
+\end{proof}
+
+Once the discrete space is larger than $\omega_1$, knowing the round number
+is not sufficient to construct a limited information strategy, due to a
+similar argument.
+
+\begin{thm}
+  $O\not\kmarkwin{k}\clusgame{\oneptcomp\omega_2}{\infty}$.
+\end{thm}
+
+\begin{proof}
+  Let $\sigma$ be a $k$-mark for $\pl O$ in
+  $\clusgame{\oneptcomp\omega_2}{\infty}$. By the closing-up lemma, the set
+    \[
+      C_\sigma
+        =
+      \{
+        \alpha<\omega_2
+          :
+        s\in\alpha^{<\omega}
+          \Rightarrow
+        \oneptcomp\omega_2\setminus\sigma\circ\mu_k(s)
+        \subset \alpha
+      \}
+    \]
+  is closed and unbounded. Let $a_\sigma:\omega_2\to C_\sigma$ be
+  an order isomorphism.
+
+  Choose $\beta_0<\dots<\beta_{k-1}<\omega_1$ such that for each $i<k$:
+    \[
+      a_\sigma(\beta_i)
+        \in
+      \bigcup_{n<\omega}
+      \sigma(
+        \<a_\sigma(\beta_0),\dots,a_\sigma(\beta_{i-1}),
+          a_\sigma(\omega_1+i),\dots,a_\sigma(\omega_1+k-1)\>,
+      n)
+    \]
+
+  Finally, observe that the legal counterattack
+    \[
+      \<a_\sigma(\beta_0),\dots,a_\sigma(\beta_{k-1}),
+        a_\sigma(\omega_1),\dots,a_\sigma(\omega_1+k-1),
+        a_\sigma(\beta_0),\dots,a_\sigma(\beta_{k-1}),
+        a_\sigma(\omega_1),\dots,a_\sigma(\omega_1+k-1),
+        \dots\>
+    \]
+  has a range outside the open neighborhood
+    \[
+      \oneptcomp\omega_2
+        \setminus
+      \{a_\sigma(\beta_0),\dots,a_\sigma(\beta_{k-1}),
+        a_\sigma(\omega_1),\dots,a_\sigma(\omega_1+k-1)\}
+    \]
+  of $\infty$. Thus $\sigma$ is not a winning $k$-mark.
+\end{proof}
+
+\section{TODO: Sigma-products}
 

### 2014-05-21 todo.tex
update todo

@@
         \item Is proximal game properties preserved under perfect maps? Or, compact proximal preserved under continuous.
-        \item Does the one-point compactification of ladder omega_1 space have Markov strategy? (Try ladder space where
-              nth rung is limit+n => is a Moore space and has G_delta diagonal)
+        \item Does the one-point compactification of ladder $\omega_1$ space have Markov strategy? (Try ladder space where
+              nth rung is limit+n $\Rightarrow$ is a Moore space and has $G_\delta$ diagonal)
         \item Does the Michael line have a predetermined/Markov strategy?
         \item Uniformly locally compact plus predtermiend implies metrizable unifomrity.
+        \item What about Bernstein set?
+        \item Is there a non-normal ladder $X$ with $\pl P\not\win\proxgame{X}$?
+          \begin{itemize}
+            \item Diamond implies there exists a ladder such that for any
+                  uncountable subset of successors, the rungs for a limit is
+                  contained.
+            \item So assume diamond, or maybe just CH.
+          \end{itemize}
       \end{itemize}

### 2014-05-28 phd/dissertation/chapter3.tex
revisions per meeting with G

@@
 
-(TODO: Any reason for the ``W''?)
-
+The ``W'' in the name merely refers to $\pl O$'s goal: to ``win'' the game.
 Gruenhage defined this game in his doctoral dissertation to define a class
@@
 \begin{defn}
-  The spaces $X$ for which $\pl O \win \congamehard{X}{x}$ for all $x\in X$ are
+  The spaces $X$ for which $\pl O \win \congame{X}{x}$ for all $x\in X$ are
   called \term{$W$-spaces}.
@@
     if and only if
-  $\pl O \prewin \congamehard{X}{x}$ for all $x\in X$.
+  $\pl O \prewin \congame{X}{x}$ for all $x\in X$.
 \end{prop}
@@
   predetermined strategy for $\pl O$ in $\congamehard{X}{x}$. There exists
-  an open neighborhood $U$ of $x$ which does not contain any $\sigma(n)$
-  (otherwise $\{\sigma(n):n<\omega\}$ would be a countable base at $x$).
-  Let $x_n$ be an element of $\sigma(n)\setminus U$ for all $n<\omega$.
-  Then $\<x_0,x_1,\dots\>$ is a winning counter-attack to $\sigma$ for $\pl P$,
-  so $\pl O$ lacks a winning predetermined strategy.
+  an open neighborhood $U$ of $x$ which does not contain any 
+  $\bigcap_{m\leq n}\sigma(m)$ (otherwise 
+  $\{\bigcap_{m\leq n}\sigma(m):n<\omega\}$ would be a countable base at $x$).
+  Let $x_n$ be an element of $\bigcap_{m\leq n}\sigma(m)\setminus U$ for all 
+  $n<\omega$. Then $\<x_0,x_1,\dots\>$ is a winning counter-attack to $\sigma$ 
+  for $\pl P$, so $\pl O$ lacks a winning predetermined strategy.
 \end{proof}
@@
 
-Put another way, $\tau(n)=\bigcap_{m\leq n}\sigma(m)$ in the predetermined
+Put more simply, $\tau(n)=\bigcap_{m\leq n}\sigma(m)$ in the predetermined
 case, and
@@
 The original proof would have been invalid if $\lambda$ was required to be, say,
-the tactical fog-of-war $\nu_1$, since the value of $\pl O$'s own second move
+the tactical fog-of-war $\nu_1$, since the value of $\pl O$'s own round $1$ move
 $\sigma\circ\nu_1(\<x_0\>)=\sigma(\<x_0\>)$

### 2014-06-02 phd/dissertation/chapter3.tex
working on sigma-product

@@
 
-(TODO: Maybe $k+2$ tacts/marks as well, but not as obvious if so.)
+Two types of questions emerge from these results.
 
-(TODO: It's feasible that $k$-limit $\Leftrightarrow$ $1$-limit for
-one variation or another.)
+\begin{ques}
+  Does $\pl O \ktactwin{2} \clusgame{X}{S}$ imply
+  $\pl O \ktactwin{2} \congame{X}{S}$? What about for $\kmarkwin{2}$?
+\end{ques}
+
+\begin{ques}
+  Could $\pl O \ktactwin{k+1} \congame{X}{S}$ actually imply
+  $\pl O \tactwin \congame{X}{S}$? What about for $\clusgame{X}{S}$?
+\end{ques}
 
@@
 \begin{thm}
-  $O\not\kmarkwin{k}\clusgame{\oneptcomp\omega_2}{\infty}$.
+  $O\not\kmarkwin{k}\clusgamehard{\oneptcomp\omega_2}{\infty}$.
 \end{thm}
@@
 
-\section{TODO: Sigma-products}
+\section{Sigma-products}
+
+Knowing the status of $W$-games in simpler spaces yields insight to larger
+spaces.
+
+\begin{prop}
+  Suppose $S\subseteq Y\subseteq X$, $\limitwin$ is any of $\win$,
+  $\ktactwin{k}$, or $\kmarkwin{k}$, and $G(X,S)$ is any of $\congame{X}{S}$,
+  $\congamehard{X}{S}$, $\clusgame{X}{S}$, or $\clusgamehard{X}{S}$.
+
+  Then $\pl O \limitwin G(X,S)$ implies $\pl O \limitwin G(Y,S)$.
+\end{prop}
+
+\begin{proof}
+  Simply intersect the output of the winning strategy in $G(X,S)$ with $Y$.
+\end{proof}
+
+A natural superspace of a Fort space is the sigma-product of a discrete
+cardinal.
+
+\begin{defn}
+  Let $\Sigma_{y} X^\kappa$ be a \term{sigma product} of $X$ with dimension
+  $\kappa$ for each $y\in X^\kappa$, the subset of the usual Tychonoff
+  product space $X^\kappa$ such that $x\in \Sigma_y X^\kappa$ if and only if
+  $\{\alpha<\kappa : x(\alpha)\not=y(\alpha)\}$ is countable.
+
+  For homogeneous spaces $X$ containing $0$, $y$ is usually assumed to be the
+  zero vector $\vec 0$ and the sigma product is written $\Sigma X^\kappa$.
+\end{defn}
+
+\begin{prop}
+  $\oneptcomp\kappa$ is homeomorphic to the space
+  \[
+    \{
+    x\in \Sigma 2^\kappa
+      :
+    x(\alpha)=0 \text{ for all but one } \alpha<\kappa
+    \}
+  \]
+\end{prop}
+
+\begin{proof}
+  Map $\alpha<\kappa$ to $x_\alpha$ such that
+  \[
+    x_\alpha(\beta) =
+    \left\{
+      \begin{array}{ll}
+        0 & \beta\not=\alpha \\
+        1 & \beta=\alpha
+      \end{array}
+    \right.
+  \]
+  and map $\infty$ to the zero vector $\vec0$.
+\end{proof}
+
+\begin{cor}
+  $\pl O\not\ktactwin{k}\clusgamehard{\SigmaProdR{\omega_1}}{\vec0}$,
+  $\pl O\not\kmarkwin{k}\congamehard{\SigmaProdR{\omega_1}}{\vec0}$, and
+  $\pl O\not\kmarkwin{k}\clusgamehard{\SigmaProdR{\omega_2}}{\vec0}$.
+\end{cor}
+
+While this closes the question on tactics and marks for high dimensional
+sigma- (and Tychonoff-) products of the real line, there is another type of
+limited information strategy to investigate.
+
+\begin{defn}
+  For a game $G=\<M,W\>$ and \term{coding strategy} or \term{code}
+  $\sigma:M^2\to M$, the \term{$\sigma$-coding fog-of-war}
+  $\gamma_\sigma: M^{<\omega}\to M^{\leq2}$ is the function defined such that
+    \[
+      \gamma_\sigma(\emptyset) = \emptyset
+    \]
+  and
+    \[
+      \gamma_\sigma(s\concat\<x\>) = \<\sigma\circ\gamma_\sigma(s),x\>
+    \]
+
+  For a coding strategy $\sigma$, its coresponding strategy is
+  $\sigma\circ\gamma_\sigma$. For a game $G$, if $\sigma\circ\gamma_\sigma$
+  is a winning strategy for $\pl A$, then $\sigma$ is a winning coding
+  strategy and we write $\pl A \codewin G$.
+\end{defn}
+
+Intuitively, a $\sigma$-coding fog-of-war converts perfect information of the
+game into the last moves of both the player and her opponent, so a player has
+a winning coding strategy when she only needs to know the move of her opponent
+and her own last move. The term ``coding'' comes from the fact
+that a player may encode information about the history of the game into
+her own moves, and use this encoded information in later rounds.
+
+Coding strategies have been studied since the earliest days of the
+Banach-Mazur game.
+
+\begin{thm}
+  (TODO: Cite the precise version of the BM game where a winning strategy
+    implies a coding strategy.)
+\end{thm}
+
+The hard and normal versions of the $W$ games are all equivalent with regards
+to coding strategies since $\pl O$
+may always ensure her new move is a subset of her previous move. For
+Fort spaces, the question is immediately closed.
+
+\begin{prop}
+  $\pl O \codewin \congame{\oneptcomp\kappa}{\infty}$.
+\end{prop}
+
+\begin{proof}
+  Let $\sigma(\emptyset)=\oneptcomp\kappa$,
+  $\sigma(\<U,\alpha\>)=U\setminus\{\alpha\}$ for $\alpha<\kappa$,
+  and $\sigma(\<U,\infty\>)=U$. $\pl P$
+  cannot legally repeat non-$\infty$ points of the set, so her points converge
+  to $\infty$.
+\end{proof}
+
+This trick does not simply extend to the $\SigmaProdR\kappa$ case, however.
+An open set may only restrict finitely many coordinates of the product,
+and a point in $\SigmaProdR\kappa$ may have countably infinite non-zero
+coordinates. Thus, information about the previous non-zero coordinates cannot be
+directly encoded into the open set.
+
+Circumventing this takes a bit of extra bookkeeping. We proceed by defining
+a simpler infinite game for each cardinal $\kappa$.
+
+\begin{game}
+  Let $\pfgame\kappa$ denote the \term{point-finite game} with players
+  $\pl F$, $\pl C$ for each cardinal $\kappa$.
+
+  In round $n$, $\pl F$ chooses $F_n\in[\kappa]^{<\omega}$, followed by
+  $\pl C$ choosing $C_n\in[\kappa\setminus\bigcup_{m\leq n}F_m]^{\leq\omega}$.
+
+  $\pl F$ wins the game if the collection $\{C_n:n<\omega\}$ is a point-finite
+  cover of its union $\bigcup_{n<\omega} C_n$, that is, each point in
+  $\bigcup_{n<\omega} C_n$ is in $C_n$ only for finitely many $n<\omega$.
+\end{game}
+
+\begin{prop}
+  $\pl F\win\pfgame\kappa$ for all cardinals $\kappa$.
+\end{prop}
+
+\begin{thm}
+  $\pl F \codewin \pfgame\kappa$ implies
+  $\pl O \codewin \congame{\SigmaProdR\kappa}{\vec0}$.
+\end{thm}
+
+\begin{proof}
+  Let $\sigma$ be a coding strategy for $\pl F$ in $\pfgame\kappa$
+  such that $\sigma(F,C)\supset F$.
+
+  For $F\in[\kappa]^{<\omega}$ and $\epsilon>0$ let $U(F,\epsilon)$ be the
+  open set in $\mathbb{R}^\kappa$ such that
+  \[
+    \pi_\alpha(U(F,\epsilon)) =
+    \left\{
+      \begin{array}{ll}
+        (-\epsilon,\epsilon) & \alpha\in F\\
+        \mathbb{R} & \alpha\not\in F
+      \end{array}
+    \right.
+  \]
+  Note that $F$ is uniquely identifible given
+  $U(F,\epsilon)\cap\SigmaProdR\kappa$.
+
+  For each point $x\in\SigmaProdR\kappa$ and $\epsilon\geq 0$, let
+  $C_\epsilon(x)\in[\kappa]^{\leq\omega}$
+  such that $\alpha\in C_\epsilon(\alpha)$ if and only if
+  $|x(\alpha)|\geq\epsilon$.
+
+  TODO: Finish
+
+  % We define the coding strategy $\tau$ for $\pl O$ in
+  % $\congame{\SigmaProdR\kappa}{\vec0}$ as follows:
+  % \[
+  %   \tau(\<U(\tau(\<U,x\>,\epsilon)\cap\SigmaProdR\kappa,x\>)
+  %     =
+  %   U(\sigma(\<F,C_{2^{-|F|}}(x)\>),2^{-|F|}) \cap \SigmaProdR\kappa
+  % \]
+
+  % Assume that $\pl O \not\codewin \congame{\SigmaProdR\kappa}{\vec0}$. Then
+  % there exists a legal attack $a=\<a_0,a_1,\dots\>$ by $\pl P$ against $\tau$.
+  % Since $a$ does not converge to $\vec0$, it follows there is some
+  % $\alpha<\kappa$ such that $a_n(\alpha)$ does not converge to $0$. Thus there
+  % is a sequence $n_0<n_1<\dots$ such that $|a_{n_i}(\alpha)|\geq 2^{-n_i}$, and
+  % it follows that $\alpha\not\in\sigma(\<F,C_{2^{-|F|}}(x)\>)$ at any stage
+  % of the game.
+
+  % Consider the attack $a'=\<$
+\end{proof}
+
+TODO:
 
@@
   Let $\textrm{cf}([\kappa]^{\leq\omega})=\kappa$.
-  Then $F \codewin PF_{F,C}(\kappa)$.
+  Then $\pl F \codewin PF_{F,C}(\kappa)$.
 \end{thm}
@@
 \begin{cor}
-  $O\codewin\congame{\sigmaprodr{\kappa}}{\vec{0}}$
+  $O\codewin\congame{\SigmaProdR{\kappa}}{\vec{0}}$
   for all cardinals $\kappa$.

### 2014-06-04 phd/dissertation/chapter3.tex
minor work on confinality case

@@
 
-\begin{prop}
-  $\pl F\win\pfgame\kappa$ for all cardinals $\kappa$.
-\end{prop}
-
 \begin{thm}
@@
 
-TODO:
+We aim to show that $\pl F \not\codewin \pfgame\kappa$ for all
+$\kappa$.
 
@@
 \end{thm}
+
+\begin{proof}
+Let $W\rest n \in [\kappa]^n$ be a subset of $W\in[\kappa]^\omega$ such that
+$W\rest n \subset W \rest (n+1)$ and $\bigcup_{n<\omega} W\rest n = W$.
+
+Define
+  \[
+    \sigma(\<N,W\>)
+      =
+    N
+      \cup
+    (|N|+1)
+      \cup
+    \{\alpha_W\}
+      \cup
+    \bigcup_{\alpha \in N} f(\alpha) \restriction |N|
+  \]
+
+Consider the play $\left<\emptyset,W_0,N_1,W_1,N_2,W_2,\dots\right>$ with $F$ following the strategy $\sigma$.
+Let $\gamma \in W_i$, and note $\gamma \in f(\alpha_{W_i})$ (and $\gamma \in f(\alpha_{W_i})\restriction |N_n|$ for sufficiently large $n$).
+\[N_{i+1} = \sigma(N_i,W_i) \supseteq \{\alpha_{W_i}\}\] and thus \[N_{n+1} = \sigma(N_n,W_n) \supseteq \bigcup_{\alpha \in N_n} f(\alpha) \restriction |N_n| \supseteq \bigcup_{\alpha \in N_{i+1}} f(\alpha) \restriction |N_n| \supseteq f(\alpha_{W_i}) \restriction |N_n|\] showing $\gamma \in N_{n+1}$.
+Since $\gamma$ is forbidden in round $n+1$, $\gamma$ appears in finitely many sets chosen by $C$.
+
+We turn our attention to $Con_{O,P}(\Sigma\mathbb{R}^\kappa)$.
+We define the winning strategy $\tau(U,p)$ for $O$ as follows: let $N(U)$ be the non-$\mathbb{R}$ coordinates in the basic open set $U$ and $W(p)$ be the non-$0$ coordinates in $p$.
+Then $\tau(U,p) = \left(\prod_{\alpha<\kappa} U_\alpha\right) \cap \Sigma\mathbb{R}^\kappa$ where if $\alpha \in \sigma(N(U),W(p))$ then $U_\alpha = (-\frac{1}{|N(U)|},\frac{1}{|N(U)|})$ and $U_\alpha=\mathbb{R}$ otherwise.
+
+Consider the play $\left<\emptyset,p_0,U_1,p_1,U_2,p_2,\dots\right>$ with $O$ following the strategy $\tau$.
+Observe that $N(\tau(U,p))=\sigma(N(U),W(p))$.
+Thus $p_i(\gamma)\not=0$ is equivalent to $\gamma \in W(p_i)$, and by the above argument, for sufficiently large $n$, $\gamma \in \sigma(N(U_n),W(p_n))$.
+Therefore from round $n$ onward the $\gamma$-coordinates of points chosen by $P$ must lay in $(-\frac{1}{|N(U)|},\frac{1}{|N(U)|})$ and converge to $0$.
+\end{proof}
 

### 2014-06-04 phd/dissertation/chapter3.tex
Finished cf case

--- 2014-06-02 phd/dissertation/chapter3.tex
@@
 
-TODO:
+We aim to show that $\pl F \codewin \pfgame\kappa$ for all
+$\kappa$.
 
 \begin{thm}
-  Let $\textrm{cf}([\kappa]^{\leq\omega})=\kappa$.
+  Let $\cf{[\kappa]^{\leq\omega}}=\kappa$.
   Then $\pl F \codewin PF_{F,C}(\kappa)$.
@@
 
+\begin{proof}
+Let $c:\kappa\to[\kappa]^{\leq \omega}$ be a funtion such that for every
+$W\in[\kappa]^{\leq\omega}$, there exists $\gamma_W<\kappa$ with
+$W\subseteq c(\gamma_W)$.
+
+Let $W\rest n \in [\kappa]^n$ be a subset of $W\in[\kappa]^\omega$ such that
+$W\rest n \subset W \rest (n+1)$ and $\bigcup_{n<\omega} W\rest n = W$.
+
+Define the coding strategy $\sigma$ as follows:
+  \[
+    \sigma(\emptyset) = \emptyset
+  \]
+  \[
+    \sigma(\<N,W\>)
+      =
+    N
+      \cup
+    (|N|+1)
+      \cup
+    \{\gamma_W\}
+      \cup
+    \bigcup_{\alpha \in N}\left(c(\alpha) \rest |N|\right)
+  \]
+
+Let $\<W_0,W_1,\dots\>$ be a legal attack against $\sigma$,
+$N_0=\sigma(\emptyset)$, and
+$N_{i+1}=\sigma(\<N_i,W_i\>)$. Then $\<N_0,W_0,N_1,W_1,\dots\>$ is the
+playthrough of the game coresponding to the coding strategy $\sigma$ and
+attack $a$.
+
+Let $\alpha\in W_i$ for some $i<\omega$. Then $\gamma_{W_i}\in N_n$ when
+$n>i$. Since $W_i\subseteq c(\gamma_{W_i})$, there exists some $n>i$ such
+that $\alpha\in c(\gamma_{W_i})\rest n$.
+Finally, we consider
+  \[
+    N_{n+1}
+      =
+    \sigma(\<N_n,W_n\>)
+      \supseteq
+    \bigcup_{\alpha\in N_n}\left(c(\alpha) \rest |N_n|\right)
+      \supseteq
+    c(\gamma_{W_i})\rest |N_n|
+  \]
+and since $|N_n|\geq n$, we may conclude $\alpha\in N_{n+1}$.
+Thus $\alpha\not\in W_j$ for $j>n$, and $\pl F$ wins the game.
+\end{proof}
+
 \begin{thm}
   Let $\kappa$ be the limit of cardinals $\kappa_n$ such that
-  $\textrm{cf}([\kappa_n]^{\leq\omega},\subseteq)=\kappa_n$.
+  $\cf{[\kappa_n]^{\leq\omega}}=\kappa_n$.
   Then $F \codewin \pfgame{\kappa}$.

### 2014-06-04 phd/dissertation/chapter3.tex
almost finished with chapter: need to finish game equivalency proof and complete sketch for the simpler game

@@
 
-We aim to show that $\pl F \codewin \pfgame\kappa$ for all
-$\kappa$.
-
 \begin{thm}
   Let $\cf{[\kappa]^{\leq\omega}}=\kappa$.
-  Then $\pl F \codewin PF_{F,C}(\kappa)$.
+  Then $\pl F \codewin \pfgame\kappa$.
 \end{thm}
@@
 
+  (TODO: The above result is cute, but unnecessary due to the below.)
+
 \begin{thm}
-  Let $\kappa$ be the limit of cardinals $\kappa_n$ such that
-  $\cf{[\kappa_n]^{\leq\omega}}=\kappa_n$.
-  Then $F \codewin \pfgame{\kappa}$.
+  $\pl F \codewin \pfgame{\kappa}$ for all cardinals $\kappa$.
 \end{thm}
 
-\begin{thm}
-  $F\codewin\pfgame{\kappa}$ for all cardinals $\kappa$.
-\end{thm}
+\begin{proof}
+  TODO: Fill in sketch.
+
+  SKETCH: For each cardinal
+  $\kappa$, assume $F\codewin\pfgame\lambda$ for $\lambda<\kappa$. Always
+  cover the upper bound of $\pl O$'s moves if possible, or use a trick
+  assuming $\cf\kappa=\omega$.
+\end{proof}
 

### 2014-06-09 miscellaneous/unorganized/2014-06-09-gameTheoryTalk.tex
Game Theory lamar Presentation

% $Header: /home/vedranm/bitbucket/beamer/solutions/generic-talks/generic-ornate-15min-45min.en.tex,v 90e850259b8b 2007/01/28 20:48:30 tantau $

\documentclass{beamer}

% This file is a solution template for:

% - Giving a talk on some subject.
% - The talk is between 15min and 45min long.
% - Style is ornate.

% Copyright 2004 by Till Tantau <tantau@users.sourceforge.net>.
%
% In principle, this file can be redistributed and/or modified under
% the terms of the GNU Public License, version 2.
%
% However, this file is supposed to be a template to be modified
% for your own needs. For this reason, if you use this file as a
% template and not specifically distribute it as part of a another
% package/program, I grant the extra permission to freely copy and
% modify this file as you see fit and even to delete this copyright
% notice.

\mode<presentation>
{
  \usetheme{Warsaw}
  % or ...

  \setbeamercovered{transparent}
  % or whatever (possibly just delete it)
}

      \theoremstyle{theorem}
      \newtheorem{proposition}[theorem]{Proposition}
      \theoremstyle{definition}
      \newtheorem{game}[theorem]{Game}
      \newtheorem{question}[theorem]{Question}

\usepackage[english]{babel}
% or whatever

\usepackage[latin1]{inputenc}
% or whatever

\usepackage{times}
\usepackage[T1]{fontenc}
% Or whatever. Note that the encoding and the font should match. If T1
% does not look nice, try deleting the line with the fontenc.

\usepackage{marvosym} % For \Smiley
\usepackage{verbatim} % for \verbatiminput

\title
{Finite and Infinite Games}

\subtitle
{at Lamar University} % (optional)

\author%[Author, Another] % (optional, use only with lots of authors)
{Steven~Clontz~\\http://stevenclontz.com}%\inst{1} \and S.~Another\inst{2}}
% - Use the \inst{?} command only if the authors have different
%   affiliation.

\institute[Auburn University] % (optional, but mostly needed)
{
  %\inst{1}%
  Department of Mathematics and Statistics\\
  Auburn University}
  %\and
  %\inst{2}%
  %Department of Theoretical Philosophy\\
  %University of Elsewhere}
% - Use the \inst command only if there are several affiliations.
% - Keep it simple, no one is interested in your street address.

\date[14-06-09] % (optional)
{June 9, 2014}

% If you have a file called "university-logo-filename.xxx", where xxx
% is a graphic format that can be processed by latex or pdflatex,
% resp., then you can add a logo as follows:

 % \pgfdeclareimage[height=1cm]{university-logo}{auburn_logo.png}
 % \logo{\pgfuseimage{university-logo}}

% Delete this, if you do not want the table of contents to pop up at
% the beginning of each subsection:
%\AtBeginSubsection[]
%{
%  \begin{frame}<beamer>{Outline}
%    \tableofcontents[currentsection,currentsubsection]
%  \end{frame}
%}

% If you wish to uncover everything in a step-wise fashion, uncomment
% the following command:

%\beamerdefaultoverlayspecification{<+->}

% My game notational definitions
\newcommand{\win}{\uparrow}
\newcommand{\prewin}{\uparrow_{\text{pre}}}
\newcommand{\markwin}{\uparrow_{\text{mark}}}
\newcommand{\tactwin}{\uparrow_{\text{tact}}}
\newcommand{\ktactwin}[1]{\uparrow_{#1\text{-tact}}}
\newcommand{\kmarkwin}[1]{\uparrow_{#1\text{-mark}}}
\newcommand{\codewin}{\uparrow_{\text{code}}}
\newcommand{\limitwin}{\uparrow_{\text{limit}}}
\newcommand{\oneptcomp}[1]{#1^*}
\newcommand{\oneptlind}[1]{#1^\dagger}
\newcommand{\congame}[2]{Con_{\pl O\pl P}(#1,#2)}
\newcommand{\clusgame}[2]{Clus_{\pl O\pl P}(#1,#2)}
\newcommand{\lfkpgame}[1]{LF_{\pl K\pl P}(#1)}
\newcommand{\lfklgame}[1]{LF_{\pl K\pl L}(#1)}
\newcommand{\pfgame}[1]{PF_{\pl F\pl C}(#1)}
\newcommand{\mengame}[1]{Cov_{\pl C\pl F}(#1)}
\newcommand{\rothgame}[1]{Cov_{\pl C\pl S}(#1)}
\newcommand{\altrothgame}[1]{Cov_{\pl P\pl O}(#1)}
\newcommand{\fillgame}[1]{Fill^{\subseteq}_{\pl M\pl N}(#1)}
\newcommand{\sfillgame}[1]{Fill^{\subsetneq}_{\pl M\pl N}(#1)}
\newcommand{\kfillgame}[1]{Fill^{\subseteq}_{\pl C\pl F}(#1)}
\newcommand{\ksfillgame}[1]{Fill^{\subsetneq}_{\pl C\pl F}(#1)}
\newcommand{\recallgame}[2]{Rec^{#1}_{\pl F\pl S}(#2)}
\newcommand{\sigmaprodr}[1]{\Sigma\mathbb{R}^{#1}}
\newcommand{\sigmaprodtwo}[1]{\Sigma2^{#1}}
\newcommand{\concat}{^\frown}
\newcommand{\rest}{\restriction}
\newcommand{\cl}[1]{\overline{#1}}
\newcommand{\pow}[1]{\mc{P}(#1)}
\newcommand{\<}{\langle}
\renewcommand{\>}{\rangle}
\newcommand{\al}[1]{{#1}^*}
\newcommand{\mc}[1]{\mathcal{#1}}
\newcommand{\po}{\mathbb{P}}
\newcommand{\pok}{\po_\kappa}
\newcommand{\Lim}{\mathrm{Lim}}
\newcommand{\Suc}{\mathrm{Suc}}
\newcommand{\ds}{\displaystyle}
\newcommand{\alcomp}{\al\parallel}
\newcommand{\rank}{\textrm{rank}}
\newcommand{\dom}{\textrm{dom}}
\newcommand{\scish}{almost-$\sigma$-(relatively compact)}

\usepackage{mathrsfs}
\newcommand{\pl}[1]{\mathscr{#1}}

\newcommand{\vpause}{\pause\vspace{1em}}

\newcommand{\term}[1]{\textbf{#1}}

\begin{document}
% \renewcommand{\pause}{}

\begin{frame}
  \titlepage
\end{frame}

% \begin{frame}{Table of Contents}
%   \tableofcontents
%   % You might wish to add the option [pausesections]
% \end{frame}

\section{Before We Begin...}

\begin{frame}{Grad School!}
  \begin{itemize}
    \item I entered graduate school at Auburn in 2008. Planned on doing
          two Masters in Math and Math Ed. Quickly switched to just Math,
          and I'm finishing up my dissertation on topological games
          to defend this fall or spring.
    \pause
    \item Kind of stumbled into my program. Worked for me, but I feel lucky!
    \pause
    \item I highly recommend graduate school in math - but keep your mind on
          your end career goal (Academia? Industry?)
  \end{itemize}
\end{frame}

\begin{frame}{Preparing for Grad School}
  \begin{itemize}
    \item Think about what you want to study. You're no longer a ``math major'',
          you'll be a graph theorist, or topologist, or algebraist.
    \pause
    \item Find professors that do what you want to study. You'll be picking
          an advisor to work with for a while. (Or, consider getting a Masters
          before PhD to get your feet wet.)
    \pause
    \item Make sure there's Graduate Assistantships available. At Auburn,
          being a GA waives tuition and gives you a paycheck.
          \textbf{Don't go into debt for grad school!}
    \pause
    \item Check website for other requirements. (Math GRE? Required letters?
          Deadlines?)
  \end{itemize}
\end{frame}

\begin{frame}{What's being a Grad Student like?}
  \begin{itemize}
    \item Classes... at first. Hopefully, only classes you're interested in!
    \pause
    \item More free time... to study or research.
    \pause
    \item Get involved! Connect with other grad students outside your
          department. Serving grad student gov't is worthwhile too.
    \pause
    \item Go to conferences. Students often can get funding to cover costs,
          you get to travel, and learn what's happening at other schools.
    \pause
    \item Teach and give talks. Being able to communicate your work is as
          important as actually doing it.
  \end{itemize}
\end{frame}

\section{Introduction}

\subsection{Abstract}

\begin{frame}{Abstract}%{Subtitles are optional.}
    \small
    Two player games of perfect information such as chess and checkers have
    been played for centuries.

    \vpause

    Such games may be mathematically modeled as a tuple $G=\<M,W\>$, where $M$
    represents the moves of the game, and $W$ represents the playthroughs
    (sequences of choices in $M$) which result in a victory for the first
    player.

    \vpause

    We will investigate the classic result that all finite length games are
    determined: that is, exactly one player has a strategy which guarantees
    victory in the game regardless of the moves of her opponent.

    \vpause

    In addition, we will learn how infinite length games are used in fields
    such as set theory and topology by using a game to prove that the real
    numbers are uncountable.
\end{frame}

\subsection{Anatomy of a Game}

\begin{frame}{Heads up}
  This talk is about \term{sequential} or \term{combinatorial} games
  of perfect information.

  \vpause

  Game theory is a broad subject, including classic games like the
  \term{Prisoner's Delimma} where two players make a \term{simultaneous}
  choice, or \term{Yahtzee} where the players face randomness from
  dice rolls.

  \vpause

  However, we're going to look at games in the family of \term{Tic Tac Toe}
  or \term{Chess}, where two players take turns making moves with full knowledge
  of their options and the history of their previous moves.
\end{frame}

\begin{frame}{Some Definitions}
  \begin{definition}
    Let $\omega=\{0,1,2,\dots\}$, and let $B^A$ be the set of all functions
    with domain $A$ and range $B$.

    Then $X^\omega$ contains all functions from $\{0,1,2,\dots\}$ to $X$, or
    equivalently, all sequences of the form $\<x_0,x_1,x_2,\dots\>$ with
    $x_i\in X$.
  \end{definition}
  \pause
  \begin{definition}
    A \term{game} $G$ is a tuple $\<M,W\>$ where $W\subseteq M^\omega$.
    $M$ represents the set of possible moves of the game, and $W$ contains
    certain sequences of moves $\<a_0,b_0,a_1,b_1,\dots\>$ called
    \term{victories} (for the first player).
  \end{definition}
\end{frame}

\begin{frame}
  In this context, all games have two players, and there are no ties.

  \vpause

  If the players of the game are $\pl A$ and $\pl B$, then a \term{playthrough}
  of the game is some sequence in $M^\omega$:
  \[
    p=\<a_0,b_0,a_1,b_1,a_2,b_2,\dots\>
  \]

  \pause

  If $p$ is in $W$, then the first player $\pl A$ has won the game; otherwise,
  the second player $\pl B$ has won the game.
\end{frame}

\begin{frame}{Example}
  As an example, let $\<M,W\>$ be the game \term{Sylver Coinage} with players
  $\pl A$, $\pl B$ where $M=\{2,3,4,\dots\}$.

  \vpause

  Defining $W$ directly as a set is usually obnoxious, so we'll define it
  implicitly by setting this rule: no player can choose a number which is
  the sum of previously chosen numbers, perhaps with repetition.

  \vpause

  Thus, if $4$ and $7$ have been chosen previously, then $25=4+7+7+7$ is not a
  legal move.

  \vpause

  Thus a sequence $\<a_0,b_0,a_1,b_1,\dots\>$ will be in $W$ if it shows the
  second player $\pl B$ breaking the rules before the first player $\pl A$.
\end{frame}

\begin{frame}
  For example, consider the playthrough beginning with
  \[
    \<4,11,6,5,7,3,2,\dots\>
  \]
  \begin{itemize}
    \item $\pl A$ chose $4$
    \item $\pl B$ chose $11$
    \item $\pl A$ chose $6$ (legal moves remaining:
          $\{2,3,5,7,9,13\}$)
    \item $\pl B$ chose $5$ (legal moves remaining:
          $\{2,3,7\}$)
    \item $\pl A$ chose $7$ (legal moves remaining:
          $\{2,3\}$)
    \item $\pl B$ chose $3$ (legal moves remaining: $\{2\}$)
    \item $\pl A$ chose $2$ (legal moves remaining: $\emptyset$)
    \item $\pl B$ chose something illegal and lost.
  \end{itemize}
\end{frame}

\begin{frame}
  This game, invented by John Conway, is an example of a \term{finite game},
  since eventually one of the players are forced to break the given rules.
  (A puzzle I'll leave for you to work on!)

  \vpause

  We've just seen that every sequence of the form $\<4,11,6,5,7,3,2,\dots\>$
  is in $W$, since $\pl A$ wins those playthroughs of the game.
  (Actually, another puzzle: show that all sequences of the form
  $\<4,11,6,5,7,\dots\>$ are in $W$.)

  \vpause

  An artifact of this game model is that all playthroughs are infinite
  sequences. After $\pl B$ makes an illegal move, there's no point to keep
  playing in reality, but the sequences in $W$ stretch on in every possible
  combination...
\end{frame}

\subsection{Strategies and Determinacy}

\begin{frame}{Strategies}
  \begin{definition}
    A \term{strategy} is a function $\sigma$ which turns a finite sequence
    of moves in $M$ into a new move in $M$.
  \end{definition}

  \pause

  Put another way, a strategy is a fixed rule which tells a player what move
  to make during each round \textit{in response} to all the previous moves
  of the game.
\end{frame}

\begin{frame}{Attacks}
  \begin{definition}
    An \term{attack} is sequence of moves in $M$.
  \end{definition}

  \pause

  Put another way, an attack is a fixed rule which tells a player what move
  to make during each round \textit{ignoring} all the previous moves of
  the game.
\end{frame}

\begin{frame}{Winning Strategies}
  \begin{definition}
    The \term{result} of a game for which $\pl A$ uses the strategy $\sigma$
    $\pl B$ uses the attack $\<b_0,b_1,\dots\>$ is the playthrough of the
    game $\<\sigma(\emptyset),b_0,\sigma(b_0),b_1,\sigma(b_0,b_1),\dots\>$
  \end{definition}

  (Or the similar definition when $\pl B$ has a strategy and $\pl A$
  has an attack.)

  \pause

  \begin{definition}
    If $\sigma$ is a strategy for $\pl A$ such that the result of the game for
    every possible attack by $\pl B$ is in $W$, then $\sigma$ is a
    \term{winning strategy}.
  \end{definition}

  (Or the similar definition when $\pl B$ has a strategy, and all results
  are not in $W$.)
\end{frame}

\begin{frame}
  \begin{definition}
    If one of the players has a winning strategy for a game, then that
    game is said to be \term{determined}.
  \end{definition}

  Obviously, both players can't have a guaranteed way to win the same
  game, but is it possible that neither player can guarantee a way to win?
  That is, for every fixed strategy by either player, could the opponent
  always have some chance of getting lucky and beating it?
\end{frame}

\section{Determinacy of Finite Games}

\subsection{Borel Determinacy Theorem}

\begin{frame}{Borel Determinacy Theorem}
  We could use a very strong topological and set-theoretic result to prove
  that finite games are determined.

  \begin{theorem}
    If $M$ is given the discrete topology, and $M^\omega$ is given the usual
    product topology, then the game $G=\<M,W\>$ is determined whenever $W$
    is a Borel subset of the space $M^\omega$.
  \end{theorem}

  \pause

  With a little topology, you can show that if $G$ is finite, then $W$ is
  an open set, which implies it's Borel. Thus finite games \textit{are}
  determined: one of the players has a winning strategy.

  \vpause

  Of course, all that requires a few semesters of graduate topology to grok,
  so maybe there's a better way...
\end{frame}

\subsection{Decision Tree Proof}

\begin{frame}{Decision Trees}
  Finite games can be modeled as a decision tree.

  \centerline{\includegraphics[width=3in]{decisionTree1.pdf}}

  The above tree models a game where $\pl A$ and $\pl B$ alternate choosing
  ``left'' or ``right'' moves to descend the tree. A player wins if they
  move into a terminal node of the tree, since the opponent cannot move farther.
\end{frame}

\begin{frame}
  \centerline{\includegraphics[width=3in]{decisionTree2.pdf}}

  \vspace{1em}

  We can label the tree by first showing the states where $\pl A$ (blue) and
  $\pl B$ (red) have already won the game.
\end{frame}

\begin{frame}
  \centerline{\includegraphics[width=3in]{decisionTree3.pdf}}

  \vspace{1em}

  Then, we can move back and label the spaces where the active player is able
  to move to a vertex of their color.
\end{frame}

\begin{frame}
  \centerline{\includegraphics[width=3in]{decisionTree4.pdf}}

  \vspace{1em}

  Eventually, we label the entire tree based on when the active player has
  the option to move into their color or not.
\end{frame}

\begin{frame}
  \centerline{\includegraphics[width=3in]{decisionTree5.pdf}}

  \vspace{1em}

  Since the top vertex is blue, $\pl A$ has a winning strategy: always make
  the choice which leads to another blue vertex.
\end{frame}

\section{Infinite Games}

\subsection{Infinite Games}

\begin{frame}{Infinite Games}
  Why do we care so much about determinacy? Why did we define game playthroughs
  to be infinite sequences?

  \vpause

  These topics come into play when considering infinite games.

  \vpause

  \begin{definition}
    A game $G$ is \term{infinite} if there exists a playthrough such that it
    is still possible for either player to win during every round of the game.
  \end{definition}
\end{frame}

\begin{frame}{How are they played?}
  Even though a game could never actually be played, we can still construct
  strategies (functions) and attacks (sequences), and we can compute the
  result of a game given a strategy and attack.

  \vpause

  Put another way, for every infinite game, there is a finite analog of the
  game which lasts exactly one round: one player chooses a strategy, followed
  by the opponent choosing an attack based upon it. The result of the infinite
  game is computed, and that determines the result of the single-round finite
  game.
\end{frame}

\begin{frame}{Determinacy}
  Like many theorems about infinite mathematical objects, whether infinite
  games are determined depend on your set-theoretic axioms. Mathematicians who
  work in foundations often use the Zermelo-Fraenkel (ZF) set theory, which
  isn't powerful enough to write proofs on the subject.

  \vpause

  The \term{Axiom of Determinacy} states that all games which
  involve (countably) infinite moves are determined: one of the players always
  can construct a winning strategy.

  \vpause

  But the more commonly used \term{Axiom of Choice} can be used to construct
  a game where if either player fixes a strategy, the other player can always
  create a counter-attack which defeats it. (See the Banach-Mazur game and
  Bernstein subsets of the real numbers.)
\end{frame}

\subsection{Applications}

\begin{frame}{Example Game}
  Let $\<M,W\>$ be \term{Convergence Game $A$} where $M$ is the set of real
  numbers $\mathbb{R}$, and $A$ is a subset of the real numbers.

  \vpause

  Players $\pl A$, $\pl B$ must follow the rule that every real number chosen is
  strictly between the latest numbers chosen by $\pl A$ and $\pl B$.

  \vpause

  The start of a playthrough could be
    \[
      \left\<
        5,
        \underset{(5<12)}{12},
        \underset{(5<2\pi<12)}{2\pi},
        \underset{(2\pi<7<12)}{7},
        \underset{(2\pi<6.5<7)}{6.5},
        \dots
      \right\>
    \]
\end{frame}

\begin{frame}{A Winning Condition}
  Since there's always infinitely many numbers between every
  two real numbers, $\pl A$ and $\pl B$ always have legal moves to choose from.

  \vpause

  That's why we must add a winning condition: if both players always make legal
  moves, then $\pl A$ wins if the numbers she chose form a sequence converging
  to a number in the set $A$, and $\pl B$ wins otherwise.

  \vpause

  For example, $\pl A$ won the earlier playthrough if the sequence
  $\<5,2\pi,6.5,\dots\>$ converges to a number in $A$.
\end{frame}

\begin{frame}{Who wins?}
  \begin{theorem}
    $\pl B$ has a winning strategy in Convergence Game $A=\{a_0,a_1,\dots\}$
    (that is, when $A$ is a ``countable'' set).
  \end{theorem}
\end{frame}

\begin{frame}
  \begin{proof}
    $\pl B$'s strategy is to take the list of numbers $\{a_0,a_1,\dots\}$,
    and every turn, $\pl B$ chooses the number furthest to the left of the list
    which is legal to play.

    \vpause

    Then, at the ``end'' of the game, assuming that $\pl A$ also followed the
    rules, every number in the list $\{a_0,a_1,\dots\}$ is either to the left
    of one of $\pl A$'s points, or to the right of one of $\pl B$'s points.

    \vpause

    Thus, $\pl A$'s points cannot converge to any of the numbers in
    $\{a_0,a_1,\dots\}$ no matter what attack she attempts.
  \end{proof}
\end{frame}

\begin{frame}{The Application}
  Using this game, we get a classic set theory result due to Cantor:

  \vpause

  \begin{theorem}
    The real numbers $\mathbb{R}$ cannot be written in a list
    $\{r_0,r_1,\dots\}$ (they are ``uncountable'').
  \end{theorem}

  \begin{proof}
    Every increasing bounded above sequence converges to a real number
    (see Cal II). Thus $\pl A$ always wins the Convergence Game $A=\mathbb{R}$.

    But since $\pl B$ wins if $A$ is a countable set which can be written like
    $\{a_0,a_1,\dots\}$, we know that $\mathbb{R}$ cannot be countable.
  \end{proof}
\end{frame}

\section*{}

\begin{frame}
Questions? Thanks for having me!
\end{frame}

\end{document}

### 2014-06-24 miscellaneous/unorganized/2014-06-24-auburnGameTheoryTalk.tex
minor changes to lamar talk for AU REU talk

--- 2014-06-09 miscellaneous/unorganized/2014-06-09-gameTheoryTalk.tex
@@
 \subtitle
-{at Lamar University} % (optional)
+{Auburn REU Presentation} % (optional)
 
@@
 
-\date[14-06-09] % (optional)
-{June 9, 2014}
+\date[14-06-24] % (optional)
+{June 24, 2014}
 
@@
 
-\section{Before We Begin...}
-
-\begin{frame}{Grad School!}
-  \begin{itemize}
-    \item I entered graduate school at Auburn in 2008. Planned on doing
-          two Masters in Math and Math Ed. Quickly switched to just Math,
-          and I'm finishing up my dissertation on topological games
-          to defend this fall or spring.
-    \pause
-    \item Kind of stumbled into my program. Worked for me, but I feel lucky!
-    \pause
-    \item I highly recommend graduate school in math - but keep your mind on
-          your end career goal (Academia? Industry?)
-  \end{itemize}
-\end{frame}
-
-\begin{frame}{Preparing for Grad School}
-  \begin{itemize}
-    \item Think about what you want to study. You're no longer a ``math major'',
-          you'll be a graph theorist, or topologist, or algebraist.
-    \pause
-    \item Find professors that do what you want to study. You'll be picking
-          an advisor to work with for a while. (Or, consider getting a Masters
-          before PhD to get your feet wet.)
-    \pause
-    \item Make sure there's Graduate Assistantships available. At Auburn,
-          being a GA waives tuition and gives you a paycheck.
-          \textbf{Don't go into debt for grad school!}
-    \pause
-    \item Check website for other requirements. (Math GRE? Required letters?
-          Deadlines?)
-  \end{itemize}
-\end{frame}
-
-\begin{frame}{What's being a Grad Student like?}
-  \begin{itemize}
-    \item Classes... at first. Hopefully, only classes you're interested in!
-    \pause
-    \item More free time... to study or research.
-    \pause
-    \item Get involved! Connect with other grad students outside your
-          department. Serving grad student gov't is worthwhile too.
-    \pause
-    \item Go to conferences. Students often can get funding to cover costs,
-          you get to travel, and learn what's happening at other schools.
-    \pause
-    \item Teach and give talks. Being able to communicate your work is as
-          important as actually doing it.
-  \end{itemize}
-\end{frame}
-
 \section{Introduction}
@@
 
-    \vpause
+    \vspace{1em}
 
@@
   is in $W$, since $\pl A$ wins those playthroughs of the game.
-  (Actually, another puzzle: show that all sequences of the form
-  $\<4,11,6,5,7,\dots\>$ are in $W$.)
 
@@
   \begin{theorem}
-    $\pl B$ has a winning strategy in Convergence Game $A=\{a_0,a_1,\dots\}$
-    (that is, when $A$ is a ``countable'' set).
+    $\pl B$ has a winning strategy in Convergence Game when $A$ can be indexed
+    by the non-negative integers: $A=\{a_0,a_1,a_2,\dots\}$
+    (that is, when $A$ is a \term{countable} set).
   \end{theorem}
@@
   \begin{theorem}
-    The real numbers $\mathbb{R}$ cannot be written in a list
-    $\{r_0,r_1,\dots\}$ (they are ``uncountable'').
+    The real numbers $\mathbb{R}$ cannot be exhaustively indexed by the
+    non-negative integers (they are \term{uncountable}).
   \end{theorem}
@@
     Every increasing bounded above sequence converges to a real number
-    (see Cal II). Thus $\pl A$ always wins the Convergence Game $A=\mathbb{R}$.
+    (see Cal II). Thus $\pl A$ has a winning strategy for
+    the Convergence Game $A=\mathbb{R}$.
 
-    But since $\pl B$ wins if $A$ is a countable set which can be written like
-    $\{a_0,a_1,\dots\}$, we know that $\mathbb{R}$ cannot be countable.
+    But since $\pl B$ has a winning strategy when $A$ is a countable set, we've
+    proven that $\mathbb{R}$ cannot be countable.
   \end{proof}

### 2014-06-27 phd/dissertation/chapter3.tex
complete point-finite and sigma-product convergence equivalence

@@
 
-Circumventing this takes a bit of extra bookkeeping. We proceed by defining
+Circumventing this takes a bit of extra machinery. We proceed by defining
 a simpler infinite game for each cardinal $\kappa$.
@@
 \begin{proof}
-  Let $\sigma$ be a coding strategy for $\pl F$ in $\pfgame\kappa$
-  such that $\sigma(F,C)\supset F$.
+  Let $\sigma$ be a winning coding strategy for $\pl F$ in $\pfgame\kappa$
+  such that $\sigma(\emptyset)\supset\emptyset$ and $\sigma(F,C)\supset F$.
 
   For $F\in[\kappa]^{<\omega}$ and $\epsilon>0$ let $U(F,\epsilon)$ be the
-  open set in $\mathbb{R}^\kappa$ such that
+  basic open set in $\mathbb{R}^\kappa$ such that each projection is of the form
   \[
@@
   \]
-  Note that $F$ is uniquely identifible given
+  Note that $F\supset\emptyset$ and $\epsilon$ are uniquely identifible given
   $U(F,\epsilon)\cap\SigmaProdR\kappa$.
 
-  For each point $x\in\SigmaProdR\kappa$ and $\epsilon\geq 0$, let
+  For each point $x\in\SigmaProdR\kappa$ and $\epsilon> 0$, let
   $C_\epsilon(x)\in[\kappa]^{\leq\omega}$
@@
 
-  TODO: Finish
+  We define the coding strategy $\tau$ for $\pl O$ in
+  $\congame{\SigmaProdR\kappa}{\vec0}$ as follows:
+  \[
+    \tau(\emptyset)
+      =
+    U(\sigma(\emptyset),1) \cap \SigmaProdR\kappa
+  \]
+  \[
+    \tau(\<U(F,\epsilon)\cap\SigmaProdR\kappa,x\>)
+      =
+    U\left(\sigma(\<F,C_{\epsilon}(x)\>),\frac{\epsilon}{2}\right)
+      \cap
+    \SigmaProdR\kappa
+  \]
 
-  % We define the coding strategy $\tau$ for $\pl O$ in
-  % $\congame{\SigmaProdR\kappa}{\vec0}$ as follows:
+  Let $\<a_0,a_1,a_2,\dots\>$ be a legal attack by $\pl P$ against $\tau$. It
+  then follows that
+    \[
+      b=\<C_{1}(a_0),C_{1/2}(a_1),C_{1/4}(a_2),\dots\>
+    \]
+  is a
+  legal attack by $\pl C$ against $\sigma$. Since $\sigma$ is a winning
+  strategy, each ordinal in $\bigcup_{n<\omega} C_{2^{-n}}(a_n)$ is in
+  $C_{2^{-n}}(a_n)$ only for finitely many $n<\omega$. Thus for every coordinate
+  $\alpha<\kappa$ it follows that there exists some $n_\alpha<\omega$ such that
+  $a_{n}(\alpha)\leq 2^{-n}$ for $n\geq n_\alpha$. We conclude $a_n\to\vec0$,
+  showing that $\tau$ is a winning strategy.
+\end{proof}
+
+% \begin{thm}
+%   Let $\cf{[\kappa]^{\leq\omega}}=\kappa$.
+%   Then $\pl F \codewin \pfgame\kappa$.
+% \end{thm}
+
+% \begin{proof}
+% Let $c:\kappa\to[\kappa]^{\leq \omega}$ be a funtion such that for every
+% $W\in[\kappa]^{\leq\omega}$, there exists $\gamma_W<\kappa$ with
+% $W\subseteq c(\gamma_W)$.
+
+% Let $W\rest n \in [\kappa]^n$ be a subset of $W\in[\kappa]^\omega$ such that
+% $W\rest n \subset W \rest (n+1)$ and $\bigcup_{n<\omega} W\rest n = W$.
+
+% Define the coding strategy $\sigma$ as follows:
 %   \[
-  %   \tau(\<U(\tau(\<U,x\>,\epsilon)\cap\SigmaProdR\kappa,x\>)
+%     \sigma(\emptyset) = \emptyset
+%   \]
+%   \[
+%     \sigma(\<N,W\>)
 %       =
-  %   U(\sigma(\<F,C_{2^{-|F|}}(x)\>),2^{-|F|}) \cap \SigmaProdR\kappa
+%     N
+%       \cup
+%     (|N|+1)
+%       \cup
+%     \{\gamma_W\}
+%       \cup
+%     \bigcup_{\alpha \in N}\left(c(\alpha) \rest |N|\right)
 %   \]
 
-  % Assume that $\pl O \not\codewin \congame{\SigmaProdR\kappa}{\vec0}$. Then
-  % there exists a legal attack $a=\<a_0,a_1,\dots\>$ by $\pl P$ against $\tau$.
-  % Since $a$ does not converge to $\vec0$, it follows there is some
-  % $\alpha<\kappa$ such that $a_n(\alpha)$ does not converge to $0$. Thus there
-  % is a sequence $n_0<n_1<\dots$ such that $|a_{n_i}(\alpha)|\geq 2^{-n_i}$, and
-  % it follows that $\alpha\not\in\sigma(\<F,C_{2^{-|F|}}(x)\>)$ at any stage
-  % of the game.
+% Let $\<W_0,W_1,\dots\>$ be a legal attack against $\sigma$,
+% $N_0=\sigma(\emptyset)$, and
+% $N_{i+1}=\sigma(\<N_i,W_i\>)$. Then $\<N_0,W_0,N_1,W_1,\dots\>$ is the
+% playthrough of the game coresponding to the coding strategy $\sigma$ and
+% attack $a$.
 
-  % Consider the attack $a'=\<$
-\end{proof}
+% Let $\alpha\in W_i$ for some $i<\omega$. Then $\gamma_{W_i}\in N_n$ when
+% $n>i$. Since $W_i\subseteq c(\gamma_{W_i})$, there exists some $n>i$ such
+% that $\alpha\in c(\gamma_{W_i})\rest n$.
+% Finally, we consider
+%   \[
+%     N_{n+1}
+%       =
+%     \sigma(\<N_n,W_n\>)
+%       \supseteq
+%     \bigcup_{\alpha\in N_n}\left(c(\alpha) \rest |N_n|\right)
+%       \supseteq
+%     c(\gamma_{W_i})\rest |N_n|
+%   \]
+% and since $|N_n|\geq n$, we may conclude $\alpha\in N_{n+1}$.
+% Thus $\alpha\not\in W_j$ for $j>n$, and $\pl F$ wins the game.
+% \end{proof}
 
-\begin{thm}
-  Let $\cf{[\kappa]^{\leq\omega}}=\kappa$.
-  Then $\pl F \codewin \pfgame\kappa$.
-\end{thm}
-
-\begin{proof}
-Let $c:\kappa\to[\kappa]^{\leq \omega}$ be a funtion such that for every
-$W\in[\kappa]^{\leq\omega}$, there exists $\gamma_W<\kappa$ with
-$W\subseteq c(\gamma_W)$.
-
-Let $W\rest n \in [\kappa]^n$ be a subset of $W\in[\kappa]^\omega$ such that
-$W\rest n \subset W \rest (n+1)$ and $\bigcup_{n<\omega} W\rest n = W$.
-
-Define the coding strategy $\sigma$ as follows:
-  \[
-    \sigma(\emptyset) = \emptyset
-  \]
-  \[
-    \sigma(\<N,W\>)
-      =
-    N
-      \cup
-    (|N|+1)
-      \cup
-    \{\gamma_W\}
-      \cup
-    \bigcup_{\alpha \in N}\left(c(\alpha) \rest |N|\right)
-  \]
-
-Let $\<W_0,W_1,\dots\>$ be a legal attack against $\sigma$,
-$N_0=\sigma(\emptyset)$, and
-$N_{i+1}=\sigma(\<N_i,W_i\>)$. Then $\<N_0,W_0,N_1,W_1,\dots\>$ is the
-playthrough of the game coresponding to the coding strategy $\sigma$ and
-attack $a$.
-
-Let $\alpha\in W_i$ for some $i<\omega$. Then $\gamma_{W_i}\in N_n$ when
-$n>i$. Since $W_i\subseteq c(\gamma_{W_i})$, there exists some $n>i$ such
-that $\alpha\in c(\gamma_{W_i})\rest n$.
-Finally, we consider
-  \[
-    N_{n+1}
-      =
-    \sigma(\<N_n,W_n\>)
-      \supseteq
-    \bigcup_{\alpha\in N_n}\left(c(\alpha) \rest |N_n|\right)
-      \supseteq
-    c(\gamma_{W_i})\rest |N_n|
-  \]
-and since $|N_n|\geq n$, we may conclude $\alpha\in N_{n+1}$.
-Thus $\alpha\not\in W_j$ for $j>n$, and $\pl F$ wins the game.
-\end{proof}
-
-  (TODO: The above result is cute, but unnecessary due to the below.)
+%   (TODO: The above result is cute, but unnecessary due to the below.)
 

### 2014-06-27 phd/dissertation/chapter3.tex
Finish draft of chapter 3

@@
 
-Coding strategies have been studied since the earliest days of the
-Banach-Mazur game.
+As an example, the existence of a winning coding strategy is necessary for the
+second player to force a win the Banach-Mazur game.
 
-\begin{thm}
-  (TODO: Cite the precise version of the BM game where a winning strategy
-    implies a coding strategy.)
+\begin{thm}\label{bmcode}
+  $\pl N\win\bmgame{X}$ if and only if $\pl N\codewin\bmgame{X}$
+  \cite{MR817083} \cite{MR831181}.
 \end{thm}
+
+We are interested in whether the same holds for $W$ games.
 
@@
 
-\begin{thm}
+This game has a strong resemblance to a game defined by Scheepers in
+\cite{MR1129143} in relationship to the Banach-Mazur game and studied
+specifically with finite and countable sets in \cite{MR1183703}. Scheeper's
+game and the results pertaining to it aren't of use here; however, they will be
+referenced in a later chapter in studying a different topological game.
+
+This game of finite and countable sets is directly applicable to the $W$
+games played upon the sigma-product of real lines.
+
+\begin{lem}
   $\pl F \codewin \pfgame\kappa$ implies
   $\pl O \codewin \congame{\SigmaProdR\kappa}{\vec0}$.
-\end{thm}
+\end{lem}
 
@@
 
-% \begin{thm}
-%   Let $\cf{[\kappa]^{\leq\omega}}=\kappa$.
-%   Then $\pl F \codewin \pfgame\kappa$.
-% \end{thm}
-
-% \begin{proof}
-% Let $c:\kappa\to[\kappa]^{\leq \omega}$ be a funtion such that for every
-% $W\in[\kappa]^{\leq\omega}$, there exists $\gamma_W<\kappa$ with
-% $W\subseteq c(\gamma_W)$.
-
-% Let $W\rest n \in [\kappa]^n$ be a subset of $W\in[\kappa]^\omega$ such that
-% $W\rest n \subset W \rest (n+1)$ and $\bigcup_{n<\omega} W\rest n = W$.
-
-% Define the coding strategy $\sigma$ as follows:
-%   \[
-%     \sigma(\emptyset) = \emptyset
-%   \]
-%   \[
-%     \sigma(\<N,W\>)
-%       =
-%     N
-%       \cup
-%     (|N|+1)
-%       \cup
-%     \{\gamma_W\}
-%       \cup
-%     \bigcup_{\alpha \in N}\left(c(\alpha) \rest |N|\right)
-%   \]
-
-% Let $\<W_0,W_1,\dots\>$ be a legal attack against $\sigma$,
-% $N_0=\sigma(\emptyset)$, and
-% $N_{i+1}=\sigma(\<N_i,W_i\>)$. Then $\<N_0,W_0,N_1,W_1,\dots\>$ is the
-% playthrough of the game coresponding to the coding strategy $\sigma$ and
-% attack $a$.
-
-% Let $\alpha\in W_i$ for some $i<\omega$. Then $\gamma_{W_i}\in N_n$ when
-% $n>i$. Since $W_i\subseteq c(\gamma_{W_i})$, there exists some $n>i$ such
-% that $\alpha\in c(\gamma_{W_i})\rest n$.
-% Finally, we consider
-%   \[
-%     N_{n+1}
-%       =
-%     \sigma(\<N_n,W_n\>)
-%       \supseteq
-%     \bigcup_{\alpha\in N_n}\left(c(\alpha) \rest |N_n|\right)
-%       \supseteq
-%     c(\gamma_{W_i})\rest |N_n|
-%   \]
-% and since $|N_n|\geq n$, we may conclude $\alpha\in N_{n+1}$.
-% Thus $\alpha\not\in W_j$ for $j>n$, and $\pl F$ wins the game.
-% \end{proof}
-
-%   (TODO: The above result is cute, but unnecessary due to the below.)
+This lemma simplifies our notation in proving the main result. Intuitively, we
+aim to show that when $\kappa$ has cofinality $\omega$, $\pl F$ can split up
+the game among $\omega$-many smaller cardinals converging to $\kappa$, and
+when $\kappa$ has a larger cofinality, $\pl F$ may exploit the fact that $\pl C$
+may only play within some ordinal smaller than $\kappa$.
 
@@
 \begin{proof}
-  TODO: Fill in sketch.
+  For each cardinal $\kappa$ and $\lambda<\kappa$,
+  assume $\sigma_\lambda$ is a winning strategy for $\pl F$ in $\pfgame\lambda$
+  such that $\sigma_\lambda(\emptyset)\supset\emptyset$ and
+  $\sigma_\lambda(\<F,C\>)\supset F$.
 
-  SKETCH: For each cardinal
-  $\kappa$, assume $F\codewin\pfgame\lambda$ for $\lambda<\kappa$. Always
-  cover the upper bound of $\pl O$'s moves if possible, or use a trick
-  assuming $\cf\kappa=\omega$.
+  In the case that $\cf\kappa=\omega$, let $\<\kappa_0,\kappa_1,\dots\>$ be
+  an increasing sequence of cardinals limiting to $\kappa$. Then we define
+  the coding strategy $\sigma$ for $\pl F$ as follows:
+    \[
+      \sigma(\emptyset) = \sigma_{K_0}(\emptyset)
+    \]
+    \[
+      \sigma(\<F,C\>)
+        =
+      \bigcup_{n\leq|F|}
+      \sigma_{\kappa_n}(\<F\cap \kappa_n,C\cap \kappa_n\>)
+    \]
+
+  Then for each legal attack $a=\<a(0),a(1),\dots\>$ by $\pl C$ against $\sigma$
+  and each $n<\omega$, the sequence
+  $b_n=\<a(n)\cap \kappa_n,a(n+1)\cap \kappa_n,\dots\>$
+  is a legal attack by $\pl C$ against the winning coding strategy
+  $\sigma_{\kappa_n}$. It follows then that $\{a(i+n)\cap \kappa_n:i<\omega\}$
+  is a point-finite cover of $\bigcup_{i<\omega}a(i+n)\cap \kappa_n$. We
+  conclude that $\{a(i):i<\omega\}$ is a point-finite cover of
+  $\bigcup_{i<\omega}a(i)$ and $\sigma$ is a winning strategy.
+
+  It remains to consider the case where $\cf\kappa>\omega$. Note that now, for
+  each $C\in[\kappa]^{\leq\omega}$, $C$ is bounded above in $\kappa$. So we
+  define the coding strategy $\sigma$ for $\pl F$ as follows:
+    \[
+      \sigma(\emptyset) = \emptyset
+    \]
+    \[
+      \sigma(\<F,C\>)
+        =
+      \{\sup(C)\}
+        \cup
+      \bigcup_{\alpha\in F}
+      \sigma_{\alpha+1}(\<F\cap(\alpha+1),C\cap(\alpha+1)\>)
+    \]
+
+  Then for each legal attack $a=\<a(0),a(1),\dots\>$ by $\pl C$ against $\sigma$
+  and each $n<\omega$, the sequence
+  $b_n=\<a(n)\cap (\sup(a(n))+1),a(n+1)\cap (\sup(a(n))+1),\dots\>$
+  is a legal attack by $\pl C$ against the winning coding strategy
+  $\sigma_{\sup(a(n))+1}$. It follows then that
+  $\{a(i+n)\cap (\sup(a(n))+1):i<\omega\}$
+  is a point-finite cover of $\bigcup_{i<\omega}a(i+n)\cap(\sup(a(n))+1)$. We
+  conclude that $\{a(i):i<\omega\}$ is a point-finite cover of
+  $\bigcup_{i<\omega}a(i)$ and $\sigma$ is a winning strategy.
 \end{proof}
@@
 \begin{cor}
-  $O\codewin\congame{\SigmaProdR{\kappa}}{\vec{0}}$
+  $\pl O\codewin\congame{\SigmaProdR{\kappa}}{\vec{0}}$
   for all cardinals $\kappa$.
 \end{cor}
+
+This leaves open the question analogous to Theorem \ref{bmcode}.
+
+\begin{ques}
+  Does $\pl O \win\congame{X}{x}$ imply $\pl O \codewin\congame{X}{x}$?
+\end{ques}

### 2014-06-30 phd/dissertation/chapter5.tex
begun work on Menger chapter

@@
 
-Results pertaining to the Locally Finite games related to $W$ games.
+placeholder
 
-\section{Characterizations using $\lfkpgame{X}$, $\lfklgame{X}$}
+% Results pertaining to the Locally Finite games related to $W$ games.
 
-\begin{thm}(G)
-  The following are equivalent for a locally compact space $X$:
-    \begin{itemize}
-      \item $X$ is paracompact
-      \item $\pl K \uparrow \lfklgame{X}$.
-    \end{itemize}
-\end{thm}
+% \section{Characterizations using $\lfkpgame{X}$, $\lfklgame{X}$}
 
-\begin{thm}(G)
-  The following are equivalent for a locally compact space $X$:
-    \begin{itemize}
-      \item $X$ is metacompact
-      \item $\pl K \tactwin \lfkpgame{X}$.
-    \end{itemize}
-\end{thm}
+% \begin{thm}(G)
+%   The following are equivalent for a locally compact space $X$:
+%     \begin{itemize}
+%       \item $X$ is paracompact
+%       \item $\pl K \uparrow \lfklgame{X}$.
+%     \end{itemize}
+% \end{thm}
 
-\begin{thm}(G)
-  The following are equivalent for a locally compact space $X$:
-    \begin{itemize}
-      \item $X$ is $\sigma$-metacompact
-      \item $\pl K \markwin \lfkpgame{X}$.
-    \end{itemize}
-\end{thm}
+% \begin{thm}(G)
+%   The following are equivalent for a locally compact space $X$:
+%     \begin{itemize}
+%       \item $X$ is metacompact
+%       \item $\pl K \tactwin \lfkpgame{X}$.
+%     \end{itemize}
+% \end{thm}
 
-\begin{obs}
-  The following are equivalent for any space $X$:
-    \begin{itemize}
-      \item $X$ is compact
-      \item $\pl K \ktactwin{0} \lfkpgame{X}$.
-    \end{itemize}
-\end{obs}
+% \begin{thm}(G)
+%   The following are equivalent for a locally compact space $X$:
+%     \begin{itemize}
+%       \item $X$ is $\sigma$-metacompact
+%       \item $\pl K \markwin \lfkpgame{X}$.
+%     \end{itemize}
+% \end{thm}
 
-\begin{thm}
-  $P \markwin G_{K,P}(X)$ where $X$ is a first-countable non-locally
-  countably compact space.
-\end{thm}
+% \begin{obs}
+%   The following are equivalent for any space $X$:
+%     \begin{itemize}
+%       \item $X$ is compact
+%       \item $\pl K \ktactwin{0} \lfkpgame{X}$.
+%     \end{itemize}
+% \end{obs}
 
-\begin{thm}
-  $P \not\tactwin G_{K,P}(M)$ where $M$ is the metric fan space.
-\end{thm}
+% \begin{thm}
+%   $P \markwin G_{K,P}(X)$ where $X$ is a first-countable non-locally
+%   countably compact space.
+% \end{thm}
 
-\begin{thm}
-  The following are equivalent for any locally compact space $X$:
-    \begin{itemize}
-      \item $X$ is Lindel\"of.
-      \item $X$ is $\sigma$-compact.
-      \item $X$ is hemicompact.
-      \item $\pl K \prewin G_{K,L}(X)$.
-      \item $\pl K \prewin G_{K,P}(X)$.
-    \end{itemize}
-\end{thm}
+% \begin{thm}
+%   $P \not\tactwin G_{K,P}(M)$ where $M$ is the metric fan space.
+% \end{thm}
 
-\begin{thm}
-  The following are equivalent for any Hausdorff $k$-space $X$:
-    \begin{itemize}
-      \item $X$ is hemicompact.
-      \item $X$ is $k_{\omega}$.
-      \item $\pl K \prewin \lfklgame{X}$.
-      \item $\pl K \prewin \lfkpgame{X}$.
-    \end{itemize}
-\end{thm}
+% \begin{thm}
+%   The following are equivalent for any locally compact space $X$:
+%     \begin{itemize}
+%       \item $X$ is Lindel\"of.
+%       \item $X$ is $\sigma$-compact.
+%       \item $X$ is hemicompact.
+%       \item $\pl K \prewin G_{K,L}(X)$.
+%       \item $\pl K \prewin G_{K,P}(X)$.
+%     \end{itemize}
+% \end{thm}
 
-\section{Non-locally compact spaces}
+% \begin{thm}
+%   The following are equivalent for any Hausdorff $k$-space $X$:
+%     \begin{itemize}
+%       \item $X$ is hemicompact.
+%       \item $X$ is $k_{\omega}$.
+%       \item $\pl K \prewin \lfklgame{X}$.
+%       \item $\pl K \prewin \lfkpgame{X}$.
+%     \end{itemize}
+% \end{thm}
 
-\begin{prop}
-  If $X=\omega\cup\mathcal{F}\subset\beta\omega$ (a non-$k$ space),
-  then $K\not\prewin \lfklgame{X}$.
-\end{prop}
+% \section{Non-locally compact spaces}
 
-\begin{prop}
-  If a selective ultrafilter $\mathcal{F}$ exists (independent of ZFC),
-  then $K \not\prewin \lfkpgame{X}$
-  for $X=\omega \cup \{\mathcal{F}\}\subset \beta\omega$.
-\end{prop}
+% \begin{prop}
+%   If $X=\omega\cup\mathcal{F}\subset\beta\omega$ (a non-$k$ space),
+%   then $K\not\prewin \lfklgame{X}$.
+% \end{prop}
 
-\begin{thm}
-  Then there is an ultrafilter $\mathcal{F}$ such that
-  then $K \prewin \lfkpgame{X}$ and $K \tactwin \lfkpgame{X}$
-  for $X=\omega \cup \{\mathcal{F}\}\subset \beta\omega$.
-\end{thm}
+% \begin{prop}
+%   If a selective ultrafilter $\mathcal{F}$ exists (independent of ZFC),
+%   then $K \not\prewin \lfkpgame{X}$
+%   for $X=\omega \cup \{\mathcal{F}\}\subset \beta\omega$.
+% \end{prop}
 
-\begin{thm}
-  Let $M$ be the \term{metric fan}, a non-locally compact $k$ space.
-  Then $P \win \lfkpgame{M}$.
-\end{thm}
+% \begin{thm}
+%   Then there is an ultrafilter $\mathcal{F}$ such that
+%   then $K \prewin \lfkpgame{X}$ and $K \tactwin \lfkpgame{X}$
+%   for $X=\omega \cup \{\mathcal{F}\}\subset \beta\omega$.
+% \end{thm}
 
-\begin{thm}
-  Let $S$ be the \term{sequential fan}, a non-locally compact $k$ space.
-  Then $K \prewin \lfkpgame{S}$ and $K\tactwin \lfkpgame{S}$.
-\end{thm}
+% \begin{thm}
+%   Let $M$ be the \term{metric fan}, a non-locally compact $k$ space.
+%   Then $P \win \lfkpgame{M}$.
+% \end{thm}
 
-(TODO: Maybe consider claim
-$K \prewin \lfkpgame{X}$ $\Rightarrow$ $X$ is a $k$-space)
+% \begin{thm}
+%   Let $S$ be the \term{sequential fan}, a non-locally compact $k$ space.
+%   Then $K \prewin \lfkpgame{S}$ and $K\tactwin \lfkpgame{S}$.
+% \end{thm}
 
-\section{Cantor tree space example}
+% (TODO: Maybe consider claim
+% $K \prewin \lfkpgame{X}$ $\Rightarrow$ $X$ is a $k$-space)
 
-\begin{ex}
-  Let $X$ be a zero-dimensional, compact L-space
-  (hereditarally Lindeloff and non-separable).
-  It is a fact that there exists a point-countable collection
-  $\mathcal{U}=\{U_\alpha : \alpha<\omega_1\}$ of clopen sets in $X$, and it is
-  also true that any point-finite subcollection of $\mathcal{U}$ is countable.
+% \section{Cantor tree space example}
 
-  Let $C = \{c_\alpha : \alpha <\omega_1\}$ be any uncountable subset of the
-  Cantor space $2^\omega$. Let $X_s = X \times \{s\}$ for each
-  $s \in 2^{<\omega}$, and $U_{\alpha,s} = U_\alpha \times \{s\}$.
+% \begin{ex}
+%   Let $X$ be a zero-dimensional, compact L-space
+%   (hereditarally Lindeloff and non-separable).
+%   It is a fact that there exists a point-countable collection
+%   $\mathcal{U}=\{U_\alpha : \alpha<\omega_1\}$ of clopen sets in $X$, and it is
+%   also true that any point-finite subcollection of $\mathcal{U}$ is countable.
 
-  Finally, let \[\mathbb{X} = C \cup \bigcup_{s\in 2^{<\omega}} X_s\] be a
-  tree of $2^{<\omega}$ copies of $X$, and where
-  \[c_\alpha \cup \bigcup_{n < \omega} U_{\alpha, x_\alpha \restriction n}\]
-  is an open set about each $c_\alpha$.
-\end{ex}
+%   Let $C = \{c_\alpha : \alpha <\omega_1\}$ be any uncountable subset of the
+%   Cantor space $2^\omega$. Let $X_s = X \times \{s\}$ for each
+%   $s \in 2^{<\omega}$, and $U_{\alpha,s} = U_\alpha \times \{s\}$.
 
-\begin{prop}
-$K \win \lfkpgame{\mathbb{X}}$.
-\end{prop}
+%   Finally, let \[\mathbb{X} = C \cup \bigcup_{s\in 2^{<\omega}} X_s\] be a
+%   tree of $2^{<\omega}$ copies of $X$, and where
+%   \[c_\alpha \cup \bigcup_{n < \omega} U_{\alpha, x_\alpha \restriction n}\]
+%   is an open set about each $c_\alpha$.
+% \end{ex}
 
-\begin{thm}(cor of G, game-theoretic proof by me)
-$K\not\tactwin\lfkpgame{\mathbb{X}}$.
-\end{thm}
+% \begin{prop}
+% $K \win \lfkpgame{\mathbb{X}}$.
+% \end{prop}
 
-\begin{thm}
-$K\not\ktactwin{k}\lfkpgame{\mathbb{X}}$.
-\end{thm}
+% \begin{thm}(cor of G, game-theoretic proof by me)
+% $K\not\tactwin\lfkpgame{\mathbb{X}}$.
+% \end{thm}
+
+% \begin{thm}
+% $K\not\ktactwin{k}\lfkpgame{\mathbb{X}}$.
+% \end{thm}

### 2014-06-30 phd/dissertation/chapter3.tex
begun work on Menger chapter
changes per discussion with G

@@
 
-\chapter{$W$ convergence and clustering games}
+\chapter{$W$ Convergence and Clustering Games}
 
@@
 \begin{proof}
-  The forward implication shows that all $W$ spaces are first-countable spaces,
+  The forward implication shows that all first-countable spaces are $W$ spaces,
   and was proven in \cite{MR0413049}: if $\{U_n:n<\omega\}$ is a countable
@@
   If $X$ is not first countable at some $x$, let $\sigma$ be a
-  predetermined strategy for $\pl O$ in $\congamehard{X}{x}$. There exists
+  predetermined strategy for $\pl O$ in $\congame{X}{x}$. There exists
   an open neighborhood $U$ of $x$ which does not contain any
@@
   Let $\sigma$ be a $k$-tactic for $\pl O$ in
-  $\clusgame{\oneptcomp\omega_1}{\infty}$. By the closing-up lemma, the set
+  $\clusgamehard{\oneptcomp\omega_1}{\infty}$. By the closing-up lemma, the set
     \[
@@
     \]
-  has a range outside the open neighborhood
+  has a range outside the open neighborhood %FIXME, say has finite range.
     \[
@@
     \]
-  is closed and unbounded. Let $a_\sigma:\omega_2\to C_\sigma$ be
+  is closed and unbounded. (Recall that $\mu_k$ is the
+  $k$-Mark\"ov fog-of-war which turns perfect information into the last $k$
+  moves and the round number.) Let $a_\sigma:\omega_2\to C_\sigma$ be
   an order isomorphism.
@@
         \in
-      \bigcup_{n<\omega}
+      \bigcap_{n<\omega}
       \sigma(
@@
     \[
-      \sigma(\emptyset) = \sigma_{K_0}(\emptyset)
+      \sigma(\emptyset) = \sigma_{\kappa_0}(\emptyset)
     \]

### 2014-07-15 phd/talks-and-presentations/2014-07-23-menger-talk.tex
half of menger talk

% $Header: /home/vedranm/bitbucket/beamer/solutions/generic-talks/generic-ornate-15min-45min.en.tex,v 90e850259b8b 2007/01/28 20:48:30 tantau $

\documentclass{beamer}

% This file is a solution template for:

% - Giving a talk on some subject.
% - The talk is between 15min and 45min long.
% - Style is ornate.

% Copyright 2004 by Till Tantau <tantau@users.sourceforge.net>.
%
% In principle, this file can be redistributed and/or modified under
% the terms of the GNU Public License, version 2.
%
% However, this file is supposed to be a template to be modified
% for your own needs. For this reason, if you use this file as a
% template and not specifically distribute it as part of a another
% package/program, I grant the extra permission to freely copy and
% modify this file as you see fit and even to delete this copyright
% notice.

\mode<presentation>
{
  \usetheme{Warsaw}
  % or ...

  \setbeamercovered{transparent}
  % or whatever (possibly just delete it)
}

      \newtheorem{proposition}[theorem]{Proposition}
      \theoremstyle{definition}
      \newtheorem{game}[theorem]{Game}
      \newtheorem{question}[theorem]{Question}

\usepackage[english]{babel}
% or whatever

\usepackage[latin1]{inputenc}
% or whatever

\usepackage{times}
\usepackage[T1]{fontenc}
% Or whatever. Note that the encoding and the font should match. If T1
% does not look nice, try deleting the line with the fontenc.

\usepackage{marvosym} % For \Smiley
\usepackage{verbatim} % for \verbatiminput

\title
{Game-theoretic strengthenings of Menger's property}

\subtitle
{29th Summer Conference on Topology and its Applications} % (optional)

\author%[Author, Another] % (optional, use only with lots of authors)
{Steven~Clontz~\\http://stevenclontz.com}%\inst{1} \and S.~Another\inst{2}}
% - Use the \inst{?} command only if the authors have different
%   affiliation.

\institute[Auburn University] % (optional, but mostly needed)
{
  %\inst{1}%
  Department of Mathematics and Statistics\\
  Auburn University}
  %\and
  %\inst{2}%
  %Department of Theoretical Philosophy\\
  %University of Elsewhere}
% - Use the \inst command only if there are several affiliations.
% - Keep it simple, no one is interested in your street address.

\date[14-07-23] % (optional)
{July 23, 2014}

% If you have a file called "university-logo-filename.xxx", where xxx
% is a graphic format that can be processed by latex or pdflatex,
% resp., then you can add a logo as follows:

 % \pgfdeclareimage[height=1cm]{university-logo}{auburn_logo.png}
 % \logo{\pgfuseimage{university-logo}}

% Delete this, if you do not want the table of contents to pop up at
% the beginning of each subsection:
%\AtBeginSubsection[]
%{
%  \begin{frame}<beamer>{Outline}
%    \tableofcontents[currentsection,currentsubsection]
%  \end{frame}
%}

% If you wish to uncover everything in a step-wise fashion, uncomment
% the following command:

%\beamerdefaultoverlayspecification{<+->}

% Strategy uparrow shortcuts
\newcommand{\win}{\uparrow}
\newcommand{\prewin}{\underset{\text{pre}}{\uparrow}}
\newcommand{\markwin}{\underset{\text{mark}}{\uparrow}}
\newcommand{\tactwin}{\underset{\text{tact}}{\uparrow}}
\newcommand{\kmarkwin}[1]{\underset{#1\text{-mark}}{\uparrow}}
\newcommand{\ktactwin}[1]{\underset{#1\text{-tact}}{\uparrow}}
\newcommand{\codewin}{\underset{\text{code}}{\uparrow}}
\newcommand{\limitwin}{\underset{\text{limit}}{\uparrow}}

\newcommand{\oneptcomp}[1]{#1^*}
\newcommand{\oneptlind}[1]{#1^\dagger}
% \newcommand{\sharp}[1]{#1^{\#}}

\newcommand{\congame}[2]{Con_{O,P}(#1,#2)}
\newcommand{\congamehard}[2]{Con_{O,P}^\star(#1,#2)}
\newcommand{\clusgame}[2]{Clus_{O,P}(#1,#2)}
\newcommand{\clusgamehard}[2]{Clus_{O,P}^\star(#1,#2)}

\newcommand{\lfkpgame}[1]{LF_{K,P}(#1)}
\newcommand{\lfklgame}[1]{LF_{K,L}(#1)}

\newcommand{\pfgame}[1]{PF_{F,C}(#1)}

\newcommand{\mengame}[1]{Cov_{C,F}(#1)}
\newcommand{\rothgame}[1]{Cov_{C,S}(#1)}
\newcommand{\altrothgame}[1]{Cov_{P,O}(#1)}

\newcommand{\fillgameS}[1]{Fill^{\cup,\subset}_{C,F}(#1)}
\newcommand{\fillgame}[1]{Fill^{\cup,\subseteq}_{C,F}(#1)}
\newcommand{\fillgameOne}[1]{Fill^{1,\subseteq}_{C,F}(#1)}
\newcommand{\fillgameInt}[1]{Fill^{\cap}_{C,F}(#1)}

\newcommand{\recallgame}[2]{Rec^{#1}_{F,S}(#2)}

\newcommand{\proxgame}[1]{Prox_{D,P}(#1)}
\newcommand{\aproxgame}[1]{aProx_{D,P}(#1)}

\newcommand{\SigmaProdR}[1]{\Sigma\mathbb{R}^{#1}}
\newcommand{\sigmaprodtwo}[1]{\Sigma2^{#1}}

\newcommand{\concat}{{^\frown}}
\newcommand{\rest}{\restriction}

\newcommand{\cl}[1]{\overline{#1}}

\newcommand{\pow}[1]{\mc{P}(#1)}

\newcommand{\<}{\langle}
\renewcommand{\>}{\rangle}

\newcommand{\al}[1]{{#1}^*}

\newcommand{\mc}[1]{\mathcal{#1}}

\newcommand{\po}{\mathbb{P}}
\newcommand{\pok}{\po_\kappa}

\newcommand{\Lim}{\mathrm{Lim}}
\newcommand{\Suc}{\mathrm{Suc}}

\newcommand{\ds}{\displaystyle}

\newcommand{\st}[2]{st\left(#1,#2\right)}

\newcommand{\alcomp}{\al\parallel}

\newcommand{\rank}{\textrm{rank}}
\newcommand{\dom}{\textrm{dom}}

\renewcommand{\mod}{\,\textrm{mod}}

\newcommand{\zip}{\bowtie}
\newcommand{\ran}[1]{\text{range}(#1)}

\newcommand{\cf}[1]{\textrm{cf}(#1)}

\newcommand{\alcompS}[1]{S(#1,\omega,\omega)}

\newcommand{\scish}{almost-$\sigma$-(relatively compact)}

\usepackage{mathrsfs}
\newcommand{\pl}[1]{\mathscr{#1}}

\newcommand{\term}{\textit}

\newcommand{\bakergame}[1]{{Lim}_{A,B}(#1)}
\newcommand{\bmgame}[1]{{Empty}_{E,N}(#1)}

\begin{document}
\renewcommand{\pause}{}
\newcommand{\vpause}{\pause\vspace{1em}}

\begin{frame}
  \titlepage
\end{frame}

% \begin{frame}{Table of Contents}
%   \tableofcontents
%   % You might wish to add the option [pausesections]
% \end{frame}

\section{Introduction}

\subsection{Abstract}

\begin{frame}{Abstract}%{Subtitles are optional.}
    \small
    A certain topological game introduced by Hurewicz characterizes Menger's
    covering property whenever the first player lacks a winning strategy. It
    was later shown by Telgarsky (and later by Scheepers using a different
    argument) that for metric spaces, the second player having a winning
    strategy characterizes the stronger property of $\sigma$-compactness.

    \vspace{1em}

    We factor out Scheepers' proof to show
    that for regular spaces, the second player having a winning $1$-Mark\"ov
    strategy characterizes $\sigma$-compactness; also, for second-countable
    spaces, the presence of a winning perfect information strategy for the
    second player implies the existence of a winning $1$-Mark\"ov strategy for
    that player. We also show the that for all $k$, the existence of a
    winning $k$-Mark\"ov strategy for the second player implies the existence
    of a winning $2$-Mark\"ov strategy, and give a space which permits
    a winning $2$-Mark\"ov strategy but not a winning $1$-Mark\"ov strategy.
\end{frame}

\section{Menger Spaces and the Menger Game}

\subsection{Definitions}

\begin{frame}{The Menger property}
  \begin{definition}
    A space $X$ is Menger if for every sequence $\<\mc U_0,\mc U_1,\dots\>$
    of open covers of $X$ there exists a sequence
    $\<\mc F_0,\mc F_1,\dots\>$ such that $\mc F_n\subseteq \mc U_n$,
    $|\mc F_n|<\omega$, and $\bigcup_{n<\omega}\mc F_n$ is a cover of $X$.
  \end{definition}

  \pause

  \begin{proposition}
    $X$ is $\sigma$-compact
      $\Rightarrow$
    $X$ is Menger
      $\Rightarrow$
    $X$ is Lindel\"of.
  \end{proposition}
\end{frame}

\begin{frame}{The Menger game}
  \begin{game}
    Let $\mengame{X}$ denote the \term{Menger game} with players
    $\pl C$, $\pl F$.
    In round $n$, $\pl C$ chooses an open cover $\mc C_n$,
    followed by $\pl F$
    choosing a finite subcollection $\mc F_n\subseteq \mc C_n$.

    $\pl F$ wins the game, that is, $\pl F \win \mengame{X}$ if
    $\bigcup_{n<\omega}\mc F_n$ is a cover for the space
    $X$, and $\pl C$ wins otherwise.
  \end{game}

  \pause

  \begin{theorem}
    $X$ is Menger if and only if $\pl C \not\win \mengame X$.
    (Hurewicz 1926, effectively)
  \end{theorem}
\end{frame}

\begin{frame}
  Menger suspected that the subsets of the real line with his property were
  exactly the $\sigma$-compact spaces; however:

  \pause

  \begin{theorem}
    There are $ZFC$ examples of non-$\sigma$-compact
    subsets of the real line which are Menger. (Fremlin, Miller 1988)
  \end{theorem}

  But metrizable non-$\sigma$-compact Menger spaces will be
  \term{undetermined} for the Menger game.

  \pause

  \begin{theorem}
    Let $X$ be metrizable. $\pl F\win\mengame X$ if and only if $X$ is
    $\sigma$-compact. (Telgarsky 1984, Scheepers 1995)
  \end{theorem}
\end{frame}

\subsection{Scheeper's Proof}

\begin{frame}
  Note that for Lindel\"of spaces, metrizability is characterized by regularity
  and secound countability.

  \vpause

  Sketch of Scheeper's proof:
  \begin{itemize}
    \item Using second-countability and the winning strategy for $\pl F$,
          construct certain subsets $R_s$ for $s \in \omega^{<\omega}$ such
          that $X = \bigcup_{s\in\omega^{<\omega}}$.
    \item Using regularity, show that each $R_s$ is compact.
    \item The result follows since $|\omega^{<\omega}|=\omega$.
  \end{itemize}

  \vpause

  By considering winning \term{limited-information strategies}, we'll be able
  to factor out this proof a bit.
\end{frame}

\subsection{Limited information strategies}

\begin{frame}{Limited information strategies}
  \begin{definition}
    A \term{(perfect information) strategy} has knowledge of all the past
    moves of the opponent.
  \end{definition}

  \pause

  \begin{definition}
    A \term{$k$-tactical strategy} has knowledge of only the past $k$
    moves of the opponent.
  \end{definition}

  \pause

  \begin{definition}
    A \term{$k$-Mark\"ov strategy} has knowledge of only the past $k$
    moves of the opponent and the round number.
  \end{definition}
\end{frame}

\begin{frame}
  Obviously,
  \[
    \pl A \ktactwin{k} G
      \Rightarrow
    \pl A \kmarkwin{k} G
      \Rightarrow
    \pl A \underset{\text{(perfect)}}{\uparrow} G
  \]

  \vpause

  But tactical strategies aren't interesting for the Menger game.

  \begin{proposition}
    For any $k<\omega$,
    $\pl F\ktactwin{k}\mengame X$ if and only if $X$ is compact.
  \end{proposition}

  Effectively, $\pl F$ needs some sort of seed to prevent from being
  stuck in a loop: there's nothing stopping $\pl C$ from playing the
  same open cover during every round of the game.
\end{frame}

\section{$1$-Mark\"ov Strategies}

\subsection{Limited info and relative compactness}

\begin{frame}
  Comparitively, Mark\"ov strategies are very powerful.

  \begin{proposition}
    If $X$ is $\sigma$-compact, then $\pl F \kmarkwin{1}\mengame X$.
  \end{proposition}

  \begin{proof}
    Let $X=\bigcup_{n<\omega}K_n$. During round $n$, $\pl F$ picks a finite
    subcollection of
    the last open cover played by $\pl C$ (the only one $\pl F$ remembers)
    which covers $K_n$.
  \end{proof}
\end{frame}

\begin{frame}
  Without assuming regularity, we can't quite reverse the implication, but
  we can get close.

  \pause

  \begin{definition}
    A subset $Y$ of $X$ is \term{relatively compact} if for every open cover
    for $X$, there exists a finite subcollection which covers $Y$.
  \end{definition}

  \begin{proposition}
    If $X$ is $\sigma$-relatively-compact, then $\pl F \kmarkwin{1}\mengame X$.
  \end{proposition}

  \pause

  \begin{proposition}
    For regular spaces, $Y\subseteq X$ is relatively compact if and only if
    $\cl Y$ is compact. So $\sigma$-relatively-compact regular spaces are
    exactly the $\sigma$-compact regular spaces.
  \end{proposition}
\end{frame}

\begin{frame}

  \begin{theorem}
    $\pl F \kmarkwin{1}\mengame X$ if and only if $X$ is
    $\sigma$-relatively-compact.
  \end{theorem}

  \pause

  \begin{proof}
    Let $\sigma(\mc U, n)$ represent a $1$-Mark\"ov strategy.
    For every open cover $\mc U\in\mathfrak C$, $\sigma(\mc{U},n)$
    witnesses relative compactness for the set
      \[
        R_n
          =
        \bigcap_{\mc U\in\mathfrak C}\bigcup \sigma(\mc U,n)
      \]

    \pause

    If $X$ is not $\sigma$-relatively compact, fix $x \not\in R_n$ for any
    $n<\omega$. Then $\pl C$ can beat
    $\sigma$ by choosing $\mc{U}_n\in\mathfrak{C}$ during each round
    such that $x\not\in \bigcup\sigma(\mc{U}_n,n)$.
  \end{proof}
\end{frame}

\subsection{Limited info in second-countable spaces}

\begin{frame}
  So for regular spaces, a winning strategy for $\pl F$ in the Menger game
  isn't sufficient to characterize $\sigma$-compactness, but a winning
  $1$-Mark\"ov strategy does the trick.

  \vpause

  We can complete Telgarsky's/Scheeper's result by showing the following:

  \begin{theorem}
    For second countable spaces $X$, $\pl F \win \mengame X$ if and only if
    $\pl F \kmarkwin{1}\mengame X$.
  \end{theorem}
\end{frame}

\begin{frame}{Proof}
  Let $\sigma$ be a perfect information strategy.
  Since $X$ is a second-countable space, we may pretend that there are only
  countably many finite collections of open sets. Thus for
  $s\in\omega^{<\omega}$, we may define open covers $\mc U_{s\concat\<n\>}$
  such that for each open cover $\mc U$, there is some $n<\omega$ where
  \[
    \sigma(\mc U_{s\rest 1},\dots,\mc U_{s},\mc U)
      =
    \sigma(\mc U_{s\rest 1},\dots,\mc U_{s},\mc U_{s\concat\<n\>})
  \]

  \vpause

  Let $t:\omega\to\omega^{<\omega}$ be a bijection. During round $n$ and
  seeing only the latest open cover $\mc U$, $\pl F$ may play the finite
  subcollection
  \[
    \tau(\mc U,n) = \sigma(\mc U_{t(n)\rest 1},\dots,\mc U_{t(n)},\mc U)
  \]
\end{frame}

\begin{frame}{Proof (cont.)}
  Suppose there exists a counter-attack $\<\mc V_0,\mc V_1,\dots\>$ which
  defeats the $1$-Mark\"ov strategy $\tau$. Then there exists
  $f:\omega\to\omega$ such that, if $\mc V^n=\mc V_{t^{-1}(f\rest n)}$
  \[
    \begin{array}{rcl}
    x & \not\in & \bigcup \tau(\mc V^n,t^{-1}(f\rest n)) \\
    & = & \bigcup\sigma(\mc U_{f\rest 1},\dots,\mc U_{f\rest n},\mc V^n) \\
    & = & \bigcup\sigma(\mc U_{f\rest 1},\dots,\mc U_{f\rest n},\mc U_{f\rest (n+1)})
    \end{array}
  \]

  \vpause

  Thus $\<\mc U_{f\rest 1}, \mc U_{f\rest 2},\dots\>$ is a successful
  counter-attack by $\pl C$ against the perfect information strategy $\sigma$.
  \qed
\end{frame}

\section{$k$-Mark\"ov strategies for $k\geq 2$}

\subsection{$k$-Mark\"ov implies $2$-Mark\"ov}

\begin{frame}
  Unlike the Banach-Mazur game, we can immediately see that knowledge
  of more than two previous moves of $\pl F$'s opponent must be infinite
  to be of any use.

  \begin{theorem}
    If $\pl F \kmarkwin{k}\mengame X$, then $\pl F \kmarkwin2\mengame X$.
  \end{theorem}

  \begin{proof}
    \[
      \tau(\<\mc U,\mc V\>,n+1)
        =
      \bigcup_{m<k+2}
        \sigma(\<
          \underbrace{\mc U,\dots,\mc U}_{k+1-m},
          \underbrace{\mc V,\dots,\mc V}_{m+1}
        \>,(n+1)(k+2)+m)
    \]
  \end{proof}
\end{frame}

\subsection{$2$-Mark\"ov but not $1$-Mark\"ov}

\begin{frame}
  foo
\end{frame}

\section*{}

\begin{frame}
Questions? Thanks for having me!
\end{frame}

\end{document}

### 2014-07-15 phd/talks-and-presentations/2014-07-23-menger-talk.tex
draft of talk on menger game for summer conference

@@
 \usepackage{verbatim} % for \verbatiminput
+
+\usepackage{tikz}
+\usetikzlibrary{matrix} % for diagrams
 
@@
 \newcommand{\limitwin}{\underset{\text{limit}}{\uparrow}}
+\newcommand{\notprewin}{\underset{\text{pre}}{\not\uparrow}}
+\newcommand{\notmarkwin}{\underset{\text{mark}}{\not\uparrow}}
+\newcommand{\nottactwin}{\underset{\text{tact}}{\not\uparrow}}
+\newcommand{\notkmarkwin}[1]{\underset{#1\text{-mark}}{\not\uparrow}}
+\newcommand{\notktactwin}[1]{\underset{#1\text{-tact}}{\not\uparrow}}
+\newcommand{\notcodewin}{\underset{\text{code}}{\not\uparrow}}
+\newcommand{\notlimitwin}{\underset{\text{limit}}{\not\uparrow}}
 
@@
 
-\newcommand{\al}[1]{{#1}^*}
-
 \newcommand{\mc}[1]{\mathcal{#1}}
@@
 
-\newcommand{\alcomp}{\al\parallel}
+\newcommand{\al}[1]{{#1}^*}
+\newcommand{\alcomp}{\wr}
 
@@
     \item Using second-countability and the winning strategy for $\pl F$,
-          construct certain subsets $R_s$ for $s \in \omega^{<\omega}$ such
-          that $X = \bigcup_{s\in\omega^{<\omega}}$.
-    \item Using regularity, show that each $R_s$ is compact.
+          construct certain subsets $K_s$ for $s \in \omega^{<\omega}$ such
+          that $X = \bigcup_{s\in\omega^{<\omega}}K_s$.
+    \item Using regularity, show that each $K_s$ is compact.
     \item The result follows since $|\omega^{<\omega}|=\omega$.
@@
 \begin{frame}
-  foo
+  Knowledge of two previous moves versus one is an important distinction:
+  in the former case, the player is able to react to change by the
+  opponent.
+
+  \pause
+
+  \begin{definition}
+    Let $\oneptlind\kappa = \kappa\cup\{\infty\}$ be the
+    \term{one point Lindel\"of-ication} of discrete $\kappa$: neighborhoods
+    of $\infty$ are exactly the co-countable sets containing it.
+  \end{definition}
+
+  \pause
+
+  $\oneptlind\kappa$ is a simple space which is a regular and Lindel\"of, but
+  not second-countable space or $\sigma$-compact. Thus
+  $\pl F\notkmarkwin{1}\mengame{\oneptlind\kappa}$, but it's easy to see
+  that $\pl F\win\mengame{\oneptlind\kappa}$. What about $2$-Mark\"ov
+  strategies?
+\end{frame}
+
+\begin{frame}
+  In 1991, Scheepers introduced the statement $\alcompS\kappa$ to study an
+  infinite game involving the countable and finite subsets of $\kappa$.
+
+  \pause
+
+  \begin{game}
+    Let $\fillgameS\kappa$ denote the \term{strict union filling game}
+    with two players $\pl C$, $\pl F$. In round $0$, $\pl C$ chooses
+    $C_0\in[\kappa]^{\leq\omega}$, followed by $\pl F$ choosing
+    $F_0\in[\kappa]^{<\omega}$. In round $n+1$, $\pl C$ chooses
+    $C_{n+1}\in[\kappa]^{\leq\omega}$ such that $C_{n+1}\supset C_n$, followed
+    by $\pl F$ choosing $F_{n+1}\in[\kappa]^{<\omega}$.
+
+    $\pl F$ wins the game if
+    $\bigcup_{n<\omega} F_n\supseteq\bigcup_{n<\omega} C_n$; otherwise, $\pl C$
+    wins.
+  \end{game}
+\end{frame}
+
+\begin{frame}
+  \begin{definition}
+    For two functions $f,g$ we say $f$ is \term{almost compatible} with
+    $g$ ($f\alcomp g$) if $|\{x\in\dom(f)\cap\dom(g):f(x)\not=g(x)\}|<\omega$.
+  \end{definition}
+  \pause
+  \begin{definition}
+    $\alcompS\kappa$ states that there exist functions
+    $f_A:A\to\omega$ for each $A\in[\kappa]^{\leq\omega}$ such that
+    $|f_A^{-1}(n)|<\omega$ for all $n<\omega$ and
+    $f_A\alcomp f_B$ for all $A,B\in[\kappa]^\omega$.
+  \end{definition}
+  \pause
+  \begin{theorem}
+    $\alcompS{\omega_1}$; $Con(\alcompS{2^\omega}+\neg CH)$;
+    $\neg\alcompS\kappa$ for $\kappa>2^\omega$.
+  \end{theorem}
+\end{frame}
+
+\begin{frame}
+  The round number is unnecessary in Scheeper's game, since $\pl C$ must
+  choose strictly increasing sets.
+
+  \begin{theorem}
+    If $\alcompS\kappa$, then $\pl F\ktactwin2 \fillgameS\kappa$.
+  \end{theorem}
+
+  \pause
+
+  As it turns out, a related game characterizes $\mengame{\oneptlind\kappa}$.
+
+  \begin{definition}
+    Let $\fillgameInt\kappa$ denote the \term{intersection filling game}
+    analogous to $\fillgameS\kappa$, except that $\pl C$ has no restriction
+    on the countable sets she choooses, but $\pl F$ need only ensure that
+    $\bigcup_{n<\omega}\mc F_n\supseteq \bigcap_{n<\omega}\mc U_n$ to win
+    the game.
+  \end{definition}
+\end{frame}
+
+\begin{frame}
+  \begin{theorem}
+    $\pl F \kmarkwin{k} \mengame{\oneptlind\kappa}$ if and only if
+    $\pl F \kmarkwin{k} \fillgameInt\kappa$.
+  \end{theorem}
+
+  \pause
+
+  \begin{theorem}
+    If $\alcompS\kappa$, then $\pl F\kmarkwin{2} \fillgameInt\kappa$.
+  \end{theorem}
+
+  \pause
+
+  \begin{proof}
+    Let $f_A:A\to\omega$ witness $\alcompS\kappa$. Then we define the
+    winning $2$-Mark\"ov strategy $\sigma$ as follows:
+      \[
+        \sigma(\<A\>,0) = \{\alpha\in A: f_A(\alpha) = 0\}
+      \]
+      \[
+        \sigma(\<A,B\>,n+1)
+          =
+        \{\alpha\in A\cap B
+          :
+        f_B(\alpha) \leq n+1
+          \text{ or }
+        f_A(\alpha)\not=f_B(\alpha)\}
+      \]
+  \end{proof}
+\end{frame}
+
+\begin{frame}
+  \begin{corollary}
+    $\pl F\kmarkwin{2}\mengame{\oneptlind\omega_1}$, but
+    $\pl F\notkmarkwin1\mengame{\oneptlind\omega_1}$.
+  \end{corollary}
+  \begin{figure}
+    \includegraphics[height=1.7in]{mengerGameChart.png}
+  \end{figure}
+\end{frame}
+
+\section{Quesitons}
+
+\begin{frame}
+  \begin{question}
+    Does $\pl F\kmarkwin2\mengame{\oneptlind\kappa}$ imply $\alcompS\kappa$?
+  \end{question}
+
+  \pause
+
+  \begin{question}
+    Are $\pl F\win\mengame X$ and $\pl F\kmarkwin2\mengame X$ distinct?
+  \end{question}
+
+  An affirmative answer to the first question answers this since
+  $\neg\alcompS\kappa$ for $\kappa>2^\omega$.
+\end{frame}
+\begin{frame}
+  \begin{question}
+    Where does $\pl F\kmarkwin2\mengame X$ fit in with other properties
+    between $\sigma$-(relatively-)compact and Menger?
+  \end{question}
+  $\pl F\kmarkwin2\mengame X$ seems to characterize an
+  ``almost-$\sigma$-(relative-)compactness''.
+
+  Any sufficient property must imply $\pl F\win\mengame X$ (ruling out
+  Hurewicz[?]), and any (interesting) necessary property shouldn't be implied by
+  $\pl F\win\mengame X$ (ruling out Alster and productively Lindel\"of for
+  regular spaces).
 \end{frame}
@@
 \begin{frame}
-Questions? Thanks for having me!
+Questions? Thanks for listening!
 \end{frame}

### 2014-07-17 phd/talks-and-presentations/2014-07-23-menger-talk.tex
incorporate feedback from G

@@
 
-\section{Introduction}
+% \section{Introduction}
 
-\subsection{Abstract}
+% \subsection{Abstract}
 
-\begin{frame}{Abstract}%{Subtitles are optional.}
-    \small
-    A certain topological game introduced by Hurewicz characterizes Menger's
-    covering property whenever the first player lacks a winning strategy. It
-    was later shown by Telgarsky (and later by Scheepers using a different
-    argument) that for metric spaces, the second player having a winning
-    strategy characterizes the stronger property of $\sigma$-compactness.
+% \begin{frame}{Abstract}%{Subtitles are optional.}
+%     \small
+%     A certain topological game introduced by Hurewicz characterizes Menger's
+%     covering property whenever the first player lacks a winning strategy. It
+%     was later shown by Telgarsky (and later by Scheepers using a different
+%     argument) that for metric spaces, the second player having a winning
+%     strategy characterizes the stronger property of $\sigma$-compactness.
 
-    \vspace{1em}
+%     \vspace{1em}
 
-    We factor out Scheepers' proof to show
-    that for regular spaces, the second player having a winning $1$-Mark\"ov
-    strategy characterizes $\sigma$-compactness; also, for second-countable
-    spaces, the presence of a winning perfect information strategy for the
-    second player implies the existence of a winning $1$-Mark\"ov strategy for
-    that player. We also show the that for all $k$, the existence of a
-    winning $k$-Mark\"ov strategy for the second player implies the existence
-    of a winning $2$-Mark\"ov strategy, and give a space which permits
-    a winning $2$-Mark\"ov strategy but not a winning $1$-Mark\"ov strategy.
-\end{frame}
+%     We factor out Scheepers' proof to show
+%     that for regular spaces, the second player having a winning $1$-Mark\"ov
+%     strategy characterizes $\sigma$-compactness; also, for second-countable
+%     spaces, the presence of a winning perfect information strategy for the
+%     second player implies the existence of a winning $1$-Mark\"ov strategy for
+%     that player. We also show the that for all $k$, the existence of a
+%     winning $k$-Mark\"ov strategy for the second player implies the existence
+%     of a winning $2$-Mark\"ov strategy, and give a space which permits
+%     a winning $2$-Mark\"ov strategy but not a winning $1$-Mark\"ov strategy.
+% \end{frame}
 
@@
     on the countable sets she choooses, but $\pl F$ need only ensure that
-    $\bigcup_{n<\omega}\mc F_n\supseteq \bigcap_{n<\omega}\mc U_n$ to win
+    $\bigcup_{n<\omega} F_n\supseteq \bigcap_{n<\omega} C_n$ to win
     the game.
@@
 
-  Any sufficient property must imply $\pl F\win\mengame X$ (ruling out
-  Hurewicz[?]), and any (interesting) necessary property shouldn't be implied by
-  $\pl F\win\mengame X$ (ruling out Alster and productively Lindel\"of for
-  regular spaces).
+  \vpause
+
+  Any sufficient property would imply $\pl F\win\mengame X$, and any
+  (interesting) necessary property shouldn't be implied by
+  $\pl F\win\mengame X$. Assuming $T_3$, properties which come to mind
+  from the literature fit the latter: e.g. Alster (Aurichi, Tall 2013),
+  and thus productively Lindel\"of (Alster 1988) and Hurewicz (Tall 2009).
 \end{frame}

### 2014-07-30 phd/dissertation/chapter2.tex
no umlaut in markov

@@
     \]
-  and the \term{$k$-Mark\"ov fog-of-war} is the function
+  and the \term{$k$-Markov fog-of-war} is the function
   $\mu_k:M^{<\omega}\to (M^{\leq k}\times\omega)$ defined by
@@
 
-  A \term{$k$-Mark\"ov strategy} or \term{$k$-mark} is a function
+  A \term{$k$-Markov strategy} or \term{$k$-mark} is a function
   $\sigma:M^{\leq k}\times\omega\to M$ yielding a corresponding strategy
@@
 usually interesting (such strategies would be constant functions); however,
-we will discuss $0$-Mark\"ov strategies, called
+we will discuss $0$-Markov strategies, called
 \term{predetermined strategies} since such a strategy only uses the round
@@
 
-  If a winning $k$-Mark\"ov strategy exists for a player $\pl A$ in the game
+  If a winning $k$-Markov strategy exists for a player $\pl A$ in the game
   $G$, then we write $\pl A \kmarkwin{k} G$. If $k=1$, then $\pl A \markwin G$,

### 2014-07-30 phd/dissertation/chapter3.tex
no umlaut in markov

@@
   For the forward implication, let $\sigma$ be a winning predetermined
-  (perfect information) strategy, and $\lambda$ be the $0$-Mark\"ov
+  (perfect information) strategy, and $\lambda$ be the $0$-Markov
   fog-of-war $\mu_0$ (the identity).
@@
 
-  In the final case, note that any Mark\"ov strategy $\sigma'$ for $\pl O$ may
+  In the final case, note that any Markov strategy $\sigma'$ for $\pl O$ may
   be strengthened to $\sigma$ defined by
   $\sigma(x,n)=\bigcap_{m\leq n}\sigma'(x,m)$.
-  So, suppose that $\sigma$ is a winning Mark\"ov strategy for $\pl O$ in
+  So, suppose that $\sigma$ is a winning Markov strategy for $\pl O$ in
   $\clusgame{X}{S}$ such that $\sigma(x,m)\supseteq\sigma(x,n)$ for all
@@
   strategy, $q$ clusters at $S$, and since every subsequence of $p$ clusters
-  at $S$, $p$ must converge to $S$. Thus $\sigma$ is also a winning Mark\"ov
+  at $S$, $p$ must converge to $S$. Thus $\sigma$ is also a winning Markov
   strategy for $\pl O$ in $\congame{X}{S}$ as well.
@@
 
-This actually can be generalized to any $k$-Mark\"ov strategy with just
+This actually can be generalized to any $k$-Markov strategy with just
 a little more bookkeeping.
@@
 However, while the clustering and convergence variants are equivalent
-for Mark\"ov strategies in the ``normal'' version of the $W$ game, they are
+for Markov strategies in the ``normal'' version of the $W$ game, they are
 \textit{not} equivalent in the ``hard'' version.
@@
 
-  We define the Mark\"ov strategy $\sigma$ by setting
+  We define the Markov strategy $\sigma$ by setting
     \[
@@
   is closed and unbounded. (Recall that $\mu_k$ is the
-  $k$-Mark\"ov fog-of-war which turns perfect information into the last $k$
+  $k$-Markov fog-of-war which turns perfect information into the last $k$
   moves and the round number.) Let $a_\sigma:\omega_2\to C_\sigma$ be

### 2014-08-25 phd/dissertation/_raw_chapter3.tex
Finish ch 2 draft, outline of results for ch 3, ch 6
Name and camelCase based game commands/definitions

--- 2014-04-30 phd/dissertation/chapter3.tex
@@
-%!TEX root = dissertation.tex
-% ^ leave for LaTeXTools build functionality
-
 \chapter{Convergence/clustering games}
@@
 \begin{defn}
-Gruenhage's open-point convergence game $\congame{X}{x}$ has $O$ choosing nested open sets and $P$ choosing a point within the last chosen open set by $O$.
+Gruenhage's open-point convergence game $\gruConGame{X}{x}$ has $O$ choosing nested open sets and $P$ choosing a point within the last chosen open set by $O$.
 $O$ wins if the points chosen by $P$ converge to $x$.
@@
 \begin{prop}
-$O\codewin \congame{\oneptcomp{\kappa}}{\infty}$ for all cardinals $\kappa$.
+$O\codewin \gruConGame{\oneptcomp{\kappa}}{\infty}$ for all cardinals $\kappa$.
 \end{prop}
@@
 \begin{prop}
-$O\prewin \congame{\oneptcomp{\omega}}{\infty}$.
+$O\prewin \gruConGame{\oneptcomp{\omega}}{\infty}$.
 \end{prop}
@@
 \begin{prop}
-$O\not\prewin \clusgame{\oneptcomp{\kappa}}{\infty}$ for $\kappa\geq\omega_1$.
+$O\not\prewin \gruClusGame{\oneptcomp{\kappa}}{\infty}$ for $\kappa\geq\omega_1$.
 \end{prop}
@@
 \begin{prop}
-$O\tactwin\congame{\oneptcomp{\omega}}{\infty}$.
+$O\tactwin\gruConGame{\oneptcomp{\omega}}{\infty}$.
 \end{prop}
@@
 \begin{thm}
-$O\not\ktactwin{k}\clusgame{\oneptcomp{\kappa}}{\infty}$ for $\kappa\geq\omega_1$.
+$O\not\ktactwin{k}\gruClusGame{\oneptcomp{\kappa}}{\infty}$ for $\kappa\geq\omega_1$.
 \end{thm}
@@
 \begin{thm}
-$O\markwin \clusgame{\oneptcomp{\omega_1}}{\infty}$.
+$O\markwin \gruClusGame{\oneptcomp{\omega_1}}{\infty}$.
 \end{thm}
@@
 \begin{prop}
-$O\uparrow\congame{\sigmaprodr{\kappa}}{\vec{0}}$.
+$O\uparrow\gruConGame{\sigmaprodr{\kappa}}{\vec{0}}$.
 \end{prop}
@@
 \begin{thm}
-For all cardinals $\kappa\leq 2^\omega$, $O\codewin\congame{\sigmaprodr{\kappa}}{\vec{0}}$.
+For all cardinals $\kappa\leq 2^\omega$, $O\codewin\gruConGame{\sigmaprodr{\kappa}}{\vec{0}}$.
 \end{thm}
@@
 Let $\kappa$ be a cardinal such that there exists a function $f:\kappa\to[\kappa]^{\leq \omega}$ where for every $W\in[\kappa]^{\leq\omega}$ there exists $\alpha_W<\kappa$ with $W\subseteq f(\alpha_W)$.
-(That is, $\textrm{cf}([\kappa]^{\leq\omega})=\kappa$.) Then $F \codewin PF_{F,C}(\kappa)$ and $O \codewin \congame{\sigmaprodr{\kappa}}{\vec{0}}$.
+(That is, $\textrm{cf}([\kappa]^{\leq\omega})=\kappa$.) Then $F \codewin PF_{F,C}(\kappa)$ and $O \codewin \gruConGame{\sigmaprodr{\kappa}}{\vec{0}}$.
 \end{thm}
@@
 Let $\kappa$ be the limit of cardinals $\kappa_n$ such that $\textrm{cf}([\kappa_n]^{\leq\omega},\subseteq)=\kappa_n$.
-Then $F \codewin PF_{F,C}(\kappa)$ and $O \codewin \congame{\sigmaprodr{\kappa}}{\vec{0}}$.
+Then $F \codewin PF_{F,C}(\kappa)$ and $O \codewin \gruConGame{\sigmaprodr{\kappa}}{\vec{0}}$.
 \end{thm}
@@
 
-We turn our attention to $\congame{\sigmaprodr{\kappa}}{\vec{0}}$.
+We turn our attention to $\gruConGame{\sigmaprodr{\kappa}}{\vec{0}}$.
 We define the winning strategy $\tau(U,p)$ for $O$ as follows: let $N(U)$ be the non-$\mathbb{R}$ coordinates in the basic open set $U$ and $W(p)$ be the non-$0$ coordinates in $p$.
@@
 \begin{thm}
-$F\codewin\pfgame{\kappa}$ for all cardinals $\kappa$.
+$F\codewin\cloPFGame{\kappa}$ for all cardinals $\kappa$.
 \end{thm}
@@
 \begin{proof}
-Let $\kappa$ be the limit of cardinals $\kappa_n$ such that $F\codewin\pfgame{\kappa_n}$ using the strategy $\sigma_n(N,W)$ such that for $M\subseteq N$, $\sigma_n(M,W)\subseteq\sigma_n(N,W)$.
+Let $\kappa$ be the limit of cardinals $\kappa_n$ such that $F\codewin\cloPFGame{\kappa_n}$ using the strategy $\sigma_n(N,W)$ such that for $M\subseteq N$, $\sigma_n(M,W)\subseteq\sigma_n(N,W)$.
 Define \[\sigma(N,W)=(|N|+1)\cup\bigcup_{n<|N|}\sigma_n(N\cap\kappa_n,W\cap\kappa_n)\]
@@
 
-Now suppose $F\codewin\pfgame{\kappa}$.
-For each $\alpha<\kappa^+$, let $\sigma_\alpha(N,W)$ be a winning coding strategy for $\pfgame{\alpha}$ such that for $M\subseteq N$, $\sigma_\alpha(M,W)\subseteq\sigma_\alpha(N,W)$.
-We define the following strategy for $F$ in $\pfgame{\kappa^+}$: \[\sigma(N,W)=N\cup\bigcup_{\alpha\in N}\sigma_{\alpha+1}(N\cap(\alpha+1),W\cap(\alpha+1))\]
+Now suppose $F\codewin\cloPFGame{\kappa}$.
+For each $\alpha<\kappa^+$, let $\sigma_\alpha(N,W)$ be a winning coding strategy for $\cloPFGame{\alpha}$ such that for $M\subseteq N$, $\sigma_\alpha(M,W)\subseteq\sigma_\alpha(N,W)$.
+We define the following strategy for $F$ in $\cloPFGame{\kappa^+}$: \[\sigma(N,W)=N\cup\bigcup_{\alpha\in N}\sigma_{\alpha+1}(N\cap(\alpha+1),W\cap(\alpha+1))\]
 
@@
 \begin{cor}
-$O\codewin\congame{\sigmaprodr{\kappa}}{\vec{0}}$ for all cardinals $\kappa$.
+$O\codewin\gruConGame{\sigmaprodr{\kappa}}{\vec{0}}$ for all cardinals $\kappa$.
 \end{cor}
@@
 \begin{proof}
-Let $\tau(N,W)$ be the winning coding strategy for $F$ in $\pfgame{\kappa}$, $N(U)\in[\kappa]^{<\omega}$ represent the non-$\mathbb{R}$ coordinates of a basic open set $U$ of $\sigmaprodr{\kappa}$, and $W(p)\in[\kappa]^{\leq\omega}$ represent the non-$0$ coordinates of a point $p$ in $\sigmaprodr{\kappa}$.
+Let $\tau(N,W)$ be the winning coding strategy for $F$ in $\cloPFGame{\kappa}$, $N(U)\in[\kappa]^{<\omega}$ represent the non-$\mathbb{R}$ coordinates of a basic open set $U$ of $\sigmaprodr{\kappa}$, and $W(p)\in[\kappa]^{\leq\omega}$ represent the non-$0$ coordinates of a point $p$ in $\sigmaprodr{\kappa}$.
 For each $\alpha<\kappa$, let \[\sigma_\alpha(U,p)=\left\{\begin{array}{ll}(-\frac{1}{|N(U)|},\frac{1}{|N(U)|})&\text{if }\alpha\in\tau(N(U),W(p))\\\mathbb{R}&\text{otherwise}\end{array}\right.\] and $\sigma(U,p)=\sigmaprodr{\kappa}\cap\prod_{\alpha<\kappa}\sigma_\alpha(U,p)$.

### 2014-08-25 phd/dissertation/_raw_chapter4.tex
Outline chapter 4,6
Name and camelCase based game commands/definitions

@@
 \begin{defn}
-  For a uniform space $X$, the simplified proximal game $\proxgame{X}$ can be defined as follows:
+  For a uniform space $X$, the simplified proximal game $\bellConGame{X}$ can be defined as follows:
 
@@
 \begin{thm}
-  $\pl D$ has a winning perfect-information strategy in Bell's game if and only if $\pl D\win\proxgame{X}$.
+  $\pl D$ has a winning perfect-information strategy in Bell's game if and only if $\pl D\win\bellConGame{X}$.
 \end{thm}
@@
 \begin{prop}
-$\pl P$ has a winning perfect-information strategy in Bell's game if and only if $\pl P \win \proxgame{X}$.
+$\pl P$ has a winning perfect-information strategy in Bell's game if and only if $\pl P \win \bellConGame{X}$.
 \end{prop}
@@
 \begin{defn}
-  A uniform space is \textbf{proximal} if $\pl D \win \proxgame{X}$.
+  A uniform space is \textbf{proximal} if $\pl D \win \bellConGame{X}$.
 \end{defn}
@@
 \begin{defn}
-  For a space $X$ and a point $x\in X$, the \textbf{$W$-convergence-game} $\congame{X}{x}$ proceeds as follows.
+  For a space $X$ and a point $x\in X$, the \textbf{$W$-convergence-game} $\gruConGame{X}{x}$ proceeds as follows.
 
@@
 \begin{defn}
-  A space is \textbf{$W$} if $\pl O \win \congame{X}{x}$ for all $x\in X$.
+  A space is \textbf{$W$} if $\pl O \win \gruConGame{X}{x}$ for all $x\in X$.
 \end{defn}
@@
     \item
-      $\pl D\win \proxgame{X} \Rightarrow \pl O \win \congame{X}{x}$
-    \item
-      $\pl D\ktactwin{2k} \proxgame{X} \Rightarrow \pl O \ktactwin{k} \congame{X}{x}$
-    \item
-      $\pl D\kmarkwin{2k} \proxgame{X} \Rightarrow \pl O \kmarkwin{k} \congame{X}{x}$
-  \end{itemize}
-\end{thm}
-
-\begin{proof}
-Let $\sigma$ witness $\pl D \ktactwin{2k}\proxgame{X}$ (resp.
-$\pl D \kmarkwin{2k}\proxgame{X}$, $\pl D\win\proxgame{X}$).
+      $\pl D\win \bellConGame{X} \Rightarrow \pl O \win \gruConGame{X}{x}$
+    \item
+      $\pl D\ktactwin{2k} \bellConGame{X} \Rightarrow \pl O \ktactwin{k} \gruConGame{X}{x}$
+    \item
+      $\pl D\kmarkwin{2k} \bellConGame{X} \Rightarrow \pl O \kmarkwin{k} \gruConGame{X}{x}$
+  \end{itemize}
+\end{thm}
+
+\begin{proof}
+Let $\sigma$ witness $\pl D \ktactwin{2k}\bellConGame{X}$ (resp.
+$\pl D \kmarkwin{2k}\bellConGame{X}$, $\pl D\win\bellConGame{X}$).
 We define the $k$-tactical (resp.
@@
 Since $q(2n)=x$, $q$ must converge to $x$.
-Thus its subsequence $p$ converges to $x$, and $\tau$ is a winning strategy in $\congame{X}{x}$.
+Thus its subsequence $p$ converges to $x$, and $\tau$ is a winning strategy in $\gruConGame{X}{x}$.
 \end{proof}
@@
     \item
-      $\pl D\ktactwin{k} \proxgame{X} \Rightarrow \pl O \ktactwin{k} \congame{X}{x}$
-    \item
-      $\pl D\kmarkwin{k} \proxgame{X} \Rightarrow \pl O \kmarkwin{k} \congame{X}{x}$
+      $\pl D\ktactwin{k} \bellConGame{X} \Rightarrow \pl O \ktactwin{k} \gruConGame{X}{x}$
+    \item
+      $\pl D\kmarkwin{k} \bellConGame{X} \Rightarrow \pl O \kmarkwin{k} \gruConGame{X}{x}$
   \end{itemize}
@@
     \item
-      $\pl O\win \congame{X\cup\{\infty\}}{\infty} \Rightarrow \pl D \win \proxgame{X\cup\{\infty\}}$
-    \item
-      $\pl O\ktactwin{k} \congame{X\cup\{\infty\}}{\infty} \Rightarrow \pl D \ktactwin{k} \proxgame{X\cup\{\infty\}}$
-    \item
-      $\pl O\kmarkwin{k} \congame{X\cup\{\infty\}}{\infty} \Rightarrow \pl D \kmarkwin{k} \proxgame{X\cup\{\infty\}}$
+      $\pl O\win \gruConGame{X\cup\{\infty\}}{\infty} \Rightarrow \pl D \win \bellConGame{X\cup\{\infty\}}$
+    \item
+      $\pl O\ktactwin{k} \gruConGame{X\cup\{\infty\}}{\infty} \Rightarrow \pl D \ktactwin{k} \bellConGame{X\cup\{\infty\}}$
+    \item
+      $\pl O\kmarkwin{k} \gruConGame{X\cup\{\infty\}}{\infty} \Rightarrow \pl D \kmarkwin{k} \bellConGame{X\cup\{\infty\}}$
   \end{itemize}
@@
 
-  Let $\sigma$ witness $\pl D \ktactwin{k}\congame{X\cap\{\infty\}}{\infty}$ (resp.
-$\pl D \kmarkwin{k}\congame{X\cap\{\infty\}}{\infty}$, $\pl D\win\congame{X\cap\{\infty\}}{\infty}$).
+  Let $\sigma$ witness $\pl D \ktactwin{k}\gruConGame{X\cap\{\infty\}}{\infty}$ (resp.
+$\pl D \kmarkwin{k}\gruConGame{X\cap\{\infty\}}{\infty}$, $\pl D\win\gruConGame{X\cap\{\infty\}}{\infty}$).
 We define the $k$-tactical (resp.
@@
     \item
-      $\pl O\win \congame{X\cup\{\infty\}}{\infty} \Leftrightarrow \pl D \win \proxgame{X\cup\{\infty\}}$
-    \item
-      $\pl O\ktactwin{k} \congame{X\cup\{\infty\}}{\infty} \Leftrightarrow \pl D \ktactwin{k} \proxgame{X\cup\{\infty\}}$
-    \item
-      $\pl O\kmarkwin{k} \congame{X\cup\{\infty\}}{\infty} \Leftrightarrow \pl D \kmarkwin{k} \proxgame{X\cup\{\infty\}}$
+      $\pl O\win \gruConGame{X\cup\{\infty\}}{\infty} \Leftrightarrow \pl D \win \bellConGame{X\cup\{\infty\}}$
+    \item
+      $\pl O\ktactwin{k} \gruConGame{X\cup\{\infty\}}{\infty} \Leftrightarrow \pl D \ktactwin{k} \bellConGame{X\cup\{\infty\}}$
+    \item
+      $\pl O\kmarkwin{k} \gruConGame{X\cup\{\infty\}}{\infty} \Leftrightarrow \pl D \kmarkwin{k} \bellConGame{X\cup\{\infty\}}$
   \end{itemize}
@@
     \item
-      $\pl O\ktactwin{k}\congame{X}{x} \Leftrightarrow \pl O\tactwin\congame{X}{x}$
-    \item
-      $\pl O\kmarkwin{k}\congame{X}{x} \Leftrightarrow \pl O\markwin\congame{X}{x}$
+      $\pl O\ktactwin{k}\gruConGame{X}{x} \Leftrightarrow \pl O\tactwin\gruConGame{X}{x}$
+    \item
+      $\pl O\kmarkwin{k}\gruConGame{X}{x} \Leftrightarrow \pl O\markwin\gruConGame{X}{x}$
   \end{itemize}
@@
 \begin{proof}
-  If $\sigma$ witnesses $\pl O\ktactwin{k}\congame{X}{x}$, let $\tau(\emptyset)=\sigma(\emptyset)$ and
+  If $\sigma$ witnesses $\pl O\ktactwin{k}\gruConGame{X}{x}$, let $\tau(\emptyset)=\sigma(\emptyset)$ and
     \[
@@
 
-  This is easily verified to be a winning strategy. The proof for $\pl O\kmarkwin{k}\congame{X}{x}$ is analogous.
+  This is easily verified to be a winning strategy. The proof for $\pl O\kmarkwin{k}\gruConGame{X}{x}$ is analogous.
 \end{proof}
@@
     \item
-      $\pl D\ktactwin{k}\proxgame{X\cup\{\infty\}} \Leftrightarrow O\tactwin\proxgame{X\cup\{\infty\}}$
-    \item
-      $\pl D\kmarkwin{k}\proxgame{X\cup\{\infty\}} \Leftrightarrow O\markwin\proxgame{X\cup\{\infty\}}$
+      $\pl D\ktactwin{k}\bellConGame{X\cup\{\infty\}} \Leftrightarrow O\tactwin\bellConGame{X\cup\{\infty\}}$
+    \item
+      $\pl D\kmarkwin{k}\bellConGame{X\cup\{\infty\}} \Leftrightarrow O\markwin\bellConGame{X\cup\{\infty\}}$
   \end{itemize}
@@
     \item
-      $\pl O\ktactwin{k}\proxgame{X} \Leftrightarrow \pl O\ktactwin{2}\proxgame{X}$
-    \item
-      $\pl O\kmarkwin{k}\proxgame{X} \Leftrightarrow \pl O\kmarkwin{2}\proxgame{X}$
+      $\pl O\ktactwin{k}\bellConGame{X} \Leftrightarrow \pl O\ktactwin{2}\bellConGame{X}$
+    \item
+      $\pl O\kmarkwin{k}\bellConGame{X} \Leftrightarrow \pl O\kmarkwin{2}\bellConGame{X}$
   \end{itemize}
@@
 \begin{proof}
-  If $\sigma$ witnesses $\pl O\ktactwin{k}\congame{X}{x}$, let $\tau(\emptyset)=\sigma(\emptyset)$ and
+  If $\sigma$ witnesses $\pl O\ktactwin{k}\bellConGame{X}{x}$, let $\tau(\emptyset)=\sigma(\emptyset)$ and
     \[
@@
 
-  This is easily verified to be a winning strategy. The proof for $\pl O\kmarkwin{k}\congame{X}{x}$ is analogous.
+  This is easily verified to be a winning strategy. The proof for $\pl O\kmarkwin{k}\bellConGame{X}{x}$ is analogous.
 \end{proof}
@@
 \begin{defn}
-  The absolute proximal game $\aproxgame{X}$ is analogous to $\proxgame{X}$, except $\pl D$ may only win if $p$ converges.
+  The absolute proximal game $\bellClusGame{X}$ is analogous to $\bellConGame{X}$, except $\pl D$ may only win if $p$ converges.
 \end{defn}
@@
   For any uniformly locally compact space $X$,
-      $\pl D\win \proxgame{X} \Leftrightarrow \pl D\win \aproxgame{X}$
+      $\pl D\win \bellConGame{X} \Leftrightarrow \pl D\win \bellClusGame{X}$
 \end{thm}
@@
   Let $M$ be a uniformly locally compact entourage.
-Let $\sigma$ witness $\pl D\win \proxgame{X}$ such that $\sigma(a)\subseteq M$ always (so $\cl{\sigma(a)[x]}\subseteq\cl{M[x]}$ is compact), and $a\supseteq b$  implies $\sigma(a)\subseteq\frac{1}{4}\sigma(b)$.
-
-  Let $\tau(p\rest n)=\frac{1}{2}\sigma(p\rest n)$. If $p$ attacks $\tau$ in $\aproxgame{X}$, then
+Let $\sigma$ witness $\pl D\win \bellConGame{X}$ such that $\sigma(a)\subseteq M$ always (so $\cl{\sigma(a)[x]}\subseteq\cl{M[x]}$ is compact), and $a\supseteq b$  implies $\sigma(a)\subseteq\frac{1}{4}\sigma(b)$.
+
+  Let $\tau(p\rest n)=\frac{1}{2}\sigma(p\rest n)$. If $p$ attacks $\tau$ in $\bellClusGame{X}$, then
     \[
@@
 
-  Finally, note that $p$ attacks the winning strategy $\sigma$ in $\proxgame{X}$, but since the intersection of a chain of nonempty compact sets is nonempty:
+  Finally, note that $p$ attacks the winning strategy $\sigma$ in $\bellConGame{X}$, but since the intersection of a chain of nonempty compact sets is nonempty:
 
@@
 \begin{cor}
-  A uniformaly locally compact space $X$ is proximal if and only if $\pl D \win \aproxgame{X}$.
+  A uniformaly locally compact space $X$ is proximal if and only if $\pl D \win \bellClusGame{X}$.
 \end{cor}
@@
 \begin{thm}
-  For any uniformly locally compact proximal space $X$, $\pl O\win \clusgame{X}{H}$ for all compact $H\subseteq X$.
-\end{thm}
-
-\begin{proof}
-  Let $\sigma$ witness $\pl D \win \aproxgame{X}$ such that $p\supseteq q$ implies $\sigma(p)\subseteq \frac{1}{4}\sigma(q)$.
+  For any uniformly locally compact proximal space $X$, $\pl O\win \gruClusGame{X}{H}$ for all compact $H\subseteq X$.
+\end{thm}
+
+\begin{proof}
+  Let $\sigma$ witness $\pl D \win \bellClusGame{X}$ such that $p\supseteq q$ implies $\sigma(p)\subseteq \frac{1}{4}\sigma(q)$.
 
@@
 
-  With this we may define the perfect information strategy $\tau$ for $\pl O$ in $\congame{X}{H}$ such that:
+  With this we may define the perfect information strategy $\tau$ for $\pl O$ in $\gruConGame{X}{H}$ such that:
   \[
@@
   Let $q'=\<i_0,h_0,j_0,x_0,i_1,h_1,j_1,x_1,\dots\>$ correspond to this infinite branch in $T(p)$, and let $q=o(q')=\<h_0,x_0,h_1,x_1,\dots\>$.
-Note that by the construction of $T(p)$, $q$ is an attack on the winning strategy $\sigma$ in $\aproxgame{X}$, so it must converge.
+Note that by the construction of $T(p)$, $q$ is an attack on the winning strategy $\sigma$ in $\bellClusGame{X}$, so it must converge.
 Since every other term of $q$ is in $H$, it must converge to $H$.
@@
 \begin{cor}
-  For any uniformly locally compact proximal space, $\pl O\win \congame{X}{H}$ for all compact $H\subseteq X$.
+  For any uniformly locally compact proximal space, $\pl O\win \gruConGame{X}{H}$ for all compact $H\subseteq X$.
 \end{cor}
@@
 \begin{proof}
-  $\pl O \win \congame{X}{H}$ if and only if $\pl O \win \clusgame{X}{H}$.
+  $\pl O \win \gruConGame{X}{H}$ if and only if $\pl O \win \gruClusGame{X}{H}$.
 \end{proof}
@@
 \begin{thm}
-  $\pl O \prewin \congame{X}{H}$ if and only if there exists a countable base 
+  $\pl O \prewin \gruConGame{X}{H}$ if and only if there exists a countable base
   around $H$.
@@
 \begin{cor}
-  $X$ is first countable if and only if $\pl O \prewin \congame{X}{x}$ for 
+  $X$ is first countable if and only if $\pl O \prewin \gruConGame{X}{x}$ for
   all $x\in X$
@@
 \begin{cor}
-  $\pl D \prewin \proxgame{X}$ implies $X$ is first countable.
+  $\pl D \prewin \bellConGame{X}$ implies $X$ is first countable.
 \end{cor}
@@
 \begin{cor}
-  If $X$ is scattered compact and $\pl O \prewin\congame{X}{x}$ for all
-  $x\in X$ (or $\pl D \prewin\proxgame{X}$), then $X$ is metrizable.
+  If $X$ is scattered compact and $\pl O \prewin\gruConGame{X}{x}$ for all
+  $x\in X$ (or $\pl D \prewin\bellConGame{X}$), then $X$ is metrizable.
 \end{cor}
@@
 \begin{ex}
-  $\pl D \not\prewin \proxgame{\oneptcomp\omega_1}$
+  $\pl D \not\prewin \bellConGame{\oneptcomp\omega_1}$
 \end{ex}
@@
   There does not exist a countable base around $\infty$, so
-    $\pl O \not\prewin \congame{X}{\omega_1}$.
+    $\pl O \not\prewin \gruConGame{X}{\omega_1}$.
 \end{proof}
@@
 \begin{ex}
-  $\pl O \tactwin \congame{\oneptcomp\kappa}{\infty}$ and 
-  $\pl D \tactwin \proxgame{\oneptcomp\kappa}$ for all cardinals $\kappa$
+  $\pl O \tactwin \gruConGame{\oneptcomp\kappa}{\infty}$ and
+  $\pl D \tactwin \bellConGame{\oneptcomp\kappa}$ for all cardinals $\kappa$
 \end{ex}
@@
 \begin{proof}
-  For $\congame{\oneptcomp\kappa}{\infty}$, let 
+  For $\gruConGame{\oneptcomp\kappa}{\infty}$, let
     $\sigma()=\sigma(\infty)=\oneptcomp\kappa$
@@
     $
-      \pl D \limitwin \proxgame{X}
+      \pl D \limitwin \bellConGame{X}
         \Rightarrow
-      \pl D \limitwin \proxgame{H}
+      \pl D \limitwin \bellConGame{H}
     $
@@
 \begin{proof}
-  Let $\sigma\circ L$ witness $\pl D \limitwin \proxgame{X}$. We define
-  $\tau\circ L$ for $\pl D$ in $\proxgame{H}$ as follows:
+  Let $\sigma\circ L$ witness $\pl D \limitwin \bellConGame{X}$. We define
+  $\tau\circ L$ for $\pl D$ in $\bellConGame{H}$ as follows:
     \[
@@
 \begin{thm}
-  If $\pl D\limitwin \proxgame{X_i}$ for $i<\omega$, then
-  $\pl D\limitwin \proxgame{\prod_{i<\omega}X_i}$, where $\limitwin$ is either
+  If $\pl D\limitwin \bellConGame{X_i}$ for $i<\omega$, then
+  $\pl D\limitwin \bellConGame{\prod_{i<\omega}X_i}$, where $\limitwin$ is either
   $\win$ or $\kmarkwin{k}$.
@@
 
-  Let $\sigma_i\circ L$ witness $\pl D\limitwin \proxgame{X_i}$ for
+  Let $\sigma_i\circ L$ witness $\pl D\limitwin \bellConGame{X_i}$ for
   $i<\omega$, and assume without loss of generality that
@@
   Then we define the strategy $\tau\circ L$ for $\pl D$ in
-  $\proxgame{\prod_{i<\omega}X_i}$ as follows:
+  $\bellConGame{\prod_{i<\omega}X_i}$ as follows:
     \[
@@
 \begin{ex}
-  $\pl D \markwin \proxgame{(\oneptcomp\kappa)^\omega}$
+  $\pl D \markwin \bellConGame{(\oneptcomp\kappa)^\omega}$
 \end{ex}
@@
 \begin{proof}
-  $\pl D \tactwin \proxgame{\oneptcomp\kappa}$ + previous result
+  $\pl D \tactwin \bellConGame{\oneptcomp\kappa}$ + previous result
 \end{proof}
@@
 \begin{lem}
-  $\pl O\prewin\clusgame{X}{S}$ if and only if $\pl O\prewin\congame{X}{S}$.
+  $\pl O\prewin\gruClusGame{X}{S}$ if and only if $\pl O\prewin\gruConGame{X}{S}$.
 \end{lem}
@@
   Suppose that $\sigma$ is a predetermined winning strategy for
-  $\clusgame{X}{S}$. Let $p$ attack $\sigma$, and $q$ be a subsequence of $p$.
+  $\gruClusGame{X}{S}$. Let $p$ attack $\sigma$, and $q$ be a subsequence of $p$.
   It follows that $q$ also attacks $\sigma$, so $q$ clusters at $S$. Thus $p$
   conveges to $S$, and $\sigma$ is a predetermined winning strategy for
-  $\congame{X}{S}$.
+  $\gruConGame{X}{S}$.
 \end{proof}
@@
   For any predetermined absolutely proximal space $X$,
-  $\pl O\prewin \congame{X}{H}$ for all compact $H\subseteq X$.
+  $\pl O\prewin \gruConGame{X}{H}$ for all compact $H\subseteq X$.
 \end{thm}
@@
   We now define the predetermined strategy $\tau$ for $\pl O$ in
-  $\clusgame{X}{H}$ such that:
+  $\gruClusGame{X}{H}$ such that:
   \[
@@
 
-  We have thus proven $\pl O\prewin\clusgame{X}{H}$, and thus
-  $\pl O\prewin\congame{X}{H}$.
+  We have thus proven $\pl O\prewin\gruClusGame{X}{H}$, and thus
+  $\pl O\prewin\gruConGame{X}{H}$.
 \end{proof}
@@
   Let $X=I\times 2$ be the Alexandrov double interval. Then
-  $\pl D \not\prewin \proxgame{X}$, but $\pl D \markwin \proxgame{X}$.
+  $\pl D \not\prewin \bellConGame{X}$, but $\pl D \markwin \bellConGame{X}$.
 \end{ex}
@@
   For any uniformly locally compact space $X$,
-      $\pl D\prewin \proxgame{X} \Leftrightarrow \pl D\prewin \aproxgame{X}$
+      $\pl D\prewin \bellConGame{X} \Leftrightarrow \pl D\prewin \bellClusGame{X}$
 \end{thm}
@@
   Let $M$ be a uniformly locally compact entourage.
-  Let $\sigma$ witness $\pl D\prewin \proxgame{X}$ such that 
+  Let $\sigma$ witness $\pl D\prewin \bellConGame{X}$ such that
   $\sigma(n)\subseteq M$ always
@@
   Let $\tau(n)=\frac{1}{2}\sigma(n)$. If $p$ attacks $\tau$ in
-  $\aproxgame{X}$, then
+  $\bellClusGame{X}$, then
     \[
@@
   Finally, note that $p$ attacks the winning strategy $\sigma$ in
-  $\proxgame{X}$, but since the intersection of a chain of nonempty compact 
+  $\bellConGame{X}$, but since the intersection of a chain of nonempty compact
   sets is nonempty:
@@
 \begin{prop}
-If $\pl D \prewin \proxgame{X}$, then $X$ has a $G_\delta$ diagonal.
+If $\pl D \prewin \bellConGame{X}$, then $X$ has a $G_\delta$ diagonal.
 \end{prop}
@@
 \begin{proof}
-  If $\pl D \prewin \proxgame{X}$ with strategy $\sigma$, then consider 
+  If $\pl D \prewin \bellConGame{X}$ with strategy $\sigma$, then consider
   $\<x,y\>\in \bigcap_{n<\omega} \sigma(n)$. It follows that
@@
 \begin{ex}
-The Sorgenfrey line $S$ has a $G_\delta$ diagonal but $\pl P\win\proxgame{S}$.
+The Sorgenfrey line $S$ has a $G_\delta$ diagonal but $\pl P\win\bellConGame{S}$.
 \end{ex}
@@
     \begin{enumerate}[(a)]
-      \item $\pl D \prewin \proxgame{X}$
-      \item $\pl D \prewin \aproxgame{X}$
+      \item $\pl D \prewin \bellConGame{X}$
+      \item $\pl D \prewin \bellClusGame{X}$
       \item $X$ has a $G_\delta$ diagonal
@@
 \begin{cor}
-  If $X$ is uniformly locally compact, then $\pl D \prewin \proxgame{X}$ 
+  If $X$ is uniformly locally compact, then $\pl D \prewin \bellConGame{X}$
   implies $X$'s topology is metrizable.
@@
 \begin{ex}
-  Let $R$ be the Michael Line. Then $\pl P\win \proxgame{X}$.
+  Let $R$ be the Michael Line. Then $\pl P\win \bellConGame{X}$.
 \end{ex}
@@
 
-  Then $\proxgame{\oneptcomp\omega_1}$ is indetermined.
+  Then $\bellConGame{\oneptcomp\omega_1}$ is indetermined.
 \end{ex}
@@
 \begin{proof}
-  $\pl D\not\win\proxgame{\oneptcomp\omega_1}$ since $\oneptcomp\omega_1$
+  $\pl D\not\win\bellConGame{\oneptcomp\omega_1}$ since $\oneptcomp\omega_1$
   isn't Corson compact.

### 2014-08-25 phd/dissertation/_raw_chapter5.tex
Name and camelCase based game commands/definitions

--- 2013-01-24 old_phd_research_results_april_2012.tex
@@
 
-\begin{proposition} 
+\begin{prop}
 If a selective ultrafilter $\mathcal{F}$ exists (this is independent of ZFC), then $K$ has no winning predetermined strategy in the compact-point game $G_{K,P}(Y)$ for the single selective ultrafilter space $Y=\omega \cup \{\mathcal{F}\}$.
-\end{proposition}
+\end{prop}
 
@@
 
-\begin{question}
+\begin{ques}
 $K \prewin G_{K,L}(X) \Rightarrow X$ is a $k$-space?
-\end{question}
+\end{ques}
 
-\centerline{\bf Another game: $Con_{O,P}(X,x)$}
+\section{Cantor space example}
 
-\begin{definition} 
-Gruenhage's open-point convergence game $Con_{O,P}(X,x)$ has $O$ choosing nested open sets and $P$ choosing a point within the last chosen open set by $O$.
-$O$ wins if the points chosen by $P$ converge to $x$.
-\end{definition}
+\begin{ex}
+Let $X$ be a zero-dimensional, compact L-space (hereditarally Lindeloff and non-separable).
+It is a fact that there exists a point-countable collection $\mathcal{U}=\{U_\alpha : \alpha<\omega_1\}$ of clopen sets in $X$, and it is also true that any point-finite subcollection of $\mathcal{U}$ is countable.
+%That is, if we let $A_x = \{\alpha : x \in U_\alpha\}$, then $|A_x|\leq\omega$ for all $x\in X$.
 
-\begin{definition}
-The one-point compactification of a space $X$ is $X\cup\{\infty\}$, where neighborhoods of points in $X$ are the same as they were originally, and neighborhoods of $\infty$ are sets $X\cup\{\infty\}\setminus K$ for compact $K$.
-If $X$ is discrete then neighborhoods of $\infty$ are cofinite sets containing $\infty$.
-\end{definition}
+Let $C = \{c_\alpha : \alpha <\omega_1\}$ be any uncountable subset of the Cantor space $2^\omega$. Let $X_s = X \times \{s\}$ for each $s \in 2^{<\omega}$, and $U_{\alpha,s} = U_\alpha \times \{s\}$.
 
-\begin{proposition}
-$O\not\prewin Con_{O,P}(\kappa\cup\{\infty\},\infty)$, where $\kappa\cup\{\infty\}$ is the one-point compactification of discrete $\kappa\geq\omega_1$.
-\end{proposition}
+Finally, let \[\mathbb{X} = C \cup \bigcup_{s\in 2^{<\omega}} X_s\] be a tree of $2^{<\omega}$ copies of $X$, and where \[c_\alpha \cup \bigcup_{n < \omega} U_{\alpha, x_\alpha \restriction n}\] is an open set about each $c_\alpha$.
+\end{ex}
+
+\begin{defn}
+Let $S\in[\omega_1]^{<\omega}$ and $m<\omega$. Define
+    \[K_S = \bigcup_{\alpha \in S} \left( c_\alpha \cup \left(\bigcup_{s < c_\alpha} U_{\alpha,s}\right)\right)\]
+    \[ A = \{z^\frown \<1\> : z \in 1^{<\omega}\}\]
+    \[ K^*_S = K_S \setminus \bigcup_{s \in A} X_s \]
+and
+    \[L_m = \bigcup_{s \in 2^{<m}} X_s\]
+and observe that every compact set is dominated by $K^*_S \cup L_m$ for some $S,m$.
+Intuitively, $K^*_S$ collects the branches of $U_\alpha$ converging up to $c_\alpha$ for each $\alpha \in S$ while avoiding copies $X_s$ of $X$ for each $s$ in an antichain $A$, and $L_m$ collects the copies $X_s$ of $X$ with $|s| < m$ at the base of the tree.
+\end{defn}
+
+\begin{prop}
+Without loss of generality, $P$ always plays points in $\bigcup_{s \in 2^{<\omega}} X_s$.
+\end{prop}
+
+\begin{prop}
+$K \win \gruKPGame{\mathbb{X}}$.
+\end{prop}
 
 \begin{proof}
-Given a predetermined strategy $\sigma(n)$ for $O$, $P$ simply chooses any ordinal in $\bigcap_{n<\omega} \sigma(n)$ to play on every turn.
+In response to a point $\<x,s\>$, $K$ observes that there are only countably many $\alpha$ such that $U_\alpha \times \{s\}$ contains $\<x,s\>$ (by point-countability of $X$).
+Enumerate these as $\alpha_n$.
+$K$ makes a promise that during round $m$, $K$ will forbid some superset of $K_{\{\alpha_n : n\leq m\}}$.
+Finally, $K$ also always forbids a superset of $L_{|s|+1}$.
+
+Suppose $P$'s moves clustered at some point.
+Since $K$ forbade $L_{|s|+1}$ during each round, that point must be $c_\alpha$ for some $\alpha$.
+$P$'s play then must have included a subsequence of points $\<x_0,s_0\>,\<x_1,s_1\>,\<x_2,s_2\>\dots$ such that $x_n \in U_\alpha$ and $s_n \leq s_{n+1} \leq c_\alpha$.
+However, in response to $\<x_0,s_0\>$, $K$ made a promise to eventually forbid a superset of $K_{\{\alpha\}}$, making every $\<x_n,t_n\>$ illegal after that round.
 \end{proof}
 
-\begin{definition}
-A \textbf{coding strategy} considers only the most recent move by each player. If Player $Z$ has a winning coding strategy for a game $G$, this may be denoted $Z \codewin G$.
-\end{definition}
-
-\begin{proposition}
-$O\codewin Con_{O,P}(\kappa\cup\{\infty\},\infty)$ for any cardinal $\kappa$. 
-\end{proposition}
+\begin{thm}
+$K\not\tactwin\gruKPGame{\mathbb{X}}$.
+\end{thm}
 
 \begin{proof}
-Define $\sigma(U,p)=U\setminus\{p\}$. A legal play by $P$ must never repeat the same point, so legal plays by $P$ converge to $\infty$.
+This is actually a corollary of G's theorem in [?]. The following is a direct game-theoretic proof.
+
+Suppose that $\sigma(\<x,s\>)$ was a winning strategy for $K$ and assume
+  \[
+    \sigma(\<x,s\>) = \bigcup_{|t|\leq |s|} \sigma(\<x,t\>) = \sigma'(x,|s|)
+  \]
+Thus there exists some $f: \omega_1 \to \omega$ such that $\sigma'(x,f(\alpha))$ covers every neighborhood of $c_\alpha$ for all $x\in U_\alpha$.
+(If not, $P$ wins by taking the $\alpha$ for which $f$ is not defined, and may always play $\<x,s\>$ in a neighborhood of $c_\alpha$ for which $\sigma'(x,|s|)$ doesn't cover a neighborhood of $c_\alpha$.) Fix $n$ for which $f(\alpha)=n$ for $\alpha$ in an uncountable set $A$.
+
+Since the collection $\{U_\alpha : \alpha \in A\}$ is uncountable, it is not point-finite.
+Fix $x$ so that $x$ belongs to $U_\alpha$ for all $\alpha$ in an infinite $B \subseteq A$.
+Finally, consider $\sigma'(x,n)$.
+For each $\alpha\in B$, $\sigma'(x,f(\alpha))=\sigma'(x,n)$ covers $c_\alpha$.
+Since $\{c_\alpha : \alpha \in B\}$ is a closed infinite discrete set, we have a contradiction to the compactness of $\sigma'(x,n)$.
 \end{proof}
 
-\begin{proposition}
-$O\not\tactwin Con_{O,P}(\kappa\cup\{\infty\},\infty)$ for $\kappa\geq\omega_1$.
-\end{proposition}
+\begin{thm}
+$K\not\ktactwin{2}\gruKPGame{\mathbb{X}}$.
+\end{thm}
 
 \begin{proof}
-Let $F(\alpha)$ be the complement of a tactical strategy for $O$.
-There exists some $n<\omega$ such that we may find an infinite $B\subseteq \omega_1$ with $n\not\in F(\beta)$ for $\beta\in B$ - if not, we may find uncountable ordinals $\alpha$ such that $\omega \subseteq F(\alpha)$, a contradiction.
-Choose $\beta\in B\setminus F(n)$, and note that repeating $n,\beta$ is a successful counter to $O$'s strategy.
+Suppose $\sigma(\<x,s\>,\<y,t\>)$ was a winning 2-tactical strategy. We may define $S(x,y,n)\in [\omega_1]^{<\omega}$ (increasing on $n$) and $n<m(x,y,n)<\omega$ such that for each $(x,y)$,
+  \[
+    \bigcup_{s,t \in 2^{\leq n}} \sigma(\<x,s\>,\<y,t\>) \subseteq
+    K^*_{S(x,y,n)} \cup L_{m(x,y,n)}
+  \]
+and so we assume
+  \[
+    \sigma(\<x,s\>,\<y,t\>) =
+    K^*_{S(x,y,\max(|s|,|t|))} \cup L_{m(x,y,\max(|s|,|t|))}
+  \]
+
+Select an arbitrary point $x' \in X$. We define a tactical strategy
+  \[
+  \tau(x,s) =
+  K^*_{S(x,x',m(x,x',|s|)+1)} \cup L_{m(x,x',m(x,x',|s|)+1)}
+  \]
+We complete the proof by showing $\tau$ is a winning tactical strategy (a contradiction).
+
+Suppose
+\[
+\<x_0, s_0\>, \<x_1, s_1\>, \<x_2, s_2\>, \dots
+\]
+successfully countered $\tau$ by clustering at $c\in C$ (the strategy trivially prevents clustering elsewhere). Let $z_n = \<0,\dots,0\>$ with $n$ zeros. We claim
+\[
+\<x_0, s_0\>, \<x', {z_{m(x_0,x',|s_0|)}}^\frown\<1\>\>, \<x_1, s_1\>, \<x', {z_{m(x_1,x',|s_1|)}}^\frown\<1\>\>,  \<x_2, s_2\>, \<x', {z_{m(x_2,x',|s_2|)}}^\frown\<1\>\>, \dots
+\]
+is a successful counter to $\sigma$.
+
+We will need the fact that, as $\<x_{i+1},s_{i+1}\>$ was legal against $\tau$:
+  \[
+    |s_i| <
+    m(x_i,x',|s_i|)+1 =
+    |{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|
+  \]
+  \[
+    <
+    m(x_i,x',m(x_i,x',|s_i|)+1) =
+    m(x_i,x',|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|) \leq
+    |s_{i+1}|
+  \]
+
+Note that $m(x,y,\max(|s|,|t|))$ is increasing throughout this play of the game versus $\sigma$:
+  \[
+    m(x_i,x',\max(|s_i|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|))
+  \]
+  \[
+    =
+    m(x_i,x',|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|)
+  \]
+  \[
+    \leq
+    |s_{i+1}|
+  \]
+  \[
+    <
+    m(x_{i+1},x',|s_{i+1}|)
+  \]
+  \[
+    =
+    m(x_{i+1},x',\max(|s_{i+1}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|))
+  \]
+  \[
+    =
+    |{z_{m(x_{i+1},x',|s_{i+1}|)}}|
+  \]
+  \[
+    <
+    |{z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>|
+  \]
+  \[
+    <
+    m(x_{i+1},x',|{z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>|)
+  \]
+  \[
+    =
+    m(x_{i+1},x',\max(|s_{i+1}|,|{z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>|))
+  \]
+
+We turn to showing that $\<x', {z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>\>$ is always a legal move.
+Since ${z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>$ is on the antichain avoided by any $K^*$, the problem is reduced to showing that this move isn't forbidden by
+  \[
+  L_{m(x_{i+1},x',\max(|s_{i+1}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|))}
+  \]
+which we can see here:
+  \[
+    m(x_{i+1},x',\max(|s_{i+1}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|)) =
+    m(x_{i+1},x',|s_{i+1}|) <
+    |{z_{m(x_{i+1},x',|s_{i+1}|)}}^\frown\<1\>|
+  \]
+
+We can conclude by showing that $\<x_{i+1},s_{i+1}\>$ is always a legal move. We can see it avoids
+  \[
+  L_{m(x_{i},x',\max(|s_{i}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|))}
+  \]
+since
+  \[
+    m(x_{i},x',\max(|s_{i}|,|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|)) =
+    m(x_{i},x',|{z_{m(x_i,x',|s_i|)}}^\frown\<1\>|) \leq
+    |s_{i+1}|
+  \]
+
+Since $\<x_{i+1},s_{i+1}\>$ was legal against $\tau$, it avoided
+  \[
+    K^*_{S(x_h,x',m(x_h,x',|s_h|)+1)} =
+    K^*_{S(x_h,x',\max(|s_h|,|{z_{m(x_h,x',|s_h|)}}^\frown\<1\>|))}
+  \]
+for $h\leq i$. And when $h<i$, we see it avoids:
+  \[
+    K^*_{S(x_{h+1},x',\max(|s_{h+1}|,|{z_{m(x_h,x',|s_h|)}}^\frown\<1\>|))} =
+    K^*_{S(x_{h+1},x',|s_{h+1}|)}
+  \]
+  \[
+    \subseteq
+    K^*_{S(x_{h+1},x',m(x_{h+1},x',|s_{h+1}|)+1)}
+  \]
+
+This concludes the proof.
 \end{proof}
 
-\begin{definition}
-A \textbf{$k$-tactical strategy} considers only the last $k$ moves by the opposing player. If Player $Z$ has a winning $k$-tactical strategy for a game $G$, this may be denoted $Z \ktactwin{k} G$.
-\end{definition}
-
-\begin{theorem}
-$O\not\ktactwin{k}Con_{O,P}(\kappa\cup\{\infty\},\infty)$ for $\kappa\geq\omega_1$.
-\end{theorem}
+\begin{thm}
+$K\not\ktactwin{k}\gruKPGame{\mathbb{X}}$.
+\end{thm}
 
 \begin{proof}
-Let $\sigma:[\omega_1]^{\leq k}\to[\omega_1]^{<\omega}$ be a $k$-tactical strategy for $O$ restricted to $\omega_1$ and $F(S)=\omega_1\setminus\sigma(S)$.
+The proof proceeds in parallel to the proof of $K\not\ktactwin{2}\gruKPGame{\mathbb{X}}$.
 
-Let $W_0=\omega_1$. We define $W_\alpha$ recursively as follows:
-    \begin{itemize}
-    \item For successor ordinals $\alpha+1$, let $\beta$ be the least element of $W_\alpha$ such that $[\beta+1,\omega_1) \cap \bigcup_{S\leq \beta} F(S)$ is nonempty, where $S \leq \beta$ is shorthand for $\{S \in [\omega_1]^{\leq k} : \forall \gamma \in S(\gamma < \beta)\}$.
-If no such $\beta$ exists, let $W_{\alpha+1}=W_\alpha$ and otherwise let $W_{\alpha+1}=W_\alpha \setminus \left([\beta+1,\omega_1) \cap \bigcup_{S\leq \beta} F(S)\right)$.
-    \item For limit ordinals $\alpha$, let $W_\alpha = \bigcap_{\beta<\alpha} W_\beta$.
-    \end{itemize}
+Suppose $\sigma(\<x_0,s_0\>,\dots,\<x_{k},s_{k}\>)$ was a winning $(k+1)$-tactical strategy.
+We may define $S(x_0,\dots,x_{k},n)\in [\omega_1]^{<\omega}$ (increasing on $n$) and $n<m(x_0,\dots,x_{k},n)<\omega$ such that for each $(x_0,\dots,x_{k})$,
+  \[
+    \bigcup_{s_0,\dots,s_k \in 2^{\leq n}} \sigma(\<x_0,s_0\>,\dots,\<x_{k},s_{k}\>) \subseteq
+    K^*_{S(x_0,\dots,x_{k},n)} \cup L_{m(x_0,\dots,x_{k},n)}
+  \]
+and so we assume
+  \[
+    \sigma(\<x_0,s_0\>,\dots,\<x_{k},s_{k}\>) =
+    K^*_{S(x_0,\dots,x_{k},\max(|s_0|,\dots,|s_k|))} \cup L_{m(x_0,\dots,x_{k},\max(|s_0|,\dots,|s_k|))}
+  \]
 
-Finally let $W=\bigcap_{\alpha<\omega_1}W_\alpha$ and observe that it is unbounded.
-Let $R$ collect all ordinals $\alpha\in W$ such that there is an ordinal $\beta$ where for all $S\in[W\cap(\beta,\omega_1)]^{\leq k}$, $\alpha \in F(S)$.
-It is easily seen that $R$ is finite.
-Let $0^*$ be the least element of $W\setminus R$.
+Select an arbitrary point $x' \in X$. Let $M^0(x,n)=m(x,x',\dots,x',n)$ and $M^{i+1}(x,n)=M^0(x,M^i(x,n)+1)$. We define a tactical strategy
+  \[
+  \tau(x,s) = K^*_{S(x,x',\dots,x',M^{k-1}(x,|s|)+1)} \cup L_{m(x,x',\dots,x',M^{k-1}(x,|s|)+1)}
+  \]
+We complete the proof by showing $\tau$ is a winning tactical strategy (a contradiction).
 
-Now, define a strictly increasing sequence of ordinals $\left<\alpha_1,\alpha_2,\alpha_3,\alpha_4,\dots\right>$ such that $\alpha_i \in W$ and $0^* \not\in F(\{\alpha_{2i+1},\dots,\alpha_{2i+k}\})$ for all $i$.
-The play $\left<0^*,\alpha_1,\dots,\alpha_k,0^*,\alpha_{k+1},\dots,\alpha_{2k},0^*,\dots\right>$ then defeats the strategy $\sigma$.
+Suppose
+\[
+\<x_0, s_0\>, \<x_1, s_1\>, \<x_2, s_2\>, \dots
+\]
+successfully countered $\tau$ by clustering at $c\in C$ (the strategy trivially prevents clustering elsewhere). Let $z_n = \<0,\dots,0\>$ with $n$ zeros. We claim
+\[
+  \<x_0, s_0\>,
+  \<x', {z_{M^0(x_0,|s_0|)}}^\frown\<1\>\>,
+  \<x', {z_{M^1(x_0,|s_0|)}}^\frown\<1\>\>,
+  \dots,
+  \<x', {z_{M^{k-1}(x_0,|s_0|)}}^\frown\<1\>\>,
+\]
+\[
+  \<x_1, s_1\>,
+  \<x', {z_{M^0(x_1,|s_1|)}}^\frown\<1\>\>,
+  \<x', {z_{M^1(x_1,|s_1|)}}^\frown\<1\>\>,
+  \dots,
+  \<x', {z_{M^{k-1}(x_1,|s_1|)}}^\frown\<1\>\>,
+  \dots
+\]
+is a successful counter to $\sigma$.
+
+We will need the fact that, as $\<x_{i+1},s_{i+1}\>$ was legal against $\tau$:
+  \[
+    |s_i| <
+    M^0(x_i,|s_i|)+1 =
+    |{z_{M^0(x_i,|s_i|)}}^\frown\<1\>| <
+    M^0(x_i,M^0(x_i,|s_i|)+1)+1
+  \]
+  \[
+    =
+    M^1(x_i,|s_i|)+1 =
+    |{z_{M^1(x_i,|s_i|)}}^\frown\<1\>| <
+    \dots <
+    |{z_{M^{k-1}(x_i,|s_i|)}}^\frown\<1\>|
+  \]
+  \[
+    =
+    M^{k-1}(x_i,|s_i|) + 1 <
+    m(x_i,x',\dots,x',M^{k-1}(x_i,|s_i|)+1) \leq
+    |s_{i+1}|
+  \]
+
+Note that $m(x_0,\dots,x_{k},\max(|s_0|,\dots,|s_k|))$ is increasing throughout this play of the game versus $\sigma$:
+  \[
+    m(x_i,x',\dots,x',\max(|s_i|,|{z_{M^0(x_i,|s_i|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_i,|s_i|)}}^\frown\<1\>|))
+  \]
+  \[
+    =
+    m(x_i,x',\dots,x',|{z_{M^{k-1}(x_i,|s_i|)}}^\frown\<1\>|)
+  \]
+  \[
+    =
+    m(x_i,x',\dots,x',M^{k-1}(x_i,|s_i|)+1)
+  \]
+  \[
+    \leq
+    |s_{i+1}|
+  \]
+  \[
+    <
+    M^0(x_{i+1},|s_{i+1}|)
+  \]
+  \[
+    =
+    m(x_{i+1},x',\dots,x',|s_{i+1}|)
+  \]
+  \[
+    =
+    m(x_{i+1},x',\dots,x',\max(|s_{i+1}|,|{z_{M^0(x_i,|s_i|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_i,|s_i|)}}^\frown\<1\>|))
+  \]
+  \[
+    =
+    |{z_{m(x_{i+1},x',\dots,x',|s_{i+1}|)}}|
+  \]
+  \[
+    =
+    |{z_{M^0(x_{i+1},|s_{i+1}|)}}|
+  \]
+  \[
+    <
+    |{z_{M^0(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|
+  \]
+  \[
+    <
+    m(x_{i+1},x',\dots,x',|{z_{M^0(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|)
+  \]
+  \[
+    =
+    m(x_{i+1},x',\dots,x',\max(|s_{i+1}|,|{z_{M^0(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|,|{z_{M^1(x_{i},|s_{i}|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_{i},|s_{i}|)}}^\frown\<1\>|))
+  \]
+  \[
+    \vdots
+  \]
+  \[
+    <
+    m(x_{i+1},x',\dots,x',\max(|s_{i+1}|,|{z_{M^0(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|))
+  \]
+
+We turn to showing that $\<x', {z_{M^j(x_{i+1},|s_{i+1}|)}}^\frown\<1\>\>$ is always a legal move.
+Since ${z_{M^j(x_{i+1},|s_{i+1}|)}}^\frown\<1\>$ is on the antichain avoided by any $K^*$, the problem is reduced to showing that this move isn't forbidden by
+  \[
+    L_{m(x_{i+1},x',\dots,x',\max(|s_{i+1}|,|{z_{M^0(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|,\dots,|{z_{M^{j-1}(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|,|{z_{M^{j}(x_{i},|s_{i}|)}}^\frown\<1\>|,\dots,|{z_{M^{k}(x_{i},|s_{i}|)}}^\frown\<1\>|))}
+  \]
+  \[
+    =
+    L_{m(x_{i+1},x',\dots,x',|{z_{M^{j-1}(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|)}
+  \]
+which we can see here:
+  \[
+    m(x_{i+1},x',\dots,x',|{z_{M^{j-1}(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|)
+  \]
+  \[
+    =
+    m(x_{i+1},x',\dots,x',M^{j-1}(x_{i+1},|s_{i+1}|)+1)
+  \]
+  \[
+    =
+    M^0(x_{i+1},M^{j-1}(x_{i+1},|s_{i+1}|)+1)
+  \]
+  \[
+    =
+    M^j(x_{i+1},s_{i+1})
+  \]
+  \[
+    <
+    |{z_{M^j(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|
+  \]
+
+We can conclude by showing that $\<x_{i+1},s_{i+1}\>$ is always a legal move. We can see it avoids
+  \[
+  L_{m(x_{i},x',\dots,x',\max(|s_{i}|,|{z_{M^0(x_i,|s_i|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_i,|s_i|)}}^\frown\<1\>|))}
+  \]
+since
+  \[
+    m(x_{i},x',\dots,x',\max(|s_{i}|,|{z_{M^0(x_i,|s_i|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_i,|s_i|)}}^\frown\<1\>|))
+  \]
+  \[
+    =
+    m(x_{i},x',\dots,x',|{z_{M^{k-1}(x_i,|s_i|)}}^\frown\<1\>|)
+  \]
+  \[
+    =
+    m(x_{i},x',\dots,x',M^{k-1}(x_i,|s_i|)+1)
+  \]
+  \[
+    \leq
+    |s_{i+1}|
+  \]
+
+Since $\<x_{i+1},s_{i+1}\>$ was legal against $\tau$, it avoided
+  \[
+    K^*_{S(x_h,x',\dots,x',M^{k-1}(x_h,|s_h|)+1)}
+  \]
+  \[
+    =
+    K^*_{S(x_h,x',\dots,x',\max(|s_h|,|{z_{M^{0}(x_h,|s_h|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_h,|s_h|)}}^\frown\<1\>|))}
+  \]
+for $h\leq i$. And when $h<i$, we see it avoids both:
+  \[
+    K^*_{S(x_{h+1},x',\dots,x',\max(|s_{h+1}|,|{z_{M^0(x_{h+1},|s_{h+1}|)}}^\frown\<1\>|,\dots,|{z_{M^{j-1}(x_{h+1},|s_{h+1}|)}}^\frown\<1\>|,|{z_{M^{j}(x_{h},|s_{h}|)}}^\frown\<1\>|,\dots,|{z_{M^{k}(x_{h},|s_{h}|)}}^\frown\<1\>|))}
+  \]
+  \[
+    =
+    K^*_{S(x_{h+1},x',\dots,x',|{z_{M^{j-1}(x_{h+1},|s_{h+1}|)}}^\frown\<1\>|)}
+  \]
+  \[
+    =
+    K^*_{S(x_{h+1},x',\dots,x',M^{j-1}(x_{h+1},|s_{h+1}|)+1)}
+  \]
+  \[
+    \subseteq
+    K^*_{S(x_{h+1},x',\dots,x',M^{k-1}(x_{h+1},|s_{h+1}|)+1)}
+  \]
+and:
+  \[
+    K^*_{S(x_{h+1},x',\dots,x',\max(|s_{h+1}|,|{z_{M^0(x_{h},|s_{h}|)}}^\frown\<1\>|,\dots,|{z_{M^{k}(x_{h},|s_{h}|)}}^\frown\<1\>|))}
+  \]
+  \[
+    =
+    K^*_{S(x_{h+1},x',\dots,x',|s_{k+1}|)}
+  \]
+  \[
+    \subseteq
+    K^*_{S(x_{h+1},x',\dots,x',M^{k-1}(x_{h+1},|s_{h+1}|)+1)}
+  \]
+
+This concludes the proof.
 \end{proof}
 
-Peter J. Nyikos has shown the following:
+\section{various examples}
 
-\begin{theorem}
-$O\not\markwin Con_{O,P}(\omega_1\cup\{\infty\},\infty)$.
-\end{theorem}
+\begin{ex}
+If $\mathcal{F}$ is a free ultrafilter on $\omega$, let $L(\mathcal{F})=\omega \cup \{\mathcal{F}\}$ as a subspace of the Stone-Cech compactification $\beta\omega$ be the \textbf{single ultrafilter line}.
+There is some ultrafilter $\mathcal{F}$ such that $K \prewin \gruKPGame{L(\mathcal{F})}$ and $K \tactwin \gruKPGame{L(\mathcal{F})}$.
 
-This can be improved:
-
-\begin{theorem}
-$O\not\kmarkwin{k} Con_{O,P}(\kappa\cup\{\infty\},\infty)$ for $\kappa\geq\omega_1$.
-\end{theorem}
+($L(\mathcal{F})$ is not compactly generated, and thus not locally compact.)
+\end{ex}
 
 \begin{proof}
-Let $F:[\omega_1]^{\leq k}\times\omega\to[\omega_1]^{<\omega}$ be the complement of a $k$-Markov strategy for $O$ restricted to $\omega_1$.
+Let $a_n$ be a sequence such that the sequence $\frac{a_n}{n}$ is unbounded above.
+Then there is an ultrafilter $\mathcal{F}$ such that $\sigma(n)=(\sum_{m\leq n} a_m )\cup \{\mathcal{F}\}$ is a winning predetermined strategy for $K$ in $\gruKPGame{L(\mathcal{F})}$.
 
-Let $W_0=\omega_1$. We define $W_\alpha$ recursively as follows:
-    \begin{itemize}
-    \item For successor ordinals $\alpha+1$, let $\beta$ be the least element of $W_\alpha$ such that \[(\beta,\omega_1) \cap \bigcup_{S\in [\beta]^{\leq k}, n<\omega} F(S,n)\] is nonempty.
-If no such $\beta$ exists, let $W_{\alpha+1}=W_\alpha$ and otherwise let \[W_{\alpha+1}=W_\alpha \setminus \left((\beta,\omega_1) \cap \bigcup_{S\in[\beta]^{\leq k}, n<\omega} F(S,n)\right)\]
-    \item For limit ordinals $\alpha$, let $W_\alpha = \bigcap_{\beta<\alpha} W_\beta$.
-    \end{itemize}
+Let $\mathcal{P}$ be the collection of all legal plays by $P$ against the strategy $\sigma$.
+Consider a finite collection of plays $P_0,\dots,P_{n-1}\in \mathcal{P}$.
+As $\frac{a_m}{m}$ is unbounded above, we may find infinitely many $m$ such that $\frac{a_m}{m}>n \Rightarrow mn<a_m$.
+As the $a_m$ partition $\omega$ such that $P$ may only play at most $m$ points in each part, there are infinitely many parts which are not filled, and thus $\bigcup_{m<n} P_m$ is not cofinite.
 
-Finally let $W=\bigcap_{\alpha<\omega_1}W_\alpha$ and observe that it is unbounded.
-Let $R$ collect all ordinals $\alpha\in W$ such that there is an ordinal $\beta_\alpha$ and number $n_\alpha<\omega$ where for all $S\in[W\cap(\beta_\alpha,\omega_1)]^{\leq k}$, $\alpha \in F(S,n_\alpha)$.
+It then follows that the closure of $\mathcal{P}$ under finite unions and subsets, along with all finite sets, is an ideal.
+Its dual filter may then be extended to an ultrafilter $\mathcal{F}$ such that every possible play by $P$ is the complement of some member of $\mathcal{F}$, making $\sigma$ a winning predetermined strategy.
 
-If $R$ was infinite, then there is $\alpha_i\in R$ for each $i<\omega$ and some $N<\omega$ where for all $S\in[W\cap(\beta_{\alpha_i},\omega_1)]^{\leq k}$, $\alpha_i \in F(S,N)$, and thus for all $S\in[W\cap(\sup \beta_{\alpha_i},\omega_1)]^{\leq k}$,  $\{\alpha_i : i<\omega\} \subset F(S,N)$, a contradiction.
-So let $0^*$ be the least element of $W\setminus R$.
-
-Now, define a strictly increasing sequence of ordinals $\left<\alpha_1,\alpha_2,\alpha_3,\alpha_4,\dots\right>$ such that $\alpha_i \in W$ and $0^* \not\in F(\{\alpha_{2i+1},\dots,\alpha_{2i+k}\})$ for all $i$.
-The play $\left<0^*,\alpha_1,\dots,\alpha_k,0^*,\alpha_{k+1},\dots,\alpha_{2k},0^*,\dots\right>$ then defeats the Markov strategy.
+A winning tactic can then be easily constructed by using the moves by $P$ as the round number in the predetermined strategy.
 \end{proof}
 
-While these counters prevent convergence to $\infty$, they do not prohibit clustering, as any sequence of points with infinite range clusters at $\infty$ in this space.
+\begin{ex}
+Let $T(\mathcal{F}) = 2^{\leq\omega}$ where $2^{<\omega}$ is discrete and for each $c\in 2^\omega$, $\{c \restriction \alpha : \alpha \leq \omega\}$ is homeomorphic to $L(\mathcal{F})$.
+This is called the \textbf{single ultrafilter tree}.
+There is some ultrafilter $\mathcal{F}$ such that $K \prewin \gruKPGame{L(\mathcal{F})}$ and $K \tactwin \gruKPGame{L(\mathcal{F})}$.
 
-\begin{definition} 
-The open-point clustering game $Clus_{O,P}(X,x)$ has $O$ choosing nested open sets and $P$ choosing a point within the last chosen open set by $O$. $O$ wins if the points chosen by $P$ cluster to $x$.
-\end{definition}
-
-Any strategy which forces convergence also forces clustering, so a coding strategy exists for player $O$. And since the counter used above to foil any tactical strategy had only finite range...
-
-\begin{proposition}
-$O\not\tactwin Clus_{O,P}(X,\infty)$.
-\end{proposition}
-
-The other counters only attempt to repeat a point infinitely often, and may have infinite range.
-
-\begin{example}
-For $\omega\leq\alpha<\omega_1$ let $\leq_{\alpha}$ be a well-ordering of $\omega_1$ such that its restriction to $\alpha$ is isomorphic to $\omega$ with isomorphism $f(n):\omega\to\alpha$.
-For $n<\omega$ let $\leq_n$ simply be $\leq$ and $f$ be the identity.
-
-The 2-tactical strategy for $O$ in $Clus_{O,P}(\omega_1\cup\{\infty\}),\infty)$ whose complement is, for $\alpha<\beta$, $F(\alpha,\beta)=\{\gamma : \gamma \leq_\beta \alpha \} \cup \{\beta\}$, forces the point-picker to chose more than three distinct points.
-\end{example}
+($T(\mathcal{F})$ is not compactly generated, and thus not locally compact.)
+\end{ex}
 
 \begin{proof}
-Suppose Player $P$ started with $\alpha_0<\alpha_1$.
-Player $O$ forbids \[F(\alpha_0,\alpha_1) = \{\gamma : \gamma \leq_{\alpha_1}\alpha_0\} \cup \{\alpha_1\}\] so Player $P$ must respond with $\alpha_2$ such that either $\alpha_0<\alpha_1<\alpha_2$ or $\alpha_0<_{\alpha_1}\alpha_2<\alpha_1$.
+Assume without loss of generality that $P$ does not play points in $2^\omega$.
 
-In the first case that $\alpha_0<\alpha_1<\alpha_2$, Player $O$ now forbids \[F(\alpha_1,\alpha_2) = \{\gamma : \gamma \leq_{\alpha_2}\alpha_1\} \cup \{\alpha_2\}\] If $\alpha_0<_{\alpha_2}\alpha_1$ we're done.
-Otherwise, Player $P$ chooses $\alpha_0>_{\alpha_2}\alpha_1$ again, and Player $O$ responds with \[F(\alpha_0,\alpha_2)=\{\gamma : \gamma \leq_{\alpha_2} \alpha_0 \} \cup \{\alpha_2\}\] which successfully forbids $\alpha_1$.
+We use a winning predetermined strategy $\sigma^*(n)$ for $L(\mathcal{F})$ and let $\sigma(n) = \bigcup_{m \in \sigma^*(n)} 2^m$.
+Note that if $P$ has a counter which converges to some $c\in \,^\omega2$, then $P$ would have a counter within a single branch.
+Since each branch is homeomorphic to $L(\mathcal{F})$; this is impossible.
 
-In the second case that $\alpha_0<_{\alpha_1}\alpha_2<\alpha_1$, Player $O$ forbids \[F(\alpha_1,\alpha_2) = \{\gamma : \gamma \leq_{\alpha_1}\alpha_2\} \cup \{\alpha_1\}\] which successfully forbids $\alpha_0$.
-
-Thus, a fourth ordinal must be selected.
+A winning tactic can then be easily constructed by using the moves by $P$, taking the level of the tree played upon as the round number in the predetermined strategy.
 \end{proof}
 
-But the fourth ordinal is all that is needed.
+\begin{ex}
+Let $M = \omega^2 \cup \{\infty\}$ be the \textbf{metric fan} where $\omega^2$ is discrete and $\infty$ has neighborhoods of the form $M \setminus (n\times\omega)$ for any $n<\omega$.
+Then $K \not\win \gruKPGame{M}$.
+(In fact, $P \markwin \gruKPGame{M}$.)
 
-\begin{theorem}
-$O\not\ktactwin{2}Clus_{O,P}(\omega_1\cup\{\infty\},\infty)$.
-\end{theorem}
+($M$ is not locally compact, but is compactly generated.)
+\end{ex}
 
 \begin{proof}
-Let $F(\alpha,\beta)$ be the complement of a k-tactical strategy for O, and assume without loss of generality that it does not forbid any ordinals larger than its inputs.
+For each compact set $C$ in $M$, there exists a minimal dominating function $f_C$ such that for each $(x,y)\in C\setminus\{\infty\}$, $f(x)> y$.
 
-Let $n_0=\min(\omega\setminus F(\emptyset)\setminus F(\omega,\omega+1))$ and $n_1 = \min(\omega\setminus F(n_0)\setminus F(n_0,\omega+1))$.
-
-It follows that $\left<n_0,n_1,\omega,\omega+1,n_0,n_1,\omega,\omega+1,\dots\right>$ is a legal counter.
+So let $P$ respond to the move $C\in K[X]$ by $K$ on round $n$ with the point $p=(n,s_C)$ such that $s_C = \min(\{y<\omega : f_C(n) < y\}$.
+It is easy to see that $p_n\rightarrow \infty$, so $P$ has a winning Markov strategy.
 \end{proof}
 
-But, in fact, a similar counter can be used for any $k$-tactical strategy.
+\begin{ex}
+Let $S = \omega^2 \cup \{\infty\}$ be the \textbf{sequential fan} where $\omega^2$ is discrete and $\infty$ has neighborhoods of the form $M \setminus \{(x,y) : x<f(y)\}$ for any $f:\omega\to\omega$.
+Then $K \prewin \gruKPGame{S}$ and $K\tactwin \gruKPGame{S}$.
 
-\begin{theorem}
-$O\not\ktactwin{k}Clus_{O,P}(\omega_1\cup\{\infty\},\infty)$.
-\end{theorem}
+($S$ is not locally compact, but is compactly generated.)
+
+\end{ex}
 
 \begin{proof}
-Let $F(\alpha_0,\dots,\alpha_{k-1})$ be the complement of a k-tactical strategy for O, and assume without loss of generality that it does not forbid any ordinals larger than its inputs.
+Let $\sigma(n)=\omega\times(n+1) \cup \{\infty\}$.
+By defining $f(y)$ to be greater than the $x$-coordinate of all $P$'s plays through round $y$, we see that $M\setminus\{(x,y): x<f(y)\}$ misses every move by $P$, so $P$ cannot converge to $\infty$.
 
-For $0\leq i < k$, we define \[n_i = \min(\omega\setminus F(n_0,\dots,n_{i-1},\omega+i,\dots,\omega+k-1)\setminus F(n_0,\dots,n_{i-1}))\]
-
-It follows that $\left<n_0,\dots,n_{k-1},\omega,\dots,\omega+k-1,n_0,\dots,n_{k-1},\omega,\dots,\omega+k-1,\dots\right>$ is a legal counter.
+A winning tactic can be easily constructed by using the $y$-coordinate of $P$'s moves as the round number in the predetermined strategy.
 \end{proof}
-
-However, a Markov strategy is sufficient to defeat $P$ in the clustering game for $\omega_1$.
-
-\begin{theorem}
-$O\markwin Clus_{O,P}(\omega_1\cup\{\infty\},\infty)$.
-\end{theorem}
-
-\begin{proof}
-For $\omega\leq\alpha<\omega_1$ let $\leq_{\alpha}$ be a well-ordering of $\omega_1$ such that its restriction to $\alpha$ is isomorphic to $\omega$ with isomorphism $f(n):\omega\to\alpha$.
-For $n<\omega$ let $\leq_n$ simply be $\leq$ and $f$ be the identity.
-
-Let $F(\alpha,n)=\{\gamma : \gamma \leq_\alpha f(n)\}$ be the complement of $O$'s Markov strategy in response to move $\alpha$ in round $n$.
-
-If a legal counter by $P$ does not repeat some largest ordinal infinitely often, it does not result in a win for $P$.
-Otherwise let $\beta$ be largest ordinal repeated infinitely often in some legal counter by $P$.
-We note that the forbidden sets responded by $O$ are of the form $F(\beta,n)$ where $n$ increases as the game progresses.
-It is impossible to repeat any ordinal less than $\beta$ infinitely often due to the increasing round number, so the range of the counter is infinite, and does not result in a win for $P$.
-\end{proof}
-
-...while it similarly fails for $\kappa>\omega_1$.
-
-\begin{theorem}
-$O\not\kmarkwin{k}Clus_{O,P}(\kappa\cup\{\infty\},\infty)$ for $\kappa>\omega_1$.
-\end{theorem}
-
-\begin{proof}
-Let $F:\omega\times[\kappa]^{\leq k} \to [\kappa]^\omega$ be the complement of a k-Markov strategy for O, and assume without loss of generality that it does not forbid any ordinals larger than its inputs.
-
-For $0\leq i < k$, we define \[\beta_i = \min(\omega\setminus \bigcup_{n<\omega} F(n,\{\beta_0,\dots,\beta_{i-1},\omega_1+i,\dots,\omega_1+k-1\})\setminus\bigcup_{n<\omega} F(n,\{\beta_0,\dots,\beta_{i-1}\}))\]
-
-It follows that $\left<\beta_0,\dots,\beta_{k-1},\omega_1,\dots,\omega_1+k-1,\beta_0,\dots,\beta_{k-1},\omega_1,\dots,\omega_1+k-1,\dots\right>$ is a legal counter.
-\end{proof}
-
-\centerline{\bf $Con_{O,P}(X,x)$ for Sigma Product}
-
-\begin{proposition}
-The player $O$ has a winning strategy for $Con_{O,P}(X,x)$ where \[X=\Sigma\mathbb{R}^{\omega_1}=\{x\in \mathbb{R}^{\omega_1}: x_\alpha = 0 \text{ for all but countably many } \alpha<\omega_1\}\]
-\end{proposition}
-
-\begin{proof}
-Without loss of generality we may assume that $x$ is the zero function.
-Let $y_n$ be the move by $P$ on turn $n$.
-For each $y_n$, let $l_n\in \omega_1^{\omega}$ enumerate the nonzero coordinates in $y_n$.
-Give $O$ the strategy $\sigma(y_0,\dots,y_{n-1}) = \prod_{\alpha<\omega_1} O_\alpha$ where if $\alpha$ is listed in the first $n$ coordinates of any term in $\left<l_k\right>_{k<n}$, then $O_\alpha=(-2^{-n},2^{-n})$, and $O_\alpha=\mathbb{R}$ otherwise.
-\end{proof}
-
-\begin{theorem}
-For all cardinals $\kappa\leq 2^\omega$, the player $O$ has a winning coding strategy for $Con_{O,P}(X,x)$ where \[X=\Sigma\mathbb{R}^{\kappa}=\{x\in \mathbb{R}^{\kappa}: x_\alpha = 0 \text{ for all but countably many } \alpha<\kappa\}\]
-\end{theorem}
-
-\begin{proof}
-Note that $|\Sigma\mathbb{R}^\kappa| \leq 2^\omega = |\mathbb{R}|$. Define the following:
-
-    \begin{itemize}
-    \item Encode every finite sequence $s$ of functions in $\Sigma\mathbb{R}^{\kappa}$ as a real number $0<r(s)<1$. 
-    \item Let $\gamma(U)$ be the function which, for basic open sets $U=\prod_{\alpha<\kappa}U_\alpha$ where $U_0=(-\frac{1}{R},\frac{1}{R})$ for some positive noninteger real number $R$, returns the sequence $r^{-1}(R-\lfloor R\rfloor)$.
-    \item Let $n(U)$ be the length of $\epsilon^{-1}(\gamma(U))$.
-    \item Let $\psi(U,y)=\epsilon^{-1}(\gamma(U))^\frown\left<y\right>$.
-    \item Define $\sigma_0(U,y)$ to be $\left(-\frac{1}{n(U)+r(\psi(U,y))},\frac{1}{n(U)+r(\psi(U,y))}\right)$.
-    \item For each $0<\alpha<\kappa$, define the interval $\sigma_\alpha(U,y)$ about $0$ as follows:
-        \begin{itemize}
-        \item If $\alpha$ is listed in the first $n(U)$ coordinates of any term in the finite sequence $\psi(U,y)$, then $\sigma_\alpha(U,y)=(-\frac{1}{n(U)+1},\frac{1}{n(U)+1})$.
-        \item Otherwise, then $\sigma_\alpha(U,y)=\mathbb{R}$.
-        \end{itemize}
-    \end{itemize}
-
-It follows that $\sigma(U,y)=\prod_{\alpha<\kappa} \sigma_\alpha(U,y)$ is a winning coding strategy.
-\end{proof}
-
-\begin{theorem}
-For all cardinals $\kappa>2^\omega$ such that $\kappa^\omega = \kappa$, the player $O$ has a winning coding strategy for $Con_{O,P}(X,x)$ where \[X=\Sigma\mathbb{R}^{\kappa}=\{x\in \mathbb{R}^{\kappa}: x_\alpha = 0 \text{ for all but countably many } \alpha<\omega_1\}\]
-\end{theorem}
-
-\begin{proof}
-Note that $|\Sigma\mathbb{R}^\kappa| = \kappa^\omega = \kappa$. Define the following:
-
-    \begin{itemize}
-    \item Encode every finite sequence $s$ of functions in $\Sigma\mathbb{R}^{\kappa}$ as an ordinal $\epsilon(s)<\kappa$. 
-    \item Let $\gamma(U)$ be the function which, for basic open sets $U=\prod_{\alpha<\kappa}U_\alpha$ with a unique factor $U_{\alpha^*}$, returns $\alpha^*$.
-    \item Let $n(U)$ be the length of $\epsilon^{-1}(\gamma(U))$.
-    \item Let $\psi(U,y)=\epsilon^{-1}(\gamma(U))^\frown\left<y\right>$.
-    \item For each $\alpha<\kappa$, define the interval $\sigma_\alpha(U,y)$ about $0$ as follows:
-        \begin{itemize}
-        \item If $\alpha$ is listed in the first $n(U)$ coordinates of any term in the finite sequence $\psi(U,y)$ and is not equal to $\epsilon(\psi(U,y))$, then $\sigma_\alpha(U,y)=(-\frac{1}{n(U)+1},\frac{1}{n(U)+1})$.
-        \item If $\alpha=\epsilon(\psi(U,y))$, then $\sigma_\alpha(U,y)=(-\frac{1}{n(U)+2},\frac{1}{n(U)+2})$.
-        \item Otherwise, then $\sigma_\alpha(U,y)=\mathbb{R}$.
-        \end{itemize}
-    \end{itemize}
-
-It follows that $\sigma(U,y)=\prod_{\alpha<\kappa} \sigma_\alpha(U,y)$ is a winning coding strategy.
-\end{proof}
-
-% NOPE
-%\begin{theorem}
-%For all cardinals $\kappa$ such that $2^\omega< \kappa < \kappa^\omega$, the player $O\not\codewin Cl_{O,P}(X,x)$ where \[X=\Sigma\mathbb{R}^{\kappa}=\{x\in% \mathbb{R}^{\kappa}: x_\alpha = 0 \text{ for all but countably many } \alpha<\omega_1\}\]
-%\end{theorem}
-%
-%\begin{proof}We begin by noting that $|\tau|=\kappa<\kappa^\omega$, where $\tau$ is the topology of $\Sigma \mathbb{R}^\kappa$.
-%
-%Suppose that for all $S\subseteq \Sigma\mathbb{R}^\kappa$ such that $\sigma(U,x)=\sigma(V,y)$ for all $x,y\in\Sigma \mathbb{R}^\kappa$ and $U,V\in\tau$, it follows that $|S|<\kappa^\omega$.
-Then \[\left|\bigcup_{V\in\tau}\sigma^{-1}(V)\right|=\max(\{\lambda : \lambda=|\tau| \,\vee\, \exists V\in\tau(\lambda=|\sigma^{-1}(V)|)\}) < \kappa^\omega \] while $\bigcup_{V\in\tau}\sigma^{-1}(V)=\tau\times \Sigma\mathbb{R}^\kappa$, a contradiction.
-%
-%It follows that we may find $S\subseteq \Sigma\mathbb{R}^\kappa$ with $|S|=\kappa^\omega$ such that $\sigma(U,x)=\sigma(V,y)$ for all $x,y\in\Sigma \mathbb{R}^\kappa$ and $U,V\in\tau$.
-%
-%If $P$ only plays sequences in $S$, then $O$ plays the same set in every round following the initial round.
-As such, $O$ only places restrictions on $\omega$-many coordinates of the sequences chosen by $P$ throughout the game.
-Call these restricted coordinates $R\subseteq \kappa$.
-If $x(\alpha)=0$ for all $x\in S$ and $\alpha\not\in R$, then it would follow that $|S|=|\mathbb{R}|^{|R|}=2^\omega<\kappa^\omega$, a contradiction.
-%
-%So, choose $x\in S$ such that $x(\alpha)\not=0$ for some $\alpha\not\in R$. The play \[\left<U_0,x,U_1=\sigma(U_0,x),x,U_2=\sigma(U_1,x)=U_1,x,U_1,x,\dots\right>\] is a counter to $\sigma$.
-%\end{proof}
-
-\centerline{\bf Finite Countable Game}
-
-\begin{theorem}
-Let $\kappa$ be a cardinal such that there exists a function $f:\kappa\to[\kappa]^{\leq \omega}$ where for every $W\in[\kappa]^{\leq\omega}$ there exists $\alpha_W<\kappa$ with $W\subseteq f(\alpha_W)$.
-Then $F \codewin PF_{F,C}(\kappa)$ and $O \codewin Con_{O,P}(\Sigma\mathbb{R}^\kappa)$.
-\end{theorem}
-
-\begin{proof}
-Long version.
-
-We begin by defining a few helpful tools. Assume $N\in[\kappa]^{<\omega}$ and $W \in [\kappa]^{\leq\omega}$.
-    \begin{itemize}
-    \item Let $N^* = N \setminus \{\max(N)\}$.
-    \item Noting that $\kappa\setminus \alpha$ is order-isomorphic to $\kappa$ for all $\alpha<\kappa$, let $\gamma_N<\kappa$ be the ordinal mapping to $\max(N)$ in $\kappa\setminus(\max(N^*)+1)$ by the appropriate order isomorphism.
-    \item Let $s: [\kappa]^{<\omega} \to \kappa$ be a bijection.
-    \item Define $W\restriction n \in [\kappa]^{<\omega}$ so that $W\restriction n \subseteq W\restriction (n+1)$ and $\bigcup_{n<\omega}W\restriction n = W$.
-    \item Let $t_N=\max(N\cap\omega)+2$.
-    \end{itemize}
-
-Let the (non-winning) coding strategy $\sigma'$ be defined as follows: \[\sigma'(N,W)=\bigcup_{\alpha \in s^{-1}(\gamma_N)} f(\alpha) \restriction t_N\]
-
-Let $\left<N_0,N_1,\dots\right>$ be a play by $F$ following the considered strategy in response to the play $\left<W_0,W_1,\dots\right>$ by $C$ in the game $PF_{F,C}(\kappa)$.
-(For technical reasons, assume $N_0$ contains at least two ordinals.) This coding strategy could have been a winning strategy for $F$ if it had only satisfied two requirements:
-
-    \begin{enumerate}
-    \item First, $s^{-1}(\gamma_{N_k})$ provided ordinals $\{\alpha_{W_0},\dots,\alpha_{W_{k-1}}\}$.
-(Thus $N_{k+1}=\bigcup_{\alpha \in s^{-1}(\gamma_{N_k})} f(\alpha) \restriction t_{N_k} = \bigcup_{0\leq m < k} f(\alpha_{W_m}) \restriction t_{N_k}$.)
-    \item In addition, $t_{N_k} \to \infty$.
-(Thus $\bigcup_{k<\omega} N_{k+1} = \bigcup_{k<\omega}\bigcup_{0\leq m < k-1} f(\alpha_{W_m}) \restriction t_{N_k} = \bigcup_{m<\omega} f(\alpha_{W_m}) \supseteq \bigcup_{m<\omega} W_m$.)
-    \end{enumerate}
-
-We shall improve $\sigma'$ so that it does satsify those requirements, beginning with the second.
-Define $\sigma^*$: \[\sigma^*(N,W)=t_N \cup \sigma'(N,W)\] Note then that $t_{N_{k+1}}\geq t_{t_{N_k}} = \max(t_{N_k})+2 = t_{N_k}-1+2=t_{N_k}+1$.
-
-Lastly, to cover the first requirement, we define $\sigma$: \[\sigma(N,W) = \sigma^*(N,W) \cup \{ \max(\sigma^*(N,W))+1+s(s^{-1}(\gamma_N)\cup\{\alpha_W\}) \}\] By induction \[s^{-1}(\gamma_{N_{k+1}}) = s^{-1}(s(s^{-1}(\gamma_{N_k})\cup\{\alpha_{W_k}\})) = s^{-1}(\gamma_{N_k})\cup\{\alpha_{W_k}\} = \{\alpha_{W_0},\dots,\alpha_{W_{k-1}}\}\cup\{\alpha_{W_k}\}\] we see the first requirement is satisfied.
-
-Finally, we turn our attention to $Con_{O,P}(\Sigma\mathbb{R}^\kappa)$.
-We define the winning strategy $\tau(U,p)$ for $O$ as follows: let $N(U)$ be the non-$\mathbb{R}$ coordinates in the basic open set $U$ and $W(p)$ be the non-$0$ coordinates in $p$.
-Then $\tau(U,p) = \left(\prod_{\alpha<\kappa} U_\alpha\right) \cap \Sigma\mathbb{R}^\kappa$ where if $\alpha \in \sigma(N(U),W(p))$ then $U_\alpha = (-1/t_{N(U)},1/t_{N(U)})$ and $U_\alpha=\mathbb{R}$ otherwise.
-\end{proof}
-
-\begin{proof}
-Short version, per GG's suggestion.
-
-Let $W\restriction n \in [\kappa]^n$ be a subset of $W\in[\kappa]^\omega$ such that $W\restriction n \subset W \restriction (n+1)$ and $\bigcup_{n<\omega} W\restriction n = W$.
-
-Define \[\sigma(N,W) = N \cup (|N|+1) \cup \{\alpha_W\} \cup \bigcup_{\alpha \in N} f(\alpha) \restriction |N|\]
-
-Consider the play $\left<\emptyset,W_0,N_1,W_1,N_2,W_2,\dots\right>$ with $F$ following the strategy $\sigma$.
-Let $\gamma \in W_i$, and note $\gamma \in f(\alpha_{W_i})$ (and $\gamma \in f(\alpha_{W_i})\restriction |N_n|$ for sufficiently large $n$).
-\[N_{i+1} = \sigma(N_i,W_i) \supseteq \{\alpha_{W_i}\}\] and thus \[N_{n+1} = \sigma(N_n,W_n) \supseteq \bigcup_{\alpha \in N_n} f(\alpha) \restriction |N_n| \supseteq \bigcup_{\alpha \in N_{i+1}} f(\alpha) \restriction |N_n| \supseteq f(\alpha_{W_i}) \restriction |N_n|\] showing $\gamma \in N_{n+1}$.
-Since $\gamma$ is forbidden in round $n+1$, $\gamma$ appears in finitely many sets chosen by $C$.
-
-We turn our attention to $Con_{O,P}(\Sigma\mathbb{R}^\kappa)$.
-We define the winning strategy $\tau(U,p)$ for $O$ as follows: let $N(U)$ be the non-$\mathbb{R}$ coordinates in the basic open set $U$ and $W(p)$ be the non-$0$ coordinates in $p$.
-Then $\tau(U,p) = \left(\prod_{\alpha<\kappa} U_\alpha\right) \cap \Sigma\mathbb{R}^\kappa$ where if $\alpha \in \sigma(N(U),W(p))$ then $U_\alpha = (-\frac{1}{|N(U)|},\frac{1}{|N(U)|})$ and $U_\alpha=\mathbb{R}$ otherwise.
-
-Consider the play $\left<\emptyset,p_0,U_1,p_1,U_2,p_2,\dots\right>$ with $O$ following the strategy $\tau$.
-Observe that $N(\tau(U,p))=\sigma(N(U),W(p))$.
-Thus $p_i(\gamma)\not=0$ is equivalent to $\gamma \in W(p_i)$, and by the above argument, for sufficiently large $n$, $\gamma \in \sigma(N(U_n),W(p_n))$.
-Therefore from round $n$ onward the $\gamma$-coordinates of points chosen by $P$ must lay in $(-\frac{1}{|N(U)|},\frac{1}{|N(U)|})$ and converge to $0$.
-\end{proof}
-
-%
-%\begin{theorem}
-%For all cardinals $\kappa \geq \omega$, the player $F \not\tactwin Cov_{F,C}(\kappa)$.
-%\end{theorem}
-%
-%\begin{proof}
-%(Based on Scheeper's Meager Nowhere Dense Games I)
-%
-%Suppose $\sigma$ is a tactical strategy for $F$ such that (without loss of generality) the first move is $\emptyset$. Let $A=\{2n: n<\omega\}$ and $B=\{2n+1:n<\omega\}$.
-%
-%By Todorcevic's Partition Relations for Partially Ordered Sets, $\mathcal{P}(A)\rightarrow(\omega)^1_B$.
-That is, for any function $\Phi$ from $\mathcal{P}(A)$ to $B$, there is some $b_\Phi\in B$ and $X_0\subseteq X_1\subseteq \dots \in \mathcal{P}(A)$ such that $\Phi(X_i)=b_\Phi$ for all $i$.
-Define $\Phi:\mathcal{P}(A)\rightarrow B$ such that $\Phi(X)\in B\setminus(\sigma(B\cup X))$.
-%
-%Observe the play $\left<\emptyset, B\cup X_0, \sigma(B\cup X_0), B \cup X_1, \sigma(B \cup X_1), B \cup X_2, \dots \right>$.
-As $b_\Phi \in B \subseteq \bigcup_{i<\omega} B \cup X_i$ but $b_\Phi \not\in \bigcup_{i<\omega} \sigma(B\cup X_i)$, this is a successful counter to any tactic by $F$.
-%\end{proof}
-%
-%\begin{proposition}
-%For all cardinals $\kappa \geq \omega_1$, the player $F \not\markwin Cov_{F,C}(\kappa)$.
-%\end{proposition}
-%
-%\begin{proof}
-%Suppose $\sigma$ is a Markov strategy for $F$ such that (without loss of generality) the first move is $\emptyset$. Let $A,B\in\mathcal{P}(\kappa)$ be disjoint with $|A|=|B|\geq\omega_1$.
-%
-%By Todorcevic's Partition Relations for Partially Ordered Sets, $\mathcal{P}(A)\rightarrow(\omega)^1_B$.
-That is, for any function $\Phi$ from $\mathcal{P}(A)$ to $B$, there is some $b_\Phi\in B$ and $X_0\subseteq X_1\subseteq \dots \in \mathcal{P}(A)$ such that $\Phi(X_i)=b_\Phi$ for all $i$.
-Define $\Phi:\mathcal{P}(A)\rightarrow B$ such that $\Phi(X)\in B\setminus(\bigcup_{n<\omega}\sigma(B\cup X,n))$.
-%
-%Observe the play $\left<\emptyset, B\cup X_0, \sigma(B\cup X_0,1), B \cup X_1, \sigma(B \cup X_1,2), B \cup X_2, \dots \right>$.
-As $b_\Phi \in B \subseteq \bigcup_{i<\omega} B \cup X_i$ but $b_\Phi \in \bigcap_{m<\omega} B \setminus (\bigcup_{n<\omega}\sigma(B\cup X_m,n))$ implying $b_\Phi \not\in \bigcup_{m<\omega}\sigma(B\cup X_m,m+1)$, this is a successful counter to any Markov strategy by $F$.
-%\end{proof}
-
-%\begin{theorem}
-%If $F\codewin Cov_{F,C}^{**}(\kappa)$ then $O\codewin C_{O,P}(\Sigma\mathbb{R}^\kappa,\vec{0})$.
-%\end{theorem}
-%
-%\begin{proof}
-%We begin by comparing
-%    \begin{itemize}
-%    \item $N\in[\kappa]^{<\omega}$ with the open set $\prod_{\alpha < \kappa} U_\alpha$ in $\Sigma2^\kappa$ where $U_\alpha=\{0\}$ for $\alpha\in N$ and $U_\alpha=\{0,1\}$ otherwise.
-%    \item $W\in[\kappa]^{\leq\omega}$ with the point $p\in\Sigma2^\kappa$ defined by $p(\alpha)=1$ for all $\alpha \in W$ and $p(\alpha)=0$ otherwise.
-%    \end{itemize}
-%
-%So if $\sigma$ is a winning coding strategy for $F$ in $Cov_{F,C}^{**}(\kappa)$, we may define $\tau$ to be a corresponding (perfect- or limited-information) winning strategy for $O$ in $C_{O,P}(\Sigma2^\kappa,\vec{0})$ by making the above conversions from finite sets played by $F$ to countable sets played by $C$ to the open sets which may be played by $O$ and points which may be played by $P$.
-As the legal moves for $C$ correspond to the legal moves for $P$, and as $\sigma$ covers any play by $C$, $\tau$ forces any nonzero coordinate found in a move by $P$ to eventually constrained to $0$.
-%
-%For the game $C_{O,P}(\Sigma\mathbb{R}^\kappa,\vec{0})$ we must instead use open sets of the form $\prod_{\alpha < \kappa} U_\alpha$ where $U_\alpha=(-1/i,1/i)$ for $\alpha\in N$ and $i$ being the turn number (with $U_\alpha=\mathbb{R}$ for $\alpha\not\in N$).
-(The turn number is easily encoded and decoded by $O$ by inspecting the non-$\mathbb{R}$ coordinates of her previous move) and associating points $p\in\Sigma\mathbb{R}^\kappa$ with $q\in\Sigma2^\kappa$ by $q(\alpha)=0$ when $|p(\alpha)|<1$ and $q(\alpha)=1$ otherwise.
-%\end{proof}
-
-\end{document}

### 2014-08-25 phd/dissertation/_raw_chapter6.tex
Name and camelCase based game commands/definitions

--- 2013-10-28 phd/menger.tex
@@
-\input{../header.tex}
-
-\begin{document}
-
-  \centerline{Menger}
-
-  \begin{definition}
+%!TEX root = dissertation.tex
+% ^ leave for LaTeXTools build functionality
+
+\chapter{Menger Game}
+
+Results pertaining to the Menger game characterizing the Menger property.
+
+\section{cut-and-paste}
+
+  \begin{defn}
     $X$ is \textbf{Menger} if for all open covers $\mathcal{U}_0,\mathcal{U}_1,\dots$ there exist finite subcollections $\mathcal{F}_n \subseteq \mathcal{U}_n$ such that $\bigcup_{n<\omega} \mathcal{F}_n$ is a cover of $X$.
-  \end{definition}
-
-  \begin{proposition}
+  \end{defn}
+
+  \begin{prop}
     $\sigma$-compact $\Rightarrow$ Menger $\Rightarrow$ Lindelof
-  \end{proposition}
-
-  \begin{definition}
-    In the two-player game $\mengame{X}$ player $C$ chooses open covers $\mathcal{U}_n$ of $X$, followed by player $F$ choosing a finite subcollection $\mathcal{F}_n\subseteq\mathcal{U}_n$.
+  \end{prop}
+
+  \begin{defn}
+    In the two-player game $\menGame{X}$ player $C$ chooses open covers $\mathcal{U}_n$ of $X$, followed by player $F$ choosing a finite subcollection $\mathcal{F}_n\subseteq\mathcal{U}_n$.
 $F$ wins if $\bigcup_{n<\omega} \mathcal{F}_n$ is a cover of $X$.
-  \end{definition}
-
-  \begin{theorem}
-    $X$ is Menger if and only if $C \not\win \mengame{X}$.
-  \end{theorem}
+  \end{defn}
+
+  \begin{thm}
+    $X$ is Menger if and only if $C \not\win \menGame{X}$.
+  \end{thm}
 
@@
 Then there would exist open covers $\mathcal{U}_0,\mathcal{U}_1,\dots$ of $X$ such that for any choice of finite subcollections $\mathcal{F}_n\subseteq\mathcal{U}_n$, $\bigcup_{n<\omega} \mathcal{F}_n$ isn't a cover of $X$.
-Thus $C\prewin\mengame{X} \Rightarrow S \not\win\mengame{X}$.
-
-    Now, assume $X$ is Menger, and consider a strategy for $C$ in $\mengame{X}$.
+Thus $C\prewin\menGame{X} \Rightarrow S \not\win\menGame{X}$.
+
+    Now, assume $X$ is Menger, and consider a strategy for $C$ in $\menGame{X}$.
 
@@
 
-  \begin{proposition}
-    $X$ is compact if and only if $F \tactwin \mengame{X}$ if and only if $F \ktactwin{k} \mengame{X}$
-  \end{proposition}
+  \begin{prop}
+    $X$ is compact if and only if $F \tactwin \menGame{X}$ if and only if $F \ktactwin{k} \menGame{X}$
+  \end{prop}
 
@@
 
-  \begin{proposition}
-    If $X$ is $\sigma$-compact then $F \markwin \mengame{X}$
-  \end{proposition}
+  \begin{prop}
+    If $X$ is $\sigma$-compact then $F \markwin \menGame{X}$
+  \end{prop}
 
@@
 
-  \begin{theorem}
-  For any topological space $X$ and all $k \geq 2$, $F \kmarkwin{k} \mengame{X}$ if and only if $F \kmarkwin{2} \mengame{X}$.
-  \end{theorem}
+  \begin{thm}
+  For any topological space $X$ and all $k \geq 2$, $F \kmarkwin{k} \menGame{X}$ if and only if $F \kmarkwin{2} \menGame{X}$.
+  \end{thm}
 
@@
 
-  \begin{example}
-    $F \win \mengame{\oneptlind{\omega_1}}$ but $F \not\markwin \mengame{\oneptlind{\omega_1}}$.
-  \end{example}
+  \begin{ex}
+    $F \win \menGame{\oneptlind{\omega_1}}$ but $F \not\markwin \menGame{\oneptlind{\omega_1}}$.
+  \end{ex}
 
@@
 
-  % \begin{definition}
-  %   A space $X$ is $H$-closed if for every open cover of $X$, there exists a finite subset of the cover whose union is dense in $X$.
-  % \end{definition}
-
-  % \begin{proposition}
-  %   For regular spaces, $X$ is $H$-closed if and only if $X$ is compact.
-  % \end{proposition}
-
-  % \begin{proof}
-  %   The backward implication is trivial, so let $X$ be $H$-closed.
-For any open cover $\mc U$ of $X$ and point $x\in X$, choose $x\in V_x\subseteq \cl{V_x}\subseteq U_x\in \mc U$.
-Then if $\mc F = \{V_{x_i}:i<n\}$ is a finite subset of $\mc V=\{V_x:x\in X\}$ with dense union in $X$, then $\mc G = \{U_{x_i}:i<n\}\subseteq \mc U$ is a finite subcover of $X$.
-  % \end{proof}
-
-  \begin{definition}
+  \begin{defn}
     A set $R\subseteq X$ is relatively compact to the topological space $X$ if for every open cover of the entire space $X$, there is a finite subcover of the set $R$.
-  \end{definition}
-
-  \begin{proposition}
+  \end{defn}
+
+  \begin{prop}
     If $X$ is regular, then $Y$ is relatively compact if and only if $\cl{Y}$ is compact.
-  \end{proposition}
+  \end{prop}
 
@@
 
-  \begin{lemma}
-    Let $\sigma(\mc{U}, n)$ be a winning Markov strategy for $F$ in $\mengame{X}$, and $\mathfrak{C}$ collect all open covers of $X$. Then for
+  \begin{lem}
+    Let $\sigma(\mc{U}, n)$ be a winning Markov strategy for $F$ in $\menGame{X}$, and $\mathfrak{C}$ collect all open covers of $X$. Then for
       \[
@@
 
-  \begin{corollary}
-    A space $X$ is $\sigma$-(relatively compact) if and only if $F \markwin \mengame{X}$.
-  \end{corollary}
-
-  \begin{corollary}
+  \begin{cor}
+    A space $X$ is $\sigma$-(relatively compact) if and only if $F \markwin \menGame{X}$.
+  \end{cor}
+
+  \begin{cor}
     For regular spaces $X$, the following are equivalent:
@@
         \item $X$ is $\sigma$-(relatively compact)
-        \item $F \markwin \mengame{X}$
+        \item $F \markwin \menGame{X}$
       \end{enumerate}
-  \end{corollary}
-
-  \begin{theorem}
+  \end{cor}
+
+  \begin{thm}
     For second-countable $X$, the following are equivalent:
@@
         \item $X$ is $\sigma$-(relatively compact)
-        \item $F \win \mengame{X}$
-        \item $F\markwin \mengame{X}$
+        \item $F \win \menGame{X}$
+        \item $F\markwin \menGame{X}$
       \end{enumerate}
-  \end{theorem}
+  \end{thm}
 
@@
         \item $X$ is $\sigma$-(relatively compact)
-        \item $F \win \mengame{X}$
-        \item $F \markwin \mengame{X}$
+        \item $F \win \menGame{X}$
+        \item $F \markwin \menGame{X}$
       \end{enumerate}
-  \end{corollary}
-
-  \begin{example}
+  \end{cor}
+
+  \begin{ex}
   Let $R$ be given the topology from example 63 from Counterexamples in Topology, the topology generated by open intervals with countable sets removed.
-This space is a non-regular example where $F \win \mengame{R}$, but $F \not\markwin \mengame{R}$, that is, $R$ is not $\sigma$-(relatively compact).
-  \end{example}
+This space is a non-regular example where $F \win \menGame{R}$, but $F \not\markwin \menGame{R}$, that is, $R$ is not $\sigma$-(relatively compact).
+  \end{ex}
 
@@
 
-  We define a new property ``\scish'' to describe a sufficient condition for $F \kmarkwin{2}\mengame{X}$.
-
-  \begin{definition}
+  We define a new property ``\scish'' to describe a sufficient condition for $F \kmarkwin{2}\menGame{X}$.
+
+  \begin{defn}
     Let $\mc U$ be a cover of $X$. We say $C\subseteq X$ is $\mc U$-compact if there exists a finite subcover of $\mc U$ which covers $C$.
@@
 
-  \begin{theorem}
-    If $X$ is \scish, then $F \kmarkwin{2}\mengame{X}$.
-  \end{theorem}
+  \begin{thm}
+    If $X$ is \scish, then $F \kmarkwin{2}\menGame{X}$.
+  \end{thm}
 
@@
             \[
-              n+1< r_{\mc U_{n+1}}(x)\leq N+1
-            \] 
-            and thus $x\in c(\mc U_{N+1},r_{\mc U_{n+1}}(x))=c(\mc U_{N+1},N+1)$.
+              r_{\mc U_{n+1}}(x)\leq N+1
+            \]
+            and thus $x\in c(\mc U_{N+1},N+1)$.
           \item For some $n \leq N$,
             \[
-              r_{\mc U_{n+1}}(x)< n+1 \leq r_{\mc U_n}(x)< N+1
-            \]
-            and thus $x\in c(\mc U_{n+1},r_{\mc U_{n+1}}(x))\subseteq c(\mc U_{n+1},n+1)$.
-          \item For some $n \leq N$, 
-            \[
-              n+1 \leq r_{\mc U_n}(x)< N+1 < r_{\mc U_{n+1}}(x)
+              r_{\mc U_n}(x)\leq N+1 < r_{\mc U_{n+1}}(x)
             \]
@@
 
-  \begin{corollary}
-    $F\kmarkwin{2}\mengame{\oneptlind{\omega_1}}$
-  \end{corollary}
-
-  \begin{definition} 
+  \begin{cor}
+    $F\kmarkwin{2}\menGame{\oneptlind{\omega_1}}$
+  \end{cor}
+
+  \begin{defn}
     The statement $S(\kappa,\mu,\lambda)$ due to Scheepers is shorthand for the following: there exist injective functions $f_A:A\to\lambda$ for each $A\in[\kappa]^\mu$ such that $f_A\alcomp_\mu f_B$ for all $A,B\in[\kappa]^\mu$.
-  \end{definition}
-
-  \begin{proposition}
+  \end{defn}
+
+  \begin{prop}
     $\neg S(\kappa,\omega,\omega)$ for $\kappa>2^\omega$
-  \end{proposition}
+  \end{prop}
 
@@
 
-  \begin{corollary}
-    $S(\kappa,\omega,\omega)$ implies $F\kmarkwin{2}\mengame{\oneptlind{\kappa}}$.
-  \end{corollary}
-
-  \begin{definition}
+  \begin{cor}
+    $S(\kappa,\omega,\omega)$ implies $F\kmarkwin{2}\menGame{\oneptlind{\kappa}}$.
+  \end{cor}
+
+  \begin{defn}
     A finite partial function $p$ from $A$ to $B$ has a domain which is a finite subset of $A$ and a range which is a finite subset of $B$.
@@
 
-  \begin{proposition}
+  \begin{prop}
     For $A\in[\kappa]^\omega$ and $\alpha\in A$, the sets
@@
 
-  \begin{corollary}
-    For each $\kappa$, $F\kmarkwin{2}\mengame{\oneptlind{\kappa}}$ is consistent with ZFC.
-  \end{corollary}
+  \begin{cor}
+    For each $\kappa$, $F\kmarkwin{2}\menGame{\oneptlind{\kappa}}$ is consistent with ZFC.
+  \end{cor}
 
@@
 
+  \centerline{Alster, Hurewicz}
+
+  Besides various limited information characterizations of $\menGame{X}$, there are other interesting covering properties between $\sigma$-(relatively compact) and Menger.
+
+  \begin{defn}
+    A colleciton of subsets of a space $X$ is (\textbf{really}) \textbf{ample} if has a finite subcover for each (relatively) compact subset of $X$.
+  \end{defn}
+
+  \begin{prop}
+    Every ample cover of a regular space $X$ is really ample.
+  \end{prop}
+
+  \begin{proof}
+    Every relatively compact set $R$ is a subset of the compact set $\overline{R}$.
+  \end{proof}
+
+  \begin{defn}
+    A space $X$ is (\textbf{relatively}) \textbf{Alster} if there exists a countable subcover for each (really) ample cover of $X$ by $G_\delta$ sets.
+  \end{defn}
+
+  \begin{prop}
+    Every regular relatively Alster space is Alster.
+  \end{prop}
+
+  \begin{thm}
+    $X$ $\sigma$-compact $\Rightarrow$ $X$ Alster $\Rightarrow$ $X$ Menger
+  \end{thm}
+
+  \begin{proof}
+    Due to Leandro F. Aurichi and Franklin D. Tall in ``Lindel\"of spaces which are indestructible, productive, or D''.
+  \end{proof}
+
+  \begin{prop}
+    $X$ $\sigma$-(relatively compact) $\Rightarrow$ $X$ relatively Alster $\Rightarrow$ $X$ Menger
+  \end{prop}
+
+  \begin{proof}
+    If $X$ is $\sigma$-(relatively compact), then there exists a countable subcover for every really ample cover of $X$ by arbitrary sets.
+
+    If $X$ is relatively Alster, we adapt Aurichi and Tall's argument for the previous theorem.
+
+    Since relatively Alster implies Lindel\"of (all open covers of $X$ are relatively ample by definition of relatively compact), it is sufficient to consider open covers $\mc U_n = \{ U_n^m : m<\omega\}$ such that $U_n^m\subseteq U_n^{m+1}$.
+Then $\mc G=\{\bigcap_{n<\omega} U_n^{f(n)} : f\in \omega^\omega\}$ is a $G_\delta$ cover.
+To see that $\mc G$ is relatively ample, note for each relatively compact $K$ in $X$, $K$ is covered by something in each $\mc U_n$, and thus there is $f_K(n)\in\omega^\omega$ such that $K\subseteq \bigcap_{n<\omega} U_n^{f_K(n)}$.
+
+    By relatively Alster, let $f_m\in\omega^\omega$ for $m<\omega$ so that $\mc G'=\{\bigcap_{n<\omega} U_n^{f_m(n)}:m<\omega\}$ covers $X$.
+
+    Then let $\mc F_n = \{U_n^{f_m(n)}:m\leq n\}\in[\mc U_n]^{<\omega}$.
+Note that if $x\in X$, then $x\in \bigcap_{n<\omega} U_n^{f_{m_x}(n)}$ for some $m_x<\omega$ as $\mc G'$ is a cover.
+Thus $x\in U_{m_x}^{f_{m_x}(m_x)}$ and is covered by $\mc F_{m_x}$.
+  \end{proof}
+
+  \begin{ex}
+    Let the real numbers $R$ be given the topology generated by open intervals with countable sets removed.
+$R$ is not relatively Alster and $F\win\menGame{R}$.
+If $S(2^\omega,\omega,\omega)$ holds, then $F\kmarkwin{2}\menGame{R}$.
+  \end{ex}
+
+  \begin{proof}
+    Since points are $G_\delta$ and its relatively compact sets are all finite, a cover by singletons is really ample and has no countable subcover, showing $R$ is not relatively Alster.
+
+    It was proven earlier that $F\win\menGame{R}$. Assuming $S(2^\omega,\omega,\omega)$, we construct a $2$-Mark\"ov strategy by first defining the following:
+      \begin{itemize}
+        \item Let $z_n$ enumerate the integers for $n<\omega$.
+        \item For each open cover $\mc V$ of $R$, let $A(\mc V)$ be a countable set such that $[z_n,z_n+1)\setminus A(V)$ is $\mc V$-compact for each $n<\omega$.
+        \item Let $f_A:A\to\omega$ for $A\subseteq R$ witness $S(2^\omega,\omega,\omega)$.
+      \end{itemize}
+
+    Then we may define $\sigma(\mc U_0,0)=\emptyset$ and define $\sigma(\mc U_n,\mc U_{n+1},n+1)$ such that it covers each of the following:
+      \[
+        \left(\bigcup_{m\leq n} [z_m,z_m+1)\right) \setminus A(\mc U_{n+1})
+      \]
+      \[
+        \{f_{A(\mc U_{n+1})}^{-1}(m) : m\leq n\}
+      \]
+      \[
+        \{x \in A(\mc U_n)\cap A(\mc U_{n+1}) : f_{A(\mc U_{n})}(x)\not= f_{A(\mc U_{n+1})}(x)\}
+      \]
+
+    For any attack $\mc U_0,\mc U_1,\dots$ on $\sigma$, let $x\in[z_n,z_n+1)$.
+      \begin{itemize}
+        \item If $x\not\in A(\mc U_{n+1})$, then $x$ is covered in round $n+1$.
+        \item If $x\in A(\mc U_{n+1})$, let $N=f_{A(\mc U_{n+1})}(x)$.
+        \begin{itemize}
+          \item If $N\leq n$, then $x$ is covered in round $n+1$.
+          \item If $N>n$ and $N=f_{A(\mc U_{p+1})}(x)$ for all $p\geq n$, then $x$ is covered in round $N$.
+          \item If $N>n$ and $N\not=f_{A(\mc U_{p+1})}(x)$ for some $p>n$, then $x$ is covered in round $p+1$.
+        \end{itemize}
+      \end{itemize}
+  \end{proof}
+
+  \begin{defn}
+    A space $X$ is \textbf{Hurewicz} if for each sequence of open covers $\mc U_n$, there are $\mc F_n \in [\mc U_n]^{<\omega}$ such that $X=\bigcup_{m<\omega}\bigcap_{m\leq n<\omega}\cup\mc F_n$.
+  \end{defn}
+
+\newpage
+
   \centerline{Filling Games}
 
-  \begin{definition}
-    The \textbf{filling game} $\fillgame{J}$ on an ideal $J$ proceeds as follows: player $M$ chooses $M_0 \in \<J\>$, the $\sigma$-completion of $J$, in the initial round, followed by $N$ choosing $N_0\in J$.
+  \begin{defn}
+    The \textbf{filling game} $\cloFillGame{J}$ on an ideal $J$ proceeds as follows: player $M$ chooses $M_0 \in \<J\>$, the $\sigma$-completion of $J$, in the initial round, followed by $N$ choosing $N_0\in J$.
 In round $n+1$, player $M$ chooses $M_{n+1}$ where $M_n\subseteq M_{n+1}\in\<J\>$, and player $N$ replies with $N_{n+1}\in J$.
@@
     The \textbf{strict filling game} $\sfillgame{J}$ proceeds analogously, with the added requirement that $M_n\subsetneq M_{n+1}$. This game has been studied by Scheepers.
-  \end{definition}
-
-  \begin{theorem}
-    $N\ktactwin{2}\sfillgame{J} \Rightarrow N\kmarkwin{2}\fillgame{J}$
-  \end{theorem}
+  \end{defn}
+
+  \begin{thm}
+    $N\ktactwin{2}\sfillgame{J} \Rightarrow N\kmarkwin{2}\cloFillGame{J}$
+  \end{thm}
 
@@
 
-    We define a $2$-Markov strategy $\tau$ for $F$ in $\fillgame{\kappa}$ as follows:
+    We define a $2$-Markov strategy $\tau$ for $F$ in $\cloFillGame{\kappa}$ as follows:
 
@@
 
-  \begin{example}
-    There is a free ideal $J$ such that $N\not\ktactwin{2}\sfillgame{J}$ but $N\kmarkwin{2}\fillgame{J}$.
-  \end{example}
+  \begin{ex}
+    There is a free ideal $J$ such that $N\not\ktactwin{2}\sfillgame{J}$ but $N\kmarkwin{2}\cloFillGame{J}$.
+  \end{ex}
 
@@
 
-    Certainly, if $J$ is the collection of nowhere dense subsets of $A\cup V$, then $F\kmarkwin{2}\fillgame{J}$. In fact, since $A\cup V$ is meager, $F\prewin\fillgame{J}$.
+    Certainly, if $J$ is the collection of nowhere dense subsets of $A\cup V$, then $F\kmarkwin{2}\cloFillGame{J}$. In fact, since $A\cup V$ is meager, $F\prewin\cloFillGame{J}$.
 
@@
 
-  \begin{definition}
+  \begin{defn}
     $X$ is \textbf{Rothberger} if for all open covers $\mathcal{U}_0,\mathcal{U}_1,\dots$ there exist open sets $U_n\in \mathcal{U}_n$ such that $\{U_n:n<\omega\}$ is a cover of $X$.
-  \end{definition}
-
-  \begin{proposition}
+  \end{defn}
+
+  \begin{prop}
     Rothberger $\Rightarrow$ Menger
-  \end{proposition}
-
-  \begin{definition}
-    In the two-player game $\rothgame{X}$ player $C$ chooses open covers $\mathcal{U}_n$ of $X$, followed by player $S$ choosing an open set $U_n\in\mathcal{U}_n$.
+  \end{prop}
+
+  \begin{defn}
+    In the two-player game $\rothGame{X}$ player $C$ chooses open covers $\mathcal{U}_n$ of $X$, followed by player $S$ choosing an open set $U_n\in\mathcal{U}_n$.
 $S$ wins if $\{U_n:n<\omega\}$ is a cover of $X$.
-  \end{definition}
-
-  \begin{theorem}
-    $X$ is Rothberger if and only if $C\not\win\rothgame{X}$.
-  \end{theorem}
+  \end{defn}
+
+  \begin{thm}
+    $X$ is Rothberger if and only if $C\not\win\rothGame{X}$.
+  \end{thm}
 
@@
         \item $X$ is scattered
-        \item $S\win\rothgame{X}$
-        \item $C\not\win\rothgame{X}$
+        \item $S\win\rothGame{X}$
+        \item $C\not\win\rothGame{X}$
       \end{enumerate}
-  \end{theorem}
+  \end{thm}
 
@@
 
-  \begin{definition}
-    In the two-player game $\altrothgame{X}$ player $P$ chooses points $x_n\in X$, followed by player $O$ choosing an open neighborhood $U_n$ of $x_n$.
+  \begin{defn}
+    In the two-player game $\rothAltGame{X}$ player $P$ chooses points $x_n\in X$, followed by player $O$ choosing an open neighborhood $U_n$ of $x_n$.
 $P$ wins if $\{U_n:n<\omega\}$ is a cover of $X$.
-  \end{definition}
-
-  \begin{theorem} $\altrothgame{X}$ is ``perfect information equivalent'' to $\rothgame{X}$. That is:
-
-    \begin{itemize}
-      \item $P\win\altrothgame{X}$ if and only if $S\win\rothgame{X}$
-      \item $O\win\altrothgame{X}$ if and only if $C\win\rothgame{X}$.
-    \end{itemize}
-  \end{theorem}
+  \end{defn}
+
+  \begin{thm} $\rothAltGame{X}$ is ``perfect information equivalent'' to $\rothGame{X}$. That is:
+
+    \begin{itemize}
+      \item $P\win\rothAltGame{X}$ if and only if $S\win\rothGame{X}$
+      \item $O\win\rothAltGame{X}$ if and only if $C\win\rothGame{X}$.
+    \end{itemize}
+  \end{thm}
 
@@
       \item
-      Let $\sigma$ be a strategy for $S$ in $\rothgame{X}$.
+      Let $\sigma$ be a strategy for $S$ in $\rothGame{X}$.
 
@@
 
-      We define a strategy for $P$ in $\altrothgame{X}$ as follows: during round $n$, $P$ chooses a point $x_n$ for which every open neighborhood is of the form $U_n = \sigma(\mc U_0,\dots,\mc U_{n-1},\mc{U}_n)$ for some open cover $\mc{U}_0$.
-
-      If $\sigma$ was a winning strategy for $S$ in $\rothgame{X}$, then the open sets chosen by $O$ in response to $P$'s strategy for $\altrothgame{X}$ are of the form $\{\sigma(\mc U_0),\sigma(\mc U_0,\mc U_1),\dots\}$ and are an open cover of $X$.
-
-      \item
-      Let $\sigma$ be a strategy for $P$ in $\altrothgame{X}$.
-
-      We define a strategy for $S$ in $\rothgame{X}$ as follows: during round $n$, if $S$ has chosen $U_0,\dots,U_{n-1}$ in previous rounds, $S$ chooses any open set in $C$'s latest cover containing the point $\sigma(U_0,\dots,U_{n-1})$.
+      We define a strategy for $P$ in $\rothAltGame{X}$ as follows: during round $n$, $P$ chooses a point $x_n$ for which every open neighborhood is of the form $U_n = \sigma(\mc U_0,\dots,\mc U_{n-1},\mc{U}_n)$ for some open cover $\mc{U}_0$.
+
+      If $\sigma$ was a winning strategy for $S$ in $\rothGame{X}$, then the open sets chosen by $O$ in response to $P$'s strategy for $\rothAltGame{X}$ are of the form $\{\sigma(\mc U_0),\sigma(\mc U_0,\mc U_1),\dots\}$ and are an open cover of $X$.
+
+      \item
+      Let $\sigma$ be a strategy for $P$ in $\rothAltGame{X}$.
+
+      We define a strategy for $S$ in $\rothGame{X}$ as follows: during round $n$, if $S$ has chosen $U_0,\dots,U_{n-1}$ in previous rounds, $S$ chooses any open set in $C$'s latest cover containing the point $\sigma(U_0,\dots,U_{n-1})$.
 If $\sigma$ was a winning strategy for $P$, then for any open sets $U_0,U_1,\dots$ containing $\sigma(\cdot),\sigma(U_0),\dots$, the collection $\{U_0,U_1,\dots\}$ is a cover for $X$.
@@
       \item
-      Let $\sigma$ be a strategy for $C$ in $\rothgame{X}$.
-
-      We define a strategy for $O$ in $\altrothgame{X}$ as follows: during round $n$, if $O$ has chosen $U_0,\dots,U_{n-1}$ in previous rounds, $O$ chooses an open set from the cover $\sigma(U_0,\dots,U_{n-1})$ containing the point chosen by $P$ that round.
+      Let $\sigma$ be a strategy for $C$ in $\rothGame{X}$.
+
+      We define a strategy for $O$ in $\rothAltGame{X}$ as follows: during round $n$, if $O$ has chosen $U_0,\dots,U_{n-1}$ in previous rounds, $O$ chooses an open set from the cover $\sigma(U_0,\dots,U_{n-1})$ containing the point chosen by $P$ that round.
 If $\sigma$ was a winning strategy for $C$, then for any open sets $U_0,U_1,\dots$ from the covers $\sigma(\cdot),\sigma(U_0),\dots$, the collection $\{U_0,U_1,\dots\}$ is not a cover for $X$.
@@
       \item
-      Let $\sigma$ be a strategy for $O$ in $\altrothgame{X}$.
-
-      We define a strategy for $C$ in $\rothgame{X}$ as follows: during round $0$, $C$ chooses $\mc{U}_0 = \{\sigma(x) : x\in X\}$.
+      Let $\sigma$ be a strategy for $O$ in $\rothAltGame{X}$.
+
+      We define a strategy for $C$ in $\rothGame{X}$ as follows: during round $0$, $C$ chooses $\mc{U}_0 = \{\sigma(x) : x\in X\}$.
 In response, $S$ chooses some $\sigma(x_0)$.
@@
 
-  \begin{theorem}
-    \begin{itemize}
-      \item $P\prewin\altrothgame{X}$ if and only if $S\markwin\rothgame{X}$
-      \item $O\markwin\altrothgame{X}$ if and only if $C\prewin\rothgame{X}$.
-    \end{itemize}
-  \end{theorem}
-
-  \begin{proof}
-
-    \begin{itemize}
-      \item
-      Let $\sigma(\mc U_n,n)$ be a Markov strategy for $S$ in $\rothgame{X}$.
+  \begin{thm}
+    \begin{itemize}
+      \item $P\prewin\rothAltGame{X}$ if and only if $S\markwin\rothGame{X}$
+      \item $O\markwin\rothAltGame{X}$ if and only if $C\prewin\rothGame{X}$.
+    \end{itemize}
+  \end{thm}
+
+  \begin{proof}
+
+    \begin{itemize}
+      \item
+      Let $\sigma(\mc U_n,n)$ be a Markov strategy for $S$ in $\rothGame{X}$.
 
@@
 
-      We define a predetermined strategy for $P$ in $\altrothgame{X}$ as follows: during round $n$, $P$ chooses a point $x_n$ for which every open neighborhood is of the form $U_n = \sigma(\mc U,n)$ for some open cover $\mc{U}$.
-
-      If $\sigma$ was a winning strategy for $S$ in $\rothgame{X}$, then the open sets chosen by $O$ in response to $P$'s strategy for $\altrothgame{X}$ are of the form $\{\sigma(\mc U_0,0),\sigma(\mc U_1,1),\dots\}$ and are an open cover of $X$.
-
-      \item
-      Let $\sigma(n)$ be a predetermined strategy for $P$ in $\altrothgame{X}$.
-
-      We define a Markov strategy for $S$ in $\rothgame{X}$ as follows: during round $n$, $S$ chooses any open set in $C$'s cover containing the point $\sigma(n)$.
+      We define a predetermined strategy for $P$ in $\rothAltGame{X}$ as follows: during round $n$, $P$ chooses a point $x_n$ for which every open neighborhood is of the form $U_n = \sigma(\mc U,n)$ for some open cover $\mc{U}$.
+
+      If $\sigma$ was a winning strategy for $S$ in $\rothGame{X}$, then the open sets chosen by $O$ in response to $P$'s strategy for $\rothAltGame{X}$ are of the form $\{\sigma(\mc U_0,0),\sigma(\mc U_1,1),\dots\}$ and are an open cover of $X$.
+
+      \item
+      Let $\sigma(n)$ be a predetermined strategy for $P$ in $\rothAltGame{X}$.
+
+      We define a Markov strategy for $S$ in $\rothGame{X}$ as follows: during round $n$, $S$ chooses any open set in $C$'s cover containing the point $\sigma(n)$.
 If $\sigma$ was a winning strategy for $P$, then for any open sets $U_0,U_1,\dots$ containing $\sigma(0),\sigma(1),\dots$, the collection $\{U_0,U_1,\dots\}$ is a cover for $X$.
@@
       \item
-      Let $\sigma(n)$ be a predetermined strategy for $C$ in $\rothgame{X}$.
-
-      We define a Markov strategy for $O$ in $\altrothgame{X}$ as follows: during round $n$, $O$ chooses an open set from the cover $\sigma(n)$ containing the point chosen by $P$ that round.
+      Let $\sigma(n)$ be a predetermined strategy for $C$ in $\rothGame{X}$.
+
+      We define a Markov strategy for $O$ in $\rothAltGame{X}$ as follows: during round $n$, $O$ chooses an open set from the cover $\sigma(n)$ containing the point chosen by $P$ that round.
 If $\sigma$ was a winning strategy for $C$, then for any open sets $U_0,U_1,\dots$ from the covers $\sigma(0),\sigma(1),\dots$, the collection $\{U_0,U_1,\dots\}$ is not a cover for $X$.
@@
       \item
-      Let $\sigma(x_n,n)$ be a Markov strategy for $O$ in $\altrothgame{X}$.
-
-      We define a predetermined strategy for $C$ in $\rothgame{X}$ as follows: during round $n$, $C$ chooses $\mc{U}_n = \{\sigma(x,n) : x\in X\}$.
+      Let $\sigma(x_n,n)$ be a Markov strategy for $O$ in $\rothAltGame{X}$.
+
+      We define a predetermined strategy for $C$ in $\rothGame{X}$ as follows: during round $n$, $C$ chooses $\mc{U}_n = \{\sigma(x,n) : x\in X\}$.
 If $\sigma$ was a winning strategy for $O$, we observe any play $\{\sigma(x_0,0),\sigma(x_1,1),\dots\}$ by $S$ is not a cover for $X$.
@@
 
-  \begin{definition}
+  \begin{defn}
     Let $\mc{N}(x)$ be the $\textbf{neighborhood network}$ of $x$, that is, the collection of all neighborhoods of $x$.
-  \end{definition}
-
-  \begin{definition}
+  \end{defn}
+
+  \begin{defn}
     A topological space $X$ is \textbf{almost countable} if there exist $x_n\in X$ for each $n<\omega$ such that $X=\bigcup_{n<\omega}\bigcap\mc{N}(x_n)$.
-  \end{definition}
-
-  \begin{theorem}
+  \end{defn}
+
+  \begin{thm}
     For any space $X$, the following are equivalent:
     \begin{itemize}
-      \item $S\markwin\rothgame{X}$ 
-      \item $P\prewin\altrothgame{X}$
+      \item $S\markwin\rothGame{X}$
+      \item $P\prewin\rothAltGame{X}$
       \item $X$ is almost countable
     \end{itemize}
-  \end{theorem}
-
-  \begin{proof}
-    If there exist $x_n\in X$ for each $n<\omega$ such that $X=\bigcup_{n<\omega}\bigcap\mc{N}(x_n)$, then let $\sigma(n)=x_n$ be a predetermined strategy for $P$ in $\altrothgame{X}$.
+  \end{thm}
+
+  \begin{proof}
+    If there exist $x_n\in X$ for each $n<\omega$ such that $X=\bigcup_{n<\omega}\bigcap\mc{N}(x_n)$, then let $\sigma(n)=x_n$ be a predetermined strategy for $P$ in $\rothAltGame{X}$.
 For any neighborhoods $O_n$ of $x_n$ chosen by $O$ to attack $\sigma$, note that $\bigcup_{n<\omega}O_n\supseteq\bigcup_{n<\omega}\bigcap\mc{N}(x_n)=X$ results in a win for $P$.
@@
 
-  \begin{theorem}
+  \begin{thm}
     For any $T_1$ space $X$, the following are equivalent:
     \begin{itemize}
-      \item $S\markwin\rothgame{X}$
-      \item $P\prewin\altrothgame{X}$
+      \item $S\markwin\rothGame{X}$
+      \item $P\prewin\rothAltGame{X}$
       \item $X$ is almost countable
@@
 
-  \begin{example}
+  \begin{ex}
     Let $X=\omega_1\cup\{\infty\}$ be a ``weak Lindel\"ofication'' of discrete $\omega_1$ such that open neighborhoods of $\infty$ contain $\omega_1\setminus\omega$.
-This space is $T_0$ but not $T_1$, and note that $S\markwin\rothgame{X}$ and $|X|>\omega$.
-  \end{example}
-
-  \begin{theorem}
+This space is $T_0$ but not $T_1$, and note that $S\markwin\rothGame{X}$ and $|X|>\omega$.
+  \end{ex}
+
+  \begin{thm}
     The following are equivalent for points-$G_\delta$ $X$:
       \begin{enumerate}[(a)]
-        \item $S\win\rothgame{X}$
-        \item $P\win\altrothgame{X}$
-        \item $S\kmarkwin{k}\rothgame{X}$ for some $k\geq 1$
-        \item $S\markwin\rothgame{X}$
-        \item $P\prewin\altrothgame{X}$
+        \item $S\win\rothGame{X}$
+        \item $P\win\rothAltGame{X}$
+        \item $S\kmarkwin{k}\rothGame{X}$ for some $k\geq 1$
+        \item $P\kmarkwin{k}\rothAltGame{X}$ for some $k\geq 1$
+        \item $S\markwin\rothGame{X}$
+        \item $P\prewin\rothAltGame{X}$
         \item $X$ is almost countable
@@
     % $(c)\Rightarrow(b)\Rightarrow(a)$ are all trivial.
-Galvin has shown $(a) \Leftrightarrow P\win\altrothgame{X} \Rightarrow (c)$ in \textit{Indeterminacy}, but a direct proof of $(a)\Rightarrow(c)$ follows.
-
-    Due to Galvin. Let $\sigma$ be a strategy for $S$ in $\rothgame{X}$.
+Galvin has shown $(a) \Leftrightarrow P\win\rothAltGame{X} \Rightarrow (c)$ in \textit{Indeterminacy}, but a direct proof of $(a)\Rightarrow(c)$ follows.
+
+    Due to Galvin. Let $\sigma$ be a strategy for $S$ in $\rothGame{X}$.
 
@@
 
-  \begin{corollary}
+  \begin{cor}
     The following are equivalent for compact points-$G_\delta$ $X$:
       \begin{enumerate}[(a)]
-        \item $S\win\rothgame{X}$
-        \item $P\win\altrothgame{X}$
-        \item $S\kmarkwin{k}\rothgame{X}$ for some $k\geq 1$
-        \item $S\markwin\rothgame{X}$
-        \item $P\prewin\altrothgame{X}$
+        \item $S\win\rothGame{X}$
+        \item $P\win\rothAltGame{X}$
+        \item $S\kmarkwin{k}\rothGame{X}$ for some $k\geq 1$
+        \item $P\kmarkwin{k}\rothAltGame{X}$ for some $k\geq 1$
+        \item $S\markwin\rothGame{X}$
+        \item $P\prewin\rothAltGame{X}$
         \item $X$ is almost countable
         \item $|X|\leq\omega$
-        \item $C\not\win\rothgame{X}$
-        \item $O\not\win\altrothgame{X}$
+        \item $C\not\win\rothGame{X}$
+        \item $O\not\win\rothAltGame{X}$
         \item $X$ is Rothberger
@@
     $S$ wins the game if $\{x_n : n<\omega\}\supseteq F_0\cup\{\infty\}$, and $F$ wins otherwise.
-  \end{definition}
-
-  \begin{proposition}
-    $S\limitwin\rothgame{\oneptlind{\kappa}} \Rightarrow S\limitwin\recallgame{m}{\kappa}$
-  \end{proposition}
-
-  \begin{proof}
-    Let $\sigma$ be a limited information strategy for $S$ in $\rothgame{\oneptlind{\kappa}}$.
+  \end{defn}
+
+  \begin{prop}
+    $S\limitwin\rothGame{\oneptlind{\kappa}} \Rightarrow S\limitwin\recallgame{m}{\kappa}$
+  \end{prop}
+
+  \begin{proof}
+    Let $\sigma$ be a limited information strategy for $S$ in $\rothGame{\oneptlind{\kappa}}$.
 

### 2014-08-25 phd/dissertation/chapter3.tex
Name and camelCase based game commands/definitions

@@
 \begin{game}
-  Let $\congame{X}{S}$ denote the \term{$W$-convergence game} with
+  Let $\gruConGame{X}{S}$ denote the \term{$W$-convergence game} with
   players $\pl O$, $\pl P$, for a topological space $X$ and $S\subseteq X$.
@@
 
-  If $S=\{x\}$ then we write $\congame{X}{x}$ for short.
+  If $S=\{x\}$ then we write $\gruConGame{X}{x}$ for short.
 \end{game}
@@
 \begin{defn}
-  The spaces $X$ for which $\pl O \win \congame{X}{x}$ for all $x\in X$ are
+  The spaces $X$ for which $\pl O \win \gruConGame{X}{x}$ for all $x\in X$ are
   called \term{$W$-spaces}.
@@
     if and only if
-  $\pl O \prewin \congame{X}{x}$ for all $x\in X$.
+  $\pl O \prewin \gruConGame{X}{x}$ for all $x\in X$.
 \end{prop}
@@
   If $X$ is not first countable at some $x$, let $\sigma$ be a
-  predetermined strategy for $\pl O$ in $\congame{X}{x}$. There exists
+  predetermined strategy for $\pl O$ in $\gruConGame{X}{x}$. There exists
   an open neighborhood $U$ of $x$ which does not contain any
@@
 
-At first glance, the difficulty of $\congame{X}{S}$ could be increased for
+At first glance, the difficulty of $\gruConGame{X}{S}$ could be increased for
 $\pl O$ by only restricting the choices for $\pl P$ to be within the most
@@
 \begin{defn}
-  Let $\congamehard{X}{S}$ denote the \term{hard $W$-convergence game} which
-  proceeds as $\congame{X}{S}$, except that $\pl P$ need only choose
+  Let $\gruConGameHard{X}{S}$ denote the \term{hard $W$-convergence game} which
+  proceeds as $\gruConGame{X}{S}$, except that $\pl P$ need only choose
   $x_n\in O_n$ rather than $x_n\in \bigcap_{m\leq n}O_m$ during each round.
@@
 \begin{prop}\label{propNormalHardCon}
-  $\pl O \limitwin \congame{X}{S}$
+  $\pl O \limitwin \gruConGame{X}{S}$
     if and only if
-  $\pl O \limitwin \congamehard{X}{S}$,
+  $\pl O \limitwin \gruConGameHard{X}{S}$,
   where $\limitwin$ is either $\win$ or $\prewin$.
@@
 \begin{game}
-  Let $\clusgame{X}{S}$ ($\clusgamehard{X}{S}$) be a variation of
-  $\congame{X}{S}$ ($\congamehard{X}{S}$) such that $x_n$ need only
+  Let $\gruClusGame{X}{S}$ ($\gruClusGameHard{X}{S}$) be a variation of
+  $\gruConGame{X}{S}$ ($\gruConGameHard{X}{S}$) such that $x_n$ need only
   cluster at $S$, that is, for every open neighborhood $U$ of $S$, $x_n\in U$
@@
 \begin{prop}
-  $\pl O \limitwin \congame{X}{S}$
+  $\pl O \limitwin \gruConGame{X}{S}$
     if and only if
-  $\pl O \limitwin \clusgame{X}{S}$
+  $\pl O \limitwin \gruClusGame{X}{S}$
   where $\limitwin$ is any of $\win$, $\prewin$, $\tactwin$, or $\markwin$.
@@
   winning predetermined (resp. tactical) strategy for $\pl O$ in
-  $\clusgame{X}{S}$. Let $p$ be a legal attack against $\sigma$, and $q$ be a
+  $\gruClusGame{X}{S}$. Let $p$ be a legal attack against $\sigma$, and $q$ be a
   subsequence of $p$. It's easily seen that $q$ is also a legal attack against
@@
   at $S$, $p$ converges to $S$, and $\sigma$ is a winning predetermined
-  (resp. tactical) strategy for $\pl O$ in $\congame{X}{S}$ as well.
+  (resp. tactical) strategy for $\pl O$ in $\gruConGame{X}{S}$ as well.
 
@@
   So, suppose that $\sigma$ is a winning Markov strategy for $\pl O$ in
-  $\clusgame{X}{S}$ such that $\sigma(x,m)\supseteq\sigma(x,n)$ for all
+  $\gruClusGame{X}{S}$ such that $\sigma(x,m)\supseteq\sigma(x,n)$ for all
   $m\leq n$.
@@
   at $S$, $p$ must converge to $S$. Thus $\sigma$ is also a winning Markov
-  strategy for $\pl O$ in $\congame{X}{S}$ as well.
+  strategy for $\pl O$ in $\gruConGame{X}{S}$ as well.
 \end{proof}
@@
 \begin{ques}
-  Does $\pl O \ktactwin{2} \clusgame{X}{S}$ imply
-  $\pl O \ktactwin{2} \congame{X}{S}$? What about for $\kmarkwin{2}$?
+  Does $\pl O \ktactwin{2} \gruClusGame{X}{S}$ imply
+  $\pl O \ktactwin{2} \gruConGame{X}{S}$? What about for $\kmarkwin{2}$?
 \end{ques}
@@
 \begin{ques}
-  Could $\pl O \ktactwin{k+1} \congame{X}{S}$ actually imply
-  $\pl O \tactwin \congame{X}{S}$? What about for $\clusgame{X}{S}$?
+  Could $\pl O \ktactwin{k+1} \gruConGame{X}{S}$ actually imply
+  $\pl O \tactwin \gruConGame{X}{S}$? What about for $\gruClusGame{X}{S}$?
 \end{ques}
@@
 \begin{prop}\label{propFortTact}
-  $\pl O \tactwin \congame{\oneptcomp\kappa}{\infty}$ for all cardinals $\kappa$
+  $\pl O \tactwin \gruConGame{\oneptcomp\kappa}{\infty}$ for all cardinals $\kappa$
 \end{prop}
@@
 \begin{cor}
-  $\pl O \win \congamehard{\oneptcomp\kappa}{\infty}$ for all cardinals $\kappa$
+  $\pl O \win \gruConGameHard{\oneptcomp\kappa}{\infty}$ for all cardinals $\kappa$
 \end{cor}
@@
 
-Since it's trivial to show that $\pl O\prewin\congame{\oneptcomp\kappa}$ if and
+Since it's trivial to show that $\pl O\prewin\gruConGame{\oneptcomp\kappa}$ if and
 only if $\kappa\leq\omega$, this closes the question on limited information
-strategies for $\congame{\oneptcomp\kappa}{\infty}$. However, limited
-information analysis of the harder $\congamehard{\oneptcomp\kappa}{\infty}$
+strategies for $\gruConGame{\oneptcomp\kappa}{\infty}$. However, limited
+information analysis of the harder $\gruConGameHard{\oneptcomp\kappa}{\infty}$
 is more interesting.
@@
 \begin{thm}
-  $\pl O \not\markwin \congamehard{\oneptcomp\omega_1}{\infty}$.
+  $\pl O \not\markwin \gruConGameHard{\oneptcomp\omega_1}{\infty}$.
 \end{thm}
@@
 \begin{thm}
-  $\pl O \not\kmarkwin{k} \congamehard{\oneptcomp\omega_1}{\infty}$.
+  $\pl O \not\kmarkwin{k} \gruConGameHard{\oneptcomp\omega_1}{\infty}$.
 \end{thm}
@@
 \begin{thm}
-  $\pl O\markwin \clusgamehard{\oneptcomp\omega_1}{\infty}$.
+  $\pl O\markwin \gruClusGameHard{\oneptcomp\omega_1}{\infty}$.
 \end{thm}
@@
 \begin{thm}
-  $O\not\ktactwin{k}\clusgamehard{\oneptcomp\omega_1}{\infty}$.
+  $O\not\ktactwin{k}\gruClusGameHard{\oneptcomp\omega_1}{\infty}$.
 \end{thm}
@@
   Let $\sigma$ be a $k$-tactic for $\pl O$ in
-  $\clusgamehard{\oneptcomp\omega_1}{\infty}$. By the closing-up lemma, the set
+  $\gruClusGameHard{\oneptcomp\omega_1}{\infty}$. By the closing-up lemma, the set
     \[
@@
 \begin{thm}
-  $O\not\kmarkwin{k}\clusgamehard{\oneptcomp\omega_2}{\infty}$.
+  $O\not\kmarkwin{k}\gruClusGameHard{\oneptcomp\omega_2}{\infty}$.
 \end{thm}
@@
   Let $\sigma$ be a $k$-mark for $\pl O$ in
-  $\clusgame{\oneptcomp\omega_2}{\infty}$. By the closing-up lemma, the set
+  $\gruClusGame{\oneptcomp\omega_2}{\infty}$. By the closing-up lemma, the set
     \[
@@
   Suppose $S\subseteq Y\subseteq X$, $\limitwin$ is any of $\win$,
-  $\ktactwin{k}$, or $\kmarkwin{k}$, and $G(X,S)$ is any of $\congame{X}{S}$,
-  $\congamehard{X}{S}$, $\clusgame{X}{S}$, or $\clusgamehard{X}{S}$.
+  $\ktactwin{k}$, or $\kmarkwin{k}$, and $G(X,S)$ is any of $\gruConGame{X}{S}$,
+  $\gruConGameHard{X}{S}$, $\gruClusGame{X}{S}$, or $\gruClusGameHard{X}{S}$.
 
@@
 \begin{cor}
-  $\pl O\not\ktactwin{k}\clusgamehard{\SigmaProdR{\omega_1}}{\vec0}$,
-  $\pl O\not\kmarkwin{k}\congamehard{\SigmaProdR{\omega_1}}{\vec0}$, and
-  $\pl O\not\kmarkwin{k}\clusgamehard{\SigmaProdR{\omega_2}}{\vec0}$.
+  $\pl O\not\ktactwin{k}\gruClusGameHard{\SigmaProdR{\omega_1}}{\vec0}$,
+  $\pl O\not\kmarkwin{k}\gruConGameHard{\SigmaProdR{\omega_1}}{\vec0}$, and
+  $\pl O\not\kmarkwin{k}\gruClusGameHard{\SigmaProdR{\omega_2}}{\vec0}$.
 \end{cor}
@@
 \begin{prop}
-  $\pl O \codewin \congame{\oneptcomp\kappa}{\infty}$.
+  $\pl O \codewin \gruConGame{\oneptcomp\kappa}{\infty}$.
 \end{prop}
@@
 \begin{game}
-  Let $\pfgame\kappa$ denote the \term{point-finite game} with players
+  Let $\cloPFGame\kappa$ denote the \term{point-finite game} with players
   $\pl F$, $\pl C$ for each cardinal $\kappa$.
@@
 \begin{lem}
-  $\pl F \codewin \pfgame\kappa$ implies
-  $\pl O \codewin \congame{\SigmaProdR\kappa}{\vec0}$.
+  $\pl F \codewin \cloPFGame\kappa$ implies
+  $\pl O \codewin \gruConGame{\SigmaProdR\kappa}{\vec0}$.
 \end{lem}
@@
 \begin{proof}
-  Let $\sigma$ be a winning coding strategy for $\pl F$ in $\pfgame\kappa$
+  Let $\sigma$ be a winning coding strategy for $\pl F$ in $\cloPFGame\kappa$
   such that $\sigma(\emptyset)\supset\emptyset$ and $\sigma(F,C)\supset F$.
@@
   We define the coding strategy $\tau$ for $\pl O$ in
-  $\congame{\SigmaProdR\kappa}{\vec0}$ as follows:
+  $\gruConGame{\SigmaProdR\kappa}{\vec0}$ as follows:
   \[
@@
 \begin{thm}
-  $\pl F \codewin \pfgame{\kappa}$ for all cardinals $\kappa$.
+  $\pl F \codewin \cloPFGame{\kappa}$ for all cardinals $\kappa$.
 \end{thm}
@@
   For each cardinal $\kappa$ and $\lambda<\kappa$,
-  assume $\sigma_\lambda$ is a winning strategy for $\pl F$ in $\pfgame\lambda$
+  assume $\sigma_\lambda$ is a winning strategy for $\pl F$ in $\cloPFGame\lambda$
   such that $\sigma_\lambda(\emptyset)\supset\emptyset$ and
@@
 \begin{cor}
-  $\pl O\codewin\congame{\SigmaProdR{\kappa}}{\vec{0}}$
+  $\pl O\codewin\gruConGame{\SigmaProdR{\kappa}}{\vec{0}}$
   for all cardinals $\kappa$.
@@
 \begin{ques}
-  Does $\pl O \win\congame{X}{x}$ imply $\pl O \codewin\congame{X}{x}$?
+  Does $\pl O \win\gruConGame{X}{x}$ imply $\pl O \codewin\gruConGame{X}{x}$?
 \end{ques}

### 2014-11-17 phd/dissertation/chapter3.tex
symmetrize chapter names
polishing limited info results on bell's game
countable products result

@@
 
-\chapter{$W$ Convergence and Clustering Games}
+\chapter{Gruenhage's Convergence and Clustering Games}
 
@@
   strategy for $\pl O$ in $\gruConGame{X}{S}$ as well.
+\end{proof}
+
+\begin{prop} For any $x\in X$ and $k<\omega$,
+  \begin{itemize}
+    \item
+      $
+      \pl O\ktactwin{k+1}\gruConGame{X}{x}
+        \Leftrightarrow
+      \pl O\tactwin\gruConGame{X}{x}
+      $
+    \item
+      $
+      \pl O\kmarkwin{k+1}\gruConGame{X}{x}
+        \Leftrightarrow
+      \pl O\markwin\gruConGame{X}{x}
+      $
+  \end{itemize}
+\end{prop}
+
+\begin{proof}
+  If $\sigma$ witnesses $\pl O\ktactwin{k+1}\gruConGame{X}{x}$,
+  let $\tau(\emptyset)=\sigma(\emptyset)$ and
+    \[
+      \tau(\<q\>)
+        =
+      \bigcap_{i< k}
+      \sigma(\<\underbrace{x,\dots,x}_{k-i},q,\underbrace{x,\dots,x}_{i+1}\>)
+    \]
+
+  Then $\tau$ is easily verified to be a winning tactic, and
+  the proof for the second part is analogous.
 \end{proof}
@@
 \begin{defn}
-  Let $\Sigma_{y} X^\kappa$ be a \term{sigma product} of $X$ with dimension
-  $\kappa$ for each $y\in X^\kappa$, the subset of the usual Tychonoff
-  product space $X^\kappa$ such that $x\in \Sigma_y X^\kappa$ if and only if
-  $\{\alpha<\kappa : x(\alpha)\not=y(\alpha)\}$ is countable.
+  Let $\Sigma_{y} \prod_{\alpha<\kappa}X_\alpha$ be a \term{sigma-product} of
+  $X$ with dimension $\kappa$ for each $y\in \prod_{\alpha<\kappa}X_\alpha$,
+  the subset of the usual Tychonoff product space $\prod_{\alpha<\kappa}X_\alpha$
+  such that $x\in \Sigma_y \prod_{\alpha<\kappa}X_\alpha$
+  if and only if $\{\alpha<\kappa : x(\alpha)\not=y(\alpha)\}$ is countable.
 
-  For homogeneous spaces $X$ containing $0$, $y$ is usually assumed to be the
-  zero vector $\vec 0$ and the sigma product is written $\Sigma X^\kappa$.
+  Unless otherwise specified, we assume $0\in X_\alpha$ for all $\alpha<\kappa$
+  and $y=\vec 0$, and write $\Sigma \prod_{\alpha<\kappa}X_\alpha$.
 \end{defn}

### 2014-11-24 phd/dissertation/chapter3.tex
fix issues found in seminar

@@
 
-Since it's trivial to show that $\pl O\prewin\gruConGame{\oneptcomp\kappa}$ if and
+Since it's trivial to show that
+$\pl O\prewin\gruConGame{\oneptcomp\kappa}{\infty}$ if and
 only if $\kappa\leq\omega$, this closes the question on limited information

### 2014-11-25 phd/dissertation/chapter5.tex
Name and camelCase based game commands/definitions
symmetrize chapter names
begin work on chapter 5

@@
 
-\chapter{Locally Finite Games}
+\chapter{Gruenhage's Locally Finite Games}
 
-placeholder
+A variation of $\gruConGame{X}{x}$, also due to Gruenhage,
+may be used to characterize various covering properties, particularly
+for locally compact spaces. We assume all spaces are $T_1$.
 
-% Results pertaining to the Locally Finite games related to $W$ games.
+\section{Characterizations using $\gruKPGame{X}$, $\gruKLGame{X}$}
 
-% \section{Characterizations using $\lfkpgame{X}$, $\lfklgame{X}$}
+\begin{game}
+  Let $\gruKPGame{X}$ denote the \term{Gruenhage compact/point game}
+  with players $\pl K$, $\pl P$. During round $n$, $\pl K$ chooses
+  a compact subset $K_n$ of $X$, followed by $\pl P$ choosing a point
+  $p_n\in X$ such that $p_n\not\in \bigcup_{m\leq n}K_m$.
 
-% \begin{thm}(G)
-%   The following are equivalent for a locally compact space $X$:
-%     \begin{itemize}
-%       \item $X$ is paracompact
-%       \item $\pl K \uparrow \lfklgame{X}$.
-%     \end{itemize}
-% \end{thm}
+  $\pl K$ wins the game if the collection $\{\{p_n\}:n<\omega\}$ is locally
+  finite in the space, and $\pl P$ wins otherwise.
+\end{game}
 
-% \begin{thm}(G)
-%   The following are equivalent for a locally compact space $X$:
-%     \begin{itemize}
-%       \item $X$ is metacompact
-%       \item $\pl K \tactwin \lfkpgame{X}$.
-%     \end{itemize}
-% \end{thm}
+This game is often formulated by requiring that the collection
+$\{\{p_n\}:n<\omega\}$ be discrete. With the knowledge of at least the latest
+move of the opponent, $\pl K$ may guarantee that if $\{\{p_n\}:n<\omega\}$
+is locally finite then it is also discrete, since she may require
+$p_n\in K_{n+1}$. Thus this formulation is essentially equivalent to the usual
+formulation for all existing applications.
 
-% \begin{thm}(G)
-%   The following are equivalent for a locally compact space $X$:
-%     \begin{itemize}
-%       \item $X$ is $\sigma$-metacompact
-%       \item $\pl K \markwin \lfkpgame{X}$.
-%     \end{itemize}
-% \end{thm}
+We may relate this game to $\gruConGame{X}{x}$ as follows:
 
-% \begin{obs}
-%   The following are equivalent for any space $X$:
-%     \begin{itemize}
-%       \item $X$ is compact
-%       \item $\pl K \ktactwin{0} \lfkpgame{X}$.
-%     \end{itemize}
-% \end{obs}
+\begin{thm}
+  If $X$ is locally compact, then for $k<2$:
+    \begin{itemize}
+      \item $\pl K\win\gruKPGame{X}$ if and only if
+        $\pl O\win\gruConGame{\oneptcomp{X}}{\infty}$.
+      \item $\pl K\kmarkwin{k}\gruKPGame{X}$ if and only if
+        $\pl O\kmarkwin{k}\gruConGame{\oneptcomp{X}}{\infty}$.
+      \item $\pl K\ktactwin{k}\gruKPGame{X}$ if and only if
+        $\pl O\ktactwin{k}\gruConGame{\oneptcomp{X}}{\infty}$.
+    \end{itemize}
+\end{thm}
 
-% \begin{thm}
-%   $P \markwin G_{K,P}(X)$ where $X$ is a first-countable non-locally
-%   countably compact space.
-% \end{thm}
+\begin{proof}
+  Let $L$ be any of $\nu_0$, $\nu_1$, $\mu_0$, $\mu_1$, or the identity.
+  For any sequence $s$ of points in $\oneptcomp X$, let $s'$ be the
+  subsequence of non-$\infty$ points in $s$.
 
-% \begin{thm}
-%   $P \not\tactwin G_{K,P}(M)$ where $M$ is the metric fan space.
-% \end{thm}
+  If $\sigma\circ L$ is a winning strategy for $\pl K$ in $\gruKPGame{X}$, let
+  $\tau\circ L$ be a strategy for $\pl O$ in $\gruConGame{\oneptcomp X}{\infty}$
+  such that $\tau(L(s)) = \oneptcomp X\setminus \sigma(L(s)')$. Then for
+  any legal attack $p$ against $\tau$, $p'$ is a legal attack against $\sigma$.
+  (The proof of this claim uses the fact that $k<2$.)
+  If $p'$ is a finite sequence, then $p$ converges to $\infty$.
+  Otherwise, the set $\{\{p'(n)\}:n<\omega\}$ is locally finite in $X$, so
+  $\{p'(n):n<\omega\}$ is a closed discrete subset of $X$. Then for every
+  neighborhood $U$ of $\infty$, $X\setminus U$ is contained in a compact set,
+  so it cannot contain a closed discrete subset. Thus $p'$ and $p$
+  converge to $\infty$.
 
-% \begin{thm}
-%   The following are equivalent for any locally compact space $X$:
-%     \begin{itemize}
-%       \item $X$ is Lindel\"of.
-%       \item $X$ is $\sigma$-compact.
-%       \item $X$ is hemicompact.
-%       \item $\pl K \prewin G_{K,L}(X)$.
-%       \item $\pl K \prewin G_{K,P}(X)$.
-%     \end{itemize}
-% \end{thm}
+  If $\sigma\circ L$ is a winning strategy for $\pl O$ in
+  $\gruConGame{\oneptcomp X}{\infty}$, let $\tau\circ L$ be a strategy for
+  $\pl K$ in $\gruKPGame{X}$ such that $\tau(L(s))= X\setminus\sigma(L(s))$.
+  Then for any legal attack $p$ against $\tau$, $p$ is a legal attack against
+  $\sigma$, so the sequence $p$ converges to $\infty$. For any point $x\in X$
+  distinct from the $p(n)$, we may choose a neighborhood $U_x$ of $x$ in $X$
+  missing every point in $p(n)$.
+  For every $n<\omega$, we may choose a neighborhood $U_{p(n)}$ of $p(n)$ in
+  $X$ which misses every distinct $p(m)$. Thus $\{\{p(n)\}:n<\omega\}$ is a
+  locally finite collection.
+\end{proof}
 
-% \begin{thm}
-%   The following are equivalent for any Hausdorff $k$-space $X$:
-%     \begin{itemize}
-%       \item $X$ is hemicompact.
-%       \item $X$ is $k_{\omega}$.
-%       \item $\pl K \prewin \lfklgame{X}$.
-%       \item $\pl K \prewin \lfkpgame{X}$.
-%     \end{itemize}
-% \end{thm}
+The reason why $\gruConGame{\oneptcomp X}{\infty}$ and $\gruKPGame{X}$ are
+not completely equivalent is due to the fact that $\pl P$ may hide information
+from $\pl O$ by playing $\infty$. These moves cannot trivially be ignored
+using a $k$-limited information strategy for $k\geq 2$, since $\pl P$ may
+ensure that only one ``useful'' move may be seen by $\pl K$ at a time by playing
+$k$ $\infty$s between each non-$\infty$.
+
+Applications of limited information strategies for $\pl K$ are already known;
+see \cite{MR858337}.
+
+\begin{thm}
+  The following are equivalent for a locally compact space $X$:
+    \begin{itemize}
+      \item $X$ is metacompact
+      \item $\pl K \tactwin \gruKPGame{X}$.
+    \end{itemize}
+\end{thm}
+
+\begin{thm}
+  The following are equivalent for a locally compact space $X$:
+    \begin{itemize}
+      \item $X$ is $\sigma$-metacompact
+      \item $\pl K \markwin \gruKPGame{X}$.
+    \end{itemize}
+\end{thm}
+
+In addition, it's trivial to show the following.
+
+\begin{prop}
+  The following are equivalent for any space $X$:
+    \begin{itemize}
+      \item $X$ is compact
+      \item $\pl K \ktactwin{0} \gruKPGame{X}$.
+    \end{itemize}
+\end{prop}
+
+\begin{proof}
+  A $0$-tactic is seeded with zero information about the moves of the opponent
+  or the round number, so it must be a constant function valued at $X$.
+\end{proof}
+
+A similar game may be considered by allowing the second player to choose
+compact sets rather than points, which also provided in \cite{MR858337}
+a game-theoretic characterization of a covering property for locally compact
+spaces.
+
+\begin{game}
+  Let $\gruKLGame{X}$ denote the \term{Gruenhage compact/compact game}
+  with players $\pl K$, $\pl L$. This game proceeds analogously to
+  $\gruKPGame{X}$, except the second player $\pl L$ chooses comapct sets $L_n$
+  missing $\bigcup_{m\leq n}K_n$,
+  and $\pl K$ wins if the collection $\{L_n:n<\omega\}$ is locally finite.
+\end{game}
+
+As above, this formulation is equivalent to requiring $\{L_n:n<\omega\}$ be
+discrete when considering strategies for $\pl K$ which use at least the latest
+move of $\pl L$.
+
+\begin{thm}
+  The following are equivalent for a locally compact space $X$:
+    \begin{itemize}
+      \item $X$ is paracompact
+      \item $\pl K \win \gruKLGame{X}$.
+    \end{itemize}
+\end{thm}
+
+\section{Predetermined strategies for $\gruKPGame{X}$, $\gruKLGame{X}$}
+
+Adding knowledge of the round number to a tactic changes the characterization
+from metacompact to $\sigma$-metacompact. In fact, the analogous result holds
+for $0$-tactics to $0$-marks, known as predetermined strategies since they
+rely only on the round number and not the moves of the opponent.
+
+\begin{thm}
+  If $X$ is a locally compact Lindel\"of space, then $\pl K \prewin G_{K,L}(X)$.
+\end{thm}
+
+\begin{proof}
+  For each $x\in X$, let $U_x$ be an open neighborhood of $x$ with $\cl{U_x}$
+  compact. Then as $X$ is Lindel\"of, choose $x_n\in X$ for $n<\omega$ such that
+  $\{U_{x_n}:n<\omega\}$ covers $X$. Define the predetermined strategy $\sigma$
+  for $\pl K$ by $\sigma(n)=\cl{U_{x_n}}$.
+
+  Let $L:\omega\to \mc K(X)$ legally attack $\sigma$, so
+  $L(n)\cap\bigcup_{m\leq n}\sigma(m)=\emptyset$. For each $x\in X$,
+  choose $n<\omega$ with $x\in U_{x_n}$. Then $U_{x_n}$ is a neighborhood of
+  $x$ which intersects finitely many $L(n)$, so $\{L(n):n<\omega\}$ is
+  locally finite.
+\end{proof}
+
+\begin{defn}
+  A space $X$ is \textbf{hemicompact} if there exist compact sets $K_n$ for
+  $n<\omega$ such that every compact set in $X$ is a subset of some $K_n$.
+\end{defn}
+
+\begin{thm}
+  If $\pl K\prewin \gruKPGame{X}$, then $X$ is hemicompact.
+\end{thm}
+
+\begin{proof}
+  Let $\sigma$ be a winning predetermined strategy for $\pl K$ in
+  $\gruKPGame{X}$. If $C\in \mc K(X)$ is compact, then for each $x\in C$ let
+  $U_x$ be an open neighborhood of $x$ which intersects finitely many
+  $\sigma(n)$. Thus there exists an open neighborhood of $C$ which intersects
+  finitely many $\sigma(n)$.
+\end{proof}
+
+\begin{cor}
+  The following are equivalent for any locally compact space $X$:
+    \begin{itemize}
+      \item $X$ is Lindel\"of.
+      \item $X$ is $\sigma$-compact.
+      \item $X$ is hemicompact.
+      \item $\pl K \prewin \gruKPGame{X}$.
+      \item $\pl K \prewin \gruKLGame{X}$.
+    \end{itemize}
+\end{cor}
+
+\section{Compactly generated spaces}
+
+\begin{defn}
+  A space $X$ is \term{compactly generated} if a set is closed if and
+  only if its intersection is closed in every compact subspace. Such
+  spaces are also known as \term{$k$-spaces}.
+\end{defn}
+
+All locally compact spaces are $k$-spaces. As will be shown,
+the games $\gruKPGame{X}$, $\gruKLGame{X}$ are equivalent for $\pl K$'s
+predetermined strategies in Hausdorff $k$-spaces.
+
+\begin{defn}
+  A space $X$ is a $k_\omega$-space if there exist compact sets $K_n$ for
+  $n<\omega$ such that a set is closed if and
+  only if its intersection is closed in every subspace $K_n$.
+\end{defn}
+
+\begin{thm}
+  If $X$ is a Hausdorff hemicompact $k$-space, then
+  $\pl K \prewin \gruKLGame{X}$.
+\end{thm}
+
+\begin{proof}
+  Let $K_n$ witness hemicompactness for $X$. Define the predetermined strategy
+  $\sigma$ for $\pl K$ by $\sigma(n)=K_n$.
+
+  Let $L:\omega\to\mc{K}(X)$ be a legal attack against $\sigma$, and let
+  $L_\omega = \bigcup_{n<\omega}L_(n)$. For each compact set (TODO FINISH)
+\end{proof}
+
+\begin{cor}
+  The following are equivalent for any Hausdorff $k$-space $X$:
+    \begin{itemize}
+      \item $X$ is hemicompact.
+      \item $X$ is $k_{\omega}$.
+      \item $\pl K \prewin \gruKPGame{X}$.
+      \item $\pl K \prewin \gruKLGame{X}$.
+    \end{itemize}
+\end{cor}
 
@@
 %   If $X=\omega\cup\mathcal{F}\subset\beta\omega$ (a non-$k$ space),
-%   then $K\not\prewin \lfklgame{X}$.
+%   then $K\not\prewin \gruKLGame{X}$.
 % \end{prop}
@@
 %   If a selective ultrafilter $\mathcal{F}$ exists (independent of ZFC),
-%   then $K \not\prewin \lfkpgame{X}$
+%   then $K \not\prewin \gruKPGame{X}$
 %   for $X=\omega \cup \{\mathcal{F}\}\subset \beta\omega$.
@@
 %   Then there is an ultrafilter $\mathcal{F}$ such that
-%   then $K \prewin \lfkpgame{X}$ and $K \tactwin \lfkpgame{X}$
+%   then $K \prewin \gruKPGame{X}$ and $K \tactwin \gruKPGame{X}$
 %   for $X=\omega \cup \{\mathcal{F}\}\subset \beta\omega$.
@@
 %   Let $M$ be the \term{metric fan}, a non-locally compact $k$ space.
-%   Then $P \win \lfkpgame{M}$.
+%   Then $P \win \gruKPGame{M}$.
 % \end{thm}
@@
 %   Let $S$ be the \term{sequential fan}, a non-locally compact $k$ space.
-%   Then $K \prewin \lfkpgame{S}$ and $K\tactwin \lfkpgame{S}$.
+%   Then $K \prewin \gruKPGame{S}$ and $K\tactwin \gruKPGame{S}$.
 % \end{thm}
@@
 % (TODO: Maybe consider claim
-% $K \prewin \lfkpgame{X}$ $\Rightarrow$ $X$ is a $k$-space)
+% $K \prewin \gruKPGame{X}$ $\Rightarrow$ $X$ is a $k$-space)
 
@@
 % \begin{prop}
-% $K \win \lfkpgame{\mathbb{X}}$.
+% $K \win \gruKPGame{\mathbb{X}}$.
 % \end{prop}
@@
 % \begin{thm}(cor of G, game-theoretic proof by me)
-% $K\not\tactwin\lfkpgame{\mathbb{X}}$.
+% $K\not\tactwin\gruKPGame{\mathbb{X}}$.
 % \end{thm}
@@
 % \begin{thm}
-% $K\not\ktactwin{k}\lfkpgame{\mathbb{X}}$.
+% $K\not\ktactwin{k}\gruKPGame{\mathbb{X}}$.
 % \end{thm}

### 2014-11-26 phd/dissertation/chapter5.tex
finish k-space results

@@
 may be used to characterize various covering properties, particularly
-for locally compact spaces. We assume all spaces are $T_1$.
+for locally compact spaces. All spaces are assumed to be $T_1$ in this
+chapter.
 
@@
   A space $X$ is \term{compactly generated} if a set is closed if and
-  only if its intersection is closed in every compact subspace. Such
+  only if its intersection with every compact set is closed. Such
   spaces are also known as \term{$k$-spaces}.
@@
   $n<\omega$ such that a set is closed if and
-  only if its intersection is closed in every subspace $K_n$.
+  only if its intersection with every $K_n$ is closed.
 \end{defn}
@@
 \begin{thm}
-  If $X$ is a Hausdorff hemicompact $k$-space, then
+  If $X$ is a $k_\omega$-space, then
   $\pl K \prewin \gruKLGame{X}$.
@@
 \begin{proof}
-  Let $K_n$ witness hemicompactness for $X$. Define the predetermined strategy
-  $\sigma$ for $\pl K$ by $\sigma(n)=K_n$.
+  Let $K_n$ witness that $X$ is a $k_\omega$-space. Define the predetermined
+  strategy $\sigma$ for $\pl K$ by $\sigma(n)=K_n$.
 
   Let $L:\omega\to\mc{K}(X)$ be a legal attack against $\sigma$, and let
-  $L_\omega = \bigcup_{n<\omega}L_(n)$. For each compact set (TODO FINISH)
+  $L_{\omega\setminus n} = \bigcup_{n\leq m<\omega}L(m)$. Then as
+    \[
+      L_{\omega\setminus n}\cap K_n
+        =
+      \bigcup_{n\leq m< p}L(m) \cap \sigma(p)
+    \]
+  is compact for each $p<\omega$, $L_{\omega\setminus n}$ is closed.
+
+  For each $x\in X$, $x\in \sigma(p)$ for some $p$, so
+  $x\in X\setminus L_{\omega\setminus p}$ which misses all but finitely
+  many $L(n)$, showing that $\{L(n):n<\omega\}$ is locally finite and
+  $\sigma$ is a winning predetermined strategy.
 \end{proof}
 
+\begin{prop}
+  Hemicompact $k$-spaces are $k_\omega$-spaces.
+\end{prop}
+
+\begin{proof}
+  Let $K_n$ for $n<\omega$ witness hemicompactness.
+  If $C\cap K_n$ is closed for each $n<\omega$, then let $K$ be any compact
+  set. Since $K\subseteq K_n$ for some $n<\omega$, $C\cap K$ is closed, and
+  therefore $C$ is closed.
+\end{proof}
+
+As we've already seen that $\pl K \prewin \gruKPGame{X}$ implies
+hemicompactness:
+
 \begin{cor}
-  The following are equivalent for any Hausdorff $k$-space $X$:
+  The following are equivalent for any $k$-space $X$:
     \begin{itemize}
+      \item $X$ is $k_{\omega}$.
       \item $X$ is hemicompact.
-      \item $X$ is $k_{\omega}$.
       \item $\pl K \prewin \gruKPGame{X}$.

### 2014-11-27 phd/dissertation/chapter5.tex
free ultrafilters

@@
 
-\section{Predetermined strategies for $\gruKPGame{X}$, $\gruKLGame{X}$}
+\section{Locally compact spaces and predetermined strategies}
 
-Adding knowledge of the round number to a tactic changes the characterization
-from metacompact to $\sigma$-metacompact. In fact, the analogous result holds
+As mentioned above, adding knowledge of the round number to a tactic changes the
+characterization from metacompact to $\sigma$-metacompact. In fact, the
+analogous result holds
 for $0$-tactics to $0$-marks, known as predetermined strategies since they
@@
 
-\section{Compactly generated spaces}
+\section{Compactly generated spaces and predetermined strategies}
 
@@
     \[
-      L_{\omega\setminus n}\cap K_n
+      L_{\omega\setminus n}\cap K_p
         =
@@
 
-% \section{Non-locally compact spaces}
+\section{Non-equivalence of $\gruKPGame{X}$, $\gruKLGame{X}$}
 
-% \begin{prop}
-%   If $X=\omega\cup\mathcal{F}\subset\beta\omega$ (a non-$k$ space),
-%   then $K\not\prewin \gruKLGame{X}$.
-% \end{prop}
+For $k$-spaces, it has been shown that $\gruKPGame{X}$ and $\gruKLGame{X}$
+are equivalent with respect to $\pl K$'s winning predetermined strategies.
+Looking at a subspace of the Stone-Cech compactification $\beta\omega$ of
+$\omega$ reveals an example for which the predetermined strategies are not
+equivalent.
+
+\begin{defn}
+  An \term{ultrafilter} on a cardinal $\kappa$ is a maximal filter of non-empty
+  subsets of $\kappa$. For each $\alpha\in \kappa$, the ultrafilter
+  $\mc F_\alpha$ containing all supersets of $\{\alpha\}$ is called a
+  \term{principal ultrafilter}. All
+  ultrafilters not of this form are called \term{free ultrafilters}.
+\end{defn}
+
+\begin{defn}
+  The \term{Stone-Cech compactification} of a cardinal
+  $\kappa$ is the space $\beta\kappa$ consisting
+  of all ultrafilters on $\kappa$, with open sets of the form
+  $U_S=\{\mc F\in\beta\kappa : S\in\mc F\}$ for $S\subseteq \kappa$.
+\end{defn}
+
+From these definitions it is easily verified that principal ultrafilters
+are isolated, so $\kappa$ with the discrete topology may be viewed as
+a dense open subspace of $\beta\kappa$. $\beta\kappa$ is also compact, so
+$\pl K\ktactwin{0}\gruKLGame{\beta\kappa}$; of greater interest is the subspace
+of $\beta\omega$ consisting of all principal ultrafilters and a single free
+ultrafilter $\mc F$, denoted $\omega\cup\{\mc F\}$.
+
+\begin{lem}
+  All compact subsets of $\omega\cup\{\mc F\}\subset\beta\omega$ are finite.
+  In particular, the difference of compact sets in $\omega\cup\{\mc F\}$
+  is compact.
+\end{lem}
+
+\begin{proof}
+  Let $I=\{n_i:i<\omega\}\cup\{\mc F\}$ be infinite.
+  Then $\{U_{\omega\setminus\{n_i:i\geq j\}}:j<\omega\}$ is an open cover of
+  $I\cup\{\mc F\}$ with no finite subcover.
+\end{proof}
+
+\begin{thm}
+  $\pl K\not\prewin \gruKLGame{\omega\cup\{\mc F\}}$ for any free
+  ultrafilter $\mc F$.
+\end{thm}
+
+\begin{proof}
+  Let $\sigma$ be a predetermined strategy for $\pl K$, and define the
+  counterattack $H:\omega\to\mc K(X)$ by
+  $H(n)=(n\cup\sigma(n+1))\setminus\sigma(n)$. Then for any neighborhood
+  $U_S$ of $\mc F$, $S$ is infinite, and since
+  $\bigcup_{n<\omega} H(n)\supseteq\omega\setminus\sigma(0)$, $U_S$ meets
+  infinitely many of the finite $H(n)$. Thus $\sigma$ is not a winning
+  predetermined strategy.
+\end{proof}
+
+\begin{thm}
+  There exists a free ultrafilter $\mc F$ such that
+  $\pl K\prewin \gruKPGame{\omega\cup\{\mc F\}}$.
+\end{thm}
+
+\begin{proof}
+  Let $\mc F$ be any free ultrafilter, and
+  define the predetermined strategy $\sigma$ by
+  $\sigma(n)=n^2\cup\{\mc F\}$.
+
+  Consider the set of all legal attacks $A\subseteq\omega^\omega$ by
+  $\pl P$ against $\sigma$. For $n<\omega$, note that for any $f\in A$,
+  $f$ maps only $n$ points into $n^2$, so the range of $f$ is coinfinite.
+  Then $\mc I=\{\ran f : f\in A\}$ is an ideal, and if
+  $\mc F\supseteq\{\omega\setminus I: I\in\mc I\}$, then $\sigma$ is a
+  winning predetermined strategy.
+\end{proof}
 

### 2014-11-27 phd/dissertation/chapter5.tex
define cantor tree of L spaces

@@
 \begin{proof}
-  Let $\sigma$ be a predetermined strategy for $\pl K$, and define the
-  counterattack $H:\omega\to\mc K(X)$ by
+  Let $\sigma$ be a predetermined strategy for $\pl K$, and define the legal
+  counter-attack $H:\omega\to\mc K(X)$ by
   $H(n)=(n\cup\sigma(n+1))\setminus\sigma(n)$. Then for any neighborhood
@@
   Consider the set of all legal attacks $A\subseteq\omega^\omega$ by
-  $\pl P$ against $\sigma$. For $n<\omega$, note that for any $f\in A$,
-  $f$ maps only $n$ points into $n^2$, so the range of $f$ is coinfinite.
-  Then $\mc I=\{\ran f : f\in A\}$ is an ideal, and if
-  $\mc F\supseteq\{\omega\setminus I: I\in\mc I\}$, then $\sigma$ is a
+  $\pl P$ against $\sigma$. For $\{f_i:i\leq m\}\in [A]^{<\omega}$ and
+  $m<n<\omega$, each $f_i$ maps only $n$ points into $n^2$, so
+  $\bigcup_{i\leq m}\ran{f_i}$ is coinfinite.
+  Then $\mc G'=\{\omega\setminus\ran f : f\in A\}$ is contained in a free
+  ultrafilter $\mc G$, and if $\mc F=\mc G$, then $\sigma$ is a
   winning predetermined strategy.
@@
 
-% \begin{prop}
-%   If a selective ultrafilter $\mathcal{F}$ exists (independent of ZFC),
-%   then $K \not\prewin \gruKPGame{X}$
-%   for $X=\omega \cup \{\mathcal{F}\}\subset \beta\omega$.
-% \end{prop}
+It is not possible to prove that $\pl K\prewin \gruKPGame{\omega\cup\{\mc F\}}$
+for arbitrary free ultrafilters in $ZFC$.
 
-% \begin{thm}
-%   Then there is an ultrafilter $\mathcal{F}$ such that
-%   then $K \prewin \gruKPGame{X}$ and $K \tactwin \gruKPGame{X}$
-%   for $X=\omega \cup \{\mathcal{F}\}\subset \beta\omega$.
-% \end{thm}
+\begin{defn}
+  A \term{selective ultrafilter} $\mc F$ is a free ultrafilter with the
+  property that for every
+  partition $\{B_n : n < \omega\}$ of nonempty subsets of $\omega$ such that
+  $B_n \not\in \mathcal{F}$ for all $n$, there exists $A \in \mc{F}$ such
+  that $|A \cap B_n|=1$ for all $n$.
+\end{defn}
 
-% \begin{thm}
-%   Let $M$ be the \term{metric fan}, a non-locally compact $k$ space.
-%   Then $P \win \gruKPGame{M}$.
-% \end{thm}
+\begin{thm}
+  CH implies the existence of a selective ultrafilter.
+  \cite{MR0080902}
+\end{thm}
 
-% \begin{thm}
-%   Let $S$ be the \term{sequential fan}, a non-locally compact $k$ space.
-%   Then $K \prewin \gruKPGame{S}$ and $K\tactwin \gruKPGame{S}$.
-% \end{thm}
+\begin{thm}
+  If $\mc F$ is a selective ultrafilter, then
+  $\pl K\not\prewin \gruKPGame{\omega\cup\{\mc F\}}$.
+\end{thm}
 
-% (TODO: Maybe consider claim
-% $K \prewin \gruKPGame{X}$ $\Rightarrow$ $X$ is a $k$-space)
+\begin{proof}
+  Let $\sigma$ be a predetermined strategy for $\pl K$ such that
+  $\sigma(n)\supset\bigcup_{m<n}\sigma(m)$.
+  Then define $B_n=\omega\cap(\sigma(n+1)\setminus\sigma(n))$. Since $B_n$
+  is always nonempty finite, $B_n\not\in\mc F$ and there exists $A\in \mc F$
+  such that $|A\cap B_n|=1$.
+
+  Define the legal counter-attack $p:\omega\to\omega\cup\{\mc F\}$ by
+  $p(n)\in A\cap B_n=A\cap(\sigma(n+1)\setminus\sigma(n))$. Since
+  $A=(A\cap\sigma(0))\cup\{p(n):n<\omega\}$, $\{p(n):n<\omega\}\in\mc F$.
+  Therefore, every neighborhood of $\mc F$ intersects infinitely many of
+  the $p(n)$, and $p$ defeats the predetermined strategy $\sigma$.
+\end{proof}
+
+Of particular note is that the author knows of no examples of a
+non-$k$-space such that $K\prewin\gruKPGame{X}$.
+
+\begin{ques}
+  Does $K\prewin\gruKPGame{X}$ imply $X$ is a $k$-space?
+\end{ques}
+
+\section{$k+1$-tactics and marks for $\gruKPGame{X}$}
+
+While $\pl O\ktactwin{k+1}\gruConGame{\oneptcomp X}{\infty}$ implies
+$\pl O\tactwin\gruConGame{\oneptcomp X}{\infty}$, and likewise for Markov
+strategies, this result cannot be
+immediately extended to $\gruKPGame{X}$. However, this section will
+demonstrate a non-trivial example of a space $\mb X$ for which
+$\pl K\win\gruKPGame{\mb X}$ but $\pl K\not\kmarkwin{k}\gruKPGame{\mb X}$
+for any $k<\omega$.
+
+\begin{defn}
+  An $L$-space is a herditarally Lindel\"of, non-separable space.
+\end{defn}
+
+\begin{thm}
+  Under $CH$(?), there exists a zero-dimensional, compact $L$-space.
+  Furthermore, there exists a point-countable collection of clopen sets
+  $\mc U=\{U_\alpha:\alpha<\omega_1\}$ in $X$ such
+  that every point-finite subcollection of $\mc U$ is countable.
+\end{thm}
+
+\begin{proof}
+  (TODO or find citation)
+\end{proof}
+
+\begin{defn}
+  Let $\mb X=(X\times 2^{<\omega})\cup 2^\omega$ denote a Cantor tree
+  of zero-dimensional, compact $L$-spaces $X$ with a point-countable collection
+  of clopen sets $\mc U=\{U_\alpha:\alpha<\omega_1\}$ such
+  that every point-finite subcollection of $\mc U$ is countable.
+  The topology on $\mb X$ is
+  given by decaring $U\times\{s\}$ to be an open
+  neighborhood of $\<x,s\>\in X\times 2^{<\omega}$ for each
+  open neighborhood $U$ of $x$ in $X$, and declaring
+  $(U_\alpha\times\{f\rest n: m\leq n<\omega\})\cup\{f\}$ to be an open
+  neighborhood of $f\in 2^\omega$ for each $\alpha<\omega_1$ and $m<\omega$.
+\end{defn}
 

### 2014-11-29 phd/dissertation/chapter5.tex
work on cantor tree space

@@
 
-\begin{defn}
-  An $L$-space is a herditarally Lindel\"of, non-separable space.
-\end{defn}
-
 \begin{thm}
-  Under $CH$(?), there exists a zero-dimensional, compact $L$-space.
-  Furthermore, there exists a point-countable collection of clopen sets
-  $\mc U=\{U_\alpha:\alpha<\omega_1\}$ in $X$ such
-  that every point-finite subcollection of $\mc U$ is countable.
+  There exists a compact, zero-dimensional topological space $X$
+  such that $X$ has a point-countable cover
+  $\mc{U} = \{U_\alpha : \alpha<\omega_1\}$ of
+  clopen sets which is not $\sigma$-point-finite.
 \end{thm}
@@
 \begin{proof}
-  (TODO or find citation)
+  (TODO)
 \end{proof}
@@
 \begin{defn}
-  Let $\mb X=(X\times 2^{<\omega})\cup 2^\omega$ denote a Cantor tree
-  of zero-dimensional, compact $L$-spaces $X$ with a point-countable collection
-  of clopen sets $\mc U=\{U_\alpha:\alpha<\omega_1\}$ such
-  that every point-finite subcollection of $\mc U$ is countable.
+  Let $\mb X=(X\times 2^{<\omega})\cup C$ denote a Cantor tree
+  of copies of a zero-dimensional, compact space $X$ with a point-countable
+  cover $\mc{U} = \{U_\alpha : \alpha<\omega_1\}$ of
+  clopen sets which is not $\sigma$-point-finite, along with an uncountable
+  subset of the Cantor set
+  $C=\{c_\alpha:\alpha<\omega_1\}\in [2^\omega]^{\omega_1}$.
   The topology on $\mb X$ is
-  given by decaring $U\times\{s\}$ to be an open
+  given by decaring $U\times\{s\}$ to be a open
   neighborhood of $\<x,s\>\in X\times 2^{<\omega}$ for each
   open neighborhood $U$ of $x$ in $X$, and declaring
-  $(U_\alpha\times\{f\rest n: m\leq n<\omega\})\cup\{f\}$ to be an open
-  neighborhood of $f\in 2^\omega$ for each $\alpha<\omega_1$ and $m<\omega$.
+  $B_{\alpha,n}=(U_\alpha\times\{f\rest n: m\leq n<\omega\})\cup\{f\}$ to be
+  an clopen neighborhood of $\alpha\in\omega_1$ for each $m<\omega$.
 \end{defn}
 
-% \section{Cantor tree space example}
+\begin{lem}
+  Let $F\in \omega_1^{<\omega}$ and $m<\omega$.
+  Then $K_F$, $K_F'$, $L_m$ are compact in $\mb X$ as defined below.
+  \[
+    K_F = \bigcup_{\alpha \in F} B_{\alpha,0}
+  \]
+  \[
+    A = \{z^\frown \<1\> : z \in \{0\}^{<\omega}\}
+  \]
+  \[
+    K_F' = K_F \setminus (X \times A)
+  \]
+  \[
+    L_m = X \times 2^{<m}
+  \]
+  Furthermore, every compact set is contained in a union of $K_F'$, $L_m$
+  for some $F\in C^{<\omega}$ and $m<\omega$.
+\end{lem}
 
-% \begin{ex}
-%   Let $X$ be a zero-dimensional, compact L-space
-%   (hereditarally Lindeloff and non-separable).
-%   It is a fact that there exists a point-countable collection
-%   $\mathcal{U}=\{U_\alpha : \alpha<\omega_1\}$ of clopen sets in $X$, and it is
-%   also true that any point-finite subcollection of $\mathcal{U}$ is countable.
+\begin{proof}
+  $K_F$ contains $C_F=\{c_\alpha: \alpha\in F\}\subseteq C$, so any
+  cover of basic open sets must include $B_{\alpha,n_\alpha}$ for each
+  $\alpha\in F$, and the remaining uncovered portion of $K_F$ is a finite
+  union of copies of closed subsets of compact $X$. Then $K_F'$ is also
+  compact as it is a closed subset of $K_F$, and $L_m$ is compact as it
+  is a finite union of copies of compact $X$.
 
-%   Let $C = \{c_\alpha : \alpha <\omega_1\}$ be any uncountable subset of the
-%   Cantor space $2^\omega$. Let $X_s = X \times \{s\}$ for each
-%   $s \in 2^{<\omega}$, and $U_{\alpha,s} = U_\alpha \times \{s\}$.
+  Let $D$ be compact. Consider the open cover
+    \[
+      \{
+        B_{\alpha,0}
+      :
+        \alpha<\omega_1
+      \}
+      \cup
+      \{
+        X\times\{s\}
+      :
+        s\in 2^{<\omega}
+      \}
+    \]
+  and note that the finite subcover for $D$ is a refinement of some
+  $K_F'$ and $L_m$.
+\end{proof}
 
-%   Finally, let \[\mathbb{X} = C \cup \bigcup_{s\in 2^{<\omega}} X_s\] be a
-%   tree of $2^{<\omega}$ copies of $X$, and where
-%   \[c_\alpha \cup \bigcup_{n < \omega} U_{\alpha, x_\alpha \restriction n}\]
-%   is an open set about each $c_\alpha$.
-% \end{ex}
+\begin{thm}
+  $\pl K\win\gruKPGame{\mb X}$.
+\end{thm}
+
+\begin{proof}
+  Since $\{U_\alpha:\alpha<\omega_1\}$ is a point-countable cover,
+  for each $x\in X$ let $\alpha_{x,n}<\omega_1$ yield
+  ordinals such that $x\in U_{\alpha_{x,n}}$ for $n<\omega$.
+
+  Let $M:\mb X\times \omega\to \mc K(\mb X)$ as follows:
+    \[
+      M(x,n)
+        =
+      \left\{
+        \begin{array}{lcl}
+          K_{\{\alpha_{x',m}:m\leq n\}}
+        & : &
+          x = \<x',s\> \in X\times 2^{<\omega}
+        \\
+          K_{\{\alpha\}}
+        & : &
+          x = c_\alpha \in C
+        \end{array}
+      \right.
+    \]
+  and use $M$ to define the strategy $\sigma$ for each $a\in\mb X^{<\omega}$:
+    \[
+      \sigma(a)
+        =
+      L_{|a|}
+        \cup
+      \bigcup_{i\leq |a|}
+      M(a(i),|a|)
+    \]
+
+  Let $p:\omega\to\mb X$ be a legal attack against $\sigma$. Then as
+  $p(n)\not\in L_n$, for each $x=\<x',s\>\in X\times 2^{<\omega}$,
+  $X\times\{s\}$ is an open neighborhood of $x$ which contains finitely
+  many $p(n)$.
+
+  Then consider $x=c_\alpha$ for some $\alpha<\omega_1$. Then if
+  $p(n)=\<x',s\>$ for some $n<\omega$, $x'\in U_\alpha$ or
+  $p(n)=c_\alpha$, then
+  $\alpha = \alpha_{p(n),N}$ for some $N<\omega$ and $p(m)\not\in B_{\alpha,0}$
+  for $n+N<m<\omega$. Otherwise, $p(m)\not\in B_{\alpha,0}$ for any $m<\omega$.
+  Either way, $B_{\alpha,0}$ is a neighborhood of $x$ which contains finitely
+  many $p(n)$. Therefore, $\sigma$ is a winning strategy.
+\end{proof}
+
+We will show that there does not exist any winning $k$-Markov strategy for
+$\pl K$ in this game. Knowledge of round number does not assist $\pl K$,
+since she may force $\pl P$ to either stay within $C$, or to seed a growing
+integer by forcing her to play outside $L_{|s|+1}$ in response to
+$\<x,s\>\in X\times 2^{<\omega}$.
+
+\begin{lem}
+  If $\pl K\markwin\gruKPGame{\mathbb{X}}$, then
+  $\pl K\tactwin\gruKPGame{\mathbb{X}}$.
+\end{lem}
+
+\begin{proof}
+  TODO
+  % Let $\sigma$ be a winning mark for $\pl K$ such that $m\leq n$ and
+  % $r$ a subsequence of $s$ implies $\sigma(r,m)\subseteq\sigma(s,n)$.
+  % Define $n:\mb X\to\omega$ by
+  %   \[
+  %     n(x)
+  %       =
+  %     \left\{
+  %       \begin{array}{lcl}
+  %         |s|+1
+  %       & : &
+  %         x = \<x',s\> \in X\times 2^{<\omega}
+  %       \\
+  %         0
+  %       & : &
+  %         x \in C
+  %       \end{array}
+  %     \right.
+  %   \]
+  % and use $n$ to define the $k+1$-tactic $\tau$ by
+  %   \[
+  %     \tau(\emptyset)=\sigma(\emptyset,0)
+  %   \]
+  %   \[
+  %     \tau(t\concat\<x\>)
+  %       =
+  %     L_{n(x)}
+  %       \cup
+  %     \{x\}
+  %       \cup
+  %     \sigma(t\concat\<x\>,n(x))
+  %   \]
+
+  % Let $p:\omega\to\mb X$ be a legal attack by $\pl P$ against $\tau$.
+  % If $p(n)\in C$ for $n>N$, then since no $p(n)$ may be repeated,
+  % $\{\{p(n)\}:N<n<\omega\}$ is a discrete collection, making
+  % $\{\{p(n)\}:n<\omega\}$ locally finite.
+
+  % Otherwise, let $q:\omega\to X\times 2^{<\omega}$ be the subsequence of $p$
+  % removing points in $C$. If $q(0)=p(0)$, then
+  %   \[
+  %     q(0)
+  %       =
+  %     p(0)
+  %       \not\in
+  %     \tau(\emptyset)
+  %       =
+  %     \sigma(\emptyset,0)
+  %   \]
+  % and for any other $q(n)=p(m+1)=$
+\end{proof}
 

### 2014-12-01 phd/dissertation/chapter5.tex
work on k+1 implies 1

@@
 
-\section{$k+1$-tactics and marks for $\gruKPGame{X}$}
+\section{Tactics and marks for $\gruKPGame{X}$}
 
@@
 
-\begin{lem}
-  Let $F\in \omega_1^{<\omega}$ and $m<\omega$.
-  Then $K_F$, $K_F'$, $L_m$ are compact in $\mb X$ as defined below.
+\begin{defn}
+  Let $F\in \omega_1^{<\omega}$ and $m,n<\omega$.
   \[
@@
   \[
-    A = \{z^\frown \<1\> : z \in \{0\}^{<\omega}\}
+    z_n:n\to\{0\}
+  \]
+  \[
+    A = \{z_n^\frown \<1\> : n<\omega\}
   \]
@@
   \]
+\end{defn}
+
+\begin{lem}
+  Then $K_F$, $K_F'$, $L_m$ are compact in $\mb X$.
   Furthermore, every compact set is contained in a union of $K_F'$, $L_m$
@@
 \begin{proof}
-  TODO
-  % Let $\sigma$ be a winning mark for $\pl K$ such that $m\leq n$ and
-  % $r$ a subsequence of $s$ implies $\sigma(r,m)\subseteq\sigma(s,n)$.
-  % Define $n:\mb X\to\omega$ by
-  %   \[
-  %     n(x)
-  %       =
-  %     \left\{
-  %       \begin{array}{lcl}
-  %         |s|+1
-  %       & : &
-  %         x = \<x',s\> \in X\times 2^{<\omega}
-  %       \\
-  %         0
-  %       & : &
-  %         x \in C
-  %       \end{array}
-  %     \right.
-  %   \]
-  % and use $n$ to define the $k+1$-tactic $\tau$ by
-  %   \[
-  %     \tau(\emptyset)=\sigma(\emptyset,0)
-  %   \]
-  %   \[
-  %     \tau(t\concat\<x\>)
-  %       =
-  %     L_{n(x)}
-  %       \cup
-  %     \{x\}
-  %       \cup
-  %     \sigma(t\concat\<x\>,n(x))
-  %   \]
+  Let $\sigma$ be a winning mark for $\pl K$ such that $m\leq n$ and
+  $\ran r \subseteq \ran s$ implies $\sigma(r,m)\subseteq\sigma(s,n)$.
+  Define $r:\mb X\to\omega$ by
+    \[
+      r(x)
+        =
+      \left\{
+        \begin{array}{lcl}
+          |s|
+        & : &
+          x = \<x',s\> \in X\times 2^{<\omega}
+        \\
+          0
+        & : &
+          x \in C
+        \end{array}
+      \right.
+    \]
+  and use $r$ to define the tactic $\tau$ by
+    \[
+      \tau(\emptyset)
+        =
+      \sigma(\emptyset,0)
+    \]
+    \[
+      \tau(\<x\>)
+        =
+      L_{r(x)+1}
+        \cup
+      \{x\}
+        \cup
+      \sigma(\<x\>,r(x))
+    \]
 
-  % Let $p:\omega\to\mb X$ be a legal attack by $\pl P$ against $\tau$.
-  % If $p(n)\in C$ for $n>N$, then since no $p(n)$ may be repeated,
-  % $\{\{p(n)\}:N<n<\omega\}$ is a discrete collection, making
-  % $\{\{p(n)\}:n<\omega\}$ locally finite.
+  Let $p:\omega\to\mb X$ be a legal attack by $\pl P$ against $\tau$.
+  If $p(n)\in C$ for $n>N$, then since no $p(n)$ may be repeated,
+  $\{\{p(n)\}:N<n<\omega\}$ is a discrete collection, making
+  $\{\{p(n)\}:n<\omega\}$ locally finite.
 
-  % Otherwise, let $q:\omega\to X\times 2^{<\omega}$ be the subsequence of $p$
-  % removing points in $C$. If $q(0)=p(0)$, then
-  %   \[
-  %     q(0)
-  %       =
-  %     p(0)
-  %       \not\in
-  %     \tau(\emptyset)
-  %       =
-  %     \sigma(\emptyset,0)
-  %   \]
-  % and for any other $q(n)=p(m+1)=$
+  Otherwise, let $q:\omega\to X\times 2^{<\omega}$ be the subsequence of $p$
+  removing points in $C$ with $p(f(i))=q(i)$ (note $f(i)\geq i$).
+  It follows that
+    \[
+      q(0)
+        =
+      p(f(0))
+        \not\in
+      \tau(\emptyset)
+        \cup
+      \bigcup_{m<f(0)}\tau(\<p(m)\>)
+        \supseteq
+      \tau(\emptyset)
+        =
+      \sigma(\emptyset,0)
+    \]
+
+  Denoting $q(n)=\<x_n',s_n\>$, it's trivial to note that $|s_0|\geq 0$.
+  Assuming that $|s_m|\geq m$ for $m\leq n$,
+  it then follows that
+    \[
+      q(n+1)
+        =
+      p(f(n+1))
+        \not\in
+      \tau(\emptyset)
+        \cup
+      \bigcup_{m<f(n+1)}\tau(\<p(m)\>)
+    \]
+    \[
+        \supseteq
+      \tau(\emptyset)
+        \cup
+      \bigcup_{m\leq n}\tau(\<p(f(m))\>)
+        =
+      \tau(\emptyset)
+        \cup
+      \bigcup_{m\leq n}\tau(\<q(m)\>)
+    \]
+    \[
+        \supseteq
+      \sigma(\emptyset,0)
+        \cup
+      \bigcup_{m\leq n}\sigma(\<q(m)\>,|s_m|)
+        \supseteq
+      \sigma(\emptyset,0)
+        \cup
+      \bigcup_{m\leq n}\sigma(\<q(m)\>,m)
+    \]
+  and $q(n+1)\not\in\tau(\<q(n)\>)\supseteq L_{|s_n|+1}$ gives
+  $|s_{n+1}|\geq|s_n|+1\geq n+1$.
+  Thus $q$ is a legal attack on the winning Markov strategy $\sigma$, so
+  the collection $\{\{q(n)\}:n<\omega\}$ is locally finite.
+  and it follows that $\{\{p(n)\}:n<\omega\}$ is also locally finite.
+\end{proof}
+
+\begin{lem}
+  If $\pl K\kmarkwin{k+1}\gruKPGame{\mathbb{X}}$, then
+  $\pl K\markwin\gruKPGame{\mathbb{X}}$.
+\end{lem}
+
+\begin{proof}
+  Let $\sigma$ be a winning $k+1$-mark for $\pl K$ such that for
+  $s\in[\mb X]^{\leq k+1}$ and $n<\omega$, there exist
+  $F(s,n)\in[\omega_1]^{<\omega}$ and $m(s,n)<\omega$ with
+  \[
+    \sigma(s,n)
+      \subseteq
+    K_{F(s,n)}'
+      \cup
+    L_{m(s,n)}
+  \]
+  Also, it may be assumed that $i<n$ and $\ran r \subseteq \ran s$ implies
+  $F(r,i)\subseteq F(s,n)$ and $m(r,i)\leq m(s,n)$, as well as $n\leq m(s,n)$.
 \end{proof}

### 2014-12-02 phd/dissertation/chapter5.tex
giving up on rewrite of main proof

--- 2014-11-27 phd/dissertation/chapter5.tex
@@
 
+The following result was observed in \cite{MR540599}; a proof is provided
+for convenience.
+
 \begin{prop}
@@
 immediately extended to $\gruKPGame{X}$. However, this section will
-demonstrate a non-trivial example of a space $\mb X$ for which
-$\pl K\win\gruKPGame{\mb X}$ but $\pl K\not\kmarkwin{k}\gruKPGame{\mb X}$
+demonstrate a non-trivial example of a space $\pmb X$ for which
+$\pl K\win\gruKPGame{\pmb X}$ but $\pl K\not\kmarkwin{k}\gruKPGame{\pmb X}$
 for any $k<\omega$.
 
-\begin{defn}
-  An $L$-space is a herditarally Lindel\"of, non-separable space.
-\end{defn}
-
 \begin{thm}
-  Under $CH$(?), there exists a zero-dimensional, compact $L$-space.
-  Furthermore, there exists a point-countable collection of clopen sets
-  $\mc U=\{U_\alpha:\alpha<\omega_1\}$ in $X$ such
-  that every point-finite subcollection of $\mc U$ is countable.
+  There exists a compact, zero-dimensional topological space $X$
+  such that $X$ has a point-countable cover
+  $\mc{U} = \{U_\alpha : \alpha<\omega_1\}$ of distinct clopen sets.
 \end{thm}
@@
 \begin{defn}
-  Let $\mb X=(X\times 2^{<\omega})\cup 2^\omega$ denote a Cantor tree
-  of zero-dimensional, compact $L$-spaces $X$ with a point-countable collection
-  of clopen sets $\mc U=\{U_\alpha:\alpha<\omega_1\}$ such
-  that every point-finite subcollection of $\mc U$ is countable.
-  The topology on $\mb X$ is
-  given by decaring $U\times\{s\}$ to be an open
+  Let $\pmb X=(X\times 2^{<\omega})\cup C$ denote a Cantor tree
+  of copies of a zero-dimensional, compact space $X$ with a point-countable
+  cover $\mc{U} = \{U_\alpha : \alpha<\omega_1\}$ of
+  clopen sets which is not $\sigma$-point-finite, along with an uncountable
+  subset of the Cantor set
+  $C=\{c_\alpha:\alpha<\omega_1\}\in [2^\omega]^{\omega_1}$.
+  The topology on $\pmb X$ is
+  given by decaring $U\times\{s\}$ to be a open
   neighborhood of $\<x,s\>\in X\times 2^{<\omega}$ for each
   open neighborhood $U$ of $x$ in $X$, and declaring
-  $(U_\alpha\times\{f\rest n: m\leq n<\omega\})\cup\{f\}$ to be an open
-  neighborhood of $f\in 2^\omega$ for each $\alpha<\omega_1$ and $m<\omega$.
+  $B_{\alpha,n}=(U_\alpha\times\{c_\alpha\rest n: m\leq n<\omega\})\cup\{c_\alpha\}$
+  to be a clopen neighborhood of $c_\alpha\in C$ for each $\alpha<\omega_1$,
+  $m<\omega$.
 \end{defn}
 
-% \section{Cantor tree space example}
+\begin{defn}
+  Let $F\in \omega_1^{<\omega}$ and $m,n<\omega$.
+  \[
+    K_F = \bigcup_{\alpha \in F} B_{\alpha,0}
+  \]
+  \[
+    a_n = \{\<i,0\>:i<n\}\cup\{\<n,1\>\}
+  \]
+  \[
+    A = \{a_n : n<\omega\}
+  \]
+  \[
+    K_F' = K_F \setminus (X \times A)
+  \]
+  \[
+    L_m = X \times 2^{<m}
+  \]
+\end{defn}
 
-% \begin{ex}
-%   Let $X$ be a zero-dimensional, compact L-space
-%   (hereditarally Lindeloff and non-separable).
-%   It is a fact that there exists a point-countable collection
-%   $\mathcal{U}=\{U_\alpha : \alpha<\omega_1\}$ of clopen sets in $X$, and it is
-%   also true that any point-finite subcollection of $\mathcal{U}$ is countable.
+\begin{lem}
+  Then $K_F$, $K_F'$, $L_m$ are compact in $\pmb X$.
+  Furthermore, every compact set is contained in a union of $K_F'$, $L_m$
+  for some $F\in C^{<\omega}$ and $m<\omega$.
+\end{lem}
 
-%   Let $C = \{c_\alpha : \alpha <\omega_1\}$ be any uncountable subset of the
-%   Cantor space $2^\omega$. Let $X_s = X \times \{s\}$ for each
-%   $s \in 2^{<\omega}$, and $U_{\alpha,s} = U_\alpha \times \{s\}$.
+\begin{proof}
+  $K_F$ contains $C_F=\{c_\alpha: \alpha\in F\}\subseteq C$, so any
+  cover of basic open sets must include $B_{\alpha,n_\alpha}$ for each
+  $\alpha\in F$, and the remaining uncovered portion of $K_F$ is a closed
+  subset of a finite union of copies of compact $X$. Then $K_F'$ is also
+  compact as it is a closed subset of $K_F$, and $L_m$ is compact as it
+  is a finite union of copies of compact $X$.
 
-%   Finally, let \[\mathbb{X} = C \cup \bigcup_{s\in 2^{<\omega}} X_s\] be a
-%   tree of $2^{<\omega}$ copies of $X$, and where
-%   \[c_\alpha \cup \bigcup_{n < \omega} U_{\alpha, x_\alpha \restriction n}\]
-%   is an open set about each $c_\alpha$.
-% \end{ex}
+  Let $D$ be compact. Consider the open cover
+    \[
+      \{
+        B_{\alpha,0}
+      :
+        \alpha<\omega_1
+      \}
+      \cup
+      \{
+        X\times\{s\}
+      :
+        s\in 2^{<\omega}
+      \}
+    \]
+  and note that the finite subcover for $D$ contains subsets of some
+  $K_F' \cup L_m$.
+\end{proof}
+
+\begin{thm}
+  $\pl K\win\gruKPGame{\pmb X}$.
+\end{thm}
+
+\begin{proof}
+  Since $\{U_\alpha:\alpha<\omega_1\}$ is a point-countable cover,
+  for each $x\in X$ let $\alpha_{x,n}<\omega_1$ yield
+  ordinals such that $x\in U_{\alpha_{x,n}}$ for $n<\omega$.
+
+  Let $M:\pmb X\times \omega\to \mc K(\pmb X)$ as follows:
+    \[
+      M(\pmb x,n)
+        =
+      \left\{
+        \begin{array}{lcl}
+          K_{\{\alpha_{x,m}:m\leq n\}}
+        & : &
+          \pmb x = \<x,s\> \in X\times 2^{<\omega}
+        \\
+          K_{\{\alpha\}}
+        & : &
+          \pmb x = c_\alpha \in C
+        \end{array}
+      \right.
+    \]
+  and use $M$ to define the strategy $\sigma$ for each $\pmb a\in\pmb X^{<\omega}$:
+    \[
+      \sigma(\pmb a)
+        =
+      L_{|\pmb a|}
+        \cup
+      \bigcup_{i< |\pmb a|}
+      M(\pmb a(i),|\pmb a|)
+    \]
+
+  Let $\pmb p:\omega\to\pmb X$ be a legal attack against $\sigma$. Then as
+  $\pmb p(n)\not\in L_n$, for each $\pmb x=\<x,s\>\in X\times 2^{<\omega}$,
+  $X\times\{s\}$ is an open neighborhood of $\pmb x$ which contains finitely
+  many $\pmb p(n)$.
+
+  Then consider $\pmb x=c_\alpha$ for some $\alpha<\omega_1$, and let $n<\omega$.
+  Then if $\pmb p(n)=\<x,s\>$ with $\alpha = \alpha_{x,N}$ for some $N<\omega$,
+  then $\pmb p(m)\not\in B_{\alpha,0}$ for $\max(n,N)<m<\omega$.
+  Or, if $\pmb p(n)=c_\alpha$, then
+  $\pmb p(m)\not\in B_{\alpha,0}$ for $n<m<\omega$.
+  Otherwise, $\pmb p(m)\not\in B_{\alpha,0}$ for any $m<\omega$.
+  In any case, $B_{\alpha,0}$ is a neighborhood of $\pmb x$ which contains finitely
+  many $\pmb p(n)$. Therefore, $\sigma$ is a winning strategy.
+\end{proof}
+
+We will show that there does not exist any winning $k$-Markov strategy for
+$\pl K$ in this game. Knowledge of round number does not assist $\pl K$,
+since she may force $\pl P$ to either stay within $C$, or to seed a growing
+integer by forcing her to play outside $L_{|s|+1}$ in response to
+$\<x,s\>\in X\times 2^{<\omega}$.
+
+\begin{lem}
+  If $\pl K\kmarkwin{k+1}\gruKPGame{\pmb X}$, then
+  $\pl K\ktactwin{k+1}\gruKPGame{\pmb X}$.
+\end{lem}
+
+\begin{proof}
+  Let $\sigma$ be a winning $k+1$-mark for $\pl K$ such that $m\leq n$ and
+  $\ran r \subseteq \ran s$ implies $\sigma(r,m)\subseteq\sigma(s,n)$.
+  For a sequence $p$, let $p\rest^k n=\nu_k(p\rest n)$ give the last $k$
+  terms of $p\rest n$.
+
+  Define $r:\pmb X\to\omega$ by
+    \[
+      r(\pmb x)
+        =
+      \left\{
+        \begin{array}{lcl}
+          |s|
+        & : &
+          \pmb x = \<x,s\> \in X\times 2^{<\omega}
+        \\
+          0
+        & : &
+          \pmb x \in C
+        \end{array}
+      \right.
+    \]
+  and use $r$ to define the $k+1$-tactic $\tau$ by
+    \[
+      \tau(\emptyset)
+        =
+      \sigma(\emptyset,0)
+    \]
+    \[
+      \tau(\pmb t\concat\<\pmb x\>)
+        =
+      L_{r(\pmb x)+1}
+        \cup
+      \{\pmb x\}
+        \cup
+      \sigma(\pmb t\concat\<\pmb x\>,r(\pmb x)+1)
+    \]
+
+  Let $\pmb p:\omega\to\pmb X$ be a legal attack by $\pl P$ against $\tau$.
+  If $\pmb p(n)\in C$ for $N<n<\omega$, then since no $\pmb p(n)$ may be legally
+  repeated, $\{\{\pmb p(n)\}:N<n<\omega\}$ is a discrete collection, making
+  $\{\{\pmb p(n)\}:n<\omega\}$ locally finite.
+
+  Otherwise, let $f\in\omega^\omega$ be increasing and define
+  $\pmb q:\omega\to X\times 2^{<\omega}$ such that $\pmb q(i)=\pmb p(f(i))$,
+  and $\pmb p(j)\in X\times 2^{<\omega}$ implies there is some $i$ with $j=f(i)$.
+  It follows that
+    \[
+      \pmb q(0)
+        =
+      \pmb p(f(0))
+        \not\in
+      \bigcup_{m\leq f(0)}\tau(\pmb p \rest^{k+1} m)
+        \supseteq
+      \tau(\emptyset)
+        =
+      \sigma(\emptyset,0)
+    \]
+
+  Denoting $\pmb q(n)=\<x_n,s_n\>$, it's trivial to note that $|s_0|\geq 0$.
+  Assuming that $|s_m|\geq m$ for $m\leq n$,
+  it then follows that
+    \[
+      \pmb q(n+1)
+        =
+      \pmb p(f(n+1))
+        \not\in
+      \bigcup_{m\leq f(n+1)}\tau(\pmb p\rest^{k+1} m)
+    \]
+    \[
+        \supseteq
+      \bigcup_{m\leq n}\tau(\pmb q\rest^{k+1} m)
+        \supseteq
+      \sigma(\emptyset,0)
+        \cup
+      \bigcup_{m < n}\sigma(\pmb q\rest^{k+1} (m+1),|s_m|+1)
+    \]
+    \[
+        \supseteq
+      \sigma(\emptyset,0)
+        \cup
+      \bigcup_{m < n}\sigma(\pmb q\rest^{k+1} (m+1),m+1)
+    \]
+  and
+    \[
+      \pmb q(n+1)
+        \not\in
+      \tau(\pmb q\rest^{k+1} (n+1))
+        \supseteq
+      L_{r(\pmb q(n))}
+        =
+      L_{|s_n|+1}
+    \]
+  gives $|s_{n+1}|\geq|s_n|+1\geq n+1$.
+  Thus $\pmb q$ is a legal attack on the winning $k+1$-Markov strategy
+  $\sigma$, so the collection $\{\{\pmb q(n)\}:n<\omega\}$ is locally finite.
+  and it follows that $\{\{\pmb p(n)\}:n<\omega\}$ is also locally finite.
+\end{proof}
+
+\begin{lem}
+  If $\pl K\ktactwin{k+2}\gruKPGame{\pmb X}$, then
+  $\pl K\ktactwin{k+1}\gruKPGame{\pmb X}$.
+\end{lem}
+
+\begin{proof}
+  \newcommand{\hi}{\text{height}}
+  \newcommand{\de}{\text{depth}}
+  Fix an arbitrary $y\in X$. For $\pmb t\in \pmb X^{<\omega}$, define the
+  following:
+    \begin{itemize}
+      \item $\hi(\pmb t)<\omega$ satisfying
+            $|s|\leq \hi(\pmb t)$ for each
+            $\<x,s\>\in(X\times 2^{<\omega})\cap \ran{\pmb t}$
+      \item $\de(\pmb t)\in [X]^{<\omega}$ satisfying
+            $x\in\de(\pmb t)$ for each
+            $\<x,s\>\in(X\times 2^{<\omega})\cap \ran{\pmb t}$
+      % \item $\pmb R(\pmb t)\in [\pmb X^{<\omega}]^{<\omega}$ such that
+      %       $\pmb r\in \pmb R(\pmb t)$
+      %       satisfies one of the following:
+      %   \begin{itemize}
+      %     \item $\pmb r(i)=c$ where $c\in C\cap\ran{\pmb t}$
+      %     \item $\pmb r(i)=\<x,s\>$ where $s\leq\hi(\pmb t)$,
+      %                                     $x\in\de(\pmb t)$
+      %     \item $\pmb r(i)=\<y,s\>$ where $s\leq\hi(\pmb t)$
+      %   \end{itemize}
+    \end{itemize}
+
+  For each compact set $C$, define $F(C)\in[\omega_1]^{<\omega}$ and
+  $m(C)<\omega$ such that $C\subseteq K'_{F(C)}\cup L_{m(C)}$.
+
+  Let $\sigma$ be a winning $k+2$-tactic for $\pl K$.
+  For $\pmb t\in \pmb X^{<\omega}$, let $\pmb r\preceq \pmb t$ denote that
+  $\pmb r$ is a subsequence of a permutation of $\pmb t$, and let
+  $\pmb r\preceq_i \pmb t$ denote that $\pmb r$ is a subsequence of a
+  permutation of $\pmb t\concat\<\<y,s\>\>$ for some $s\in 2^{\leq i}$.
+
+  Let $M(\pmb t)=\max_{\pmb r\preceq \pmb t} m(\sigma(\pmb r\rest^{k+2}))$.
+  We construct a $k+1$-tactic $\tau$ for $\pl K$ as follows:
+    \[
+      \tau(\pmb t)
+        =
+      \bigcup_{\pmb r\preceq_{|M(\pmb t)|} \pmb t}
+      \sigma(\pmb r)
+    \]
+  Let $\pmb p:\omega\to\pmb X$ be a legal attack against $\tau$, so
+    \[
+      \pmb p(n)
+        \not\in
+      \bigcup_{m\leq n}
+      \tau(\pmb p\rest^{k+1} m)
+    \]
+  Define the attack $\pmb q:\omega\to\pmb X$ as follows for $i<\omega$,
+  $j<k+1$:
+    \[
+      \pmb q((k+2)i+j) = \pmb p((k+1)i+j)
+    \]
+    \[
+      \pmb q((k+2)i+(k+1)) = \<y,a_{|M()|}\>
+    \]
+
+\end{proof}
 
 % \begin{prop}
-% $K \win \gruKPGame{\mathbb{X}}$.
+% $K \win \gruKPGame{\pmb X}$.
 % \end{prop}
@@
 % \begin{thm}(cor of G, game-theoretic proof by me)
-% $K\not\tactwin\gruKPGame{\mathbb{X}}$.
+% $K\not\tactwin\gruKPGame{\pmb X}$.
 % \end{thm}
@@
 % \begin{thm}
-% $K\not\ktactwin{k}\gruKPGame{\mathbb{X}}$.
+% $K\not\ktactwin{k}\gruKPGame{\pmb X}$.
 % \end{thm}

### 2014-12-03 phd/dissertation/chapter5.tex
reproducing original proof of main ch 5 result

@@
 \begin{lem}
-  If $\pl K\ktactwin{k+2}\gruKPGame{\pmb X}$, then
-  $\pl K\ktactwin{k+1}\gruKPGame{\pmb X}$.
+  If $\pl K\ktactwin{k+1}\gruKPGame{\pmb X}$, then
+  $\pl K\tactwin\gruKPGame{\pmb X}$.
 \end{lem}
@@
 \begin{proof}
-  \newcommand{\hi}{\text{height}}
-  \newcommand{\de}{\text{depth}}
-  Fix an arbitrary $y\in X$. For $\pmb t\in \pmb X^{<\omega}$, define the
-  following:
-    \begin{itemize}
-      \item $\hi(\pmb t)<\omega$ satisfying
-            $|s|\leq \hi(\pmb t)$ for each
-            $\<x,s\>\in(X\times 2^{<\omega})\cap \ran{\pmb t}$
-      \item $\de(\pmb t)\in [X]^{<\omega}$ satisfying
-            $x\in\de(\pmb t)$ for each
-            $\<x,s\>\in(X\times 2^{<\omega})\cap \ran{\pmb t}$
-      % \item $\pmb R(\pmb t)\in [\pmb X^{<\omega}]^{<\omega}$ such that
-      %       $\pmb r\in \pmb R(\pmb t)$
-      %       satisfies one of the following:
-      %   \begin{itemize}
-      %     \item $\pmb r(i)=c$ where $c\in C\cap\ran{\pmb t}$
-      %     \item $\pmb r(i)=\<x,s\>$ where $s\leq\hi(\pmb t)$,
-      %                                     $x\in\de(\pmb t)$
-      %     \item $\pmb r(i)=\<y,s\>$ where $s\leq\hi(\pmb t)$
-      %   \end{itemize}
-    \end{itemize}
+  Let $\sigma$ be a winning $(k+1)$-tactical strategy, and without loss of
+  generality assume it ignores order.
 
-  For each compact set $C$, define $F(C)\in[\omega_1]^{<\omega}$ and
-  $m(C)<\omega$ such that $C\subseteq K'_{F(C)}\cup L_{m(C)}$.
+  Define $S(x_0,\dots,x_{k},n)\in [C]^{<\omega}$ (increasing on $n$) and
+  $n<m(x_0,\dots,x_{k},n)<\omega$ such that for each
+  $\<x_0,\dots,x_{k}\>\in X^{k+1}$,
+  \[
+    \bigcup_{s_0,\dots,s_k \in 2^{\leq n}}
+    \sigma(\<x_0,s_0\>,\dots,\<x_{k},s_{k}\>)
+      \subseteq
+    K'_{S(x_0,\dots,x_{k},n)} \cup L_{m(x_0,\dots,x_{k},n)}
+  \]
+  and assume without loss of generality that
+  \[
+    \sigma(\<x_0,s_0\>,\dots,\<x_{k},s_{k}\>)
+      =
+    K'_{S(x_0,\dots,x_{k},\max(|s_0|,\dots,|s_k|))}
+      \cup
+    L_{m(x_0,\dots,x_{k},\max(|s_0|,\dots,|s_k|))}
+  \]
 
-  Let $\sigma$ be a winning $k+2$-tactic for $\pl K$.
-  For $\pmb t\in \pmb X^{<\omega}$, let $\pmb r\preceq \pmb t$ denote that
-  $\pmb r$ is a subsequence of a permutation of $\pmb t$, and let
-  $\pmb r\preceq_i \pmb t$ denote that $\pmb r$ is a subsequence of a
-  permutation of $\pmb t\concat\<\<y,s\>\>$ for some $s\in 2^{\leq i}$.
+  Select an arbitrary point $y \in X$.
+  Let $M^0(x,n)=m(x,y,\dots,y,n)$ and $M^{i+1}(x,n)=M^0(x,M^i(x,n)+1)$, and
+  define the tactical strategy $\tau$ as follows:
+  \[
+    \tau(\<x,s\>)
+      =
+    K'_{S(x,y,\dots,y,M^k(x,|s|)+1)}
+      \cup
+    L_{M^k(x,|s|)+1}
+  \]
 
-  Let $M(\pmb t)=\max_{\pmb r\preceq \pmb t} m(\sigma(\pmb r\rest^{k+2}))$.
-  We construct a $k+1$-tactic $\tau$ for $\pl K$ as follows:
+  Let $\pmb p:\omega\to X\times 2^{<\omega}$ be a legal attack against
+  $\tau$, such that $\pmb p(n)=\<x_n,s_n\>$.
+  Then consider the attack $\pmb q:\omega\to X\times 2^{<\omega}$ against
+  $\sigma$ defined by
     \[
-      \tau(\pmb t)
-        =
-      \bigcup_{\pmb r\preceq_{|M(\pmb t)|} \pmb t}
-      \sigma(\pmb r)
-    \]
-  Let $\pmb p:\omega\to\pmb X$ be a legal attack against $\tau$, so
-    \[
-      \pmb p(n)
-        \not\in
-      \bigcup_{m\leq n}
-      \tau(\pmb p\rest^{k+1} m)
-    \]
-  Define the attack $\pmb q:\omega\to\pmb X$ as follows for $i<\omega$,
-  $j<k+1$:
-    \[
-      \pmb q((k+2)i+j) = \pmb p((k+1)i+j)
+      \pmb q((k+1)n)=\pmb p(n)=\<x_n,s_n\>
     \]
     \[
-      \pmb q((k+2)i+(k+1)) = \<y,a_{|M()|}\>
+      \pmb q((k+1)n+(i+1))=\<y, a_{M^i(x_n,|s_n|)}\>
     \]
+  for $i<k$.
+
+  Since $\pmb p(n+1)\not\in\tau(\pmb p(n))$, it follows that
+  $|s_{n+1}|\geq M^{i+1}(x_n,|s_n|)+1$; furthermore, for $i<k$,
+    \[
+      |s_n|
+        <
+      M^i(x_n,|s_n|)
+        <
+      M^i(x_n,|s_n|)+1
+        \leq
+      M^{i+1}(x_n,|s_n|)
+        <
+      M^{i+1}(x_n,|s_n|)+1
+        \leq
+      |s_{n+1}|
+    \]
+  so the second coordinate of $\pmb q(n)$ is always strictly increasing.
+
+  By the definition of $\tau$,
+  $\pmb q((k+1)n)=\pmb p(n)\not\in\sigma(\pmb q\rest^{k+1} (k+1)n)$.
+  Since $\pmb q((k+1)n+(i+1))=\<y, a_{M^i(x_n,|s_n|)}\>\in X\times A$,
+  $\pmb q((k+1)n+(i+1))\not\in K'_F$ for any $F\in[\omega_1]^{<\omega}$.
+
+  Then it's sufficient to note that
+    \[
+      |a_{M^0(x_n,|s_n|)}|
+        >
+      M^0(x_n,|s_n|)
+        =
+      m(x_n,y,\dots,y,|s_n|)
+    \]
+  and
+    \[
+      |a_{M^{i+1}(x_n,|s_n|)}|
+        >
+      M^{i+1}(x_n,|s_n|)
+        =
+      m(x_n,y,\dots,y,M^i(x_n,|s_n|)+1)
+    \]
+  to show that
+  $\pmb q((k+1)n+(i+1))\not\in\sigma(\pmb q\rest^{k+1} (k+1)n+(i+1))$.
+
+% Note that $m(x_0,\dots,x_{k},\max(|s_0|,\dots,|s_k|))$ is increasing throughout this play of the game versus $\sigma$:
+%   \[
+%     m(x_i,x',\dots,x',\max(|s_i|,|{z_{M^0(x_i,|s_i|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_i,|s_i|)}}^\frown\<1\>|))
+%   \]
+%   \[
+%     =
+%     m(x_i,x',\dots,x',|{z_{M^{k-1}(x_i,|s_i|)}}^\frown\<1\>|)
+%   \]
+%   \[
+%     =
+%     m(x_i,x',\dots,x',M^{k-1}(x_i,|s_i|)+1)
+%   \]
+%   \[
+%     \leq
+%     |s_{i+1}|
+%   \]
+%   \[
+%     <
+%     M^0(x_{i+1},|s_{i+1}|)
+%   \]
+%   \[
+%     =
+%     m(x_{i+1},x',\dots,x',|s_{i+1}|)
+%   \]
+%   \[
+%     =
+%     m(x_{i+1},x',\dots,x',\max(|s_{i+1}|,|{z_{M^0(x_i,|s_i|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_i,|s_i|)}}^\frown\<1\>|))
+%   \]
+%   \[
+%     =
+%     |{z_{m(x_{i+1},x',\dots,x',|s_{i+1}|)}}|
+%   \]
+%   \[
+%     =
+%     |{z_{M^0(x_{i+1},|s_{i+1}|)}}|
+%   \]
+%   \[
+%     <
+%     |{z_{M^0(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|
+%   \]
+%   \[
+%     <
+%     m(x_{i+1},x',\dots,x',|{z_{M^0(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|)
+%   \]
+%   \[
+%     =
+%     m(x_{i+1},x',\dots,x',\max(|s_{i+1}|,|{z_{M^0(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|,|{z_{M^1(x_{i},|s_{i}|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_{i},|s_{i}|)}}^\frown\<1\>|))
+%   \]
+%   \[
+%     \vdots
+%   \]
+%   \[
+%     <
+%     m(x_{i+1},x',\dots,x',\max(|s_{i+1}|,|{z_{M^0(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|))
+%   \]
+
+% We turn to showing that $\<x', {z_{M^j(x_{i+1},|s_{i+1}|)}}^\frown\<1\>\>$ is always a legal move.
+Since ${z_{M^j(x_{i+1},|s_{i+1}|)}}^\frown\<1\>$ is on the antichain avoided by any $K^*$, the problem is reduced to showing that this move isn't forbidden by
+%   \[
+%     L_{m(x_{i+1},x',\dots,x',\max(|s_{i+1}|,|{z_{M^0(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|,\dots,|{z_{M^{j-1}(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|,|{z_{M^{j}(x_{i},|s_{i}|)}}^\frown\<1\>|,\dots,|{z_{M^{k}(x_{i},|s_{i}|)}}^\frown\<1\>|))}
+%   \]
+%   \[
+%     =
+%     L_{m(x_{i+1},x',\dots,x',|{z_{M^{j-1}(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|)}
+%   \]
+% which we can see here:
+%   \[
+%     m(x_{i+1},x',\dots,x',|{z_{M^{j-1}(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|)
+%   \]
+%   \[
+%     =
+%     m(x_{i+1},x',\dots,x',M^{j-1}(x_{i+1},|s_{i+1}|)+1)
+%   \]
+%   \[
+%     =
+%     M^0(x_{i+1},M^{j-1}(x_{i+1},|s_{i+1}|)+1)
+%   \]
+%   \[
+%     =
+%     M^j(x_{i+1},s_{i+1})
+%   \]
+%   \[
+%     <
+%     |{z_{M^j(x_{i+1},|s_{i+1}|)}}^\frown\<1\>|
+%   \]
+
+% We can conclude by showing that $\<x_{i+1},s_{i+1}\>$ is always a legal move. We can see it avoids
+%   \[
+%   L_{m(x_{i},x',\dots,x',\max(|s_{i}|,|{z_{M^0(x_i,|s_i|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_i,|s_i|)}}^\frown\<1\>|))}
+%   \]
+% since
+%   \[
+%     m(x_{i},x',\dots,x',\max(|s_{i}|,|{z_{M^0(x_i,|s_i|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_i,|s_i|)}}^\frown\<1\>|))
+%   \]
+%   \[
+%     =
+%     m(x_{i},x',\dots,x',|{z_{M^{k-1}(x_i,|s_i|)}}^\frown\<1\>|)
+%   \]
+%   \[
+%     =
+%     m(x_{i},x',\dots,x',M^{k-1}(x_i,|s_i|)+1)
+%   \]
+%   \[
+%     \leq
+%     |s_{i+1}|
+%   \]
+
+% Since $\<x_{i+1},s_{i+1}\>$ was legal against $\tau$, for $h\leq i$ it avoided
+%   \[
+%     K^*_{S(x_h,x',\dots,x',M^{k-1}(x_h,|s_h|)+1)}
+%   \]
+%   \[
+%     =
+%     K^*_{S(x_h,x',\dots,x',\max(|s_h|,|{z_{M^{0}(x_h,|s_h|)}}^\frown\<1\>|,\dots,|{z_{M^{k-1}(x_h,|s_h|)}}^\frown\<1\>|))}
+%   \]
+% and when $h<i$, we see it avoids both:
+%   \[
+%     K^*_{S(x_{h+1},x',\dots,x',\max(|s_{h+1}|,|{z_{M^0(x_{h+1},|s_{h+1}|)}}^\frown\<1\>|,\dots,|{z_{M^{j-1}(x_{h+1},|s_{h+1}|)}}^\frown\<1\>|,|{z_{M^{j}(x_{h},|s_{h}|)}}^\frown\<1\>|,\dots,|{z_{M^{k}(x_{h},|s_{h}|)}}^\frown\<1\>|))}
+%   \]
+%   \[
+%     =
+%     K^*_{S(x_{h+1},x',\dots,x',|{z_{M^{j-1}(x_{h+1},|s_{h+1}|)}}^\frown\<1\>|)}
+%   \]
+%   \[
+%     =
+%     K^*_{S(x_{h+1},x',\dots,x',M^{j-1}(x_{h+1},|s_{h+1}|)+1)}
+%   \]
+%   \[
+%     \subseteq
+%     K^*_{S(x_{h+1},x',\dots,x',M^{k-1}(x_{h+1},|s_{h+1}|)+1)}
+%   \]
+% and:
+%   \[
+%     K^*_{S(x_{h+1},x',\dots,x',\max(|s_{h+1}|,|{z_{M^0(x_{h},|s_{h}|)}}^\frown\<1\>|,\dots,|{z_{M^{k}(x_{h},|s_{h}|)}}^\frown\<1\>|))}
+%   \]
+%   \[
+%     =
+%     K^*_{S(x_{h+1},x',\dots,x',|s_{k+1}|)}
+%   \]
+%   \[
+%     \subseteq
+%     K^*_{S(x_{h+1},x',\dots,x',M^{k-1}(x_{h+1},|s_{h+1}|)+1)}
+%   \]
 

### 2014-12-03 phd/dissertation/chapter5.tex
finish rewrite of main ch 5 proof

--- 2014-12-02 phd/dissertation/chapter5.tex
@@
 \begin{proof}
-  \newcommand{\hi}{\text{height}}
-  \newcommand{\de}{\text{depth}}
-  Fix an arbitrary $y\in X$. For $\pmb t\in \pmb X^{<\omega}$, define the
-  following:
-    \begin{itemize}
-      \item $\hi(\pmb t)<\omega$ satisfying
-            $|s|\leq \hi(\pmb t)$ for each
-            $\<x,s\>\in(X\times 2^{<\omega})\cap \ran{\pmb t}$
-      \item $\de(\pmb t)\in [X]^{<\omega}$ satisfying
-            $x\in\de(\pmb t)$ for each
-            $\<x,s\>\in(X\times 2^{<\omega})\cap \ran{\pmb t}$
-      % \item $\pmb R(\pmb t)\in [\pmb X^{<\omega}]^{<\omega}$ such that
-      %       $\pmb r\in \pmb R(\pmb t)$
-      %       satisfies one of the following:
-      %   \begin{itemize}
-      %     \item $\pmb r(i)=c$ where $c\in C\cap\ran{\pmb t}$
-      %     \item $\pmb r(i)=\<x,s\>$ where $s\leq\hi(\pmb t)$,
-      %                                     $x\in\de(\pmb t)$
-      %     \item $\pmb r(i)=\<y,s\>$ where $s\leq\hi(\pmb t)$
-      %   \end{itemize}
-    \end{itemize}
+  Let $\sigma$ be a winning $(k+1)$-tactical strategy, and without loss of
+  generality assume it ignores order.
 
-  For each compact set $C$, define $F(C)\in[\omega_1]^{<\omega}$ and
-  $m(C)<\omega$ such that $C\subseteq K'_{F(C)}\cup L_{m(C)}$.
+  Define $F(x_0,\dots,x_{k},n)\in [C]^{<\omega}$ and
+  $m(x_0,\dots,x_{k},n)\in\omega\setminus(n+1)$, both increasing on $n$,
+  such that for each $\<x_0,\dots,x_{k}\>\in X^{k+1}$,
+  \[
+    \bigcup_{s_0,\dots,s_k \in 2^{\leq n}}
+    \sigma(\<x_0,s_0\>,\dots,\<x_{k},s_{k}\>)
+      \subseteq
+    K'_{F(x_0,\dots,x_{k},n)} \cup L_{m(x_0,\dots,x_{k},n)}
+  \]
 
-  Let $\sigma$ be a winning $k+2$-tactic for $\pl K$.
-  For $\pmb t\in \pmb X^{<\omega}$, let $\pmb r\preceq \pmb t$ denote that
-  $\pmb r$ is a subsequence of a permutation of $\pmb t$, and let
-  $\pmb r\preceq_i \pmb t$ denote that $\pmb r$ is a subsequence of a
-  permutation of $\pmb t\concat\<\<y,s\>\>$ for some $s\in 2^{\leq i}$.
+  Select an arbitrary point $y \in X$.
+  Let
+    \[
+      M^0(x,n)=n
+    \]
+    \[
+      M^{i+1}(x,n)=m(x,y,\dots,y,M^i(x,n)+1)
+    \]
+  and define the tactical strategy $\tau$ as follows:
+  \[
+    \tau(\emptyset)
+      =
+    \sigma(\emptyset)
+  \]
+  \[
+    \tau(\<c_\alpha\>)
+      =
+    \{c_\alpha\}
+  \]
+  \[
+    \tau(\<\<x,s\>\>)
+      =
+    K'_{F(x,y,\dots,y,M^k(x,|s|)+1)}
+      \cup
+    L_{m(x,y,\dots,y,M^k(x,|s|)+1)}
+  \]
 
-  Let $M(\pmb t)=\max_{\pmb r\preceq \pmb t} m(\sigma(\pmb r\rest^{k+2}))$.
-  We construct a $k+1$-tactic $\tau$ for $\pl K$ as follows:
+  Let $\pmb p:\omega\to \pmb X$ be a legal attack against
+  $\tau$, and assume $\pmb p(n)=\<x_n,s_n\>\in X\times 2^{<\omega}$.
+  Then consider the attack $\pmb q:\omega\to X\times 2^{<\omega}$ against
+  $\sigma$ defined by, for $n<\omega$ and $i<k$,
     \[
-      \tau(\pmb t)
+      \pmb q((k+1)n)=\pmb p(n)=\<x_n,s_n\>
+    \]
+    \[
+      \pmb q((k+1)n+(i+1))=\<y, a_{M^{i+1}(x_n,|s_n|)}\>
+    \]
+
+  Since
+    \[
+      \<x_{n+1},s_{n+1}\>
         =
-      \bigcup_{\pmb r\preceq_{|M(\pmb t)|} \pmb t}
-      \sigma(\pmb r)
+      \pmb p(n+1)
+        \not\in
+      \tau(\<\pmb p(n)\>)
+        \supseteq
+      L_{M^{k+1}(x_n,|s_n|)+1}
     \]
-  Let $\pmb p:\omega\to\pmb X$ be a legal attack against $\tau$, so
+  it follows that
+  $|s_{n+1}|\geq M^{i+1}(x_n,|s_n|)+1$ for $i<k$; furthermore,
     \[
+      |s_n|
+        \leq
+      M^i(x_n,|s_n|)
+        <
+      M^i(x_n,|s_n|)+1
+        \leq
+      M^{i+1}(x_n,|s_n|)
+        <
+      M^{i+1}(x_n,|s_n|)+1
+        \leq
+      |s_{n+1}|
+    \]
+  so the second coordinate of $\pmb q(n)$ is always strictly increasing.
+
+  By the definition of $\tau$,
+    \[
+      \pmb q((k+1)n)
+        =
       \pmb p(n)
@@
       \bigcup_{m\leq n}
-      \tau(\pmb p\rest^{k+1} m)
-    \]
-  Define the attack $\pmb q:\omega\to\pmb X$ as follows for $i<\omega$,
-  $j<k+1$:
-    \[
-      \pmb q((k+2)i+j) = \pmb p((k+1)i+j)
-    \]
-    \[
-      \pmb q((k+2)i+(k+1)) = \<y,a_{|M()|}\>
+      \tau(\pmb p\rest^1 m)
+        \supseteq
+      \bigcup_{m\leq (k+1)n}
+      \sigma(\pmb q\rest^{k+1} m)
     \]
 
+  Since
+    \[
+      \pmb q((k+1)n+(i+1))
+        =
+      \<y, a_{M^{i+1}(x_n,|s_n|)}\>
+        \in
+      X\times A
+    \]
+  it follows that $\pmb q((k+1)n+(i+1))\not\in K'_F$ for any
+  $F\in[\omega_1]^{<\omega}$.
+
+  Then it's sufficient to note that
+    \[
+      |a_{M^{i+1}(x_n,|s_n|)}|
+        =
+      M^{i+1}(x_n,|s_n|) + 1
+        >
+      m(x_n,y,\dots,y,M^i(x_n,|s_n|)+1)
+    \]
+  to show that
+    \[
+      \pmb q((k+1)n+(i+1))
+        =
+      \<y, a_{M^{i+1}(x_n,|s_n|)}\>
+        \not\in
+      L_{m(x_n,y,\dots,y,M^i(x_n,|s_n|)+1)}
+    \]
+  and therefore $\pmb q((k+1)n+(i+1))$ is a legal move.
+
+  As a result, $\pmb q$ is a legal attack against $\sigma$, and
+  $\{\{\pmb q(n)\}:n<\omega\}\supseteq\{\{\pmb p(n)\}:n<\omega\}$ are
+  both locally finite.
+
+  Finally, if the range of $\pmb p$ intersects $C$, those moves may be safely
+  ignored as they cannot be repeated and lay in a closed discrete set,
+  so the proof is complete.
 \end{proof}

### 2014-12-04 phd/dissertation/chapter5.tex
finish chapter 5 draft

@@
 immediately extended to $\gruKPGame{X}$. However, this section will
-demonstrate a non-trivial example of a space $\pmb X$ for which
+demonstrate a non-trivial example of a locally-compact space $\pmb X$ for which
 $\pl K\win\gruKPGame{\pmb X}$ but $\pl K\not\kmarkwin{k}\gruKPGame{\pmb X}$
 for any $k<\omega$.
-
-\begin{thm}
-  There exists a compact, zero-dimensional topological space $X$
-  such that $X$ has a point-countable cover
-  $\mc{U} = \{U_\alpha : \alpha<\omega_1\}$ of distinct clopen sets.
-\end{thm}
-
-\begin{proof}
-  (TODO)
-\end{proof}
 
@@
   of copies of a zero-dimensional, compact space $X$ with a point-countable
-  cover $\mc{U} = \{U_\alpha : \alpha<\omega_1\}$ of
-  clopen sets which is not $\sigma$-point-finite, along with an uncountable
-  subset of the Cantor set
+  cover $\mc{U} = \{U_\alpha : \alpha<\omega_1\}$ of distinct
+  clopen sets, along with an uncountable subset of the Cantor set
   $C=\{c_\alpha:\alpha<\omega_1\}\in [2^\omega]^{\omega_1}$.
-  The topology on $\pmb X$ is
-  given by decaring $U\times\{s\}$ to be a open
+  The topology on $\pmb X$ is given by decaring $U\times\{s\}$ to be a open
   neighborhood of $\<x,s\>\in X\times 2^{<\omega}$ for each
@@
 
+\begin{cor}
+  $\pmb X$ is $\sigma$-metacompact if and only if $\pmb X$ is metacompact.
+\end{cor}
+
 \begin{lem}
@@
 
-% \begin{prop}
-% $K \win \gruKPGame{\pmb X}$.
-% \end{prop}
+Therefore if $\pmb X$ can be constructed which is not metacompact, then
+$\pl K$ lacks a $k$-Markov strategy for any $k<\omega$.
 
-% \begin{thm}(cor of G, game-theoretic proof by me)
-% $K\not\tactwin\gruKPGame{\pmb X}$.
-% \end{thm}
+\begin{thm}
+  $\pmb X$ is metacompact
+    if and only if
+  $\{U_\alpha:\alpha<\omega_1\}$ is $\sigma$-point-finite.
+\end{thm}
 
-% \begin{thm}
-% $K\not\ktactwin{k}\gruKPGame{\pmb X}$.
-% \end{thm}
+\begin{proof}
+  Let $\omega_1=\bigcup_{n<\omega}A_n$ such that
+  $\{U_\alpha:\alpha\in A_n\}$ is point-finite for each $n<\omega$.
+
+  Let $\mc U$ be a cover of $\pmb X$, and for each $s\in 2^\omega$
+  let $\mc V_s$ be a finite open refinement of $\mc C$ covering the compact
+  set $X\times\{s\}$. Then let $\mc W_n = \{B_{\alpha,n_\alpha}:\alpha\in A_n\}$
+  be an open refinement of $\mc C$ for each $n<\omega$, and note that it
+  is point-finite. It follows that
+  $\mc U' = \bigcup_{s\in 2^{<\omega}} \mc V_s \cup \bigcup_{n<\omega} \mc W_n$
+  is an open $\sigma$-point-finite refinement of $\mc U$, so $\pmb X$
+  is $\sigma$-metacompact, and therefore it is metacompact.
+
+  For the other direction, consider the open cover
+  $\mc U = \{B_{\alpha,0}:\alpha<\omega_1\}$ of the closed subset $C$ of
+  metacompact $\pmb X$, and let $\{B_{\alpha,n_\alpha}:\alpha<\omega_1\}$ be
+  a point-finite refinement. Then
+  $\mc U_s = \{ U_\alpha : c_\alpha \rest n_\alpha = s\}$ is
+  point-finite for $s\in 2^{<\omega}$ and
+  $U_\alpha\in\mc U_{c_\alpha\rest n_\alpha}$ for each $\alpha<\omega_1$.
+  Therefore $\mc U = \bigcup_{s\in 2^{<\omega}} \mc U_s$ is
+  $\sigma$-point-finite.
+\end{proof}
+
+The following example was suggested by Gary Gruenhage.
+
+\begin{thm}
+  There exists a compact, zero-dimensional topological space $X$
+  with a clopen cover $\{U_\alpha : \alpha<\omega_1\}$ of distinct
+  sets which is not $\sigma$-point-finite.
+\end{thm}
+
+\begin{proof}
+  Let $Y$ be a zero-dimensional Corson compact space which is not Eberlein
+  compact; one such space was constructed in \cite{Marciszewski1991291}
+  and let $X=Y^2$.
+  Then by characterizations of Corson and Eberlien compacts found in
+  \cite{MR752278},
+  $Y^2\setminus\Delta$ is meta-Lindel\"of but not $\sigma$-metacompact, so
+  there exists a point-countable clopen cover $\mc U$ of $Y^2\setminus\Delta$
+  which is not $\sigma$-point-finite. Then $\mc U\cup\{X\}$ is a point-countable
+  clopen cover of $X$ which is not $\sigma$-point-finite.
+\end{proof}
+
+\begin{cor}
+  There exists a space $X$ such that $\pl K\win\gruKPGame{X}$ but
+  $\pl K\not\kmarkwin{k} \gruKPGame{X}$ for all $k<\omega$.
+\end{cor}
+
+So the following question remains open:
+
+\begin{ques}
+  Does $\pl K\ktactwin{k+1}\gruKPGame{X}$ imply
+  $\pl K\tactwin\gruKPGame{X}$ always? What about for Markov strategies?
+\end{ques}

### 2014-12-04 phd/dissertation/chapter2.tex
overall cleanup

@@
   If a winning strategy exists for a player $\pl A$ in the game $G$, then we
-  write $\pl A \win G$. Otherwise, we write $\pl A \not\win G$.
+  write $\pl A \win G$. Otherwise, we write $\pl A \notwin G$.
 \end{defn}
@@
 If we wish to show that a winning strategy does not exist for a player
-(i.e. $\pl A\not\win G$), we
+(i.e. $\pl A\notwin G$), we
 often consider an arbitrary legal strategy, and use it to define a legal
@@
   $\pl A\win \bakergame{\mathbb{R}}$, since $a_n$ must converge to some
-  real number. This implies $\pl B\not\win \bakergame{\mathbb{R}}$, and thus
+  real number. This implies $\pl B\notwin \bakergame{\mathbb{R}}$, and thus
   $\mathbb{R}$ is not countable.
@@
 \begin{thm}
-$\pl E\not\win \bmgame{X}$ if and only if $X$ is a Baire space.
+$\pl E\notwin \bmgame{X}$ if and only if $X$ is a Baire space.
 \cite{MR0431104}

### 2014-12-04 phd/dissertation/chapter5.tex
overall cleanup

@@
 \begin{thm}
-  $\pl K\not\prewin \gruKLGame{\omega\cup\{\mc F\}}$ for any free
+  $\pl K\notprewin \gruKLGame{\omega\cup\{\mc F\}}$ for any free
   ultrafilter $\mc F$.
@@
   If $\mc F$ is a selective ultrafilter, then
-  $\pl K\not\prewin \gruKPGame{\omega\cup\{\mc F\}}$.
+  $\pl K\notprewin \gruKPGame{\omega\cup\{\mc F\}}$.
 \end{thm}
@@
 demonstrate a non-trivial example of a locally-compact space $\pmb X$ for which
-$\pl K\win\gruKPGame{\pmb X}$ but $\pl K\not\kmarkwin{k}\gruKPGame{\pmb X}$
+$\pl K\win\gruKPGame{\pmb X}$ but $\pl K\notkmarkwin{k}\gruKPGame{\pmb X}$
 for any $k<\omega$.
@@
   There exists a space $X$ such that $\pl K\win\gruKPGame{X}$ but
-  $\pl K\not\kmarkwin{k} \gruKPGame{X}$ for all $k<\omega$.
+  $\pl K\notkmarkwin{k} \gruKPGame{X}$ for all $k<\omega$.
 \end{cor}

### 2014-12-04 phd/dissertation/abstract.tex
finish first draft of dissertation

%!TEX root = dissertation.tex
% ^ leave for LaTeXTools build functionality

\begin{abstract}
A topological game $G(X)$ is a two-player game which characterizes
properties of a topological space $X$ based upon the existence of winning
perfect-information
strategies for players in the game. If the property $P$ is characterized by a
player having a winning perfect information strategy, then a property
stronger than $P$ is characterized by that player having a winning
limited information strategy. This paper investigates the existence of
limited information strategies for four types of topological games
from the literature, and the topological properties
characterized by those strategies.
\end{abstract}

### 2014-12-04 phd/dissertation/acknowledgments.tex
finish first draft of dissertation

%!TEX root = dissertation.tex
% ^ leave for LaTeXTools build functionality

\begin{acknowledgments}
I'm very grateful for the support of all my friends and family during
the completion of this manuscript, particularly for all the faculty members
and graduate student colleagues I've worked with over the years at
Auburn. I'd like especially to thank my
adviser Gary Gruenhage for all his support and insight on writing this
paper and beginning my mathematical career.

This dissertation is dedicated to my wife Jessica, for her love and
encouragement.
\end{acknowledgments}

### 2014-12-04 phd/dissertation/chapter2.tex
finish first draft of dissertation

@@
 
-\chapter{Toplogical Games and Strategies\\ of Perfect and Limited Information}
+\chapter{Introduction}
 
 The goal of this paper is to explore the applications of limited information
-strategies in existing topological games. There are a variety of frameworks
-for modeling such games, so we establish one within this chapter which we
-will use for this manuscript.
+strategies in existing topological games.
 
@@
 of a topological game is the Banach-Mazur game, proposed by Stanislaw Mazur
-as Problem 43 in Stefan Banach's Scottish Book (1935). A more comprehensive
+as Problem 43 in Stefan Banach's Scottish Book in 1935, and solved by
+Banach later that year \cite{MR666400}. A more comprehensive
 history of the Banacy-Mazur and other topological games may be found in
@@
 $N_{n+1}$ such that
-$N_{n+1}\subseteq\cl{N_{n+1}}\subseteq O_{n+1}\subseteq N_n$
-(possible since $N_n$ is a compact Hausdorff $\Rightarrow$ normal space).
+$N_{n+1}\subseteq\cl{N_{n+1}}\subseteq E_{n+1}\subseteq N_n$.
 Since $\bigcap_{n<\omega} E_n = \bigcap_{n<\omega} N_n$ is the decreasing

### 2014-12-14 phd/dissertation/chapter1.tex
introductory chapter

@@
 
-Basic overview of combinatorial games, topological games, limited info strategies,
-and applications in topology.
+Topological games have been studied since the 1930s to characterize
+properties of topological spaces. Generally speaking, a topological game $G(X)$
+is a two player game defined for each topological space $X$ such that a
+topological property $P$ is characterized by a player $\pl A$
+having a so-called ``winning'' strategy for $G(X)$ which cannot be countered
+by the opponent, denoted $\pl A\win G(X)$.
 
-% \section{heading}
+The study of limited information strategies in topological games involves
+the following observation. If the existence of a winning strategy for a player
+in $G(X)$ characterizes property $P$, then the existence of a winning strategy
+which doesn't require perfect information about the history of the game
+characterizes a (perhaps non-strictly) stronger property $Q$.
 
-% \subsection{other heading}
+This document is organized into five chapters in addition to this introductory
+chapter. The second provides preliminary definitions and conventions used
+throughout the paper, and the remaining chapters each consider different
+topological games from the literature and extend results on these games
+by considering limited information strategies.
+
+The first game considered is Gruenhage's convergence game $\gruConGame{X}{x}$,
+originally called the $W$-game and introduced in \cite{MR0428275} to
+answer a question of Phil Zenor, and later used to characterize the $W$-space
+property generalizing first-countability. With regards to limited information
+and the one-point compactification of an uncountable cardinal, denoted
+$\oneptcomp\kappa$, Peter Nyikos
+noted that the first player $\pl O$ has a winning tactical strategy considering
+only the most recent move of the opponent, denoted
+$\pl O\tactwin\gruConGame{\oneptcomp\kappa}{\infty}$. If the game is
+slightly altered to $\gruConGameHard{X}{x}$, perfect information strategies are
+preserved. However, Nyikos demonstrated that $\pl O$ lacks a winning Markov
+strategy considering only the most recent move of the opponent and the round
+number, denoted $\pl O\notmarkwin\gruConGameHard{\oneptcomp\kappa}{\infty}$.
+This result has been extended as follows:
+
+\begin{thm*}
+  $\pl O\notkmarkwin{k}\gruConGameHard{\oneptcomp\kappa}{\infty}$ for
+  $\kappa>\omega$, $k<\omega$.
+  That is, $\pl O$ cannot force a win in the game with a $k$-Markov strategy
+  which only considers $k$ previous moves of the opponent and the round number.
+\end{thm*}
+
+The game is made easier for $\pl O$ by weakening the game to
+$\gruClusGameHard{X}{x}$, exchanging the convergence requirement with
+clustering. In this scenario, the author has shown the size of the
+uncountable cardinal $\kappa$ matters.
+
+\begin{thm*}
+  $\pl O\markwin\gruClusGameHard{\oneptcomp\kappa}{\infty}$ if and only if
+  $\kappa\leq\omega_1$.
+\end{thm*}
+
+Based upon this game is a relatively new game from the literature,
+Bell's ``proximal'' game $\bellConGame{X}$. Peter Nyikos noted that
+Corson compact spaces satisfy $\pl D\win\bellConGame{X}$, and asked if this
+in fact was a characterization of Corson compacts. The author
+answered this question with Gary Gruenhage in $\cite{MR3227201}$.
+
+\begin{thm*}
+  Among compact Hausdorff spaces, $X$ is Corson compact if and only if
+  $\pl D\win\bellConGame{X}$.
+\end{thm*}
+
+Many perfect information results on $\bellConGame{X}$ may be easily extended to
+limited information analogs, but others are more elusive. Bell showed
+in \cite{MR3239205} that $\pl D\win\bellConGame{X}$ extends to arbitrary
+sigma-products, but the proof makes non-trivial use of perfect information.
+Thus for $k$-Markov strategies, the result has only been shown to hold for
+countable products.
+
+\begin{thm*}
+  For $k<\omega$, if $\pl D\kmarkwin{k}\bellConGame{X_i}$ for all $i<\omega$,
+  then $\pl D\kmarkwin{k}\bellConGame{\prod_{i<\omega} X_i}$.
+\end{thm*}
+
+Another game due to Gruenhage is the compact-point game $\gruKPGame{X}$
+which may be used to characterize metacompactness and $\sigma$-metacompactness
+among locally compact spaces using tactical and Markov strategies. Using
+predetermined strategies which only consider the round number:
+
+\begin{thm*}
+  For locally compact spaces, $\pl K\prewin\gruKPGame{X}$ if and only if
+  $X$ is hemicompact.
+\end{thm*}
+
+The compact-compact variation $\gruKLGame{X}$ may be used to characterize
+paracompactness among locally compact spaces
+using perfect information strategies.
+However, the existence of winning predetermined strategies for $\gruKLGame{X}$
+coincides
+with $\gruKPGame{X}$ when considering locally compact or even compactly generated
+spaces. By investigating the subspace $\omega\cup\{\mc F\}$ of the Stone-Cech
+compactification $\beta\omega$ consisting of a single free ultrafilter,
+a distinction between the two games is revealed.
+
+\begin{thm*}
+  There exists a free ultrafilter $\mc F$ such that
+  $\pl K \prewin\gruKPGame{\omega\cup\{\mc F\}}$, but
+  $\pl K \notprewin\gruKLGame{\omega\cup\{\mc F\}}$ for any free
+  ultrafilter $\mc F$.
+\end{thm*}
+\begin{thm*}
+  Assuming $CH$, there exists a free ultrafilter $\mc S$ such that
+  $\pl K \notprewin\gruKPGame{\omega\cup\{\mc S\}}$.
+\end{thm*}
+
+A winning $k+1$-Markov strategy for $\gruConGame{X}{x}$ may be improved to
+a winning Markov strategy; however, it remains open whether this same
+result holds true for $\gruKPGame{X}$. The chapter on $\gruKPGame{X}$ concludes
+with a class of spaces which may seem to provide a counterexample at first,
+however:
+
+\begin{thm*}
+  The space $\pmb X$ satisfies $\pl K\win\gruKPGame{\pmb X}$, but
+  $\pl K\notkmarkwin{k}\gruKPGame{\pmb X}$ for all $k<\omega$.
+\end{thm*}
+
+The final chapter is based upon one of the oldest topological games:
+the Menger game $\menGame{X}$, characterizing Menger's covering property.
+In this game, $k$-Markov strategies need only consider at most
+two moves of the opponent.
+
+\begin{thm*}
+  $\pl F\kmarkwin{k+2}\menGame{X}$ if and only if
+  $\pl F\kmarkwin{2}\menGame{X}$.
+\end{thm*}
+
+For a one-point Lindel\"of-ication $\oneptlind\kappa$ of discrete $\kappa$,
+the topological game $\menGame{\oneptlind\kappa}$ is equivalent to a
+set-theoretic game $\cloFillIntGame{\kappa}$ with respect to $\pl F$'s $k$-Markov
+strategies. Using this game, one may see the following.
+
+This game has similarities to a game introduced by
+Scheepers \cite{MR1129143}, who also introduced a set-theoretic axiom
+$\alcompS\kappa$ to study it. This axiom may also be applied to study
+$\menGame{\oneptlind\kappa}$.
+
+\begin{thm*}
+  Assume $\alcompS{\kappa}$. Then
+  $\pl F\kmarkwin{2}\menGame{\oneptlind\kappa}$.
+\end{thm*}
+
+Scheepers observed that $\alcompS{\omega_1}$ is a theorem of $ZFC$.
+
+\begin{thm*}
+  $\pl F\kmarkwin{2}\menGame{\oneptlind\omega_1}$ but
+  $\pl F\notmarkwin\menGame{\oneptlind\omega_1}$.
+\end{thm*}
+
+Telgarsky \cite{MR753073} and Scheepers \cite{MR1273523} provided different
+proofs to show that among metrizable spaces, $\pl F\markwin\menGame{X}$
+characterizes $\sigma$-compactness. These results may be extended by considering
+Markov strategies. Recall that for Lindel\"of spaces, metrizability is
+characterized by regularity and second-countability.
+
+\begin{thm*}
+  For regular spaces, $\pl F\markwin\menGame{X}$ if and only if
+  $X$ is $\sigma$-compact.
+\end{thm*}
+
+\begin{thm*}
+  For second-countable spaces, $\pl F\markwin\menGame{X}$ if and only if
+  $\pl F\win\menGame{X}$.
+\end{thm*}
+
+The topological property characterized by $\pl F\kmarkwin{2}\menGame{X}$
+seems to be heretofore unstudied. The final chapter concludes by
+introducing the sufficient robustly Menger property, and uses it to study the
+space $R_\omega$ finer than the usual Euclidean real line.
+
+\begin{thm*}
+  Assume $\alcompS{2^\omega}$. Then $\pl F\kmarkwin{2}\menGame{R_\omega}$.
+\end{thm*}

### 2014-12-14 phd/dissertation/chapter5.tex
introductory chapter

@@
 \begin{defn}
-  A \term{selective ultrafilter} $\mc F$ is a free ultrafilter with the
+  A \term{selective ultrafilter} $\mc S$ is a free ultrafilter with the
   property that for every
   partition $\{B_n : n < \omega\}$ of nonempty subsets of $\omega$ such that
-  $B_n \not\in \mathcal{F}$ for all $n$, there exists $A \in \mc{F}$ such
+  $B_n \not\in \mc{S}$ for all $n$, there exists $A \in \mc{S}$ such
   that $|A \cap B_n|=1$ for all $n$.
@@
 \begin{thm}
-  If $\mc F$ is a selective ultrafilter, then
-  $\pl K\notprewin \gruKPGame{\omega\cup\{\mc F\}}$.
+  If $\mc S$ is a selective ultrafilter, then
+  $\pl K\notprewin \gruKPGame{\omega\cup\{\mc S\}}$.
 \end{thm}
@@
   Then define $B_n=\omega\cap(\sigma(n+1)\setminus\sigma(n))$. Since $B_n$
-  is always nonempty finite, $B_n\not\in\mc F$ and there exists $A\in \mc F$
+  is always nonempty finite, $B_n\not\in\mc F$ and there exists $A\in \mc S$
   such that $|A\cap B_n|=1$.
 
-  Define the legal counter-attack $p:\omega\to\omega\cup\{\mc F\}$ by
+  Define the legal counter-attack $p:\omega\to\omega\cup\{\mc S\}$ by
   $p(n)\in A\cap B_n=A\cap(\sigma(n+1)\setminus\sigma(n))$. Since
-  $A=(A\cap\sigma(0))\cup\{p(n):n<\omega\}$, $\{p(n):n<\omega\}\in\mc F$.
+  $A=(A\cap\sigma(0))\cup\{p(n):n<\omega\}$, $\{p(n):n<\omega\}\in\mc S$.
   Therefore, every neighborhood of $\mc F$ intersects infinitely many of

### 2014-12-16 phd/dissertation/chapter2.tex
introductory chapter
make changes suggested by G

@@
 
-\chapter{Introduction}
+\chapter{Definitions and Examples}
 
-The goal of this paper is to explore the applications of limited information
-strategies in existing topological games.
+This chapter outlines the set-theoretic and game-theoretic preliminaries
+required for this paper.
+
+\section{Set Theory}
+
+In general, all required set-theoretic concepts are taken from Kunen's
+text \cite{MR597342}.
+
+\begin{defn}
+  Define \term{ordinals} and \term{cardinals} as in Kunen's text.
+  In particular, $0=\emptyset$, $\omega=\{0,1,2,\dots\}$,
+  $\omega_1$ is the smallest uncountable ordinal, and
+  $\alpha+1=\alpha\cup\{\alpha\}$. The order on ordinals and cardinals
+  is given by $\alpha<\beta$ if and only if $\alpha\in\beta$.
+\end{defn}
+
+\begin{defn}
+  Let $R^D$ denote the set of functions from $D$ to $R$. For an ordinal
+  $\alpha$, $R^{<\alpha}=\bigcup_{\beta<\alpha}R^\beta$ and
+  $R^{\leq\alpha}=\bigcup_{\beta\leq\alpha}R^\beta$.
+\end{defn}
+
+\begin{defn}
+  A \term{sequence} is a function $f\in A^\omega$, denoted
+  $f=\<f(0),f(1),\dots\>$.
+  A \term{finite sequence} is a function
+  $t\in A^{<\omega}$, denoted $t=\<t(0),\dots,t(|t|-1)\>$.
+\end{defn}
+
+Ordered pairs, triples, etc. are considered to be finite sequences.
+
+\begin{defn}
+  For $s,t\in A^{<\omega}$, let $s\concat t\in A^{<\omega}$ be the
+  \term{concatenation} of $s$ and $t$, so that $(s\concat t)(i)=s(i)$
+  for $i<|s|$, and $(s\concat t)(i+|s|)=t(i)$ for $i<|t|$.
+\end{defn}
+
+\begin{defn}
+  For $f:D\to R$ and $A\subseteq D$, let $f\rest A : A\to R$ be the
+  \term{restriction} of $f$ to $A$.
+\end{defn}
 
@@
 but we will find it convenient to think of them in terms defined by
-Gale and Stewart. \cite{MR0054922}
+Gale and Stewart \cite{MR0054922}.
 
@@
   Let $\bakergame{X}$ denote a game with players $\pl A$ and $\pl B$,
-  defined for each subset $A\subset \mathbb{R}$.
+  defined for each subset $X\subset \mathbb{R}$.
   In round $0$, $\pl A$ chooses a number $a_0$, followed by $\pl B$ choosing
@@
 
-  $\pl A$ wins the game if the sequence $\<a_n:n<\omega\>$ limits to a
+  $\pl A$ wins the game if the sequence $\<a_n:n<\omega\>$ converges to a
   point in $X$, and $\pl B$ wins otherwise.
@@
   Adapted from \cite{noMRbaker}.
-  Let $X=\{x_0,x_1,\dots\}$. Let $i(a,b)$ be the least integer such that
+  Let $X=\{x_i:i<\omega\}$. Let $i(a,b)$ be the least integer such that
   $a<x_{i(x,y)}<b$, if it exists. We define a strategy $\sigma$ for $\pl B$
@@
   \begin{itemize}
-    \item $\sigma(\<a_0\>)=x_{i(a_0,\infty)}$.
-          If $i(a_0,\infty)$ does not exist, then the choice of $\sigma(\<a_0\>)$
-          is arbitary, say, $a_0+1$.
-    \item $\sigma(\<a_0,...,a_{n+1}\>)=x_{i(a_{n+1},b_n)}$, where
-          $b_n=\sigma(\<a_0,\dots,a_n\>)$.
-          If $i(a_{n+1},b_n)$ does not exist, then the choice of
-          $\sigma(\<a_0,...,a_{n+1}\>)$ is arbitrary, say,
-          $
-            \sigma(\<a_0,...,a_{n+1}\>)
-              =
-            \frac{a_{n+1}+b_n}{2}
-          $.
+    \item If $i(a_0,\infty)$ exists, $\sigma(\<a_0\>)=x_{i(a_0,\infty)}$.
+    \item Let $b_n=\sigma(\<a_0,\dots,a_n\>)$
+          If $i(a_{n+1},b_n)$ exists,
+          $\sigma(\<a_0,...,a_{n+1}\>)=x_{i(a_{n+1},b_n)}$.
+    \item Otherwise, the choice of $\sigma(t)$ may be any legal move.
   \end{itemize}
@@
   since $a_0<\sigma(\<a_0\>)$ and $a_{n+1}<\sigma(\<a_0,\dots,a_{n+1}\>)<b_n$.
-  We claim this is a winning strategy for $\pl B$. Let $a=\<a_0,a_1,\dots\>$
-  be a legal attack by $\pl A$ against $\sigma$: we will show that the
-  resulting playthrough is a victory for $\pl B$, that is,
-  $\lim_{n\to\infty} a_n\not\in X$. Let $b_n=\sigma(\<a_0,\dots,a_n\>)$.
-  Note that
-    \[
-      a_0<a_1<\dots<\lim_{n\to\infty}a_n<\dots<b_1<b_0
-    \]
-
-  If $i(a_0,\infty)$ does not exist, then $a_0$ is greater than every element
-  of $X$, and thus
-  $\lim_{n\to\infty} a_n \not\in X$. A similar argument follows if some
-  $i(a_{n+1},b_n)$ does not exist.
-
-  Otherwise,
-    \[
-      i(a_0,\infty)<i(a_1,b_0)<i(a_2,b_1)<\dots
-    \]
-  and for each $i<\omega$, one of the following must hold.
-    \begin{itemize}
-      \item $i<i(a_0,\infty)$. Then $x_i\leq a_0<\lim_{n\to\infty}a_n$.
-      \item $i = i(a_0,\infty)$. Then $x_i=b_0>\lim_{n\to\infty}a_n$.
-      \item $i(a_0,\infty)<i<i(a_1,b_0)$.
-            Then $x_i\leq a_1<\lim_{n\to\infty}a_n$ or
-            $x_i\geq b_0>\lim_{n\to\infty}a_n$.
-      \item $i = i(a_{n+1},b_n)$ for some $n<\omega$.
-            Then $x_i=b_{n+1}>\lim_{n\to\infty}a_n$.
-      \item $i(a_{n+1},b_n)<i<i(a_{n+2},b_{n+1})$ for some $n<\omega$.
-            Then $x_i\leq a_{n+2}<\lim_{n\to\infty}a_n$ or
-            $x_i\geq b_{n+1}>\lim_{n\to\infty}a_n$.
-    \end{itemize}
-  In any case, $x_i\not=\lim_{n\to\infty}a_n$, and thus
-  $\lim_{n\to\infty}a_n\not\in X$.
+  Note every $x_i$
+  was either chosen by $\pl B$ during a round, or it was illegal to choose.
+  In either case, there exist $a_n,b_n$ with $x_i\not\in(a_n,b_n)$, so
+  $\lim_{n\to\infty}a_n\not\in X$ and thus $\sigma$ is a winning strategy.
 \end{proof}
 
-More informally, $\pl B$ can force a win by enumerating the countable set
-$X$ and playing every legal choice by the end of the game.
-This yields a classical result.
+This yields the classical result from undergraduate set theory.
 

### 2014-12-16 phd/dissertation/chapter3.tex
overall cleanup
all theorems/definitions within sections for numbering
make changes suggested by G

@@
 
-We begin by investigating a game due to Gary Gruenhage.
+We begin by investigating a game due to Gary Gruenhage, introduced in
+his doctoral dissertation to solve a problem due to Phil Zenor.
+
+\section{Definitions}
 
@@
 \begin{thm}
-  $\pl O \not\markwin \gruConGameHard{\oneptcomp\omega_1}{\infty}$.
+  $\pl O \notmarkwin \gruConGameHard{\oneptcomp\omega_1}{\infty}$.
 \end{thm}
@@
 \begin{thm}
-  $\pl O \not\kmarkwin{k} \gruConGameHard{\oneptcomp\omega_1}{\infty}$.
+  $\pl O \notkmarkwin{k} \gruConGameHard{\oneptcomp\omega_1}{\infty}$.
 \end{thm}
@@
 
-However, knowledge of the round number is critical.
+However, knowledge of the round number is critical. First recall the
+following ``closing-up lemma'' (see \cite{MR597342}):
+
+\begin{lem}
+  For any function $f:\omega_1^{<\omega}\to\omega_1$, the following set is closed
+  and unbounded in $\omega_1$:
+    \[
+      \{
+        \alpha<\omega_1
+      :
+        s\in\alpha^{<\omega} \Rightarrow f(s)\subseteq\alpha
+      \}
+    \]
+\end{lem}
 
 \begin{thm}
-  $O\not\ktactwin{k}\gruClusGameHard{\oneptcomp\omega_1}{\infty}$.
+  $\pl O\notktactwin{k}\gruClusGameHard{\oneptcomp\omega_1}{\infty}$.
 \end{thm}
@@
         \oneptcomp\omega_1\setminus\sigma(s)
-        \subset \alpha
+        \subseteq \alpha
       \}
@@
 \begin{thm}
-  $O\not\kmarkwin{k}\gruClusGameHard{\oneptcomp\omega_2}{\infty}$.
+  $\pl O\notkmarkwin{k}\gruClusGameHard{\oneptcomp\omega_2}{\infty}$.
 \end{thm}
@@
         \oneptcomp\omega_2\setminus\sigma\circ\mu_k(s)
-        \subset \alpha
+        \subseteq \alpha
       \}
@@
 \begin{defn}
-  Let $\Sigma_{y} \prod_{\alpha<\kappa}X_\alpha$ be a \term{sigma-product} of
-  $X$ with dimension $\kappa$ for each $y\in \prod_{\alpha<\kappa}X_\alpha$,
-  the subset of the usual Tychonoff product space $\prod_{\alpha<\kappa}X_\alpha$
-  such that $x\in \Sigma_y \prod_{\alpha<\kappa}X_\alpha$
-  if and only if $\{\alpha<\kappa : x(\alpha)\not=y(\alpha)\}$ is countable.
+  Let
+    \[
+      \sum_{\alpha<\kappa}^y X_\alpha
+        =
+      \left\{
+        x \in \prod_{\alpha<\kappa} X_\alpha
+         :
+        |\{x(\alpha)\not=y(\alpha):\alpha<\kappa\}|\leq\omega
+      \right\}
+    \]
+  denote the \term{sigma-product}
+  of $\{X_\alpha:\alpha<\kappa\}$ with base point
+  $y\in \prod_{\alpha<\kappa}X_\alpha$. The topology on this space
+  is given by the subspace topology.
 
-  Unless otherwise specified, we assume $0\in X_\alpha$ for all $\alpha<\kappa$
-  and $y=\vec 0$, and write $\Sigma \prod_{\alpha<\kappa}X_\alpha$.
+  Note also the following syntactic sugar:
+  $\sum_{\alpha<\kappa}X_\alpha=\sum_{\alpha<\kappa}^{\vec 0}X_\alpha$,
+  $\sum^{y} X^\kappa = \sum_{\alpha<\kappa}^{y} X$, and
+  $\sum X^\kappa = \sum_{\alpha<\kappa}^{\vec 0} X$.
 \end{defn}
@@
   \[
-    \{
-    x\in \Sigma 2^\kappa
+    \left\{
+    x\in \sum 2^\kappa
       :
-    x(\alpha)=0 \text{ for all but one } \alpha<\kappa
-    \}
+    |\{\alpha<\kappa:x(\alpha)=1\}|\leq 1
+    \right\}
   \]
@@
     \left\{
-      \begin{array}{ll}
+      \begin{array}{l@{\,:\,}l}
         0 & \beta\not=\alpha \\
@@
 \begin{cor}
-  $\pl O\not\ktactwin{k}\gruClusGameHard{\SigmaProdR{\omega_1}}{\vec0}$,
-  $\pl O\not\kmarkwin{k}\gruConGameHard{\SigmaProdR{\omega_1}}{\vec0}$, and
-  $\pl O\not\kmarkwin{k}\gruClusGameHard{\SigmaProdR{\omega_2}}{\vec0}$.
+  $\pl O\notktactwin{k}\gruClusGameHard{\SigmaProdR{\omega_1}}{\vec0}$,
+  $\pl O\notkmarkwin{k}\gruConGameHard{\SigmaProdR{\omega_1}}{\vec0}$, and
+  $\pl O\notkmarkwin{k}\gruClusGameHard{\SigmaProdR{\omega_2}}{\vec0}$.
 \end{cor}
@@
   For a game $G=\<M,W\>$ and \term{coding strategy} or \term{code}
-  $\sigma:M^2\to M$, the \term{$\sigma$-coding fog-of-war}
+  $\sigma:M^{\leq2}\to M$, the \term{$\sigma$-coding fog-of-war}
   $\gamma_\sigma: M^{<\omega}\to M^{\leq2}$ is the function defined such that

### 2014-12-16 phd/dissertation/chapter5.tex
make changes suggested by G

@@
 ensure that only one ``useful'' move may be seen by $\pl K$ at a time by playing
-$k$ $\infty$s between each non-$\infty$.
+$k$ $\infty$'s between each non-$\infty$.
 
@@
 see \cite{MR858337}.
+
+\begin{defn}
+  A space is \term{metacompact} if for every open cover $\mc U$ there exists a
+  point-finite open refinement $\mc V$ of $\mc U$ also covering the space.
+\end{defn}
 
@@
 \end{thm}
+
+\begin{defn}
+  A space is \term{$\sigma$-metacompact} if for every open cover $\mc U$ there
+  exist point-finite open refinements $\mc V_n$ of $\mc U$ such that
+  $\bigcup_{n<\omega}\mc V_n$ also covers the space.
+\end{defn}
 
@@
 A similar game may be considered by allowing the second player to choose
-compact sets rather than points, which also provided in \cite{MR858337}
-a game-theoretic characterization of a covering property for locally compact
+compact sets rather than points, which provided in \cite{MR858337}
+a game-theoretic characterization of paracompactness for locally compact
 spaces.
@@
   with players $\pl K$, $\pl L$. This game proceeds analogously to
-  $\gruKPGame{X}$, except the second player $\pl L$ chooses comapct sets $L_n$
+  $\gruKPGame{X}$, except the second player $\pl L$ chooses compact sets $L_n$
   missing $\bigcup_{m\leq n}K_n$,
@@
 move of $\pl L$.
+
+\begin{defn}
+  A space is \term{paracompact} if for every open cover $\mc U$ there exists a
+  locally-finite open refinement $\mc V$ of $\mc U$ also covering the space.
+\end{defn}
 
@@
 \begin{defn}
-  A space $X$ is \textbf{hemicompact} if there exist compact sets $K_n$ for
+  A space $X$ is \term{hemicompact} if there exist compact sets $K_n$ for
   $n<\omega$ such that every compact set in $X$ is a subset of some $K_n$.
@@
   $U_x$ be an open neighborhood of $x$ which intersects finitely many
-  $\sigma(n)$. Thus there exists an open neighborhood of $C$ which intersects
-  finitely many $\sigma(n)$.
+  $\sigma(n)$. Choose $x_i\in C$ for $i<n<\omega$ such that
+  $\{U_{x_i}:i<n\}$ covers $C$. Then $\bigcup_{i<n}U_{x_i}$ contains $C$
+  and intersects finitely many $\sigma(n)$, and thus
+  $\{\bigcup_{m\leq n}\sigma(m):n<\omega\}$ witnesses hemicompactness.
 \end{proof}
@@
 
-It is not possible to prove that $\pl K\prewin \gruKPGame{\omega\cup\{\mc F\}}$
-for arbitrary free ultrafilters in $ZFC$.
+It is not possible to prove in $ZFC$ that
+$\pl K\prewin \gruKPGame{\omega\cup\{\mc F\}}$
+for arbitrary free ultrafilters.
 
@@
   open neighborhood $U$ of $x$ in $X$, and declaring
-  $B_{\alpha,n}=(U_\alpha\times\{c_\alpha\rest n: m\leq n<\omega\})\cup\{c_\alpha\}$
+  $B_{\alpha,m}=(U_\alpha\times\{c_\alpha\rest n: m\leq n<\omega\})\cup\{c_\alpha\}$
   to be a clopen neighborhood of $c_\alpha\in C$ for each $\alpha<\omega_1$,
@@
 \begin{lem}
-  Then $K_F$, $K_F'$, $L_m$ are compact in $\pmb X$.
+  $K_F$, $K_F'$, and $L_m$ are compact in $\pmb X$.
   Furthermore, every compact set is contained in a union of $K_F'$, $L_m$
@@
 
-  Then consider $\pmb x=c_\alpha$ for some $\alpha<\omega_1$, and let $n<\omega$.
+  Now consider $\pmb x=c_\alpha$ for some $\alpha<\omega_1$, and let $n<\omega$.
   Then if $\pmb p(n)=\<x,s\>$ with $\alpha = \alpha_{x,N}$ for some $N<\omega$,
@@
   Let $Y$ be a zero-dimensional Corson compact space which is not Eberlein
-  compact; one such space was constructed in \cite{Marciszewski1991291}
-  and let $X=Y^2$.
+  compact; one such space was constructed in \cite{Marciszewski1991291}.
+  >et $X=Y^2$.
   Then by characterizations of Corson and Eberlien compacts found in
@@
 \begin{cor}
-  There exists a space $X$ such that $\pl K\win\gruKPGame{X}$ but
-  $\pl K\notkmarkwin{k} \gruKPGame{X}$ for all $k<\omega$.
+  There exists a locally compact space $X$ such that $\pl K\win\gruKPGame{X}$
+  but $\pl K\notkmarkwin{k} \gruKPGame{X}$ for all $k<\omega$.
 \end{cor}
 
-So the following question remains open:
+So the following questions remain open:
 
@@
   Does $\pl K\ktactwin{k+1}\gruKPGame{X}$ imply
-  $\pl K\tactwin\gruKPGame{X}$ always? What about for Markov strategies?
+  $\pl K\tactwin\gruKPGame{X}$ for all locally compact spaces?
+  Equivalently, is metacompactness characterized by
+  $\pl K\ktactwin{k+1}\gruKPGame{X}$ for all locally compact spaces?
+  What about for Markov strategies and $\sigma$-metacompactness?
 \end{ques}

### 2015-01-30 phd/dissertation/chapter2.tex
fixes suggested by Dr. Rodger

@@
   A \term{game} is a tuple $\<M,W\>$ such that
-  $W\subseteq M^{\omega}$. $M$ is set of \term{moves} for
+  $W\subseteq M^{\omega}$. $M$ is the set of \term{moves} for
   the game, and $M^{\omega}$ is the set of all possible
@@
 Intuitively, a strategy is a rule for one of the players on how to play
-the game based upon the previous (finite) moves of her opponent, while an
+the game based upon the previous (finite) moves of the opponent, while an
 attack is a fixed strike by an opponent indexed by round number.
@@
 
-We now may rigorously define the notion of ``forcing'' a win in a game.
+We now rigorously define the notion of ``forcing'' a win in a game.
 
@@
   If a winning $k$-tactical strategy exists for a player $\pl A$ in the game
-  $G$, then we write $\pl A \ktactwin{k} G$. If $k=1$, then $\pl A \tactwin G$.
+  $G$, then we write $\pl A \ktactwin{k} G$. If $k=1$, then
+  we may write $\pl A \tactwin G$.
 
   If a winning $k$-Markov strategy exists for a player $\pl A$ in the game
-  $G$, then we write $\pl A \kmarkwin{k} G$. If $k=1$, then $\pl A \markwin G$,
-  and if $k=0$, then $\pl A \prewin G$.
+  $G$, then we write $\pl A \kmarkwin{k} G$. If $k=1$, then we may write
+  $\pl A \markwin G$;
+  if $k=0$, then we may write $\pl A \prewin G$.
 \end{defn}
@@
 \begin{defn}
-  $X$ is an \term{$\alpha$-favorable space}
+  $X$ is said to be an \term{$\alpha$-favorable space}
   when $\pl N \tactwin \bmgame{X}$.
-  $X$ is a \term{weakly $\alpha$-favorable space}
+  $X$ is said to be a \term{weakly $\alpha$-favorable space}
   when $\pl N \win \bmgame{X}$.

### 2015-02-04 phd/dissertation/chapter2.tex
tweaks based on meeting with Rodger

@@
   \term{playthroughs} of the game.
-
   $W$ is the set of \term{winning playthroughs} or \term{victories} for the
@@
 the game based upon the previous (finite) moves of the opponent, while an
-attack is a fixed strike by an opponent indexed by round number.
+attack is a fixed sequence of moves determined by the opponent before
+the game begins.
 
@@
 the game for that strategy and counter-attack is a victory for the opponent,
-then a winning strategy does not exist.
+then a winning strategy does not exist for that player.
 
-Unlike finite games, is not the case that a winning strategy must exist for
+Unlike finite games, it is not the case that a winning strategy must exist for
 one of the players in an infinite game.

### 2015-02-20 phd/dissertation/chapter1.tex
revisions suggested by outside reader

@@
 
-A winning $k+1$-Markov strategy for $\gruConGame{X}{x}$ may be improved to
+A winning $(k+1)$-Markov strategy for $\gruConGame{X}{x}$ may be improved to
 a winning Markov strategy; however, it remains open whether this same

### 2015-02-20 phd/dissertation/chapter2.tex
revisions suggested by outside reader

@@
 This chapter outlines the set-theoretic and game-theoretic preliminaries
-required for this paper.
+required for this dissertation.
 
@@
 This concept of when (and how) a player can ``force'' a win in certain
-topological games is the focus of this manuscript.
+topological games is the focus of this dissertation.
 

### 2015-02-20 phd/dissertation/chapter3.tex
revisions suggested by outside reader

@@
 We begin by investigating a game due to Gary Gruenhage, introduced in
-his doctoral dissertation to solve a problem due to Phil Zenor.
+his doctoral dissertation to solve a problem due to Phil Zenor
+\cite{MR0394561}.
 
@@
 interchangibly. However, it is possible to find spaces for which the games are
-not equivalent when considering $k+1$-tactics and $k+1$-marks, as we will
+not equivalent when considering $(k+1)$-tactics and $(k+1)$-marks, as we will
 soon see.
@@
 As an example, the existence of a winning coding strategy is necessary for the
-second player to force a win the Banach-Mazur game.
+second player to force a win in the Banach-Mazur game.
 

### 2015-02-20 phd/dissertation/chapter5.tex
revisions suggested by outside reader

@@
 \begin{proof}
-  Let $\sigma$ be a winning $k+1$-mark for $\pl K$ such that $m\leq n$ and
+  Let $\sigma$ be a winning $(k+1)$-mark for $\pl K$ such that $m\leq n$ and
   $\ran r \subseteq \ran s$ implies $\sigma(r,m)\subseteq\sigma(s,n)$.
@@
     \]
-  and use $r$ to define the $k+1$-tactic $\tau$ by
+  and use $r$ to define the $(k+1)$-tactic $\tau$ by
     \[
@@
   gives $|s_{n+1}|\geq|s_n|+1\geq n+1$.
-  Thus $\pmb q$ is a legal attack on the winning $k+1$-Markov strategy
+  Thus $\pmb q$ is a legal attack on the winning $(k+1)$-Markov strategy
   $\sigma$, so the collection $\{\{\pmb q(n)\}:n<\omega\}$ is locally finite.
@@
   compact; one such space was constructed in \cite{Marciszewski1991291}.
-  >et $X=Y^2$.
+  Let $X=Y^2$.
   Then by characterizations of Corson and Eberlien compacts found in

### 2015-03-06 phd/talks-and-presentations/2015-03-11-defense.tex
update through chapter 4 intro

% $Header: /home/vedranm/bitbucket/beamer/solutions/generic-talks/generic-ornate-15min-45min.en.tex,v 90e850259b8b 2007/01/28 20:48:30 tantau $

\documentclass{beamer}

% This file is a solution template for:

% - Giving a talk on some subject.
% - The talk is between 15min and 45min long.
% - Style is ornate.

% Copyright 2004 by Till Tantau <tantau@users.sourceforge.net>.
%
% In principle, this file can be redistributed and/or modified under
% the terms of the GNU Public License, version 2.
%
% However, this file is supposed to be a template to be modified
% for your own needs. For this reason, if you use this file as a
% template and not specifically distribute it as part of a another
% package/program, I grant the extra permission to freely copy and
% modify this file as you see fit and even to delete this copyright
% notice.

\mode<presentation>
{
  \usetheme{Warsaw}
  % or ...

  \setbeamercovered{transparent}
  % or whatever (possibly just delete it)
}

      \newtheorem{proposition}[theorem]{Proposition}
      \theoremstyle{definition}
      \newtheorem{game}[theorem]{Game}
      \newtheorem{question}[theorem]{Question}

\usepackage[english]{babel}
% or whatever

\usepackage[latin1]{inputenc}
% or whatever

\usepackage{times}
\usepackage[T1]{fontenc}
% Or whatever. Note that the encoding and the font should match. If T1
% does not look nice, try deleting the line with the fontenc.

\usepackage{marvosym} % For \Smiley
\usepackage{verbatim} % for \verbatiminput

\usepackage{tikz}
\usetikzlibrary{matrix} % for diagrams

\title
{Limited information strategies for topological games}

\subtitle
{PhD Defense} % (optional)

\author%[Author, Another] % (optional, use only with lots of authors)
{Steven~Clontz~http://stevenclontz.com}%\inst{1} \and S.~Another\inst{2}}
% - Use the \inst{?} command only if the authors have different
%   affiliation.

\institute[Auburn University] % (optional, but mostly needed)
{
  %\inst{1}%
  Department of Mathematics and Statistics\\
  Auburn University}
  %\and
  %\inst{2}%
  %Department of Theoretical Philosophy\\
  %University of Elsewhere}
% - Use the \inst command only if there are several affiliations.
% - Keep it simple, no one is interested in your street address.

\date[15-03-11] % (optional)
{March 11, 2015}

% If you have a file called "university-logo-filename.xxx", where xxx
% is a graphic format that can be processed by latex or pdflatex,
% resp., then you can add a logo as follows:

 % \pgfdeclareimage[height=1cm]{university-logo}{auburn_logo.png}
 % \logo{\pgfuseimage{university-logo}}

% Delete this, if you do not want the table of contents to pop up at
% the beginning of each subsection:
%\AtBeginSubsection[]
%{
%  \begin{frame}<beamer>{Outline}
%    \tableofcontents[currentsection,currentsubsection]
%  \end{frame}
%}

% If you wish to uncover everything in a step-wise fashion, uncomment
% the following command:

%\beamerdefaultoverlayspecification{<+->}

% Strategy uparrow shortcuts
\newcommand{\win}{\uparrow}
\newcommand{\prewin}{\underset{\text{pre}}{\uparrow}}
\newcommand{\markwin}{\underset{\text{mark}}{\uparrow}}
\newcommand{\tactwin}{\underset{\text{tact}}{\uparrow}}
\newcommand{\kmarkwin}[1]{\underset{#1\text{-mark}}{\uparrow}}
\newcommand{\ktactwin}[1]{\underset{#1\text{-tact}}{\uparrow}}
\newcommand{\codewin}{\underset{\text{code}}{\uparrow}}
\newcommand{\limitwin}{\underset{\text{limit}}{\uparrow}}
\newcommand{\notwin}{\not\uparrow}
\newcommand{\notprewin}{\underset{\text{pre}}{\not\uparrow}}
\newcommand{\notmarkwin}{\underset{\text{mark}}{\not\uparrow}}
\newcommand{\nottactwin}{\underset{\text{tact}}{\not\uparrow}}
\newcommand{\notkmarkwin}[1]{\underset{#1\text{-mark}}{\not\uparrow}}
\newcommand{\notktactwin}[1]{\underset{#1\text{-tact}}{\not\uparrow}}
\newcommand{\notcodewin}{\underset{\text{code}}{\not\uparrow}}
\newcommand{\notlimitwin}{\underset{\text{limit}}{\not\uparrow}}

\newcommand{\oneptcomp}[1]{#1^*}
\newcommand{\oneptlind}[1]{#1^\dagger}
% \newcommand{\sharp}[1]{#1^{\#}}

% Games
\newcommand{\gruConGame}[2]{Gru_{O,P}^{\to}\left({#1},{#2}\right)}
\newcommand{\gruConGameHard}[2]{Gru_{O,P}^{\to,\star}\left({#1},{#2}\right)}
\newcommand{\gruClusGame}[2]{Gru_{O,P}^{\leadsto}\left({#1},{#2}\right)}
\newcommand{\gruClusGameHard}[2]{Gru_{O,P}^{\leadsto,\star}\left({#1},{#2}\right)}

\newcommand{\gruKPGame}[1]{Gru_{K,P}\left({#1}\right)}
\newcommand{\gruKLGame}[1]{Gru_{K,L}\left({#1}\right)}

\newcommand{\cloPFGame}[1]{PtFin_{F,C}\left({#1}\right)}

\newcommand{\menGame}[1]{Men_{C,F}\left({#1}\right)}
\newcommand{\rothGame}[1]{Roth_{C,S}\left({#1}\right)}
\newcommand{\rothAltGame}[1]{Roth_{P,O}\left({#1}\right)}

\newcommand{\cloFillStrictGame}[1]{Fill^{\cup,\subset}_{C,F}\left({#1}\right)}
\newcommand{\cloFillGame}[1]{Fill^{\cup,\subseteq}_{C,F}\left({#1}\right)}
\newcommand{\cloFillInitialGame}[1]{Fill^{1,\subseteq}_{C,F}\left({#1}\right)}
\newcommand{\cloFillIntGame}[1]{Fill^{\cap}_{C,F}\left({#1}\right)}

\newcommand{\bellUniGame}[1]{Bell_{D,P}^{\textrm{uni}}\left({#1}\right)}
\newcommand{\bellConGame}[1]{Bell_{D,P}^{\rightharpoonup}\left({#1}\right)}
\newcommand{\bellConHardGame}[1]{Bell_{D,P}^{\rightharpoonup,\star}\left({#1}\right)}
\newcommand{\bellAbsConGame}[1]{Bell_{D,P}^{\to}\left({#1}\right)}
\newcommand{\bellAbsConHardGame}[1]{Bell_{D,P}^{\to,\star}\left({#1}\right)}

\newcommand{\SigmaProdR}[1]{\Sigma\mathbb{R}^{#1}}
\newcommand{\sigmaprodtwo}[1]{\Sigma2^{#1}}

\newcommand{\concat}{{^\frown}}
\newcommand{\rest}{\restriction}

\newcommand{\cl}[1]{\overline{#1}}

\newcommand{\pow}[1]{\mc{P}(#1)}

\newcommand{\<}{\langle}
\renewcommand{\>}{\rangle}

\newcommand{\al}[1]{{#1}^*}

\newcommand{\mc}[1]{\mathcal{#1}}
\newcommand{\mb}[1]{\mathbb{#1}}

\newcommand{\po}{\mathbb{P}}
\newcommand{\pok}{\po_\kappa}

\newcommand{\Lim}{\mathrm{Lim}}
\newcommand{\Suc}{\mathrm{Suc}}

\newcommand{\ds}{\displaystyle}

\newcommand{\st}[2]{st\left(#1,#2\right)}

\newcommand{\alcomp}{\al\parallel}

\newcommand{\rank}{\textrm{rank}}
\newcommand{\dom}{\textrm{dom}}

\renewcommand{\mod}{\,\textrm{mod}}

\newcommand{\zip}{\bowtie}
\newcommand{\ran}[1]{\text{range}(#1)}

\newcommand{\cf}[1]{\textrm{cf}(#1)}

\newcommand{\alcompS}[1]{S(#1)}

\newcommand{\scish}{almost-$\sigma$-(relatively compact)}

\usepackage{mathrsfs}
\newcommand{\pl}[1]{\mathscr{#1}}

\newcommand{\term}{\textit}

\newcommand{\bmGame}[1]{{BM}_{E,N}(#1)}

\begin{document}
\renewcommand{\pause}{}
\newcommand{\vspacing}{\vspace{1em}}
\newcommand{\vpause}{\pause\vspacing}

\begin{frame}
  \titlepage
\end{frame}

\section{Topological Games}

\subsection{Defintion}

\begin{frame}
  A \term{topological game} is a two-player game $G(X)$ of length
  $\omega=\{0,1,2,\dots\}$ defined for certain topological spaces $X$.

  \vpause

  During each round $n$, the first and second player take turns choosing
  certain topological objects from $X$ (e.g. point, open set, open cover, etc.).

  \vpause

  At the ``end'' of the game, a winner is declared by inspecting the sequences
  of choices made throughout the game.

  \vpause

  The study of such games involves finding when a player has a
  \term{winning strategy} which defeats every possible counterattack by
  the opponent.

  \vpause

  {\tiny See Telgarsky's excellent survey on topological games for more
  details: \cite{MR892457}}
\end{frame}

\subsection{Example}

\begin{frame}
  \small
  \begin{game}
    The \term{Banach-Mazur Game}
    $\bmGame{X}$ (1935) \cite{MR666400}

    \begin{figure}
      \includegraphics[width=0.6\linewidth]{bmGame.pdf}
    \end{figure}

  The first player $\pl N$ wins the game if the intersection of all the chosen
  open sets is nonempty.
  \end{game}
\end{frame}

\begin{frame}
  \begin{theorem}
    $X$ is Baire if and only if $\pl N$ lacks a winning strategy
    in the Banach Mazur game ($\pl N\not\win\bmGame{X}$).
  \end{theorem}

  \pause

  Thus the topological property of being a Baire space has a game-theoretic
  characterization using $\bmGame{X}$.

  \vpause

  By considering \term{limited information strategies}, we may characterize
  more properties.
\end{frame}

\begin{frame}
  Consider the following:

  \begin{theorem}
    $X$ is $\alpha$-favorable $\Rightarrow$
    $X$ is weakly $\alpha$-favorable $\Rightarrow$
    $X$ is Baire
  \end{theorem}

  \pause

  $\alpha$-favorability is characterized by $\pl E\tactwin\bmGame{X}$:
  player $\pl E$ has a \term{tactical} winning strategy which only considers
  the most recent move of the opponent.

  \vpause

  This is stronger than weak
  $\alpha$-favorability, characterized by $\pl E\win\bmGame{X}$.
  In this case $\pl E$ still has a winning strategy, but it may
  rely on perfect information of the history of the game.
\end{frame}

\subsection{Motivation}

\begin{frame}
  By characterizing topological properties using the theory of
  topological games, we introduce new proof techniques for demonstrating
  the structure of given topological spaces.

  \vpause

  The aim of my dissertation was to investigate four topological games
  from the literature with unknown limited information implications.

  \vpause

  In doing so I uncovered several new results in general topology,
  advancing research done by
  G. Gruenhage, P. Nyikos, F. Gavin, R. Telg{\' a}rksy, J. Bell,
  M. Scheepers, and others.
\end{frame}

\section{Gruenhage's Convergence/Clustering Games}

\subsection{Definition}

\begin{frame}
  \small
  \begin{game}
  Gruenhage's convergence game $\gruConGame{X}{x}$
  and clustering game $\gruClusGame{X}{x}$ proceed as follows:
    \begin{figure}
      \includegraphics[width=0.6\linewidth]{convergenceGame.pdf}
    \end{figure}

  $\pl O$ wins the game if the points chosen by $\pl P$ converge/cluster
  to the given point $x\in X$. Otherwise, $\pl P$ wins.
  \end{game}

  \tiny
  Note that $\pl O$ need not know anything about the history of the game
  to play each round.
\end{frame}

\subsection{Motivation}

\begin{frame}
  If $\pl O\win \gruConGame{X}{x}$, then $x$ is called a $W$-point in $X$.
  Obviously, all points of first-countablity are $W$-points, but
  $\pl O\win\gruConGame{\oneptcomp\kappa}{\infty}$ also, where $\infty$
  is the added point in the one-point compactification $\oneptcomp\kappa$
  of uncountable discrete $\kappa$.

  \vpause

  Points of first-countability may in fact be characterized by this game
  as well:
  \begin{theorem}
    $x$ has a countable local base in $X$ if and only if
    $\pl O\prewin \gruConGame{X}{x}$ ($\pl O$ has
    a winning \term{predetermined}
    strategy using only the round number).
  \end{theorem}

  \pause

  If every point in a space $X$ is a $W$-point, then $X$ is a $W$-space.
\end{frame}

\subsection{Results}

\begin{frame}
  A variation of this game which is harder for $\pl O$ yields some
  difficult infinite combinatorial questions:

  \begin{game}
  Gruenhage's hard convergence game $\gruConGameHard{X}{x}$
  and hard clustering game $\gruClusGameHard{X}{x}$ proceed as follows:
    \begin{figure}
      \includegraphics[width=0.6\linewidth]{convergenceHardGame.pdf}
    \end{figure}
  \end{game}
\end{frame}

\begin{frame}
  Nyikos observed in \cite{MR1031771} that:
  \begin{theorem}
    $\pl O \notmarkwin \gruConGameHard{\oneptcomp\omega_1}{\infty}$.

    {\small ($\pl O$ cannot guarantee a win using a \term{Markov strategy}
    which considers only the round number and most recent move.) }
  \end{theorem}

  \vpause

  Some more work shows that in fact
  \begin{theorem}
    $\pl O \notkmarkwin{k} \gruConGameHard{\oneptcomp\omega_1}{\infty}$.

    {\small ($\pl O$ cannot guarantee a win using a $k$-\term{Markov strategy}
    which considers only the round number and $k$ most recent moves.) }
  \end{theorem}
\end{frame}

\begin{frame}
  Interestingly, the strategy which prevents convergence won't
  prevent clustering as well unless the cardinality of the space is
  sufficiently large.

  \begin{theorem}
    $\pl O\markwin \gruClusGameHard{\oneptcomp\omega_1}{\infty}$, but
    $\pl O\notkmarkwin{k}\gruClusGameHard{\oneptcomp\omega_2}{\infty}$.
  \end{theorem}

  \pause

  But knowledge of the round number is used non-trivially in doing so.

  \begin{theorem}
    $\pl O\notktactwin{k}\gruClusGameHard{\oneptcomp\omega_1}{\infty}$.
  \end{theorem}
\end{frame}

\section{Gruenhage's Locally Finite Games}

\subsection{Definition}

\begin{frame}
  \small
  \begin{game}
  Gruenhage's locally finite games $\gruKPGame{X}$ and
  $\gruKLGame{X}$ proceed as follows:
    \begin{figure}
      \includegraphics[width=0.6\linewidth]{compactPointGame.pdf}
    \end{figure}

  $\pl K$ wins the game if the points/sets chosen by $\pl P$/$\pl L$ are
  locally finite in the space. Otherwise, $\pl P$/$\pl L$  wins.
  \end{game}
\end{frame}

% \subsection{Proximal Game}

% \begin{frame}
%   \term{Proximal Game} (2014)
%   \cite{MR3239205}

%   \vspacing

%   \begin{figure}
%     \includegraphics[width=0.8\linewidth]{proximalGame.pdf}
%   \end{figure}
%   {\tiny for compact $T_1$ $0$-dim spaces}

%   \vpause

%   The first player $\pl D$ wins the game if the points chosen by the
%   second player $\pl P$ converge. If $\pl D$ has a winning
%   strategy for this game, call $X$ \term{proximal}.
% \end{frame}

% \begin{frame}
%   Some results related to the Proximal Game due to Jocelyn Bell:

%   \begin{proposition}
%     If $X$ is metrizable, then $X$ is proximal.
%   \end{proposition}

%   \begin{theorem}
%     If $X$ is proximal, then $X$ is collectionwise normal.
%   \end{theorem}

%   \begin{theorem}
%     $\Sigma$-products and closed subspaces of proximal spaces are proximal.
%   \end{theorem}

%   \pause

%   \begin{corollary}
%     The $\Sigma$-product of metrizable spaces is collectionwise normal.
%     \cite{MR0461410} \cite{MR716576}
%   \end{corollary}
% \end{frame}

% \section{Main Result}

% \subsection{Corson compact}

% \begin{frame}
%   A \term{Corson compact} space is a space homeomorphic to a compact
%   subset of the $\Sigma$-product of real lines.

%   \vpause

%   Peter Nyikos observed:

%   \begin{proposition}
%     Every Corson compact space is proximal compact. \cite{nyikosProximalPreprint}
%   \end{proposition}

%   \pause

%   C. and Gruenhage showed in \cite{MR3227201} that any compact proximal
%   space must be Corson compact, using another game-theoretic characterization
%   of Corson compact due to Gruenhage:
% \end{frame}

% \subsection{Showing proximal compact implies Corson compact}

% \begin{frame}
%   \small
%   \term{Diagonal Game} (1984) \cite{MR752278}:

%   \begin{figure}
%     \includegraphics[width=0.7\linewidth]{diagonalGame.pdf}
%   \end{figure}
%   {\tiny for compact $T_1$ $0$-dim spaces}

%   \vpause

%   The first player $\pl O$ wins the game if any open set containing the
%   diagonal also contains infinitely many of $\pl P$'s chosen points.

%   \begin{theorem}
%     For $X$ compact, $\pl O$ has a winning strategy for the diagonal game
%     if and only if $X$ is Corson compact.
%   \end{theorem}
% \end{frame}

% \begin{frame}
%   One may use a winning strategy $\sigma$ for $\pl D$ in the proximal game to
%   construct a strategy $\tau$ for $\pl O$ in the diagonal game.

%   \begin{figure}
%     \includegraphics[width=0.7\linewidth]{convertingStrategy.pdf}
%   \end{figure}
% \end{frame}

% \begin{frame}
%   In general:
%   \[
%     \tau(a)
%       =
%     \bigcup_{s\concat\<i,h_{s,i},j\>\in\max(T(a))}
%     \frac{1}{4}\sigma(o_s\concat\<h_{s,i}\>)[h_{s,i,j}]
%   \]

%   \vspacing

%   Using the strategy $\tau$ defined for every proximal compact space,
%   $\pl O$ cannot be defeated in the diagonal game, and therefore all
%   proximal compacts are Corson compact. \qed
% \end{frame}

% \section{Questions and References}

% \begin{frame}
%   Open questions:

%   \begin{itemize}
%     \item If compactness is dropped, does the proximal game characterize
%     all copies of \textit{closed} subspaces of a $\Sigma$-product of reals?
%     (Nyikos)
%     \item If the winning strategy for the proximal game is \term{Markov}
%     (relies on only the latest move and round number) for a compact space,
%     does that imply that the space is \term{Eberlein} compact?
%     (This holds for the diagonal game.)
%   \end{itemize}
% \end{frame}

\begin{frame}[allowframebreaks]
  \tiny
  \bibliographystyle{plain}
  \bibliography{../dissertation/bibliography}
\end{frame}

\begin{frame}
  Any questions?
\end{frame}

\end{document}

### 2015-03-09 phd/talks-and-presentations/2015-03-11-defense.tex
almost complete first draft of defense slides

@@
   advancing research done by
-  G. Gruenhage, P. Nyikos, F. Gavin, R. Telg{\' a}rksy, J. Bell,
+  G. Gruenhage, P. Nyikos, R. Telg{\' a}rksy, J. Bell,
   M. Scheepers, and others.
@@
 
+\section{Bell's Proximal Game}
+
+\subsection{Definition}
+
+\begin{frame}
+  \small
+  \begin{game}
+  Bell's proximal game $\bellAbsConGame{X}$ for compact zero-dimensional
+  $X$:
+    \begin{figure}
+      \includegraphics[width=0.6\linewidth]{proximalGameAlt.pdf}
+    \end{figure}
+
+  $\pl D$ wins the game if the points chosen by $\pl P$ converge.
+  Otherwise, $\pl P$ wins.
+  \end{game}
+\end{frame}
+
+\subsection{Motivation}
+
+\begin{frame}
+  If $\pl D\win \bellAbsConGame{X}$, then $X$ is called a proximal compact.
+  This game was brought to my attention due to this result: \cite{MR3239205}
+
+  \begin{theorem}
+    Every proximal space is a $W$-space. So
+    $\pl D\win\bellAbsConGame{X} \Rightarrow \pl O\win\gruConGame{X}{x}$
+    for all $x\in X$.
+  \end{theorem}
+
+  \vpause
+
+  Proximal spaces have strong preservation properties, as any
+  closed subset or $\Sigma$-product of proximal spaces is proximal. Since
+  any proximal space is collectionwise normal, Bell's game gives an elegant
+  proof of the classic result:
+
+  \begin{theorem}
+    A $\Sigma$-product of metrizable spaces is collection-wise normal.
+  \end{theorem}
+\end{frame}
+
+\subsection{Results}
+
+\begin{frame}
+  Nyikos \cite{nyikosProximalPreprint} observed that
+  \begin{proposition}
+    Corson compact spaces are proximal.
+  \end{proposition}
+  and asked if the converse holds as well.
+
+  \vpause
+
+  With Gruenhage, I showed that the answer is yes:
+  \begin{theorem}
+    A compact space is Corson compact if and only if it is proximal.
+  \end{theorem}
+\end{frame}
+
+\begin{frame}\small
+  A winning limited information strategy may always be passed down
+  to win in a closed subspace, but Bell's result that winning strategies
+  are preserved for $\Sigma$-products does not quite generalize as well:
+
+  \begin{theorem}
+    For $k<\omega$, if $\pl D\kmarkwin{k}\bellAbsConGame{X_i}$ for all $i<\omega$,
+    then $\pl D\kmarkwin{k}\bellAbsConGame{\prod_{i<\omega} X_i}$.
+  \end{theorem}
+
+  \pause
+
+  Other limited information lemmas proved in my dissertation allowed me
+  to prove a game-theoretic characterization of another compactness property
+  (paper in preparation):
+
+  \begin{theorem}
+    A compact space is strong Eberlein compact if and only if
+    $\pl D\tactwin\bellAbsConGame{X}$.
+  \end{theorem}
+\end{frame}
+
 \section{Gruenhage's Locally Finite Games}
@@
 
-% \subsection{Proximal Game}
+\subsection{Motivation}
 
-% \begin{frame}
-%   \term{Proximal Game} (2014)
-%   \cite{MR3239205}
+\begin{frame}
+  Gruenhage used these games in \cite{MR752278} to characterize
+  metacompactness and $\sigma$-metacompactness amongst locally compact
+  spaces:
 
-%   \vspacing
+  \begin{theorem}
+    For locally compact spaces, $\pl K\tactwin\gruKPGame{X}$ if and only if
+    $X$ is metacompact.
+  \end{theorem}
 
-%   \begin{figure}
-%     \includegraphics[width=0.8\linewidth]{proximalGame.pdf}
-%   \end{figure}
-%   {\tiny for compact $T_1$ $0$-dim spaces}
+  \begin{theorem}
+    For locally compact spaces, $\pl K\markwin\gruKPGame{X}$ if and only if
+    $X$ is $\sigma$-metacompact.
+  \end{theorem}
+\end{frame}
 
-%   \vpause
+\subsection{Results}
 
-%   The first player $\pl D$ wins the game if the points chosen by the
-%   second player $\pl P$ converge. If $\pl D$ has a winning
-%   strategy for this game, call $X$ \term{proximal}.
-% \end{frame}
+\begin{frame}
+  By removing knowledge of the round number, an analogous result is
+  unsurfaced:
 
-% \begin{frame}
-%   Some results related to the Proximal Game due to Jocelyn Bell:
+  \begin{theorem}
+    For locally compact spaces, $\pl K\prewin\gruKPGame{X}$ if and only if
+    $X$ is $\sigma$-compact.
+  \end{theorem}
 
-%   \begin{proposition}
-%     If $X$ is metrizable, then $X$ is proximal.
-%   \end{proposition}
+  \pause
 
-%   \begin{theorem}
-%     If $X$ is proximal, then $X$ is collectionwise normal.
-%   \end{theorem}
+  Actually, for locally compact or even compactly-generated spaces,
+  $\pl K\prewin\gruKPGame{X}$ if and only if $\pl K\prewin\gruKLGame{X}$.
+  However, there is a non-compactly-generated counterexample:
 
-%   \begin{theorem}
-%     $\Sigma$-products and closed subspaces of proximal spaces are proximal.
-%   \end{theorem}
+  \begin{theorem}
+    There exists a free ultrafilter $\mc F$ such that
+    $\pl K \prewin\gruKPGame{\omega\cup\{\mc F\}}$, but
+    $\pl K \notprewin\gruKLGame{\omega\cup\{\mc F\}}$ for any free
+    ultrafilter $\mc F$.
+  \end{theorem}
+\end{frame}
 
-%   \pause
+\section{Menger's Game}
 
-%   \begin{corollary}
-%     The $\Sigma$-product of metrizable spaces is collectionwise normal.
-%     \cite{MR0461410} \cite{MR716576}
-%   \end{corollary}
-% \end{frame}
+\subsection{Definition}
 
-% \section{Main Result}
+\begin{frame}
+  \small
+  \begin{game}
+  Menger's game $\menGame{X}$ proceeds as follows:
 
-% \subsection{Corson compact}
+  (this space intentionally left blank until I make a picture)
 
-% \begin{frame}
-%   A \term{Corson compact} space is a space homeomorphic to a compact
-%   subset of the $\Sigma$-product of real lines.
+  $\pl F$ wins the game if her finitely coverable subsets
+  union to the space. Otherwise, $\pl C$  wins.
+  \end{game}
+\end{frame}
 
-%   \vpause
+\subsection{Motivation}
 
-%   Peter Nyikos observed:
+\begin{frame}
+  A covering property generalizing $\sigma$-compactness is characterized
+  by this game, demonstrated by Hurewicz in the 1920's. \cite{MR1544773}
 
-%   \begin{proposition}
-%     Every Corson compact space is proximal compact. \cite{nyikosProximalPreprint}
-%   \end{proposition}
+  \begin{theorem}
+    A space is Menger if and only if $\pl C\not\win\menGame{X}$.
+  \end{theorem}
 
-%   \pause
+  \pause
 
-%   C. and Gruenhage showed in \cite{MR3227201} that any compact proximal
-%   space must be Corson compact, using another game-theoretic characterization
-%   of Corson compact due to Gruenhage:
-% \end{frame}
+  It was originally suspected that Menger subspaces of the real line were
+  exactly the $\sigma$-compact subspaces, but as was shown by Telgarsky
+  and Scheepers, $\sigma$-compact spaces
+  have slightly more structure. \cite{MR753073} \cite{MR1273523}
 
-% \subsection{Showing proximal compact implies Corson compact}
+  \begin{theorem}
+    A metrizable space $X$ is $\sigma$-compact if and only if
+    $\pl F\win\menGame{X}$.
+  \end{theorem}
+\end{frame}
 
-% \begin{frame}
-%   \small
-%   \term{Diagonal Game} (1984) \cite{MR752278}:
+\subsection{Results}
 
-%   \begin{figure}
-%     \includegraphics[width=0.7\linewidth]{diagonalGame.pdf}
-%   \end{figure}
-%   {\tiny for compact $T_1$ $0$-dim spaces}
+\begin{frame}
+  By considering Markov strategies, the previous theorem may be factored
+  into two subresults.
 
-%   \vpause
+  \begin{theorem}
+    A regular space $X$ is $\sigma$-compact if and only if
+    $\pl F\markwin\menGame{X}$.
+  \end{theorem}
+  \begin{theorem}
+    For a second-countable space $X$, $\pl F\win\menGame{X}$ if and only if
+    $\pl F\markwin\menGame{X}$.
+  \end{theorem}
 
-%   The first player $\pl O$ wins the game if any open set containing the
-%   diagonal also contains infinitely many of $\pl P$'s chosen points.
+  Note that since the spaces we are considering are all Lindel\"of,
+  metrizability is characterized by regularity and second-countability.
+\end{frame}
 
-%   \begin{theorem}
-%     For $X$ compact, $\pl O$ has a winning strategy for the diagonal game
-%     if and only if $X$ is Corson compact.
-%   \end{theorem}
-% \end{frame}
+\subsection{More Motivation}
 
-% \begin{frame}
-%   One may use a winning strategy $\sigma$ for $\pl D$ in the proximal game to
-%   construct a strategy $\tau$ for $\pl O$ in the diagonal game.
+\begin{frame}
+  Limited information strategies in topological games such as
+  $\menGame{X}$ often have set-theoretic
+  consequences. The statement $\alcompS\kappa$ due to M. Scheepers
+  \cite{MR1129143} says that there exist
+  almost-compatible functions $f_A:A\to\omega$ for each $A\in[\kappa]^\omega$.
 
-%   \begin{figure}
-%     \includegraphics[width=0.7\linewidth]{convertingStrategy.pdf}
-%   \end{figure}
-% \end{frame}
+  \begin{theorem}
+    $\alcompS{\omega_1}$ and $\neg\alcompS{(2^\omega)^+}$ are theorems
+    of $ZFC$, but $\alcompS\kappa$ is independent of $ZFC$ for
+    $\omega_1<\kappa\leq 2^\omega$.
+  \end{theorem}
 
-% \begin{frame}
-%   In general:
-%   \[
-%     \tau(a)
-%       =
-%     \bigcup_{s\concat\<i,h_{s,i},j\>\in\max(T(a))}
-%     \frac{1}{4}\sigma(o_s\concat\<h_{s,i}\>)[h_{s,i,j}]
-%   \]
+  \begin{theorem}
+    If $\alcompS{\kappa}$ holds, then
+    $\pl F\ktactwin2 \cloFillStrictGame{\kappa}$.
+  \end{theorem}
+\end{frame}
 
-%   \vspacing
+\subsection{More Results}
 
-%   Using the strategy $\tau$ defined for every proximal compact space,
-%   $\pl O$ cannot be defeated in the diagonal game, and therefore all
-%   proximal compacts are Corson compact. \qed
-% \end{frame}
+\begin{frame}
+  Let $\oneptlind\kappa$ be the one-point ``Lindel\"of-ication'' of
+  discrete $\kappa$.
 
-% \section{Questions and References}
+  \begin{theorem}
+    \begin{figure}
+      \includegraphics[width=0.6\linewidth]{mengerGameChart.png}
+    \end{figure}
+  \end{theorem}
+\end{frame}
 
-% \begin{frame}
-%   Open questions:
+\begin{frame}\small
+  For most of the games in the previous chart, including the Menger game
+  $\menGame{X}$, there's no need to consider larger amounts of limited
+  information.
 
-%   \begin{itemize}
-%     \item If compactness is dropped, does the proximal game characterize
-%     all copies of \textit{closed} subspaces of a $\Sigma$-product of reals?
-%     (Nyikos)
-%     \item If the winning strategy for the proximal game is \term{Markov}
-%     (relies on only the latest move and round number) for a compact space,
-%     does that imply that the space is \term{Eberlein} compact?
-%     (This holds for the diagonal game.)
-%   \end{itemize}
-% \end{frame}
+  \begin{theorem}
+    For each $k<\omega$,
+    $\pl F\kmarkwin{k+2}\menGame{X}$ if and only if
+    $\pl F\kmarkwin2\menGame{X}$
+  \end{theorem}
+
+  The topological property $\pl F\kmarkwin2\menGame{X}$ seems to
+  depend on the set-theoretic axioms at play.
+
+  \begin{theorem}
+    If $\alcompS{2^\omega}$, then $\pl F\kmarkwin2\menGame{R_\omega}$.
+  \end{theorem}
+\end{frame}
 

### 2015-03-10 phd/talks-and-presentations/2015-03-11-defense.tex
Add pictures to defense presentation

@@
 % - Style is ornate.
+
+\usepackage{amssymb}
 
@@
 
-\newcommand{\bmGame}[1]{{BM}_{E,N}(#1)}
+\newcommand{\bmGame}[1]{{BM}_{N,E}(#1)}
 
@@
     \begin{figure}
-      \includegraphics[width=0.6\linewidth]{bmGame.pdf}
+      \includegraphics[width=0.6\linewidth]{bmGameAlt.pdf}
     \end{figure}
@@
   This is stronger than weak
-  $\alpha$-favorability, characterized by $\pl E\win\bmGame{X}$.
+  $\alpha$-favorability \cite{MR817083}, characterized by $\pl E\win\bmGame{X}$.
   In this case $\pl E$ still has a winning strategy, but it may
@@
 
+\begin{frame}
+  For the related game $\gruConGame{X}{x}$, a $(k+1)$-tactic/mark may always
+  be improved to only use the most recent move of the opponent. If this
+  also holds for $\gruKPGame{X}$, then metacompactness and
+  $\sigma$-metacompactness may would be characterized by the existence
+  of any winning $(k+1)$-tactic/mark.
+
+  \vpause
+
+  Due to a technical difference in the games, it's unclear if this is true.
+  However, for a tricky non-$\sigma$-metacompact example $\pmb X$:
+
+  \begin{theorem}
+    $\pl K\win\gruKPGame{\pmb X}$ but
+    $\pl K\notkmarkwin{k}\gruKPGame{\pmb X}$.
+  \end{theorem}
+\end{frame}
+
 \section{Menger's Game}
@@
   Menger's game $\menGame{X}$ proceeds as follows:
-
-  (this space intentionally left blank until I make a picture)
+    \begin{figure}
+      \includegraphics[width=0.6\linewidth]{mengerGame.pdf}
+    \end{figure}
 

### 2015-03-10 phd/talks-and-presentations/2015-03-11-defense.tex
add convergence game proofs

@@
 
+\begin{frame}{
+  Proof that $\pl O\markwin \gruClusGameHard{\oneptcomp\omega_1}{\infty}$
+}\small
+  For each $\alpha<\omega_1$, let $f_\alpha:\alpha\to\omega$ be injective.
+
+  \vpause
+
+  Note that for each $F\in[\omega_1]^{<\omega}$, there is some $n_F<\omega$
+  such that $f_{\alpha+1}(\beta)<n_F$ for all $\beta,\alpha\in F$.
+
+  \vpause
+
+  Let $\sigma$ be a Markov strategy for $\pl O$ such that
+    \[
+      \sigma(\<\alpha\>,n)
+        \subseteq
+      \oneptcomp\omega_1 \setminus
+      \{\beta<\omega_1:f_{\alpha+1}(\beta)<n\}
+    \]
+  for $\alpha<\omega_1$.
+
+  \vpause
+
+  Thus as any legal counterattack cannot have finite range in $\omega_1$
+  without repeating $\infty$ co-finitely,
+  $\sigma$ is a winning Markov strategy. $\qed$
+\end{frame}
+
+\begin{frame}{
+  Proof that $\pl O\nottactwin\gruClusGameHard{\oneptcomp\omega_1}{\infty}$
+}\small
+  Let $\sigma$ be a tactic for $\pl O$ in
+  $\gruClusGameHard{\oneptcomp\omega_1}{\infty}$.
+
+  \vpause
+
+  Then this set is closed and unbounded in $\omega_1$:
+    \[
+      C_\sigma
+        =
+      \{
+        \alpha<\omega_1
+          :
+        \beta<\alpha
+          \Rightarrow
+        \oneptcomp\omega_1\setminus\sigma(\<\beta\>)
+        \subseteq \alpha
+      \}
+    \]
+
+  \vpause
+
+  If $a_\sigma:\omega_1\to C_\sigma$ is an order isomorphism, then
+  there is $n<\omega$ such that $a_\sigma(n)\in\sigma(\<a_\sigma(\omega)\>)$.
+
+  \vpause
+
+  Then since $a_\sigma(\omega)>a_\sigma(n)$ implies
+  $a_\sigma(\omega)\in\sigma(\<a_\sigma(n)\>)$
+  (by the definition of $C_\sigma$), it follows that
+  $\<a_\sigma(n),a_\sigma(\omega),a_\sigma(n),a_\sigma(\omega),\dots\>$
+  is a legal counterattack against $\sigma$ which does not cluster at
+  $\infty$. $\qed$
+\end{frame}
+
 \section{Bell's Proximal Game}
@@
 
+\section{}
+
+\begin{frame}
+  Any questions?
+\end{frame}
+
 \begin{frame}[allowframebreaks]
@@
 
-\begin{frame}
-  Any questions?
-\end{frame}
-
 \end{document}

### 2015-03-10 phd/talks-and-presentations/2015-03-11-defense.tex
final draft of defense slides

@@
 
+\begin{frame}{
+Proof that $\sigma$-compact $\Leftrightarrow$ $\pl F\markwin\menGame{X}$
+}\small
+  Assume $X$ is regular.
+
+  \vpause
+
+  If $X=\bigcup_{n<\omega} K_n$, then $\pl F$ may choose $K_n$ each round,
+  which is a winning predetermined (and therefore Markov) strategy.
+
+  \vpause
+
+  If $X$ is not $\sigma$-compact,
+  let $\sigma$ be any Markov strategy for $\pl F$. Then for
+    \[
+      R_n = \bigcap_{\mc{U}\in\mathfrak{C}} \sigma(\<\mc{U}\>,n)
+    \]
+  and any open cover $\mc U$ of the space $X$,
+  $\sigma(\<\mc{U}\>,n)$ is a finite subcover of $R_n$. Thus $\cl{R_n}$
+  is compact by the regularity of $X$.
+
+  \vpause
+
+  Since $X$ is not $\sigma$-compact, choose a point $x$ not in any $R_n$.
+  Then there is a sequence of open covers $\mc U_0,\mc U_1,\dots$ for which
+  $x\not\in\sigma(\<\mc U_n\>,n)$ for all $n$, and thus $\sigma$
+  is not a winning Markov strategy.
+\end{frame}
+
+\begin{frame}{
+Proof that $\pl F\win\menGame{X}$ $\Leftrightarrow$ $\pl F\markwin\menGame{X}$
+}\small
+  Assume $X$ is second-countable. Without loss of generality, assume
+  $\pl C$ only chooses coverings using open sets from the countable base
+  $\{U_n:n<\omega\}$.
+
+  \vpause
+
+  If $\pl F$ has a winning Markov strategy, then she has a winning strategy.
+
+  \vpause
+
+  Let $\sigma$ be a winning strategy, and assume $\mc U_t$ is an open cover
+  of basic open sets for each $t\leq s\in\omega^{<\omega}$.
+  % Since $\sigma(\<\mc U_{s\rest1},\dots,\mc U_{s},\mc U\>)$
+  % is finitely coverable by $\mc U$,
+  % there is some $F\in[\omega]^{<\omega}$ such that
+  % $
+  %   \sigma(\<\mc U_{s\rest1},\dots,\mc U_{s},\mc U\>)
+  %     \subseteq
+  %   \bigcup_{n\in F}U_n
+  % $.
+  % Since there are only countably many $F\in[\omega]^{<\omega}$,
+  By exploiting the countable base, we may choose
+  $\mc U_{s\concat\<n\>}$ for each $n<\omega$, such that for every open cover
+  $\mc U$ there exists $n<\omega$ where
+  $
+    \sigma(\<\mc U_{s\rest1},\dots,\mc U_{s},\mc U\>)
+      \subseteq
+    \sigma(\<\mc U_{s\rest1},\dots,\mc U_{s},\mc U_{s\concat\<n\>}\>)
+  $.
+
+  \vpause
+
+  Then
+  $\tau(\<\mc U\>,n)=\sigma(\<\mc U_{f(n)\rest1},\dots,\mc U_{f(n)},\mc U\>$
+  where $f:\omega\to\omega^{<\omega}$ is a bijection is a winning strategy.
+\end{frame}
+
 \subsection{More Motivation}

### 2015-03-11 phd/talks-and-presentations/2015-03-11-defense.tex
Fix bmgame typos

@@
 
-\newcommand{\bmGame}[1]{{BM}_{N,E}(#1)}
+\newcommand{\bmGame}[1]{{BM}_{E,N}(#1)}
 
@@
 
-  The first player $\pl N$ wins the game if the intersection of all the chosen
-  open sets is nonempty.
+  The first player $\pl E$ wins the game if the intersection of all the chosen
+  open sets is empty.
   \end{game}
@@
   \begin{theorem}
-    $X$ is Baire if and only if $\pl N$ lacks a winning strategy
-    in the Banach Mazur game ($\pl N\not\win\bmGame{X}$).
+    $X$ is Baire if and only if $\pl E$ lacks a winning strategy
+    in the Banach Mazur game ($\pl E\not\win\bmGame{X}$).
   \end{theorem}
@@
     $X$ is $\alpha$-favorable $\Rightarrow$
-    $X$ is weakly $\alpha$-favorable $\Rightarrow$
+    $X$ is Choquet $\Rightarrow$
     $X$ is Baire
@@
 
-  $\alpha$-favorability is characterized by $\pl E\tactwin\bmGame{X}$:
+  $\alpha$-favorability is characterized by $\pl N\tactwin\bmGame{X}$:
   player $\pl E$ has a \term{tactical} winning strategy which only considers
@@
 
-  This is stronger than weak
-  $\alpha$-favorability \cite{MR817083}, characterized by $\pl E\win\bmGame{X}$.
-  In this case $\pl E$ still has a winning strategy, but it may
+  This is stronger than the Choquet property \cite{MR817083},
+  characterized by $\pl N\win\bmGame{X}$.
+  In this case $\pl N$ still has a winning strategy, but it may
   rely on perfect information of the history of the game.

### 2015-03-13 phd/talks-and-presentations/2015-03-11-defense.tex
add in pauses to slides
remove redundant question

@@
 \begin{document}
-\renewcommand{\pause}{}
+% \renewcommand{\pause}{}
 \newcommand{\vspacing}{\vspace{1em}}
@@
 
-  The aim of my dissertation was to investigate four topological games
-  from the literature with unknown limited information implications.
+  In my dissertation I investigate four topological games
+  from the literature to find new limited information characterizations.
 
@@
   Note that for each $F\in[\omega_1]^{<\omega}$, there is some $n_F<\omega$
-  such that $f_{\alpha+1}(\beta)<n_F$ for all $\beta,\alpha\in F$.
+  such that $f_{\alpha+1}(\beta)<n_F$ for all $\beta\leq\alpha\in F$.
 

### 2015-03-25 articles/k-tactics-in-gruenhages-compact-point-game/article.tex
draft of compact point game paper

\documentclass{amsart}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}

\usepackage{graphicx}

\usepackage{../../clontzDefinitions}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{game}[theorem]{Game}
\newtheorem{example}[theorem]{Example}
\newtheorem{question}[theorem]{Question}

\begin{document}

% \title{Proximal compact spaces are Corson compact\tnoteref{t1}}
% \tnotetext[t1]{2010 Mathematics Subject Classification. 54E15, 54D30, 54A20.}
\title{On $k$-tactics in Gruenhage's compact-point game}

% \author[aub]{S.~Clontz\fnref{fn1}}
% \ead{steven.clontz@auburn.edu}
% \author[aub]{G.~Gruenhage\fnref{fn2}}
% \ead{gruengf@auburn.edu}

% \address[aub]{Department of Mathematics, Auburn University,
%  Auburn, AL 36830}

\author{Steven Clontz}
\address{Department of Mathematics, Auburn University,
Auburn, AL 36830}
\email{steven.clontz@gmail.edu}
\urladdr{www.stevenclontz.com}

\keywords{topological game, limited information strategy, metacompact spaces,
$\sigma$-metacompact spaces}

\subjclass[2010]{54D20, 54D45}

\begin{abstract}
Gary Gruenhage showed in \cite{MR858337} that metacompactness and
$\sigma$-metacompactness may be characterized for locally compact spaces
by way of a certain topological game using limited information strategies
which consider only the most recent move of the opponent (tactical/stationary
strategies) and possibly the round number (Markov strategies). This paper
demonstrates a non-trivial example of a space for which a winning strategy
exists but every limited information strategy considering a maximum of $k$
moves of the opponent and the round number may be defeated. The question
follows: are metacompactness and $\sigma$-metacompactness characterized by
winning $k$-tactical and $k$-Markov strategies?
\end{abstract}

\maketitle

\section{Introduction}

Consider the following topological game.

\begin{game}
  Let $\gruKPGame{X}$ denote the \term{Gruenhage compact/point game}
  with players $\pl K$, $\pl P$. During round $n$, $\pl K$ chooses
  a compact subset $K_n$ of $X$, followed by $\pl P$ choosing a point
  $p_n\in X$ such that $p_n\not\in \bigcup_{m\leq n}K_m$.

  $\pl K$ wins the game if the points $p_n$ are locally
  finite in the space, and $\pl P$ wins otherwise.
\end{game}

\begin{definition}
  A \term{strategy} for a game $G$ with moveset $M$ is a function
  $\sigma:M^{<\omega}\to M$; intuitively, this is a fixed rule for one player's
  choices in consideration of her opponent's moves. If using such a strategy
  always results in a win for the player $\pl P$ using it, then it is called a
  \term{winning strategy} and we write $\pl P\win G$.
\end{definition}

When $G(X)$ is a topological game played with space $X$, then $\pl P\win G(X)$
and $\pl P\not\win G(X)$ are topological properties of the space $X$.

The above game was used by the author's adviser Gary Gruenhage in
\cite{MR858337} to characterize
metacompactness (every open cover of the space has a point-finite open
refinement covering the space) and $\sigma$-metacompactness
(every open cover of the space has a $\sigma$-point-finite open refinement
covering the space) in locally compact spaces. However, the characterization
considers so-called \term{limited information strategies} which do not use
full information of the history of the game.

\begin{definition}
  A $k$-tactical strategy for a game $G$ with moveset $M$ is a function
  $\sigma:M^{\leq k}\to M$; intuitively, it is a strategy which only considers
  the previous $k$ moves of the opponent. If using such a strategy
  always results in a win for the player $\pl P$ using it, then
  we write $\pl P\ktactwin{k} G$.
\end{definition}

\begin{definition}
  A $k$-Markov strategy for a game $G$ with moveset $M$ is a function
  $\sigma:M^{\leq k}\times\omega\to M$; intuitively, it is a strategy which
  only considers the previous $k$ moves of the opponent and the round number.
  If using such a strategy
  always results in a win for the player $\pl P$ using it, then
  we write $\pl P\kmarkwin{k} G$.
\end{definition}

We will call $k$-tactical strategies ``$k$-tactics'' and $k$-Markov strategies
``$k$-marks''. If the $k$ is omitted then it is assumed that $k=1$. In
addition, note that some authors refer to tactics as
\term{stationary strategies}.

In this language, one may write Gruenhage's results as follows:

\begin{theorem}
  If $X$ is a locally compact space, then
  \begin{itemize}
    \item
    $X$ is metacompact if and only if $\pl K\tactwin\gruKPGame{X}$, and
    \item
    $X$ is $\sigma$-metacompact if and only if $\pl K\markwin\gruKPGame{X}$
  \end{itemize}
\end{theorem}

The main question essentially asks whether (at least for locally compact
spaces) a winning $(k+2)$-tactic or $(k+2)$-mark may always be improved to a
$1$-tactic or $1$-mark.

\begin{question}
  Let $X$ be a locally compact space and $k<\omega$.
  Does $\pl K\ktactwin{(k+2)}\gruKPGame{X}$ imply $X$ is metacompact?
  Does $\pl K\kmarkwin{(k+2)}\gruKPGame{X}$ imply $X$ is $\sigma$-metacompact?
\end{question}

This question is very similar to the open question on the well-known
Banach-Mazur (also known as Choquet) game $\bmGame{X}$ where $\pl N$
is the player wishing for a nonempty intersection: does there exist a
space for which
$\pl N\ktactwin{3}\bmGame{X}$ but $\pl N\notktactwin{2}\bmGame{X}$?
(The analogous question for $2$- and $1$-tactics was answered in the
affirmative by Gabriel Debs in \cite{MR817083}.) For fans
of such infinite combinatorial game theory puzzles, we may restate the
main question as follows.

\begin{question}
  Does there exist a locally compact space $X$ such that
  $\pl K\ktactwin{2}\gruKPGame{X}$ but $\pl K\nottactwin\gruKPGame{X}$?
  What about for Markov strategies?
\end{question}

\section{Related results}

The game $\gruKPGame{X}$ has its roots in another topological game due to
Gruenhage.

\begin{game}
  Let $\gruConGame{X}{x}$ denote \term{Gruenhage's $W$-convergence game} with
  players $\pl O$, $\pl P$, for a topological space $X$ and point $x\in X$.
  In round $n$, $\pl O$ chooses an open neighborhood $O_n$ of $x$, followed
  by $\pl P$ choosing a point $p_n\in \bigcap_{m\leq n}O_m$.

  $\pl O$ wins the game if the points $p_n$ converge to $x$, and $\pl P$
  wins otherwise.
\end{game}

Let $\onePtComp{X}=X\cup\{\infty\}$ be the \term{one-point compactification}
of a noncompact locally compact space $X$, where points in $X$ have their
usual neighborhoods, and neighborhoods of $\infty$ are complements of
compact sets in $X$. Then convergence to $\infty$ in $\onePtComp{X}$
corresponds to local finiteness in the subspace $X$. One may then assume that
$\gruKPGame{X}$ and $\gruConGame{\onePtComp X}{\infty}$ are equivalent games
when $X$ is locally compact.
Considering perfect information, $1$-tactical, and $1$-Markov strategies, this
is essentially true.

\begin{theorem}
  If $X$ is locally compact, then
    \begin{itemize}
      \item $\pl K\win\gruKPGame{X}$ if and only if
        $\pl O\win\gruConGame{\onePtComp{X}}{\infty}$.
      \item $\pl K\markwin\gruKPGame{X}$ if and only if
        $\pl O\markwin\gruConGame{\onePtComp{X}}{\infty}$.
      \item $\pl K\tactwin\gruKPGame{X}$ if and only if
        $\pl O\tactwin\gruConGame{\onePtComp{X}}{\infty}$.
    \end{itemize}
\end{theorem}

\begin{proof}
  Let $\sigma$ be a winning mark for $\pl K$ in $\gruKPGame{X}$.
  Define the tactic $\tau$ for $\pl O$ in $\gruConGame{\onePtComp X}{\infty}$
  as follows:
    \[
      \tau(\emptyset,0) = \onePtComp{X}\setminus \sigma(\emptyset,0)
    \]
    \[
      \tau(\<x\>,n) =
        \left\{
          \begin{array}{lcr}
            \onePtComp{X} &
            : &
            x=\infty
              \\
            \onePtComp{X} \setminus \bigcup_{m\leq n}\sigma(\<x\>,m) &
            : &
            x\not=\infty
          \end{array}
        \right.
    \]
  Then for any legal attack $p$ against $\tau$, consider its subsequence
  $p'$ which removes all instances of $\infty$.
  If $p'$ is a finite sequence, then $p$ contains $\infty$ co-finitely and
  therefore converges to $\infty$.

  Note that for each $n<\omega$, $p'(n)=p(f(n))$ for some $f(n)\geq n$. Since
  $p$ is a legal attack against $\tau$,
    \[
      p'(n)
        =
      p(f(n))
        \in
      \tau(\emptyset,0)
        \cap
      \bigcap_{m<f(n)}\tau(\<p(m)\>,m+1)
    \]
    \[
        =
      \tau(\emptyset,0)
        \cap
      \bigcap_{m<n}\tau(\<p'(m)\>,f(m)+1)
        =
      \onePtComp{X}
        \setminus
      \left(
        \sigma(\emptyset,0)
          \cup
        \bigcup_{m<n,i\leq f(m)+1}\sigma(\<p'(m)\>,i)
      \right)
    \]
    \[
        \subseteq
      \onePtComp{X}
        \setminus
      \left(
        \sigma(\emptyset,0)
          \cup
        \bigcup_{m<n}\sigma(\<p'(m)\>,m+1)
      \right)
    \]
  so $p'$ is a legal attack against $\sigma$. Since $\sigma$ is a winning
  strategy, the points $p'(n)$ are locally finite in $X$, so
  $p'$ and therefore $p$ converge to $\infty$.

  If $\sigma$ is a winning mark for $\pl O$ in
  $\gruConGame{\onePtComp X}{\infty}$, let $\tau$ be a mark for
  $\pl K$ in $\gruKPGame{X}$ such that
    \[
      \tau(s,n) = X\setminus \sigma(s,n)
    \]
  Then for any legal attack $p$ against $\tau$, $p$ is a legal attack against
  $\sigma$. Since $\sigma$ is a winning
  strategy, $p$ converges to $\infty$,
  and therefore the points $p(n)$ are locally finite in $X$.

  The proofs of the first and third bullets are similar and are left to
  the reader.
\end{proof}

The reason why the games are not entirely equivalent is related to the extra
point $\infty$ in $\onePtComp X$, which gives $\pl P$ an extra choice in
$\gruConGame{\onePtComp X}{\infty}$ unavailable in $\gruKPGame{X}$.
In fact, a generalization of the above proof for a $(k+2)$-mark would not
hold.

For instance, suppose $\pl P$ wants to use a winning $2$-tactic $\sigma$ from
$\gruKPGame{X}$ to create a winning $2$-tactic for
$\gruConGame{\onePtComp X}{\infty}$. If $\pl P$ is attacked by
$\<x_0,\infty,x_2,\infty,\dots\>$, then $\pl P$ must ensure that the $x_{2n}$
converge without using the point $\infty\not\in X$.
It's difficult to see how, as $\pl P$ may not take advantage of
$\sigma(\<x_{2n},x_{2n+2}\>)$;
$x_{2n},x_{2n+2}$ are not consecutive moves in the original game.

So we cannot (at least easily) find a result for $\gruKPGame{X}$
comparable to the following result for $\gruConGame{X}{x}$:

\begin{proposition} For any $x\in X$ and $k<\omega$,
  \begin{itemize}
    \item
      $
      \pl O\ktactwin{(k+1)}\gruConGame{X}{x}
        \Leftrightarrow
      \pl O\tactwin\gruConGame{X}{x}
      $
    \item
      $
      \pl O\kmarkwin{(k+1)}\gruConGame{X}{x}
        \Leftrightarrow
      \pl O\markwin\gruConGame{X}{x}
      $
  \end{itemize}
\end{proposition}

\begin{proof}
  If $\sigma$ witnesses $\pl O\ktactwin{(k+1)}\gruConGame{X}{x}$,
  let $\tau(\emptyset)=\sigma(\emptyset)$ and
    \[
      \tau(\<p\>)
        =
      \bigcap_{i< k}
      \sigma(\<\underbrace{x,\dots,x}_{k-i},p,\underbrace{x,\dots,x}_{i+1}\>)
    \]

  Then $\tau$ is easily verified to be a winning tactic, and
  the proof for the second part is analogous.
\end{proof}

Note that this proof ironically relies on $\pl P$ playing
the point $x$ she wishes to avoid convergence to; a luxury not allowed to
$\pl P$ in $\gruKPGame{X}$ as that point ($\infty$) is fictional.

So we do have this corollary at least.

\begin{corollary}
  If $X$ is a locally compact space, then
  \begin{itemize}
    \item
    $X$ is metacompact if and only if
    $\pl K\tactwin\gruConGame{\onePtComp X}{\infty}$ if and only if
    $\pl K\ktactwin{(k+1)}\gruConGame{\onePtComp X}{\infty}$
    for some $k<\omega$, and
    \item
    $X$ is $\sigma$-metacompact if and only if
    $\pl K\markwin\gruConGame{\onePtComp X}{\infty}$ if and only if
    $\pl K\kmarkwin{(k+1)}\gruConGame{\onePtComp X}{\infty}$
    for some $k<\omega$.
  \end{itemize}
\end{corollary}

\section{A non-trivial example}

So if the analogous result does not hold for $\gruKPGame{X}$, then we
should be able to find a counterexample. Gruenhage suggested the following
class of spaces to the author:

\begin{definition}
  Let $\pmb X=(X\times 2^{<\omega})\cup C$ denote a Cantor tree
  of copies of a zero-dimensional, compact space $X$ with a point-countable
  cover $\mc{U} = \{U_\alpha : \alpha<\omega_1\}$ of distinct
  clopen sets, along with an uncountable subset of the Cantor set
  $C=\{c_\alpha:\alpha<\omega_1\}\in [2^\omega]^{\omega_1}$.
  The topology on $\pmb X$ is given by decaring $U\times\{s\}$ to be a open
  neighborhood of $\<x,s\>\in X\times 2^{<\omega}$ for each
  open neighborhood $U$ of $x$ in $X$, and declaring
  $
    B_{\alpha,m}
      =
    (U_\alpha\times\{c_\alpha\rest n: m\leq n<\omega\})\cup\{c_\alpha\}
  $
  to be a clopen neighborhood of $c_\alpha\in C$ for each $\alpha<\omega_1$,
  $m<\omega$.
\end{definition}

\begin{definition}
  Let $F\in \omega_1^{<\omega}$ and $m,n<\omega$.
  \[
    K_F = \bigcup_{\alpha \in F} B_{\alpha,0}
  \]
  \[
    a_n = \{\<i,0\>:i<n\}\cup\{\<n,1\>\}
  \]
  \[
    A = \{a_n : n<\omega\}
  \]
  \[
    K_F' = K_F \setminus (X \times A)
  \]
  \[
    L_m = X \times 2^{<m}
  \]
\end{definition}

Figure \ref{fig:pmbX} provides a rough illustration of
$\pmb X$, $L_m$ (the triangle at the base), and $K_F'$
(the branches of open sets descending from $C$).

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{pmbX.pdf}
  \caption{$\pmb X$, with $L_m$ and $K_F'$}
  \label{fig:pmbX}
\end{figure}

\begin{lemma}
  $K_F$, $K_F'$, and $L_m$ are compact in $\pmb X$.
  Furthermore, every compact set is contained in a union of $K_F'$, $L_m$
  for some $F\in C^{<\omega}$ and $m<\omega$.
\end{lemma}

\begin{proof}
  $K_F$ contains $C_F=\{c_\alpha: \alpha\in F\}\subseteq C$, so any
  cover of basic open sets must include $B_{\alpha,n_\alpha}$ for each
  $\alpha\in F$, and the remaining uncovered portion of $K_F$ is a closed
  subset of a finite union of copies of compact $X$. Then $K_F'$ is also
  compact as it is a closed subset of $K_F$, and $L_m$ is compact as it
  is a finite union of copies of compact $X$.

  Let $D$ be compact. Consider the open cover
    \[
      \{
        B_{\alpha,0}
      :
        \alpha<\omega_1
      \}
      \cup
      \{
        X\times\{s\}
      :
        s\in 2^{<\omega}
      \}
    \]
  and note that the finite subcover for $D$ contains subsets of some
  $K_F' \cup L_m$.
\end{proof}

\begin{theorem}
  $\pl K\win\gruKPGame{\pmb X}$.
\end{theorem}

\begin{proof}
  Since $\{U_\alpha:\alpha<\omega_1\}$ is a point-countable cover,
  for each $x\in X$ let $\alpha_{x,n}<\omega_1$ yield
  ordinals such that $x\in U_{\alpha_{x,n}}$ for $n<\omega$.

  Let $M:\pmb X\times \omega\to \mc K(\pmb X)$ as follows:
    \[
      M(\pmb x,n)
        =
      \left\{
        \begin{array}{lcl}
          K_{\{\alpha_{x,m}:m\leq n\}}
        & : &
          \pmb x = \<x,s\> \in X\times 2^{<\omega}
        \\
          K_{\{\alpha\}}
        & : &
          \pmb x = c_\alpha \in C
        \end{array}
      \right.
    \]
  and use $M$ to define the strategy $\sigma$ for each
  $\pmb a\in\pmb X^{<\omega}$:
    \[
      \sigma(\pmb a)
        =
      L_{|\pmb a|}
        \cup
      \bigcup_{i< |\pmb a|}
      M(\pmb a(i),|\pmb a|)
    \]

  Let $\pmb p:\omega\to\pmb X$ be a legal attack against $\sigma$. Then as
  $\pmb p(n)\not\in L_n$, for each $\pmb x=\<x,s\>\in X\times 2^{<\omega}$,
  $X\times\{s\}$ is an open neighborhood of $\pmb x$ which contains finitely
  many $\pmb p(n)$.

  Now consider $\pmb x=c_\alpha$ for some $\alpha<\omega_1$, and let $n<\omega$.
  Then if $\pmb p(n)=\<x,s\>$ with $\alpha = \alpha_{x,N}$ for some $N<\omega$,
  then $\pmb p(m)\not\in B_{\alpha,0}$ for $\max(n,N)<m<\omega$.
  Or, if $\pmb p(n)=c_\alpha$, then
  $\pmb p(m)\not\in B_{\alpha,0}$ for $n<m<\omega$.
  Otherwise, $\pmb p(m)\not\in B_{\alpha,0}$ for any $m<\omega$.
  In any case, $B_{\alpha,0}$ is a neighborhood of $\pmb x$ which
  contains finitely
  many $\pmb p(n)$. Therefore, $\sigma$ is a winning strategy.
\end{proof}

One might hope then that $\pl K\nottactwin\gruKPGame{\pmb X}$ but
$\pl K\ktactwin{2}\gruKPGame{\pmb X}$, giving us our counterexample.
However, we will see that in fact, any winning $k$-mark for $\pl K$ may
be improved to a winning tactic by exploiting the structure of the Cantor tree.

In particular, knowledge of round number does not assist $\pl K$,
since she may force $\pl P$ to either stay within $C$, or to seed a growing
integer which could be used in place of the round number
by forcing her to play outside $L_{|s|+1}$ in response to
$\<x,s\>\in X\times 2^{<\omega}$.

\begin{lemma}
  If $\pl K\kmarkwin{(k+1)}\gruKPGame{\pmb X}$, then
  $\pl K\ktactwin{(k+1)}\gruKPGame{\pmb X}$.
\end{lemma}

\begin{proof}
  Let $\sigma$ be a winning $(k+1)$-mark for $\pl K$ such that $m\leq n$ and
  $\ran r \subseteq \ran s$ implies $\sigma(r,m)\subseteq\sigma(s,n)$.
  For a sequence $p$, let $p\rest^k n=\nu_k(p\rest n)$ give the last $k$
  terms of $p\rest n$.

  Define $r:\pmb X\to\omega$ by
    \[
      r(\pmb x)
        =
      \left\{
        \begin{array}{lcl}
          |s|
        & : &
          \pmb x = \<x,s\> \in X\times 2^{<\omega}
        \\
          0
        & : &
          \pmb x \in C
        \end{array}
      \right.
    \]
  and use $r$ to define the $(k+1)$-tactic $\tau$ by
    \[
      \tau(\emptyset)
        =
      \sigma(\emptyset,0)
    \]
    \[
      \tau(\pmb t\concat\<\pmb x\>)
        =
      L_{r(\pmb x)+1}
        \cup
      \{\pmb x\}
        \cup
      \sigma(\pmb t\concat\<\pmb x\>,r(\pmb x)+1)
    \]

  Let $\pmb p:\omega\to\pmb X$ be a legal attack by $\pl P$ against $\tau$.
  If $\pmb p(n)\in C$ for $N<n<\omega$, then since no $\pmb p(n)$ may be legally
  repeated, $\{\{\pmb p(n)\}:N<n<\omega\}$ is a discrete collection, making
  the points $p(n)$ locally finite.

  Otherwise, let $f\in\omega^\omega$ be increasing and define
  $\pmb q:\omega\to X\times 2^{<\omega}$ such that $\pmb q(i)=\pmb p(f(i))$,
  and $\pmb p(j)\in X\times 2^{<\omega}$ implies there is some $i$ with $j=f(i)$.
  It follows that
    \[
      \pmb q(0)
        =
      \pmb p(f(0))
        \not\in
      \bigcup_{m\leq f(0)}\tau(\pmb p \rest^{k+1} m)
        \supseteq
      \tau(\emptyset)
        =
      \sigma(\emptyset,0)
    \]

  Denoting $\pmb q(n)=\<x_n,s_n\>$, it's trivial to note that $|s_0|\geq 0$.
  Assuming that $|s_m|\geq m$ for $m\leq n$,
  it then follows that
    \[
      \pmb q(n+1)
        =
      \pmb p(f(n+1))
        \not\in
      \bigcup_{m\leq f(n+1)}\tau(\pmb p\rest^{k+1} m)
    \]
    \[
        \supseteq
      \bigcup_{m\leq n}\tau(\pmb q\rest^{k+1} m)
        \supseteq
      \sigma(\emptyset,0)
        \cup
      \bigcup_{m < n}\sigma(\pmb q\rest^{k+1} (m+1),|s_m|+1)
    \]
    \[
        \supseteq
      \sigma(\emptyset,0)
        \cup
      \bigcup_{m < n}\sigma(\pmb q\rest^{k+1} (m+1),m+1)
    \]
  and
    \[
      \pmb q(n+1)
        \not\in
      \tau(\pmb q\rest^{k+1} (n+1))
        \supseteq
      L_{r(\pmb q(n))}
        =
      L_{|s_n|+1}
    \]
  gives $|s_{n+1}|\geq|s_n|+1\geq n+1$.
  Thus $\pmb q$ is a legal attack on the winning $(k+1)$-Markov strategy
  $\sigma$, so the points $q(n)$ are locally finite,
  and it follows that the points $p(n)$ are also locally finite.
\end{proof}

\begin{corollary}
  $\pmb X$ is $\sigma$-metacompact if and only if $\pmb X$ is metacompact.
\end{corollary}

On the other hand, recalling a maximum of $k+1$ moves is only as good as
recalling the most recent move for $\pl K$, since $\pl P$ may always choose
to burn $k$ out of every $k+1$ moves
by moving down an antichain of the Cantor tree. Such movement would certainly
be locally finite (and therefore not directly benefit $\pl P$), but would
at least succeed in overloading $\pl K$'s limited memory.

\begin{lemma}
  If $\pl K\ktactwin{(k+1)}\gruKPGame{\pmb X}$, then
  $\pl K\tactwin\gruKPGame{\pmb X}$.
\end{lemma}

\begin{proof}
  Let $\sigma$ be a winning $(k+1)$-tactical strategy, and without loss of
  generality assume it ignores order.

  Define $F(x_0,\dots,x_{k},n)\in [C]^{<\omega}$ and
  $m(x_0,\dots,x_{k},n)\in\omega\setminus(n+1)$, both increasing on $n$,
  such that for each $\<x_0,\dots,x_{k}\>\in X^{k+1}$,
  \[
    \bigcup_{s_0,\dots,s_k \in 2^{\leq n}}
    \sigma(\<x_0,s_0\>,\dots,\<x_{k},s_{k}\>)
      \subseteq
    K'_{F(x_0,\dots,x_{k},n)} \cup L_{m(x_0,\dots,x_{k},n)}
  \]

  Select an arbitrary point $y \in X$.
  Let
    \[
      M^0(x,n)=n
    \]
    \[
      M^{i+1}(x,n)=m(x,y,\dots,y,M^i(x,n)+1)
    \]
  and define the tactical strategy $\tau$ as follows:
  \[
    \tau(\emptyset)
      =
    \sigma(\emptyset)
  \]
  \[
    \tau(\<c_\alpha\>)
      =
    \{c_\alpha\}
  \]
  \[
    \tau(\<\<x,s\>\>)
      =
    K'_{F(x,y,\dots,y,M^k(x,|s|)+1)}
      \cup
    L_{m(x,y,\dots,y,M^k(x,|s|)+1)}
  \]

  Let $\pmb p:\omega\to \pmb X$ be a legal attack against
  $\tau$, and assume $\pmb p(n)=\<x_n,s_n\>\in X\times 2^{<\omega}$.
  Then consider the attack $\pmb q:\omega\to X\times 2^{<\omega}$ against
  $\sigma$ defined by, for $n<\omega$ and $i<k$,
    \[
      \pmb q((k+1)n)=\pmb p(n)=\<x_n,s_n\>
    \]
    \[
      \pmb q((k+1)n+(i+1))=\<y, a_{M^{i+1}(x_n,|s_n|)}\>
    \]

  Since
    \[
      \<x_{n+1},s_{n+1}\>
        =
      \pmb p(n+1)
        \not\in
      \tau(\<\pmb p(n)\>)
        \supseteq
      L_{M^{k+1}(x_n,|s_n|)+1}
    \]
  it follows that
  $|s_{n+1}|\geq M^{i+1}(x_n,|s_n|)+1$ for $i<k$; furthermore,
    \[
      |s_n|
        \leq
      M^i(x_n,|s_n|)
        <
      M^i(x_n,|s_n|)+1
        \leq
      M^{i+1}(x_n,|s_n|)
        <
      M^{i+1}(x_n,|s_n|)+1
        \leq
      |s_{n+1}|
    \]
  so the second coordinate of $\pmb q(n)$ is always strictly increasing.

  By the definition of $\tau$,
    \[
      \pmb q((k+1)n)
        =
      \pmb p(n)
        \not\in
      \bigcup_{m\leq n}
      \tau(\pmb p\rest^1 m)
        \supseteq
      \bigcup_{m\leq (k+1)n}
      \sigma(\pmb q\rest^{k+1} m)
    \]

  Since
    \[
      \pmb q((k+1)n+(i+1))
        =
      \<y, a_{M^{i+1}(x_n,|s_n|)}\>
        \in
      X\times A
    \]
  it follows that $\pmb q((k+1)n+(i+1))\not\in K'_F$ for any
  $F\in[\omega_1]^{<\omega}$.

  Then it's sufficient to note that
    \[
      |a_{M^{i+1}(x_n,|s_n|)}|
        =
      M^{i+1}(x_n,|s_n|) + 1
        >
      m(x_n,y,\dots,y,M^i(x_n,|s_n|)+1)
    \]
  to show that
    \[
      \pmb q((k+1)n+(i+1))
        =
      \<y, a_{M^{i+1}(x_n,|s_n|)}\>
        \not\in
      L_{m(x_n,y,\dots,y,M^i(x_n,|s_n|)+1)}
    \]
  and therefore $\pmb q((k+1)n+(i+1))$ is a legal move.

  As a result, $\pmb q$ is a legal attack against $\sigma$, and
  $\{\{\pmb q(n)\}:n<\omega\}\supseteq\{\{\pmb p(n)\}:n<\omega\}$ are
  both locally finite.

  Finally, if the range of $\pmb p$ intersects $C$, those moves may be safely
  ignored as they cannot be repeated and lay in a closed discrete set,
  so the proof is complete.
\end{proof}

So our hopes for a counterexample to our main question
in $\pmb X$ are thusly defeated. Our
consolation prize will be to show that for a certain choice of $X$
and $\{U_\alpha:\alpha<\omega_1\}$, $\pmb X$ is at least
an example of a space which allows a winning strategy for $\gruKPGame{\pmb X}$
but no winning $k$-tactics or $k$-marks.

To this end, we will show that $\{U_\alpha:\alpha<\omega_1\}$ may be chosen
such that $\pmb X$ is not metacompact, and therefore
$\pl K$ lacks a $k$-Markov strategy for any $k<\omega$.

\begin{theorem}
  $\pmb X$ is metacompact
    if and only if
  $\{U_\alpha:\alpha<\omega_1\}$ is $\sigma$-point-finite.
\end{theorem}

\begin{proof}
  Let $\omega_1=\bigcup_{n<\omega}A_n$ such that
  $\{U_\alpha:\alpha\in A_n\}$ is point-finite for each $n<\omega$.

  Let $\mc U$ be a cover of $\pmb X$, and for each $s\in 2^\omega$
  let $\mc V_s$ be a finite open refinement of $\mc C$ covering the compact
  set $X\times\{s\}$. Then let $\mc W_n = \{B_{\alpha,n_\alpha}:\alpha\in A_n\}$
  be an open refinement of $\mc C$ for each $n<\omega$, and note that it
  is point-finite. It follows that
  $\mc U' = \bigcup_{s\in 2^{<\omega}} \mc V_s \cup \bigcup_{n<\omega} \mc W_n$
  is an open $\sigma$-point-finite refinement of $\mc U$, so $\pmb X$
  is $\sigma$-metacompact, and therefore it is metacompact.

  For the other direction, consider the open cover
  $\mc U = \{B_{\alpha,0}:\alpha<\omega_1\}$ of the closed subset $C$ of
  metacompact $\pmb X$, and let $\{B_{\alpha,n_\alpha}:\alpha<\omega_1\}$ be
  a point-finite refinement. Then
  $\mc U_s = \{ U_\alpha : c_\alpha \rest n_\alpha = s\}$ is
  point-finite for $s\in 2^{<\omega}$ and
  $U_\alpha\in\mc U_{c_\alpha\rest n_\alpha}$ for each $\alpha<\omega_1$.
  Therefore $\mc U = \bigcup_{s\in 2^{<\omega}} \mc U_s$ is
  $\sigma$-point-finite.
\end{proof}

\begin{theorem}
  There exists a compact, zero-dimensional topological space $X$
  with a clopen cover $\{U_\alpha : \alpha<\omega_1\}$ of distinct
  sets which is not $\sigma$-point-finite.
\end{theorem}

\begin{proof}
  Let $Y$ be a zero-dimensional Corson compact space which is not Eberlein
  compact; one such space was constructed in \cite{Marciszewski1991291}.
  Let $X=Y^2$.
  Then by characterizations of Corson and Eberlien compacts found in
  \cite{MR752278},
  $Y^2\setminus\Delta$ is meta-Lindel\"of but not $\sigma$-metacompact, so
  there exists a point-countable clopen cover $\mc U$ of $Y^2\setminus\Delta$
  which is not $\sigma$-point-finite. Then $\mc U\cup\{X\}$ is a point-countable
  clopen cover of $X$ which is not $\sigma$-point-finite.
\end{proof}

\begin{corollary}
  There exists a locally compact space $X$ such that $\pl K\win\gruKPGame{X}$
  but $\pl K\notkmarkwin{k} \gruKPGame{X}$ for all $k<\omega$.
\end{corollary}

\bibliographystyle{plain}
\bibliography{../../bibliography}

\end{document}

### 2015-03-25 articles/k-tactics-in-gruenhages-compact-point-game/article.tex
add acknowledgements and other small tweaks

@@
 This question is very similar to the open question on the well-known
-Banach-Mazur (also known as Choquet) game $\bmGame{X}$ where $\pl N$
-is the player wishing for a nonempty intersection: does there exist a
+Banach-Mazur (a.k.a. Choquet) game $\bmGame{X}$: does there exist a
 space for which
-$\pl N\ktactwin{3}\bmGame{X}$ but $\pl N\notktactwin{2}\bmGame{X}$?
-(The analogous question for $2$- and $1$-tactics was answered in the
-affirmative by Gabriel Debs in \cite{MR817083}.) For fans
+$\pl N\ktactwin{3}\bmGame{X}$ but $\pl N\notktactwin{2}\bmGame{X}$
+(where $\pl N$
+is the player wishing for a nonempty intersection)?\footnote{
+  The analogous question for $2$- and $1$-tactics was answered in the
+  affirmative by Gabriel Debs in \cite{MR817083}.
+}
+For fans
 of such infinite combinatorial game theory puzzles, we may restate the
@@
 
+\section{Acknowledgements}
+
+The author would like to thank his PhD advisor Gary Gruenhage for his
+support and mentorship while the author developed these results as a part of
+his dissertation.
+
 \bibliographystyle{plain}

### 2015-03-27 articles/k-tactics-in-gruenhages-compact-point-game/article.tex
incorporate suggestions from G

@@
 \begin{abstract}
-Gary Gruenhage showed in \cite{MR858337} that metacompactness and
+Gary Gruenhage showed in \cite{MR858337} that metacompactness and\break
 $\sigma$-metacompactness may be characterized for locally compact spaces
-by way of a certain topological game using limited information strategies
+by way of a certain topological game using limited information strategies:
+strategies
 which consider only the most recent move of the opponent (tactical/stationary
@@
 follows: are metacompactness and $\sigma$-metacompactness characterized by
-winning $k$-tactical and $k$-Markov strategies?
+winning $k$-tactical and $k$-Markov strategies for $k>1$?
 \end{abstract}
@@
 \begin{game}
-  Let $\gruKPGame{X}$ denote the \term{Gruenhage compact/point game}
+  Let $\gruKPGame{X}$ denote \term{Gruenhage's compact/point game}
   with players $\pl K$, $\pl P$. During round $n$, $\pl K$ chooses
@@
   always results in a win for the player $\pl P$ using it, then it is called a
-  \term{winning strategy} and we write $\pl P\win G$.
+  \term{winning strategy}. If a winning strategy exists for $\pl P$ in the
+  game $G$, then we write $\pl P\win G$.
 \end{definition}
@@
 
-The above game was used by the author's adviser Gary Gruenhage in
+$\gruKPGame{X}$ was used by Gary Gruenhage in
 \cite{MR858337} to characterize
@@
 (every open cover of the space has a $\sigma$-point-finite open refinement
-covering the space) in locally compact spaces. However, the characterization
+covering the space) in locally compact spaces. This characterization
 considers so-called \term{limited information strategies} which do not use
@@
   $\sigma:M^{\leq k}\to M$; intuitively, it is a strategy which only considers
-  the previous $k$ moves of the opponent. If using such a strategy
-  always results in a win for the player $\pl P$ using it, then
-  we write $\pl P\ktactwin{k} G$.
+  the previous $k$ moves of the opponent. If a winning $k$-tactical strategy
+  exists for $\pl P$ in the game $G$, then we write $\pl P\ktactwin{k} G$.
 \end{definition}
@@
   only considers the previous $k$ moves of the opponent and the round number.
-  If using such a strategy
-  always results in a win for the player $\pl P$ using it, then
-  we write $\pl P\kmarkwin{k} G$.
+  If a winning $k$-Markov strategy exists for
+  $\pl P$ in the game $G$, then we write $\pl P\kmarkwin{k} G$.
 \end{definition}
@@
 
-For instance, suppose $\pl P$ wants to use a winning $2$-tactic $\sigma$ from
+For instance, suppose $\pl O$ wants to use a winning $2$-tactic $\sigma$
+for $\pl K$ in
 $\gruKPGame{X}$ to create a winning $2$-tactic for
-$\gruConGame{\onePtComp X}{\infty}$. If $\pl P$ is attacked by
-$\<x_0,\infty,x_2,\infty,\dots\>$, then $\pl P$ must ensure that the $x_{2n}$
-converge without using the point $\infty\not\in X$.
-It's difficult to see how, as $\pl P$ may not take advantage of
+$\gruConGame{\onePtComp X}{\infty}$. If $\pl O$ is attacked by
+$\<x_0,\infty,x_2,\infty,\dots\>$, then $\pl O$ must ensure that the $x_{2n}$
+converge without considering the point $\infty\not\in X$.
+It's difficult to see how, as $\pl O$ may not take advantage of
 $\sigma(\<x_{2n},x_{2n+2}\>)$;
@@
 \begin{definition}
-  Let $\pmb X=(X\times 2^{<\omega})\cup C$ denote a Cantor tree
+  Let $\mb X=(X\times 2^{<\omega})\cup C$ denote a Cantor tree
   of copies of a zero-dimensional, compact space $X$ with a point-countable
@@
   $C=\{c_\alpha:\alpha<\omega_1\}\in [2^\omega]^{\omega_1}$.
-  The topology on $\pmb X$ is given by decaring $U\times\{s\}$ to be a open
+  The topology on $\mb X$ is given by decaring $U\times\{s\}$ to be a open
   neighborhood of $\<x,s\>\in X\times 2^{<\omega}$ for each
@@
 Figure \ref{fig:pmbX} provides a rough illustration of
-$\pmb X$, $L_m$ (the triangle at the base), and $K_F'$
+$\mb X$, $L_m$ (the triangle at the base), and $K_F'$
 (the branches of open sets descending from $C$).
@@
   \includegraphics[width=\linewidth]{pmbX.pdf}
-  \caption{$\pmb X$, with $L_m$ and $K_F'$}
+  \caption{$\mb X$, with $L_m$ and $K_F'$}
   \label{fig:pmbX}
@@
 \begin{lemma}
-  $K_F$, $K_F'$, and $L_m$ are compact in $\pmb X$.
+  $K_F$, $K_F'$, and $L_m$ are compact in $\mb X$.
   Furthermore, every compact set is contained in a union of $K_F'$, $L_m$
@@
 \begin{theorem}
-  $\pl K\win\gruKPGame{\pmb X}$.
+  $\pl K\win\gruKPGame{\mb X}$.
 \end{theorem}
@@
 
-  Let $M:\pmb X\times \omega\to \mc K(\pmb X)$ as follows:
+  Let $M:\mb X\times \omega\to \mc K(\mb X)$ as follows:
     \[
@@
   and use $M$ to define the strategy $\sigma$ for each
-  $\pmb a\in\pmb X^{<\omega}$:
+  $\pmb a\in\mb X^{<\omega}$:
     \[
@@
 
-  Let $\pmb p:\omega\to\pmb X$ be a legal attack against $\sigma$. Then as
+  Let $\pmb p:\omega\to\mb X$ be a legal attack against $\sigma$. Then as
   $\pmb p(n)\not\in L_n$, for each $\pmb x=\<x,s\>\in X\times 2^{<\omega}$,
@@
 
-One might hope then that $\pl K\nottactwin\gruKPGame{\pmb X}$ but
-$\pl K\ktactwin{2}\gruKPGame{\pmb X}$, giving us our counterexample.
-However, we will see that in fact, any winning $k$-mark for $\pl K$ may
+One might hope then that $\pl K\nottactwin\gruKPGame{\mb X}$ but
+$\pl K\ktactwin{2}\gruKPGame{\mb X}$, giving us our counterexample.
+However, we will see that in fact, any winning $k$-tactic or even
+$k$-mark for $\pl K$ may
 be improved to a winning tactic by exploiting the structure of the Cantor tree.
 
-In particular, knowledge of round number does not assist $\pl K$,
+We first show that knowledge of round number does not assist $\pl K$,
 since she may force $\pl P$ to either stay within $C$, or to seed a growing
@@
 \begin{lemma}
-  If $\pl K\kmarkwin{(k+1)}\gruKPGame{\pmb X}$, then
-  $\pl K\ktactwin{(k+1)}\gruKPGame{\pmb X}$.
+  If $\pl K\kmarkwin{(k+1)}\gruKPGame{\mb X}$, then
+  $\pl K\ktactwin{(k+1)}\gruKPGame{\mb X}$.
 \end{lemma}
@@
 
-  Define $r:\pmb X\to\omega$ by
+  Define $r:\mb X\to\omega$ by
     \[
@@
 
-  Let $\pmb p:\omega\to\pmb X$ be a legal attack by $\pl P$ against $\tau$.
+  Let $\pmb p:\omega\to\mb X$ be a legal attack by $\pl P$ against $\tau$.
   If $\pmb p(n)\in C$ for $N<n<\omega$, then since no $\pmb p(n)$ may be legally
@@
 \begin{corollary}
-  $\pmb X$ is $\sigma$-metacompact if and only if $\pmb X$ is metacompact.
+  $\mb X$ is $\sigma$-metacompact if and only if $\mb X$ is metacompact.
 \end{corollary}
@@
 \begin{lemma}
-  If $\pl K\ktactwin{(k+1)}\gruKPGame{\pmb X}$, then
-  $\pl K\tactwin\gruKPGame{\pmb X}$.
+  If $\pl K\ktactwin{(k+1)}\gruKPGame{\mb X}$, then
+  $\pl K\tactwin\gruKPGame{\mb X}$.
 \end{lemma}
@@
 
-  Let $\pmb p:\omega\to \pmb X$ be a legal attack against
+  Let $\pmb p:\omega\to \mb X$ be a legal attack against
   $\tau$, and assume $\pmb p(n)=\<x_n,s_n\>\in X\times 2^{<\omega}$.
@@
 So our hopes for a counterexample to our main question
-in $\pmb X$ are thusly defeated. Our
+in $\mb X$ are thusly defeated. Our
 consolation prize will be to show that for a certain choice of $X$
-and $\{U_\alpha:\alpha<\omega_1\}$, $\pmb X$ is at least
-an example of a space which allows a winning strategy for $\gruKPGame{\pmb X}$
+and $\{U_\alpha:\alpha<\omega_1\}$, $\mb X$ is at least
+an example of a space which allows a winning strategy for $\gruKPGame{\mb X}$
 but no winning $k$-tactics or $k$-marks.
@@
 To this end, we will show that $\{U_\alpha:\alpha<\omega_1\}$ may be chosen
-such that $\pmb X$ is not metacompact, and therefore
+such that $\mb X$ is not metacompact, and therefore
 $\pl K$ lacks a $k$-Markov strategy for any $k<\omega$.
@@
 \begin{theorem}
-  $\pmb X$ is metacompact
+  $\mb X$ is metacompact
     if and only if
@@
 
-  Let $\mc U$ be a cover of $\pmb X$, and for each $s\in 2^\omega$
+  Let $\mc U$ be a cover of $\mb X$, and for each $s\in 2^\omega$
   let $\mc V_s$ be a finite open refinement of $\mc C$ covering the compact
@@
   $\mc U' = \bigcup_{s\in 2^{<\omega}} \mc V_s \cup \bigcup_{n<\omega} \mc W_n$
-  is an open $\sigma$-point-finite refinement of $\mc U$, so $\pmb X$
+  is an open $\sigma$-point-finite refinement of $\mc U$, so $\mb X$
   is $\sigma$-metacompact, and therefore it is metacompact.
@@
   $\mc U = \{B_{\alpha,0}:\alpha<\omega_1\}$ of the closed subset $C$ of
-  metacompact $\pmb X$, and let $\{B_{\alpha,n_\alpha}:\alpha<\omega_1\}$ be
+  metacompact $\mb X$, and let $\{B_{\alpha,n_\alpha}:\alpha<\omega_1\}$ be
   a point-finite refinement. Then

### 2015-03-28 phd/talks-and-presentations/2015-03-29-topological-proximal-game.tex
Add topological proximal game talk

% $Header: /home/vedranm/bitbucket/beamer/solutions/generic-talks/generic-ornate-15min-45min.en.tex,v 90e850259b8b 2007/01/28 20:48:30 tantau $

\documentclass{beamer}

% This file is a solution template for:

% - Giving a talk on some subject.
% - The talk is between 15min and 45min long.
% - Style is ornate.

\usepackage{amssymb}

% Copyright 2004 by Till Tantau <tantau@users.sourceforge.net>.
%
% In principle, this file can be redistributed and/or modified under
% the terms of the GNU Public License, version 2.
%
% However, this file is supposed to be a template to be modified
% for your own needs. For this reason, if you use this file as a
% template and not specifically distribute it as part of a another
% package/program, I grant the extra permission to freely copy and
% modify this file as you see fit and even to delete this copyright
% notice.

\mode<presentation>
{
  \usetheme{Warsaw}
  % or ...

  \setbeamercovered{transparent}
  % or whatever (possibly just delete it)
}

      \newtheorem{proposition}[theorem]{Proposition}
      \theoremstyle{definition}
      \newtheorem{game}[theorem]{Game}
      \newtheorem{question}[theorem]{Question}

\usepackage[english]{babel}
% or whatever

\usepackage[latin1]{inputenc}
% or whatever

\usepackage{times}
\usepackage[T1]{fontenc}
% Or whatever. Note that the encoding and the font should match. If T1
% does not look nice, try deleting the line with the fontenc.

\usepackage{marvosym} % For \Smiley
\usepackage{verbatim} % for \verbatiminput

\usepackage{tikz}
\usetikzlibrary{matrix} % for diagrams

\title
{Limited information strategies for a topological proximal game}

\subtitle
{AMS Southeastern Sectional Meeting} % (optional)

\author%[Author, Another] % (optional, use only with lots of authors)
{Steven~Clontz~http://stevenclontz.com}%\inst{1} \and S.~Another\inst{2}}
% - Use the \inst{?} command only if the authors have different
%   affiliation.

\institute[Auburn University] % (optional, but mostly needed)
{
  %\inst{1}%
  Department of Mathematics and Statistics\\
  Auburn University}
  %\and
  %\inst{2}%
  %Department of Theoretical Philosophy\\
  %University of Elsewhere}
% - Use the \inst command only if there are several affiliations.
% - Keep it simple, no one is interested in your street address.

\date[15-03-29] % (optional)
{March 29, 2015}

% If you have a file called "university-logo-filename.xxx", where xxx
% is a graphic format that can be processed by latex or pdflatex,
% resp., then you can add a logo as follows:

 % \pgfdeclareimage[height=1cm]{university-logo}{auburn_logo.png}
 % \logo{\pgfuseimage{university-logo}}

% Delete this, if you do not want the table of contents to pop up at
% the beginning of each subsection:
%\AtBeginSubsection[]
%{
%  \begin{frame}<beamer>{Outline}
%    \tableofcontents[currentsection,currentsubsection]
%  \end{frame}
%}

% If you wish to uncover everything in a step-wise fashion, uncomment
% the following command:

%\beamerdefaultoverlayspecification{<+->}

\usepackage{../../clontzDefinitions}

\begin{document}
\renewcommand{\pause}{}
\newcommand{\vspacing}{\vspace{1em}}
\newcommand{\vpause}{\pause\vspacing}

\begin{frame}
  \titlepage
\end{frame}

\section{Bell's Proximal Game}

\subsection{Definition}

\begin{frame}
  \small
  \begin{game}
  Bell's absolutely proximal game $\bellAbsConGame{X}$ \cite{MR3239205} (2014)
    \begin{figure}
      \includegraphics[width=0.6\linewidth]{proximalGameAlt.pdf}
    \end{figure}

  $\pl D$ wins the game if the points chosen by $\pl P$ converge.
  Otherwise, $\pl P$ wins.
  \end{game}
\end{frame}

\subsection{Motivation}

\begin{frame}
  If $\pl D\win \bellAbsConGame{X}$, then $X$ is called an
  \term{absolutely proximal space}.
  ``Absolutely proximal'' is a strengthening of ``proximal'', but these
  concepts coincide for (uniformlly locally) compact spaces.

  \vpause

  This game was brought to my attention due to this result: \cite{MR3239205}

  \begin{theorem}
    Every proximal space is a $W$-space. So
    $\pl D\win\bellAbsConGame{X} \Rightarrow \pl O\win\gruConGame{X}{x}$
    for all $x\in X$.
  \end{theorem}
\end{frame}

\begin{frame}
  Proximal spaces have strong preservation properties, as any
  closed subset or $\Sigma$-product of proximal spaces is proximal.

  \vpause

  Since any metrizable space is proximal, and
  any proximal space is collectionwise normal, Bell's game gives an elegant
  proof of the classic result of Rudin and Gulko:

  \begin{theorem}
    A $\Sigma$-product of metrizable spaces is collection-wise normal.
  \end{theorem}
\end{frame}

\begin{frame}
  Nyikos \cite{MR3288115} observed that
  \begin{proposition}
    Corson compact spaces are proximal.
  \end{proposition}
  and asked if the converse holds as well.

  \vpause

  With Gruenhage, I showed that the answer is yes: \cite{MR3227201}
  \begin{theorem}
    A compact space is Corson compact if and only if it is proximal.
  \end{theorem}
\end{frame}

\section{Topologizing Bell's game}

\subsection{Uniform Spaces}

\begin{frame}
  Player $\pl D$ chooses \term{entourages} of the diagonal: elements of
  a \term{uniformity} inducing the topology of the space.

  \vpause

  A uniformity $\mb D$ on $X$ is a filter of subsets of $X^2$
  satisfying:
  \begin{itemize}
    \item $\bigcap \mb D = \Delta=\{\<x,x\>:x\in X\}$
    \item $D\in\mb D$ implies $D^{-1}=\{\<y,x\>:\<x,y\>\in D\}\in\mb D$
    \item for each $D\in\mb D$ there is $\frac{1}{2}D\in\mb D$ such that
          $\frac{1}{2}D\circ\frac{1}{2}D\subseteq D$
  \end{itemize}

  \vpause

  The topology induced by a uniformity is the smallest topology such that
  $D[x]=\{y:\<x,y\>\in D\}$ is a neighborhood of $x$ for each $D\in\mb D$.
\end{frame}

\subsection{Universal uniformity}

\begin{frame}
  Our goal is to obtain a purely topological characterization of the
  proximal properties.

  \vpause

  As it turns out, the union of all uniformities inducing a topology is
  itself a uniformity inducing that topology, called the
  \term{universal uniformity}. Furthermore, $\pl D\win\bellAbsConGame{X}$
  if and only if $\pl D$ is required to choose from the universal uniformity.

  \vpause

  This reduces our goal to characterizing the universal entourages.
\end{frame}

\begin{frame}
  From Willard's topology text \cite{MR2048350}, we have such
  a characterization:

  \begin{theorem}
    A neighborhood $U$ of the diagonal is a universal uniformity if
    and only if there
    exist neighborhoods $U_n$ for $n<\omega$ where $U=U_0$ and
    $U_{n+1}\circ U_{n+1}\subseteq U_n$.
  \end{theorem}

  \pause

  As a bonus, for strongly collectionwise normal
  ($\Leftarrow$ paracompact) spaces, \textit{all} neighborhoods of
  the diagonal have this property.

  \vpause

  So we topologize Bell's game by
  saying an ``entourage'' is any (open symmetric) neighborhood of the
  diagonal with this property, and discard the need to consider a
  specific uniform structure.
\end{frame}

\section{Limited information strategies}

\subsection{Definitions}

\begin{frame}
  A \term{perfect information strategy} uses full information of the
  previous moves of the opponent. ($\pl A\win G$)

  \vpause
  A \term{$k$-tactical strategy} only uses the last $k$
  previous moves of the opponent. ($\pl A\ktactwin{k} G$)

  \vpause
  A \term{$k$-Markov strategy} only uses the round number and the last $k$
  previous moves of the opponent. ($\pl A\kmarkwin{k} G$)

  \vpause
  If omitted, assume $k=1$.
\end{frame}

\subsection{Lemmas and generalizations}

\begin{frame}\small
  Bell showed that a winning perfect information strategy may always
  be passed down to win in a closed subspace.

  \begin{proposition}
    If $\pl D\win\bellAbsConGame{X}$, then
    $\pl D\win\bellAbsConGame{H}$ for every closed subspace $H$ of $X$.
  \end{proposition}

  \pause

  This actually holds in general:

  \begin{proposition}
    If $\pl D\ktactwin{k}\bellAbsConGame{X}$, then
    $\pl D\ktactwin{k}\bellAbsConGame{H}$ for every closed subspace $H$ of $X$.
  \end{proposition}

  \begin{proposition}
    If $\pl D\kmarkwin{k}\bellAbsConGame{X}$, then
    $\pl D\kmarkwin{k}\bellAbsConGame{H}$ for every closed subspace $H$ of $X$.
  \end{proposition}
\end{frame}

\begin{frame}
  Bell's also showed that winning strategies
  are preserved for $\Sigma$-products.

  \begin{theorem}
    If $\pl D\win\bellAbsConGame{X_\alpha}$ for $\alpha<\kappa$, then
    $\pl D\win\bellAbsConGame{\sum_{\alpha<\kappa}X_\alpha}$.
  \end{theorem}

  \vpause

  Idea of proof: during round $n$, consider the first $n$ non-zero coordinates
  of the previous $n$ moves by $\pl P$ and use the winning strategies for
  those finite coordinates. Note that this uses the round number
  and perfect information of all previous moves.

\end{frame}

\begin{frame}
  We settle for considering a countable product instead (but still require
  knowledge of the round number).

  \begin{theorem}
    If $\pl D\kmarkwin{k}\bellAbsConGame{X_i}$ for $i<\omega$,
    then $\pl D\kmarkwin{k}\bellAbsConGame{\prod_{i<\omega} X_i}$.
  \end{theorem}

  Probable counter-example for generalization:
  $\pl D\notmarkwin\bellAbsConGame{\sum_{\alpha<\omega_1} 2}$?
\end{frame}

\subsection{An application}

\begin{frame}
  Existence of a winning limited information strategy characterizes a
  stronger topological property than the existence of a winning perfect
  information strategy.

  \vpause

  As it turns out:

  \begin{theorem}
    A compact space $X$ is strongly Eberlein compact if and only if
    $\pl D\tactwin\bellAbsConGame{X}$.
  \end{theorem}
\end{frame}

\begin{frame}{Sketch of Proof}
  Easy direction:

  \begin{definition}
    Strong Eberlein compacts embed in $\sigmaProdTwo\kappa$ for
    some $\kappa$.
  \end{definition}

  \begin{lemma}
    $\pl D\tactwin\bellAbsConGame{\sigmaProdTwo\kappa}$.
  \end{lemma}
\end{frame}

\begin{frame}{Sketch of Proof (cont.)}
  Lemmas which give the other direction:

  \begin{lemma}[Gruenhage \cite{MR752278}]
    Scattered proximal compacts are strong Eberlein compact.
  \end{lemma}

  \begin{lemma}
    Non-scattered proximal compacts contain copies of the Cantor space
    $2^\omega$.
  \end{lemma}

  \begin{lemma}
    $\pl D\nottactwin\bellAbsConGame{2^\omega}$.
  \end{lemma}
\end{frame}

\section{Questions?}

\begin{frame}
  Any questions?
\end{frame}

\begin{frame}[allowframebreaks]
  \tiny
  \bibliographystyle{plain}
  \bibliography{../../bibliography}
\end{frame}

\end{document}

### 2015-05-14 phd/talks-and-presentations/2015-05-13-topological-proximal-game.tex
add topological proximal game talk for spring topology conference

--- 2015-03-28 phd/talks-and-presentations/2015-03-29-topological-proximal-game.tex
@@
 \subtitle
-{AMS Southeastern Sectional Meeting} % (optional)
+{Spring Topology Conference 2015} % (optional)
 
@@
 
-\institute[Auburn University] % (optional, but mostly needed)
+\institute[Auburn, AL] % (optional, but mostly needed)
 {
   %\inst{1}%
-  Department of Mathematics and Statistics\\
-  Auburn University}
+  Auburn, AL}
   %\and
@@
 
-\date[15-03-29] % (optional)
-{March 29, 2015}
+\date[15-05-13] % (optional)
+{May 13, 2015}
 
@@
     \begin{figure}
-      \includegraphics[width=0.6\linewidth]{proximalGameAlt.pdf}
+      \includegraphics[width=0.6\linewidth]{proximalGamePrime.pdf}
     \end{figure}
@@
 
-  This game was brought to my attention due to this result: \cite{MR3239205}
+  This game connects to a game of Gary Gruenhage: \cite{MR3239205}
 

### 2015-05-15 phd/talks-and-presentations/2015-05-13-topological-proximal-game.tex
final touches to conference talk

@@
 \subtitle
-{Spring Topology Conference 2015} % (optional)
+{Spring Topology and Dynamics Conference 2015\\
+Bowling Green State University} % (optional)
 
 \author%[Author, Another] % (optional, use only with lots of authors)
-{Steven~Clontz~http://stevenclontz.com}%\inst{1} \and S.~Another\inst{2}}
+{Steven~Clontz}%\inst{1} \and S.~Another\inst{2}}
 % - Use the \inst{?} command only if the authors have different
@@
 \begin{document}
-% \renewcommand{\pause}{}
+\renewcommand{\pause}{}
 \newcommand{\vspacing}{\vspace{1em}}
@@
 
-\section{Bell's Proximal Game}
+\section{Proximal Game}
 
@@
   \term{absolutely proximal space}.
-  ``Absolutely proximal'' is a strengthening of ``proximal'', but these
-  concepts coincide for (uniformlly locally) compact spaces.
+  ``Absolutely proximal'' is a strengthening of ``proximal'' characterized
+  by an easier game (for \(\pl D\)), but these games are equivalent for
+  compact spaces.
 
@@
 
-\section{Topologizing Bell's game}
+\section{Topological proximal game}
 
@@
   itself a uniformity inducing that topology, called the
-  \term{universal uniformity}. Furthermore, $\pl D\win\bellAbsConGame{X}$
+  \term{fine} or \term{universal uniformity}.
+  Furthermore, $\pl D\win\bellAbsConGame{X}$
   if and only if $\pl D$ is required to choose from the universal uniformity.
@@
 \begin{frame}
-  From Willard's topology text \cite{MR2048350}, we have such
-  a characterization:
+  If you look in the right textbook \cite{MR2048350}, you'll
+  find the answer:
 
   \begin{theorem}
-    A neighborhood $U$ of the diagonal is a universal uniformity if
+    A neighborhood $U$ of the diagonal is a universal entourage if
     and only if there
@@
 
-  As a bonus, for strongly collectionwise normal
-  ($\Leftarrow$ paracompact) spaces, \textit{all} neighborhoods of
-  the diagonal have this property.
+  As a bonus, for paracompact spaces, \textit{all} neighborhoods of
+  the diagonal have this property (entourages may be converted to open
+  covers and then star-refined).
 
@@
 
-  So we topologize Bell's game by
-  saying an ``entourage'' is any (open symmetric) neighborhood of the
-  diagonal with this property, and discard the need to consider a
-  specific uniform structure.
+  So we topologize Bell's game by simply calling the open symmetric
+  neighborhoods of the diagonal with the above property ``entourages'',
+  and discard the need to consider a specific uniform structure.
 \end{frame}
@@
   \vpause
-  A \term{$k$-Markov strategy} only uses the round number and the last $k$
-  previous moves of the opponent. ($\pl A\kmarkwin{k} G$)
+  A \term{$k$-Markov strategy} only uses the last $k$
+  previous moves of the opponent and the round number.
+  ($\pl A\kmarkwin{k} G$)
 
@@
 \begin{frame}\small
-  Bell showed that a winning perfect information strategy may always
+  Bell observed that a winning perfect information strategy may always
   be passed down to win in a closed subspace.
@@
 
-  This actually holds in general:
+  This also holds for limited information strategies:
 
@@
 \begin{frame}
-  We settle for considering a countable product instead (but still require
-  knowledge of the round number).
+  If we allow ourselves the round number, we may at least handle countable
+  products:
 
@@
 
+\begin{frame}
+  A neat corollary:
+
+  \pause
+
+  \begin{itemize}
+  \item For compact spaces, \(\pl O\win\gruConGame{X^2}{\Delta}\) if and only
+  if \(\pl D\win\bellAbsConGame{X}\).
+  \end{itemize}
+
+  \pause
+
+  but:
+
+  \begin{itemize}
+  \item Any metric space satisfies \(\pl O\tactwin\gruConGame{X^2}{\Delta}\),
+  but \(\pl D\tactwin\bellAbsConGame{X}\) implies zero-dimensionality for
+  compact spaces.
+  \end{itemize}
+\end{frame}
+
 \section{Questions?}

### 2015-05-15 phd/talks-and-presentations/2015-05-13-topological-proximal-game.tex
final draft - add pauses

@@
   Our goal is to obtain a purely topological characterization of the
-  proximal properties.
+  proximal property.
 
@@
   \term{fine} or \term{universal uniformity}.
-  Furthermore, $\pl D\win\bellAbsConGame{X}$
-  if and only if $\pl D$ is required to choose from the universal uniformity.
+  Furthermore, the proximal property is agnostic to which uniformity
+  is chosen for the space's topology.
 
@@
 
-  This reduces our goal to characterizing the universal entourages.
+  If there's a winning strategy for $\pl D$ given any uniformity for
+  the topology on $X$, then
+  that strategy also works with the universal uniformity for $X$
+  containing it.
+  This reduces our goal to characterizing the entourages of the
+  universal uniformity.
 \end{frame}
@@
 
-  So we topologize Bell's game by simply calling the open symmetric
-  neighborhoods of the diagonal with the above property ``entourages'',
+  So we topologize Bell's game by simply saying an ``entourage''
+  is any open symmetric neighborhood of the diagonal with the above property,
   and discard the need to consider a specific uniform structure.
@@
 
-  Probable counter-example for generalization:
-  $\pl D\notmarkwin\bellAbsConGame{\sum_{\alpha<\omega_1} 2}$?
+  It seems likely that
+  $\pl D\notmarkwin\bellAbsConGame{\sum_{\alpha<\omega_1} 2}$,
+  but I don't have a proof. Whether
+  $\pl D\kmarkwin{2}\bellAbsConGame{\sum_{\alpha<\omega_1} 2}$
+  holds is less clear.
 \end{frame}
@@
   \item Any metric space satisfies \(\pl O\tactwin\gruConGame{X^2}{\Delta}\),
-  but \(\pl D\tactwin\bellAbsConGame{X}\) implies zero-dimensionality for
-  compact spaces.
+  but for compact spaces, \(\pl D\tactwin\bellAbsConGame{X}\) implies
+  \(X\) is scattered.
   \end{itemize}

### 2015-05-19 postdoctoral/flexibly_markov.tex
add 2tactic proximal observation, add flexibly Markov notes

\documentclass[11pt]{article}

\usepackage{../clontzStyle}
\usepackage{../clontzDefinitions}

\begin{document}

  \begin{definition}
    A \term{flexibly Markov} strategy for a game \(\<G,M\>\)
    is a pair of functions
    \(\<\sigma,\rho\>\in M^{M\times\omega}\times M^{M^{<\omega}}\).
    Intuitively, \(\sigma\) is a Markov strategy using a single move
    of the opponent and the round number, and \(\tau\) is a strategy
    which applies the Markov strategy to each of the opponent's
    previous moves individually each round.

    Let \(\sigma':M^{<\omega}\to M^{<\omega}\) be
    defined by \(|\sigma'(s)|=|s|\) and
    \(\sigma'(s)(m)=\sigma(s(m),|s|)\).
    Then more rigorously, \(\<\sigma,\rho\>\)
    is a winning flexibly Markov strategy if and only if
    \(\tau:M^{<\omega}\to M\) defined by
    \(\tau(s)=\rho\circ\sigma'(s)\) is a winning strategy.
  \end{definition}

  \begin{definition}
    A \term{semi-flexibly Markov} strategy for a game \(\<G,M\>\)
    is a pair of functions
    \(\<\sigma,\phi\>\in M^{M\times\omega}\times\omega^{\omega}\).
    Intuitively, \(\sigma\) is a Markov strategy using a single move
    of the opponent and the round number, and \(\phi\) is a strategy
    for choosing how far in the past the move of the opponent should be
    chosen.

    More rigorously, \(\<\sigma,\phi\>\) is a winning semi-flexibly
    Markov strategy if and only if \(\tau:M^{<\omega}\to M\) defined
    by \(\tau(s)=\sigma(s(|s|-1-\phi(|s|)),|s|)\) is a winning
    strategy.
  \end{definition}

  \begin{proposition}
    \(\pl F\semiflexmarkwin\schFillWeakGame{\kappa}\)
  \end{proposition}

  \begin{proof}
    Let \(\phi\) satisfy \(|\phi^{-1}(n)|=\omega\) and
    \(\sigma(C,n)=C\rest n\). Then since \(\sigma\) sees every move
    of \(\pl C\) infinitely often, it follows that it covers every move
    of \(\pl C\).
  \end{proof}

  \begin{proposition}
    For compact \(X\),
    \(\pl D\win\bellAbsConGame{X}\) if and only if
    \(\pl D\flexmarkwin\bellAbsConGame{X}\)
  \end{proposition}

  \begin{proof}
    The forward direction is the only interesting direction. In this case,
    \(X\) is Corson compact and embeddable in the \(\Sigma\)-product of
    reals.
    Let \(\phi\) satisfy \(|\phi^{-1}(n)|=\omega\), and let \(supp(x)\)
    be the countable support of \(x\), with
    \(supp_{n+1}(x)\supseteq supp_{n}(x)\) finite and
    \(\bigcup_{n<\omega}supp_n(x)=supp(x)\).

    Let \(\sigma(x,n)=D(2^{-n},supp_n(x))\). Then since \(\sigma\) sees
    every move infinitely often, the non-zero coordinates are all Cauchy
    and converge.
  \end{proof}

\end{document}

### 2015-05-28 postdoctoral/strategic_fan_tightness.tex
add strategic fan tightness result

\documentclass[11pt]{article}

\usepackage{../clontzStyle}
\usepackage{../clontzDefinitions}

\begin{document}

  \begin{definition}
    Let \(\menGame{X}\) be the Menger game played on \(X\).
    Let \(\barmanDowFanGame{X}{x}\) be the countable fan tightness
    game introduced by Barman and Dow in \cite{MR2678950}: \(\pl B\)
    chooses a set \(B_n\) with \(x\in\cl{B_n}\), followed by
    \(\pl F\) choosing \(F_n\in[B_n]^{<\omega}\), where \(\pl F\)
    wins if \(x\in\cl{\bigcup_{n<\omega} F_n}\).
  \end{definition}

  \begin{theorem}
    \(X^k\) is Menger for all \(k<\omega\) if and only if
    \(C_p(X)\) has countable fan tightness.
  \end{theorem}

  \begin{proof}
    Arhangel'ski{\u\i} in \cite{MR526012}.
  \end{proof}

  \begin{theorem}
    If \(\pl F\markwin\menGame{X}\), then
    \(\pl F\markwin\barmanDowFanGame{C_p(X)}{\vec 0}\).
  \end{theorem}

  \begin{proof}
    Essentially \cite[2.6]{MR2868880}, once one observes that
    \(\pl F\markwin\menGame{X}\) characterizes
    \(\sigma\)-relative-compactness (equivalent to \(\sigma\)-compactness
    in regular spaces). Note further that this
    property is preserved for finite powers.
  \end{proof}

  \begin{theorem}
    If \(\pl F\win\menGame{X^k}\) for all \(k<\omega\), then
    \(\pl F\win\barmanDowFanGame{C_p(X)}{\vec 0}\).
  \end{theorem}

  \begin{proof}
    For a sequence of blades
    \(s\concat\<B\>\in(\mc P(X))^{\leq\omega}\) satisfying
    \(\vec 0\in \cl{s(i)}\) for all \(i<|s|\), let
    \(t_k^m(s\concat\<B\>)\) be the sequence defined by
      \[
        t_k^m(s\concat\<B\>)(i)
          =
        \{
          (f^{-1}[(-2^{-i-m},2^{-i-m})])^k
        :
          f\in s\concat\<B\>(i)
        \}
      \]
    for each \(i\leq|s|\). In the case \(i=|s|\), note
      \[
        t_k^m(s\concat\<B\>)(|s|)
          =
        \{
          (f^{-1}[(-2^{-|s|-m},2^{-|s|-m})])^k
        :
          f\in B
        \}
      \]

    We claim that \(t_k(s\concat\<B\>)(i)\) is an open cover of \(X^k\) for
    each \(i\leq|s|\).
    Indeed, for \(\alpha\in X^k\), \(U(\vec 0,\text{ran}\alpha,2^{-i-m})\) is
    an open neighborhood of \(\vec 0\), and thus must hit some
    \(f\in s\concat\<B\>(i)\). Note then that
    \(\alpha\in(f^{-1}[(-2^{-i-m},2^{-i-m})])^k\).

    For a sequence \(s\) of length \(\leq\omega\), define its offset by
    \(n\), \(s\offset n\), as follows. Let
    \(s\offset n=\emptyset\) when \(n\geq|s|\) and otherwise
    satsify \(|s\offset n|+n=|s|\) and \(s\offset n(i)=s(n+i)\).

    If \(\sigma_k\) is the winning strategy for \(\pl F\) in \(\menGame{X^k}\),
    then let \(\tau^m\) be a strategy for \(\pl F\) in
    \(\barmanDowFanGame{C_p(X)}{\vec 0}\) satisfying
      \[
        \sigma_k(t_k^m(s\concat\<B\>))
          \subseteq
        \{
          (f^{-1}[(-2^{-|s|-m},2^{-|s|-m})])^k
        :
          f\in \tau^m(s\concat\<B\>)
        \}
      \]
    and \(\tau\) be a winning strategy satisfying
      \[
        \tau(s\concat\<B\>)
          =
        \bigcup_{m\leq|s|}
        \tau^m((s\offset m)\concat\<B\>)
      \]

    Attack \(\tau\) with \(a\). Let \(\alpha\in X^k\) and \(m<\omega\).
    Since \(t_k^m(a\offset m)\) is an attack on \(\sigma\) in
    \(\menGame{X^k}\), there is some \(n<\omega\) where
    \(\alpha\in\bigcup\sigma_k(t_k^m((a\offset m)\rest(n+1)))\),
    and therefore \(\alpha\in (f^{-1}[(-2^{-n-m},2^{-n-m})])^k\) for
    some \(f\in\tau^m((a\offset m)\rest(n+1))\), so
    \(
      f
        \in
      U(\vec 0,\text{ran}\alpha,2^{-n})
        \cap
      \tau(a\rest(n+m+1))
    \).
  \end{proof}

\newpage
\bibliographystyle{plain}
\bibliography{../bibliography}

\end{document}

### 2015-08-19 articles/destroying-metrizability-in-generalized-inverse-limits/article.tex
add scott's article draft

\documentclass{amsart}

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}

\usepackage{graphicx}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{game}[theorem]{Game}
\newtheorem{example}[theorem]{Example}
\newtheorem{question}[theorem]{Question}

\newcommand{\<}{\langle}
\renewcommand{\>}{\rangle}

\title{Joint work on long u.s.c. inverse limits}

\author{Steven Clontz, Scott Varagona}

\date{\today}

\begin{document}

\begin{abstract}
If $X$ is a compact Hausdorff space, an upper semi-continuous bonding function $f: X \rightarrow 2^{X}$ is said to be idempotent if $f^2 = f$. In this short paper, we prove that if $f: [0,1] \rightarrow C([0,1])$ is u.s.c., idempotent and surjective, but $f$ is not the identity, then the inverse limit with the single bonding function $f$ and with factor spaces indexed by the ordinal $\kappa$ contains a copy of $\kappa + 1$. It follows that such an inverse limit is only metric in the case where the index set $\kappa$ is countable.
\end{abstract}

\maketitle

\section{Introduction}

As various recent papers have shown (e.g., \cite{char roe}, \cite{varagona}, \cite{vernon}), continuum theorists have begun to broaden their study of generalized inverse limits to the case where the factor spaces are indexed by sets other than the positive integers. This more inclusive approach opens many new avenues for research, and has already produced some interesting results. For example, Patrick Vernon showed that an inverse limit indexed by the set of all integers with a single upper semi-continuous bonding function can be homeomorphic to a 2-cell \cite{vernon}, whereas V. Nall previously showed this is impossible for such an inverse limit indexed by the positive integers alone \cite{nall 2cell}.
\

In another recent paper \cite{varagona}, S. Varagona generalized many previously known theorems (from, e.g., \cite{ingram mahavier} and \cite{nall connected}) to the case of u.s.c. inverse limits indexed by arbitrary totally ordered sets. As he showed, in that context, inverse limits with a single idempotent upper semi-continuous bonding function become especially important. Relatively little is known about the kind of continua that may be produced by such inverse limits, however.
\

This short paper focuses on the case of an inverse limit with a single idempotent, surjective, upper semi-continuous, continuum-valued bonding function on $[0,1]$, when the index set of the inverse limit is some ordinal $\kappa$. In particular, we show that (so long as the bonding function is not the identity) such an inverse limit is metric exactly when $\kappa$ is countable. The strategy, as will be seen, is to show that the inverse limit must contain a copy of $\kappa + 1$.

\

\section{Background Definitions and Lemmas}

We begin with some useful notation. Let $X$ be a non-empty compact Hausdorff space. Then we denote by $2^X$ the set of all non-empty compact subsets of $X$. We say a subset $A$ of $X$ is a \emph{continuum} if $A$ is non-empty, compact and connected. $C(X)$ denotes the set of all elements of $2^X$ that are continua.
\

Suppose $X$ and $Y$ are non-empty compact Hausdorff spaces. Then the set-valued function $f: X \rightarrow 2^{Y}$ is said to be \emph{upper semi-continuous} (u.s.c.) at $x \in X$ if, for every open set $V$ in $Y$ with $f(x) \subseteq V$, there exists an open set $U$ in $X$ with $x \in U$ and $f(u) \subseteq V$ for each $u \in U$. If $f$ is u.s.c. at each $x \in X$, we simply say \emph{$f$ is u.s.c.} If $f: X \rightarrow 2^{Y}$ is a set-valued function, then the \emph{graph of $f$}, denoted $G(f)$, is given by $G(f) = \{\langle x , y \rangle \in X \times Y \ | \ y \in f(x)\}$. (Note that, to help distinguish between ordered pairs and interval subsets of the real line, we will use pointed brackets to denote ordered pairs, e.g., $\langle x , y \rangle$, whereas intervals are given in the traditional way with brackets or parentheses, e.g., $(a,b), [c,d]$, etc.) The set-valued function $f: X \rightarrow 2^{Y}$ is said to be \emph{surjective} if, for every $y \in Y$, there exists $x \in X$ with $y \in f(x)$. If a u.s.c. function $f: X \rightarrow 2^{Y}$ has the property that $f(x)$ is connected for each $x \in X$, then $f$ is \emph{continuum-valued}, and we denote this by writing  $f: X \rightarrow C(Y).$
\

The following characterization of u.s.c. functions (from \cite{i m paper}) is well-known and often more convenient to work with than the original definition:

\begin{lemma} If $X$ and $Y$ are non-empty compact Hausdorff spaces, then $f: X \rightarrow 2^{Y}$ is u.s.c. if and only if $G(f)$ is closed.
\end{lemma}

If $X$, $Y$, and $Z$ are non-empty compact Hausdorff spaces and $f : X \rightarrow 2^{Y}$ and $g: Y \rightarrow 2^{Z}$ are u.s.c., then the composition $g \circ f : X \rightarrow 2^{Z}$ is the u.s.c. function given by $(g \circ f)(x) = \{z \in Z \ | \ $There exists $y \in Y$ such that $y \in f(x)$ and $z \in g(y)\}$. In the special case where $f: X \rightarrow 2^{X}$, we denote $f \circ f$ by $f^2$. If $f^2 = f$, then we say $f$ is \emph{idempotent}.
\

Let $\kappa$ be an ordinal. (We follow the convention of set theory in which an ordinal is equal to the set of its predecessors. For more detailed background on ordinals, see, for example, \cite{Kunen}.) Suppose that for each $\alpha \in \kappa$, $X_{\alpha}$ is a non-empty compact Hausdorff space and whenever $\alpha \le \beta \in \kappa$, the set-valued function $f_{\alpha \beta} : X_{\beta} \rightarrow 2^{X_{\alpha}}$ is u.s.c. (With this notation, $f_{\alpha \alpha}$ always denotes the identity on $X_{\alpha}$.) Suppose further that, whenever $\alpha \le \beta \le \eta \in \kappa$, we have $f_{\alpha \beta} \circ f_{\beta \eta} = f_{\alpha \eta}$. Then the collection $\textbf{f} = \{ f_{\alpha \beta} \ | \ \alpha \le \beta \in \kappa\}$ of u.s.c. functions is said to be \emph{exact}. In this case, we say $\{X_{\alpha}, f_{\alpha \beta}, \kappa\}$ is an \emph{inverse limit system}; the \emph{inverse limit}, $\varprojlim \{X_{\alpha}, f_{\alpha \beta}, \kappa\}$, of this system is $\{ \textbf{x} \in \prod_{\alpha \in \kappa} X_{\alpha} \ | \ x_{\alpha} \in f_{\alpha \beta}(x_{\beta})$ for all $\alpha \le \beta \in \kappa\}$. (In keeping with tradition, a boldface $\textbf{x}$ always denotes an element of $\prod_{\alpha \in \kappa} X_{\alpha}$; the $\alpha$th coordinate of such an $\textbf{x}$ will be denoted $\textbf{x}(\alpha)$.)  We call the u.s.c. functions $f_{\alpha \beta}$ the \emph{bonding functions} of the inverse limit, and each $X_{\alpha}$ is called a \emph{factor space} of the inverse limit.
\

Because it can be difficult to check if a large collection of u.s.c. functions is exact, a much more tractable case would be that of an inverse limit system with a single idempotent bonding function $f$. That is, suppose $X$ is a non-empty compact Hausdorff space and $f: X \rightarrow 2^{X}$ is an idempotent u.s.c. function. If $X_{\alpha} = X$ for each $\alpha \in \kappa$ and $f_{\alpha \beta} = f$ for each $\alpha < \beta \in \kappa$, then $\{X_{\alpha}, f_{\alpha \beta}, \kappa\} = \{X, f, \kappa\}$ is an \emph{inverse limit system with the single bonding function $f$}, and we denote the inverse limit of the system as $\varprojlim \{X, f, \kappa\}$. (Of course, since $f$ is idempotent, the collection $\textbf{f}$ of bonding functions is automatically exact.) We note that, although the only continuous idempotent surjective function from a compact Hausdorff space $X$ to itself is the identity map, there are many non-trivial examples of u.s.c. idempotent surjective functions on $X$.
\

A detailed study of inverse limits with a single idempotent surjective u.s.c. bonding function was begun in \cite{varagona}. The following is a lemma from that paper which will be used repeatedly (often without being referenced explicitly) in the proofs to come.

\begin{lemma} \label{idemlemma}  Let $X$ be a compact Hausdorff space and let $f: X \rightarrow 2^{X}$ be u.s.c. Then $f$ is idempotent if and only if, whenever $f(x) = A$ for some $x \in X$ and $A \subseteq X$, $f(A) = A$.
\end{lemma}

\section{Main Results}

We now focus on the case of an inverse limit with a single idempotent, surjective, u.s.c. bonding function $f: [0,1] \rightarrow C([0,1])$. The main goal of this paper is to prove that if such an $f$ is not the identity map, then the inverse limit $\varprojlim \{[0,1], f, \kappa\}$ is metric exactly when the index set $\kappa$ is a countable ordinal.
\

Let us say a subset $S$ of $[0,1]^2$ satisfies condition $\Gamma$ if, for some $x, y \in [0,1]$ with $x \ne y$, $\<x,x\> \in S$, $\<y,y\> \in S$, and either $\<x,y\>$ or $\<y,x\> \in S$. Let $\Delta = \{\<a,a\> \ | \ a \in [0,1]\}$, and notice that $[0,1]^2 \setminus \Delta$ is the union of two disjoint open sets. Let $\iota$ be the identity map $\iota(x)=\{x\}$.

\begin{lemma}
If $f: [0,1] \rightarrow C([0,1])$ is u.s.c., then for some $x \in [0,1]$, $\<x,x\> \in G(f)$.
\end{lemma}

\begin{proof}
Suppose that $\<x,x\> \not\in S$ for all $x \in [0,1]$. Then $y > 0$ for all $y \in f(0)$, and $z < 1$ for all $z \in f(1)$. This means $([0,1]^2 \setminus \Delta) \cap G(f) = G(f)$ is the union of two non-empty disjoint open sets. However, since $f$ was continuum-valued and u.s.c., $G(f)$ was connected (by Theorem 2.5 from \cite{ingram intro}), yielding a contradiction.
\end{proof}

\begin{lemma}
If $f: [0,1] \rightarrow C([0,1])$ is u.s.c., idempotent, and surjective, then for some $x, y \in [0,1]$ with $x \not= y$, $\<x,x\> \in G(f)$ and $\<y,y\> \in G(f)$.
\end{lemma}

\begin{proof}
By Lemma 1, for some $x \in [0,1]$, $\<x,x\> \in G(f)$. Suppose by way of contradiction that, for all $y \in [0,1]$ with $y \not= x$, $\<y,y\> \not\in G(f)$.

\textbf{Case 1:}
$x = 0$. Since $\<1,1\> \not\in G(f)$, it follows that $f(1) \subseteq [0,1)$. It follows then that $f(z)\subseteq[0,z)$ for all $z\in(0,1]$, since $f(z)$ is an interval not containing $z$ and the graph of $f$ is connected. Therefore, as $f$ is surjective and $1 \not\in f(z)$ for all $z \in (0,1]$, $1 \in f(0)$. In fact, as $f(0)$ is connected and contains both $0$ and $1$, we know $f(0) = [0,1]$. Then for $z \in (0,1]$, $f(f(z))=f(z)\subseteq[0,z)\not=[0,1]$, and thus $0\not\in f(z)$, that is, $f(z)\subseteq(0,z)$.

Now consider $f(1)=[a,b]\subseteq(0,1)$. Then $f(f(1))=f([a,b])=[a,b]$, and in particular, $f(a)\subseteq[a,b]$. However, since $a\in(0,1]$, we also have $f(a)\subseteq(0,a)$, a contradiction.

\textbf{Case 2:}
$x = 1$. The proof is analogous to Case 1.

\textbf{Case 3:}
$x\in(0,1)$. Since $f(0)\subseteq(0,1]$ and the graph of $f$ is connected, $0\not\in f([0,x))$. Likewise, $f(1)\subseteq[0,1)$ and $1\not\in f((x,1])$. Since $f$ is surjective, $1\in f(v)$ for some $v\in[0,x]$ and $0\in f(w)$ for some $w\in[x,1]$. Let us say $f(v) = [k,1]$.

We note that in fact, $v=x$. If $v<x$ could hold, then $f(v)=[k,1]\subseteq(v,1]$. Then $f(f(v))=f([k,1])=[k,1]$, which forces $k\leq x$ as $1\not\in f((x,1])$. This results in a contradiction, as then $f([x,1])\subseteq f([k,1])=[k,1]$ while $0\in f(w)\subseteq f([x,1])$. So $[x,1]\subseteq f(x)$, and as $1\not\in f(1)$, we have that $x\not\in f(1)$ by the idempotence of $f$.

So, $f(1) = [a,b]$ where $[a,b] \subseteq [0,x)$ or $[a,b] \subseteq (x,1)$. If $[a,b] \subseteq (x,1)$, then since $a > x$, $f(a) \subseteq [0,a)$ while $f(a)\subseteq f([a,b])=f(f(1))=f(1)=[a,b]$, contradiction. On the other hand, if $[a,b] \subseteq [0,x)$, then since $b<x$, $f(b) \subseteq (b,1]$ while $f(b) \subseteq f([a,b])=f(f(1)=f(1)=[a,b]$, another contradiction. Since each possible case results in a contradiction, the proof is complete.

\end{proof}

\begin{lemma} \label{big lemma}
If $f: [0,1] \rightarrow C([0,1])$ is u.s.c., idempotent, and surjective, but $f \not=\iota$, then $G(f)$ satisfies condition $\Gamma$.
\end{lemma}

\begin{proof}
If $\Delta$ is a subset of $G(f)$, then since $f \not=\iota$, there must exist some point $\<x,y\> \in G(f)$ with $x \not= y$, and the result follows. So, suppose $\Delta$ is not a subset of $G(f)$. The result follows in either of two possible cases.

\textbf{Case 1.} There exist $x<y$ in $[0,1]$ such that $\<x,x\>$ and $\<y,y\>$ are elements of $G(f)$ but $\<p,p\>$ is not for all $x<p<y$.

Because $f$ is continuum-valued, we may assume $\min(f(p))>p$ for all $p\in(x,y)$. (The case $\max(f(p))<p$ is similar.) If $\max(f(x))<y$, then by the definition of u.s.c., there is some $p\in(x,y)$ such that $f(p)=[a,b]$ where $b<y$. It then follows from idempotence of $f$ that $f(b)\subseteq [a,b]\cap(b,1]=\emptyset$, a contradiction. Thus $\max(f(x))\geq y$ and therefore $\<x,y\>$, $\<x,x\>$, and $\<y,y\>$ all belong to $G(f)$.

\textbf{Case 2.} There exists $[x,y]\subsetneq[0,1]$ with $x<y$ and $\<p,p\>\in G(f)$ exactly when $p\in[x,y]$. Since $\Delta$ is not a subset of $G(f)$, this means either $0 \not\in [x,y]$ or $1 \not\in [x,y]$. Let us suppose $0\not\in[x,y]$. (The case $1\not\in[x,y]$ is similar.) Choose the minimal $z\in[0,1]$ satisfying $0\in f(z)$. Because $0 \not\in f(0)$, we know $f(0) \subseteq (0,1]$ and thus (because $G(f)$ is connected) $f(p) \subseteq (p,1]$ for $p \in [0,x)$. Thus, $z \in [x,1]$.

If $z=x$, then we claim that $\max(f(x))>x$. As justification, suppose not. Then $f(x) = [0,x]$ and $f([0,x]) = [0,x]$. Now if $x \in f(0)$, then $[0,x] = f(x) \subseteq f(f(0)) = f(0)$, which would imply that $0 \in f(0)$, contradicting the earlier statement that $0 \not\in f(0)$. So, $f(0) = [a,b] \subseteq (0,x)$. That means $f([a,b]) = [a,b]$, so $f(b) \subseteq [a,b]$. However, $f(b) \subseteq (b,1]$ also; this is also a contradiction. So indeed, $\max(f(x))>x$, and the result follows.

If $z\in(x,y]$, then the result follows immediately.

Finally, we demonstrate that $z\in(y,1]$ results in a contradiction. Let $f(z)=[0,d]\subseteq[0,z)$. Since $[0,d]=f(z)=f(f(z))=f([0,d])$, there is some $z'\in[0,d]\subseteq[0,z)$ satisfying $0\in f(z')$, even though $z$ was chosen to be minimal.
\end{proof}

\begin{lemma} \label{general lemma}
If $f:[0,1] \to 2^{[0,1]}$ is u.s.c. and idempotent and $G(f)$ satisfies condition $\Gamma$, then $\varprojlim\<[0,1],f,\kappa\>$ contains a copy of $\kappa + 1$.
\end{lemma}

\begin{proof}
As $G(f)$ satisfies $\Gamma$, let us say without loss of generality that $\<x,x\>, \<y,y\>$ and $\<x,y\>$ are elements of $G(f)$. $\varprojlim\<[0,1],f,\kappa\>$ contains the points $\textbf{x}_\alpha$ for $\alpha\leq\kappa$, defined by $\textbf{x}_\alpha(\beta)=y$ for $\beta<\alpha$ and $\textbf{x}_\alpha(\beta)=x$ otherwise. It's easy to see that $\{\textbf{x}_\alpha:\alpha\leq\kappa\}$ is a copy of $\kappa+1$.
\end{proof}

\begin{theorem} \label{main theorem}
If $f:[0,1]\to C([0,1])$ is u.s.c., idempotent, and surjective, but $f\not=\iota$, then $\varprojlim\<[0,1],f,\kappa\>$ contains a copy of $\kappa+1$.
\end{theorem}

\begin{proof}
The result follows immediately from Lemma \ref{big lemma} and Lemma \ref{general lemma}.
\end{proof}

\begin{corollary} \label{main corr}
An inverse limit with a single u.s.c., idempotent, surjective bonding function $f: [0,1] \rightarrow C([0,1])$ and index set $\kappa$, an ordinal, is only metric (in fact, Corson compact) in the case that $\kappa$ is countable or the bonding map is trivial.
\end{corollary}

\begin{proof}
If $f = \iota$, then of course the inverse limit is homeomorphic to $[0,1]$. So, suppose $f \ne \iota$. If $\kappa$ is countable, then because the inverse limit is a subspace of $[0,1]^{\kappa}$, it is metric. However, if $\kappa$ is uncountable, then by Theorem \ref{main theorem}, the inverse limit contains a copy of $\kappa + 1$ and is therefore non-metric.
\end{proof}

\section{Examples}

The following example helped inspire the main theorem of this paper.

\begin{example} \label{ex1} Let $f: [0,1] \rightarrow C([0,1])$ be given by $f(0) = [0,1]$ and $f(x) = \{1\}$ for each $x \ne 0$. Then $\varprojlim \langle [0,1], f, \kappa \rangle$ is metric exactly when $\kappa$ is a countable ordinal.
\end{example}

\begin{proof} $f$ is u.s.c. because $G(f)$ is closed, and obviously $f$ is continuum-valued and surjective. Since $f([0,1]) = [0,1]$ and $f(\{1\}) = \{1\}$, by Lemma \ref{idemlemma}, $f$ is idempotent. Thus, Corollary \ref{main corr} applies. (Note that one could also verify directly that $G(f)$ satisfies condition $\Gamma$ because $G(f)$ contains the ordered pairs $\langle 0,0 \rangle, \langle 1,1 \rangle, \langle 0,1 \rangle$).
\end{proof}

The discussion of this example in \cite{varagona} implies that this inverse limit is homeomorphic to a metric arc whenever $\kappa$ is a limit ordinal satifying $0 < \kappa < \omega_1$, but homeomorphic to the compactified long line when $\kappa = \omega_1$.
\

We give one more simple example to show that the surjectivity of the bonding function $f$ is necessary.

\begin{example} \label{ex2} Let $f: [0,1] \rightarrow C([0,1])$ be given by $f(x) = \{x\}$ for $0 \le x < 1/2$ and $f(x) = 1/2$ for $x \ge 1/2$.
\end{example}

Clearly $f$ is u.s.c. and idempotent and $f \ne \iota$; however, $G(f)$ does not satisfy condition $\Gamma$. Indeed, $\varprojlim \langle [0,1], f, \kappa \rangle$ is homeomorphic to a metric arc for all $\kappa > 0$.

\bibliographystyle{plain}
\begin{thebibliography}{10}

\smallskip

\bibitem{char roe} Wlodzimierz J. Charatonik and Robert P. Roe, {\it On Mahavier Products}, Topology and its Applications,
166, (2014), 92-97.

\smallskip

\bibitem{ingram mahavier} W. T. Ingram, William S. Mahavier, {\it Inverse Limits: from Continua to Chaos}, Springer, Developments in Mathematics (vol. 25), 2012.

\smallskip

\bibitem{i m paper} W. T. Ingram, William S. Mahavier, {\it Inverse limits of upper semi-continuous set valued functions}, Houston Journal of Mathematics, vol. 32 (2006) no. 1, 119-130.

\smallskip

\bibitem{ingram intro} W. T. Ingram, {\it An introduction to inverse limits with set-valued functions}, Springer Briefs in Mathematics, 2012.

\smallskip

\bibitem{Kunen} Kenneth Kunen, {\it Set Theory: An Introduction to Independence Proofs}, Elsevier B.V., 1980.

\smallskip

\bibitem{nall 2cell} Van Nall, {\it Inverse limits with set valued functions}, Houston Journal of Mathematics, 37 (2011), no. 4, 1323-1332.

\smallskip

\bibitem{nall connected} Van Nall, {\it Connected inverse limits with a set-valued function}, Topology Proc. 40 (2012), 167-177.

\smallskip

\bibitem{varagona} Scott Varagona, {\it Generalized Inverse Limits Indexed by Totally Ordered Sets}, preprint, 2015.

\smallskip

\bibitem{vernon} Patrick Vernon, {\it Inverse limits of set-valued functions indexed by the integers}, Topology Applications 171 (2014), 35-40.
\end{thebibliography}

\end{document}

### 2015-08-19 articles/destroying-metrizability-in-generalized-inverse-limits/article.tex
add my revisions

@@
 
-\title{Joint work on long u.s.c. inverse limits}
+\parskip=0.5em
+
+\title{Destruction of metrizability in generalized inverse limits}
 
@@
 Nall previously showed this is impossible for such an inverse limit indexed by the positive integers alone \cite{nall 2cell}.
-\
 
@@
 Relatively little is known about the kind of continua that may be produced by such inverse limits, however.
-\
 
@@
 The strategy, as will be seen, is to show that the inverse limit must contain a copy of $\kappa + 1$.
-
-\
 
@@
 $C(X)$ denotes the set of all elements of $2^X$ that are continua.
-\
 
@@
 at each $x \in X$, we simply say \emph{$f$ is u.s.c.} If $f: X \rightarrow 2^{Y}$ is a set-valued function, then the \emph{graph of $f$}, denoted $G(f)$, is given by $G(f) = \{\langle x , y \rangle \in X \times Y \ | \ y \in f(x)\}$.
-(Note that, to help distinguish between ordered pairs and interval subsets of the real line, we will use pointed brackets to denote ordered pairs, e.g., $\langle x , y \rangle$, whereas intervals are given in the traditional way with brackets or parentheses, e.g., $(a,b), [c,d]$, etc.) The set-valued function $f: X \rightarrow 2^{Y}$ is said to be \emph{surjective} if, for every $y \in Y$, there exists $x \in X$ with $y \in f(x)$.
+(Note that, to help distinguish between ordered pairs and intervals on a linearly ordered space, we will use pointed brackets to denote ordered pairs, e.g., $\langle x , y \rangle$, whereas intervals are given in the traditional way with brackets or parentheses, e.g., $(a,b), [c,d]$, etc.) The set-valued function $f: X \rightarrow 2^{Y}$ is said to be \emph{surjective} if, for every $y \in Y$, there exists $x \in X$ with $y \in f(x)$.
 If a u.s.c.
 function $f: X \rightarrow 2^{Y}$ has the property that $f(x)$ is connected for each $x \in X$, then $f$ is \emph{continuum-valued}, and we denote this by writing  $f: X \rightarrow C(Y).$
-\
 
@@
 If $f^2 = f$, then we say $f$ is \emph{idempotent}.
-\
 
@@
 functions is said to be \emph{exact}.
-In this case, we say $\{X_{\alpha}, f_{\alpha \beta}, \kappa\}$ is an \emph{inverse limit system}; the \emph{inverse limit}, $\varprojlim \{X_{\alpha}, f_{\alpha \beta}, \kappa\}$, of this system is $\{ \textbf{x} \in \prod_{\alpha \in \kappa} X_{\alpha} \ | \ x_{\alpha} \in f_{\alpha \beta}(x_{\beta})$ for all $\alpha \le \beta \in \kappa\}$.
+In this case, we say $\<X_{\alpha}, f_{\alpha \beta}, \kappa\>$ is an \emph{inverse limit system}; the \emph{inverse limit}, $\varprojlim \<X_{\alpha}, f_{\alpha \beta}, \kappa\>$, of this system is $\{ \textbf{x} \in \prod_{\alpha \in \kappa} X_{\alpha} \ | \ x_{\alpha} \in f_{\alpha \beta}(x_{\beta})$ for all $\alpha \le \beta \in \kappa\}$.
 (In keeping with tradition, a boldface $\textbf{x}$ always denotes an element of $\prod_{\alpha \in \kappa} X_{\alpha}$; the $\alpha$th coordinate of such an $\textbf{x}$ will be denoted $\textbf{x}(\alpha)$.)  We call the u.s.c.
 functions $f_{\alpha \beta}$ the \emph{bonding functions} of the inverse limit, and each $X_{\alpha}$ is called a \emph{factor space} of the inverse limit.
-\
 
@@
 function.
-If $X_{\alpha} = X$ for each $\alpha \in \kappa$ and $f_{\alpha \beta} = f$ for each $\alpha < \beta \in \kappa$, then $\{X_{\alpha}, f_{\alpha \beta}, \kappa\} = \{X, f, \kappa\}$ is an \emph{inverse limit system with the single bonding function $f$}, and we denote the inverse limit of the system as $\varprojlim \{X, f, \kappa\}$.
+If $X_{\alpha} = X$ for each $\alpha \in \kappa$ and $f_{\alpha \beta} = f$ for each $\alpha < \beta \in \kappa$, then $\<X_{\alpha}, f_{\alpha \beta}, \kappa\> = \<X, f, \kappa\>$ is an \emph{inverse limit system with the single bonding function $f$}, and we denote the inverse limit of the system as $\varprojlim \<X, f, \kappa\>$.
 (Of course, since $f$ is idempotent, the collection $\textbf{f}$ of bonding functions is automatically exact.) We note that, although the only continuous idempotent surjective function from a compact Hausdorff space $X$ to itself is the identity map, there are many non-trivial examples of u.s.c.
-idempotent surjective functions on $X$.
-\
+idempotent surjective functions on $X$; see Figure \ref{idempotentUsc} for examples.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\linewidth]{idempotent_usc.pdf}
+\end{center}
+\caption{Examples of u.s.c. idempotent surjective functions on [0,1]}
+\label{idempotentUsc}
+\end{figure}
 
@@
 The main goal of this paper is to prove that if such an $f$ is not the identity map, then the inverse limit $\varprojlim \{[0,1], f, \kappa\}$ is metric exactly when the index set $\kappa$ is a countable ordinal.
-\
 
@@
 Since each possible case results in a contradiction, the proof is complete.
-
 \end{proof}
@@
 
+Recall that a \textit{Corson compact} space is a compact space which embeds in a $\Sigma$-product of real lines (see \cite{alster}).
+All compact metric spaces are embeddable in $\mathbb R^\omega$ and therefore Corson compact.
+
 \begin{corollary} \label{main corr}
@@
 If $\kappa$ is countable, then because the inverse limit is a subspace of $[0,1]^{\kappa}$, it is metric.
-However, if $\kappa$ is uncountable, then by Theorem \ref{main theorem}, the inverse limit contains a copy of $\kappa + 1$ and is therefore non-metric.
+However, if $\kappa$ is uncountable, then by Theorem \ref{main theorem}, the inverse limit contains a copy of the non-Corson compact space $\kappa + 1$.
 \end{proof}
@@
 \begin{thebibliography}{10}
+
+\smallskip
+
+\bibitem{alster} Alster, K., and Pol, Roman. "On function spaces of compact subspaces of $\Sigma$-products of the real line." Fundamenta Mathematicae 107.2 (1980): 135-143.
 

### 2015-08-20 articles/destroying-metrizability-in-generalized-inverse-limits/article.tex
set bracket notation for inverse limits

@@
 functions is said to be \emph{exact}.
-In this case, we say $\<X_{\alpha}, f_{\alpha \beta}, \kappa\>$ is an \emph{inverse limit system}; the \emph{inverse limit}, $\varprojlim \<X_{\alpha}, f_{\alpha \beta}, \kappa\>$, of this system is $\{ \textbf{x} \in \prod_{\alpha \in \kappa} X_{\alpha} \ | \ x_{\alpha} \in f_{\alpha \beta}(x_{\beta})$ for all $\alpha \le \beta \in \kappa\}$.
+In this case, we say $\{X_{\alpha}, f_{\alpha \beta}, \kappa\}$ is an \emph{inverse limit system}; the \emph{inverse limit}, $\varprojlim \{X_{\alpha}, f_{\alpha \beta}, \kappa\}$, of this system is $\{ \textbf{x} \in \prod_{\alpha \in \kappa} X_{\alpha} \ | \ x_{\alpha} \in f_{\alpha \beta}(x_{\beta})$ for all $\alpha \le \beta \in \kappa\}$.
 (In keeping with tradition, a boldface $\textbf{x}$ always denotes an element of $\prod_{\alpha \in \kappa} X_{\alpha}$; the $\alpha$th coordinate of such an $\textbf{x}$ will be denoted $\textbf{x}(\alpha)$.)  We call the u.s.c.
@@
 function.
-If $X_{\alpha} = X$ for each $\alpha \in \kappa$ and $f_{\alpha \beta} = f$ for each $\alpha < \beta \in \kappa$, then $\<X_{\alpha}, f_{\alpha \beta}, \kappa\> = \<X, f, \kappa\>$ is an \emph{inverse limit system with the single bonding function $f$}, and we denote the inverse limit of the system as $\varprojlim \<X, f, \kappa\>$.
+If $X_{\alpha} = X$ for each $\alpha \in \kappa$ and $f_{\alpha \beta} = f$ for each $\alpha < \beta \in \kappa$, then $\{X_{\alpha}, f_{\alpha \beta}, \kappa\} = \{X, f, \kappa\}$ is an \emph{inverse limit system with the single bonding function $f$}, and we denote the inverse limit of the system as $\varprojlim \{X, f, \kappa\}$.
 (Of course, since $f$ is idempotent, the collection $\textbf{f}$ of bonding functions is automatically exact.) We note that, although the only continuous idempotent surjective function from a compact Hausdorff space $X$ to itself is the identity map, there are many non-trivial examples of u.s.c.
@@
 \begin{lemma} \label{general lemma}
-If $f:[0,1] \to 2^{[0,1]}$ is u.s.c. and idempotent and $G(f)$ satisfies condition $\Gamma$, then $\varprojlim\<[0,1],f,\kappa\>$ contains a copy of $\kappa + 1$.
+If $f:[0,1] \to 2^{[0,1]}$ is u.s.c. and idempotent and $G(f)$ satisfies condition $\Gamma$, then $\varprojlim\{[0,1],f,\kappa\}$ contains a copy of $\kappa + 1$.
 \end{lemma}
@@
 As $G(f)$ satisfies $\Gamma$, let us say without loss of generality that $\<x,x\>, \<y,y\>$ and $\<x,y\>$ are elements of $G(f)$.
-$\varprojlim\<[0,1],f,\kappa\>$ contains the points $\textbf{x}_\alpha$ for $\alpha\leq\kappa$, defined by $\textbf{x}_\alpha(\beta)=y$ for $\beta<\alpha$ and $\textbf{x}_\alpha(\beta)=x$ otherwise.
+$\varprojlim\{[0,1],f,\kappa\}$ contains the points $\textbf{x}_\alpha$ for $\alpha\leq\kappa$, defined by $\textbf{x}_\alpha(\beta)=y$ for $\beta<\alpha$ and $\textbf{x}_\alpha(\beta)=x$ otherwise.
 It's easy to see that $\{\textbf{x}_\alpha:\alpha\leq\kappa\}$ is a copy of $\kappa+1$.
@@
 \begin{theorem} \label{main theorem}
-If $f:[0,1]\to C([0,1])$ is u.s.c., idempotent, and surjective, but $f\not=\iota$, then $\varprojlim\<[0,1],f,\kappa\>$ contains a copy of $\kappa+1$.
+If $f:[0,1]\to C([0,1])$ is u.s.c., idempotent, and surjective, but $f\not=\iota$, then $\varprojlim\{[0,1],f,\kappa\}$ contains a copy of $\kappa+1$.
 \end{theorem}
@@
 \begin{example} \label{ex1} Let $f: [0,1] \rightarrow C([0,1])$ be given by $f(0) = [0,1]$ and $f(x) = \{1\}$ for each $x \ne 0$.
-Then $\varprojlim \langle [0,1], f, \kappa \rangle$ is metric exactly when $\kappa$ is a countable ordinal.
+Then $\varprojlim \{ [0,1], f, \kappa \}$ is metric exactly when $\kappa$ is a countable ordinal.
 \end{example}
@@
 and idempotent and $f \ne \iota$; however, $G(f)$ does not satisfy condition $\Gamma$.
-Indeed, $\varprojlim \langle [0,1], f, \kappa \rangle$ is homeomorphic to a metric arc for all $\kappa > 0$.
+Indeed, $\varprojlim \{ [0,1], f, \kappa \}$ is homeomorphic to a metric arc for all $\kappa > 0$.
 
@@
 
-\bibitem{alster} Alster, K., and Pol, Roman. "On function spaces of compact subspaces of $\Sigma$-products of the real line." Fundamenta Mathematicae 107.2 (1980): 135-143.
+\bibitem{alster} Alster, K., and Pol, Roman. ``On function spaces of compact subspaces of $\Sigma$-products of the real line.'' Fundamenta Mathematicae 107.2 (1980): 135-143.
 

### 2015-08-21 articles/destroying-metrizability-in-generalized-inverse-limits/article.tex
corrects per Scott's comments

@@
 If $X$ is a compact Hausdorff space, an upper semi-continuous bonding function $f: X \rightarrow 2^{X}$ is said to be idempotent if $f^2 = f$.
-In this short paper, we prove that if $f: [0,1] \rightarrow C([0,1])$ is u.s.c., idempotent and surjective, but $f$ is not the identity, then the inverse limit with the single bonding function $f$ and with factor spaces indexed by the ordinal $\kappa$ contains a copy of $\kappa + 1$.
+In this short paper, we prove that if $f: [0,1] \rightarrow C([0,1])$ is u.s.c., idempotent and surjective, but $f$ is not the identity, then the inverse limit with the single bonding function $f$ and with factor spaces indexed by a nonzero ordinal $\kappa$ contains a copy of $\kappa + 1$.
 It follows that such an inverse limit is only metric in the case where the index set $\kappa$ is countable.
@@
 
-This short paper focuses on the case of an inverse limit with a single idempotent, surjective, upper semi-continuous, continuum-valued bonding function on $[0,1]$, when the index set of the inverse limit is some ordinal $\kappa$.
+This short paper focuses on the case of an inverse limit with a single idempotent, surjective, upper semi-continuous, continuum-valued bonding function on $[0,1]$, when the index set of the inverse limit is some nonzero ordinal $\kappa$.
 In particular, we show that (so long as the bonding function is not the identity) such an inverse limit is metric exactly when $\kappa$ is countable.
@@
 (We follow the convention of set theory in which an ordinal is equal to the set of its predecessors.
-For more detailed background on ordinals, see, for example, \cite{Kunen}.) Suppose that for each $\alpha \in \kappa$, $X_{\alpha}$ is a non-empty compact Hausdorff space and whenever $\alpha \le \beta \in \kappa$, the set-valued function $f_{\alpha \beta} : X_{\beta} \rightarrow 2^{X_{\alpha}}$ is u.s.c.
+For more detailed background on ordinals, see, for example, \cite{Kunen}.
+Assume all ordinals are nonzero.) Suppose that for each $\alpha \in \kappa$, $X_{\alpha}$ is a non-empty compact Hausdorff space and whenever $\alpha \le \beta \in \kappa$, the set-valued function $f_{\alpha \beta} : X_{\beta} \rightarrow 2^{X_{\alpha}}$ is u.s.c.
 (With this notation, $f_{\alpha \alpha}$ always denotes the identity on $X_{\alpha}$.) Suppose further that, whenever $\alpha \le \beta \le \eta \in \kappa$, we have $f_{\alpha \beta} \circ f_{\beta \eta} = f_{\alpha \eta}$.
@@
 \textbf{Case 3:}
-$x\in(0,1)$.
-Since $f(0)\subseteq(0,1]$ and the graph of $f$ is connected, $0\not\in f([0,x))$.
-Likewise, $f(1)\subseteq[0,1)$ and $1\not\in f((x,1])$.
-Since $f$ is surjective, $1\in f(v)$ for some $v\in[0,x]$ and $0\in f(w)$ for some $w\in[x,1]$.
-Let us say $f(v) = [k,1]$.
+$x \in (0,1)$.
+Since $f(0) \subseteq (0,1]$ and the graph of $f$ is connected, $f(z) \subseteq (z,1]$ for each $z \in [0,x)$; thus, $0 \not\in f([0,x))$.
+Likewise,  since $f(1) \subseteq [0,1)$, we have $f(z) \subseteq [0,z)$ for each $z \in (x,1]$; thus, $1 \not\in f((x,1])$.
+Since $f$ is surjective,
+$1\in f(v)$ for some $v\in[0,x]$ and $0\in f(w)$ for some $w\in[x,1]$. Let us say $f(v) = [k,1]$.
 
@@
 If $[a,b] \subseteq (x,1)$, then since $a > x$, $f(a) \subseteq [0,a)$ while $f(a)\subseteq f([a,b])=f(f(1))=f(1)=[a,b]$, contradiction.
-On the other hand, if $[a,b] \subseteq [0,x)$, then since $b<x$, $f(b) \subseteq (b,1]$ while $f(b) \subseteq f([a,b])=f(f(1)=f(1)=[a,b]$, another contradiction.
+On the other hand, if $[a,b] \subseteq [0,x)$, then since $b<x$, $f(b) \subseteq (b,1]$ while $f(b) \subseteq f([a,b])=f(f(1))=f(1)=[a,b]$, another contradiction.
 Since each possible case results in a contradiction, the proof is complete.
@@
 $\varprojlim\{[0,1],f,\kappa\}$ contains the points $\textbf{x}_\alpha$ for $\alpha\leq\kappa$, defined by $\textbf{x}_\alpha(\beta)=y$ for $\beta<\alpha$ and $\textbf{x}_\alpha(\beta)=x$ otherwise.
-It's easy to see that $\{\textbf{x}_\alpha:\alpha\leq\kappa\}$ is a copy of $\kappa+1$.
+It is easy to see that $\{\textbf{x}_\alpha:\alpha\leq\kappa\}$ is a copy of $\kappa+1$.
 \end{proof}
@@
 
-Recall that a \textit{Corson compact} space is a compact space which embeds in a $\Sigma$-product of real lines (see \cite{alster}).
+A \textit{Corson compact} space is a compact space which embeds in a $\Sigma$-product of real lines (see \cite{alster}).
 All compact metric spaces are embeddable in $\mathbb R^\omega$ and therefore Corson compact.
@@
 
-\bibitem{alster} Alster, K., and Pol, Roman. ``On function spaces of compact subspaces of $\Sigma$-products of the real line.'' Fundamenta Mathematicae 107.2 (1980): 135-143.
+\bibitem{alster} Alster, K., and Pol, Roman, \textit{On function spaces of compact subspaces of $\Sigma$-products of the real line}, Fundamenta Mathematicae 107.2 (1980): 135-143.
 

### 2015-08-25 articles/applications-of-limited-information-strategies-in-mengers-game/article.tex
add copy/paste of chapter 6 to begin menger game article

\documentclass{amsart}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}

\usepackage{../../clontzDefinitions}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{game}[theorem]{Game}
\newtheorem{example}[theorem]{Example}
\newtheorem{question}[theorem]{Question}

\parskip=0.5em

\begin{document}

% \title{Proximal compact spaces are Corson compact\tnoteref{t1}}
% \tnotetext[t1]{2010 Mathematics Subject Classification. 54E15, 54D30, 54A20.}
\title{Applications of limited information strategies in Menger's game}

% \author[aub]{S.~Clontz\fnref{fn1}}
% \ead{steven.clontz@auburn.edu}
% \author[aub]{G.~Gruenhage\fnref{fn2}}
% \ead{gruengf@auburn.edu}

% \address[aub]{Department of Mathematics, Auburn University,
%  Auburn, AL 36830}

\author{Steven Clontz}
\address{Department of Mathematics and Statistics, UNC Charlotte,
Charlotte, NC 28262}
\email{steven.clontz@gmail.edu}
\urladdr{stevenclontz.com}

\keywords{Menger's property, Menger's game, limited information strategies}
% \begin{keyword}
%   Proximal\sep absolutely proximal\sep Corson compact\sep uniform space\sep $W$-space
% \end{keyword}

\subjclass[2010]{03E35, 54D20, 54D45, 91A44}

\begin{abstract}
  I need an abstract
\end{abstract}

\maketitle

I require an introduction.

\section{The Menger property and game}

Recall the following definition.

\begin{definition}
  A space $X$ is Menger if for every sequence $\<\mc U_0,\mc U_1,\dots\>$
  of open covers of $X$ there exists a sequence
  $\<\mc F_0,\mc F_1,\dots\>$ such that $\mc F_n\subseteq \mc U_n$,
  $|\mc F_n|<\omega$, and $\bigcup_{n<\omega}\mc F_n$ is a cover of $X$.
\end{definition}

Note that many authors refer to this property as \(S_{fin}(\mc O,\mc O)\),
where \(\mc O\) is the collection of open covers of \(X\), and
\(S_{fin}(A,B)\) denotes the selection property such that for each
sequence in \(A^\omega\), there are finite subsets of each entry for which
the union of these subsets belongs in \(B\).

\begin{proposition}
  $X$ is $\sigma$-compact
    $\Rightarrow$
  $X$ is Menger
    $\Rightarrow$
  $X$ is Lindel\"of.
\end{proposition}

None of these implications may be reversed; the irrationals are a simple example
of a Lindel\"of space which is not Menger, and we'll see several examples of
Menger spaces which are not $\sigma$-compact.

It can be shown via a non-trivial
proof that the following game can be used to characterize the Menger property.

\begin{definition}
  For each cover $\mc U$ of $X$, $S\subseteq X$ is \term{$\mc U$-finite} if
  there exists a finite subcollection of $\mc U$ which covers $C$.
\end{definition}

Of course, a compact space is $\mc U$-finite for all open covers $\mc U$.

\begin{game}
  Let $\menGame{X}$ denote the \term{Menger game} with players $\pl C$, $\pl F$.
  In round $n$, $\pl C$ chooses an open cover $\mc U_n$, followed by $\pl F$
  choosing a $\mc U_n$-finite subset $F_n$ of $X$.

  $\pl F$ wins the game if $X = \bigcup_{n<\omega}F_n$,
  and $\pl C$ wins otherwise.
\end{game}

\begin{theorem}
  A space $X$ is Menger if and only if $\pl C\notwin\menGame{X}$
  \cite{MR1544773}.
\end{theorem}

The typical characterization of the Menger game involves $\pl F$ choosing
a finite subcollection $\mc F_n$ of $\mc U_n$, but it is easy to see that the
characterization given above is equivalent, and will be convenient for use
in our proofs.

\section{Markov strategies}

To the author's knowledge, no other direct work has been done on limited
information strategies pertaining to the Menger game, although as we'll see
there are results which can be sharpened when considering them.
However, we immediately see that tactics are not of any real interest.

\begin{proposition}
  $X$ is compact if and only if
  $\pl F \tactwin \menGame{X}$ if and only if
  $\pl F \ktactwin{k} \menGame{X}$.
\end{proposition}

\begin{proof}
  If $\sigma$ is a winning $k$-tactic, then for each open cover $\mc U$,
  $\sigma$ defeats the attack $\<\mc U,\mc U,\dots\>$. Then
  \[
    \bigcup_{i\leq k} \sigma(\<\underbrace{\mc U,\dots,\mc U}_i\>) = X
  \]
  and $X$ is $\mc U$-finite.
\end{proof}

Essentially, because $\pl C$ may repeat the same finite sequence of open covers,
$\pl F$ needs to be seeded with knowledge of the round number to prevent being
trapped in a loop.

If $\pl F$'s memory of $\pl C$'s past moves is bounded, then
there is no need to consider more than the two most recent moves. The
intuitive reason is that $\pl C$ could simply play the same cover repeatedly
until $\pl F$'s memory is exhausted, in which case $\pl F$ would only ever
see the change from one cover to another.

\begin{theorem}
  For each $k<\omega$, $F \kmarkwin{(k+2)} \menGame{X}$
  if and only if $F \kmarkwin2 \menGame{X}$.
\end{theorem}

\begin{proof}
  Let $\sigma$ be a winning $(k+2)$-mark. We define the $2$-mark $\tau$ as
  follows:
    \[
      \tau(\<\mc U\>,0)
        =
      \bigcup_{m<k+2}
        \sigma(\<\underbrace{\mc U,\dots,\mc U}_{m+1}\>,m)
    \]
    \[
      \tau(\<\mc U,\mc V\>,n+1)
        =
      \bigcup_{m<k+2}
        \sigma(\<
          \underbrace{\mc U,\dots,\mc U}_{k+1-m},
          \underbrace{\mc V,\dots,\mc V}_{m+1}
        \>,(n+1)(k+2)+m)
    \]

  Let $\<\mc U_0,\mc U_1,\dots\>$ be an attack by $\pl C$ against $\tau$.
  Then consider the attack
    \[
      \<
        \underbrace{\mc U_0,\dots,\mc U_0}_{k+2},
        \underbrace{\mc U_1,\dots,\mc U_1}_{k+2},
        \dots
      \>
    \]
  by $\pl C$ against $\sigma$. Since $\sigma$ is a winning $(k+2)$-mark,
    \[
      X
        =
      \bigcup_{m<k+2}
        \sigma(\<\underbrace{\mc U_0,\dots,\mc U_0}_{m+1}\>,m)
      \cup
      \bigcup_{n<\omega}
      \bigcup_{m<k+2}
        \sigma(\<
          \underbrace{\mc U_n,\dots,\mc U_n}_{k+1-m},
          \underbrace{\mc U_{n+1},\dots,\mc U_{n+1}}_{m+1}
        \>,(n+1)(k+2)+m)
    \]
    \[
      =
      \tau(\<\mc U_0\>,0)
      \cup
      \bigcup_{n<\omega}
      \tau(\<\mc U_n,\mc U_{n+1}\>,n+1)
    \]
  Thus $\tau$ is a winning $2$-mark.
\end{proof}

A natural question arises: is there an example of a space $X$ for which
$\pl F\kmarkwin{2}\menGame{X}$ but $\pl F\notmarkwin\menGame{X}$? We quickly
see that perhaps the simplest example of a Lindel\"of non-$\sigma$-compact
space has this property.

\begin{definition}
  For any cardinal $\kappa$, let $\oneptlind\kappa=\kappa\cup\{\infty\}$ denote
  the \term{one-point Lindel\"of-ication} of discrete $\kappa$, where points in
  $\kappa$ are isolated, and the neighborhoods of $\infty$ are the co-countable
  sets containing it.
\end{definition}

\begin{theorem}
  $\pl F \notmarkwin \menGame{\oneptlind{\omega_1}}$.
\end{theorem}

\begin{proof}
  This result will later follow from the fact that
  $\oneptlind\omega_1$ is not a $\sigma$-compact space (all its compact subsets
  are finite).

  For now, let $\sigma$ be a Markov strategy for $\pl F$. For
  each $\alpha<\omega_1$, let $\mc U_\alpha$ be the open cover
  $\{\{\beta\}:\beta<\alpha\}\cup\{\oneptlind{\omega_1}\setminus\alpha\}$ of
  $\oneptlind{\omega_1}$, and set $F(\alpha,n)$ to be the finite set
  $\alpha\cap\sigma(\<\mc U_\alpha\>,n)$.

  If
    $
      P_n =
      \{\beta: \beta < \alpha < \omega_1 \Rightarrow \beta \in F(\alpha,n)\}
    $,
  then $P_n\subseteq F(\sup(P_n)+1,n)$. Thus $P_n$ is finite for $n<\omega$.
  Choose $\beta\in\omega_1\setminus \bigcup_{n<\omega}P_n$
  and $\alpha_n>\beta$ such that $\beta\not\in F(\alpha_n,n)$.
  Then $\pl C$ may attack
  $\sigma$ with $\<\mc U_{\alpha_0}, \mc U_{\alpha_1},\dots\>$,
  and it follows that
  $\beta\not\in \bigcup_{n<\omega}F(\alpha_n,n)$ and
  $\beta\not\in \bigcup_{n<\omega}\sigma(\<\mc U_{\alpha_n}\>,n)$.
\end{proof}

The greatest advantage of a strategy which has knowledge of two or more previous
moves of the opponent, versus only knowledge of the most recent move, is the
ability to react to changes from one round to the next. It's this ability to
react that will give $\pl F$ her winning $2$-Markov strategy in the Menger
game on $\oneptlind\omega_1$.

For inspiration, we turn to a game whose $n$-tactics were studied by Marion
Scheepers in \cite{MR1129143} which has similar goals to the Menger game when
played upon $\oneptlind\kappa$.

\begin{game}
  Let $\cloFillStrictGame\kappa$ denote the \term{strict union filling game}
  with two players $\pl C$, $\pl F$. In round $0$, $\pl C$ chooses
  $C_0\in[\kappa]^{\leq\omega}$, followed by $\pl F$ choosing
  $F_0\in[\kappa]^{<\omega}$. In round $n+1$, $\pl C$ chooses
  $C_{n+1}\in[\kappa]^{\leq\omega}$ such that $C_{n+1}\supset C_n$, followed
  by $\pl F$ choosing $F_{n+1}\in[\kappa]^{<\omega}$.

  $\pl F$ wins the game if
  $\bigcup_{n<\omega} F_n\supseteq\bigcup_{n<\omega} C_n$; otherwise, $\pl C$
  wins.
\end{game}

In $\menGame{\oneptlind\kappa}$, $\pl C$ essentially chooses a countable set
to not include in her neighborhood of $\infty$, followed by $\pl F$ choosing
a finite subset of this complement to cover during each round. Thus,
$\pl F$ need only be concerned with the \textit{intersection} of the
countable sets chosen by $\pl C$ in $\menGame{\oneptlind\kappa}$, rather
than the union as in $\cloFillStrictGame\kappa$.

Another difference: Scheepers required that $\pl C$ always choose strictly
growing countable sets. The reasoning is clear: if the goal is to study tactics,
then $\pl C$ cannot be allowed to trap $\pl F$ in a loop by repeating the same
moves. But by eliminating this requirement, the study can then turn to Markov
strategies, bringing the game further in line with the Menger game played upon
$\oneptlind\kappa$.

We introduce a few games to make the relationship between Scheeper's
$\cloFillStrictGame\kappa$ and $\menGame{\oneptlind\kappa}$ more precise.

\begin{game}
  Let $\cloFillGame\kappa$ denote the
  \term{union filling game} which proceeds analogously
  to $\cloFillStrictGame\kappa$, except that $\pl C$'s restriction in round $n+1$
  is reduced to $C_{n+1}\supseteq C_n$.
\end{game}

\begin{game}
  Let $\cloFillInitialGame\kappa$ denote the
  \term{initial filling game} which proceeds analogously
  to $\cloFillGame\kappa$, except that $\pl F$ wins whenever
  $\bigcup_{n<\omega}F_n\supseteq C_0$.
\end{game}

\begin{game}
  Let $\cloFillIntGame\kappa$ denote the
  \term{intersection filling game} which proceeds analogously
  to $\cloFillInitialGame\kappa$, except that $\pl C$ may choose any
  $C_n\in[\kappa]^{\leq\omega}$ each round, and $\pl F$ wins whenever
  $\bigcup_{n<\omega}F_n\supseteq\bigcap_{n<\omega}C_n$.
\end{game}

\begin{figure}[h]
\begin{center}
% \begin{tikzpicture}
%   \matrix (m) [matrix of math nodes,row sep=3em,column sep=1em,minimum width=2em]
%   {
%     \pl F \kmarkwin{k}\menGame{\oneptlind\kappa} &
%     \pl F \kmarkwin{k}\cloFillIntGame\kappa \\

%     \pl F \kmarkwin{k}\cloFillInitialGame\kappa &
%     \pl F \kmarkwin{k}\cloFillGame\kappa \\

%     &
%     \pl F \ktactwin{k}\cloFillStrictGame\kappa \\
%   };
%   \path[>=latex,->]
%     (m-1-1) edge (m-2-1)
%     (m-1-2) edge (m-2-2)
%     (m-3-2) edge (m-2-2);
%   \path[>=latex,<->]
%     (m-1-1) edge (m-1-2)
%     (m-2-1) edge (m-2-2);
% \end{tikzpicture}
\end{center}
\caption{Diagram of Filling/Menger game implications}
\label{fillingGamesDiagram}
\end{figure}

\begin{theorem}
For any cardinal $\kappa>\omega$ and integer $k<\omega$,
Figure \ref{fillingGamesDiagram} holds.
\end{theorem}

\begin{proof}
  $\pl F \kmarkwin{k}\menGame{\oneptlind\kappa}
    \Rightarrow
  \pl F \kmarkwin{k}\cloFillIntGame\kappa$:
  Let $\sigma$ be a winning $k$-mark for $\pl F$ in
  $\menGame{\oneptlind\kappa}$. Let $\mc U(C)$ (resp. $\mc U(s)$) convert each
  countable subset $C$ of $\kappa$ (resp. finite sequence $s$ of such subsets)
  into the open cover $[C]^1\cup\{\oneptlind\kappa\setminus C\}$
  (resp. finite sequence of such open covers). Then $\tau$ defined by
    \[
      \tau(s\concat\<C\>,n)
        =
      C\cap\sigma(\mc U(s\concat\<C\>),n)
    \]
  is a winning $k$-mark for $\pl F$ in $\cloFillIntGame\kappa$.

  $\pl F \kmarkwin{k}\cloFillIntGame\kappa
    \Rightarrow
  \pl F \kmarkwin{k}\menGame{\oneptlind\kappa}$:
  Let $\sigma$ be a winning $k$-mark for $\pl F$ in
  $\cloFillIntGame\kappa$. Let $C(\mc U)$ (resp. $C(s)$) convert each open
  cover $\mc U$ of $\oneptlind\kappa$ (resp. finite sequence $s$ of such covers)
  into a countable set $C$ which is the complement of some neighborhood of
  $\infty$ in $\mc U$ (resp. finite sequence of such countable sets).
  Then $\tau$ defined by
    \[
      \tau(s\concat\<\mc U\>,n)
        =
      (\oneptlind\kappa\setminus C(\mc U))
        \cup
      \sigma(C(s\concat\<\mc U)\>),n)
    \]
  is a winning $k$-mark for $\pl F$ in $\menGame{\oneptlind\kappa}$.

  $\pl F \kmarkwin{k}\cloFillIntGame\kappa
    \Rightarrow
  \pl F \kmarkwin{k}\cloFillInitialGame\kappa$:
  Let $\sigma$ be a winning $k$-mark for $\pl F$ in
  $\cloFillIntGame\kappa$. $\sigma$ is also a winning $k$-mark for $\pl F$
  in $\cloFillInitialGame\kappa$.

  $\pl F \kmarkwin{k}\cloFillInitialGame\kappa
    \Rightarrow
  \pl F \kmarkwin{k}\cloFillGame\kappa$: Let $\sigma$ be a winning $k$-mark for $\pl F$ in
  $\cloFillInitialGame\kappa$. For each finite sequence $s$, let $t\preceq s$ mean $t$
  is a final subsequence of $s$. Then $\tau$ defined by
    \[
      \tau(s\concat\<C\>,n)
        =
      \bigcup_{t\preceq s, m\leq n}
      \sigma(t\concat\<C\>,m)
    \]
  is a winning $k$-mark for $\pl F$ in $\cloFillGame\kappa$.

  $\pl F \kmarkwin{k}\cloFillGame\kappa
    \Rightarrow
  \pl F \kmarkwin{k}\cloFillInitialGame\kappa$:
  Let $\sigma$ be a winning $k$-mark for $\pl F$ in
  $\cloFillGame\kappa$. $\sigma$ is also a winning $k$-mark for $\pl F$
  in $\cloFillInitialGame\kappa$.

  $\pl F \ktactwin{k}\cloFillStrictGame\kappa
    \Rightarrow
  \pl F \kmarkwin{k}\cloFillGame\kappa$:
  Let $\sigma$ be a winning $k$-tactic for $\pl F$ in
  $\cloFillStrictGame\kappa$. For each countable subset $C$ of $\kappa$, let $C+n$
  be the union of $C$ with the $n$ least ordinals in $\kappa\setminus C$.
  Then $\tau$ defined by
    \[
      \tau(\<C_0,\dots,C_i\>,n)
        =
      \sigma(\<C_0+(n-i),\dots,C_i+n\>)
    \]
  is a winning $k$-mark for $\pl F$ in $\cloFillGame\kappa$.
\end{proof}

While we have not proven a direct implication between the Menger game and
Scheeper's original filling game, Scheepers introduced the statement
$\alcompS\kappa$ relating to the almost-compatability of functions
from countable subsets of $\kappa$ into $\omega$ which may be applied to
both.

\begin{definition}
  For two functions $f,g$ we say $f$ is \textbf{$\mu$-almost compatible} with
  $g$ ($f\alcomp_\mu g$) if $|\{x\in\dom(f)\cap\dom(g):f(x)\not=g(x)\}|<\mu$.
  If $\mu=\omega$ then we say $f,g$ are \textbf{almost compatible}
  ($f\alcomp g$).
\end{definition}

\begin{definition}
  $\alcompS\kappa$ states that there exist functions
  $f_A:A\to\omega$ for each $A\in[\kappa]^{\leq\omega}$ such that
  $|\{\alpha\in A:f_A(\alpha)\leq n\}|<\omega$ for all $n<\omega$ and
  $f_A\alcomp f_B$ for all $A,B\in[\kappa]^\omega$.
  \footnote{
  This is equivalent to the original characterization given in
  \cite{MR1129143}: there exist injections $g_A:A\to\omega$
  such that $g_A\alcomp g_B$ for all $A,B\in[\kappa]^\omega$ and $A\subset B$.
  }
\end{definition}

Scheepers went on to show that $\alcompS\kappa$ implies
$\pl F \ktactwin2 \cloFillStrictGame\kappa$. This proof, along with the following
facts, give us inspiration for
finding a winning $2$-Markov strategy in the Menger game played on
$\oneptlind\kappa$.

\begin{theorem}
  $\alcompS{\omega_1}$ and $\kappa>2^\omega\Rightarrow\neg\alcompS\kappa$
  are theorems of $ZFC$.
  $\alcompS{2^\omega}$ is a theorem of $ZFC+CH$ and consistent with
  $ZFC+\neg CH$.
\end{theorem}

\begin{proof}
  For $\alcompS{\omega_1}$, look at pg. 70 of \cite{MR597342}; this of course
  implies $\alcompS{2^\omega}$ under $CH$.
  $\neg\alcompS{(2^\omega)^+}$ is shown by a cardinality argument
  in \cite{MR1129143}.
  The consistency result under $ZFC+\neg CH$
  is a lemma for the main theorem in \cite{MR1129143}.
\end{proof}

\begin{figure}[h]
\begin{center}
% \begin{tikzpicture}
%   \matrix (m) [matrix of math nodes,row sep=3em,column sep=1em,minimum width=2em]
%   {
%     &
%     \pl F \kmarkwin2\menGame{\oneptlind\kappa} &
%     \pl F \kmarkwin2\cloFillIntGame\kappa \\

%     \alcompS\kappa &
%     \pl F \kmarkwin2\cloFillInitialGame\kappa &
%     \pl F \kmarkwin2\cloFillGame\kappa \\

%     &
%     &
%     \pl F \ktactwin2\cloFillStrictGame\kappa \\
%   };
%   \path[>=latex,->]
%     (m-2-1) edge (m-1-2)
%     (m-2-1) edge (m-2-2)
%     (m-2-1) edge (m-3-3)
%     (m-1-2) edge (m-2-2)
%     (m-1-3) edge (m-2-3)
%     (m-3-3) edge (m-2-3);
%   \path[>=latex,<->]
%     (m-1-2) edge (m-1-3)
%     (m-2-2) edge (m-2-3);
% \end{tikzpicture}
\end{center}
\caption{Diagram of Filling/Menger game implications with $\alcompS\kappa$}
\label{fillingGamesDiagram2}
\end{figure}

\begin{theorem}
  $\alcompS\kappa$ implies the game-theoretic results in
  Figure \ref{fillingGamesDiagram2}.
\end{theorem}

\begin{proof}
  Since $\alcompS\kappa\Rightarrow\pl F \ktactwin2\cloFillStrictGame\kappa$ was
  a main result of \cite{MR1129143}, it is sufficient to show that
  $\alcompS\kappa\Rightarrow \pl F \kmarkwin2\cloFillIntGame\kappa$.

  Let $f_A$ for $A\in[\kappa]^{\leq\omega}$ witness $\alcompS\kappa$. We define
  the $2$-mark $\sigma$ as follows:
    \[
      \sigma(\<A\>,0) = \{\alpha\in A: f_A(\alpha) \leq 0 \}
    \]
    \[
      \sigma(\<A,B\>,n+1)
        =
      \{
        \alpha \in A\cap B
      :
        f_B(\alpha) \leq n+1 \text{ or }
        f_A(\alpha)\not=f_B(\alpha)
      \}
    \]
  For any attack $\<A_0,A_1,\dots\>$ by $\pl C$ and
  $\alpha\in\bigcap_{n<\omega}A_n$, either $f_{A_n}(\alpha)$ is constant for
  all $n$, or $f_{A_n}(\alpha)\not=f_{A_{n+1}}(\alpha)$ for some $n$;
  either way, $\alpha$ is covered.
\end{proof}

\begin{corollary}
  $\pl F \kmarkwin2\menGame{\oneptlind\omega_1}$.
\end{corollary}

\section{Menger game derived covering properties}

\begin{figure}[h]
\begin{center}
% \begin{tikzpicture}
%   \matrix (m) [matrix of math nodes,row sep=3em,column sep=1em,minimum width=2em]
%   {
%      \pl F \markwin \menGame{X} &
%      \pl F \kmarkwin2 \menGame{X} &
%      \pl F \win \menGame{X} &
%      \pl C \notwin \menGame{X} \\

%      \text{Markov Menger} &
%      2\text{-Markov Menger} &
%      \text{Perfect Menger} &
%      \text{Menger} \\
%   };
%   \path[>=latex,<->]
%     (m-1-1) edge (m-2-1)
%     (m-1-2) edge (m-2-2)
%     (m-1-3) edge (m-2-3)
%     (m-1-4) edge (m-2-4);
%   \path[>=latex,->]
%     (m-1-1) edge (m-1-2)
%     (m-2-1) edge (m-2-2)
%     (m-1-2) edge (m-1-3)
%     (m-2-2) edge (m-2-3)
%     (m-1-3) edge (m-1-4)
%     (m-2-3) edge (m-2-4);
%   \path[>=latex,->,bend right=30, dotted]
%     (m-1-2) edge node {$ \not $} (m-1-1)
%     (m-2-2) edge node {$ \not $} (m-2-1)
%     (m-1-4) edge node {$ \not $} (m-1-3)
%     (m-2-4) edge node {$ \not $} (m-2-3);
%   \path[>=latex,->,bend right=30, dotted]
%     (m-1-3) edge node {$ ? $} (m-1-2)
%     (m-2-3) edge node {$ ? $} (m-2-2);
% \end{tikzpicture}
\end{center}
\caption{Diagram of covering properties related to the Menger game}
\label{menSpec}
\end{figure}

Limited information strategies for the Menger game naturally define a spectrum
of covering properties, see Figure \ref{menSpec}. However,
we do not know if the middle two properties are actually distinct.

\begin{question}\label{perfectTo2Mark}
  Does there exist a space $X$ such that $\pl F \win \menGame{X}$ but
  $\pl F \notkmarkwin2 \menGame{X}$?
\end{question}

Note that while it's consistent that
$\pl F\kmarkwin2\menGame{\oneptlind{(2^\omega)}}$, $\oneptlind{\kappa}$
for $\kappa>2^\omega$ is a candidate to answer the above question.

We are also interested in non-game-theoretic characterizations of these
covering properties. It has been known for some time that for metrizable spaces,
winning Menger spaces are exactly the $\sigma$-compact spaces, shown first
by Telgarksy in \cite{MR753073} and later directly by Scheepers in
\cite{MR1273523}.

In the interest of generality, we will first characterize the Markov Menger
spaces without any separation axioms.

\begin{definition}
  A subset $Y$ of $X$ is \term{relatively compact} to $X$ if for every open
  cover of $X$, there exists a finite subcollection which covers $Y$.
\end{definition}

For example, any bounded subset of Euclidean space is relatively compact
whether it is closed or not. Actually, relative compactness can be thought
of as an analogue of boundedness for regular spaces.

\begin{proposition}
  For regular spaces, $Y$ is relatively compact to $X$ if and only if
  $\cl Y$ is compact in $X$.
  \footnote{
    It should be noted that some authors define relative compactness in
    this way, but such a definition creates pathological implications for
    non-regular spaces. For example, the singleton containing
    the particular point of an infinite space with the particular point topology
    would not be relatively compact since its closure is not compact, even
    though it is finite.
  }
\end{proposition}

\begin{proof}
  For any space, any subset of a compact set is relatively compact.

  Assume $Y$ is relatively compact, let $\mc U$ be an open cover of $\cl Y$,
  and define $x\in V_x\subseteq \cl{V_x}\subseteq U_x \in \mc U$ for each
  $x\in X$. Then if we take a subcollection $\mc F = \{V_{x_i} : i<n\}$ covering
  $Y$ by relative compactness, then $\{U_{x_i}:i<n\}$ is a finite subcollection
  of $\mc U$ covering $\cl Y$, showing compactness.
\end{proof}

We now begin the process of factoring out Scheeper's proof to reveal the
limited information implications at work.

\begin{lemma}
  Let $\sigma(\mc{U}, n)$ be a Markov strategy for $F$ in
  $\menGame{X}$, and $\mathfrak{C}$ collect all open covers of $X$. Then the
  set
    \[
      R_n = \bigcap_{\mc{U}\in\mathfrak{C}} \sigma(\mc{U},n)
    \]
  is relatively compact to $X$. If $\sigma$ is a winning
  Markov startegy, then $\bigcup_{n<\omega} R_n = X$.
\end{lemma}

\begin{proof}
  First, for every open cover $\mc U\in\mathfrak C$,
  $R_n\subseteq\sigma(\mc U,n)$ is covered by a finite subcollection of $\mc U$.

  Suppose that $x \not\in R_n$ for any $n<\omega$. Then for each $n$,
  pick $\mc{U}_n\in\mathfrak{C}$ such that $x\not\in \sigma(\mc{U}_n,n)$. Then
  $\pl C$ may counter $\sigma$ with the attack $\<\mc U_0,\mc U_1,\dots\>$.
\end{proof}

\begin{definition}
  A \term{$\sigma$-relatively-compact} space is the countable union of
  relatively compact subsets.
\end{definition}

\begin{corollary}
  The following are equivalent:
  \begin{itemize}
    \item $X$ is $\sigma$-relatively-compact
    \item $\pl F \prewin \menGame X$
    \item $\pl F \markwin \menGame X$
  \end{itemize}
\end{corollary}

\begin{proof}
  If $X=\bigcup_{n<\omega} R_n$ for $R_n$ relatively compact, then
  $\sigma(n)=R_n$ is a winning predetermined strategy, which yields a
  winning Markov strategy. The previous lemma finishes the proof.
\end{proof}

\begin{corollary}
  Let $X$ be a regular space. The following are equivalent:
  \begin{itemize}
    \item $X$ is $\sigma$-compact
    \item $X$ is $\sigma$-relatively-compact
    \item $\pl F \prewin \menGame X$
    \item $\pl F \markwin \menGame X$
  \end{itemize}
\end{corollary}

For Lindel\"of spaces, metrizability is characterized by regularity and
second-countability, the latter of which was essentially used by Scheepers in
this way:

\begin{lemma}
  Let $X$ be a second-countable space. $\pl F\win\menGame{X}$ if and only if
  $\pl F\markwin\menGame{X}$.
\end{lemma}

\begin{proof}
  Let $\sigma$ be a strategy for $\pl F$, and note that
  it's sufficient to consider playthroughs with only basic open covers.

  So if $\mc U_t$ is a basic open cover for $t<s\in\omega^{<\omega}$, and
  $\mc V$ is any basic open cover, we may choose a finite subcollection
  $\mc F(s,\mc V)$ of $\mc V$ such that
  \[
    \sigma(\<\mc U_{s\rest 1},\dots,\mc U_{s},\mc V\>)
      \subseteq
    \bigcup \mc F(s,\mc V)
  \]

  Note that there are only countably-many finite collections of basic open sets.
  Thus we may choose basic open covers $\mc U_{s\concat\<n\>}$ for $n<\omega$
  such that for any basic open cover $\mc V$, there exists $n<\omega$ where
  $\mc F(s,\mc V)=\mc F(s,\mc U_{s\concat\<n\>})$.

  Let $t:\omega\to\omega^{<\omega}$ be a bijection. We define the Mark\"ov
  strategy $\tau$ as follows:
  \[
    \tau(\<\mc V\>, n)
      =
    \bigcup \mc F(t(n),\mc V)
  \]

  Suppose there exists a counter-attack $\<\mc V_0,\mc V_1,\dots\>$ of
  basic open covers which defeats $\tau$. Then there exists
  $f:\omega\to\omega$ such that, letting $t(m_n)=f\rest n$:
  \[
    \begin{array}{rcl}
    x & \not\in & \tau(\<\mc V_{m_n}\>,m_n) \\
    & = & \bigcup\mc F(f\rest n,\mc V_{m_n}) \\
    & = & \bigcup\mc F(f\rest n,\mc U_{f\rest (n+1)}) \\
    & \supseteq & \sigma(\<\mc U_{f\rest 1},\dots,\mc U_{f\rest(n+1)}\>)
    \end{array}
  \]

  Thus $\<\mc U_{f\rest 1}, \mc U_{f\rest 2},\dots\>$ is a successful
  counter-attack by $\pl C$ against the perfect information strategy $\sigma$.
\end{proof}

\begin{corollary}
  Let $X$ be a second-countable space. The following are equivalent:
  \begin{itemize}
    \item $X$ is $\sigma$-relatively-compact
    \item $F \prewin \menGame{X}$
    \item $F \markwin \menGame{X}$
    \item $F \win \menGame{X}$
  \end{itemize}
\end{corollary}

\begin{corollary}
  Let $X$ be a metrizable space. The following are equivalent:
  \begin{itemize}
    \item $X$ is $\sigma$-compact
    \item $X$ is $\sigma$-relatively-compact
    \item $F \prewin \menGame{X}$
    \item $F \markwin \menGame{X}$
    \item $F \win \menGame{X}$
  \end{itemize}
\end{corollary}

\begin{proof}
  Each property implies Lindel\"of, so $X$ may be assumed to be
  regular and second-countable.
\end{proof}

\section{Robustly Lindel\"of}

To help describe $\pl F\kmarkwin2\menGame{X}$ topologically, we introduce a
subset variant of the Menger game and a related covering property.

\begin{game}
  Let $\menGame{X,Y}$ denote the \term{Menger subspace game} which proceeds
  analogously to the Menger game, except that $\pl F$ wins whenever
  $\bigcup_{n<\omega} \mc F_n$ is a cover for $Y\subseteq X$.
\end{game}

Note of course that $\menGame{X,X}=\menGame{X}$.

\begin{definition}
  A subset $Y$ of $X$ is \term{relatively robustly Menger} if there exist
  functions $r_{\mc V}:Y\to\omega$
  for each open cover $\mc V$ of $X$ such that
  for all open covers $\mc U,\mc V$ and numbers $n<\omega$,
  the following sets are $\mc V$-finite:
    \[
      c(\mc V,n)=\{ x\in Y : r_{\mc V}(x)\leq n\}
    \]
    \[
      p(\mc U,\mc V,n+1)=\{ x\in Y : n<r_{\mc U}(x)<r_{\mc V}(x)\}
    \]
\end{definition}

\begin{definition}
  A space $X$ is \term{robustly Menger} if it is relatively robustly
  Menger to itself.
\end{definition}

\begin{proposition}
  All $\sigma$-relatively-compact spaces are robustly Menger.
\end{proposition}

\begin{proof}
  If $X=\bigcup_{n<\omega}R_n$, then for all $\mc U$, let $r_{\mc U}(x)$ be the
  least $n$ such that $x\in R_n$. Then $c(\mc V,n)=\bigcup_{m\leq n}R_m$ and
  $p(\mc U,\mc V) = \emptyset$.
\end{proof}

\begin{theorem}
  If $Y\subseteq X$ is relatively robustly Menger, then
  $\pl F\kmarkwin2\menGame{X,Y}$.
\end{theorem}

\begin{proof}
  We define the Markov strategy $\sigma$ as follows.
  Let $\sigma(\<\mc U\>,0)=c(\mc U,0)$, and let
  $\sigma(\<\mc U,\mc V\>,n+1)=c(\mc V,n+1)\cup p(\mc U, \mc V,n+1)$.

  For any attack $\<\mc{U}_0,\mc{U}_1,\dots\>$ by $\pl C$ and $x\in Y$,
  one of the following must occur:

  \begin{itemize}
    \item
      $r_{\mc U_0}(x)=0$ and thus
      $x\in c(\mc U_0,0)\subseteq \sigma(\<\mc U_0\>,0)$.

    \item
      $r_{\mc U_0}(x)=N+1$ for some $N\geq 0$ and:
      \begin{itemize}
        \item
          For all $n\leq N$,
          \[
            r_{\mc U_{n+1}}(x)\leq N+1
          \]
          and thus
          $x\in c(\mc U_{N+1},N+1) \subseteq
            \sigma(\<U_N,U_{N+1}\>,N+1)$.
        \item
          For some $n \leq N$,
          \[ r_{\mc U_n}(x)\leq n \]
          and thus
          $x\in c(\mc U_{n+1},n+1) \subseteq
            \sigma(\<U_n,U_{n+1}\>,n+1)$.
        \item
          For some $n \leq N$,
          \[
            n < r_{\mc U_n}(x)\leq N+1 < r_{\mc U_{n+1}}(x)
          \]
         and thus
         $x\in p(\mc U_n,\mc U_{n+1},n+1) \subseteq
          \sigma(\<U_n,U_{n+1}\>,n+1)$
       \end{itemize}
  \end{itemize}
\end{proof}

\begin{theorem}
  $\alcompS\kappa$ implies $\oneptlind\kappa$ is
  robustly Menger, and thus
  $\pl F\kmarkwin2\menGame{\oneptlind\kappa}$.
\end{theorem}

\begin{proof}
  Let $f_A$ for $A\in[\kappa]^{\leq\omega}$ witness $\alcompS\kappa$ and fix
  $A(\mc U)\in[\kappa]^{\leq\omega}$ for each open cover $\mc U$ such that
  $\oneptlind\kappa\setminus A(\mc U)$ is contained in some element of
  $\mc U$.
  Then let $r_{\mc U}(x)=0$ for $x\in\oneptlind\kappa\setminus A(\mc U)$,
  and $r_{\mc U}(\alpha)=f_{A(\mc U)}(\alpha)$ for $\alpha\in A(\mc U)$.

  It follows that
    \[
      c(\mc U,n)
        =
      \left(\oneptlind\kappa\setminus A(\mc U)\right)
        \cup
      \{\alpha\in A(\mc U) : f_{A(\mc U)}(\alpha)\leq n \}
    \]
  is $\mc U$-finite, $\bigcup_{n<\omega}c(\mc U,n)=X$, and
    \[
      p(\mc U,\mc V,n+1)
        =
      \{
        \alpha\in A(\mc U)\cap A(\mc V)
          :
        n < f_{A(\mc U)}(\alpha) < f_{A(\mc V)}(\alpha)
      \}
    \]
  is finite.
\end{proof}

We may also consider common (non-regular) counterexamples which are finer
than the usual Euclidean line.

\begin{definition}
  Let $R_{\mathbb Q}$ be the real line with the topology generated by open
  intervals with or without the rationals removed.
\end{definition}

\begin{theorem}
  $R_{\mathbb Q}$ is non-regular and non-$\sigma$-compact, but is
  second-countable and $\sigma$-relatively-compact.
\end{theorem}

\begin{proof}
  Compact sets in $R_{\mathbb Q}$ can be shown to not contain open intervals,
  and thus are nowhere dense in nonmeager $\mathbb R$,
  so $R_{\mathbb Q}$ is not $\sigma$-compact. The usual base of
  intervals with rational endpoints (with or without rationals removed)
  witnesses second-countability.

  To see that $R_{\mathbb Q}$ is $\sigma$-relatively compact, consider
  $[a,b]\setminus\mathbb{Q}$. Let $\mc U$ be a cover of $R_{\mathbb Q}$, and
  let $\mc U'$ fill in the missing rationals for any open set in $\mc U$.
  There is a finite subcover $\mc V'\subseteq \mc U'$ for $[a,b]$ since
  $\mc U'$ contains open sets from the Euclidean topology. Let
  $\mc V= \{V\setminus\mathbb{Q}:V\in V'\}$: this is a finite refinment of
  $\mc U$ covering $[a,b]\setminus\mathbb{Q}$, so $[a,b]\setminus\mathbb{Q}$
  is relatively compact. It follows then that $R_{\mathbb Q}\setminus\mathbb Q$
  is $\sigma$-relatively-compact, and since $\mathbb Q$ is countable,
  $R_{\mathbb Q}$ is $\sigma$-relatively-compact. Non-regularity follows since
  regular and $\sigma$-relatively-compact implies $\sigma$-compact.
\end{proof}

\begin{definition}
  Let $R_\omega$ be the real line with the topology generated by open
  intervals with countably many points removed.
\end{definition}

\begin{theorem}
  $R_\omega$ is non-regular, non-second-countable, and
  non-$\sigma$-relatively-compact, but $\pl F\win\menGame{R_\omega}$.
\end{theorem}

\begin{proof}
  The closure of any open set is its closure in the usual Euclidean topology,
  so $R_\omega$ is not regular. If $S\supseteq\{s_n:n<\omega\}$ for $s_n$
  discrete, then $U_m=R_\omega\setminus\{s_n:m<n<\omega\}$ yields an
  infinite cover $\{U_m:m<\omega\}$ with no finite subcollection covering $S$,
  showing that all relatively compact sets are finite, and $R_\omega$ is not
  $\sigma$-relatively-compact.

  Define the winning strategy $\sigma$ for $\pl F$ in $\menGame{R_\omega}$ as
  follows: let $\sigma(\mc{U}_0,\dots,\mc{U}_{2n})=[-n,n]\setminus C_n$
  for some countable $C_n=\{c_{n,m}: m<\omega\}$,
  and let $\sigma(\mc{U}_0,\dots,\mc{U}_{2n+1})=\{c_{i,j} : i,j < n\}$.
  Non-second-countable follows since
  second-countable and $\pl F\win\menGame{X}$ implies
  $\sigma$-relatively-compact.
\end{proof}

We will soon see that, assuming $\alcompS{2^\omega}$, $\pl F$ has a winning
$2$-Mark\"ov strategy for $\menGame{R_\omega}$ as well.

\begin{proposition}
  Let $\limitwin$ be either $\kmarkwin{k}$ or $\win$.
  If $X=\bigcup_{i<\omega} X_i$ and $\pl F \limitwin \menGame{X,X_i}$
  for $i<\omega$, then $\pl F \limitwin \menGame{X}$
\end{proposition}

\begin{proof}
  Let $L$ be the $k$-Markov fog-of-war $\mu_k$ (resp. the identity),
  and let $\sigma_i$ be a $k$-Markov strategy (resp. perfect information
  strategy) for $\pl F$ in $\menGame{X,X_i}$.

  We define the $k$-Markov strategy (resp. perfect information strategy)
  $\sigma$ for $\menGame{X}$ as follows:
    \[
      \sigma\circ L(\<\mc U_0,\dots,\mc U_n\>)
        =
      \bigcup_{i\leq n}
      \sigma_i\circ L(\<\mc U_i,\dots,\mc U_n\>)
    \]

  Let $\<\mc U_0,\mc U_1,\dots\>$ be a successful counter-attack by $\pl C$
  against $\sigma$. Then there exists $x\in X_i$ for
  some $i<\omega$ such that $x$ is not covered by
  $\bigcup_{n<\omega}\sigma\circ L(\<\mc U_0,\dots,\mc U_n\>)$.
  It follows that $x$ is not covered by
  $\bigcup_{n<\omega}\sigma_i\circ L(\<\mc U_i,\dots,\mc U_{i+n}\>)$,
  and $\<\mc U_i,\mc U_{i+1},\dots\>$ is a successful counter-attack
  by $\pl C$ against $\sigma_i$.
\end{proof}

\begin{theorem}
  If $\alcompS{2^\omega}$, then $\pl F\kmarkwin2\menGame{R_\omega}$.
\end{theorem}

\begin{proof}
  It's sufficient to show that $[0,1]\subseteq R_\omega$ is relatively
  robustly Menger. Let $f_A$ witness $\alcompS{2^\omega}$
  for $A\in[[a,b]]^{\leq\omega}$.
  For each open cover $\mc U$, let $A_{\mc U}$ be
  such that $[0,1]\setminus A_{\mc U}$ is $\mc U$-finite.
  Let $r_{\mc U}(x)=0$ if $x\in[0,1]\setminus A_{\mc U}$ and
  $r_{\mc U}(x)=f_{\mc A_{\mc U}}(x)$ otherwise.

  It follows then that
    \[
      c(\mc U,n) = [0,1]\setminus\{x\in A_{\mc U}:f_{\mc A_{\mc U}}(x)>n\}
    \]
  is $\mc U$-finite and
    \[
      p(\mc U,\mc V,n+1)
        =
      \{x\in A_{\mc U}\cap A_{\mc V}
        :
      n<f_{\mc A_{\mc U}}(x)<f_{\mc A_{\mc V}}(x)\}
    \]
  is finite.
\end{proof}

\bibliographystyle{plain}
\bibliography{../../bibliography}

\end{document}

### 2015-08-25 articles/applications-of-limited-information-strategies-in-mengers-game/article.tex
deflated $..$ to \(..\)

@@
 % \begin{keyword}
-%   Proximal\sep absolutely proximal\sep Corson compact\sep uniform space\sep $W$-space
+%   Proximal\sep absolutely proximal\sep Corson compact\sep uniform space\sep \(W\)-space
 % \end{keyword}
@@
 \begin{definition}
-  A space $X$ is Menger if for every sequence $\<\mc U_0,\mc U_1,\dots\>$
-  of open covers of $X$ there exists a sequence
-  $\<\mc F_0,\mc F_1,\dots\>$ such that $\mc F_n\subseteq \mc U_n$,
-  $|\mc F_n|<\omega$, and $\bigcup_{n<\omega}\mc F_n$ is a cover of $X$.
+  A space \(X\) is Menger if for every sequence \(\<\mc U_0,\mc U_1,\dots\>\)
+  of open covers of \(X\) there exists a sequence
+  \(\<\mc F_0,\mc F_1,\dots\>\) such that \(\mc F_n\subseteq \mc U_n\),
+  \(|\mc F_n|<\omega\), and \(\bigcup_{n<\omega}\mc F_n\) is a cover of \(X\).
 \end{definition}
@@
 \begin{proposition}
-  $X$ is $\sigma$-compact
-    $\Rightarrow$
-  $X$ is Menger
-    $\Rightarrow$
-  $X$ is Lindel\"of.
+  \(X\) is \(\sigma\)-compact
+    \(\Rightarrow\)
+  \(X\) is Menger
+    \(\Rightarrow\)
+  \(X\) is Lindel\"of.
 \end{proposition}
@@
 of a Lindel\"of space which is not Menger, and we'll see several examples of
-Menger spaces which are not $\sigma$-compact.
+Menger spaces which are not \(\sigma\)-compact.
 
@@
 \begin{definition}
-  For each cover $\mc U$ of $X$, $S\subseteq X$ is \term{$\mc U$-finite} if
-  there exists a finite subcollection of $\mc U$ which covers $C$.
+  For each cover \(\mc U\) of \(X\), \(S\subseteq X\) is \term{\(\mc U\)-finite} if
+  there exists a finite subcollection of \(\mc U\) which covers \(C\).
 \end{definition}
 
-Of course, a compact space is $\mc U$-finite for all open covers $\mc U$.
+Of course, a compact space is \(\mc U\)-finite for all open covers \(\mc U\).
 
 \begin{game}
-  Let $\menGame{X}$ denote the \term{Menger game} with players $\pl C$, $\pl F$.
-  In round $n$, $\pl C$ chooses an open cover $\mc U_n$, followed by $\pl F$
-  choosing a $\mc U_n$-finite subset $F_n$ of $X$.
-
-  $\pl F$ wins the game if $X = \bigcup_{n<\omega}F_n$,
-  and $\pl C$ wins otherwise.
+  Let \(\menGame{X}\) denote the \term{Menger game} with players \(\pl C\), \(\pl F\).
+  In round \(n\), \(\pl C\) chooses an open cover \(\mc U_n\), followed by \(\pl F\)
+  choosing a \(\mc U_n\)-finite subset \(F_n\) of \(X\).
+
+  \(\pl F\) wins the game if \(X = \bigcup_{n<\omega}F_n\),
+  and \(\pl C\) wins otherwise.
 \end{game}
@@
 \begin{theorem}
-  A space $X$ is Menger if and only if $\pl C\notwin\menGame{X}$
+  A space \(X\) is Menger if and only if \(\pl C\notwin\menGame{X}\)
   \cite{MR1544773}.
@@
 
-The typical characterization of the Menger game involves $\pl F$ choosing
-a finite subcollection $\mc F_n$ of $\mc U_n$, but it is easy to see that the
+The typical characterization of the Menger game involves \(\pl F\) choosing
+a finite subcollection \(\mc F_n\) of \(\mc U_n\), but it is easy to see that the
 characterization given above is equivalent, and will be convenient for use
@@
 \begin{proposition}
-  $X$ is compact if and only if
-  $\pl F \tactwin \menGame{X}$ if and only if
-  $\pl F \ktactwin{k} \menGame{X}$.
+  \(X\) is compact if and only if
+  \(\pl F \tactwin \menGame{X}\) if and only if
+  \(\pl F \ktactwin{k} \menGame{X}\).
 \end{proposition}
@@
 \begin{proof}
-  If $\sigma$ is a winning $k$-tactic, then for each open cover $\mc U$,
-  $\sigma$ defeats the attack $\<\mc U,\mc U,\dots\>$. Then
+  If \(\sigma\) is a winning \(k\)-tactic, then for each open cover \(\mc U\),
+  \(\sigma\) defeats the attack \(\<\mc U,\mc U,\dots\>\). Then
   \[
@@
   \]
-  and $X$ is $\mc U$-finite.
-\end{proof}
-
-Essentially, because $\pl C$ may repeat the same finite sequence of open covers,
-$\pl F$ needs to be seeded with knowledge of the round number to prevent being
+  and \(X\) is \(\mc U\)-finite.
+\end{proof}
+
+Essentially, because \(\pl C\) may repeat the same finite sequence of open covers,
+\(\pl F\) needs to be seeded with knowledge of the round number to prevent being
 trapped in a loop.
 
-If $\pl F$'s memory of $\pl C$'s past moves is bounded, then
+If \(\pl F\)'s memory of \(\pl C\)'s past moves is bounded, then
 there is no need to consider more than the two most recent moves. The
-intuitive reason is that $\pl C$ could simply play the same cover repeatedly
-until $\pl F$'s memory is exhausted, in which case $\pl F$ would only ever
+intuitive reason is that \(\pl C\) could simply play the same cover repeatedly
+until \(\pl F\)'s memory is exhausted, in which case \(\pl F\) would only ever
 see the change from one cover to another.
@@
 \begin{theorem}
-  For each $k<\omega$, $F \kmarkwin{(k+2)} \menGame{X}$
-  if and only if $F \kmarkwin2 \menGame{X}$.
+  For each \(k<\omega\), \(F \kmarkwin{(k+2)} \menGame{X}\)
+  if and only if \(F \kmarkwin2 \menGame{X}\).
 \end{theorem}
@@
 \begin{proof}
-  Let $\sigma$ be a winning $(k+2)$-mark. We define the $2$-mark $\tau$ as
+  Let \(\sigma\) be a winning \((k+2)\)-mark. We define the \(2\)-mark \(\tau\) as
   follows:
@@
 
-  Let $\<\mc U_0,\mc U_1,\dots\>$ be an attack by $\pl C$ against $\tau$.
+  Let \(\<\mc U_0,\mc U_1,\dots\>\) be an attack by \(\pl C\) against \(\tau\).
   Then consider the attack
@@
     \]
-  by $\pl C$ against $\sigma$. Since $\sigma$ is a winning $(k+2)$-mark,
+  by \(\pl C\) against \(\sigma\). Since \(\sigma\) is a winning \((k+2)\)-mark,
     \[
@@
     \]
-  Thus $\tau$ is a winning $2$-mark.
-\end{proof}
-
-A natural question arises: is there an example of a space $X$ for which
-$\pl F\kmarkwin{2}\menGame{X}$ but $\pl F\notmarkwin\menGame{X}$? We quickly
-see that perhaps the simplest example of a Lindel\"of non-$\sigma$-compact
+  Thus \(\tau\) is a winning \(2\)-mark.
+\end{proof}
+
+A natural question arises: is there an example of a space \(X\) for which
+\(\pl F\kmarkwin{2}\menGame{X}\) but \(\pl F\notmarkwin\menGame{X}\)? We quickly
+see that perhaps the simplest example of a Lindel\"of non-\(\sigma\)-compact
 space has this property.
@@
 \begin{definition}
-  For any cardinal $\kappa$, let $\oneptlind\kappa=\kappa\cup\{\infty\}$ denote
-  the \term{one-point Lindel\"of-ication} of discrete $\kappa$, where points in
-  $\kappa$ are isolated, and the neighborhoods of $\infty$ are the co-countable
+  For any cardinal \(\kappa\), let \(\oneptlind\kappa=\kappa\cup\{\infty\}\) denote
+  the \term{one-point Lindel\"of-ication} of discrete \(\kappa\), where points in
+  \(\kappa\) are isolated, and the neighborhoods of \(\infty\) are the co-countable
   sets containing it.
@@
 \begin{theorem}
-  $\pl F \notmarkwin \menGame{\oneptlind{\omega_1}}$.
+  \(\pl F \notmarkwin \menGame{\oneptlind{\omega_1}}\).
 \end{theorem}
@@
   This result will later follow from the fact that
-  $\oneptlind\omega_1$ is not a $\sigma$-compact space (all its compact subsets
+  \(\oneptlind\omega_1\) is not a \(\sigma\)-compact space (all its compact subsets
   are finite).
 
-  For now, let $\sigma$ be a Markov strategy for $\pl F$. For
-  each $\alpha<\omega_1$, let $\mc U_\alpha$ be the open cover
-  $\{\{\beta\}:\beta<\alpha\}\cup\{\oneptlind{\omega_1}\setminus\alpha\}$ of
-  $\oneptlind{\omega_1}$, and set $F(\alpha,n)$ to be the finite set
-  $\alpha\cap\sigma(\<\mc U_\alpha\>,n)$.
+  For now, let \(\sigma\) be a Markov strategy for \(\pl F\). For
+  each \(\alpha<\omega_1\), let \(\mc U_\alpha\) be the open cover
+  \(\{\{\beta\}:\beta<\alpha\}\cup\{\oneptlind{\omega_1}\setminus\alpha\}\) of
+  \(\oneptlind{\omega_1}\), and set \(F(\alpha,n)\) to be the finite set
+  \(\alpha\cap\sigma(\<\mc U_\alpha\>,n)\).
 
   If
-    $
+    \(
       P_n =
       \{\beta: \beta < \alpha < \omega_1 \Rightarrow \beta \in F(\alpha,n)\}
-    $,
-  then $P_n\subseteq F(\sup(P_n)+1,n)$. Thus $P_n$ is finite for $n<\omega$.
-  Choose $\beta\in\omega_1\setminus \bigcup_{n<\omega}P_n$
-  and $\alpha_n>\beta$ such that $\beta\not\in F(\alpha_n,n)$.
-  Then $\pl C$ may attack
-  $\sigma$ with $\<\mc U_{\alpha_0}, \mc U_{\alpha_1},\dots\>$,
+    \),
+  then \(P_n\subseteq F(\sup(P_n)+1,n)\). Thus \(P_n\) is finite for \(n<\omega\).
+  Choose \(\beta\in\omega_1\setminus \bigcup_{n<\omega}P_n\)
+  and \(\alpha_n>\beta\) such that \(\beta\not\in F(\alpha_n,n)\).
+  Then \(\pl C\) may attack
+  \(\sigma\) with \(\<\mc U_{\alpha_0}, \mc U_{\alpha_1},\dots\>\),
   and it follows that
-  $\beta\not\in \bigcup_{n<\omega}F(\alpha_n,n)$ and
-  $\beta\not\in \bigcup_{n<\omega}\sigma(\<\mc U_{\alpha_n}\>,n)$.
+  \(\beta\not\in \bigcup_{n<\omega}F(\alpha_n,n)\) and
+  \(\beta\not\in \bigcup_{n<\omega}\sigma(\<\mc U_{\alpha_n}\>,n)\).
 \end{proof}
@@
 ability to react to changes from one round to the next. It's this ability to
-react that will give $\pl F$ her winning $2$-Markov strategy in the Menger
-game on $\oneptlind\omega_1$.
-
-For inspiration, we turn to a game whose $n$-tactics were studied by Marion
+react that will give \(\pl F\) her winning \(2\)-Markov strategy in the Menger
+game on \(\oneptlind\omega_1\).
+
+For inspiration, we turn to a game whose \(n\)-tactics were studied by Marion
 Scheepers in \cite{MR1129143} which has similar goals to the Menger game when
-played upon $\oneptlind\kappa$.
+played upon \(\oneptlind\kappa\).
 
 \begin{game}
-  Let $\cloFillStrictGame\kappa$ denote the \term{strict union filling game}
-  with two players $\pl C$, $\pl F$. In round $0$, $\pl C$ chooses
-  $C_0\in[\kappa]^{\leq\omega}$, followed by $\pl F$ choosing
-  $F_0\in[\kappa]^{<\omega}$. In round $n+1$, $\pl C$ chooses
-  $C_{n+1}\in[\kappa]^{\leq\omega}$ such that $C_{n+1}\supset C_n$, followed
-  by $\pl F$ choosing $F_{n+1}\in[\kappa]^{<\omega}$.
-
-  $\pl F$ wins the game if
-  $\bigcup_{n<\omega} F_n\supseteq\bigcup_{n<\omega} C_n$; otherwise, $\pl C$
+  Let \(\cloFillStrictGame\kappa\) denote the \term{strict union filling game}
+  with two players \(\pl C\), \(\pl F\). In round \(0\), \(\pl C\) chooses
+  \(C_0\in[\kappa]^{\leq\omega}\), followed by \(\pl F\) choosing
+  \(F_0\in[\kappa]^{<\omega}\). In round \(n+1\), \(\pl C\) chooses
+  \(C_{n+1}\in[\kappa]^{\leq\omega}\) such that \(C_{n+1}\supset C_n\), followed
+  by \(\pl F\) choosing \(F_{n+1}\in[\kappa]^{<\omega}\).
+
+  \(\pl F\) wins the game if
+  \(\bigcup_{n<\omega} F_n\supseteq\bigcup_{n<\omega} C_n\); otherwise, \(\pl C\)
   wins.
@@
 
-In $\menGame{\oneptlind\kappa}$, $\pl C$ essentially chooses a countable set
-to not include in her neighborhood of $\infty$, followed by $\pl F$ choosing
+In \(\menGame{\oneptlind\kappa}\), \(\pl C\) essentially chooses a countable set
+to not include in her neighborhood of \(\infty\), followed by \(\pl F\) choosing
 a finite subset of this complement to cover during each round. Thus,
-$\pl F$ need only be concerned with the \textit{intersection} of the
-countable sets chosen by $\pl C$ in $\menGame{\oneptlind\kappa}$, rather
-than the union as in $\cloFillStrictGame\kappa$.
-
-Another difference: Scheepers required that $\pl C$ always choose strictly
+\(\pl F\) need only be concerned with the \textit{intersection} of the
+countable sets chosen by \(\pl C\) in \(\menGame{\oneptlind\kappa}\), rather
+than the union as in \(\cloFillStrictGame\kappa\).
+
+Another difference: Scheepers required that \(\pl C\) always choose strictly
 growing countable sets. The reasoning is clear: if the goal is to study tactics,
-then $\pl C$ cannot be allowed to trap $\pl F$ in a loop by repeating the same
+then \(\pl C\) cannot be allowed to trap \(\pl F\) in a loop by repeating the same
 moves. But by eliminating this requirement, the study can then turn to Markov
 strategies, bringing the game further in line with the Menger game played upon
-$\oneptlind\kappa$.
+\(\oneptlind\kappa\).
 
 We introduce a few games to make the relationship between Scheeper's
-$\cloFillStrictGame\kappa$ and $\menGame{\oneptlind\kappa}$ more precise.
+\(\cloFillStrictGame\kappa\) and \(\menGame{\oneptlind\kappa}\) more precise.
 
 \begin{game}
-  Let $\cloFillGame\kappa$ denote the
+  Let \(\cloFillGame\kappa\) denote the
   \term{union filling game} which proceeds analogously
-  to $\cloFillStrictGame\kappa$, except that $\pl C$'s restriction in round $n+1$
-  is reduced to $C_{n+1}\supseteq C_n$.
+  to \(\cloFillStrictGame\kappa\), except that \(\pl C\)'s restriction in round \(n+1\)
+  is reduced to \(C_{n+1}\supseteq C_n\).
 \end{game}
@@
 \begin{game}
-  Let $\cloFillInitialGame\kappa$ denote the
+  Let \(\cloFillInitialGame\kappa\) denote the
   \term{initial filling game} which proceeds analogously
-  to $\cloFillGame\kappa$, except that $\pl F$ wins whenever
-  $\bigcup_{n<\omega}F_n\supseteq C_0$.
+  to \(\cloFillGame\kappa\), except that \(\pl F\) wins whenever
+  \(\bigcup_{n<\omega}F_n\supseteq C_0\).
 \end{game}
@@
 \begin{game}
-  Let $\cloFillIntGame\kappa$ denote the
+  Let \(\cloFillIntGame\kappa\) denote the
   \term{intersection filling game} which proceeds analogously
-  to $\cloFillInitialGame\kappa$, except that $\pl C$ may choose any
-  $C_n\in[\kappa]^{\leq\omega}$ each round, and $\pl F$ wins whenever
-  $\bigcup_{n<\omega}F_n\supseteq\bigcap_{n<\omega}C_n$.
+  to \(\cloFillInitialGame\kappa\), except that \(\pl C\) may choose any
+  \(C_n\in[\kappa]^{\leq\omega}\) each round, and \(\pl F\) wins whenever
+  \(\bigcup_{n<\omega}F_n\supseteq\bigcap_{n<\omega}C_n\).
 \end{game}
@@
 \begin{theorem}
-For any cardinal $\kappa>\omega$ and integer $k<\omega$,
+For any cardinal \(\kappa>\omega\) and integer \(k<\omega\),
 Figure \ref{fillingGamesDiagram} holds.
@@
 \begin{proof}
-  $\pl F \kmarkwin{k}\menGame{\oneptlind\kappa}
+  \(\pl F \kmarkwin{k}\menGame{\oneptlind\kappa}
     \Rightarrow
-  \pl F \kmarkwin{k}\cloFillIntGame\kappa$:
-  Let $\sigma$ be a winning $k$-mark for $\pl F$ in
-  $\menGame{\oneptlind\kappa}$. Let $\mc U(C)$ (resp. $\mc U(s)$) convert each
-  countable subset $C$ of $\kappa$ (resp. finite sequence $s$ of such subsets)
-  into the open cover $[C]^1\cup\{\oneptlind\kappa\setminus C\}$
-  (resp. finite sequence of such open covers). Then $\tau$ defined by
+  \pl F \kmarkwin{k}\cloFillIntGame\kappa\):
+  Let \(\sigma\) be a winning \(k\)-mark for \(\pl F\) in
+  \(\menGame{\oneptlind\kappa}\). Let \(\mc U(C)\) (resp. \(\mc U(s)\)) convert each
+  countable subset \(C\) of \(\kappa\) (resp. finite sequence \(s\) of such subsets)
+  into the open cover \([C]^1\cup\{\oneptlind\kappa\setminus C\}\)
+  (resp. finite sequence of such open covers). Then \(\tau\) defined by
     \[
@@
     \]
-  is a winning $k$-mark for $\pl F$ in $\cloFillIntGame\kappa$.
-
-  $\pl F \kmarkwin{k}\cloFillIntGame\kappa
+  is a winning \(k\)-mark for \(\pl F\) in \(\cloFillIntGame\kappa\).
+
+  \(\pl F \kmarkwin{k}\cloFillIntGame\kappa
     \Rightarrow
-  \pl F \kmarkwin{k}\menGame{\oneptlind\kappa}$:
-  Let $\sigma$ be a winning $k$-mark for $\pl F$ in
-  $\cloFillIntGame\kappa$. Let $C(\mc U)$ (resp. $C(s)$) convert each open
-  cover $\mc U$ of $\oneptlind\kappa$ (resp. finite sequence $s$ of such covers)
-  into a countable set $C$ which is the complement of some neighborhood of
-  $\infty$ in $\mc U$ (resp. finite sequence of such countable sets).
-  Then $\tau$ defined by
+  \pl F \kmarkwin{k}\menGame{\oneptlind\kappa}\):
+  Let \(\sigma\) be a winning \(k\)-mark for \(\pl F\) in
+  \(\cloFillIntGame\kappa\). Let \(C(\mc U)\) (resp. \(C(s)\)) convert each open
+  cover \(\mc U\) of \(\oneptlind\kappa\) (resp. finite sequence \(s\) of such covers)
+  into a countable set \(C\) which is the complement of some neighborhood of
+  \(\infty\) in \(\mc U\) (resp. finite sequence of such countable sets).
+  Then \(\tau\) defined by
     \[
@@
     \]
-  is a winning $k$-mark for $\pl F$ in $\menGame{\oneptlind\kappa}$.
-
-  $\pl F \kmarkwin{k}\cloFillIntGame\kappa
+  is a winning \(k\)-mark for \(\pl F\) in \(\menGame{\oneptlind\kappa}\).
+
+  \(\pl F \kmarkwin{k}\cloFillIntGame\kappa
     \Rightarrow
-  \pl F \kmarkwin{k}\cloFillInitialGame\kappa$:
-  Let $\sigma$ be a winning $k$-mark for $\pl F$ in
-  $\cloFillIntGame\kappa$. $\sigma$ is also a winning $k$-mark for $\pl F$
-  in $\cloFillInitialGame\kappa$.
-
-  $\pl F \kmarkwin{k}\cloFillInitialGame\kappa
+  \pl F \kmarkwin{k}\cloFillInitialGame\kappa\):
+  Let \(\sigma\) be a winning \(k\)-mark for \(\pl F\) in
+  \(\cloFillIntGame\kappa\). \(\sigma\) is also a winning \(k\)-mark for \(\pl F\)
+  in \(\cloFillInitialGame\kappa\).
+
+  \(\pl F \kmarkwin{k}\cloFillInitialGame\kappa
     \Rightarrow
-  \pl F \kmarkwin{k}\cloFillGame\kappa$: Let $\sigma$ be a winning $k$-mark for $\pl F$ in
-  $\cloFillInitialGame\kappa$. For each finite sequence $s$, let $t\preceq s$ mean $t$
-  is a final subsequence of $s$. Then $\tau$ defined by
+  \pl F \kmarkwin{k}\cloFillGame\kappa\): Let \(\sigma\) be a winning \(k\)-mark for \(\pl F\) in
+  \(\cloFillInitialGame\kappa\). For each finite sequence \(s\), let \(t\preceq s\) mean \(t\)
+  is a final subsequence of \(s\). Then \(\tau\) defined by
     \[
@@
     \]
-  is a winning $k$-mark for $\pl F$ in $\cloFillGame\kappa$.
-
-  $\pl F \kmarkwin{k}\cloFillGame\kappa
+  is a winning \(k\)-mark for \(\pl F\) in \(\cloFillGame\kappa\).
+
+  \(\pl F \kmarkwin{k}\cloFillGame\kappa
     \Rightarrow
-  \pl F \kmarkwin{k}\cloFillInitialGame\kappa$:
-  Let $\sigma$ be a winning $k$-mark for $\pl F$ in
-  $\cloFillGame\kappa$. $\sigma$ is also a winning $k$-mark for $\pl F$
-  in $\cloFillInitialGame\kappa$.
-
-  $\pl F \ktactwin{k}\cloFillStrictGame\kappa
+  \pl F \kmarkwin{k}\cloFillInitialGame\kappa\):
+  Let \(\sigma\) be a winning \(k\)-mark for \(\pl F\) in
+  \(\cloFillGame\kappa\). \(\sigma\) is also a winning \(k\)-mark for \(\pl F\)
+  in \(\cloFillInitialGame\kappa\).
+
+  \(\pl F \ktactwin{k}\cloFillStrictGame\kappa
     \Rightarrow
-  \pl F \kmarkwin{k}\cloFillGame\kappa$:
-  Let $\sigma$ be a winning $k$-tactic for $\pl F$ in
-  $\cloFillStrictGame\kappa$. For each countable subset $C$ of $\kappa$, let $C+n$
-  be the union of $C$ with the $n$ least ordinals in $\kappa\setminus C$.
-  Then $\tau$ defined by
+  \pl F \kmarkwin{k}\cloFillGame\kappa\):
+  Let \(\sigma\) be a winning \(k\)-tactic for \(\pl F\) in
+  \(\cloFillStrictGame\kappa\). For each countable subset \(C\) of \(\kappa\), let \(C+n\)
+  be the union of \(C\) with the \(n\) least ordinals in \(\kappa\setminus C\).
+  Then \(\tau\) defined by
     \[
@@
     \]
-  is a winning $k$-mark for $\pl F$ in $\cloFillGame\kappa$.
+  is a winning \(k\)-mark for \(\pl F\) in \(\cloFillGame\kappa\).
 \end{proof}
@@
 Scheeper's original filling game, Scheepers introduced the statement
-$\alcompS\kappa$ relating to the almost-compatability of functions
-from countable subsets of $\kappa$ into $\omega$ which may be applied to
+\(\alcompS\kappa\) relating to the almost-compatability of functions
+from countable subsets of \(\kappa\) into \(\omega\) which may be applied to
 both.
@@
 \begin{definition}
-  For two functions $f,g$ we say $f$ is \textbf{$\mu$-almost compatible} with
-  $g$ ($f\alcomp_\mu g$) if $|\{x\in\dom(f)\cap\dom(g):f(x)\not=g(x)\}|<\mu$.
-  If $\mu=\omega$ then we say $f,g$ are \textbf{almost compatible}
-  ($f\alcomp g$).
+  For two functions \(f,g\) we say \(f\) is \textbf{\(\mu\)-almost compatible} with
+  \(g\) (\(f\alcomp_\mu g\)) if \(|\{x\in\dom(f)\cap\dom(g):f(x)\not=g(x)\}|<\mu\).
+  If \(\mu=\omega\) then we say \(f,g\) are \textbf{almost compatible}
+  (\(f\alcomp g\)).
 \end{definition}
@@
 \begin{definition}
-  $\alcompS\kappa$ states that there exist functions
-  $f_A:A\to\omega$ for each $A\in[\kappa]^{\leq\omega}$ such that
-  $|\{\alpha\in A:f_A(\alpha)\leq n\}|<\omega$ for all $n<\omega$ and
-  $f_A\alcomp f_B$ for all $A,B\in[\kappa]^\omega$.
+  \(\alcompS\kappa\) states that there exist functions
+  \(f_A:A\to\omega\) for each \(A\in[\kappa]^{\leq\omega}\) such that
+  \(|\{\alpha\in A:f_A(\alpha)\leq n\}|<\omega\) for all \(n<\omega\) and
+  \(f_A\alcomp f_B\) for all \(A,B\in[\kappa]^\omega\).
   \footnote{
   This is equivalent to the original characterization given in
-  \cite{MR1129143}: there exist injections $g_A:A\to\omega$
-  such that $g_A\alcomp g_B$ for all $A,B\in[\kappa]^\omega$ and $A\subset B$.
+  \cite{MR1129143}: there exist injections \(g_A:A\to\omega\)
+  such that \(g_A\alcomp g_B\) for all \(A,B\in[\kappa]^\omega\) and \(A\subset B\).
   }
@@
 
-Scheepers went on to show that $\alcompS\kappa$ implies
-$\pl F \ktactwin2 \cloFillStrictGame\kappa$. This proof, along with the following
+Scheepers went on to show that \(\alcompS\kappa\) implies
+\(\pl F \ktactwin2 \cloFillStrictGame\kappa\). This proof, along with the following
 facts, give us inspiration for
-finding a winning $2$-Markov strategy in the Menger game played on
-$\oneptlind\kappa$.
+finding a winning \(2\)-Markov strategy in the Menger game played on
+\(\oneptlind\kappa\).
 
 \begin{theorem}
-  $\alcompS{\omega_1}$ and $\kappa>2^\omega\Rightarrow\neg\alcompS\kappa$
-  are theorems of $ZFC$.
-  $\alcompS{2^\omega}$ is a theorem of $ZFC+CH$ and consistent with
-  $ZFC+\neg CH$.
+  \(\alcompS{\omega_1}\) and \(\kappa>2^\omega\Rightarrow\neg\alcompS\kappa\)
+  are theorems of \(ZFC\).
+  \(\alcompS{2^\omega}\) is a theorem of \(ZFC+CH\) and consistent with
+  \(ZFC+\neg CH\).
 \end{theorem}
@@
 \begin{proof}
-  For $\alcompS{\omega_1}$, look at pg. 70 of \cite{MR597342}; this of course
-  implies $\alcompS{2^\omega}$ under $CH$.
-  $\neg\alcompS{(2^\omega)^+}$ is shown by a cardinality argument
+  For \(\alcompS{\omega_1}\), look at pg. 70 of \cite{MR597342}; this of course
+  implies \(\alcompS{2^\omega}\) under \(CH\).
+  \(\neg\alcompS{(2^\omega)^+}\) is shown by a cardinality argument
   in \cite{MR1129143}.
-  The consistency result under $ZFC+\neg CH$
+  The consistency result under \(ZFC+\neg CH\)
   is a lemma for the main theorem in \cite{MR1129143}.
@@
 \end{center}
-\caption{Diagram of Filling/Menger game implications with $\alcompS\kappa$}
+\caption{Diagram of Filling/Menger game implications with \(\alcompS\kappa\)}
 \label{fillingGamesDiagram2}
@@
 \begin{theorem}
-  $\alcompS\kappa$ implies the game-theoretic results in
+  \(\alcompS\kappa\) implies the game-theoretic results in
   Figure \ref{fillingGamesDiagram2}.
@@
 \begin{proof}
-  Since $\alcompS\kappa\Rightarrow\pl F \ktactwin2\cloFillStrictGame\kappa$ was
+  Since \(\alcompS\kappa\Rightarrow\pl F \ktactwin2\cloFillStrictGame\kappa\) was
   a main result of \cite{MR1129143}, it is sufficient to show that
-  $\alcompS\kappa\Rightarrow \pl F \kmarkwin2\cloFillIntGame\kappa$.
-
-  Let $f_A$ for $A\in[\kappa]^{\leq\omega}$ witness $\alcompS\kappa$. We define
-  the $2$-mark $\sigma$ as follows:
+  \(\alcompS\kappa\Rightarrow \pl F \kmarkwin2\cloFillIntGame\kappa\).
+
+  Let \(f_A\) for \(A\in[\kappa]^{\leq\omega}\) witness \(\alcompS\kappa\). We define
+  the \(2\)-mark \(\sigma\) as follows:
     \[
@@
     \]
-  For any attack $\<A_0,A_1,\dots\>$ by $\pl C$ and
-  $\alpha\in\bigcap_{n<\omega}A_n$, either $f_{A_n}(\alpha)$ is constant for
-  all $n$, or $f_{A_n}(\alpha)\not=f_{A_{n+1}}(\alpha)$ for some $n$;
-  either way, $\alpha$ is covered.
+  For any attack \(\<A_0,A_1,\dots\>\) by \(\pl C\) and
+  \(\alpha\in\bigcap_{n<\omega}A_n\), either \(f_{A_n}(\alpha)\) is constant for
+  all \(n\), or \(f_{A_n}(\alpha)\not=f_{A_{n+1}}(\alpha)\) for some \(n\);
+  either way, \(\alpha\) is covered.
 \end{proof}
@@
 \begin{corollary}
-  $\pl F \kmarkwin2\menGame{\oneptlind\omega_1}$.
+  \(\pl F \kmarkwin2\menGame{\oneptlind\omega_1}\).
 \end{corollary}
@@
 %   \path[>=latex,->,bend right=30, dotted]
-%     (m-1-2) edge node {$ \not $} (m-1-1)
-%     (m-2-2) edge node {$ \not $} (m-2-1)
-%     (m-1-4) edge node {$ \not $} (m-1-3)
-%     (m-2-4) edge node {$ \not $} (m-2-3);
+%     (m-1-2) edge node {\( \not \)} (m-1-1)
+%     (m-2-2) edge node {\( \not \)} (m-2-1)
+%     (m-1-4) edge node {\( \not \)} (m-1-3)
+%     (m-2-4) edge node {\( \not \)} (m-2-3);
 %   \path[>=latex,->,bend right=30, dotted]
-%     (m-1-3) edge node {$ ? $} (m-1-2)
-%     (m-2-3) edge node {$ ? $} (m-2-2);
+%     (m-1-3) edge node {\( ? \)} (m-1-2)
+%     (m-2-3) edge node {\( ? \)} (m-2-2);
 % \end{tikzpicture}
@@
 \begin{question}\label{perfectTo2Mark}
-  Does there exist a space $X$ such that $\pl F \win \menGame{X}$ but
-  $\pl F \notkmarkwin2 \menGame{X}$?
+  Does there exist a space \(X\) such that \(\pl F \win \menGame{X}\) but
+  \(\pl F \notkmarkwin2 \menGame{X}\)?
 \end{question}
@@
 Note that while it's consistent that
-$\pl F\kmarkwin2\menGame{\oneptlind{(2^\omega)}}$, $\oneptlind{\kappa}$
-for $\kappa>2^\omega$ is a candidate to answer the above question.
+\(\pl F\kmarkwin2\menGame{\oneptlind{(2^\omega)}}\), \(\oneptlind{\kappa}\)
+for \(\kappa>2^\omega\) is a candidate to answer the above question.
 
@@
 covering properties. It has been known for some time that for metrizable spaces,
-winning Menger spaces are exactly the $\sigma$-compact spaces, shown first
+winning Menger spaces are exactly the \(\sigma\)-compact spaces, shown first
 by Telgarksy in \cite{MR753073} and later directly by Scheepers in
@@
 \begin{definition}
-  A subset $Y$ of $X$ is \term{relatively compact} to $X$ if for every open
-  cover of $X$, there exists a finite subcollection which covers $Y$.
+  A subset \(Y\) of \(X\) is \term{relatively compact} to \(X\) if for every open
+  cover of \(X\), there exists a finite subcollection which covers \(Y\).
 \end{definition}
@@
 \begin{proposition}
-  For regular spaces, $Y$ is relatively compact to $X$ if and only if
-  $\cl Y$ is compact in $X$.
+  For regular spaces, \(Y\) is relatively compact to \(X\) if and only if
+  \(\cl Y\) is compact in \(X\).
   \footnote{
@@
 
-  Assume $Y$ is relatively compact, let $\mc U$ be an open cover of $\cl Y$,
-  and define $x\in V_x\subseteq \cl{V_x}\subseteq U_x \in \mc U$ for each
-  $x\in X$. Then if we take a subcollection $\mc F = \{V_{x_i} : i<n\}$ covering
-  $Y$ by relative compactness, then $\{U_{x_i}:i<n\}$ is a finite subcollection
-  of $\mc U$ covering $\cl Y$, showing compactness.
+  Assume \(Y\) is relatively compact, let \(\mc U\) be an open cover of \(\cl Y\),
+  and define \(x\in V_x\subseteq \cl{V_x}\subseteq U_x \in \mc U\) for each
+  \(x\in X\). Then if we take a subcollection \(\mc F = \{V_{x_i} : i<n\}\) covering
+  \(Y\) by relative compactness, then \(\{U_{x_i}:i<n\}\) is a finite subcollection
+  of \(\mc U\) covering \(\cl Y\), showing compactness.
 \end{proof}
@@
 \begin{lemma}
-  Let $\sigma(\mc{U}, n)$ be a Markov strategy for $F$ in
-  $\menGame{X}$, and $\mathfrak{C}$ collect all open covers of $X$. Then the
+  Let \(\sigma(\mc{U}, n)\) be a Markov strategy for \(F\) in
+  \(\menGame{X}\), and \(\mathfrak{C}\) collect all open covers of \(X\). Then the
   set
@@
     \]
-  is relatively compact to $X$. If $\sigma$ is a winning
-  Markov startegy, then $\bigcup_{n<\omega} R_n = X$.
+  is relatively compact to \(X\). If \(\sigma\) is a winning
+  Markov startegy, then \(\bigcup_{n<\omega} R_n = X\).
 \end{lemma}
@@
 \begin{proof}
-  First, for every open cover $\mc U\in\mathfrak C$,
-  $R_n\subseteq\sigma(\mc U,n)$ is covered by a finite subcollection of $\mc U$.
-
-  Suppose that $x \not\in R_n$ for any $n<\omega$. Then for each $n$,
-  pick $\mc{U}_n\in\mathfrak{C}$ such that $x\not\in \sigma(\mc{U}_n,n)$. Then
-  $\pl C$ may counter $\sigma$ with the attack $\<\mc U_0,\mc U_1,\dots\>$.
+  First, for every open cover \(\mc U\in\mathfrak C\),
+  \(R_n\subseteq\sigma(\mc U,n)\) is covered by a finite subcollection of \(\mc U\).
+
+  Suppose that \(x \not\in R_n\) for any \(n<\omega\). Then for each \(n\),
+  pick \(\mc{U}_n\in\mathfrak{C}\) such that \(x\not\in \sigma(\mc{U}_n,n)\). Then
+  \(\pl C\) may counter \(\sigma\) with the attack \(\<\mc U_0,\mc U_1,\dots\>\).
 \end{proof}
@@
 \begin{definition}
-  A \term{$\sigma$-relatively-compact} space is the countable union of
+  A \term{\(\sigma\)-relatively-compact} space is the countable union of
   relatively compact subsets.
@@
   \begin{itemize}
-    \item $X$ is $\sigma$-relatively-compact
-    \item $\pl F \prewin \menGame X$
-    \item $\pl F \markwin \menGame X$
+    \item \(X\) is \(\sigma\)-relatively-compact
+    \item \(\pl F \prewin \menGame X\)
+    \item \(\pl F \markwin \menGame X\)
   \end{itemize}
@@
 \begin{proof}
-  If $X=\bigcup_{n<\omega} R_n$ for $R_n$ relatively compact, then
-  $\sigma(n)=R_n$ is a winning predetermined strategy, which yields a
+  If \(X=\bigcup_{n<\omega} R_n\) for \(R_n\) relatively compact, then
+  \(\sigma(n)=R_n\) is a winning predetermined strategy, which yields a
   winning Markov strategy. The previous lemma finishes the proof.
@@
 \begin{corollary}
-  Let $X$ be a regular space. The following are equivalent:
+  Let \(X\) be a regular space. The following are equivalent:
   \begin{itemize}
-    \item $X$ is $\sigma$-compact
-    \item $X$ is $\sigma$-relatively-compact
-    \item $\pl F \prewin \menGame X$
-    \item $\pl F \markwin \menGame X$
+    \item \(X\) is \(\sigma\)-compact
+    \item \(X\) is \(\sigma\)-relatively-compact
+    \item \(\pl F \prewin \menGame X\)
+    \item \(\pl F \markwin \menGame X\)
   \end{itemize}
@@
 \begin{lemma}
-  Let $X$ be a second-countable space. $\pl F\win\menGame{X}$ if and only if
-  $\pl F\markwin\menGame{X}$.
+  Let \(X\) be a second-countable space. \(\pl F\win\menGame{X}\) if and only if
+  \(\pl F\markwin\menGame{X}\).
 \end{lemma}
@@
 \begin{proof}
-  Let $\sigma$ be a strategy for $\pl F$, and note that
+  Let \(\sigma\) be a strategy for \(\pl F\), and note that
   it's sufficient to consider playthroughs with only basic open covers.
 
-  So if $\mc U_t$ is a basic open cover for $t<s\in\omega^{<\omega}$, and
-  $\mc V$ is any basic open cover, we may choose a finite subcollection
-  $\mc F(s,\mc V)$ of $\mc V$ such that
+  So if \(\mc U_t\) is a basic open cover for \(t<s\in\omega^{<\omega}\), and
+  \(\mc V\) is any basic open cover, we may choose a finite subcollection
+  \(\mc F(s,\mc V)\) of \(\mc V\) such that
   \[
@@
   Note that there are only countably-many finite collections of basic open sets.
-  Thus we may choose basic open covers $\mc U_{s\concat\<n\>}$ for $n<\omega$
-  such that for any basic open cover $\mc V$, there exists $n<\omega$ where
-  $\mc F(s,\mc V)=\mc F(s,\mc U_{s\concat\<n\>})$.
-
-  Let $t:\omega\to\omega^{<\omega}$ be a bijection. We define the Mark\"ov
-  strategy $\tau$ as follows:
+  Thus we may choose basic open covers \(\mc U_{s\concat\<n\>}\) for \(n<\omega\)
+  such that for any basic open cover \(\mc V\), there exists \(n<\omega\) where
+  \(\mc F(s,\mc V)=\mc F(s,\mc U_{s\concat\<n\>})\).
+
+  Let \(t:\omega\to\omega^{<\omega}\) be a bijection. We define the Mark\"ov
+  strategy \(\tau\) as follows:
   \[
@@
 
-  Suppose there exists a counter-attack $\<\mc V_0,\mc V_1,\dots\>$ of
-  basic open covers which defeats $\tau$. Then there exists
-  $f:\omega\to\omega$ such that, letting $t(m_n)=f\rest n$:
+  Suppose there exists a counter-attack \(\<\mc V_0,\mc V_1,\dots\>\) of
+  basic open covers which defeats \(\tau\). Then there exists
+  \(f:\omega\to\omega\) such that, letting \(t(m_n)=f\rest n\):
   \[
@@
 
-  Thus $\<\mc U_{f\rest 1}, \mc U_{f\rest 2},\dots\>$ is a successful
-  counter-attack by $\pl C$ against the perfect information strategy $\sigma$.
+  Thus \(\<\mc U_{f\rest 1}, \mc U_{f\rest 2},\dots\>\) is a successful
+  counter-attack by \(\pl C\) against the perfect information strategy \(\sigma\).
 \end{proof}
@@
 \begin{corollary}
-  Let $X$ be a second-countable space. The following are equivalent:
+  Let \(X\) be a second-countable space. The following are equivalent:
   \begin{itemize}
-    \item $X$ is $\sigma$-relatively-compact
-    \item $F \prewin \menGame{X}$
-    \item $F \markwin \menGame{X}$
-    \item $F \win \menGame{X}$
+    \item \(X\) is \(\sigma\)-relatively-compact
+    \item \(F \prewin \menGame{X}\)
+    \item \(F \markwin \menGame{X}\)
+    \item \(F \win \menGame{X}\)
   \end{itemize}
@@
 \begin{corollary}
-  Let $X$ be a metrizable space. The following are equivalent:
+  Let \(X\) be a metrizable space. The following are equivalent:
   \begin{itemize}
-    \item $X$ is $\sigma$-compact
-    \item $X$ is $\sigma$-relatively-compact
-    \item $F \prewin \menGame{X}$
-    \item $F \markwin \menGame{X}$
-    \item $F \win \menGame{X}$
+    \item \(X\) is \(\sigma\)-compact
+    \item \(X\) is \(\sigma\)-relatively-compact
+    \item \(F \prewin \menGame{X}\)
+    \item \(F \markwin \menGame{X}\)
+    \item \(F \win \menGame{X}\)
   \end{itemize}
@@
 \begin{proof}
-  Each property implies Lindel\"of, so $X$ may be assumed to be
+  Each property implies Lindel\"of, so \(X\) may be assumed to be
   regular and second-countable.
@@
 
-To help describe $\pl F\kmarkwin2\menGame{X}$ topologically, we introduce a
+To help describe \(\pl F\kmarkwin2\menGame{X}\) topologically, we introduce a
 subset variant of the Menger game and a related covering property.
@@
 \begin{game}
-  Let $\menGame{X,Y}$ denote the \term{Menger subspace game} which proceeds
-  analogously to the Menger game, except that $\pl F$ wins whenever
-  $\bigcup_{n<\omega} \mc F_n$ is a cover for $Y\subseteq X$.
+  Let \(\menGame{X,Y}\) denote the \term{Menger subspace game} which proceeds
+  analogously to the Menger game, except that \(\pl F\) wins whenever
+  \(\bigcup_{n<\omega} \mc F_n\) is a cover for \(Y\subseteq X\).
 \end{game}
 
-Note of course that $\menGame{X,X}=\menGame{X}$.
+Note of course that \(\menGame{X,X}=\menGame{X}\).
 
 \begin{definition}
-  A subset $Y$ of $X$ is \term{relatively robustly Menger} if there exist
-  functions $r_{\mc V}:Y\to\omega$
-  for each open cover $\mc V$ of $X$ such that
-  for all open covers $\mc U,\mc V$ and numbers $n<\omega$,
-  the following sets are $\mc V$-finite:
+  A subset \(Y\) of \(X\) is \term{relatively robustly Menger} if there exist
+  functions \(r_{\mc V}:Y\to\omega\)
+  for each open cover \(\mc V\) of \(X\) such that
+  for all open covers \(\mc U,\mc V\) and numbers \(n<\omega\),
+  the following sets are \(\mc V\)-finite:
     \[
@@
 \begin{definition}
-  A space $X$ is \term{robustly Menger} if it is relatively robustly
+  A space \(X\) is \term{robustly Menger} if it is relatively robustly
   Menger to itself.
@@
 \begin{proposition}
-  All $\sigma$-relatively-compact spaces are robustly Menger.
+  All \(\sigma\)-relatively-compact spaces are robustly Menger.
 \end{proposition}
@@
 \begin{proof}
-  If $X=\bigcup_{n<\omega}R_n$, then for all $\mc U$, let $r_{\mc U}(x)$ be the
-  least $n$ such that $x\in R_n$. Then $c(\mc V,n)=\bigcup_{m\leq n}R_m$ and
-  $p(\mc U,\mc V) = \emptyset$.
+  If \(X=\bigcup_{n<\omega}R_n\), then for all \(\mc U\), let \(r_{\mc U}(x)\) be the
+  least \(n\) such that \(x\in R_n\). Then \(c(\mc V,n)=\bigcup_{m\leq n}R_m\) and
+  \(p(\mc U,\mc V) = \emptyset\).
 \end{proof}
@@
 \begin{theorem}
-  If $Y\subseteq X$ is relatively robustly Menger, then
-  $\pl F\kmarkwin2\menGame{X,Y}$.
+  If \(Y\subseteq X\) is relatively robustly Menger, then
+  \(\pl F\kmarkwin2\menGame{X,Y}\).
 \end{theorem}
@@
 \begin{proof}
-  We define the Markov strategy $\sigma$ as follows.
-  Let $\sigma(\<\mc U\>,0)=c(\mc U,0)$, and let
-  $\sigma(\<\mc U,\mc V\>,n+1)=c(\mc V,n+1)\cup p(\mc U, \mc V,n+1)$.
-
-  For any attack $\<\mc{U}_0,\mc{U}_1,\dots\>$ by $\pl C$ and $x\in Y$,
+  We define the Markov strategy \(\sigma\) as follows.
+  Let \(\sigma(\<\mc U\>,0)=c(\mc U,0)\), and let
+  \(\sigma(\<\mc U,\mc V\>,n+1)=c(\mc V,n+1)\cup p(\mc U, \mc V,n+1)\).
+
+  For any attack \(\<\mc{U}_0,\mc{U}_1,\dots\>\) by \(\pl C\) and \(x\in Y\),
   one of the following must occur:
@@
     \item
-      $r_{\mc U_0}(x)=0$ and thus
-      $x\in c(\mc U_0,0)\subseteq \sigma(\<\mc U_0\>,0)$.
+      \(r_{\mc U_0}(x)=0\) and thus
+      \(x\in c(\mc U_0,0)\subseteq \sigma(\<\mc U_0\>,0)\).
 
     \item
-      $r_{\mc U_0}(x)=N+1$ for some $N\geq 0$ and:
+      \(r_{\mc U_0}(x)=N+1\) for some \(N\geq 0\) and:
       \begin{itemize}
         \item
-          For all $n\leq N$,
+          For all \(n\leq N\),
           \[
@@
           and thus
-          $x\in c(\mc U_{N+1},N+1) \subseteq
-            \sigma(\<U_N,U_{N+1}\>,N+1)$.
+          \(x\in c(\mc U_{N+1},N+1) \subseteq
+            \sigma(\<U_N,U_{N+1}\>,N+1)\).
         \item
-          For some $n \leq N$,
+          For some \(n \leq N\),
           \[ r_{\mc U_n}(x)\leq n \]
           and thus
-          $x\in c(\mc U_{n+1},n+1) \subseteq
-            \sigma(\<U_n,U_{n+1}\>,n+1)$.
+          \(x\in c(\mc U_{n+1},n+1) \subseteq
+            \sigma(\<U_n,U_{n+1}\>,n+1)\).
         \item
-          For some $n \leq N$,
+          For some \(n \leq N\),
           \[
@@
          and thus
-         $x\in p(\mc U_n,\mc U_{n+1},n+1) \subseteq
-          \sigma(\<U_n,U_{n+1}\>,n+1)$
+         \(x\in p(\mc U_n,\mc U_{n+1},n+1) \subseteq
+          \sigma(\<U_n,U_{n+1}\>,n+1)\)
        \end{itemize}
@@
 \begin{theorem}
-  $\alcompS\kappa$ implies $\oneptlind\kappa$ is
+  \(\alcompS\kappa\) implies \(\oneptlind\kappa\) is
   robustly Menger, and thus
-  $\pl F\kmarkwin2\menGame{\oneptlind\kappa}$.
+  \(\pl F\kmarkwin2\menGame{\oneptlind\kappa}\).
 \end{theorem}
@@
 \begin{proof}
-  Let $f_A$ for $A\in[\kappa]^{\leq\omega}$ witness $\alcompS\kappa$ and fix
-  $A(\mc U)\in[\kappa]^{\leq\omega}$ for each open cover $\mc U$ such that
-  $\oneptlind\kappa\setminus A(\mc U)$ is contained in some element of
-  $\mc U$.
-  Then let $r_{\mc U}(x)=0$ for $x\in\oneptlind\kappa\setminus A(\mc U)$,
-  and $r_{\mc U}(\alpha)=f_{A(\mc U)}(\alpha)$ for $\alpha\in A(\mc U)$.
+  Let \(f_A\) for \(A\in[\kappa]^{\leq\omega}\) witness \(\alcompS\kappa\) and fix
+  \(A(\mc U)\in[\kappa]^{\leq\omega}\) for each open cover \(\mc U\) such that
+  \(\oneptlind\kappa\setminus A(\mc U)\) is contained in some element of
+  \(\mc U\).
+  Then let \(r_{\mc U}(x)=0\) for \(x\in\oneptlind\kappa\setminus A(\mc U)\),
+  and \(r_{\mc U}(\alpha)=f_{A(\mc U)}(\alpha)\) for \(\alpha\in A(\mc U)\).
 
@@
     \]
-  is $\mc U$-finite, $\bigcup_{n<\omega}c(\mc U,n)=X$, and
+  is \(\mc U\)-finite, \(\bigcup_{n<\omega}c(\mc U,n)=X\), and
     \[
@@
 \begin{definition}
-  Let $R_{\mathbb Q}$ be the real line with the topology generated by open
+  Let \(R_{\mathbb Q}\) be the real line with the topology generated by open
   intervals with or without the rationals removed.
@@
 \begin{theorem}
-  $R_{\mathbb Q}$ is non-regular and non-$\sigma$-compact, but is
-  second-countable and $\sigma$-relatively-compact.
+  \(R_{\mathbb Q}\) is non-regular and non-\(\sigma\)-compact, but is
+  second-countable and \(\sigma\)-relatively-compact.
 \end{theorem}
@@
 \begin{proof}
-  Compact sets in $R_{\mathbb Q}$ can be shown to not contain open intervals,
-  and thus are nowhere dense in nonmeager $\mathbb R$,
-  so $R_{\mathbb Q}$ is not $\sigma$-compact. The usual base of
+  Compact sets in \(R_{\mathbb Q}\) can be shown to not contain open intervals,
+  and thus are nowhere dense in nonmeager \(\mathbb R\),
+  so \(R_{\mathbb Q}\) is not \(\sigma\)-compact. The usual base of
   intervals with rational endpoints (with or without rationals removed)
@@
 
-  To see that $R_{\mathbb Q}$ is $\sigma$-relatively compact, consider
-  $[a,b]\setminus\mathbb{Q}$. Let $\mc U$ be a cover of $R_{\mathbb Q}$, and
-  let $\mc U'$ fill in the missing rationals for any open set in $\mc U$.
-  There is a finite subcover $\mc V'\subseteq \mc U'$ for $[a,b]$ since
-  $\mc U'$ contains open sets from the Euclidean topology. Let
-  $\mc V= \{V\setminus\mathbb{Q}:V\in V'\}$: this is a finite refinment of
-  $\mc U$ covering $[a,b]\setminus\mathbb{Q}$, so $[a,b]\setminus\mathbb{Q}$
-  is relatively compact. It follows then that $R_{\mathbb Q}\setminus\mathbb Q$
-  is $\sigma$-relatively-compact, and since $\mathbb Q$ is countable,
-  $R_{\mathbb Q}$ is $\sigma$-relatively-compact. Non-regularity follows since
-  regular and $\sigma$-relatively-compact implies $\sigma$-compact.
+  To see that \(R_{\mathbb Q}\) is \(\sigma\)-relatively compact, consider
+  \([a,b]\setminus\mathbb{Q}\). Let \(\mc U\) be a cover of \(R_{\mathbb Q}\), and
+  let \(\mc U'\) fill in the missing rationals for any open set in \(\mc U\).
+  There is a finite subcover \(\mc V'\subseteq \mc U'\) for \([a,b]\) since
+  \(\mc U'\) contains open sets from the Euclidean topology. Let
+  \(\mc V= \{V\setminus\mathbb{Q}:V\in V'\}\): this is a finite refinment of
+  \(\mc U\) covering \([a,b]\setminus\mathbb{Q}\), so \([a,b]\setminus\mathbb{Q}\)
+  is relatively compact. It follows then that \(R_{\mathbb Q}\setminus\mathbb Q\)
+  is \(\sigma\)-relatively-compact, and since \(\mathbb Q\) is countable,
+  \(R_{\mathbb Q}\) is \(\sigma\)-relatively-compact. Non-regularity follows since
+  regular and \(\sigma\)-relatively-compact implies \(\sigma\)-compact.
 \end{proof}
@@
 \begin{definition}
-  Let $R_\omega$ be the real line with the topology generated by open
+  Let \(R_\omega\) be the real line with the topology generated by open
   intervals with countably many points removed.
@@
 \begin{theorem}
-  $R_\omega$ is non-regular, non-second-countable, and
-  non-$\sigma$-relatively-compact, but $\pl F\win\menGame{R_\omega}$.
+  \(R_\omega\) is non-regular, non-second-countable, and
+  non-\(\sigma\)-relatively-compact, but \(\pl F\win\menGame{R_\omega}\).
 \end{theorem}
@@
   The closure of any open set is its closure in the usual Euclidean topology,
-  so $R_\omega$ is not regular. If $S\supseteq\{s_n:n<\omega\}$ for $s_n$
-  discrete, then $U_m=R_\omega\setminus\{s_n:m<n<\omega\}$ yields an
-  infinite cover $\{U_m:m<\omega\}$ with no finite subcollection covering $S$,
-  showing that all relatively compact sets are finite, and $R_\omega$ is not
-  $\sigma$-relatively-compact.
-
-  Define the winning strategy $\sigma$ for $\pl F$ in $\menGame{R_\omega}$ as
-  follows: let $\sigma(\mc{U}_0,\dots,\mc{U}_{2n})=[-n,n]\setminus C_n$
-  for some countable $C_n=\{c_{n,m}: m<\omega\}$,
-  and let $\sigma(\mc{U}_0,\dots,\mc{U}_{2n+1})=\{c_{i,j} : i,j < n\}$.
+  so \(R_\omega\) is not regular. If \(S\supseteq\{s_n:n<\omega\}\) for \(s_n\)
+  discrete, then \(U_m=R_\omega\setminus\{s_n:m<n<\omega\}\) yields an
+  infinite cover \(\{U_m:m<\omega\}\) with no finite subcollection covering \(S\),
+  showing that all relatively compact sets are finite, and \(R_\omega\) is not
+  \(\sigma\)-relatively-compact.
+
+  Define the winning strategy \(\sigma\) for \(\pl F\) in \(\menGame{R_\omega}\) as
+  follows: let \(\sigma(\mc{U}_0,\dots,\mc{U}_{2n})=[-n,n]\setminus C_n\)
+  for some countable \(C_n=\{c_{n,m}: m<\omega\}\),
+  and let \(\sigma(\mc{U}_0,\dots,\mc{U}_{2n+1})=\{c_{i,j} : i,j < n\}\).
   Non-second-countable follows since
-  second-countable and $\pl F\win\menGame{X}$ implies
-  $\sigma$-relatively-compact.
-\end{proof}
-
-We will soon see that, assuming $\alcompS{2^\omega}$, $\pl F$ has a winning
-$2$-Mark\"ov strategy for $\menGame{R_\omega}$ as well.
+  second-countable and \(\pl F\win\menGame{X}\) implies
+  \(\sigma\)-relatively-compact.
+\end{proof}
+
+We will soon see that, assuming \(\alcompS{2^\omega}\), \(\pl F\) has a winning
+\(2\)-Mark\"ov strategy for \(\menGame{R_\omega}\) as well.
 
 \begin{proposition}
-  Let $\limitwin$ be either $\kmarkwin{k}$ or $\win$.
-  If $X=\bigcup_{i<\omega} X_i$ and $\pl F \limitwin \menGame{X,X_i}$
-  for $i<\omega$, then $\pl F \limitwin \menGame{X}$
+  Let \(\limitwin\) be either \(\kmarkwin{k}\) or \(\win\).
+  If \(X=\bigcup_{i<\omega} X_i\) and \(\pl F \limitwin \menGame{X,X_i}\)
+  for \(i<\omega\), then \(\pl F \limitwin \menGame{X}\)
 \end{proposition}
@@
 \begin{proof}
-  Let $L$ be the $k$-Markov fog-of-war $\mu_k$ (resp. the identity),
-  and let $\sigma_i$ be a $k$-Markov strategy (resp. perfect information
-  strategy) for $\pl F$ in $\menGame{X,X_i}$.
-
-  We define the $k$-Markov strategy (resp. perfect information strategy)
-  $\sigma$ for $\menGame{X}$ as follows:
+  Let \(L\) be the \(k\)-Markov fog-of-war \(\mu_k\) (resp. the identity),
+  and let \(\sigma_i\) be a \(k\)-Markov strategy (resp. perfect information
+  strategy) for \(\pl F\) in \(\menGame{X,X_i}\).
+
+  We define the \(k\)-Markov strategy (resp. perfect information strategy)
+  \(\sigma\) for \(\menGame{X}\) as follows:
     \[
@@
 
-  Let $\<\mc U_0,\mc U_1,\dots\>$ be a successful counter-attack by $\pl C$
-  against $\sigma$. Then there exists $x\in X_i$ for
-  some $i<\omega$ such that $x$ is not covered by
-  $\bigcup_{n<\omega}\sigma\circ L(\<\mc U_0,\dots,\mc U_n\>)$.
-  It follows that $x$ is not covered by
-  $\bigcup_{n<\omega}\sigma_i\circ L(\<\mc U_i,\dots,\mc U_{i+n}\>)$,
-  and $\<\mc U_i,\mc U_{i+1},\dots\>$ is a successful counter-attack
-  by $\pl C$ against $\sigma_i$.
+  Let \(\<\mc U_0,\mc U_1,\dots\>\) be a successful counter-attack by \(\pl C\)
+  against \(\sigma\). Then there exists \(x\in X_i\) for
+  some \(i<\omega\) such that \(x\) is not covered by
+  \(\bigcup_{n<\omega}\sigma\circ L(\<\mc U_0,\dots,\mc U_n\>)\).
+  It follows that \(x\) is not covered by
+  \(\bigcup_{n<\omega}\sigma_i\circ L(\<\mc U_i,\dots,\mc U_{i+n}\>)\),
+  and \(\<\mc U_i,\mc U_{i+1},\dots\>\) is a successful counter-attack
+  by \(\pl C\) against \(\sigma_i\).
 \end{proof}
@@
 \begin{theorem}
-  If $\alcompS{2^\omega}$, then $\pl F\kmarkwin2\menGame{R_\omega}$.
+  If \(\alcompS{2^\omega}\), then \(\pl F\kmarkwin2\menGame{R_\omega}\).
 \end{theorem}
@@
 \begin{proof}
-  It's sufficient to show that $[0,1]\subseteq R_\omega$ is relatively
-  robustly Menger. Let $f_A$ witness $\alcompS{2^\omega}$
-  for $A\in[[a,b]]^{\leq\omega}$.
-  For each open cover $\mc U$, let $A_{\mc U}$ be
-  such that $[0,1]\setminus A_{\mc U}$ is $\mc U$-finite.
-  Let $r_{\mc U}(x)=0$ if $x\in[0,1]\setminus A_{\mc U}$ and
-  $r_{\mc U}(x)=f_{\mc A_{\mc U}}(x)$ otherwise.
+  It's sufficient to show that \([0,1]\subseteq R_\omega\) is relatively
+  robustly Menger. Let \(f_A\) witness \(\alcompS{2^\omega}\)
+  for \(A\in[[a,b]]^{\leq\omega}\).
+  For each open cover \(\mc U\), let \(A_{\mc U}\) be
+  such that \([0,1]\setminus A_{\mc U}\) is \(\mc U\)-finite.
+  Let \(r_{\mc U}(x)=0\) if \(x\in[0,1]\setminus A_{\mc U}\) and
+  \(r_{\mc U}(x)=f_{\mc A_{\mc U}}(x)\) otherwise.
 
@@
     \]
-  is $\mc U$-finite and
+  is \(\mc U\)-finite and
     \[

### 2015-08-25 articles/applications-of-limited-information-strategies-in-mengers-game/article.tex
edited through end of 3rd section

@@
 \usepackage{../../clontzDefinitions}
+
+\usepackage{tikz}
+\usetikzlibrary{matrix}
 
@@
 \keywords{Menger's property, Menger's game, limited information strategies}
-% \begin{keyword}
-%   Proximal\sep absolutely proximal\sep Corson compact\sep uniform space\sep \(W\)-space
-% \end{keyword}
 
@@
 
-It can be shown via a non-trivial
-proof that the following game can be used to characterize the Menger property.
-
-\begin{definition}
-  For each cover \(\mc U\) of \(X\), \(S\subseteq X\) is \term{\(\mc U\)-finite} if
-  there exists a finite subcollection of \(\mc U\) which covers \(C\).
+It will be convenient to consider subsets of \(X\) rather than subsets of
+the open covers.
+
+\begin{definition}
+  For each cover \(\mc U\) of \(X\), \(S\subseteq X\) is
+  \term{\(\mc U\)-finite} if
+  there exists a finite subcollection of \(\mc U\) which covers \(S\).
 \end{definition}
@@
 Of course, a compact space is \(\mc U\)-finite for all open covers \(\mc U\).
+
+\begin{proposition}
+  A space \(X\) is Menger if and only if
+  for every sequence \(\<\mc U_0,\mc U_1,\dots\>\)
+  of open covers of \(X\) there exists a sequence
+  \(\<F_0,F_1,\dots\>\) such that \(F_n\subseteq X\), \(F_n\) is
+  \(\mc U_n\)-finite, and \(X=\bigcup_{n<\omega}F_n\).
+\end{proposition}
+
+This is the characterization we will use in this paper.
+A game version of the Menger property is also often considered.
 
@@
 
-\begin{theorem}
-  A space \(X\) is Menger if and only if \(\pl C\notwin\menGame{X}\)
-  \cite{MR1544773}.
+As with the Menger property, authors usually characterize this game using
+finite subsets \(\mc F_n\)
+of \(\mc U_n\) instead (and often refer to it as \(G(\mc O,\mc O)\) as
+with the selection property above).
+This is obviously equivalent in the case of perfect
+information, and is also equivalent
+in the case of limited information, provided \(\pl F\)
+knows \(\mc U_n\) during round \(n\). However, we make this change as we
+will investigate \(0\)-Markov strategies which consider no moves of
+the opponent, and instead rely only on the current round number.
+
+This game may be used to characterize the Menger property.
+
+\begin{definition}
+  If \(\pl A\) has a winning strategy for a game \(G\) (which defeats every
+  possible counterattack by her opponent), then we write \(\pl A\win G\).
+\end{definition}
+
+\begin{theorem}[Hurewicz \cite{MR1544773}]
+  A space \(X\) is Menger if and only if \(\pl C\notwin\menGame{X}\).
 \end{theorem}
 
-The typical characterization of the Menger game involves \(\pl F\) choosing
-a finite subcollection \(\mc F_n\) of \(\mc U_n\), but it is easy to see that the
-characterization given above is equivalent, and will be convenient for use
-in our proofs.
-
-\section{Markov strategies}
-
-To the author's knowledge, no other direct work has been done on limited
-information strategies pertaining to the Menger game, although as we'll see
-there are results which can be sharpened when considering them.
-However, we immediately see that tactics are not of any real interest.
+\section{Limited information strategies}
+
+Recall the following definitions.
+
+\begin{definition}
+  A \(k\)-tactical strategy for a game \(G\) with moveset \(M\) is a function
+  \(\sigma:M^{\leq k}\to M\); intuitively, it is a strategy which only considers
+  the previous \(k\) moves of the opponent. If a winning \(k\)-tactical strategy
+  exists for \(\pl P\) in the game \(G\), then we write \(\pl P\ktactwin{k} G\).
+\end{definition}
+
+\begin{definition}
+  A \(k\)-Markov strategy for a game \(G\) with moveset \(M\) is a function
+  \(\sigma:M^{\leq k}\times\omega\to M\); intuitively, it is a strategy which
+  only considers the previous \(k\) moves of the opponent and the round number.
+  If a winning \(k\)-Markov strategy exists for
+  \(\pl P\) in the game \(G\), then we write \(\pl P\kmarkwin{k} G\).
+\end{definition}
+
+We will call \(k\)-tactical strategies ``\(k\)-tactics'' and \(k\)-Markov strategies
+``\(k\)-marks''. If the \(k\) is omitted then it is assumed that \(k=1\). In
+addition, note that some authors refer to tactics as
+\term{stationary strategies}.
+
+Tactics will be of interest in a game discussed later; proving
+the following is an easy exercise.
 
@@
   \(\pl F \tactwin \menGame{X}\) if and only if
-  \(\pl F \ktactwin{k} \menGame{X}\).
+  \(\pl F \ktactwin{k+1} \menGame{X}\) for some \(k<\omega\).
 \end{proposition}
-
-\begin{proof}
-  If \(\sigma\) is a winning \(k\)-tactic, then for each open cover \(\mc U\),
-  \(\sigma\) defeats the attack \(\<\mc U,\mc U,\dots\>\). Then
-  \[
-    \bigcup_{i\leq k} \sigma(\<\underbrace{\mc U,\dots,\mc U}_i\>) = X
-  \]
-  and \(X\) is \(\mc U\)-finite.
-\end{proof}
 
@@
 
-\begin{theorem}
-  \(\pl F \notmarkwin \menGame{\oneptlind{\omega_1}}\).
-\end{theorem}
-
-\begin{proof}
-  This result will later follow from the fact that
-  \(\oneptlind\omega_1\) is not a \(\sigma\)-compact space (all its compact subsets
-  are finite).
-
-  For now, let \(\sigma\) be a Markov strategy for \(\pl F\). For
-  each \(\alpha<\omega_1\), let \(\mc U_\alpha\) be the open cover
-  \(\{\{\beta\}:\beta<\alpha\}\cup\{\oneptlind{\omega_1}\setminus\alpha\}\) of
-  \(\oneptlind{\omega_1}\), and set \(F(\alpha,n)\) to be the finite set
-  \(\alpha\cap\sigma(\<\mc U_\alpha\>,n)\).
-
-  If
-    \(
-      P_n =
-      \{\beta: \beta < \alpha < \omega_1 \Rightarrow \beta \in F(\alpha,n)\}
-    \),
-  then \(P_n\subseteq F(\sup(P_n)+1,n)\). Thus \(P_n\) is finite for \(n<\omega\).
-  Choose \(\beta\in\omega_1\setminus \bigcup_{n<\omega}P_n\)
-  and \(\alpha_n>\beta\) such that \(\beta\not\in F(\alpha_n,n)\).
-  Then \(\pl C\) may attack
-  \(\sigma\) with \(\<\mc U_{\alpha_0}, \mc U_{\alpha_1},\dots\>\),
-  and it follows that
-  \(\beta\not\in \bigcup_{n<\omega}F(\alpha_n,n)\) and
-  \(\beta\not\in \bigcup_{n<\omega}\sigma(\<\mc U_{\alpha_n}\>,n)\).
-\end{proof}
+\begin{proposition}
+  \(\pl F \notmarkwin \menGame{\oneptlind{\omega_1}}\); in fact,
+  \(\oneptlind{\omega_1}\) is not \(\sigma\)-compact.
+\end{proposition}
 
@@
 react that will give \(\pl F\) her winning \(2\)-Markov strategy in the Menger
-game on \(\oneptlind\omega_1\).
-
-For inspiration, we turn to a game whose \(n\)-tactics were studied by Marion
-Scheepers in \cite{MR1129143} which has similar goals to the Menger game when
-played upon \(\oneptlind\kappa\).
+game on \(\oneptlind\omega_1\). This may be proven directly; however, we will
+postpone giving a proof so that we may take advantage of an equivalent
+game characterization of this property.
+
+\section{Scheepers' filling games}
+
+We now turn to a related game whose \(k\)-tactics were studied by Marion
+Scheepers in \cite{MR1129143}.
 
 \begin{game}
-  Let \(\cloFillStrictGame\kappa\) denote the \term{strict union filling game}
+  Let \(\schFillStrictGame\kappa\) denote
+  \term{Scheepers' strict union filling game}
   with two players \(\pl C\), \(\pl F\). In round \(0\), \(\pl C\) chooses
@@
   \(\pl F\) wins the game if
-  \(\bigcup_{n<\omega} F_n\supseteq\bigcup_{n<\omega} C_n\); otherwise, \(\pl C\)
-  wins.
+  \(\bigcup_{n<\omega} F_n\supseteq\bigcup_{n<\omega} C_n\); otherwise,
+  \(\pl C\) wins.
 \end{game}
@@
 countable sets chosen by \(\pl C\) in \(\menGame{\oneptlind\kappa}\), rather
-than the union as in \(\cloFillStrictGame\kappa\).
-
-Another difference: Scheepers required that \(\pl C\) always choose strictly
-growing countable sets. The reasoning is clear: if the goal is to study tactics,
-then \(\pl C\) cannot be allowed to trap \(\pl F\) in a loop by repeating the same
+than the union as in \(\schFillStrictGame\kappa\).
+
+Another difference between these games:
+Scheepers required that \(\pl C\) always choose strictly
+growing countable sets. If the goal is to study tactics,
+then \(\pl C\) cannot be allowed to trap \(\pl F\) in a loop by
+repeating the same
 moves. But by eliminating this requirement, the study can then turn to Markov
@@
 We introduce a few games to make the relationship between Scheeper's
-\(\cloFillStrictGame\kappa\) and \(\menGame{\oneptlind\kappa}\) more precise.
+\(\schFillStrictGame\kappa\) and \(\menGame{\oneptlind\kappa}\) more precise.
 
 \begin{game}
-  Let \(\cloFillGame\kappa\) denote the
+  Let \(\schFillGame\kappa\) denote the
   \term{union filling game} which proceeds analogously
-  to \(\cloFillStrictGame\kappa\), except that \(\pl C\)'s restriction in round \(n+1\)
+  to \(\schFillStrictGame\kappa\), except that \(\pl C\)'s restriction in round \(n+1\)
   is reduced to \(C_{n+1}\supseteq C_n\).
@@
 \begin{game}
-  Let \(\cloFillInitialGame\kappa\) denote the
+  Let \(\schFillInitialGame\kappa\) denote the
   \term{initial filling game} which proceeds analogously
-  to \(\cloFillGame\kappa\), except that \(\pl F\) wins whenever
+  to \(\schFillGame\kappa\), except that \(\pl F\) wins whenever
   \(\bigcup_{n<\omega}F_n\supseteq C_0\).
@@
 \begin{game}
-  Let \(\cloFillIntGame\kappa\) denote the
+  Let \(\schFillIntGame\kappa\) denote the
   \term{intersection filling game} which proceeds analogously
-  to \(\cloFillInitialGame\kappa\), except that \(\pl C\) may choose any
+  to \(\schFillInitialGame\kappa\), except that \(\pl C\) may choose any
   \(C_n\in[\kappa]^{\leq\omega}\) each round, and \(\pl F\) wins whenever
@@
 \begin{center}
-% \begin{tikzpicture}
-%   \matrix (m) [matrix of math nodes,row sep=3em,column sep=1em,minimum width=2em]
-%   {
-%     \pl F \kmarkwin{k}\menGame{\oneptlind\kappa} &
-%     \pl F \kmarkwin{k}\cloFillIntGame\kappa \\
-
-%     \pl F \kmarkwin{k}\cloFillInitialGame\kappa &
-%     \pl F \kmarkwin{k}\cloFillGame\kappa \\
-
-%     &
-%     \pl F \ktactwin{k}\cloFillStrictGame\kappa \\
-%   };
-%   \path[>=latex,->]
-%     (m-1-1) edge (m-2-1)
-%     (m-1-2) edge (m-2-2)
-%     (m-3-2) edge (m-2-2);
-%   \path[>=latex,<->]
-%     (m-1-1) edge (m-1-2)
-%     (m-2-1) edge (m-2-2);
-% \end{tikzpicture}
+\begin{tikzpicture}
+  \matrix (m) [matrix of math nodes,row sep=3em,column sep=1em,minimum width=2em]
+  {
+    \pl F \kmarkwin{k+1}\menGame{\oneptlind\kappa} &
+    \pl F \kmarkwin{k+1}\schFillIntGame\kappa \\
+
+    \pl F \kmarkwin{k+1}\schFillInitialGame\kappa &
+    \pl F \kmarkwin{k+1}\schFillGame\kappa \\
+
+    &
+    \pl F \ktactwin{k+1}\schFillStrictGame\kappa \\
+  };
+  \path[>=latex,->]
+    (m-1-1) edge (m-2-1)
+    (m-1-2) edge (m-2-2)
+    (m-3-2) edge (m-2-2);
+  \path[>=latex,<->]
+    (m-1-1) edge (m-1-2)
+    (m-2-1) edge (m-2-2);
+\end{tikzpicture}
 \end{center}
-\caption{Diagram of Filling/Menger game implications}
+\caption{Diagram of Scheepers/Menger game implications}
 \label{fillingGamesDiagram}
@@
 \begin{theorem}
-For any cardinal \(\kappa>\omega\) and integer \(k<\omega\),
+For any cardinal \(\kappa\geq\omega\) and integer \(k<\omega\),
 Figure \ref{fillingGamesDiagram} holds.
@@
 \begin{proof}
-  \(\pl F \kmarkwin{k}\menGame{\oneptlind\kappa}
+  \(\pl F \kmarkwin{k+1}\menGame{\oneptlind\kappa}
     \Rightarrow
-  \pl F \kmarkwin{k}\cloFillIntGame\kappa\):
+  \pl F \kmarkwin{k+1}\schFillIntGame\kappa\):
   Let \(\sigma\) be a winning \(k\)-mark for \(\pl F\) in
@@
     \]
-  is a winning \(k\)-mark for \(\pl F\) in \(\cloFillIntGame\kappa\).
-
-  \(\pl F \kmarkwin{k}\cloFillIntGame\kappa
+  is a winning \((k+1)\)-mark for \(\pl F\) in \(\schFillIntGame\kappa\).
+
+  \(\pl F \kmarkwin{k+1}\schFillIntGame\kappa
     \Rightarrow
-  \pl F \kmarkwin{k}\menGame{\oneptlind\kappa}\):
+  \pl F \kmarkwin{k+1}\menGame{\oneptlind\kappa}\):
   Let \(\sigma\) be a winning \(k\)-mark for \(\pl F\) in
-  \(\cloFillIntGame\kappa\). Let \(C(\mc U)\) (resp. \(C(s)\)) convert each open
+  \(\schFillIntGame\kappa\). Let \(C(\mc U)\) (resp. \(C(s)\)) convert each open
   cover \(\mc U\) of \(\oneptlind\kappa\) (resp. finite sequence \(s\) of such covers)
@@
     \]
-  is a winning \(k\)-mark for \(\pl F\) in \(\menGame{\oneptlind\kappa}\).
-
-  \(\pl F \kmarkwin{k}\cloFillIntGame\kappa
+  is a winning \((k+1)\)-mark for \(\pl F\) in \(\menGame{\oneptlind\kappa}\).
+
+  \(\pl F \kmarkwin{k+1}\schFillIntGame\kappa
     \Rightarrow
-  \pl F \kmarkwin{k}\cloFillInitialGame\kappa\):
+  \pl F \kmarkwin{k+1}\schFillInitialGame\kappa\):
   Let \(\sigma\) be a winning \(k\)-mark for \(\pl F\) in
-  \(\cloFillIntGame\kappa\). \(\sigma\) is also a winning \(k\)-mark for \(\pl F\)
-  in \(\cloFillInitialGame\kappa\).
-
-  \(\pl F \kmarkwin{k}\cloFillInitialGame\kappa
+  \(\schFillIntGame\kappa\). \(\sigma\) is also a winning \(k\)-mark for \(\pl F\)
+  in \(\schFillInitialGame\kappa\).
+
+  \(\pl F \kmarkwin{k+1}\schFillInitialGame\kappa
     \Rightarrow
-  \pl F \kmarkwin{k}\cloFillGame\kappa\): Let \(\sigma\) be a winning \(k\)-mark for \(\pl F\) in
-  \(\cloFillInitialGame\kappa\). For each finite sequence \(s\), let \(t\preceq s\) mean \(t\)
+  \pl F \kmarkwin{k+1}\schFillGame\kappa\): Let \(\sigma\) be a winning \(k\)-mark for \(\pl F\) in
+  \(\schFillInitialGame\kappa\). For each finite sequence \(s\), let \(t\preceq s\) mean \(t\)
   is a final subsequence of \(s\). Then \(\tau\) defined by
@@
     \]
-  is a winning \(k\)-mark for \(\pl F\) in \(\cloFillGame\kappa\).
-
-  \(\pl F \kmarkwin{k}\cloFillGame\kappa
+  is a winning \((k+1)\)-mark for \(\pl F\) in \(\schFillGame\kappa\).
+
+  \(\pl F \kmarkwin{k+1}\schFillGame\kappa
     \Rightarrow
-  \pl F \kmarkwin{k}\cloFillInitialGame\kappa\):
+  \pl F \kmarkwin{k+1}\schFillInitialGame\kappa\):
   Let \(\sigma\) be a winning \(k\)-mark for \(\pl F\) in
-  \(\cloFillGame\kappa\). \(\sigma\) is also a winning \(k\)-mark for \(\pl F\)
-  in \(\cloFillInitialGame\kappa\).
-
-  \(\pl F \ktactwin{k}\cloFillStrictGame\kappa
+  \(\schFillGame\kappa\). \(\sigma\) is also a winning
+  \((k+1)\)-mark for \(\pl F\)
+  in \(\schFillInitialGame\kappa\).
+
+  \(\pl F \ktactwin{k+1}\schFillStrictGame\kappa
     \Rightarrow
-  \pl F \kmarkwin{k}\cloFillGame\kappa\):
+  \pl F \kmarkwin{k+1}\schFillGame\kappa\):
   Let \(\sigma\) be a winning \(k\)-tactic for \(\pl F\) in
-  \(\cloFillStrictGame\kappa\). For each countable subset \(C\) of \(\kappa\), let \(C+n\)
+  \(\schFillStrictGame\kappa\). For each countable subset \(C\) of \(\kappa\), let \(C+n\)
   be the union of \(C\) with the \(n\) least ordinals in \(\kappa\setminus C\).
@@
     \]
-  is a winning \(k\)-mark for \(\pl F\) in \(\cloFillGame\kappa\).
-\end{proof}
-
-While we have not proven a direct implication between the Menger game and
+  is a winning \((k+1)\)-mark for \(\pl F\) in \(\schFillGame\kappa\).
+\end{proof}
+
+While we have not shown a direct implication between the Menger game and
 Scheeper's original filling game, Scheepers introduced the statement
@@
 Scheepers went on to show that \(\alcompS\kappa\) implies
-\(\pl F \ktactwin2 \cloFillStrictGame\kappa\). This proof, along with the following
+\(\pl F \ktactwin2 \schFillStrictGame\kappa\). This proof, along with the following
 facts, give us inspiration for
@@
 \begin{center}
-% \begin{tikzpicture}
-%   \matrix (m) [matrix of math nodes,row sep=3em,column sep=1em,minimum width=2em]
-%   {
-%     &
-%     \pl F \kmarkwin2\menGame{\oneptlind\kappa} &
-%     \pl F \kmarkwin2\cloFillIntGame\kappa \\
-
-%     \alcompS\kappa &
-%     \pl F \kmarkwin2\cloFillInitialGame\kappa &
-%     \pl F \kmarkwin2\cloFillGame\kappa \\
-
-%     &
-%     &
-%     \pl F \ktactwin2\cloFillStrictGame\kappa \\
-%   };
-%   \path[>=latex,->]
-%     (m-2-1) edge (m-1-2)
-%     (m-2-1) edge (m-2-2)
-%     (m-2-1) edge (m-3-3)
-%     (m-1-2) edge (m-2-2)
-%     (m-1-3) edge (m-2-3)
-%     (m-3-3) edge (m-2-3);
-%   \path[>=latex,<->]
-%     (m-1-2) edge (m-1-3)
-%     (m-2-2) edge (m-2-3);
-% \end{tikzpicture}
+\begin{tikzpicture}
+  \matrix (m) [matrix of math nodes,row sep=3em,column sep=1em,minimum width=2em]
+  {
+    &
+    \pl F \kmarkwin2\menGame{\oneptlind\kappa} &
+    \pl F \kmarkwin2\schFillIntGame\kappa \\
+
+    \alcompS\kappa &
+    \pl F \kmarkwin2\schFillInitialGame\kappa &
+    \pl F \kmarkwin2\schFillGame\kappa \\
+
+    &
+    &
+    \pl F \ktactwin2\schFillStrictGame\kappa \\
+  };
+  \path[>=latex,->]
+    (m-2-1) edge (m-1-2)
+    (m-2-1) edge (m-2-2)
+    (m-2-1) edge (m-3-3)
+    (m-1-2) edge (m-2-2)
+    (m-1-3) edge (m-2-3)
+    (m-3-3) edge (m-2-3);
+  \path[>=latex,<->]
+    (m-1-2) edge (m-1-3)
+    (m-2-2) edge (m-2-3);
+\end{tikzpicture}
 \end{center}
@@
 \begin{proof}
-  Since \(\alcompS\kappa\Rightarrow\pl F \ktactwin2\cloFillStrictGame\kappa\) was
+  Since \(\alcompS\kappa\Rightarrow\pl F \ktactwin2\schFillStrictGame\kappa\) was
   a main result of \cite{MR1129143}, it is sufficient to show that
-  \(\alcompS\kappa\Rightarrow \pl F \kmarkwin2\cloFillIntGame\kappa\).
+  \(\alcompS\kappa\Rightarrow \pl F \kmarkwin2\schFillIntGame\kappa\).
 
@@
 \begin{center}
-% \begin{tikzpicture}
-%   \matrix (m) [matrix of math nodes,row sep=3em,column sep=1em,minimum width=2em]
-%   {
-%      \pl F \markwin \menGame{X} &
-%      \pl F \kmarkwin2 \menGame{X} &
-%      \pl F \win \menGame{X} &
-%      \pl C \notwin \menGame{X} \\
-
-%      \text{Markov Menger} &
-%      2\text{-Markov Menger} &
-%      \text{Perfect Menger} &
-%      \text{Menger} \\
-%   };
-%   \path[>=latex,<->]
-%     (m-1-1) edge (m-2-1)
-%     (m-1-2) edge (m-2-2)
-%     (m-1-3) edge (m-2-3)
-%     (m-1-4) edge (m-2-4);
-%   \path[>=latex,->]
-%     (m-1-1) edge (m-1-2)
-%     (m-2-1) edge (m-2-2)
-%     (m-1-2) edge (m-1-3)
-%     (m-2-2) edge (m-2-3)
-%     (m-1-3) edge (m-1-4)
-%     (m-2-3) edge (m-2-4);
-%   \path[>=latex,->,bend right=30, dotted]
-%     (m-1-2) edge node {\( \not \)} (m-1-1)
-%     (m-2-2) edge node {\( \not \)} (m-2-1)
-%     (m-1-4) edge node {\( \not \)} (m-1-3)
-%     (m-2-4) edge node {\( \not \)} (m-2-3);
-%   \path[>=latex,->,bend right=30, dotted]
-%     (m-1-3) edge node {\( ? \)} (m-1-2)
-%     (m-2-3) edge node {\( ? \)} (m-2-2);
-% \end{tikzpicture}
+\begin{tikzpicture}
+  \matrix (m) [matrix of math nodes,row sep=3em,column sep=1em,minimum width=2em]
+  {
+     \pl F \markwin \menGame{X} &
+     \pl F \kmarkwin2 \menGame{X} &
+     \pl F \win \menGame{X} &
+     \pl C \notwin \menGame{X} \\
+
+     \text{Markov Menger} &
+     2\text{-Markov Menger} &
+     \text{Perfect Menger} &
+     \text{Menger} \\
+  };
+  \path[>=latex,<->]
+    (m-1-1) edge (m-2-1)
+    (m-1-2) edge (m-2-2)
+    (m-1-3) edge (m-2-3)
+    (m-1-4) edge (m-2-4);
+  \path[>=latex,->]
+    (m-1-1) edge (m-1-2)
+    (m-2-1) edge (m-2-2)
+    (m-1-2) edge (m-1-3)
+    (m-2-2) edge (m-2-3)
+    (m-1-3) edge (m-1-4)
+    (m-2-3) edge (m-2-4);
+  \path[>=latex,->,bend right=30, dotted]
+    (m-1-2) edge node {\( \not \)} (m-1-1)
+    (m-2-2) edge node {\( \not \)} (m-2-1)
+    (m-1-4) edge node {\( \not \)} (m-1-3)
+    (m-2-4) edge node {\( \not \)} (m-2-3);
+  \path[>=latex,->,bend right=30, dotted]
+    (m-1-3) edge node {\( ? \)} (m-1-2)
+    (m-2-3) edge node {\( ? \)} (m-2-2);
+\end{tikzpicture}
 \end{center}

### 2015-08-26 articles/applications-of-limited-information-strategies-in-mengers-game/article.tex
finish draft sans abstract and introduction

@@
 \begin{definition}
-  For two functions \(f,g\) we say \(f\) is \textbf{\(\mu\)-almost compatible} with
-  \(g\) (\(f\alcomp_\mu g\)) if \(|\{x\in\dom(f)\cap\dom(g):f(x)\not=g(x)\}|<\mu\).
-  If \(\mu=\omega\) then we say \(f,g\) are \textbf{almost compatible}
-  (\(f\alcomp g\)).
+  For two functions \(f,g\) we say \(f\) is \textbf{almost compatible} with
+  \(g\) (\(f\alcomp g\)) if \(|\{x\in\dom(f)\cap\dom(g):f(x)\not=g(x)\}|<\omega\).
 \end{definition}
@@
 \begin{theorem}
-  \(\alcompS{\omega_1}\) and \(\kappa>2^\omega\Rightarrow\neg\alcompS\kappa\)
+  \(\alcompS{\omega_1}\) and \(\neg\alcompS{\mf c^+}\)
   are theorems of \(ZFC\).
-  \(\alcompS{2^\omega}\) is a theorem of \(ZFC+CH\) and consistent with
+  \(\alcompS{\mf c}\) is a theorem of \(ZFC+CH\) and consistent with
   \(ZFC+\neg CH\).
@@
 \begin{proof}
-  For \(\alcompS{\omega_1}\), look at pg. 70 of \cite{MR597342}; this of course
-  implies \(\alcompS{2^\omega}\) under \(CH\).
-  \(\neg\alcompS{(2^\omega)^+}\) is shown by a cardinality argument
+  For \(\alcompS{\omega_1}\), consider the construction of an Aronzajn tree
+  as in \cite{MR597342}; this of course
+  implies \(\alcompS{\mf c}\) under \(CH\).
+  \(\neg\alcompS{\mf c^+}\) is shown by a cardinality argument
   in \cite{MR1129143}.
@@
 Note that while it's consistent that
-\(\pl F\kmarkwin2\menGame{\oneptlind{(2^\omega)}}\), \(\oneptlind{\kappa}\)
-for \(\kappa>2^\omega\) is a candidate to answer the above question.
+\(\pl F\kmarkwin2\menGame{\oneptlind{\mf c}}\), \(\oneptlind{\kappa}\)
+for \(\kappa>\mf c\) is a candidate to answer the above question.
 
 We are also interested in non-game-theoretic characterizations of these
-covering properties. It has been known for some time that for metrizable spaces,
-winning Menger spaces are exactly the \(\sigma\)-compact spaces, shown first
+covering properties. It has been known for some time that metrizable perfect
+Menger spaces are exactly the metrizable \(\sigma\)-compact spaces, shown first
 by Telgarksy in \cite{MR753073} and later directly by Scheepers in
@@
 
-For example, any bounded subset of Euclidean space is relatively compact
-whether it is closed or not. Actually, relative compactness can be thought
-of as an analogue of boundedness for regular spaces.
-
 \begin{proposition}
@@
   \(\cl Y\) is compact in \(X\).
-  \footnote{
-    It should be noted that some authors define relative compactness in
-    this way, but such a definition creates pathological implications for
-    non-regular spaces. For example, the singleton containing
-    the particular point of an infinite space with the particular point topology
-    would not be relatively compact since its closure is not compact, even
-    though it is finite.
-  }
 \end{proposition}
-
-\begin{proof}
-  For any space, any subset of a compact set is relatively compact.
-
-  Assume \(Y\) is relatively compact, let \(\mc U\) be an open cover of \(\cl Y\),
-  and define \(x\in V_x\subseteq \cl{V_x}\subseteq U_x \in \mc U\) for each
-  \(x\in X\). Then if we take a subcollection \(\mc F = \{V_{x_i} : i<n\}\) covering
-  \(Y\) by relative compactness, then \(\{U_{x_i}:i<n\}\) is a finite subcollection
-  of \(\mc U\) covering \(\cl Y\), showing compactness.
-\end{proof}
-
-We now begin the process of factoring out Scheeper's proof to reveal the
-limited information implications at work.
 
@@
     \item \(X\) is \(\sigma\)-relatively-compact
-    \item \(\pl F \prewin \menGame X\)
+    \item \(\pl F \kmarkwin0 \menGame X\)
     \item \(\pl F \markwin \menGame X\)
@@
   If \(X=\bigcup_{n<\omega} R_n\) for \(R_n\) relatively compact, then
-  \(\sigma(n)=R_n\) is a winning predetermined strategy, which yields a
-  winning Markov strategy. The previous lemma finishes the proof.
+  \(\sigma(n)=R_n\) is a winning \(0\)-mark, which of course gives a
+  winning \(1\)-mark. The previous lemma finishes the proof.
 \end{proof}
@@
     \item \(X\) is \(\sigma\)-relatively-compact
-    \item \(F \prewin \menGame{X}\)
+    \item \(F \kmarkwin0 \menGame{X}\)
     \item \(F \markwin \menGame{X}\)
@@
 \begin{proof}
-  Each property implies Lindel\"of, so \(X\) may be assumed to be
+  Each bullet implies \(X\) is Lindel\"of, so \(X\) may be assumed to be
   regular and second-countable.
@@
 To help describe \(\pl F\kmarkwin2\menGame{X}\) topologically, we introduce a
-subset variant of the Menger game and a related covering property.
+slight variant of the Menger game and a related covering property.
 
@@
 
-We may also consider common (non-regular) counterexamples which are finer
+We may also consider common counterexamples which are finer
 than the usual Euclidean line.
@@
 
-\begin{theorem}
+\begin{example}
   \(R_{\mathbb Q}\) is non-regular and non-\(\sigma\)-compact, but is
   second-countable and \(\sigma\)-relatively-compact.
-\end{theorem}
+\end{example}
 
 \begin{proof}
-  Compact sets in \(R_{\mathbb Q}\) can be shown to not contain open intervals,
+  Compact sets in \(R_{\mathbb Q}\) cannot contain open intervals,
   and thus are nowhere dense in nonmeager \(\mathbb R\),
@@
   intervals with rational endpoints (with or without rationals removed)
-  witnesses second-countability.
-
-  To see that \(R_{\mathbb Q}\) is \(\sigma\)-relatively compact, consider
-  \([a,b]\setminus\mathbb{Q}\). Let \(\mc U\) be a cover of \(R_{\mathbb Q}\), and
-  let \(\mc U'\) fill in the missing rationals for any open set in \(\mc U\).
-  There is a finite subcover \(\mc V'\subseteq \mc U'\) for \([a,b]\) since
-  \(\mc U'\) contains open sets from the Euclidean topology. Let
-  \(\mc V= \{V\setminus\mathbb{Q}:V\in V'\}\): this is a finite refinment of
-  \(\mc U\) covering \([a,b]\setminus\mathbb{Q}\), so \([a,b]\setminus\mathbb{Q}\)
-  is relatively compact. It follows then that \(R_{\mathbb Q}\setminus\mathbb Q\)
-  is \(\sigma\)-relatively-compact, and since \(\mathbb Q\) is countable,
-  \(R_{\mathbb Q}\) is \(\sigma\)-relatively-compact. Non-regularity follows since
-  regular and \(\sigma\)-relatively-compact implies \(\sigma\)-compact.
+  witnesses second-countability, and \([-n,n]\) is relatively compact.
 \end{proof}
@@
 
-\begin{theorem}
+\begin{example}
   \(R_\omega\) is non-regular, non-second-countable, and
   non-\(\sigma\)-relatively-compact, but \(\pl F\win\menGame{R_\omega}\).
-\end{theorem}
+\end{example}
 
 \begin{proof}
-  The closure of any open set is its closure in the usual Euclidean topology,
-  so \(R_\omega\) is not regular. If \(S\supseteq\{s_n:n<\omega\}\) for \(s_n\)
+  If \(S\supseteq\{s_n:n<\omega\}\) for \(s_n\)
   discrete, then \(U_m=R_\omega\setminus\{s_n:m<n<\omega\}\) yields an
@@
   Define the winning strategy \(\sigma\) for \(\pl F\) in \(\menGame{R_\omega}\) as
-  follows: let \(\sigma(\mc{U}_0,\dots,\mc{U}_{2n})=[-n,n]\setminus C_n\)
+  follows: let \(\sigma(\<\mc{U}_0,\dots,\mc{U}_{2n}\>)=[-n,n]\setminus C_n\)
   for some countable \(C_n=\{c_{n,m}: m<\omega\}\),
-  and let \(\sigma(\mc{U}_0,\dots,\mc{U}_{2n+1})=\{c_{i,j} : i,j < n\}\).
-  Non-second-countable follows since
-  second-countable and \(\pl F\win\menGame{X}\) implies
-  \(\sigma\)-relatively-compact.
+  and let \(\sigma(\<\mc{U}_0,\dots,\mc{U}_{2n+1}\>)=\{c_{i,j} : i,j < n\}\).
 \end{proof}
 
-We will soon see that, assuming \(\alcompS{2^\omega}\), \(\pl F\) has a winning
+We will soon see that, assuming \(\alcompS{\mf c}\), \(\pl F\) has a winning
 \(2\)-Mark\"ov strategy for \(\menGame{R_\omega}\) as well.
@@
 \begin{proposition}
-  Let \(\limitwin\) be either \(\kmarkwin{k}\) or \(\win\).
-  If \(X=\bigcup_{i<\omega} X_i\) and \(\pl F \limitwin \menGame{X,X_i}\)
-  for \(i<\omega\), then \(\pl F \limitwin \menGame{X}\)
+  If \(X=\bigcup_{i<\omega} X_i\) and \(\pl F \kmarkwin{k} \menGame{X,X_i}\)
+  for \(i<\omega\), then \(\pl F \kmarkwin{k} \menGame{X}\)
 \end{proposition}
@@
 \begin{proof}
-  Let \(L\) be the \(k\)-Markov fog-of-war \(\mu_k\) (resp. the identity),
-  and let \(\sigma_i\) be a \(k\)-Markov strategy (resp. perfect information
-  strategy) for \(\pl F\) in \(\menGame{X,X_i}\).
+  Let \(\sigma_i\) be a \(k\)-Markov strategy
+  for \(\pl F\) in \(\menGame{X,X_i}\).
 
-  We define the \(k\)-Markov strategy (resp. perfect information strategy)
+  We define the \(k\)-Markov strategy
   \(\sigma\) for \(\menGame{X}\) as follows:
     \[
-      \sigma\circ L(\<\mc U_0,\dots,\mc U_n\>)
+      \sigma(\<\mc U_0,\dots,\mc U_n\>)
         =
       \bigcup_{i\leq n}
-      \sigma_i\circ L(\<\mc U_i,\dots,\mc U_n\>)
+      \sigma_i(\<\mc U_i,\dots,\mc U_n\>)
     \]
@@
   some \(i<\omega\) such that \(x\) is not covered by
-  \(\bigcup_{n<\omega}\sigma\circ L(\<\mc U_0,\dots,\mc U_n\>)\).
+  \(\bigcup_{n<\omega}\sigma(\<\mc U_0,\dots,\mc U_n\>)\).
   It follows that \(x\) is not covered by
-  \(\bigcup_{n<\omega}\sigma_i\circ L(\<\mc U_i,\dots,\mc U_{i+n}\>)\),
+  \(\bigcup_{n<\omega}\sigma_i(\<\mc U_i,\dots,\mc U_{i+n}\>)\),
   and \(\<\mc U_i,\mc U_{i+1},\dots\>\) is a successful counter-attack
@@
 
-\begin{theorem}
-  If \(\alcompS{2^\omega}\), then \(\pl F\kmarkwin2\menGame{R_\omega}\).
+\begin{theorem}[\(\alcompS{\mf c}\)]
+  \(\pl F\kmarkwin2\menGame{R_\omega}\).
 \end{theorem}
@@
   It's sufficient to show that \([0,1]\subseteq R_\omega\) is relatively
-  robustly Menger. Let \(f_A\) witness \(\alcompS{2^\omega}\)
+  robustly Menger. Let \(f_A\) witness \(\alcompS{\mf c}\)
   for \(A\in[[a,b]]^{\leq\omega}\).

### 2015-09-01 postdoctoral/S_prime_kappa.tex
work on S' example by Dow

\documentclass[11pt]{article}

\usepackage{../clontzStyle}
\usepackage{../clontzDefinitions}

\begin{document}

  \begin{remark}
    Scheeper's \(S(\kappa)\) requiring injections is stronger than my
    \(S'(\kappa)\) requiring finite-to-one maps. Dow suggests that
    \(S'(\omega_2)\) holds in ZFC. Here's my writeup of his argument.
  \end{remark}

  \begin{definition}
    A topological space is said to be \(\omega\)-bounded if each countable
    subset of the space has compact closure.
  \end{definition}

  \begin{claim*}
    There exists a topology on \(\omega_2\) which is locally countable
    and \(\aleph_0\)-bounded.
  \end{claim*}

  \begin{proposition}
    A space which is locally countable and \(\omega\)-bounded is also
    locally compact, locally second-countable, and scattered.
  \end{proposition}

  \begin{proof}
    A countable neighborhood has compact closure by \(\omega\)-boundedness,
    which gives local compactness.

    By local countability, we have local secound-countability.

    TODO: figure out trick to get scattered.
  \end{proof}

  \begin{theorem*}
    \(S'(\omega_2)\).
  \end{theorem*}

  \begin{proof}
    For \(\alpha<\omega_2\), let \(W_\alpha\) be the
    intersection of a countable and compact neighborhood in the claimed topology
    on \(\omega_2\).
  \end{proof}

\end{document}

### 2015-09-17 articles/destroying-metrizability-in-generalized-inverse-limits/article.tex
update with vargona's latest draft

@@
+% This file requires figure.pdf and it should be processed by pdflatex.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%           Topology Proceedings Sample Latex Article             %%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \documentclass{amsart}
+\usepackage[T1]{fontenc}   %%%%%%%Please do not change
+\usepackage{graphics}                  %%%%%%%
 
@@
 \usepackage{graphicx}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Please do not change this paragraph. %%%%%%%
+\setcounter{page}{1}                   %%%%%%%
+\setlength{\textwidth}{4.4in}          %%%%%%%
+\setlength{\textheight}{7.0in}         %%%%%%%
+\setlength{\evensidemargin}{1in}       %%%%%%%
+\setlength{\oddsidemargin}{1in}        %%%%%%%
+\setlength{\topmargin}{.8in}           %%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Please do not change the page size   %%%%%%%
+% and do not redefine the baselineskip.%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \newtheorem{definition}[theorem]{Definition}
-\newtheorem{game}[theorem]{Game}
 \newtheorem{example}[theorem]{Example}
@@
 
+\begin{document}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% This a placeholder for the TOPLOGY PROCEEDINGS logo %%%%%%
+\noindent                                             %%%%%%
+\begin{picture}(150,36)                               %%%%%%
+\put(5,20){\tiny{Submitted to}}                       %%%%%%
+\put(5,7){\textbf{Topology Proceedings}}              %%%%%%
+\put(0,0){\framebox(140,34){}}                        %%%%%%
+\put(2,2){\framebox(136,30){}}                        %%%%%%
+\end{picture}                                        %%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\vspace{0.5in}
+
+\renewcommand{\bf}{\bfseries}
+\renewcommand{\sc}{\scshape}
 \newcommand{\<}{\langle}
 \renewcommand{\>}{\rangle}
+%insert defs/styles
+\vspace{0.5in}
 
-\parskip=0.5em
+\title[Destruction of metrizability in generalized inverse limits]%
+{Destruction of metrizability in generalized inverse limits}
 
-\title{Destruction of metrizability in generalized inverse limits}
+%    Information for first author:
+\author{Steven Clontz}
+\address{Department of Mathematics and Statistics, Fretwell Hall, UNC Charlotte, NC 28223}
+%    Current address (if needed):
+%\curraddr{}
+\email{steven.clontz@gmail.com}
+%\thanks{}
 
-\author{Steven Clontz, Scott Varagona}
+%    Information for second author (if needed):
+\author{Scott Varagona}
+\address{Department of Biology, Chemistry \& Mathematics, University of Montevallo,
+Montevallo, AL 35115}
+\email{svaragona@montevallo.edu}
+%\thanks{Support information for the second author.}
 
-\date{\today}
+%    General info
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subjclass[2010]{Primary 54F15, 54H20}                                    %
+%                                                                                                                           %
+%         Please use the current 2010 Mathematics Subject Classification:             %
+%         http://www.ams.org/mathscinet/msc/                                                        %
+%         http://www.zentralblatt-math.org/msc/en/                                                 %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\begin{document}
+\keywords{Inverse Limits, Inverse Limits with set-valued functions, continuum theory, metrizability, idempotent.}
+\thanks {}
 
@@
 If a u.s.c.
-function $f: X \rightarrow 2^{Y}$ has the property that $f(x)$ is connected for each $x \in X$, then $f$ is \emph{continuum-valued}, and we denote this by writing  $f: X \rightarrow C(Y).$
+function $f: X \rightarrow 2^{Y}$ has the property that $f(x)$ is connected for each $x \in X$, then $f$ is \emph{continuum-valued}, and we denote this by writing  $f: X \rightarrow C(Y).$ The \emph{identity on} $X$ is the u.s.c.
+function $\iota$ given by $\iota(x) = \{x\}$ for all $x \in X$; we may simply say the \emph{identity} (or, more simply, $\iota$) when the space $X$ is understood from context.
 
@@
 (We follow the convention of set theory in which an ordinal is equal to the set of its predecessors.
-For more detailed background on ordinals, see, for example, \cite{Kunen}.
-Assume all ordinals are nonzero.) Suppose that for each $\alpha \in \kappa$, $X_{\alpha}$ is a non-empty compact Hausdorff space and whenever $\alpha \le \beta \in \kappa$, the set-valued function $f_{\alpha \beta} : X_{\beta} \rightarrow 2^{X_{\alpha}}$ is u.s.c.
-(With this notation, $f_{\alpha \alpha}$ always denotes the identity on $X_{\alpha}$.) Suppose further that, whenever $\alpha \le \beta \le \eta \in \kappa$, we have $f_{\alpha \beta} \circ f_{\beta \eta} = f_{\alpha \eta}$.
+For more detailed background on ordinals, see, for example, \cite{Kunen}.) Suppose that for each $\alpha \in \kappa$, $X_{\alpha}$ is a non-empty compact Hausdorff space and whenever $\alpha \le \beta \in \kappa$, the set-valued function $f_{\alpha \beta} : X_{\beta} \rightarrow 2^{X_{\alpha}}$ is u.s.c.
+(With this notation, $f_{\alpha \alpha}$ is always the identity $\iota$ on $X_{\alpha}$.) Suppose further that, whenever $\alpha \le \beta \le \eta \in \kappa$, we have $f_{\alpha \beta} \circ f_{\beta \eta} = f_{\alpha \eta}$.
 Then the collection $\textbf{f} = \{ f_{\alpha \beta} \ | \ \alpha \le \beta \in \kappa\}$ of u.s.c.
@@
 bonding function $f: [0,1] \rightarrow C([0,1])$.
-The main goal of this paper is to prove that if such an $f$ is not the identity map, then the inverse limit $\varprojlim \{[0,1], f, \kappa\}$ is metric exactly when the index set $\kappa$ is a countable ordinal.
+The main goal of this paper is to prove that if such an $f$ is not the identity and $\kappa$ is a nonzero ordinal, then the inverse limit $\varprojlim \{[0,1], f, \kappa\}$ is metric exactly when the index set $\kappa$ is countable.
 
@@
 Let $\Delta = \{\<a,a\> \ | \ a \in [0,1]\}$, and notice that $[0,1]^2 \setminus \Delta$ is the union of two disjoint open sets.
-Let $\iota$ be the identity map $\iota(x)=\{x\}$.
 
-\begin{lemma}
+\begin{lemma} \label{first lemma}
 If $f: [0,1] \rightarrow C([0,1])$ is u.s.c., then for some $x \in [0,1]$, $\<x,x\> \in G(f)$.
@@
 \begin{proof}
-By Lemma 1, for some $x \in [0,1]$, $\<x,x\> \in G(f)$. Suppose by way of contradiction that, for all $y \in [0,1]$ with $y \not= x$, $\<y,y\> \not\in G(f)$.
+By Lemma \ref{first lemma}, for some $x \in [0,1]$, $\<x,x\> \in G(f)$. Suppose by way of contradiction that, for all $y \in [0,1]$ with $y \not= x$, $\<y,y\> \not\in G(f)$.
 
@@
 
-Now consider $f(1)=[a,b]\subseteq(0,1)$. Then $f(f(1))=f([a,b])=[a,b]$, and in particular, $f(a)\subseteq[a,b]$. However, since $a\in(0,1]$, we also have $f(a)\subseteq(0,a)$, a contradiction.
+Now consider $f(1)=[a,b]\subseteq(0,1)$, where $a \le b$.
+(If $a = b$, then $[a,b] = \{a\}$ and the following argument will still apply.) Then $f(f(1))=f([a,b])=[a,b]$, and in particular, $f(a)\subseteq[a,b]$.
+However, since $a\in(0,1]$, we also have $f(a)\subseteq(0,a)$, a contradiction.
 
@@
 Likewise,  since $f(1) \subseteq [0,1)$, we have $f(z) \subseteq [0,z)$ for each $z \in (x,1]$; thus, $1 \not\in f((x,1])$.
-Since $f$ is surjective,
-$1\in f(v)$ for some $v\in[0,x]$ and $0\in f(w)$ for some $w\in[x,1]$. Let us say $f(v) = [k,1]$.
+Since $f$ is surjective, $1\in f(v)$ for some $v\in[0,x]$ and $0\in f(w)$ for some $w\in[x,1]$.
+If $f(v) = \{1\}$, then $f(f(v)) = f(\{1\}) = \{1\}$, which is a contradiction since $\<1,1\> \not\in G(f)$.
+So, let us say $f(v) = [k,1]$ for some $k < 1$.
 
@@
 
-So, $f(1) = [a,b]$ where $[a,b] \subseteq [0,x)$ or $[a,b] \subseteq (x,1)$.
+So, $f(1) = [a,b]$ for some $a \le b$, where $[a,b] \subseteq [0,x)$ or $[a,b] \subseteq (x,1)$.
 If $[a,b] \subseteq (x,1)$, then since $a > x$, $f(a) \subseteq [0,a)$ while $f(a)\subseteq f([a,b])=f(f(1))=f(1)=[a,b]$, contradiction.
@@
 
-\textbf{Case 1.} There exist $x<y$ in $[0,1]$ such that $\<x,x\>$ and $\<y,y\>$ are elements of $G(f)$ but $\<p,p\>$ is not for all $x<p<y$.
+\textbf{Case 1.} $G(f) \cap \Delta$ is not connected.
+Then there exist $x<y$ in $[0,1]$ such that $\<x,x\>$ and $\<y,y\>$ are elements of $G(f)$ but for all $p$ with $x < p < y$, $\< p, p \> \not\in G(f)$.
 
@@
 
-\textbf{Case 2.} There exists $[x,y]\subsetneq[0,1]$ with $x<y$ and $\<p,p\>\in G(f)$ exactly when $p\in[x,y]$.
+\textbf{Case 2.} $G(f) \cap \Delta$ is connected.
+Then there exists $[x,y]\subsetneq[0,1]$ with $x<y$ and $\<p,p\>\in G(f)$ exactly when $p\in[x,y]$.
 Since $\Delta$ is not a subset of $G(f)$, this means either $0 \not\in [x,y]$ or $1 \not\in [x,y]$.
@@
 \begin{lemma} \label{general lemma}
-If $f:[0,1] \to 2^{[0,1]}$ is u.s.c. and idempotent and $G(f)$ satisfies condition $\Gamma$, then $\varprojlim\{[0,1],f,\kappa\}$ contains a copy of $\kappa + 1$.
+Let $\kappa$ be a nonzero ordinal. If $f:[0,1] \to 2^{[0,1]}$ is u.s.c. and idempotent and $G(f)$ satisfies condition $\Gamma$, then $\varprojlim\{[0,1],f,\kappa\}$ contains a copy of $\kappa + 1$.
 \end{lemma}
@@
 \begin{theorem} \label{main theorem}
-If $f:[0,1]\to C([0,1])$ is u.s.c., idempotent, and surjective, but $f\not=\iota$, then $\varprojlim\{[0,1],f,\kappa\}$ contains a copy of $\kappa+1$.
+Let $\kappa$ be a nonzero ordinal. If $f:[0,1]\to C([0,1])$ is u.s.c., idempotent, and surjective, but $f\not=\iota$, then $\varprojlim\{[0,1],f,\kappa\}$ contains a copy of $\kappa+1$.
 \end{theorem}
@@
 \begin{corollary} \label{main corr}
-An inverse limit with a single u.s.c., idempotent, surjective bonding function $f: [0,1] \rightarrow C([0,1])$ and index set $\kappa$, an ordinal, is only metric (in fact, Corson compact) in the case that $\kappa$ is countable or the bonding map is trivial.
+An inverse limit with a single u.s.c., idempotent, surjective bonding function $f: [0,1] \rightarrow C([0,1])$ and index set $\kappa$, a nonzero ordinal, is only metric (in fact, Corson compact) in the case that $\kappa$ is countable or the bonding map is trivial.
 \end{corollary}
@@
 
-\begin{example} \label{ex1} Let $f: [0,1] \rightarrow C([0,1])$ be given by $f(0) = [0,1]$ and $f(x) = \{1\}$ for each $x \ne 0$.
-Then $\varprojlim \{ [0,1], f, \kappa \}$ is metric exactly when $\kappa$ is a countable ordinal.
+\begin{example} \label{ex1} Let $\kappa$ be a nonzero ordinal, and let $f: [0,1] \rightarrow C([0,1])$ be given by $f(0) = [0,1]$ and $f(x) = \{1\}$ for each $x \ne 0$.
+Then $\varprojlim \{ [0,1], f, \kappa \}$ is metric exactly when $\kappa$ is countable.
 \end{example}
@@
 
-The discussion of this example in \cite{varagona} implies that this inverse limit is homeomorphic to a metric arc whenever $\kappa$ is a limit ordinal satifying $0 < \kappa < \omega_1$, but homeomorphic to the compactified long line when $\kappa = \omega_1$.
+The discussion of this example in \cite{varagona} implies that this inverse limit is homeomorphic to $Y = (\kappa \times [0,1)) \cup \{\< \kappa, 0 \>\}$ (with the lexicographic order topology) whenever $\kappa$ is a nonzero limit ordinal.
+If $0 < \kappa < \omega_1$, $Y$ is a metric arc.
+However, when $\kappa = \omega_1$, $Y$ is the compactified long line, a non-metric space.
 \
@@
 
-\begin{example} \label{ex2} Let $f: [0,1] \rightarrow C([0,1])$ be given by $f(x) = \{x\}$ for $0 \le x < 1/2$ and $f(x) = 1/2$ for $x \ge 1/2$.
+\begin{example} \label{ex2} Let $f: [0,1] \rightarrow C([0,1])$ be given by $f(x) = \{x\}$ for $0 \le x < 1/2$ and $f(x) = \{1/2\}$ for $x \ge 1/2$.
 \end{example}
@@
 
-\bibitem{varagona} Scott Varagona, {\it Generalized Inverse Limits Indexed by Totally Ordered Sets}, preprint, 2015.
+\bibitem{varagona} Scott Varagona, {\it Generalized Inverse Limits Indexed by Totally Ordered Sets}, preprint (submitted to Topology Proceedings), 2015.
 

### 2015-09-17 articles/destroying-metrizability-in-generalized-inverse-limits/article.tex
mention nonempty compactness, connectedness for kappa=omega. elaborate on corson compactness

@@
 
+Ingram and Mahavier showed in \cite{i m paper} that $\varprojlim \{X_{\alpha}, f_{\alpha \beta}, \omega\}$ is non-empty and compact. They also found that
+if $f_{\alpha \beta}$ is always continuum-valued, then $\varprojlim \{X_{\alpha}, f_{\alpha \beta}, \omega\}$ is also connected, and therefore a Hausdorff continuum.
+Greenwood and Kennedy showed in \cite{greenwood kennedy} that there is a non-continuum-valued u.s.c.
+surjective idempotent bonding map $f$ for which $\varprojlim \{X_{\alpha}, f_{\alpha \beta}, \omega\}$ is disconnected.
+
 \section{Main Results}
@@
 
-Let us say a subset $S$ of $[0,1]^2$ satisfies condition $\Gamma$ if, for some $x, y \in [0,1]$ with $x \ne y$, $\<x,x\> \in S$, $\<y,y\> \in S$, and either $\<x,y\>$ or $\<y,x\> \in S$.
+Let us say a subset $S$ of $[0,1]^2$ satisfies condition $\Gamma$ if, for some $x, y \in [0,1]$ with $x \ne y$, $\<x,x\> \in S$, $\<y,y\> \in S$, and either $\<x,y\>$ or $\<y,x\> \in S$; see Figure \ref{conditionGamma}.
 Let $\Delta = \{\<a,a\> \ | \ a \in [0,1]\}$, and notice that $[0,1]^2 \setminus \Delta$ is the union of two disjoint open sets.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=\linewidth]{idempotent_usc_4.pdf}
+\end{center}
+\caption{Non-trivial u.s.c. surjections satisfying condition $\Gamma$}
+\label{conditionGamma}
+\end{figure}
 
@@
 
-A \textit{Corson compact} space is a compact space which embeds in a $\Sigma$-product of real lines (see \cite{alster}).
-All compact metric spaces are embeddable in $\mathbb R^\omega$ and therefore Corson compact.
+Note that when $\kappa\geq\omega_1$, $\omega_1\in\kappa+1$ is a point of non-first-countability; therefore any space containing $\kappa+1$ as a subspace is nonmetrizable.
+
+The presence of $\kappa+1$ prevents more than just metrizability, however.
+Let $\Sigma\mathbb R^\kappa\subseteq \mathbb R^\kappa$ denote the \textit{Sigma-product} of $\kappa$ copies of $\mathbb R$: the subspace for which each sequence has only countably many coordinates of nonzero value.
+A \textit{Corson compact} space is a compact space which embeds in $\Sigma\mathbb R^\kappa$ for some $\kappa$ (see \cite{alster}).
+
+All compact metric spaces are embeddable in $\mathbb R^\omega=\Sigma\mathbb R^\omega$ and therefore Corson compact.
+In addition, every closed subspace of a Corson compact is Corson compact.
+While $\Sigma\mathbb R^\kappa$ is not first-countable for $\kappa\geq\omega_1$, any subspace holds the weaker notion of being a $W$-space as defined by Gruenhage in \cite{gruenhage}.
+However, $\omega_1+1$ does not, as every countable sequence of ordinals less than $\omega_1$ is bounded above and therefore cannot converge to $\omega_1$ itself; therefore any space containing $\kappa+1$ for $\kappa\geq\omega_1$ cannot even be Corson compact.
 
@@
 So, suppose $f \ne \iota$.
-If $\kappa$ is countable, then because the inverse limit is a subspace of $[0,1]^{\kappa}$, it is metric.
-However, if $\kappa$ is uncountable, then by Theorem \ref{main theorem}, the inverse limit contains a copy of the non-Corson compact space $\kappa + 1$.
+If $\kappa$ is countable, then because the inverse limit is a subspace of $[0,1]^{\kappa}$, it is metrizable.
+However, if $\kappa$ is uncountable, then by Theorem \ref{main theorem}, the inverse limit contains a copy of $\kappa + 1$, preventing metrizability and Corson compactness.
 \end{proof}
@@
 However, when $\kappa = \omega_1$, $Y$ is the compactified long line, a non-metric space.
-\
 
@@
 166, (2014), 92-97.
+
+\smallskip
+
+\bibitem{greenwood kennedy} Greenwood, Sina and Kennedy, Judy, {\it Connected generalized inverse limits}, Topology and its Applications,
+159 (2012), no. 1, 57–68.
+
+\smallskip
+
+\bibitem{gruenhage} G. Gruenhage, {\it Infinite games and generalizations of first-countable spaces}, Gen. Topol. Appl., 6 (1976), pp. 339–352
 

### 2015-09-17 articles/destroying-metrizability-in-generalized-inverse-limits/article.tex
add reference generalizing kappa from omega, add note of open question about Gamma for non-continuum valued maps

@@
 if $f_{\alpha \beta}$ is always continuum-valued, then $\varprojlim \{X_{\alpha}, f_{\alpha \beta}, \omega\}$ is also connected, and therefore a Hausdorff continuum.
+Varagona generalized these results for other index sets (including ordinals $\kappa$) in Theorems 2.1 and 2.2 of \cite{varagona}.
 Greenwood and Kennedy showed in \cite{greenwood kennedy} that there is a non-continuum-valued u.s.c.
-surjective idempotent bonding map $f$ for which $\varprojlim \{X_{\alpha}, f_{\alpha \beta}, \omega\}$ is disconnected.
+surjective idempotent bonding map $f$ for which $\varprojlim \{X_{\alpha}, f, \omega\}$ is disconnected.
 
@@
 
-Let us say a subset $S$ of $[0,1]^2$ satisfies condition $\Gamma$ if, for some $x, y \in [0,1]$ with $x \ne y$, $\<x,x\> \in S$, $\<y,y\> \in S$, and either $\<x,y\>$ or $\<y,x\> \in S$; see Figure \ref{conditionGamma}.
+Let us say a subset $S$ of $[0,1]^2$ satisfies \textit{condition $\Gamma$} if, for some $x, y \in [0,1]$ with $x \ne y$, $\<x,x\> \in S$, $\<y,y\> \in S$, and either $\<x,y\>$ or $\<y,x\> \in S$; see Figure \ref{conditionGamma}.
 Let $\Delta = \{\<a,a\> \ | \ a \in [0,1]\}$, and notice that $[0,1]^2 \setminus \Delta$ is the union of two disjoint open sets.
@@
 \end{proof}
+
+Note that while we have assumed that $f:[0,1]\to C([0,1])$ (which also guarantees that the inverse limit is a continuum), it is an open question whether $\Gamma$ must also hold for any surjective idempotent u.s.c.
+$f:[0,1]\to 2^{[0,1]}$ (regardless if the inverse limit remains connected).
 

### 2015-09-22 articles/destroying-metrizability-in-generalized-inverse-limits/article.tex
scott's revisions

@@
 If a u.s.c.
-function $f: X \rightarrow 2^{Y}$ has the property that $f(x)$ is connected for each $x \in X$, then $f$ is \emph{continuum-valued}, and we denote this by writing  $f: X \rightarrow C(Y).$ The \emph{identity on} $X$ is the u.s.c.
+function $f: X \rightarrow 2^{Y}$ has the property that $f(x)$ is connected for each $x \in X$, then $f$ is \emph{continuum-valued}, and we denote this by writing  $f: X \rightarrow C(Y).$ The \emph{identity on} $X$ (also called the \emph{trivial} function on $X$) is the u.s.c.
 function $\iota$ given by $\iota(x) = \{x\}$ for all $x \in X$; we may simply say the \emph{identity} (or, more simply, $\iota$) when the space $X$ is understood from context.
@@
 If $X_{\alpha} = X$ for each $\alpha \in \kappa$ and $f_{\alpha \beta} = f$ for each $\alpha < \beta \in \kappa$, then $\{X_{\alpha}, f_{\alpha \beta}, \kappa\} = \{X, f, \kappa\}$ is an \emph{inverse limit system with the single bonding function $f$}, and we denote the inverse limit of the system as $\varprojlim \{X, f, \kappa\}$.
-(Of course, since $f$ is idempotent, the collection $\textbf{f}$ of bonding functions is automatically exact.) We note that, although the only continuous idempotent surjective function from a compact Hausdorff space $X$ to itself is the identity map, there are many non-trivial examples of u.s.c.
+(Of course, since $f$ is idempotent, the collection $\textbf{f}$ of bonding functions is automatically exact.) We note that, although the only continuous idempotent surjective function from a compact Hausdorff space $X$ to itself is the identity map, there are many nontrivial examples of u.s.c.
 idempotent surjective functions on $X$; see Figure \ref{idempotentUsc} for examples.
@@
 
-Ingram and Mahavier showed in \cite{i m paper} that $\varprojlim \{X_{\alpha}, f_{\alpha \beta}, \omega\}$ is non-empty and compact. They also found that
-if $f_{\alpha \beta}$ is always continuum-valued, then $\varprojlim \{X_{\alpha}, f_{\alpha \beta}, \omega\}$ is also connected, and therefore a Hausdorff continuum.
-Varagona generalized these results for other index sets (including ordinals $\kappa$) in Theorems 2.1 and 2.2 of \cite{varagona}.
-Greenwood and Kennedy showed in \cite{greenwood kennedy} that there is a non-continuum-valued u.s.c.
-surjective idempotent bonding map $f$ for which $\varprojlim \{X_{\alpha}, f, \omega\}$ is disconnected.
+By applying results by Ingram and Mahavier \cite{ingram mahavier} and by Charatonik and Roe \cite{char roe}, Varagona stated theorems (2.1 and 2.2 in \cite{varagona}) that imply $\varprojlim \{[0,1], f, \kappa\}$ is a continuum when $f$ is u.s.c., idempotent, and continuum-valued (and $\kappa > 0$).
+On the other hand, Greenwood and Kennedy showed in \cite{greenwood kennedy} that there is a non-continuum-valued u.s.c.
+surjective idempotent bonding function $f$ (with a connected graph) for which $\varprojlim \{[0,1], f, \omega\}$ is disconnected.
 
@@
 \end{center}
-\caption{Non-trivial u.s.c. surjections satisfying condition $\Gamma$}
+\caption{Idempotent u.s.c. functions with highlighted points illustrating condition $\Gamma$}
 \label{conditionGamma}
@@
 
-Note that while we have assumed that $f:[0,1]\to C([0,1])$ (which also guarantees that the inverse limit is a continuum), it is an open question whether $\Gamma$ must also hold for any surjective idempotent u.s.c.
-$f:[0,1]\to 2^{[0,1]}$ (regardless if the inverse limit remains connected).
+Note that while we have assumed that $f:[0,1]\to C([0,1])$ (which also guarantees that the inverse limit is a continuum), it is an open question whether $\Gamma$ must also hold for any nontrivial surjective idempotent u.s.c.
+$f:[0,1]\to 2^{[0,1]}$ (regardless of whether the inverse limit remains connected).
 
@@
 
-Note that when $\kappa\geq\omega_1$, $\omega_1\in\kappa+1$ is a point of non-first-countability; therefore any space containing $\kappa+1$ as a subspace is nonmetrizable.
+Note that when $\kappa\geq\omega_1$, $\omega_1\in\kappa+1$ is a point of non-first-countability; therefore, any space containing $\kappa+1$ as a subspace is nonmetrizable.
 
@@
 All compact metric spaces are embeddable in $\mathbb R^\omega=\Sigma\mathbb R^\omega$ and therefore Corson compact.
-In addition, every closed subspace of a Corson compact is Corson compact.
-While $\Sigma\mathbb R^\kappa$ is not first-countable for $\kappa\geq\omega_1$, any subspace holds the weaker notion of being a $W$-space as defined by Gruenhage in \cite{gruenhage}.
-However, $\omega_1+1$ does not, as every countable sequence of ordinals less than $\omega_1$ is bounded above and therefore cannot converge to $\omega_1$ itself; therefore any space containing $\kappa+1$ for $\kappa\geq\omega_1$ cannot even be Corson compact.
+In addition, every closed subspace of a Corson compact space is Corson compact.
+While $\Sigma\mathbb R^\kappa$ is not first-countable for $\kappa\geq\omega_1$, any subspace of $\Sigma\mathbb R^\kappa$ has the weaker property of being \textit{Fr\'echet-Urysohn}: each limit point of a set is converged to by a countable sequence in the set.
+However, $\omega_1+1$ is not Fr\'echet-Urysohn, as every countable sequence of ordinals less than $\omega_1$ is bounded above and therefore cannot converge to $\omega_1$ itself.
+Therefore, any space containing $\kappa+1$ for $\kappa\geq\omega_1$ cannot even be Corson compact.
 
@@
 \bibitem{greenwood kennedy} Greenwood, Sina and Kennedy, Judy, {\it Connected generalized inverse limits}, Topology and its Applications,
-159 (2012), no. 1, 57–68.
-
-\smallskip
-
-\bibitem{gruenhage} G. Gruenhage, {\it Infinite games and generalizations of first-countable spaces}, Gen. Topol. Appl., 6 (1976), pp. 339–352
+159 (2012), no. 1, 57-68.
 

### 2015-09-23 todo.tex
man these are out of date, but not gonna fix them today

--- 2014-01-20 todo.tex
@@
-\input{header.tex}
+\input{header}
 
@@
   \begin{itemize}
-    \item Menger/Rothberger properties and games results
-      \begin{itemize}
-        \item Is there a slick characterization of $F\kmarkwin{2}\mengame{X}$ for regular/general spaces?
-        \item Is $F\uparrow_{?}\mengame{X}$ or $F\uparrow_{?}\rothgame{X}$ a hereditary property under closed subsets for any type of limited information? (The Menger property is; is Rothberger?)
-        \item Investigate Markov strategies for $S$ in $\rothgame{X}$ or $P$ in $\altrothgame{X}$.
-        \item $S\kmarkwin{2}\rothgame{X}\Leftrightarrow S\kmarkwin{k}\rothgame{X}$?
-        \item $S\kmarkwin{2}\rothgame{\oneptcomp{\omega_1}}$ or $S\kmarkwin{2}\rothgame{\oneptlind{\omega_1}}$?
-        \item $F\kmarkwin{k}\kfillgame{\kappa} \Rightarrow F\kmarkwin{k}\mengame{\oneptlind{\kappa}}$?
-        \item Would Lindelof scattered spaces have a $2$-Markov strategy in the Menger game?
-      \end{itemize}
-    \item Filling games
-      \begin{itemize}
-        \item Show/disprove $F\ktactwin{3}\sfillgame{J}$ implies $F\kmarkwin{3}\fillgame{J}$.
-        \item Show/disprove $F\kmarkwin{2}\mengame{\oneptlind{\kappa}}$ implies $F\kmarkwin{2}\kfillgame{\kappa}$.
-      \end{itemize}
-    \item Search for a class of spaces where $K\ktactwin{2}\lfkpgame{X}$ characterizes metacompact (aka implies $K\tactwin\lfkpgame{X}$)
-      \begin{itemize}
-        \item Investigate the ladder space suggested by G.
-        \item Try zero-dimensional.
-      \end{itemize}
-    \item Proximity Game
-      \begin{itemize}
-        \item Question: predetermined strategy for D on abs. proxmial space, does that imply predetermined strategy for O in con(X,H) for H compact.
-        \item Is proximal game properties preserved under perfect maps? Or, compact proximal preserved under continuous.
-        \item Alexandrof duplicate of unit interval: EC, not metrizable, what about Markov proximal?
-      \end{itemize}
+    \item write these TODOs
   \end{itemize}

### 2015-09-23 articles/applications-of-limited-information-strategies-in-mengers-game/article.tex
fix section title
polish paper, missing citation for 4.3 and intro/abstr

@@
 
-Note that many authors refer to this property as \(S_{fin}(\mc O,\mc O)\),
+Note that many authors refer to this property as \(S_{fin}(\mc O,\mc O)\)
+\cite{MR1378387},
 where \(\mc O\) is the collection of open covers of \(X\), and
@@
 finite subsets \(\mc F_n\)
-of \(\mc U_n\) instead (and often refer to it as \(G(\mc O,\mc O)\) as
-with the selection property above).
+of \(\mc U_n\) instead (and often refer to it as the selection game
+\(G_{fin}(\mc O,\mc O)\)).
 This is obviously equivalent in the case of perfect
@@
 
+It's worth noting that the above proof holds for any selection game of
+the form \(G_{fin}(A,B)\).
+
 A natural question arises: is there an example of a space \(X\) for which
@@
 
-\begin{proposition}
-  \(\pl F \notmarkwin \menGame{\oneptlind{\omega_1}}\); in fact,
-  \(\oneptlind{\omega_1}\) is not \(\sigma\)-compact.
-\end{proposition}
+One may prove directly that
+  \(\pl F \notmarkwin \menGame{\oneptlind{\omega_1}}\)
+without much effort; however, we postpone stating this until we have
+shown that being Markov Menger is equivalent to being \(\sigma\)-compact
+in regular spaces.
 
@@
 ability to react to changes from one round to the next. It's this ability to
-react that will give \(\pl F\) her winning \(2\)-Markov strategy in the Menger
-game on \(\oneptlind\omega_1\). This may be proven directly; however, we will
-postpone giving a proof so that we may take advantage of an equivalent
-game characterization of this property.
+react that often allows a player to wield a winning \(2\)-Markov strategy when
+a winning \(1\)-Markov strategy does not exist.
 
@@
 Scheeper's original filling game, Scheepers introduced the statement
-\(\alcompS\kappa\) relating to the almost-compatability of functions
+\(\alcompS\kappa\) relating to the almost-compatability of injective functions
 from countable subsets of \(\kappa\) into \(\omega\) which may be applied to
@@
 \begin{definition}
-  \(\alcompS\kappa\) states that there exist functions
+  \(\alcompS\kappa\) states that there exist injective functions
   \(f_A:A\to\omega\) for each \(A\in[\kappa]^{\leq\omega}\) such that
-  \(|\{\alpha\in A:f_A(\alpha)\leq n\}|<\omega\) for all \(n<\omega\) and
   \(f_A\alcomp f_B\) for all \(A,B\in[\kappa]^\omega\).
-  \footnote{
-  This is equivalent to the original characterization given in
-  \cite{MR1129143}: there exist injections \(g_A:A\to\omega\)
-  such that \(g_A\alcomp g_B\) for all \(A,B\in[\kappa]^\omega\) and \(A\subset B\).
-  }
 \end{definition}
@@
      2\text{-Markov Menger} &
-     \text{Perfect Menger} &
+     \text{Strategic Menger} &
      \text{Menger} \\
@@
 by Telgarksy in \cite{MR753073} and later directly by Scheepers in
-\cite{MR1273523}.
+\cite{MR1273523}. It's Scheepers' technique which gives inspiration to
+the following.
 
@@
 
+%TODO cite source?
+
 \begin{lemma}
   Let \(\sigma(\mc{U}, n)\) be a Markov strategy for \(F\) in
-  \(\menGame{X}\), and \(\mathfrak{C}\) collect all open covers of \(X\). Then the
+  \(\menGame{X}\), and \(\mc{O}\) collect all open covers of \(X\). Then the
   set
     \[
-      R_n = \bigcap_{\mc{U}\in\mathfrak{C}} \sigma(\mc{U},n)
+      R_n = \bigcap_{\mc{U}\in\mc{O}} \sigma(\mc{U},n)
     \]
@@
 \begin{proof}
-  First, for every open cover \(\mc U\in\mathfrak C\),
+  First, for every open cover \(\mc U\in\mc{O}\),
   \(R_n\subseteq\sigma(\mc U,n)\) is covered by a finite subcollection of \(\mc U\).
@@
   Suppose that \(x \not\in R_n\) for any \(n<\omega\). Then for each \(n\),
-  pick \(\mc{U}_n\in\mathfrak{C}\) such that \(x\not\in \sigma(\mc{U}_n,n)\). Then
+  pick \(\mc{U}_n\in\mc{O}\) such that \(x\not\in \sigma(\mc{U}_n,n)\). Then
   \(\pl C\) may counter \(\sigma\) with the attack \(\<\mc U_0,\mc U_1,\dots\>\).
@@
 
-For Lindel\"of spaces, metrizability is characterized by regularity and
-second-countability, the latter of which was essentially used by Scheepers in
-this way:
+\begin{corollary}
+  \(\pl F\notmarkwin\menGame{\oneptlind{\omega_1}}\).
+\end{corollary}
+
+Note that for Lindel\"of spaces, metrizability is characterized by regularity
+and second-countability.
 
@@
 
-  Let \(t:\omega\to\omega^{<\omega}\) be a bijection. We define the Mark\"ov
+  Let \(t:\omega\to\omega^{<\omega}\) be a bijection. We define the Markov
   strategy \(\tau\) as follows:
@@
 
-\section{Robustly Lindel\"of}
+\section{Robustly Menger}
 
@@
 We will soon see that, assuming \(\alcompS{\mf c}\), \(\pl F\) has a winning
-\(2\)-Mark\"ov strategy for \(\menGame{R_\omega}\) as well.
+\(2\)-Markov strategy for \(\menGame{R_\omega}\) as well.
 
 \begin{proposition}
-  If \(X=\bigcup_{i<\omega} X_i\) and \(\pl F \kmarkwin{k} \menGame{X,X_i}\)
-  for \(i<\omega\), then \(\pl F \kmarkwin{k} \menGame{X}\)
+  If \(X=\bigcup_{i<\omega} X_i\) and \(\pl F \kmarkwin{2} \menGame{X,X_i}\)
+  for \(i<\omega\), then \(\pl F \kmarkwin{2} \menGame{X}\)
 \end{proposition}
@@
 \begin{proof}
-  Let \(\sigma_i\) be a \(k\)-Markov strategy
+  Let \(\sigma_i\) be a \(2\)-Markov strategy
   for \(\pl F\) in \(\menGame{X,X_i}\).
 
-  We define the \(k\)-Markov strategy
+  We define the \(2\)-Markov strategy
   \(\sigma\) for \(\menGame{X}\) as follows:
     \[
-      \sigma(\<\mc U_0,\dots,\mc U_n\>)
+      \sigma(\<\mc U\>,0) = \sigma_0(\<\mc U\>,0)
+    \]
+    \[
+      \sigma(\<\mc U,\mc V\>,n+1)
         =
-      \bigcup_{i\leq n}
-      \sigma_i(\<\mc U_i,\dots,\mc U_n\>)
+      \bigcup_{i,j\leq n}
+      \sigma_i(\<\mc V\>,0)
+        \cup
+      \sigma_i(\<\mc U,\mc V\>,j+1)
     \]
@@
   against \(\sigma\). Then there exists \(x\in X_i\) for
-  some \(i<\omega\) such that \(x\) is not covered by
-  \(\bigcup_{n<\omega}\sigma(\<\mc U_0,\dots,\mc U_n\>)\).
-  It follows that \(x\) is not covered by
-  \(\bigcup_{n<\omega}\sigma_i(\<\mc U_i,\dots,\mc U_{i+n}\>)\),
+  some \(i<\omega\) such that \(x\) is not contained in
+  \[
+    \sigma(\<\mc U_0\>,0)
+      \cup
+    \bigcup_{n<\omega}
+    \sigma(\<\mc U_n,\mc U_{n+1}\>,n+1)
+  \]
+  It then follows that \(x\) is not contained in
+  \[
+    \sigma_i(\<\mc U_i\>,0)
+      \cup
+    \bigcup_{n<\omega}
+    \sigma_i(\<\mc U_{i+n},\mc U_{i+n+1}\>,n+1)
+  \]
   and \(\<\mc U_i,\mc U_{i+1},\dots\>\) is a successful counter-attack
@@
 
+The following is left open:
+
+\begin{question}
+  Does there exist a space which is \(2\)-Markov Menger, but not
+  robustly Menger?
+\end{question}
+
+\section*{Acknowlegements}
+
+The author wishes to thank Gary Gruenhage and Alan Dow for their
+very useful comments during the writing of this paper.
+
 \bibliographystyle{plain}

### 2015-09-25 articles/applications-of-limited-information-strategies-in-mengers-game/article.tex
finished except for abstract/intro

@@
 \begin{definition}
-  A subset \(Y\) of \(X\) is \term{relatively compact} to \(X\) if for every open
+  A subset \(Y\) of \(X\) is \term{relatively compact} to \(X\), or
+  \(Y\) is \term{compact in} \(X\), if for every open
   cover of \(X\), there exists a finite subcollection which covers \(Y\).
 \end{definition}
+
+\begin{definition}
+  A subset \(Y\) of \(X\) is \term{precompact} in \(X\) if
+  \(\text{cl}_X(Y)\) is compact.
+\end{definition}
+
+Some authors use the term
+relative compactness to denote precompactness, which causes
+no confusion in the context of regular spaces.
 
@@
   For regular spaces, \(Y\) is relatively compact to \(X\) if and only if
-  \(\cl Y\) is compact in \(X\).
+  \(Y\) is precompact in \(X\).
 \end{proposition}
 
-%TODO cite source?
+\begin{proof}
+  Shown by Arhangel'skii in \cite{MR1885790}; a proof is provided for the
+  convenience of the reader.
+
+  Let \(\mc U=\{U_\alpha:\alpha<\kappa\}\) be an
+  open cover of \(\text{cl}_X(Y)\); for \(y\in Y\), apply regularity to get
+  \(V_\alpha\subseteq\text{cl}_X(V_\alpha)\subseteq U_\alpha\)
+  with \(V_\alpha\) open.
+  Use relative compactness to obtain a finite subcollection of
+  \(\{X\setminus\text{cl}_X(Y)\}\cup\{V_\alpha:\alpha<\kappa\}\)
+  covering \(Y\): \(\{V_{\alpha_i}:i<n\}\). Then since
+  \(\bigcup\{\text{cl}_X(V_{\alpha_i}):i<n\}\) is a closed set in \(X\)
+  containing \(Y\), it contains \(\text{cl}_X(Y)\), and thus
+  \(\{U_{\alpha_i}:i<n\}\) is a finite subcollection of \(\mc U\) covering
+  \(\text{cl}_X(Y)\).
+
+  For the reverse direction, simply take a finite subcover of
+  \(\text{cl}_X(Y)\) to obtain a finite subcover of \(Y\).
+\end{proof}
 
@@
 
-\begin{theorem}[\(\alcompS{\mf c}\)]
+\begin{theorem}
+  Assuming \(CH\) or just \(\alcompS{\mf c}\),
   \(\pl F\kmarkwin2\menGame{R_\omega}\).

### 2015-09-25 articles/applications-of-limited-information-strategies-in-mengers-game/article.tex
preprint ready to rock

@@
 \begin{abstract}
-  I need an abstract
+  As shown by Telgarsky and Scheepers,
+  winning strategies in the Menger game characterize
+  \(\sigma\)-compactness amongst metrizable spaces. This is improved
+  by showing that winning Markov strategies in the Menger game
+  characterize \(\sigma\)-compactness amongst
+  regular spaces, and that winning strategies may be improved to winning
+  Markov strategies in second-countable spaces.
+  An investigation of
+  \(2\)-Markov strategies introduces a new topological property between
+  \(\sigma\)-compact and Menger spaces.
 \end{abstract}
@@
 
-I require an introduction.
-
 \section{The Menger property and game}
-
-Recall the following definition.
 
@@
 
-Recall the following definitions.
-
 \begin{definition}
@@
 
-A natural question arises: is there an example of a space \(X\) for which
-\(\pl F\kmarkwin{2}\menGame{X}\) but \(\pl F\notmarkwin\menGame{X}\)? We quickly
-see that perhaps the simplest example of a Lindel\"of non-\(\sigma\)-compact
-space has this property.
+One might wonder if a \(2\)-mark may always be improved to a \(1\)-mark
+as well; this is not the case.
 
@@
 shown that being Markov Menger is equivalent to being \(\sigma\)-compact
-in regular spaces.
-
-The greatest advantage of a strategy which has knowledge of two or more previous
+in regular spaces. Likewise, we postpone proving
+  \(\pl F \kmarkwin2 \menGame{\oneptlind{\omega_1}}\)
+in order to consider an equivalent set-theoretic game.
+
+Essentially,
+the greatest advantage of a strategy which has knowledge of two or more previous
 moves of the opponent, versus only knowledge of the most recent move, is the
@@
 
-\section{Scheepers' filling games}
+\section{Scheepers' countable-finite games}
 
@@
   Let \(\schFillStrictGame\kappa\) denote
-  \term{Scheepers' strict union filling game}
+  \term{Scheepers' strict countable-finite union game}
   with two players \(\pl C\), \(\pl F\). In round \(0\), \(\pl C\) chooses
@@
   Let \(\schFillGame\kappa\) denote the
-  \term{union filling game} which proceeds analogously
+  \term{Scheepers countable-finite union game} which proceeds analogously
   to \(\schFillStrictGame\kappa\), except that \(\pl C\)'s restriction in round \(n+1\)
@@
   Let \(\schFillInitialGame\kappa\) denote the
-  \term{initial filling game} which proceeds analogously
+  \term{Scheepers countable-finite initial game} which proceeds analogously
   to \(\schFillGame\kappa\), except that \(\pl F\) wins whenever
@@
   Let \(\schFillIntGame\kappa\) denote the
-  \term{intersection filling game} which proceeds analogously
+  \term{Scheepers countable-finite intersection game} which proceeds analogously
   to \(\schFillInitialGame\kappa\), except that \(\pl C\) may choose any
@@
 \caption{Diagram of Scheepers/Menger game implications}
-\label{fillingGamesDiagram}
+\label{GamesDiagram}
 \end{figure}
@@
 For any cardinal \(\kappa\geq\omega\) and integer \(k<\omega\),
-Figure \ref{fillingGamesDiagram} holds.
+Figure \ref{GamesDiagram} holds.
 \end{theorem}
@@
 While we have not shown a direct implication between the Menger game and
-Scheeper's original filling game, Scheepers introduced the statement
+Scheeper's original countable-finite game, Scheepers introduced the statement
 \(\alcompS\kappa\) relating to the almost-compatability of injective functions
@@
 \end{center}
-\caption{Diagram of Filling/Menger game implications with \(\alcompS\kappa\)}
-\label{fillingGamesDiagram2}
+\caption{Diagram of Scheeper/Menger game implications with \(\alcompS\kappa\)}
+\label{GamesDiagram2}
 \end{figure}
@@
   \(\alcompS\kappa\) implies the game-theoretic results in
-  Figure \ref{fillingGamesDiagram2}.
+  Figure \ref{GamesDiagram2}.
 \end{theorem}
@@
 
-Note that while it's consistent that
-\(\pl F\kmarkwin2\menGame{\oneptlind{\mf c}}\), \(\oneptlind{\kappa}\)
-for \(\kappa>\mf c\) is a candidate to answer the above question.
-
 We are also interested in non-game-theoretic characterizations of these
-covering properties. It has been known for some time that metrizable perfect
+covering properties. It has been known for some time that metrizable strategic
 Menger spaces are exactly the metrizable \(\sigma\)-compact spaces, shown first
@@
 
-To help describe \(\pl F\kmarkwin2\menGame{X}\) topologically, we introduce a
+To help instigate the topological property \(\pl F\kmarkwin2\menGame{X}\),
+we introduce a
 slight variant of the Menger game and a related covering property.
@@
   analogously to the Menger game, except that \(\pl F\) wins whenever
-  \(\bigcup_{n<\omega} \mc F_n\) is a cover for \(Y\subseteq X\).
+  \(Y\subseteq\bigcup_{n<\omega} F_n\).
 \end{game}
@@
   \(\alcompS\kappa\) implies \(\oneptlind\kappa\) is
-  robustly Menger, and thus
-  \(\pl F\kmarkwin2\menGame{\oneptlind\kappa}\).
+  robustly Menger.
 \end{theorem}
@@
 \begin{question}
-  Does there exist a space which is \(2\)-Markov Menger, but not
+  Are all \(2\)-Markov Menger spaces
   robustly Menger?

### 2015-10-07 postdoctoral/S_prime_kappa.tex
add nearly complete omega_2 proof

@@
     \(S'(\kappa)\) requiring finite-to-one maps. Dow suggests that
-    \(S'(\omega_2)\) holds in ZFC. Here's my writeup of his argument.
+    \(S'(\omega_\omega)\) holds in ZFC by the following.
   \end{remark}
@@
 
-  \begin{claim*}
-    There exists a topology on \(\omega_2\) which is locally countable
-    and \(\aleph_0\)-bounded.
-  \end{claim*}
-
-  \begin{proposition}
-    A space which is locally countable and \(\omega\)-bounded is also
-    locally compact, locally second-countable, and scattered.
-  \end{proposition}
+  \begin{theorem}
+    There exists a topology on \(\omega_2\) which
+    is \(\omega\)-bounded, locally compact, and locally countable.
+  \end{theorem}
 
   \begin{proof}
-    A countable neighborhood has compact closure by \(\omega\)-boundedness,
-    which gives local compactness.
+    Note that the natural linear order on \(\omega_1\) induces such
+    a topology for it.
 
-    By local countability, we have local secound-countability.
+    Let \(\alpha<\omega_2\), and suppose we've defined compatible topologies on
+    \(\omega_1\cdot (\beta+1)\) for all \(0\leq\beta<\alpha\).
+    If \(\alpha=\beta+1\), then let
+    \(\omega_1\cdot(\alpha+1)=\omega_1\cdot(\beta+2)\) be the topological sum
+    of the previously defined \(\omega_1\cdot(\beta+1)\) and the linear order
+    on \(\omega_1\cdot(\beta+2)\setminus\omega_1\cdot(\beta+1)\cong\omega_1\).
+    Similarly, if \(cf(\alpha)>\omega\), then let \(\omega_1\cdot(\alpha+1)\)
+    be the topological sum of \(\bigcup_{\beta<\alpha}\omega_1\cdot(\beta+1)\)
+    and the linear order on
+    \(\omega_1\cdot(\alpha+1)\setminus\omega_1\cdot\alpha\cong\omega_1\).
 
-    TODO: figure out trick to get scattered.
+    The remaining case is where \(\alpha\) is the limit of increasing
+    \(\alpha_n\) for \(n<\omega\). Fix a bijection
+    \(
+      f_\alpha
+        :
+      \omega_1\cdot(\alpha+1)\setminus\omega_1\cdot\alpha
+        \to
+      \omega_1\cdot\alpha
+    \). Points in \(\omega_1\cdot(\alpha_n+1)\) for some \(n<\omega\)
+    have their usual base induced by that previously defined topology. So let
+    \(\gamma\in\omega_1\cdot(\alpha+1)\setminus\omega_1\cdot\alpha\).
+    Basic open neighborhoods of \(\gamma\) are of the form
+    \(
+      [\gamma',\gamma]
+        \cup
+      f_\alpha[[\omega_1\cdot\alpha,\gamma]]
+        \setminus
+      \omega_1\cdot(\alpha_n+1)
+    \),
+    where \(\omega_1\cdot\alpha\leq\gamma'<\gamma\)
+    and \(n<\omega\).
+
+    We wish to show that \(\omega_2\) with the topology induced by
+    \(\bigcup_{\alpha<\omega_2}\omega_1\cdot(\alpha+1)\) is \(\omega\)-bounded,
+    locally compact, and locally countable. If
+    \(\gamma\in\omega_1\cdot(\alpha+1)\setminus\omega_1\cdot\alpha\) where
+    \(cf(\alpha)\not=\omega\), then we immediately see that it is in a clopen
+    copy of \(\omega_1\) giving us local compactness and local countability
+    immediately. Otherwise, \(\gamma\) has a basic open neighborhood of the form
+    \(
+      [\gamma',\gamma]
+        \cup
+      f_\alpha[[\omega_1\cdot\alpha,\gamma]]
+        \setminus
+      \omega_1\cdot(\alpha_n+1)
+    \),
+    which is obviously countable. Likewise, its closure is compact:
+    the closure operation does not add any ordinals greater than \(\gamma\),
+    and any open cover
+    contains another basic open neighborhood of \(\gamma\) such as
+    \(
+      [\gamma'',\gamma]
+        \cup
+      f_\alpha[[\omega_1\cdot\alpha,\gamma]]
+        \setminus
+      \omega_1\cdot(\alpha_m+1)
+    \)
+    which misses only the compact set \([\gamma',\gamma'']\) and the
+    closure of the countable set
+    \(
+      f_\alpha[[\omega_1\cdot\alpha,\gamma]]
+        \cap
+      \omega_1\cdot(\alpha_{\min(m,n)}+1)
+    \), which will be proven to be compact once we show that
+    \(\omega_1\cdot(\alpha+1)\) is \(\omega\)-bounded for all
+    \(\alpha<\omega_2\). This also will show that \(\omega_2\) with our
+    topology is itself \(\omega\)-compact, finishing the proof.
+
   \end{proof}
@@
   \begin{theorem*}
-    \(S'(\omega_2)\).
+    \(S'(\omega_\omega)\).
   \end{theorem*}
 
-  \begin{proof}
-    For \(\alpha<\omega_2\), let \(W_\alpha\) be the
-    intersection of a countable and compact neighborhood in the claimed topology
-    on \(\omega_2\).
-  \end{proof}
-
 \end{document}

### 2015-10-07 postdoctoral/S_prime_kappa.tex
proof for omega_2

@@
     There exists a topology on \(\omega_2\) which
-    is \(\omega\)-bounded, locally compact, and locally countable.
+    is \(\omega\)-bounded and locally countable.
   \end{theorem}
@@
     We wish to show that \(\omega_2\) with the topology induced by
-    \(\bigcup_{\alpha<\omega_2}\omega_1\cdot(\alpha+1)\) is \(\omega\)-bounded,
-    locally compact, and locally countable. If
+    \(\bigcup_{\alpha<\omega_2}\omega_1\cdot(\alpha+1)\) is \(\omega\)-bounded
+    and locally countable. If
     \(\gamma\in\omega_1\cdot(\alpha+1)\setminus\omega_1\cdot\alpha\) where
     \(cf(\alpha)\not=\omega\), then we immediately see that it is in a clopen
-    copy of \(\omega_1\) giving us local compactness and local countability
+    copy of \(\omega_1\) giving us local countability
     immediately. Otherwise, \(\gamma\) has a basic open neighborhood of the form
@@
     \),
-    which is obviously countable. Likewise, its closure is compact:
+    which is obviously countable.
+
+    Let \(C\) be a countable subset of \(\omega_1\cdot(\alpha+1)\).
+    In the case that \(\alpha=\beta+1\), we may use the \(\omega\)-boundedness
+    of each part in the clopen partition \(\omega_1\cdot(\beta+1)\) and
+    \(\omega_1\cdot(\beta+2)\setminus\omega_1\cdot(\beta+1)\cong\omega_1\)
+    to conclude that the closure of \(C\) is compact.
+    Similarly, if \(cf(\alpha)>\omega\),
+    then we may use the  \(\omega\)-boundedness
+    of each part in the clopen partition
+    \(\bigcup_{\beta<\alpha}\omega_1\cdot(\beta+1)\) and
+    \(\omega_1\cdot(\alpha+1)\setminus\omega_1\cdot\alpha\cong\omega_1\)
+    to conclude that the closure of \(C\) is compact.
+
+    The remaining case is again where \(\alpha\) is the limit of increasing
+    \(\alpha_n\) for \(n<\omega\). Then
+    \(
+      C
+        \subseteq
+      [\gamma',\gamma]
+        \cup
+      f_\alpha[[\omega_1\cdot\alpha,\gamma]]
+    \)
+    for some \(\omega_1\cdot\alpha\leq\gamma'<\gamma<\omega_1\cdot(\alpha+1)\).
+    Its closure is compact:
     the closure operation does not add any ordinals greater than \(\gamma\),
@@
       \omega_1\cdot(\alpha_{\min(m,n)}+1)
-    \), which will be proven to be compact once we show that
-    \(\omega_1\cdot(\alpha+1)\) is \(\omega\)-bounded for all
-    \(\alpha<\omega_2\). This also will show that \(\omega_2\) with our
-    topology is itself \(\omega\)-compact, finishing the proof.
+    \), which is compact by the \(\omega\)-boundedness of
+    \(\omega_1\cdot(\alpha_{\min(m,n)}+1)\).
 
+    Finally, since every countable subset of \(\omega_2\) is contained in
+    some \(\omega_1\cdot(\alpha+1)\), we conclude \(\omega_2\) is
+    \(\omega\)-bounded.
   \end{proof}
@@
   \begin{theorem*}
-    \(S'(\omega_\omega)\).
+    \(S'(\omega_2)\).
   \end{theorem*}

### 2015-10-08 postdoctoral/S_prime_kappa.tex
incomplete kappa_n generalization

--- 2015-09-01 postdoctoral/S_prime_kappa.tex
@@
 
-  \begin{claim*}
-    There exists a topology on \(\omega_2\) which is locally countable
-    and \(\aleph_0\)-bounded.
-  \end{claim*}
-
-  \begin{proposition}
-    A space which is locally countable and \(\omega\)-bounded is also
-    locally compact, locally second-countable, and scattered.
-  \end{proposition}
+  \begin{theorem}
+    For each \(k<\omega\) there exists a topology on \(\omega_k\) which
+    is \(\omega\)-bounded and locally countable.
+  \end{theorem}
 
   \begin{proof}
-    A countable neighborhood has compact closure by \(\omega\)-boundedness,
-    which gives local compactness.
+    Assume we've defined such a topology for \(\omega_k\)
+    such that \(\gamma+1=[0,\gamma]\) is clopen for all \(\gamma<\omega_k\).
+    Note that the usual linear order on \(\omega_1\) satisfies these requirements.
 
-    By local countability, we have local secound-countability.
+    Let \(\alpha<\omega_{k+1}\), and suppose we've defined compatible topologies on
+    \(\omega_k\cdot (\beta+1)\) for all \(0\leq\beta<\alpha\).
+    If \(\alpha=\beta+1\), then let
+    \(\omega_k\cdot(\alpha+1)=\omega_k\cdot(\beta+2)\) be the topological sum
+    of the previously defined \(\omega_k\cdot(\beta+1)\) and the
+    previously defined
+    \(\omega_k\cdot(\beta+2)\setminus\omega_k\cdot(\beta+1)\cong\omega_k\).
+    Similarly, if \(cf(\alpha)>\omega\), then let \(\omega_k\cdot(\alpha+1)\)
+    be the topological sum of \(\bigcup_{\beta<\alpha}\omega_k\cdot(\beta+1)\)
+    and the previously defined
+    \(\omega_k\cdot(\alpha+1)\setminus\omega_k\cdot\alpha\cong\omega_k\).
 
-    TODO: figure out trick to get scattered.
+    The remaining case is where \(\alpha\) is the limit of increasing
+    \(\alpha_n\) for \(n<\omega\). Fix a bijection
+    \(
+      f_\alpha
+        :
+      \omega_k\cdot(\alpha+1)\setminus\omega_k\cdot\alpha
+        \to
+      \omega_k\cdot\alpha
+    \). Points in \(\omega_k\cdot(\alpha_n+1)\) for some \(n<\omega\)
+    have their usual base induced by that previously defined topology. So let
+    \(\gamma\in\omega_k\cdot(\alpha+1)\setminus\omega_k\cdot\alpha\).
+    Basic open neighborhoods of \(\gamma\) are of the form
+    \(
+      W
+        \cup
+      f_\alpha[W]
+        \setminus
+      \omega_k\cdot(\alpha_n+1)
+    \),
+    where \(n<\omega\) and
+    \(W\subseteq\gamma+1\) is any countable neighborhood of \(\gamma\).
+
+    We wish to show that \(\omega_{k+1}\) with the topology induced by
+    \(\bigcup_{\alpha<\omega_{k+1}}\omega_k\cdot(\alpha+1)\) is \(\omega\)-bounded
+    and locally countable. If
+    \(\gamma\in\omega_k\cdot(\alpha+1)\setminus\omega_k\cdot\alpha\) where
+    \(cf(\alpha)\not=\omega\), then we immediately see that it is in a clopen
+    copy of \(\omega_k\) giving us local countability
+    immediately. Otherwise, \(\gamma\) has a basic open neighborhood of the form
+    \(
+      W
+        \cup
+      f_\alpha[W]
+        \setminus
+      \omega_k\cdot(\alpha_n+1)
+    \),
+    which is obviously countable.
+
+    Let \(C\) be a countable subset of \(\omega_k\cdot(\alpha+1)\).
+    In the case that \(\alpha=\beta+1\), we may use the \(\omega\)-boundedness
+    of each part in the clopen partition \(\omega_k\cdot(\beta+1)\) and
+    \(\omega_k\cdot(\beta+2)\setminus\omega_k\cdot(\beta+1)\cong\omega_k\)
+    to conclude that the closure of \(C\) is compact.
+    Similarly, if \(cf(\alpha)>\omega\),
+    then we may use the  \(\omega\)-boundedness
+    of each part in the clopen partition
+    \(\bigcup_{\beta<\alpha}\omega_k\cdot(\beta+1)\) and
+    \(\omega_k\cdot(\alpha+1)\setminus\omega_k\cdot\alpha\cong\omega_k\)
+    to conclude that the closure of \(C\) is compact.
+
+    The remaining case is again where \(\alpha\) is the limit of increasing
+    \(\alpha_n\) for \(n<\omega\). Then
+    TODO: generalize for \(k+1\)
+    % \(
+    %   C
+    %     \subseteq
+    %   [\gamma',\gamma]
+    %     \cup
+    %   f_\alpha[[\omega_k\cdot\alpha,\gamma]]
+    % \)
+    % for some \(\omega_k\cdot\alpha\leq\gamma'<\gamma<\omega_k\cdot(\alpha+1)\).
+    % Its closure is compact:
+    % the closure operation does not add any ordinals greater than \(\gamma\),
+    % and any open cover
+    % contains another basic open neighborhood of \(\gamma\) such as
+    % \(
+    %   [\gamma'',\gamma]
+    %     \cup
+    %   f_\alpha[[\omega_k\cdot\alpha,\gamma]]
+    %     \setminus
+    %   \omega_k\cdot(\alpha_m+1)
+    % \)
+    % which misses only the compact set \([\gamma',\gamma'']\) and the
+    % closure of the countable set
+    % \(
+    %   f_\alpha[[\omega_k\cdot\alpha,\gamma]]
+    %     \cap
+    %   \omega_k\cdot(\alpha_{\min(m,n)}+1)
+    % \), which is compact by the \(\omega\)-boundedness of
+    % \(\omega_k\cdot(\alpha_{\min(m,n)}+1)\).
+
+    Finally, since every countable subset of \(\omega_{k+1}\) is contained in
+    some \(\omega_k\cdot(\alpha+1)\), we conclude \(\omega_{k+1}\) is
+    \(\omega\)-bounded.
   \end{proof}

### 2015-10-16 articles/zero-markov-information-in-a-topological-game/article.tex
add zero-mark paper

\documentclass{amsart}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}

\usepackage{graphicx}

\usepackage{../../clontzDefinitions}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{game}[theorem]{Game}
\newtheorem{example}[theorem]{Example}
\newtheorem{question}[theorem]{Question}

\begin{document}

% \title{Proximal compact spaces are Corson compact\tnoteref{t1}}
% \tnotetext[t1]{2010 Mathematics Subject Classification. 54E15, 54D30, 54A20.}
\title{Zero-Markov information in topological games}

% \author[aub]{S.~Clontz\fnref{fn1}}
% \ead{steven.clontz@auburn.edu}
% \author[aub]{G.~Gruenhage\fnref{fn2}}
% \ead{gruengf@auburn.edu}

% \address[aub]{Department of Mathematics, Auburn University,
%  Auburn, AL 36830}

\author{Steven Clontz}
\address{Department of Mathematics and Statistics, Univeristy of North Carolina
at Charlotte, Charlotte, NC 28223}
\email{steven.clontz@gmail.edu}
\urladdr{clontz.org}

\keywords{topological game, limited information strategy, \(k\)-spaces,
\(\sigma\)-compact spaces, hemicompact spaces}

\subjclass[2010]{54D20, 54D45}

\begin{abstract}
A \(0\)-Markov strategy in a topological game considers only the round number
and ignores all moves by the opponent. The existence of a winning \(0\)-Markov
strategy in either of two games due to Gruenhage characterizes hemicompactness
in either locally compact or compactly generated spaces. However, there
exists a non-compactly generated space for which there exists a winning
\(0\)-Markov strategy in one game but not the other.
\end{abstract}

\maketitle

\section{Introduction}

The following two topological games were introduced by Gary Gruenhage
in \cite{MR858337}.

\begin{game}
  Let $\gruKPGame{X}$ denote the \term{Gruenhage compact/point game}
  with players $\pl K$, $\pl P$ played on a topological space \(X\).
  During round $n$, $\pl K$ chooses
  a compact subset $K_n$ of $X$, followed by $\pl P$ choosing a point
  $p_n\in X$ such that $p_n\not\in \bigcup_{m\leq n}K_m$.

  $\pl K$ wins the game if the collection $\{\{p_n\}:n<\omega\}$ is locally
  finite in the space, and $\pl P$ wins otherwise.
\end{game}

\begin{game}
  Let $\gruKLGame{X}$ denote the \term{Gruenhage compact/compact game}
  with players $\pl K$, $\pl L$ played on a topological space \(X\).
  This game proceeds analogously to
  $\gruKPGame{X}$, except the second player $\pl L$ chooses compact sets $L_n$
  missing $\bigcup_{m\leq n}K_n$,
  and $\pl K$ wins if the collection $\{L_n:n<\omega\}$ is locally finite.
\end{game}

A \term{strategy} for a game defines the move a player makes each round as
a function of the history of the game (previous moves, the round number, etc.).
A \term{winning strategy} defeats every possible counterattack by the
opponent.
Note that a winning strategy in \(\gruKLGame{X}\) is also a winning strategy
in \(\gruKPGame{X}\) since singletons are compact.
In his paper, Gruenhage used these games to characterize several covering
properties using the existence of various kinds of winning strategies for
\(\pl K\) in the games. These results hold in the context of
\term{locally compact} spaces for which every point has a compact neighborhood.

\begin{definition}
  A space is \term{paracompact} if for every open cover $\mc U$ there exists a
  locally-finite open refinement $\mc V$ of $\mc U$ also covering the space.
\end{definition}

\begin{theorem}
  The following are equivalent for a locally compact space $X$:
    \begin{itemize}
      \item $X$ is paracompact
      \item $\pl K \win \gruKLGame{X}$. (\(\pl K\) has a winning strategy
      for the game.)
    \end{itemize}
\end{theorem}

\begin{definition}
  A space is \term{metacompact} if for every open cover $\mc U$ there exists a
  point-finite open refinement $\mc V$ of $\mc U$ also covering the space.
\end{definition}

\begin{theorem}
  The following are equivalent for a locally compact space $X$:
    \begin{itemize}
      \item $X$ is metacompact
      \item $\pl K \tactwin \gruKPGame{X}$ (\(\pl K\) has a \term{tactical}
      winning strategy which only considers the most recent move of
      the opponent each round)
    \end{itemize}
\end{theorem}

\begin{definition}
  A space is \term{$\sigma$-metacompact} if for every open cover $\mc U$ there
  exist point-finite open refinements $\mc V_n$ of $\mc U$ such that
  $\bigcup_{n<\omega}\mc V_n$ also covers the space.
\end{definition}

\begin{theorem}
  The following are equivalent for a locally compact space $X$:
    \begin{itemize}
      \item $X$ is $\sigma$-metacompact
      \item $\pl K \markwin \gruKPGame{X}$ (\(\pl K\) has a \term{Markov}
      winning strategy which only considers the most recent move of
      the opponent and the round number each round)
    \end{itemize}
\end{theorem}

Tactical and Markov strategies are examples of \term{limited information}
strategies. These may be generalized to \term{\(k\)-tactical} and
\term{\(k\)-Markov} strategies by allowing the player to use the \(k\)
most recent moves of the opponent; so \(1\)-tactical strategies are
simply tactical strategies, and similar for Markov. Of course, if
\(k<l\) then a winning \(k\)-tactical (resp. Markov) strategy
is itself a winning \(l\)-tactical (resp. Markov) strategy.
In \cite{QAClontzPreprint}
the author investigated \((k+1)\)-tactical/Markov strategies in \(\gruKPGame{X}\)
and showed that even for a complexly constructed space they can often be
improved to simply a tactical strategy; it remains open if this is always
the case.

In this paper we investigate the applications of \(0\)-Markov strategies
in both \(\gruKPGame{X}\) and \(\gruKLGame{X}\),
which we will call \term{predetermined} strategies as each move is determined
completely by the round number of the game and ignores all moves of the
opponent. It will be shown that for compactly generated spaces that a
predetermined winning strategy in \(\gruKPGame{X}\) can be used to get a
predetermined winning strategy in \(\gruKLGame{X}\).
However, there exists a non-compactly generated space
for which this does not work out.

\section{Locally compact spaces and predetermined strategies}

It's a known fact \cite{MR2048350} that amongst locally compact spaces the
following properties are equivalent.

\begin{definition}
  A space \(X\) is \term{Lindel\"of} if for every open cover of \(X\) there
  exists a countable subcover.
\end{definition}

\begin{definition}
  A space \(X\) is \term{\(\sigma\)-compact} if \(X=\bigcup_{n<\omega}K_n\)
  for \(K_n\) compact.
\end{definition}

\begin{definition}
  A space \(X\) is \term{hemicompact} if \(X=\bigcup_{n<\omega}K_n\)
  for \(K_n\) compact and every compact subset of \(X\) is contained in some
  \(K_n\).
\end{definition}

In general, hemicompact spaces are \(\sigma\)-compact, and \(\sigma\)-compact
spaces are Lindel\"of. By considering the games \(\gruKPGame{X}\) and
\(\gruKLGame{X}\) we will obtain an alternate proof that locally compact
Lindel\"of spaces are hemicompact.

\begin{theorem}
  If \(X\) is a locally compact Lindel\"of space, then
  \(\pl K \prewin \gruKLGame{X}\) (\(\pl K\) has a winning \(0\)-Markov
  a.k.a. predetermined strategy for the game.)
\end{theorem}

\begin{proof}
  For each \(x\in X\), let \(U_x\) be an open neighborhood of \(x\) with \(\cl{U_x}\)
  compact. Then as \(X\) is Lindel\"of, choose \(x_n\in X\) for \(n<\omega\) such that
  \(\{U_{x_n}:n<\omega\}\) covers \(X\). Define the predetermined strategy \(\sigma\)
  for \(\pl K\) by \(\sigma(n)=\cl{U_{x_n}}\).

  Let \(L:\omega\to \mc K(X)\) legally attack \(\sigma\), so
  \(L(n)\cap\bigcup_{m\leq n}\sigma(m)=\emptyset\). For each \(x\in X\),
  choose \(n<\omega\) with \(x\in U_{x_n}\). Then \(U_{x_n}\) is a neighborhood of
  \(x\) which intersects finitely many \(L(n)\), so \(\{L(n):n<\omega\}\) is
  locally finite.
\end{proof}

\begin{theorem}
  If \(\pl K\prewin \gruKPGame{X}\), then \(X\) is hemicompact.
\end{theorem}

\begin{proof}
  Let \(\sigma\) be a winning predetermined strategy for \(\pl K\) in
  \(\gruKPGame{X}\). If \(C\in \mc K(X)\) is compact, then for each \(x\in C\) let
  \(U_x\) be an open neighborhood of \(x\) which intersects finitely many
  \(\sigma(n)\). Choose \(x_i\in C\) for \(i<n<\omega\) such that
  \(\{U_{x_i}:i<n\}\) covers \(C\). Then \(\bigcup_{i<n}U_{x_i}\) contains \(C\)
  and intersects finitely many \(\sigma(n)\), and thus
  \(\{\bigcup_{m\leq n}\sigma(m):n<\omega\}\) witnesses hemicompactness.
\end{proof}

\begin{corollary}
  The following are equivalent for any locally compact space \(X\):
    \begin{itemize}
      \item \(X\) is Lindel\"of.
      \item \(X\) is \(\sigma\)-compact.
      \item \(X\) is hemicompact.
      \item \(\pl K \prewin \gruKPGame{X}\).
      \item \(\pl K \prewin \gruKLGame{X}\).
    \end{itemize}
\end{corollary}

\section{Compactly generated spaces and predetermined strategies}

\begin{definition}
  A space \(X\) is \term{compactly generated} if a set is closed if and
  only if its intersection with every compact set is closed. Such
  spaces are also known as \term{\(k\)-spaces}.
\end{definition}

All locally compact spaces are \(k\)-spaces. As will be shown,
the games \(\gruKPGame{X}\), \(\gruKLGame{X}\) are equivalent for \(\pl K\)'s
predetermined strategies in Hausdorff \(k\)-spaces.

\begin{definition}
  A space \(X\) is a \(k_\omega\)-space if there exist compact sets \(K_n\) for
  \(n<\omega\) such that a set is closed if and
  only if its intersection with every \(K_n\) is closed.
\end{definition}

\begin{theorem}
  If \(X\) is a \(k_\omega\)-space, then
  \(\pl K \prewin \gruKLGame{X}\).
\end{theorem}

\begin{proof}
  Let \(K_n\) witness that \(X\) is a \(k_\omega\)-space. Define the predetermined
  strategy \(\sigma\) for \(\pl K\) by \(\sigma(n)=K_n\).

  Let \(L:\omega\to\mc{K}(X)\) be a legal attack against \(\sigma\), and let
  \(L_{\omega\setminus n} = \bigcup_{n\leq m<\omega}L(m)\). Then as
    \[
      L_{\omega\setminus n}\cap K_p
        =
      \bigcup_{n\leq m< p}L(m) \cap \sigma(p)
    \]
  is compact for each \(p<\omega\), \(L_{\omega\setminus n}\) is closed.

  For each \(x\in X\), \(x\in \sigma(p)\) for some \(p\), so
  \(x\in X\setminus L_{\omega\setminus p}\) which misses all but finitely
  many \(L(n)\), showing that \(\{L(n):n<\omega\}\) is locally finite and
  \(\sigma\) is a winning predetermined strategy.
\end{proof}

The following result was observed in \cite{MR540599}; a proof is provided
for convenience.

\begin{proposition}
  Hemicompact \(k\)-spaces are \(k_\omega\)-spaces.
\end{proposition}

\begin{proof}
  Let \(K_n\) for \(n<\omega\) witness hemicompactness.
  If \(C\cap K_n\) is closed for each \(n<\omega\), then let \(K\) be any compact
  set. Since \(K\subseteq K_n\) for some \(n<\omega\), \(C\cap K\) is closed, and
  therefore \(C\) is closed.
\end{proof}

As we've already seen that \(\pl K \prewin \gruKPGame{X}\) implies
hemicompactness:

\begin{corollary}
  The following are equivalent for any \(k\)-space \(X\):
    \begin{itemize}
      \item \(X\) is \(k_{\omega}\).
      \item \(X\) is hemicompact.
      \item \(\pl K \prewin \gruKPGame{X}\).
      \item \(\pl K \prewin \gruKLGame{X}\).
    \end{itemize}
\end{corollary}

\section{
Non-equivalence of \(\pl K\prewin\gruKPGame{X}\), \(\pl K\prewin\gruKLGame{X}\)
}

For \(k\)-spaces, it has been shown that \(\gruKPGame{X}\) and \(\gruKLGame{X}\)
are equivalent with respect to \(\pl K\)'s winning predetermined strategies.
Looking at a subspace of the Stone-Cech compactification \(\beta\omega\) of
\(\omega\) reveals an example for which the predetermined strategies are not
equivalent.

\begin{definition}
  An \term{ultrafilter} on a cardinal \(\kappa\) is a maximal filter of non-empty
  subsets of \(\kappa\). For each \(\alpha\in \kappa\), the ultrafilter
  \(\mc F_\alpha\) containing all supersets of \(\{\alpha\}\) is called a
  \term{principal ultrafilter}. All
  ultrafilters not of this form are called \term{free ultrafilters}.
\end{definition}

\begin{definition}
  The \term{Stone-Cech compactification} of a cardinal
  \(\kappa\) is the space \(\beta\kappa\) consisting
  of all ultrafilters on \(\kappa\), with open sets of the form
  \(U_S=\{\mc F\in\beta\kappa : S\in\mc F\}\) for \(S\subseteq \kappa\).
\end{definition}

From these definitions it is easily verified that principal ultrafilters
are isolated, so \(\kappa\) with the discrete topology may be viewed as
a dense open subspace of \(\beta\kappa\).
We wish to consider the subspace
of \(\beta\omega\) consisting of all principal ultrafilters and a single free
ultrafilter \(\mc F\), denoted by \(\omega\cup\{\mc F\}\).

\begin{lemma}
  All compact subsets of \(\omega\cup\{\mc F\}\subset\beta\omega\) are finite.
  In particular, the difference of compact sets in \(\omega\cup\{\mc F\}\)
  is compact.
\end{lemma}

\begin{proof}
  Let \(I=\{n_i:i<\omega\}\cup\{\mc F\}\) be infinite.
  Then \(\{U_{\omega\setminus\{n_i:i\geq j\}}:j<\omega\}\) is an open cover of
  \(I\cup\{\mc F\}\) with no finite subcover.
\end{proof}

\begin{theorem}
  \(\pl K\notprewin \gruKLGame{\omega\cup\{\mc F\}}\) for any free
  ultrafilter \(\mc F\).
\end{theorem}

\begin{proof}
  Let \(\sigma\) be a predetermined strategy for \(\pl K\), and define the legal
  counter-attack \(H:\omega\to\mc K(X)\) by
  \(H(n)=(n\cup\sigma(n+1))\setminus\sigma(n)\). Then for any neighborhood
  \(U_S\) of \(\mc F\), \(S\) is infinite, and since
  \(\bigcup_{n<\omega} H(n)\supseteq\omega\setminus\sigma(0)\), \(U_S\) meets
  infinitely many of the finite \(H(n)\). Thus \(\sigma\) is not a winning
  predetermined strategy.
\end{proof}

\begin{theorem}
  There exists a free ultrafilter \(\mc F\) such that
  \(\pl K\prewin \gruKPGame{\omega\cup\{\mc F\}}\).
\end{theorem}

\begin{proof}
  Let \(\mc F\) be any free ultrafilter, and
  define the predetermined strategy \(\sigma\) by
  \(\sigma(n)=n^2\cup\{\mc F\}\).

  Consider the set of all legal attacks \(A\subseteq\omega^\omega\) by
  \(\pl P\) against \(\sigma\). For \(\{f_i:i\leq m\}\in [A]^{<\omega}\) and
  \(m<n<\omega\), each \(f_i\) maps only \(n\) points into \(n^2\), so
  \(\bigcup_{i\leq m}\ran{f_i}\) is coinfinite.
  Then \(\mc G'=\{\omega\setminus\ran f : f\in A\}\) is contained in a free
  ultrafilter \(\mc G\), and if \(\mc F=\mc G\), then \(\sigma\) is a
  winning predetermined strategy.
\end{proof}

It is not possible to prove in \(ZFC\) that
\(\pl K\prewin \gruKPGame{\omega\cup\{\mc F\}}\)
for arbitrary free ultrafilters.

\begin{definition}
  A \term{selective ultrafilter} \(\mc S\) is a free ultrafilter with the
  property that for every
  partition \(\{B_n : n < \omega\}\) of nonempty subsets of \(\omega\) such that
  \(B_n \not\in \mc{S}\) for all \(n\), there exists \(A \in \mc{S}\) such
  that \(|A \cap B_n|=1\) for all \(n\).
\end{definition}

\begin{theorem}
  CH implies the existence of a selective ultrafilter.
  \cite{MR0080902}
\end{theorem}

\begin{theorem}
  If \(\mc S\) is a selective ultrafilter, then
  \(\pl K\notprewin \gruKPGame{\omega\cup\{\mc S\}}\).
\end{theorem}

\begin{proof}
  Let \(\sigma\) be a predetermined strategy for \(\pl K\) such that
  \(\sigma(n)\supset\bigcup_{m<n}\sigma(m)\).
  Then define \(B_n=\omega\cap(\sigma(n+1)\setminus\sigma(n))\). Since \(B_n\)
  is always nonempty finite, \(B_n\not\in\mc F\) and there exists \(A\in \mc S\)
  such that \(|A\cap B_n|=1\).

  Define the legal counter-attack \(p:\omega\to\omega\cup\{\mc S\}\) by
  \(p(n)\in A\cap B_n=A\cap(\sigma(n+1)\setminus\sigma(n))\). Since
  \(A=(A\cap\sigma(0))\cup\{p(n):n<\omega\}\), \(\{p(n):n<\omega\}\in\mc S\).
  Therefore, every neighborhood of \(\mc F\) intersects infinitely many of
  the \(p(n)\), and \(p\) defeats the predetermined strategy \(\sigma\).
\end{proof}

Of particular note is that the author knows of no examples of a
non-\(k\)-space such that \(K\prewin\gruKPGame{X}\).

\begin{question}
  Does \(K\prewin\gruKPGame{X}\) imply \(X\) is a \(k\)-space?
\end{question}

\section{Acknowledgements}

The author would like to thank his PhD advisor Gary Gruenhage for his
support and mentorship while the author developed these results as a part of
his dissertation.

\bibliographystyle{plain}
\bibliography{../../bibliography}

\end{document}

### 2015-10-16 postdoctoral/S_prime_kappa.tex
still incomplete omega_k generalization

@@
   \begin{proof}
-    Assume we've defined such a topology for \(\omega_k\)
-    such that \(\gamma+1=[0,\gamma]\) is clopen for all \(\gamma<\omega_k\).
-    Note that the usual linear order on \(\omega_1\) satisfies these requirements.
+    Assume we've defined an \(\omega\)-bounded topology for \(\omega_k\) such that
+    for each \(\gamma\in\omega_k\) there exists a decreasing countable base
+    \(\{W_{\gamma,n}:n<\omega\}\) such that each
+    \(W_{\gamma,n}\) is countable, compact,
+    and contains no ordinals greater than \(\gamma\).
+    Note that the usual linear order on \(\omega_1\) satisfies this requirement.
 
-    Let \(\alpha<\omega_{k+1}\), and suppose we've defined compatible topologies on
+    Let \(\alpha<\omega_{k+1}\), and suppose we've defined compatible topologies
+    satisfying the induction hypothesis on
     \(\omega_k\cdot (\beta+1)\) for all \(0\leq\beta<\alpha\).
@@
     \(\omega_k\cdot(\alpha+1)\setminus\omega_k\cdot\alpha\cong\omega_k\).
+    In either case, \(\omega_k\cdot(\alpha+1)\setminus\omega_k\cdot\alpha\)
+    is a clopen copy of \(\omega_k\) under the homeomorphism
+    \(\gamma\mapsto\omega_k\cdot\alpha+\gamma\). Then for each
+    \(\gamma\in\omega_k\) we may define the witnessing decreasing countable base
+    \(\{W_{\omega_k\cdot\alpha+\gamma,n}:n<\omega\}\) for
+    \(\omega_k\cdot\alpha+\gamma\) by
+    \(
+      W_{\omega_k\cdot\alpha+\gamma,n}
+        =
+      \{\omega_k\cdot\alpha+\delta:\delta\in W_{\gamma,n}\}
+    \). Note that for \(cf(\alpha)>\omega\),
+    \(\bigcup_{\beta<\alpha}\omega_k\cdot(\beta+1)\) is \(\omega\)-bounded
+    since any countable set is contained in some \(\omega_k\cdot(\beta+1)\);
+    thus in either case \(\omega_k\cdot(\alpha+1)\) is the topological
+    sum of two \(\omega\)-bounded spaces and therefore itself \(\omega\)-bounded.
 
@@
         :
-      \omega_k\cdot(\alpha+1)\setminus\omega_k\cdot\alpha
+      \omega_k
         \to
       \omega_k\cdot\alpha
-    \). Points in \(\omega_k\cdot(\alpha_n+1)\) for some \(n<\omega\)
-    have their usual base induced by that previously defined topology. So let
-    \(\gamma\in\omega_k\cdot(\alpha+1)\setminus\omega_k\cdot\alpha\).
-    Basic open neighborhoods of \(\gamma\) are of the form
-    \(
-      W
+    \). Let
+    \(\gamma\in\omega_k\) and define
+    \[
+      W_{\omega_k\cdot\alpha+\gamma,n}
+        =
+      \{\omega_k\cdot\alpha+\delta:\delta\in W_{\gamma,n}\}
         \cup
-      f_\alpha[W]
+      f_\alpha[W_{\gamma,0}]
         \setminus
       \omega_k\cdot(\alpha_n+1)
-    \),
-    where \(n<\omega\) and
-    \(W\subseteq\gamma+1\) is any countable neighborhood of \(\gamma\).
+    \]
+    to be the countable decreasing
+    base \(\{W_{\omega_k\cdot\alpha+\gamma,n}:n<\omega\}\)
+    for \(\omega_k\cdot\alpha+\gamma\).
+    Note that \(\omega_k\cdot(\alpha+1)\setminus\omega_k\cdot\alpha\) is
+    then a closed (but not open) copy of \(\omega_k\) under the homeomorphism
+    \(\gamma\mapsto\omega_k\cdot\alpha+\gamma\).
 
-    We wish to show that \(\omega_{k+1}\) with the topology induced by
-    \(\bigcup_{\alpha<\omega_{k+1}}\omega_k\cdot(\alpha+1)\) is \(\omega\)-bounded
-    and locally countable. If
-    \(\gamma\in\omega_k\cdot(\alpha+1)\setminus\omega_k\cdot\alpha\) where
-    \(cf(\alpha)\not=\omega\), then we immediately see that it is in a clopen
-    copy of \(\omega_k\) giving us local countability
-    immediately. Otherwise, \(\gamma\) has a basic open neighborhood of the form
+    We wish to demonstrate the induction hypothesis for
+    \(\omega_k\cdot(\alpha+1)\). Each
+    \(W_{\omega_k\cdot\alpha+\gamma,n}\) is countable and contains no
+    ordinals greater than \(\omega_k\cdot\alpha+\gamma\). To see that it is
+    compact, note that \(\{\omega_k\cdot\alpha+\delta:\delta\in W_{\gamma,n}\}\)
+    is a copy of compact \(W_{\gamma,n}\), and for any basic neighborhood
+    \(W_{\omega_k\cdot\alpha+\gamma,m}\)
+    of \(\omega_k\cdot\alpha+\gamma\), the set
     \(
-      W
-        \cup
-      f_\alpha[W]
-        \setminus
-      \omega_k\cdot(\alpha_n+1)
-    \),
-    which is obviously countable.
+      f_\alpha[W_{\gamma,0}]
+        \cap
+      \omega_k\cdot(\alpha_m+1)
+    \)
+    is a countable subspace of \(\omega_k\cdot(\alpha_m+2)\)
 
-    Let \(C\) be a countable subset of \(\omega_k\cdot(\alpha+1)\).
-    In the case that \(\alpha=\beta+1\), we may use the \(\omega\)-boundedness
-    of each part in the clopen partition \(\omega_k\cdot(\beta+1)\) and
-    \(\omega_k\cdot(\beta+2)\setminus\omega_k\cdot(\beta+1)\cong\omega_k\)
-    to conclude that the closure of \(C\) is compact.
-    Similarly, if \(cf(\alpha)>\omega\),
-    then we may use the  \(\omega\)-boundedness
-    of each part in the clopen partition
-    \(\bigcup_{\beta<\alpha}\omega_k\cdot(\beta+1)\) and
-    \(\omega_k\cdot(\alpha+1)\setminus\omega_k\cdot\alpha\cong\omega_k\)
-    to conclude that the closure of \(C\) is compact.
+    % If \(\gamma\in\omega_k\cdot(\alpha+1)\setminus\omega_k\cdot\alpha\) where
+    % \(cf(\alpha)\not=\omega\), then we immediately see that it is in a clopen
+    % copy of \(\omega_k\) giving the result immediately. Otherwise,
+    % \(\alpha\) is the limit of increasing
+    % \(\alpha_n\) for \(n<\omega\), and we claim that
+    % \(
+    %   \{\omega_k\cdot\alpha+\delta:\delta\in W\}
+    %     \cup
+    %   f_\alpha[W]
+    %     \setminus
+    %   \omega_k\cdot(\alpha_n+1)
+    % \) is compact. Since \(W\) is compact in \(\omega_k\) and
+    % \(\omega_k\cdot(\alpha+1)\setminus\omega_k\cdot\alpha\) is
+    % a closed linear copy of \(\omega_k\), we get that
+    % \(\{\omega_k\cdot\alpha+\delta:\delta\in W\}\) is compact.
 
-    The remaining case is again where \(\alpha\) is the limit of increasing
-    \(\alpha_n\) for \(n<\omega\). Then
-    TODO: generalize for \(k+1\)
+    % Let \(C\) be a countable subset of \(\omega_k\cdot(\alpha+1)\).
+    % In the case that \(\alpha=\beta+1\), we may use the \(\omega\)-boundedness
+    % of each part in the clopen partition \(\omega_k\cdot(\beta+1)\) and
+    % \(\omega_k\cdot(\beta+2)\setminus\omega_k\cdot(\beta+1)\cong\omega_k\)
+    % to conclude that the closure of \(C\) is compact.
+    % Similarly, if \(cf(\alpha)>\omega\),
+    % then we may use the  \(\omega\)-boundedness
+    % of each part in the clopen partition
+    % \(\bigcup_{\beta<\alpha}\omega_k\cdot(\beta+1)\) and
+    % \(\omega_k\cdot(\alpha+1)\setminus\omega_k\cdot\alpha\cong\omega_k\)
+    % to conclude that the closure of \(C\) is compact.
+
+    % The remaining case is again where \(\alpha\) is the limit of increasing
+    % \(\alpha_n\) for \(n<\omega\). Then there exists \(\gamma\in\omega_k\)
+    % and a countable neighborhood \(W\subseteq[0,\gamma]\) of \(\gamma\)
+    % such that
     % \(
@@
     %     \subseteq
-    %   [\gamma',\gamma]
+    %   \{\omega_k\cdot\alpha+\delta:\delta\in W\}
     %     \cup
-    %   f_\alpha[[\omega_k\cdot\alpha,\gamma]]
-    % \)
-    % for some \(\omega_k\cdot\alpha\leq\gamma'<\gamma<\omega_k\cdot(\alpha+1)\).
+    %   f_\alpha[W]
+    % \).
     % Its closure is compact:
-    % the closure operation does not add any ordinals greater than \(\gamma\),
-    % and any open cover
-    % contains another basic open neighborhood of \(\gamma\) such as
+    % the closure operation does not add any ordinals greater than
+    % \(\omega_k\cdot\alpha+\gamma\), and any open cover
+    % contains another basic open neighborhood of \(\omega_k\cdot\alpha+\gamma\)
+    % such as
     % \(
-    %   [\gamma'',\gamma]
+    %   \{\omega_k\cdot\alpha+\delta:\delta\in V\}
     %     \cup
-    %   f_\alpha[[\omega_k\cdot\alpha,\gamma]]
+    %   f_\alpha[V]
     %     \setminus
@@
     % \)
-    % which misses only the compact set \([\gamma',\gamma'']\) and the
+    % which misses only the compact set
+    % \(\{\omega_k\cdot\alpha+\delta:\delta\in W\setminus V\}\) and the
     % closure of the countable set
-    % \(
-    %   f_\alpha[[\omega_k\cdot\alpha,\gamma]]
-    %     \cap
-    %   \omega_k\cdot(\alpha_{\min(m,n)}+1)
-    % \), which is compact by the \(\omega\)-boundedness of
-    % \(\omega_k\cdot(\alpha_{\min(m,n)}+1)\).
+    % % \(
+    % %   f_\alpha[[\omega_k\cdot\alpha,\gamma]]
+    % %     \cap
+    % %   \omega_k\cdot(\alpha_{\min(m,n)}+1)
+    % % \), which is compact by the \(\omega\)-boundedness of
+    % % \(\omega_k\cdot(\alpha_{\min(m,n)}+1)\).
 
-    Finally, since every countable subset of \(\omega_{k+1}\) is contained in
-    some \(\omega_k\cdot(\alpha+1)\), we conclude \(\omega_{k+1}\) is
-    \(\omega\)-bounded.
+    % Finally, since every countable subset of \(\omega_{k+1}\) is contained in
+    % some \(\omega_k\cdot(\alpha+1)\), we conclude \(\omega_{k+1}\) is
+    % \(\omega\)-bounded.
   \end{proof}

### 2015-10-26 postdoctoral/gamma_functions.tex
some preliminary results on gamma function on linearly ordered inverse limits

\documentclass[11pt]{article}

\usepackage{../clontzStyle}
\usepackage{../clontzDefinitions}

\begin{document}

  \begin{definition}
    Let a V-map be a u.s.c. idempotent surjection.
  \end{definition}

  \begin{definition}
    For any LOS \(\<L,\leq\>\), let \(\hat L\) be the collection of
    left-closed subsets of \(L\)
    (closed subsets for which \(b\in L,a\leq b\Rightarrow a\in L\))
    linearly ordered by \(\subseteq\).
  \end{definition}

  It's well-known that \(\hat L\) is compact. If \(L\) lacks a least element,
  \(L\) embeds as a dense subspace (consider the sets
  \((\leftarrow,l]\) for \(l\in L\)).

  \begin{definition}
    For any compact LOTS \(K\) with minimum \(0\) and maximum \(1\),
    let \(\Gamma\) be the V-map on \(K\) where \(\Gamma(0)=K\) and \(\Gamma(t)=\{1\}\)
    for \(t>0\).
  \end{definition}

  \begin{theorem}
    \(X=\varprojlim \{2, \Gamma, L\}\cong \hat L\)
  \end{theorem}

  \begin{proof}
    We start by placing an order on \(X\). Let \(\vec x<\vec y\) if
    there exists \(a\in L\) with \(\vec x(a)=0,\vec y(a)=1\). We claim this is
    a total order inducing the topology on \(X\).

    We first observe that if \(\vec x(b)=1\), then for all \(a\leq b\),
    \(\vec x(a)\in\Gamma(1)=\{1\}\). If \(\vec x\not=\vec y\), then assume
    without loss of generality that \(\vec x(a)=0,\vec y(a)=1\), so
    \(\vec x<\vec y\). Also, whenever \(\vec x(b)=1\), we have that \(b<a\),
    so \(\vec y(b)=1\), preventing \(\vec y<\vec x\). Finally if
    \(\vec x<\vec y\) and \(\vec y<\vec z\), take \(a,b\) with
    \(\vec x(a)=0\), \(\vec y(a)=1\),\(\vec y(b)=0\),\(\vec z(b)=1\). It
    follows that \(a<b\) so \(\vec z(a)=1\) and \(\vec x<\vec z\).

    Consider the basic open set \(B(\vec x,F)\) for a finite set
    \(F\in [L]^{<\omega}\)
    about the sequence \(\vec x\in X\) which contains all sequences
    \(\vec y\) agreeing with \(\vec x\) on \(F\). If \(\vec x(a)=1\) for all
    \(a\in F\), then let \(\vec w\in X\) be \(0\) on the maximum of \(F\),
    and \(1\) for anything less. It follows that
    \(B(\vec x,F)=(\vec w,\rightarrow)\). If \(\vec x(a)=0\) for all
    \(a\in F\), then let \(\vec y\in X\) be \(1\) on the minimum of \(F\),
    and \(0\) for anything greater. It follows that
    \(B(\vec x,F)=(\leftarrow,\vec y)\). Finally if \(\vec x(a)=1\) and
    \(\vec x(b)=0\) for \(a<b\) in \(F\) and nothing between \(a,b\) is in
    \(F\), then let \(\vec w\in X\) be \(0\) on \(a\)
    and \(1\) for anything less, and let \(\vec y\in X\) be \(1\) on \(b\)
    and \(0\) for anything greater. It follows that
    \(B(\vec x,F)=(\vec w,\vec y)\).

    Let \(\phi\) evaluate each \(\vec x\in X\subseteq 2^L\) as the
    characteristic function for a subset of \(L\). It's easy to see that
    \(\phi\) is an order isomorphism between \((X,\leq)\) and \((\hat L,\subseteq)\).
  \end{proof}

\newpage
\bibliographystyle{plain}
\bibliography{../bibliography}

\end{document}

### 2015-10-27 postdoctoral/gamma_functions.tex
notes on gamma functions and 2

@@
 \usepackage{../clontzDefinitions}
+
+\renewcommand{\int}{\textrm{int}}
+\renewcommand{\cl}{\textrm{cl}}
+\newcommand{\lexTimes}{\times_{\textrm{lex}}}
 
@@
   \begin{definition}
-    For any LOS \(\<L,\leq\>\), let \(\hat L\) be the collection of
-    left-closed subsets of \(L\)
-    (closed subsets for which \(b\in L,a\leq b\Rightarrow a\in L\))
+    For any LOS \(\<L,\leq\>\), let \(\check L\) be the collection of
+    leftward subsets of \(L\)
+    (subsets for which \(b\in L,a\leq b\Rightarrow a\in L\))
+    linearly ordered by \(\subseteq\), and let \(\hat L\) be the collection
+    of left-open subsets of \(L\) (leftward subsets which are open)
     linearly ordered by \(\subseteq\).
@@
 
-  It's well-known that \(\hat L\) is compact. If \(L\) lacks a least element,
-  \(L\) embeds as a dense subspace (consider the sets
-  \((\leftarrow,l]\) for \(l\in L\)).
+  \begin{proposition}
+    \(\check L\), \(\hat L\) are compact.
+  \end{proposition}
+
+  \begin{proof}
+    Each subset \(S\) has a supremum \(\cup S\) and infimum \(\cap S\)
+    (or \(\int(\cap S)\)).
+  \end{proof}
+
+  Note that \(\check L\)
+  this is not a ``compactification'' as \(L\) does not necessarily
+  embed as a dense subspace of \(\check L\): if \(L=I\), we might attempt to embed
+  \(t\mapsto [0,t)\), but then note that the subspace topology induces the
+  reverse Sorgenfrey interval as \(([0,s),[0,t])=([0,s),[0,t)]\) is open.
+  However \(\hat L\) is basically
+  the typical way of compactifying a linearly ordered space \(L\) (actually,
+  left-closed is more typical, but this works similarly and fits our applications
+  later),
+  provided \(L\) lacks a maximum element (otherwise the whole space is an [easily
+  removable] isolated point in \(\hat L\)).
 
@@
     For any compact LOTS \(K\) with minimum \(0\) and maximum \(1\),
-    let \(\Gamma\) be the V-map on \(K\) where \(\Gamma(0)=K\) and \(\Gamma(t)=\{1\}\)
+    let \(\gamma\) be the V-map on \(K\) where \(\gamma(0)=K\) and \(\gamma(t)=\{1\}\)
     for \(t>0\).
@@
 
+  \begin{definition}
+    For any LOTS \(M\) with minimum element \(0\),
+    let \(\nu\) be the V-map on \(M\) where \(\nu(0)=K\) and \(\nu(t)=\{t\}\)
+    for \(t>0\).
+  \end{definition}
+
+  Note for \(K=M=2\) that \(\gamma=\nu\).
+
   \begin{theorem}
-    \(X=\varprojlim \{2, \Gamma, L\}\cong \hat L\)
+    \(X=\varprojlim \{2, \nu, L\}\cong \check L\)
   \end{theorem}
@@
     We first observe that if \(\vec x(b)=1\), then for all \(a\leq b\),
-    \(\vec x(a)\in\Gamma(1)=\{1\}\). If \(\vec x\not=\vec y\), then assume
+    \(\vec x(a)\in\nu(1)=\{1\}\). If \(\vec x\not=\vec y\), then assume
     without loss of generality that \(\vec x(a)=0,\vec y(a)=1\), so
@@
     characteristic function for a subset of \(L\). It's easy to see that
-    \(\phi\) is an order isomorphism between \((X,\leq)\) and \((\hat L,\subseteq)\).
+    \(\phi\) is an order isomorphism between \(\<X,\leq\>\) and
+    \(\<\check L,\subseteq\>\).
   \end{proof}
+
+  We introduce an alternate definition of an arbitrarily indexed
+  inverse limit.
+
+  \begin{definition}
+    Let \(\varprojlim^\star\{X,f,L\}\subseteq\varprojlim\{X,f,L\}\) satisfy
+    that \(\vec x(a)=\lim_{t\to a}\vec x(t)\) for all \(a\in L\)
+    (for any open neighborhood
+    \(U\)of \(\vec x(a)\) there is \(b<a\) where \(\vec x(t)\in U\)
+    for all \(t\in(b,a]\)).
+  \end{definition}
+
+  \begin{theorem}
+    \(Y=\varprojlim^\star \{2, \nu, L\}\cong \hat L\).
+  \end{theorem}
+
+  \begin{proof}
+    Consider \(Y\) as a subspace of \(X=\varprojlim \{2, \nu, L\}\) with
+    the linear order described above. We claim that if \(\phi\) is the
+    characteristic function for a subset of \(L\), then \(\int\circ\phi\)
+    is an order isomorphsim between \(\<Y,\leq\>\) and
+    \(\<\hat L,\subseteq\>\).
+
+    Let \(A\) be a left-open subset of \(L\). Then let \(\vec x(a)=1\) when
+    \(a\in\cl A\) and \(0\) otherwise. Then \(\vec x\in Y\),
+    \(\phi(\vec x)=\cl A\), and \(\int\circ\phi(\vec x)=\int\cl A=A\).
+
+    Let \(\vec x,\vec y\in Y\). If
+    \(\int\circ\phi(\vec x)=\int\circ\phi(\vec y)=A\), then \(A\) is a
+    left-open set where \(\vec x(a)=\vec y(a)=1\) for \(a\in A\). It follows
+    that if \(b\in\cl A\), then as \(\vec x,\vec y\in Y\),
+    \(\vec x(b)=\vec y(b)=1\) as well. And if \(c\not\in\cl A\), then
+    as \(c\not\in\phi(x)\),
+    \(\vec x(c)=\vec y(c)=0\), so \(\vec x=\vec y\).
+
+    Finally let \(\vec x<\vec y\), so there exists \(a\in L\) with
+    \(\vec x(a)=0,\vec y(a)=1\). Then
+    \(
+      \int\circ\phi(\vec x)
+        \subseteq
+      \phi(\vec x)
+        \subseteq
+      (\leftarrow,a)
+        \subseteq
+      \int\circ\phi(\vec y)
+    \). Thus \(\int\circ\phi\) preserves order.
+  \end{proof}
+
+  \begin{corollary}
+    \(\varprojlim^\star \{2, \nu, \kappa\}=\kappa+1\)
+  \end{corollary}
+
+  % \begin{theorem}
+  %   Let \(K\) be a compact LOTS with minimum \(0\) and maximum \(1\). Then
+  %   \(Z=\varprojlim^\star \{K, \nu, L\}\cong \hat L\lexTimes K / \sim\)
+  %   where \(\lexTimes\) induces the lexicographic ordering on the product,
+  %   \(\<k,1\>\sim\<m,0\>\) when \(k<m\) and \((k,m)=\emptyset\).
+  % \end{theorem}
+
+  % \begin{proof}
+  %   Similar to before, we introduce a linear order to \(Z\) where
+  %   \(\vec x<\vec y\) if there exists \(a\in L\) where \(\vec x(a)=0\) and
+  %   \(\vec y(a)>0\).
+  % \end{proof}
 

### 2015-10-28 postdoctoral/gamma_functions.tex
prove corollary
typos
change kappa to alpha
partial lexicographic result. need to refactor for traditional \hat L

@@
 \newcommand{\lexTimes}{\times_{\textrm{lex}}}
+\newcommand{\vect}{\vec}
 
@@
   \begin{proof}
-    We start by placing an order on \(X\). Let \(\vec x<\vec y\) if
-    there exists \(a\in L\) with \(\vec x(a)=0,\vec y(a)=1\). We claim this is
+    We start by placing an order on \(X\). Let \(\vect x<\vect y\) if
+    there exists \(a\in L\) with \(\vect x(a)=0,\vect y(a)=1\). We claim this is
     a total order inducing the topology on \(X\).
 
-    We first observe that if \(\vec x(b)=1\), then for all \(a\leq b\),
-    \(\vec x(a)\in\nu(1)=\{1\}\). If \(\vec x\not=\vec y\), then assume
-    without loss of generality that \(\vec x(a)=0,\vec y(a)=1\), so
-    \(\vec x<\vec y\). Also, whenever \(\vec x(b)=1\), we have that \(b<a\),
-    so \(\vec y(b)=1\), preventing \(\vec y<\vec x\). Finally if
-    \(\vec x<\vec y\) and \(\vec y<\vec z\), take \(a,b\) with
-    \(\vec x(a)=0\), \(\vec y(a)=1\),\(\vec y(b)=0\),\(\vec z(b)=1\). It
-    follows that \(a<b\) so \(\vec z(a)=1\) and \(\vec x<\vec z\).
+    We first observe that if \(\vect x(b)=1\), then for all \(a\leq b\),
+    \(\vect x(a)\in\nu(1)=\{1\}\). If \(\vect x\not=\vect y\), then assume
+    without loss of generality that \(\vect x(a)=0,\vect y(a)=1\), so
+    \(\vect x<\vect y\). Also, whenever \(\vect x(b)=1\), we have that \(b<a\),
+    so \(\vect y(b)=1\), preventing \(\vect y<\vect x\). Finally if
+    \(\vect x<\vect y\) and \(\vect y<\vect z\), take \(a,b\) with
+    \(\vect x(a)=0\), \(\vect y(a)=1\),\(\vect y(b)=0\),\(\vect z(b)=1\). It
+    follows that \(a<b\) so \(\vect z(a)=1\) and \(\vect x<\vect z\).
 
-    Consider the basic open set \(B(\vec x,F)\) for a finite set
+    Consider the basic open set \(B(\vect x,F)\) for a finite set
     \(F\in [L]^{<\omega}\)
-    about the sequence \(\vec x\in X\) which contains all sequences
-    \(\vec y\) agreeing with \(\vec x\) on \(F\). If \(\vec x(a)=1\) for all
-    \(a\in F\), then let \(\vec w\in X\) be \(0\) on the maximum of \(F\),
+    about the sequence \(\vect x\in X\) which contains all sequences
+    \(\vect y\) agreeing with \(\vect x\) on \(F\). If \(\vect x(a)=1\) for all
+    \(a\in F\), then let \(\vect w\in X\) be \(0\) on the maximum of \(F\),
     and \(1\) for anything less. It follows that
-    \(B(\vec x,F)=(\vec w,\rightarrow)\). If \(\vec x(a)=0\) for all
-    \(a\in F\), then let \(\vec y\in X\) be \(1\) on the minimum of \(F\),
+    \(B(\vect x,F)=(\vect w,\rightarrow)\). If \(\vect x(a)=0\) for all
+    \(a\in F\), then let \(\vect y\in X\) be \(1\) on the minimum of \(F\),
     and \(0\) for anything greater. It follows that
-    \(B(\vec x,F)=(\leftarrow,\vec y)\). Finally if \(\vec x(a)=1\) and
-    \(\vec x(b)=0\) for \(a<b\) in \(F\) and nothing between \(a,b\) is in
-    \(F\), then let \(\vec w\in X\) be \(0\) on \(a\)
-    and \(1\) for anything less, and let \(\vec y\in X\) be \(1\) on \(b\)
+    \(B(\vect x,F)=(\leftarrow,\vect y)\). Finally if \(\vect x(a)=1\) and
+    \(\vect x(b)=0\) for \(a<b\) in \(F\) and nothing between \(a,b\) is in
+    \(F\), then let \(\vect w\in X\) be \(0\) on \(a\)
+    and \(1\) for anything less, and let \(\vect y\in X\) be \(1\) on \(b\)
     and \(0\) for anything greater. It follows that
-    \(B(\vec x,F)=(\vec w,\vec y)\).
+    \(B(\vect x,F)=(\vect w,\vect y)\).
 
-    Let \(\phi\) evaluate each \(\vec x\in X\subseteq 2^L\) as the
+    Let \(\phi\) evaluate each \(\vect x\in X\subseteq 2^L\) as the
     characteristic function for a subset of \(L\). It's easy to see that
@@
     Let \(\varprojlim^\star\{X,f,L\}\subseteq\varprojlim\{X,f,L\}\) satisfy
-    that \(\vec x(a)=\lim_{t\to a}\vec x(t)\) for all \(a\in L\)
+    that \(\vect x(a)=\lim_{t\to a}\vect x(t)\) for all \(a\in L\)
     (for any open neighborhood
-    \(U\)of \(\vec x(a)\) there is \(b<a\) where \(\vec x(t)\in U\)
+    \(U\)of \(\vect x(a)\) there is \(b<a\) where \(\vect x(t)\in U\)
     for all \(t\in(b,a]\)).
@@
 
-    Let \(A\) be a left-open subset of \(L\). Then let \(\vec x(a)=1\) when
-    \(a\in\cl A\) and \(0\) otherwise. Then \(\vec x\in Y\),
-    \(\phi(\vec x)=\cl A\), and \(\int\circ\phi(\vec x)=\int\cl A=A\).
+    Let \(A\) be a left-open subset of \(L\). Then let \(\vect x(a)=1\) when
+    \(a\in\cl A\) and \(0\) otherwise. Then \(\vect x\in Y\),
+    \(\phi(\vect x)=\cl A\), and \(\int\circ\phi(\vect x)=\int\cl A=A\).
 
-    Let \(\vec x,\vec y\in Y\). If
-    \(\int\circ\phi(\vec x)=\int\circ\phi(\vec y)=A\), then \(A\) is a
-    left-open set where \(\vec x(a)=\vec y(a)=1\) for \(a\in A\). It follows
-    that if \(b\in\cl A\), then as \(\vec x,\vec y\in Y\),
-    \(\vec x(b)=\vec y(b)=1\) as well. And if \(c\not\in\cl A\), then
+    Let \(\vect x,\vect y\in Y\). If
+    \(\int\circ\phi(\vect x)=\int\circ\phi(\vect y)=A\), then \(A\) is a
+    left-open set where \(\vect x(a)=\vect y(a)=1\) for \(a\in A\). It follows
+    that if \(b\in\cl A\), then as \(\vect x,\vect y\in Y\),
+    \(\vect x(b)=\vect y(b)=1\) as well. And if \(c\not\in\cl A\), then
     as \(c\not\in\phi(x)\),
-    \(\vec x(c)=\vec y(c)=0\), so \(\vec x=\vec y\).
+    \(\vect x(c)=\vect y(c)=0\), so \(\vect x=\vect y\).
 
-    Finally let \(\vec x<\vec y\), so there exists \(a\in L\) with
-    \(\vec x(a)=0,\vec y(a)=1\). Then
+    Finally let \(\vect x<\vect y\), so there exists \(a\in L\) with
+    \(\vect x(a)=0,\vect y(a)=1\). Then
     \(
-      \int\circ\phi(\vec x)
+      \int\circ\phi(\vect x)
         \subseteq
-      \phi(\vec x)
+      \phi(\vect x)
         \subseteq
@@
         \subseteq
-      \int\circ\phi(\vec y)
+      \int\circ\phi(\vect y)
     \). Thus \(\int\circ\phi\) preserves order.
@@
   \begin{corollary}
-    \(\varprojlim^\star \{2, \nu, \kappa\}=\kappa+1\)
+    \(
+      \varprojlim \{2, \nu, \alpha\}
+      \cong
+      \varprojlim^\star \{2, \nu, \alpha\}
+      \cong
+      \alpha+1
+    \)
+    for every ordinal \(\alpha\).
   \end{corollary}
 
-  % \begin{theorem}
-  %   Let \(K\) be a compact LOTS with minimum \(0\) and maximum \(1\). Then
-  %   \(Z=\varprojlim^\star \{K, \nu, L\}\cong \hat L\lexTimes K / \sim\)
-  %   where \(\lexTimes\) induces the lexicographic ordering on the product,
-  %   \(\<k,1\>\sim\<m,0\>\) when \(k<m\) and \((k,m)=\emptyset\).
-  % \end{theorem}
+  \begin{proof}
+    Since \(\hat\alpha=\alpha+1\) (actually equals, not just homeomorphic!),
+    we get \(\varprojlim^\star \{2, \nu, \alpha\}
+      \cong \hat\alpha =
+    \alpha+1\) for free. Then observe that all leftward sets in \(\alpha\) are
+    open: \(A=[0,\min(\alpha+1\setminus A))\).
+    Thus we have
+    \(\varprojlim \{2, \nu, \alpha\}\cong\check\alpha=\hat\alpha=\alpha+1\).
+  \end{proof}
 
-  % \begin{proof}
-  %   Similar to before, we introduce a linear order to \(Z\) where
-  %   \(\vec x<\vec y\) if there exists \(a\in L\) where \(\vec x(a)=0\) and
-  %   \(\vec y(a)>0\).
-  % \end{proof}
+  \begin{theorem}
+    Let \(M\) be a LOTS with minimum \(0\).
+    \(Z=\varprojlim^\star \{M, \nu, L\}\cong \{-\infty\}\cup \hat L\lexTimes M'\)
+    where \(M'=M\setminus\{0\}\),
+    \(\lexTimes\) induces the lexicographic ordering on the product,
+    and \(-\infty\) is a least element.
+  \end{theorem}
+
+  \begin{proof}
+    Let \(\rho(\vect x)=\int\{a\in L:\exists b> a(\vect x(b)>0)\}\);
+    this is obviously leftwards, and it's open since for each
+    \(a\in\rho(\vect x)\), \(a\in(\leftarrow,b)\subseteq\rho(\vect x)\).
+    Then we give \(Z\) the linear order where \(\vect x<\vect y\) if
+    \(\rho(\vect x)\subsetneq\rho(\vect y)\) or both
+    \(\rho(\vect x)=\rho(\vect y)\)
+    and \(\vect x(l)<\vect y(l)\) for some \(l\in L\).
+
+    Define \(r:Z\to \hat L\lexTimes M\)
+    by \(r(\vect 0)=-\infty\) and \(r(\vect x)=\<\rho(\vect x),m\>\) where
+    \(\vect x(l)=m>0\) for some \(l\in L\) otherwise.
+
+    We first show that \(r\) is a bijection. Let \(A\) be left-open
+    and \(m\in M'\). Then let \(\vect x_{A,m}\) satisfy \(\vect x_{A,m}(a)=m\)
+    for \(a\in A\) and \(\vect x_{A,m}(a)=0\) otherwise.
+  \end{proof}
 

### 2015-10-28 postdoctoral/gamma_functions.tex
broke compactness sadface :-(

@@
     linearly ordered by \(\subseteq\), and let \(\hat L\) be the collection
-    of left-open subsets of \(L\) (leftward subsets which are open)
+    of left-closed subsets of \(L\) (leftward subsets which are closed)
     linearly ordered by \(\subseteq\).
@@
   \begin{proof}
-    Each subset \(S\) has a supremum \(\cup S\) and infimum \(\cap S\)
-    (or \(\int(\cap S)\)).
+    Each subset \(S\) has an infimum \(\cap S\) and a supremum \(\cup S\)
+    (or \(\cl(\cap S)\)).
   \end{proof}
@@
   Note that \(\check L\)
-  this is not a ``compactification'' as \(L\) does not necessarily
+  is not a ``compactification'' as \(L\) does not necessarily
   embed as a dense subspace of \(\check L\): if \(L=I\), we might attempt to embed
@@
   reverse Sorgenfrey interval as \(([0,s),[0,t])=([0,s),[0,t)]\) is open.
-  However \(\hat L\) is basically
-  the typical way of compactifying a linearly ordered space \(L\) (actually,
-  left-closed is more typical, but this works similarly and fits our applications
-  later),
-  provided \(L\) lacks a maximum element (otherwise the whole space is an [easily
+  However \(\hat L\) is
+  the typical way of compactifying a linearly ordered space \(L\),
+  provided \(L\) lacks a least element (otherwise the empty set is an [easily
   removable] isolated point in \(\hat L\)).
@@
 
+  \begin{corollary}
+    \(
+      \varprojlim \{2, \nu, \alpha\}
+      \cong
+      \alpha+1
+    \)
+    for every ordinal \(\alpha\).
+  \end{corollary}
+
+  \begin{proof}
+    Since \(\check\alpha=\alpha+1\) (actually equals, not just homeomorphic!),
+    we get \(\varprojlim^\star \{2, \nu, \alpha\}
+      \cong \check\alpha =
+    \alpha+1\) for free.
+  \end{proof}
+
   We introduce an alternate definition of an arbitrarily indexed
@@
     the linear order described above. We claim that if \(\phi\) is the
-    characteristic function for a subset of \(L\), then \(\int\circ\phi\)
+    characteristic function for a subset of \(L\), then \(\phi\)
     is an order isomorphsim between \(\<Y,\leq\>\) and
@@
 
-    Let \(A\) be a left-open subset of \(L\). Then let \(\vect x(a)=1\) when
-    \(a\in\cl A\) and \(0\) otherwise. Then \(\vect x\in Y\),
-    \(\phi(\vect x)=\cl A\), and \(\int\circ\phi(\vect x)=\int\cl A=A\).
+    Let \(A\) be a left-closed subset of \(L\). Let \(\vect x(a)=1\) when
+    \(a\in A\) and \(\vect x(a)=0\) otherwise. Then \(\vect x\in Y\) and
+    \(\phi(\vect x)=A\).
 
     Let \(\vect x,\vect y\in Y\). If
-    \(\int\circ\phi(\vect x)=\int\circ\phi(\vect y)=A\), then \(A\) is a
-    left-open set where \(\vect x(a)=\vect y(a)=1\) for \(a\in A\). It follows
-    that if \(b\in\cl A\), then as \(\vect x,\vect y\in Y\),
-    \(\vect x(b)=\vect y(b)=1\) as well. And if \(c\not\in\cl A\), then
-    as \(c\not\in\phi(x)\),
-    \(\vect x(c)=\vect y(c)=0\), so \(\vect x=\vect y\).
+    \(\phi(\vect x)=\phi(\vect y)=A\), then \(A\) is a
+    left-closed set where \(\vect x(a)=\vect y(a)=1\) for \(a\in A\)
+    and \(\vect x(a)=\vect y(a)=0\) otherwise, so \(\vect x=\vect y\).
 
     Finally let \(\vect x<\vect y\), so there exists \(a\in L\) with
-    \(\vect x(a)=0,\vect y(a)=1\). Then
+    \(\vect x(a)=0\), \(\vect y(a)=1\). Then
     \(
-      \int\circ\phi(\vect x)
-        \subseteq
       \phi(\vect x)
@@
         \subseteq
-      \int\circ\phi(\vect y)
-    \). Thus \(\int\circ\phi\) preserves order.
+      \phi(\vect y)
+    \). Thus \(\phi\) preserves order.
   \end{proof}
@@
     \(
-      \varprojlim \{2, \nu, \alpha\}
-      \cong
       \varprojlim^\star \{2, \nu, \alpha\}
@@
     \)
-    for every ordinal \(\alpha\).
+    for every infinite limit or finite ordinal \(\alpha\).
   \end{corollary}
@@
   \begin{proof}
-    Since \(\hat\alpha=\alpha+1\) (actually equals, not just homeomorphic!),
-    we get \(\varprojlim^\star \{2, \nu, \alpha\}
-      \cong \hat\alpha =
-    \alpha+1\) for free. Then observe that all leftward sets in \(\alpha\) are
-    open: \(A=[0,\min(\alpha+1\setminus A))\).
-    Thus we have
-    \(\varprojlim \{2, \nu, \alpha\}\cong\check\alpha=\hat\alpha=\alpha+1\).
+    If \(\alpha\) is finite, then of course all (leftward) sets are
+    closed and we get \(\hat\alpha=\check\alpha=\alpha+1\) for free.
+    Otherwise, since \(\alpha\) lacks a greatest point, \(\hat\alpha\)
+    is homeomorphic to its usual compactification \(\alpha+1\).
   \end{proof}
+
+  In fact, \(\hat\alpha=\alpha+1\setminus L(\alpha)\) where \(L(\alpha)\)
+  is the colleciton of all limit ordinals less than \(\alpha\), which also
+  shows \(\hat\alpha\cong\alpha\) for infinite successor ordinals \(\alpha\).
 
@@
     Let \(M\) be a LOTS with minimum \(0\).
-    \(Z=\varprojlim^\star \{M, \nu, L\}\cong \{-\infty\}\cup \hat L\lexTimes M'\)
+    \(
+      Z
+        =
+      \varprojlim^\star \{M, \nu, L\}
+        \cong
+      \{-\infty\}\cup (\hat L\setminus\emptyset)\lexTimes M'
+    \)
     where \(M'=M\setminus\{0\}\),
@@
   \begin{proof}
-    Let \(\rho(\vect x)=\int\{a\in L:\exists b> a(\vect x(b)>0)\}\);
-    this is obviously leftwards, and it's open since for each
-    \(a\in\rho(\vect x)\), \(a\in(\leftarrow,b)\subseteq\rho(\vect x)\).
+    Let \(\rho(\vect x)=\{a\in L:\vect x(a)>0\}\);
+    this is obviously leftwards, and it's closed for all \(\vect x\in Z\).
     Then we give \(Z\) the linear order where \(\vect x<\vect y\) if
@@
 
-    We first show that \(r\) is a bijection. Let \(A\) be left-open
+    We first show that \(r\) is a bijection. Let \(A\) be left-closed
     and \(m\in M'\). Then let \(\vect x_{A,m}\) satisfy \(\vect x_{A,m}(a)=m\)
-    for \(a\in A\) and \(\vect x_{A,m}(a)=0\) otherwise.
+    for \(a\in A\) and \(\vect x_{A,m}(a)=0\) otherwise and note
+    \(\vect x_{A,m}\in Z\), \(r(\vect x_{A,m})=\<A,m\>\). Showing one-to-one
+    is similarly trivial.
+
+    Finally let \(\vect 0<\vect x<\vect y\).
+    If \(\rho(\vect x)\subsetneq\rho(\vect y)\), then \(r(\vect x)<r(\vect y)\).
+    Otherwise \(\rho(\vect x)=\rho(\vect y)\), but \(0<\vect x(l)<\vect y(l)\)
+    for some \(l\in L\) and therefore \(r(\vect x)<r(\vect y)\).
+  \end{proof}
+
+  This gives us the previous result as a corollary:
+  \(
+    \varprojlim^\star \{2, \nu, L\}
+      \cong
+    \{-\infty\}\cup(\hat L\setminus\{\emptyset\})\lexTimes\{1\}
+      \cong
+    \hat L
+  \). Unfortunately, the result is not always compact.
+
+  \begin{example}
+    \(
+      \varprojlim^\star \{I, \nu, I\}
+        \cong
+      \{-\infty\}\cup (0,1]\lexTimes(0,1]
+    \)
+  is not compact.
+  \end{example}
+
+  \begin{proof}
+    The infinite set \(\{\<1-\frac{1}{2^n},1-\frac{1}{2^n}\>:0<n<\omega\}\)
+    is closed discrete.
   \end{proof}

### 2015-10-29 postdoctoral/gamma_functions.tex
whoops, that linear order doesn't induce the topology

@@
 
-  \begin{theorem}
-    Let \(M\) be a LOTS with minimum \(0\).
-    \(
-      Z
-        =
-      \varprojlim^\star \{M, \nu, L\}
-        \cong
-      \{-\infty\}\cup (\hat L\setminus\emptyset)\lexTimes M'
-    \)
-    where \(M'=M\setminus\{0\}\),
-    \(\lexTimes\) induces the lexicographic ordering on the product,
-    and \(-\infty\) is a least element.
-  \end{theorem}
+  % \begin{theorem}
+  %   Let \(M\) be a LOTS with minimum \(0\).
+  %   \(
+  %     Z
+  %       =
+  %     \varprojlim^\star \{M, \nu, L\}
+  %       \cong
+  %     \{-\infty\}\cup (\hat L\setminus\emptyset)\lexTimes M'
+  %   \)
+  %   where \(M'=M\setminus\{0\}\),
+  %   \(\lexTimes\) induces the lexicographic ordering on the product,
+  %   and \(-\infty\) is a least element.
+  % \end{theorem}
 
-  \begin{proof}
-    Let \(\rho(\vect x)=\{a\in L:\vect x(a)>0\}\);
-    this is obviously leftwards, and it's closed for all \(\vect x\in Z\).
-    Then we give \(Z\) the linear order where \(\vect x<\vect y\) if
-    \(\rho(\vect x)\subsetneq\rho(\vect y)\) or both
-    \(\rho(\vect x)=\rho(\vect y)\)
-    and \(\vect x(l)<\vect y(l)\) for some \(l\in L\).
+  % \begin{proof}
+  %   Let \(\rho(\vect x)=\{a\in L:\vect x(a)>0\}\);
+  %   this is obviously leftwards, and it's closed for all \(\vect x\in Z\).
+  %   Then we give \(Z\) the linear order where \(\vect x<\vect y\) if
+  %   \(\rho(\vect x)\subsetneq\rho(\vect y)\) or both
+  %   \(\rho(\vect x)=\rho(\vect y)\)
+  %   and \(\vect x(l)<\vect y(l)\) for some \(l\in L\).
 
-    Define \(r:Z\to \hat L\lexTimes M\)
-    by \(r(\vect 0)=-\infty\) and \(r(\vect x)=\<\rho(\vect x),m\>\) where
-    \(\vect x(l)=m>0\) for some \(l\in L\) otherwise.
+  %   Define \(r:Z\to \hat L\lexTimes M\)
+  %   by \(r(\vect 0)=-\infty\) and \(r(\vect x)=\<\rho(\vect x),m\>\) where
+  %   \(\vect x(l)=m>0\) for some \(l\in L\) otherwise.
 
-    We first show that \(r\) is a bijection. Let \(A\) be left-closed
-    and \(m\in M'\). Then let \(\vect x_{A,m}\) satisfy \(\vect x_{A,m}(a)=m\)
-    for \(a\in A\) and \(\vect x_{A,m}(a)=0\) otherwise and note
-    \(\vect x_{A,m}\in Z\), \(r(\vect x_{A,m})=\<A,m\>\). Showing one-to-one
-    is similarly trivial.
+  %   We first show that \(r\) is a bijection. Let \(A\) be left-closed
+  %   and \(m\in M'\). Then let \(\vect x_{A,m}\) satisfy \(\vect x_{A,m}(a)=m\)
+  %   for \(a\in A\) and \(\vect x_{A,m}(a)=0\) otherwise and note
+  %   \(\vect x_{A,m}\in Z\), \(r(\vect x_{A,m})=\<A,m\>\). Showing one-to-one
+  %   is similarly trivial.
 
-    Finally let \(\vect 0<\vect x<\vect y\).
-    If \(\rho(\vect x)\subsetneq\rho(\vect y)\), then \(r(\vect x)<r(\vect y)\).
-    Otherwise \(\rho(\vect x)=\rho(\vect y)\), but \(0<\vect x(l)<\vect y(l)\)
-    for some \(l\in L\) and therefore \(r(\vect x)<r(\vect y)\).
-  \end{proof}
+  %   Finally let \(\vect 0<\vect x<\vect y\).
+  %   If \(\rho(\vect x)\subsetneq\rho(\vect y)\), then \(r(\vect x)<r(\vect y)\).
+  %   Otherwise \(\rho(\vect x)=\rho(\vect y)\), but \(0<\vect x(l)<\vect y(l)\)
+  %   for some \(l\in L\) and therefore \(r(\vect x)<r(\vect y)\).
+  % \end{proof}
 
-  This gives us the previous result as a corollary:
-  \(
-    \varprojlim^\star \{2, \nu, L\}
-      \cong
-    \{-\infty\}\cup(\hat L\setminus\{\emptyset\})\lexTimes\{1\}
-      \cong
-    \hat L
-  \). Unfortunately, the result is not always compact.
+  % This gives us the previous result as a corollary:
+  % \(
+  %   \varprojlim^\star \{2, \nu, L\}
+  %     \cong
+  %   \{-\infty\}\cup(\hat L\setminus\{\emptyset\})\lexTimes\{1\}
+  %     \cong
+  %   \hat L
+  % \). Unfortunately, the result is not always compact.
 
-  \begin{example}
-    \(
-      \varprojlim^\star \{I, \nu, I\}
-        \cong
-      \{-\infty\}\cup (0,1]\lexTimes(0,1]
-    \)
-  is not compact.
-  \end{example}
+  % \begin{example}
+  %   \(
+  %     \varprojlim^\star \{I, \nu, I\}
+  %       \cong
+  %     \{-\infty\}\cup (0,1]\lexTimes(0,1]
+  %   \)
+  % is not compact.
+  % \end{example}
 
-  \begin{proof}
-    The infinite set \(\{\<1-\frac{1}{2^n},1-\frac{1}{2^n}\>:0<n<\omega\}\)
-    is closed discrete.
-  \end{proof}
+  % \begin{proof}
+  %   The infinite set \(\{\<1-\frac{1}{2^n},1-\frac{1}{2^n}\>:0<n<\omega\}\)
+  %   is closed discrete.
+  % \end{proof}
 

### 2015-10-29 postdoctoral/gamma_functions.tex
some examples of limit computations

--- 2015-10-28 postdoctoral/gamma_functions.tex
@@
 
+  \bigskip
+
+  The ready may verify the following examples:
+
+  \begin{example}
+    \(\varprojlim\{2,\gamma,I\}\cong \check L\lexTimes 1\)
+  \end{example}
+  \begin{example}
+    \(\varprojlim\{I,\gamma,I\}\cong I\lexTimes I\)
+  \end{example}
+  \begin{example}
+    \(\varprojlim\{I,\gamma,\omega\}\cong (\omega\lexTimes[0,1))\cup\{\infty\}\)
+  \end{example}
+  \begin{example}
+    \(\varprojlim\{I,\gamma,\omega+1\}\cong \omega+1\lexTimes I\)
+  \end{example}
+  \begin{example}
+    \(\varprojlim\{I,\gamma,-\omega\}\cong \{-\infty\}\cup(-\omega\lexTimes(0,1])\)
+  \end{example}
+  \begin{example}
+    \(\varprojlim\{I,\gamma,I\}\cong I\lexTimes I\)
+  \end{example}
+
   \begin{theorem}
-    Let \(M\) be a LOTS with minimum \(0\).
-    \(
-      Z
-        =
-      \varprojlim^\star \{M, \nu, L\}
-        \cong
-      \{-\infty\}\cup (\hat L\setminus\emptyset)\lexTimes M'
-    \)
-    where \(M'=M\setminus\{0\}\),
-    \(\lexTimes\) induces the lexicographic ordering on the product,
-    and \(-\infty\) is a least element.
+    If \(K,L\) are compact linearly orders, then
+    \(\varprojlim\{K,\gamma,L\}\cong L\lexTimes K\).
   \end{theorem}
@@
   \begin{proof}
-    Let \(\rho(\vect x)=\{a\in L:\vect x(a)>0\}\);
-    this is obviously leftwards, and it's closed for all \(\vect x\in Z\).
-    Then we give \(Z\) the linear order where \(\vect x<\vect y\) if
-    \(\rho(\vect x)\subsetneq\rho(\vect y)\) or both
-    \(\rho(\vect x)=\rho(\vect y)\)
-    and \(\vect x(l)<\vect y(l)\) for some \(l\in L\).
 
-    Define \(r:Z\to \hat L\lexTimes M\)
-    by \(r(\vect 0)=-\infty\) and \(r(\vect x)=\<\rho(\vect x),m\>\) where
-    \(\vect x(l)=m>0\) for some \(l\in L\) otherwise.
-
-    We first show that \(r\) is a bijection. Let \(A\) be left-closed
-    and \(m\in M'\). Then let \(\vect x_{A,m}\) satisfy \(\vect x_{A,m}(a)=m\)
-    for \(a\in A\) and \(\vect x_{A,m}(a)=0\) otherwise and note
-    \(\vect x_{A,m}\in Z\), \(r(\vect x_{A,m})=\<A,m\>\). Showing one-to-one
-    is similarly trivial.
-
-    Finally let \(\vect 0<\vect x<\vect y\).
-    If \(\rho(\vect x)\subsetneq\rho(\vect y)\), then \(r(\vect x)<r(\vect y)\).
-    Otherwise \(\rho(\vect x)=\rho(\vect y)\), but \(0<\vect x(l)<\vect y(l)\)
-    for some \(l\in L\) and therefore \(r(\vect x)<r(\vect y)\).
-  \end{proof}
-
-  This gives us the previous result as a corollary:
-  \(
-    \varprojlim^\star \{2, \nu, L\}
-      \cong
-    \{-\infty\}\cup(\hat L\setminus\{\emptyset\})\lexTimes\{1\}
-      \cong
-    \hat L
-  \). Unfortunately, the result is not always compact.
-
-  \begin{example}
-    \(
-      \varprojlim^\star \{I, \nu, I\}
-        \cong
-      \{-\infty\}\cup (0,1]\lexTimes(0,1]
-    \)
-  is not compact.
-  \end{example}
-
-  \begin{proof}
-    The infinite set \(\{\<1-\frac{1}{2^n},1-\frac{1}{2^n}\>:0<n<\omega\}\)
-    is closed discrete.
   \end{proof}

### 2015-10-29 postdoctoral/gamma_functions.tex
switch to using gamma over nu

@@
   \begin{theorem}
-    \(X=\varprojlim \{2, \nu, L\}\cong \check L\)
+    \(X=\varprojlim \{2, \gamma, L\}\cong \check L\)
   \end{theorem}
@@
     We first observe that if \(\vect x(b)=1\), then for all \(a\leq b\),
-    \(\vect x(a)\in\nu(1)=\{1\}\). If \(\vect x\not=\vect y\), then assume
+    \(\vect x(a)\in\gamma(1)=\{1\}\). If \(\vect x\not=\vect y\), then assume
     without loss of generality that \(\vect x(a)=0,\vect y(a)=1\), so
@@
     \(
-      \varprojlim \{2, \nu, \alpha\}
+      \varprojlim \{2, \gamma, \alpha\}
       \cong
@@
     Since \(\check\alpha=\alpha+1\) (actually equals, not just homeomorphic!),
-    we get \(\varprojlim^\star \{2, \nu, \alpha\}
+    we get \(\varprojlim^\star \{2, \gamma, \alpha\}
       \cong \check\alpha =
@@
   \begin{theorem}
-    \(Y=\varprojlim^\star \{2, \nu, L\}\cong \hat L\).
+    \(Y=\varprojlim^\star \{2, \gamma, L\}\cong \hat L\).
   \end{theorem}
@@
   \begin{proof}
-    Consider \(Y\) as a subspace of \(X=\varprojlim \{2, \nu, L\}\) with
+    Consider \(Y\) as a subspace of \(X=\varprojlim \{2, \gamma, L\}\) with
     the linear order described above. We claim that if \(\phi\) is the
@@
     \(
-      \varprojlim^\star \{2, \nu, \alpha\}
+      \varprojlim^\star \{2, \gamma, \alpha\}
       \cong

### 2015-10-30 postdoctoral/gamma_functions.tex
WIP compact lex prod proof
nailed the answer for \gamma

@@
   provided \(L\) lacks a least element (otherwise the empty set is an [easily
-  removable] isolated point in \(\hat L\)).
+  removable] isolated point in \(\hat L\)). Note that we \textbf{always}
+  assume that \(\emptyset\in\hat L\):
+
+  \begin{example}
+    \(\hat I\cong\{-\infty\}\cup I\) where
+    \(\emptyset\mapsto-\infty\) and \([0,t]\mapsto t\).
+  \end{example}
+
+  \begin{example}
+    For limit ordinals \(\alpha\), \(\hat \alpha\cong \alpha+1\),
+    and for all other infinite ordinals, \(\hat\alpha\cong\alpha\).
+    (The addition of a new least isolated point is of course irrelevant).
+  \end{example}
 
@@
     \alpha+1\) for free.
+    Note that C and Varagona used this in (TODO create citataion) to break
+    metrizability in uncountable-ordinal-indexed inverse limits (for any V-map
+    there exists a two-point set \(2\) such that \(f\rest 2\supseteq\gamma\),
+    that is, ``\(f\) has condition \(\Gamma\)'').
   \end{proof}
+
+  \bigskip
+
+  We may generalize theorem 8 as follows:
+
+  \begin{theorem}
+    If \(M\) is a LOTS with minimum \(0\) and maximum \(1\),
+    then \(\varprojlim\{M,\gamma,L\}\cong \hat L\lexTimes M/\sim\),
+    where \(\<(\leftarrow,l_0],1\>\sim\<(\leftarrow,l_1],0\>\) if
+    \(l_0<l_1\) and \((l_0,l_1)=\emptyset\),
+    and where \(\<A,m\>\sim\<A,m'\>\) if \(A\in\hat L\setminus L\).
+  \end{theorem}
+
+  \begin{proof}
+    Let \(\rho(\vect x)=\cl\{l\in L:\vect x(l)>0\}\), \(v(\vect 0)=0\),
+    and \(v(\vect x)=\min\{\vect x(l):l\in\rho(\vect x)\}\) otherwise.
+    Say \(\vect x<\vect y\) if \(\rho(\vect x)\subsetneq\rho(\vect y)\)
+    or both \(\rho(\vect x)=\rho(\vect y)\) and \(v(\vect x)<v(\vect y)\).
+    The reader may verify that this is a linear order on
+    \(\varprojlim\{M,\gamma,L\}\), and
+    \(\theta(\vect x)=\<\rho(\vect x),v(\vect x)\>\in\hat L\lexTimes M/\sim\)
+    preserves order.
+    For each left-closed set \(A\) and \(m\in M\),
+    let \(\vect x_{A,m}(l)=1\) for \(l\in A\) unless \(l\) is the supremum
+    element of \(A\),
+    \(\vect x_{A,m}(l)=m\) if \(l\) is the supremum of \(A\),
+    and \(\vect x_{A,m}(l)=0\) for \(l\not\in A\).
+    To complete the proof, we should demonstrate that the linear order we
+    defined induces the topology of the inverse limit, and that \(\theta\)
+    is a surjection.
+
+    A basic open set in \(\varprojlim\{M,\gamma,L\}\subseteq L^m\)
+    is of the form
+    \([U,F]\) where \(U(l)\) is an open interval in \(M\) for each
+    \(l\in F\in [L]^{<\omega}\), and
+    \([U,F]=\{\vect x:l\in F\Rightarrow\vect x(l)\in U(l)\}\).
+    If we assume that \([U,F]\) is non-empty, one of the following
+    must hold:
+
+    \begin{itemize}
+      \item
+        \(U[l_0]=(a,b)\) for some \(l_0\in F\).
+        Then \([U,F]=[U,\{l_0\}]\), and note that
+        \(
+          [U,\{l_0\}]
+            =
+          (\vect x_{(\leftarrow,l_0],a},\vect x_{(\leftarrow,l_0],b})
+        \).
+      \item
+        \(U(l_0)=(a,1]\) and \(U(l_1)=[0,b)\) for some \(l_0<l_1\in L\)
+        and \([U,F]=[U,\{l_0,l_1\}]\). Then
+        \([U,\{l_0,l_1\}]=(\vect x_{l_0,a},\vect x_{l_1,b})\).
+    \end{itemize}
+    In the other direction, consider \(\vect y\in(\vect x,\vect z)\).
+    \begin{itemize}
+      \item
+        In the case that \(l_0\in\rho(\vect y)\setminus\rho(\vect x)\)
+        and \(l_1\in\rho(\vect z)\setminus\rho(\vect y)\), let
+        \(U(l_0)=(0,1]\), \(U(l_1)=[0,v(\vect z))\) and note
+        \(\vect y\in[U,\{l_0,l_1\}]\subseteq(\vect x,\vect z)\).
+      \item
+        In the case that \(l_0\in\rho(\vect y)\setminus\rho(\vect x)\),
+        \(\rho(\vect y)=\rho(\vect z)\), and \(v(\vect y)<v(\vect z)\),
+        it follows that \(\rho(\vect y)=\rho(\vect z)=(\leftarrow,l_1]\),
+        so let \(U(l_0)=(0,1]\), \(U(l_1)=[0,v(\vect z))\) and note
+        \(\vect y\in[U,\{l_0,l_1\}]\subseteq(\vect x,\vect z)\).
+      \item
+        In the case that
+        \(\rho(\vect x)=\rho(\vect y)\), \(v(\vect x)<v(\vect y)\),
+        and \(l_1\in\rho(\vect z)\setminus\rho(\vect y)\),
+        it follows that \(\rho(\vect x)=\rho(\vect y)=(\leftarrow,l_0]\),
+        so let \(U(l_0)=(v(\vect x),1]\), \(U(l_1)=[0,v(\vect z))\) and note
+        \(\vect y\in[U,\{l_0,l_1\}]\subseteq(\vect x,\vect z)\).
+      \item
+        In the case that
+        \(\rho(\vect x)=\rho(\vect y)=\rho(\vect z)\) and
+        \(v(\vect x)<v(\vect y)<v(\vect z)\),
+        it follows that
+        \(\rho(\vect x)=\rho(\vect y)=\rho(\vect z)=(\leftarrow,l_0]\),
+        so let \(U(l_0)=(v(\vect x),v(\vect z))\) and note
+        \(\vect y\in[U,\{l_0\}]=(\vect x,\vect z)\).
+    \end{itemize}
+
+    We conclude by
+    showing that \(\theta\) is a surjection. If \(B\in\hat L\setminus L\)
+    and \(m\in M\), consider \(\<B,m\>\).
+    \(B\) lacks a supremum in \(L\), so
+    \(\vect x_{B,0}(l)=1\) for \(l\in B\) and \(\vect x_{B,0}(l)=0\) otherwise.
+    So \(\theta(\vect x_{B,0})=\<\cl B,1\>=\<B,1\>\sim\<B,m\>\) for all
+    \(m\in M\). Otherwise, \(B=(\leftarrow,l_1]\) for some \(l_1\in L\).
+    Let \(m>0\).
+    Then
+    \(
+      \theta(\vect x_{(\leftarrow,l_1],m})
+        =
+      \<\cl (\leftarrow,l_1],v(\vect x_{(\leftarrow,l_1],m})\>
+        =
+      \<(\leftarrow,l_1],m\>
+    \).
+    Finally, we want to map onto \(\<(\leftarrow,l_1],0\>\).
+    If there exists \(l_0<l_1\) with \((l_0,l_1)=\emptyset\), then
+    \(
+      \theta(\vect x_{(\leftarrow,l_1],0})
+        =
+      \theta(\vect x_{(\leftarrow,l_0],1})
+        =
+      \<(\leftarrow,l_0],1\>
+    \)
+    will suffice. Otherwise,
+    \(
+      \theta(\vect x_{(\leftarrow,l_1],0})
+        =
+      \<\cl (\leftarrow,l_1),v(\vect x_{(\leftarrow,l_1),0})\>
+        =
+      \<(\leftarrow,l_1],0\>
+    \).
+  \end{proof}
+
+  Here are some applications:
+
+  \begin{example}
+    \(
+      \varprojlim\{2,\gamma,I\}
+        \cong
+      (\hat I\setminus\emptyset)\lexTimes 2
+        \cong
+      I\lexTimes 2
+        \cong
+      \check I
+    \) (of course, this could be found quicker with theorem 8).
+  \end{example}
+
+  \begin{example}
+    \(
+      \varprojlim\{I,\gamma,I\}
+        \cong
+      (\hat I\setminus\emptyset)\lexTimes I
+        \cong
+      I\lexTimes I
+    \).
+  \end{example}
+
+  \begin{example}
+    For infinite ordinals \(\alpha\),
+    \(
+      \varprojlim\{I,\gamma,\alpha\}
+        \cong
+      (\alpha\lexTimes[0,1))\cup\{\infty\}
+    \).
+    In particular, \(\alpha=\kappa\) for an infinite cardinal \(\kappa\)
+    gives the closed long ray of length \(\kappa\).
+  \end{example}
+
+  \bigskip
 
@@
     closed and we get \(\hat\alpha=\check\alpha=\alpha+1\) for free.
-    Otherwise, since \(\alpha\) lacks a greatest point, \(\hat\alpha\)
-    is homeomorphic to its usual compactification \(\alpha+1\).
+    Otherwise, as observed previously \(\hat\alpha\)
+    is homeomorphic to its usual compactification \(\alpha+1\) for
+    limit ordinals.
   \end{proof}
@@
 
-  \bigskip
-
-  The ready may verify the following examples:
-
-  \begin{example}
-    \(\varprojlim\{2,\gamma,I\}\cong \check L\lexTimes 1\)
-  \end{example}
-  \begin{example}
-    \(\varprojlim\{I,\gamma,I\}\cong I\lexTimes I\)
-  \end{example}
-  \begin{example}
-    \(\varprojlim\{I,\gamma,\omega\}\cong (\omega\lexTimes[0,1))\cup\{\infty\}\)
-  \end{example}
-  \begin{example}
-    \(\varprojlim\{I,\gamma,\omega+1\}\cong \omega+1\lexTimes I\)
-  \end{example}
-  \begin{example}
-    \(\varprojlim\{I,\gamma,-\omega\}\cong \{-\infty\}\cup(-\omega\lexTimes(0,1])\)
-  \end{example}
-  \begin{example}
-    \(\varprojlim\{I,\gamma,I\}\cong I\lexTimes I\)
-  \end{example}
-
-  \begin{theorem}
-    If \(K,L\) are compact linearly orders, then
-    \(\varprojlim\{K,\gamma,L\}\cong L\lexTimes K\).
-  \end{theorem}
-
-  \begin{proof}
-
-  \end{proof}
-
 \newpage

### 2015-11-04 articles/destroying-metrizability-in-generalized-inverse-limits/article.tex
final draft of preprint

@@
 
-\bibitem{varagona} Scott Varagona, {\it Generalized Inverse Limits Indexed by Totally Ordered Sets}, preprint (submitted to Topology Proceedings), 2015.
+\bibitem{varagona} Scott Varagona, {\it Generalized Inverse Limits Indexed by Totally Ordered Sets}, preprint (2015). Available at http://arxiv.org/abs/1511.00266
 

### 2015-11-09 postdoctoral/S_prime_kappa.tex
start writing up notes based on alan's input

--- 2015-10-08 postdoctoral/S_prime_kappa.tex
@@
   \begin{proof}
-    Assume we've defined such a topology for \(\omega_k\)
-    such that \(\gamma+1=[0,\gamma]\) is clopen for all \(\gamma<\omega_k\).
-    Note that the usual linear order on \(\omega_1\) satisfies these requirements.
-
-    Let \(\alpha<\omega_{k+1}\), and suppose we've defined compatible topologies on
-    \(\omega_k\cdot (\beta+1)\) for all \(0\leq\beta<\alpha\).
-    If \(\alpha=\beta+1\), then let
-    \(\omega_k\cdot(\alpha+1)=\omega_k\cdot(\beta+2)\) be the topological sum
-    of the previously defined \(\omega_k\cdot(\beta+1)\) and the
-    previously defined
-    \(\omega_k\cdot(\beta+2)\setminus\omega_k\cdot(\beta+1)\cong\omega_k\).
-    Similarly, if \(cf(\alpha)>\omega\), then let \(\omega_k\cdot(\alpha+1)\)
-    be the topological sum of \(\bigcup_{\beta<\alpha}\omega_k\cdot(\beta+1)\)
-    and the previously defined
-    \(\omega_k\cdot(\alpha+1)\setminus\omega_k\cdot\alpha\cong\omega_k\).
-
-    The remaining case is where \(\alpha\) is the limit of increasing
-    \(\alpha_n\) for \(n<\omega\). Fix a bijection
-    \(
-      f_\alpha
-        :
-      \omega_k\cdot(\alpha+1)\setminus\omega_k\cdot\alpha
-        \to
-      \omega_k\cdot\alpha
-    \). Points in \(\omega_k\cdot(\alpha_n+1)\) for some \(n<\omega\)
-    have their usual base induced by that previously defined topology. So let
-    \(\gamma\in\omega_k\cdot(\alpha+1)\setminus\omega_k\cdot\alpha\).
-    Basic open neighborhoods of \(\gamma\) are of the form
-    \(
-      W
-        \cup
-      f_\alpha[W]
-        \setminus
-      \omega_k\cdot(\alpha_n+1)
-    \),
-    where \(n<\omega\) and
-    \(W\subseteq\gamma+1\) is any countable neighborhood of \(\gamma\).
-
-    We wish to show that \(\omega_{k+1}\) with the topology induced by
-    \(\bigcup_{\alpha<\omega_{k+1}}\omega_k\cdot(\alpha+1)\) is \(\omega\)-bounded
-    and locally countable. If
-    \(\gamma\in\omega_k\cdot(\alpha+1)\setminus\omega_k\cdot\alpha\) where
-    \(cf(\alpha)\not=\omega\), then we immediately see that it is in a clopen
-    copy of \(\omega_k\) giving us local countability
-    immediately. Otherwise, \(\gamma\) has a basic open neighborhood of the form
-    \(
-      W
-        \cup
-      f_\alpha[W]
-        \setminus
-      \omega_k\cdot(\alpha_n+1)
-    \),
-    which is obviously countable.
-
-    Let \(C\) be a countable subset of \(\omega_k\cdot(\alpha+1)\).
-    In the case that \(\alpha=\beta+1\), we may use the \(\omega\)-boundedness
-    of each part in the clopen partition \(\omega_k\cdot(\beta+1)\) and
-    \(\omega_k\cdot(\beta+2)\setminus\omega_k\cdot(\beta+1)\cong\omega_k\)
-    to conclude that the closure of \(C\) is compact.
-    Similarly, if \(cf(\alpha)>\omega\),
-    then we may use the  \(\omega\)-boundedness
-    of each part in the clopen partition
-    \(\bigcup_{\beta<\alpha}\omega_k\cdot(\beta+1)\) and
-    \(\omega_k\cdot(\alpha+1)\setminus\omega_k\cdot\alpha\cong\omega_k\)
-    to conclude that the closure of \(C\) is compact.
-
-    The remaining case is again where \(\alpha\) is the limit of increasing
-    \(\alpha_n\) for \(n<\omega\). Then
-    TODO: generalize for \(k+1\)
-    % \(
-    %   C
-    %     \subseteq
-    %   [\gamma',\gamma]
-    %     \cup
-    %   f_\alpha[[\omega_k\cdot\alpha,\gamma]]
-    % \)
-    % for some \(\omega_k\cdot\alpha\leq\gamma'<\gamma<\omega_k\cdot(\alpha+1)\).
-    % Its closure is compact:
-    % the closure operation does not add any ordinals greater than \(\gamma\),
-    % and any open cover
-    % contains another basic open neighborhood of \(\gamma\) such as
-    % \(
-    %   [\gamma'',\gamma]
-    %     \cup
-    %   f_\alpha[[\omega_k\cdot\alpha,\gamma]]
-    %     \setminus
-    %   \omega_k\cdot(\alpha_m+1)
-    % \)
-    % which misses only the compact set \([\gamma',\gamma'']\) and the
-    % closure of the countable set
-    % \(
-    %   f_\alpha[[\omega_k\cdot\alpha,\gamma]]
-    %     \cap
-    %   \omega_k\cdot(\alpha_{\min(m,n)}+1)
-    % \), which is compact by the \(\omega\)-boundedness of
-    % \(\omega_k\cdot(\alpha_{\min(m,n)}+1)\).
-
-    Finally, since every countable subset of \(\omega_{k+1}\) is contained in
-    some \(\omega_k\cdot(\alpha+1)\), we conclude \(\omega_{k+1}\) is
-    \(\omega\)-bounded.
+    TODO: write up Alan's proof
   \end{proof}
 
-  \begin{theorem*}
-    \(S'(\omega_\omega)\).
-  \end{theorem*}
+  \begin{definition}
+    A Kurepa family \(\mc K\)
+    is a family of countable sets such that for each \(A\in\mc K\),
+    \(\mc K\rest A=\{K\cap A:K\in\mc K\}\) is countable.
+  \end{definition}
+
+  \begin{corollary}
+    There exists a Kurepa family cofinal in \([\omega_k]^\omega\)
+    for each \(k<\omega\).
+  \end{corollary}
+
+  \begin{proof}
+    This is actually a corollary of an observation of Todorcevic communicated
+    by Dow in [TODO cite Gen Prog in Top I]:
+    if every Kurepa family of size at most \(\theta\)
+    extends to a cofinal Kurepa family, then the same is true of \(\theta^+\).
+    So the result follows as
+    every Kurepa family of size \(\omega\) extends to
+    the cofinal Kurepa family \([\omega]^\omega\). (TODO am I understanding
+    this right?)
+
+    We may alternatively
+    obtain the result from the previous topological argument by using the family
+    \(\mc K\) of compact sets in the constructed topology on
+    \(\omega_k\) as our witness. Of course, every Lindel\"of set in
+    a locally countable space is countable. Thus \(\mc K\)
+    is cofinal since for every countable set \(A\), \(\cl A\) is compact
+    and countable.
+    It is Kurepa since for every compact (countable) set \(A\), (TODO).
+  \end{proof}
+
+  \begin{theorem}
+    \(S'(\omega_k)\) for each \(k<\omega\).
+  \end{theorem}
+
+  \begin{proof}
+    Let \(k<\omega\), and \(\mc K\) be a cofinal Kurepa family on \(\omega_k\).
+    (TODO finish)
+  \end{proof}
 

### 2015-11-10 postdoctoral/S_prime_kappa.tex
start scaffolding results with Alan

@@
 
-  \begin{remark}
-    Scheeper's \(S(\kappa)\) requiring injections is stronger than my
-    \(S'(\kappa)\) requiring finite-to-one maps. Dow suggests that
-    \(S'(\omega_\omega)\) holds in ZFC by the following.
-  \end{remark}
+  (joint work with Alan Dow)
+
+  \begin{definition}
+    Two functions \(f,g\) are almost compatible if
+    \(\{a\in\dom f\cap\dom g:f(a)\not=g(a)\}\) is finite.
+  \end{definition}
+
+  \begin{definition}
+    \(S'(\theta)\) states that there exists a cofinal family
+    \(\mc S\subseteq[\theta]^{\omega}\) and a collection of pairwise
+    almost compatible
+    finite-to-one functions \(\{f_S\in\omega^S:S\in\mc S\}\)
+  \end{definition}
+
+  \begin{definition}
+    \(S(\theta)\) strengthens \(S'(\theta)\) by requiring the collection
+    to contain one-to-one functions.
+  \end{definition}
+
+  We wish to show that Scheeper's original \(S(\theta)\) is strictly stronger
+  than \(S'(\theta)\).
 
@@
 
+  % TODO: read through Alan's proof and fit to rest of document
           \begin{theorem}
-    For each \(k<\omega\) there exists a topology on \(\omega_k\) which
-    is \(\omega\)-bounded and locally countable.
+           For each $n\in \omega$, there is a locally countable,
+            $\omega$-bounded topology on $\omega_n$. Note
+            that this means that the closure of any set has
+            the same cardinality and weight as the set.
           \end{theorem}
 
+          To prove the theorem, we must actually prove a stronger lemma.
+
+          \begin{lemma}
+          Assume that $X$ has cardinality at most $\omega_n$ (for
+          any $n\in \omega$),
+          and is locally countable, locally compact, and the closure
+          of each set has the same cardinality as the set.
+          Then $X$ has an $\omega$-bounded extension with the
+          same properties.
+          \end{lemma}
+
             \begin{proof}
-    TODO: write up Alan's proof
+            We prove this by induction on $n$.
+            In fact, we make our inductive statement that  if $\tilde X$
+            is the extension of $X$, then  $\tilde X \setminus X$ also
+            has cardinality $\omega_n$.
+             If $n=0$,
+              then we can just take the free union of two copies of $X$
+              and then the one-point compactification.
+             So suppose $n>0$ and
+            that $X$ is such a topology on the ordinal $\omega_n$.
+            For each $\alpha<\omega_n$, the closure of the initial
+            segment $\alpha$ is bounded by some $\gamma_\alpha$.
+            Also, because $X$ is locally countable, $\gamma_\alpha$
+            can be chosen so that $\alpha$ is contained  in the interior
+            of $\gamma_\alpha$. There is a cub  $C\subset \omega_n$
+            with the property that for each $\delta\in C$ and $\alpha<\delta$,
+             $\gamma_\alpha$ is also less than $\delta$. This implies
+             that for each $\delta\in C$, the initial segment $\delta$ is
+             open, and if $\delta$ has uncountable cofinality, then
+              $\delta$ is clopen.
+
+              The proof will be easier to visualize if we now
+              identify the points of $X$ with the point set
+               $\omega_n\times \{0\}$ and we will add the points
+                $\omega_n\times \{1\}$ to create the extension.
+             By induction on $\lambda \in C$ we define a topology
+             on $\omega_n\times\{0\}\cup \lambda\times \{1\}$ so that
+             $\omega_n \times \{0\}$ is an open subset. We also ensure,
+             by induction, for each $\alpha<\lambda$,
+             the closure of $\alpha\times 2$ is an
+              $\omega$-bounded  subset of $\lambda\times 2$.
+
+          In the case that $n=1$, then  choose any sequence
+           $\lambda_n : n\in \omega$ increasing cofinal in $\lambda$.
+           If $\lambda $ is a limit in $C$, then we simply take the
+           topology we have constructed so far on $\lambda\times 2$
+           and there's nothing more needs to be done. Otherwise
+          we may assume that $\lambda_0$ is the predecessor
+          of $\lambda\in C$ and
+           we set $Y_\lambda $ to equal the countable set
+            $\overline{\lambda}\setminus \lambda$. For convenience,
+             and with no loss, we assume that $\lambda$ itself is a limit
+             of limits.
+           And we have a topology on
+           $$\lambda_0\times 2 \cup (\lambda \cup Y_\lambda)\times\{0\}~.$$
+            Recursively
+            choose clopen sets $U_n$ in this topology
+             so that $\lambda_0\times 2\subset U_0$,
+             $U_{n}\cup \lambda_{n+1}\times \{0\}$ is contained
+              $ U_{n+1}$ while $U_{n+1}$ is disjoint from $Y_\lambda$.
+              It is easy to see that we can have all the points
+              in $(\lambda\setminus \{\lambda_n : n\in\omega\})\times \{1\}$
+              be isolated, and arrange that $(\lambda_n,1) $ is the
+              point at infinity in the one-point compactification
+              $U_n\cup (\lambda_n\times \{1\})$.
+
+                Now we handle the case $n>1$ and we can shrink $C$
+                and now assume
+                that $C$ is the closure of $\{\lambda\in C : \mbox{cf}(\lambda)>\omega\}$.
+                We again proceed by induction on $\lambda\in C$.  If
+                $\lambda$ is a limit in $C$, then there is nothing to do: we
+                simply have defined an appropriate topology on
+                $\omega_n\times  \{0\}\cup \lambda\times \{1\}$ so that
+                for each $\mu\in C\cap \lambda$ with $\mbox{cf}(\mu)>\omega$,
+                 $\mu\times 2$ is a clopen $\omega$-bounded subspace.
+                In case $\lambda$ is not a limit of $C$, then $\lambda$
+                has uncountable cofinality and a predecessor $\mu\in C$.
+                We therefore have that $\lambda\times\{0\}$ is clopen
+                in $\omega_n\times \{0\}$.
+                 We apply the induction hypothesis
+                to the space $\lambda\times \{0\} \cup \mu\times 2$ to choose
+                the topology on $\lambda\times 2$.
+
             \end{proof}
@@
   \begin{definition}
-    A Kurepa family \(\mc K\)
-    is a family of countable sets such that for each \(A\in\mc K\),
-    \(\mc K\rest A=\{K\cap A:K\in\mc K\}\) is countable.
+    A Kurepa family \(\mc K\subseteq[\theta]^{\omega}\) on \(\theta\)
+    satisfies that
+    \(\mc K\rest A=\{K\cap A:K\in\mc K\}\) is countable
+    for each \(A\in[\theta]^\omega\).
   \end{definition}
@@
     So the result follows as
-    every Kurepa family of size \(\omega\) extends to
-    the cofinal Kurepa family \([\omega]^\omega\). (TODO am I understanding
-    this right?)
+    every Kurepa family \(\mc K\) of size \(\omega\) extends to
+    the cofinal Kurepa family \([\bigcup\mc K]^\omega\).
 
@@
     a locally countable space is countable. Thus \(\mc K\)
-    is cofinal since for every countable set \(A\), \(\cl A\) is compact
-    and countable.
-    It is Kurepa since for every compact (countable) set \(A\), (TODO).
+    is cofinal in \([\omega_k]^\omega\)
+    since for every countable set \(A\), \(\cl A\) is compact and countable.
+    It is Kurepa since for every countable set \(A\), let (TODO)
   \end{proof}
@@
   \begin{theorem}
-    \(S'(\omega_k)\) for each \(k<\omega\).
+    \(S'(\theta)\) holds whenever there exists a cofinal Kurepa family on \(\theta\).
   \end{theorem}
@@
   \begin{proof}
-    Let \(k<\omega\), and \(\mc K\) be a cofinal Kurepa family on \(\omega_k\).
-    (TODO finish)
+    Let \(k<\omega\), and \(\mc K=\{K_\alpha:\alpha<\kappa\}\)
+    be a cofinal Kurepa family on \(\theta\).
+    We should define \(f_\alpha:K_\alpha\to\omega\) for each \(\alpha<\kappa\).
+
+    Suppose we've defined pairwise almost compatible
+    \(\{f_\beta:\beta<\alpha\}\). To define
+    \(f_\alpha\), we first recall that \(\mc K\rest K_\alpha\) is countable,
+    so we may choose \(\beta_n<\alpha\) for \(n<\omega\) such that
+    \(
+      \{K_\beta:\beta<\alpha\}\rest K_\alpha \setminus \{\emptyset\}
+        =
+      \{K_\alpha\cap K_{\beta_n}:n<\omega\}
+    \).
+    Let \(K_\alpha=\{\delta_{i,j}:i\leq\omega,j<w_i\}\) where
+    \(w_i\leq\omega\) for each \(i\leq\omega\),
+    \(
+      K_\alpha\cap \left(K_{\beta_n}\setminus\bigcup_{m<n}K_{\beta_m}\right)
+        =
+      \{\delta_{n,j}:j<w_n\}
+    \),
+    and
+    \(
+      K_\alpha\setminus\bigcup_{n<\omega}K_{\beta_n}
+        =
+      \{
+        \delta_{\omega,j}:j<w_\omega
+      \}
+    \).
+    Then let \(f_\alpha(\delta_{n,j})=\max(n,f_{\beta_n}(\delta_{n,j}))\) for
+    \(n<\omega\) and \(f_\alpha(\delta_{\omega,j})=j\) otherwise.
+
+    We should show that \(f_\alpha\) is finite-to-one. Let \(n<\omega\).
+    We need only worry about \(\delta_{m,j}\) for \(m\leq n\) since
+    \(f_\alpha(\delta_{m,j})\geq m\). Since each
+    \(f_{\beta_m}\) is finite-to-one, \(f_{\beta_m}(\delta_{m,j})\leq n\)
+    for only finitely many \(j\). Thus \(f_\alpha\) maps to
+    \(n\) only finitely often.
+
+    We now want to demonstrate that \(f_\alpha\sim f_{\beta_n}\) for all
+    \(n<\omega\). We again need only concern ourselves with \(\delta_{m,j}\) for
+    \(m\leq n\) since otherwise \(\delta_{m,j}\not\in K_{\beta_n}\).
+    For \(m=n\), we have
+    \(f_\alpha(\delta_{n,j})=\max(n,f_{\beta_n}(\delta_{n,j}))\) which differs
+    from \(f_{\beta_n}(\delta_{n,j})\) for only the finitely many \(j\) which
+    are mapped below \(n\) by \(f_{\beta_n}\).
+    For \(m<n\) and \(\delta_{m,j}\in K_{\beta_n}\),we have
+    \(f_\alpha(\delta_{m,j})=\max(m,f_{\beta_m}(\delta_{m,j}))\) which can
+    only differ
+    from \(f_{\beta_n}(\delta_{m,j})\) for only the finitely many \(j\) which
+    are mapped below \(m\) by \(f_{\beta_m}\) or the finitely many \(j\)
+    for which the
+    almost compatible \(f_{\beta_n}\sim f_{\beta_m}\) differ.
+  \end{proof}
+
+  \begin{corollary}
+    \(S'(\omega_k)\) holds for all \(k<\omega\).
+  \end{corollary}
+
+  As noted in [TODO cite Dow],
+  Jensen's one-gap two-cardinal theorem under \(V=L\) [TODO cite] can be used
+  to show that there exist cofinal Kurepa families on every cardinal.
+
+  \begin{corollary}[\(V=L\)]
+    \(S'(\theta)\) holds for all cardinals.
+  \end{corollary}
+
+  In particular, \(S(\omega_2)\) fails under \(CH\), showing the two are
+  unique. Actually, \(CH\) is not required to have \(S(\omega_2)\) fail.
+
+  % TODO: read through Alan's proof and fit to rest of document
+  \begin{theorem}
+    Adding \(\omega_2\) Cohen reals to a model of \(CH\) forces
+    \(\mf c=\omega_2\) and \(\neg S(\omega_2)\).
+  \end{theorem}
+
+  \begin{proof}
+    TODO add Alan's proof
   \end{proof}

### 2015-11-10 postdoctoral/S_prime_kappa.tex
menger game on limits

@@
 \usepackage{../clontzDefinitions}
+
+\usepackage{tikz}
+\usetikzlibrary{matrix}
 
@@
   In particular, \(S(\omega_2)\) fails under \(CH\), showing the two are
-  unique. Actually, \(CH\) is not required to have \(S(\omega_2)\) fail.
+  distinct. Actually, \(CH\) is not required to have \(S(\omega_2)\) fail.
 
   % TODO: read through Alan's proof and fit to rest of document
+        We are going to need a technical lemma (available in Kunen).
+        \bigskip
+
+        \begin{lemma}
+        Assume that $G\subset \operatorname{Fn}(\omega_2,2)$ is a generic filter,
+         and let $\mu\in \omega_2$. Then the final model $V[G]$ can be
+         regarded as forcing  with $\operatorname{Fn}(\omega_2\setminus \mu,
+         2)$ over the model $V[G_\mu]$.
+        In addition, for each $\operatorname{Fn}(\omega_2,2)$-name $\dot A$
+        of a subset of $\omega$ (treat as a subset of $\omega\times
+        \operatorname{Fn}(\omega_2,2) $),
+        there is a canonical name $\dot A(G_\mu)$ where,
+        $$\dot A(G_\mu) = \{ (n,p\restriction [\mu,\omega_2))  :
+         (n,p)\in \dot A\ \ \mbox{and} \ \ p\restriction \mu\in G_\mu\}$$
+        and we get that the valuation of $\dot A(G_\mu)$ by the tail
+        of the generic, $G_{\omega_2\setminus \mu}$, is the same as
+        the valuation of $\dot A$ by the full generic.
+        \end{lemma}
+
         \begin{theorem}
-    Adding \(\omega_2\) Cohen reals to a model of \(CH\) forces
-    \(\mf c=\omega_2\) and \(\neg S(\omega_2)\).
+          If we add $\omega_2$ Cohen reals to a model of CH we get
+        that Scheepers' $S(\omega_2)$ (still) fails.
         \end{theorem}
@@
         \begin{proof}
-    TODO add Alan's proof
+        The forcing poset is $\operatorname{Fn}(\omega_2, 2)$.
+        Let $\{ \dot f_{A} : A\in [\omega_2]^\omega\}$ be a family of
+        names such that $\dot f_{A}$ is a one-to-one function from $A$ into
+        $\omega$. It suffices to only consider sets $A$ from the ground
+        model.
+        \bigskip
+
+        Put all the lemma  stuff in an elementary submodel $M$ of the universe
+        (technically of $H(\kappa)$,  or of $V_\kappa$,
+         for some large $\kappa$). Standard methods says that we can assume that
+         $|M|=\omega_1 =\mathfrak c$ and that $M^\omega\subset M$ (which means
+         that every countable subset of $M$ is a member of $M$).
+        \bigskip
+
+        Let $\lambda = M\cap \omega_2$ (same as the supremum of $M\cap
+        \omega_2$). Consider the name  $\dot f_{[\lambda,\lambda+\omega)}$.
+        What is such a name?  We can assume that it is a set of pairs
+         of the form $( (\lambda+k,m), p)$ where $p\in \mathop{Fn}(\omega_2,
+         2)$ and, of course, $k,m\in \omega$. This is (almost) equivalent to
+         saying
+         that $p$ forces that $\dot f_{[\lambda,\lambda+\omega)}(\lambda+k) =
+         m$. We don't take all such $p$, in fact for each $k,m$ it is enough
+        to take a
+         countable set of such $p$ to get an equivalent name
+         (Kunen calls it a nice name if we take, for each $k,m$ an
+        antichain that is maximal among such conditions).
+        Given any such name $\dot f$, let $\operatorname{supp}(\dot f)$
+        denote the union of the domains of conditions $p$ appearing in the
+        name.
+
+         Also let $Y$ equal $\operatorname{supp}(\dot
+         f_{[\lambda,\lambda+\omega)})\setminus \lambda$.
+         Let $\delta$ denote the order type of
+         $Y$ and let the 2-parameter notation
+         $\varphi_{\mu,\lambda}$ be the order-preserving function from
+        $\mu\cup Y$ onto  the ordinal $\mu+\delta$.  This lifts canonically to
+        an order-preserving bijection $\varphi_{\mu,\lambda}:
+        \operatorname{Fn}(\mu\cup Y,2) \mapsto
+        \operatorname{Fn}(\mu+\delta,2)$.
+        Similarly, we make sense of the name
+         $\varphi_{\mu,\lambda}(\dot f_{[\lambda,\lambda+\omega)})$, call it $F_M$.
+        Here simply, for each tuple $(~(k,m)~, p)\in \dot
+        f_{[\lambda,\lambda+\omega)}$,
+         we have that $(~(k,m)~,\varphi_{\mu,\lambda}(p))$ is in $F_M$.
+        Again, let $\varphi_{\mu,\lambda}(\dot f_{[\lambda,\lambda+\omega)})$
+        be interpreted in the above sense as giving $F_M$ (which is an element
+        of $M$).  Note that we do not regard $\delta$ as fixed here, but
+        rather simply depending on the $\operatorname{supp}(\dot
+        f_{[\lambda,\lambda+\omega)})$ described above. Other values
+        replacing $\lambda>\mu$ will result in their own set $Y$
+        and canonical map $\varphi_{\mu,\lambda}$; but one thing we do have to
+        assume (or arrange) for other values $\alpha$ replacing $\lambda$
+        is that $\operatorname{supp}(\dot f_{[\alpha,\alpha+\omega)})$
+        intersected with
+        $\alpha$ is contained in $\mu$.
+
+        Now the object $F_M$ is an
+        element of $M$, and $M$ believes this statement is true:
+        $$
+        (\forall \beta\in\omega_2)~ (\exists \beta<\lambda\in \omega_2)~~~
+        \operatorname{supp}(\dot f_{[\lambda,\lambda+\omega)})
+        \cap \lambda\subset \mu \ \ \mbox{and}\ \
+        F_M = \varphi_{\mu,\lambda}(\dot f_{[\lambda,\lambda+\omega)})$$
+
+        But now, this  means that,
+        not only is there  an $\alpha\in M$,
+        $ F_M = \varphi_{\mu,\alpha}(\dot f_{[\alpha,\alpha+\omega)})$
+        but also that there is an increasing sequence
+         $\{\alpha_\xi : \xi  \in \omega_1\}\subset \lambda$ of
+         such $\alpha$'s satisfying that, for each $\xi$
+        we have that $\operatorname{supp}(\dot
+        f_{[\alpha_\xi,\alpha_\xi+\omega)})$ is contained in $\alpha_{\xi+1}$.
+
+        Choose such a sequence.
+         This means that if we let $A = \bigcup_{n>0} [\alpha_n,\alpha_n+\omega)$ we
+         have the name $\dot f_A$ in $M$. This then means that all
+         the $( (\beta,m) , p)$ appearing in $\dot f_A$ have the property
+         that $\mathop{dom}(p)$ is contained in $M$.
+        There is, within $M$, a name $\dot g$ satisfying that
+         $\dot f_A(\alpha_n+k) = \dot f_{[\alpha_n,\alpha_n+\omega)}(\alpha_n+k)$
+        for all $k >\dot g(n)$.
+
+        \bigskip
+
+        We now apply the above Lemma using $\mu = \mu_0$ and we are now
+        working in the extension $V[G_\mu]$. We will abuse the notation
+        and use $\dot f_{[\alpha_n,\alpha_n+\omega)}$ instead of
+          $\dot f_{[\alpha_n,\alpha_n+\omega)}(G_{\mu})$ as defined in
+          the Lemma.
+        We work for a contradiction. Something special has now happened,
+         namely,  the supports of the names $\{
+        \dot f_{[\alpha_n, \alpha_n+\omega)} :  0< n<\omega\}$ are pairwise disjoint
+        and also disjoint from the support of the name
+         $\dot f_{[\lambda,\lambda+\omega)}$ (under the same convention about
+         $G_\mu$.  And not only that, these names are pairwise isomorphic (in
+         the way that they all map to $F_M$).
+
+        \bigskip
+
+        Since $A$ is disjoint from $[\lambda,\lambda+\omega)$,
+        there must be an integer $\ell$
+        together with a condition
+         $q\in \mathop{Fn}(\omega_2\setminus \mu,2)$ satisfying that for all
+         $n>\ell$ , $q$ forces that
+
+        \centerline{
+         ``if $k>\dot g(n)$ (since  $\alpha_n+k\in A$) then
+         $\dot f_{[\alpha_n,\alpha_n+\omega)}(\alpha_n+k) \neq
+        \dot f_{[\lambda,\lambda+\omega)}(\lambda +k)$''.}
+
+        Choose $n$ large enough so that $\mathop{dom}(q) \cap [\alpha_n,
+        \mu_{n+1})$ is
+        empty.
+         Choose $q_1<q\restriction \lambda$ (in $M$) so that
+        $$ \varphi_{\mu,\alpha_n}(q_1\restriction \operatorname{supp}(
+         \dot f_{[\alpha_n,\alpha_n+\omega)}) =
+        \varphi_{\mu,\lambda}(q\restriction \operatorname{supp}(
+         \dot f_{[\lambda,\lambda+\omega)}) $$
+        and then (again in $M$) choose $q_2 < q_1$
+        so that it both forces a value
+         $L$ on $\ell+\dot g(n)$
+        and subsequently forces a value $m$ on
+         $\dot f_{[\alpha_n, \alpha_n+\omega)}(\alpha_n+L+1)$.
+        But now, again calculate
+        $$ q_3 = \varphi_{\mu,\lambda}^{-1} \circ \varphi_{\mu,\alpha_n}
+        (q_2\restriction \operatorname{supp}(\dot
+        f_{[\alpha_n,\alpha_n+\omega)}))$$
+        and, by the isomorphisms, we have that $q_3$ forces that
+         $\dot f_{[\lambda,\lambda+\omega)}(\lambda+L+1) = m$.
+
+        Technically (or with more care)  all of this is taking place in the
+        poset $\operatorname{Fn}(\omega_2\setminus \mu,2)$ and this means
+        that $q_3$ and $q$ are all compatible with each other.
+
+        Follow
+        the bouncing ball: it suffices to consider
+         $q(\beta)=e$ and to assume that $q_3(\beta)$ is defined.
+        Since $q_3(\beta)$ is defined, we have that
+        there is a  $\beta'\in\mathop{dom}(q_2)$ such that $
+         \varphi_{\mu,\lambda}(\beta) = \varphi_{\mu,\alpha_n}(\beta')$,
+        and that $q_3(\beta) = q_2(\beta')$.
+        But, by definition of $q_1$, $\beta'\in\mathop{dom}(q_1)$
+        and even  that $q_1(\beta') = q(\beta)$.
+         Then, since $q_2<q_1$, we have that $q_2(\beta')=q_1(\beta') =
+         q(\beta)$. This completes the circle that $q_3(\beta) = q(\beta)$.
+        \bigskip
+
+        Finally, our contradiction is that $q_3\cup q_2\cup q$
+        forces that
+         $k=L+1$ violates the quoted statement above.
         \end{proof}
 
+  On the other hand, it's also consistent that \(S'(\theta)\) can fail.
+
+  \begin{theorem}
+    There's a model where \(S'(\omega_\omega)\)
+    fails? (TODO: get Alan to send this argument.)
+  \end{theorem}
+
+  \section*{Applications!}
+
+  \begin{figure}[h]
+\begin{center}
+\begin{tikzpicture}
+  \matrix (m) [matrix of math nodes,row sep=3em,column sep=1em,minimum width=2em]
+  {
+    &
+    \pl F \kmarkwin2\menGame{\oneptlind\kappa} &
+    \pl F \kmarkwin2\schFillIntGame\kappa \\
+
+    S'(\kappa) &
+    \pl F \kmarkwin2\schFillInitialGame\kappa &
+    \pl F \kmarkwin2\schFillGame\kappa \\
+
+    &
+    &
+    \pl F \ktactwin2\schFillStrictGame\kappa \\
+  };
+  \path[>=latex,->]
+    (m-2-1) edge (m-1-2)
+    (m-2-1) edge (m-2-2)
+    (m-2-1) edge (m-3-3)
+    (m-1-2) edge (m-2-2)
+    (m-1-3) edge (m-2-3)
+    (m-3-3) edge (m-2-3);
+  \path[>=latex,<->]
+    (m-1-2) edge (m-1-3)
+    (m-2-2) edge (m-2-3);
+\end{tikzpicture}
+\end{center}
+\caption{Diagram of Scheeper/Menger game implications with \(S'(\kappa)\)}
+\label{GamesDiagram2}
+\end{figure}
+
+  \begin{theorem}
+    Figure \ref{GamesDiagram2} holds. (Proven in [TODO cite])
+  \end{theorem}
+
+  It was left open if these implications can be reversed. The answer is
+  consistently no.
+
+  \begin{theorem}
+    Let \(\alpha\) be the limit of increasing ordinals \(\beta_n\) for \(n<\omega\).
+    If \(\pl F \kmarkwin2\schFillIntGame{\omega_{\beta_n}}\) for all
+    \(n<\omega\), then \(\pl F\kmarkwin2\schFillIntGame{\omega_\alpha}\).
+  \end{theorem}
+
+  \begin{proof}
+    Let \(\sigma_n\) be a winning \(2\)-mark for \(\pl F\) in
+    \(\schFillIntGame{\omega_{\beta_n}}\). Define the \(2\)-mark \(\sigma\)
+    for \(\pl F\) in \(\schFillIntGame{\omega_\alpha}\) as follows:
+    \[
+      \sigma(\<C\>,0)
+        =
+      \sigma_0(\<C\cap\omega_{\beta_0}\>,0)
+    \]
+    \[
+      \sigma(\<C,D\>,n+1)
+        =
+      \sigma_{n+1}(\<D\cap\omega_{\beta_{n+1}}\>,0)
+        \cup
+      \bigcup_{m\leq n}
+      \sigma_m(\<C\cap\omega_{\beta_m},D\cap\omega_{\beta_m}\>,n-m+1)
+    \]
+
+    Let \(\<C_0,C_1,\dots\>\) be an attack by
+    \(\pl C\) in \(\schFillIntGame{\omega_\alpha}\), and
+    \(\alpha\in\bigcap_{n<\omega}C_n\).
+    Choose \(N<\omega\) with \(\alpha<\omega_{\beta_{N+1}}\). Consider the
+    attack
+    \(\<C_{N+1}\cap\omega_{\beta_{N+1}},C_{N+2}\cap\omega_{\beta_{N+1}},\dots\>\)
+    by \(\pl C\) in \(\schFillIntGame{\omega_{\beta_{N+1}}}\). Since
+    \(\sigma_{N+1}\) is a winning strategy and
+    \(\alpha\in\bigcap_{n<\omega}C_{N+n+1}\cap\omega_{\beta_{N+1}}\), either
+    \(\alpha\in\sigma_{N+1}(\<C_{N+1}\cap\omega_{\beta_{N+1}}\>,0)\) and thus
+    \(\alpha\in\sigma(\<C_N,C_{N+1}\>,N+1)\), or
+    \(
+      \alpha
+        \in
+      \sigma_{N+1}(
+        \<C_{N+M+1}\cap\omega_{\beta_{N+1}},C_{N+M+2}\cap\omega_{\beta_{N+1}}\>
+        ,M+1
+      )
+    \)
+    for some \(M<\omega\) and thus
+    \(
+      \alpha
+        \in
+      \sigma(
+        \<C_{N+M+1},C_{N+M+2}\>,
+        N+M+2
+      )
+    \). Thus \(\sigma\) is a winning strategy.
+  \end{proof}
 \end{document}

### 2015-11-11 postdoctoral/S_prime_kappa.tex
add topological stuff

@@
 
+  \begin{question}
+    Is \(S'(\theta)\) equivalent to having a Kurepa family on \(\theta\)?
+  \end{question}
+
   \section*{Applications!}
@@
     Figure \ref{GamesDiagram2} holds. (Proven in [TODO cite])
+    (Actually, TODO double-check that it works with just S', particularly
+    the strict game)
   \end{theorem}
@@
   \end{proof}
+
+  \begin{theorem}
+    Let \(\alpha\) be the limit of increasing ordinals \(\beta_n\) for \(n<\omega\).
+    If \(\pl F \kmarkwin2\schFillInitialGame{\omega_{\beta_n}}\) for all
+    \(n<\omega\), then \(\pl F\kmarkwin2\schFillInitialGame{\omega_\alpha}\).
+  \end{theorem}
+
+  \begin{proof}
+    Let \(\sigma_n\) be a winning \(2\)-mark for \(\pl F\) in
+    \(\schFillInitialGame{\omega_{\beta_n}}\). Define the \(2\)-mark \(\sigma\)
+    for \(\pl F\) in \(\schFillInitialGame{\omega_\alpha}\) as follows:
+    \[
+      \sigma(\<C\>,0)
+        =
+      \sigma_0(\<C\cap\omega_{\beta_0}\>,0)
+    \]
+    \[
+      \sigma(\<C,D\>,n+1)
+        =
+      \sigma_{n+1}(\<D\cap\omega_{\beta_{n+1}}\>,0)
+        \cup
+      \bigcup_{m\leq n}
+      \sigma_m(\<C\cap\omega_{\beta_m},D\cap\omega_{\beta_m}\>,n-m+1)
+    \]
+
+    Let \(\<C_0,C_1,\dots\>\) be an attack by
+    \(\pl C\) in \(\schFillInitialGame{\omega_\alpha}\), and
+    \(\alpha\in C_0\).
+    Choose \(N<\omega\) with \(\alpha<\omega_{\beta_{N+1}}\). Consider the
+    attack
+    \(\<C_{N+1}\cap\omega_{\beta_{N+1}},C_{N+2}\cap\omega_{\beta_{N+1}},\dots\>\)
+    by \(\pl C\) in \(\schFillInitialGame{\omega_{\beta_{N+1}}}\). Since
+    \(\sigma_{N+1}\) is a winning strategy and
+    \(\alpha\in C_{N+1}\cap\omega_{\beta_{N+1}}\), either
+    \(\alpha\in\sigma_{N+1}(\<C_{N+1}\cap\omega_{\beta_{N+1}}\>,0)\) and thus
+    \(\alpha\in\sigma(\<C_N,C_{N+1}\>,N+1)\), or
+    \(
+      \alpha
+        \in
+      \sigma_{N+1}(
+        \<C_{N+M+1}\cap\omega_{\beta_{N+1}},C_{N+M+2}\cap\omega_{\beta_{N+1}}\>
+        ,M+1
+      )
+    \)
+    for some \(M<\omega\) and thus
+    \(
+      \alpha
+        \in
+      \sigma(
+        \<C_{N+M+1},C_{N+M+2}\>,
+        N+M+2
+      )
+    \). Thus \(\sigma\) is a winning strategy.
+  \end{proof}
+
+  \begin{corollary}
+    It is consistent that \(S'(\omega_\omega)\) fails,
+    but as \(S'(\omega_k)\) holds for all \(k<\omega\), we have
+    \(\pl F\kmarkwin2\schFillIntGame{\omega_\omega}\) and
+    \(\pl F\kmarkwin2\schFillInitialGame{\omega_\omega}\).
+  \end{corollary}
+
+  A tricky topological question: does \(\pl F\win\menGame{X}\) imply
+  \(\pl F\kmarkwin2\menGame{X}\)?
+  (C showed that )
+  Under \(V=L\), we cannot hope to find
+  a counterexample using \(X=\oneptlind\kappa\) since
+  \(S'(\kappa)\) and thus \(\pl F\kmarkwin2\schFillIntGame{\kappa}\)
+  always holds.
+
+  \begin{definition}
+    Let \(R_\omega\) be the real numbers with the topology of the usual
+    open intervals with countably many elements removed.
+  \end{definition}
+
+  \begin{theorem}
+    \(\pl F\win\menGame{R_\omega}\).
+    If there exists a Kurepa family on the reals, then
+    \(\pl F\kmarkwin2\menGame{R_\omega}\).
+  \end{theorem}
+
 \end{document}

### 2015-11-12 postdoctoral/gamma_functions.tex
partial proof of normal product result

@@
   \end{definition}
-
-  \begin{definition}
-    For any LOTS \(M\) with minimum element \(0\),
-    let \(\nu\) be the V-map on \(M\) where \(\nu(0)=K\) and \(\nu(t)=\{t\}\)
-    for \(t>0\).
-  \end{definition}
-
-  Note for \(K=M=2\) that \(\gamma=\nu\).
 
@@
 
-  \bigskip
+  \newpage
+
+  \begin{definition}
+    For any \(M\) containing a point \(0\),
+    let \(\nu\) be the V-map on \(M\) where \(\nu(0)=M\) and \(\nu(t)=\{t\}\)
+    for \(t>0\).
+  \end{definition}
+
+  Note for \(M=2\) that \(\nu=\gamma\).
+
+  \begin{corollary}
+    \(\varprojlim\{2,\nu,L\}\cong\check L\).
+  \end{corollary}
+
+  \begin{theorem}
+    If \(M\) is \(T_2\) or regular, then
+    \(
+      \varprojlim\{M,\nu,L\}\setminus\{\vect 0\}
+        \cong
+      (\check L\setminus\{\emptyset\})\times(M\setminus\{0\})
+    \) with the usual product topology.
+  \end{theorem}
+
+  \begin{proof}
+    Each point in \(\varprojlim\{M,\nu,L\}\setminus\{\vect 0\}\) is of the
+    form \(\vect x_{A,m}\) where \(A\in\check L\setminus\{\emptyset\}\)
+    and \(m\in M\setminus\{0\}\) defined by \(\vect x_{A,m}(l)=m\) for \(l\in A\)
+    and \(x_{A,m}(l)=0\) otherwise.
+
+    We claim that the bijection \(\theta(\vect x_{A,m})=\<A,m\>\) is a
+    homeomorphism. Note that basic open sets of
+    \(\varprojlim\{M,\nu,L\}\) are of the form \([U,F]\) where \(U(l)\) is
+    an open subset of \(M\) for each \(l\in F\in[L]^{<\omega}\).
+
+    Consider the point \(\<C,m\>\) in the basic open set \(V\times W\) in
+    \((\check L\setminus\{\emptyset\})\times(M\setminus\{0\})\). Note that
+    \(V\) is either of the form \((A,L]\) or \((A,B)\), and we may choose
+    \(l_0\in C\setminus A\). We also may assume that \(W\) misses an open
+    neighborhood \(Z\) of \(0\) as \(M\) is \(T_2\) or regular.
+    In the case that \(V=(A,L]\) we let \(U(l_0)=W\).
+    Then since \(l_0\in C\) and \(m\in W=U(l_0)\), it follows that
+    \(\vect x_{C,m}\in[U,\{l_0\}]\).
+    For any \(\vect x_{D,n}\in[U,\{l_0\}]\) we have that \(\vect x_{D,n}(l_0)=n\in W\);
+    in particular, it's nonzero. So
+    \(A\subsetneq (\leftarrow,l_0]\subseteq D\), putting \(D\in(A,L]=V\). Thus
+    \(\theta(\vect x_{D,n})=\<D,n\>\in V\times W\).
+
+    In the case that \(V=(A,B)\), we may also choose \(l_1\in B\setminus C\).
+    We again let \(U(l_0)=W\), and we also let \(U(l_1)=Z\). Then as
+    \(\vect x_{C,m}(l_0)=m\in W=U(l_0)\) and
+    \(\vect x_{C,m}(l_1)=0\in Z=U(l_1)\), we have shown
+    \(\vect x_{C,m}\in[U,\{l_0,l_1\}]\). For any \(\vect x_{D,n}\in[U,\{l_0,l_1\}]\),
+    \(\vect x_{D,n}(l_0)\in W\) and \(\vect x_{D,n}(l_1)\in Z\).
+    This shows that \(\vect x_{D,n}(l_0)=n\in W\) and \(\vect x_{D,n}(l_1)=0\), so
+    \(
+      A
+        \subsetneq
+      (\leftarrow,l_0]
+        \subseteq
+      D
+        \subsetneq
+      (\leftarrow,l_1]
+        \subseteq
+      B
+    \), putting \(D\in(A,B)=V\). Thus
+    \(\theta(\vect x_{D,n})=\<D,n\>\in V\times W\).
+
+    On the other hand, consider the point \(\vect x_{C,m}\) in the basic
+    open set \([U,F]\). It follows that \(m\in U(l)\) for all \(l\in C\cap F\),
+    and \(0\in U(l)\) for all \(l\in F\setminus C\).
+
+    TODO finish
+  \end{proof}
+
+  \newpage
 

### 2015-11-13 postdoctoral/gamma_functions.tex
got nu product lemma

@@
 
-  \begin{theorem}
-    If \(M\) is \(T_2\) or regular, then
+  \begin{lemma}
+    If \(M\) is \(T_2\), then
     \(
@@
     \) with the usual product topology.
-  \end{theorem}
+  \end{lemma}
 
@@
     Each point in \(\varprojlim\{M,\nu,L\}\setminus\{\vect 0\}\) is of the
-    form \(\vect x_{A,m}\) where \(A\in\check L\setminus\{\emptyset\}\)
-    and \(m\in M\setminus\{0\}\) defined by \(\vect x_{A,m}(l)=m\) for \(l\in A\)
-    and \(x_{A,m}(l)=0\) otherwise.
+    form \(\vect x_{C,m}\) where \(C\in\check L\setminus\{\emptyset\}\)
+    and \(m\in M\setminus\{0\}\) defined by \(\vect x_{C,m}(l)=m\) for \(l\in C\)
+    and \(x_{C,m}(l)=0\) otherwise.
 
-    We claim that the bijection \(\theta(\vect x_{A,m})=\<A,m\>\) is a
+    We claim that the bijection \(\theta(\vect x_{C,m})=\<C,m\>\) is a
     homeomorphism. Note that basic open sets of
@@
     \(l_0\in C\setminus A\). We also may assume that \(W\) misses an open
-    neighborhood \(Z\) of \(0\) as \(M\) is \(T_2\) or regular.
+    neighborhood \(Z\) of \(0\) as \(M\) is \(T_2\).
+
     In the case that \(V=(A,L]\) we let \(U(l_0)=W\).
@@
     On the other hand, consider the point \(\vect x_{C,m}\) in the basic
-    open set \([U,F]\). It follows that \(m\in U(l)\) for all \(l\in C\cap F\),
+    open set \([U,F]\) of
+    \(\varprojlim\{M,\nu,L\}\setminus\{\vect 0\}\).
+    It follows that \(m\in U(l)\) for all \(l\in F\cap C\),
     and \(0\in U(l)\) for all \(l\in F\setminus C\).
 
-    TODO finish
+    If \(F\subseteq C\), then let \(l_0\) be the maximum element of \(F\) and
+    \(U'=\bigcap_{l\in F}U(l)\). Note \(\<C,m\>\in((\leftarrow,l_0),L]\times U'\).
+    So let \(\<D,n\>\in((\leftarrow,l_0),L]\times U'\). Since \(l_0\in D\),
+    \(\vect x_{D,n}(l_0)=n\in U'\). Since \(n\not=0\), we have
+    \(\vect x_{D,n}(l)=n\in U'\subseteq U(l)\) for all \(l\in F\), so
+    \(\vect x_{D,n}\in[U,F]\).
+
+    If \(F\cap C=\emptyset\), then
+    let \(l_1\) be the minimum element of \(F\setminus C\).
+    Note \(\<C,m\>\in(\emptyset,(\leftarrow,l_1])\times (M\setminus \{0\})\).
+    So let \(\<D,n\>\in(\emptyset,(\leftarrow,l_1])\times (M\setminus \{0\})\).
+    Since \(l_1\not\in D\), \(\vect x_{D,n}(l)=0\in U(l)\) for all \(l\in F\),
+    giving \(\vect x_{D,n}\in[U,F]\).
+
+    Otherwise, let \(l_0\) be the maximum element of \(F\cap C\) and
+    \(l_1\) be the minimum element of \(F\setminus C\).
+    Let \(U'\subseteq \bigcap_{l\in C\cap F}U(l)\) and
+    \(U''\subseteq \bigcap_{l\in F\setminus C}U(l)\).
+    Note \(\<C,m\>\in((\leftarrow,l_0),(\leftarrow,l_1])\times U'\).
+    So let \(\<D,n\>\in((\leftarrow,l_0),(\leftarrow,l_1])\times U'\).
+    Since \(l_0\in D\) and \(l_1\not\in D\), we have
+    \(\vect x_{D,n}(l_0)=n\in U'\) and
+    \(\vect x_{D,n}(l_1)=0\in U''\). Furthermore,
+    \(\vect x_{D,n}(l)=n\in U'\subseteq U(l)\) for all \(l\in F\cap C\), and
+    \(\vect x_{D,n}(l)=0\in U''\subseteq U(l)\) for all \(l\in F\setminus C\),
+    so \(\vect x_{D,n}\in[U,F]\).
   \end{proof}

### 2015-11-13 postdoctoral/gamma_functions.tex
got the nu result

@@
 
+  \begin{theorem}
+    If \(M\) is \(T_2\), then
+    \(
+      \varprojlim\{M,\nu,L\}
+        \cong
+      (\check L\times M)/\sim
+    \) with the usual product topology, where \(\sim\) identifies every
+    point in \(\{\emptyset\}\times M\cup\check L\times \{0\}\).
+  \end{theorem}
+
+  \begin{proof}
+    We will extend \(\theta\) as defined in the previous lemma so that
+    \(\theta(\vect 0)\) is sent to the points identified in
+    \(\{\emptyset\}\times M\cup\check L\times \{0\}\).
+
+    Consider the basic open neighborhood \([U,F]\) of \(\vect 0\) in
+    \(\varprojlim\{M,\nu,L\}\). Let \(l_1\) be the least element of \(F\),
+    and \(U'=\bigcap_{l\in F}U(l)\). Note that
+    \(
+      \{\emptyset\}\times M\cup\check L\times \{0\}
+        \subseteq
+      [\emptyset,(\leftarrow,l_1])\times M
+      \cup
+      \check L\times U'
+    \). So let
+    \(
+      \vect x_{C,m}
+        \in
+      [\emptyset,(\leftarrow,l_1])\times M
+    \),
+    and note that as \(l_1\not\in C\), \(\vect x_{C,m}(l)=0\in U(l)\) for all
+    \(l\in F\), and thus \(\vect x_{C,m}\in[U,F]\).
+    Likewise if we let
+    \(
+      \vect x_{C,m}
+        \subseteq
+      \check L\times U'
+    \),
+    we have that \(x_{C,m}(l)\in U'\subseteq U(l)\) for all \(l\in L\), and
+    thus \(\vect x_{C,m}\in[U,F]\).
+
+    Now in \((\check L\times M)/\sim\)
+    consider the basic open set formed by the union of
+    \(V\times M\) containing \(\{\emptyset\}\times M\) and
+    \(\check L\times W\) containing \(\check L\times \{0\}\).
+    \(V=[\emptyset,B)\) for some nonempty leftward set \(B\),
+    so choose \(l_0\in B\) and note that as
+    \((\leftarrow,l_0]\subseteq B\) we have
+    \([\emptyset,(\leftarrow,l_0])\subseteq[\emptyset,B)=V\).
+    So let \(U(l_0)=W\) and note \(\vect 0\in[U,\{l_0\}]\). For any
+    \(\vect x_{C,m}\in[U,\{l_0\}]\), we have two cases.
+
+    If \(l_0\in C\), then \(\vect x_{C,m}(l)=m\in U(l_0)=W\) for all \(l\in C\),
+    and \(\vect x_{C,m}(l)=0\in W\) otherwise. Thus
+    \(\<C,m\>\in\check L\times W\).
+
+    Otherwise \(l_0\not\in C\), and thus \(C\subsetneq(\leftarrow,l_0]\).
+    Then as \(C\in [\emptyset,(\leftarrow,l_0])\subseteq V\),
+    we have \(\<C,m\>\in V\times M\).
+    \end{proof}
+
   \newpage

### 2015-11-13 postdoctoral/gamma_functions.tex
abstracted inverse limits with uncountable indices are trivial or nonmetrizable

@@
 \newcommand{\vect}{\vec}
+
+\usepackage{stmaryrd}
+
+\newcommand{\lb}{\llbracket}
+\newcommand{\rb}{\rrbracket}
 
@@
     (or \(\cl(\cap S)\)).
+  \end{proof}
+
+  \begin{theorem}
+    \(\check L\) is metrizable if and only if \(L\) is countable.
+  \end{theorem}
+
+  \begin{proof}
+    If \(L\) is uncountable, let \(\mc B\) be a base for \(\check L\).
+    For each \(l\in L\), there is some neighborhood \(B_l\in\mc B\) of
+    \((\leftarrow,l)\) which is a subset of
+    \([\emptyset,(\leftarrow,l])=[\emptyset,(\leftarrow,l)]\). Each \(B_l\)
+    is unique, so \(\check L\) is compact but not second countable,
+    and therefore nonmetrizable.
+
+    If \(L\) is countable, then note that the union of
+    \(\mc S=\{((\leftarrow,l),L]:l\in L\}\) and
+    \(\mc T=\{[\emptyset,(\leftarrow,l]):l\in L\}\)
+    generates a countable base for \(\check L\). Thus \(\check L\) is
+    compact second-countable, and therefore metrizable.
   \end{proof}
@@
     is of the form
-    \([U,F]\) where \(U(l)\) is an open interval in \(M\) for each
+    \(\lb U,F \rb\) where \(U(l)\) is an open interval in \(M\) for each
     \(l\in F\in [L]^{<\omega}\), and
-    \([U,F]=\{\vect x:l\in F\Rightarrow\vect x(l)\in U(l)\}\).
-    If we assume that \([U,F]\) is non-empty, one of the following
+    \(\lb U,F\rb=\{\vect x:l\in F\Rightarrow\vect x(l)\in U(l)\}\).
+    If we assume that \(\lb U,F \rb\) is non-empty, one of the following
     must hold:
@@
         \(U[l_0]=(a,b)\) for some \(l_0\in F\).
-        Then \([U,F]=[U,\{l_0\}]\), and note that
+        Then \(\lb U,F\rb=\lb U,\{l_0\}\rb \), and note that
         \(
-          [U,\{l_0\}]
+          \lb U,\{l_0\}\rb
             =
@@
         \(U(l_0)=(a,1]\) and \(U(l_1)=[0,b)\) for some \(l_0<l_1\in L\)
-        and \([U,F]=[U,\{l_0,l_1\}]\). Then
-        \([U,\{l_0,l_1\}]=(\vect x_{l_0,a},\vect x_{l_1,b})\).
+        and \(\lb U,F\rb=\lb U,\{l_0,l_1\}\rb \). Then
+        \(\lb U,\{l_0,l_1\}\rb =(\vect x_{l_0,a},\vect x_{l_1,b})\).
     \end{itemize}
@@
         \(U(l_0)=(0,1]\), \(U(l_1)=[0,v(\vect z))\) and note
-        \(\vect y\in[U,\{l_0,l_1\}]\subseteq(\vect x,\vect z)\).
+        \(\vect y\in\lb U,\{l_0,l_1\}\rb \subseteq(\vect x,\vect z)\).
       \item
@@
         so let \(U(l_0)=(0,1]\), \(U(l_1)=[0,v(\vect z))\) and note
-        \(\vect y\in[U,\{l_0,l_1\}]\subseteq(\vect x,\vect z)\).
+        \(\vect y\in\lb U,\{l_0,l_1\}\rb \subseteq(\vect x,\vect z)\).
       \item
@@
         so let \(U(l_0)=(v(\vect x),1]\), \(U(l_1)=[0,v(\vect z))\) and note
-        \(\vect y\in[U,\{l_0,l_1\}]\subseteq(\vect x,\vect z)\).
+        \(\vect y\in\lb U,\{l_0,l_1\}\rb \subseteq(\vect x,\vect z)\).
       \item
@@
         so let \(U(l_0)=(v(\vect x),v(\vect z))\) and note
-        \(\vect y\in[U,\{l_0\}]=(\vect x,\vect z)\).
+        \(\vect y\in\lb U,\{l_0\}\rb =(\vect x,\vect z)\).
     \end{itemize}
@@
     homeomorphism. Note that basic open sets of
-    \(\varprojlim\{M,\nu,L\}\) are of the form \([U,F]\) where \(U(l)\) is
+    \(\varprojlim\{M,\nu,L\}\) are of the form \(\lb U,F \rb\) where \(U(l)\) is
     an open subset of \(M\) for each \(l\in F\in[L]^{<\omega}\).
@@
     Then since \(l_0\in C\) and \(m\in W=U(l_0)\), it follows that
-    \(\vect x_{C,m}\in[U,\{l_0\}]\).
-    For any \(\vect x_{D,n}\in[U,\{l_0\}]\) we have that \(\vect x_{D,n}(l_0)=n\in W\);
+    \(\vect x_{C,m}\in\lb U,\{l_0\}\rb \).
+    For any \(\vect x_{D,n}\in\lb U,\{l_0\}\rb \) we have that \(\vect x_{D,n}(l_0)=n\in W\);
     in particular, it's nonzero. So
@@
     \(\vect x_{C,m}(l_1)=0\in Z=U(l_1)\), we have shown
-    \(\vect x_{C,m}\in[U,\{l_0,l_1\}]\). For any \(\vect x_{D,n}\in[U,\{l_0,l_1\}]\),
+    \(\vect x_{C,m}\in\lb U,\{l_0,l_1\}\rb \). For any \(\vect x_{D,n}\in\lb U,\{l_0,l_1\}\rb \),
     \(\vect x_{D,n}(l_0)\in W\) and \(\vect x_{D,n}(l_1)\in Z\).
@@
     On the other hand, consider the point \(\vect x_{C,m}\) in the basic
-    open set \([U,F]\) of
+    open set \(\lb U,F \rb\) of
     \(\varprojlim\{M,\nu,L\}\setminus\{\vect 0\}\).
@@
     \(\vect x_{D,n}(l)=n\in U'\subseteq U(l)\) for all \(l\in F\), so
-    \(\vect x_{D,n}\in[U,F]\).
+    \(\vect x_{D,n}\in\lb U,F\rb\).
 
@@
     Since \(l_1\not\in D\), \(\vect x_{D,n}(l)=0\in U(l)\) for all \(l\in F\),
-    giving \(\vect x_{D,n}\in[U,F]\).
+    giving \(\vect x_{D,n}\in\lb U,F\rb\).
 
@@
     \(\vect x_{D,n}(l)=0\in U''\subseteq U(l)\) for all \(l\in F\setminus C\),
-    so \(\vect x_{D,n}\in[U,F]\).
+    so \(\vect x_{D,n}\in\lb U,F\rb\).
   \end{proof}
@@
 
-    Consider the basic open neighborhood \([U,F]\) of \(\vect 0\) in
+    Consider the basic open neighborhood \(\lb U,F]\) of \(\vect 0\) in
     \(\varprojlim\{M,\nu,L\}\). Let \(l_1\) be the least element of \(F\),
@@
     and note that as \(l_1\not\in C\), \(\vect x_{C,m}(l)=0\in U(l)\) for all
-    \(l\in F\), and thus \(\vect x_{C,m}\in[U,F]\).
+    \(l\in F\), and thus \(\vect x_{C,m}\in\lb U,F\rb\).
     Likewise if we let
@@
     we have that \(x_{C,m}(l)\in U'\subseteq U(l)\) for all \(l\in L\), and
-    thus \(\vect x_{C,m}\in[U,F]\).
+    thus \(\vect x_{C,m}\in\lb U,F\rb\).
 
@@
     \([\emptyset,(\leftarrow,l_0])\subseteq[\emptyset,B)=V\).
-    So let \(U(l_0)=W\) and note \(\vect 0\in[U,\{l_0\}]\). For any
-    \(\vect x_{C,m}\in[U,\{l_0\}]\), we have two cases.
+    So let \(U(l_0)=W\) and note \(\vect 0\in\lb U,\{l_0\}\rb \). For any
+    \(\vect x_{C,m}\in\lb U,\{l_0\}\rb \), we have two cases.
 

### 2015-11-13 postdoctoral/gamma_functions.tex
make metrizability result explicit

@@
   \begin{theorem}
-    \(\check L\) is metrizable if and only if \(L\) is countable.
+    \(\check L\) is second-countable if and only if \(L\) is countable.
   \end{theorem}
@@
     \([\emptyset,(\leftarrow,l])=[\emptyset,(\leftarrow,l)]\). Each \(B_l\)
-    is unique, so \(\check L\) is compact but not second countable,
-    and therefore nonmetrizable.
+    is unique, so \(\check L\) is not second-countable.
 
@@
     \(\mc T=\{[\emptyset,(\leftarrow,l]):l\in L\}\)
-    generates a countable base for \(\check L\). Thus \(\check L\) is
-    compact second-countable, and therefore metrizable.
+    generates a countable base for \(\check L\).
   \end{proof}
+
+  \begin{corollary}
+    \(\check L\) is metrizable if and only if \(L\) is countable.
+  \end{corollary}
 
@@
     \(\<\check L,\subseteq\>\).
+  \end{proof}
+
+  \begin{corollary}
+    If \(f\) is a non-trivial V-map satisfying condition \(\Gamma\), then
+    \(\varprojlim \{X, f, L\}\) is metrizable if and only if
+    \(X\) is metrizable and \(L\) is countable.
+  \end{corollary}
+
+  \begin{proof}
+    If \(X\) is metrizable and \(L\) is countable, then of course
+    \(\varprojlim \{X,f,L\}\subseteq X^L\) is metrizable. If \(X\) is
+    nonmetrizable, then \(\varprojlim \{X,f,L\}\) cannot be metrizable
+    as it contains a copy of \(X\). Finally, if \(L\) is uncountable,
+    then \(\varprojlim \{X,f,L\}\) cannot be metrizable as it
+    contains a copy of \(\varprojlim \{2,\gamma,L\}\cong\check L\).
   \end{proof}

### 2015-11-13 postdoctoral/gamma_functions.tex
generalize clontz-varagona result to comp conn LOTS

@@
   \end{definition}
+
+  \begin{definition}
+    A u.s.c. map \(f\subseteq X^2\)
+    satisfies condition \(\Gamma\) if there exists \(x,y\in X\) such that
+    \(\<x,x\>,\<y,y\>,\<x,y\>\in f\).
+  \end{definition}
+
+  \begin{theorem}
+    Every V-map on a compact connected LOTS satisfies condition \(\Gamma\).
+  \end{theorem}
+
+  This was proven in \cite{CLONTZVARAGONA} for the case \(M\) is a closed
+  interval of real numbers; however, the same proof applies to this more
+  general case.
+
+\newpage
 
@@
   Note that \(\check L\)
-  is not a ``compactification'' as \(L\) does not necessarily
+  is not a ``compactification'' in the usual sense of word
+  as \(L\) does not necessarily
   embed as a dense subspace of \(\check L\): if \(L=I\), we might attempt to embed
@@
   \begin{example}
-    \(\hat I\cong\{-\infty\}\cup I\) where
-    \(\emptyset\mapsto-\infty\) and \([0,t]\mapsto t\).
+    \(\hat I\cong\{-1\}\cup [0,1]\) where
+    \(\emptyset\mapsto-1\) and \([0,t]\mapsto t\).
   \end{example}
@@
     contains a copy of \(\varprojlim \{2,\gamma,L\}\cong\check L\).
+  \end{proof}
+
+  \begin{corollary}
+    If \(f\) is a nontrivial V-map
+    and \(K\) is a compact connected LOTS, then
+    \(\varprojlim \{K, f, L\}\) is metrizable if and only if
+    \(K=I\) and \(L\) is countable.
+  \end{corollary}
+
+  \begin{proof}
+    \(I\) is the only nontrivial compact connected metrizable LOTS, and all V-maps
+    on compact connected LOTS satisfy condition \(\Gamma\).
   \end{proof}

### 2015-11-16 postdoctoral/S_prime_kappa.tex
Add alan's result and some gamma function stuff shoot I meant to do separate commits

@@
 \usetikzlibrary{matrix}
+
+% dow stuff
+          \def\Succ{\mathop{Succ}}
+          \def\dom{\mathop{dom}}
+          \def\val{\operatorname{val}}
+          \def\N{\mathbb N}
+          \def\Nstar{\mathbb N^*}
 
@@
     There's a model where \(S'(\omega_\omega)\)
-    fails? (TODO: get Alan to send this argument.)
+    fails.
   \end{theorem}
+
+  \begin{proof}
+          We will need the model constructed in \cite{MR1045371} in
+           which an instance of Chang's conjecture
+           $(\aleph_{\omega+1},\aleph_\omega) \rlap{$\rightarrow$}\,{\rightarrow}
+           (\aleph_1,\aleph_0)$ is shown to fail.
+
+          We can take as a given (as shown in \cite[Theorem 5]{MR1045371}) that we may
+          assume that we have a model $V$
+          of GCH in which there are regular limit cardinals $\kappa<\lambda$
+          satisfying that
+          $(\lambda^{+\omega+1},\lambda^{+\omega})\rlap{$\rightarrow$}\,{\rightarrow}
+          (\kappa^{+\omega+1},\kappa^{+\omega})$.
+
+          What this says is that if $L$ is a countable language
+          with at least one unary relation symbol $R$ and
+           $M$ is a model of $L$  with base set $\lambda^{+\omega+1}$
+          in which the interpretation of $R$ has cardinality
+           $\lambda^{+\omega}$, then $M$ has an elementary submodel
+           $N$ of cardinality $\kappa^{+\omega+1}$ in which
+          $R\cap N$ has cardinality $\kappa^{+\omega}$ (of course
+           $R\cap N$ is the interpretation of $R$ in $N$ because
+          $N\prec M$).
+
+          The interested reader will want to know that it is shown in
+          \cite{MR1045371} that if $\kappa$ is a 2-huge cardinal and $j$ is the 2-huge
+          embedding with critical point $\kappa$, then with
+           $\lambda = j(\kappa)$ one has that
+          $(\lambda^{+\omega+1},\lambda^{+\omega})\rlap{$\rightarrow$}\,{\rightarrow}
+          (\kappa^{+\omega+1},\kappa^{+\omega})$ holds.
+          \bigskip
+
+          Let $\{ h_\xi : \xi \in \lambda^{+\omega+1}\}$
+          be a scale in $\Pi\{ \lambda^{+n+1} : n\in \omega\}$
+           ordered by the usual mod finite coordinatewise
+          ordering. For convenience we may assume that $h_\xi(n) \geq
+          \lambda^{+n}$ for all $\xi$ and all $n$.  If $P$ is any poset of
+          cardinality less than $\lambda^{+\omega}$, then in the forcing
+          extension by $P$,  the sequence
+          $\{ h_\xi : \xi \in \lambda^{+\omega+1}\}$  remains cofinal in
+           $\Pi\{ \lambda^{+n+1} : n\in \omega\}$.
+
+          \bigskip
+
+          The forcing notion $\mathbb P_0$ is simply the finite condition
+          collapse of $\kappa^{+\omega}$, i.e. $\mathbb P_0 = \left(
+           \kappa^{+\omega}\right)^{<\omega}$. In the forcing extension by
+           $\mathbb P_0$, one now has that the ordinal $\kappa^{+\omega+1}$
+           from $V$ is the first uncountable cardinal $\aleph_1$. Then in this
+           forcing extension we let $\mathbb P_1$ be the countable condition
+           Levy collapse, $Lv(\lambda,\omega_2)$, which collapses all cardinals
+           less than $\lambda$ to have cardinality at most $\aleph_1$. The poset
+           $\mathbb P_1$ has cardinality $\lambda$. We treat
+          $\mathbb P_1$ as containing $\mathbb P_0$
+          as a subposet by identifying each $(p_0,1)$ with $p_0$.
+          After forcing with $\mathbb P_0*\mathbb P_1$ we will have
+          that $\omega_1$ is the ordinal $\left(\kappa^{+\omega+1}\right)^V$,
+           $\omega_2$ is the ordinal $\lambda$, and $\omega_\omega$ is the
+           ordinal $\left(\lambda^{+\omega}\right)^V$.
+
+          \bigskip
+
+          Now we assume that we have an assignment $\dot f_{\dot A}$ of a
+           $\mathbb P_0*\mathbb P_1$-name of a finite-to-one function from
+           $\dot A$ into $\omega$ for each
+           $\mathbb P_0*\mathbb P_1$-name of a countable subset of
+           $\lambda^{+\omega+1}$. We will obtain a contradiction.
+
+          Let $\{ \dot A_\xi : \xi \in \lambda^{+\omega+1}\}$ be an enumeration
+          of all the  nice $\mathbb P_0$-names of countable
+          subsets of $\lambda^{+\omega}$. For each $\xi\in \lambda^{+\omega+1}$,
+           let $\dot f_\xi$ be another notation for $\dot f_{\dot A_\xi}$.
+          Since $\mathbb P_0$ forces that $\mathbb P_1$ is countably closed,
+          the collection of all nice  $\mathbb P_0$-names will produce all
+          the countable sets in the extension by $\mathbb P_0* \mathbb
+          P_1$, but $\mathbb P_0*\mathbb P_1$ can introduce new enumerations of
+          these names.
+          For each $\xi\in \lambda^{+\omega+1}$,
+          there is a minimal $\zeta_\xi$ so that $\dot A_{\zeta_\xi}$ is the
+          canonical name for the range of $h_\xi$. This means that
+           $\dot f_{\zeta_\xi} \circ h_\xi$ is simply the
+           $\mathbb P_0 *\mathbb P_1$-name of a finite-to-one function from
+           $\omega$ to $\omega$.
+            For each $\xi\in \lambda^{+\omega+1}$,
+           choose any $p_\xi \in \mathbb P_0*\mathbb P_1$ so that
+           there is a nice $\mathbb P_0$-name, $\dot H_\xi$,
+           that is forced by
+           $p_\xi$  to equal $\dot f_{\zeta_\xi}\circ h_\xi$.
+            Choose $\Lambda\subset \lambda^{+\omega+1}$
+            of cardinality $\lambda^{+\omega+1}$
+            and so that there is a pair $p,\dot H$
+            satisfying that $p_\xi = p$ and $\dot H_\xi = \dot H$
+            for all $\xi\in \Lambda$. We may assume that $p$
+            is in a generic filter $  G$.
+
+          Let $\{ x_\xi : \xi\in \lambda^{+\omega+1}\}$ be any enumeration of
+           $H(\lambda^{+\omega+1})$  such that
+           $\{ x_\xi : \xi\in \lambda^{+\omega}\}$ is also equal to
+           $H(\lambda^{+\omega})$. We choose this enumeration in such a way that
+           $x_\xi\in x_\eta$ implies $\xi<\eta$.
+          We use relation symbol $R_0$ to code
+          (and well order)
+           $(H(\lambda^{+\omega+1}), \in)$ as follows: $(\xi,\eta)\in R_0$
+          if and only if $x_\xi\in x_\eta$.
+          Let $R_1$ be a binary relation on $\kappa^{+\omega}$ so that
+          $(\kappa^{+\omega},R_1)$ is isomorphic to $\mathbb P_0$. Let
+           $R_2$ be a binary relation on $\lambda$ so that
+           $R_2\cap (\kappa^{+\omega}\times \kappa^{+\omega})=R_1$ and
+           $(\lambda,R_2)$ is isomorphic to $\mathbb P_0*\mathbb P_1$.
+          Let $\psi$ be the poset isomorphism from $\lambda$ to
+           $\mathbb P_0*\mathbb P_1$.
+
+          We continue coding. We can code the sequence
+           $\{ h_\xi : \xi\in \lambda^{+\omega+1}\}$ as another binary  relation
+           $R_3$ on $\lambda^{+\omega+1}$ where $R_3\cap \left(\{\xi\}\times
+           \lambda^{+\omega+1}\right) = \{ (\xi,h_\xi(n) ) : n\in \omega\}$
+          for each $\xi\in \lambda^{+\omega+1}$. The relation symbol $R_4$ can
+          code the sequence $\{ \dot A_\xi : \xi \in \lambda^{+\omega+1}\}$
+          where $(\xi, \alpha, \zeta) \in R_4$ if and only if
+          $(\check \alpha, \psi(\zeta))$ is in the name $\dot A_\xi$.
+           Let $R_5$ code this collection, i.e.
+           $(\gamma,n,m,\eta)\in R_5$ if and only if
+           $(\check{(n,m)}, \psi(\eta))\in \dot H_\gamma$. Also let $R_6$ code
+           (equal)  the set $\Lambda$.
+          Finally we use the relation symbol $R_7$ to similarly code the
+          sequence $\{ \dot f_\xi  : \xi \in \lambda^{+\omega+1}\}$:
+           $(\xi, \alpha, n, \zeta) \in R_7$ if and only if
+          $(\check {(\alpha,n)}, \psi(\zeta))$ is in the name $\dot f_\xi$.
+
+          Needless to say, the unary relation symbol $R$
+          is interpreted as the set $\lambda^{+\omega}$ for the application of
+          $(\lambda^{+\omega+1},\lambda^{+\omega})\rlap{$\rightarrow$}\,{\rightarrow}
+          (\kappa^{+\omega+1},\kappa^{+\omega})$.
+           Now  we have defined our model
+          $M$  of the language $L= \{\in, R, R_0,\ldots, R_7\}$,
+           and we choose an elementary submodel
+          $N$ witnessing
+          $(\lambda^{+\omega+1},\lambda^{+\omega})\rlap{$\rightarrow$}\,{\rightarrow}
+          (\kappa^{+\omega+1},\kappa^{+\omega})$. Of course $N$ is really just
+          a $\kappa^{+\omega+1}$ sized subset of $\lambda^{+\omega+1}$
+          with the additional property that $N\cap \lambda^{+\omega}$ has
+          cardinality $\kappa^{+\omega}$.  In the
+          forcing extension $N$ has cardinality $\omega_1$ and
+           $A= N\cap \lambda^{+\omega}$ is countable.
+
+          We will need the following claim from \cite{MR1045371}
+
+          \begin{claim*} We may assume that $N$ satisfies that
+           $N\cap \kappa^{+\omega+1}$ is transitive (i.e. an initial segment).
+          \end{claim*}
+
+          \begin{proof}[Proof of Claim]
+          Suppose  our originally supplied $N$ fails the conclusion of the
+          claim.
+          We   know that $\kappa^{+\omega}\in N$,
+          (  via $R_1$)
+          in which case so is $\kappa^{+\omega+1}$.
+
+          Then set $\beta_0 = \sup(N\cap \kappa^{+\omega+1})$ and consider the
+          Skolem closure $\mathop{Hull}(N\cup \beta_0, M)$.  A little informally
+          (in that we have to formalize the enumeration of formulas)
+          let $\{\varphi_n : n\in \omega\}$ is the enumeration of all formulas
+          in the language $L$, and let  $\ell_n$ be the minimal integer such
+          that the free variables of $\varphi_n$ are among
+           $\{ v_0, \ldots, v_{\ell_n}\}$.
+          Then,   for each tuple
+          $\langle \xi_1,\ldots, \xi_{\ell_n} \rangle$
+          of elements of $\lambda^{+\omega+1}$,
+           we define $f_n(\xi_1,\ldots, \xi_{\ell_n})$ to be
+           the minimal $\xi_0\in \lambda^{+\omega+1}$ such that
+           $M\models \varphi_n(\xi_0,\ldots, \xi_{\ell_n})$.
+          If there is no such $\xi_0$,
+             in other words if $M\models \lnot\exists x~~  \varphi_n(x,\xi_1,
+          \ldots,\xi_{\ell_n})$, then set
+           $f_n(\xi_1,\ldots, \xi_{\ell_n})$ to be $0$.
+          Now $\mathop{Hull}(N\cup \beta_0,M)$ is just the minimal superset
+           $X$
+          of $N\cup \beta_0$ that satisfies that
+           $f_n[X^{\{1,\ldots,\ell_n\}}] \subset X$ for all $n$. Since this is
+           simply a large algebra, we can generate all the terms $t$ of
+          the algebraic operations $\{ f_n : n\in \omega\}$.
+          It is easily seen that for each $\zeta \in X$, there is a term
+          $t(v_1,\ldots, v_m)$ such that $\zeta  = t(\delta_1,\ldots, \delta_m)$
+           for some sequence $\langle \delta_1,\ldots, \delta_m\rangle$ with
+           each $\delta_i\in  N\cup \beta_0$.
+           Assume that
+            $\zeta\in \kappa^{+\omega+1}$. By
+            re-indexing the variables in the term we can assume
+            that there is an $n\leq m$ so that
+             $\delta_i  <\beta_0$ for $1\leq i\leq n$
+              and $\kappa^{+\omega+1}\leq \delta_i$ for $n<i\leq m$.
+              Let $\vec a $ denote
+              the tuple $\langle \delta_{n+1},\ldots, \delta_m\rangle$.
+            Choose $\eta\in N\cap \kappa^{+\omega+1}$ large enough so that
+           $ \{  \delta_1, \ldots, \delta_n\}$ is contained in  $\eta$. Since set-membership
+           in $M$ is coded by $R_0$ rather than $\in$ we have to argue a little
+           less naturally.
+           Consider the set
+             $s_0(\eta,\vec a) = \{ t(\gamma_1,\ldots, \gamma_n,\vec a) :
+          \{\gamma_1,\cdots,\gamma_n\} \in [\eta]^{\leq n}\}$. Clearly
+           $s_0(\eta,\vec a)$ is a member of $H(\lambda^{+\omega+1})$.
+           Now define $s_1(\eta,\vec a) $ to be
+           $\{ x_\alpha : \alpha\in s_0(\eta, \vec a)\}$,
+           and choose the
+           unique $\zeta_1\in \lambda^{+\omega+1}$ such
+           that $x_{\zeta_1} = s_1(\eta,\vec a)$. We claim that $\zeta_1\in N$.
+           Note that $\alpha R_0\zeta_1$ holds if and only if
+            $ \alpha \in s_0(\eta,\vec a)$, and therefore
+           $$M\models (\forall \alpha)\left[\alpha R_0 \zeta_1 ~~\mbox{iff}~~
+           (\exists   \gamma_1\in \eta)\cdots(\exists \gamma_n\in\eta)(\alpha=
+           t(\gamma_1,\ldots, \gamma_n,\vec a))\right]~.$$
+           By elementarity then we have that $\zeta_1\in N$,
+           and by similar reasoning the supremum, $\zeta_0$,
+          of $\zeta_1\cap \kappa^{+\omega+1}$ is also in $N$.
+             This of course means that $\zeta < \xi_0$.
+          \end{proof}
+
+          We use the elementarity of
+           $N$  to deduce properties of the families
+           $\{ \dot A_\xi : \xi\in N\}$ and $\{ \dot f_\xi : \xi \in
+           N\}$.  Actually the collection we are most interested in
+           is the family $\{ h_\xi : \xi\in \Lambda\cap N\}$.
+
+           Since  $\mathfrak c < \kappa^{+\omega+1}$ there
+            is a function $\langle \varrho_n : n\in \omega\rangle$
+            in $\Pi_n \lambda^{+\omega}   $ such that the sequence
+             $\{ h_\xi : \xi \in N\}$ is unbounded mod finite
+             in $\Pi_n \varrho_n$ (by Shelah's pcf theory).
+             This is in Jech somewhere.
+             For each $n$, $\rho_n \leq \sup(N\cap \lambda^{+n+2})$.
+
+             Since $\mathbb P_0$ has cardinality less than $|N|=\kappa^{+\omega+1}$,
+              the sequence $\{ h_\xi : \xi \in \Lambda\cap N\}$ remains unbounded
+              mod finite in $\Pi_n \varrho_n$ (and in
+               $\Pi_n (\varrho_n\cap N)$).  Now pass to the extension by
+                $G\cap \mathbb P_0$ and let $H$ be the function
+                 $\operatorname{val}_{G}(\dot H)$, and we recall
+                 that $f_{\zeta_\xi}(h_\xi(n)) = H(n)$ for all $n\in \omega$.
+           Now pass to the full extension $V[G]$ and again, since
+            $\mathbb P_1$ was forced to be countably closed,
+             the family $\{ h_\xi : \xi \in \Lambda\cap N\}$ is still
+             unbounded in $\Pi_n (\varrho_n \cap N)$. We let
+             $A$ be the countable set $N\cap \lambda^{+\omega}$,
+             and for  each
+             $\xi\in \Lambda\cap N$, there is an $n_\xi$ such that
+              $f_{\xi}(h_\xi(m)) = f_A(h_\xi(m))$ for all $m>n_\xi$.
+              There is a single $n$ so that $\Lambda_n
+               = \{\xi\in \Lambda\cap N       : n_\xi = n\}$ has cardinality
+                $\omega_1 $, and thus
+                $\{ h_\xi : \xi\in \Lambda_n\cap N\}$ is also unbounded
+                in $\Pi_n (\rho_n\cap N)$.
+          This certainly implies that there is an $m>n$
+          such that $\{ h_\xi (m) : \xi\in \Lambda_n\cap N\}$ is infinite.
+          This completes the proof since  $f_{A}(h_\xi(m)) = H(m)$
+          for all $\xi\in \Lambda_n\cap N$.
+
+  \end{proof}
 
@@
 
+\newpage
+\bibliographystyle{plain}
+\bibliography{../bibliography}
 \end{document}

### 2015-11-16 postdoctoral/gamma_functions.tex
Add alan's result and some gamma function stuff shoot I meant to do separate commits

@@
   \begin{definition}
-    For any compact LOTS \(K\) with minimum \(0\) and maximum \(1\),
-    let \(\gamma\) be the V-map on \(K\) where \(\gamma(0)=K\) and \(\gamma(t)=\{1\}\)
-    for \(t>0\).
+    For any space \(M\) containing the points \(0\) and \(1\),
+    let \(\gamma\) be the surjective u.s.c. map on \(K\) where
+    \(\gamma(0)=M\) and \(\gamma(t)=\{1\}\)
+    for \(t\not=0\).
   \end{definition}
+
+  Note when \(M\) is a Hausdorff continuum, then \(\gamma\) is a V-map.
+  It's usually assumed \(0\) is the minimum and \(1\) is the maximum
+  when \(M\) is a LOTS.
 
@@
 
-  We may generalize theorem 8 as follows:
+  We may generalize theorem whatevs as follows:
 
-  \begin{theorem}
+  \begin{theorem} %TODO fix first \sim to use A,B instead of l_0,l_1
     If \(M\) is a LOTS with minimum \(0\) and maximum \(1\),
@@
   \end{example}
+
+  We now discard the linear order on \(M\). Denote points in the topological
+  sum \(\bigoplus_{l\in \hat L} M\) of \(\hat L\) copies of \(M\)
+  by the ordered pairs \(\<A,m\>\)
+  for \(A\in \hat L\), \(m\in M\). The previous proof may be generalized to
+  show the following:
+
+  \begin{theorem}
+    If \(M\) is a Hausdorff space with points \(0\) and \(1\),
+    then \(\varprojlim\{M,\gamma,L\}\cong \bigoplus_{l\in \hat L} M/\sim\),
+    where \(\<(\leftarrow,l_0],1\>\sim\<(\leftarrow,l_1],0\>\) if
+    \(l_0<l_1\) and \((l_0,l_1)=\emptyset\),
+    and where \(\<A,m\>\sim\<A,m'\>\) if \(A\in\hat L\setminus L\).
+  \end{theorem}
+
+  % \begin{proof}
+  %   Partially order \(M\) by \(0\leq m\leq 1\) for all \(m\in M\).
+  %   Note that the range of any
+  %   \(\vect x\in\varprojlim\{M,\gamma,L\}\) is totally ordered by \(\leq\).
+
+  %   Let \(\rho(\vect x)=\cl\{l\in L:\vect x(l)>0\}\), \(v(\vect 0)=0\),
+  %   and \(v(\vect x)=\min\{\vect x(l):l\in\rho(\vect x)\}\) otherwise.
+  %   Let
+  %   \(\theta(\vect x)=\<\rho(\vect x),v(\vect x)\>\in\hat L\lexTimes M/\sim\).
+  %   For each left-closed set \(A\) and \(m\in M\),
+  %   let \(\vect x_{A,m}(l)=1\) for \(l\in A\) unless \(l\) is the supremum
+  %   element of \(A\),
+  %   \(\vect x_{A,m}(l)=m\) if \(l\) is the supremum of \(A\),
+  %   and \(\vect x_{A,m}(l)=0\) for \(l\not\in A\).
+  %   We wish to show that \(\theta\) is a homeomorphism.
+
+  %   We begin by
+  %   showing that \(\theta\) is a surjection. If \(B\in\hat L\setminus L\)
+  %   and \(m\in M\), consider \(\<B,m\>\).
+  %   \(B\) lacks a supremum in \(L\), so
+  %   \(\vect x_{B,0}(l)=1\) for \(l\in B\) and \(\vect x_{B,0}(l)=0\) otherwise.
+  %   So \(\theta(\vect x_{B,0})=\<\cl B,1\>=\<B,1\>\sim\<B,m\>\) for all
+  %   \(m\in M\). Otherwise, \(B=(\leftarrow,l_1]\) for some \(l_1\in L\).
+  %   Let \(m>0\).
+  %   Then
+  %   \(
+  %     \theta(\vect x_{(\leftarrow,l_1],m})
+  %       =
+  %     \<\cl (\leftarrow,l_1],v(\vect x_{(\leftarrow,l_1],m})\>
+  %       =
+  %     \<(\leftarrow,l_1],m\>
+  %   \).
+  %   Finally, we want to map onto \(\<(\leftarrow,l_1],0\>\).
+  %   If there exists \(l_0<l_1\) with \((l_0,l_1)=\emptyset\), then
+  %   \(
+  %     \theta(\vect x_{(\leftarrow,l_1],0})
+  %       =
+  %     \theta(\vect x_{(\leftarrow,l_0],1})
+  %       =
+  %     \<(\leftarrow,l_0],1\>
+  %   \)
+  %   will suffice. Otherwise,
+  %   \(
+  %     \theta(\vect x_{(\leftarrow,l_1],0})
+  %       =
+  %     \<\cl (\leftarrow,l_1),v(\vect x_{(\leftarrow,l_1),0})\>
+  %       =
+  %     \<(\leftarrow,l_1],0\>
+  %   \).
+
+  %   To see that \(\theta\) is injective, first let
+  %   \(A\subsetneq B\)... TODO
+
+  %   % A basic open set in \(\varprojlim\{M,\gamma,L\}\subseteq L^m\)
+  %   % is of the form
+  %   % \(\lb U,F \rb\) where \(U(l)\) is an open interval in \(M\) for each
+  %   % \(l\in F\in [L]^{<\omega}\), and
+  %   % \(\lb U,F\rb=\{\vect x:l\in F\Rightarrow\vect x(l)\in U(l)\}\).
+  %   % If we assume that \(\lb U,F \rb\) is non-empty, one of the following
+  %   % must hold:
+
+  %   % \begin{itemize}
+  %   %   \item
+  %   %     \(U[l_0]=(a,b)\) for some \(l_0\in F\).
+  %   %     Then \(\lb U,F\rb=\lb U,\{l_0\}\rb \), and note that
+  %   %     \(
+  %   %       \lb U,\{l_0\}\rb
+  %   %         =
+  %   %       (\vect x_{(\leftarrow,l_0],a},\vect x_{(\leftarrow,l_0],b})
+  %   %     \).
+  %   %   \item
+  %   %     \(U(l_0)=(a,1]\) and \(U(l_1)=[0,b)\) for some \(l_0<l_1\in L\)
+  %   %     and \(\lb U,F\rb=\lb U,\{l_0,l_1\}\rb \). Then
+  %   %     \(\lb U,\{l_0,l_1\}\rb =(\vect x_{l_0,a},\vect x_{l_1,b})\).
+  %   % \end{itemize}
+  %   % In the other direction, consider \(\vect y\in(\vect x,\vect z)\).
+  %   % \begin{itemize}
+  %   %   \item
+  %   %     In the case that \(l_0\in\rho(\vect y)\setminus\rho(\vect x)\)
+  %   %     and \(l_1\in\rho(\vect z)\setminus\rho(\vect y)\), let
+  %   %     \(U(l_0)=(0,1]\), \(U(l_1)=[0,v(\vect z))\) and note
+  %   %     \(\vect y\in\lb U,\{l_0,l_1\}\rb \subseteq(\vect x,\vect z)\).
+  %   %   \item
+  %   %     In the case that \(l_0\in\rho(\vect y)\setminus\rho(\vect x)\),
+  %   %     \(\rho(\vect y)=\rho(\vect z)\), and \(v(\vect y)<v(\vect z)\),
+  %   %     it follows that \(\rho(\vect y)=\rho(\vect z)=(\leftarrow,l_1]\),
+  %   %     so let \(U(l_0)=(0,1]\), \(U(l_1)=[0,v(\vect z))\) and note
+  %   %     \(\vect y\in\lb U,\{l_0,l_1\}\rb \subseteq(\vect x,\vect z)\).
+  %   %   \item
+  %   %     In the case that
+  %   %     \(\rho(\vect x)=\rho(\vect y)\), \(v(\vect x)<v(\vect y)\),
+  %   %     and \(l_1\in\rho(\vect z)\setminus\rho(\vect y)\),
+  %   %     it follows that \(\rho(\vect x)=\rho(\vect y)=(\leftarrow,l_0]\),
+  %   %     so let \(U(l_0)=(v(\vect x),1]\), \(U(l_1)=[0,v(\vect z))\) and note
+  %   %     \(\vect y\in\lb U,\{l_0,l_1\}\rb \subseteq(\vect x,\vect z)\).
+  %   %   \item
+  %   %     In the case that
+  %   %     \(\rho(\vect x)=\rho(\vect y)=\rho(\vect z)\) and
+  %   %     \(v(\vect x)<v(\vect y)<v(\vect z)\),
+  %   %     it follows that
+  %   %     \(\rho(\vect x)=\rho(\vect y)=\rho(\vect z)=(\leftarrow,l_0]\),
+  %   %     so let \(U(l_0)=(v(\vect x),v(\vect z))\) and note
+  %   %     \(\vect y\in\lb U,\{l_0\}\rb =(\vect x,\vect z)\).
+  %   % \end{itemize}
+
+  %   % We conclude by
+  %   % showing that \(\theta\) is a surjection. If \(B\in\hat L\setminus L\)
+  %   % and \(m\in M\), consider \(\<B,m\>\).
+  %   % \(B\) lacks a supremum in \(L\), so
+  %   % \(\vect x_{B,0}(l)=1\) for \(l\in B\) and \(\vect x_{B,0}(l)=0\) otherwise.
+  %   % So \(\theta(\vect x_{B,0})=\<\cl B,1\>=\<B,1\>\sim\<B,m\>\) for all
+  %   % \(m\in M\). Otherwise, \(B=(\leftarrow,l_1]\) for some \(l_1\in L\).
+  %   % Let \(m>0\).
+  %   % Then
+  %   % \(
+  %   %   \theta(\vect x_{(\leftarrow,l_1],m})
+  %   %     =
+  %   %   \<\cl (\leftarrow,l_1],v(\vect x_{(\leftarrow,l_1],m})\>
+  %   %     =
+  %   %   \<(\leftarrow,l_1],m\>
+  %   % \).
+  %   % Finally, we want to map onto \(\<(\leftarrow,l_1],0\>\).
+  %   % If there exists \(l_0<l_1\) with \((l_0,l_1)=\emptyset\), then
+  %   % \(
+  %   %   \theta(\vect x_{(\leftarrow,l_1],0})
+  %   %     =
+  %   %   \theta(\vect x_{(\leftarrow,l_0],1})
+  %   %     =
+  %   %   \<(\leftarrow,l_0],1\>
+  %   % \)
+  %   % will suffice. Otherwise,
+  %   % \(
+  %   %   \theta(\vect x_{(\leftarrow,l_1],0})
+  %   %     =
+  %   %   \<\cl (\leftarrow,l_1),v(\vect x_{(\leftarrow,l_1),0})\>
+  %   %     =
+  %   %   \<(\leftarrow,l_1],0\>
+  %   % \).
+  % \end{proof}
 

### 2015-11-16 articles/zero-markov-information-in-a-topological-game/article.tex
revisions per the referee

@@
 
-\begin{theorem}
+\begin{theorem} \cite[Theorem 5]{MR858337}
   The following are equivalent for a locally compact space $X$:
@@
 
-\begin{theorem}
+\begin{theorem} \cite[Theorem 2]{MR858337}
   The following are equivalent for a locally compact space $X$:
@@
 
-\begin{theorem}
+\begin{theorem} \cite[Theorem 3]{MR858337}
   The following are equivalent for a locally compact space $X$:
@@
 \begin{proof}
-  Let \(K_n\) for \(n<\omega\) witness hemicompactness.
-  If \(C\cap K_n\) is closed for each \(n<\omega\), then let \(K\) be any compact
-  set. Since \(K\subseteq K_n\) for some \(n<\omega\), \(C\cap K\) is closed, and
-  therefore \(C\) is closed.
+  Let \(\{K_n:n<\omega\}\) be a collection of compact subsets
+  which witnesses the hemicompactness of the space.
+  Suppose \(C\cap K_n\) is closed for each \(n<\omega\).
+  Let \(K\) be any compact subset of the space.
+  There exists some \(n<\omega\) such that \(K\subseteq K_n\).
+  Then \(C\cap K=(C\cap K_n)\cap K\) is closed. Therefore \(C\)
+  is closed by the definition of \(k\)-space.
 \end{proof}
@@
 
+In particular note that for any ultrafilter on \(\kappa\) and subset
+\(S\subseteq\kappa\), exactly one of \(S,\kappa\setminus S\) belongs to
+the ultrafilter.
+
 \begin{definition}
@@
 are isolated, so \(\kappa\) with the discrete topology may be viewed as
-a dense open subspace of \(\beta\kappa\).
+a dense open subspace of \(\beta\kappa\), with \(\beta\kappa\setminus\kappa\)
+representing the free ultrafilters on \(\kappa\).
+In that case, one might interpret \(U_S\) as
+\(
+  \{\mc F\in\beta\kappa\setminus\kappa:S\in\mc F\}
+    \cup
+  \{\alpha\in\kappa:\alpha\in S\}
+\).
+
 We wish to consider the subspace
@@
 \begin{proof}
-  Let \(I=\{n_i:i<\omega\}\cup\{\mc F\}\) be infinite.
-  Then \(\{U_{\omega\setminus\{n_i:i\geq j\}}:j<\omega\}\) is an open cover of
-  \(I\cup\{\mc F\}\) with no finite subcover.
+  Let \(n_i<\omega\) be distinct for each \(i<\omega\).
+  Since \(\{n_i:i<\omega\}\) is infinite and discrete, it
+  cannot be compact.
+  So we consider \(I=\{n_i:i<\omega\}\cup\{\mc F\}\).
+  Let \(S=\{n_{2i}:i<\omega\}\). If \(S\in \mc F\), then \(U_S\) is a
+  neighborhood of \(\mc F\) missing \(\{n_{2i+1}:i<\omega\}\), so \(I\)
+  contains a closed infinite discrete set and cannot be compact.
+  Otherwise \(\omega\setminus S\in \mc F\) and \(U_{\omega\setminus S}\)
+  is a neighborhood of \(\mc F\) missing \(\{n_{2i}:i<\omega\}\); again
+  \(I\) contains a closed infinite discrete set and cannot be compact.
 \end{proof}
@@
   \(U_S\) of \(\mc F\), \(S\) is infinite, and since
-  \(\bigcup_{n<\omega} H(n)\supseteq\omega\setminus\sigma(0)\), \(U_S\) meets
-  infinitely many of the finite \(H(n)\). Thus \(\sigma\) is not a winning
+  \(\bigcup_{n<\omega} H(n)\supseteq\omega\setminus\sigma(0)\)
+  and \(|H(n)|<\omega\), \(U_S\) meets
+  infinitely many of the \(H(n)\). Thus \(\sigma\) is not a winning
   predetermined strategy.
@@
 
-It is not possible to prove in \(ZFC\) that
+We now show that it is not possible to prove in \(ZFC\) that
 \(\pl K\prewin \gruKPGame{\omega\cup\{\mc F\}}\)
-for arbitrary free ultrafilters.
+for every free ultrafilter; assuming the continuum hypothesis (\(CH\)),
+we may find a counter-example.
 
@@
 \begin{theorem}
+  \cite{MR0080902}
   CH implies the existence of a selective ultrafilter.
-  \cite{MR0080902}
 \end{theorem}
@@
 Of particular note is that the author knows of no examples of a
-non-\(k\)-space such that \(K\prewin\gruKPGame{X}\).
+non-\(k\)-space such that \(\pl K\prewin\gruKLGame{X}\).
 
 \begin{question}
-  Does \(K\prewin\gruKPGame{X}\) imply \(X\) is a \(k\)-space?
+  Does \(\pl K\prewin\gruKLGame{X}\) imply \(X\) is a \(k\)-space?
 \end{question}

### 2015-11-17 articles/almost-compatible-functions-and-topological-games/article.tex
add scaffolding for clontz/Dow paper

--- 2015-09-23 articles/applications-of-limited-information-strategies-in-mengers-game/article.tex
@@
 % \tnotetext[t1]{2010 Mathematics Subject Classification. 54E15, 54D30, 54A20.}
-\title{Applications of limited information strategies in Menger's game}
+\title{Almost compatible functions and infinite length games}
 
@@
 Charlotte, NC 28262}
-\email{steven.clontz@gmail.edu}
-\urladdr{stevenclontz.com}
+\email{steven.clontz@gmail.com}
+\author{Alan Dow}
+\address{Department of Mathematics and Statistics, UNC Charlotte,
+Charlotte, NC 28262}
+\email{adow@uncc.edu}
 
-\keywords{Menger's property, Menger's game, limited information strategies}
+\keywords{TODO}
 
-\subjclass[2010]{03E35, 54D20, 54D45, 91A44}
+% TODO
+\subjclass[2010]{}
 
 \begin{abstract}
-  I need an abstract
+  TODO
 \end{abstract}
@@
 
-I require an introduction.
-
-\section{The Menger property and game}
-
-Recall the following definition.
-
-\begin{definition}
-  A space \(X\) is Menger if for every sequence \(\<\mc U_0,\mc U_1,\dots\>\)
-  of open covers of \(X\) there exists a sequence
-  \(\<\mc F_0,\mc F_1,\dots\>\) such that \(\mc F_n\subseteq \mc U_n\),
-  \(|\mc F_n|<\omega\), and \(\bigcup_{n<\omega}\mc F_n\) is a cover of \(X\).
-\end{definition}
-
-Note that many authors refer to this property as \(S_{fin}(\mc O,\mc O)\)
-\cite{MR1378387},
-where \(\mc O\) is the collection of open covers of \(X\), and
-\(S_{fin}(A,B)\) denotes the selection property such that for each
-sequence in \(A^\omega\), there are finite subsets of each entry for which
-the union of these subsets belongs in \(B\).
-
-\begin{proposition}
-  \(X\) is \(\sigma\)-compact
-    \(\Rightarrow\)
-  \(X\) is Menger
-    \(\Rightarrow\)
-  \(X\) is Lindel\"of.
-\end{proposition}
-
-None of these implications may be reversed; the irrationals are a simple example
-of a Lindel\"of space which is not Menger, and we'll see several examples of
-Menger spaces which are not \(\sigma\)-compact.
-
-It will be convenient to consider subsets of \(X\) rather than subsets of
-the open covers.
-
-\begin{definition}
-  For each cover \(\mc U\) of \(X\), \(S\subseteq X\) is
-  \term{\(\mc U\)-finite} if
-  there exists a finite subcollection of \(\mc U\) which covers \(S\).
-\end{definition}
-
-Of course, a compact space is \(\mc U\)-finite for all open covers \(\mc U\).
-
-\begin{proposition}
-  A space \(X\) is Menger if and only if
-  for every sequence \(\<\mc U_0,\mc U_1,\dots\>\)
-  of open covers of \(X\) there exists a sequence
-  \(\<F_0,F_1,\dots\>\) such that \(F_n\subseteq X\), \(F_n\) is
-  \(\mc U_n\)-finite, and \(X=\bigcup_{n<\omega}F_n\).
-\end{proposition}
-
-This is the characterization we will use in this paper.
-A game version of the Menger property is also often considered.
-
-\begin{game}
-  Let \(\menGame{X}\) denote the \term{Menger game} with players \(\pl C\), \(\pl F\).
-  In round \(n\), \(\pl C\) chooses an open cover \(\mc U_n\), followed by \(\pl F\)
-  choosing a \(\mc U_n\)-finite subset \(F_n\) of \(X\).
-
-  \(\pl F\) wins the game if \(X = \bigcup_{n<\omega}F_n\),
-  and \(\pl C\) wins otherwise.
-\end{game}
-
-As with the Menger property, authors usually characterize this game using
-finite subsets \(\mc F_n\)
-of \(\mc U_n\) instead (and often refer to it as the selection game
-\(G_{fin}(\mc O,\mc O)\)).
-This is obviously equivalent in the case of perfect
-information, and is also equivalent
-in the case of limited information, provided \(\pl F\)
-knows \(\mc U_n\) during round \(n\). However, we make this change as we
-will investigate \(0\)-Markov strategies which consider no moves of
-the opponent, and instead rely only on the current round number.
-
-This game may be used to characterize the Menger property.
-
-\begin{definition}
-  If \(\pl A\) has a winning strategy for a game \(G\) (which defeats every
-  possible counterattack by her opponent), then we write \(\pl A\win G\).
-\end{definition}
-
-\begin{theorem}[Hurewicz \cite{MR1544773}]
-  A space \(X\) is Menger if and only if \(\pl C\notwin\menGame{X}\).
-\end{theorem}
-
-\section{Limited information strategies}
-
-Recall the following definitions.
-
-\begin{definition}
-  A \(k\)-tactical strategy for a game \(G\) with moveset \(M\) is a function
-  \(\sigma:M^{\leq k}\to M\); intuitively, it is a strategy which only considers
-  the previous \(k\) moves of the opponent. If a winning \(k\)-tactical strategy
-  exists for \(\pl P\) in the game \(G\), then we write \(\pl P\ktactwin{k} G\).
-\end{definition}
-
-\begin{definition}
-  A \(k\)-Markov strategy for a game \(G\) with moveset \(M\) is a function
-  \(\sigma:M^{\leq k}\times\omega\to M\); intuitively, it is a strategy which
-  only considers the previous \(k\) moves of the opponent and the round number.
-  If a winning \(k\)-Markov strategy exists for
-  \(\pl P\) in the game \(G\), then we write \(\pl P\kmarkwin{k} G\).
-\end{definition}
-
-We will call \(k\)-tactical strategies ``\(k\)-tactics'' and \(k\)-Markov strategies
-``\(k\)-marks''. If the \(k\) is omitted then it is assumed that \(k=1\). In
-addition, note that some authors refer to tactics as
-\term{stationary strategies}.
-
-Tactics will be of interest in a game discussed later; proving
-the following is an easy exercise.
-
-\begin{proposition}
-  \(X\) is compact if and only if
-  \(\pl F \tactwin \menGame{X}\) if and only if
-  \(\pl F \ktactwin{k+1} \menGame{X}\) for some \(k<\omega\).
-\end{proposition}
-
-Essentially, because \(\pl C\) may repeat the same finite sequence of open covers,
-\(\pl F\) needs to be seeded with knowledge of the round number to prevent being
-trapped in a loop.
-
-If \(\pl F\)'s memory of \(\pl C\)'s past moves is bounded, then
-there is no need to consider more than the two most recent moves. The
-intuitive reason is that \(\pl C\) could simply play the same cover repeatedly
-until \(\pl F\)'s memory is exhausted, in which case \(\pl F\) would only ever
-see the change from one cover to another.
-
-\begin{theorem}
-  For each \(k<\omega\), \(F \kmarkwin{(k+2)} \menGame{X}\)
-  if and only if \(F \kmarkwin2 \menGame{X}\).
-\end{theorem}
-
-\begin{proof}
-  Let \(\sigma\) be a winning \((k+2)\)-mark. We define the \(2\)-mark \(\tau\) as
-  follows:
-    \[
-      \tau(\<\mc U\>,0)
-        =
-      \bigcup_{m<k+2}
-        \sigma(\<\underbrace{\mc U,\dots,\mc U}_{m+1}\>,m)
-    \]
-    \[
-      \tau(\<\mc U,\mc V\>,n+1)
-        =
-      \bigcup_{m<k+2}
-        \sigma(\<
-          \underbrace{\mc U,\dots,\mc U}_{k+1-m},
-          \underbrace{\mc V,\dots,\mc V}_{m+1}
-        \>,(n+1)(k+2)+m)
-    \]
-
-  Let \(\<\mc U_0,\mc U_1,\dots\>\) be an attack by \(\pl C\) against \(\tau\).
-  Then consider the attack
-    \[
-      \<
-        \underbrace{\mc U_0,\dots,\mc U_0}_{k+2},
-        \underbrace{\mc U_1,\dots,\mc U_1}_{k+2},
-        \dots
-      \>
-    \]
-  by \(\pl C\) against \(\sigma\). Since \(\sigma\) is a winning \((k+2)\)-mark,
-    \[
-      X
-        =
-      \bigcup_{m<k+2}
-        \sigma(\<\underbrace{\mc U_0,\dots,\mc U_0}_{m+1}\>,m)
-      \cup
-      \bigcup_{n<\omega}
-      \bigcup_{m<k+2}
-        \sigma(\<
-          \underbrace{\mc U_n,\dots,\mc U_n}_{k+1-m},
-          \underbrace{\mc U_{n+1},\dots,\mc U_{n+1}}_{m+1}
-        \>,(n+1)(k+2)+m)
-    \]
-    \[
-      =
-      \tau(\<\mc U_0\>,0)
-      \cup
-      \bigcup_{n<\omega}
-      \tau(\<\mc U_n,\mc U_{n+1}\>,n+1)
-    \]
-  Thus \(\tau\) is a winning \(2\)-mark.
-\end{proof}
-
-It's worth noting that the above proof holds for any selection game of
-the form \(G_{fin}(A,B)\).
-
-A natural question arises: is there an example of a space \(X\) for which
-\(\pl F\kmarkwin{2}\menGame{X}\) but \(\pl F\notmarkwin\menGame{X}\)? We quickly
-see that perhaps the simplest example of a Lindel\"of non-\(\sigma\)-compact
-space has this property.
-
-\begin{definition}
-  For any cardinal \(\kappa\), let \(\oneptlind\kappa=\kappa\cup\{\infty\}\) denote
-  the \term{one-point Lindel\"of-ication} of discrete \(\kappa\), where points in
-  \(\kappa\) are isolated, and the neighborhoods of \(\infty\) are the co-countable
-  sets containing it.
-\end{definition}
-
-One may prove directly that
-  \(\pl F \notmarkwin \menGame{\oneptlind{\omega_1}}\)
-without much effort; however, we postpone stating this until we have
-shown that being Markov Menger is equivalent to being \(\sigma\)-compact
-in regular spaces.
-
-The greatest advantage of a strategy which has knowledge of two or more previous
-moves of the opponent, versus only knowledge of the most recent move, is the
-ability to react to changes from one round to the next. It's this ability to
-react that often allows a player to wield a winning \(2\)-Markov strategy when
-a winning \(1\)-Markov strategy does not exist.
-
-\section{Scheepers' filling games}
-
-We now turn to a related game whose \(k\)-tactics were studied by Marion
-Scheepers in \cite{MR1129143}.
-
-\begin{game}
-  Let \(\schFillStrictGame\kappa\) denote
-  \term{Scheepers' strict union filling game}
-  with two players \(\pl C\), \(\pl F\). In round \(0\), \(\pl C\) chooses
-  \(C_0\in[\kappa]^{\leq\omega}\), followed by \(\pl F\) choosing
-  \(F_0\in[\kappa]^{<\omega}\). In round \(n+1\), \(\pl C\) chooses
-  \(C_{n+1}\in[\kappa]^{\leq\omega}\) such that \(C_{n+1}\supset C_n\), followed
-  by \(\pl F\) choosing \(F_{n+1}\in[\kappa]^{<\omega}\).
-
-  \(\pl F\) wins the game if
-  \(\bigcup_{n<\omega} F_n\supseteq\bigcup_{n<\omega} C_n\); otherwise,
-  \(\pl C\) wins.
-\end{game}
-
-In \(\menGame{\oneptlind\kappa}\), \(\pl C\) essentially chooses a countable set
-to not include in her neighborhood of \(\infty\), followed by \(\pl F\) choosing
-a finite subset of this complement to cover during each round. Thus,
-\(\pl F\) need only be concerned with the \textit{intersection} of the
-countable sets chosen by \(\pl C\) in \(\menGame{\oneptlind\kappa}\), rather
-than the union as in \(\schFillStrictGame\kappa\).
-
-Another difference between these games:
-Scheepers required that \(\pl C\) always choose strictly
-growing countable sets. If the goal is to study tactics,
-then \(\pl C\) cannot be allowed to trap \(\pl F\) in a loop by
-repeating the same
-moves. But by eliminating this requirement, the study can then turn to Markov
-strategies, bringing the game further in line with the Menger game played upon
-\(\oneptlind\kappa\).
-
-We introduce a few games to make the relationship between Scheeper's
-\(\schFillStrictGame\kappa\) and \(\menGame{\oneptlind\kappa}\) more precise.
-
-\begin{game}
-  Let \(\schFillGame\kappa\) denote the
-  \term{union filling game} which proceeds analogously
-  to \(\schFillStrictGame\kappa\), except that \(\pl C\)'s restriction in round \(n+1\)
-  is reduced to \(C_{n+1}\supseteq C_n\).
-\end{game}
-
-\begin{game}
-  Let \(\schFillInitialGame\kappa\) denote the
-  \term{initial filling game} which proceeds analogously
-  to \(\schFillGame\kappa\), except that \(\pl F\) wins whenever
-  \(\bigcup_{n<\omega}F_n\supseteq C_0\).
-\end{game}
-
-\begin{game}
-  Let \(\schFillIntGame\kappa\) denote the
-  \term{intersection filling game} which proceeds analogously
-  to \(\schFillInitialGame\kappa\), except that \(\pl C\) may choose any
-  \(C_n\in[\kappa]^{\leq\omega}\) each round, and \(\pl F\) wins whenever
-  \(\bigcup_{n<\omega}F_n\supseteq\bigcap_{n<\omega}C_n\).
-\end{game}
-
-\begin{figure}[h]
-\begin{center}
-\begin{tikzpicture}
-  \matrix (m) [matrix of math nodes,row sep=3em,column sep=1em,minimum width=2em]
-  {
-    \pl F \kmarkwin{k+1}\menGame{\oneptlind\kappa} &
-    \pl F \kmarkwin{k+1}\schFillIntGame\kappa \\
-
-    \pl F \kmarkwin{k+1}\schFillInitialGame\kappa &
-    \pl F \kmarkwin{k+1}\schFillGame\kappa \\
-
-    &
-    \pl F \ktactwin{k+1}\schFillStrictGame\kappa \\
-  };
-  \path[>=latex,->]
-    (m-1-1) edge (m-2-1)
-    (m-1-2) edge (m-2-2)
-    (m-3-2) edge (m-2-2);
-  \path[>=latex,<->]
-    (m-1-1) edge (m-1-2)
-    (m-2-1) edge (m-2-2);
-\end{tikzpicture}
-\end{center}
-\caption{Diagram of Scheepers/Menger game implications}
-\label{fillingGamesDiagram}
-\end{figure}
-
-\begin{theorem}
-For any cardinal \(\kappa\geq\omega\) and integer \(k<\omega\),
-Figure \ref{fillingGamesDiagram} holds.
-\end{theorem}
-
-\begin{proof}
-  \(\pl F \kmarkwin{k+1}\menGame{\oneptlind\kappa}
-    \Rightarrow
-  \pl F \kmarkwin{k+1}\schFillIntGame\kappa\):
-  Let \(\sigma\) be a winning \(k\)-mark for \(\pl F\) in
-  \(\menGame{\oneptlind\kappa}\). Let \(\mc U(C)\) (resp. \(\mc U(s)\)) convert each
-  countable subset \(C\) of \(\kappa\) (resp. finite sequence \(s\) of such subsets)
-  into the open cover \([C]^1\cup\{\oneptlind\kappa\setminus C\}\)
-  (resp. finite sequence of such open covers). Then \(\tau\) defined by
-    \[
-      \tau(s\concat\<C\>,n)
-        =
-      C\cap\sigma(\mc U(s\concat\<C\>),n)
-    \]
-  is a winning \((k+1)\)-mark for \(\pl F\) in \(\schFillIntGame\kappa\).
-
-  \(\pl F \kmarkwin{k+1}\schFillIntGame\kappa
-    \Rightarrow
-  \pl F \kmarkwin{k+1}\menGame{\oneptlind\kappa}\):
-  Let \(\sigma\) be a winning \(k\)-mark for \(\pl F\) in
-  \(\schFillIntGame\kappa\). Let \(C(\mc U)\) (resp. \(C(s)\)) convert each open
-  cover \(\mc U\) of \(\oneptlind\kappa\) (resp. finite sequence \(s\) of such covers)
-  into a countable set \(C\) which is the complement of some neighborhood of
-  \(\infty\) in \(\mc U\) (resp. finite sequence of such countable sets).
-  Then \(\tau\) defined by
-    \[
-      \tau(s\concat\<\mc U\>,n)
-        =
-      (\oneptlind\kappa\setminus C(\mc U))
-        \cup
-      \sigma(C(s\concat\<\mc U)\>),n)
-    \]
-  is a winning \((k+1)\)-mark for \(\pl F\) in \(\menGame{\oneptlind\kappa}\).
-
-  \(\pl F \kmarkwin{k+1}\schFillIntGame\kappa
-    \Rightarrow
-  \pl F \kmarkwin{k+1}\schFillInitialGame\kappa\):
-  Let \(\sigma\) be a winning \(k\)-mark for \(\pl F\) in
-  \(\schFillIntGame\kappa\). \(\sigma\) is also a winning \(k\)-mark for \(\pl F\)
-  in \(\schFillInitialGame\kappa\).
-
-  \(\pl F \kmarkwin{k+1}\schFillInitialGame\kappa
-    \Rightarrow
-  \pl F \kmarkwin{k+1}\schFillGame\kappa\): Let \(\sigma\) be a winning \(k\)-mark for \(\pl F\) in
-  \(\schFillInitialGame\kappa\). For each finite sequence \(s\), let \(t\preceq s\) mean \(t\)
-  is a final subsequence of \(s\). Then \(\tau\) defined by
-    \[
-      \tau(s\concat\<C\>,n)
-        =
-      \bigcup_{t\preceq s, m\leq n}
-      \sigma(t\concat\<C\>,m)
-    \]
-  is a winning \((k+1)\)-mark for \(\pl F\) in \(\schFillGame\kappa\).
-
-  \(\pl F \kmarkwin{k+1}\schFillGame\kappa
-    \Rightarrow
-  \pl F \kmarkwin{k+1}\schFillInitialGame\kappa\):
-  Let \(\sigma\) be a winning \(k\)-mark for \(\pl F\) in
-  \(\schFillGame\kappa\). \(\sigma\) is also a winning
-  \((k+1)\)-mark for \(\pl F\)
-  in \(\schFillInitialGame\kappa\).
-
-  \(\pl F \ktactwin{k+1}\schFillStrictGame\kappa
-    \Rightarrow
-  \pl F \kmarkwin{k+1}\schFillGame\kappa\):
-  Let \(\sigma\) be a winning \(k\)-tactic for \(\pl F\) in
-  \(\schFillStrictGame\kappa\). For each countable subset \(C\) of \(\kappa\), let \(C+n\)
-  be the union of \(C\) with the \(n\) least ordinals in \(\kappa\setminus C\).
-  Then \(\tau\) defined by
-    \[
-      \tau(\<C_0,\dots,C_i\>,n)
-        =
-      \sigma(\<C_0+(n-i),\dots,C_i+n\>)
-    \]
-  is a winning \((k+1)\)-mark for \(\pl F\) in \(\schFillGame\kappa\).
-\end{proof}
-
-While we have not shown a direct implication between the Menger game and
-Scheeper's original filling game, Scheepers introduced the statement
-\(\alcompS\kappa\) relating to the almost-compatability of injective functions
-from countable subsets of \(\kappa\) into \(\omega\) which may be applied to
-both.
-
-\begin{definition}
-  For two functions \(f,g\) we say \(f\) is \textbf{almost compatible} with
-  \(g\) (\(f\alcomp g\)) if \(|\{x\in\dom(f)\cap\dom(g):f(x)\not=g(x)\}|<\omega\).
-\end{definition}
-
-\begin{definition}
-  \(\alcompS\kappa\) states that there exist injective functions
-  \(f_A:A\to\omega\) for each \(A\in[\kappa]^{\leq\omega}\) such that
-  \(f_A\alcomp f_B\) for all \(A,B\in[\kappa]^\omega\).
-\end{definition}
-
-Scheepers went on to show that \(\alcompS\kappa\) implies
-\(\pl F \ktactwin2 \schFillStrictGame\kappa\). This proof, along with the following
-facts, give us inspiration for
-finding a winning \(2\)-Markov strategy in the Menger game played on
-\(\oneptlind\kappa\).
-
-\begin{theorem}
-  \(\alcompS{\omega_1}\) and \(\neg\alcompS{\mf c^+}\)
-  are theorems of \(ZFC\).
-  \(\alcompS{\mf c}\) is a theorem of \(ZFC+CH\) and consistent with
-  \(ZFC+\neg CH\).
-\end{theorem}
-
-\begin{proof}
-  For \(\alcompS{\omega_1}\), consider the construction of an Aronzajn tree
-  as in \cite{MR597342}; this of course
-  implies \(\alcompS{\mf c}\) under \(CH\).
-  \(\neg\alcompS{\mf c^+}\) is shown by a cardinality argument
-  in \cite{MR1129143}.
-  The consistency result under \(ZFC+\neg CH\)
-  is a lemma for the main theorem in \cite{MR1129143}.
-\end{proof}
-
-\begin{figure}[h]
-\begin{center}
-\begin{tikzpicture}
-  \matrix (m) [matrix of math nodes,row sep=3em,column sep=1em,minimum width=2em]
-  {
-    &
-    \pl F \kmarkwin2\menGame{\oneptlind\kappa} &
-    \pl F \kmarkwin2\schFillIntGame\kappa \\
-
-    \alcompS\kappa &
-    \pl F \kmarkwin2\schFillInitialGame\kappa &
-    \pl F \kmarkwin2\schFillGame\kappa \\
-
-    &
-    &
-    \pl F \ktactwin2\schFillStrictGame\kappa \\
-  };
-  \path[>=latex,->]
-    (m-2-1) edge (m-1-2)
-    (m-2-1) edge (m-2-2)
-    (m-2-1) edge (m-3-3)
-    (m-1-2) edge (m-2-2)
-    (m-1-3) edge (m-2-3)
-    (m-3-3) edge (m-2-3);
-  \path[>=latex,<->]
-    (m-1-2) edge (m-1-3)
-    (m-2-2) edge (m-2-3);
-\end{tikzpicture}
-\end{center}
-\caption{Diagram of Filling/Menger game implications with \(\alcompS\kappa\)}
-\label{fillingGamesDiagram2}
-\end{figure}
-
-\begin{theorem}
-  \(\alcompS\kappa\) implies the game-theoretic results in
-  Figure \ref{fillingGamesDiagram2}.
-\end{theorem}
-
-\begin{proof}
-  Since \(\alcompS\kappa\Rightarrow\pl F \ktactwin2\schFillStrictGame\kappa\) was
-  a main result of \cite{MR1129143}, it is sufficient to show that
-  \(\alcompS\kappa\Rightarrow \pl F \kmarkwin2\schFillIntGame\kappa\).
-
-  Let \(f_A\) for \(A\in[\kappa]^{\leq\omega}\) witness \(\alcompS\kappa\). We define
-  the \(2\)-mark \(\sigma\) as follows:
-    \[
-      \sigma(\<A\>,0) = \{\alpha\in A: f_A(\alpha) \leq 0 \}
-    \]
-    \[
-      \sigma(\<A,B\>,n+1)
-        =
-      \{
-        \alpha \in A\cap B
-      :
-        f_B(\alpha) \leq n+1 \text{ or }
-        f_A(\alpha)\not=f_B(\alpha)
-      \}
-    \]
-  For any attack \(\<A_0,A_1,\dots\>\) by \(\pl C\) and
-  \(\alpha\in\bigcap_{n<\omega}A_n\), either \(f_{A_n}(\alpha)\) is constant for
-  all \(n\), or \(f_{A_n}(\alpha)\not=f_{A_{n+1}}(\alpha)\) for some \(n\);
-  either way, \(\alpha\) is covered.
-\end{proof}
-
-\begin{corollary}
-  \(\pl F \kmarkwin2\menGame{\oneptlind\omega_1}\).
-\end{corollary}
-
-\section{Menger game derived covering properties}
-
-\begin{figure}[h]
-\begin{center}
-\begin{tikzpicture}
-  \matrix (m) [matrix of math nodes,row sep=3em,column sep=1em,minimum width=2em]
-  {
-     \pl F \markwin \menGame{X} &
-     \pl F \kmarkwin2 \menGame{X} &
-     \pl F \win \menGame{X} &
-     \pl C \notwin \menGame{X} \\
-
-     \text{Markov Menger} &
-     2\text{-Markov Menger} &
-     \text{Strategic Menger} &
-     \text{Menger} \\
-  };
-  \path[>=latex,<->]
-    (m-1-1) edge (m-2-1)
-    (m-1-2) edge (m-2-2)
-    (m-1-3) edge (m-2-3)
-    (m-1-4) edge (m-2-4);
-  \path[>=latex,->]
-    (m-1-1) edge (m-1-2)
-    (m-2-1) edge (m-2-2)
-    (m-1-2) edge (m-1-3)
-    (m-2-2) edge (m-2-3)
-    (m-1-3) edge (m-1-4)
-    (m-2-3) edge (m-2-4);
-  \path[>=latex,->,bend right=30, dotted]
-    (m-1-2) edge node {\( \not \)} (m-1-1)
-    (m-2-2) edge node {\( \not \)} (m-2-1)
-    (m-1-4) edge node {\( \not \)} (m-1-3)
-    (m-2-4) edge node {\( \not \)} (m-2-3);
-  \path[>=latex,->,bend right=30, dotted]
-    (m-1-3) edge node {\( ? \)} (m-1-2)
-    (m-2-3) edge node {\( ? \)} (m-2-2);
-\end{tikzpicture}
-\end{center}
-\caption{Diagram of covering properties related to the Menger game}
-\label{menSpec}
-\end{figure}
-
-Limited information strategies for the Menger game naturally define a spectrum
-of covering properties, see Figure \ref{menSpec}. However,
-we do not know if the middle two properties are actually distinct.
-
-\begin{question}\label{perfectTo2Mark}
-  Does there exist a space \(X\) such that \(\pl F \win \menGame{X}\) but
-  \(\pl F \notkmarkwin2 \menGame{X}\)?
-\end{question}
-
-Note that while it's consistent that
-\(\pl F\kmarkwin2\menGame{\oneptlind{\mf c}}\), \(\oneptlind{\kappa}\)
-for \(\kappa>\mf c\) is a candidate to answer the above question.
-
-We are also interested in non-game-theoretic characterizations of these
-covering properties. It has been known for some time that metrizable perfect
-Menger spaces are exactly the metrizable \(\sigma\)-compact spaces, shown first
-by Telgarksy in \cite{MR753073} and later directly by Scheepers in
-\cite{MR1273523}. It's Scheepers' technique which gives inspiration to
-the following.
-
-In the interest of generality, we will first characterize the Markov Menger
-spaces without any separation axioms.
-
-\begin{definition}
-  A subset \(Y\) of \(X\) is \term{relatively compact} to \(X\) if for every open
-  cover of \(X\), there exists a finite subcollection which covers \(Y\).
-\end{definition}
-
-\begin{proposition}
-  For regular spaces, \(Y\) is relatively compact to \(X\) if and only if
-  \(\cl Y\) is compact in \(X\).
-\end{proposition}
-
-%TODO cite source?
-
-\begin{lemma}
-  Let \(\sigma(\mc{U}, n)\) be a Markov strategy for \(F\) in
-  \(\menGame{X}\), and \(\mc{O}\) collect all open covers of \(X\). Then the
-  set
-    \[
-      R_n = \bigcap_{\mc{U}\in\mc{O}} \sigma(\mc{U},n)
-    \]
-  is relatively compact to \(X\). If \(\sigma\) is a winning
-  Markov startegy, then \(\bigcup_{n<\omega} R_n = X\).
-\end{lemma}
-
-\begin{proof}
-  First, for every open cover \(\mc U\in\mc{O}\),
-  \(R_n\subseteq\sigma(\mc U,n)\) is covered by a finite subcollection of \(\mc U\).
-
-  Suppose that \(x \not\in R_n\) for any \(n<\omega\). Then for each \(n\),
-  pick \(\mc{U}_n\in\mc{O}\) such that \(x\not\in \sigma(\mc{U}_n,n)\). Then
-  \(\pl C\) may counter \(\sigma\) with the attack \(\<\mc U_0,\mc U_1,\dots\>\).
-\end{proof}
-
-\begin{definition}
-  A \term{\(\sigma\)-relatively-compact} space is the countable union of
-  relatively compact subsets.
-\end{definition}
-
-\begin{corollary}
-  The following are equivalent:
-  \begin{itemize}
-    \item \(X\) is \(\sigma\)-relatively-compact
-    \item \(\pl F \kmarkwin0 \menGame X\)
-    \item \(\pl F \markwin \menGame X\)
-  \end{itemize}
-\end{corollary}
-
-\begin{proof}
-  If \(X=\bigcup_{n<\omega} R_n\) for \(R_n\) relatively compact, then
-  \(\sigma(n)=R_n\) is a winning \(0\)-mark, which of course gives a
-  winning \(1\)-mark. The previous lemma finishes the proof.
-\end{proof}
-
-\begin{corollary}
-  Let \(X\) be a regular space. The following are equivalent:
-  \begin{itemize}
-    \item \(X\) is \(\sigma\)-compact
-    \item \(X\) is \(\sigma\)-relatively-compact
-    \item \(\pl F \kmarkwin0 \menGame X\)
-    \item \(\pl F \markwin \menGame X\)
-  \end{itemize}
-\end{corollary}
-
-\begin{corollary}
-  \(\pl F\notmarkwin\menGame{\oneptlind{\omega_1}}\).
-\end{corollary}
-
-Note that for Lindel\"of spaces, metrizability is characterized by regularity
-and second-countability.
-
-\begin{lemma}
-  Let \(X\) be a second-countable space. \(\pl F\win\menGame{X}\) if and only if
-  \(\pl F\markwin\menGame{X}\).
-\end{lemma}
-
-\begin{proof}
-  Let \(\sigma\) be a strategy for \(\pl F\), and note that
-  it's sufficient to consider playthroughs with only basic open covers.
-
-  So if \(\mc U_t\) is a basic open cover for \(t<s\in\omega^{<\omega}\), and
-  \(\mc V\) is any basic open cover, we may choose a finite subcollection
-  \(\mc F(s,\mc V)\) of \(\mc V\) such that
-  \[
-    \sigma(\<\mc U_{s\rest 1},\dots,\mc U_{s},\mc V\>)
-      \subseteq
-    \bigcup \mc F(s,\mc V)
-  \]
-
-  Note that there are only countably-many finite collections of basic open sets.
-  Thus we may choose basic open covers \(\mc U_{s\concat\<n\>}\) for \(n<\omega\)
-  such that for any basic open cover \(\mc V\), there exists \(n<\omega\) where
-  \(\mc F(s,\mc V)=\mc F(s,\mc U_{s\concat\<n\>})\).
-
-  Let \(t:\omega\to\omega^{<\omega}\) be a bijection. We define the Markov
-  strategy \(\tau\) as follows:
-  \[
-    \tau(\<\mc V\>, n)
-      =
-    \bigcup \mc F(t(n),\mc V)
-  \]
-
-  Suppose there exists a counter-attack \(\<\mc V_0,\mc V_1,\dots\>\) of
-  basic open covers which defeats \(\tau\). Then there exists
-  \(f:\omega\to\omega\) such that, letting \(t(m_n)=f\rest n\):
-  \[
-    \begin{array}{rcl}
-    x & \not\in & \tau(\<\mc V_{m_n}\>,m_n) \\
-    & = & \bigcup\mc F(f\rest n,\mc V_{m_n}) \\
-    & = & \bigcup\mc F(f\rest n,\mc U_{f\rest (n+1)}) \\
-    & \supseteq & \sigma(\<\mc U_{f\rest 1},\dots,\mc U_{f\rest(n+1)}\>)
-    \end{array}
-  \]
-
-  Thus \(\<\mc U_{f\rest 1}, \mc U_{f\rest 2},\dots\>\) is a successful
-  counter-attack by \(\pl C\) against the perfect information strategy \(\sigma\).
-\end{proof}
-
-\begin{corollary}
-  Let \(X\) be a second-countable space. The following are equivalent:
-  \begin{itemize}
-    \item \(X\) is \(\sigma\)-relatively-compact
-    \item \(F \kmarkwin0 \menGame{X}\)
-    \item \(F \markwin \menGame{X}\)
-    \item \(F \win \menGame{X}\)
-  \end{itemize}
-\end{corollary}
-
-\begin{corollary}
-  Let \(X\) be a metrizable space. The following are equivalent:
-  \begin{itemize}
-    \item \(X\) is \(\sigma\)-compact
-    \item \(X\) is \(\sigma\)-relatively-compact
-    \item \(F \kmarkwin0 \menGame{X}\)
-    \item \(F \markwin \menGame{X}\)
-    \item \(F \win \menGame{X}\)
-  \end{itemize}
-\end{corollary}
-
-\begin{proof}
-  Each bullet implies \(X\) is Lindel\"of, so \(X\) may be assumed to be
-  regular and second-countable.
-\end{proof}
-
-\section{Robustly Menger}
-
-To help describe \(\pl F\kmarkwin2\menGame{X}\) topologically, we introduce a
-slight variant of the Menger game and a related covering property.
-
-\begin{game}
-  Let \(\menGame{X,Y}\) denote the \term{Menger subspace game} which proceeds
-  analogously to the Menger game, except that \(\pl F\) wins whenever
-  \(\bigcup_{n<\omega} \mc F_n\) is a cover for \(Y\subseteq X\).
-\end{game}
-
-Note of course that \(\menGame{X,X}=\menGame{X}\).
-
-\begin{definition}
-  A subset \(Y\) of \(X\) is \term{relatively robustly Menger} if there exist
-  functions \(r_{\mc V}:Y\to\omega\)
-  for each open cover \(\mc V\) of \(X\) such that
-  for all open covers \(\mc U,\mc V\) and numbers \(n<\omega\),
-  the following sets are \(\mc V\)-finite:
-    \[
-      c(\mc V,n)=\{ x\in Y : r_{\mc V}(x)\leq n\}
-    \]
-    \[
-      p(\mc U,\mc V,n+1)=\{ x\in Y : n<r_{\mc U}(x)<r_{\mc V}(x)\}
-    \]
-\end{definition}
-
-\begin{definition}
-  A space \(X\) is \term{robustly Menger} if it is relatively robustly
-  Menger to itself.
-\end{definition}
-
-\begin{proposition}
-  All \(\sigma\)-relatively-compact spaces are robustly Menger.
-\end{proposition}
-
-\begin{proof}
-  If \(X=\bigcup_{n<\omega}R_n\), then for all \(\mc U\), let \(r_{\mc U}(x)\) be the
-  least \(n\) such that \(x\in R_n\). Then \(c(\mc V,n)=\bigcup_{m\leq n}R_m\) and
-  \(p(\mc U,\mc V) = \emptyset\).
-\end{proof}
-
-\begin{theorem}
-  If \(Y\subseteq X\) is relatively robustly Menger, then
-  \(\pl F\kmarkwin2\menGame{X,Y}\).
-\end{theorem}
-
-\begin{proof}
-  We define the Markov strategy \(\sigma\) as follows.
-  Let \(\sigma(\<\mc U\>,0)=c(\mc U,0)\), and let
-  \(\sigma(\<\mc U,\mc V\>,n+1)=c(\mc V,n+1)\cup p(\mc U, \mc V,n+1)\).
-
-  For any attack \(\<\mc{U}_0,\mc{U}_1,\dots\>\) by \(\pl C\) and \(x\in Y\),
-  one of the following must occur:
-
-  \begin{itemize}
-    \item
-      \(r_{\mc U_0}(x)=0\) and thus
-      \(x\in c(\mc U_0,0)\subseteq \sigma(\<\mc U_0\>,0)\).
-
-    \item
-      \(r_{\mc U_0}(x)=N+1\) for some \(N\geq 0\) and:
-      \begin{itemize}
-        \item
-          For all \(n\leq N\),
-          \[
-            r_{\mc U_{n+1}}(x)\leq N+1
-          \]
-          and thus
-          \(x\in c(\mc U_{N+1},N+1) \subseteq
-            \sigma(\<U_N,U_{N+1}\>,N+1)\).
-        \item
-          For some \(n \leq N\),
-          \[ r_{\mc U_n}(x)\leq n \]
-          and thus
-          \(x\in c(\mc U_{n+1},n+1) \subseteq
-            \sigma(\<U_n,U_{n+1}\>,n+1)\).
-        \item
-          For some \(n \leq N\),
-          \[
-            n < r_{\mc U_n}(x)\leq N+1 < r_{\mc U_{n+1}}(x)
-          \]
-         and thus
-         \(x\in p(\mc U_n,\mc U_{n+1},n+1) \subseteq
-          \sigma(\<U_n,U_{n+1}\>,n+1)\)
-       \end{itemize}
-  \end{itemize}
-\end{proof}
-
-\begin{theorem}
-  \(\alcompS\kappa\) implies \(\oneptlind\kappa\) is
-  robustly Menger, and thus
-  \(\pl F\kmarkwin2\menGame{\oneptlind\kappa}\).
-\end{theorem}
-
-\begin{proof}
-  Let \(f_A\) for \(A\in[\kappa]^{\leq\omega}\) witness \(\alcompS\kappa\) and fix
-  \(A(\mc U)\in[\kappa]^{\leq\omega}\) for each open cover \(\mc U\) such that
-  \(\oneptlind\kappa\setminus A(\mc U)\) is contained in some element of
-  \(\mc U\).
-  Then let \(r_{\mc U}(x)=0\) for \(x\in\oneptlind\kappa\setminus A(\mc U)\),
-  and \(r_{\mc U}(\alpha)=f_{A(\mc U)}(\alpha)\) for \(\alpha\in A(\mc U)\).
-
-  It follows that
-    \[
-      c(\mc U,n)
-        =
-      \left(\oneptlind\kappa\setminus A(\mc U)\right)
-        \cup
-      \{\alpha\in A(\mc U) : f_{A(\mc U)}(\alpha)\leq n \}
-    \]
-  is \(\mc U\)-finite, \(\bigcup_{n<\omega}c(\mc U,n)=X\), and
-    \[
-      p(\mc U,\mc V,n+1)
-        =
-      \{
-        \alpha\in A(\mc U)\cap A(\mc V)
-          :
-        n < f_{A(\mc U)}(\alpha) < f_{A(\mc V)}(\alpha)
-      \}
-    \]
-  is finite.
-\end{proof}
-
-We may also consider common counterexamples which are finer
-than the usual Euclidean line.
-
-\begin{definition}
-  Let \(R_{\mathbb Q}\) be the real line with the topology generated by open
-  intervals with or without the rationals removed.
-\end{definition}
-
-\begin{example}
-  \(R_{\mathbb Q}\) is non-regular and non-\(\sigma\)-compact, but is
-  second-countable and \(\sigma\)-relatively-compact.
-\end{example}
-
-\begin{proof}
-  Compact sets in \(R_{\mathbb Q}\) cannot contain open intervals,
-  and thus are nowhere dense in nonmeager \(\mathbb R\),
-  so \(R_{\mathbb Q}\) is not \(\sigma\)-compact. The usual base of
-  intervals with rational endpoints (with or without rationals removed)
-  witnesses second-countability, and \([-n,n]\) is relatively compact.
-\end{proof}
-
-\begin{definition}
-  Let \(R_\omega\) be the real line with the topology generated by open
-  intervals with countably many points removed.
-\end{definition}
-
-\begin{example}
-  \(R_\omega\) is non-regular, non-second-countable, and
-  non-\(\sigma\)-relatively-compact, but \(\pl F\win\menGame{R_\omega}\).
-\end{example}
-
-\begin{proof}
-  If \(S\supseteq\{s_n:n<\omega\}\) for \(s_n\)
-  discrete, then \(U_m=R_\omega\setminus\{s_n:m<n<\omega\}\) yields an
-  infinite cover \(\{U_m:m<\omega\}\) with no finite subcollection covering \(S\),
-  showing that all relatively compact sets are finite, and \(R_\omega\) is not
-  \(\sigma\)-relatively-compact.
-
-  Define the winning strategy \(\sigma\) for \(\pl F\) in \(\menGame{R_\omega}\) as
-  follows: let \(\sigma(\<\mc{U}_0,\dots,\mc{U}_{2n}\>)=[-n,n]\setminus C_n\)
-  for some countable \(C_n=\{c_{n,m}: m<\omega\}\),
-  and let \(\sigma(\<\mc{U}_0,\dots,\mc{U}_{2n+1}\>)=\{c_{i,j} : i,j < n\}\).
-\end{proof}
-
-We will soon see that, assuming \(\alcompS{\mf c}\), \(\pl F\) has a winning
-\(2\)-Markov strategy for \(\menGame{R_\omega}\) as well.
-
-\begin{proposition}
-  If \(X=\bigcup_{i<\omega} X_i\) and \(\pl F \kmarkwin{2} \menGame{X,X_i}\)
-  for \(i<\omega\), then \(\pl F \kmarkwin{2} \menGame{X}\)
-\end{proposition}
-
-\begin{proof}
-  Let \(\sigma_i\) be a \(2\)-Markov strategy
-  for \(\pl F\) in \(\menGame{X,X_i}\).
-
-  We define the \(2\)-Markov strategy
-  \(\sigma\) for \(\menGame{X}\) as follows:
-    \[
-      \sigma(\<\mc U\>,0) = \sigma_0(\<\mc U\>,0)
-    \]
-    \[
-      \sigma(\<\mc U,\mc V\>,n+1)
-        =
-      \bigcup_{i,j\leq n}
-      \sigma_i(\<\mc V\>,0)
-        \cup
-      \sigma_i(\<\mc U,\mc V\>,j+1)
-    \]
-
-  Let \(\<\mc U_0,\mc U_1,\dots\>\) be a successful counter-attack by \(\pl C\)
-  against \(\sigma\). Then there exists \(x\in X_i\) for
-  some \(i<\omega\) such that \(x\) is not contained in
-  \[
-    \sigma(\<\mc U_0\>,0)
-      \cup
-    \bigcup_{n<\omega}
-    \sigma(\<\mc U_n,\mc U_{n+1}\>,n+1)
-  \]
-  It then follows that \(x\) is not contained in
-  \[
-    \sigma_i(\<\mc U_i\>,0)
-      \cup
-    \bigcup_{n<\omega}
-    \sigma_i(\<\mc U_{i+n},\mc U_{i+n+1}\>,n+1)
-  \]
-  and \(\<\mc U_i,\mc U_{i+1},\dots\>\) is a successful counter-attack
-  by \(\pl C\) against \(\sigma_i\).
-\end{proof}
-
-\begin{theorem}[\(\alcompS{\mf c}\)]
-  \(\pl F\kmarkwin2\menGame{R_\omega}\).
-\end{theorem}
-
-\begin{proof}
-  It's sufficient to show that \([0,1]\subseteq R_\omega\) is relatively
-  robustly Menger. Let \(f_A\) witness \(\alcompS{\mf c}\)
-  for \(A\in[[a,b]]^{\leq\omega}\).
-  For each open cover \(\mc U\), let \(A_{\mc U}\) be
-  such that \([0,1]\setminus A_{\mc U}\) is \(\mc U\)-finite.
-  Let \(r_{\mc U}(x)=0\) if \(x\in[0,1]\setminus A_{\mc U}\) and
-  \(r_{\mc U}(x)=f_{\mc A_{\mc U}}(x)\) otherwise.
-
-  It follows then that
-    \[
-      c(\mc U,n) = [0,1]\setminus\{x\in A_{\mc U}:f_{\mc A_{\mc U}}(x)>n\}
-    \]
-  is \(\mc U\)-finite and
-    \[
-      p(\mc U,\mc V,n+1)
-        =
-      \{x\in A_{\mc U}\cap A_{\mc V}
-        :
-      n<f_{\mc A_{\mc U}}(x)<f_{\mc A_{\mc V}}(x)\}
-    \]
-  is finite.
-\end{proof}
-
-The following is left open:
-
-\begin{question}
-  Does there exist a space which is \(2\)-Markov Menger, but not
-  robustly Menger?
-\end{question}
-
-\section*{Acknowlegements}
-
-The author wishes to thank Gary Gruenhage and Alan Dow for their
-very useful comments during the writing of this paper.
+\section{asdf}
 

### 2015-11-17 articles/almost-compatible-functions-and-topological-games/article.tex
paste in s prime notes

@@
 
-\usepackage{../../clontzDefinitions}
-
 \usepackage{tikz}
@@
 
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{proposition}[theorem]{Proposition}
+\usepackage{../../clontzDefinitions}
+
+      \theoremstyle{plain}
+      \newtheorem{theorem}{Theorem}
       \newtheorem{lemma}[theorem]{Lemma}
       \newtheorem{corollary}[theorem]{Corollary}
+      \newtheorem{proposition}[theorem]{Proposition}
+      \newtheorem{conjecture}[theorem]{Conjecture}
+      \newtheorem{question}[theorem]{Question}
+      \newtheorem{claim}[theorem]{Claim}
 
@@
       \newtheorem{definition}[theorem]{Definition}
+      \newtheorem{example}[theorem]{Example}
       \newtheorem{game}[theorem]{Game}
-\newtheorem{example}[theorem]{Example}
-\newtheorem{question}[theorem]{Question}
+
+      \theoremstyle{remark}
+      \newtheorem{remark}[theorem]{Remark}
+
+      \theoremstyle{plain}
+      \newtheorem*{theorem*}{Theorem}
+      \newtheorem*{lemma*}{Lemma}
+      \newtheorem*{corollary*}{Corollary}
+      \newtheorem*{proposition*}{Proposition}
+      \newtheorem*{conjecture*}{Conjecture}
+      \newtheorem*{question*}{Question}
+      \newtheorem*{claim*}{Claim}
+
+      \theoremstyle{definition}
+      \newtheorem*{definition*}{Definition}
+      \newtheorem*{example*}{Example}
+      \newtheorem*{game*}{Game}
+
+      \theoremstyle{remark}
+      \newtheorem*{remark*}{Remark}
 
 \parskip=0.5em
+
+% dow stuff
+          \def\Succ{\mathop{Succ}}
+          \def\dom{\mathop{dom}}
+          \def\val{\operatorname{val}}
+          \def\N{\mathbb N}
+          \def\Nstar{\mathbb N^*}
 
@@
 
-\section{asdf}
+\section{Almost compatible functions}
+
+  \begin{definition}
+    \(S'(\theta)\) states that there exists a cofinal family
+    \(\mc S\subseteq[\theta]^{\omega}\) and a collection of pairwise
+    almost compatible
+    finite-to-one functions \(\{f_S\in\omega^S:S\in\mc S\}\)
+  \end{definition}
+
+  \begin{definition}
+    \(S(\theta)\) strengthens \(S'(\theta)\) by requiring the collection
+    to contain one-to-one functions.
+  \end{definition}
+
+  We wish to show that Scheeper's original \(S(\theta)\) is strictly stronger
+  than \(S'(\theta)\).
+
+  \begin{definition}
+    A topological space is said to be \(\omega\)-bounded if each countable
+    subset of the space has compact closure.
+  \end{definition}
+
+  % TODO: read through Alan's proof and fit to rest of document
+          \begin{theorem}
+           For each $n\in \omega$, there is a locally countable,
+            $\omega$-bounded topology on $\omega_n$. Note
+            that this means that the closure of any set has
+            the same cardinality and weight as the set.
+          \end{theorem}
+
+          To prove the theorem, we must actually prove a stronger lemma.
+
+          \begin{lemma}
+          Assume that $X$ has cardinality at most $\omega_n$ (for
+          any $n\in \omega$),
+          and is locally countable, locally compact, and the closure
+          of each set has the same cardinality as the set.
+          Then $X$ has an $\omega$-bounded extension with the
+          same properties.
+          \end{lemma}
+
+            \begin{proof}
+            We prove this by induction on $n$.
+            In fact, we make our inductive statement that  if $\tilde X$
+            is the extension of $X$, then  $\tilde X \setminus X$ also
+            has cardinality $\omega_n$.
+             If $n=0$,
+              then we can just take the free union of two copies of $X$
+              and then the one-point compactification.
+             So suppose $n>0$ and
+            that $X$ is such a topology on the ordinal $\omega_n$.
+            For each $\alpha<\omega_n$, the closure of the initial
+            segment $\alpha$ is bounded by some $\gamma_\alpha$.
+            Also, because $X$ is locally countable, $\gamma_\alpha$
+            can be chosen so that $\alpha$ is contained  in the interior
+            of $\gamma_\alpha$. There is a cub  $C\subset \omega_n$
+            with the property that for each $\delta\in C$ and $\alpha<\delta$,
+             $\gamma_\alpha$ is also less than $\delta$. This implies
+             that for each $\delta\in C$, the initial segment $\delta$ is
+             open, and if $\delta$ has uncountable cofinality, then
+              $\delta$ is clopen.
+
+              The proof will be easier to visualize if we now
+              identify the points of $X$ with the point set
+               $\omega_n\times \{0\}$ and we will add the points
+                $\omega_n\times \{1\}$ to create the extension.
+             By induction on $\lambda \in C$ we define a topology
+             on $\omega_n\times\{0\}\cup \lambda\times \{1\}$ so that
+             $\omega_n \times \{0\}$ is an open subset. We also ensure,
+             by induction, for each $\alpha<\lambda$,
+             the closure of $\alpha\times 2$ is an
+              $\omega$-bounded  subset of $\lambda\times 2$.
+
+          In the case that $n=1$, then  choose any sequence
+           $\lambda_n : n\in \omega$ increasing cofinal in $\lambda$.
+           If $\lambda $ is a limit in $C$, then we simply take the
+           topology we have constructed so far on $\lambda\times 2$
+           and there's nothing more needs to be done. Otherwise
+          we may assume that $\lambda_0$ is the predecessor
+          of $\lambda\in C$ and
+           we set $Y_\lambda $ to equal the countable set
+            $\overline{\lambda}\setminus \lambda$. For convenience,
+             and with no loss, we assume that $\lambda$ itself is a limit
+             of limits.
+           And we have a topology on
+           $$\lambda_0\times 2 \cup (\lambda \cup Y_\lambda)\times\{0\}~.$$
+            Recursively
+            choose clopen sets $U_n$ in this topology
+             so that $\lambda_0\times 2\subset U_0$,
+             $U_{n}\cup \lambda_{n+1}\times \{0\}$ is contained
+              $ U_{n+1}$ while $U_{n+1}$ is disjoint from $Y_\lambda$.
+              It is easy to see that we can have all the points
+              in $(\lambda\setminus \{\lambda_n : n\in\omega\})\times \{1\}$
+              be isolated, and arrange that $(\lambda_n,1) $ is the
+              point at infinity in the one-point compactification
+              $U_n\cup (\lambda_n\times \{1\})$.
+
+                Now we handle the case $n>1$ and we can shrink $C$
+                and now assume
+                that $C$ is the closure of $\{\lambda\in C : \mbox{cf}(\lambda)>\omega\}$.
+                We again proceed by induction on $\lambda\in C$.  If
+                $\lambda$ is a limit in $C$, then there is nothing to do: we
+                simply have defined an appropriate topology on
+                $\omega_n\times  \{0\}\cup \lambda\times \{1\}$ so that
+                for each $\mu\in C\cap \lambda$ with $\mbox{cf}(\mu)>\omega$,
+                 $\mu\times 2$ is a clopen $\omega$-bounded subspace.
+                In case $\lambda$ is not a limit of $C$, then $\lambda$
+                has uncountable cofinality and a predecessor $\mu\in C$.
+                We therefore have that $\lambda\times\{0\}$ is clopen
+                in $\omega_n\times \{0\}$.
+                 We apply the induction hypothesis
+                to the space $\lambda\times \{0\} \cup \mu\times 2$ to choose
+                the topology on $\lambda\times 2$.
+
+            \end{proof}
+
+  \begin{definition}
+    A Kurepa family \(\mc K\subseteq[\theta]^{\omega}\) on \(\theta\)
+    satisfies that
+    \(\mc K\rest A=\{K\cap A:K\in\mc K\}\) is countable
+    for each \(A\in[\theta]^\omega\).
+  \end{definition}
+
+  \begin{corollary}
+    There exists a Kurepa family cofinal in \([\omega_k]^\omega\)
+    for each \(k<\omega\).
+  \end{corollary}
+
+  \begin{proof}
+    This is actually a corollary of an observation of Todorcevic communicated
+    by Dow in [TODO cite Gen Prog in Top I]:
+    if every Kurepa family of size at most \(\theta\)
+    extends to a cofinal Kurepa family, then the same is true of \(\theta^+\).
+    So the result follows as
+    every Kurepa family \(\mc K\) of size \(\omega\) extends to
+    the cofinal Kurepa family \([\bigcup\mc K]^\omega\).
+
+    We may alternatively
+    obtain the result from the previous topological argument by using the family
+    \(\mc K\) of compact sets in the constructed topology on
+    \(\omega_k\) as our witness. Of course, every Lindel\"of set in
+    a locally countable space is countable. Thus \(\mc K\)
+    is cofinal in \([\omega_k]^\omega\)
+    since for every countable set \(A\), \(\cl A\) is compact and countable.
+    It is Kurepa since for every countable set \(A\), let (TODO)
+  \end{proof}
+
+  \begin{theorem}
+    \(S'(\theta)\) holds whenever there exists a cofinal Kurepa family on \(\theta\).
+  \end{theorem}
+
+  \begin{proof}
+    Let \(k<\omega\), and \(\mc K=\{K_\alpha:\alpha<\kappa\}\)
+    be a cofinal Kurepa family on \(\theta\).
+    We should define \(f_\alpha:K_\alpha\to\omega\) for each \(\alpha<\kappa\).
+
+    Suppose we've defined pairwise almost compatible
+    \(\{f_\beta:\beta<\alpha\}\). To define
+    \(f_\alpha\), we first recall that \(\mc K\rest K_\alpha\) is countable,
+    so we may choose \(\beta_n<\alpha\) for \(n<\omega\) such that
+    \(
+      \{K_\beta:\beta<\alpha\}\rest K_\alpha \setminus \{\emptyset\}
+        =
+      \{K_\alpha\cap K_{\beta_n}:n<\omega\}
+    \).
+    Let \(K_\alpha=\{\delta_{i,j}:i\leq\omega,j<w_i\}\) where
+    \(w_i\leq\omega\) for each \(i\leq\omega\),
+    \(
+      K_\alpha\cap \left(K_{\beta_n}\setminus\bigcup_{m<n}K_{\beta_m}\right)
+        =
+      \{\delta_{n,j}:j<w_n\}
+    \),
+    and
+    \(
+      K_\alpha\setminus\bigcup_{n<\omega}K_{\beta_n}
+        =
+      \{
+        \delta_{\omega,j}:j<w_\omega
+      \}
+    \).
+    Then let \(f_\alpha(\delta_{n,j})=\max(n,f_{\beta_n}(\delta_{n,j}))\) for
+    \(n<\omega\) and \(f_\alpha(\delta_{\omega,j})=j\) otherwise.
+
+    We should show that \(f_\alpha\) is finite-to-one. Let \(n<\omega\).
+    We need only worry about \(\delta_{m,j}\) for \(m\leq n\) since
+    \(f_\alpha(\delta_{m,j})\geq m\). Since each
+    \(f_{\beta_m}\) is finite-to-one, \(f_{\beta_m}(\delta_{m,j})\leq n\)
+    for only finitely many \(j\). Thus \(f_\alpha\) maps to
+    \(n\) only finitely often.
+
+    We now want to demonstrate that \(f_\alpha\sim f_{\beta_n}\) for all
+    \(n<\omega\). We again need only concern ourselves with \(\delta_{m,j}\) for
+    \(m\leq n\) since otherwise \(\delta_{m,j}\not\in K_{\beta_n}\).
+    For \(m=n\), we have
+    \(f_\alpha(\delta_{n,j})=\max(n,f_{\beta_n}(\delta_{n,j}))\) which differs
+    from \(f_{\beta_n}(\delta_{n,j})\) for only the finitely many \(j\) which
+    are mapped below \(n\) by \(f_{\beta_n}\).
+    For \(m<n\) and \(\delta_{m,j}\in K_{\beta_n}\),we have
+    \(f_\alpha(\delta_{m,j})=\max(m,f_{\beta_m}(\delta_{m,j}))\) which can
+    only differ
+    from \(f_{\beta_n}(\delta_{m,j})\) for only the finitely many \(j\) which
+    are mapped below \(m\) by \(f_{\beta_m}\) or the finitely many \(j\)
+    for which the
+    almost compatible \(f_{\beta_n}\sim f_{\beta_m}\) differ.
+  \end{proof}
+
+  \begin{corollary}
+    \(S'(\omega_k)\) holds for all \(k<\omega\).
+  \end{corollary}
+
+  As noted in [TODO cite Dow],
+  Jensen's one-gap two-cardinal theorem under \(V=L\) [TODO cite] can be used
+  to show that there exist cofinal Kurepa families on every cardinal.
+
+  \begin{corollary}[\(V=L\)]
+    \(S'(\theta)\) holds for all cardinals.
+  \end{corollary}
+
+  In particular, \(S(\omega_2)\) fails under \(CH\), showing the two are
+  distinct. Actually, \(CH\) is not required to have \(S(\omega_2)\) fail.
+
+  % TODO: read through Alan's proof and fit to rest of document
+        We are going to need a technical lemma (available in Kunen).
+        \bigskip
+
+        \begin{lemma}
+        Assume that $G\subset \operatorname{Fn}(\omega_2,2)$ is a generic filter,
+         and let $\mu\in \omega_2$. Then the final model $V[G]$ can be
+         regarded as forcing  with $\operatorname{Fn}(\omega_2\setminus \mu,
+         2)$ over the model $V[G_\mu]$.
+        In addition, for each $\operatorname{Fn}(\omega_2,2)$-name $\dot A$
+        of a subset of $\omega$ (treat as a subset of $\omega\times
+        \operatorname{Fn}(\omega_2,2) $),
+        there is a canonical name $\dot A(G_\mu)$ where,
+        $$\dot A(G_\mu) = \{ (n,p\restriction [\mu,\omega_2))  :
+         (n,p)\in \dot A\ \ \mbox{and} \ \ p\restriction \mu\in G_\mu\}$$
+        and we get that the valuation of $\dot A(G_\mu)$ by the tail
+        of the generic, $G_{\omega_2\setminus \mu}$, is the same as
+        the valuation of $\dot A$ by the full generic.
+        \end{lemma}
+
+        \begin{theorem}
+          If we add $\omega_2$ Cohen reals to a model of CH we get
+        that Scheepers' $S(\omega_2)$ (still) fails.
+        \end{theorem}
+
+        \begin{proof}
+        The forcing poset is $\operatorname{Fn}(\omega_2, 2)$.
+        Let $\{ \dot f_{A} : A\in [\omega_2]^\omega\}$ be a family of
+        names such that $\dot f_{A}$ is a one-to-one function from $A$ into
+        $\omega$. It suffices to only consider sets $A$ from the ground
+        model.
+        \bigskip
+
+        Put all the lemma  stuff in an elementary submodel $M$ of the universe
+        (technically of $H(\kappa)$,  or of $V_\kappa$,
+         for some large $\kappa$). Standard methods says that we can assume that
+         $|M|=\omega_1 =\mathfrak c$ and that $M^\omega\subset M$ (which means
+         that every countable subset of $M$ is a member of $M$).
+        \bigskip
+
+        Let $\lambda = M\cap \omega_2$ (same as the supremum of $M\cap
+        \omega_2$). Consider the name  $\dot f_{[\lambda,\lambda+\omega)}$.
+        What is such a name?  We can assume that it is a set of pairs
+         of the form $( (\lambda+k,m), p)$ where $p\in \mathop{Fn}(\omega_2,
+         2)$ and, of course, $k,m\in \omega$. This is (almost) equivalent to
+         saying
+         that $p$ forces that $\dot f_{[\lambda,\lambda+\omega)}(\lambda+k) =
+         m$. We don't take all such $p$, in fact for each $k,m$ it is enough
+        to take a
+         countable set of such $p$ to get an equivalent name
+         (Kunen calls it a nice name if we take, for each $k,m$ an
+        antichain that is maximal among such conditions).
+        Given any such name $\dot f$, let $\operatorname{supp}(\dot f)$
+        denote the union of the domains of conditions $p$ appearing in the
+        name.
+
+         Also let $Y$ equal $\operatorname{supp}(\dot
+         f_{[\lambda,\lambda+\omega)})\setminus \lambda$.
+         Let $\delta$ denote the order type of
+         $Y$ and let the 2-parameter notation
+         $\varphi_{\mu,\lambda}$ be the order-preserving function from
+        $\mu\cup Y$ onto  the ordinal $\mu+\delta$.  This lifts canonically to
+        an order-preserving bijection $\varphi_{\mu,\lambda}:
+        \operatorname{Fn}(\mu\cup Y,2) \mapsto
+        \operatorname{Fn}(\mu+\delta,2)$.
+        Similarly, we make sense of the name
+         $\varphi_{\mu,\lambda}(\dot f_{[\lambda,\lambda+\omega)})$, call it $F_M$.
+        Here simply, for each tuple $(~(k,m)~, p)\in \dot
+        f_{[\lambda,\lambda+\omega)}$,
+         we have that $(~(k,m)~,\varphi_{\mu,\lambda}(p))$ is in $F_M$.
+        Again, let $\varphi_{\mu,\lambda}(\dot f_{[\lambda,\lambda+\omega)})$
+        be interpreted in the above sense as giving $F_M$ (which is an element
+        of $M$).  Note that we do not regard $\delta$ as fixed here, but
+        rather simply depending on the $\operatorname{supp}(\dot
+        f_{[\lambda,\lambda+\omega)})$ described above. Other values
+        replacing $\lambda>\mu$ will result in their own set $Y$
+        and canonical map $\varphi_{\mu,\lambda}$; but one thing we do have to
+        assume (or arrange) for other values $\alpha$ replacing $\lambda$
+        is that $\operatorname{supp}(\dot f_{[\alpha,\alpha+\omega)})$
+        intersected with
+        $\alpha$ is contained in $\mu$.
+
+        Now the object $F_M$ is an
+        element of $M$, and $M$ believes this statement is true:
+        $$
+        (\forall \beta\in\omega_2)~ (\exists \beta<\lambda\in \omega_2)~~~
+        \operatorname{supp}(\dot f_{[\lambda,\lambda+\omega)})
+        \cap \lambda\subset \mu \ \ \mbox{and}\ \
+        F_M = \varphi_{\mu,\lambda}(\dot f_{[\lambda,\lambda+\omega)})$$
+
+        But now, this  means that,
+        not only is there  an $\alpha\in M$,
+        $ F_M = \varphi_{\mu,\alpha}(\dot f_{[\alpha,\alpha+\omega)})$
+        but also that there is an increasing sequence
+         $\{\alpha_\xi : \xi  \in \omega_1\}\subset \lambda$ of
+         such $\alpha$'s satisfying that, for each $\xi$
+        we have that $\operatorname{supp}(\dot
+        f_{[\alpha_\xi,\alpha_\xi+\omega)})$ is contained in $\alpha_{\xi+1}$.
+
+        Choose such a sequence.
+         This means that if we let $A = \bigcup_{n>0} [\alpha_n,\alpha_n+\omega)$ we
+         have the name $\dot f_A$ in $M$. This then means that all
+         the $( (\beta,m) , p)$ appearing in $\dot f_A$ have the property
+         that $\mathop{dom}(p)$ is contained in $M$.
+        There is, within $M$, a name $\dot g$ satisfying that
+         $\dot f_A(\alpha_n+k) = \dot f_{[\alpha_n,\alpha_n+\omega)}(\alpha_n+k)$
+        for all $k >\dot g(n)$.
+
+        \bigskip
+
+        We now apply the above Lemma using $\mu = \mu_0$ and we are now
+        working in the extension $V[G_\mu]$. We will abuse the notation
+        and use $\dot f_{[\alpha_n,\alpha_n+\omega)}$ instead of
+          $\dot f_{[\alpha_n,\alpha_n+\omega)}(G_{\mu})$ as defined in
+          the Lemma.
+        We work for a contradiction. Something special has now happened,
+         namely,  the supports of the names $\{
+        \dot f_{[\alpha_n, \alpha_n+\omega)} :  0< n<\omega\}$ are pairwise disjoint
+        and also disjoint from the support of the name
+         $\dot f_{[\lambda,\lambda+\omega)}$ (under the same convention about
+         $G_\mu$.  And not only that, these names are pairwise isomorphic (in
+         the way that they all map to $F_M$).
+
+        \bigskip
+
+        Since $A$ is disjoint from $[\lambda,\lambda+\omega)$,
+        there must be an integer $\ell$
+        together with a condition
+         $q\in \mathop{Fn}(\omega_2\setminus \mu,2)$ satisfying that for all
+         $n>\ell$ , $q$ forces that
+
+        \centerline{
+         ``if $k>\dot g(n)$ (since  $\alpha_n+k\in A$) then
+         $\dot f_{[\alpha_n,\alpha_n+\omega)}(\alpha_n+k) \neq
+        \dot f_{[\lambda,\lambda+\omega)}(\lambda +k)$''.}
+
+        Choose $n$ large enough so that $\mathop{dom}(q) \cap [\alpha_n,
+        \mu_{n+1})$ is
+        empty.
+         Choose $q_1<q\restriction \lambda$ (in $M$) so that
+        $$ \varphi_{\mu,\alpha_n}(q_1\restriction \operatorname{supp}(
+         \dot f_{[\alpha_n,\alpha_n+\omega)}) =
+        \varphi_{\mu,\lambda}(q\restriction \operatorname{supp}(
+         \dot f_{[\lambda,\lambda+\omega)}) $$
+        and then (again in $M$) choose $q_2 < q_1$
+        so that it both forces a value
+         $L$ on $\ell+\dot g(n)$
+        and subsequently forces a value $m$ on
+         $\dot f_{[\alpha_n, \alpha_n+\omega)}(\alpha_n+L+1)$.
+        But now, again calculate
+        $$ q_3 = \varphi_{\mu,\lambda}^{-1} \circ \varphi_{\mu,\alpha_n}
+        (q_2\restriction \operatorname{supp}(\dot
+        f_{[\alpha_n,\alpha_n+\omega)}))$$
+        and, by the isomorphisms, we have that $q_3$ forces that
+         $\dot f_{[\lambda,\lambda+\omega)}(\lambda+L+1) = m$.
+
+        Technically (or with more care)  all of this is taking place in the
+        poset $\operatorname{Fn}(\omega_2\setminus \mu,2)$ and this means
+        that $q_3$ and $q$ are all compatible with each other.
+
+        Follow
+        the bouncing ball: it suffices to consider
+         $q(\beta)=e$ and to assume that $q_3(\beta)$ is defined.
+        Since $q_3(\beta)$ is defined, we have that
+        there is a  $\beta'\in\mathop{dom}(q_2)$ such that $
+         \varphi_{\mu,\lambda}(\beta) = \varphi_{\mu,\alpha_n}(\beta')$,
+        and that $q_3(\beta) = q_2(\beta')$.
+        But, by definition of $q_1$, $\beta'\in\mathop{dom}(q_1)$
+        and even  that $q_1(\beta') = q(\beta)$.
+         Then, since $q_2<q_1$, we have that $q_2(\beta')=q_1(\beta') =
+         q(\beta)$. This completes the circle that $q_3(\beta) = q(\beta)$.
+        \bigskip
+
+        Finally, our contradiction is that $q_3\cup q_2\cup q$
+        forces that
+         $k=L+1$ violates the quoted statement above.
+        \end{proof}
+
+  On the other hand, it's also consistent that \(S'(\theta)\) can fail.
+
+  \begin{theorem}
+    There's a model where \(S'(\omega_\omega)\)
+    fails.
+  \end{theorem}
+
+  \begin{proof}
+          We will need the model constructed in \cite{MR1045371} in
+           which an instance of Chang's conjecture
+           $(\aleph_{\omega+1},\aleph_\omega) \rlap{$\rightarrow$}\,{\rightarrow}
+           (\aleph_1,\aleph_0)$ is shown to fail.
+
+          We can take as a given (as shown in \cite[Theorem 5]{MR1045371}) that we may
+          assume that we have a model $V$
+          of GCH in which there are regular limit cardinals $\kappa<\lambda$
+          satisfying that
+          $(\lambda^{+\omega+1},\lambda^{+\omega})\rlap{$\rightarrow$}\,{\rightarrow}
+          (\kappa^{+\omega+1},\kappa^{+\omega})$.
+
+          What this says is that if $L$ is a countable language
+          with at least one unary relation symbol $R$ and
+           $M$ is a model of $L$  with base set $\lambda^{+\omega+1}$
+          in which the interpretation of $R$ has cardinality
+           $\lambda^{+\omega}$, then $M$ has an elementary submodel
+           $N$ of cardinality $\kappa^{+\omega+1}$ in which
+          $R\cap N$ has cardinality $\kappa^{+\omega}$ (of course
+           $R\cap N$ is the interpretation of $R$ in $N$ because
+          $N\prec M$).
+
+          The interested reader will want to know that it is shown in
+          \cite{MR1045371} that if $\kappa$ is a 2-huge cardinal and $j$ is the 2-huge
+          embedding with critical point $\kappa$, then with
+           $\lambda = j(\kappa)$ one has that
+          $(\lambda^{+\omega+1},\lambda^{+\omega})\rlap{$\rightarrow$}\,{\rightarrow}
+          (\kappa^{+\omega+1},\kappa^{+\omega})$ holds.
+          \bigskip
+
+          Let $\{ h_\xi : \xi \in \lambda^{+\omega+1}\}$
+          be a scale in $\Pi\{ \lambda^{+n+1} : n\in \omega\}$
+           ordered by the usual mod finite coordinatewise
+          ordering. For convenience we may assume that $h_\xi(n) \geq
+          \lambda^{+n}$ for all $\xi$ and all $n$.  If $P$ is any poset of
+          cardinality less than $\lambda^{+\omega}$, then in the forcing
+          extension by $P$,  the sequence
+          $\{ h_\xi : \xi \in \lambda^{+\omega+1}\}$  remains cofinal in
+           $\Pi\{ \lambda^{+n+1} : n\in \omega\}$.
+
+          \bigskip
+
+          The forcing notion $\mathbb P_0$ is simply the finite condition
+          collapse of $\kappa^{+\omega}$, i.e. $\mathbb P_0 = \left(
+           \kappa^{+\omega}\right)^{<\omega}$. In the forcing extension by
+           $\mathbb P_0$, one now has that the ordinal $\kappa^{+\omega+1}$
+           from $V$ is the first uncountable cardinal $\aleph_1$. Then in this
+           forcing extension we let $\mathbb P_1$ be the countable condition
+           Levy collapse, $Lv(\lambda,\omega_2)$, which collapses all cardinals
+           less than $\lambda$ to have cardinality at most $\aleph_1$. The poset
+           $\mathbb P_1$ has cardinality $\lambda$. We treat
+          $\mathbb P_1$ as containing $\mathbb P_0$
+          as a subposet by identifying each $(p_0,1)$ with $p_0$.
+          After forcing with $\mathbb P_0*\mathbb P_1$ we will have
+          that $\omega_1$ is the ordinal $\left(\kappa^{+\omega+1}\right)^V$,
+           $\omega_2$ is the ordinal $\lambda$, and $\omega_\omega$ is the
+           ordinal $\left(\lambda^{+\omega}\right)^V$.
+
+          \bigskip
+
+          Now we assume that we have an assignment $\dot f_{\dot A}$ of a
+           $\mathbb P_0*\mathbb P_1$-name of a finite-to-one function from
+           $\dot A$ into $\omega$ for each
+           $\mathbb P_0*\mathbb P_1$-name of a countable subset of
+           $\lambda^{+\omega+1}$. We will obtain a contradiction.
+
+          Let $\{ \dot A_\xi : \xi \in \lambda^{+\omega+1}\}$ be an enumeration
+          of all the  nice $\mathbb P_0$-names of countable
+          subsets of $\lambda^{+\omega}$. For each $\xi\in \lambda^{+\omega+1}$,
+           let $\dot f_\xi$ be another notation for $\dot f_{\dot A_\xi}$.
+          Since $\mathbb P_0$ forces that $\mathbb P_1$ is countably closed,
+          the collection of all nice  $\mathbb P_0$-names will produce all
+          the countable sets in the extension by $\mathbb P_0* \mathbb
+          P_1$, but $\mathbb P_0*\mathbb P_1$ can introduce new enumerations of
+          these names.
+          For each $\xi\in \lambda^{+\omega+1}$,
+          there is a minimal $\zeta_\xi$ so that $\dot A_{\zeta_\xi}$ is the
+          canonical name for the range of $h_\xi$. This means that
+           $\dot f_{\zeta_\xi} \circ h_\xi$ is simply the
+           $\mathbb P_0 *\mathbb P_1$-name of a finite-to-one function from
+           $\omega$ to $\omega$.
+            For each $\xi\in \lambda^{+\omega+1}$,
+           choose any $p_\xi \in \mathbb P_0*\mathbb P_1$ so that
+           there is a nice $\mathbb P_0$-name, $\dot H_\xi$,
+           that is forced by
+           $p_\xi$  to equal $\dot f_{\zeta_\xi}\circ h_\xi$.
+            Choose $\Lambda\subset \lambda^{+\omega+1}$
+            of cardinality $\lambda^{+\omega+1}$
+            and so that there is a pair $p,\dot H$
+            satisfying that $p_\xi = p$ and $\dot H_\xi = \dot H$
+            for all $\xi\in \Lambda$. We may assume that $p$
+            is in a generic filter $  G$.
+
+          Let $\{ x_\xi : \xi\in \lambda^{+\omega+1}\}$ be any enumeration of
+           $H(\lambda^{+\omega+1})$  such that
+           $\{ x_\xi : \xi\in \lambda^{+\omega}\}$ is also equal to
+           $H(\lambda^{+\omega})$. We choose this enumeration in such a way that
+           $x_\xi\in x_\eta$ implies $\xi<\eta$.
+          We use relation symbol $R_0$ to code
+          (and well order)
+           $(H(\lambda^{+\omega+1}), \in)$ as follows: $(\xi,\eta)\in R_0$
+          if and only if $x_\xi\in x_\eta$.
+          Let $R_1$ be a binary relation on $\kappa^{+\omega}$ so that
+          $(\kappa^{+\omega},R_1)$ is isomorphic to $\mathbb P_0$. Let
+           $R_2$ be a binary relation on $\lambda$ so that
+           $R_2\cap (\kappa^{+\omega}\times \kappa^{+\omega})=R_1$ and
+           $(\lambda,R_2)$ is isomorphic to $\mathbb P_0*\mathbb P_1$.
+          Let $\psi$ be the poset isomorphism from $\lambda$ to
+           $\mathbb P_0*\mathbb P_1$.
+
+          We continue coding. We can code the sequence
+           $\{ h_\xi : \xi\in \lambda^{+\omega+1}\}$ as another binary  relation
+           $R_3$ on $\lambda^{+\omega+1}$ where $R_3\cap \left(\{\xi\}\times
+           \lambda^{+\omega+1}\right) = \{ (\xi,h_\xi(n) ) : n\in \omega\}$
+          for each $\xi\in \lambda^{+\omega+1}$. The relation symbol $R_4$ can
+          code the sequence $\{ \dot A_\xi : \xi \in \lambda^{+\omega+1}\}$
+          where $(\xi, \alpha, \zeta) \in R_4$ if and only if
+          $(\check \alpha, \psi(\zeta))$ is in the name $\dot A_\xi$.
+           Let $R_5$ code this collection, i.e.
+           $(\gamma,n,m,\eta)\in R_5$ if and only if
+           $(\check{(n,m)}, \psi(\eta))\in \dot H_\gamma$. Also let $R_6$ code
+           (equal)  the set $\Lambda$.
+          Finally we use the relation symbol $R_7$ to similarly code the
+          sequence $\{ \dot f_\xi  : \xi \in \lambda^{+\omega+1}\}$:
+           $(\xi, \alpha, n, \zeta) \in R_7$ if and only if
+          $(\check {(\alpha,n)}, \psi(\zeta))$ is in the name $\dot f_\xi$.
+
+          Needless to say, the unary relation symbol $R$
+          is interpreted as the set $\lambda^{+\omega}$ for the application of
+          $(\lambda^{+\omega+1},\lambda^{+\omega})\rlap{$\rightarrow$}\,{\rightarrow}
+          (\kappa^{+\omega+1},\kappa^{+\omega})$.
+           Now  we have defined our model
+          $M$  of the language $L= \{\in, R, R_0,\ldots, R_7\}$,
+           and we choose an elementary submodel
+          $N$ witnessing
+          $(\lambda^{+\omega+1},\lambda^{+\omega})\rlap{$\rightarrow$}\,{\rightarrow}
+          (\kappa^{+\omega+1},\kappa^{+\omega})$. Of course $N$ is really just
+          a $\kappa^{+\omega+1}$ sized subset of $\lambda^{+\omega+1}$
+          with the additional property that $N\cap \lambda^{+\omega}$ has
+          cardinality $\kappa^{+\omega}$.  In the
+          forcing extension $N$ has cardinality $\omega_1$ and
+           $A= N\cap \lambda^{+\omega}$ is countable.
+
+          We will need the following claim from \cite{MR1045371}
+
+          \begin{claim*} We may assume that $N$ satisfies that
+           $N\cap \kappa^{+\omega+1}$ is transitive (i.e. an initial segment).
+          \end{claim*}
+
+          \begin{proof}[Proof of Claim]
+          Suppose  our originally supplied $N$ fails the conclusion of the
+          claim.
+          We   know that $\kappa^{+\omega}\in N$,
+          (  via $R_1$)
+          in which case so is $\kappa^{+\omega+1}$.
+
+          Then set $\beta_0 = \sup(N\cap \kappa^{+\omega+1})$ and consider the
+          Skolem closure $\mathop{Hull}(N\cup \beta_0, M)$.  A little informally
+          (in that we have to formalize the enumeration of formulas)
+          let $\{\varphi_n : n\in \omega\}$ is the enumeration of all formulas
+          in the language $L$, and let  $\ell_n$ be the minimal integer such
+          that the free variables of $\varphi_n$ are among
+           $\{ v_0, \ldots, v_{\ell_n}\}$.
+          Then,   for each tuple
+          $\langle \xi_1,\ldots, \xi_{\ell_n} \rangle$
+          of elements of $\lambda^{+\omega+1}$,
+           we define $f_n(\xi_1,\ldots, \xi_{\ell_n})$ to be
+           the minimal $\xi_0\in \lambda^{+\omega+1}$ such that
+           $M\models \varphi_n(\xi_0,\ldots, \xi_{\ell_n})$.
+          If there is no such $\xi_0$,
+             in other words if $M\models \lnot\exists x~~  \varphi_n(x,\xi_1,
+          \ldots,\xi_{\ell_n})$, then set
+           $f_n(\xi_1,\ldots, \xi_{\ell_n})$ to be $0$.
+          Now $\mathop{Hull}(N\cup \beta_0,M)$ is just the minimal superset
+           $X$
+          of $N\cup \beta_0$ that satisfies that
+           $f_n[X^{\{1,\ldots,\ell_n\}}] \subset X$ for all $n$. Since this is
+           simply a large algebra, we can generate all the terms $t$ of
+          the algebraic operations $\{ f_n : n\in \omega\}$.
+          It is easily seen that for each $\zeta \in X$, there is a term
+          $t(v_1,\ldots, v_m)$ such that $\zeta  = t(\delta_1,\ldots, \delta_m)$
+           for some sequence $\langle \delta_1,\ldots, \delta_m\rangle$ with
+           each $\delta_i\in  N\cup \beta_0$.
+           Assume that
+            $\zeta\in \kappa^{+\omega+1}$. By
+            re-indexing the variables in the term we can assume
+            that there is an $n\leq m$ so that
+             $\delta_i  <\beta_0$ for $1\leq i\leq n$
+              and $\kappa^{+\omega+1}\leq \delta_i$ for $n<i\leq m$.
+              Let $\vec a $ denote
+              the tuple $\langle \delta_{n+1},\ldots, \delta_m\rangle$.
+            Choose $\eta\in N\cap \kappa^{+\omega+1}$ large enough so that
+           $ \{  \delta_1, \ldots, \delta_n\}$ is contained in  $\eta$. Since set-membership
+           in $M$ is coded by $R_0$ rather than $\in$ we have to argue a little
+           less naturally.
+           Consider the set
+             $s_0(\eta,\vec a) = \{ t(\gamma_1,\ldots, \gamma_n,\vec a) :
+          \{\gamma_1,\cdots,\gamma_n\} \in [\eta]^{\leq n}\}$. Clearly
+           $s_0(\eta,\vec a)$ is a member of $H(\lambda^{+\omega+1})$.
+           Now define $s_1(\eta,\vec a) $ to be
+           $\{ x_\alpha : \alpha\in s_0(\eta, \vec a)\}$,
+           and choose the
+           unique $\zeta_1\in \lambda^{+\omega+1}$ such
+           that $x_{\zeta_1} = s_1(\eta,\vec a)$. We claim that $\zeta_1\in N$.
+           Note that $\alpha R_0\zeta_1$ holds if and only if
+            $ \alpha \in s_0(\eta,\vec a)$, and therefore
+           $$M\models (\forall \alpha)\left[\alpha R_0 \zeta_1 ~~\mbox{iff}~~
+           (\exists   \gamma_1\in \eta)\cdots(\exists \gamma_n\in\eta)(\alpha=
+           t(\gamma_1,\ldots, \gamma_n,\vec a))\right]~.$$
+           By elementarity then we have that $\zeta_1\in N$,
+           and by similar reasoning the supremum, $\zeta_0$,
+          of $\zeta_1\cap \kappa^{+\omega+1}$ is also in $N$.
+             This of course means that $\zeta < \xi_0$.
+          \end{proof}
+
+          We use the elementarity of
+           $N$  to deduce properties of the families
+           $\{ \dot A_\xi : \xi\in N\}$ and $\{ \dot f_\xi : \xi \in
+           N\}$.  Actually the collection we are most interested in
+           is the family $\{ h_\xi : \xi\in \Lambda\cap N\}$.
+
+           Since  $\mathfrak c < \kappa^{+\omega+1}$ there
+            is a function $\langle \varrho_n : n\in \omega\rangle$
+            in $\Pi_n \lambda^{+\omega}   $ such that the sequence
+             $\{ h_\xi : \xi \in N\}$ is unbounded mod finite
+             in $\Pi_n \varrho_n$ (by Shelah's pcf theory).
+             This is in Jech somewhere.
+             For each $n$, $\rho_n \leq \sup(N\cap \lambda^{+n+2})$.
+
+             Since $\mathbb P_0$ has cardinality less than $|N|=\kappa^{+\omega+1}$,
+              the sequence $\{ h_\xi : \xi \in \Lambda\cap N\}$ remains unbounded
+              mod finite in $\Pi_n \varrho_n$ (and in
+               $\Pi_n (\varrho_n\cap N)$).  Now pass to the extension by
+                $G\cap \mathbb P_0$ and let $H$ be the function
+                 $\operatorname{val}_{G}(\dot H)$, and we recall
+                 that $f_{\zeta_\xi}(h_\xi(n)) = H(n)$ for all $n\in \omega$.
+           Now pass to the full extension $V[G]$ and again, since
+            $\mathbb P_1$ was forced to be countably closed,
+             the family $\{ h_\xi : \xi \in \Lambda\cap N\}$ is still
+             unbounded in $\Pi_n (\varrho_n \cap N)$. We let
+             $A$ be the countable set $N\cap \lambda^{+\omega}$,
+             and for  each
+             $\xi\in \Lambda\cap N$, there is an $n_\xi$ such that
+              $f_{\xi}(h_\xi(m)) = f_A(h_\xi(m))$ for all $m>n_\xi$.
+              There is a single $n$ so that $\Lambda_n
+               = \{\xi\in \Lambda\cap N       : n_\xi = n\}$ has cardinality
+                $\omega_1 $, and thus
+                $\{ h_\xi : \xi\in \Lambda_n\cap N\}$ is also unbounded
+                in $\Pi_n (\rho_n\cap N)$.
+          This certainly implies that there is an $m>n$
+          such that $\{ h_\xi (m) : \xi\in \Lambda_n\cap N\}$ is infinite.
+          This completes the proof since  $f_{A}(h_\xi(m)) = H(m)$
+          for all $\xi\in \Lambda_n\cap N$.
+
+  \end{proof}
+
+  \begin{question}
+    Is \(S'(\theta)\) equivalent to having a Kurepa family on \(\theta\)?
+  \end{question}
+
+  \section*{Applications!}
+
+  \begin{figure}[h]
+\begin{center}
+\begin{tikzpicture}
+  \matrix (m) [matrix of math nodes,row sep=3em,column sep=1em,minimum width=2em]
+  {
+    &
+    \pl F \kmarkwin2\menGame{\oneptlind\kappa} &
+    \pl F \kmarkwin2\schFillIntGame\kappa \\
+
+    S'(\kappa) &
+    \pl F \kmarkwin2\schFillInitialGame\kappa &
+    \pl F \kmarkwin2\schFillGame\kappa \\
+
+    &
+    &
+    \pl F \ktactwin2\schFillStrictGame\kappa \\
+  };
+  \path[>=latex,->]
+    (m-2-1) edge (m-1-2)
+    (m-2-1) edge (m-2-2)
+    (m-2-1) edge (m-3-3)
+    (m-1-2) edge (m-2-2)
+    (m-1-3) edge (m-2-3)
+    (m-3-3) edge (m-2-3);
+  \path[>=latex,<->]
+    (m-1-2) edge (m-1-3)
+    (m-2-2) edge (m-2-3);
+\end{tikzpicture}
+\end{center}
+\caption{Diagram of Scheeper/Menger game implications with \(S'(\kappa)\)}
+\label{GamesDiagram2}
+\end{figure}
+
+  \begin{theorem}
+    Figure \ref{GamesDiagram2} holds. (Proven in [TODO cite])
+    (Actually, TODO double-check that it works with just S', particularly
+    the strict game)
+  \end{theorem}
+
+  It was left open if these implications can be reversed. The answer is
+  consistently no.
+
+  \begin{theorem}
+    Let \(\alpha\) be the limit of increasing ordinals \(\beta_n\) for \(n<\omega\).
+    If \(\pl F \kmarkwin2\schFillIntGame{\omega_{\beta_n}}\) for all
+    \(n<\omega\), then \(\pl F\kmarkwin2\schFillIntGame{\omega_\alpha}\).
+  \end{theorem}
+
+  \begin{proof}
+    Let \(\sigma_n\) be a winning \(2\)-mark for \(\pl F\) in
+    \(\schFillIntGame{\omega_{\beta_n}}\). Define the \(2\)-mark \(\sigma\)
+    for \(\pl F\) in \(\schFillIntGame{\omega_\alpha}\) as follows:
+    \[
+      \sigma(\<C\>,0)
+        =
+      \sigma_0(\<C\cap\omega_{\beta_0}\>,0)
+    \]
+    \[
+      \sigma(\<C,D\>,n+1)
+        =
+      \sigma_{n+1}(\<D\cap\omega_{\beta_{n+1}}\>,0)
+        \cup
+      \bigcup_{m\leq n}
+      \sigma_m(\<C\cap\omega_{\beta_m},D\cap\omega_{\beta_m}\>,n-m+1)
+    \]
+
+    Let \(\<C_0,C_1,\dots\>\) be an attack by
+    \(\pl C\) in \(\schFillIntGame{\omega_\alpha}\), and
+    \(\alpha\in\bigcap_{n<\omega}C_n\).
+    Choose \(N<\omega\) with \(\alpha<\omega_{\beta_{N+1}}\). Consider the
+    attack
+    \(\<C_{N+1}\cap\omega_{\beta_{N+1}},C_{N+2}\cap\omega_{\beta_{N+1}},\dots\>\)
+    by \(\pl C\) in \(\schFillIntGame{\omega_{\beta_{N+1}}}\). Since
+    \(\sigma_{N+1}\) is a winning strategy and
+    \(\alpha\in\bigcap_{n<\omega}C_{N+n+1}\cap\omega_{\beta_{N+1}}\), either
+    \(\alpha\in\sigma_{N+1}(\<C_{N+1}\cap\omega_{\beta_{N+1}}\>,0)\) and thus
+    \(\alpha\in\sigma(\<C_N,C_{N+1}\>,N+1)\), or
+    \(
+      \alpha
+        \in
+      \sigma_{N+1}(
+        \<C_{N+M+1}\cap\omega_{\beta_{N+1}},C_{N+M+2}\cap\omega_{\beta_{N+1}}\>
+        ,M+1
+      )
+    \)
+    for some \(M<\omega\) and thus
+    \(
+      \alpha
+        \in
+      \sigma(
+        \<C_{N+M+1},C_{N+M+2}\>,
+        N+M+2
+      )
+    \). Thus \(\sigma\) is a winning strategy.
+  \end{proof}
+
+  \begin{theorem}
+    Let \(\alpha\) be the limit of increasing ordinals \(\beta_n\) for \(n<\omega\).
+    If \(\pl F \kmarkwin2\schFillInitialGame{\omega_{\beta_n}}\) for all
+    \(n<\omega\), then \(\pl F\kmarkwin2\schFillInitialGame{\omega_\alpha}\).
+  \end{theorem}
+
+  \begin{proof}
+    Let \(\sigma_n\) be a winning \(2\)-mark for \(\pl F\) in
+    \(\schFillInitialGame{\omega_{\beta_n}}\). Define the \(2\)-mark \(\sigma\)
+    for \(\pl F\) in \(\schFillInitialGame{\omega_\alpha}\) as follows:
+    \[
+      \sigma(\<C\>,0)
+        =
+      \sigma_0(\<C\cap\omega_{\beta_0}\>,0)
+    \]
+    \[
+      \sigma(\<C,D\>,n+1)
+        =
+      \sigma_{n+1}(\<D\cap\omega_{\beta_{n+1}}\>,0)
+        \cup
+      \bigcup_{m\leq n}
+      \sigma_m(\<C\cap\omega_{\beta_m},D\cap\omega_{\beta_m}\>,n-m+1)
+    \]
+
+    Let \(\<C_0,C_1,\dots\>\) be an attack by
+    \(\pl C\) in \(\schFillInitialGame{\omega_\alpha}\), and
+    \(\alpha\in C_0\).
+    Choose \(N<\omega\) with \(\alpha<\omega_{\beta_{N+1}}\). Consider the
+    attack
+    \(\<C_{N+1}\cap\omega_{\beta_{N+1}},C_{N+2}\cap\omega_{\beta_{N+1}},\dots\>\)
+    by \(\pl C\) in \(\schFillInitialGame{\omega_{\beta_{N+1}}}\). Since
+    \(\sigma_{N+1}\) is a winning strategy and
+    \(\alpha\in C_{N+1}\cap\omega_{\beta_{N+1}}\), either
+    \(\alpha\in\sigma_{N+1}(\<C_{N+1}\cap\omega_{\beta_{N+1}}\>,0)\) and thus
+    \(\alpha\in\sigma(\<C_N,C_{N+1}\>,N+1)\), or
+    \(
+      \alpha
+        \in
+      \sigma_{N+1}(
+        \<C_{N+M+1}\cap\omega_{\beta_{N+1}},C_{N+M+2}\cap\omega_{\beta_{N+1}}\>
+        ,M+1
+      )
+    \)
+    for some \(M<\omega\) and thus
+    \(
+      \alpha
+        \in
+      \sigma(
+        \<C_{N+M+1},C_{N+M+2}\>,
+        N+M+2
+      )
+    \). Thus \(\sigma\) is a winning strategy.
+  \end{proof}
+
+  \begin{corollary}
+    It is consistent that \(S'(\omega_\omega)\) fails,
+    but as \(S'(\omega_k)\) holds for all \(k<\omega\), we have
+    \(\pl F\kmarkwin2\schFillIntGame{\omega_\omega}\) and
+    \(\pl F\kmarkwin2\schFillInitialGame{\omega_\omega}\).
+  \end{corollary}
+
+  A tricky topological question: does \(\pl F\win\menGame{X}\) imply
+  \(\pl F\kmarkwin2\menGame{X}\)?
+  (C showed that )
+  Under \(V=L\), we cannot hope to find
+  a counterexample using \(X=\oneptlind\kappa\) since
+  \(S'(\kappa)\) and thus \(\pl F\kmarkwin2\schFillIntGame{\kappa}\)
+  always holds.
+
+  \begin{definition}
+    Let \(R_\omega\) be the real numbers with the topology of the usual
+    open intervals with countably many elements removed.
+  \end{definition}
+
+  \begin{theorem}
+    \(\pl F\win\menGame{R_\omega}\).
+    If there exists a Kurepa family on the reals, then
+    \(\pl F\kmarkwin2\menGame{R_\omega}\).
+  \end{theorem}
 

### 2015-11-17 articles/almost-compatible-functions-and-topological-games/article.tex
introduction to s'kappa paper

@@
 
-\section{Almost compatible functions}
+\section{Introduction}
+
+  \begin{definition}
+    Two functions \(f,g\) are almost compatible, that is, \(f\sim g\) when
+    \(\{a\in\dom f\cap\dom g:f(a)\not=g(a)\}\) is finite.
+  \end{definition}
+
+  Marion Scheepers used almost compatible functions in \cite{MR1129143} in order
+  to study the existence of limited information strategies on a variation
+  of the meager-nowhere dense game he introduced in \cite{MR1183703}.
+
+  \begin{game}
+    Let \(\schFillStrictGame\kappa\) denote
+    \term{Scheepers' strict countable-finite union game}
+    with two players \(\pl C\), \(\pl F\). In round \(0\), \(\pl C\) chooses
+    \(C_0\in[\kappa]^{\leq\omega}\), followed by \(\pl F\) choosing
+    \(F_0\in[\kappa]^{<\omega}\). In round \(n+1\), \(\pl C\) chooses
+    \(C_{n+1}\in[\kappa]^{\leq\omega}\) such that \(C_{n+1}\supset C_n\), followed
+    by \(\pl F\) choosing \(F_{n+1}\in[\kappa]^{<\omega}\).
+
+    \(\pl F\) wins the game if
+    \(\bigcup_{n<\omega} F_n\supseteq\bigcup_{n<\omega} C_n\); otherwise,
+    \(\pl C\) wins.
+  \end{game}
+
+  Of course, with perfect information this game is trivial: during round
+  \(n\) player \(\pl F\) simply chooses \(n\) ordinals from each of the
+  \(n\) countable sets played by \(\pl C\). However, if \(\pl F\) is limited
+  to using information from the last \(k\) moves by \(\pl C\) during each
+  round, the task becomes more difficult. Call such a strategy a
+  \term{\(k\)-tactical strategy} or \term{\(k\)-tactic}; if using the round
+  number is allowed, then the strategy is called a \term{\(k\)-Markov strategy}
+  or a \term{\(k\)-mark}.
+
+  \begin{definition}
+    The statement \(S(\kappa)\) (given as \(S(\kappa,\aleph_0,\omega)\)
+    in \cite{MR1129143}) claims that there exist injections
+    \(f_A:A\to\omega\) for each \(A\in[\kappa]^{\leq\aleph_0}\) such that
+    the collection \(\{f_A:A\in[\kappa]^{\leq\aleph_0}\}\) is pairwise
+    almost compatible.
+  \end{definition}
+
+  In the same paper, Scheepers noted that \(S(\omega_1)\) holds in \(ZFC\),
+  and that it's possible to force \(\mf c\) to be arbitrarily large
+  while preserving \(S(\mf c)\). However, \(S(\mf c^+)\) always fails.
+  This axiom may be applied to obtain a winning \(2\)-tactic for \(\pl F\)
+  in the countable-finite game.
+
+  In \cite{clontzMengerGamePreprint}, Clontz related this game to a game
+  which may be used to characterize the Menger covering property of a
+  topological space.
+
+  \begin{game}
+    Let \(\menGame{X}\) denote the \term{Menger game} with players \(\pl C\),
+    \(\pl F\).
+    In round \(n\), \(\pl C\) chooses an open cover \(\mc U_n\), followed by
+    \(\pl F\)
+    choosing subset \(F_n\) of \(X\) which may be finitely covered by \(\mc U_n\).
+
+    \(\pl F\) wins the game if \(X = \bigcup_{n<\omega}F_n\),
+    and \(\pl C\) wins otherwise.
+  \end{game}
+
+  This characterization is slightly different than the typical characterization
+  in which the second player first chooses a specific
+  finite subcollection \(\mc F_n\) of the cover itself and lets
+  \(F_n=\bigcup \mc F_n\), denoted as \(G_{fin}(\mc O,\mc O)\)
+  in \cite{MR1378387}.
+  However, it's easily seen that these games are equivalent
+  for perfect information strategies (so both characterize
+  the Menger property), and this characterization is
+  more convenient for our concerns.
+
+  \begin{definition}
+    Let \(\oneptlind\kappa=\kappa\cup\{\infty\}\) where \(\kappa\) is
+    discrete and \(\infty\)'s neighborhoods are the co-countable sets
+    containing it.
+  \end{definition}
+
+  The relationship between \(\schFillStrictGame\kappa\) and
+  \(\menGame{\oneptlind\kappa}\) is strong; in both games \(\pl C\) essentially
+  chooses a countable subset of \(\kappa\) followed by \(\pl F\) choosing
+  a finite subset of that choice, and it's easy to see the winning perfect
+  information strategy for \(\pl F\) in both games.
+  In addition, it was shown in
+  \cite{clontzMengerGamePreprint} that when \(S(\kappa)\) holds,
+  \(\pl F\) has a winning \(2\)-Markov strategy in
+  \(\menGame{\oneptlind\kappa}\).
+
+  One source of motivation is to make progress on the following open question:
+
+  \begin{question}
+    Does there exist a topological space \(X\) for which
+    \(\pl F\win\menGame{X}\) but \(\pl F\notkmarkwin{2}\menGame{X}\)?
+    (That is, the second player can win the Menger game on \(X\)
+    with perfect information but not with \(2\)-Markov information.)
+  \end{question}
+
+  One might hope that \(\oneptlind{(\mf c^+)}\) might answer this question
+  in the affirmative as \(S(\mf c^+)\) fails, but we will show that assuming
+  \(V=L\), \(\pl F\kmarkwin{2}\menGame{\oneptlind\kappa}\) for all
+  cardinals \(\kappa\).
+
+  \section{One-to-one and finite-to-one almost compatible functions}
+
+  We may weaken Scheeper's \(S(\kappa)\) as follows:
 

### 2015-11-17 articles/almost-compatible-functions-and-topological-games/article.tex
partial revision of kurepa family to S' proof

@@
     The statement \(S(\kappa)\) (given as \(S(\kappa,\aleph_0,\omega)\)
-    in \cite{MR1129143}) claims that there exist injections
+    in \cite{MR1129143}) claims that there exist one-to-one functions
     \(f_A:A\to\omega\) for each \(A\in[\kappa]^{\leq\aleph_0}\) such that
@@
   \begin{definition}
-    \(S'(\theta)\) states that there exists a cofinal family
-    \(\mc S\subseteq[\theta]^{\omega}\) and a collection of pairwise
-    almost compatible
-    finite-to-one functions \(\{f_S\in\omega^S:S\in\mc S\}\)
+    The statement \(S'(\kappa)\) weakens \(S(\kappa)\) be only requiring
+    the witness functions \(f_A:A\to\omega\) to be finite-to-one.
   \end{definition}
 
+  The following observation will be convenient.
+
+  \begin{proposition}
+    \(S(\kappa)\) and \(S'(\kappa)\) need only be witnessed by
+    functions \(\{f_A:A\in\mc S\}\) for some family \(\mc S\)
+    cofinal in \([\kappa]^{\leq\aleph_0}\).
+  \end{proposition}
+
+  \begin{proof}
+    For each \(A\in[\kappa]^{\leq\aleph_0}\) choose \(A'\supseteq A\)
+    from \(\mc S\) and let \(g_A=f_{A'}\rest A\).
+  \end{proof}
+
+  In the next section we will show that \(S'(\kappa)\) is sufficient
+  for the applications to the Scheepers and Menger games.
+  In the meantime, we will demonstrate that \(S'(\kappa)\) is strictly
+  weaker than \(S(\kappa)\).
+
+  Recall the following.
+
   \begin{definition}
-    \(S(\theta)\) strengthens \(S'(\theta)\) by requiring the collection
-    to contain one-to-one functions.
-  \end{definition}
-
-  We wish to show that Scheeper's original \(S(\theta)\) is strictly stronger
-  than \(S'(\theta)\).
-
-  \begin{definition}
-    A topological space is said to be \(\omega\)-bounded if each countable
-    subset of the space has compact closure.
-  \end{definition}
-
-  % TODO: read through Alan's proof and fit to rest of document
-          \begin{theorem}
-           For each $n\in \omega$, there is a locally countable,
-            $\omega$-bounded topology on $\omega_n$. Note
-            that this means that the closure of any set has
-            the same cardinality and weight as the set.
-          \end{theorem}
-
-          To prove the theorem, we must actually prove a stronger lemma.
-
-          \begin{lemma}
-          Assume that $X$ has cardinality at most $\omega_n$ (for
-          any $n\in \omega$),
-          and is locally countable, locally compact, and the closure
-          of each set has the same cardinality as the set.
-          Then $X$ has an $\omega$-bounded extension with the
-          same properties.
-          \end{lemma}
-
-            \begin{proof}
-            We prove this by induction on $n$.
-            In fact, we make our inductive statement that  if $\tilde X$
-            is the extension of $X$, then  $\tilde X \setminus X$ also
-            has cardinality $\omega_n$.
-             If $n=0$,
-              then we can just take the free union of two copies of $X$
-              and then the one-point compactification.
-             So suppose $n>0$ and
-            that $X$ is such a topology on the ordinal $\omega_n$.
-            For each $\alpha<\omega_n$, the closure of the initial
-            segment $\alpha$ is bounded by some $\gamma_\alpha$.
-            Also, because $X$ is locally countable, $\gamma_\alpha$
-            can be chosen so that $\alpha$ is contained  in the interior
-            of $\gamma_\alpha$. There is a cub  $C\subset \omega_n$
-            with the property that for each $\delta\in C$ and $\alpha<\delta$,
-             $\gamma_\alpha$ is also less than $\delta$. This implies
-             that for each $\delta\in C$, the initial segment $\delta$ is
-             open, and if $\delta$ has uncountable cofinality, then
-              $\delta$ is clopen.
-
-              The proof will be easier to visualize if we now
-              identify the points of $X$ with the point set
-               $\omega_n\times \{0\}$ and we will add the points
-                $\omega_n\times \{1\}$ to create the extension.
-             By induction on $\lambda \in C$ we define a topology
-             on $\omega_n\times\{0\}\cup \lambda\times \{1\}$ so that
-             $\omega_n \times \{0\}$ is an open subset. We also ensure,
-             by induction, for each $\alpha<\lambda$,
-             the closure of $\alpha\times 2$ is an
-              $\omega$-bounded  subset of $\lambda\times 2$.
-
-          In the case that $n=1$, then  choose any sequence
-           $\lambda_n : n\in \omega$ increasing cofinal in $\lambda$.
-           If $\lambda $ is a limit in $C$, then we simply take the
-           topology we have constructed so far on $\lambda\times 2$
-           and there's nothing more needs to be done. Otherwise
-          we may assume that $\lambda_0$ is the predecessor
-          of $\lambda\in C$ and
-           we set $Y_\lambda $ to equal the countable set
-            $\overline{\lambda}\setminus \lambda$. For convenience,
-             and with no loss, we assume that $\lambda$ itself is a limit
-             of limits.
-           And we have a topology on
-           $$\lambda_0\times 2 \cup (\lambda \cup Y_\lambda)\times\{0\}~.$$
-            Recursively
-            choose clopen sets $U_n$ in this topology
-             so that $\lambda_0\times 2\subset U_0$,
-             $U_{n}\cup \lambda_{n+1}\times \{0\}$ is contained
-              $ U_{n+1}$ while $U_{n+1}$ is disjoint from $Y_\lambda$.
-              It is easy to see that we can have all the points
-              in $(\lambda\setminus \{\lambda_n : n\in\omega\})\times \{1\}$
-              be isolated, and arrange that $(\lambda_n,1) $ is the
-              point at infinity in the one-point compactification
-              $U_n\cup (\lambda_n\times \{1\})$.
-
-                Now we handle the case $n>1$ and we can shrink $C$
-                and now assume
-                that $C$ is the closure of $\{\lambda\in C : \mbox{cf}(\lambda)>\omega\}$.
-                We again proceed by induction on $\lambda\in C$.  If
-                $\lambda$ is a limit in $C$, then there is nothing to do: we
-                simply have defined an appropriate topology on
-                $\omega_n\times  \{0\}\cup \lambda\times \{1\}$ so that
-                for each $\mu\in C\cap \lambda$ with $\mbox{cf}(\mu)>\omega$,
-                 $\mu\times 2$ is a clopen $\omega$-bounded subspace.
-                In case $\lambda$ is not a limit of $C$, then $\lambda$
-                has uncountable cofinality and a predecessor $\mu\in C$.
-                We therefore have that $\lambda\times\{0\}$ is clopen
-                in $\omega_n\times \{0\}$.
-                 We apply the induction hypothesis
-                to the space $\lambda\times \{0\} \cup \mu\times 2$ to choose
-                the topology on $\lambda\times 2$.
-
-            \end{proof}
-
-  \begin{definition}
-    A Kurepa family \(\mc K\subseteq[\theta]^{\omega}\) on \(\theta\)
+    A Kurepa family \(\mc K\subseteq[\kappa]^{\aleph_0}\) on \(\kappa\)
     satisfies that
     \(\mc K\rest A=\{K\cap A:K\in\mc K\}\) is countable
-    for each \(A\in[\theta]^\omega\).
+    for each \(A\in[\kappa]^{\aleph_0}\).
   \end{definition}
 
-  \begin{corollary}
-    There exists a Kurepa family cofinal in \([\omega_k]^\omega\)
-    for each \(k<\omega\).
-  \end{corollary}
+  \begin{theorem}
+    \(S'(\kappa)\) holds whenever there exists a cofinal Kurepa family on \(\kappa\).
+  \end{theorem}
 
   \begin{proof}
-    This is actually a corollary of an observation of Todorcevic communicated
-    by Dow in [TODO cite Gen Prog in Top I]:
-    if every Kurepa family of size at most \(\theta\)
-    extends to a cofinal Kurepa family, then the same is true of \(\theta^+\).
-    So the result follows as
-    every Kurepa family \(\mc K\) of size \(\omega\) extends to
-    the cofinal Kurepa family \([\bigcup\mc K]^\omega\).
-
-    We may alternatively
-    obtain the result from the previous topological argument by using the family
-    \(\mc K\) of compact sets in the constructed topology on
-    \(\omega_k\) as our witness. Of course, every Lindel\"of set in
-    a locally countable space is countable. Thus \(\mc K\)
-    is cofinal in \([\omega_k]^\omega\)
-    since for every countable set \(A\), \(\cl A\) is compact and countable.
-    It is Kurepa since for every countable set \(A\), let (TODO)
-  \end{proof}
-
-  \begin{theorem}
-    \(S'(\theta)\) holds whenever there exists a cofinal Kurepa family on \(\theta\).
-  \end{theorem}
-
-  \begin{proof}
-    Let \(k<\omega\), and \(\mc K=\{K_\alpha:\alpha<\kappa\}\)
-    be a cofinal Kurepa family on \(\theta\).
-    We should define \(f_\alpha:K_\alpha\to\omega\) for each \(\alpha<\kappa\).
-
-    Suppose we've defined pairwise almost compatible
+    Let \(\mc K=\{K_\alpha:\alpha<\theta\}\)
+    be a cofinal Kurepa family on \(\kappa\).
+    We first define \(f_\alpha:K_\alpha\to\omega\) for each \(\alpha<\theta\).
+
+    Suppose we've already defined pairwise almost compatible finite-to-one functions
     \(\{f_\beta:\beta<\alpha\}\). To define
@@
     We should show that \(f_\alpha\) is finite-to-one. Let \(n<\omega\).
-    We need only worry about \(\delta_{m,j}\) for \(m\leq n\) since
-    \(f_\alpha(\delta_{m,j})\geq m\). Since each
+    Since \(f_\alpha(\delta_{m,j})\geq m\), we only consider the finite cases
+    where \(m\leq n\). Since each
     \(f_{\beta_m}\) is finite-to-one, \(f_{\beta_m}(\delta_{m,j})\leq n\)
-    for only finitely many \(j\). Thus \(f_\alpha\) maps to
-    \(n\) only finitely often.
-
+    for only finitely many \(j\). Thus
+    \(f_\alpha(\delta_{m,j})=\max(m,f_{\beta_m}(\delta_{m,j}))\) maps to
+    \(n\) for only finitely many \(j\).
+
+    %TODO proof
     We now want to demonstrate that \(f_\alpha\sim f_{\beta_n}\) for all
@@
     almost compatible \(f_{\beta_n}\sim f_{\beta_m}\) differ.
+  \end{proof}
+
+  \newpage
+
+  \section{TODO ALL THIS STUFF NEEDS EDITING STILL}
+
+  \begin{definition}
+    A topological space is said to be \(\omega\)-bounded if each countable
+    subset of the space has compact closure.
+  \end{definition}
+
+  % TODO: read through Alan's proof and fit to rest of document
+          \begin{theorem}
+           For each $n\in \omega$, there is a locally countable,
+            $\omega$-bounded topology on $\omega_n$. Note
+            that this means that the closure of any set has
+            the same cardinality and weight as the set.
+          \end{theorem}
+
+          To prove the theorem, we must actually prove a stronger lemma.
+
+          \begin{lemma}
+          Assume that $X$ has cardinality at most $\omega_n$ (for
+          any $n\in \omega$),
+          and is locally countable, locally compact, and the closure
+          of each set has the same cardinality as the set.
+          Then $X$ has an $\omega$-bounded extension with the
+          same properties.
+          \end{lemma}
+
+            \begin{proof}
+            We prove this by induction on $n$.
+            In fact, we make our inductive statement that  if $\tilde X$
+            is the extension of $X$, then  $\tilde X \setminus X$ also
+            has cardinality $\omega_n$.
+             If $n=0$,
+              then we can just take the free union of two copies of $X$
+              and then the one-point compactification.
+             So suppose $n>0$ and
+            that $X$ is such a topology on the ordinal $\omega_n$.
+            For each $\alpha<\omega_n$, the closure of the initial
+            segment $\alpha$ is bounded by some $\gamma_\alpha$.
+            Also, because $X$ is locally countable, $\gamma_\alpha$
+            can be chosen so that $\alpha$ is contained  in the interior
+            of $\gamma_\alpha$. There is a cub  $C\subset \omega_n$
+            with the property that for each $\delta\in C$ and $\alpha<\delta$,
+             $\gamma_\alpha$ is also less than $\delta$. This implies
+             that for each $\delta\in C$, the initial segment $\delta$ is
+             open, and if $\delta$ has uncountable cofinality, then
+              $\delta$ is clopen.
+
+              The proof will be easier to visualize if we now
+              identify the points of $X$ with the point set
+               $\omega_n\times \{0\}$ and we will add the points
+                $\omega_n\times \{1\}$ to create the extension.
+             By induction on $\lambda \in C$ we define a topology
+             on $\omega_n\times\{0\}\cup \lambda\times \{1\}$ so that
+             $\omega_n \times \{0\}$ is an open subset. We also ensure,
+             by induction, for each $\alpha<\lambda$,
+             the closure of $\alpha\times 2$ is an
+              $\omega$-bounded  subset of $\lambda\times 2$.
+
+          In the case that $n=1$, then  choose any sequence
+           $\lambda_n : n\in \omega$ increasing cofinal in $\lambda$.
+           If $\lambda $ is a limit in $C$, then we simply take the
+           topology we have constructed so far on $\lambda\times 2$
+           and there's nothing more needs to be done. Otherwise
+          we may assume that $\lambda_0$ is the predecessor
+          of $\lambda\in C$ and
+           we set $Y_\lambda $ to equal the countable set
+            $\overline{\lambda}\setminus \lambda$. For convenience,
+             and with no loss, we assume that $\lambda$ itself is a limit
+             of limits.
+           And we have a topology on
+           $$\lambda_0\times 2 \cup (\lambda \cup Y_\lambda)\times\{0\}~.$$
+            Recursively
+            choose clopen sets $U_n$ in this topology
+             so that $\lambda_0\times 2\subset U_0$,
+             $U_{n}\cup \lambda_{n+1}\times \{0\}$ is contained
+              $ U_{n+1}$ while $U_{n+1}$ is disjoint from $Y_\lambda$.
+              It is easy to see that we can have all the points
+              in $(\lambda\setminus \{\lambda_n : n\in\omega\})\times \{1\}$
+              be isolated, and arrange that $(\lambda_n,1) $ is the
+              point at infinity in the one-point compactification
+              $U_n\cup (\lambda_n\times \{1\})$.
+
+                Now we handle the case $n>1$ and we can shrink $C$
+                and now assume
+                that $C$ is the closure of $\{\lambda\in C : \mbox{cf}(\lambda)>\omega\}$.
+                We again proceed by induction on $\lambda\in C$.  If
+                $\lambda$ is a limit in $C$, then there is nothing to do: we
+                simply have defined an appropriate topology on
+                $\omega_n\times  \{0\}\cup \lambda\times \{1\}$ so that
+                for each $\mu\in C\cap \lambda$ with $\mbox{cf}(\mu)>\omega$,
+                 $\mu\times 2$ is a clopen $\omega$-bounded subspace.
+                In case $\lambda$ is not a limit of $C$, then $\lambda$
+                has uncountable cofinality and a predecessor $\mu\in C$.
+                We therefore have that $\lambda\times\{0\}$ is clopen
+                in $\omega_n\times \{0\}$.
+                 We apply the induction hypothesis
+                to the space $\lambda\times \{0\} \cup \mu\times 2$ to choose
+                the topology on $\lambda\times 2$.
+
+            \end{proof}
+
+  \begin{corollary}
+    There exists a Kurepa family cofinal in \([\omega_k]^\omega\)
+    for each \(k<\omega\).
+  \end{corollary}
+
+  \begin{proof}
+    This is actually a corollary of an observation of Todorcevic communicated
+    by Dow in [TODO cite Gen Prog in Top I]:
+    if every Kurepa family of size at most \(\theta\)
+    extends to a cofinal Kurepa family, then the same is true of \(\theta^+\).
+    So the result follows as
+    every Kurepa family \(\mc K\) of size \(\omega\) extends to
+    the cofinal Kurepa family \([\bigcup\mc K]^\omega\).
+
+    We may alternatively
+    obtain the result from the previous topological argument by using the family
+    \(\mc K\) of compact sets in the constructed topology on
+    \(\omega_k\) as our witness. Of course, every Lindel\"of set in
+    a locally countable space is countable. Thus \(\mc K\)
+    is cofinal in \([\omega_k]^\omega\)
+    since for every countable set \(A\), \(\cl A\) is compact and countable.
+    It is Kurepa since for every countable set \(A\), let (TODO)
   \end{proof}

### 2015-11-18 articles/almost-compatible-functions-and-topological-games/article.tex
get kurepa family => S'(kappa)
writing up alan's proof of omega_n topology

@@
 
-    %TODO proof
     We now want to demonstrate that \(f_\alpha\sim f_{\beta_n}\) for all
-    \(n<\omega\). We again need only concern ourselves with \(\delta_{m,j}\) for
-    \(m\leq n\) since otherwise \(\delta_{m,j}\not\in K_{\beta_n}\).
+    \(n<\omega\). Note \(\delta_{m,j}\in K_{\beta_n}\) implies
+    \(m\leq n\).
     For \(m=n\), we have
@@
     almost compatible \(f_{\beta_n}\sim f_{\beta_m}\) differ.
+
+    Finally for any \(\beta<\alpha\), we may conclude \(f_\alpha\sim f_\beta\)
+    since there is some \(\beta_n\) with
+    \(K_\alpha\cap K_\beta=K_\alpha\cap K_{\beta_n}\),
+    \(f_\alpha\sim f_{\beta_n}\), and \(f_{\beta_n}\sim f_\beta\).
   \end{proof}
 
-  \newpage
-
-  \section{TODO ALL THIS STUFF NEEDS EDITING STILL}
+  We now construct a topology on \(\omega_n\) for each \(n<\omega\) which
+  will witness a Kurepa family on \(\aleph_n\).
 
@@
 
-  % TODO: read through Alan's proof and fit to rest of document
+\begin{lemma}
+    Let \(X\) be a Hausdorff space of cardinality less than
+    \(\aleph_\omega\) which is locally countable, locally compact, and the
+    closure of each set has the same cardinality as the set.
+    Then \(X\) has an \(\omega\)-bounded extension \(\tilde X\)
+    with the same properties,
+    such that \(\tilde X\setminus X\) has the same cardinality
+    as \(X\).
+  \end{lemma}
+
+  \begin{proof}
+    We prove this by induction on \(n\).
+    If \(n=0\), then we can just use the one-point compactification of two
+    copies of \(X\).
+    So suppose \(n>0\) and
+    that \(X=\{\alpha:\alpha<\omega_n\}\) has such a topology.
+    For each \(\alpha<\omega_n\), \(\gamma_\alpha\) may be chosen such that
+    both the closure of \(\alpha\) in \(X\) and a countable neighborhood of
+    \(\alpha\) are subsets of \(\gamma_\alpha\). Note that
+    the set
+    \(C'=\{\lambda<\omega_n:\alpha<\lambda\Rightarrow\gamma_\alpha<\lambda\}\)
+    is a cub subset of \(\omega_n\).
+    It will be convenient later to use the cub \(C=C'\cap L\), where
+    \(L\) contains the limits of limit ordinals in \(\omega_n\).
+    Now for each \(\lambda\in C\), the initial segment \(\lambda\) is
+    open as \(\alpha<\lambda\) belongs to the neighborhood
+    \(\gamma_\alpha\subsetneq\lambda\). Also, if \(\lambda\) has uncountable
+    cofinality, then for \(\beta\geq\lambda\) and any countable neighborhood
+    \(U\) of \(\beta\), \(U\cap\lambda=U\cap\alpha\)
+    for some \(\alpha<\lambda\); thus \(U\setminus\cl\alpha\)
+    is a neighborhood of \(\beta\) missing \(\lambda\), showing that \(\lambda\)
+    is clopen.
+
+    Let \(\tilde X=\omega_n\times 2\).
+    By induction on \(\lambda \in C\) we will define a topology
+    for \(\omega_n\times\{0\}\cup \lambda\times \{1\}\) such that
+    \begin{itemize}
+      \item \(\omega_n \times \{0\}\) is an open copy of \(X\),
+      \item the space is locally compact, and
+      \item for each \(\alpha<\lambda\), the closure of \(\alpha\times 2\) is
+        an \(\omega\)-bounded  subset of \(\lambda\times 2\).
+    \end{itemize}
+
+    In the case that \(n=1\), if \(\lambda\) is a limit in \(C\),
+    then we simply give
+    \(
+      \omega_n\times\{0\}\cup\lambda\times\{1\}
+    \) the topology induced by the union of the previously defined
+    \(
+      \omega_n\times\{0\}\cup\lambda'\times\{1\}
+    \).
+    Otherwise we choose an increasing sequence of limit
+    ordinals \(\{\alpha_k : k\in \omega\}\) with limit \(\lambda\)
+    such that \(\alpha_0\) is the predecessor of
+    \(\lambda\) in \(C\) (or \(0\) if \(\lambda\) is the least element of
+    \(C\)).
+
+    %TODO finish edits
+    The subspace \(\cl\lambda\times\{0\}\cup\alpha_0\times\{1\}\) of \(X\)
+    is countable and locally compact; therefore it is
+    metrizable and zero-dimensional.
+    So we may choose sets \(U_k\) for \(k<\omega\) which are
+    clopen in this topology and satisfy
+    \(
+      \cl{\alpha_k}\times\{0\}\cup\alpha_0\times\{1\}
+        \subseteq
+      U_n
+        \subseteq
+      \lambda\times\{0\}\cup\alpha_0\times\{1\}
+    \).
+
+    We need only describe a base for the points in
+    \((\lambda\setminus\alpha_0)\times\{1\}\); we do so by letting
+    \(\<\alpha,1\>\) be isolated when \(\alpha\not\in\{\alpha_k:k<\omega\}\),
+    and letting \(\<\alpha_k,1\>\) be a compactifying point for
+    \(U_n\cup(\alpha_k\times\{1\})\).
+
+    This results in a locally compact space: for \(\alpha\geq\lambda\),
+    \(\<\alpha,0\>\) has its usual compact neighborhoods within the copy
+    \(\omega_n\times\{0\}\) of \(X\).
+
+    Now we handle the case \(n>1\) and we can shrink \(C\)
+    and now assume
+    that \(C\) is the closure of \(\{\lambda\in C : \mbox{cf}(\lambda)>\omega\}\).
+    We again proceed by induction on \(\lambda\in C\).  If
+    \(\lambda\) is a limit in \(C\), then there is nothing to do: we
+    simply have defined an appropriate topology on
+    \(\omega_n\times  \{0\}\cup \lambda\times \{1\}\) so that
+    for each \(\mu\in C\cap \lambda\) with \(\mbox{cf}(\mu)>\omega\),
+     \(\mu\times 2\) is a clopen \(\omega\)-bounded subspace.
+    In case \(\lambda\) is not a limit of \(C\), then \(\lambda\)
+    has uncountable cofinality and a predecessor \(\mu\in C\).
+    We therefore have that \(\lambda\times\{0\}\) is clopen
+    in \(\omega_n\times \{0\}\).
+     We apply the induction hypothesis
+    to the space \(\lambda\times \{0\} \cup \mu\times 2\) to choose
+    the topology on \(\lambda\times 2\).
+  \end{proof}
+
   \begin{theorem}
@@
 
-          To prove the theorem, we must actually prove a stronger lemma.
-
-          \begin{lemma}
-          Assume that $X$ has cardinality at most $\omega_n$ (for
-          any $n\in \omega$),
-          and is locally countable, locally compact, and the closure
-          of each set has the same cardinality as the set.
-          Then $X$ has an $\omega$-bounded extension with the
-          same properties.
-          \end{lemma}
-
   \begin{proof}
-            We prove this by induction on $n$.
-            In fact, we make our inductive statement that  if $\tilde X$
-            is the extension of $X$, then  $\tilde X \setminus X$ also
-            has cardinality $\omega_n$.
-             If $n=0$,
-              then we can just take the free union of two copies of $X$
-              and then the one-point compactification.
-             So suppose $n>0$ and
-            that $X$ is such a topology on the ordinal $\omega_n$.
-            For each $\alpha<\omega_n$, the closure of the initial
-            segment $\alpha$ is bounded by some $\gamma_\alpha$.
-            Also, because $X$ is locally countable, $\gamma_\alpha$
-            can be chosen so that $\alpha$ is contained  in the interior
-            of $\gamma_\alpha$. There is a cub  $C\subset \omega_n$
-            with the property that for each $\delta\in C$ and $\alpha<\delta$,
-             $\gamma_\alpha$ is also less than $\delta$. This implies
-             that for each $\delta\in C$, the initial segment $\delta$ is
-             open, and if $\delta$ has uncountable cofinality, then
-              $\delta$ is clopen.
-
-              The proof will be easier to visualize if we now
-              identify the points of $X$ with the point set
-               $\omega_n\times \{0\}$ and we will add the points
-                $\omega_n\times \{1\}$ to create the extension.
-             By induction on $\lambda \in C$ we define a topology
-             on $\omega_n\times\{0\}\cup \lambda\times \{1\}$ so that
-             $\omega_n \times \{0\}$ is an open subset. We also ensure,
-             by induction, for each $\alpha<\lambda$,
-             the closure of $\alpha\times 2$ is an
-              $\omega$-bounded  subset of $\lambda\times 2$.
-
-          In the case that $n=1$, then  choose any sequence
-           $\lambda_n : n\in \omega$ increasing cofinal in $\lambda$.
-           If $\lambda $ is a limit in $C$, then we simply take the
-           topology we have constructed so far on $\lambda\times 2$
-           and there's nothing more needs to be done. Otherwise
-          we may assume that $\lambda_0$ is the predecessor
-          of $\lambda\in C$ and
-           we set $Y_\lambda $ to equal the countable set
-            $\overline{\lambda}\setminus \lambda$. For convenience,
-             and with no loss, we assume that $\lambda$ itself is a limit
-             of limits.
-           And we have a topology on
-           $$\lambda_0\times 2 \cup (\lambda \cup Y_\lambda)\times\{0\}~.$$
-            Recursively
-            choose clopen sets $U_n$ in this topology
-             so that $\lambda_0\times 2\subset U_0$,
-             $U_{n}\cup \lambda_{n+1}\times \{0\}$ is contained
-              $ U_{n+1}$ while $U_{n+1}$ is disjoint from $Y_\lambda$.
-              It is easy to see that we can have all the points
-              in $(\lambda\setminus \{\lambda_n : n\in\omega\})\times \{1\}$
-              be isolated, and arrange that $(\lambda_n,1) $ is the
-              point at infinity in the one-point compactification
-              $U_n\cup (\lambda_n\times \{1\})$.
-
-                Now we handle the case $n>1$ and we can shrink $C$
-                and now assume
-                that $C$ is the closure of $\{\lambda\in C : \mbox{cf}(\lambda)>\omega\}$.
-                We again proceed by induction on $\lambda\in C$.  If
-                $\lambda$ is a limit in $C$, then there is nothing to do: we
-                simply have defined an appropriate topology on
-                $\omega_n\times  \{0\}\cup \lambda\times \{1\}$ so that
-                for each $\mu\in C\cap \lambda$ with $\mbox{cf}(\mu)>\omega$,
-                 $\mu\times 2$ is a clopen $\omega$-bounded subspace.
-                In case $\lambda$ is not a limit of $C$, then $\lambda$
-                has uncountable cofinality and a predecessor $\mu\in C$.
-                We therefore have that $\lambda\times\{0\}$ is clopen
-                in $\omega_n\times \{0\}$.
-                 We apply the induction hypothesis
-                to the space $\lambda\times \{0\} \cup \mu\times 2$ to choose
-                the topology on $\lambda\times 2$.
-
+    Take a topological sum of \(\aleph_{n+1}\) copies of \(\omega_n\)
+    with an appropriate topology (a convergent sequence for \(\omega\), the
+    result of this theorem for larger cardinals),
+    and apply the previous lemma.
+
+    TODO: write an argument for the note.
   \end{proof}
+
+  \newpage
+
+  \section{TODO ALL THIS STUFF NEEDS EDITING STILL}
 

### 2015-11-20 articles/almost-compatible-functions-and-topological-games/article.tex
topology proof

@@
 
+  \begin{proposition}
+    Let \(X\) be a \(T_2\) locally countable \(\omega\)-bounded space.
+    Then for each \(A\subseteq X\), \(\cl A\) has the same cardinality and
+    weight as \(A\).
+  \end{proposition}
+
+  %TODO?
+
   \begin{lemma}
-    Let \(X\) be a Hausdorff space of cardinality less than
-    \(\aleph_\omega\) which is locally countable, locally compact, and the
-    closure of each set has the same cardinality as the set.
+    Let \(X\) be a \(T_2\) space of cardinality less than
+    \(\aleph_\omega\) which is locally countable, locally compact,
+    and the closure of each set has the same cardinality as the set.
     Then \(X\) has an \(\omega\)-bounded extension \(\tilde X\)
@@
     If \(n=0\), then we can just use the one-point compactification of two
-    copies of \(X\).
-    So suppose \(n>0\) and
-    that \(X=\{\alpha:\alpha<\omega_n\}\) has such a topology.
+    copies of \(X\). So suppose \(n>0\) and
+    that \(X=\omega_n\) has such a topology. Note that
+    \(X\) has a base of compact open neighborhoods
+    with countable cardinality. To see this,
+    for each point \(x\) let \(K\) be a countable and compact neighborhood
+    of \(x\), and it follows that it is contained in a countable, open,
+    and locally compact neighborhood \(W\) of \(x\), which in turn
+    is zero-dimensional and metrizable. So choose \(V\) clopen
+    in \(W\) such that \(x\in V\subseteq K\); \(V\) is a compact open
+    neighborhood of \(x\) in \(X\).
+
     For each \(\alpha<\omega_n\), \(\gamma_\alpha\) may be chosen such that
-    both the closure of \(\alpha\) in \(X\) and a countable neighborhood of
-    \(\alpha\) are subsets of \(\gamma_\alpha\). Note that
-    the set
-    \(C'=\{\lambda<\omega_n:\alpha<\lambda\Rightarrow\gamma_\alpha<\lambda\}\)
-    is a cub subset of \(\omega_n\).
-    It will be convenient later to use the cub \(C=C'\cap L\), where
-    \(L\) contains the limits of limit ordinals in \(\omega_n\).
+    both the closure of the set \(\alpha\) in \(X\) and a countable
+    neighborhood of the point \(\alpha\) are subsets of \(\gamma_\alpha\).
+    Note that the set
+    \(\{\lambda<\omega_n:\alpha<\lambda\Rightarrow\gamma_\alpha<\lambda\}\)
+    is a cub subset of \(\omega_n\) with a cub subset
+    \(C\) containing only limits of limit ordinals.
     Now for each \(\lambda\in C\), the initial segment \(\lambda\) is
@@
     \(U\) of \(\beta\), \(U\cap\lambda=U\cap\alpha\)
-    for some \(\alpha<\lambda\); thus \(U\setminus\cl\alpha\)
-    is a neighborhood of \(\beta\) missing \(\lambda\), showing that \(\lambda\)
+    for some \(\alpha<\lambda\); thus \(U\setminus\cl\alpha=U\setminus\lambda\)
+    is a neighborhood of \(\beta\), showing that \(\lambda\)
     is clopen.
@@
     By induction on \(\lambda \in C\) we will define a topology
-    for \(\omega_n\times\{0\}\cup \lambda\times \{1\}\) such that
+    for \(\tilde X_\lambda=\omega_n\times\{0\}\cup\lambda\times\{1\}\)
+    such that
     \begin{itemize}
       \item \(\omega_n \times \{0\}\) is an open copy of \(X\),
-      \item the space is locally compact, and
+      \item \(\lambda\times 2\) is open, and also closed when \(\cf\lambda>\omega\),
+      \item the space has a base of compact open neighborhoods with
+        countable cardinality, and
       \item for each \(\alpha<\lambda\), the closure of \(\alpha\times 2\) is
@@
     \end{itemize}
-
-    In the case that \(n=1\), if \(\lambda\) is a limit in \(C\),
-    then we simply give
+    and note that \(\omega_n\times\{0\}\cup 0\times\{1\}\) satisfies these
+    requirements.
+
+    We first consider the case \(n=1\).
+    If \(\lambda\) is a limit in \(C\), then
     \(
       \omega_n\times\{0\}\cup\lambda\times\{1\}
-    \) the topology induced by the union of the previously defined
-    \(
-      \omega_n\times\{0\}\cup\lambda'\times\{1\}
-    \).
+        =
+      \bigcup_{\mu\in C\cap\lambda}\omega_n\times\{0\}\cup\mu\times\{1\}
+    \)
+    will have the topology induced by that union which
+    satisfies the induction requirements.
     Otherwise we choose an increasing sequence of limit
     ordinals \(\{\alpha_k : k\in \omega\}\) with limit \(\lambda\)
-    such that \(\alpha_0\) is the predecessor of
-    \(\lambda\) in \(C\) (or \(0\) if \(\lambda\) is the least element of
-    \(C\)).
-
-    %TODO finish edits
+    such that \(\alpha_0\) is the predecessor of \(\lambda\) in \(C\),
+    or \(\alpha_0=0\) if \(\lambda\) is the least element of \(C\).
+
     The subspace \(\cl\lambda\times\{0\}\cup\alpha_0\times\{1\}\) of \(X\)
@@
     metrizable and zero-dimensional.
-    So we may choose sets \(U_k\) for \(k<\omega\) which are
+    So we may choose increasing sets \(U_k\) for \(k<\omega\) which are
     clopen in this topology and satisfy
-    \(
+    \[
+      \cl{\alpha_k\times\{0\}\cup\alpha_0\times\{1\}}
+        =
       \cl{\alpha_k}\times\{0\}\cup\alpha_0\times\{1\}
         \subseteq
-      U_n
+      U_k
         \subseteq
-      \lambda\times\{0\}\cup\alpha_0\times\{1\}
-    \).
-
-    We need only describe a base for the points in
-    \((\lambda\setminus\alpha_0)\times\{1\}\); we do so by letting
+      \lambda\times\{0\}\cup\alpha_0\times 2
+    \]
+
+    We need only describe a base for the points
+    \(\<\alpha,1\>\in(\lambda\setminus\alpha_0)\times\{1\}\);
+    we do so by letting
     \(\<\alpha,1\>\) be isolated when \(\alpha\not\in\{\alpha_k:k<\omega\}\),
     and letting \(\<\alpha_k,1\>\) be a compactifying point for
-    \(U_n\cup(\alpha_k\times\{1\})\).
-
-    This results in a locally compact space: for \(\alpha\geq\lambda\),
-    \(\<\alpha,0\>\) has its usual compact neighborhoods within the copy
-    \(\omega_n\times\{0\}\) of \(X\).
-
-    Now we handle the case \(n>1\) and we can shrink \(C\)
-    and now assume
-    that \(C\) is the closure of \(\{\lambda\in C : \mbox{cf}(\lambda)>\omega\}\).
-    We again proceed by induction on \(\lambda\in C\).  If
-    \(\lambda\) is a limit in \(C\), then there is nothing to do: we
-    simply have defined an appropriate topology on
-    \(\omega_n\times  \{0\}\cup \lambda\times \{1\}\) so that
-    for each \(\mu\in C\cap \lambda\) with \(\mbox{cf}(\mu)>\omega\),
-     \(\mu\times 2\) is a clopen \(\omega\)-bounded subspace.
+    \(U_k\cup(\alpha_k\times\{1\})\).
+
+    The first two requirements of our inductive hypothesis are obviously
+    satsified. Note \(U_k\cup((\alpha_k+1)\times\{1\})\) is
+    a compact open neighborhood of countable cardinality
+    for points in \(\lambda\times 2\), and for points in
+    \((\omega_n\setminus\cl\lambda)\times\{0\}\) we may use a compact
+    open neighborhood of countable cardinality from \(X\setminus\lambda\).
+    Finally let \(\<\alpha,0\>\in(\cl\lambda\setminus\lambda)\times\{0\}\)
+    and let \(K\subseteq\cl\lambda\times\{0\}\cup\alpha_0\times\{1\}\) be a
+    compact open neighborhood in that subspace missing \(\alpha_0\times 2\).
+    Then for each \(k<\omega\), \(\<\alpha_k,1\>\) has a neighborhood missing
+    the compact set \(K\cap U_k\), so \(K\) gains no new limit points in
+    \(\cl\lambda\times\{0\}\cup\lambda\times\{1\}\) and thus remains compact.
+    So the third requirement is also satisfied.
+    For the final requirement, note that for \(\alpha<\lambda\), we may
+    choose \(\alpha<\alpha_k<\lambda\) and note that
+    \(\alpha\times 2\) is contained in the compact
+    set \(U_k\cup((\alpha_k+1)\times\{1\})\).
+
+    For the case \(n>1\), we may assume that the successors in \(C\)
+    have uncountable cofinality.
+    We again proceed by induction on \(\lambda\in C\).  Again when
+    \(\lambda\) is a limit in \(C\), the union of the previously defined
+    \(\omega_n\times\{0\}\cup\mu\times\{1\}\) satisfies the given
+    requirements; in particular if \(\alpha<\lambda\), then
+    \(\alpha<\mu<\lambda\) for some successor \(\mu\in C\) with uncountable
+    cofinality. As such, the closure of \(\alpha\times2\) is
+    an \(\omega\)-bounded subset of the clopen \(\mu\times 2\) and
+    therefore also of \(\lambda\times 2\).
     In case \(\lambda\) is not a limit of \(C\), then \(\lambda\)
@@
     We therefore have that \(\lambda\times\{0\}\) is clopen
-    in \(\omega_n\times \{0\}\).
-     We apply the induction hypothesis
-    to the space \(\lambda\times \{0\} \cup \mu\times 2\) to choose
-    the topology on \(\lambda\times 2\).
+    in \(\omega_n\times \{0\}\). Since the cardinality of
+    \(\lambda\times \{0\} \cup \mu\times 2\) is less than \(\aleph_n\),
+    we may simply apply the induction hypothesis
+    to choose an appropriate topology for \(\lambda\times 2\).
+
+    As a result, \(\tilde X=\bigcup_{\lambda\in C}\tilde X_\lambda\)
+    is easily seen to be locally compact and locally countable. It is also
+    \(\omega\)-bounded as any countable set is contained in some
+    \(\alpha\times 2\) for \(\alpha<\lambda\in C\). Finally by the previous
+    proposition, the closure operation cannot increase cardinalities.
   \end{proof}
@@
   \begin{theorem}
-    For each $n\in \omega$, there is a locally countable,
-    $\omega$-bounded topology on $\omega_n$. Note
-    that this means that the closure of any set has
-    the same cardinality and weight as the set.
+    For each $n\in \omega$, there is a \(T_2\) locally countable,
+    $\omega$-bounded topology on $\omega_n$.
   \end{theorem}
@@
   \begin{proof}
-    Take a topological sum of \(\aleph_{n+1}\) copies of \(\omega_n\)
-    with an appropriate topology (a convergent sequence for \(\omega\), the
-    result of this theorem for larger cardinals),
-    and apply the previous lemma.
-
-    TODO: write an argument for the note.
+    Apply the previous lemma to \(\omega_n\) with the discrete topology.
   \end{proof}

### 2015-11-24 articles/almost-compatible-functions-and-topological-games/article.tex
fleshed out topology construction proof

@@
 
+  \begin{proposition}
+    Let \(X\) be a \(T_2\) space with a base of countable and compact
+    neighborhoods.
+    Then \(X\) is locally metrizable, \(X\)
+    has a base of compact open countable sets,
+    and its closure operation preserves cardinality and weight.
+  \end{proposition}
+
+  \begin{proof}
+    For each point \(x\) let \(K\) be a countable and compact neighborhood
+    of \(x\), and it follows that it is contained in a countable, open,
+    and locally compact neighborhood \(W\) of \(x\), which in turn
+    is zero-dimensional and metrizable. So choose \(V\) clopen
+    in \(W\) such that \(x\in V\subseteq K\); \(V\) is a compact open
+    neighborhood of \(x\) in \(X\).
+
+    Since the space is locally metrizable and thus first-countable,
+    the weight and cardinality of any
+    subspace coincide. Then for infinite \(A\subseteq X\), cover \(\cl A\) with
+    open sets of countable cardinality, and say
+    \(x\sim y\) if there's a finite linked chain joining them; since
+    \(x\sim a\) for some \(a\in A\), \(\cl A\) is covered by
+    \(|A|\)-many sets each of size \(\aleph_0\). Thus
+    \(|A|\leq|\cl A|\leq|A|\otimes\aleph_0=|A|\).
+  \end{proof}
+
   \begin{definition}
@@
 
-  \begin{proposition}
-    Let \(X\) be a \(T_2\) locally countable \(\omega\)-bounded space.
-    Then for each \(A\subseteq X\), \(\cl A\) has the same cardinality and
-    weight as \(A\).
-  \end{proposition}
-
-  %TODO?
-
   \begin{lemma}
     Let \(X\) be a \(T_2\) space of cardinality less than
-    \(\aleph_\omega\) which is locally countable, locally compact,
-    and the closure of each set has the same cardinality as the set.
+    \(\aleph_\omega\) with a base of countable and compact neighborhoods.
     Then \(X\) has an \(\omega\)-bounded extension \(\tilde X\)
@@
     copies of \(X\). So suppose \(n>0\) and
-    that \(X=\omega_n\) has such a topology. Note that
-    \(X\) has a base of compact open neighborhoods
-    with countable cardinality. To see this,
-    for each point \(x\) let \(K\) be a countable and compact neighborhood
-    of \(x\), and it follows that it is contained in a countable, open,
-    and locally compact neighborhood \(W\) of \(x\), which in turn
-    is zero-dimensional and metrizable. So choose \(V\) clopen
-    in \(W\) such that \(x\in V\subseteq K\); \(V\) is a compact open
-    neighborhood of \(x\) in \(X\).
+    that \(X=\omega_n\) has an appropriate topology.
 
@@
     \(\{\lambda<\omega_n:\alpha<\lambda\Rightarrow\gamma_\alpha<\lambda\}\)
-    is a cub subset of \(\omega_n\) with a cub subset
-    \(C\) containing only limits of limit ordinals.
+    is a cub subset of \(\omega_n\) containing a cub subset \(C\)
+    of limit ordinals.
     Now for each \(\lambda\in C\), the initial segment \(\lambda\) is
@@
       \item \(\omega_n \times \{0\}\) is an open copy of \(X\),
-      \item \(\lambda\times 2\) is open, and also closed when \(\cf\lambda>\omega\),
-      \item the space has a base of compact open neighborhoods with
-        countable cardinality, and
+      \item \(\lambda\times 2\) is open, and when \(\cf\lambda>\omega\) also closed,
+      \item the space has a base of countable and compact neighborhoods, and
       \item for each \(\alpha<\lambda\), the closure of \(\alpha\times 2\) is
@@
     satisfies the induction requirements.
-    Otherwise we choose an increasing sequence of limit
+    Otherwise we choose an increasing sequence of
     ordinals \(\{\alpha_k : k\in \omega\}\) with limit \(\lambda\)
@@
     We need only describe a base for the points
-    \(\<\alpha,1\>\in(\lambda\setminus\alpha_0)\times\{1\}\);
-    we do so by letting
+    \(\<\alpha,1\>\in(\lambda\setminus\alpha_0)\times\{1\}\).
+    We do so by letting
     \(\<\alpha,1\>\) be isolated when \(\alpha\not\in\{\alpha_k:k<\omega\}\),
-    and letting \(\<\alpha_k,1\>\) be a compactifying point for
+    and giving \(\<\alpha_k,1\>\) the neighborhoods
+    \(U_k\cup((\alpha_k+1)\times\{1\})\setminus K\)
+    for each compact \(K\) in \(U_k\cup(\alpha_k\times\{1\})\); that is,
+    let \(\<\alpha_k,1\>\) be the one point compactifying
     \(U_k\cup(\alpha_k\times\{1\})\).
@@
     satsified. Note \(U_k\cup((\alpha_k+1)\times\{1\})\) is
-    a compact open neighborhood of countable cardinality
+    a compact neighborhood of countable cardinality
     for points in \(\lambda\times 2\), and for points in
     \((\omega_n\setminus\cl\lambda)\times\{0\}\) we may use a compact
-    open neighborhood of countable cardinality from \(X\setminus\lambda\).
+    neighborhood of countable cardinality from \(X\setminus\lambda\).
     Finally let \(\<\alpha,0\>\in(\cl\lambda\setminus\lambda)\times\{0\}\)
     and let \(K\subseteq\cl\lambda\times\{0\}\cup\alpha_0\times\{1\}\) be a
-    compact open neighborhood in that subspace missing \(\alpha_0\times 2\).
-    Then for each \(k<\omega\), \(\<\alpha_k,1\>\) has a neighborhood missing
-    the compact set \(K\cap U_k\), so \(K\) gains no new limit points in
+    compact neighborhood in that subspace missing \(\alpha_0\times 2\).
+    Then for each \(k<\omega\), \(\<\alpha_k,1\>\) has the neighborhood
+    \(U_k\cup((\alpha_k+1)\times\{1\})\setminus K\),
+    so \(K\) gains no new limit points in
     \(\cl\lambda\times\{0\}\cup\lambda\times\{1\}\) and thus remains compact.
@@
     As a result, \(\tilde X=\bigcup_{\lambda\in C}\tilde X_\lambda\)
-    is easily seen to be locally compact and locally countable. It is also
+    is
     \(\omega\)-bounded as any countable set is contained in some
-    \(\alpha\times 2\) for \(\alpha<\lambda\in C\). Finally by the previous
-    proposition, the closure operation cannot increase cardinalities.
+    \(\alpha\times 2\) for \(\alpha<\lambda\in C\).
   \end{proof}
@@
   \begin{theorem}
-    For each $n\in \omega$, there is a \(T_2\) locally countable,
+    For each $n\in \omega$, there is a \(T_2\), locally countable,
     $\omega$-bounded topology on $\omega_n$.

### 2015-11-24 articles/almost-compatible-functions-and-topological-games/article.tex
S'(omega_2) but not S(omega_2) under CH

@@
 
-  \newpage
-
-  \section{TODO ALL THIS STUFF NEEDS EDITING STILL}
-
   \begin{corollary}
@@
   \begin{proof}
-    This is actually a corollary of an observation of Todorcevic communicated
-    by Dow in [TODO cite Gen Prog in Top I]:
+    We use the family \(\mc K\) which is a base of \(\aleph_0\)-many compact
+    open sets for each point in the constructed topology on
+    \(\omega_n\) as our witness. Of course, every Lindel\"of set in
+    a locally countable space is countable, and the closure of every
+    countable set is a compact countable set. Thus \(\mc K\)
+    is cofinal in \([\omega_n]^\omega\).
+    It is Kurepa since for every countable set \(A\), there are only countably
+    many compact open sets in \(\mc K\)
+    joined to \(A\) by a finite linked chain.
+  \end{proof}
+
+  This is alternatively a corollary of an observation of Todorcevic
+  communicated by Dow in \cite{MR1229125}:
   if every Kurepa family of size at most \(\theta\)
@@
 
-    We may alternatively
-    obtain the result from the previous topological argument by using the family
-    \(\mc K\) of compact sets in the constructed topology on
-    \(\omega_k\) as our witness. Of course, every Lindel\"of set in
-    a locally countable space is countable. Thus \(\mc K\)
-    is cofinal in \([\omega_k]^\omega\)
-    since for every countable set \(A\), \(\cl A\) is compact and countable.
-    It is Kurepa since for every countable set \(A\), let (TODO)
-  \end{proof}
+  So we have our desired result.
 
   \begin{corollary}
-    \(S'(\omega_k)\) holds for all \(k<\omega\).
+    \(S'(\omega_n)\) holds for all \(n<\omega\). Under \(CH\), we have
+    both \(S'(\omega_2)\) and \(\neg S(\omega_2)\).
   \end{corollary}
+
+  \newpage
+
+  \section{TODO ALL THIS STUFF NEEDS EDITING STILL}
 

### 2015-11-25 articles/almost-compatible-functions-and-topological-games/article.tex
fix topology consturction

@@
     Let \(X\) be a \(T_2\) space with a base of countable and compact
-    neighborhoods.
-    Then \(X\) is locally metrizable, \(X\)
-    has a base of compact open countable sets,
-    and its closure operation preserves cardinality and weight.
+    neighborhoods. Then \(X\) is locally metrizable with
+    a base of compact open countable sets.
   \end{proposition}
@@
     neighborhood of \(x\) in \(X\).
-
-    Since the space is locally metrizable and thus first-countable,
-    the weight and cardinality of any
-    subspace coincide. Then for infinite \(A\subseteq X\), cover \(\cl A\) with
-    open sets of countable cardinality, and say
-    \(x\sim y\) if there's a finite linked chain joining them; since
-    \(x\sim a\) for some \(a\in A\), \(\cl A\) is covered by
-    \(|A|\)-many sets each of size \(\aleph_0\). Thus
-    \(|A|\leq|\cl A|\leq|A|\otimes\aleph_0=|A|\).
   \end{proof}
@@
 
+  \begin{proposition}
+    Let \(X\) be a \(T_2\) space with cardinality less than \(\aleph_\omega\)
+    which is locally countable and
+    \(\omega\)-bounded. Then the closure operation preserves cardinality and
+    weight.
+  \end{proposition}
+
+  \begin{proof}
+    Note that the closure of any countable neighborhood is compact, and
+    any Lindel\"of set is countable. This space is locally metrizable
+    and thus first-countable, so cardinality and weight coincide for any
+    subspace. The result is obvious if \(A\) is countable; otherwise
+    let \(A=\{a_\alpha:\alpha<\omega_{n+1}\}\) and since basic neighborhoods
+    are countable note any limit point is
+    a limit point of \(A_\beta=\{a_\alpha:\alpha<\beta\}\)
+    for some \(\beta<\omega_{n+1}\).
+    Thus \(\cl A=\bigcup_{\beta<\omega_{n+1}}\cl{A_\beta}\) and
+    by induction \(|\cl A|=|A|\).
+  \end{proof}
+
   \begin{lemma}
-    Let \(X\) be a \(T_2\) space of cardinality less than
-    \(\aleph_\omega\) with a base of countable and compact neighborhoods.
+    Let \(X\) be a \(T_2\) space with cardinality less than \(\aleph_\omega\)
+    which is locally countable and locally compact, and such that
+    its closure operation preserves cardinalities.
     Then \(X\) has an \(\omega\)-bounded extension \(\tilde X\)
-    with the same properties,
-    such that \(\tilde X\setminus X\) has the same cardinality
-    as \(X\).
+    with the same properties where \(\tilde X\setminus X\) has the same
+    cardinality as \(X\).
   \end{lemma}
@@
     copies of \(X\). So suppose \(n>0\) and
-    that \(X=\omega_n\) has an appropriate topology.
+    that \(X=\omega_n\) has an appropriate topology. Note that \(X\) has
+    a base of countable and compact neighborhoods since the closure operation
+    preserves cardinalities.
 
@@
     of limit ordinals.
-    Now for each \(\lambda\in C\), the initial segment \(\lambda\) is
+    Now for each \(\lambda\in C\), the set \(\lambda\) is
     open as \(\alpha<\lambda\) belongs to the neighborhood
@@
     Let \(\tilde X=\omega_n\times 2\).
-    By induction on \(\lambda \in C\) we will define a topology
+    By induction on \(\lambda \in C\) we will define compatible topologies
     for \(\tilde X_\lambda=\omega_n\times\{0\}\cup\lambda\times\{1\}\)
@@
       \item the space has a base of countable and compact neighborhoods, and
-      \item for each \(\alpha<\lambda\), the closure of \(\alpha\times 2\) is
+      \item when \(\lambda\) is a successor,
+        for each \(\alpha<\lambda\) the closure of \(\alpha\times 2\) is
         an \(\omega\)-bounded  subset of \(\lambda\times 2\).
     \end{itemize}
-    and note that \(\omega_n\times\{0\}\cup 0\times\{1\}\) satisfies these
-    requirements.
 
@@
     \(
-      \omega_n\times\{0\}\cup\lambda\times\{1\}
+      \tilde X_\lambda
         =
-      \bigcup_{\mu\in C\cap\lambda}\omega_n\times\{0\}\cup\mu\times\{1\}
+      \bigcup_{\mu\in C\cap\lambda}\tilde X_\mu
     \)
-    will have the topology induced by that union which
     satisfies the induction requirements.
@@
 
-    The subspace \(\cl\lambda\times\{0\}\cup\alpha_0\times\{1\}\) of \(X\)
+    The subspace \(\cl\lambda\times\{0\}\cup\alpha_0\times2\) of \(X\)
     is countable and locally compact; therefore it is
@@
     \[
-      \cl{\alpha_k\times\{0\}\cup\alpha_0\times\{1\}}
+      \cl{\alpha_k\times\{0\}\cup\alpha_0\times2}
         =
-      \cl{\alpha_k}\times\{0\}\cup\alpha_0\times\{1\}
+      \cl{\alpha_k}\times\{0\}\cup\alpha_0\times2
         \subseteq
@@
     \]
+    Note that \(U_k\) is also clopen in \(\tilde X_{\alpha_0}\) since it is
+    closed in \(\cl\lambda\times\{0\}\cup\alpha_0\times2\) and open in
+    \(\lambda\times\{0\}\cup\alpha_0\times 2\).
 
@@
     \(\<\alpha,1\>\) be isolated when \(\alpha\not\in\{\alpha_k:k<\omega\}\),
-    and giving \(\<\alpha_k,1\>\) the neighborhoods
-    \(U_k\cup((\alpha_k+1)\times\{1\})\setminus K\)
-    for each compact \(K\) in \(U_k\cup(\alpha_k\times\{1\})\); that is,
-    let \(\<\alpha_k,1\>\) be the one point compactifying
+    and giving \(\<\alpha_k,1\>\) the open neighborhoods
+    \((U_k\cup((\alpha_k+1)\times\{1\}))\setminus K\) for each compact
+    subset \(K\) of \(U_k\cup(\alpha_k\times\{1\})\); that is,
+    \(\<\alpha_k,1\>\) is the one point compactifying
     \(U_k\cup(\alpha_k\times\{1\})\).
@@
     The first two requirements of our inductive hypothesis are obviously
-    satsified. Note \(U_k\cup((\alpha_k+1)\times\{1\})\) is
-    a compact neighborhood of countable cardinality
-    for points in \(\lambda\times 2\), and for points in
-    \((\omega_n\setminus\cl\lambda)\times\{0\}\) we may use a compact
-    neighborhood of countable cardinality from \(X\setminus\lambda\).
-    Finally let \(\<\alpha,0\>\in(\cl\lambda\setminus\lambda)\times\{0\}\)
-    and let \(K\subseteq\cl\lambda\times\{0\}\cup\alpha_0\times\{1\}\) be a
-    compact neighborhood in that subspace missing \(\alpha_0\times 2\).
-    Then for each \(k<\omega\), \(\<\alpha_k,1\>\) has the neighborhood
-    \(U_k\cup((\alpha_k+1)\times\{1\})\setminus K\),
-    so \(K\) gains no new limit points in
-    \(\cl\lambda\times\{0\}\cup\lambda\times\{1\}\) and thus remains compact.
-    So the third requirement is also satisfied.
+    satsified. Note points in \(\lambda\times 2\) are covered by
+    the compact countable neighborhood \(U_k\cup((\alpha_k+1)\times\{1\})\)
+    for some \(k<\omega\), and for points in
+    \((\omega_n\setminus\lambda)\times\{0\}\) we may use a compact
+    countable neighborhood from \(X\).
     For the final requirement, note that for \(\alpha<\lambda\), we may
@@
     \(\alpha\times 2\) is contained in the compact
-    set \(U_k\cup((\alpha_k+1)\times\{1\})\).
+    subset \(U_k\cup((\alpha_k+1)\times\{1\})\) of \(\lambda\times2\).
 
@@
     We again proceed by induction on \(\lambda\in C\).  Again when
-    \(\lambda\) is a limit in \(C\), the union of the previously defined
-    \(\omega_n\times\{0\}\cup\mu\times\{1\}\) satisfies the given
+    \(\lambda\) is a limit in \(C\),
+    \(
+      \tilde X_\lambda
+        =
+      \bigcup_{\mu\in C\cap\lambda}\tilde X_\mu
+    \)
+    satisfies the given
     requirements; in particular if \(\alpha<\lambda\), then

### 2015-11-25 articles/almost-compatible-functions-and-topological-games/article.tex
mark kurepa proof as unfinished

@@
   \begin{proof}
-    We use the family \(\mc K\) which is a base of \(\aleph_0\)-many compact
-    open sets for each point in the constructed topology on
+    We use the family \(\mc K\) of all compact
+    open sets in the constructed topology on
     \(\omega_n\) as our witness. Of course, every Lindel\"of set in
     a locally countable space is countable, and the closure of every
-    countable set is a compact countable set. Thus \(\mc K\)
+    countable set is a compact countable set; thus \(\mc K\)
     is cofinal in \([\omega_n]^\omega\).
-    It is Kurepa since for every countable set \(A\), there are only countably
-    many compact open sets in \(\mc K\)
-    joined to \(A\) by a finite linked chain.
+    It is Kurepa since for every countable set \(A\), there are only
+    countably many distinct compact open sets in \(\cl A\): TODO finish
   \end{proof}

### 2015-12-02 articles/almost-compatible-functions-and-topological-games/article.tex
finish kurepa family argument

@@
     is cofinal in \([\omega_n]^\omega\).
-    It is Kurepa since for every countable set \(A\), there are only
-    countably many distinct compact open sets in \(\cl A\): TODO finish
+    It is Kurepa since every countable set is contained in a countable
+    compact open subspace of \(\omega_n\); this subspace has a countable
+    base of compact open sets, which closed under finite unions enumerates
+    all compact open subsets of the subspace.
   \end{proof}

### 2015-12-02 articles/almost-compatible-functions-and-topological-games/article.tex
cite weiss et al
change S to alcompS since S(kappa) means other things in other papers. more connections to splendid paper

--- 2015-11-25 articles/almost-compatible-functions-and-topological-games/article.tex
@@
   \begin{definition}
-    The statement \(S(\kappa)\) (given as \(S(\kappa,\aleph_0,\omega)\)
-    in \cite{MR1129143}) claims that there exist one-to-one functions
+    The statement \(\alcompS\kappa\) (given as \(S(\kappa,\aleph_0,\omega)\)
+    in \cite{MR1129143} and \(S(\kappa)\) in \cite{clontzMengerGamePreprint})
+    claims that there exist one-to-one functions
     \(f_A:A\to\omega\) for each \(A\in[\kappa]^{\leq\aleph_0}\) such that
@@
 
-  In the same paper, Scheepers noted that \(S(\omega_1)\) holds in \(ZFC\),
+  In the same paper, Scheepers noted that \(\alcompS{\omega_1}\) holds in \(ZFC\),
   and that it's possible to force \(\mf c\) to be arbitrarily large
-  while preserving \(S(\mf c)\). However, \(S(\mf c^+)\) always fails.
+  while preserving \(\alcompS{\mf c}\). However, \(\alcompS{\mf c^+}\) always fails.
   This axiom may be applied to obtain a winning \(2\)-tactic for \(\pl F\)
@@
   In addition, it was shown in
-  \cite{clontzMengerGamePreprint} that when \(S(\kappa)\) holds,
+  \cite{clontzMengerGamePreprint} that when \(\alcompS{\kappa}\) holds,
   \(\pl F\) has a winning \(2\)-Markov strategy in
@@
   One might hope that \(\oneptlind{(\mf c^+)}\) might answer this question
-  in the affirmative as \(S(\mf c^+)\) fails, but we will show that assuming
+  in the affirmative as \(\alcompS{\mf c^+}\) fails, but we will show that assuming
   \(V=L\), \(\pl F\kmarkwin{2}\menGame{\oneptlind\kappa}\) for all
@@
 
-  We may weaken Scheeper's \(S(\kappa)\) as follows:
+  We may weaken Scheeper's \(\alcompS{\kappa}\) as follows:
 
   \begin{definition}
-    The statement \(S'(\kappa)\) weakens \(S(\kappa)\) be only requiring
+    The statement \(\alcompSP{\kappa}\) weakens \(\alcompS{\kappa}\) be only requiring
     the witness functions \(f_A:A\to\omega\) to be finite-to-one.
@@
 
-  The following observation will be convenient.
-
   \begin{proposition}
-    \(S(\kappa)\) and \(S'(\kappa)\) need only be witnessed by
+    \(\alcompS{\kappa}\) and \(\alcompSP{\kappa}\) need only be witnessed by
     functions \(\{f_A:A\in\mc S\}\) for some family \(\mc S\)
@@
 
-  In the next section we will show that \(S'(\kappa)\) is sufficient
+  In the next section we will show that \(\alcompSP{\kappa}\) is sufficient
   for the applications to the Scheepers and Menger games.
-  In the meantime, we will demonstrate that \(S'(\kappa)\) is strictly
-  weaker than \(S(\kappa)\).
+  In the meantime, we will demonstrate that \(\alcompSP{\kappa}\) is strictly
+  weaker than \(\alcompS{\kappa}\).
 
@@
   \begin{theorem}
-    \(S'(\kappa)\) holds whenever there exists a cofinal Kurepa family on \(\kappa\).
+    \(\alcompSP{\kappa}\) holds whenever there exists a cofinal Kurepa family on \(\kappa\).
   \end{theorem}
@@
   We now construct a topology on \(\omega_n\) for each \(n<\omega\) which
-  will witness a Kurepa family on \(\aleph_n\).
+  will witness a Kurepa family of size \(\aleph_n\). A similar construction
+  was previously shown in \cite{MR539228}.
 
@@
 
+  We note that in
+  \cite{MR539228} a \(T_2\) locally countable \(\omega\)-bounded space
+  was called \term{splendid}, and the claim that there exists a splendid
+  space of cardinality \(\kappa\) was called \(S(\kappa)\).
+
   \begin{proposition}
@@
     let \(A=\{a_\alpha:\alpha<\omega_{n+1}\}\) and since basic neighborhoods
-    are countable note any limit point is
+    are countable note any limit point of \(A\) is
     a limit point of \(A_\beta=\{a_\alpha:\alpha<\beta\}\)
@@
   \begin{theorem}
-    For each $n\in \omega$, there is a \(T_2\), locally countable,
-    $\omega$-bounded topology on $\omega_n$.
+    For each \(k< \omega\), there is a \(T_2\), locally countable,
+    \(\omega\)-bounded topology on \(\omega_k\). (That is, \(S(\omega_k)\)
+    for all \(k<\omega\)).
   \end{theorem}
@@
   \end{proof}
+
+  \begin{lemma}
+    The family of compact open sets in a locally countable, \(\omega\)-bounded
+    topological space is a Kurepa family cofinal in \([X]^\omega\).
+  \end{lemma}
+
+  \begin{proof}
+    Let \(\mc K\) collect all compact
+    open subsets of \(X\). Of course, every Lindel\"of set in
+    a locally countable space is countable, and the closure of every
+    countable set is a compact countable set; thus \(\mc K\)
+    is cofinal in \([X]^\omega\).
+    It is Kurepa since every countable set is contained in a countable
+    compact open subspace of \(X\); this subspace has a countable
+    base of compact open sets, which closed under finite unions enumerates
+    all compact open subsets of the subspace.
+  \end{proof}
+
+  The above lemma may alternatively be stated as ``\(S(\kappa)\) implies
+      the existence of a cofinal Kurepa family on \(\kappa\)''.
 
@@
 
-  \begin{proof}
-    We use the family \(\mc K\) of all compact
-    open sets in the constructed topology on
-    \(\omega_n\) as our witness. Of course, every Lindel\"of set in
-    a locally countable space is countable, and the closure of every
-    countable set is a compact countable set; thus \(\mc K\)
-    is cofinal in \([\omega_n]^\omega\).
-    It is Kurepa since for every countable set \(A\), there are only
-    countably many distinct compact open sets in \(\cl A\): TODO finish
-  \end{proof}
-
-  This is alternatively a corollary of an observation of Todorcevic
+  This corollary is also an observation of Todorcevic
   communicated by Dow in \cite{MR1229125}:
@@
 
-  So we have our desired result.
+  With this we have our desired result.
 
   \begin{corollary}
-    \(S'(\omega_n)\) holds for all \(n<\omega\). Under \(CH\), we have
-    both \(S'(\omega_2)\) and \(\neg S(\omega_2)\).
+    \(\alcompSP{\aleph_k}\) holds for all \(k<\omega\). Under \(CH\), we have
+    both \(\alcompSP{\aleph_2}\) and \(\neg\alcompS{\aleph_2}\).
   \end{corollary}
@@
   \begin{corollary}[\(V=L\)]
-    \(S'(\theta)\) holds for all cardinals.
+    \(\alcompSP{\theta}\) holds for all cardinals.
   \end{corollary}
 
-  In particular, \(S(\omega_2)\) fails under \(CH\), showing the two are
-  distinct. Actually, \(CH\) is not required to have \(S(\omega_2)\) fail.
+  In particular, \(\alcompS{\omega_2}\) fails under \(CH\), showing the two are
+  distinct. Actually, \(CH\) is not required to have \(\alcompS{\omega_2}\) fail.
 
@@
 
-  On the other hand, it's also consistent that \(S'(\theta)\) can fail.
+  On the other hand, it's also consistent that \(\alcompSP{\theta}\) can fail.
 
   \begin{theorem}
-    There's a model where \(S'(\omega_\omega)\)
+    There's a model where \(\alcompSP{\omega_\omega}\)
     fails.
@@
   \begin{question}
-    Is \(S'(\theta)\) equivalent to having a Kurepa family on \(\theta\)?
+    Is \(\alcompSP{\theta}\) equivalent to having a Kurepa family on \(\theta\)?
   \end{question}
@@
 \end{center}
-\caption{Diagram of Scheeper/Menger game implications with \(S'(\kappa)\)}
+\caption{Diagram of Scheeper/Menger game implications with \(\alcompSP{\kappa}\)}
 \label{GamesDiagram2}
@@
 
-  \begin{theorem}
-    Figure \ref{GamesDiagram2} holds. (Proven in [TODO cite])
+  \begin{theorem}[\cite{clontzMengerGamePreprint}]
+    Figure \ref{GamesDiagram2} holds.
     (Actually, TODO double-check that it works with just S', particularly
@@
   \begin{corollary}
-    It is consistent that \(S'(\omega_\omega)\) fails,
-    but as \(S'(\omega_k)\) holds for all \(k<\omega\), we have
+    It is consistent that \(\alcompSP{\omega_\omega}\) fails,
+    but as \(\alcompSP{\omega_k}\) holds for all \(k<\omega\), we have
     \(\pl F\kmarkwin2\schFillIntGame{\omega_\omega}\) and
@@
   a counterexample using \(X=\oneptlind\kappa\) since
-  \(S'(\kappa)\) and thus \(\pl F\kmarkwin2\schFillIntGame{\kappa}\)
+  \(\alcompSP{\kappa}\) and thus \(\pl F\kmarkwin2\schFillIntGame{\kappa}\)
   always holds.

### 2015-12-03 articles/almost-compatible-functions-and-topological-games/article.tex
paper complete modulo editing of Dow's results and topological implications

@@
   \begin{definition}
-    The statement \(\alcompSP{\kappa}\) weakens \(\alcompS{\kappa}\) be only requiring
-    the witness functions \(f_A:A\to\omega\) to be finite-to-one.
+    The statement \(\alcompSP{\kappa}\) weakens \(\alcompS{\kappa}\) by only
+    requiring the witnessing almost-compatible functions \(f_A:A\to\omega\)
+    to be finite-to-one.
   \end{definition}
@@
     for each \(A\in[\kappa]^{\aleph_0}\).
+    Let \(\kurepaS\kappa\) be the statement claiming there exists
+    a Kurepa family on \(\kappa\)
+    cofinal in \([\kappa]^{\aleph_0}\).
   \end{definition}
@@
   \begin{theorem}
-    \(\alcompSP{\kappa}\) holds whenever there exists a cofinal Kurepa family on \(\kappa\).
+    \(\kurepaS\kappa \Rightarrow \alcompSP{\kappa}\).
   \end{theorem}
@@
   will witness a Kurepa family of size \(\aleph_n\). A similar construction
-  was previously shown in \cite{MR539228}.
+  was previously shown by Juh\'asz et. al. in \cite{MR539228},
+  and the relationship of
+  Kurepa families and such spaces has also been investigated in a preprint
+  of Nyikos \cite{NYIKOSKUREPA}.
 
@@
     subset of the space has compact closure.
+    As in \cite{MR539228} we call a
+    \(T_2\), locally countable, \(\omega\)-bounded space
+    \term{splendid}, and let \(\splendidS\kappa\) represent
+    the claim that there exists a splendid space of cardinality \(\kappa\).
   \end{definition}
-
-  We note that in
-  \cite{MR539228} a \(T_2\) locally countable \(\omega\)-bounded space
-  was called \term{splendid}, and the claim that there exists a splendid
-  space of cardinality \(\kappa\) was called \(S(\kappa)\).
 
@@
     For each \(k< \omega\), there is a \(T_2\), locally countable,
-    \(\omega\)-bounded topology on \(\omega_k\). (That is, \(S(\omega_k)\)
-    for all \(k<\omega\)).
+    \(\omega\)-bounded topology on \(\omega_k\). That is, \(\splendidS{\aleph_k}\)
+    for all \(k<\omega\).
   \end{theorem}
@@
     The family of compact open sets in a locally countable, \(\omega\)-bounded
-    topological space is a Kurepa family cofinal in \([X]^\omega\).
+    topological space \(X\)
+    is a Kurepa family cofinal in \([X]^\omega\). That is,
+    \(\splendidS\kappa \Rightarrow \kurepaS\kappa\).
   \end{lemma}
@@
 
-  The above lemma may alternatively be stated as ``\(S(\kappa)\) implies
-      the existence of a cofinal Kurepa family on \(\kappa\)''.
-
   \begin{corollary}
-    There exists a Kurepa family cofinal in \([\omega_k]^\omega\)
-    for each \(k<\omega\).
+    \(\kurepaS{\aleph_k}\) for all \(k<\omega\).
   \end{corollary}
 
-  This corollary is also an observation of Todorcevic
+  Alternatively, the previous corollary may be obtained
+  via an observation of Todorcevic
   communicated by Dow in \cite{MR1229125}:
-  if every Kurepa family of size at most \(\theta\)
-  extends to a cofinal Kurepa family, then the same is true of \(\theta^+\).
-  So the result follows as
-  every Kurepa family \(\mc K\) of size \(\omega\) extends to
-  the cofinal Kurepa family \([\bigcup\mc K]^\omega\).
-
-  With this we have our desired result.
+  if every Kurepa family of size at most \(\kappa\)
+  extends to a cofinal Kurepa family, then the same is true of \(\kappa^+\).
+
+  Nyikos points out in \cite{NYIKOSKUREPA} that a cofinal Kurepa family may
+  be used to construct a locally metrizable, \(\omega\)-bounded,
+  zero-dimensional space with appropriate cardinality,
+  but whether this can be
+  strengthened to locally countable and \(\omega\)-bounded (as asked in
+  \cite{MR539228}) remains an open question.
+
+  Also left open is this extension of the question asked in \cite{NYIKOSKUREPA}
+  and \cite{MR539228} on the possible equivalence of \(\splendidS\kappa\)
+  and \(\kurepaS\kappa\).
+
+  \begin{question}
+    May any of the implications in the theorem
+    \(\splendidS\kappa\Rightarrow\kurepaS\kappa\Rightarrow\alcompSP\kappa\)
+    be reversed?
+  \end{question}
+
+  Regardless, we have obtained our desired result.
 
   \begin{corollary}
-    \(\alcompSP{\aleph_k}\) holds for all \(k<\omega\). Under \(CH\), we have
-    both \(\alcompSP{\aleph_2}\) and \(\neg\alcompS{\aleph_2}\).
+    \(\alcompSP{\aleph_k}\) for all \(k<\omega\).
   \end{corollary}
 
-  \newpage
-
-  \section{TODO ALL THIS STUFF NEEDS EDITING STILL}
-
-  As noted in [TODO cite Dow],
-  Jensen's one-gap two-cardinal theorem under \(V=L\) [TODO cite] can be used
-  to show that there exist cofinal Kurepa families on every cardinal.
+  \section{More consistency results}
+
+  As noted in \cite{MR1229125}, Jensen's one-gap two-cardinal theorem under
+  \(V=L\) introduced in \cite{MR0309729} implies that \(\kurepaS\kappa\)
+  holds for all cardinals \(\kappa\).
 
   \begin{corollary}[\(V=L\)]
-    \(\alcompSP{\theta}\) holds for all cardinals.
+    \(\alcompSP{\kappa}\) for all cardinals \(\kappa\).
   \end{corollary}
 
-  In particular, \(\alcompS{\omega_2}\) fails under \(CH\), showing the two are
-  distinct. Actually, \(CH\) is not required to have \(\alcompS{\omega_2}\) fail.
-
-  % TODO: read through Alan's proof and fit to rest of document
-        We are going to need a technical lemma (available in Kunen).
-        \bigskip
-
-        \begin{lemma}
+  Weakening to the continuum hypothesis, we have an obvious consequence.
+
+  \begin{corollary}[\(CH\)]
+    \(\alcompSP{\aleph_2}\), but \(\neg\alcompS{\aleph_2}\).
+  \end{corollary}
+
+  But \(CH\) is not required to have \(\alcompS{\aleph_2}\) fail.
+
+  % TODO: read through Alan's proofs and fit to rest of document
+
+            \begin{lemma}[\cite{MR597342}]
             Assume that $G\subset \operatorname{Fn}(\omega_2,2)$ is a generic filter,
@@
             \begin{theorem}
-          If we add $\omega_2$ Cohen reals to a model of CH we get
-        that Scheepers' $S(\omega_2)$ (still) fails.
+              There exists a model of \(ZFC\) for which \(\mf c=\aleph_2\)
+              and \(\neg\alcompS{\aleph_2}\).
             \end{theorem}
@@
 
-  On the other hand, it's also consistent that \(\alcompSP{\theta}\) can fail.
+  We are also able to force \(\alcompSP{\kappa}\) to fail for some cardinal.
 
   \begin{theorem}
-    There's a model where \(\alcompSP{\omega_\omega}\)
-    fails.
+    There exists a model of \(ZFC\) for which \(\neg\alcompSP{\aleph_\omega}\).
   \end{theorem}
@@
 
-          We will need the following claim from \cite{MR1045371}
+          We will need the following claim from \cite{MR1045371}:
 
@@
           for all $\xi\in \Lambda_n\cap N$.
-
   \end{proof}
 
-  \begin{question}
-    Is \(\alcompSP{\theta}\) equivalent to having a Kurepa family on \(\theta\)?
-  \end{question}
+  \newpage
+
+  \section{TODO ALL THIS STUFF NEEDS EDITING STILL}
 

### 2015-12-03 articles/almost-compatible-functions-and-topological-games/article.tex
almost-complete infinite length game applications

@@
 
-  \begin{question}
+  \begin{question}\label{mainQuestion}
     Does there exist a topological space \(X\) for which
@@
   \end{question}
-
-  One might hope that \(\oneptlind{(\mf c^+)}\) might answer this question
-  in the affirmative as \(\alcompS{\mf c^+}\) fails, but we will show that assuming
-  \(V=L\), \(\pl F\kmarkwin{2}\menGame{\oneptlind\kappa}\) for all
-  cardinals \(\kappa\).
 
@@
 
-  \section{More consistency results}
+  \section{Consistency results}
 
@@
 
-  We are also able to force \(\alcompSP{\kappa}\) to fail for some cardinal.
+  We are also able to force \(\alcompSP{\kappa}\) to fail for every cardinal
+  other than the first \(\omega\)-many we've already guaranteed.
 
@@
 
-  \newpage
-
-  \section{TODO ALL THIS STUFF NEEDS EDITING STILL}
-
-  \section*{Applications!}
+  \section{Applications to infinite length games}
+
+  We introduce three variations of Scheeper's game which we defined in
+  the introduction.
+
+  \begin{game}
+    Let \(\schFillGame\kappa\) denote the
+    \term{Scheepers countable-finite union game} which proceeds analogously
+    to \(\schFillStrictGame\kappa\), except that \(\pl C\)'s restriction in round \(n+1\)
+    is weakened to \(C_{n+1}\supseteq C_n\).
+  \end{game}
+
+  \begin{game}
+    Let \(\schFillInitialGame\kappa\) denote the
+    \term{Scheepers countable-finite initial game} which proceeds analogously
+    to \(\schFillGame\kappa\), except that \(\pl F\)'s winning condition is
+    weakened to \(\bigcup_{n<\omega}F_n\supseteq C_0\).
+  \end{game}
+
+  \begin{game}
+    Let \(\schFillIntGame\kappa\) denote the
+    \term{Scheepers countable-finite intersection game} which proceeds analogously
+    to \(\schFillInitialGame\kappa\), except that \(\pl C\) may choose any
+    \(C_n\in[\kappa]^{\leq\omega}\) each round, and \(\pl F\)'s winning condition
+    is weakened to
+    \(\bigcup_{n<\omega}F_n\supseteq\bigcap_{n<\omega}C_n\).
+  \end{game}
+
+  In \cite{clontzMengerGamePreprint} Clontz extended Scheepers' application of
+  almost-compatible injections to these game variants as well as
+  \(\menGame{\oneptlind\kappa}\).
 
@@
 
-    S'(\kappa) &
+    \alcompSP\kappa \\
+
+    &
     \pl F \kmarkwin2\schFillInitialGame\kappa &
     \pl F \kmarkwin2\schFillGame\kappa \\
-
-    &
-    &
-    \pl F \ktactwin2\schFillStrictGame\kappa \\
   };
@@
     (m-2-1) edge (m-1-2)
-    (m-2-1) edge (m-2-2)
-    (m-2-1) edge (m-3-3)
-    (m-1-2) edge (m-2-2)
-    (m-1-3) edge (m-2-3)
-    (m-3-3) edge (m-2-3);
+    (m-2-1) edge (m-3-2)
+    (m-1-2) edge (m-3-2)
+    (m-1-3) edge (m-3-3);
   \path[>=latex,<->]
     (m-1-2) edge (m-1-3)
-    (m-2-2) edge (m-2-3);
+    (m-3-2) edge (m-3-3);
 \end{tikzpicture}
@@
 
-  \begin{theorem}[\cite{clontzMengerGamePreprint}]
-    Figure \ref{GamesDiagram2} holds.
-    (Actually, TODO double-check that it works with just S', particularly
-    the strict game)
+%   \begin{figure}[h]
+% \begin{center}
+% \begin{tikzpicture}
+%   \matrix (m) [matrix of math nodes,row sep=3em,column sep=1em,minimum width=2em]
+%   {
+%     &
+%     \pl F \kmarkwin2\menGame{\oneptlind\kappa} &
+%     \pl F \kmarkwin2\schFillIntGame\kappa \\
+
+%     \alcompSP\kappa &
+%     \pl F \kmarkwin2\schFillInitialGame\kappa &
+%     \pl F \kmarkwin2\schFillGame\kappa \\
+
+%     &
+%     &
+%     \pl F \ktactwin2\schFillStrictGame\kappa \\
+%   };
+%   \path[>=latex,->]
+%     (m-2-1) edge (m-1-2)
+%     (m-2-1) edge (m-2-2)
+%     (m-2-1) edge (m-3-3)
+%     (m-1-2) edge (m-2-2)
+%     (m-1-3) edge (m-2-3)
+%     (m-3-3) edge (m-2-3);
+%   \path[>=latex,<->]
+%     (m-1-2) edge (m-1-3)
+%     (m-2-2) edge (m-2-3);
+% \end{tikzpicture}
+% \end{center}
+% \caption{Diagram of Scheeper/Menger game implications with \(\alcompSP{\kappa}\)}
+% \label{GamesDiagram2}
+% \end{figure}
+
+  \begin{theorem}
+    \(\alcompSP\kappa\) implies the game-theoretic conditions
+    shown in Figure \ref{GamesDiagram2}.
   \end{theorem}
 
-  It was left open if these implications can be reversed. The answer is
-  consistently no.
+  \begin{proof}
+    The weaker claim
+    \(\alcompS\kappa\Rightarrow\pl F \kmarkwin2\schFillIntGame\kappa\)
+    was proven in \cite{clontzMengerGamePreprint};
+    however, the strategy
+    only required that the \(f_A\) be pairwise almost-compatible and
+    that preimages of finite sets in each \(f_A\)
+    are finite, which is also possible assuming \(\alcompSP\kappa\).
+  \end{proof}
+
+    %TODO maybe this can be made to work...
+    % In \cite{MR1129143} Scheepers used a proof of Todorcevic to demonstrate
+    % \(\alcompS\kappa\Rightarrow\pl F \ktactwin2\schFillStrictGame\kappa\).
+    % For the convenience of the reader we explicitly demonstrate
+    % the generalization as follows.
+
+    % Let \(\{f_A:A\in[\kappa]^{\leq\aleph_0}\}\) witness
+    % \(\alcompSP\kappa\), and define \(g_A:A\to\omega\) by
+    % \(g_A(\alpha)=f_A(\alpha)-|\{\beta\in A:f_A(\beta)<f_A(\alpha)\}|\).
+
+    % We claim that \(\{\alpha\in A:g_A(\alpha)\leq g_B(\alpha)\}\)
+    % must be finite as it is bounded above by
+    % \(\max\{M,f_A(\alpha),f_B(\alpha):f_A(\alpha)\not=f_B(\alpha)\}\)
+    % where \(M=f_B(\alpha)\) for some \(\alpha\in B\setminus A\).
+    % To see this, let \(f_A(\alpha)=f_B(\alpha)=N>M\) and assume
+    % \(f_A(\beta)\not=f_B(\beta)\) implies \(f_A(\beta),f_B(\beta)<N\).
+    % Then
+    % \[
+    %   g_A(\alpha)
+    %     =
+    %   N-|\{\beta\in A:f_A(\beta)<N\}|
+    %     >
+    %   N-|\{\beta\in B:f_B(\beta)<N\}|
+    %     =
+    %   g_B(\alpha)
+    % \]
+    % with the strictness of the inequality witnessed by \(f_B(\alpha)=M<N\)
+    % for some \(\alpha\in B\setminus A\).
+
+    % As a result,
+    % \[
+    %   \sigma(\<A,B\>)
+    %     =
+    %   \{\alpha\in A:f_A(\alpha)\not=f_B(\alpha)\}
+    %     \cup
+    %   \{\alpha\in A:g_A(\alpha)\leq g_B(\alpha)\}
+    % \]
+    % is a legal \(2\)-tactic for \(\pl F\). Let \(C=\<C_0,C_1,\dots\>\) be
+    % a strictly increasing sequence of countable sets and
+    % \(\alpha\in C_n\). Of course if
+    % \(f_{C_{n+m}}(\alpha)\not=f_{C_{n+m+1}}(\alpha)\) for some
+    % \(m<\omega\) we have \(\alpha\in\sigma(\<C_{n+m},C_{n+m+1}\>)\) immediately.
+    % Otherwise let \(f_{C_{n+m}}(\alpha)=f_{C_{n+m+1}}(\alpha)=N\)
+    % for all \(m<\omega\).
+
+  It was left open if \(\alcompSP\kappa\) was equivalent to these
+  game-theoretic conditions. The answer is consistently negative.
 
@@
   \begin{proof}
-    Let \(\sigma_n\) be a winning \(2\)-mark for \(\pl F\) in
-    \(\schFillInitialGame{\omega_{\beta_n}}\). Define the \(2\)-mark \(\sigma\)
-    for \(\pl F\) in \(\schFillInitialGame{\omega_\alpha}\) as follows:
-    \[
-      \sigma(\<C\>,0)
-        =
-      \sigma_0(\<C\cap\omega_{\beta_0}\>,0)
-    \]
-    \[
-      \sigma(\<C,D\>,n+1)
-        =
-      \sigma_{n+1}(\<D\cap\omega_{\beta_{n+1}}\>,0)
-        \cup
-      \bigcup_{m\leq n}
-      \sigma_m(\<C\cap\omega_{\beta_m},D\cap\omega_{\beta_m}\>,n-m+1)
-    \]
-
-    Let \(\<C_0,C_1,\dots\>\) be an attack by
-    \(\pl C\) in \(\schFillInitialGame{\omega_\alpha}\), and
-    \(\alpha\in C_0\).
-    Choose \(N<\omega\) with \(\alpha<\omega_{\beta_{N+1}}\). Consider the
-    attack
-    \(\<C_{N+1}\cap\omega_{\beta_{N+1}},C_{N+2}\cap\omega_{\beta_{N+1}},\dots\>\)
-    by \(\pl C\) in \(\schFillInitialGame{\omega_{\beta_{N+1}}}\). Since
-    \(\sigma_{N+1}\) is a winning strategy and
-    \(\alpha\in C_{N+1}\cap\omega_{\beta_{N+1}}\), either
-    \(\alpha\in\sigma_{N+1}(\<C_{N+1}\cap\omega_{\beta_{N+1}}\>,0)\) and thus
-    \(\alpha\in\sigma(\<C_N,C_{N+1}\>,N+1)\), or
-    \(
-      \alpha
-        \in
-      \sigma_{N+1}(
-        \<C_{N+M+1}\cap\omega_{\beta_{N+1}},C_{N+M+2}\cap\omega_{\beta_{N+1}}\>
-        ,M+1
-      )
-    \)
-    for some \(M<\omega\) and thus
-    \(
-      \alpha
-        \in
-      \sigma(
-        \<C_{N+M+1},C_{N+M+2}\>,
-        N+M+2
-      )
-    \). Thus \(\sigma\) is a winning strategy.
+    The proof proceeds nearly identically to the previous proof.
   \end{proof}
+    % Let \(\sigma_n\) be a winning \(2\)-mark for \(\pl F\) in
+    % \(\schFillInitialGame{\omega_{\beta_n}}\). Define the \(2\)-mark \(\sigma\)
+    % for \(\pl F\) in \(\schFillInitialGame{\omega_\alpha}\) as follows:
+    % \[
+    %   \sigma(\<C\>,0)
+    %     =
+    %   \sigma_0(\<C\cap\omega_{\beta_0}\>,0)
+    % \]
+    % \[
+    %   \sigma(\<C,D\>,n+1)
+    %     =
+    %   \sigma_{n+1}(\<D\cap\omega_{\beta_{n+1}}\>,0)
+    %     \cup
+    %   \bigcup_{m\leq n}
+    %   \sigma_m(\<C\cap\omega_{\beta_m},D\cap\omega_{\beta_m}\>,n-m+1)
+    % \]
+
+    % Let \(\<C_0,C_1,\dots\>\) be an attack by
+    % \(\pl C\) in \(\schFillInitialGame{\omega_\alpha}\), and
+    % \(\alpha\in C_0\).
+    % Choose \(N<\omega\) with \(\alpha<\omega_{\beta_{N+1}}\). Consider the
+    % attack
+    % \(\<C_{N+1}\cap\omega_{\beta_{N+1}},C_{N+2}\cap\omega_{\beta_{N+1}},\dots\>\)
+    % by \(\pl C\) in \(\schFillInitialGame{\omega_{\beta_{N+1}}}\). Since
+    % \(\sigma_{N+1}\) is a winning strategy and
+    % \(\alpha\in C_{N+1}\cap\omega_{\beta_{N+1}}\), either
+    % \(\alpha\in\sigma_{N+1}(\<C_{N+1}\cap\omega_{\beta_{N+1}}\>,0)\) and thus
+    % \(\alpha\in\sigma(\<C_N,C_{N+1}\>,N+1)\), or
+    % \(
+    %   \alpha
+    %     \in
+    %   \sigma_{N+1}(
+    %     \<C_{N+M+1}\cap\omega_{\beta_{N+1}},C_{N+M+2}\cap\omega_{\beta_{N+1}}\>
+    %     ,M+1
+    %   )
+    % \)
+    % for some \(M<\omega\) and thus
+    % \(
+    %   \alpha
+    %     \in
+    %   \sigma(
+    %     \<C_{N+M+1},C_{N+M+2}\>,
+    %     N+M+2
+    %   )
+    % \). Thus \(\sigma\) is a winning strategy.
 
   \begin{corollary}
-    It is consistent that \(\alcompSP{\omega_\omega}\) fails,
-    but as \(\alcompSP{\omega_k}\) holds for all \(k<\omega\), we have
+    It is consistent that \(\alcompSP{\aleph_\omega}\) fails,
+    but as \(\alcompSP{\aleph_k}\) holds for all \(k<\omega\), we have
     \(\pl F\kmarkwin2\schFillIntGame{\omega_\omega}\) and
@@
 
-  A tricky topological question: does \(\pl F\win\menGame{X}\) imply
-  \(\pl F\kmarkwin2\menGame{X}\)?
-  (C showed that )
-  Under \(V=L\), we cannot hope to find
-  a counterexample using \(X=\oneptlind\kappa\) since
-  \(\alcompSP{\kappa}\) and thus \(\pl F\kmarkwin2\schFillIntGame{\kappa}\)
-  always holds.
-
-  \begin{definition}
-    Let \(R_\omega\) be the real numbers with the topology of the usual
-    open intervals with countably many elements removed.
-  \end{definition}
-
-  \begin{theorem}
-    \(\pl F\win\menGame{R_\omega}\).
-    If there exists a Kurepa family on the reals, then
-    \(\pl F\kmarkwin2\menGame{R_\omega}\).
-  \end{theorem}
+  Our topological question \ref{mainQuestion} remains unsolved; however,
+  our results have revealed that we cannot hope to find a \(ZFC\)
+  counterexample where \(X=\oneptlind\kappa\). This is
+  because if we also assume \(V=L\), it follows that
+  \(\alcompSP{\kappa}\) and therefore \(\pl F\kmarkwin2\menGame{X}\)
+  for every cardinal.
+
+  \section{Generalized Kurepa families and almost-compactible functions}
+
+  TODO
 

### 2015-12-03 articles/almost-compatible-functions-and-topological-games/article.tex
clear up A,A' for tactics, marks

@@
   almost-compatible injections to these game variants as well as
-  \(\menGame{\oneptlind\kappa}\).
+  \(\menGame{\oneptlind\kappa}\). However, when considering Markov strategies,
+  finite-to-one functions suffice.
 
@@
 
-    %TODO maybe this can be made to work...
-    % In \cite{MR1129143} Scheepers used a proof of Todorcevic to demonstrate
-    % \(\alcompS\kappa\Rightarrow\pl F \ktactwin2\schFillStrictGame\kappa\).
-    % For the convenience of the reader we explicitly demonstrate
-    % the generalization as follows.
-
-    % Let \(\{f_A:A\in[\kappa]^{\leq\aleph_0}\}\) witness
-    % \(\alcompSP\kappa\), and define \(g_A:A\to\omega\) by
-    % \(g_A(\alpha)=f_A(\alpha)-|\{\beta\in A:f_A(\beta)<f_A(\alpha)\}|\).
-
-    % We claim that \(\{\alpha\in A:g_A(\alpha)\leq g_B(\alpha)\}\)
-    % must be finite as it is bounded above by
-    % \(\max\{M,f_A(\alpha),f_B(\alpha):f_A(\alpha)\not=f_B(\alpha)\}\)
-    % where \(M=f_B(\alpha)\) for some \(\alpha\in B\setminus A\).
-    % To see this, let \(f_A(\alpha)=f_B(\alpha)=N>M\) and assume
-    % \(f_A(\beta)\not=f_B(\beta)\) implies \(f_A(\beta),f_B(\beta)<N\).
-    % Then
-    % \[
-    %   g_A(\alpha)
-    %     =
-    %   N-|\{\beta\in A:f_A(\beta)<N\}|
-    %     >
-    %   N-|\{\beta\in B:f_B(\beta)<N\}|
-    %     =
-    %   g_B(\alpha)
-    % \]
-    % with the strictness of the inequality witnessed by \(f_B(\alpha)=M<N\)
-    % for some \(\alpha\in B\setminus A\).
-
-    % As a result,
-    % \[
-    %   \sigma(\<A,B\>)
-    %     =
-    %   \{\alpha\in A:f_A(\alpha)\not=f_B(\alpha)\}
-    %     \cup
-    %   \{\alpha\in A:g_A(\alpha)\leq g_B(\alpha)\}
-    % \]
-    % is a legal \(2\)-tactic for \(\pl F\). Let \(C=\<C_0,C_1,\dots\>\) be
-    % a strictly increasing sequence of countable sets and
-    % \(\alpha\in C_n\). Of course if
-    % \(f_{C_{n+m}}(\alpha)\not=f_{C_{n+m+1}}(\alpha)\) for some
-    % \(m<\omega\) we have \(\alpha\in\sigma(\<C_{n+m},C_{n+m+1}\>)\) immediately.
-    % Otherwise let \(f_{C_{n+m}}(\alpha)=f_{C_{n+m+1}}(\alpha)=N\)
-    % for all \(m<\omega\).
-
-  It was left open if \(\alcompSP\kappa\) was equivalent to these
-  game-theoretic conditions. The answer is consistently negative.
+  We include the following proof from \cite{MR1129143} for the convenience
+  of the reader.
+
+  \begin{theorem}
+    \(\alcompS\kappa\Rightarrow\pl F \ktactwin2\schFillStrictGame\kappa\)
+  \end{theorem}
+
+  \begin{proof}
+    Let \(\{f_A:A\in[\kappa]^{\leq\aleph_0}\}\) witness
+    \(\alcompS\kappa\), and define \(g_A:A\to\omega\) by
+    \(g_A(\alpha)=f_A(\alpha)-|\{\beta\in A:f_A(\beta)<f_A(\alpha)\}|\).
+
+    We claim that \(\{\alpha\in A:g_A(\alpha)\leq g_B(\alpha)\}\)
+    must be finite as it is bounded above by
+    \(\max\{M,f_A(\alpha),f_B(\alpha):f_A(\alpha)\not=f_B(\alpha)\}\)
+    where \(M=f_B(\alpha)\) for some \(\alpha\in B\setminus A\).
+    To see this, let \(f_A(\alpha)=f_B(\alpha)=N>M\) and assume
+    \(f_A(\beta)\not=f_B(\beta)\) implies \(f_A(\beta),f_B(\beta)<N\).
+    Then
+    \[
+      g_A(\alpha)
+        =
+      N-|\{\beta\in A:f_A(\beta)<N\}|
+        >
+      N-|\{\beta\in B:f_B(\beta)<N\}|
+        =
+      g_B(\alpha)
+    \]
+    with the strictness of the inequality witnessed by \(f_B(\alpha)=M<N\)
+    for some \(\alpha\in B\setminus A\).
+
+    As a result,
+    \[
+      \sigma(\<A,B\>)
+        =
+      \{\alpha\in A:g_A(\alpha)\leq g_B(\alpha)\}
+    \]
+    is a legal \(2\)-tactic for \(\pl F\). Let \(C=\<C_0,C_1,\dots\>\) be
+    a strictly increasing sequence of countable sets and
+    \(\alpha\in C_n\). Noting that \(f_A\) is an injection and not
+    just finite-to-one, \(0\leq g_{C_{n+m}}(\alpha)\) for all
+    \(m<\omega\), and it follows that
+    \(g_{C_{n+m}}(\alpha)\leq g_{C_{n+m+1}}(\alpha)\) for some \(m<\omega\).
+    Therefore \(\alpha\in\sigma(\<C_{n+m},C_{n+m+1}\>)\).
+  \end{proof}
+
+  So it would seem that \(\alcompSP\kappa\) is sufficient only when
+  considering Markov strategies. (Of course,
+  \(\alcompSP\kappa\Rightarrow\pl F\kmarkwin2\schFillGame\kappa
+  \Rightarrow\pl F\kmarkwin2\schFillStrictGame{\kappa}\).)
+  We would like to demonstrate that \(\alcompSP\kappa\) is not
+  necessary.
 
@@
     Let \(\alpha\) be the limit of increasing ordinals \(\beta_n\) for \(n<\omega\).
-    If \(\pl F \kmarkwin2\schFillIntGame{\omega_{\beta_n}}\) for all
-    \(n<\omega\), then \(\pl F\kmarkwin2\schFillIntGame{\omega_\alpha}\).
+    If \(\pl F \kmarkwin2\schFillIntGame{\aleph_{\beta_n}}\) for all
+    \(n<\omega\), then \(\pl F\kmarkwin2\schFillIntGame{\aleph_\alpha}\).
   \end{theorem}
@@
     Let \(\sigma_n\) be a winning \(2\)-mark for \(\pl F\) in
-    \(\schFillIntGame{\omega_{\beta_n}}\). Define the \(2\)-mark \(\sigma\)
-    for \(\pl F\) in \(\schFillIntGame{\omega_\alpha}\) as follows:
+    \(\schFillIntGame{\aleph_{\beta_n}}\). Define the \(2\)-mark \(\sigma\)
+    for \(\pl F\) in \(\schFillIntGame{\aleph_\alpha}\) as follows:
     \[
@@
         =
-      \sigma_0(\<C\cap\omega_{\beta_0}\>,0)
+      \sigma_0(\<C\cap\aleph_{\beta_0}\>,0)
     \]
@@
         =
-      \sigma_{n+1}(\<D\cap\omega_{\beta_{n+1}}\>,0)
+      \sigma_{n+1}(\<D\cap\aleph_{\beta_{n+1}}\>,0)
         \cup
       \bigcup_{m\leq n}
-      \sigma_m(\<C\cap\omega_{\beta_m},D\cap\omega_{\beta_m}\>,n-m+1)
+      \sigma_m(\<C\cap\aleph_{\beta_m},D\cap\aleph_{\beta_m}\>,n-m+1)
     \]
@@
     Let \(\<C_0,C_1,\dots\>\) be an attack by
-    \(\pl C\) in \(\schFillIntGame{\omega_\alpha}\), and
+    \(\pl C\) in \(\schFillIntGame{\aleph_\alpha}\), and
     \(\alpha\in\bigcap_{n<\omega}C_n\).
-    Choose \(N<\omega\) with \(\alpha<\omega_{\beta_{N+1}}\). Consider the
+    Choose \(N<\omega\) with \(\alpha<\aleph_{\beta_{N+1}}\). Consider the
     attack
-    \(\<C_{N+1}\cap\omega_{\beta_{N+1}},C_{N+2}\cap\omega_{\beta_{N+1}},\dots\>\)
-    by \(\pl C\) in \(\schFillIntGame{\omega_{\beta_{N+1}}}\). Since
+    \(\<C_{N+1}\cap\aleph_{\beta_{N+1}},C_{N+2}\cap\aleph_{\beta_{N+1}},\dots\>\)
+    by \(\pl C\) in \(\schFillIntGame{\aleph_{\beta_{N+1}}}\). Since
     \(\sigma_{N+1}\) is a winning strategy and
-    \(\alpha\in\bigcap_{n<\omega}C_{N+n+1}\cap\omega_{\beta_{N+1}}\), either
-    \(\alpha\in\sigma_{N+1}(\<C_{N+1}\cap\omega_{\beta_{N+1}}\>,0)\) and thus
+    \(\alpha\in\bigcap_{n<\omega}C_{N+n+1}\cap\aleph_{\beta_{N+1}}\), either
+    \(\alpha\in\sigma_{N+1}(\<C_{N+1}\cap\aleph_{\beta_{N+1}}\>,0)\) and thus
     \(\alpha\in\sigma(\<C_N,C_{N+1}\>,N+1)\), or
@@
       \sigma_{N+1}(
-        \<C_{N+M+1}\cap\omega_{\beta_{N+1}},C_{N+M+2}\cap\omega_{\beta_{N+1}}\>
+        \<C_{N+M+1}\cap\aleph_{\beta_{N+1}},C_{N+M+2}\cap\aleph_{\beta_{N+1}}\>
         ,M+1
@@
     Let \(\alpha\) be the limit of increasing ordinals \(\beta_n\) for \(n<\omega\).
-    If \(\pl F \kmarkwin2\schFillInitialGame{\omega_{\beta_n}}\) for all
-    \(n<\omega\), then \(\pl F\kmarkwin2\schFillInitialGame{\omega_\alpha}\).
+    If \(\pl F \kmarkwin2\schFillInitialGame{\aleph_{\beta_n}}\) for all
+    \(n<\omega\), then \(\pl F\kmarkwin2\schFillInitialGame{\aleph_\alpha}\).
   \end{theorem}
@@
     It is consistent that \(\alcompSP{\aleph_\omega}\) fails,
-    but as \(\alcompSP{\aleph_k}\) holds for all \(k<\omega\), we have
-    \(\pl F\kmarkwin2\schFillIntGame{\omega_\omega}\) and
-    \(\pl F\kmarkwin2\schFillInitialGame{\omega_\omega}\).
+    but as \(\alcompSP{\aleph_k}\) holds in \(ZFC\) for all \(k<\omega\),
+    both
+    \(\pl F\kmarkwin2\schFillIntGame{\aleph_\omega}\) and
+    \(\pl F\kmarkwin2\schFillInitialGame{\aleph_\omega}\) hold in \(ZFC\).
   \end{corollary}
 
-  Our topological question \ref{mainQuestion} remains unsolved; however,
+  Note that Question \ref{mainQuestion} remains unsolved; however,
   our results have revealed that we cannot hope to find a \(ZFC\)
@@
   \(\alcompSP{\kappa}\) and therefore \(\pl F\kmarkwin2\menGame{X}\)
-  for every cardinal.
+  for every cardinal. Although, one may consider the following weaker question.
+
+  \begin{question}
+    Is there a model of \(ZFC\) where both
+    \(\pl F\kmarkwin2\menGame{\oneptlind{\aleph_{\omega+1}}}\) and
+    \(\alcompSP{\aleph_\omega}\) fail?
+  \end{question}
 

### 2015-12-04 articles/almost-compatible-functions-and-topological-games/article.tex
complete draft modulo Dow's results

@@
   \begin{definition}
-    A topological space is said to be \(\omega\)-bounded if each countable
-    subset of the space has compact closure.
+    A topological space is said to be \term{\(\omega\)-bounded}
+    if each countable subset of the space has compact closure.
     As in \cite{MR539228} we call a
@@
     are finite, which is also possible assuming \(\alcompSP\kappa\).
+    Note that the relationships amongst the games were all shown in
+    \cite{clontzMengerGamePreprint}.
   \end{proof}
@@
 
-  \section{Generalized Kurepa families and almost-compactible functions}
-
-  TODO
+  % \section{Generalized Kurepa families and almost-compactible functions}
+
+  % TODO
 

### 2015-12-04 articles/almost-compatible-functions-and-topological-games/article.tex
add abstract

@@
 
-\keywords{TODO}
-
-% TODO
-\subjclass[2010]{}
+% \keywords{TODO}
+% \subjclass[2010]{}
 
 \begin{abstract}
-  TODO
+  \(\alcompSP\kappa\) asserts the existence of pairwise
+  almost compatible finite-to-one functions \(A\to\omega\) for each
+  countable subset \(A\) of \(\kappa\).
+  The existence of winning \(2\)-Markov strategies in
+  several infinite-length games, including
+  the Menger game on the one-point Lindel\"ofication \(\oneptlind\kappa\)
+  of \(\kappa\), are guaranteed by \(\alcompSP\kappa\). \(\alcompSP\kappa\) is
+  implied by the existence of cofinal Kurepa families of size \(\kappa\),
+  and thus holds for all cardinals less than \(\aleph_\omega\).
+  It's consistent that \(\alcompSP{\aleph_\omega}\) fails, but
+  there must always be a winning \(2\)-Markov strategy for the second
+  player in the Menger game on \(\oneptlind{\omega_\omega}\).
 \end{abstract}
@@
 
-  Weakening to the continuum hypothesis, we have an obvious consequence.
+  Weakening to the continuum hypothesis, we see an obvious consequence.
 
   \begin{corollary}[\(CH\)]
-    \(\alcompSP{\aleph_2}\), but \(\neg\alcompS{\aleph_2}\).
+    \(\alcompSP{\mf c^+}\), but \(\neg\alcompS{\mf c^+}\).
   \end{corollary}
@@
 
-  % TODO: read through Alan's proofs and fit to rest of document
+  % Alan's results
 

### 2015-12-08 articles/almost-compatible-functions-and-topological-games/article.tex
updated proof from Alan

@@
 
-  \begin{theorem}
-    There exists a model of \(ZFC\) for which \(\neg\alcompSP{\aleph_\omega}\).
+\begin{theorem} It follows from the existence of a $2$-huge cardinal
+that there is a model of $ZFC$ for which $\lnot \mathcal A'(\aleph_{\omega})$.
 \end{theorem}
@@
             The interested reader will want to know that it is shown in
-          \cite{MR1045371} that if $\kappa$ is a 2-huge cardinal and $j$ is the 2-huge
+            \cite{MR1045371} that if $\kappa$ is a 2-huge cardinal
+            and $j$ is the 2-huge
             embedding with critical point $\kappa$, then with
@@
             $(\lambda^{+\omega+1},\lambda^{+\omega})\rlap{$\rightarrow$}\,{\rightarrow}
-          (\kappa^{+\omega+1},\kappa^{+\omega})$ holds.
+            (\kappa^{+\omega+1},\kappa^{+\omega})$ holds. There is no loss of
+            generality to  also assume that GCH holds in this model.
+
             \bigskip
@@
             ordering. For convenience we may assume that $h_\xi(n) \geq
-          \lambda^{+n}$ for all $\xi$ and all $n$.  If $P$ is any poset of
-          cardinality less than $\lambda^{+\omega}$, then in the forcing
+            \lambda^{+n}$ for all $\xi$ and all $n$. For each integer
+             $m$ the cofinality of the mod finite ordering on
+             $\Pi\{ \lambda^{+n+1} : m< n\in \omega\}$
+            is the same as it is for the entire product
+             $\Pi\{ \lambda^{+n+1} : n\in \omega\}$. If $P$
+            is any poset of cardinality less than
+             $\lambda^{+m}$ then, in the forcing extension by $P$,
+            every function in
+             $\Pi\{ \lambda^{+n+1} : m< n\in \omega\}$ is bounded
+            above by a ground model function.
+            It therefore
+            follows easily that  in the forcing
             extension by $P$,  the sequence
@@
              $\mathbb P_1$ has cardinality $\lambda$. We treat
-          $\mathbb P_1$ as containing $\mathbb P_0$
+            $\mathbb P*\mathbb P_1$ as containing $\mathbb P_0$
             as a subposet by identifying each $(p_0,1)$ with $p_0$.
@@
             \bigskip
+
+            \newpage
 
@@
              $(\lambda,R_2)$ is isomorphic to $\mathbb P_0*\mathbb P_1$.
-          Let $\psi$ be the poset isomorphism from $\lambda$ to
+            Let $\psi$ be the poset isomorphism from $(\lambda,R_2)$ to
              $\mathbb P_0*\mathbb P_1$.
@@
 
-          \begin{proof}[Proof of Claim]
+            \bgroup
+            \def\proofname{Proof of Claim:\/}
+
+            \begin{proof}
             Suppose  our originally supplied $N$ fails the conclusion of the
@@
             Skolem closure $\mathop{Hull}(N\cup \beta_0, M)$.  A little informally
-          (in that we have to formalize the enumeration of formulas)
-          let $\{\varphi_n : n\in \omega\}$ is the enumeration of all formulas
+            (in that we have to formalize the enumeration of formulas as per
+            G\"odel coding)
+            let $\{\varphi_n : n\in \omega\}$ be an enumeration of all formulas
             in the language $L$, and let  $\ell_n$ be the minimal integer such
@@
 
+            \egroup
+
             We use the elementarity of
@@
 
-           Since  $\mathfrak c < \kappa^{+\omega+1}$ there
+            Now we need a result from Shelah's pcf theory which
+            is proven in  Jech \cite[24.9]{MR1940513}.
+             Since  $\aleph_1=\mathfrak c < \kappa^{+\omega+1}$ there
               is a function $\langle \varrho_n : n\in \omega\rangle$
@@
                $\{ h_\xi : \xi \in N\}$ is unbounded mod finite
-             in $\Pi_n \varrho_n$ (by Shelah's pcf theory).
-             This is in Jech somewhere.
-             For each $n$, $\rho_n \leq \sup(N\cap \lambda^{+n+2})$.
-
-             Since $\mathbb P_0$ has cardinality less than $|N|=\kappa^{+\omega+1}$,
-              the sequence $\{ h_\xi : \xi \in \Lambda\cap N\}$ remains unbounded
+               in $\Pi_n \varrho_n$
+               For each $n$, $\varrho_n \leq \sup(N\cap \lambda^{+n+2})$.
+                  Since $\mathbb P_0$ has cardinality $\kappa^{+\omega}$,
+            and so less than $|N|=\kappa^{+\omega+1}$, a standard argument
+            (analogous to the fact that adding a Cohen real does
+             not add a dominating real)
+             shows that    the sequence $\{ h_\xi : \xi \in \Lambda\cap N\}$ remains
+             unbounded
                 mod finite in $\Pi_n \varrho_n$ (and in
-               $\Pi_n (\varrho_n\cap N)$).  Now pass to the extension by
+                 $\Pi_n (\varrho_n\cap N)$).
+
+            Now pass to the extension by
                   $G\cap \mathbb P_0$ and let $H$ be the function
                    $\operatorname{val}_{G}(\dot H)$, and we recall
-                 that $f_{\zeta_\xi}(h_\xi(n)) = H(n)$ for all $n\in \omega$.
+                   that $f_{\zeta_\xi}(h_\xi(n)) = H(n)$ for all $n\in \omega$
+            and $\xi\in \Lambda$.
              Now pass to the full extension $V[G]$ and again, since
@@
                the family $\{ h_\xi : \xi \in \Lambda\cap N\}$ is still
-             unbounded in $\Pi_n (\varrho_n \cap N)$. We let
+               unbounded in $\Pi_n (\varrho_n \cap N)$ (no new elements
+            were added). We let
                $A$ be the countable set $N\cap \lambda^{+\omega}$,

### 2015-12-10 articles/almost-compatible-functions-and-topological-games/article.tex
begin cleaning omega_2 cohen reals argument, including deflation of math mode

@@
   But \(CH\) is not required to have \(\alcompS{\aleph_2}\) fail.
-
-  % Alan's results
+  We take the following lemma from Kunen.
 
@@
     In addition, for each $\operatorname{Fn}(\omega_2,2)$-name $\dot A$
-            of a subset of $\omega$ (treat as a subset of $\omega\times
-            \operatorname{Fn}(\omega_2,2) $),
+    for $A\subseteq\omega$ (abusing notation and letting \(n\) represent
+    its own $\operatorname{Fn}(\omega_2,2)$-name and
+    $\operatorname{Fn}(\omega_2\setminus \mu, 2)$-name),
     there is a canonical name $\dot A(G_\mu)$ where,
@@
     (n,p)\in \dot A\ \ \mbox{and} \ \ p\restriction \mu\in G_\mu\}$$
-            and we get that the valuation of $\dot A(G_\mu)$ by the tail
+    and the valuation of $\dot A(G_\mu)$ by the tail
     of the generic, $G_{\omega_2\setminus \mu}$, is the same as
@@
 
+ \begin{lemma}[\cite{MR597342}]
+    Assume that \(G\subset \operatorname{Fn}(\omega_2,2)\) is a generic filter,
+    and let \(\mu\in \omega_2\). Then the final model \(V[G]\) can be
+    regarded as forcing  with \(\operatorname{Fn}(\omega_2\setminus \mu,
+    2)\) over the model \(V[G_\mu]\).
+    In addition, for each \(\operatorname{Fn}(\omega_2,2)\)-name \(\dot A\)
+    for \(A\subseteq\omega\) (abusing notation and letting \(n\) represent
+    its own \(\operatorname{Fn}(\omega_2,2)\)-name and
+    \(\operatorname{Fn}(\omega_2\setminus \mu, 2)\)-name),
+    there is a canonical name \(\dot A(G_\mu)\) where,
+    \[\dot A(G_\mu) = \{ (n,p\restriction [\mu,\omega_2))  :
+    (n,p)\in \dot A\ \ \mbox{and} \ \ p\restriction \mu\in G_\mu\}\]
+    and the valuation of \(\dot A(G_\mu)\) by the tail
+    of the generic, \(G_{\omega_2\setminus \mu}\), is the same as
+    the valuation of \(\dot A\) by the full generic.
+  \end{lemma}
+
   \begin{theorem}
-              There exists a model of \(ZFC\) for which \(\mf c=\aleph_2\)
+    It follows from the consistency of \(ZFC\) that
+    there exists a model of \(ZFC\) for which \(\mf c=\aleph_2\)
     and \(\neg\alcompS{\aleph_2}\).
@@
   \begin{proof}
-            The forcing poset is $\operatorname{Fn}(\omega_2, 2)$.
-            Let $\{ \dot f_{A} : A\in [\omega_2]^\omega\}$ be a family of
-            names such that $\dot f_{A}$ is a one-to-one function from $A$ into
-            $\omega$. It suffices to only consider sets $A$ from the ground
-            model.
-            \bigskip
-
-            Put all the lemma  stuff in an elementary submodel $M$ of the universe
-            (technically of $H(\kappa)$,  or of $V_\kappa$,
-             for some large $\kappa$). Standard methods says that we can assume that
-             $|M|=\omega_1 =\mathfrak c$ and that $M^\omega\subset M$ (which means
-             that every countable subset of $M$ is a member of $M$).
-            \bigskip
-
-            Let $\lambda = M\cap \omega_2$ (same as the supremum of $M\cap
-            \omega_2$). Consider the name  $\dot f_{[\lambda,\lambda+\omega)}$.
-            What is such a name?  We can assume that it is a set of pairs
-             of the form $( (\lambda+k,m), p)$ where $p\in \mathop{Fn}(\omega_2,
-             2)$ and, of course, $k,m\in \omega$. This is (almost) equivalent to
+    The forcing poset is \(\operatorname{Fn}(\omega_2, 2)\).
+    Let \(\{ \dot f_{A} : A\in [\omega_2]^\omega\}\) be a family of
+    names such that \(f_{A}\) is a one-to-one function from \(A\) into
+    \(\omega\) in the ground model. Let \(M\) be an elementary submodel
+    of the universe such that
+    \(|M|=\omega_1 =\mathfrak c\) and \(M^\omega\subset M\).
+
+    Let \(\lambda = M\cap \omega_2=\sup(M\cap\omega_2)\).
+    Consider the name
+    \[
+      \dot f_{[\lambda,\lambda+\omega)}
+        =
+      \{
+        ( (\lambda+k,m), p)
+      :
+        p\in \mathop{Fn}(\omega_2,2);k,m\in \omega
+      \}
+    \]
+    This is (almost) equivalent to
              saying
-             that $p$ forces that $\dot f_{[\lambda,\lambda+\omega)}(\lambda+k) =
-             m$. We don't take all such $p$, in fact for each $k,m$ it is enough
+             that \(p\) forces that \(\dot f_{[\lambda,\lambda+\omega)}(\lambda+k) =
+             m\). We don't take all such \(p\), in fact for each \(k,m\) it is enough
             to take a
-             countable set of such $p$ to get an equivalent name
-             (Kunen calls it a nice name if we take, for each $k,m$ an
+             countable set of such \(p\) to get an equivalent name
+             (Kunen calls it a nice name if we take, for each \(k,m\) an
             antichain that is maximal among such conditions).
-            Given any such name $\dot f$, let $\operatorname{supp}(\dot f)$
-            denote the union of the domains of conditions $p$ appearing in the
+            Given any such name \(\dot f\), let \(\operatorname{supp}(\dot f)\)
+            denote the union of the domains of conditions \(p\) appearing in the
             name.
 
-             Also let $Y$ equal $\operatorname{supp}(\dot
-             f_{[\lambda,\lambda+\omega)})\setminus \lambda$.
-             Let $\delta$ denote the order type of
-             $Y$ and let the 2-parameter notation
-             $\varphi_{\mu,\lambda}$ be the order-preserving function from
-            $\mu\cup Y$ onto  the ordinal $\mu+\delta$.  This lifts canonically to
-            an order-preserving bijection $\varphi_{\mu,\lambda}:
+             Also let \(Y\) equal \(\operatorname{supp}(\dot
+             f_{[\lambda,\lambda+\omega)})\setminus \lambda\).
+             Let \(\delta\) denote the order type of
+             \(Y\) and let the 2-parameter notation
+             \(\varphi_{\mu,\lambda}\) be the order-preserving function from
+            \(\mu\cup Y\) onto  the ordinal \(\mu+\delta\).  This lifts canonically to
+            an order-preserving bijection \(\varphi_{\mu,\lambda}:
             \operatorname{Fn}(\mu\cup Y,2) \mapsto
-            \operatorname{Fn}(\mu+\delta,2)$.
+            \operatorname{Fn}(\mu+\delta,2)\).
             Similarly, we make sense of the name
-             $\varphi_{\mu,\lambda}(\dot f_{[\lambda,\lambda+\omega)})$, call it $F_M$.
-            Here simply, for each tuple $(~(k,m)~, p)\in \dot
-            f_{[\lambda,\lambda+\omega)}$,
-             we have that $(~(k,m)~,\varphi_{\mu,\lambda}(p))$ is in $F_M$.
-            Again, let $\varphi_{\mu,\lambda}(\dot f_{[\lambda,\lambda+\omega)})$
-            be interpreted in the above sense as giving $F_M$ (which is an element
-            of $M$).  Note that we do not regard $\delta$ as fixed here, but
-            rather simply depending on the $\operatorname{supp}(\dot
-            f_{[\lambda,\lambda+\omega)})$ described above. Other values
-            replacing $\lambda>\mu$ will result in their own set $Y$
-            and canonical map $\varphi_{\mu,\lambda}$; but one thing we do have to
-            assume (or arrange) for other values $\alpha$ replacing $\lambda$
-            is that $\operatorname{supp}(\dot f_{[\alpha,\alpha+\omega)})$
+             \(\varphi_{\mu,\lambda}(\dot f_{[\lambda,\lambda+\omega)})\), call it \(F_M\).
+            Here simply, for each tuple \((~(k,m)~, p)\in \dot
+            f_{[\lambda,\lambda+\omega)}\),
+             we have that \((~(k,m)~,\varphi_{\mu,\lambda}(p))\) is in \(F_M\).
+            Again, let \(\varphi_{\mu,\lambda}(\dot f_{[\lambda,\lambda+\omega)})\)
+            be interpreted in the above sense as giving \(F_M\) (which is an element
+            of \(M\)).  Note that we do not regard \(\delta\) as fixed here, but
+            rather simply depending on the \(\operatorname{supp}(\dot
+            f_{[\lambda,\lambda+\omega)})\) described above. Other values
+            replacing \(\lambda>\mu\) will result in their own set \(Y\)
+            and canonical map \(\varphi_{\mu,\lambda}\); but one thing we do have to
+            assume (or arrange) for other values \(\alpha\) replacing \(\lambda\)
+            is that \(\operatorname{supp}(\dot f_{[\alpha,\alpha+\omega)})\)
             intersected with
-            $\alpha$ is contained in $\mu$.
-
-            Now the object $F_M$ is an
-            element of $M$, and $M$ believes this statement is true:
-            $$
+            \(\alpha\) is contained in \(\mu\).
+
+            Now the object \(F_M\) is an
+            element of \(M\), and \(M\) believes this statement is true:
+            \[
             (\forall \beta\in\omega_2)~ (\exists \beta<\lambda\in \omega_2)~~~
@@
             \cap \lambda\subset \mu \ \ \mbox{and}\ \
-            F_M = \varphi_{\mu,\lambda}(\dot f_{[\lambda,\lambda+\omega)})$$
+            F_M = \varphi_{\mu,\lambda}(\dot f_{[\lambda,\lambda+\omega)})\]
 
             But now, this  means that,
-            not only is there  an $\alpha\in M$,
-            $ F_M = \varphi_{\mu,\alpha}(\dot f_{[\alpha,\alpha+\omega)})$
+            not only is there  an \(\alpha\in M\),
+            \( F_M = \varphi_{\mu,\alpha}(\dot f_{[\alpha,\alpha+\omega)})\)
             but also that there is an increasing sequence
-             $\{\alpha_\xi : \xi  \in \omega_1\}\subset \lambda$ of
-             such $\alpha$'s satisfying that, for each $\xi$
-            we have that $\operatorname{supp}(\dot
-            f_{[\alpha_\xi,\alpha_\xi+\omega)})$ is contained in $\alpha_{\xi+1}$.
+             \(\{\alpha_\xi : \xi  \in \omega_1\}\subset \lambda\) of
+             such \(\alpha\)'s satisfying that, for each \(\xi\)
+            we have that \(\operatorname{supp}(\dot
+            f_{[\alpha_\xi,\alpha_\xi+\omega)})\) is contained in \(\alpha_{\xi+1}\).
 
             Choose such a sequence.
-             This means that if we let $A = \bigcup_{n>0} [\alpha_n,\alpha_n+\omega)$ we
-             have the name $\dot f_A$ in $M$. This then means that all
-             the $( (\beta,m) , p)$ appearing in $\dot f_A$ have the property
-             that $\mathop{dom}(p)$ is contained in $M$.
-            There is, within $M$, a name $\dot g$ satisfying that
-             $\dot f_A(\alpha_n+k) = \dot f_{[\alpha_n,\alpha_n+\omega)}(\alpha_n+k)$
-            for all $k >\dot g(n)$.
+             This means that if we let \(A = \bigcup_{n>0} [\alpha_n,\alpha_n+\omega)\) we
+             have the name \(\dot f_A\) in \(M\). This then means that all
+             the \(( (\beta,m) , p)\) appearing in \(\dot f_A\) have the property
+             that \(\mathop{dom}(p)\) is contained in \(M\).
+            There is, within \(M\), a name \(\dot g\) satisfying that
+             \(\dot f_A(\alpha_n+k) = \dot f_{[\alpha_n,\alpha_n+\omega)}(\alpha_n+k)\)
+            for all \(k >\dot g(n)\).
 
@@
 
-            We now apply the above Lemma using $\mu = \mu_0$ and we are now
-            working in the extension $V[G_\mu]$. We will abuse the notation
-            and use $\dot f_{[\alpha_n,\alpha_n+\omega)}$ instead of
-              $\dot f_{[\alpha_n,\alpha_n+\omega)}(G_{\mu})$ as defined in
+            We now apply the above Lemma using \(\mu = \mu_0\) and we are now
+            working in the extension \(V[G_\mu]\). We will abuse the notation
+            and use \(\dot f_{[\alpha_n,\alpha_n+\omega)}\) instead of
+              \(\dot f_{[\alpha_n,\alpha_n+\omega)}(G_{\mu})\) as defined in
               the Lemma.
             We work for a contradiction. Something special has now happened,
-             namely,  the supports of the names $\{
-            \dot f_{[\alpha_n, \alpha_n+\omega)} :  0< n<\omega\}$ are pairwise disjoint
+             namely,  the supports of the names \(\{
+            \dot f_{[\alpha_n, \alpha_n+\omega)} :  0< n<\omega\}\) are pairwise disjoint
             and also disjoint from the support of the name
-             $\dot f_{[\lambda,\lambda+\omega)}$ (under the same convention about
-             $G_\mu$.  And not only that, these names are pairwise isomorphic (in
-             the way that they all map to $F_M$).
+             \(\dot f_{[\lambda,\lambda+\omega)}\) (under the same convention about
+             \(G_\mu\).  And not only that, these names are pairwise isomorphic (in
+             the way that they all map to \(F_M\)).
 
@@
 
-            Since $A$ is disjoint from $[\lambda,\lambda+\omega)$,
-            there must be an integer $\ell$
+            Since \(A\) is disjoint from \([\lambda,\lambda+\omega)\),
+            there must be an integer \(\ell\)
             together with a condition
-             $q\in \mathop{Fn}(\omega_2\setminus \mu,2)$ satisfying that for all
-             $n>\ell$ , $q$ forces that
+             \(q\in \mathop{Fn}(\omega_2\setminus \mu,2)\) satisfying that for all
+             \(n>\ell\) , \(q\) forces that
 
             \centerline{
-             ``if $k>\dot g(n)$ (since  $\alpha_n+k\in A$) then
-             $\dot f_{[\alpha_n,\alpha_n+\omega)}(\alpha_n+k) \neq
-            \dot f_{[\lambda,\lambda+\omega)}(\lambda +k)$''.}
-
-            Choose $n$ large enough so that $\mathop{dom}(q) \cap [\alpha_n,
-            \mu_{n+1})$ is
+             ``if \(k>\dot g(n)\) (since  \(\alpha_n+k\in A\)) then
+             \(\dot f_{[\alpha_n,\alpha_n+\omega)}(\alpha_n+k) \neq
+            \dot f_{[\lambda,\lambda+\omega)}(\lambda +k)\)''.}
+
+            Choose \(n\) large enough so that \(\mathop{dom}(q) \cap [\alpha_n,
+            \mu_{n+1})\) is
             empty.
-             Choose $q_1<q\restriction \lambda$ (in $M$) so that
-            $$ \varphi_{\mu,\alpha_n}(q_1\restriction \operatorname{supp}(
+             Choose \(q_1<q\restriction \lambda\) (in \(M\)) so that
+            \[ \varphi_{\mu,\alpha_n}(q_1\restriction \operatorname{supp}(
              \dot f_{[\alpha_n,\alpha_n+\omega)}) =
             \varphi_{\mu,\lambda}(q\restriction \operatorname{supp}(
-             \dot f_{[\lambda,\lambda+\omega)}) $$
-            and then (again in $M$) choose $q_2 < q_1$
+             \dot f_{[\lambda,\lambda+\omega)}) \]
+            and then (again in \(M\)) choose \(q_2 < q_1\)
             so that it both forces a value
-             $L$ on $\ell+\dot g(n)$
-            and subsequently forces a value $m$ on
-             $\dot f_{[\alpha_n, \alpha_n+\omega)}(\alpha_n+L+1)$.
+             \(L\) on \(\ell+\dot g(n)\)
+            and subsequently forces a value \(m\) on
+             \(\dot f_{[\alpha_n, \alpha_n+\omega)}(\alpha_n+L+1)\).
             But now, again calculate
-            $$ q_3 = \varphi_{\mu,\lambda}^{-1} \circ \varphi_{\mu,\alpha_n}
+            \[ q_3 = \varphi_{\mu,\lambda}^{-1} \circ \varphi_{\mu,\alpha_n}
             (q_2\restriction \operatorname{supp}(\dot
-            f_{[\alpha_n,\alpha_n+\omega)}))$$
-            and, by the isomorphisms, we have that $q_3$ forces that
-             $\dot f_{[\lambda,\lambda+\omega)}(\lambda+L+1) = m$.
+            f_{[\alpha_n,\alpha_n+\omega)}))\]
+            and, by the isomorphisms, we have that \(q_3\) forces that
+             \(\dot f_{[\lambda,\lambda+\omega)}(\lambda+L+1) = m\).
 
             Technically (or with more care)  all of this is taking place in the
-            poset $\operatorname{Fn}(\omega_2\setminus \mu,2)$ and this means
-            that $q_3$ and $q$ are all compatible with each other.
+            poset \(\operatorname{Fn}(\omega_2\setminus \mu,2)\) and this means
+            that \(q_3\) and \(q\) are all compatible with each other.
 
@@
             the bouncing ball: it suffices to consider
-             $q(\beta)=e$ and to assume that $q_3(\beta)$ is defined.
-            Since $q_3(\beta)$ is defined, we have that
-            there is a  $\beta'\in\mathop{dom}(q_2)$ such that $
-             \varphi_{\mu,\lambda}(\beta) = \varphi_{\mu,\alpha_n}(\beta')$,
-            and that $q_3(\beta) = q_2(\beta')$.
-            But, by definition of $q_1$, $\beta'\in\mathop{dom}(q_1)$
-            and even  that $q_1(\beta') = q(\beta)$.
-             Then, since $q_2<q_1$, we have that $q_2(\beta')=q_1(\beta') =
-             q(\beta)$. This completes the circle that $q_3(\beta) = q(\beta)$.
+             \(q(\beta)=e\) and to assume that \(q_3(\beta)\) is defined.
+            Since \(q_3(\beta)\) is defined, we have that
+            there is a  \(\beta'\in\mathop{dom}(q_2)\) such that \(
+             \varphi_{\mu,\lambda}(\beta) = \varphi_{\mu,\alpha_n}(\beta')\),
+            and that \(q_3(\beta) = q_2(\beta')\).
+            But, by definition of \(q_1\), \(\beta'\in\mathop{dom}(q_1)\)
+            and even  that \(q_1(\beta') = q(\beta)\).
+             Then, since \(q_2<q_1\), we have that \(q_2(\beta')=q_1(\beta') =
+             q(\beta)\). This completes the circle that \(q_3(\beta) = q(\beta)\).
             \bigskip
 
-            Finally, our contradiction is that $q_3\cup q_2\cup q$
+            Finally, our contradiction is that \(q_3\cup q_2\cup q\)
             forces that
-             $k=L+1$ violates the quoted statement above.
+             \(k=L+1\) violates the quoted statement above.
             \end{proof}

### 2015-12-11 articles/almost-compatible-functions-and-topological-games/article.tex
partial edits of omega_2 cohen reals proof

@@
  \begin{lemma}[\cite{MR597342}]
-    Assume that $G\subset \operatorname{Fn}(\omega_2,2)$ is a generic filter,
-    and let $\mu\in \omega_2$. Then the final model $V[G]$ can be
-    regarded as forcing  with $\operatorname{Fn}(\omega_2\setminus \mu,
-    2)$ over the model $V[G_\mu]$.
-    In addition, for each $\operatorname{Fn}(\omega_2,2)$-name $\dot A$
-    for $A\subseteq\omega$ (abusing notation and letting \(n\) represent
-    its own $\operatorname{Fn}(\omega_2,2)$-name and
-    $\operatorname{Fn}(\omega_2\setminus \mu, 2)$-name),
-    there is a canonical name $\dot A(G_\mu)$ where,
-    $$\dot A(G_\mu) = \{ (n,p\restriction [\mu,\omega_2))  :
-    (n,p)\in \dot A\ \ \mbox{and} \ \ p\restriction \mu\in G_\mu\}$$
-    and the valuation of $\dot A(G_\mu)$ by the tail
-    of the generic, $G_{\omega_2\setminus \mu}$, is the same as
-    the valuation of $\dot A$ by the full generic.
-  \end{lemma}
-
- \begin{lemma}[\cite{MR597342}]
     Assume that \(G\subset \operatorname{Fn}(\omega_2,2)\) is a generic filter,
     and let \(\mu\in \omega_2\). Then the final model \(V[G]\) can be
-    regarded as forcing  with \(\operatorname{Fn}(\omega_2\setminus \mu,
-    2)\) over the model \(V[G_\mu]\).
-    In addition, for each \(\operatorname{Fn}(\omega_2,2)\)-name \(\dot A\)
-    for \(A\subseteq\omega\) (abusing notation and letting \(n\) represent
-    its own \(\operatorname{Fn}(\omega_2,2)\)-name and
-    \(\operatorname{Fn}(\omega_2\setminus \mu, 2)\)-name),
-    there is a canonical name \(\dot A(G_\mu)\) where,
-    \[\dot A(G_\mu) = \{ (n,p\restriction [\mu,\omega_2))  :
-    (n,p)\in \dot A\ \ \mbox{and} \ \ p\restriction \mu\in G_\mu\}\]
-    and the valuation of \(\dot A(G_\mu)\) by the tail
-    of the generic, \(G_{\omega_2\setminus \mu}\), is the same as
-    the valuation of \(\dot A\) by the full generic.
+    regarded as forcing with
+    \(\operatorname{Fn}(\omega_2\setminus \mu, 2)\) over the model \(V[G_\mu]\).
+    Let \(\dot n,\ddot n\) be a
+    \(\operatorname{Fn}(\omega_2,2)\)-,
+    \(\operatorname{Fn}(\omega_2\setminus\mu,2)\)-name respectively for each
+    \(n<\omega\). Then for each \(\operatorname{Fn}(\omega_2,2)\)-name \(\dot A\)
+    for \(A\subseteq\omega\), there is a canonical
+    \(\operatorname{Fn}(\omega_2\setminus \mu, 2)\)-name
+    \[
+      \ddot A
+        =
+      \{
+        (\ddot n,p\rest [\mu,\omega_2))
+      :
+        (\dot n,p)\in \dot A
+      \}
+    \]
+    which satisfies
+    \(
+      A
+        =
+      \operatorname{val}(\dot A,G)
+        =
+      \operatorname{val}(\ddot A,G_\mu)
+    \).
   \end{lemma}
@@
   \begin{proof}
-    The forcing poset is \(\operatorname{Fn}(\omega_2, 2)\).
+    The forcing poset is \(\mb P=\operatorname{Fn}(\omega_2, 2)\).
     Let \(\{ \dot f_{A} : A\in [\omega_2]^\omega\}\) be a family of
-    names such that \(f_{A}\) is a one-to-one function from \(A\) into
+    \(\mb P\)-names such that \(f_{A}\) is a one-to-one function from \(A\) into
     \(\omega\) in the ground model. Let \(M\) be an elementary submodel
-    of the universe such that
+    of the universe containing \(\mb P\) such that
     \(|M|=\omega_1 =\mathfrak c\) and \(M^\omega\subset M\).
 
-    Let \(\lambda = M\cap \omega_2=\sup(M\cap\omega_2)\).
-    Consider the name
-    \[
+    Let \(\lambda\) be the ordinal \(M\cap \omega_2\).
+    We may assume
+    \(
       \dot f_{[\lambda,\lambda+\omega)}
@@
       \{
-        ( (\lambda+k,m), p)
+        ((\lambda+k_p,m_p)^\cdot, p)
       :
-        p\in \mathop{Fn}(\omega_2,2);k,m\in \omega
+        p\in C
       \}
-    \]
-    This is (almost) equivalent to
-             saying
-             that \(p\) forces that \(\dot f_{[\lambda,\lambda+\omega)}(\lambda+k) =
-             m\). We don't take all such \(p\), in fact for each \(k,m\) it is enough
-            to take a
-             countable set of such \(p\) to get an equivalent name
-             (Kunen calls it a nice name if we take, for each \(k,m\) an
-            antichain that is maximal among such conditions).
-            Given any such name \(\dot f\), let \(\operatorname{supp}(\dot f)\)
-            denote the union of the domains of conditions \(p\) appearing in the
-            name.
-
-             Also let \(Y\) equal \(\operatorname{supp}(\dot
-             f_{[\lambda,\lambda+\omega)})\setminus \lambda\).
-             Let \(\delta\) denote the order type of
-             \(Y\) and let the 2-parameter notation
-             \(\varphi_{\mu,\lambda}\) be the order-preserving function from
-            \(\mu\cup Y\) onto  the ordinal \(\mu+\delta\).  This lifts canonically to
-            an order-preserving bijection \(\varphi_{\mu,\lambda}:
-            \operatorname{Fn}(\mu\cup Y,2) \mapsto
-            \operatorname{Fn}(\mu+\delta,2)\).
-            Similarly, we make sense of the name
-             \(\varphi_{\mu,\lambda}(\dot f_{[\lambda,\lambda+\omega)})\), call it \(F_M\).
-            Here simply, for each tuple \((~(k,m)~, p)\in \dot
-            f_{[\lambda,\lambda+\omega)}\),
-             we have that \((~(k,m)~,\varphi_{\mu,\lambda}(p))\) is in \(F_M\).
-            Again, let \(\varphi_{\mu,\lambda}(\dot f_{[\lambda,\lambda+\omega)})\)
-            be interpreted in the above sense as giving \(F_M\) (which is an element
-            of \(M\)).  Note that we do not regard \(\delta\) as fixed here, but
-            rather simply depending on the \(\operatorname{supp}(\dot
-            f_{[\lambda,\lambda+\omega)})\) described above. Other values
-            replacing \(\lambda>\mu\) will result in their own set \(Y\)
-            and canonical map \(\varphi_{\mu,\lambda}\); but one thing we do have to
-            assume (or arrange) for other values \(\alpha\) replacing \(\lambda\)
-            is that \(\operatorname{supp}(\dot f_{[\alpha,\alpha+\omega)})\)
-            intersected with
-            \(\alpha\) is contained in \(\mu\).
+    \)
+    for some countable \(C\subseteq\operatorname{Fn}(\omega_2,\omega)\).
+    Let
+    \(
+      \operatorname{supp}(\dot f_{[\lambda,\lambda+\omega)})
+        =
+      \bigcup_{p\in C}\operatorname{dom} p
+    \).
+
+    Let \(\delta_\lambda\) denote the order type of
+    \(\operatorname{supp}(\dot f_{[\lambda,\lambda+\omega)})\setminus \lambda\),
+    and for \(\mu\leq\lambda\) let \(\varphi_{\mu,\lambda}'\) be the
+    order-preserving bijection from
+    \(
+      \mu\cup
+      \left(\operatorname{supp}(\dot f_{[\lambda,\lambda+\omega)})
+        \setminus
+      \lambda\right)
+    \)
+    onto the ordinal \(\mu+\delta_\lambda\).
+    This lifts canonically to an order-preserving bijection
+    \(
+      \varphi_{\mu,\lambda}
+        :
+      \operatorname{Fn}(\mu\cup Y,2)
+        \to
+      \operatorname{Fn}(\mu+\delta,2)
+    \).
+
+    Consider the \(\mb P\)-name
+    \(
+      F_M
+        =
+      \{
+        ((\lambda+k_p,m_p)^\cdot,\varphi_{\mu,\lambda}(p))
+      :
+        ((\lambda+k_p,m_p)^\cdot,p)\in\dot f_A
+      \}
+    \).
+
+    % Other values
+    %         replacing \(\lambda>\mu\) will result in their own set \(Y\)
+    %         and canonical map \(\varphi_{\mu,\lambda}\); but one thing we do have to
+    %         assume (or arrange) for other values \(\alpha\) replacing \(\lambda\)
+    %         is that \(\operatorname{supp}(\dot f_{[\alpha,\alpha+\omega)})\)
+    %         intersected with
+    %         \(\alpha\) is contained in \(\mu\).
 

### 2016-01-20 articles/almost-compatible-functions-and-topological-games/article.tex
misc work on gamma functions notes and alcomp preprint

@@
  \begin{lemma}[\cite{MR597342}]
-    Assume that \(G\subset \operatorname{Fn}(\omega_2,2)\) is a generic filter,
-    and let \(\mu\in \omega_2\). Then the final model \(V[G]\) can be
+    Assume that \(G\subset \operatorname{Fn}(\omega_2,2)\) is a generic filter
+    over a model \(M\),
+    and let \(\mu\in \omega_2\). Then the generic extension \(M[G]\) can be
     regarded as forcing with
-    \(\operatorname{Fn}(\omega_2\setminus \mu, 2)\) over the model \(V[G_\mu]\).
+    \(\operatorname{Fn}(\omega_2\setminus \mu, 2)\) over the model \(M[G_\mu]\).
     Let \(\dot n,\ddot n\) be a
@@
   \begin{theorem}
-    It follows from the consistency of \(ZFC\) that
-    there exists a model of \(ZFC\) for which \(\mf c=\aleph_2\)
+    There exists a model of \(ZFC\) for which \(\mf c=\aleph_2\)
     and \(\neg\alcompS{\aleph_2}\).
@@
     Let \(\{ \dot f_{A} : A\in [\omega_2]^\omega\}\) be a family of
-    \(\mb P\)-names such that \(f_{A}\) is a one-to-one function from \(A\) into
-    \(\omega\) in the ground model. Let \(M\) be an elementary submodel
-    of the universe containing \(\mb P\) such that
-    \(|M|=\omega_1 =\mathfrak c\) and \(M^\omega\subset M\).
-
-    Let \(\lambda\) be the ordinal \(M\cap \omega_2\).
-    We may assume
+    \(\mb P\)-names such that \(f_{A}\) is a one-to-one function from \(A\)
+    into \(\omega\) in the ground model. Let \(M\) be an elementary submodel
+    of \(ZFC+CH\) containing all its countable subsets, containing \(\mb P\),
+    and satisfying \(|M|=\omega_1 =\mathfrak c\).
+
+    Let \(\lambda\) be the ordinal \(M\cap \omega_2\). For
+    \(\alpha\leq\lambda\) we may assume
     \(
-      \dot f_{[\lambda,\lambda+\omega)}
+      \dot f_{[\alpha,\alpha+\omega)}
         =
       \{
-        ((\lambda+k_p,m_p)^\cdot, p)
+        ((\alpha+k_p,m_p)^\cdot, p)
       :
-        p\in C
+        p\in C_\alpha
       \}
     \)
-    for some countable \(C\subseteq\operatorname{Fn}(\omega_2,\omega)\).
+    for some countable \(C_\alpha\subseteq\operatorname{Fn}(\omega_2,\omega)\).
     Let
     \(
-      \operatorname{supp}(\dot f_{[\lambda,\lambda+\omega)})
-        =
-      \bigcup_{p\in C}\operatorname{dom} p
+      \operatorname{supp}(\dot f_{[\alpha,\alpha+\omega)})
+        =
+      \bigcup_{p\in C_\alpha}\operatorname{dom} p
     \).
 
-    Let \(\delta_\lambda\) denote the order type of
-    \(\operatorname{supp}(\dot f_{[\lambda,\lambda+\omega)})\setminus \lambda\),
-    and for \(\mu\leq\lambda\) let \(\varphi_{\mu,\lambda}'\) be the
-    order-preserving bijection from
+    For each \(\alpha\leq\lambda\),
+    let \(\delta_{\alpha}\) denote the order type of
+    \(\operatorname{supp}(\dot f_{[\alpha,\alpha+\omega)})\setminus \alpha\),
+    and when \(\mu\leq\alpha\) and
+    \(
+      \operatorname{supp}(\dot f_{[\alpha,\alpha+\omega)})
+        \cap
+      \alpha
+        \subseteq
+      \mu
+    \)
+    let \(\varphi'_{\mu,\alpha}\) be the order-preserving bijection from
     \(
       \mu\cup
-      \left(\operatorname{supp}(\dot f_{[\lambda,\lambda+\omega)})
+      \left(\operatorname{supp}(\dot f_{[\alpha,\alpha+\omega)})
         \setminus
-      \lambda\right)
+      \alpha\right)
     \)
-    onto the ordinal \(\mu+\delta_\lambda\).
+    onto the ordinal \(\mu+\delta_\alpha\).
     This lifts canonically to an order-preserving bijection
     \(
-      \varphi_{\mu,\lambda}
+      \varphi_{\mu,\alpha}
         :
-      \operatorname{Fn}(\mu\cup Y,2)
+      \operatorname{Fn}(\mu\cup
+        \left(\operatorname{supp}(\dot f_{[\alpha,\alpha+\omega)})
+          \setminus
+        \alpha\right)
+      ,2)
         \to
-      \operatorname{Fn}(\mu+\delta,2)
+      \operatorname{Fn}(\mu+\delta_\alpha,2)
     \).
 
-    Consider the \(\mb P\)-name
-    \(
-      F_M
+    We now fix \(\mu<\lambda\) such that
+    \[
+      \bigcup_{\alpha\leq\lambda}
+      \operatorname{supp}(\dot f_{[\alpha,\alpha+\omega)})
+        \cap
+      \alpha
+        \subseteq
+      \mu
+    \]
+    (TODO how?) and define the \(\mb P\)-name
+    \[
+      F
+      %   =
+      % \varphi_{\mu,\lambda}(\dot f_{[\lambda,\lambda+\omega)})
         =
@@
       :
-        ((\lambda+k_p,m_p)^\cdot,p)\in\dot f_A
+        ((\lambda+k_p,m_p)^\cdot,p)\in\dot f_{[\lambda,\lambda+\omega)}
       \}
-    \).
-
-    % Other values
-    %         replacing \(\lambda>\mu\) will result in their own set \(Y\)
-    %         and canonical map \(\varphi_{\mu,\lambda}\); but one thing we do have to
-    %         assume (or arrange) for other values \(\alpha\) replacing \(\lambda\)
-    %         is that \(\operatorname{supp}(\dot f_{[\alpha,\alpha+\omega)})\)
-    %         intersected with
-    %         \(\alpha\) is contained in \(\mu\).
-
-            Now the object \(F_M\) is an
-            element of \(M\), and \(M\) believes this statement is true:
+    .\]
+
+    So in \(M\), we may reason (TODO why)
+    that for each \(\beta<\omega_2\) there exists
+    some \(\alpha\in\omega_2\setminus\beta\) where
     \[
-            (\forall \beta\in\omega_2)~ (\exists \beta<\lambda\in \omega_2)~~~
-            \operatorname{supp}(\dot f_{[\lambda,\lambda+\omega)})
-            \cap \lambda\subset \mu \ \ \mbox{and}\ \
-            F_M = \varphi_{\mu,\lambda}(\dot f_{[\lambda,\lambda+\omega)})\]
-
-            But now, this  means that,
-            not only is there  an \(\alpha\in M\),
-            \( F_M = \varphi_{\mu,\alpha}(\dot f_{[\alpha,\alpha+\omega)})\)
+      \operatorname{supp}(\dot f_{[\alpha,\alpha+\omega)})
+      \cap \alpha\subseteq \mu
+    \]
+    and
+    \[
+      F
+        =
+      \{
+        ((\alpha+k_p,m_p)^\cdot,\varphi_{\mu,\alpha}(p))
+      :
+        ((\alpha+k_p,m_p)^\cdot,p)\in\dot f_{[\alpha,\alpha+\omega)}
+      \}
+    .\]
+
+    But now, this means not only is there an \(\alpha<\lambda\) such that
+    \( F = \varphi(\dot f_{[\alpha,\alpha+\omega)})\),
     but also that there is an increasing sequence
-             \(\{\alpha_\xi : \xi  \in \omega_1\}\subset \lambda\) of
-             such \(\alpha\)'s satisfying that, for each \(\xi\)
-            we have that \(\operatorname{supp}(\dot
-            f_{[\alpha_\xi,\alpha_\xi+\omega)})\) is contained in \(\alpha_{\xi+1}\).
-
-            Choose such a sequence.
-             This means that if we let \(A = \bigcup_{n>0} [\alpha_n,\alpha_n+\omega)\) we
-             have the name \(\dot f_A\) in \(M\). This then means that all
-             the \(( (\beta,m) , p)\) appearing in \(\dot f_A\) have the property
-             that \(\mathop{dom}(p)\) is contained in \(M\).
+    \(\{\alpha_\xi : \xi  \in \omega_1\}\subseteq \lambda\)
+    satisfying that \(F=\varphi(\dot f_{[\alpha_\xi,\alpha_\xi+\omega)})\) and
+    \(\operatorname{supp}(\dot f_{[\alpha_\xi,\alpha_\xi+\omega)})\) is
+    contained in \(\alpha_{\xi+1}\) (TODO why not \(\mu\)?).
+
+    Choose such a sequence, and let
+    \(A = \bigcup_{0<n<\omega} [\alpha_n,\alpha_n+\omega)\). Consider
+    the name \(\dot f_A\) in \(M\). Note all the \(((\beta,m)^\cdot, p)\)
+    appearing in \(\dot f_A\) have the property that
+    \(\operatorname{dom}(p)\) is contained in \(M\) (QUESTION: isn't the
+    domain of any member of \(\mb P\) in the domain?)
     There is, within \(M\), a name \(\dot g\) satisfying that
      \(\dot f_A(\alpha_n+k) = \dot f_{[\alpha_n,\alpha_n+\omega)}(\alpha_n+k)\)
-            for all \(k >\dot g(n)\).
-
-            \bigskip
-
-            We now apply the above Lemma using \(\mu = \mu_0\) and we are now
-            working in the extension \(V[G_\mu]\). We will abuse the notation
-            and use \(\dot f_{[\alpha_n,\alpha_n+\omega)}\) instead of
-              \(\dot f_{[\alpha_n,\alpha_n+\omega)}(G_{\mu})\) as defined in
-              the Lemma.
+    for all \(k >\dot g(n)\) (TODO: why?).
+
+    (TODO catch up to here)
+
+            We now apply the above Lemma and work in \(M[G_\mu]\).
             We work for a contradiction. Something special has now happened,
@@
              \dot f_{[\alpha_n,\alpha_n+\omega)}) =
-            \varphi_{\mu,\lambda}(q\restriction \operatorname{supp}(
+            \varphi(q\restriction \operatorname{supp}(
              \dot f_{[\lambda,\lambda+\omega)}) \]
@@
             But now, again calculate
-            \[ q_3 = \varphi_{\mu,\lambda}^{-1} \circ \varphi_{\mu,\alpha_n}
+            \[ q_3 = \varphi^{-1} \circ \varphi_{\mu,\alpha_n}
             (q_2\restriction \operatorname{supp}(\dot
@@
             there is a  \(\beta'\in\mathop{dom}(q_2)\) such that \(
-             \varphi_{\mu,\lambda}(\beta) = \varphi_{\mu,\alpha_n}(\beta')\),
+             \varphi(\beta) = \varphi_{\mu,\alpha_n}(\beta')\),
             and that \(q_3(\beta) = q_2(\beta')\).

### 2016-01-20 postdoctoral/gamma_functions.tex
misc work on gamma functions notes and alcomp preprint

@@
 
+  All spaces are assumed to be Hausdorff. Continuum means ``Hausdorff, compact,
+  and connected''.
+
   \begin{definition}
-    Let a V-map be a u.s.c. idempotent surjection.
+    A generalized inverse limit \(\varprojlim \{X_p, f_{p,q}, D\}\) is a
+    subspace of \(\prod_{p\in D}X_p\) defined for
+    a directed set \(\<D,\leq\>\),
+    topological spaces \(X_p\) for each \(p\in D\),
+    and relations \(f_{p,q}\subseteq X_q\times X_p\) for each
+    \(p,q\in D\) where \(p\leq q\). Elements in  \(\varprojlim \{X, f, D\}\)
+    are the sequences \(\vect x\) such that \(p\leq q\) implies
+    \(\vect x(p)\in f_{p,q}(\vect x(q))\).
+  \end{definition}
+
+  \begin{definition}
+    An uppersemicontinuous (u.s.c.) relation is a closed subset of the
+    square.
+  \end{definition}
+
+  \begin{theorem}[summarized in \cite{VARAGONApreprint}]
+    If \(L\) is totally ordered, \(X_p\) is a continuum for all \(p\in L\),
+    and \(f_{p,q}\) is u.s.c. and continuum-valued for each \(p\leq q\in L\),
+    then \(\varprojlim\{X,f,L\}\) is a continuum.
+  \end{theorem}
+
+  \begin{definition}
+    An idempotent relation on \(X^2\) satisfies \(f[f(x)]=f(x)\) for all
+    \(x\in X\).
+  \end{definition}
+
+  \begin{definition}
+    A V-map \(f\subseteq X^2\) is a continuum-valued u.s.c. idempotent
+    surjection.
   \end{definition}
@@
 
-  \begin{theorem}
+  \begin{theorem}[\cite{CLONTZVARAGONA}]
     Every V-map on a compact connected LOTS satisfies condition \(\Gamma\).
@@
 
-  This was proven in \cite{CLONTZVARAGONA} for the case \(M\) is a closed
-  interval of real numbers; however, the same proof applies to this more
-  general case.
-
 \newpage
 
+  Assume \(L\) is a total order.
+
   \begin{definition}
-    For any LOS \(\<L,\leq\>\), let \(\check L\) be the collection of
+    For any total order \(\<L,\leq\>\), let \(\check L\) be the collection of
     leftward subsets of \(L\)
@@
   \begin{proposition}
-    \(\check L\), \(\hat L\) are compact.
+    \(\check L\), \(\hat L\) are compact LOTS.
   \end{proposition}
@@
     \(\mc T=\{[\emptyset,(\leftarrow,l]):l\in L\}\)
-    generates a countable base for \(\check L\).
+    is a countable subbase for \(\check L\).
   \end{proof}
@@
   \begin{example}
-    For limit ordinals \(\alpha\), \(\hat \alpha\cong \alpha+1\),
-    and for all other infinite ordinals, \(\hat\alpha\cong\alpha\).
-    (The addition of a new least isolated point is of course irrelevant).
+    For finite and limit ordinals \(\alpha\), \(\hat \alpha\cong \alpha+1\),
+    and for all other ordinals, \(\hat\alpha\cong\alpha\).
   \end{example}
@@
     Since \(\check\alpha=\alpha+1\) (actually equals, not just homeomorphic!),
-    we get \(\varprojlim^\star \{2, \gamma, \alpha\}
+    we get \(\varprojlim \{2, \gamma, \alpha\}
       \cong \check\alpha =
     \alpha+1\) for free.
-    Note that C and Varagona used this in (TODO create citataion) to break
-    metrizability in uncountable-ordinal-indexed inverse limits (for any V-map
-    there exists a two-point set \(2\) such that \(f\rest 2\supseteq\gamma\),
-    that is, ``\(f\) has condition \(\Gamma\)'').
+    This is essentially what the author and Varagona used
+    in \cite{CLONTZVARAGONA} to break
+    metrizability in uncountable-ordinal-indexed inverse limits.
   \end{proof}
@@
 
-  We may generalize theorem whatevs as follows:
+  We may generalize theorem 15 as follows:
 
-  \begin{theorem} %TODO fix first \sim to use A,B instead of l_0,l_1
+  \begin{theorem}
     If \(M\) is a LOTS with minimum \(0\) and maximum \(1\),
     then \(\varprojlim\{M,\gamma,L\}\cong \hat L\lexTimes M/\sim\),
-    where \(\<(\leftarrow,l_0],1\>\sim\<(\leftarrow,l_1],0\>\) if
-    \(l_0<l_1\) and \((l_0,l_1)=\emptyset\),
+    where \(\<A,1\>\sim\<B,0\>\) if
+    \(A\subsetneq B\) and \((A,B)=\emptyset\),
     and where \(\<A,m\>\sim\<A,m'\>\) if \(A\in\hat L\setminus L\).
@@
 
-    A basic open set in \(\varprojlim\{M,\gamma,L\}\subseteq L^m\)
+    A basic open set in \(\varprojlim\{M,\gamma,L\}\subseteq L^M\)
     is of the form
@@
 
-  We now discard the linear order on \(M\). Denote points in the topological
-  sum \(\bigoplus_{l\in \hat L} M\) of \(\hat L\) copies of \(M\)
-  by the ordered pairs \(\<A,m\>\)
-  for \(A\in \hat L\), \(m\in M\). The previous proof may be generalized to
-  show the following:
+  % We now discard the linear order on \(M\). Denote points in the topological
+  % sum \(\bigoplus_{l\in \hat L} M\) of \(\hat L\) copies of \(M\)
+  % by the ordered pairs \(\<A,m\>\)
+  % for \(A\in \hat L\), \(m\in M\). The previous proof may be generalized to
+  % show the following:
 
-  \begin{theorem}
-    If \(M\) is a Hausdorff space with points \(0\) and \(1\),
-    then \(\varprojlim\{M,\gamma,L\}\cong \bigoplus_{l\in \hat L} M/\sim\),
-    where \(\<(\leftarrow,l_0],1\>\sim\<(\leftarrow,l_1],0\>\) if
-    \(l_0<l_1\) and \((l_0,l_1)=\emptyset\),
-    and where \(\<A,m\>\sim\<A,m'\>\) if \(A\in\hat L\setminus L\).
-  \end{theorem}
+  % \begin{theorem}
+  %   If \(M\) is a Hausdorff space with points \(0\) and \(1\),
+  %   then \(\varprojlim\{M,\gamma,L\}\cong \bigoplus_{l\in \hat L} M/\sim\),
+  %   where \(\<(\leftarrow,l_0],1\>\sim\<(\leftarrow,l_1],0\>\) if
+  %   \(l_0<l_1\) and \((l_0,l_1)=\emptyset\),
+  %   and where \(\<A,m\>\sim\<A,m'\>\) if \(A\in\hat L\setminus L\).
+  % \end{theorem}
 

### 2016-02-03 articles/almost-compatible-functions-and-topological-games/article.tex
near final draft of alcomp paper

--- 2015-12-11 articles/almost-compatible-functions-and-topological-games/article.tex
@@
     In round \(n\), \(\pl C\) chooses an open cover \(\mc U_n\), followed by
-    \(\pl F\)
-    choosing subset \(F_n\) of \(X\) which may be finitely covered by \(\mc U_n\).
+    \(\pl F\) choosing a
+    subset \(F_n\) of \(X\) which may be finitely covered by \(\mc U_n\).
 
@@
   for perfect information strategies (so both characterize
-  the Menger property), and this characterization is
+  the Menger property in the same way), and this characterization is
   more convenient for our concerns.
@@
   But \(CH\) is not required to have \(\alcompS{\aleph_2}\) fail.
-  We take the following lemma from Kunen.
-
- \begin{lemma}[\cite{MR597342}]
-    Assume that \(G\subset \operatorname{Fn}(\omega_2,2)\) is a generic filter,
-    and let \(\mu\in \omega_2\). Then the final model \(V[G]\) can be
-    regarded as forcing with
-    \(\operatorname{Fn}(\omega_2\setminus \mu, 2)\) over the model \(V[G_\mu]\).
-    Let \(\dot n,\ddot n\) be a
-    \(\operatorname{Fn}(\omega_2,2)\)-,
-    \(\operatorname{Fn}(\omega_2\setminus\mu,2)\)-name respectively for each
-    \(n<\omega\). Then for each \(\operatorname{Fn}(\omega_2,2)\)-name \(\dot A\)
-    for \(A\subseteq\omega\), there is a canonical
-    \(\operatorname{Fn}(\omega_2\setminus \mu, 2)\)-name
-    \[
-      \ddot A
-        =
-      \{
-        (\ddot n,p\rest [\mu,\omega_2))
-      :
-        (\dot n,p)\in \dot A
-      \}
+
+            The forcing extension of a model $M$ by a poset $\mathbb P\in M$ is
+            obtained simply by evaluating all $\mathbb P$-names from $M$ by a
+            generic filter $G$.
+             A set $\tau$ is a $\mathbb P$-name if $\tau$ is a
+             (possibly empty)
+            set of ordered pairs $(\sigma,p)$ where $p\in \mathbb P$ and
+             $\sigma$ is also itself a $\mathbb P$-name.
+            If $G$ is a $\mathbb P$-generic filter, then
+             $\val_G(\tau) $ is defined to equal
+              $\{ \val_G(\sigma) : ~~(\exists p\in G)~~(\sigma,p)\in \tau\}$.
+
+            If $x\in M$, then the canonical
+            $\mathbb P$-name, $\check x$, is generally, and recursively,
+             taken to be
+             $\{ (\check y, 1) : y\in x\}$ where $1$ is the maximum element of
+             $\mathbb P$.  However, it will be convenient to consider, when the
+            context is clear, $(x,p)$ (for any $p\in \mathbb P$)
+            to be a kind of $\mathbb P$-name.
+            In particular
+            if $\tau \subset X\times \mathbb P$ (for some fixed $X\in M$),
+            then we may let $\tau[G] = \{ x : ~~(\exists p\in
+            G)~~(x,p)\in\tau\}$.
+
+            Thus,  $\val_G(\tau)$ will denote the recursive evaluation by $G$ and
+             $\tau[G]$ will be defined as above.
+            In fact, if $\tau\in M$ is any set then each of
+             $\val_G(\tau)$ and $\tau[G]$ are well defined.
+            It is a standard convention to use a dotted letter, such
+            as $\dot x$, to indicate that we are discussing a $\mathbb P$-name.
+
+            One says that a condition $p\in \mathbb P$ forces a statement
+            $\varphi$
+              to hold, denoted $p\Vdash \varphi$,
+            if that statement holds in $M[G]$ for all $\mathbb P$-generic filters
+            with $p\in G$. The forcing theorem states that if $M[G]\models
+            \varphi$,
+             then there is some $p\in G$ forcing that $\varphi$ holds.
+            The following is an immediate consequence of the forcing theorem.
+
+            \begin{lemma*} If $X\in M$ and $\dot x$ is a $\mathbb P$-name,
+            then\label{easyname}
+             there is a $\tau\subset X\times \mathbb P$, such that
+            for any generic $G$, $\tau[G] = X\cap \val_G(\dot x)$.
+            \end{lemma*}
+
+            In other words, the family of subsets of any $X\in M$ in
+            the extension $M[G]$ is equal to
+             $\{ \tau[G] : \tau \subset X\times \mathbb P, \ \
+            \tau\in M\ \}$.  We will be using
+            the forcing poset is $\operatorname{Fn}(\omega_2, 2)$.
+            The elements of this poset are all the finite partial functions
+            from $\omega_2$ into $2$ ordered by reverse inclusion.
+            It follows that, for any $\lambda\in \omega_2$,
+             each of
+             $\operatorname{Fn}(\lambda,2)$ and $\operatorname{Fn}(\omega_2\setminus
+             \lambda,2)$ are subposets. For any
+             $\operatorname{Fn}(\omega_2,2)$-generic
+            filter  $G$, it easily follows that $G_\lambda = G\cap
+            \operatorname{Fn}(\lambda,2)$ and
+             $G^\lambda = G\cap
+            \operatorname{Fn}(\omega_2\setminus
+             \lambda,2)$ are also generic filters. But a much stronger statement is
+             true.
+
+            \begin{lemma*}\cite{MR597342}
+            Assume that $G\subset \operatorname{Fn}(\omega_2,2)$ is a
+             generic\label{factor} filter,
+             and let $\lambda\in \omega_2$. Then the final model $M[G]$
+            is equal to $(M[G_\lambda])[G^\lambda]$ in the sense that
+            $G^\lambda$ is a $\operatorname{Fn}(\omega_2\setminus \lambda,
+             2)$-generic filter   over the model $M[G_\lambda]$.
+
+            In addition, for each $X\in M$ and name $\dot A\subset
+            X\times \operatorname{Fn}(\omega_2,2)$, we get that
+             \[ (\dot A(G_\lambda))[G^\lambda] = \dot A [G]\ \ \mbox{where}\
+            \dot A(G_\lambda) =
+             \{ (x,p\restriction [\lambda,\omega_2))  :
+             (x,p)\in \dot A\ \ \mbox{and} \ \ p\restriction \lambda\in G_\lambda\}
             \]
-    which satisfies
-    \(
-      A
-        =
-      \operatorname{val}(\dot A,G)
-        =
-      \operatorname{val}(\ddot A,G_\mu)
-    \).
-  \end{lemma}
-
-  \begin{theorem}
-    It follows from the consistency of \(ZFC\) that
-    there exists a model of \(ZFC\) for which \(\mf c=\aleph_2\)
-    and \(\neg\alcompS{\aleph_2}\).
+            \end{lemma*}
+
+            With these lemmas in hand we are ready to prove the theorem. The idea
+            of the proof comes from  Kunen's result about no $\omega_2$ length mod
+            finite chains of subset of $\omega$. We consider any  family of
+            names  of suitable one-to-one functions from countable subsets of
+            $\omega_2$ into $\omega$. We identify a large enough $\lambda\in \omega_2$
+            so that a pattern has emerged and we pass to the model $M[G_\lambda]$. We
+            then show that this pattern can not continue out to $\omega_2$.
+
+            \begin{theorem} There exists a model of ZFC for which
+             $\mathfrak c=\aleph_2$ and $\lnot \mathcal A(\aleph_2)$.
             \end{theorem}
@@
             \begin{proof}
-    The forcing poset is \(\mb P=\operatorname{Fn}(\omega_2, 2)\).
-    Let \(\{ \dot f_{A} : A\in [\omega_2]^\omega\}\) be a family of
-    \(\mb P\)-names such that \(f_{A}\) is a one-to-one function from \(A\) into
-    \(\omega\) in the ground model. Let \(M\) be an elementary submodel
-    of the universe containing \(\mb P\) such that
-    \(|M|=\omega_1 =\mathfrak c\) and \(M^\omega\subset M\).
-
-    Let \(\lambda\) be the ordinal \(M\cap \omega_2\).
-    We may assume
-    \(
-      \dot f_{[\lambda,\lambda+\omega)}
-        =
-      \{
-        ((\lambda+k_p,m_p)^\cdot, p)
-      :
-        p\in C
-      \}
-    \)
-    for some countable \(C\subseteq\operatorname{Fn}(\omega_2,\omega)\).
-    Let
-    \(
-      \operatorname{supp}(\dot f_{[\lambda,\lambda+\omega)})
-        =
-      \bigcup_{p\in C}\operatorname{dom} p
-    \).
-
-    Let \(\delta_\lambda\) denote the order type of
-    \(\operatorname{supp}(\dot f_{[\lambda,\lambda+\omega)})\setminus \lambda\),
-    and for \(\mu\leq\lambda\) let \(\varphi_{\mu,\lambda}'\) be the
-    order-preserving bijection from
-    \(
-      \mu\cup
-      \left(\operatorname{supp}(\dot f_{[\lambda,\lambda+\omega)})
-        \setminus
-      \lambda\right)
-    \)
-    onto the ordinal \(\mu+\delta_\lambda\).
-    This lifts canonically to an order-preserving bijection
-    \(
-      \varphi_{\mu,\lambda}
-        :
-      \operatorname{Fn}(\mu\cup Y,2)
-        \to
-      \operatorname{Fn}(\mu+\delta,2)
-    \).
-
-    Consider the \(\mb P\)-name
-    \(
-      F_M
-        =
-      \{
-        ((\lambda+k_p,m_p)^\cdot,\varphi_{\mu,\lambda}(p))
-      :
-        ((\lambda+k_p,m_p)^\cdot,p)\in\dot f_A
-      \}
-    \).
-
-    % Other values
-    %         replacing \(\lambda>\mu\) will result in their own set \(Y\)
-    %         and canonical map \(\varphi_{\mu,\lambda}\); but one thing we do have to
-    %         assume (or arrange) for other values \(\alpha\) replacing \(\lambda\)
-    %         is that \(\operatorname{supp}(\dot f_{[\alpha,\alpha+\omega)})\)
-    %         intersected with
-    %         \(\alpha\) is contained in \(\mu\).
-
-            Now the object \(F_M\) is an
-            element of \(M\), and \(M\) believes this statement is true:
-            \[
-            (\forall \beta\in\omega_2)~ (\exists \beta<\lambda\in \omega_2)~~~
+            We start with a model $M$ of GCH and suppose that $G$ is a
+            $\operatorname{Fn}(\omega_2,2)$-generic filter. The argument takes
+            place in $M$.
+            Let $\{ \dot f_{A} : A\in [\omega_2]^\omega\}$ be a family of
+            names (in $M$)
+             such that, for any generic $G$ and each $A\in [\omega_2]^\omega\cap
+             M$,
+             $\dot f_{A}[G]$ is a one-to-one function from $A$ into
+            $\omega$.  We also assume that whenever $B\subset A$ are members of
+            $[\omega_2]^\omega$, we have that $\dot f_{B}[G]\subset^* \dot
+            f_{A}[G]$. If we now obtain a contradiction
+            then we will have shown that $\mathcal A(\aleph_2)$ fails.
+
+            By \cite[1.5]{MR1031969}, there is a set $H\subset H(\aleph_3)$
+            such that the family $\{ \dot f_{A} : A\in [\omega_2]^{\omega}\}$ is an
+            element of $H$,  $H$ is an elementary submodel of
+            $ H(\aleph_3)$, $H$ has cardinality
+            $\aleph_1$, and $H^\omega\subset H$ (every
+             countable subset of $H$ is an element of $H$).
+
+            Let $\lambda = H\cap \omega_2$ (same as the supremum of $H\cap
+            \omega_2$). Consider the name  $\dot f_{[\lambda,\lambda+\omega)}$.
+            What is such a name?  By Lemma \ref{easyname},
+            we can assume that it is a set of pairs
+             of the form $( (\lambda+k,m), p)$ where $p\in \mathop{Fn}(\omega_2,
+             2)$ and, of course, $k,m\in \omega$.
+            Furthermore,  for each $k,m$ it is enough
+            (see \cite[5.11,5.12]{MR597342})
+            to take a  countable set of such $p$ to get an equivalent
+            (\textit{nice}\/) name.
+            Given any such nice name $\dot f$, let $\operatorname{supp}(\dot f)$
+            denote the union of the domains of conditions $p$ appearing in the
+            name.
+
+             Now let $Y$ equal $\operatorname{supp}(\dot
+             f_{[\lambda,\lambda+\omega)})\setminus \lambda$. Furthermore,
+             fix any $\mu\in \lambda\subset H$ such that
+               $\operatorname{supp}(\dot
+             f_{[\lambda,\lambda+\omega)})\cap \lambda$ is contained in $\mu$.
+             Let $\delta\in \omega_1$ denote the order type of
+             $Y$ and let  $\varphi_{\mu,\lambda}$ be the order-preserving function
+             from  $\mu\cup Y$ onto  the ordinal $\mu+\delta$.  This lifts
+             canonically to
+            an order-preserving bijection $\varphi_{\mu,\lambda}:
+            \operatorname{Fn}(\mu\cup Y,2) \mapsto
+            \operatorname{Fn}(\mu+\delta,2)$.
+            Now fix any  $\mu<\lambda$ so that
+             $\operatorname{supp}(\dot
+             f_{[\lambda,\lambda+\omega)})\cap \lambda\subset \mu$.
+            We can similarly make sense of the name
+             $\varphi_{\mu,\lambda}(\dot f_{[\lambda,\lambda+\omega)})$, call it $F_H$.
+            Here simply, for each tuple $(\,(k,m), p)\in \dot
+            f_{[\lambda,\lambda+\omega)}$,
+             we have that $(\,(k,m),\varphi_{\mu,\lambda}(p))$ is in $F_H$.
+            Again, let $\varphi_{\mu,\lambda}(\dot f_{[\lambda,\lambda+\omega)})$
+            be interpreted in the above sense as giving $F_H$ (which is an element
+            of $H$).
+
+             Other values
+            replacing $\lambda>\mu$ will result in their own set $Y$
+            and canonical map $\varphi_{\mu,\lambda}$.
+            Now the object $F_H$ is an
+            element of $H$, and $H$ believes this statement is true:
+            $$
+            (\forall \beta\in\omega_2)~ (\exists \lambda\in \omega_2\setminus \beta)~~~
             \operatorname{supp}(\dot f_{[\lambda,\lambda+\omega)})
             \cap \lambda\subset \mu \ \ \mbox{and}\ \
-            F_M = \varphi_{\mu,\lambda}(\dot f_{[\lambda,\lambda+\omega)})\]
+            F_H = \varphi_{\mu,\lambda}(\dot f_{[\lambda,\lambda+\omega)})$$
 
             But now, this  means that,
-            not only is there  an \(\alpha\in M\),
-            \( F_M = \varphi_{\mu,\alpha}(\dot f_{[\alpha,\alpha+\omega)})\)
+            not only is there  an $\alpha\in H$,
+            $ F_H = \varphi_{\mu,\alpha}(\dot f_{[\alpha,\alpha+\omega)})$
             but also that there is an increasing sequence
-             \(\{\alpha_\xi : \xi  \in \omega_1\}\subset \lambda\) of
-             such \(\alpha\)'s satisfying that, for each \(\xi\)
-            we have that \(\operatorname{supp}(\dot
-            f_{[\alpha_\xi,\alpha_\xi+\omega)})\) is contained in \(\alpha_{\xi+1}\).
+             $\{\alpha_\xi : \xi  \in \omega_1\}\subset \lambda$ of
+             such $\alpha$'s satisfying that, for each $\xi$
+            we have that $\operatorname{supp}(\dot
+            f_{[\alpha_\xi,\alpha_\xi+\omega)})$ is contained in $\alpha_{\xi+1}$.
 
             Choose such a sequence.
-             This means that if we let \(A = \bigcup_{n>0} [\alpha_n,\alpha_n+\omega)\) we
-             have the name \(\dot f_A\) in \(M\). This then means that all
-             the \(( (\beta,m) , p)\) appearing in \(\dot f_A\) have the property
-             that \(\mathop{dom}(p)\) is contained in \(M\).
-            There is, within \(M\), a name \(\dot g\) satisfying that
-             \(\dot f_A(\alpha_n+k) = \dot f_{[\alpha_n,\alpha_n+\omega)}(\alpha_n+k)\)
-            for all \(k >\dot g(n)\).
-
-            \bigskip
-
-            We now apply the above Lemma using \(\mu = \mu_0\) and we are now
-            working in the extension \(V[G_\mu]\). We will abuse the notation
-            and use \(\dot f_{[\alpha_n,\alpha_n+\omega)}\) instead of
-              \(\dot f_{[\alpha_n,\alpha_n+\omega)}(G_{\mu})\) as defined in
-              the Lemma.
+             This means that if we let $A = \bigcup_{n>0} [\alpha_n,\alpha_n+\omega)$ we
+             have the name $\dot f_A$ in $H$. This then means that all
+             the $( (\beta,m) , p)$ appearing in (the nice name)
+            $\dot f_A$ have the property
+             that $\mathop{dom}(p)$ is contained in $H$.
+            There is, also within $H$, a name $\dot g$ satisfying that
+             $\dot f_A(\alpha_n+k) = \dot f_{[\alpha_n,\alpha_n+\omega)}(\alpha_n+k)$
+            for all $k >\dot g(n)$,
+            or more precisely,
+             $\dot g\subset (\omega\times\omega) \times
+             \operatorname{Fn}(\omega_2,2)$ satisfies that
+             $\dot g[G]\in \omega^\omega$ and
+              $\dot f_{A}[G](\alpha_n+k) = \dot
+              f_{[\alpha_n,\alpha_n+\omega)}[G](\alpha+k)$
+            for all $k>\dot g[G](n)$.
+
+            We now apply  Lemma \ref{factor} and we are now
+            working in the extension $M[G_\mu]$.
             We work for a contradiction. Something special has now happened,
-             namely,  the supports of the names \(\{
-            \dot f_{[\alpha_n, \alpha_n+\omega)} :  0< n<\omega\}\) are pairwise disjoint
+             namely,  the supports of the names $\{
+            \dot f_{[\alpha_n, \alpha_n+\omega)} (G_\mu):  0< n<\omega\}$ are pairwise disjoint
             and also disjoint from the support of the name
-             \(\dot f_{[\lambda,\lambda+\omega)}\) (under the same convention about
-             \(G_\mu\).  And not only that, these names are pairwise isomorphic (in
-             the way that they all map to \(F_M\)).
-
-            \bigskip
-
-            Since \(A\) is disjoint from \([\lambda,\lambda+\omega)\),
-            there must be an integer \(\ell\)
+             $\dot f_{[\lambda,\lambda+\omega)}(G_\mu)$.
+             And not only that, these names are pairwise isomorphic (in
+             the way that they all map to $F_H$).
+
+             Since $A$ is disjoint from $[\lambda,\lambda+\omega)$,
+            there must be an integer $\ell$
             together with a condition
-             \(q\in \mathop{Fn}(\omega_2\setminus \mu,2)\) satisfying that for all
-             \(n>\ell\) , \(q\) forces that
+             $q\in \mathop{Fn}(\omega_2\setminus \mu,2)$ satisfying that for all
+             $n>\ell$ , $q$ forces that
 
             \centerline{
-             ``if \(k>\dot g(n)\) (since  \(\alpha_n+k\in A\)) then
-             \(\dot f_{[\alpha_n,\alpha_n+\omega)}(\alpha_n+k) \neq
-            \dot f_{[\lambda,\lambda+\omega)}(\lambda +k)\)''.}
-
-            Choose \(n\) large enough so that \(\mathop{dom}(q) \cap [\alpha_n,
-            \mu_{n+1})\) is
+             ``if $k>\dot g(n)$ then
+             $(\dot f_{[\alpha_n,\alpha_n+\omega)}(G_\mu))(\alpha_n+k) \neq
+            (\dot f_{[\lambda,\lambda+\omega)}(G_\mu))(\lambda +k)$''.}
+
+            Choose $n>\ell$ large enough so that $\mathop{dom}(q) \cap [\alpha_n,
+            \alpha_{n+1})$ is
             empty.
-             Choose \(q_1<q\restriction \lambda\) (in \(M\)) so that
-            \[ \varphi_{\mu,\alpha_n}(q_1\restriction \operatorname{supp}(
+             Choose $q_1<q\restriction \lambda$ (in $H$) so that
+            $$ \varphi_{\mu,\alpha_n}(q_1\restriction \operatorname{supp}(
              \dot f_{[\alpha_n,\alpha_n+\omega)}) =
             \varphi_{\mu,\lambda}(q\restriction \operatorname{supp}(
-             \dot f_{[\lambda,\lambda+\omega)}) \]
-            and then (again in \(M\)) choose \(q_2 < q_1\)
+             \dot f_{[\lambda,\lambda+\omega)}) $$
+            and then (again in $H$) choose $q_2 < q_1$
             so that it both forces a value
-             \(L\) on \(\ell+\dot g(n)\)
-            and subsequently forces a value \(m\) on
-             \(\dot f_{[\alpha_n, \alpha_n+\omega)}(\alpha_n+L+1)\).
+             $L$ on $\ell+\dot g(n)$
+            and subsequently forces a value $m$ on
+             $\dot f_{[\alpha_n, \alpha_n+\omega)}(\alpha_n+L+1)$.
             But now, again calculate
-            \[ q_3 = \varphi_{\mu,\lambda}^{-1} \circ \varphi_{\mu,\alpha_n}
+            $$ q_3 = \varphi_{\mu,\lambda}^{-1} \circ \varphi_{\mu,\alpha_n}
             (q_2\restriction \operatorname{supp}(\dot
-            f_{[\alpha_n,\alpha_n+\omega)}))\]
-            and, by the isomorphisms, we have that \(q_3\) forces that
-             \(\dot f_{[\lambda,\lambda+\omega)}(\lambda+L+1) = m\).
+            f_{[\alpha_n,\alpha_n+\omega)}))$$
+            and, by the isomorphisms, we have that $q_3$ forces that
+             $\dot f_{[\lambda,\lambda+\omega)}(\lambda+L+1) = m$.
 
             Technically (or with more care)  all of this is taking place in the
-            poset \(\operatorname{Fn}(\omega_2\setminus \mu,2)\) and this means
-            that \(q_3\) and \(q\) are all compatible with each other.
-
-            Follow
-            the bouncing ball: it suffices to consider
-             \(q(\beta)=e\) and to assume that \(q_3(\beta)\) is defined.
-            Since \(q_3(\beta)\) is defined, we have that
-            there is a  \(\beta'\in\mathop{dom}(q_2)\) such that \(
-             \varphi_{\mu,\lambda}(\beta) = \varphi_{\mu,\alpha_n}(\beta')\),
-            and that \(q_3(\beta) = q_2(\beta')\).
-            But, by definition of \(q_1\), \(\beta'\in\mathop{dom}(q_1)\)
-            and even  that \(q_1(\beta') = q(\beta)\).
-             Then, since \(q_2<q_1\), we have that \(q_2(\beta')=q_1(\beta') =
-             q(\beta)\). This completes the circle that \(q_3(\beta) = q(\beta)\).
-            \bigskip
-
-            Finally, our contradiction is that \(q_3\cup q_2\cup q\)
+            poset $\operatorname{Fn}(\omega_2\setminus \mu,2)$ and this means
+            that $q_3$ and $q$ are  with each other.
+            To verify this it suffices to consider
+             $q(\beta)=e$ and to assume that $q_3(\beta)$ is defined.
+            Since $q_3(\beta)$ is defined, we have that
+            there is a  $\beta'\in\mathop{dom}(q_2)$ such that $
+             \varphi_{\mu,\lambda}(\beta) = \varphi_{\mu,\alpha_n}(\beta')$,
+            and that $q_3(\beta) = q_2(\beta')$.
+            But, by definition of $q_1$, $\beta'\in\mathop{dom}(q_1)$
+            and even  that $q_1(\beta') = q(\beta)$.
+             Then, since $q_2<q_1$, we have that $q_2(\beta')=q_1(\beta') =
+             q(\beta)$. This completes the circle that $q_3(\beta) = q(\beta)$.
+
+            Finally, our contradiction is that $q_3\cup q_2\cup q$
             forces that
-             \(k=L+1\) violates the quoted statement above.
+             $k=L+1$ violates the quoted statement above.
             \end{proof}
@@
             generality to  also assume that GCH holds in this model.
-
-            \bigskip
 
@@
 
-            \bigskip
-
             The forcing notion $\mathbb P_0$ is simply the finite condition
@@
              ordinal $\left(\lambda^{+\omega}\right)^V$.
-
-            \bigskip
-
-            \newpage
 
@@
   because if we also assume \(V=L\), it follows that
-  \(\alcompSP{\kappa}\) and therefore \(\pl F\kmarkwin2\menGame{X}\)
-  for every cardinal. Although, one may consider the following weaker question.
+  \(\alcompSP{\kappa}\) and therefore
+  \(\pl F\kmarkwin2\menGame{\oneptlind\kappa}\)
+  for every cardinal \(\kappa\).
+  Although, one may consider the following question.
 
@@
 
-  % \section{Generalized Kurepa families and almost-compactible functions}
-
-  % TODO
-
 \bibliographystyle{plain}

### 2016-02-03 articles/almost-compatible-functions-and-topological-games/article.tex
alan's revisions

@@
 \maketitle
+\footnotetext[1]{The second author acknowledges support provided by
+NSF-DMS 1501506}
 
@@
 
-            \begin{lemma*} If $X\in M$ and $\dot x$ is a $\mathbb P$-name,
+            \begin{lemma} If $X\in M$ and $\dot x$ is a $\mathbb P$-name,
             then\label{easyname}
@@
             for any generic $G$, $\tau[G] = X\cap \val_G(\dot x)$.
-            \end{lemma*}
+            \end{lemma}
 
@@
 
-            \begin{lemma*}\cite{MR597342}
+            \begin{lemma}\cite{MR597342}
             Assume that $G\subset \operatorname{Fn}(\omega_2,2)$ is a
@@
             \]
-            \end{lemma*}
+            \end{lemma}
 
@@
             of the proof comes from  Kunen's result about no $\omega_2$ length mod
-            finite chains of subset of $\omega$. We consider any  family of
+            finite chains of subsets of $\omega$. We consider any  family of
             names  of suitable one-to-one functions from countable subsets of
@@
             \operatorname{Fn}(\mu+\delta,2)$.
-            Now fix any  $\mu<\lambda$ so that
-             $\operatorname{supp}(\dot
-             f_{[\lambda,\lambda+\omega)})\cap \lambda\subset \mu$.
             We can similarly make sense of the name

### 2016-03-15 postdoctoral/gamma_functions.tex
some tweaks to gamma functions notes

@@
     topological spaces \(X_p\) for each \(p\in D\),
-    and relations \(f_{p,q}\subseteq X_q\times X_p\) for each
-    \(p,q\in D\) where \(p\leq q\). Elements in  \(\varprojlim \{X, f, D\}\)
+    and bonding relations \(f_{p,q}\subseteq X_q\times X_p\) for each
+    \(p,q\in D\) where \(p\leq q\). Elements in
+    \(\varprojlim \{X_p, f_{p,q}, D\}\)
     are the sequences \(\vect x\) such that \(p\leq q\) implies
@@
   \begin{definition}
-    An uppersemicontinuous (u.s.c.) relation is a closed subset of the
-    square.
+    An left-total relation on \(X\times Y\) satisfies
+    \(\forall x\in X\exists y\in Y(\<x,y\>\in f)\).
+  \end{definition}
+
+  \begin{definition}
+    A left-total relation which is a closed subset of the rectangle
+    \(X\times Y\) is called upper-semicontinuous or u.s.c.
+    (Equivalently, its corresponding set-valued map \(X\to C(Y)\)
+    is continuous.)
   \end{definition}
@@
     and \(f_{p,q}\) is u.s.c. and continuum-valued for each \(p\leq q\in L\),
-    then \(\varprojlim\{X,f,L\}\) is a continuum.
+    then \(\varprojlim\{X_p,f_{p,q},L\}\) is a continuum.
   \end{theorem}
+
+  \begin{definition}
+    An surjective relation on \(X\times Y\) satisfies
+    \(\forall y\in Y\exists x\in X(\<x,y\>\in f)\).
+  \end{definition}
 
@@
   \begin{definition}
-    A V-map \(f\subseteq X^2\) is a continuum-valued u.s.c. idempotent
-    surjection.
+    A u.s.c. idempotent surjective relation
+    \(f\subseteq X^2\) is called a V-relation.
   \end{definition}
@@
   \begin{definition}
-    A u.s.c. map \(f\subseteq X^2\)
+    A continuum-valued V-relation is called a CV-relation.
+  \end{definition}
+
+  \begin{definition}
+    A relation \(f\subseteq X^2\)
     satisfies condition \(\Gamma\) if there exists \(x,y\in X\) such that
@@
   \begin{theorem}[\cite{CLONTZVARAGONA}]
-    Every V-map on a compact connected LOTS satisfies condition \(\Gamma\).
+    Every CV-relation on a compact connected LOTS satisfies condition \(\Gamma\).
   \end{theorem}
@@
     (subsets for which \(b\in L,a\leq b\Rightarrow a\in L\))
-    linearly ordered by \(\subseteq\), and let \(\hat L\) be the collection
+    totally ordered by \(\subseteq\), and let \(\hat L\) be the collection
     of left-closed subsets of \(L\) (leftward subsets which are closed)
-    linearly ordered by \(\subseteq\).
+    totally ordered by \(\subseteq\).
   \end{definition}
@@
     Each subset \(S\) has an infimum \(\cap S\) and a supremum \(\cup S\)
-    (or \(\cl(\cap S)\)).
+    (or \(\cl(\cup S)\)).
   \end{proof}
@@
     For any space \(M\) containing the points \(0\) and \(1\),
-    let \(\gamma\) be the surjective u.s.c. map on \(K\) where
+    let \(\gamma\) be the V-relation on \(K\) where
     \(\gamma(0)=M\) and \(\gamma(t)=\{1\}\)
@@
 
-  Note when \(M\) is a Hausdorff continuum, then \(\gamma\) is a V-map.
+  Note when \(M\) is a Hausdorff continuum, then \(\gamma\) is a CV-relation.
   It's usually assumed \(0\) is the minimum and \(1\) is the maximum

### 2016-03-21 articles/lexicographical-products-and-idempotent-inverse-limits/article.tex
add abstract for idempotent inverse limits paper

--- 2016-01-20 articles/almost-compatible-functions-and-topological-games/article.tex
@@
 
-% dow stuff
-          \def\Succ{\mathop{Succ}}
-          \def\dom{\mathop{dom}}
-          \def\val{\operatorname{val}}
-          \def\N{\mathbb N}
-          \def\Nstar{\mathbb N^*}
-
 \begin{document}
@@
 % \tnotetext[t1]{2010 Mathematics Subject Classification. 54E15, 54D30, 54A20.}
-\title{Almost compatible functions and infinite length games}
+\title{Lexicographic products and idempotent inverse limits}
 
@@
 \author{Steven Clontz}
-\address{Department of Mathematics and Statistics, UNC Charlotte,
-Charlotte, NC 28262}
+\address{Department of Mathematics and Statistics, UNC Charlotte}
 \email{steven.clontz@gmail.com}
-\author{Alan Dow}
-\address{Department of Mathematics and Statistics, UNC Charlotte,
-Charlotte, NC 28262}
-\email{adow@uncc.edu}
 
@@
 \begin{abstract}
-  \(\alcompSP\kappa\) asserts the existence of pairwise
-  almost compatible finite-to-one functions \(A\to\omega\) for each
-  countable subset \(A\) of \(\kappa\).
-  The existence of winning \(2\)-Markov strategies in
-  several infinite-length games, including
-  the Menger game on the one-point Lindel\"ofication \(\oneptlind\kappa\)
-  of \(\kappa\), are guaranteed by \(\alcompSP\kappa\). \(\alcompSP\kappa\) is
-  implied by the existence of cofinal Kurepa families of size \(\kappa\),
-  and thus holds for all cardinals less than \(\aleph_\omega\).
-  It's consistent that \(\alcompSP{\aleph_\omega}\) fails, but
-  there must always be a winning \(2\)-Markov strategy for the second
-  player in the Menger game on \(\oneptlind{\omega_\omega}\).
+  The inverse limit \(\varprojlim\{X,\gamma,L\}\) may
+  be characterized as the quotient of a generalized lexicogrphic product of
+  the compactification \(\hat L\) and \(X\). A special case of
+  this fact is used to show that when \(f\) is any nontrivial
+  idempotent bonding relation and \(L\) is uncountable,
+  the inverse limit \(\varprojlim\{X,f,L\}\) cannot be Corson compact,
+  and therefore cannot be metrizable.
 \end{abstract}
@@
 
-  \begin{definition}
-    Two functions \(f,g\) are almost compatible, that is, \(f\sim g\) when
-    \(\{a\in\dom f\cap\dom g:f(a)\not=g(a)\}\) is finite.
-  \end{definition}
-
-  Marion Scheepers used almost compatible functions in \cite{MR1129143} in order
-  to study the existence of limited information strategies on a variation
-  of the meager-nowhere dense game he introduced in \cite{MR1183703}.
-
-  \begin{game}
-    Let \(\schFillStrictGame\kappa\) denote
-    \term{Scheepers' strict countable-finite union game}
-    with two players \(\pl C\), \(\pl F\). In round \(0\), \(\pl C\) chooses
-    \(C_0\in[\kappa]^{\leq\omega}\), followed by \(\pl F\) choosing
-    \(F_0\in[\kappa]^{<\omega}\). In round \(n+1\), \(\pl C\) chooses
-    \(C_{n+1}\in[\kappa]^{\leq\omega}\) such that \(C_{n+1}\supset C_n\), followed
-    by \(\pl F\) choosing \(F_{n+1}\in[\kappa]^{<\omega}\).
-
-    \(\pl F\) wins the game if
-    \(\bigcup_{n<\omega} F_n\supseteq\bigcup_{n<\omega} C_n\); otherwise,
-    \(\pl C\) wins.
-  \end{game}
-
-  Of course, with perfect information this game is trivial: during round
-  \(n\) player \(\pl F\) simply chooses \(n\) ordinals from each of the
-  \(n\) countable sets played by \(\pl C\). However, if \(\pl F\) is limited
-  to using information from the last \(k\) moves by \(\pl C\) during each
-  round, the task becomes more difficult. Call such a strategy a
-  \term{\(k\)-tactical strategy} or \term{\(k\)-tactic}; if using the round
-  number is allowed, then the strategy is called a \term{\(k\)-Markov strategy}
-  or a \term{\(k\)-mark}.
-
-  \begin{definition}
-    The statement \(\alcompS\kappa\) (given as \(S(\kappa,\aleph_0,\omega)\)
-    in \cite{MR1129143} and \(S(\kappa)\) in \cite{clontzMengerGamePreprint})
-    claims that there exist one-to-one functions
-    \(f_A:A\to\omega\) for each \(A\in[\kappa]^{\leq\aleph_0}\) such that
-    the collection \(\{f_A:A\in[\kappa]^{\leq\aleph_0}\}\) is pairwise
-    almost compatible.
-  \end{definition}
-
-  In the same paper, Scheepers noted that \(\alcompS{\omega_1}\) holds in \(ZFC\),
-  and that it's possible to force \(\mf c\) to be arbitrarily large
-  while preserving \(\alcompS{\mf c}\). However, \(\alcompS{\mf c^+}\) always fails.
-  This axiom may be applied to obtain a winning \(2\)-tactic for \(\pl F\)
-  in the countable-finite game.
-
-  In \cite{clontzMengerGamePreprint}, Clontz related this game to a game
-  which may be used to characterize the Menger covering property of a
-  topological space.
-
-  \begin{game}
-    Let \(\menGame{X}\) denote the \term{Menger game} with players \(\pl C\),
-    \(\pl F\).
-    In round \(n\), \(\pl C\) chooses an open cover \(\mc U_n\), followed by
-    \(\pl F\)
-    choosing subset \(F_n\) of \(X\) which may be finitely covered by \(\mc U_n\).
-
-    \(\pl F\) wins the game if \(X = \bigcup_{n<\omega}F_n\),
-    and \(\pl C\) wins otherwise.
-  \end{game}
-
-  This characterization is slightly different than the typical characterization
-  in which the second player first chooses a specific
-  finite subcollection \(\mc F_n\) of the cover itself and lets
-  \(F_n=\bigcup \mc F_n\), denoted as \(G_{fin}(\mc O,\mc O)\)
-  in \cite{MR1378387}.
-  However, it's easily seen that these games are equivalent
-  for perfect information strategies (so both characterize
-  the Menger property), and this characterization is
-  more convenient for our concerns.
-
-  \begin{definition}
-    Let \(\oneptlind\kappa=\kappa\cup\{\infty\}\) where \(\kappa\) is
-    discrete and \(\infty\)'s neighborhoods are the co-countable sets
-    containing it.
-  \end{definition}
-
-  The relationship between \(\schFillStrictGame\kappa\) and
-  \(\menGame{\oneptlind\kappa}\) is strong; in both games \(\pl C\) essentially
-  chooses a countable subset of \(\kappa\) followed by \(\pl F\) choosing
-  a finite subset of that choice, and it's easy to see the winning perfect
-  information strategy for \(\pl F\) in both games.
-  In addition, it was shown in
-  \cite{clontzMengerGamePreprint} that when \(\alcompS{\kappa}\) holds,
-  \(\pl F\) has a winning \(2\)-Markov strategy in
-  \(\menGame{\oneptlind\kappa}\).
-
-  One source of motivation is to make progress on the following open question:
-
-  \begin{question}\label{mainQuestion}
-    Does there exist a topological space \(X\) for which
-    \(\pl F\win\menGame{X}\) but \(\pl F\notkmarkwin{2}\menGame{X}\)?
-    (That is, the second player can win the Menger game on \(X\)
-    with perfect information but not with \(2\)-Markov information.)
-  \end{question}
-
-  \section{One-to-one and finite-to-one almost compatible functions}
-
-  We may weaken Scheeper's \(\alcompS{\kappa}\) as follows:
-
-  \begin{definition}
-    The statement \(\alcompSP{\kappa}\) weakens \(\alcompS{\kappa}\) by only
-    requiring the witnessing almost-compatible functions \(f_A:A\to\omega\)
-    to be finite-to-one.
-  \end{definition}
-
-  \begin{proposition}
-    \(\alcompS{\kappa}\) and \(\alcompSP{\kappa}\) need only be witnessed by
-    functions \(\{f_A:A\in\mc S\}\) for some family \(\mc S\)
-    cofinal in \([\kappa]^{\leq\aleph_0}\).
-  \end{proposition}
-
-  \begin{proof}
-    For each \(A\in[\kappa]^{\leq\aleph_0}\) choose \(A'\supseteq A\)
-    from \(\mc S\) and let \(g_A=f_{A'}\rest A\).
-  \end{proof}
-
-  In the next section we will show that \(\alcompSP{\kappa}\) is sufficient
-  for the applications to the Scheepers and Menger games.
-  In the meantime, we will demonstrate that \(\alcompSP{\kappa}\) is strictly
-  weaker than \(\alcompS{\kappa}\).
-
-  Recall the following.
-
-  \begin{definition}
-    A Kurepa family \(\mc K\subseteq[\kappa]^{\aleph_0}\) on \(\kappa\)
-    satisfies that
-    \(\mc K\rest A=\{K\cap A:K\in\mc K\}\) is countable
-    for each \(A\in[\kappa]^{\aleph_0}\).
-    Let \(\kurepaS\kappa\) be the statement claiming there exists
-    a Kurepa family on \(\kappa\)
-    cofinal in \([\kappa]^{\aleph_0}\).
-  \end{definition}
-
-  \begin{theorem}
-    \(\kurepaS\kappa \Rightarrow \alcompSP{\kappa}\).
-  \end{theorem}
-
-  \begin{proof}
-    Let \(\mc K=\{K_\alpha:\alpha<\theta\}\)
-    be a cofinal Kurepa family on \(\kappa\).
-    We first define \(f_\alpha:K_\alpha\to\omega\) for each \(\alpha<\theta\).
-
-    Suppose we've already defined pairwise almost compatible finite-to-one functions
-    \(\{f_\beta:\beta<\alpha\}\). To define
-    \(f_\alpha\), we first recall that \(\mc K\rest K_\alpha\) is countable,
-    so we may choose \(\beta_n<\alpha\) for \(n<\omega\) such that
-    \(
-      \{K_\beta:\beta<\alpha\}\rest K_\alpha \setminus \{\emptyset\}
-        =
-      \{K_\alpha\cap K_{\beta_n}:n<\omega\}
-    \).
-    Let \(K_\alpha=\{\delta_{i,j}:i\leq\omega,j<w_i\}\) where
-    \(w_i\leq\omega\) for each \(i\leq\omega\),
-    \(
-      K_\alpha\cap \left(K_{\beta_n}\setminus\bigcup_{m<n}K_{\beta_m}\right)
-        =
-      \{\delta_{n,j}:j<w_n\}
-    \),
-    and
-    \(
-      K_\alpha\setminus\bigcup_{n<\omega}K_{\beta_n}
-        =
-      \{
-        \delta_{\omega,j}:j<w_\omega
-      \}
-    \).
-    Then let \(f_\alpha(\delta_{n,j})=\max(n,f_{\beta_n}(\delta_{n,j}))\) for
-    \(n<\omega\) and \(f_\alpha(\delta_{\omega,j})=j\) otherwise.
-
-    We should show that \(f_\alpha\) is finite-to-one. Let \(n<\omega\).
-    Since \(f_\alpha(\delta_{m,j})\geq m\), we only consider the finite cases
-    where \(m\leq n\). Since each
-    \(f_{\beta_m}\) is finite-to-one, \(f_{\beta_m}(\delta_{m,j})\leq n\)
-    for only finitely many \(j\). Thus
-    \(f_\alpha(\delta_{m,j})=\max(m,f_{\beta_m}(\delta_{m,j}))\) maps to
-    \(n\) for only finitely many \(j\).
-
-    We now want to demonstrate that \(f_\alpha\sim f_{\beta_n}\) for all
-    \(n<\omega\). Note \(\delta_{m,j}\in K_{\beta_n}\) implies
-    \(m\leq n\).
-    For \(m=n\), we have
-    \(f_\alpha(\delta_{n,j})=\max(n,f_{\beta_n}(\delta_{n,j}))\) which differs
-    from \(f_{\beta_n}(\delta_{n,j})\) for only the finitely many \(j\) which
-    are mapped below \(n\) by \(f_{\beta_n}\).
-    For \(m<n\) and \(\delta_{m,j}\in K_{\beta_n}\),we have
-    \(f_\alpha(\delta_{m,j})=\max(m,f_{\beta_m}(\delta_{m,j}))\) which can
-    only differ
-    from \(f_{\beta_n}(\delta_{m,j})\) for only the finitely many \(j\) which
-    are mapped below \(m\) by \(f_{\beta_m}\) or the finitely many \(j\)
-    for which the
-    almost compatible \(f_{\beta_n}\sim f_{\beta_m}\) differ.
-
-    Finally for any \(\beta<\alpha\), we may conclude \(f_\alpha\sim f_\beta\)
-    since there is some \(\beta_n\) with
-    \(K_\alpha\cap K_\beta=K_\alpha\cap K_{\beta_n}\),
-    \(f_\alpha\sim f_{\beta_n}\), and \(f_{\beta_n}\sim f_\beta\).
-  \end{proof}
-
-  We now construct a topology on \(\omega_n\) for each \(n<\omega\) which
-  will witness a Kurepa family of size \(\aleph_n\). A similar construction
-  was previously shown by Juh\'asz et. al. in \cite{MR539228},
-  and the relationship of
-  Kurepa families and such spaces has also been investigated in a preprint
-  of Nyikos \cite{NYIKOSKUREPA}.
-
-  \begin{proposition}
-    Let \(X\) be a \(T_2\) space with a base of countable and compact
-    neighborhoods. Then \(X\) is locally metrizable with
-    a base of compact open countable sets.
-  \end{proposition}
-
-  \begin{proof}
-    For each point \(x\) let \(K\) be a countable and compact neighborhood
-    of \(x\), and it follows that it is contained in a countable, open,
-    and locally compact neighborhood \(W\) of \(x\), which in turn
-    is zero-dimensional and metrizable. So choose \(V\) clopen
-    in \(W\) such that \(x\in V\subseteq K\); \(V\) is a compact open
-    neighborhood of \(x\) in \(X\).
-  \end{proof}
-
-  \begin{definition}
-    A topological space is said to be \term{\(\omega\)-bounded}
-    if each countable subset of the space has compact closure.
-    As in \cite{MR539228} we call a
-    \(T_2\), locally countable, \(\omega\)-bounded space
-    \term{splendid}, and let \(\splendidS\kappa\) represent
-    the claim that there exists a splendid space of cardinality \(\kappa\).
-  \end{definition}
-
-  \begin{proposition}
-    Let \(X\) be a \(T_2\) space with cardinality less than \(\aleph_\omega\)
-    which is locally countable and
-    \(\omega\)-bounded. Then the closure operation preserves cardinality and
-    weight.
-  \end{proposition}
-
-  \begin{proof}
-    Note that the closure of any countable neighborhood is compact, and
-    any Lindel\"of set is countable. This space is locally metrizable
-    and thus first-countable, so cardinality and weight coincide for any
-    subspace. The result is obvious if \(A\) is countable; otherwise
-    let \(A=\{a_\alpha:\alpha<\omega_{n+1}\}\) and since basic neighborhoods
-    are countable note any limit point of \(A\) is
-    a limit point of \(A_\beta=\{a_\alpha:\alpha<\beta\}\)
-    for some \(\beta<\omega_{n+1}\).
-    Thus \(\cl A=\bigcup_{\beta<\omega_{n+1}}\cl{A_\beta}\) and
-    by induction \(|\cl A|=|A|\).
-  \end{proof}
-
-  \begin{lemma}
-    Let \(X\) be a \(T_2\) space with cardinality less than \(\aleph_\omega\)
-    which is locally countable and locally compact, and such that
-    its closure operation preserves cardinalities.
-    Then \(X\) has an \(\omega\)-bounded extension \(\tilde X\)
-    with the same properties where \(\tilde X\setminus X\) has the same
-    cardinality as \(X\).
-  \end{lemma}
-
-  \begin{proof}
-    We prove this by induction on \(n\).
-    If \(n=0\), then we can just use the one-point compactification of two
-    copies of \(X\). So suppose \(n>0\) and
-    that \(X=\omega_n\) has an appropriate topology. Note that \(X\) has
-    a base of countable and compact neighborhoods since the closure operation
-    preserves cardinalities.
-
-    For each \(\alpha<\omega_n\), \(\gamma_\alpha\) may be chosen such that
-    both the closure of the set \(\alpha\) in \(X\) and a countable
-    neighborhood of the point \(\alpha\) are subsets of \(\gamma_\alpha\).
-    Note that the set
-    \(\{\lambda<\omega_n:\alpha<\lambda\Rightarrow\gamma_\alpha<\lambda\}\)
-    is a cub subset of \(\omega_n\) containing a cub subset \(C\)
-    of limit ordinals.
-    Now for each \(\lambda\in C\), the set \(\lambda\) is
-    open as \(\alpha<\lambda\) belongs to the neighborhood
-    \(\gamma_\alpha\subsetneq\lambda\). Also, if \(\lambda\) has uncountable
-    cofinality, then for \(\beta\geq\lambda\) and any countable neighborhood
-    \(U\) of \(\beta\), \(U\cap\lambda=U\cap\alpha\)
-    for some \(\alpha<\lambda\); thus \(U\setminus\cl\alpha=U\setminus\lambda\)
-    is a neighborhood of \(\beta\), showing that \(\lambda\)
-    is clopen.
-
-    Let \(\tilde X=\omega_n\times 2\).
-    By induction on \(\lambda \in C\) we will define compatible topologies
-    for \(\tilde X_\lambda=\omega_n\times\{0\}\cup\lambda\times\{1\}\)
-    such that
-    \begin{itemize}
-      \item \(\omega_n \times \{0\}\) is an open copy of \(X\),
-      \item \(\lambda\times 2\) is open, and when \(\cf\lambda>\omega\) also closed,
-      \item the space has a base of countable and compact neighborhoods, and
-      \item when \(\lambda\) is a successor,
-        for each \(\alpha<\lambda\) the closure of \(\alpha\times 2\) is
-        an \(\omega\)-bounded  subset of \(\lambda\times 2\).
-    \end{itemize}
-
-    We first consider the case \(n=1\).
-    If \(\lambda\) is a limit in \(C\), then
-    \(
-      \tilde X_\lambda
-        =
-      \bigcup_{\mu\in C\cap\lambda}\tilde X_\mu
-    \)
-    satisfies the induction requirements.
-    Otherwise we choose an increasing sequence of
-    ordinals \(\{\alpha_k : k\in \omega\}\) with limit \(\lambda\)
-    such that \(\alpha_0\) is the predecessor of \(\lambda\) in \(C\),
-    or \(\alpha_0=0\) if \(\lambda\) is the least element of \(C\).
-
-    The subspace \(\cl\lambda\times\{0\}\cup\alpha_0\times2\) of \(X\)
-    is countable and locally compact; therefore it is
-    metrizable and zero-dimensional.
-    So we may choose increasing sets \(U_k\) for \(k<\omega\) which are
-    clopen in this topology and satisfy
-    \[
-      \cl{\alpha_k\times\{0\}\cup\alpha_0\times2}
-        =
-      \cl{\alpha_k}\times\{0\}\cup\alpha_0\times2
-        \subseteq
-      U_k
-        \subseteq
-      \lambda\times\{0\}\cup\alpha_0\times 2
-    \]
-    Note that \(U_k\) is also clopen in \(\tilde X_{\alpha_0}\) since it is
-    closed in \(\cl\lambda\times\{0\}\cup\alpha_0\times2\) and open in
-    \(\lambda\times\{0\}\cup\alpha_0\times 2\).
-
-    We need only describe a base for the points
-    \(\<\alpha,1\>\in(\lambda\setminus\alpha_0)\times\{1\}\).
-    We do so by letting
-    \(\<\alpha,1\>\) be isolated when \(\alpha\not\in\{\alpha_k:k<\omega\}\),
-    and giving \(\<\alpha_k,1\>\) the open neighborhoods
-    \((U_k\cup((\alpha_k+1)\times\{1\}))\setminus K\) for each compact
-    subset \(K\) of \(U_k\cup(\alpha_k\times\{1\})\); that is,
-    \(\<\alpha_k,1\>\) is the one point compactifying
-    \(U_k\cup(\alpha_k\times\{1\})\).
-
-    The first two requirements of our inductive hypothesis are obviously
-    satsified. Note points in \(\lambda\times 2\) are covered by
-    the compact countable neighborhood \(U_k\cup((\alpha_k+1)\times\{1\})\)
-    for some \(k<\omega\), and for points in
-    \((\omega_n\setminus\lambda)\times\{0\}\) we may use a compact
-    countable neighborhood from \(X\).
-    For the final requirement, note that for \(\alpha<\lambda\), we may
-    choose \(\alpha<\alpha_k<\lambda\) and note that
-    \(\alpha\times 2\) is contained in the compact
-    subset \(U_k\cup((\alpha_k+1)\times\{1\})\) of \(\lambda\times2\).
-
-    For the case \(n>1\), we may assume that the successors in \(C\)
-    have uncountable cofinality.
-    We again proceed by induction on \(\lambda\in C\).  Again when
-    \(\lambda\) is a limit in \(C\),
-    \(
-      \tilde X_\lambda
-        =
-      \bigcup_{\mu\in C\cap\lambda}\tilde X_\mu
-    \)
-    satisfies the given
-    requirements; in particular if \(\alpha<\lambda\), then
-    \(\alpha<\mu<\lambda\) for some successor \(\mu\in C\) with uncountable
-    cofinality. As such, the closure of \(\alpha\times2\) is
-    an \(\omega\)-bounded subset of the clopen \(\mu\times 2\) and
-    therefore also of \(\lambda\times 2\).
-    In case \(\lambda\) is not a limit of \(C\), then \(\lambda\)
-    has uncountable cofinality and a predecessor \(\mu\in C\).
-    We therefore have that \(\lambda\times\{0\}\) is clopen
-    in \(\omega_n\times \{0\}\). Since the cardinality of
-    \(\lambda\times \{0\} \cup \mu\times 2\) is less than \(\aleph_n\),
-    we may simply apply the induction hypothesis
-    to choose an appropriate topology for \(\lambda\times 2\).
-
-    As a result, \(\tilde X=\bigcup_{\lambda\in C}\tilde X_\lambda\)
-    is
-    \(\omega\)-bounded as any countable set is contained in some
-    \(\alpha\times 2\) for \(\alpha<\lambda\in C\).
-  \end{proof}
-
-  \begin{theorem}
-    For each \(k< \omega\), there is a \(T_2\), locally countable,
-    \(\omega\)-bounded topology on \(\omega_k\). That is, \(\splendidS{\aleph_k}\)
-    for all \(k<\omega\).
-  \end{theorem}
-
-  \begin{proof}
-    Apply the previous lemma to \(\omega_n\) with the discrete topology.
-  \end{proof}
-
-  \begin{lemma}
-    The family of compact open sets in a locally countable, \(\omega\)-bounded
-    topological space \(X\)
-    is a Kurepa family cofinal in \([X]^\omega\). That is,
-    \(\splendidS\kappa \Rightarrow \kurepaS\kappa\).
-  \end{lemma}
-
-  \begin{proof}
-    Let \(\mc K\) collect all compact
-    open subsets of \(X\). Of course, every Lindel\"of set in
-    a locally countable space is countable, and the closure of every
-    countable set is a compact countable set; thus \(\mc K\)
-    is cofinal in \([X]^\omega\).
-    It is Kurepa since every countable set is contained in a countable
-    compact open subspace of \(X\); this subspace has a countable
-    base of compact open sets, which closed under finite unions enumerates
-    all compact open subsets of the subspace.
-  \end{proof}
-
-  \begin{corollary}
-    \(\kurepaS{\aleph_k}\) for all \(k<\omega\).
-  \end{corollary}
-
-  Alternatively, the previous corollary may be obtained
-  via an observation of Todorcevic
-  communicated by Dow in \cite{MR1229125}:
-  if every Kurepa family of size at most \(\kappa\)
-  extends to a cofinal Kurepa family, then the same is true of \(\kappa^+\).
-
-  Nyikos points out in \cite{NYIKOSKUREPA} that a cofinal Kurepa family may
-  be used to construct a locally metrizable, \(\omega\)-bounded,
-  zero-dimensional space with appropriate cardinality,
-  but whether this can be
-  strengthened to locally countable and \(\omega\)-bounded (as asked in
-  \cite{MR539228}) remains an open question.
-
-  Also left open is this extension of the question asked in \cite{NYIKOSKUREPA}
-  and \cite{MR539228} on the possible equivalence of \(\splendidS\kappa\)
-  and \(\kurepaS\kappa\).
-
-  \begin{question}
-    May any of the implications in the theorem
-    \(\splendidS\kappa\Rightarrow\kurepaS\kappa\Rightarrow\alcompSP\kappa\)
-    be reversed?
-  \end{question}
-
-  Regardless, we have obtained our desired result.
-
-  \begin{corollary}
-    \(\alcompSP{\aleph_k}\) for all \(k<\omega\).
-  \end{corollary}
-
-  \section{Consistency results}
-
-  As noted in \cite{MR1229125}, Jensen's one-gap two-cardinal theorem under
-  \(V=L\) introduced in \cite{MR0309729} implies that \(\kurepaS\kappa\)
-  holds for all cardinals \(\kappa\).
-
-  \begin{corollary}[\(V=L\)]
-    \(\alcompSP{\kappa}\) for all cardinals \(\kappa\).
-  \end{corollary}
-
-  Weakening to the continuum hypothesis, we see an obvious consequence.
-
-  \begin{corollary}[\(CH\)]
-    \(\alcompSP{\mf c^+}\), but \(\neg\alcompS{\mf c^+}\).
-  \end{corollary}
-
-  But \(CH\) is not required to have \(\alcompS{\aleph_2}\) fail.
-  We take the following lemma from Kunen.
-
- \begin{lemma}[\cite{MR597342}]
-    Assume that \(G\subset \operatorname{Fn}(\omega_2,2)\) is a generic filter
-    over a model \(M\),
-    and let \(\mu\in \omega_2\). Then the generic extension \(M[G]\) can be
-    regarded as forcing with
-    \(\operatorname{Fn}(\omega_2\setminus \mu, 2)\) over the model \(M[G_\mu]\).
-    Let \(\dot n,\ddot n\) be a
-    \(\operatorname{Fn}(\omega_2,2)\)-,
-    \(\operatorname{Fn}(\omega_2\setminus\mu,2)\)-name respectively for each
-    \(n<\omega\). Then for each \(\operatorname{Fn}(\omega_2,2)\)-name \(\dot A\)
-    for \(A\subseteq\omega\), there is a canonical
-    \(\operatorname{Fn}(\omega_2\setminus \mu, 2)\)-name
-    \[
-      \ddot A
-        =
-      \{
-        (\ddot n,p\rest [\mu,\omega_2))
-      :
-        (\dot n,p)\in \dot A
-      \}
-    \]
-    which satisfies
-    \(
-      A
-        =
-      \operatorname{val}(\dot A,G)
-        =
-      \operatorname{val}(\ddot A,G_\mu)
-    \).
-  \end{lemma}
-
-  \begin{theorem}
-    There exists a model of \(ZFC\) for which \(\mf c=\aleph_2\)
-    and \(\neg\alcompS{\aleph_2}\).
-  \end{theorem}
-
-  \begin{proof}
-    The forcing poset is \(\mb P=\operatorname{Fn}(\omega_2, 2)\).
-    Let \(\{ \dot f_{A} : A\in [\omega_2]^\omega\}\) be a family of
-    \(\mb P\)-names such that \(f_{A}\) is a one-to-one function from \(A\)
-    into \(\omega\) in the ground model. Let \(M\) be an elementary submodel
-    of \(ZFC+CH\) containing all its countable subsets, containing \(\mb P\),
-    and satisfying \(|M|=\omega_1 =\mathfrak c\).
-
-    Let \(\lambda\) be the ordinal \(M\cap \omega_2\). For
-    \(\alpha\leq\lambda\) we may assume
-    \(
-      \dot f_{[\alpha,\alpha+\omega)}
-        =
-      \{
-        ((\alpha+k_p,m_p)^\cdot, p)
-      :
-        p\in C_\alpha
-      \}
-    \)
-    for some countable \(C_\alpha\subseteq\operatorname{Fn}(\omega_2,\omega)\).
-    Let
-    \(
-      \operatorname{supp}(\dot f_{[\alpha,\alpha+\omega)})
-        =
-      \bigcup_{p\in C_\alpha}\operatorname{dom} p
-    \).
-
-    For each \(\alpha\leq\lambda\),
-    let \(\delta_{\alpha}\) denote the order type of
-    \(\operatorname{supp}(\dot f_{[\alpha,\alpha+\omega)})\setminus \alpha\),
-    and when \(\mu\leq\alpha\) and
-    \(
-      \operatorname{supp}(\dot f_{[\alpha,\alpha+\omega)})
-        \cap
-      \alpha
-        \subseteq
-      \mu
-    \)
-    let \(\varphi'_{\mu,\alpha}\) be the order-preserving bijection from
-    \(
-      \mu\cup
-      \left(\operatorname{supp}(\dot f_{[\alpha,\alpha+\omega)})
-        \setminus
-      \alpha\right)
-    \)
-    onto the ordinal \(\mu+\delta_\alpha\).
-    This lifts canonically to an order-preserving bijection
-    \(
-      \varphi_{\mu,\alpha}
-        :
-      \operatorname{Fn}(\mu\cup
-        \left(\operatorname{supp}(\dot f_{[\alpha,\alpha+\omega)})
-          \setminus
-        \alpha\right)
-      ,2)
-        \to
-      \operatorname{Fn}(\mu+\delta_\alpha,2)
-    \).
-
-    We now fix \(\mu<\lambda\) such that
-    \[
-      \bigcup_{\alpha\leq\lambda}
-      \operatorname{supp}(\dot f_{[\alpha,\alpha+\omega)})
-        \cap
-      \alpha
-        \subseteq
-      \mu
-    \]
-    (TODO how?) and define the \(\mb P\)-name
-    \[
-      F
-      %   =
-      % \varphi_{\mu,\lambda}(\dot f_{[\lambda,\lambda+\omega)})
-        =
-      \{
-        ((\lambda+k_p,m_p)^\cdot,\varphi_{\mu,\lambda}(p))
-      :
-        ((\lambda+k_p,m_p)^\cdot,p)\in\dot f_{[\lambda,\lambda+\omega)}
-      \}
-    .\]
-
-    So in \(M\), we may reason (TODO why)
-    that for each \(\beta<\omega_2\) there exists
-    some \(\alpha\in\omega_2\setminus\beta\) where
-    \[
-      \operatorname{supp}(\dot f_{[\alpha,\alpha+\omega)})
-      \cap \alpha\subseteq \mu
-    \]
-    and
-    \[
-      F
-        =
-      \{
-        ((\alpha+k_p,m_p)^\cdot,\varphi_{\mu,\alpha}(p))
-      :
-        ((\alpha+k_p,m_p)^\cdot,p)\in\dot f_{[\alpha,\alpha+\omega)}
-      \}
-    .\]
-
-    But now, this means not only is there an \(\alpha<\lambda\) such that
-    \( F = \varphi(\dot f_{[\alpha,\alpha+\omega)})\),
-    but also that there is an increasing sequence
-    \(\{\alpha_\xi : \xi  \in \omega_1\}\subseteq \lambda\)
-    satisfying that \(F=\varphi(\dot f_{[\alpha_\xi,\alpha_\xi+\omega)})\) and
-    \(\operatorname{supp}(\dot f_{[\alpha_\xi,\alpha_\xi+\omega)})\) is
-    contained in \(\alpha_{\xi+1}\) (TODO why not \(\mu\)?).
-
-    Choose such a sequence, and let
-    \(A = \bigcup_{0<n<\omega} [\alpha_n,\alpha_n+\omega)\). Consider
-    the name \(\dot f_A\) in \(M\). Note all the \(((\beta,m)^\cdot, p)\)
-    appearing in \(\dot f_A\) have the property that
-    \(\operatorname{dom}(p)\) is contained in \(M\) (QUESTION: isn't the
-    domain of any member of \(\mb P\) in the domain?)
-    There is, within \(M\), a name \(\dot g\) satisfying that
-     \(\dot f_A(\alpha_n+k) = \dot f_{[\alpha_n,\alpha_n+\omega)}(\alpha_n+k)\)
-    for all \(k >\dot g(n)\) (TODO: why?).
-
-    (TODO catch up to here)
-
-            We now apply the above Lemma and work in \(M[G_\mu]\).
-            We work for a contradiction. Something special has now happened,
-            namely,  the supports of the names \(\{
-            \dot f_{[\alpha_n, \alpha_n+\omega)} :  0< n<\omega\}\) are pairwise disjoint
-            and also disjoint from the support of the name
-            \(\dot f_{[\lambda,\lambda+\omega)}\) (under the same convention about
-            \(G_\mu\).  And not only that, these names are pairwise isomorphic (in
-            the way that they all map to \(F_M\)).
-
-            \bigskip
-
-            Since \(A\) is disjoint from \([\lambda,\lambda+\omega)\),
-            there must be an integer \(\ell\)
-            together with a condition
-             \(q\in \mathop{Fn}(\omega_2\setminus \mu,2)\) satisfying that for all
-             \(n>\ell\) , \(q\) forces that
-
-            \centerline{
-             ``if \(k>\dot g(n)\) (since  \(\alpha_n+k\in A\)) then
-             \(\dot f_{[\alpha_n,\alpha_n+\omega)}(\alpha_n+k) \neq
-            \dot f_{[\lambda,\lambda+\omega)}(\lambda +k)\)''.}
-
-            Choose \(n\) large enough so that \(\mathop{dom}(q) \cap [\alpha_n,
-            \mu_{n+1})\) is
-            empty.
-             Choose \(q_1<q\restriction \lambda\) (in \(M\)) so that
-            \[ \varphi_{\mu,\alpha_n}(q_1\restriction \operatorname{supp}(
-             \dot f_{[\alpha_n,\alpha_n+\omega)}) =
-            \varphi(q\restriction \operatorname{supp}(
-             \dot f_{[\lambda,\lambda+\omega)}) \]
-            and then (again in \(M\)) choose \(q_2 < q_1\)
-            so that it both forces a value
-             \(L\) on \(\ell+\dot g(n)\)
-            and subsequently forces a value \(m\) on
-             \(\dot f_{[\alpha_n, \alpha_n+\omega)}(\alpha_n+L+1)\).
-            But now, again calculate
-            \[ q_3 = \varphi^{-1} \circ \varphi_{\mu,\alpha_n}
-            (q_2\restriction \operatorname{supp}(\dot
-            f_{[\alpha_n,\alpha_n+\omega)}))\]
-            and, by the isomorphisms, we have that \(q_3\) forces that
-             \(\dot f_{[\lambda,\lambda+\omega)}(\lambda+L+1) = m\).
-
-            Technically (or with more care)  all of this is taking place in the
-            poset \(\operatorname{Fn}(\omega_2\setminus \mu,2)\) and this means
-            that \(q_3\) and \(q\) are all compatible with each other.
-
-            Follow
-            the bouncing ball: it suffices to consider
-             \(q(\beta)=e\) and to assume that \(q_3(\beta)\) is defined.
-            Since \(q_3(\beta)\) is defined, we have that
-            there is a  \(\beta'\in\mathop{dom}(q_2)\) such that \(
-             \varphi(\beta) = \varphi_{\mu,\alpha_n}(\beta')\),
-            and that \(q_3(\beta) = q_2(\beta')\).
-            But, by definition of \(q_1\), \(\beta'\in\mathop{dom}(q_1)\)
-            and even  that \(q_1(\beta') = q(\beta)\).
-             Then, since \(q_2<q_1\), we have that \(q_2(\beta')=q_1(\beta') =
-             q(\beta)\). This completes the circle that \(q_3(\beta) = q(\beta)\).
-            \bigskip
-
-            Finally, our contradiction is that \(q_3\cup q_2\cup q\)
-            forces that
-             \(k=L+1\) violates the quoted statement above.
-            \end{proof}
-
-  We are also able to force \(\alcompSP{\kappa}\) to fail for every cardinal
-  other than the first \(\omega\)-many we've already guaranteed.
-
-\begin{theorem} It follows from the existence of a $2$-huge cardinal
-that there is a model of $ZFC$ for which $\lnot \mathcal A'(\aleph_{\omega})$.
-\end{theorem}
-
-            \begin{proof}
-            We will need the model constructed in \cite{MR1045371} in
-             which an instance of Chang's conjecture
-             $(\aleph_{\omega+1},\aleph_\omega) \rlap{$\rightarrow$}\,{\rightarrow}
-             (\aleph_1,\aleph_0)$ is shown to fail.
-
-            We can take as a given (as shown in \cite[Theorem 5]{MR1045371}) that we may
-            assume that we have a model $V$
-            of GCH in which there are regular limit cardinals $\kappa<\lambda$
-            satisfying that
-            $(\lambda^{+\omega+1},\lambda^{+\omega})\rlap{$\rightarrow$}\,{\rightarrow}
-            (\kappa^{+\omega+1},\kappa^{+\omega})$.
-
-            What this says is that if $L$ is a countable language
-            with at least one unary relation symbol $R$ and
-             $M$ is a model of $L$  with base set $\lambda^{+\omega+1}$
-            in which the interpretation of $R$ has cardinality
-             $\lambda^{+\omega}$, then $M$ has an elementary submodel
-             $N$ of cardinality $\kappa^{+\omega+1}$ in which
-            $R\cap N$ has cardinality $\kappa^{+\omega}$ (of course
-             $R\cap N$ is the interpretation of $R$ in $N$ because
-            $N\prec M$).
-
-            The interested reader will want to know that it is shown in
-            \cite{MR1045371} that if $\kappa$ is a 2-huge cardinal
-            and $j$ is the 2-huge
-            embedding with critical point $\kappa$, then with
-             $\lambda = j(\kappa)$ one has that
-            $(\lambda^{+\omega+1},\lambda^{+\omega})\rlap{$\rightarrow$}\,{\rightarrow}
-            (\kappa^{+\omega+1},\kappa^{+\omega})$ holds. There is no loss of
-            generality to  also assume that GCH holds in this model.
-
-            \bigskip
-
-            Let $\{ h_\xi : \xi \in \lambda^{+\omega+1}\}$
-            be a scale in $\Pi\{ \lambda^{+n+1} : n\in \omega\}$
-             ordered by the usual mod finite coordinatewise
-            ordering. For convenience we may assume that $h_\xi(n) \geq
-            \lambda^{+n}$ for all $\xi$ and all $n$. For each integer
-             $m$ the cofinality of the mod finite ordering on
-             $\Pi\{ \lambda^{+n+1} : m< n\in \omega\}$
-            is the same as it is for the entire product
-             $\Pi\{ \lambda^{+n+1} : n\in \omega\}$. If $P$
-            is any poset of cardinality less than
-             $\lambda^{+m}$ then, in the forcing extension by $P$,
-            every function in
-             $\Pi\{ \lambda^{+n+1} : m< n\in \omega\}$ is bounded
-            above by a ground model function.
-            It therefore
-            follows easily that  in the forcing
-            extension by $P$,  the sequence
-            $\{ h_\xi : \xi \in \lambda^{+\omega+1}\}$  remains cofinal in
-             $\Pi\{ \lambda^{+n+1} : n\in \omega\}$.
-
-            \bigskip
-
-            The forcing notion $\mathbb P_0$ is simply the finite condition
-            collapse of $\kappa^{+\omega}$, i.e. $\mathbb P_0 = \left(
-             \kappa^{+\omega}\right)^{<\omega}$. In the forcing extension by
-             $\mathbb P_0$, one now has that the ordinal $\kappa^{+\omega+1}$
-             from $V$ is the first uncountable cardinal $\aleph_1$. Then in this
-             forcing extension we let $\mathbb P_1$ be the countable condition
-             Levy collapse, $Lv(\lambda,\omega_2)$, which collapses all cardinals
-             less than $\lambda$ to have cardinality at most $\aleph_1$. The poset
-             $\mathbb P_1$ has cardinality $\lambda$. We treat
-            $\mathbb P*\mathbb P_1$ as containing $\mathbb P_0$
-            as a subposet by identifying each $(p_0,1)$ with $p_0$.
-            After forcing with $\mathbb P_0*\mathbb P_1$ we will have
-            that $\omega_1$ is the ordinal $\left(\kappa^{+\omega+1}\right)^V$,
-             $\omega_2$ is the ordinal $\lambda$, and $\omega_\omega$ is the
-             ordinal $\left(\lambda^{+\omega}\right)^V$.
-
-            \bigskip
-
-            \newpage
-
-            Now we assume that we have an assignment $\dot f_{\dot A}$ of a
-             $\mathbb P_0*\mathbb P_1$-name of a finite-to-one function from
-             $\dot A$ into $\omega$ for each
-             $\mathbb P_0*\mathbb P_1$-name of a countable subset of
-             $\lambda^{+\omega+1}$. We will obtain a contradiction.
-
-            Let $\{ \dot A_\xi : \xi \in \lambda^{+\omega+1}\}$ be an enumeration
-            of all the  nice $\mathbb P_0$-names of countable
-            subsets of $\lambda^{+\omega}$. For each $\xi\in \lambda^{+\omega+1}$,
-             let $\dot f_\xi$ be another notation for $\dot f_{\dot A_\xi}$.
-            Since $\mathbb P_0$ forces that $\mathbb P_1$ is countably closed,
-            the collection of all nice  $\mathbb P_0$-names will produce all
-            the countable sets in the extension by $\mathbb P_0* \mathbb
-            P_1$, but $\mathbb P_0*\mathbb P_1$ can introduce new enumerations of
-            these names.
-            For each $\xi\in \lambda^{+\omega+1}$,
-            there is a minimal $\zeta_\xi$ so that $\dot A_{\zeta_\xi}$ is the
-            canonical name for the range of $h_\xi$. This means that
-             $\dot f_{\zeta_\xi} \circ h_\xi$ is simply the
-             $\mathbb P_0 *\mathbb P_1$-name of a finite-to-one function from
-             $\omega$ to $\omega$.
-              For each $\xi\in \lambda^{+\omega+1}$,
-             choose any $p_\xi \in \mathbb P_0*\mathbb P_1$ so that
-             there is a nice $\mathbb P_0$-name, $\dot H_\xi$,
-             that is forced by
-             $p_\xi$  to equal $\dot f_{\zeta_\xi}\circ h_\xi$.
-              Choose $\Lambda\subset \lambda^{+\omega+1}$
-              of cardinality $\lambda^{+\omega+1}$
-              and so that there is a pair $p,\dot H$
-              satisfying that $p_\xi = p$ and $\dot H_\xi = \dot H$
-              for all $\xi\in \Lambda$. We may assume that $p$
-              is in a generic filter $  G$.
-
-            Let $\{ x_\xi : \xi\in \lambda^{+\omega+1}\}$ be any enumeration of
-             $H(\lambda^{+\omega+1})$  such that
-             $\{ x_\xi : \xi\in \lambda^{+\omega}\}$ is also equal to
-             $H(\lambda^{+\omega})$. We choose this enumeration in such a way that
-             $x_\xi\in x_\eta$ implies $\xi<\eta$.
-            We use relation symbol $R_0$ to code
-            (and well order)
-             $(H(\lambda^{+\omega+1}), \in)$ as follows: $(\xi,\eta)\in R_0$
-            if and only if $x_\xi\in x_\eta$.
-            Let $R_1$ be a binary relation on $\kappa^{+\omega}$ so that
-            $(\kappa^{+\omega},R_1)$ is isomorphic to $\mathbb P_0$. Let
-             $R_2$ be a binary relation on $\lambda$ so that
-             $R_2\cap (\kappa^{+\omega}\times \kappa^{+\omega})=R_1$ and
-             $(\lambda,R_2)$ is isomorphic to $\mathbb P_0*\mathbb P_1$.
-            Let $\psi$ be the poset isomorphism from $(\lambda,R_2)$ to
-             $\mathbb P_0*\mathbb P_1$.
-
-            We continue coding. We can code the sequence
-             $\{ h_\xi : \xi\in \lambda^{+\omega+1}\}$ as another binary  relation
-             $R_3$ on $\lambda^{+\omega+1}$ where $R_3\cap \left(\{\xi\}\times
-             \lambda^{+\omega+1}\right) = \{ (\xi,h_\xi(n) ) : n\in \omega\}$
-            for each $\xi\in \lambda^{+\omega+1}$. The relation symbol $R_4$ can
-            code the sequence $\{ \dot A_\xi : \xi \in \lambda^{+\omega+1}\}$
-            where $(\xi, \alpha, \zeta) \in R_4$ if and only if
-            $(\check \alpha, \psi(\zeta))$ is in the name $\dot A_\xi$.
-             Let $R_5$ code this collection, i.e.
-             $(\gamma,n,m,\eta)\in R_5$ if and only if
-             $(\check{(n,m)}, \psi(\eta))\in \dot H_\gamma$. Also let $R_6$ code
-             (equal)  the set $\Lambda$.
-            Finally we use the relation symbol $R_7$ to similarly code the
-            sequence $\{ \dot f_\xi  : \xi \in \lambda^{+\omega+1}\}$:
-             $(\xi, \alpha, n, \zeta) \in R_7$ if and only if
-            $(\check {(\alpha,n)}, \psi(\zeta))$ is in the name $\dot f_\xi$.
-
-            Needless to say, the unary relation symbol $R$
-            is interpreted as the set $\lambda^{+\omega}$ for the application of
-            $(\lambda^{+\omega+1},\lambda^{+\omega})\rlap{$\rightarrow$}\,{\rightarrow}
-            (\kappa^{+\omega+1},\kappa^{+\omega})$.
-             Now  we have defined our model
-            $M$  of the language $L= \{\in, R, R_0,\ldots, R_7\}$,
-             and we choose an elementary submodel
-            $N$ witnessing
-            $(\lambda^{+\omega+1},\lambda^{+\omega})\rlap{$\rightarrow$}\,{\rightarrow}
-            (\kappa^{+\omega+1},\kappa^{+\omega})$. Of course $N$ is really just
-            a $\kappa^{+\omega+1}$ sized subset of $\lambda^{+\omega+1}$
-            with the additional property that $N\cap \lambda^{+\omega}$ has
-            cardinality $\kappa^{+\omega}$.  In the
-            forcing extension $N$ has cardinality $\omega_1$ and
-             $A= N\cap \lambda^{+\omega}$ is countable.
-
-            We will need the following claim from \cite{MR1045371}:
-
-            \begin{claim*} We may assume that $N$ satisfies that
-             $N\cap \kappa^{+\omega+1}$ is transitive (i.e. an initial segment).
-            \end{claim*}
-
-            \bgroup
-            \def\proofname{Proof of Claim:\/}
-
-            \begin{proof}
-            Suppose  our originally supplied $N$ fails the conclusion of the
-            claim.
-            We   know that $\kappa^{+\omega}\in N$,
-            (  via $R_1$)
-            in which case so is $\kappa^{+\omega+1}$.
-
-            Then set $\beta_0 = \sup(N\cap \kappa^{+\omega+1})$ and consider the
-            Skolem closure $\mathop{Hull}(N\cup \beta_0, M)$.  A little informally
-            (in that we have to formalize the enumeration of formulas as per
-            G\"odel coding)
-            let $\{\varphi_n : n\in \omega\}$ be an enumeration of all formulas
-            in the language $L$, and let  $\ell_n$ be the minimal integer such
-            that the free variables of $\varphi_n$ are among
-             $\{ v_0, \ldots, v_{\ell_n}\}$.
-            Then,   for each tuple
-            $\langle \xi_1,\ldots, \xi_{\ell_n} \rangle$
-            of elements of $\lambda^{+\omega+1}$,
-             we define $f_n(\xi_1,\ldots, \xi_{\ell_n})$ to be
-             the minimal $\xi_0\in \lambda^{+\omega+1}$ such that
-             $M\models \varphi_n(\xi_0,\ldots, \xi_{\ell_n})$.
-            If there is no such $\xi_0$,
-               in other words if $M\models \lnot\exists x~~  \varphi_n(x,\xi_1,
-            \ldots,\xi_{\ell_n})$, then set
-             $f_n(\xi_1,\ldots, \xi_{\ell_n})$ to be $0$.
-            Now $\mathop{Hull}(N\cup \beta_0,M)$ is just the minimal superset
-             $X$
-            of $N\cup \beta_0$ that satisfies that
-             $f_n[X^{\{1,\ldots,\ell_n\}}] \subset X$ for all $n$. Since this is
-             simply a large algebra, we can generate all the terms $t$ of
-            the algebraic operations $\{ f_n : n\in \omega\}$.
-            It is easily seen that for each $\zeta \in X$, there is a term
-            $t(v_1,\ldots, v_m)$ such that $\zeta  = t(\delta_1,\ldots, \delta_m)$
-             for some sequence $\langle \delta_1,\ldots, \delta_m\rangle$ with
-             each $\delta_i\in  N\cup \beta_0$.
-             Assume that
-              $\zeta\in \kappa^{+\omega+1}$. By
-              re-indexing the variables in the term we can assume
-              that there is an $n\leq m$ so that
-               $\delta_i  <\beta_0$ for $1\leq i\leq n$
-                and $\kappa^{+\omega+1}\leq \delta_i$ for $n<i\leq m$.
-                Let $\vec a $ denote
-                the tuple $\langle \delta_{n+1},\ldots, \delta_m\rangle$.
-              Choose $\eta\in N\cap \kappa^{+\omega+1}$ large enough so that
-             $ \{  \delta_1, \ldots, \delta_n\}$ is contained in  $\eta$. Since set-membership
-             in $M$ is coded by $R_0$ rather than $\in$ we have to argue a little
-             less naturally.
-             Consider the set
-               $s_0(\eta,\vec a) = \{ t(\gamma_1,\ldots, \gamma_n,\vec a) :
-            \{\gamma_1,\cdots,\gamma_n\} \in [\eta]^{\leq n}\}$. Clearly
-             $s_0(\eta,\vec a)$ is a member of $H(\lambda^{+\omega+1})$.
-             Now define $s_1(\eta,\vec a) $ to be
-             $\{ x_\alpha : \alpha\in s_0(\eta, \vec a)\}$,
-             and choose the
-             unique $\zeta_1\in \lambda^{+\omega+1}$ such
-             that $x_{\zeta_1} = s_1(\eta,\vec a)$. We claim that $\zeta_1\in N$.
-             Note that $\alpha R_0\zeta_1$ holds if and only if
-              $ \alpha \in s_0(\eta,\vec a)$, and therefore
-             $$M\models (\forall \alpha)\left[\alpha R_0 \zeta_1 ~~\mbox{iff}~~
-             (\exists   \gamma_1\in \eta)\cdots(\exists \gamma_n\in\eta)(\alpha=
-             t(\gamma_1,\ldots, \gamma_n,\vec a))\right]~.$$
-             By elementarity then we have that $\zeta_1\in N$,
-             and by similar reasoning the supremum, $\zeta_0$,
-            of $\zeta_1\cap \kappa^{+\omega+1}$ is also in $N$.
-               This of course means that $\zeta < \xi_0$.
-            \end{proof}
-
-            \egroup
-
-            We use the elementarity of
-             $N$  to deduce properties of the families
-             $\{ \dot A_\xi : \xi\in N\}$ and $\{ \dot f_\xi : \xi \in
-             N\}$.  Actually the collection we are most interested in
-             is the family $\{ h_\xi : \xi\in \Lambda\cap N\}$.
-
-            Now we need a result from Shelah's pcf theory which
-            is proven in  Jech \cite[24.9]{MR1940513}.
-             Since  $\aleph_1=\mathfrak c < \kappa^{+\omega+1}$ there
-              is a function $\langle \varrho_n : n\in \omega\rangle$
-              in $\Pi_n \lambda^{+\omega}   $ such that the sequence
-               $\{ h_\xi : \xi \in N\}$ is unbounded mod finite
-               in $\Pi_n \varrho_n$
-               For each $n$, $\varrho_n \leq \sup(N\cap \lambda^{+n+2})$.
-                  Since $\mathbb P_0$ has cardinality $\kappa^{+\omega}$,
-            and so less than $|N|=\kappa^{+\omega+1}$, a standard argument
-            (analogous to the fact that adding a Cohen real does
-             not add a dominating real)
-             shows that    the sequence $\{ h_\xi : \xi \in \Lambda\cap N\}$ remains
-             unbounded
-                mod finite in $\Pi_n \varrho_n$ (and in
-                 $\Pi_n (\varrho_n\cap N)$).
-
-            Now pass to the extension by
-                  $G\cap \mathbb P_0$ and let $H$ be the function
-                   $\operatorname{val}_{G}(\dot H)$, and we recall
-                   that $f_{\zeta_\xi}(h_\xi(n)) = H(n)$ for all $n\in \omega$
-            and $\xi\in \Lambda$.
-             Now pass to the full extension $V[G]$ and again, since
-              $\mathbb P_1$ was forced to be countably closed,
-               the family $\{ h_\xi : \xi \in \Lambda\cap N\}$ is still
-               unbounded in $\Pi_n (\varrho_n \cap N)$ (no new elements
-            were added). We let
-               $A$ be the countable set $N\cap \lambda^{+\omega}$,
-               and for  each
-               $\xi\in \Lambda\cap N$, there is an $n_\xi$ such that
-                $f_{\xi}(h_\xi(m)) = f_A(h_\xi(m))$ for all $m>n_\xi$.
-                There is a single $n$ so that $\Lambda_n
-                 = \{\xi\in \Lambda\cap N       : n_\xi = n\}$ has cardinality
-                  $\omega_1 $, and thus
-                  $\{ h_\xi : \xi\in \Lambda_n\cap N\}$ is also unbounded
-                  in $\Pi_n (\rho_n\cap N)$.
-            This certainly implies that there is an $m>n$
-            such that $\{ h_\xi (m) : \xi\in \Lambda_n\cap N\}$ is infinite.
-            This completes the proof since  $f_{A}(h_\xi(m)) = H(m)$
-            for all $\xi\in \Lambda_n\cap N$.
-            \end{proof}
-
-  \section{Applications to infinite length games}
-
-  We introduce three variations of Scheeper's game which we defined in
-  the introduction.
-
-  \begin{game}
-    Let \(\schFillGame\kappa\) denote the
-    \term{Scheepers countable-finite union game} which proceeds analogously
-    to \(\schFillStrictGame\kappa\), except that \(\pl C\)'s restriction in round \(n+1\)
-    is weakened to \(C_{n+1}\supseteq C_n\).
-  \end{game}
-
-  \begin{game}
-    Let \(\schFillInitialGame\kappa\) denote the
-    \term{Scheepers countable-finite initial game} which proceeds analogously
-    to \(\schFillGame\kappa\), except that \(\pl F\)'s winning condition is
-    weakened to \(\bigcup_{n<\omega}F_n\supseteq C_0\).
-  \end{game}
-
-  \begin{game}
-    Let \(\schFillIntGame\kappa\) denote the
-    \term{Scheepers countable-finite intersection game} which proceeds analogously
-    to \(\schFillInitialGame\kappa\), except that \(\pl C\) may choose any
-    \(C_n\in[\kappa]^{\leq\omega}\) each round, and \(\pl F\)'s winning condition
-    is weakened to
-    \(\bigcup_{n<\omega}F_n\supseteq\bigcap_{n<\omega}C_n\).
-  \end{game}
-
-  In \cite{clontzMengerGamePreprint} Clontz extended Scheepers' application of
-  almost-compatible injections to these game variants as well as
-  \(\menGame{\oneptlind\kappa}\). However, when considering Markov strategies,
-  finite-to-one functions suffice.
-
-  \begin{figure}[h]
-\begin{center}
-\begin{tikzpicture}
-  \matrix (m) [matrix of math nodes,row sep=3em,column sep=1em,minimum width=2em]
-  {
-    &
-    \pl F \kmarkwin2\menGame{\oneptlind\kappa} &
-    \pl F \kmarkwin2\schFillIntGame\kappa \\
-
-    \alcompSP\kappa \\
-
-    &
-    \pl F \kmarkwin2\schFillInitialGame\kappa &
-    \pl F \kmarkwin2\schFillGame\kappa \\
-  };
-  \path[>=latex,->]
-    (m-2-1) edge (m-1-2)
-    (m-2-1) edge (m-3-2)
-    (m-1-2) edge (m-3-2)
-    (m-1-3) edge (m-3-3);
-  \path[>=latex,<->]
-    (m-1-2) edge (m-1-3)
-    (m-3-2) edge (m-3-3);
-\end{tikzpicture}
-\end{center}
-\caption{Diagram of Scheeper/Menger game implications with \(\alcompSP{\kappa}\)}
-\label{GamesDiagram2}
-\end{figure}
-
-%   \begin{figure}[h]
-% \begin{center}
-% \begin{tikzpicture}
-%   \matrix (m) [matrix of math nodes,row sep=3em,column sep=1em,minimum width=2em]
-%   {
-%     &
-%     \pl F \kmarkwin2\menGame{\oneptlind\kappa} &
-%     \pl F \kmarkwin2\schFillIntGame\kappa \\
-
-%     \alcompSP\kappa &
-%     \pl F \kmarkwin2\schFillInitialGame\kappa &
-%     \pl F \kmarkwin2\schFillGame\kappa \\
-
-%     &
-%     &
-%     \pl F \ktactwin2\schFillStrictGame\kappa \\
-%   };
-%   \path[>=latex,->]
-%     (m-2-1) edge (m-1-2)
-%     (m-2-1) edge (m-2-2)
-%     (m-2-1) edge (m-3-3)
-%     (m-1-2) edge (m-2-2)
-%     (m-1-3) edge (m-2-3)
-%     (m-3-3) edge (m-2-3);
-%   \path[>=latex,<->]
-%     (m-1-2) edge (m-1-3)
-%     (m-2-2) edge (m-2-3);
-% \end{tikzpicture}
-% \end{center}
-% \caption{Diagram of Scheeper/Menger game implications with \(\alcompSP{\kappa}\)}
-% \label{GamesDiagram2}
-% \end{figure}
-
-  \begin{theorem}
-    \(\alcompSP\kappa\) implies the game-theoretic conditions
-    shown in Figure \ref{GamesDiagram2}.
-  \end{theorem}
-
-  \begin{proof}
-    The weaker claim
-    \(\alcompS\kappa\Rightarrow\pl F \kmarkwin2\schFillIntGame\kappa\)
-    was proven in \cite{clontzMengerGamePreprint};
-    however, the strategy
-    only required that the \(f_A\) be pairwise almost-compatible and
-    that preimages of finite sets in each \(f_A\)
-    are finite, which is also possible assuming \(\alcompSP\kappa\).
-    Note that the relationships amongst the games were all shown in
-    \cite{clontzMengerGamePreprint}.
-  \end{proof}
-
-  We include the following proof from \cite{MR1129143} for the convenience
-  of the reader.
-
-  \begin{theorem}
-    \(\alcompS\kappa\Rightarrow\pl F \ktactwin2\schFillStrictGame\kappa\)
-  \end{theorem}
-
-  \begin{proof}
-    Let \(\{f_A:A\in[\kappa]^{\leq\aleph_0}\}\) witness
-    \(\alcompS\kappa\), and define \(g_A:A\to\omega\) by
-    \(g_A(\alpha)=f_A(\alpha)-|\{\beta\in A:f_A(\beta)<f_A(\alpha)\}|\).
-
-    We claim that \(\{\alpha\in A:g_A(\alpha)\leq g_B(\alpha)\}\)
-    must be finite as it is bounded above by
-    \(\max\{M,f_A(\alpha),f_B(\alpha):f_A(\alpha)\not=f_B(\alpha)\}\)
-    where \(M=f_B(\alpha)\) for some \(\alpha\in B\setminus A\).
-    To see this, let \(f_A(\alpha)=f_B(\alpha)=N>M\) and assume
-    \(f_A(\beta)\not=f_B(\beta)\) implies \(f_A(\beta),f_B(\beta)<N\).
-    Then
-    \[
-      g_A(\alpha)
-        =
-      N-|\{\beta\in A:f_A(\beta)<N\}|
-        >
-      N-|\{\beta\in B:f_B(\beta)<N\}|
-        =
-      g_B(\alpha)
-    \]
-    with the strictness of the inequality witnessed by \(f_B(\alpha)=M<N\)
-    for some \(\alpha\in B\setminus A\).
-
-    As a result,
-    \[
-      \sigma(\<A,B\>)
-        =
-      \{\alpha\in A:g_A(\alpha)\leq g_B(\alpha)\}
-    \]
-    is a legal \(2\)-tactic for \(\pl F\). Let \(C=\<C_0,C_1,\dots\>\) be
-    a strictly increasing sequence of countable sets and
-    \(\alpha\in C_n\). Noting that \(f_A\) is an injection and not
-    just finite-to-one, \(0\leq g_{C_{n+m}}(\alpha)\) for all
-    \(m<\omega\), and it follows that
-    \(g_{C_{n+m}}(\alpha)\leq g_{C_{n+m+1}}(\alpha)\) for some \(m<\omega\).
-    Therefore \(\alpha\in\sigma(\<C_{n+m},C_{n+m+1}\>)\).
-  \end{proof}
-
-  So it would seem that \(\alcompSP\kappa\) is sufficient only when
-  considering Markov strategies. (Of course,
-  \(\alcompSP\kappa\Rightarrow\pl F\kmarkwin2\schFillGame\kappa
-  \Rightarrow\pl F\kmarkwin2\schFillStrictGame{\kappa}\).)
-  We would like to demonstrate that \(\alcompSP\kappa\) is not
-  necessary.
-
-  \begin{theorem}
-    Let \(\alpha\) be the limit of increasing ordinals \(\beta_n\) for \(n<\omega\).
-    If \(\pl F \kmarkwin2\schFillIntGame{\aleph_{\beta_n}}\) for all
-    \(n<\omega\), then \(\pl F\kmarkwin2\schFillIntGame{\aleph_\alpha}\).
-  \end{theorem}
-
-  \begin{proof}
-    Let \(\sigma_n\) be a winning \(2\)-mark for \(\pl F\) in
-    \(\schFillIntGame{\aleph_{\beta_n}}\). Define the \(2\)-mark \(\sigma\)
-    for \(\pl F\) in \(\schFillIntGame{\aleph_\alpha}\) as follows:
-    \[
-      \sigma(\<C\>,0)
-        =
-      \sigma_0(\<C\cap\aleph_{\beta_0}\>,0)
-    \]
-    \[
-      \sigma(\<C,D\>,n+1)
-        =
-      \sigma_{n+1}(\<D\cap\aleph_{\beta_{n+1}}\>,0)
-        \cup
-      \bigcup_{m\leq n}
-      \sigma_m(\<C\cap\aleph_{\beta_m},D\cap\aleph_{\beta_m}\>,n-m+1)
-    \]
-
-    Let \(\<C_0,C_1,\dots\>\) be an attack by
-    \(\pl C\) in \(\schFillIntGame{\aleph_\alpha}\), and
-    \(\alpha\in\bigcap_{n<\omega}C_n\).
-    Choose \(N<\omega\) with \(\alpha<\aleph_{\beta_{N+1}}\). Consider the
-    attack
-    \(\<C_{N+1}\cap\aleph_{\beta_{N+1}},C_{N+2}\cap\aleph_{\beta_{N+1}},\dots\>\)
-    by \(\pl C\) in \(\schFillIntGame{\aleph_{\beta_{N+1}}}\). Since
-    \(\sigma_{N+1}\) is a winning strategy and
-    \(\alpha\in\bigcap_{n<\omega}C_{N+n+1}\cap\aleph_{\beta_{N+1}}\), either
-    \(\alpha\in\sigma_{N+1}(\<C_{N+1}\cap\aleph_{\beta_{N+1}}\>,0)\) and thus
-    \(\alpha\in\sigma(\<C_N,C_{N+1}\>,N+1)\), or
-    \(
-      \alpha
-        \in
-      \sigma_{N+1}(
-        \<C_{N+M+1}\cap\aleph_{\beta_{N+1}},C_{N+M+2}\cap\aleph_{\beta_{N+1}}\>
-        ,M+1
-      )
-    \)
-    for some \(M<\omega\) and thus
-    \(
-      \alpha
-        \in
-      \sigma(
-        \<C_{N+M+1},C_{N+M+2}\>,
-        N+M+2
-      )
-    \). Thus \(\sigma\) is a winning strategy.
-  \end{proof}
-
-  \begin{theorem}
-    Let \(\alpha\) be the limit of increasing ordinals \(\beta_n\) for \(n<\omega\).
-    If \(\pl F \kmarkwin2\schFillInitialGame{\aleph_{\beta_n}}\) for all
-    \(n<\omega\), then \(\pl F\kmarkwin2\schFillInitialGame{\aleph_\alpha}\).
-  \end{theorem}
-
-  \begin{proof}
-    The proof proceeds nearly identically to the previous proof.
-  \end{proof}
-    % Let \(\sigma_n\) be a winning \(2\)-mark for \(\pl F\) in
-    % \(\schFillInitialGame{\omega_{\beta_n}}\). Define the \(2\)-mark \(\sigma\)
-    % for \(\pl F\) in \(\schFillInitialGame{\omega_\alpha}\) as follows:
-    % \[
-    %   \sigma(\<C\>,0)
-    %     =
-    %   \sigma_0(\<C\cap\omega_{\beta_0}\>,0)
-    % \]
-    % \[
-    %   \sigma(\<C,D\>,n+1)
-    %     =
-    %   \sigma_{n+1}(\<D\cap\omega_{\beta_{n+1}}\>,0)
-    %     \cup
-    %   \bigcup_{m\leq n}
-    %   \sigma_m(\<C\cap\omega_{\beta_m},D\cap\omega_{\beta_m}\>,n-m+1)
-    % \]
-
-    % Let \(\<C_0,C_1,\dots\>\) be an attack by
-    % \(\pl C\) in \(\schFillInitialGame{\omega_\alpha}\), and
-    % \(\alpha\in C_0\).
-    % Choose \(N<\omega\) with \(\alpha<\omega_{\beta_{N+1}}\). Consider the
-    % attack
-    % \(\<C_{N+1}\cap\omega_{\beta_{N+1}},C_{N+2}\cap\omega_{\beta_{N+1}},\dots\>\)
-    % by \(\pl C\) in \(\schFillInitialGame{\omega_{\beta_{N+1}}}\). Since
-    % \(\sigma_{N+1}\) is a winning strategy and
-    % \(\alpha\in C_{N+1}\cap\omega_{\beta_{N+1}}\), either
-    % \(\alpha\in\sigma_{N+1}(\<C_{N+1}\cap\omega_{\beta_{N+1}}\>,0)\) and thus
-    % \(\alpha\in\sigma(\<C_N,C_{N+1}\>,N+1)\), or
-    % \(
-    %   \alpha
-    %     \in
-    %   \sigma_{N+1}(
-    %     \<C_{N+M+1}\cap\omega_{\beta_{N+1}},C_{N+M+2}\cap\omega_{\beta_{N+1}}\>
-    %     ,M+1
-    %   )
-    % \)
-    % for some \(M<\omega\) and thus
-    % \(
-    %   \alpha
-    %     \in
-    %   \sigma(
-    %     \<C_{N+M+1},C_{N+M+2}\>,
-    %     N+M+2
-    %   )
-    % \). Thus \(\sigma\) is a winning strategy.
-
-  \begin{corollary}
-    It is consistent that \(\alcompSP{\aleph_\omega}\) fails,
-    but as \(\alcompSP{\aleph_k}\) holds in \(ZFC\) for all \(k<\omega\),
-    both
-    \(\pl F\kmarkwin2\schFillIntGame{\aleph_\omega}\) and
-    \(\pl F\kmarkwin2\schFillInitialGame{\aleph_\omega}\) hold in \(ZFC\).
-  \end{corollary}
-
-  Note that Question \ref{mainQuestion} remains unsolved; however,
-  our results have revealed that we cannot hope to find a \(ZFC\)
-  counterexample where \(X=\oneptlind\kappa\). This is
-  because if we also assume \(V=L\), it follows that
-  \(\alcompSP{\kappa}\) and therefore \(\pl F\kmarkwin2\menGame{X}\)
-  for every cardinal. Although, one may consider the following weaker question.
-
-  \begin{question}
-    Is there a model of \(ZFC\) where both
-    \(\pl F\kmarkwin2\menGame{\oneptlind{\aleph_{\omega+1}}}\) and
-    \(\alcompSP{\aleph_\omega}\) fail?
-  \end{question}
-
-  % \section{Generalized Kurepa families and almost-compactible functions}
-
-  % TODO
-
 \bibliographystyle{plain}

### 2016-05-07 articles/lexicographical-products-and-idempotent-inverse-limits/article.tex
add a few preliminary results on generalized lexicographic products

@@
 \author{Steven Clontz}
-\address{Department of Mathematics and Statistics, UNC Charlotte}
+\address{Department of Mathematics and Statistics, The University of South Alabama}
 \email{steven.clontz@gmail.com}
@@
   the compactification \(\hat L\) and \(X\). A special case of
-  this fact is used to show that when \(f\) is any nontrivial
-  idempotent bonding relation and \(L\) is uncountable,
+  this fact is used to show that when \(f\) satisfies condition \(\Gamma\)
+  and \(L\) is uncountable,
   the inverse limit \(\varprojlim\{X,f,L\}\) cannot be Corson compact,
@@
 
+All topological spaces are assumed to be \(T_1\).
+
+\begin{definition}
+  Let \(L, M\) be total orders. Define their \term{lexicographic product}
+  \(L\lexTimes M\) by the total ordering \(\<l,m\><\<l',m'\>\) if and
+  only if \(l<l'\) or both \(l=l'\) and \(m<m'\).
+\end{definition}
+
+\begin{definition}
+  Let \(L\) be a total order, and let \(X\) be a topological space with
+  two distinguished points \(0,1\). Define their \term{generalized lexicographic
+  product} \(L\glTimes X\) to have the topology generated by the following
+  neighborhood bases:
+  \begin{itemize}
+    \item For \(l\in L\) and \(t\in X\setminus\{0,1\}\), \(\<l,t\>\) has
+      neighborhoods of the form \(\{l\}\times U\setminus\{0,1\}\) for all
+      neighborhoods \(U\) of \(t\) in \(X\).
+    \item For non-minimal \(l\in L\), \(\<l,0\>\) has neighborhoods of the form
+    \(
+      (\{l^-\}\times V\setminus\{0\})
+        \cup
+      ((l^-,l)\times X)
+        \cup
+      (\{l\}\times U\setminus \{1\})
+    \)
+      such that \(l^-<l\), \(U\) is a neighborhood of \(0\) in \(X\), and \(V\)
+      is either empty or a neighborhood of \(1\) in \(X\).
+    \item For \(l=\min L\), \(\<l,0\>\) has neighborhoods of the form
+    \(
+      (\{l\}\times U\setminus \{1\})
+    \)
+      such that \(U\) is a neighborhood of \(0\) in \(X\).
+    \item For non-maximal \(l\in L\), \(\<l,1\>\) has neighborhoods of the form
+    \(
+      (\{l\}\times V\setminus\{0\})
+        \cup
+      ((l,l^+)\times X)
+        \cup
+      (\{l^+\}\times U\setminus \{1\})
+    \)
+      such that \(l<l^+\), \(U\) is either empty or a neighborhood of \(0\) in
+      \(X\), and \(V\) is a neighborhood of \(1\) in \(X\).
+    \item For \(l=\max L\), \(\<l,1\>\) has neighborhoods of the form
+    \(
+      (\{l\}\times V\setminus \{0\})
+    \)
+      such that \(V\) is a neighborhood of \(1\) in \(X\)
+  \end{itemize}
+\end{definition}
+
+\begin{proposition}
+  Let \(L,M\) be LOTS such that \(M\) has distinguished points \(0=\min M\)
+  and \(1=\max M\). Then \(L\glTimes M \cong L\lexTimes M\).
+\end{proposition}
+
+\begin{definition}
+  Let \(X\) be a topological space with
+  two distinguished points \(0,1\). Define \(\gamma\subseteq X^2\) to be the
+  idempotent bonding relation defined by \(\gamma(0)=X\) and
+  \(\gamma(t)=\{1\}\) for all \(t\in X\setminus\{0\}\).
+\end{definition}
+
+\begin{theorem}
+  Let \(L\) be a total order, and let \(X\) be a topological space with
+  two distinguished points \(0,1\). Then
+  \(\inverseLimit{X,\gamma,L}=(\hat L\glTimes X)/\sim\), where the
+  equivalence relation \(\sim\) is given by
+  \begin{itemize}
+    \item \(\<A,t\>\sim\<A,1\>\) for all \(A\in\hat L\setminus \dot L\).
+    \item \(\<A,1\>\sim\<B,0\>\) whenever \(|B\setminus A|=1\).
+  \end{itemize}
+\end{theorem}
+
+\begin{proof}
+  We first observe that for \(\vec x\in\inverseLimit{X,\gamma,L}\) there
+  exists a maximal left-closed set
+  \(A_{\vec x}\in\hat L\) such that \(\vec x[\interior A_{\vec x}]=\{1\}\)
+  and \(\vec x[\exterior A_{\vec x}]=\{0\}\). Note that if \(A_{\vec x}\) has
+  a maximum element, i.e. \(A_{\vec x}\in \dot L\),
+  then \(\vec x(\max A_{\vec x})\) may be valued at almost any point of \(X\).
+  The lone exception occurs when \(\max A_{\vec x}\) has a successor in \(L\);
+  \(\vec x(\max A_{\vec x})=1\) would then violate the maximality of
+  \(A_{\vec x}\).
+
+  Define \(\theta:\inverseLimit{X,\gamma,L}\to(\hat L\glTimes X)/\sim\)
+  by \(\theta(\vec x)=\<A_{\vec x},1\>\) whenever
+  \(A_{\vec x}\in\hat L\setminus \dot L\), and
+  \(\theta(\vec x)=\<A_{\vec x},\vec x(\max A_{\vec x})\>\) otherwise.
+  It's then evident from our construction of \(A_{\vec x}\)
+  that \(\theta\) is a bijection.
+
+  Let \(B=(\leftarrow,l]\in\dot L\). If \(t\in X\setminus\{0,1\}\), note
+  \(\<B,t\>\) has a base of neighborhoods of
+  the form \(\{B\}\times U\setminus\{0,1\}\) which is equal to
+  \(\theta[\pi_l^{-1}[U\setminus\{0,1\}]]\).
+
+  Suppose \(|B\setminus A|=1\) for \(A=(\leftarrow,k]\in\dot L\).
+  Then \(\<B,0\>\) has a base of neighborhoods of the form
+  \(
+    (\{A\}\times V\setminus\{0\})
+      \cup
+    (\{B\}\times U\setminus \{1\})
+  \), which is equal to
+  \(\theta[\pi_k^{-1}[V\setminus\{0\}]]\cap\theta[\pi_l^{-1}[U\setminus\{1\}]]\).
+
+\end{proof}
+
 \bibliographystyle{plain}

### 2016-09-06 articles/almost-compatible-functions-and-topological-games/article.tex
minor revisions from referee

@@
             \tau\in M\ \}$.  We will be using
-            the forcing poset is $\operatorname{Fn}(\omega_2, 2)$.
+            the forcing poset $\operatorname{Fn}(\omega_2, 2)$.
             The elements of this poset are all the finite partial functions
@@
              $\varphi_{\mu,\lambda}(\dot f_{[\lambda,\lambda+\omega)})$, call it $F_H$.
-            Here simply, for each tuple $(\,(k,m), p)\in \dot
+            Here simply, for each tuple $(\,(\lambda+k,m), p)\in \dot
             f_{[\lambda,\lambda+\omega)}$,
-             we have that $(\,(k,m),\varphi_{\mu,\lambda}(p))$ is in $F_H$.
+             we have that $(\,(\mu+k,m),\varphi_{\mu,\lambda}(p))$ is in $F_H$.
             Again, let $\varphi_{\mu,\lambda}(\dot f_{[\lambda,\lambda+\omega)})$
@@
              $(\aleph_{\omega+1},\aleph_\omega) \rlap{$\rightarrow$}\,{\rightarrow}
-             (\aleph_1,\aleph_0)$ is shown to fail.
+             (\aleph_1,\aleph_0)$ is shown to hold.
 
@@
              $\mathbb P_1$ has cardinality $\lambda$. We treat
-            $\mathbb P*\mathbb P_1$ as containing $\mathbb P_0$
+            $\mathbb P_0*\mathbb P_1$ as containing $\mathbb P_0$
             as a subposet by identifying each $(p_0,1)$ with $p_0$.
@@
              $\mathbb P_0*\mathbb P_1$-name of a countable subset of
-             $\lambda^{+\omega+1}$. We will obtain a contradiction.
+             $\lambda^{+\omega+1}$. We will obtain a contradiction
+             to the claim of coherence.
 
@@
             of $\zeta_1\cap \kappa^{+\omega+1}$ is also in $N$.
-               This of course means that $\zeta < \xi_0$.
+               This of course means that $\zeta < \beta_0$.
             \end{proof}
@@
 
-  \begin{figure}[h]
+  \begin{figure}[ht]
 \begin{center}
@@
     by \(\pl C\) in \(\schFillIntGame{\aleph_{\beta_{N+1}}}\). Since
-    \(\sigma_{N+1}\) is a winning strategy and
+    \(\sigma_{N+1}\) is a winning \(2\)-mark and
     \(\alpha\in\bigcap_{n<\omega}C_{N+n+1}\cap\aleph_{\beta_{N+1}}\), either
@@
       )
-    \). Thus \(\sigma\) is a winning strategy.
+    \). Thus \(\sigma\) is a winning \(2\)-mark.
   \end{proof}
@@
   \begin{proof}
-    The proof proceeds nearly identically to the previous proof.
+    The proof proceeds nearly identically to the previous proof: substitute
+    \(\alpha\in C_0\) in place of \(\alpha\in\bigcap_{n<\omega}C_n\) and proceed.
   \end{proof}

### 2016-09-06 articles/almost-compatible-functions-and-topological-games/article.tex
improve the final question, reflecting reviewer feedback
more work on the paper ending

@@
 
-  \begin{corollary}[\(V=L\)]
+  \begin{corollary}[\(V=L\)]\label{alcompSPunderV=L}
     \(\alcompSP{\kappa}\) for all cardinals \(\kappa\).
@@
 
-  Note that Question \ref{mainQuestion} remains unsolved; however,
-  our results have revealed that we cannot hope to find a \(ZFC\)
-  counterexample where \(X=\oneptlind\kappa\). This is
-  because if we also assume \(V=L\), it follows that
+  We conclude by returning our attention to Question \ref{mainQuestion},
+  which asks whether there exists a space for which the second player
+  \(\pl F\) in the Menger game \(\menGame{X}\) has a winning strategy
+  without a winning \(2\)-mark.
+
+  \begin{question}
+    Does
+    \(\pl F\kmarkwin2\schFillIntGame{\kappa}\) hold for all cardinals
+    \(\kappa\) in ZFC?
+  \end{question}
+
+  If not, the model producing \(\kappa>\aleph_\omega\) where
+  \(\pl F\notkmarkwin2\schFillIntGame{\kappa}\) yields a positive
+  answer to Question \ref{mainQuestion}:
+  \(X=\oneptlind{\kappa}\). On the other hand, under \(V=L\)
+  Corollary \ref{alcompSPunderV=L} shows that
   \(\alcompSP{\kappa}\) and therefore
   \(\pl F\kmarkwin2\menGame{\oneptlind\kappa}\)
-  for every cardinal \(\kappa\).
-  Although, one may consider the following question.
+  for every cardinal \(\kappa\), so a more exotic example than
+  \(X=\oneptlind{\kappa}\) would be required to
+  answer Question \ref{mainQuestion} in \(ZFC\).
+
+  Solving the following weaker question would not answer Question
+  \ref{mainQuestion} by itself, but an solution would be interesting nonetheless.
 
   \begin{question}
-    Is there a model of \(ZFC\) where both
-    \(\pl F\kmarkwin2\menGame{\oneptlind{\aleph_{\omega+1}}}\) and
-    \(\alcompSP{\aleph_\omega}\) fail?
+    Does
+    \(\pl F\kmarkwin2\schFillGame{\kappa}\) hold for all cardinals
+    \(\kappa\) in ZFC?
   \end{question}

### 2016-09-08 articles/almost-compatible-functions-and-topological-games/article.tex
many many revisions to address the referee's concerns

@@
 \usepackage{tikz}
-\usetikzlibrary{matrix}
+% \usetikzlibrary{matrix}
+\usetikzlibrary{arrows}
 
@@
 \author{Steven Clontz}
-\address{Department of Mathematics and Statistics, UNC Charlotte,
-Charlotte, NC 28262}
+\address{Department of Mathematics and Statistics,
+The University of South Alabama,
+Mobile, AL 36606}
 \email{steven.clontz@gmail.com}
@@
     The statement \(\alcompS\kappa\) (given as \(S(\kappa,\aleph_0,\omega)\)
-    in \cite{MR1129143} and \(S(\kappa)\) in \cite{clontzMengerGamePreprint})
+    in \cite{MR1129143})
     claims that there exist one-to-one functions
@@
 
-  In the same paper, Scheepers noted that \(\alcompS{\omega_1}\) holds in \(ZFC\),
+  In \cite{MR1129143}, Scheepers noted that \(\alcompS{\omega_1}\) holds in \(ZFC\),
   and that it's possible to force \(\mf c\) to be arbitrarily large
@@
 
-  In the next section we will show that \(\alcompSP{\kappa}\) is sufficient
-  for the applications to the Scheepers and Menger games.
+  In the final section we will show that \(\alcompSP{\kappa}\) is sufficient
+  for many applications to the Scheepers and Menger games.
   In the meantime, we will demonstrate that \(\alcompSP{\kappa}\) is strictly
@@
   We now construct a topology on \(\omega_n\) for each \(n<\omega\) which
-  will witness a Kurepa family of size \(\aleph_n\). A similar construction
-  was previously shown by Juh\'asz et. al. in \cite{MR539228},
-  and the relationship of
-  Kurepa families and such spaces has also been investigated in a preprint
-  of Nyikos \cite{NYIKOSKUREPA}.
-
-  \begin{proposition}
-    Let \(X\) be a \(T_2\) space with a base of countable and compact
-    neighborhoods. Then \(X\) is locally metrizable with
-    a base of compact open countable sets.
-  \end{proposition}
-
-  \begin{proof}
-    For each point \(x\) let \(K\) be a countable and compact neighborhood
-    of \(x\), and it follows that it is contained in a countable, open,
-    and locally compact neighborhood \(W\) of \(x\), which in turn
-    is zero-dimensional and metrizable. So choose \(V\) clopen
-    in \(W\) such that \(x\in V\subseteq K\); \(V\) is a compact open
-    neighborhood of \(x\) in \(X\).
-  \end{proof}
+  will witness a Kurepa family of size \(\aleph_n\), exploiting a theorem of
+  Juh\'asz et. al. in \cite{MR539228}.
 
@@
 
-  \begin{proposition}
-    Let \(X\) be a \(T_2\) space with cardinality less than \(\aleph_\omega\)
-    which is locally countable and
-    \(\omega\)-bounded. Then the closure operation preserves cardinality and
-    weight.
-  \end{proposition}
-
-  \begin{proof}
-    Note that the closure of any countable neighborhood is compact, and
-    any Lindel\"of set is countable. This space is locally metrizable
-    and thus first-countable, so cardinality and weight coincide for any
-    subspace. The result is obvious if \(A\) is countable; otherwise
-    let \(A=\{a_\alpha:\alpha<\omega_{n+1}\}\) and since basic neighborhoods
-    are countable note any limit point of \(A\) is
-    a limit point of \(A_\beta=\{a_\alpha:\alpha<\beta\}\)
-    for some \(\beta<\omega_{n+1}\).
-    Thus \(\cl A=\bigcup_{\beta<\omega_{n+1}}\cl{A_\beta}\) and
-    by induction \(|\cl A|=|A|\).
-  \end{proof}
-
-  \begin{lemma}
-    Let \(X\) be a \(T_2\) space with cardinality less than \(\aleph_\omega\)
-    which is locally countable and locally compact, and such that
-    its closure operation preserves cardinalities.
-    Then \(X\) has an \(\omega\)-bounded extension \(\tilde X\)
-    with the same properties where \(\tilde X\setminus X\) has the same
-    cardinality as \(X\).
-  \end{lemma}
-
-  \begin{proof}
-    We prove this by induction on \(n\).
-    If \(n=0\), then we can just use the one-point compactification of two
-    copies of \(X\). So suppose \(n>0\) and
-    that \(X=\omega_n\) has an appropriate topology. Note that \(X\) has
-    a base of countable and compact neighborhoods since the closure operation
-    preserves cardinalities.
-
-    For each \(\alpha<\omega_n\), \(\gamma_\alpha\) may be chosen such that
-    both the closure of the set \(\alpha\) in \(X\) and a countable
-    neighborhood of the point \(\alpha\) are subsets of \(\gamma_\alpha\).
-    Note that the set
-    \(\{\lambda<\omega_n:\alpha<\lambda\Rightarrow\gamma_\alpha<\lambda\}\)
-    is a cub subset of \(\omega_n\) containing a cub subset \(C\)
-    of limit ordinals.
-    Now for each \(\lambda\in C\), the set \(\lambda\) is
-    open as \(\alpha<\lambda\) belongs to the neighborhood
-    \(\gamma_\alpha\subsetneq\lambda\). Also, if \(\lambda\) has uncountable
-    cofinality, then for \(\beta\geq\lambda\) and any countable neighborhood
-    \(U\) of \(\beta\), \(U\cap\lambda=U\cap\alpha\)
-    for some \(\alpha<\lambda\); thus \(U\setminus\cl\alpha=U\setminus\lambda\)
-    is a neighborhood of \(\beta\), showing that \(\lambda\)
-    is clopen.
-
-    Let \(\tilde X=\omega_n\times 2\).
-    By induction on \(\lambda \in C\) we will define compatible topologies
-    for \(\tilde X_\lambda=\omega_n\times\{0\}\cup\lambda\times\{1\}\)
-    such that
-    \begin{itemize}
-      \item \(\omega_n \times \{0\}\) is an open copy of \(X\),
-      \item \(\lambda\times 2\) is open, and when \(\cf\lambda>\omega\) also closed,
-      \item the space has a base of countable and compact neighborhoods, and
-      \item when \(\lambda\) is a successor,
-        for each \(\alpha<\lambda\) the closure of \(\alpha\times 2\) is
-        an \(\omega\)-bounded  subset of \(\lambda\times 2\).
-    \end{itemize}
-
-    We first consider the case \(n=1\).
-    If \(\lambda\) is a limit in \(C\), then
-    \(
-      \tilde X_\lambda
-        =
-      \bigcup_{\mu\in C\cap\lambda}\tilde X_\mu
-    \)
-    satisfies the induction requirements.
-    Otherwise we choose an increasing sequence of
-    ordinals \(\{\alpha_k : k\in \omega\}\) with limit \(\lambda\)
-    such that \(\alpha_0\) is the predecessor of \(\lambda\) in \(C\),
-    or \(\alpha_0=0\) if \(\lambda\) is the least element of \(C\).
-
-    The subspace \(\cl\lambda\times\{0\}\cup\alpha_0\times2\) of \(X\)
-    is countable and locally compact; therefore it is
-    metrizable and zero-dimensional.
-    So we may choose increasing sets \(U_k\) for \(k<\omega\) which are
-    clopen in this topology and satisfy
-    \[
-      \cl{\alpha_k\times\{0\}\cup\alpha_0\times2}
-        =
-      \cl{\alpha_k}\times\{0\}\cup\alpha_0\times2
-        \subseteq
-      U_k
-        \subseteq
-      \lambda\times\{0\}\cup\alpha_0\times 2
-    \]
-    Note that \(U_k\) is also clopen in \(\tilde X_{\alpha_0}\) since it is
-    closed in \(\cl\lambda\times\{0\}\cup\alpha_0\times2\) and open in
-    \(\lambda\times\{0\}\cup\alpha_0\times 2\).
-
-    We need only describe a base for the points
-    \(\<\alpha,1\>\in(\lambda\setminus\alpha_0)\times\{1\}\).
-    We do so by letting
-    \(\<\alpha,1\>\) be isolated when \(\alpha\not\in\{\alpha_k:k<\omega\}\),
-    and giving \(\<\alpha_k,1\>\) the open neighborhoods
-    \((U_k\cup((\alpha_k+1)\times\{1\}))\setminus K\) for each compact
-    subset \(K\) of \(U_k\cup(\alpha_k\times\{1\})\); that is,
-    \(\<\alpha_k,1\>\) is the one point compactifying
-    \(U_k\cup(\alpha_k\times\{1\})\).
-
-    The first two requirements of our inductive hypothesis are obviously
-    satsified. Note points in \(\lambda\times 2\) are covered by
-    the compact countable neighborhood \(U_k\cup((\alpha_k+1)\times\{1\})\)
-    for some \(k<\omega\), and for points in
-    \((\omega_n\setminus\lambda)\times\{0\}\) we may use a compact
-    countable neighborhood from \(X\).
-    For the final requirement, note that for \(\alpha<\lambda\), we may
-    choose \(\alpha<\alpha_k<\lambda\) and note that
-    \(\alpha\times 2\) is contained in the compact
-    subset \(U_k\cup((\alpha_k+1)\times\{1\})\) of \(\lambda\times2\).
-
-    For the case \(n>1\), we may assume that the successors in \(C\)
-    have uncountable cofinality.
-    We again proceed by induction on \(\lambda\in C\).  Again when
-    \(\lambda\) is a limit in \(C\),
-    \(
-      \tilde X_\lambda
-        =
-      \bigcup_{\mu\in C\cap\lambda}\tilde X_\mu
-    \)
-    satisfies the given
-    requirements; in particular if \(\alpha<\lambda\), then
-    \(\alpha<\mu<\lambda\) for some successor \(\mu\in C\) with uncountable
-    cofinality. As such, the closure of \(\alpha\times2\) is
-    an \(\omega\)-bounded subset of the clopen \(\mu\times 2\) and
-    therefore also of \(\lambda\times 2\).
-    In case \(\lambda\) is not a limit of \(C\), then \(\lambda\)
-    has uncountable cofinality and a predecessor \(\mu\in C\).
-    We therefore have that \(\lambda\times\{0\}\) is clopen
-    in \(\omega_n\times \{0\}\). Since the cardinality of
-    \(\lambda\times \{0\} \cup \mu\times 2\) is less than \(\aleph_n\),
-    we may simply apply the induction hypothesis
-    to choose an appropriate topology for \(\lambda\times 2\).
-
-    As a result, \(\tilde X=\bigcup_{\lambda\in C}\tilde X_\lambda\)
-    is
-    \(\omega\)-bounded as any countable set is contained in some
-    \(\alpha\times 2\) for \(\alpha<\lambda\in C\).
-  \end{proof}
-
-  \begin{theorem}
-    For each \(k< \omega\), there is a \(T_2\), locally countable,
-    \(\omega\)-bounded topology on \(\omega_k\). That is, \(\splendidS{\aleph_k}\)
-    for all \(k<\omega\).
+  \begin{theorem}[\cite{MR539228}]
+    \(\splendidS{\aleph_k}\) for \(k<\omega\).
   \end{theorem}
-
-  \begin{proof}
-    Apply the previous lemma to \(\omega_n\) with the discrete topology.
-  \end{proof}
 
@@
 
-  Weakening to the continuum hypothesis, we see an obvious consequence.
-
-  \begin{corollary}[\(CH\)]
-    \(\alcompSP{\mf c^+}\), but \(\neg\alcompS{\mf c^+}\).
-  \end{corollary}
-
-  But \(CH\) is not required to have \(\alcompS{\aleph_2}\) fail.
+  As noted earlier, Scheepers proved in \cite{MR1129143}
+  that \(\neg\alcompS{\mf c^+}\) is a theorem of ZFC, showing
+  \(\alcompSP{\kappa}\) is not equivalent to \(\alcompS{\kappa}\).
+
+  We now demonstrate that \(CH\) is not required to have \(\alcompS{\aleph_2}\)
+  fail.
 
@@
 \begin{center}
-\begin{tikzpicture}
-  \matrix (m) [matrix of math nodes,row sep=3em,column sep=1em,minimum width=2em]
-  {
-    &
-    \pl F \kmarkwin2\menGame{\oneptlind\kappa} &
-    \pl F \kmarkwin2\schFillIntGame\kappa \\
-
-    \alcompSP\kappa \\
-
-    &
-    \pl F \kmarkwin2\schFillInitialGame\kappa &
-    \pl F \kmarkwin2\schFillGame\kappa \\
-  };
-  \path[>=latex,->]
-    (m-2-1) edge (m-1-2)
-    (m-2-1) edge (m-3-2)
-    (m-1-2) edge (m-3-2)
-    (m-1-3) edge (m-3-3);
-  \path[>=latex,<->]
-    (m-1-2) edge (m-1-3)
-    (m-3-2) edge (m-3-3);
+\begin{tikzpicture}[x=0.8in,y=0.5in]
+  \node at (-3.5,2) {\(\alcompS\kappa\)};
+  \node at (-3.5,0) {\(\pl F \ktactwin2\schFillStrictGame\kappa\)};
+  \node at (0,2) {\(\alcompSP\kappa\)};
+  \node at (-1,1) {\(\pl F \kmarkwin2\menGame{\oneptlind\kappa}\)};
+  \node at (0,1) {\(\Leftrightarrow\)};
+  \node at (1,1) {\(\pl F \kmarkwin2\schFillIntGame\kappa\)};
+  \node at (-1,0) {\(\pl F \kmarkwin2\schFillInitialGame\kappa\)};
+  \node at (0,0) {\(\Leftrightarrow\)};
+  \node at (1,0) {\(\pl F \kmarkwin2\schFillGame\kappa\)};
+  \node at (0,-1) {\(\pl F \kmarkwin2\schFillStrictGame\kappa\)};
+  \draw[-implies,double equal sign distance] (-3.2,2) -- (-0.3,2);
+  \draw[-implies,double equal sign distance] (-2.6,0) -- (-1.9,0);
+  \draw[-implies,double equal sign distance] (-3.5,1.65) -- (-3.5,0.35);
+  \draw[-implies,double equal sign distance] (0,1.65) -- (0,1.35);
+  \draw[-implies,double equal sign distance] (0,0.65) -- (0,0.35);
+  \draw[-implies,double equal sign distance] (0,-0.35) -- (0,-0.65);
 \end{tikzpicture}
 \end{center}
-\caption{Diagram of Scheeper/Menger game implications with \(\alcompSP{\kappa}\)}
-\label{GamesDiagram2}
+\caption{Diagram of Scheeper/Menger game implications with \(\alcompS{\kappa},\alcompS{\kappa}\)}
+\label{GamesDiagram}
 \end{figure}
 
-%   \begin{figure}[h]
-% \begin{center}
-% \begin{tikzpicture}
-%   \matrix (m) [matrix of math nodes,row sep=3em,column sep=1em,minimum width=2em]
-%   {
-%     &
-%     \pl F \kmarkwin2\menGame{\oneptlind\kappa} &
-%     \pl F \kmarkwin2\schFillIntGame\kappa \\
-
-%     \alcompSP\kappa &
-%     \pl F \kmarkwin2\schFillInitialGame\kappa &
-%     \pl F \kmarkwin2\schFillGame\kappa \\
-
-%     &
-%     &
-%     \pl F \ktactwin2\schFillStrictGame\kappa \\
-%   };
-%   \path[>=latex,->]
-%     (m-2-1) edge (m-1-2)
-%     (m-2-1) edge (m-2-2)
-%     (m-2-1) edge (m-3-3)
-%     (m-1-2) edge (m-2-2)
-%     (m-1-3) edge (m-2-3)
-%     (m-3-3) edge (m-2-3);
-%   \path[>=latex,<->]
-%     (m-1-2) edge (m-1-3)
-%     (m-2-2) edge (m-2-3);
-% \end{tikzpicture}
-% \end{center}
-% \caption{Diagram of Scheeper/Menger game implications with \(\alcompSP{\kappa}\)}
-% \label{GamesDiagram2}
-% \end{figure}
-
   \begin{theorem}
-    \(\alcompSP\kappa\) implies the game-theoretic conditions
-    shown in Figure \ref{GamesDiagram2}.
+    Figure \ref{GamesDiagram}.
   \end{theorem}
@@
   \begin{proof}
-    The weaker claim
-    \(\alcompS\kappa\Rightarrow\pl F \kmarkwin2\schFillIntGame\kappa\)
-    was proven in \cite{clontzMengerGamePreprint};
-    however, the strategy
-    only required that the \(f_A\) be pairwise almost-compatible and
-    that preimages of finite sets in each \(f_A\)
-    are finite, which is also possible assuming \(\alcompSP\kappa\).
-    Note that the relationships amongst the games were all shown in
-    \cite{clontzMengerGamePreprint}.
+    \(\alcompS\kappa\Rightarrow\pl F \ktactwin2\schFillStrictGame\kappa\) was
+    shown by Scheepers in \cite{MR1129143} (also, see the following theorem).
+    Most of the other results in the figure were proven
+    in \cite{clontzMengerGamePreprint}, with the exception that
+    \(\alcompSP\kappa\) was not considered at the time.
+    The following proof that
+    \(\alcompSP\kappa\Rightarrow\pl F \kmarkwin2\schFillIntGame\kappa\)
+    is a trivial modification of the proof presented in
+    \cite{clontzMengerGamePreprint} assuming \(\alcompS\kappa\), but as
+    that paper is under review at the time
+    of this writing, we provide it here.
+
+    Let \(f_A\) for \(A\in[\kappa]^{\leq\omega}\) witness \(\alcompSP\kappa\).
+    We define a \(2\)-mark \(\sigma\) for \(\schFillIntGame\kappa\) as follows:
+      \[
+        \sigma(\<A\>,0) = \{\alpha\in A: f_A(\alpha) = 0 \}
+      \]
+      \[
+        \sigma(\<A,B\>,n+1)
+          =
+        \{
+          \alpha \in A\cap B
+        :
+          f_B(\alpha) \leq n+1 \text{ or }
+          f_A(\alpha)\not=f_B(\alpha)
+        \}
+      \]
+    For any attack \(\<A_0,A_1,\dots\>\) by \(\pl C\) and
+    \(\alpha\in\bigcap_{n<\omega}A_n\), either \(f_{A_n}(\alpha)\) is constant for
+    all \(n\), or \(f_{A_n}(\alpha)\not=f_{A_{n+1}}(\alpha)\) for some \(n\);
+    either way, \(\alpha\) is covered.
   \end{proof}
 
-  We include the following proof from \cite{MR1129143} for the convenience
-  of the reader.
-
-  \begin{theorem}
+  We include the following proof from \cite{MR1129143} to point
+  out why \(\alcompSP\kappa\) seems insufficient for providing \(\pl F\) a
+  winning \(2\)-tactic in \(\schFillStrictGame\kappa\), despite that it
+  witnesses a winning \(2\)-mark.
+
+  \begin{theorem}[\cite{MR1129143}]
     \(\alcompS\kappa\Rightarrow\pl F \ktactwin2\schFillStrictGame\kappa\)
@@
     a strictly increasing sequence of countable sets and
-    \(\alpha\in C_n\). Noting that \(f_A\) is an injection and not
-    just finite-to-one, \(0\leq g_{C_{n+m}}(\alpha)\) for all
+    \(\alpha\in C_n\).
+
+    Noting that \(f_A\) is an injection
+    (not just finite-to-one), \(0\leq g_{C_{n+m}}(\alpha)\) for all
     \(m<\omega\), and it follows that
@@
 
-  So it would seem that \(\alcompSP\kappa\) is sufficient only when
-  considering Markov strategies. (Of course,
-  \(\alcompSP\kappa\Rightarrow\pl F\kmarkwin2\schFillGame\kappa
-  \Rightarrow\pl F\kmarkwin2\schFillStrictGame{\kappa}\).)
+  While the above proof cannot be trivially modified to utilize
+  the finite-to-one functions witnessed by
+  \(\alcompSP\kappa\) in constructing a winning \(2\)-tactical strategy
+  for \(\schFillStrictGame{\kappa}\), whether
+  \(\alcompSP\kappa\) is sufficient for
+  \(\pl F\ktactwin2\schFillStrictGame{\kappa}\) after all
+  does remain open:
+
+  \begin{question}
+    May the previous theorem be improved by replacing \(\alcompS\kappa\)
+    with \(\alcompSP\kappa\)?
+  \end{question}
+
   We would like to demonstrate that \(\alcompSP\kappa\) is not
-  necessary.
+  necessary for constructing winning \(2\)-Markov strategies in
+  \(\schFillIntGame\kappa\).
 
@@
   \end{proof}
-    % Let \(\sigma_n\) be a winning \(2\)-mark for \(\pl F\) in
-    % \(\schFillInitialGame{\omega_{\beta_n}}\). Define the \(2\)-mark \(\sigma\)
-    % for \(\pl F\) in \(\schFillInitialGame{\omega_\alpha}\) as follows:
-    % \[
-    %   \sigma(\<C\>,0)
-    %     =
-    %   \sigma_0(\<C\cap\omega_{\beta_0}\>,0)
-    % \]
-    % \[
-    %   \sigma(\<C,D\>,n+1)
-    %     =
-    %   \sigma_{n+1}(\<D\cap\omega_{\beta_{n+1}}\>,0)
-    %     \cup
-    %   \bigcup_{m\leq n}
-    %   \sigma_m(\<C\cap\omega_{\beta_m},D\cap\omega_{\beta_m}\>,n-m+1)
-    % \]
-
-    % Let \(\<C_0,C_1,\dots\>\) be an attack by
-    % \(\pl C\) in \(\schFillInitialGame{\omega_\alpha}\), and
-    % \(\alpha\in C_0\).
-    % Choose \(N<\omega\) with \(\alpha<\omega_{\beta_{N+1}}\). Consider the
-    % attack
-    % \(\<C_{N+1}\cap\omega_{\beta_{N+1}},C_{N+2}\cap\omega_{\beta_{N+1}},\dots\>\)
-    % by \(\pl C\) in \(\schFillInitialGame{\omega_{\beta_{N+1}}}\). Since
-    % \(\sigma_{N+1}\) is a winning strategy and
-    % \(\alpha\in C_{N+1}\cap\omega_{\beta_{N+1}}\), either
-    % \(\alpha\in\sigma_{N+1}(\<C_{N+1}\cap\omega_{\beta_{N+1}}\>,0)\) and thus
-    % \(\alpha\in\sigma(\<C_N,C_{N+1}\>,N+1)\), or
-    % \(
-    %   \alpha
-    %     \in
-    %   \sigma_{N+1}(
-    %     \<C_{N+M+1}\cap\omega_{\beta_{N+1}},C_{N+M+2}\cap\omega_{\beta_{N+1}}\>
-    %     ,M+1
-    %   )
-    % \)
-    % for some \(M<\omega\) and thus
-    % \(
-    %   \alpha
-    %     \in
-    %   \sigma(
-    %     \<C_{N+M+1},C_{N+M+2}\>,
-    %     N+M+2
-    %   )
-    % \). Thus \(\sigma\) is a winning strategy.
 
@@
   which asks whether there exists a space for which the second player
-  \(\pl F\) in the Menger game \(\menGame{X}\) has a winning strategy
+  \(\pl F\) in the game \(\menGame{X}\) has a winning strategy
   without a winning \(2\)-mark.
@@
   Solving the following weaker question would not answer Question
-  \ref{mainQuestion} by itself, but an solution would be interesting nonetheless.
+  \ref{mainQuestion} by itself, but a solution would be interesting nonetheless.
 
@@
 
+  Although, it's still open whether the previous two questions are even
+  distinct.
+
+  \begin{question}
+    Can a winning \(2\)-Markov strategy in \(\schFillGame{\kappa}\)
+    be used to construct a winning \(2\)-Markov strategy in
+    \(\schFillIntGame{\kappa}\)?
+  \end{question}
+
 \bibliographystyle{plain}

### 2016-09-08 articles/almost-compatible-functions-and-topological-games/article.tex
remove contractions

@@
   and thus holds for all cardinals less than \(\aleph_\omega\).
-  It's consistent that \(\alcompSP{\aleph_\omega}\) fails, but
+  It is consistent that \(\alcompSP{\aleph_\omega}\) fails, but
   there must always be a winning \(2\)-Markov strategy for the second
@@
   In \cite{MR1129143}, Scheepers noted that \(\alcompS{\omega_1}\) holds in \(ZFC\),
-  and that it's possible to force \(\mf c\) to be arbitrarily large
+  and that it is possible to force \(\mf c\) to be arbitrarily large
   while preserving \(\alcompS{\mf c}\). However, \(\alcompS{\mf c^+}\) always fails.
@@
   in \cite{MR1378387}.
-  However, it's easily seen that these games are equivalent
+  However, it is easily seen that these games are equivalent
   for perfect information strategies (so both characterize
@@
   chooses a countable subset of \(\kappa\) followed by \(\pl F\) choosing
-  a finite subset of that choice, and it's easy to see the winning perfect
+  a finite subset of that choice, and it is easy to see the winning perfect
   information strategy for \(\pl F\) in both games.
@@
 
-  Although, it's still open whether the previous two questions are even
+  Although, it is still open whether the previous two questions are even
   distinct.

### 2016-10-11 articles/relating-games-menger-cft-ss/article.tex
start writing up M/CFT/SS results

\documentclass{amsart}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}

\usepackage{tikz}
% \usetikzlibrary{matrix}
\usetikzlibrary{arrows}

\usepackage{../../clontzDefinitions}

      \theoremstyle{plain}
      \newtheorem{theorem}{Theorem}
      \newtheorem{lemma}[theorem]{Lemma}
      \newtheorem{corollary}[theorem]{Corollary}
      \newtheorem{proposition}[theorem]{Proposition}
      \newtheorem{conjecture}[theorem]{Conjecture}
      \newtheorem{question}[theorem]{Question}
      \newtheorem{claim}[theorem]{Claim}

      \theoremstyle{definition}
      \newtheorem{definition}[theorem]{Definition}
      \newtheorem{notation}[theorem]{Notation}
      \newtheorem{example}[theorem]{Example}
      \newtheorem{game}[theorem]{Game}

      \theoremstyle{remark}
      \newtheorem{remark}[theorem]{Remark}

      \theoremstyle{plain}
      \newtheorem*{theorem*}{Theorem}
      \newtheorem*{lemma*}{Lemma}
      \newtheorem*{corollary*}{Corollary}
      \newtheorem*{proposition*}{Proposition}
      \newtheorem*{conjecture*}{Conjecture}
      \newtheorem*{question*}{Question}
      \newtheorem*{claim*}{Claim}

      \theoremstyle{definition}
      \newtheorem*{definition*}{Definition}
      \newtheorem*{example*}{Example}
      \newtheorem*{game*}{Game}

      \theoremstyle{remark}
      \newtheorem*{remark*}{Remark}

\begin{document}

% \title{Proximal compact spaces are Corson compact\tnoteref{t1}}
% \tnotetext[t1]{2010 Mathematics Subject Classification. 54E15, 54D30, 54A20.}
\title{Relating games of Menger, countable fan tightness, and selective separability}

% \author[aub]{S.~Clontz\fnref{fn1}}
% \ead{steven.clontz@auburn.edu}
% \author[aub]{G.~Gruenhage\fnref{fn2}}
% \ead{gruengf@auburn.edu}

% \address[aub]{Department of Mathematics, Auburn University,
%  Auburn, AL 36830}

\author{Steven Clontz}
\address{Department of Mathematics and Statistics,
The University of South Alabama,
Mobile, AL 36606}
\email{steven.clontz@gmail.com}

% \keywords{TODO}
% \subjclass[2010]{}

\begin{abstract}
  By adapting techniques of Arhangelskii, Barman, and Dow, we may
  equate the existence of perfect-information, Markov, and tactical
  strategies between two interesting selection games.
  These results shed some light on Gruenhage's question asking whether all
  strategically selectively separable spaces are Markov selectively
  separable.
\end{abstract}

\maketitle

\section{Introduction}

\begin{definition}
  The \term{selection principle} \(\schSelProp{\mc A}{\mc B}\) states that
  given \(A_n\in\mc A\) for \(n<\omega\), there exist \(B_n\in[A_n]^{<\omega}\)
  such that \(\bigcup_{n<\omega}B_n\in\mc B\).
\end{definition}

\begin{definition}
  The \term{selection game} \(\schSelGame{\mc A}{\mc B}\) is the
  analogous game to \(\schSelProp{\mc A}{\mc B}\), where during each
  round \(n<\omega\), Player \(\plI\) first
  chooses \(A_n\in\mc A\), and then Player \(\plII\) chooses
  \(B_n\in[A_n]^{<\omega}\).
  Player \(\plII\) wins in the case that \(\bigcup_{n<\omega}B_n\in\mc B\),
  and Player \(\plI\) wins otherwise.
\end{definition}

This game and property were first formally investigated
by Scheepers in ``Combinatorics of open covers'' \cite{MR1378387}, which
inspired a series of ten sequels with several co-authors. We may quickly
observe that if \(\plII\) has a winning strategy for the game
\(\schSelGame{\mc A}{\mc B}\), then \(\schSelProp{\mc A}{\mc B}\) will hold,
but the converse need not follow.

The power of this selection principle and game comes from their ability
to characterize several properties and games from the literature.
Of interest to us are the following.

\begin{definition}
  Let \(\mc O_X\) be the collection of open covers for a topological space
  \(X\). Then \(\schSelProp{\mc O_X}{\mc O_X}\) is the well-known
  \term{Menger property} for \(X\) (\(M\) for short), and
  \(\schSelGame{\mc O_X}{\mc O_X}\) is the
  well-known \term{Menger game}.
\end{definition}

\begin{definition}
  An \term{\(\omega\)-cover} \(\mc U\)
  for a topological space \(X\) is an open cover
  such that for every \(F\in[X]^{<\omega}\), there exists some \(U\in\mc U\)
  such that \(F\subseteq U\).
\end{definition}

\begin{definition}
  Let \(\Omega_X\) be the collection of \(\omega\)-covers for a topological
  space \(X\). Then \(\schSelProp{\Omega_X}{\Omega_X}\) is the
  \term{\(\Omega\)-Menger property} for \(X\) (\(\Omega M\) for short), and
  \(\schSelGame{\Omega_X}{\Omega_X}\) is the \term{\(\Omega\)-Menger game}.
\end{definition}

In \cite[Theorem 3.9]{MR1419798} it was shown that \(X\) is \(\Omega\)-Menger
if and only if \(X^n\) is Menger for all \(n<\omega\).

\begin{definition}
  Let \(\mc B_{X,x}\) be the collection of subsets \(A\subset X\) where
  \(x\in\closure{A}\). (Call \(A\) a \term{blade} of \(x\).)
  Then \(\schSelProp{\mc B_{X,x}}{\mc B_{X,x}}\) is the
  \term{countable fan tightness property} for \(X\) at \(x\)
  (\(CFT_x\) for short), and
  \(\schSelGame{\mc B_{X,x}}{\mc B_{X,x}}\) is the
  \term{countable fan tightness game} for \(X\) at \(x\).
\end{definition}

\begin{definition}
  A space \(X\) has \term{countable fan tightness} (\(CFT\) for short)
  if it has
  countable fan tightness at each point \(x\in X\).
\end{definition}

\begin{definition}
  Let \(\mc D_{X}\) be the collection of dense subsets of a topological
  space \(X\). (So, \(\mc D_X\subseteq \mc B_{X,x}\) for all \(x\in X\).)
  Then \(\schSelProp{\mc D_X}{\mc B_{X,x}}\) is the
  \term{countable dense fan tightness property} for \(X\) at \(x\)
  (\(CDFT_x\) for short), and
  \(\schSelGame{\mc D_X}{\mc B_{X,x}}\) is the
  \term{countable dense fan tightness game} for \(X\) at \(x\).
\end{definition}

\begin{definition}
  A space \(X\) has \term{countable dense fan tightness}
  (\(CDFT\) for short) if it has
  countable dense fan tightness at each point \(x\in X\).
\end{definition}

The notion of countable fan tightness was first studied by
by Arhangel'skii in \cite{MR837289}. A result of that paper showed
that for \(T_{3\frac{1}{2}}\) spaces \(X\), the countable fan tightness
of the function space of pointwise convergence \(C_p(X)\) is characterized by
the \(\Omega\)-Menger property of \(X\).

\begin{definition}
  \(\schSelProp{\mc D_X}{\mc D_X}\) is the
  \term{selective separability property} for \(X\)
  (\(SS\) for short), and
  \(\schSelGame{\mc D_X}{\mc D_X}\) is the
  \term{selective separability game} for \(X\).
\end{definition}

Of course, one may easily observe that a selective separable space is
separable. In \cite{MR2678950} Barman and Dow demonstrated that all
separable Frechet spaces are selectively separable. They were also able
to produce a space which is selectively separable, but does not allow
\(\plII\) a winning strategy in the selective separability game.

The object of this paper is to investigate the game-theoretic properties
characterized by the presence of winning \term{limited information}
strategies in these selection games.

\begin{definition}
  A \term{strategy} for \(\plII\) in the game \(\schSelGame{\mc A}{\mc B}\)
  is a function \(\sigma\) satisfying
  \(\sigma(\<A_0,\dots,A_n\>)\in[A_n]^{<\omega}\) for
  \(\<A_0\,\dots,A_n\>\in\mc A^{n+1}\). We say this strategy is
  \term{winning} if whenever \(\plI\) plays \(A_n\in\mc A\) during each
  round \(n<\omega\), \(\plII\) wins the game by playing
  \(\sigma(\<A_0,\dots,A_n\>)\) during each round \(n<\omega\).
  If a winning strategy exists, then we write
  \(\plII\win\schSelGame{\mc A}{\mc B}\).
\end{definition}

\begin{definition}
  A \term{Markov strategy} for \(\plII\) in the game
  \(\schSelGame{\mc A}{\mc B}\)
  is a function \(\sigma\) satisfying
  \(\sigma(A,n)\in[A_n]^{<\omega}\) for
  \(A\in\mc A\) and \(n<\omega\). We say this Markov strategy is
  \term{winning} if whenever \(\plI\) plays \(A_n\in\mc A\) during each
  round \(n<\omega\), \(\plII\) wins the game by playing
  \(\sigma(A_n,n)\) during each round \(n<\omega\).
  If a winning Markov strategy exists, then we write
  \(\plII\markwin\schSelGame{\mc A}{\mc B}\).
\end{definition}

\begin{notation}
  If \(\schSelProp{\mc A}{\mc B}\) characterizes the property \(P\),
  then we say \(\plII\win\schSelGame{\mc A}{\mc B}\) characterizes
  \(P^+\) (``strategically \(P\)''), and
  \(\plII\markwin\schSelGame{\mc A}{\mc B}\) characterizes
  \(P^{+mark}\) (``Markov \(P\)'').
  Of course, \(P^{+mark}\Rightarrow P^+ \Rightarrow P\).
\end{notation}

In this notation,
Barman and Dow showed that \(SS\) does not imply
\(SS^+\). We aim to make progress on the following question attributed to
Gary Gruenhage:

\begin{question}\label{mainQuestion}
  Does \(SS^+\) imply \(SS^{+mark}\)?
\end{question}

The solution is known to be ``yes'' in the context of countable spaces
\cite{MR2678950}. However in general, winning strategies in selection games
cannot be improved to be winning Markov strategies. In
\cite{clontzMengerGamePreprint} the author showed that while \(M^+\) implies
\(M^{+mark}\) for second-countable spaces, there exists a simple
example of a regular non-second-countable space which is
\(M^+\) but not \(M^{+mark}\).

\section{\(CFT\) and \(SS\)}

We begin by generalizing the following result:

\begin{lemma}[Lem 2.7 of \cite{MR2678950}]
  The following are equivalent for any topological space \(X\).
  \begin{itemize}
    \item \(X\) is \(SS\).
    \item \(X\) is separable and \(CDFT\).
    \item \(X\) has a countable dense subset \(D\) where
          \(CDFT_x\) holds for all \(x\in D\).
  \end{itemize}
\end{lemma}

\begin{lemma}
  The following are equivalent for any topological space \(X\).
  \begin{itemize}
    \item \(X\) is \(SS\) (resp. \(SS^+\), \(SS^{+mark}\)).
    \item \(X\) is separable and \(CDFT\)
          (resp. \(CDFT^+\), \(CDFT^{+mark}\)).
    \item \(X\) has a countable dense subset \(D\) where
          \(CDFT_x\) (resp. \(CDFT_x^+\), \(CDFT_x^{+mark}\))
          holds for all \(x\in D\).
  \end{itemize}
\end{lemma}

\begin{proof}
  We need only show that the final condition implies the first,
  and we may assume that \(X\) lacks isolated points.
  Let \(D=\{d_i:i<\omega\}\).

  Let \(\sigma_i\) be a winning strategy witnessing \(CDFT_{d_i}^+\)
  for each \(i<\omega\). We define the strategy \(\tau\) for the
  \(SS\) game by
  \[
    \tau(\<D_0,\dots,D_n\>)
      =
    \bigcup_{i\leq n}
    \sigma_i(\<D_i,\dots,D_n\>)
  .\]

  By \(CDFT_{d_i}^+\), we have
  \[
    d_i
      \in
    \cl{\bigcup_{i\leq n<\omega}\sigma_i(\<D_i,\dots,D_n\>)}
      \subseteq
    \cl{\bigcup_{i\leq n<\omega}\tau(\<D_0,\dots,D_n\>)}
      \subseteq
    \cl{\bigcup_{n<\omega}\tau(\<D_0,\dots,D_n\>)}
  \]
  and so it follows that
  \[
    X
      \subseteq
    \cl D
      \subseteq
    \cl{\cl{\bigcup_{n<\omega}\tau(\<D_0,\dots,D_n\>)}}
      =
    \cl{\bigcup_{n<\omega}\tau(\<D_0,\dots,D_n\>)}
  .\]
  Therefore \(\tau\) witnesses \(SS^+\).

  The above proof may be easily modified for the Markov case by
  replacing \(\sigma_i(\<D_i,\dots,D_n\>)\) with \(\sigma_i(D_n,n)\)
  and \(\tau(\<D_0,\dots,D_n\>)\) with \(\tau(D_n,n)\).
\end{proof}

\bibliographystyle{plain}
\bibliography{../../bibliography}

\end{document}

### 2016-10-11 articles/relating-games-menger-cft-ss/article.tex
proved selection case for 3->1

@@
 \begin{abstract}
-  By adapting techniques of Arhangelskii, Barman, and Dow, we may
+  By adapting techniques of Arhangel'skii, Barman, and Dow, we may
   equate the existence of perfect-information, Markov, and tactical
@@
 
+Note that \(CFT\Rightarrow CDFT\) for any space \(X\) as
+\(\mc D_X\subseteq \mc B_{X,x}\).
+
 The notion of countable fan tightness was first studied by
@@
 that for \(T_{3\frac{1}{2}}\) spaces \(X\), the countable fan tightness
-of the function space of pointwise convergence \(C_p(X)\) is characterized by
+of the space of real-vaued continuous functions with
+pointwise convergence \(C_p(X)\) is characterized by
 the \(\Omega\)-Menger property of \(X\).
@@
 
-\section{\(CFT\) and \(SS\)}
+\section{\(CFT\), \(CDFT\) and \(SS\)}
 
@@
 
-\begin{lemma}[Lem 2.7 of \cite{MR2678950}]
+\begin{theorem}[Lem 2.7 of \cite{MR2678950}]
   The following are equivalent for any topological space \(X\).
@@
   \end{itemize}
-\end{lemma}
+\end{theorem}
 
-\begin{lemma}
+\begin{theorem}
   The following are equivalent for any topological space \(X\).
@@
   \end{itemize}
-\end{lemma}
+\end{theorem}
 
 \begin{proof}
-  We need only show that the final condition implies the first,
-  and we may assume that \(X\) lacks isolated points.
+  We need only show that the final condition implies the first.
   Let \(D=\{d_i:i<\omega\}\).
@@
   \]
-  and so it follows that
+  and as \(D\subseteq\cl{\bigcup_{n<\omega}\tau(\<D_0,\dots,D_n\>)}\)
+  it follows that
   \[
@@
 
+  \sloppy
   The above proof may be easily modified for the Markov case by
@@
   and \(\tau(\<D_0,\dots,D_n\>)\) with \(\tau(D_n,n)\).
+\end{proof}
+
+\fussy
+
+So amongst separable spaces, we see that \(SS\)
+(resp. \(SS^+\), \(SS^{+mark}\)) and
+\(CDFT\) (resp. \(CDFT^+\), \(CDFT^{+mark}\))
+are equivalent. We now further bridge the gap between \(CDFT\)
+and \(CFT\) in the context of function spaces.
+Consider the following result of Arhangel'skii.
+
+\begin{theorem}[\cite{MR837289}]
+  The following are equivalent for any \(T_{3\frac{1}{2}}\)
+  topological space \(X\).
+    \begin{itemize}
+      \item \(X\) is \(\Omega M\).
+      \item \(C_p(X)\) is \(CFT\).
+    \end{itemize}
+\end{theorem}
+
+This result may similarly be generalized in a game theoretic sense.
+In addition, this proof will demonstrate the equivalence of
+\(CFT\) and \(CDFT\) in \(C_p(X)\).
+It is unknown to the author whether Arhangel'skii
+used a strategy similar to the following proof in \cite{MR837289},
+but Sakai employed a similar technique
+in \cite{MR964873} to relate the \(\Omega\)-Rothberger and
+countable strong fan tightness properties
+(and essentially, the countable strong dense fan tightness property).
+Due to the difficulty in obtaining an English translation of
+\cite{MR837289}, we reprove Arhangel'skii's theorem above in our
+more general context below.
+
+\begin{definition}
+  Let \(X\) be a \(T_{3\frac{1}{2}}\) topological space.
+  For \(\vec x\in C_p(X)\), \(F\in[X]^{<\omega}\), and
+  \(\epsilon>0\), let
+  \[
+    [\vec x,F,\epsilon]
+      =
+    \{
+      \vec y\in C_p(x)
+    :
+      |\vec y(t)-\vec x(t)|<\epsilon
+    \text{ for all }
+      t\in F
+    \}
+  \]
+  give a basic open neighborhood of \(\vec x\).
+\end{definition}
+
+\begin{lemma}
+  Let \(X\) be a \(T_{3\frac{1}{2}}\) topological space.
+  If \(X\) is \(\Omega M\)
+  (resp. \(\Omega M^+\), \(\Omega M^{+mark}\)).
+  then \(C_p(X)\) is \(CFT_{\vec 0}\)
+  (resp. \(CFT_{\vec 0}^+\), \(CFT_{\vec 0}^{+mark}\)).
+\end{lemma}
+
+\begin{proof}
+
+\end{proof}
+
+\begin{lemma}
+  Let \(X\) be a \(T_{3\frac{1}{2}}\) topological space.
+  If \(C_p(X)\) is \(CDFT_{\vec 0}\)
+  (resp. \(CDFT_{\vec 0}^+\), \(CDFT_{\vec 0}^{+mark}\)),
+  then \(X\) is \(\Omega M\)
+  (resp. \(\Omega M^+\), \(\Omega M^{+mark}\)).
+\end{lemma}
+
+\begin{proof}
+  For each \(\mc U\in\Omega_{X}\) define
+  \[
+    D(\mc U)
+      =
+    \{
+      \vec y\in C_p(X)
+    :
+      \vec y[X\setminus U_{\vec y,\mc U}]=\{1\}
+      \text{ for some }
+      U_{\vec y,\mc U}\in\mc U
+    \}
+  .\]
+  Consider the point \(\vec x\in C_p(X)\) and its basic open neighborhood
+  \([\vec x,G,\epsilon]\). If \(\mc U\) is an \(\omega\)-cover
+  of \(X\), \(G\subseteq U\) for some \(U_{\vec y,\mc U}\in\mc U\).
+  Since \(X\) is
+  \(T_{3\frac{1}{2}}\), \(X\setminus U_{\vec y,\mc U}\) is closed, and \(G\)
+  is finite and disjoint from \(X\setminus U_{\vec y,\mc U}\),
+  we may choose some function \(\vec y\in C_p(X)\) where
+  \(\vec y[X\setminus U_{\vec y,\mc U}]=\{1\}\) and \(\vec x(t)=\vec y(t)\)
+  for each \(t\in G\).
+  It follows \(\vec y\in [\vec x,G,\epsilon]\cap D\), so \(D(\mc U)\)
+  is dense in \(C_p(X)\).
+
+  Consider the sequence of \(\omega\)-covers
+  \(\<\mc U_0,\mc U_1,\dots\>\in\Omega_X^\omega\), and the
+  corresponding sequence of dense subsets
+  \(\<D(\mc U_0),D(\mc U_1),\dots\>\in\mc D_{C_p(X)}^\omega\).
+
+  Assuming \(C_p(X)\) is \(CDFT_{\vec 0}\), choose a witness
+  \(\<F_0,F_1,\dots\>\) such that \(F_n\in[D(\mc U_n)]^{<\omega}\)
+  and \(\vec 0 \in \cl{\bigcup_{n<\omega} F_n}\). Now let
+  \[
+    \mc F_n
+      =
+    \{
+      U_{\vec y,\mc U_n}
+    :
+      \vec y \in F_n
+    \}
+      \in
+    [\mc U_n]^{<\omega}
+  .\]
+  We claim that \(\bigcup_{n<\omega}\mc F_n\) is an \(\omega\)-cover.
+  Let \(G\in[X]^{<\omega}\). The neighborhood \([\vec 0,G,\frac{1}{2}]\)
+  contains some point \(\vec y\in F_n\) for some \(n<\omega\). It follows
+  that \(U_{\vec y,\mc U_n}\in\mc U_n\) and
+  \(\vec y[X\setminus U_{\vec y,\mc U_n}]=\{1\}\). It follows that
+  \(G\cap(X\setminus U_{\vec y,\mc U_n})=\emptyset\), and therefore
+  \(G\subseteq U_{\vec y,\mc U_n}\in\mc F_n\).
+\end{proof}
+
+\begin{theorem}
+  The following are equivalent for any \(T_{3\frac{1}{2}}\)
+  topological space \(X\).
+    \begin{itemize}
+      \item \(X\) is \(\Omega M\)
+            (resp. \(\Omega M^+\), \(\Omega M^{+mark}\)).
+      \item \(C_p(X)\) is \(CFT\)
+            (resp. \(CFT^+\), \(CFT^{+mark}\)).
+      \item \(C_p(X)\) is \(CDFT\)
+            (resp. \(CDFT^+\), \(CDFT^{+mark}\)).
+    \end{itemize}
+\end{theorem}
+
+\begin{proof}
+  Since \(\mc D_X\subseteq \mc B_{X,x}\), the second condition trivially
+  implies the first. As \(C_p(X)\) is homogeneous, the \(C(D)FT\) properties
+  are characterized by \(C(D)FT_{\vec 0}\). So the result follows from the
+  previous lemmas.
 \end{proof}

### 2016-10-11 articles/relating-games-menger-cft-ss/article.tex
finish strategic/mark cases for 3->1

@@
   Assuming \(C_p(X)\) is \(CDFT_{\vec 0}\), choose a witness
-  \(\<F_0,F_1,\dots\>\) such that \(F_n\in[D(\mc U_n)]^{<\omega}\)
-  and \(\vec 0 \in \cl{\bigcup_{n<\omega} F_n}\). Now let
+  \(\<F_0,F_1,\dots\>\) such that
+  \[
+    \vec 0 \in \cl{\bigcup_{n<\omega} F_n}
+  .\]
+  Now let
   \[
@@
   \(G\subseteq U_{\vec y,\mc U_n}\in\mc F_n\).
+
+  Assuming \(C_p(X)\) is \(CDFT_{\vec 0}^+\), choose a witness
+  \(\sigma\) such that
+  \[
+    \vec 0
+      \in
+    \cl{\bigcup_{n<\omega} \sigma(\<D(\mc U_0),\dots,D(\mc U_n)\>)}
+  .\]
+  Now let
+  \[
+    \tau(\<\mc U_0,\dots,\mc U_n\>)
+      =
+    \{
+      U_{\vec y,\mc U_n}
+    :
+      \vec y \in \sigma(\<D(\mc U_0),\dots,D(\mc U_n)\>)
+    \}
+      \in
+    [\mc U_n]^{<\omega}
+  .\]
+  We claim that \(\bigcup_{n<\omega}\tau(\<\mc U_0,\dots,\mc U_n\>)\)
+  is an \(\omega\)-cover.
+  Let \(G\in[X]^{<\omega}\). The neighborhood \([\vec 0,G,\frac{1}{2}]\)
+  contains some point \(\vec y\in \sigma(\<D(\mc U_0),\dots,D(\mc U_n)\>)\)
+  for some \(n<\omega\). It follows
+  that \(U_{\vec y,\mc U_n}\in\mc U_n\) and
+  \(\vec y[X\setminus U_{\vec y,\mc U_n}]=\{1\}\). As a result
+  \(G\cap(X\setminus U_{\vec y,\mc U_n})=\emptyset\), and therefore
+  \(G\subseteq U_{\vec y,\mc U_n}\in\mc \tau(\<\mc U_0,\dots,\mc U_n\>)\).
+
+  Assuming \(C_p(X)\) is \(CDFT_{\vec 0}^{+mark}\), choose a witness
+  \(\sigma\) such that
+  \[
+    \vec 0
+      \in
+    \cl{\bigcup_{n<\omega} \sigma(D(\mc U_n),n)}
+  .\]
+  Now let
+  \[
+    \tau(\mc U_n,n)
+      =
+    \{
+      U_{\vec y,\mc U_n}
+    :
+      \vec y \in \sigma(D(\mc U_n),n)
+    \}
+      \in
+    [\mc U_n]^{<\omega}
+  .\]
+  We claim that \(\bigcup_{n<\omega}\tau(\mc U_n,n)\)
+  is an \(\omega\)-cover.
+  Let \(G\in[X]^{<\omega}\). The neighborhood \([\vec 0,G,\frac{1}{2}]\)
+  contains some point \(\vec y\in \sigma(D(\mc U_n),n)\)
+  for some \(n<\omega\). It follows
+  that \(U_{\vec y,\mc U_n}\in\mc U_n\) and
+  \(\vec y[X\setminus U_{\vec y,\mc U_n}]=\{1\}\). As a result
+  \(G\cap(X\setminus U_{\vec y,\mc U_n})=\emptyset\), and therefore
+  \(G\subseteq U_{\vec y,\mc U_n}\in\mc \tau(\mc U_n,n)\).
 \end{proof}

### 2016-10-12 articles/relating-games-menger-cft-ss/article.tex
awful commit message, just see the diff

@@
 
+\begin{proposition}
+  Any witness for \(\Omega M\) (resp. \(\Omega M^+,\Omega M^{+mark}\))
+  may be improved such that any final sequence of the chosen
+  finite subcollections is an \(\omega\)-cover.
+\end{proposition}
+
+\begin{proof}
+  Consider any sequence \(\<\mc U_0,\mc U_1,\dots\>\) of open covers.
+  For \(\Omega M\), choose the witness
+  \(\<\mc F_n^n,\mc F_{n+1}^n,\dots\>\) for the final
+  sequence \(\<\mc U_n,\mc U_{n+1},\dots\>\) for each \(n<\omega\),
+  and let \(\mc F_n=\bigcup_{i\leq n}\mc F_n^i\).
+  For \(\Omega M^+\), the winning strategy \(\sigma\) may be improved to
+  \(\tau\) where
+  \(
+    \tau(\<\mc U_0,\dots,\mc U_n\>)
+      =
+    \bigcup_{i\leq n}\sigma(\<\mc U_i,\dots,\mc U_n\>)
+  \). For \(\Omega M^{+mark}\), the winning Markov strategy \(\sigma\) may
+  be improved to \(\tau\) where
+  \(
+    \tau(\mc U,n)
+      =
+    \bigcup_{i\leq n}\sigma(\mc U,i)
+  \).
+\end{proof}
+
 \begin{definition}
@@
 \begin{proof}
+  For each \(B\in\mc B_{C_p(X),\vec 0}\) define
+  \[
+    \mc U_n(B)
+      =
+    \left\{
+      \vec x^{-1}\left[\left(-\frac{1}{2^n},\frac{1}{2^n}\right)\right]
+    :
+      \vec x\in B
+    \right\}
+  .\]
+  Consider the finite set \(F\in[X]^{<\omega}\). Since
+  \(\vec 0\in\cl B\), choose \(\vec x\in B\cap[\vec 0,F,1]\).
+  It follows that \(F\subseteq x^{-1}[(-1,1)]\in\mc U_n(B)\),
+  so \(\mc U_n(B)\) is an \(\omega\)-cover of \(X\).
 
+  Consider the sequence of blades
+  \(\<B_0,B_1,\dots\>\in\mc B_{C_p(X),\vec 0}^\omega\), and the
+  corresponding sequence of \(\omega\)-covers
+  \(\<\mc U_0(B_0),\mc U_1(B_1),\dots\>\in \Omega_X^\omega\).
+
+  Assuming \(X\) is \(\Omega M\), choose a witness
+  \(\<\mc F_0,\mc F_1,\dots\>\) such that
+  \(\mc F_n\in[\mc U_n(B_n)]^{<\omega}\) and
+  \[
+    \bigcup_{i\leq n<\omega} \mc F_n
+  \]
+  is an \(\omega\)-cover of \(X\) for all \(i<\omega\).
+  Now let
+  \[
+    F_n
+      =
+    \left\{
+      \vec x\in B_n
+    :
+      \vec x^{-1}\left[\left(-\frac{1}{2^n},\frac{1}{2^n}\right)\right]
+        \in
+      \mc F_n
+    \right\}
+  .\]
+  We claim that \(\vec 0\in\cl{\bigcup_{n<\omega}F_n}\).
+  Let \(G\in[X]^{<\omega},\epsilon>0\). Choose \(i<\omega\) such that
+  \(\frac{1}{2^i}<\epsilon\) and then choose
+  \(i\leq n<\omega,\vec x^{-1}[(-\frac{1}{2^n},\frac{1}{2^n})]\in\mc F_n\)
+  such that \(G\subseteq \vec x^{-1}[(-\frac{1}{2^n},\frac{1}{2^n})]\)
+  and therefore \(G\subseteq \vec x^{-1}[(-\epsilon,\epsilon)]\).
+  It follows that \(\vec x\in F_n\cap[\vec 0,G,\epsilon]\), and therefore
+  every basic open neighborhood of \(\vec 0\) intersects
+  \(\bigcup_{n<\omega}F_n\).
+
+  Assuming \(X\) is \(\Omega M^+\), choose a witness
+  \(\sigma\) such that
+  \[
+    \bigcup_{i\leq n<\omega} \sigma(\<\mc U_0(B_0),\dots,\mc U_n(B_n)\>)
+  \]
+  is an \(\omega\)-cover of \(X\) for all \(i<\omega\).
+  Now let
+  \[
+    \tau(\<B_0,\dots,B_n\>)
+      =
+    \left\{
+      \vec x\in B_n
+    :
+      \vec x^{-1}\left[\left(-\frac{1}{2^n},\frac{1}{2^n}\right)\right]
+        \in
+      \sigma(\<\mc U_0(B_0),\dots,\mc U_n(B_n)\>)
+    \right\}
+  .\]
+  We claim that \(\vec 0\in\cl{\bigcup_{n<\omega}\tau(\<B_0,\dots,B_n\>)}\).
+  Let \(G\in[X]^{<\omega},\epsilon>0\). Choose \(i<\omega\) such that
+  \(\frac{1}{2^i}<\epsilon\) and then choose
+  \(i\leq n<\omega,\vec x^{-1}[(-\frac{1}{2^n},\frac{1}{2^n})]\in\sigma(\<\mc U_0(B_0),\dots,\mc U_n(B_n)\>)\)
+  such that \(G\subseteq \vec x^{-1}[(-\frac{1}{2^n},\frac{1}{2^n})]\)
+  and therefore \(G\subseteq \vec x^{-1}[(-\epsilon,\epsilon)]\).
+  It follows that \(\vec x\in \tau(\<B_0,\dots,B_n\>)\cap[\vec 0,G,\epsilon]\), and therefore
+  every basic open neighborhood of \(\vec 0\) intersects
+  \(\bigcup_{n<\omega}\tau(\<B_0,\dots,B_n\>)\).
+
+  Assuming \(X\) is \(\Omega M^{+mark}\), choose a witness
+  \(\sigma\) such that
+  \[
+    \bigcup_{i\leq n<\omega} \sigma(\mc U_n(B_n),n)
+  \]
+  is an \(\omega\)-cover of \(X\) for all \(i<\omega\).
+  Now let
+  \[
+    \tau(B_n,n)
+      =
+    \left\{
+      \vec x\in B_n
+    :
+      \vec x^{-1}\left[\left(-\frac{1}{2^n},\frac{1}{2^n}\right)\right]
+        \in
+      \sigma(\mc U_n(B_n),n)
+    \right\}
+  .\]
+  We claim that \(\vec 0\in\cl{\bigcup_{n<\omega}\tau(B_n,n)}\).
+  Let \(G\in[X]^{<\omega},\epsilon>0\). Choose \(i<\omega\) such that
+  \(\frac{1}{2^i}<\epsilon\) and then choose
+  \(i\leq n<\omega,\vec x^{-1}[(-\frac{1}{2^n},\frac{1}{2^n})]\in\sigma(\mc U_n(B_n),n)\)
+  such that \(G\subseteq \vec x^{-1}[(-\frac{1}{2^n},\frac{1}{2^n})]\)
+  and therefore \(G\subseteq \vec x^{-1}[(-\epsilon,\epsilon)]\).
+  It follows that \(\vec x\in \tau(B_n,n)\cap[\vec 0,G,\epsilon]\), and therefore
+  every basic open neighborhood of \(\vec 0\) intersects
+  \(\bigcup_{n<\omega}\tau(B_n,n)\).
 \end{proof}
@@
   implies the first. As \(C_p(X)\) is homogeneous, the \(C(D)FT\) properties
-  are characterized by \(C(D)FT_{\vec 0}\). So the result follows from the
+  follow from \(C(D)FT_{\vec 0}\). So the result follows from the
   previous lemmas.
+\end{proof}
+
+\section{A space which is \(CFT^+\) but not \(CDFT^{+mark}\)}
+
+Our goal is to now demonstrate a space which is \(CFT^+\),
+but not even \(CDFT^{+mark}\). To do so, we will find a space \(X\)
+which is \(\Omega M^+\) but not \(\Omega M^{+mark}\), yielding \(C_p(X)\)
+as our example.
+
+\begin{proposition}\label{altCompactCharacterization}
+  A space \(X\) is compact if and only if for each \(\omega\)-cover
+  \(\mc U\) of \(X\) and \(n<\omega\), there exists a finite subcollection
+  \(\mc F\in[\mc U]^{<\omega}\) such that for each \(F\in[X]^{\leq n}\)
+  there exists some \(U\in\mc F\) where \(F\subseteq U\).
+\end{proposition}
+
+\begin{proof}
+  Let \(X\) and therefore \(X^n\) be compact.
+  Let \(\mc F_n\) be the finite subcover of the
+  open cover \(\mc U_n=\{U^n:U\in\mc U\}\). Then
+  \(\mc F=\{U:U^n\in\mc F_n\}\) witnesses our desired result.
+\end{proof}
+
+\begin{lemma}
+  The following are equivalent for a regular topological space \(X\):
+  \begin{itemize}
+    \item \(X\) is \(\sigma\)-compact
+    \item \(X\) is \(\Omega M^{+mark}\)
+    \item \(X\) is \(M^{+mark}\)
+  \end{itemize}
+\end{lemma}
+
+\begin{proof}
+  The equivalence of \(\sigma\)-compact and \(M^{+mark}\) in regular spaces
+  was shown in \cite{clontzMengerGamePreprint}. As \(\Omega M^{+mark}\)
+  trivially implies \(M^{+mark}\), we need only demonstrate that
+  if \(X=\bigcup_{n<\omega} K_n\) for \(K_n\) compact and increasing,
+  then \(X\) is \(\Omega M^{+mark}\).
+
+  We define \(\sigma(\mc U,n)\) for each \(\omega\)-cover \(\mc U\) and
+  \(n<\omega\) to witness Proposition \ref{altCompactCharacterization}
+  for \(\mc U\), \(K_n\), and \(n\). It follows that for every sequence of
+  \(\omega\)-covers \(\<\mc U_0,\mc U_1,\dots\>\) and \(F\in[X]^{<\omega}\),
+  \(F\in[K_n]^{\leq n}\) for some \(n\geq|F|\), and thus there exists some
+  \(U\in\sigma(\mc U_n,n)\) where \(F\subseteq U\). Therefore
+  \(\bigcup_{n<\omega}\sigma(\mc U,n)\) is an \(\omega\)-cover of \(X\).
+\end{proof}
+
+\begin{definition}
+  Let \(X\) be a topological space such that all countable sets are
+  closed. Then \(\onePtLind{X}=X\cup\{\infty\}\)
+  is the \term{one-point Lindel\"of-ication} of \(X\), with a basis given
+  by the usual open sets of \(X\) and the co-countable sets containing
+  \(\infty\).
+\end{definition}
+
+\begin{theorem}
+  Let \(\omega_1\) have the discrete topology. Then
+  \(\onePtLind{\omega_1}\) is \(\Omega M^+\) but not \(\Omega M^{+mark}\).
+\end{theorem}
+
+\begin{proof}
+  The proof that \(X=\onePtLind{\omega_1}\) is not
+  \(\sigma\)-compact is simply the fact that its countably infinite subsets
+  are closed and discrete.
+  We define the strategy \(\sigma\) for \(\plII\) in
+  \(\schSelGame{\Omega_X}{\Omega_X}\) as follows.
+
+  % Let \(\sigma_0(\<\mc U_0\>)=\{I_0\}\) where \(I_0\) is a co-countable set
+  % containing \(\infty\). Denote
+  % \(\onePtLind{\omega_1}\setminus I_0=\{\alpha_{0,n}:n<\omega\}\),
+  % and then let \(\sigma_0(\<\mc U_0,\dots,\mc U_{n+1}\>)\) contain exactly
+  % one superset of \(\{\infty\}\cup\{\alpha_{0,n}\}\).
+
+  For \(n<\omega\)
+  let \(\sigma_n(\<\mc U_n\>)=\{I_n\}\)
+  where \(I_n\) is a co-countable set containing \(\infty\).
+  Denote
+  \(\onePtLind{\omega_1}\setminus I_n=\{\alpha_{n,m}:m<\omega\}\),
+  and then for \(m<\omega\)
+  let \(\sigma_n(\<\mc U_n,\dots,\mc U_{n+m}\>)\) contain exactly
+  one set, a superset of \(\{\infty\}\cup\{\alpha_{i,j}:i\leq n,j\leq n+m\}\).
+
+  TODO: finish
 \end{proof}

### 2016-10-15 articles/relating-games-menger-cft-ss/article.tex
slick strategic<=>Markov generalization

@@
 \usepackage{../../clontzDefinitions}
+
+\renewcommand{\vec}{\mathbf}
 
@@
 Barman and Dow showed that \(SS\) does not imply
-\(SS^+\). We aim to make progress on the following question attributed to
-Gary Gruenhage:
+\(SS^+\). Our goal is to make progress on the following question
+attributed to Gary Gruenhage:
 
@@
 
-The solution is known to be ``yes'' in the context of countable spaces
+The solution is already known to be ``yes'' in the context of countable spaces
 \cite{MR2678950}. However in general, winning strategies in selection games
@@
     \left\{
-      \vec x^{-1}\left[\left(-\frac{1}{2^n},\frac{1}{2^n}\right)\right]
+      \vec x^{\leftarrow}\left[\left(-\frac{1}{2^n},\frac{1}{2^n}\right)\right]
     :
@@
   \(\vec 0\in\cl B\), choose \(\vec x\in B\cap[\vec 0,F,1]\).
-  It follows that \(F\subseteq x^{-1}[(-1,1)]\in\mc U_n(B)\),
+  It follows that \(F\subseteq x^{\leftarrow}[(-1,1)]\in\mc U_n(B)\),
   so \(\mc U_n(B)\) is an \(\omega\)-cover of \(X\).
@@
     :
-      \vec x^{-1}\left[\left(-\frac{1}{2^n},\frac{1}{2^n}\right)\right]
+      \vec x^{\leftarrow}\left[\left(-\frac{1}{2^n},\frac{1}{2^n}\right)\right]
         \in
@@
   \(\frac{1}{2^i}<\epsilon\) and then choose
-  \(i\leq n<\omega,\vec x^{-1}[(-\frac{1}{2^n},\frac{1}{2^n})]\in\mc F_n\)
-  such that \(G\subseteq \vec x^{-1}[(-\frac{1}{2^n},\frac{1}{2^n})]\)
-  and therefore \(G\subseteq \vec x^{-1}[(-\epsilon,\epsilon)]\).
+  \(i\leq n<\omega,\vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\in\mc F_n\)
+  such that \(G\subseteq \vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\)
+  and therefore \(G\subseteq \vec x^{\leftarrow}[(-\epsilon,\epsilon)]\).
   It follows that \(\vec x\in F_n\cap[\vec 0,G,\epsilon]\), and therefore
@@
   \(\frac{1}{2^i}<\epsilon\) and then choose
-  \(i\leq n<\omega,\vec x^{-1}[(-\frac{1}{2^n},\frac{1}{2^n})]\in\sigma(\<\mc U_0(B_0),\dots,\mc U_n(B_n)\>)\)
-  such that \(G\subseteq \vec x^{-1}[(-\frac{1}{2^n},\frac{1}{2^n})]\)
-  and therefore \(G\subseteq \vec x^{-1}[(-\epsilon,\epsilon)]\).
+  \(i\leq n<\omega,\vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\in\sigma(\<\mc U_0(B_0),\dots,\mc U_n(B_n)\>)\)
+  such that \(G\subseteq \vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\)
+  and therefore \(G\subseteq \vec x^{\leftarrow}[(-\epsilon,\epsilon)]\).
   It follows that \(\vec x\in \tau(\<B_0,\dots,B_n\>)\cap[\vec 0,G,\epsilon]\), and therefore
@@
   \(\frac{1}{2^i}<\epsilon\) and then choose
-  \(i\leq n<\omega,\vec x^{-1}[(-\frac{1}{2^n},\frac{1}{2^n})]\in\sigma(\mc U_n(B_n),n)\)
-  such that \(G\subseteq \vec x^{-1}[(-\frac{1}{2^n},\frac{1}{2^n})]\)
-  and therefore \(G\subseteq \vec x^{-1}[(-\epsilon,\epsilon)]\).
+  \(i\leq n<\omega,\vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\in\sigma(\mc U_n(B_n),n)\)
+  such that \(G\subseteq \vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\)
+  and therefore \(G\subseteq \vec x^{\leftarrow}[(-\epsilon,\epsilon)]\).
   It follows that \(\vec x\in \tau(B_n,n)\cap[\vec 0,G,\epsilon]\), and therefore
@@
       \in
-    [\mc U_n]^{<\omega}
+    [\mc U_n]^{<\omega}S
   .\]
@@
   The proof that \(X=\onePtLind{\omega_1}\) is not
-  \(\sigma\)-compact is simply the fact that its countably infinite subsets
+  \(\sigma\)-compact (and therefore not \(\Omega M^{+mark}\))
+  is simply the fact that its countably infinite subsets
   are closed and discrete.
@@
   For \(n<\omega\)
-  let \(\sigma_n(\<\mc U_n\>)=\{I_n\}\)
-  where \(I_n\) is a co-countable set containing \(\infty\).
-  Denote
-  \(\onePtLind{\omega_1}\setminus I_n=\{\alpha_{n,m}:m<\omega\}\),
-  and then for \(m<\omega\)
-  let \(\sigma_n(\<\mc U_n,\dots,\mc U_{n+m}\>)\) contain exactly
-  one set, a superset of \(\{\infty\}\cup\{\alpha_{i,j}:i\leq n,j\leq n+m\}\).
+  let \(\sigma(\<\mc U_0,\dots,\mc U_n\>)=\{U(\<\mc U_0,\dots,\mc U_n\>)\}\),
+  where
+  \[
+    U(\<\mc U_0,\dots,\mc U_n\>)
+      =
+    \onePtLind{\omega_1}
+      \setminus
+    \{\alpha_{n,m}:m<\omega\}
+  \]
+  is a co-countable set
+  containing \(\{\infty\}\cup\{\alpha_{i,j}:i,j<n\}\).
 
-  TODO: finish
+  Consider the arbitrary sequence of moves \(\<\mc U_0,\mc U_1,\dots\>\)
+  by \(\plI\). For \(F\in[\onePtLind{\omega_1}]^{<\omega}\), choose
+  \(n<\omega\) such that
+  \[
+    F\cap\{\alpha_{i,j}:i,j<\omega\}
+      =
+    F\cap\{\alpha_{i,j}:i,j<n\}
+      \subseteq
+    U(\<\mc U_0,\dots,\mc U_n\>)
+  \]
+  It follows that as
+  \[
+    F
+      \setminus
+    \{\alpha_{i,j}:i,j<\omega\}
+      \subseteq
+    F
+      \setminus
+    \{\alpha_{n,m}:m<\omega\}
+      \subseteq
+    U(\<\mc U_0,\dots,\mc U_n\>)
+  \]
+  \(F\) is a subset of
+  \(U(\<\mc U_0,\dots,\mc U_n\>)\), making
+  \(
+    \bigcup_{n<\omega}
+    \sigma(\<\mc U_0,\dots,\mc U_n\>)
+  \)
+  an \(\omega\)-cover.
 \end{proof}
+
+\begin{corollary}
+  \(C_p(\onePtLind{\omega_1})\) is \(CFT^+\) but not \(CDFT^{+mark}\).
+\end{corollary}
+
+If \(C_p(\onePtLind{\omega_1})\) were separable, it would be a negative
+solution to Question \ref{mainQuestion}. However, it is not.
+
+\begin{lemma}[\cite{MR953314}]
+  For a \(T_{3\frac{1}{2}}\) topological space \(X\),
+  \(C_p(X)\) is separable if and only if \(X\) has a coarser separable
+  metrizable topology.
+\end{lemma}
+
+\begin{corollary}
+  \(C_p(\onePtLind{\omega_1})\) is not separable.
+\end{corollary}
+
+\begin{proof}
+  Every metrizable topological space has points \(G_\delta\).
+  However, if every neighborhood of \(\infty\) is
+  co-countable, \(\{\infty\}\) cannot be the intersection of countably many
+  open sets.
+\end{proof}
+
+% It's easily seen that \(CFT^+\) is a hereditary property for all subspaces.
+
+\section{Equivalence of certain strategic and Markov seleciton properties}
+
+Barman and Dow
+previously demonstrated that \(SS^+\) is equivalent to
+\(SS^{+mark}\) amongst countable spaces.
+A similar result by the author
+showed that \(M^+\) is equivalent to \(M^{+mark}\) in second-countable
+spaces. The following result generalizes both.
+
+\begin{lemma}\label{mainLemma}
+  Let \(\mc A\) be a family of sets where
+  \(|\bigcup\mc A|\leq\omega\)
+  and let \(\mc B\) be a family of sets closed under supersets. Then
+  \(\plII\win\schSelGame{\mc A}{\mc B}\) if and only if
+  \(\plII\markwin\schSelGame{\mc A}{\mc B}\).
+\end{lemma}
+
+\begin{proof}
+  Let \(\sigma\) witness \(\plII\win\schSelGame{\mc A}{\mc B}\).
+
+  For \(t\in\omega^{<\omega}\), suppose
+  \(Z_s\in\mc A\) has been defined for all \(s\leq t\). Note then that
+  \(
+    \{\sigma(\<Z_{t\rest1},Z_{t\rest2},\dots,Z_t,A\>:A\in\mc A\}
+      \subseteq
+    [\bigcup\mc A]^{<\omega}
+  \)
+  and therefore is countable.
+  So choose \(Z_{t\concat\<n\>}\in\mc A\) for \(n<\omega\) such that
+  \(
+    \{\sigma(\<Z_{t\rest1},Z_{t\rest2},\dots,Z_t,A\>:A\in\mc A\}
+      =
+    \{\sigma(\<Z_{t\rest1},Z_{t\rest2},\dots,Z_t,Z_{t\concat\<n\>}\>):n<\omega\}
+  \).
+
+  Let \(b:\omega\to\omega^{<\omega}\) be a bijection,
+  and define
+  \(\tau(A,n)=\sigma(\<Z_{b(n)\rest 1},Z_{b(n)\rest 2},\dots,Z_{b(n)},A\>)\).
+  Consider \(\<A_0,A_1,\dots\>\in\mc A^\omega\).
+
+  Define \(f\in\omega^\omega\) as follows.
+  Let \(n<\omega\) and suppose that \(f\rest n\) has been already
+  been defined. Then choose \(f(n)<\omega\) such that
+  \(
+    \sigma(\<Z_{f\rest1},Z_{f\rest2},\dots,Z_{f\rest n},A_{b^{\leftarrow}(f\rest n)}\>)
+      =
+    \sigma(\<Z_{f\rest1},Z_{f\rest2},\dots,Z_{f\rest n},Z_{f\rest (n+1)}\>)
+  \).
+
+  Since \(\<Z_{f\rest1},Z_{f\rest2},\dots\>\in\mc A^\omega\), it follows
+  that
+  \(
+    \bigcup_{n<\omega}\sigma(\<Z_{f\rest1},Z_{f\rest2},\dots,Z_{f\rest n}\>)
+      \in
+    \mc B
+  \).
+  The result then follows from
+  \begin{align*}
+    \bigcup_{n<\omega}\tau(A_n,n)
+      & =
+    \bigcup_{n<\omega}
+    \sigma(\<Z_{b(n)\rest 1},Z_{b(n)\rest 2},\dots,Z_{b(n)},A_n\>)
+      \\ & \supseteq
+    \bigcup_{n<\omega,b(n)<f}
+    \sigma(\<Z_{b(n)\rest 1},Z_{b(n)\rest 2},\dots,Z_{b(n)},A_n\>)
+      \\ & =
+    \bigcup_{n<\omega,b(n)<f}
+    \sigma(\<Z_{f\rest 1},Z_{f\rest 2},\dots,Z_{f\rest|b(n)|},A_{b^{\leftarrow}(f\rest|b(n)|)}\>)
+      \\ & =
+    \bigcup_{n<\omega,b(n)<f}
+    \sigma(\<Z_{f\rest 1},Z_{f\rest 2},\dots,Z_{f\rest|b(n)|},Z_{f\rest(|b(n)|+1)}\>)
+      \\ & =
+    \bigcup_{n<\omega}
+    \sigma(\<Z_{f\rest 1},Z_{f\rest 2},\dots,Z_{f\rest n}\>)
+      \\ & \in
+    \mc B
+  \end{align*}
+  as \(\mc B\) is closed under supersets.
+\end{proof}
+
+\begin{corollary}[\cite{MR2868880}]
+  A countable space \(X\) is \(SS^+\) if and only if it is
+  \(SS^{+mark}\).
+\end{corollary}
+
+\begin{proof}
+  \(\bigcup\mc D_X=X\) is countable, and any set containing a dense
+  set is dense.
+\end{proof}
+
+\begin{corollary}
+  A second-countable space \(X\) is \(\Omega M^+\) if and only if
+  it is \(\Omega M^{+mark}\).
+\end{corollary}
+
+\begin{proof}
+  First note that any witness for
+  \(\Omega M^+\) is a witness for
+  \(\plII\win\schSelGame{\Omega_X^*}{\Omega_X^*}\).
+  Fix a countable base \(\mc B\) for \(X\) closed under finite unions, and let
+  \(\Omega_X^*\) be the collection of \(\omega\)-covers of \(X\) which only
+  use basic open sets. Then
+  \(\bigcup\Omega_X^*=\mc B\) is countable, and any set containing an
+  \(\omega\)-cover is an \(\omega\)-cover; therefore
+  \(\plII\win\schSelGame{\Omega_X^*}{\Omega_X^*}\) if and only if
+  \(\plII\markwin\schSelGame{\Omega_X^*}{\Omega_X^*}\).
+
+  So let \(\sigma\) witness
+  \(\plII\markwin\schSelGame{\Omega_X^*}{\Omega_X^*}\).
+  For each \(\omega\)-cover \(\mc U\) and finite set \(F\in[X]^{<\omega}\),
+  choose \(U_{\mc U,F}\in\mc U\) such that \(F\subseteq U\). Then choose a
+  basic open set \(U_{\mc U,F}^*\) such that
+  \(F\subseteq U_{\mc U,F}^*\subseteq U_{\mc U,F}\). Finally, for each
+  \(\omega\)-cover \(\mc U\), let
+  \[
+    \mc U^*
+      =
+    \{
+      U_{\mc U,F}^*
+        :
+      F\in[X]^{<\omega}
+    \}
+      \in
+    \Omega_X^*
+  .\]
+
+  Define the strategy \(\tau\) such that
+  \(\tau(\mc U,n)=\{U_{\mc U,F}:U_{\mc U,F}^*\in\sigma(\mc U^*,n)\}\).
+  For any sequence of \(\omega\)-covers \(\<\mc U_0,\mc U_1,\dots\>\),
+  it follows that \(\bigcup_{n<\omega}\sigma(\mc U_n^*,n)\) is an
+  \(\omega\)-cover, and therefore
+  \(\bigcup_{n<\omega}\tau(\mc U_n,n)\) is an \(\omega\)-cover also.
+\end{proof}
+
+\begin{corollary}[\cite{clontzMengerGamePreprint}]
+  A second-countable space \(X\) is \(M^+\) if and only if
+  it is \(M^{+mark}\).
+\end{corollary}
+
+\begin{proof}
+  An easy adapatation of the preceding proof, replacing \(\omega\)-covers
+  with open covers, and replacing \(F\in[X]^{<\omega}\) with \(x\in X\).
+\end{proof}
+
+\section{Acknowledgements}
+The author would like to thank Ziqin Feng for his helpful comments on
+this topic during
+the 31st Summer Conference on Topology and its Applications.
 

### 2016-10-15 articles/relating-games-menger-cft-ss/article.tex
preprint ready to share

@@
 
-  Let \(\sigma_i\) be a winning strategy witnessing \(CDFT_{d_i}^+\)
+  Let \(\sigma_i\) be a witness for \(CDFT_{d_i}^+\)
   for each \(i<\omega\). We define the strategy \(\tau\) for the
@@
 
+  Let \(\<D_0,D_1,\dots\>\in\mc D_X^\omega\).
   By \(CDFT_{d_i}^+\), we have
@@
 
-  \sloppy
-  The above proof may be easily modified for the Markov case by
-  replacing \(\sigma_i(\<D_i,\dots,D_n\>)\) with \(\sigma_i(D_n,n)\)
-  and \(\tau(\<D_0,\dots,D_n\>)\) with \(\tau(D_n,n)\).
-\end{proof}
-
-\fussy
+  Now let \(\sigma_i\) be a witness for \(CDFT_{d_i}^{+mark}\)
+  for each \(i<\omega\). We define the Markov strategy \(\tau\) for the
+  \(SS\) game by
+  \[
+    \tau(D,n)
+      =
+    \bigcup_{i\leq n}
+    \sigma_i(D,n-i)
+  .\]
+
+  Let \(\<D_0,D_1,\dots\>\in\mc D_X^\omega\).
+  By \(CDFT_{d_i}^{+mark}\), we have
+  \[
+    d_i
+      \in
+    \cl{\bigcup_{i\leq n<\omega}\sigma_i(D_n,n-i)}
+      \subseteq
+    \cl{\bigcup_{i\leq n<\omega}\tau(D_n,n)}
+      \subseteq
+    \cl{\bigcup_{n<\omega}\tau(D_n,n)}
+  \]
+  and as \(D\subseteq\cl{\bigcup_{n<\omega}\tau(D_n,n)}\)
+  it follows that
+  \[
+    X
+      \subseteq
+    \cl D
+      \subseteq
+    \cl{\cl{\bigcup_{n<\omega}\tau(D,n)}}
+      =
+    \cl{\bigcup_{n<\omega}\tau(D,n)}
+  .\]
+  Therefore \(\tau\) witnesses \(SS^{+mark}\).
+\end{proof}
 
@@
 
-\begin{lemma}
+\begin{lemma}\label{mengerFanLemma1}
   Let \(X\) be a \(T_{3\frac{1}{2}}\) topological space.
@@
 
-\begin{lemma}
+\begin{lemma}\label{mengerFanLemma2}
   Let \(X\) be a \(T_{3\frac{1}{2}}\) topological space.
@@
 
-\begin{theorem}
+\begin{theorem}\label{mengerFanTheorem}
   The following are equivalent for any \(T_{3\frac{1}{2}}\)
@@
 
+The reader may note that with this lemma, we may view Theorem
+\ref{mengerFanTheorem} as a generalization of
+\cite[Proposition 2.6]{MR2868880}.
+
 \begin{definition}
@@
 
-\begin{theorem}
+\begin{theorem}\label{omega1OmegaMenger}
   Let \(\omega_1\) have the discrete topology. Then
@@
   \(\schSelGame{\Omega_X}{\Omega_X}\) as follows.
-
-  % Let \(\sigma_0(\<\mc U_0\>)=\{I_0\}\) where \(I_0\) is a co-countable set
-  % containing \(\infty\). Denote
-  % \(\onePtLind{\omega_1}\setminus I_0=\{\alpha_{0,n}:n<\omega\}\),
-  % and then let \(\sigma_0(\<\mc U_0,\dots,\mc U_{n+1}\>)\) contain exactly
-  % one superset of \(\{\infty\}\cup\{\alpha_{0,n}\}\).
 
@@
 
-% It's easily seen that \(CFT^+\) is a hereditary property for all subspaces.
+An affirmative answer to either of these questions would answer
+Question \ref{mainQuestion} negatively.
+
+\begin{question}
+  Does there exist a separable subspace of \(C_p(\onePtLind{\omega_1})\)
+  which is not \(CDFT^{+mark}\)?
+\end{question}
+
+\begin{question}
+  Does there exist a non-\(\sigma\)-compact \(\Omega M^+\) space
+  with a coarser separable metrizable topology?
+\end{question}
 
@@
 \begin{corollary}[\cite{MR2868880}]
-  A countable space \(X\) is \(SS^+\) if and only if it is
+  A countable space is \(SS^+\) if and only if it is
   \(SS^{+mark}\).
@@
 \begin{corollary}
-  A second-countable space \(X\) is \(\Omega M^+\) if and only if
+  A second-countable space is \(\Omega M^+\) if and only if
   it is \(\Omega M^{+mark}\).
@@
 \begin{corollary}[\cite{clontzMengerGamePreprint}]
-  A second-countable space \(X\) is \(M^+\) if and only if
+  A second-countable space is \(M^+\) if and only if
   it is \(M^{+mark}\).
@@
 
+\section{Strong variants of selection princples and games}
+
+Let \(\schStrongSelProp{\mc A}{\mc B},\schStrongSelGame{\mc A}{\mc B}\)
+be the natural variants of
+\(\schSelProp{\mc A}{\mc B},\schSelGame{\mc A}{\mc B}\) where each choice
+by \(\plII\) must either be a single element or singleton
+(whichever is more convenient for the proof at hand), rather than a finite
+set. Convention calls for denoting these as
+\term{strong} versions of the corresponding selection princples and games,
+although the ``strong Menger'' property is commonly known as ``Rothberger''
+who first investigated the principle in \cite{Rothberger1938}. We will thus
+call ``strong \(\Omega\)-Menger'' ``\(\Omega\)-Rothberger'' and shorten it
+with \(\Omega R\), and otherwise attach the prefix ``s''
+when abbreviating to all other strong variants.
+
+\begin{theorem}
+  The following are equivalent for any topological space \(X\).
+  \begin{itemize}
+    \item \(X\) is \(sSS\) (resp. \(sSS^+\), \(sSS^{+mark}\)).
+    \item \(X\) is separable and \(sCDFT\)
+          (resp. \(sCDFT^+\), \(sCDFT^{+mark}\)).
+    \item \(X\) has a countable dense subset \(D\) where
+          \(sCDFT_x\) (resp. \(sCDFT_x^+\), \(sCDFT_x^{+mark}\))
+          holds for all \(x\in D\).
+  \end{itemize}
+\end{theorem}
+
+\begin{proof}
+  We need only show that the final condition implies the first.
+  Let \(D=\{d_i:i<\omega\}\).
+
+  Let \(\{D_{m,n}\in\mc D_X:m,n<\omega\}\), and let \(x_{i,n}\in D_{i,n}\)
+  witness \(sCDFT_{d_i}\), so
+  \[
+    d_i
+      \in
+    \cl{\{x_{i,n}:n<\omega\}}
+      \subseteq
+    \cl{\{x_{m,n}:m,n<\omega\}}
+  \]
+  and as \(D\subseteq\cl{\{x_{m,n}:m,n<\omega\}}\)
+  it follows that
+  \[
+    X
+      \subseteq
+    \cl D
+      \subseteq
+    \cl{\cl{\{x_{m,n}:m,n<\omega\}}}
+      =
+    \cl{\{x_{m,n}:m,n<\omega\}}
+  .\]
+  Therefore \(x_{m,n}\in D_{m,n}\) witnesses \(sSS\).
+
+  Let \(\sigma_i\) be a witness for \(sCDFT_{d_i}^+\)
+  for each \(i<\omega\). Define \(p:\omega\to\omega\) partition \(\omega\)
+  into infinite sets \(\{p(i):i<\omega\}\).
+  For a nonempty finite sequence \(t\), let \(t'\) be its subsequence removing
+  all terms of index \(n\) such that \(p(n)\not=p(|t|-1)\).
+  (Note that this process preserves the final term.)
+  We then define the strategy \(\tau\) by
+  \[
+    \tau(t)
+      =
+    \sigma_{p(|t|-1)}(t')
+  .\]
+
+  Let \(\alpha\in\mc D_X^\omega\), and let \(\alpha_i\) be its subsequence
+  removing all terms of index \(n\) such that \(p(n)\not=i\).
+  By \(sCDFT_{d_i}^+\), we have
+  \[
+    d_i
+      \in
+    \cl{\{\sigma_i(\alpha_i\rest (n+1)):n<\omega\}}
+      =
+    \cl{\{\tau(\alpha\rest(n+1)):n\in p^{\leftarrow}(i)\}}
+      \subseteq
+    \cl{\{\tau(\alpha\rest(n+1)):n<\omega\}}
+  \]
+  and as \(D\subseteq\cl{\{\tau(\alpha\rest(n+1)):n<\omega\}}\)
+  it follows that
+  \[
+    X
+      \subseteq
+    \cl D
+      \subseteq
+    \cl{\cl{\{\tau(\alpha\rest(n+1)):n<\omega\}}}
+      =
+    \cl{\{\tau(\alpha\rest(n+1)):n<\omega\}}
+  .\]
+  Therefore \(\tau\) witnesses \(SS^+\).
+
+  Let \(\sigma_i\) be a witness for \(sCDFT_{d_i}^{+mark}\)
+  for each \(i<\omega\). Define \(p:\omega\to\omega\) partition \(\omega\)
+  into infinite sets \(\{p(i):i<\omega\}\).
+  We then define the Markov strategy \(\tau\) by
+  \[
+    \tau(D,n)
+      =
+    \sigma_{p(n)}(D,|\{m\in p(n):m\leq n\}|)
+  .\]
+
+  Let \(\alpha\in\mc D_X^\omega\), and let \(\alpha_i\) be its subsequence
+  removing all terms of index \(n\) such that \(p(n)\not=i\).
+  By \(sCDFT_{d_i}^{+mark}\), we have
+  \[
+    d_i
+      \in
+    \cl{\{\sigma_i(\alpha_i(n),n):n<\omega\}}
+      =
+    \cl{\{\tau(\alpha(n),n):n\in p^{\leftarrow}(i)\}}
+      \subseteq
+    \cl{\{\tau(\alpha(n),n):n<\omega\}}
+  \]
+  and as \(D\subseteq\cl{\{\tau(\alpha(n),n):n<\omega\}}\)
+  it follows that
+  \[
+    X
+      \subseteq
+    \cl D
+      \subseteq
+    \cl{\cl{\{\tau(\alpha(n),n):n<\omega\}}}
+      =
+    \cl{\{\tau(\alpha(n),n):n<\omega\}}
+  .\]
+  Therefore \(\tau\) witnesses \(SS^{+mark}\).
+\end{proof}
+
+As mentioned earlier, the following is a result of Sakai:
+
+\begin{theorem}[\cite{MR964873}]
+  The following are equivalent for any \(T_{3\frac{1}{2}}\)
+  topological space \(X\).
+    \begin{itemize}
+      \item \(X\) is \(\Omega R\).
+      \item \(C_p(X)\) is \(sCFT\).
+      \item \(C_p(X)\) is \(sCDFT\).
+    \end{itemize}
+\end{theorem}
+
+The corresponding game-theoretic results also hold.
+
+\begin{theorem}
+  The following are equivalent for any \(T_{3\frac{1}{2}}\)
+  topological space \(X\).
+    \begin{itemize}
+      \item \(X\) is \(\Omega R\)
+            (resp. \(\Omega R^+\), \(\Omega R^{+mark}\)).
+      \item \(C_p(X)\) is \(sCFT\)
+            (resp. \(sCFT^+\), \(sCFT^{+mark}\)).
+      \item \(C_p(X)\) is \(sCDFT\)
+            (resp. \(sCDFT^+\), \(sCDFT^{+mark}\)).
+    \end{itemize}
+\end{theorem}
+
+\begin{proof}
+  In Lemmas \ref{mengerFanLemma1} and \ref{mengerFanLemma2},
+  \(|\tau(t)|=|\sigma(t)|\). Therefore they may be extended to
+  the strong cases requiring \(|\tau(t)|=|\sigma(t)|=1\),
+  which yields our result.
+\end{proof}
+
+\begin{theorem}
+  Let \(\omega_1\) have the discrete topology. Then
+  \(\onePtLind{\omega_1}\) is \(\Omega R^+\) but not \(\Omega M^{+mark}\).
+\end{theorem}
+
+\begin{proof}
+  The strategy constructed in Theorem \ref{omega1OmegaMenger} is a witness.
+\end{proof}
+
+\begin{corollary}
+  \(C_p(\onePtLind{\omega_1})\) is \(sCFT^+\) but not \(CDFT^{+mark}\).
+\end{corollary}
+
+\begin{lemma}
+  Let \(\mc A\) be a family of sets where
+  \(|\bigcup\mc A|\leq\omega\)
+  and let \(\mc B\) be a family of sets closed under supersets. Then
+  \(\plII\win\schStrongSelGame{\mc A}{\mc B}\) if and only if
+  \(\plII\markwin\schStrongSelGame{\mc A}{\mc B}\).
+\end{lemma}
+
+\begin{proof}
+  In the proof of Lemma \ref{mainLemma}, \(|\tau(t)|=|\sigma(t)|\).
+\end{proof}
+
+\begin{corollary}
+  A countable space is \(sSS^+\) if and only if it is
+  \(sSS^{+mark}\).
+\end{corollary}
+
+\begin{corollary}
+  A second-countable space is \(\Omega R^+\) if and only if
+  it is \(\Omega R^{+mark}\).
+\end{corollary}
+
+\begin{corollary}
+  A second-countable space is \(R^+\) if and only if
+  it is \(R^{+mark}\).
+\end{corollary}
+
 \section{Acknowledgements}
-The author would like to thank Ziqin Feng for his helpful comments on
-this topic during
-the 31st Summer Conference on Topology and its Applications.
+The author would like to thank Ziqin Feng and Gary Gruenhage
+for their helpful comments on the topic of \(C_p(\onePtLind{\omega_1})\).
 

### 2016-11-17 articles/applications-of-limited-information-strategies-in-mengers-game/article.tex
add keyword
partial revisions

@@
 \usetikzlibrary{matrix}
+\usetikzlibrary{arrows}
 
@@
 
-\keywords{Menger's property, Menger's game, limited information strategies}
+\keywords{Menger property, Menger game, \(\sigma\)-compact spaces,
+limited information strategies}
 
@@
   \(\sigma:M^{\leq k}\to M\); intuitively, it is a strategy which only considers
-  the previous \(k\) moves of the opponent. If a winning \(k\)-tactical strategy
+  the previous \(k\) or less moves of the opponent \(t\in M^{\leq k}\), and yields
+  the appropriate move \(\sigma(t)\) for the player using it.
+  If a winning \(k\)-tactical strategy
   exists for \(\pl P\) in the game \(G\), then we write \(\pl P\ktactwin{k} G\).
@@
   \(\sigma:M^{\leq k}\times\omega\to M\); intuitively, it is a strategy which
-  only considers the previous \(k\) moves of the opponent and the round number.
+  only considers the previous \(k\) or less moves of the opponent
+  \(t\in M^{\leq k}\) and the round number \(n<\omega\),
+  and yields the appropriate move \(\sigma(t,n)\) for the player using it.
   If a winning \(k\)-Markov strategy exists for
@@
         \sigma(\<\underbrace{\mc U,\dots,\mc U}_{m+1}\>,m)
-    \]
+    ,\]
     \[
@@
         \>,(n+1)(k+2)+m)
-    \]
+    .\]
 
@@
       \tau(\<\mc U_n,\mc U_{n+1}\>,n+1)
-    \]
-  Thus \(\tau\) is a winning \(2\)-mark.
+    .\]
+  Thus \(\tau\) is a winning \(2\)-mark. Of course, it is trivial to
+  define a winning \((k+2)\)-mark from a \(2\)-mark by simply ignoring
+  the extra \(k\) moves.
 \end{proof}
@@
 \begin{definition}
-  For any cardinal \(\kappa\), let \(\oneptlind\kappa=\kappa\cup\{\infty\}\) denote
+  For any cardinal \(\kappa\), let \(\onePtLind\kappa=\kappa\cup\{\infty\}\) denote
   the \term{one-point Lindel\"of-ication} of discrete \(\kappa\), where points in
@@
 One may prove directly that
-  \(\pl F \notmarkwin \menGame{\oneptlind{\omega_1}}\)
+  \(\pl F \notmarkwin \menGame{\onePtLind{\omega_1}}\)
 without much effort; however, we postpone stating this until we have
@@
 in regular spaces. Likewise, we postpone proving
-  \(\pl F \kmarkwin2 \menGame{\oneptlind{\omega_1}}\)
+  \(\pl F \kmarkwin2 \menGame{\onePtLind{\omega_1}}\)
 in order to consider an equivalent set-theoretic game.
@@
 
-In \(\menGame{\oneptlind\kappa}\), \(\pl C\) essentially chooses a countable set
+In \(\menGame{\onePtLind\kappa}\), \(\pl C\) essentially chooses a countable set
 to not include in her neighborhood of \(\infty\), followed by \(\pl F\) choosing
@@
 \(\pl F\) need only be concerned with the \textit{intersection} of the
-countable sets chosen by \(\pl C\) in \(\menGame{\oneptlind\kappa}\), rather
+countable sets chosen by \(\pl C\) in \(\menGame{\onePtLind\kappa}\), rather
 than the union as in \(\schFillStrictGame\kappa\).
@@
 strategies, bringing the game further in line with the Menger game played upon
-\(\oneptlind\kappa\).
+\(\onePtLind\kappa\).
 
 We introduce a few games to make the relationship between Scheeper's
-\(\schFillStrictGame\kappa\) and \(\menGame{\oneptlind\kappa}\) more precise.
+\(\schFillStrictGame\kappa\) and \(\menGame{\onePtLind\kappa}\) more precise.
 
@@
 
-\begin{figure}[h]
+% \begin{figure}[h]
+% \begin{center}
+% \begin{tikzpicture}
+%   \matrix (m) [matrix of math nodes,row sep=3em,column sep=1em,minimum width=2em]
+%   {
+%     \pl F \kmarkwin{k+1}\menGame{\onePtLind\kappa} &
+%     \pl F \kmarkwin{k+1}\schFillIntGame\kappa \\
+%
+%     \pl F \kmarkwin{k+1}\schFillInitialGame\kappa &
+%     \pl F \kmarkwin{k+1}\schFillGame\kappa \\
+%
+%     &
+%     \pl F \ktactwin{k+1}\schFillStrictGame\kappa \\
+%   };
+%   \path[>=latex,->]
+%     (m-1-1) edge (m-2-1)
+%     (m-1-2) edge (m-2-2)
+%     (m-3-2) edge (m-2-2);
+%   \path[>=latex,<->]
+%     (m-1-1) edge (m-1-2)
+%     (m-2-1) edge (m-2-2);
+% \end{tikzpicture}
+% \end{center}
+% \caption{Diagram of Scheepers/Menger game implications}
+% \label{GamesDiagram}
+% \end{figure}
+
+\begin{figure}[ht]
 \begin{center}
-\begin{tikzpicture}
-  \matrix (m) [matrix of math nodes,row sep=3em,column sep=1em,minimum width=2em]
-  {
-    \pl F \kmarkwin{k+1}\menGame{\oneptlind\kappa} &
-    \pl F \kmarkwin{k+1}\schFillIntGame\kappa \\
-
-    \pl F \kmarkwin{k+1}\schFillInitialGame\kappa &
-    \pl F \kmarkwin{k+1}\schFillGame\kappa \\
-
-    &
-    \pl F \ktactwin{k+1}\schFillStrictGame\kappa \\
-  };
-  \path[>=latex,->]
-    (m-1-1) edge (m-2-1)
-    (m-1-2) edge (m-2-2)
-    (m-3-2) edge (m-2-2);
-  \path[>=latex,<->]
-    (m-1-1) edge (m-1-2)
-    (m-2-1) edge (m-2-2);
+\begin{tikzpicture}[x=0.8in,y=0.5in]
+% \node at (-3.5,2) {\(\alcompS\kappa\)};
+\node at (-3.5,0) {\(\pl F \ktactwin{(k+1)}\schFillStrictGame\kappa\)};
+% \node at (0,2) {\(\alcompSP\kappa\)};
+\node at (-1.1,1) {\(\pl F \kmarkwin{(k+1)}\menGame{\onePtLind\kappa}\)};
+\node at (0,1) {\(\Leftrightarrow\)};
+\node at (1,1) {\(\pl F \kmarkwin{(k+1)}\schFillIntGame\kappa\)};
+\node at (-1,0) {\(\pl F \kmarkwin{(k+1)}\schFillInitialGame\kappa\)};
+\node at (0,0) {\(\Leftrightarrow\)};
+\node at (1,0) {\(\pl F \kmarkwin{(k+1)}\schFillGame\kappa\)};
+\node at (0,-1) {\(\pl F \kmarkwin{(k+1)}\schFillStrictGame\kappa\)};
+% \draw[-implies,double equal sign distance] (-3.2,2) -- (-0.3,2);
+\draw[-implies,double equal sign distance] (-2.5,0) -- (-2,0);
+% \draw[-implies,double equal sign distance] (-3.5,1.65) -- (-3.5,0.35);
+% \draw[-implies,double equal sign distance] (0,1.65) -- (0,1.35);
+\draw[-implies,double equal sign distance] (0,0.65) -- (0,0.35);
+\draw[-implies,double equal sign distance] (0,-0.35) -- (0,-0.65);
 \end{tikzpicture}
 \end{center}
-\caption{Diagram of Scheepers/Menger game implications}
+\caption{Diagram of Scheeper/Menger game implications}% with \(\alcompS{\kappa},\alcompS{\kappa}\)}
 \label{GamesDiagram}
@@
 \begin{proof}
-  \(\pl F \kmarkwin{k+1}\menGame{\oneptlind\kappa}
+  \(\pl F \kmarkwin{(k+1)}\menGame{\onePtLind\kappa}
     \Rightarrow
-  \pl F \kmarkwin{k+1}\schFillIntGame\kappa\):
-  Let \(\sigma\) be a winning \(k\)-mark for \(\pl F\) in
-  \(\menGame{\oneptlind\kappa}\). Let \(\mc U(C)\) (resp. \(\mc U(s)\)) convert each
+  \pl F \kmarkwin{(k+1)}\schFillIntGame\kappa\):
+  Let \(\sigma\) be a winning \((k+1)\)-mark for \(\pl F\) in
+  \(\menGame{\onePtLind\kappa}\). Let \(\mc U(C)\) (resp. \(\mc U(s)\)) convert each
   countable subset \(C\) of \(\kappa\) (resp. finite sequence \(s\) of such subsets)
-  into the open cover \([C]^1\cup\{\oneptlind\kappa\setminus C\}\)
+  into the open cover \([C]^1\cup\{\onePtLind\kappa\setminus C\}\)
   (resp. finite sequence of such open covers). Then \(\tau\) defined by
@@
 
-  \(\pl F \kmarkwin{k+1}\schFillIntGame\kappa
+  \(\pl F \kmarkwin{(k+1)}\schFillIntGame\kappa
     \Rightarrow
-  \pl F \kmarkwin{k+1}\menGame{\oneptlind\kappa}\):
-  Let \(\sigma\) be a winning \(k\)-mark for \(\pl F\) in
+  \pl F \kmarkwin{(k+1)}\menGame{\onePtLind\kappa}\):
+  Let \(\sigma\) be a winning \((k+1)\)-mark for \(\pl F\) in
   \(\schFillIntGame\kappa\). Let \(C(\mc U)\) (resp. \(C(s)\)) convert each open
-  cover \(\mc U\) of \(\oneptlind\kappa\) (resp. finite sequence \(s\) of such covers)
+  cover \(\mc U\) of \(\onePtLind\kappa\) (resp. finite sequence \(s\) of such covers)
   into a countable set \(C\) which is the complement of some neighborhood of
@@
         =
-      (\oneptlind\kappa\setminus C(\mc U))
+      (\onePtLind\kappa\setminus C(\mc U))
         \cup
-      \sigma(C(s\concat\<\mc U)\>),n)
-    \]
-  is a winning \((k+1)\)-mark for \(\pl F\) in \(\menGame{\oneptlind\kappa}\).
-
-  \(\pl F \kmarkwin{k+1}\schFillIntGame\kappa
+      \sigma(C(s\concat\<\mc U\>),n)
+    \]
+  is a winning \((k+1)\)-mark for \(\pl F\) in \(\menGame{\onePtLind\kappa}\).
+
+  \(\pl F \kmarkwin{(k+1)}\schFillIntGame\kappa
     \Rightarrow
-  \pl F \kmarkwin{k+1}\schFillInitialGame\kappa\):
-  Let \(\sigma\) be a winning \(k\)-mark for \(\pl F\) in
-  \(\schFillIntGame\kappa\). \(\sigma\) is also a winning \(k\)-mark for \(\pl F\)
+  \pl F \kmarkwin{(k+1)}\schFillInitialGame\kappa\):
+  Let \(\sigma\) be a winning \((k+1)\)-mark for \(\pl F\) in
+  \(\schFillIntGame\kappa\). \(\sigma\) is also a winning \((k+1)\)-mark for \(\pl F\)
   in \(\schFillInitialGame\kappa\).
 
-  \(\pl F \kmarkwin{k+1}\schFillInitialGame\kappa
+  \(\pl F \kmarkwin{(k+1)}\schFillInitialGame\kappa
     \Rightarrow
-  \pl F \kmarkwin{k+1}\schFillGame\kappa\): Let \(\sigma\) be a winning \(k\)-mark for \(\pl F\) in
-  \(\schFillInitialGame\kappa\). For each finite sequence \(s\), let \(t\preceq s\) mean \(t\)
+  \pl F \kmarkwin{(k+1)}\schFillGame\kappa\): Let \(\sigma\) be a winning
+  \((k+1)\)-mark for \(\pl F\) in
+  \(\schFillInitialGame\kappa\). For each finite sequence \(s\), let
+  \(t\preceq s\) mean \(t\)
   is a final subsequence of \(s\). Then \(\tau\) defined by
@@
     \]
-  is a winning \((k+1)\)-mark for \(\pl F\) in \(\schFillGame\kappa\).
-
-  \(\pl F \kmarkwin{k+1}\schFillGame\kappa
+  is a winning \((k+1)\)-mark for \(\pl F\) in \(\schFillGame\kappa\),
+  considering that \(\sigma\) ensures that \(C_n\) is covered when
+  attacked by \(\<C_n,C_{n+1},\dots\>\) for all \(n<\omega\).
+
+  \(\pl F \kmarkwin{(k+1)}\schFillGame\kappa
     \Rightarrow
-  \pl F \kmarkwin{k+1}\schFillInitialGame\kappa\):
-  Let \(\sigma\) be a winning \(k\)-mark for \(\pl F\) in
+  \pl F \kmarkwin{(k+1)}\schFillInitialGame\kappa\):
+  Let \(\sigma\) be a winning \((k+1)\)-mark for \(\pl F\) in
   \(\schFillGame\kappa\). \(\sigma\) is also a winning
@@
 
-  \(\pl F \ktactwin{k+1}\schFillStrictGame\kappa
+  \(\pl F \ktactwin{(k+1)}\schFillStrictGame\kappa
     \Rightarrow
-  \pl F \kmarkwin{k+1}\schFillGame\kappa\):
-  Let \(\sigma\) be a winning \(k\)-tactic for \(\pl F\) in
+  \pl F \kmarkwin{(k+1)}\schFillGame\kappa\):
+  Let \(\sigma\) be a winning \((k+1)\)-tactic for \(\pl F\) in
   \(\schFillStrictGame\kappa\). For each countable subset \(C\) of \(\kappa\), let \(C+n\)
   be the union of \(C\) with the \(n\) least ordinals in \(\kappa\setminus C\).
-  Then \(\tau\) defined by
-    \[
-      \tau(\<C_0,\dots,C_i\>,n)
-        =
-      \sigma(\<C_0+(n-i),\dots,C_i+n\>)
-    \]
-  is a winning \((k+1)\)-mark for \(\pl F\) in \(\schFillGame\kappa\).
+  Then for every valid attack \(\<C_0,C_1,C_2,\dots\>\) by \(\pl C\) in
+  \(\schFillGame\kappa\), it follows that \(\<C_0,C_1+1,C_2+2,\dots\>\) is a
+  valid attack by \(\pl C\) in \(\schFillStrictGame\kappa\) as
+  \(C_{n+1}\supseteq C_n\) ensures that
+  \(C_{n+1}+(n+1)\) includes all the \(n\) added elements in \(C_n+n\)
+  in addition to at least one more.
+  Thus \(\tau\) defined by
+    \[
+      \tau(\<C_n,\dots,C_{n+i}\>,n+i)
+        =
+      \sigma(\<C_n+n,\dots,C_{n+i}+(n+i)\>)
+    \]
+  is a winning \((k+1)\)-mark for \(\pl F\) in \(\schFillGame\kappa\),
+  considering that \(\sigma\) ensures that
+  \(\bigcup_{n<\omega}(C_n+n)\supseteq\bigcup_{n<\omega}C_n\)
+  is covered when attacked by \(\<C_0,C_1+1,C_2+2,\dots\>\).
+
+  \(\pl F \kmarkwin{(k+1)}\schFillGame\kappa
+    \Rightarrow
+  \pl F \kmarkwin{(k+1)}\schFillStrictGame\kappa\):
+  Let \(\sigma\) be a winning \((k+1)\)-mark for \(\pl F\) in
+  \(\schFillGame\kappa\). \(\sigma\) is also a winning
+  \((k+1)\)-mark for \(\pl F\)
+  in \(\schFillStrictGame\kappa\).
 \end{proof}
@@
 finding a winning \(2\)-Markov strategy in the Menger game played on
-\(\oneptlind\kappa\).
+\(\onePtLind\kappa\).
 
@@
 
-\begin{figure}[h]
+\begin{figure}[ht]
 \begin{center}
-\begin{tikzpicture}
-  \matrix (m) [matrix of math nodes,row sep=3em,column sep=1em,minimum width=2em]
-  {
-    &
-    \pl F \kmarkwin2\menGame{\oneptlind\kappa} &
-    \pl F \kmarkwin2\schFillIntGame\kappa \\
-
-    \alcompS\kappa &
-    \pl F \kmarkwin2\schFillInitialGame\kappa &
-    \pl F \kmarkwin2\schFillGame\kappa \\
-
-    &
-    &
-    \pl F \ktactwin2\schFillStrictGame\kappa \\
-  };
-  \path[>=latex,->]
-    (m-2-1) edge (m-1-2)
-    (m-2-1) edge (m-2-2)
-    (m-2-1) edge (m-3-3)
-    (m-1-2) edge (m-2-2)
-    (m-1-3) edge (m-2-3)
-    (m-3-3) edge (m-2-3);
-  \path[>=latex,<->]
-    (m-1-2) edge (m-1-3)
-    (m-2-2) edge (m-2-3);
+\begin{tikzpicture}[x=0.8in,y=0.5in]
+\node at (-3.5,1) {\(\alcompS\kappa\)};
+\node at (-3.5,0) {\(\pl F \ktactwin2\schFillStrictGame\kappa\)};
+% \node at (0,2) {\(\alcompSP\kappa\)};
+\node at (-1,1) {\(\pl F \kmarkwin2\menGame{\onePtLind\kappa}\)};
+\node at (0,1) {\(\Leftrightarrow\)};
+\node at (1,1) {\(\pl F \kmarkwin2\schFillIntGame\kappa\)};
+\node at (-1,0) {\(\pl F \kmarkwin2\schFillInitialGame\kappa\)};
+\node at (0,0) {\(\Leftrightarrow\)};
+\node at (1,0) {\(\pl F \kmarkwin2\schFillGame\kappa\)};
+\node at (0,-1) {\(\pl F \kmarkwin2\schFillStrictGame\kappa\)};
+\draw[-implies,double equal sign distance] (-3.2,1) -- (-1.9,1);
+\draw[-implies,double equal sign distance] (-2.6,0) -- (-1.9,0);
+\draw[-implies,double equal sign distance] (-3.5,0.65) -- (-3.5,0.35);
+% \draw[-implies,double equal sign distance] (0,1.65) -- (0,1.35);
+\draw[-implies,double equal sign distance] (0,0.65) -- (0,0.35);
+\draw[-implies,double equal sign distance] (0,-0.35) -- (0,-0.65);
 \end{tikzpicture}
 \end{center}
-\caption{Diagram of Scheeper/Menger game implications with \(\alcompS\kappa\)}
+\caption{Diagram of Scheeper/Menger game implications}% with \(\alcompS{\kappa},\alcompS{\kappa}\)}
 \label{GamesDiagram2}
@@
       \}
-    \]
+    .\]
   For any attack \(\<A_0,A_1,\dots\>\) by \(\pl C\) and
@@
 \begin{corollary}
-  \(\pl F \kmarkwin2\menGame{\oneptlind\omega_1}\).
+  \(\pl F \kmarkwin2\menGame{\onePtLind\omega_1}\).
 \end{corollary}
@@
   };
-  \path[>=latex,<->]
-    (m-1-1) edge (m-2-1)
-    (m-1-2) edge (m-2-2)
-    (m-1-3) edge (m-2-3)
-    (m-1-4) edge (m-2-4);
-  \path[>=latex,->]
-    (m-1-1) edge (m-1-2)
-    (m-2-1) edge (m-2-2)
-    (m-1-2) edge (m-1-3)
-    (m-2-2) edge (m-2-3)
-    (m-1-3) edge (m-1-4)
-    (m-2-3) edge (m-2-4);
+
+  \draw[implies-implies,double equal sign distance]
+    (m-1-1) -- (m-2-1);
+  \draw[implies-implies,double equal sign distance]
+    (m-1-2) -- (m-2-2);
+  \draw[implies-implies,double equal sign distance]
+    (m-1-3) -- (m-2-3);
+  \draw[implies-implies,double equal sign distance]
+    (m-1-4) -- (m-2-4);
+
+  \draw[-implies,double equal sign distance]
+    (m-1-1) -- (m-1-2);
+  \draw[-implies,double equal sign distance]
+    (m-2-1) -- (m-2-2);
+  \draw[-implies,double equal sign distance]
+    (m-1-2) -- (m-1-3);
+  \draw[-implies,double equal sign distance]
+    (m-2-2) -- (m-2-3);
+  \draw[-implies,double equal sign distance]
+    (m-1-3) -- (m-1-4);
+  \draw[-implies,double equal sign distance]
+    (m-2-3) -- (m-2-4);
+
+  \draw[-implies,double equal sign distance,bend right=30]
+    (m-1-2) -- node {\( \not \)} (m-1-1);
   \path[>=latex,->,bend right=30, dotted]
-    (m-1-2) edge node {\( \not \)} (m-1-1)
     (m-2-2) edge node {\( \not \)} (m-2-1)
@@
 \end{center}
-\caption{Diagram of covering properties related to the Menger game}
+\caption{Diagram of covering properties related to the Menger game TODO FIX}
 \label{menSpec}
@@
 \begin{corollary}
-  \(\pl F\notmarkwin\menGame{\oneptlind{\omega_1}}\).
+  \(\pl F\notmarkwin\menGame{\onePtLind{\omega_1}}\).
 \end{corollary}
@@
     \bigcup \mc F(s,\mc V)
-  \]
+  .\]
 
@@
     \bigcup \mc F(t(n),\mc V)
-  \]
+  .\]
 
@@
     \end{array}
-  \]
+  .\]
 
@@
       c(\mc V,n)=\{ x\in Y : r_{\mc V}(x)\leq n\}
-    \]
+    ,\]
     \[
       p(\mc U,\mc V,n+1)=\{ x\in Y : n<r_{\mc U}(x)<r_{\mc V}(x)\}
-    \]
+    .\]
 \end{definition}
@@
 \begin{theorem}
-  \(\alcompS\kappa\) implies \(\oneptlind\kappa\) is
+  \(\alcompS\kappa\) implies \(\onePtLind\kappa\) is
   robustly Menger.
@@
   \(A(\mc U)\in[\kappa]^{\leq\omega}\) for each open cover \(\mc U\) such that
-  \(\oneptlind\kappa\setminus A(\mc U)\) is contained in some element of
+  \(\onePtLind\kappa\setminus A(\mc U)\) is contained in some element of
   \(\mc U\).
-  Then let \(r_{\mc U}(x)=0\) for \(x\in\oneptlind\kappa\setminus A(\mc U)\),
+  Then let \(r_{\mc U}(x)=0\) for \(x\in\onePtLind\kappa\setminus A(\mc U)\),
   and \(r_{\mc U}(\alpha)=f_{A(\mc U)}(\alpha)\) for \(\alpha\in A(\mc U)\).
@@
         =
-      \left(\oneptlind\kappa\setminus A(\mc U)\right)
+      \left(\onePtLind\kappa\setminus A(\mc U)\right)
         \cup
@@
       \sigma(\<\mc U\>,0) = \sigma_0(\<\mc U\>,0)
-    \]
+    ,\]
     \[
@@
       \sigma_i(\<\mc U,\mc V\>,j+1)
-    \]
+    .\]
 
@@
     \sigma(\<\mc U_n,\mc U_{n+1}\>,n+1)
-  \]
+  .\]
   It then follows that \(x\) is not contained in

### 2016-11-30 articles/applications-of-limited-information-strategies-in-mengers-game/article.tex
finish revisions

@@
 \usetikzlibrary{arrows}
+
+\usepackage{tikz-cd}
+\usetikzlibrary{decorations.markings}
+\tikzset{not/.style={
+  decoration={markings,
+    mark= at position 0.5 with {
+      \node[transform shape] (tempnode) {$\backslash$};
+    }
+  },
+  postaction={decorate}
+}}
+\tikzset{maybe/.style={
+  color=gray,
+  decoration={markings,
+    mark=at position 0.5 with {
+      \node[color=black] (tempnode) {$?$};
+    }
+  },
+  postaction={decorate}
+}}
 
@@
 \author{Steven Clontz}
-\address{Department of Mathematics and Statistics, UNC Charlotte,
-Charlotte, NC 28262}
-\email{steven.clontz@gmail.edu}
-\urladdr{stevenclontz.com}
+\address{Department of Mathematics and Statistics, University of South Alabama,
+Mobile, AL 36688}
+\email{sclontz@southalabama.edu}
+\urladdr{clontz.org}
 
@@
 \begin{abstract}
-  As shown by Telgarsky and Scheepers,
+  As shown by Telg\'arsky and Scheepers,
   winning strategies in the Menger game characterize
@@
 \begin{center}
-\begin{tikzpicture}[x=0.8in,y=0.5in]
-% \node at (-3.5,2) {\(\alcompS\kappa\)};
-\node at (-3.5,0) {\(\pl F \ktactwin{(k+1)}\schFillStrictGame\kappa\)};
-% \node at (0,2) {\(\alcompSP\kappa\)};
-\node at (-1.1,1) {\(\pl F \kmarkwin{(k+1)}\menGame{\onePtLind\kappa}\)};
-\node at (0,1) {\(\Leftrightarrow\)};
-\node at (1,1) {\(\pl F \kmarkwin{(k+1)}\schFillIntGame\kappa\)};
-\node at (-1,0) {\(\pl F \kmarkwin{(k+1)}\schFillInitialGame\kappa\)};
-\node at (0,0) {\(\Leftrightarrow\)};
-\node at (1,0) {\(\pl F \kmarkwin{(k+1)}\schFillGame\kappa\)};
-\node at (0,-1) {\(\pl F \kmarkwin{(k+1)}\schFillStrictGame\kappa\)};
-% \draw[-implies,double equal sign distance] (-3.2,2) -- (-0.3,2);
-\draw[-implies,double equal sign distance] (-2.5,0) -- (-2,0);
-% \draw[-implies,double equal sign distance] (-3.5,1.65) -- (-3.5,0.35);
-% \draw[-implies,double equal sign distance] (0,1.65) -- (0,1.35);
-\draw[-implies,double equal sign distance] (0,0.65) -- (0,0.35);
-\draw[-implies,double equal sign distance] (0,-0.35) -- (0,-0.65);
-\end{tikzpicture}
+\begin{tikzcd}[arrows=Rightarrow]
+  &
+  \pl F \kmarkwin{k+1} \menGame{\onePtLind\kappa}
+  \Leftrightarrow
+  \pl F \kmarkwin{k+1} \schFillIntGame{\kappa}
+    \arrow[d] \\
+  \pl F \ktactwin{k+1} \schFillStrictGame{\kappa}
+    \arrow[r] &
+  \pl F \kmarkwin{k+1}\schFillGame{\kappa}
+  \Leftrightarrow
+  \pl F \kmarkwin{k+1} \schFillInitialGame{\kappa}
+      \arrow[d] \\
+  &
+  \pl F \kmarkwin{k+1} \schFillStrictGame{\kappa}
+\end{tikzcd}
 \end{center}
-\caption{Diagram of Scheeper/Menger game implications}% with \(\alcompS{\kappa},\alcompS{\kappa}\)}
+\caption{Diagram of Scheeper/Menger game implications}
 \label{GamesDiagram}
@@
 \begin{proof}
-  For \(\alcompS{\omega_1}\), consider the construction of an Aronzajn tree
-  as in \cite{MR597342}; this of course
+  The construction of an Aronzajn tree in \cite[Theorem 5.9]{MR597342}
+  produced a witness for \(\alcompS{\omega_1}\); this of course
   implies \(\alcompS{\mf c}\) under \(CH\).
@@
 \begin{figure}[ht]
-\begin{center}
-\begin{tikzpicture}[x=0.8in,y=0.5in]
-\node at (-3.5,1) {\(\alcompS\kappa\)};
-\node at (-3.5,0) {\(\pl F \ktactwin2\schFillStrictGame\kappa\)};
-% \node at (0,2) {\(\alcompSP\kappa\)};
-\node at (-1,1) {\(\pl F \kmarkwin2\menGame{\onePtLind\kappa}\)};
-\node at (0,1) {\(\Leftrightarrow\)};
-\node at (1,1) {\(\pl F \kmarkwin2\schFillIntGame\kappa\)};
-\node at (-1,0) {\(\pl F \kmarkwin2\schFillInitialGame\kappa\)};
-\node at (0,0) {\(\Leftrightarrow\)};
-\node at (1,0) {\(\pl F \kmarkwin2\schFillGame\kappa\)};
-\node at (0,-1) {\(\pl F \kmarkwin2\schFillStrictGame\kappa\)};
-\draw[-implies,double equal sign distance] (-3.2,1) -- (-1.9,1);
-\draw[-implies,double equal sign distance] (-2.6,0) -- (-1.9,0);
-\draw[-implies,double equal sign distance] (-3.5,0.65) -- (-3.5,0.35);
-% \draw[-implies,double equal sign distance] (0,1.65) -- (0,1.35);
-\draw[-implies,double equal sign distance] (0,0.65) -- (0,0.35);
-\draw[-implies,double equal sign distance] (0,-0.35) -- (0,-0.65);
-\end{tikzpicture}
-\end{center}
-\caption{Diagram of Scheeper/Menger game implications}% with \(\alcompS{\kappa},\alcompS{\kappa}\)}
+\begin{tikzcd}[arrows=Rightarrow]
+  \alcompS\kappa
+    \arrow[r]
+    \arrow[d] &
+  \pl F \kmarkwin2 \menGame{\onePtLind\kappa}
+  \Leftrightarrow
+  \pl F \kmarkwin2 \schFillIntGame{\kappa}
+    \arrow[d] \\
+  \pl F \ktactwin2 \schFillStrictGame{\kappa}
+    \arrow[r] &
+  \pl F \kmarkwin2\schFillGame{\kappa}
+  \Leftrightarrow
+  \pl F \kmarkwin2 \schFillInitialGame{\kappa}
+      \arrow[d] \\
+  &
+  \pl F \kmarkwin2 \schFillStrictGame{\kappa}
+\end{tikzcd}
+\caption{Diagram of Scheeper/Menger game implications with \(\alcompS\kappa\)}
 \label{GamesDiagram2}
@@
   Since \(\alcompS\kappa\Rightarrow\pl F \ktactwin2\schFillStrictGame\kappa\) was
-  a main result of \cite{MR1129143}, it is sufficient to show that
+  a main result of \cite{MR1129143}, we need only show that
   \(\alcompS\kappa\Rightarrow \pl F \kmarkwin2\schFillIntGame\kappa\).
@@
     \[
-      \sigma(\<A\>,0) = \{\alpha\in A: f_A(\alpha) \leq 0 \}
-    \]
-    \[
-      \sigma(\<A,B\>,n+1)
+      \sigma(\<C\>,0) = \{\alpha\in C: f_C(\alpha) \leq 0 \}
+    \]
+    \[
+      \sigma(\<C,D\>,n+1)
         =
       \{
-        \alpha \in A\cap B
+        \alpha \in C\cap D
       :
-        f_B(\alpha) \leq n+1 \text{ or }
-        f_A(\alpha)\not=f_B(\alpha)
+        f_D(\alpha) \leq n+1 \text{ or }
+        f_C(\alpha)\not=f_D(\alpha)
       \}
     .\]
-  For any attack \(\<A_0,A_1,\dots\>\) by \(\pl C\) and
-  \(\alpha\in\bigcap_{n<\omega}A_n\), either \(f_{A_n}(\alpha)\) is constant for
-  all \(n\), or \(f_{A_n}(\alpha)\not=f_{A_{n+1}}(\alpha)\) for some \(n\);
+  For any attack \(\<C_0,C_1,\dots\>\) by \(\pl C\) and
+  \(\alpha\in\bigcap_{n<\omega}C_n\), either \(f_{C_n}(\alpha)\) is constant for
+  all \(n\), or \(f_{C_n}(\alpha)\not=f_{C_{n+1}}(\alpha)\) for some \(n\);
   either way, \(\alpha\) is covered.
@@
 \begin{corollary}
-  \(\pl F \kmarkwin2\menGame{\onePtLind\omega_1}\).
+  \(\pl F \kmarkwin2\menGame{\onePtLind{\omega_1}}\).
 \end{corollary}
@@
 \begin{figure}[h]
-\begin{center}
-\begin{tikzpicture}
-  \matrix (m) [matrix of math nodes,row sep=3em,column sep=1em,minimum width=2em]
-  {
-     \pl F \markwin \menGame{X} &
-     \pl F \kmarkwin2 \menGame{X} &
-     \pl F \win \menGame{X} &
-     \pl C \notwin \menGame{X} \\
-
+\begin{tikzcd}[arrows=Rightarrow]
+  \pl F \markwin \menGame{X}
+    \arrow[r]
+    \arrow[d,Leftrightarrow] &
+  \pl F \kmarkwin2 \menGame{X}
+    \arrow[r]
+    \arrow[out=150,in=30,not,l]
+    \arrow[d,Leftrightarrow] &
+  \pl F \win \menGame{X}
+    \arrow[r]
+    \arrow[out=150,in=30,maybe,l]
+    \arrow[d,Leftrightarrow] &
+  \pl C \notwin \menGame{X}
+    \arrow[out=150,in=30,not,l]
+    \arrow[d,Leftrightarrow] \\
   \text{Markov Menger} &
   2\text{-Markov Menger} &
-     \text{Strategic Menger} &
-     \text{Menger} \\
-  };
-
-  \draw[implies-implies,double equal sign distance]
-    (m-1-1) -- (m-2-1);
-  \draw[implies-implies,double equal sign distance]
-    (m-1-2) -- (m-2-2);
-  \draw[implies-implies,double equal sign distance]
-    (m-1-3) -- (m-2-3);
-  \draw[implies-implies,double equal sign distance]
-    (m-1-4) -- (m-2-4);
-
-  \draw[-implies,double equal sign distance]
-    (m-1-1) -- (m-1-2);
-  \draw[-implies,double equal sign distance]
-    (m-2-1) -- (m-2-2);
-  \draw[-implies,double equal sign distance]
-    (m-1-2) -- (m-1-3);
-  \draw[-implies,double equal sign distance]
-    (m-2-2) -- (m-2-3);
-  \draw[-implies,double equal sign distance]
-    (m-1-3) -- (m-1-4);
-  \draw[-implies,double equal sign distance]
-    (m-2-3) -- (m-2-4);
-
-  \draw[-implies,double equal sign distance,bend right=30]
-    (m-1-2) -- node {\( \not \)} (m-1-1);
-  \path[>=latex,->,bend right=30, dotted]
-    (m-2-2) edge node {\( \not \)} (m-2-1)
-    (m-1-4) edge node {\( \not \)} (m-1-3)
-    (m-2-4) edge node {\( \not \)} (m-2-3);
-  \path[>=latex,->,bend right=30, dotted]
-    (m-1-3) edge node {\( ? \)} (m-1-2)
-    (m-2-3) edge node {\( ? \)} (m-2-2);
-\end{tikzpicture}
-\end{center}
-\caption{Diagram of covering properties related to the Menger game TODO FIX}
+  \text{strategic Menger} &
+  \text{Menger}
+\end{tikzcd}
+\caption{Diagram of covering properties related to the Menger game}
 \label{menSpec}
@@
 
-Limited information strategies for the Menger game naturally define a spectrum
-of covering properties, see Figure \ref{menSpec}. However,
+Limited information strategies for the Menger game naturally define the
+spectrum of covering properties shown in Figure \ref{menSpec}. However,
 we do not know if the middle two properties are actually distinct.
@@
 Menger spaces are exactly the metrizable \(\sigma\)-compact spaces, shown first
-by Telgarksy in \cite{MR753073} and later directly by Scheepers in
+by Telg\'arsky in \cite{MR753073} and later directly by Scheepers in
 \cite{MR1273523}. It's Scheepers' technique which gives inspiration to
@@
 
-  Let \(\mc U=\{U_\alpha:\alpha<\kappa\}\) be an
-  open cover of \(\text{cl}_X(Y)\); for \(y\in Y\), apply regularity to get
-  \(V_\alpha\subseteq\text{cl}_X(V_\alpha)\subseteq U_\alpha\)
-  with \(V_\alpha\) open.
-  Use relative compactness to obtain a finite subcollection of
-  \(\{X\setminus\text{cl}_X(Y)\}\cup\{V_\alpha:\alpha<\kappa\}\)
-  covering \(Y\): \(\{V_{\alpha_i}:i<n\}\). Then since
-  \(\bigcup\{\text{cl}_X(V_{\alpha_i}):i<n\}\) is a closed set in \(X\)
+  Let \(\mc U=\{U_y:y\in\text{cl}_X(Y)\}\) where each \(U_y\) is an open
+  set in \(X\) containing \(y\); apply regularity to get
+  \(y\in V_{y}\subseteq\text{cl}_X(V_{y})\subseteq U_{y}\)
+  with \(V_{y}\) open in \(X\).
+  Then \(\{X\setminus\text{cl}_X(Y)\}\cup\{V_{y}:y\in \text{cl}_X(Y)\}\)
+  is an open cover of \(X\), so
+  use relative compactness to choose a finite subset \(F\) of \(\text{cl}_X(Y)\)
+  such that \(\{V_{y}:y\in F\}\) is a finite cover of \(Y\). Then since
+  \(\bigcup\{\text{cl}_X(V_{y}):y\in F\}\) is a closed set in \(X\)
   containing \(Y\), it contains \(\text{cl}_X(Y)\), and thus
-  \(\{U_{\alpha_i}:i<n\}\) is a finite subcollection of \(\mc U\) covering
+  \(\{U_{y}:y\in F\}\) is a finite subcollection of \(\mc U\) covering
   \(\text{cl}_X(Y)\).
@@
 
+  We proceed by constructing basic open covers indexed by \(\omega^{<\omega}\)
+  which will turn out to emulate the behavior of \(\pl C\) well enough
+  that \(\pl F\) will be able to define a Markov strategy from a perfect
+  information strategy by substituting
+  these covers in the place of perfect information.
   So if \(\mc U_t\) is a basic open cover for \(t<s\in\omega^{<\omega}\), and
@@
 \begin{proof}
-  If \(X=\bigcup_{n<\omega}R_n\), then for all \(\mc U\), let \(r_{\mc U}(x)\) be the
+  If \(X=\bigcup_{n<\omega}R_n\) for \(R_n\) relatively compact to \(X\),
+  then for all \(\mc U\), let \(r_{\mc U}(x)\) be the
   least \(n\) such that \(x\in R_n\). Then \(c(\mc V,n)=\bigcup_{m\leq n}R_m\) and
-  \(p(\mc U,\mc V) = \emptyset\).
+  \(p(\mc U,\mc V,n+1) = \emptyset\).
 \end{proof}
@@
 
-We may also consider common counterexamples which are finer
+We may also consider common counterexamples (specifically, examples
+67 and 63 of \cite{MR1382863}) which are finer
 than the usual Euclidean line.
@@
   intervals with rational endpoints (with or without rationals removed)
-  witnesses second-countability, and \([-n,n]\) is relatively compact.
+  witnesses second-countability.
+
+  We now will show that \([-n,n]\setminus\mathbb Q\) is relatively compact.
+  Let \(\mc U\) be a cover of
+  \(R_{\mathbb Q}\) by open intervals with the rationals removed,
+  and let \(\mc V\) be the corresponding cover of open intervals.
+  There exists a finite subcollection of \(\mc V\) which covers
+  \([-n,n]\), so there exists a corresponding subcollection of
+  \(\mc U\) which covers \([-n,n]\setminus\mathbb Q\).
+  Thus
+  \(R_{\mathbb Q}=\mathbb Q\cup\bigcup_{n<\omega}([-n,n]\setminus\mathbb Q)\)
+  is a countable union of relatively compact subsets.
 \end{proof}
@@
 \end{definition}
+
+\begin{lemma}\label{rOmegaLemma}
+  For each compact subset \(K\) of \(\mathbb R\)
+  and open cover \(\mc U\) of \(R_\omega\),
+  there exists a countable set \(C\) such that \([a,b]\setminus C\)
+  is \(\mc U\)-finite.
+\end{lemma}
+
+\begin{proof}
+  Let \(\mc V\) be the corresponding open cover of \(\mathbb R\) where
+  \(\mc U\) may be obtained by removing countable sets from members of
+  \(\mc V\). Choose a finite subcollection \(\mc G\) of \(\mc V\) which
+  covers \(K\), and then note that the corresponding finite subcollection
+  \(\mc F\) of \(\mc U\) covers \([-n,n]\setminus C\) where \(C\) is the
+  finite union of the countable sets removed from sets in \(\mc G\)
+  to obtain the sets in \(\mc F\).
+\end{proof}
 
@@
 \begin{proof}
-  If \(S\supseteq\{s_n:n<\omega\}\) for \(s_n\)
-  discrete, then \(U_m=R_\omega\setminus\{s_n:m<n<\omega\}\) yields an
-  infinite cover \(\{U_m:m<\omega\}\) with no finite subcollection covering \(S\),
-  showing that all relatively compact sets are finite, and \(R_\omega\) is not
-  \(\sigma\)-relatively-compact.
-
-  Define the winning strategy \(\sigma\) for \(\pl F\) in \(\menGame{R_\omega}\) as
-  follows: let \(\sigma(\<\mc{U}_0,\dots,\mc{U}_{2n}\>)=[-n,n]\setminus C_n\)
-  for some countable \(C_n=\{c_{n,m}: m<\omega\}\),
+  If \(S\supseteq\{s_n:n<\omega\}\) for distinct \(s_n\),
+  then \(U_m=R_\omega\setminus\{s_n:m<n<\omega\}\) yields an
+  infinite cover \(\{U_m:m<\omega\}\) with no finite subcollection covering
+  \(S\), showing that all relatively compact sets are finite, and \(R_\omega\)
+  is not \(\sigma\)-relatively-compact. The set \(R_\omega\setminus\mathbb Q\)
+  is open, but the closure of any open subset must contain a rational, so
+  this space is not regular. Finally, the space is not second-countable,
+  since for any countable collection of open sets \(\{U_n:n<\omega\}\),
+  we may choose \(p_n\in U_n\)
+  and note \(R_\omega\setminus\{p_n:n<\omega\}\) is an open set not containing
+  any \(U_n\).
+
+  Define the winning strategy \(\sigma\) for \(\pl F\) in
+  \(\menGame{R_\omega}\) as follows: let
+  \(\sigma(\<\mc{U}_0,\dots,\mc{U}_{2n}\>)=[-n,n]\setminus C_n\)
+  where \(C_n\) witnesses Lemma \ref{rOmegaLemma} for \([-n,n]\)
+  and \(\mc U_{2n}\),
   and let \(\sigma(\<\mc{U}_0,\dots,\mc{U}_{2n+1}\>)=\{c_{i,j} : i,j < n\}\).
@@
   robustly Menger. Let \(f_A\) witness \(\alcompS{\mf c}\)
-  for \(A\in[[a,b]]^{\leq\omega}\).
-  For each open cover \(\mc U\), let \(A_{\mc U}\) be
-  such that \([0,1]\setminus A_{\mc U}\) is \(\mc U\)-finite.
+  for \(A\in[[0,1]]^{\leq\omega}\).
+  For each open cover \(\mc U\), let \(A_{\mc U}\) witness Lemma
+  \ref{rOmegaLemma} for \([0,1]\) and \(\mc U\).
   Let \(r_{\mc U}(x)=0\) if \(x\in[0,1]\setminus A_{\mc U}\) and

### 2016-11-30 articles/applications-of-limited-information-strategies-in-mengers-game/article.tex
fix lem 5.10

@@
 
-\keywords{Menger property, Menger game, \(\sigma\)-compact spaces,
+\keywords{Menger property, Menger game, , \(\sigma\)-compact spaces,
 limited information strategies}
@@
   and open cover \(\mc U\) of \(R_\omega\),
-  there exists a countable set \(C\) such that \([a,b]\setminus C\)
+  there exists a countable set \(C\) such that \(K\setminus C\)
   is \(\mc U\)-finite.
@@
   covers \(K\), and then note that the corresponding finite subcollection
-  \(\mc F\) of \(\mc U\) covers \([-n,n]\setminus C\) where \(C\) is the
+  \(\mc F\) of \(\mc U\) covers \(K\setminus C\) where \(C\) is the
   finite union of the countable sets removed from sets in \(\mc G\)

### 2017-01-24 articles/almost-compatible-functions-and-topological-games/article.tex
final revisions per referee

@@
   and that it is possible to force \(\mf c\) to be arbitrarily large
-  while preserving \(\alcompS{\mf c}\). However, \(\alcompS{\mf c^+}\) always fails.
+  while preserving \(\alcompS{\mf c}\); however,
+  it was also shown that \(\alcompS{\mf c^+}\) always fails.
   This axiom may be applied to obtain a winning \(2\)-tactic for \(\pl F\)
@@
 
-  We now construct a topology on \(\omega_n\) for each \(n<\omega\) which
-  will witness a Kurepa family of size \(\aleph_n\), exploiting a theorem of
+  We now make use of
+  a topology on \(\omega_n\) for each \(n<\omega\) that
+  witnesses a Kurepa family of size \(\aleph_n\), due to a theorem of
   Juh\'asz et. al. in \cite{MR539228}.
@@
   As noted in \cite{MR1229125}, Jensen's one-gap two-cardinal theorem under
-  \(V=L\) introduced in \cite{MR0309729} implies that \(\kurepaS\kappa\)
-  holds for all cardinals \(\kappa\).
-
-  \begin{corollary}[\(V=L\)]\label{alcompSPunderV=L}
-    \(\alcompSP{\kappa}\) for all cardinals \(\kappa\).
+  \(V=L\) introduced in \cite{MR0309729} implies that \(\kurepaS\kappa\),
+  and therefore \(\alcompSP\kappa\), holds for all cardinals \(\kappa\).
+  However, the authors wish to thank their anonymous referree for
+  observing the following improvement:
+
+  \begin{corollary}\label{alcompSPunderV=L}
+    Assume the covering lemma over the Core Model holds. Then
+    \(\alcompSP{\kappa}\) holds for all cardinals \(\kappa\).
   \end{corollary}
+
+  \begin{proof}
+    Juh\'asz and Weiss note in \cite[pg. 186]{juhaszgood} that the covering
+    lemma over the Core Model guarantees \(\splendidS\kappa\), and therefore
+    \(\kurepaS\kappa\) and \(\alcompSP\kappa\), when
+    \(\cf\kappa>\omega\).
+  \end{proof}
 
@@
   We are also able to force \(\alcompSP{\kappa}\) to fail for every cardinal
-  other than the first \(\omega\)-many we've already guaranteed.
+  other than the first \(\omega\)-many we've already guaranteed. The authors
+  again thank the referee for observing that the following result
+  contrasts very nicely with Corollary \ref{alcompSPunderV=L}: large cardinals
+  are necessary to find \(\kappa>\aleph_\omega\) with \(\cf\kappa>\omega\)
+  where \(\splendidS\kappa\) fails.
 
@@
 \end{center}
-\caption{Diagram of Scheeper/Menger game implications with \(\alcompS{\kappa},\alcompS{\kappa}\)}
+\caption{Diagram of Scheeper/Menger game implications with \(\alcompS{\kappa},\alcompSP{\kappa}\)}
 \label{GamesDiagram}

### 2017-03-15 articles/applications-of-limited-information-strategies-in-mengers-game/article.tex
update applications of limited info menger with final revisions

@@
   For any cardinal \(\kappa\), let \(\onePtLind\kappa=\kappa\cup\{\infty\}\) denote
-  the \term{one-point Lindel\"of-ication} of discrete \(\kappa\), where points in
+  the \term{one-point Lindel\"ofication} of discrete \(\kappa\), where points in
   \(\kappa\) are isolated, and the neighborhoods of \(\infty\) are the co-countable
@@
   \(F_0\in[\kappa]^{<\omega}\). In round \(n+1\), \(\pl C\) chooses
-  \(C_{n+1}\in[\kappa]^{\leq\omega}\) such that \(C_{n+1}\supset C_n\), followed
-  by \(\pl F\) choosing \(F_{n+1}\in[\kappa]^{<\omega}\).
+  \(C_{n+1}\in[\kappa]^{\leq\omega}\) such that \(C_{n+1}\supsetneq C_n\),
+  followed by \(\pl F\) choosing \(F_{n+1}\in[\kappa]^{<\omega}\).
 
@@
   &
-  \pl F \kmarkwin{k+1} \menGame{\onePtLind\kappa}
-  \Leftrightarrow
-  \pl F \kmarkwin{k+1} \schFillIntGame{\kappa}
+  \pl F \kmarkwin{(k+1)} \menGame{\onePtLind\kappa}
+    \arrow[d]
+    \arrow[r,Leftrightarrow]
+  &
+  \pl F \kmarkwin{(k+1)} \schFillIntGame{\kappa}
       \arrow[d]  \\
-  \pl F \ktactwin{k+1} \schFillStrictGame{\kappa}
+  \pl F \ktactwin{(k+1)} \schFillStrictGame{\kappa}
     \arrow[r] &
-  \pl F \kmarkwin{k+1}\schFillGame{\kappa}
-  \Leftrightarrow
-  \pl F \kmarkwin{k+1} \schFillInitialGame{\kappa}
-      \arrow[d] \\
+  \pl F \kmarkwin{(k+1)}\schFillGame{\kappa}
+      \arrow[d]
+      \arrow[r,Leftrightarrow]
   &
-  \pl F \kmarkwin{k+1} \schFillStrictGame{\kappa}
+  \pl F \kmarkwin{(k+1)} \schFillInitialGame{\kappa}
+    \arrow[ld]\\
+  &
+  \pl F \kmarkwin{(k+1)} \schFillStrictGame{\kappa}
 \end{tikzcd}
@@
     \]
+  where \(|s|\leq k\)
   is a winning \((k+1)\)-mark for \(\pl F\) in \(\schFillIntGame\kappa\).
@@
     \]
+  where \(|s|\leq k\)
   is a winning \((k+1)\)-mark for \(\pl F\) in \(\menGame{\onePtLind\kappa}\).
@@
     \]
+  where \(|s|\leq k\)
   is a winning \((k+1)\)-mark for \(\pl F\) in \(\schFillGame\kappa\),
@@
     \]
+  where \(i\leq k\)
   is a winning \((k+1)\)-mark for \(\pl F\) in \(\schFillGame\kappa\),
@@
     \arrow[d] &
-  \pl F \kmarkwin2 \menGame{\onePtLind\kappa}
-  \Leftrightarrow
-  \pl F \kmarkwin2 \schFillIntGame{\kappa}
+      \pl F \kmarkwin{(k+1)} \menGame{\onePtLind\kappa}
+        \arrow[d]
+        \arrow[r,Leftrightarrow]
+      &
+      \pl F \kmarkwin{(k+1)} \schFillIntGame{\kappa}
           \arrow[d]  \\
-  \pl F \ktactwin2 \schFillStrictGame{\kappa}
+      \pl F \ktactwin{(k+1)} \schFillStrictGame{\kappa}
         \arrow[r] &
-  \pl F \kmarkwin2\schFillGame{\kappa}
-  \Leftrightarrow
-  \pl F \kmarkwin2 \schFillInitialGame{\kappa}
-      \arrow[d] \\
+      \pl F \kmarkwin{(k+1)}\schFillGame{\kappa}
+          \arrow[d]
+          \arrow[r,Leftrightarrow]
       &
-  \pl F \kmarkwin2 \schFillStrictGame{\kappa}
+      \pl F \kmarkwin{(k+1)} \schFillInitialGame{\kappa}
+        \arrow[ld]\\
+      &
+      \pl F \kmarkwin{(k+1)} \schFillStrictGame{\kappa}
 \end{tikzcd}
@@
 \begin{lemma}
-  Let \(\sigma(\mc{U}, n)\) be a Markov strategy for \(F\) in
+  Let \(\sigma\) be a Markov strategy for \(\pl F\) in
   \(\menGame{X}\), and \(\mc{O}\) collect all open covers of \(X\). Then the
@@
   If \(X=\bigcup_{n<\omega} R_n\) for \(R_n\) relatively compact, then
-  \(\sigma(n)=R_n\) is a winning \(0\)-mark, which of course gives a
+  \(\sigma(n)=R_n\) defines a winning \(0\)-mark \(\sigma\),
+  which of course gives a
   winning \(1\)-mark. The previous lemma finishes the proof.
@@
 \begin{proof}
+  Note that \(\pi\) is a point that cannot be separated from the closed
+  set \(\mathbb Q\) by open sets, demonstrating non-regularity.
   Compact sets in \(R_{\mathbb Q}\) cannot contain open intervals,
@@
   this space is not regular. Finally, the space is not second-countable,
-  since for any countable collection of open sets \(\{U_n:n<\omega\}\),
-  we may choose \(p_n\in U_n\)
+  since for any countable collection of nonempty
+  open sets \(\{U_n:n<\omega\}\), we may choose \(p_n\in U_n\)
   and note \(R_\omega\setminus\{p_n:n<\omega\}\) is an open set not containing
@@
   \(\sigma(\<\mc{U}_0,\dots,\mc{U}_{2n}\>)=[-n,n]\setminus C_n\)
-  where \(C_n\) witnesses Lemma \ref{rOmegaLemma} for \([-n,n]\)
+  where \(C_n=\{c_{i,n}:i<\omega\}\)
+  witnesses Lemma \ref{rOmegaLemma} for \([-n,n]\)
   and \(\mc U_{2n}\),

### 2017-08-26 articles/relating-games-menger-cft-ss/article.tex
help out arxiv
proofread menger paper

@@
 
-\usepackage{../../clontzDefinitions}
+\usepackage{clontzDefinitions}
 
@@
 \begin{definition}
-  Let \(\mc B_{X,x}\) be the collection of subsets \(A\subset X\) where
+  Let \(\Omega_{X,x}\) be the collection of subsets \(A\subset X\) where
   \(x\in\closure{A}\). (Call \(A\) a \term{blade} of \(x\).)
-  Then \(\schSelProp{\mc B_{X,x}}{\mc B_{X,x}}\) is the
+  Then \(\schSelProp{\Omega_{X,x}}{\Omega_{X,x}}\) is the
   \term{countable fan tightness property} for \(X\) at \(x\)
   (\(CFT_x\) for short), and
-  \(\schSelGame{\mc B_{X,x}}{\mc B_{X,x}}\) is the
+  \(\schSelGame{\Omega_{X,x}}{\Omega_{X,x}}\) is the
   \term{countable fan tightness game} for \(X\) at \(x\).
 \end{definition}
+
+The similar notations for \(\omega\)-covers \(\Omega_X\) and
+blades \(\Omega_{X,x}\) is well-established, see e.g.
+\cite[Topological games and Ramsey theory]{19362020070101} (wherein
+the notation is more succently given as \(\Omega,\Omega_x\)).  The
+relationship between such sets becomes apparent in the study of
+\(C_p\)-theory; for this reason we choose to always denote the space
+explicitly to help distinguish the ambient spaces when discussing
+the relationship between \(\Omega_X\) and
+\(\Omega_{C_p(X),\vec 0}\).
 
@@
   Let \(\mc D_{X}\) be the collection of dense subsets of a topological
-  space \(X\). (So, \(\mc D_X\subseteq \mc B_{X,x}\) for all \(x\in X\).)
-  Then \(\schSelProp{\mc D_X}{\mc B_{X,x}}\) is the
+  space \(X\).
+  Then \(\schSelProp{\mc D_X}{\Omega_{X,x}}\) is the
   \term{countable dense fan tightness property} for \(X\) at \(x\)
   (\(CDFT_x\) for short), and
-  \(\schSelGame{\mc D_X}{\mc B_{X,x}}\) is the
+  \(\schSelGame{\mc D_X}{\Omega_{X,x}}\) is the
   \term{countable dense fan tightness game} for \(X\) at \(x\).
@@
 Note that \(CFT\Rightarrow CDFT\) for any space \(X\) as
-\(\mc D_X\subseteq \mc B_{X,x}\).
+\(\mc D_X\subseteq \Omega_{X,x}\) for all \(x\in X\).
 
@@
 Of course, one may easily observe that a selective separable space is
-separable. In \cite{MR2678950} Barman and Dow demonstrated that all
+separable, and \(SS\Rightarrow CDFT\).
+In \cite{MR2678950} Barman and Dow demonstrated that all
 separable Frechet spaces are selectively separable. They were also able
@@
 cannot be improved to be winning Markov strategies. In
-\cite{clontzMengerGamePreprint} the author showed that while \(M^+\) implies
-\(M^{+mark}\) for second-countable spaces, there exists a simple
+\cite{clontzMengerCMUC} the author showed that \(M^+\) implies
+\(M^{+mark}\) for second-countable spaces; however, the one-point
+Lindel\"of-ication \(\onePtLind{\omega_1}\) of a discrete space of size
+\(\omega_1\) is a simple
 example of a regular non-second-countable space which is
-\(M^+\) but not \(M^{+mark}\).
+\(M^+\) but not \(M^{+mark}\) (equivalently, not \(\sigma\)-compact).
+It will later be shown that it is no coincidence
+that countable \(SS^+\) implies \(SS^{+mark}\) and
+second-countable \(M^+\) implies \(M^{+mark}\).
 
@@
 \begin{proposition}
-  Any witness for \(\Omega M\) (resp. \(\Omega M^+,\Omega M^{+mark}\))
+  Any witness for \(\Omega M\) (resp.
+  \(\Omega M^+,\Omega M^{+mark}\))
   may be improved such that any final sequence of the chosen
@@
 \begin{proof}
-  Consider any sequence \(\<\mc U_0,\mc U_1,\dots\>\) of open covers.
-  For \(\Omega M\), choose the witness
-  \(\<\mc F_n^n,\mc F_{n+1}^n,\dots\>\) for the final
-  sequence \(\<\mc U_n,\mc U_{n+1},\dots\>\) for each \(n<\omega\),
-  and let \(\mc F_n=\bigcup_{i\leq n}\mc F_n^i\).
+  Consider any sequence \(\<\mc U_0,\mc U_1,\dots\>\) of \(\omega\)-covers.
+  For each \(n<\omega\), let
+  \(\<\mc F_n^n,\mc F_{n+1}^n,\dots\>\) witness \(\Omega M\) for the final
+  sequence \(\<\mc U_n,\mc U_{n+1},\dots\>\),
+  and let \(\mc F_n=\bigcup_{i\leq n}\mc F_n^i\); it follows that
+  \(\<\mc F_0,\mc F_1,\dots\>\) satisfies the proposition.
+
   For \(\Omega M^+\), the winning strategy \(\sigma\) may be improved to
@@
     \bigcup_{i\leq n}\sigma(\mc U,i)
-  \).
+  \). Both improved strategies are easily seen to satisfy the proposition.
 \end{proof}
@@
 \begin{proof}
-  For each \(B\in\mc B_{C_p(X),\vec 0}\) define
+  For each \(B\in\Omega_{C_p(X),\vec 0}\) define
   \[
@@
   Consider the finite set \(F\in[X]^{<\omega}\). Since
-  \(\vec 0\in\cl B\), choose \(\vec x\in B\cap[\vec 0,F,1]\).
-  It follows that \(F\subseteq x^{\leftarrow}[(-1,1)]\in\mc U_n(B)\),
+  \(\vec 0\in\cl B\), choose \(\vec x\in B\cap[\vec 0,F,1/2^n]\).
+  It follows that
+  \(F\subseteq \vec x^{\leftarrow}[(-1/2^n,1/2^n)]\in\mc U_n(B)\),
   so \(\mc U_n(B)\) is an \(\omega\)-cover of \(X\).
@@
   Consider the sequence of blades
-  \(\<B_0,B_1,\dots\>\in\mc B_{C_p(X),\vec 0}^\omega\), and the
+  \(\<B_0,B_1,\dots\>\in\Omega_{C_p(X),\vec 0}^\omega\), and the
   corresponding sequence of \(\omega\)-covers
@@
   Let \(G\in[X]^{<\omega},\epsilon>0\). Choose \(i<\omega\) such that
-  \(\frac{1}{2^i}<\epsilon\) and then choose
-  \(i\leq n<\omega,\vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\in\mc F_n\)
-  such that \(G\subseteq \vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\)
-  and therefore \(G\subseteq \vec x^{\leftarrow}[(-\epsilon,\epsilon)]\).
-  It follows that \(\vec x\in F_n\cap[\vec 0,G,\epsilon]\), and therefore
+  \(\frac{1}{2^i}<\epsilon\). Since \(\bigcup_{i\leq n<\omega} \mc F_n\)
+  is an \(\omega\)-cover, we may choose
+  \(i\leq n<\omega\) and
+  \(\vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\in\mc F_n\)
+  such that \(G\subseteq \vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\).
+  Therefore, \(G\subseteq \vec x^{\leftarrow}[(-\epsilon,\epsilon)]\).
+  It follows that \(\vec x\in F_n\cap[\vec 0,G,\epsilon]\), and thus
   every basic open neighborhood of \(\vec 0\) intersects
@@
   Let \(G\in[X]^{<\omega},\epsilon>0\). Choose \(i<\omega\) such that
-  \(\frac{1}{2^i}<\epsilon\) and then choose
-  \(i\leq n<\omega,\vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\in\sigma(\<\mc U_0(B_0),\dots,\mc U_n(B_n)\>)\)
-  such that \(G\subseteq \vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\)
-  and therefore \(G\subseteq \vec x^{\leftarrow}[(-\epsilon,\epsilon)]\).
-  It follows that \(\vec x\in \tau(\<B_0,\dots,B_n\>)\cap[\vec 0,G,\epsilon]\), and therefore
-  every basic open neighborhood of \(\vec 0\) intersects
+  \(\frac{1}{2^i}<\epsilon\). Since
+  \(\bigcup_{i\leq n<\omega} \sigma(\<\mc U_0(B_0),\dots,\mc U_n(B_n)\>)\)
+  is an \(\omega\)-cover, we may choose
+  \(i\leq n<\omega\) and \(\vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]
+  \in\sigma(\<\mc U_0(B_0),\dots,\mc U_n(B_n)\>)\)
+  such that \(G\subseteq \vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\).
+  Therefore \(G\subseteq \vec x^{\leftarrow}[(-\epsilon,\epsilon)]\).
+  It follows that \(\vec x\in \tau(\<B_0,\dots,B_n\>)\cap[\vec 0,G,\epsilon]\),
+  and thus every basic open neighborhood of \(\vec 0\) intersects
   \(\bigcup_{n<\omega}\tau(\<B_0,\dots,B_n\>)\).
@@
   Let \(G\in[X]^{<\omega},\epsilon>0\). Choose \(i<\omega\) such that
-  \(\frac{1}{2^i}<\epsilon\) and then choose
-  \(i\leq n<\omega,\vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\in\sigma(\mc U_n(B_n),n)\)
-  such that \(G\subseteq \vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\)
-  and therefore \(G\subseteq \vec x^{\leftarrow}[(-\epsilon,\epsilon)]\).
-  It follows that \(\vec x\in \tau(B_n,n)\cap[\vec 0,G,\epsilon]\), and therefore
+  \(\frac{1}{2^i}<\epsilon\). Since
+  \(\bigcup_{i\leq n<\omega} \sigma(\mc U_n(B_n),n)\) is an \(\omega\)-cover,
+  we may choose \(i\leq n<\omega\) and
+  \(\vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\in\sigma(\mc U_n(B_n),n)\)
+  such that \(G\subseteq \vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\).
+  Therefore \(G\subseteq \vec x^{\leftarrow}[(-\epsilon,\epsilon)]\).
+  It follows that \(\vec x\in \tau(B_n,n)\cap[\vec 0,G,\epsilon]\), and thus
   every basic open neighborhood of \(\vec 0\) intersects
@@
   \([\vec x,G,\epsilon]\). If \(\mc U\) is an \(\omega\)-cover
-  of \(X\), \(G\subseteq U\) for some \(U_{\vec y,\mc U}\in\mc U\).
+  of \(X\), \(G\subseteq U\)
+  for some \(U\in\mc U\).
   Since \(X\) is
-  \(T_{3\frac{1}{2}}\), \(X\setminus U_{\vec y,\mc U}\) is closed, and \(G\)
-  is finite and disjoint from \(X\setminus U_{\vec y,\mc U}\),
+  \(T_{3\frac{1}{2}}\), \(X\setminus U\) is closed, and \(G\)
+  is finite and disjoint from \(X\setminus U\),
   we may choose some function \(\vec y\in C_p(X)\) where
-  \(\vec y[X\setminus U_{\vec y,\mc U}]=\{1\}\) and \(\vec x(t)=\vec y(t)\)
+  \(\vec y[X\setminus U]=\{1\}\) and \(\vec x(t)=\vec y(t)\)
   for each \(t\in G\).
-  It follows \(\vec y\in [\vec x,G,\epsilon]\cap D\), so \(D(\mc U)\)
+  It follows \(\vec y\in [\vec x,G,\epsilon]\cap D(\mc U)\), so \(D(\mc U)\)
   is dense in \(C_p(X)\).
@@
 \begin{proof}
-  Since \(\mc D_X\subseteq \mc B_{X,x}\), the second condition trivially
+  Since \(\mc D_X\subseteq \Omega_{X,x}\), the second condition trivially
   implies the first. As \(C_p(X)\) is homogeneous, the \(C(D)FT\) properties
@@
   open cover \(\mc U_n=\{U^n:U\in\mc U\}\). Then
-  \(\mc F=\{U:U^n\in\mc F_n\}\) witnesses our desired result.
+  \(\mc F=\{U:U^n\in\mc F_n\}\) satisfies that for each \(F\in[X]^{\leq n}\)
+  there exists some \(U\in\mc F\) where \(F\subseteq U\).
+
+  Conversely, assume that for each \(\omega\)-cover
+  \(\mc U\) of \(X\) and \(n<\omega\), there exists a finite subcollection
+  \(\mc F\in[\mc U]^{<\omega}\) such that for each \(F\in[X]^{\leq n}\)
+  there exists some \(U\in\mc F\) where \(F\subseteq U\). Given an
+  arbitrary open cover \(\mc V\), close it under finite unions to obtain
+  an \(\omega\)-cover \(\mc U\). Then the finite subcollection \(\mc F\)
+  of \(\mc U\) is of course a finite subcover,
+  and since each member of \(\mc F\) is a finite union of open sets in
+  \(\mc V\), there exists a finite subcover \(\mc G\) of \(\mc V\).
 \end{proof}
@@
   The equivalence of \(\sigma\)-compact and \(M^{+mark}\) in regular spaces
-  was shown in \cite{clontzMengerGamePreprint}. As \(\Omega M^{+mark}\)
+  was shown in \cite{clontzMengerCMUC}. As \(\Omega M^{+mark}\)
   trivially implies \(M^{+mark}\), we need only demonstrate that
@@
   \(\sigma\)-compact (and therefore not \(\Omega M^{+mark}\))
-  is simply the fact that its countably infinite subsets
-  are closed and discrete.
-  We define the strategy \(\sigma\) for \(\plII\) in
+  follows from the fact that its countably infinite subsets
+  are closed and discrete, so all of its compact subsets are finite.
+
+  To show \(\Omega M^+\),
+  we define the strategy \(\sigma\) for \(\plII\) in
   \(\schSelGame{\Omega_X}{\Omega_X}\) as follows.
-
-  For \(n<\omega\)
-  let \(\sigma(\<\mc U_0,\dots,\mc U_n\>)=\{U(\<\mc U_0,\dots,\mc U_n\>)\}\),
-  where
-  \[
+  For a given partial play \(\<\mc U_0,\dots,\mc U_n\>\), suppose
+  \(\{\alpha_{i,m}:i<n,m<\omega\}\subseteq\omega_1\) has already been defined.
+  Then as \(\mc U_n\) is an \(\omega\)-cover, we may
+  choose \(U(\<\mc U_0,\dots,\mc U_n\>)\in\mc U_n\) that contains
+  \(\{\infty\}\cup\{\alpha_{i,j}:i,j<n\}\). Since
+  \(U(\<\mc U_0,\dots,\mc U_n\>)\) is co-countable, define
+  \(\{\alpha_{n,m}:m<\omega\}\) such that
+  \(
     U(\<\mc U_0,\dots,\mc U_n\>)
@@
     \{\alpha_{n,m}:m<\omega\}
-  \]
-  is a co-countable set
-  containing \(\{\infty\}\cup\{\alpha_{i,j}:i,j<n\}\).
+  \). Then let
+  \(\sigma(\<\mc U_0,\dots,\mc U_n\>)=\{U(\<\mc U_0,\dots,\mc U_n\>)\}\).
 
@@
 
+Note that the preceding result could be worded more strongly:
+\(\onePtLind{\omega_1}\)
+is strategically \(\Omega\)-Rothberger, since the winning strategy only
+uses a single set of the \(\omega\)-cover during each round.
+This topic will be discussed further in a later section.
+
 \begin{corollary}
@@
 \begin{proof}
-  Every metrizable topological space has points \(G_\delta\).
-  However, if every neighborhood of \(\infty\) is
-  co-countable, \(\{\infty\}\) cannot be the intersection of countably many
-  open sets.
+  Consider a topology coarser than the topology of \(\onePtLind{\omega_1}\).
+  Since open neighborhoods of \(\infty\) in this topology are co-countable,
+  a countable intersection of \(\infty\) neighborhoods is not
+  \(\{\infty\}\). Since every metrizable topological space has points
+  \(G_\delta\), this topology cannot be metrizable.
 \end{proof}
@@
 
-\section{Equivalence of certain strategic and Markov seleciton properties}
+\section{Equivalence of certain strategic and Markov selection properties}
 
@@
   \).
+  Let \(b(n)\prec f\) denote that \(b(n)\in\omega^{<\omega}\) is a finite
+  restriction of \(f\in\omega^\omega\).
   The result then follows from
@@
       \\ & \supseteq
-    \bigcup_{n<\omega,b(n)<f}
+    \bigcup_{n<\omega,b(n)\prec f}
     \sigma(\<Z_{b(n)\rest 1},Z_{b(n)\rest 2},\dots,Z_{b(n)},A_n\>)
       \\ & =
-    \bigcup_{n<\omega,b(n)<f}
+    \bigcup_{n<\omega,b(n)\prec f}
     \sigma(\<Z_{f\rest 1},Z_{f\rest 2},\dots,Z_{f\rest|b(n)|},A_{b^{\leftarrow}(f\rest|b(n)|)}\>)
       \\ & =
-    \bigcup_{n<\omega,b(n)<f}
+    \bigcup_{n<\omega,b(n)\prec f}
     \sigma(\<Z_{f\rest 1},Z_{f\rest 2},\dots,Z_{f\rest|b(n)|},Z_{f\rest(|b(n)|+1)}\>)
@@
 \begin{proof}
-  First note that any witness for
-  \(\Omega M^+\) is a witness for
-  \(\plII\win\schSelGame{\Omega_X^*}{\Omega_X^*}\).
   Fix a countable base \(\mc B\) for \(X\) closed under finite unions, and let
   \(\Omega_X^*\) be the collection of \(\omega\)-covers of \(X\) which only
-  use basic open sets. Then
+  use basic open sets.
+  One may quickly verify that
+  \(\Omega M^+\) implies
+  \(\plII\win\schSelGame{\Omega_X^*}{\Omega_X^*}\).
+
+  Note now that
   \(\bigcup\Omega_X^*=\mc B\) is countable, and any set containing an
@@
 
-\begin{corollary}[\cite{clontzMengerGamePreprint}]
+\begin{corollary}[\cite{clontzMengerCMUC}]
   A second-countable space is \(M^+\) if and only if
@@
   Let \(\sigma_i\) be a witness for \(sCDFT_{d_i}^+\)
-  for each \(i<\omega\). Define \(p:\omega\to\omega\) partition \(\omega\)
-  into infinite sets \(\{p(i):i<\omega\}\).
-  For a nonempty finite sequence \(t\), let \(t'\) be its subsequence removing
-  all terms of index \(n\) such that \(p(n)\not=p(|t|-1)\).
-  (Note that this process preserves the final term.)
-  We then define the strategy \(\tau\) by
+  for each \(i<\omega\). Define \(p:\omega\to\omega\) partitioning \(\omega\)
+  such that \(|p^\leftarrow(i)|=\omega\) for all \(i<\omega\).
+  Essentially, we will partition each
+  attack by \(\plI\) according to \(p\) into \(\omega\)-many subattacks, and
+  defeat each subattack to produce a blade of \(d_n\).
+
+  For a nonempty finite sequence \(t\), let \(t'\) be its subsequence deleting
+  all terms of index \(n\) where \(p(n)\not=p(|t|-1)\).
+  Note that the final term of \(t\) is the final term of \(t'\).
+  Thus the function \(\tau\) defined by
   \[
@@
     \sigma_{p(|t|-1)}(t')
-  .\]
-
-  Let \(\alpha\in\mc D_X^\omega\), and let \(\alpha_i\) be its subsequence
-  removing all terms of index \(n\) such that \(p(n)\not=i\).
+  \]
+  is a legal strategy.
+
+  Let \(\alpha\in\mc D_X^\omega\) be an attack by \(\plI\),
+  and let \(\alpha_i\) be its subsequence
+  deleting all terms of index \(n\) where \(p(n)\not=i\).
   By \(sCDFT_{d_i}^+\), we have
@@
   Let \(\sigma_i\) be a witness for \(sCDFT_{d_i}^{+mark}\)
-  for each \(i<\omega\). Define \(p:\omega\to\omega\) partition \(\omega\)
-  into infinite sets \(\{p(i):i<\omega\}\).
-  We then define the Markov strategy \(\tau\) by
+  for each \(i<\omega\).
+  Again, we will partition each
+  attack by \(\plI\) according to \(p\) into \(\omega\)-many subattacks, and
+  defeat each subattack to produce a blade of \(d_n\).
+
+  We define the Markov strategy \(\tau\) by
   \[
@@
       =
-    \sigma_{p(n)}(D,|\{m\in p(n):m\leq n\}|)
+    \sigma_{p(n)}(D,|\{m< n:p(m)=p(n)\}|)
   .\]

### 2017-12-06 postdoctoral/k-markov-tactic-banach-mazur.tex
incomplete draft on k-limited BM strats

\documentclass[11pt]{article}

\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{amsthm}

\usepackage[letterpaper,margin=1in]{geometry}

\usepackage{enumerate}

      \theoremstyle{plain}
      \newtheorem{theorem}{Theorem}
      \newtheorem{lemma}[theorem]{Lemma}
      \newtheorem{corollary}[theorem]{Corollary}
      \newtheorem{proposition}[theorem]{Proposition}
      \newtheorem{conjecture}[theorem]{Conjecture}
      \newtheorem{question}[theorem]{Question}
      \newtheorem{claim}[theorem]{Claim}

      \theoremstyle{definition}
      \newtheorem{definition}[theorem]{Definition}
      \newtheorem{example}[theorem]{Example}
      \newtheorem{game}[theorem]{Game}

      \theoremstyle{remark}
      \newtheorem{remark}[theorem]{Remark}

      \theoremstyle{plain}
      \newtheorem*{theorem*}{Theorem}
      \newtheorem*{lemma*}{Lemma}
      \newtheorem*{corollary*}{Corollary}
      \newtheorem*{proposition*}{Proposition}
      \newtheorem*{conjecture*}{Conjecture}
      \newtheorem*{question*}{Question}
      \newtheorem*{claim*}{Claim}

      \theoremstyle{definition}
      \newtheorem*{definition*}{Definition}
      \newtheorem*{example*}{Example}
      \newtheorem*{game*}{Game}

      \theoremstyle{remark}
      \newtheorem*{remark*}{Remark}

\title{\(k\)-Limited Strategies in Banach Mazur Games}
\author{Steven Clontz}

\usepackage{../clontzDefinitions}

\newcommand{\bmPoGame}[2]{BM_{po}(#1,#2)}

\begin{document}

\maketitle

  \begin{definition}
    Let \(\mb P\) be partially ordered by \(\leq\).
    Let \(\mb P^{\downarrow}=\{f\in\mb P^\omega : f(n)\geq f(n+1)\}\).
    Then for \(f,g\in\mb P^\downarrow\), we say that \(f,g\) zip into each
    other if for all \(m<\omega\) there exists \(n<\omega\) such that
    \(f(m)\geq g(n)\) and \(g(m)\geq f(n)\).
  \end{definition}

  \begin{definition}
    \(\bmPoGame{\mb P}{W}\) is a game defined for all non-empty partial orders
    \(\mb P\) and all subsets \(W\subseteq\mb P^\downarrow\) closed under
    zipping. During round \(0\), \(\plI\) chooses \(a_0\in\mb P\),
    and then \(\plII\) chooses \(b_0\leq a_0\); during around \(n+1\),
    \(\plI\) chooses \(a_{n+1}\leq b_n\), and then \(\plII\) chooses
    \(b_{n+1}\leq a_{n+1}\). \(\plII\) wins this game if
    \(\<a_0,a_1,\dots\>\in W\).
  \end{definition}

  \begin{theorem}
    \(\plII\kmarkwin{(k+1)}\bmPoGame{\mb P}{W}\) if and only if
    \(\plII\ktactwin{(k+1)}\bmPoGame{\mb P}{W}\).
  \end{theorem}

  \begin{proof}
    Let \(\tau(\vec p,n)\) be a winning \((k+1)\)-mark for \(\plII\).
    Let \(\preceq\) well-order \(\mb P^{k+1}\).
    For \(f\in\mb P^\omega\), let
    \(f_n=\<f(n),\dots,f(n+k)\>\in\mb P^{k+1}\).
    For \(\vec p,\vec r\in\mb P^{k+1}\) say that \(\vec p\) improves \(\vec r\)
    if for each \(m\leq k\), there exists \(n\leq k\) such that
    \(\vec r(m)\geq\vec p(n)\).

    For \(\vec p\in \mb P^{k+1}\) and \(q\in\mb P\), say \(\vec p\) is
    \(n\)-above \(q\) if there exists \(s_n(\vec p)\in\mb P^{k+1}\)
    improving \(\vec p\)
    such that
    \[
      \vec p(k)
    \geq
      s_n(\vec p)(k)
    \geq
      \tau(s_n(\vec p),n+k)
    \geq
      q
    \]
    (noting \(\vec p(k)\geq s_n(\vec p)(k)\) is just a consequence of
    \(s_n(\vec p)\) improving \(\vec p\)).

    Say \(\vec p\) is \(\omega\)-above \(q\) if \(\vec p\) is \(n\)-above
    \(q\) for all \(n<\omega\). If \(\vec p\) is \(\omega\)-above some
    \(l(\vec p)\), then say \(\vec p\) is long; otherwise call \(\vec p\)
    short. Note any \(\vec p\) improved by a long vector is itself long,
    so any \(\vec p\) improving a short vector is itself short.

    For \(\vec p\) short, let
    \[
      \mu(\vec p)
        =
      \min_{\preceq}\{
        \vec r\text{ short}
          :
        \vec{p}\text{ improves }\vec{r}
      \}
    \]
    and since \(\mu(\vec p)\) is not \(n\)-above \(\vec p\) for some \(n\), let
    \[
      N(\vec p)
        =
      \min\{
        n<\omega
      :
        \mu(\vec p)\text{ is not }n\text{-above }\vec p
      \}
    .\]

    We define
    \[
      \sigma(\vec p)
        =
      \begin{cases}
        \tau(\vec p,|\vec p|-1) & 0<|\vec p|\leq k \\
        l(\vec p) & \vec p \text{ is long} \\
        \tau^{N(\vec p)+1}(\vec p) & \vec p \text{ is short}
     \end{cases}
    .\]

    Suppose \(\sigma\) is legally attacked by \(a\in\mb P^\omega\).
    % Suppose \(b\) is a subsequence of \(a\) where
    % \(b_n\) is long for all \(n<\omega\).
    % Since \(b_n\) improves \(a_n\)
    % for all \(n<\omega\), it follows that
    % \(a_n\) is long for all \(n<\omega\).
    Thus for \(n<k\),
    \[
      a(n)
        \geq
      \tau(a\rest(n+1),n)
        =
      \sigma(a\rest(n+1))
        \geq
      a(n+1)
    .\]
    For \(n\leq\omega\), if \(a_n\) is long, then \(a_n\) is \(n\)-above
    \(l(a_n)\). Therefore,
    \[
      a(n+k)
        =
      a_n(k)
        \geq
      s_n(a_n)(k)
        \geq
      \tau(s_n(a_n),n+k)
        \geq
      l(a_n)
        =
      \sigma(a_n)
        \geq
      a(n+k+1)
    .\]
    Thus if \(a_n\) is long for \(n<\omega\), it follows that  \(\<a(0),\dots,a(k-1),s_0(a_0)(k),s_1(a_1)(k),\dots\>\)
    is a legal attack against \(\tau\). Since \(\tau\) is winning,
    this attack belongs to \(W\). Since this attack zips into \(a\),
    \(a\) also belongs to \(W\).

    Otherwise, we may choose \(k<N<\omega\) such that
      \begin{itemize}
        \item \(a_{n+N}\) is short for all \(n<\omega\),
              since \(a_m\) short implies \(a_n\) short for all \(m\leq n\).
        \item \(\mu(a_{n+N})=\vec m\) is fixed for all \(n<\omega\), since
              there cannot be an infinite \(\preceq\)-decreasing sequence.
      \end{itemize}
    As a result, \(a_{n+N}\) is...
    Thus for \(n<k\),
    \[
      b(n)
        \geq
      \tau(b\rest(n+1),n)
        =
      \sigma(a\rest(n+1))
        \geq
      a(n+1)
    .\]

  \end{proof}

\end{document}

### 2017-12-07 postdoctoral/k-markov-tactic-banach-mazur.tex
abandon generalization attempt - will now write up case k=0

@@
   \begin{proof}
-    Let \(\tau(\vec p,n)\) be a winning \((k+1)\)-mark for \(\plII\).
+    Let \(\tau(\vec p,n+1)\) be a winning \((k+1)\)-mark for \(\plII\),
+    where \(n+1\) is the number of moves previously made by \(\plI\).
     Let \(\preceq\) well-order \(\mb P^{k+1}\).
@@
     \(f_n=\<f(n),\dots,f(n+k)\>\in\mb P^{k+1}\).
-    For \(\vec p,\vec r\in\mb P^{k+1}\) say that \(\vec p\) improves \(\vec r\)
-    if for each \(m\leq k\), there exists \(n\leq k\) such that
-    \(\vec r(m)\geq\vec p(n)\).
 
     For \(\vec p\in \mb P^{k+1}\) and \(q\in\mb P\), say \(\vec p\) is
-    \(n\)-above \(q\) if there exists \(s_n(\vec p)\in\mb P^{k+1}\)
-    improving \(\vec p\)
+    \(n\)-above \(q\) if there exists \(s_n(\vec p)\in\mb P\)
     such that
@@
     \geq
-      s_n(\vec p)(k)
+      s_n(\vec p)
     \geq
-      \tau(s_n(\vec p),n+k)
+      \tau(\vec r\concat\<s_n(\vec p)\>,n+k+1)
     \geq
@@
     \]
-    (noting \(\vec p(k)\geq s_n(\vec p)(k)\) is just a consequence of
-    \(s_n(\vec p)\) improving \(\vec p\)).
+    for all \(\vec r\in\mb P^k\) ``between \(\vec p(0)\) and \(\vec p(k)\)''.
+
+    For \(\vec p\in\mb P^{k+1}\), let \(t^0(\vec p)=\vec p\),
+    \(\tau^{n+1}(\vec p)=\tau(t^n(\vec p),n+1)\), and
+    \(t^{n+1}(\vec p)=(t^n(\vec p)\last k)\concat\<\tau^{n+1}(\vec p)\>\).
 
@@
     \(l(\vec p)\), then say \(\vec p\) is long; otherwise call \(\vec p\)
-    short. Note any \(\vec p\) improved by a long vector is itself long,
-    so any \(\vec p\) improving a short vector is itself short.
+    short.
 
@@
           :
-        \vec{p}\text{ improves }\vec{r}
+        \vec{r}(k)\geq\vec{p}(k)
       \}
     \]
-    and since \(\mu(\vec p)\) is not \(n\)-above \(\vec p\) for some \(n\), let
+    and since \(\mu(\vec p)\) is not \(n\)-above \(\vec p(k)\) for some \(n\),
+    let
     \[
@@
       :
-        \mu(\vec p)\text{ is not }n\text{-above }\vec p
+        \mu(\vec p)\text{ is not }n\text{-above }\vec p(k)
       \}
@@
       \begin{cases}
-        \tau(\vec p,|\vec p|-1) & 0<|\vec p|\leq k \\
+        \tau(\vec p,|\vec p|) & |\vec p|\leq k \\
         l(\vec p) & \vec p \text{ is long} \\
@@
         \geq
-      s_n(a_n)(k)
+      s_n(a_n)
         \geq
-      \tau(s_n(a_n),n+k)
+      \tau((a_n\last k)\concat\<s_n(a_n)\>,n+k)
         \geq

### 2017-12-07 postdoctoral/k-markov-tactic-banach-mazur.tex
write up notes on marks/tactics

@@
       \newtheorem{example}[theorem]{Example}
+      \newtheorem{observation}[theorem]{Observation}
       \newtheorem{game}[theorem]{Game}
@@
       \newtheorem*{example*}{Example}
+      \newtheorem*{observation*}{Observation}
       \newtheorem*{game*}{Game}
@@
 
-\title{\(k\)-Limited Strategies in Banach Mazur Games}
+\title{Tactics and Marks in Banach Mazur Games}
 \author{Steven Clontz}
@@
 \maketitle
+
+  My notes on Galvin/Telgarsky's Theorem 5 from \cite{MR831181}.
 
@@
     \(\bmPoGame{\mb P}{W}\) is a game defined for all non-empty partial orders
-    \(\mb P\) and all subsets \(W\subseteq\mb P^\downarrow\) closed under
-    zipping. During round \(0\), \(\plI\) chooses \(a_0\in\mb P\),
+    \(\mb P\) and all subsets \(W\subseteq\mb P^\downarrow\).
+    During round \(0\), \(\plI\) chooses \(a_0\in\mb P\),
     and then \(\plII\) chooses \(b_0\leq a_0\); during around \(n+1\),
@@
   \begin{theorem}
-    \(\plII\kmarkwin{(k+1)}\bmPoGame{\mb P}{W}\) if and only if
-    \(\plII\ktactwin{(k+1)}\bmPoGame{\mb P}{W}\).
+    Let \(W\subseteq\mb P^\downarrow\) be closed under zipping.
+    \(\plII\markwin\bmPoGame{\mb P}{W}\) if and only if
+    \(\plII\tactwin\bmPoGame{\mb P}{W}\).
   \end{theorem}
@@
   \begin{proof}
-    Let \(\tau(\vec p,n+1)\) be a winning \((k+1)\)-mark for \(\plII\),
-    where \(n+1\) is the number of moves previously made by \(\plI\).
-    Let \(\preceq\) well-order \(\mb P^{k+1}\).
-    For \(f\in\mb P^\omega\), let
-    \(f_n=\<f(n),\dots,f(n+k)\>\in\mb P^{k+1}\).
+    Let \(\tau(p,n+1)\) be a winning mark for \(\plII\), where \(p\)
+    is the most recent move by \(\plI\) and \(n+1\)
+    is the number of moves made by \(\plI\).
+    Define \(\tau^0(p)=p\) and \(\tau^{n+1}(p)=\tau(\tau^n(p),n+1)\).
+    Let \(\preceq\) well-order \(\mb P\).
 
-    For \(\vec p\in \mb P^{k+1}\) and \(q\in\mb P\), say \(\vec p\) is
-    \(n\)-above \(q\) if there exists \(s_n(\vec p)\in\mb P\)
+    For \(p,q\in \mb P\), say \(p\geq_n q\) if there exist
+    \(s_m(p)\in\mb P\) for \(m\leq n\)
     such that
     \[
-      \vec p(k)
+      p
     \geq
-      s_n(\vec p)
+      s_m(p)
     \geq
-      \tau(\vec r\concat\<s_n(\vec p)\>,n+k+1)
+      \tau(s_m(p),n+1)
     \geq
       q
-    \]
-    for all \(\vec r\in\mb P^k\) ``between \(\vec p(0)\) and \(\vec p(k)\)''.
+    .\]
+    Note that \(p'\geq p\geq_n q\geq q'\) implies \(p'\geq_n q'\),
+    and \(p\geq_n \tau^n(p)\).
 
-    For \(\vec p\in\mb P^{k+1}\), let \(t^0(\vec p)=\vec p\),
-    \(\tau^{n+1}(\vec p)=\tau(t^n(\vec p),n+1)\), and
-    \(t^{n+1}(\vec p)=(t^n(\vec p)\last k)\concat\<\tau^{n+1}(\vec p)\>\).
+    Say \(p\geq_\omega q\) whenever \(p\geq_n q\) for all \(n<\omega\).
+    If \(p\geq_\omega l(p)\) for some \(l(p)\), then say \(p\) is long;
+    otherwise call \(p\) short.
 
-    Say \(\vec p\) is \(\omega\)-above \(q\) if \(\vec p\) is \(n\)-above
-    \(q\) for all \(n<\omega\). If \(\vec p\) is \(\omega\)-above some
-    \(l(\vec p)\), then say \(\vec p\) is long; otherwise call \(\vec p\)
-    short.
-
-    For \(\vec p\) short, let
+    For \(p\) short, let
     \[
-      \mu(\vec p)
+      \mu(p)
         =
       \min_{\preceq}\{
-        \vec r\text{ short}
+        r\text{ short}
           :
-        \vec{r}(k)\geq\vec{p}(k)
+        r\geq p
       \}
     \]
-    and since \(\mu(\vec p)\) is not \(n\)-above \(\vec p(k)\) for some \(n\),
-    let
+    and since \(\mu(p)\not\geq_n p\) for some \(n\), let
     \[
-      N(\vec p)
+      N(p)
         =
@@
       :
-        \mu(\vec p)\text{ is not }n\text{-above }\vec p(k)
+        \mu(p)\not\geq_n p
       \}
     .\]
+    Note that whenever \(\mu(p)=\mu(q)\) for \(p\geq_n q\),
+    it follows that \(\mu(p)\geq_n q\) and therefore \(N(p)<N(q)\).
 
@@
     \[
-      \sigma(\vec p)
+      \sigma( p)
         =
       \begin{cases}
-        \tau(\vec p,|\vec p|) & |\vec p|\leq k \\
-        l(\vec p) & \vec p \text{ is long} \\
-        \tau^{N(\vec p)+1}(\vec p) & \vec p \text{ is short}
+        l(p) & p \text{ is long} \\
+        \tau^{N(p)+1}( p) &  p \text{ is short}
      \end{cases}
@@
     Suppose \(\sigma\) is legally attacked by \(a\in\mb P^\omega\).
-    % Suppose \(b\) is a subsequence of \(a\) where
-    % \(b_n\) is long for all \(n<\omega\).
-    % Since \(b_n\) improves \(a_n\)
-    % for all \(n<\omega\), it follows that
-    % \(a_n\) is long for all \(n<\omega\).
-    Thus for \(n<k\),
+    For \(n\leq\omega\), if \(a(n)\) is long, then \(a(n)\geq_n l(a(n))\).
+    Therefore,
     \[
@@
         \geq
-      \tau(a\rest(n+1),n)
+      s_n(a(n))
+        \geq
+      \tau(s_n(a(n)),n+1)
+        \geq
+      l(a(n))
         =
-      \sigma(a\rest(n+1))
+      \sigma(a(n))
         \geq
@@
     .\]
-    For \(n\leq\omega\), if \(a_n\) is long, then \(a_n\) is \(n\)-above
-    \(l(a_n)\). Therefore,
-    \[
-      a(n+k)
-        =
-      a_n(k)
-        \geq
-      s_n(a_n)
-        \geq
-      \tau((a_n\last k)\concat\<s_n(a_n)\>,n+k)
-        \geq
-      l(a_n)
-        =
-      \sigma(a_n)
-        \geq
-      a(n+k+1)
-    .\]
-    Thus if \(a_n\) is long for \(n<\omega\), it follows that  \(\<a(0),\dots,a(k-1),s_0(a_0)(k),s_1(a_1)(k),\dots\>\)
+    Thus if \(a(n)\) is long for \(n<\omega\), it follows that
+    \(c\in\mb P^\downarrow\) defined by \(c(n)=s_n(a(n))\)
     is a legal attack against \(\tau\). Since \(\tau\) is winning,
-    this attack belongs to \(W\). Since this attack zips into \(a\),
-    \(a\) also belongs to \(W\).
+    \(c\in W\), and since \(c\) zips into \(a\),
+    \(a\in W\) as well.
 
-    Otherwise, we may choose \(k<N<\omega\) such that
+    Otherwise, we may choose a final subsequence \(b\) of \(a\) such that
       \begin{itemize}
-        \item \(a_{n+N}\) is short for all \(n<\omega\),
-              since \(a_m\) short implies \(a_n\) short for all \(m\leq n\).
-        \item \(\mu(a_{n+N})=\vec m\) is fixed for all \(n<\omega\), since
+        \item \(b(n)\) is short for all \(n<\omega\),
+              since \(a(m)\) short implies \(a(n+m)\) short for all
+              \(n<\omega\).
+        \item \(\mu(b(n))=\mu'\) is fixed for all \(n<\omega\), since
               there cannot be an infinite \(\preceq\)-decreasing sequence.
       \end{itemize}
-    As a result, \(a_{n+N}\) is...
-    Thus for \(n<k\),
+    As a result,
+    \[
+      b(n)
+        \geq_{N(b(n))}
+      \tau^{N(b(n))+1}(b(n))
+        =
+      \sigma(b(n))
+        \geq
+      b(n+1)
+    \]
+    and therefore \(N(b(n))<N(b(n+1))\). In particular, \(N(b(n))\geq n\).
+
+    Thus for \(n<\omega\),
     \[
@@
         \geq
-      \tau(b\rest(n+1),n)
+      \tau^{n}(b(n))
+        \geq
+      \tau(\tau^{n}(b(n)),n+1)
+        \geq
+      \tau^{N(b(n))+1}(b(n))
         =
-      \sigma(a\rest(n+1))
+      \sigma(b(n))
         \geq
-      a(n+1)
+      b(n+1)
     .\]
-
+    As a result, \(c\in\mb P^\downarrow\) defined by \(c(n)=\tau^n(b(n))\)
+    is a legal attack against the winning strategy \(\tau\). Therefore
+    \(c\in W\), and since \(c\) zips into \(b\) and \(a\), we conclude
+    \(a\in W\).
   \end{proof}
 
+  \begin{observation}
+    When \(\mb P=T(X)\setminus\{\emptyset\}\) is ordered by set-inclusion
+    and \(W=\{U\in\mb P^\downarrow:\bigcap_{n<\omega}U(n)\not=\emptyset\}\),
+    then \(\bmPoGame{\mb P}{W}\) is exactly the topological Banach Mazur game
+    \(\bmGame{X}\). Note \(W\) is closed under zipping.
+  \end{observation}
+
+  \begin{corollary}
+  \(\plII\markwin\bmGame{X}\) if and only if
+  \(\plII\tactwin\bmGame{X}\).
+  \end{corollary}
+
+  \begin{observation}
+    When \(\mb P=\{(U,x):U\in T(X)\setminus\{\emptyset\},x\in U\}\)
+    is ordered by \((U,x)\geq(V,y)\) whenever \(x\in V\subseteq U\)
+    and \(W=\{\<U(n),x(n)\>_{n<\omega}\in\mb
+    P^\downarrow:\bigcap_{n<\omega}U(n)\not=\emptyset\}\),
+    then \(\bmPoGame{\mb P}{W}\) is almost the Choquet game, except the first
+    player also gets to choose a point. Note \(W\) is closed under zipping.
+  \end{observation}
+
+  \bibliographystyle{plain}
+  \bibliography{../bibliography}
+
 \end{document}

### 2017-12-07 postdoctoral/k-markov-tactic-banach-mazur.tex
correct interpretation of Choquet game

@@
     P^\downarrow:\bigcap_{n<\omega}U(n)\not=\emptyset\}\),
-    then \(\bmPoGame{\mb P}{W}\) is almost the Choquet game, except the first
+    then \(\bmPoGame{\mb P}{W}\) is almost the Choquet game, except the second
     player also gets to choose a point. Note \(W\) is closed under zipping.

### 2018-02-21 postdoctoral/k-markov-tactic-banach-mazur.tex
add work towards (k+2)-mark to (k+2)-tactic

--- 2017-12-07 postdoctoral/k-markov-tactic-banach-mazur.tex
@@
 \maketitle
+
+  \section*{marks and tactics}
 
@@
 
-  \begin{observation}
-    When \(\mb P=\{(U,x):U\in T(X)\setminus\{\emptyset\},x\in U\}\)
-    is ordered by \((U,x)\geq(V,y)\) whenever \(x\in V\subseteq U\)
-    and \(W=\{\<U(n),x(n)\>_{n<\omega}\in\mb
-    P^\downarrow:\bigcap_{n<\omega}U(n)\not=\emptyset\}\),
-    then \(\bmPoGame{\mb P}{W}\) is almost the Choquet game, except the first
-    player also gets to choose a point. Note \(W\) is closed under zipping.
-  \end{observation}
+  \section*{2+ marks and tactics}
+
+  And this stuff is based on section 4.5.1 of \cite{bartoszynski1993covering}.
+
+    % \begin{proposition}
+    %   Suppose that for every finite collection \(\{\mb P_i:i<n\}\)
+    %   such that \(\mb P=\bigcup_{i<n}\mb P_i\),
+    %   some \(\mb P_i\) contains two incompatible points.
+    %   Then \(\mb P\) contains an infinite antichain.
+    % \end{proposition}
+    %
+    % \begin{proof}
+    %   Suppose \(a_i\in\mb P_i\) have been defined for \(i<n\) such that
+    %   \(a_i\not\in\bigcup_{j<i}\mb P_j\) and
+    %   each \(\mb P_i\) is pairwise-compatible. It follows that
+    %   \(\mb P\not=\bigcup_{i<n}\mb P_i\), so choose
+    %   \(a_n\not\in\bigcup_{i<n}\mb P_i\) and let \(\mb P_n\) be a maximal family
+    %   containing \(a_n\) such that \(\mb P_n\) is pairwise-compatible.
+    %
+    %   It follows that \(A=\{a_n:n<\omega\}\) is an antichain, since for
+    %   every pair \(a_i,a_j\in A\) with \(i<j\), \(a_j\not\in\mb P_i\), so
+    %   \(a_j\) is not compatible with something in \(\mb P_i\)...
+    % \end{proof}
+
+  \begin{definition}
+    Let \(f\in S^{\leq\omega}\). Then \(f\rest n\in S^n\) is defined by
+    \((f\rest n)(i)=f(i)\). (\(f\rest n\) gives the first \(n\) terms of \(f\).)
+
+    Let \(t\in S^{<\omega}\). Then \(t\last k\in S^k\) is defined by
+    \((t\last k)(i)=t(i+|t|-k)\). (\(t\last k\) gives the last \(n\) terms
+    of \(t\).)
+  \end{definition}
+
+\begin{definition}
+  For every partial order \(\mb P\) and compatible \(p,q\in\mb P\),
+  let \(p\wedge q\) satisfy \(p\wedge q\leq p,q\).
+\end{definition}
+
+  \begin{claim}
+    \(\mb P\) contains no infinite antichains if and only if every
+    antichain in \(\mb P\) is of size \(n\) or less for some \(n<\omega\).
+  \end{claim}
+
+  \begin{proof}
+    MAYBE? Apparently true for \(\mb P=\tau\setminus\{\emptyset\}\) due to
+    Lemma 2.10 of \cite{comfort_negrepontis_1982}.
+  \end{proof}
+
+  \begin{proposition}
+    Let \(W\subseteq\mb P^\downarrow\) be closed under zipping.
+    Suppose every antichain in \(\mb P\) is of size \(n<\omega\) or less,
+    and \(\plII\win\bmPoGame{\mb P}{W}\). Then
+    \(\plII\autowin\bmPoGame{\mb P}{W}\) (i.e. \(\plII\) wins every
+    play of \(\bmPoGame{\mb P}{W}\), i.e. \(W=\mb P^\downarrow\)).
+  \end{proposition}
+
+  \begin{proof}
+    First, let \(\{p_i:i<n\}\) be an antichain of size \(n<\omega\),
+    then let \(\mb P_i\) be a maximal pairwise-compatible subset of \(\mb P\)
+    containing \(p_i\). Note that if there existed
+    \(q\in\mb P\setminus\bigcup_{i<n}\mb P_i\),
+    \(q\) must be incompatible with some \(q_i\in\mb P_i\) for \(i<n\).
+    Since \(p_i,q_i\in\mb P_i\), they are compatible, so let
+    \(r_i=p_i\wedge q_i\). Since \(q\) is incompatible with \(q_i\) for \(i<n\),
+    \(q\) is incompatible with \(r_i\) for \(i<n\). Since \(p_i\) is
+    incompatible with \(p_j\) for \(i<j<n\), \(r_i\) is incompatible with
+    \(r_j\) for \(i<j<n\). But that makes \(\{q\}\cup\{r_i:i<n\}\) an
+    antichain of size \(n+1\), contradicting the assumption of the proposition.
+    Thus \(\mb P=\bigcup_{i<n}\mb P_i\).
+
+    We now show that if \(s\in\mb P_i^\downarrow\) for some \(i\),
+    then \(s\in W\). Let \(\sigma\) be a
+    winning strategy for \(\plII\) in \(\bmPoGame{\mb P}{W}\),
+    and attack \(\sigma\) with \(q(0)=s(0)\wedge p_i\) and
+    \(q(n+1)=s(n+1)\wedge\sigma(\<q(0),\dots,q(n)\>)\). Note that the choice
+    of \(q(0)\) is valid as \(s(0),p_i\in\mb P_i\). Similarly,
+    \(\sigma(\<q(0),\dots,q(n)\>)\leq q(0)\leq p_i\), so
+    \(\sigma(\<q(0),\dots,q(n)\>)\) cannot be compatible with any \(p_j\)
+    where \(j\not=i\). Thus \(s(n+1),\sigma(\<q(0),\dots,q(n)\>)\in\mb P_i\),
+    making the choice of \(q(n+1)\) valid. Since \(\sigma\) is winning for
+    \(\plII\), we see that \(q\in W\), and therefore \(s\in W\).
+
+    Finally, consider any play of \(\bmPoGame{\mb P}{W}\). It must contain
+    have a subsequence \(s\in\mb P_i^\downarrow\) for some \(i<n\),
+    so \(s\in W\) and therefore
+    the play is also in \(W\), securing a victory for \(\plII\).
+  \end{proof}
+
+  \begin{lemma}
+    Let \(W\subseteq\mb P^\downarrow\) be closed under zipping.
+    Suppose that for every \(p\in\mb P\), there exists an infinite
+    antichain \(A_p=\{a_p(n):n<\omega\}\subseteq\{q\in\mb P:q\leq p\}\).
+    Then \(\plII\kmarkwin{(k+2)}\bmPoGame{\mb P}{W}\) if and only if
+    \(\plII\ktactwin{(k+2)}\bmPoGame{\mb P}{W}\).
+  \end{lemma}
+
+  \begin{proof}
+    Let \(\sigma\) witness \(\plII\kmarkwin{(k+2)}\bmPoGame{\mb P}{W}\).
+    Define \(\tau(t)=\sigma(\<a_{t(0)}(0)\>,1)\) for \(t\in\mb P^1\).
+    Since \(\tau(t)=\sigma(\<a_{t(0)}(0)\>,1)\leq a_{t(0)}(0)\leq t(0)\),
+    this is a legal move.
+
+    Consider \(t\in\mb P^{j+2}\) for \(j\leq k\).
+    If there exists \(l_t<\omega\) such that
+    \(t(j+1)\leq a_{t(j)}(l_t+j)\),
+    define \(t'\in\mb P^{j+2}\) by \(t'(i)=a_{t(i)}(l_t+i)\) and let
+    \(\tau(t)=\sigma(t',l_t+|t|)\). Note that since
+    \[
+      \tau(t)
+        =
+      \sigma(t',l_t+|t|)
+        \leq
+      t'(j+1)
+        =
+      a_{t(j+1)}(l_t+j+1)
+        \leq
+      t(j+1)
+    \]
+    this is a legal move. (If \(l_t\) failed to exist,
+    we could arbitrarily let, say,
+    \(\tau(t)=t(|t|-1)\); as we will see, this case will never occur
+    for any legal attack against \(\tau\).)
+
+    Let \(f\) be a legal attack against \(\tau\). The intuition of the
+    following proof is simple: by construction, \(l_t\) will produce
+    the number of \(\plI\)'s moves forgotten by \(\plII\)'s \((k+2)\)-tactic,
+    allowing the \((k+2)\)-tactic to deduce the round number and thus exploit
+    the winning \((k+2)\)-mark.
+
+    We may quickly verify
+    that \(l_{f\rest 2}=0\) since
+    \[
+      (f\rest 2)(1)
+        =
+      f(1)
+        \leq
+      \tau(f\rest 1)
+        =
+      \sigma(\<a_{f(0)}(0)\>,1)
+        \leq
+      a_{f(0)}(0)
+        =
+      a_{(f\rest 2)(0)}(0+0)
+    .\]
+    We claim in general that \(l_{f\rest(j+2)}=0\) for \(j\leq k\).
+    Assuming \(l_{f\rest(j+2)}=0\) for \(j<k\),
+    \[
+      (f\rest(j+3))(j+2)
+        =
+      f(j+2)
+        \leq
+      \tau(f\rest(j+2))
+        =
+      \sigma(f\rest(j+2)',0+j+2)
+        \leq
+      f\rest(j+2)'(j+1)
+    \]
+    \[
+        =
+      a_{(f\rest(j+2))(j+1)}(j+1)
+        =
+      a_{(f\rest(j+3))(j+1)}(0+(j+1))
+    \]
+    proving \(l_{f\rest(j+3)}=0\).
+
+    Now we show that \(l_{f\rest(j+2)\last(k+2)}=j-k\) for \(j\geq k\).
+    We've just shown that this is true for our base case \(j=k\).
+    Now assuming \(l_{f\rest(j+2)\last(k+2)}=j-k\), we show...
+  \end{proof}
 

### 2018-02-22 postdoctoral/k-markov-tactic-banach-mazur.tex
finish proof for improving (k+2)-mark to (k+2)-tactic

@@
   \begin{proof}
+    The intuition of the following proof is simple: consider the case
+    \(k=0\). During the first round,
+    \(\plI\) plays some \(p_0\in\mb P\), and
+    \(\plII\) can store the round number \(0\) (known by \(\plII\) since they
+    only have knowledge of one move) by pretending \(\plI\) chose
+    \(a_{p_0}(0)\leq p_0\) instead, and applying the winning \(2\)-mark.
+    Thus when \(\plI\) plays \(p_1\leq a_{p_0}(0)\), \(\plII\) will have
+    knowledge of both \(p_0\) and \(p_1\), and thus can observe that as
+    \(p_1\leq a_{p_0}(0)\), it must be round \(1\) rather than some future
+    round, and can repeat this process by pretending \(\plI\) chose
+    \(a_{p_1}(1)\leq p_1\) and \(a_{p_0}(0)\leq p_0\) instead.
+
+    We now proceed with a formal proof.
     Let \(\sigma\) witness \(\plII\kmarkwin{(k+2)}\bmPoGame{\mb P}{W}\).
@@
 
-    Let \(f\) be a legal attack against \(\tau\). The intuition of the
-    following proof is simple: by construction, \(l_t\) will produce
-    the number of \(\plI\)'s moves forgotten by \(\plII\)'s \((k+2)\)-tactic,
-    allowing the \((k+2)\)-tactic to deduce the round number and thus exploit
-    the winning \((k+2)\)-mark.
-
+    Let \(f\) be a legal attack against \(\tau\).
     We may quickly verify
     that \(l_{f\rest 2}=0\) since
-    \[
+    \begin{align*}
       (f\rest 2)(1)
-        =
+        &=
       f(1)
-        \leq
+        \\&\leq
       \tau(f\rest 1)
-        =
+        \\&=
       \sigma(\<a_{f(0)}(0)\>,1)
-        \leq
+        \\&\leq
       a_{f(0)}(0)
-        =
+        \\&=
       a_{(f\rest 2)(0)}(0+0)
-    .\]
+    \end{align*}
     We claim in general that \(l_{f\rest(j+2)}=0\) for \(j\leq k\).
     Assuming \(l_{f\rest(j+2)}=0\) for \(j<k\),
-    \[
+    \begin{align*}
       (f\rest(j+3))(j+2)
-        =
+        &=
       f(j+2)
-        \leq
+        \\&\leq
       \tau(f\rest(j+2))
-        =
-      \sigma(f\rest(j+2)',0+j+2)
-        \leq
+        \\&=
+      \sigma(f\rest(j+2)',0+(j+2))
+        \\&\leq
       f\rest(j+2)'(j+1)
-    \]
-    \[
-        =
-      a_{(f\rest(j+2))(j+1)}(j+1)
-        =
+        \\&=
+      a_{(f\rest(j+2))(j+1)}(0+(j+1))
+        \\&=
       a_{(f\rest(j+3))(j+1)}(0+(j+1))
-    \]
+    \end{align*}
     proving \(l_{f\rest(j+3)}=0\).
 
-    Now we show that \(l_{f\rest(j+2)\last(k+2)}=j-k\) for \(j\geq k\).
-    We've just shown that this is true for our base case \(j=k\).
-    Now assuming \(l_{f\rest(j+2)\last(k+2)}=j-k\), we show...
+    Now we show that \(l_{f\rest(n+2)\last(k+2)}=j-k\) for \(n\geq k\).
+    We've just shown that this is true for our base case \(n=k\)
+    since in that case \(f\rest(n+2)\last(k+2)=f\rest(k+2)\).
+    Now assuming \(l_{f\rest(n+2)\last(k+2)}=n-k\) for some \(n\geq k\),
+    we observe
+    \begin{align*}
+      (f\rest(n+3)\last(k+2))(k+1)
+        &=
+      f(n+2)
+        \\&\leq
+      \tau(f\rest(n+2)\last(k+2))
+        \\&=
+      \sigma((f\rest(n+2)\last(k+2))',(n-k)+(k+2))
+        \\&\leq
+      (f\rest(n+2)\last(k+2))'(k+1)
+        \\&=
+      a_{(f\rest(n+2)\last(k+2))(k+1)}((n-k)+(k+1))
+        \\&=
+      a_{(f\rest(n+3)\last(k+2))(k)}((n+1-k)+(k))
+    \end{align*}
+    and conclude \(l_{f\rest(n+3)\last(k+2)}=n+1-k\).
+
+    Define \(g\in\mb P^\downarrow\) by \(g(0)=f(0)\) and
+    \(g(j+1)=a_{f(j+1)}(j+1)\).
+    Reviewing the above, the reader may confirm that we have shown for
+    \(n<k+2\)
+    \[
+      f(n+1)
+        \leq
+      \tau(f\rest(n+1))
+        =
+      \sigma(g\rest(n+1),n+1)
+        \leq
+      g(n)
+        \leq
+      f(n)
+    \]
+    and for \(n\geq k+2\)
+    \[
+      f(n+1)
+        \leq
+      \tau(f\rest(n+1)\last(k+2))
+        =
+      \sigma(g\rest(n+1)\last(k+2),n+1)
+        \leq
+      g(n)
+        \leq
+      f(n)
+    \]
+    Thus \(g\) is a legal attack against \(\sigma\), and since \(\sigma\)
+    is winning, \(g\in W\). Since \(W\) is closed under zipping,
+    \(f\in W\), and therefore \(\tau\) is also winning.
   \end{proof}

### 2018-02-23 postdoctoral/k-markov-tactic-banach-mazur.tex
almost finish poset banach mazur game result

@@
     Let \(\mb P\) be partially ordered by \(\leq\).
-    Let \(\mb P^{\downarrow}=\{f\in\mb P^\omega : f(n)\geq f(n+1)\}\).
-    Then for \(f,g\in\mb P^\downarrow\), we say that \(f,g\) zip into each
+    Let \(\mb P^{\omega,\downarrow}=\{f\in\mb P^\omega : f(n)\geq f(n+1)\}\).
+    Then for \(f,g\in\mb P^{\omega,\downarrow}\), we say that \(f,g\) zip into each
     other if for all \(m<\omega\) there exists \(n<\omega\) such that
@@
     \(\bmPoGame{\mb P}{W}\) is a game defined for all non-empty partial orders
-    \(\mb P\) and all subsets \(W\subseteq\mb P^\downarrow\).
+    \(\mb P\) and all subsets \(W\subseteq\mb P^{\omega,\downarrow}\).
     During round \(0\), \(\plI\) chooses \(a_0\in\mb P\),
@@
   \begin{theorem}
-    Let \(W\subseteq\mb P^\downarrow\) be closed under zipping.
+    Let \(W\subseteq\mb P^{\omega,\downarrow}\) be closed under zipping.
     \(\plII\markwin\bmPoGame{\mb P}{W}\) if and only if
@@
     Thus if \(a(n)\) is long for \(n<\omega\), it follows that
-    \(c\in\mb P^\downarrow\) defined by \(c(n)=s_n(a(n))\)
+    \(c\in\mb P^{\omega,\downarrow}\) defined by \(c(n)=s_n(a(n))\)
     is a legal attack against \(\tau\). Since \(\tau\) is winning,
@@
     .\]
-    As a result, \(c\in\mb P^\downarrow\) defined by \(c(n)=\tau^n(b(n))\)
+    As a result, \(c\in\mb P^{\omega,\downarrow}\) defined by \(c(n)=\tau^n(b(n))\)
     is a legal attack against the winning strategy \(\tau\). Therefore
@@
     When \(\mb P=T(X)\setminus\{\emptyset\}\) is ordered by set-inclusion
-    and \(W=\{U\in\mb P^\downarrow:\bigcap_{n<\omega}U(n)\not=\emptyset\}\),
+    and \(W=\{U\in\mb P^{\omega,\downarrow}:\bigcap_{n<\omega}U(n)\not=\emptyset\}\),
     then \(\bmPoGame{\mb P}{W}\) is exactly the topological Banach Mazur game
@@
 
-    % \begin{proposition}
-    %   Suppose that for every finite collection \(\{\mb P_i:i<n\}\)
-    %   such that \(\mb P=\bigcup_{i<n}\mb P_i\),
-    %   some \(\mb P_i\) contains two incompatible points.
-    %   Then \(\mb P\) contains an infinite antichain.
-    % \end{proposition}
-    %
-    % \begin{proof}
-    %   Suppose \(a_i\in\mb P_i\) have been defined for \(i<n\) such that
-    %   \(a_i\not\in\bigcup_{j<i}\mb P_j\) and
-    %   each \(\mb P_i\) is pairwise-compatible. It follows that
-    %   \(\mb P\not=\bigcup_{i<n}\mb P_i\), so choose
-    %   \(a_n\not\in\bigcup_{i<n}\mb P_i\) and let \(\mb P_n\) be a maximal family
-    %   containing \(a_n\) such that \(\mb P_n\) is pairwise-compatible.
-    %
-    %   It follows that \(A=\{a_n:n<\omega\}\) is an antichain, since for
-    %   every pair \(a_i,a_j\in A\) with \(i<j\), \(a_j\not\in\mb P_i\), so
-    %   \(a_j\) is not compatible with something in \(\mb P_i\)...
-    % \end{proof}
-
   \begin{definition}
@@
     For every partial order \(\mb P\) and compatible \(p,q\in\mb P\),
-  let \(p\wedge q\) satisfy \(p\wedge q\leq p,q\).
+    write \(p\not\perp q\) and let \(p\wedge q\) satisfy \(p\wedge q\leq p,q\).
+    If \(p,q\) are incompatible, write \(p\perp q\).
   \end{definition}
 
-  \begin{claim}
+  \begin{definition}
+    For every partial order \(\mb P\) and compatible \(p\in\mb P\),
+    let \(p^\downarrow=\{q\in\mb P:q\leq p\}\).
+\end{definition}
+
+  \begin{lemma}
     \(\mb P\) contains no infinite antichains if and only if every
     antichain in \(\mb P\) is of size \(n\) or less for some \(n<\omega\).
-  \end{claim}
+  \end{lemma}
 
   \begin{proof}
-    MAYBE? Apparently true for \(\mb P=\tau\setminus\{\emptyset\}\) due to
-    Lemma 2.10 of \cite{comfort_negrepontis_1982}.
+    This was shown to be true for \(\mb P=\tau\setminus\{\emptyset\}\) in
+    Lemma 2.10 of \cite{comfort_negrepontis_1982}. It's likely known
+    for general \(\mb P\), but I can't find a citation, so let's roll
+    our own proof here. Assume \(\mb P\) has antichains of size \(n\)
+    for all \(n<\omega\).
+
+    Say \(p\in\mb P\) is bad if there exists \(r_p\leq p\) such that
+    \(r_p^\downarrow\) is pairwise compatible. Let
+    \(\mb P_{bad}\) collect all bad points in \(\mb P\), and say
+    \(p\sim q\) for \(p,q\in\mb P_{bad}\) if \(r_p\not\perp r_q\).
+    This is obviously symmetric and reflexive, and if we assume
+    \(p\sim q,q\sim t\), then let \(s_p=r_p\wedge r_q\) and
+    \(s_r=r_q\wedge r_t\). Since \(r_q^\downarrow\in\mb P_{bad}\),
+    \(s_p\not\perp s_r\), so \(r_p\not\perp r_t\) and thus
+    \(p\sim t\). Thus \(\sim\) is an equivalence relation.
+
+    If \(\mb P_{bad}/\sim\) is infinite, we may choose \(p_i\in\mb P_{bad}\)
+    such that \(p_i\not\sim p_j\) for \(i<j<\omega\). Thus
+    \(r_{p_i}\perp r_{p_j}\) for \(i<j<\omega\), giving us
+    an infinite antichain \(\{r_{p_i}:i<\omega\}\).
+
+    Otherwise \(|\mb P_{bad}/\sim|=n<\omega\), and choose an antichain
+    \(\{p_i:i\leq n\}\) in \(\mb P\). If \(\{p_i:i<n\}\subseteq\mb P_{bad}\),
+    \(p_i\perp p_j\) implies \(r_{p_i}\perp r_{p_j}\)
+    and \(p_i\not\sim p_j\) for all
+    \(i\leq n\). Thus \(\mb P_{bad}=\bigcup_{i<n}\overset{\sim}{p_i}\),
+    and \(p_n\not\in\mb P_{bad}\).
+
+    So we've found \(b_0\in\mb P\setminus\mb P_{bad}\).
+    Given \(b_n\in\mb P\setminus\mb P_{bad}\), we may choose
+    \(a_n,b_{n+1}\leq b_n\) such that \(a_n\perp b_{n+1}\).
+    Thus by construction, \(a_n\perp a_{m+1}\) for all
+    \(n\leq m<\omega\). Therefore
+    \(\{a_n:n<\omega\}\) is an antichain.
   \end{proof}
@@
   \begin{proposition}
-    Let \(W\subseteq\mb P^\downarrow\) be closed under zipping.
+    Let \(W\subseteq\mb P^{\omega,\downarrow}\) be closed under zipping.
     Suppose every antichain in \(\mb P\) is of size \(n<\omega\) or less,
@@
     \(\plII\autowin\bmPoGame{\mb P}{W}\) (i.e. \(\plII\) wins every
-    play of \(\bmPoGame{\mb P}{W}\), i.e. \(W=\mb P^\downarrow\)).
+    play of \(\bmPoGame{\mb P}{W}\), i.e. \(W=\mb P^{\omega,\downarrow}\)).
   \end{proposition}
@@
   \begin{lemma}
-    Let \(W\subseteq\mb P^\downarrow\) be closed under zipping.
+    Let \(W\subseteq\mb P^{\omega,\downarrow}\) be closed under zipping.
     Suppose that for every \(p\in\mb P\), there exists an infinite
@@
 
-    Define \(g\in\mb P^\downarrow\) by \(g(0)=f(0)\) and
+    Define \(g\in\mb P^{\omega,\downarrow}\) by \(g(0)=f(0)\) and
     \(g(j+1)=a_{f(j+1)}(j+1)\).

### 2018-03-02 articles/relating-games-menger-cft-ss/article.tex
add keywords, subject classes
incorporate referee typesetting feedback

@@
 
-% \keywords{TODO}
-% \subjclass[2010]{}
+\keywords{Selection property, selection game,
+limited information strategies, covering properties, Cp theory}
+
+\subjclass[2010]{54C30, 54D20, 54D45, 91A44}
 
@@
 \cite[Topological games and Ramsey theory]{19362020070101} (wherein
-the notation is more succently given as \(\Omega,\Omega_x\)).  The
+the notation is more succinctly given as \(\Omega,\Omega_x\)).  The
 relationship between such sets becomes apparent in the study of
@@
 
-Of course, one may easily observe that a selective separable space is
+Of course, one may easily observe that a selectively separable space is
 separable, and \(SS\Rightarrow CDFT\).
@@
   \(\plII\markwin\schSelGame{\mc A}{\mc B}\) characterizes
-  \(P^{+mark}\) (``Markov \(P\)'').
-  Of course, \(P^{+mark}\Rightarrow P^+ \Rightarrow P\).
+  \(P^{\plusMark}\) (``Markov \(P\)'').
+  Of course, \(P^{\plusMark}\Rightarrow P^+ \Rightarrow P\).
 \end{notation}
@@
 \begin{question}\label{mainQuestion}
-  Does \(SS^+\) imply \(SS^{+mark}\)?
+  Does \(SS^+\) imply \(SS^{\plusMark}\)?
 \end{question}
@@
 \cite{clontzMengerCMUC} the author showed that \(M^+\) implies
-\(M^{+mark}\) for second-countable spaces; however, the one-point
+\(M^{\plusMark}\) for second-countable spaces; however, the one-point
 Lindel\"of-ication \(\onePtLind{\omega_1}\) of a discrete space of size
@@
 example of a regular non-second-countable space which is
-\(M^+\) but not \(M^{+mark}\) (equivalently, not \(\sigma\)-compact).
+\(M^+\) but not \(M^{\plusMark}\) (equivalently, not \(\sigma\)-compact).
 It will later be shown that it is no coincidence
-that countable \(SS^+\) implies \(SS^{+mark}\) and
-second-countable \(M^+\) implies \(M^{+mark}\).
+that countable \(SS^+\) implies \(SS^{\plusMark}\) and
+second-countable \(M^+\) implies \(M^{\plusMark}\).
 
@@
 
-\begin{theorem}[Lem 2.7 of \cite{MR2678950}]
+\begin{theorem}[Lemma 2.7 of \cite{MR2678950}]
   The following are equivalent for any topological space \(X\).
@@
   \begin{itemize}
-    \item \(X\) is \(SS\) (resp. \(SS^+\), \(SS^{+mark}\)).
+    \item \(X\) is \(SS\) (resp. \(SS^+\), \(SS^{\plusMark}\)).
     \item \(X\) is separable and \(CDFT\)
-          (resp. \(CDFT^+\), \(CDFT^{+mark}\)).
+          (resp. \(CDFT^+\), \(CDFT^{\plusMark}\)).
     \item \(X\) has a countable dense subset \(D\) where
-          \(CDFT_x\) (resp. \(CDFT_x^+\), \(CDFT_x^{+mark}\))
+          \(CDFT_x\) (resp. \(CDFT_x^+\), \(CDFT_x^{\plusMark}\))
           holds for all \(x\in D\).
@@
 
-  Now let \(\sigma_i\) be a witness for \(CDFT_{d_i}^{+mark}\)
+  Now let \(\sigma_i\) be a witness for \(CDFT_{d_i}^{\plusMark}\)
   for each \(i<\omega\). We define the Markov strategy \(\tau\) for the
@@
   Let \(\<D_0,D_1,\dots\>\in\mc D_X^\omega\).
-  By \(CDFT_{d_i}^{+mark}\), we have
+  By \(CDFT_{d_i}^{\plusMark}\), we have
   \[
@@
   .\]
-  Therefore \(\tau\) witnesses \(SS^{+mark}\).
+  Therefore \(\tau\) witnesses \(SS^{\plusMark}\).
 \end{proof}
@@
 So amongst separable spaces, we see that \(SS\)
-(resp. \(SS^+\), \(SS^{+mark}\)) and
-\(CDFT\) (resp. \(CDFT^+\), \(CDFT^{+mark}\))
+(resp. \(SS^+\), \(SS^{\plusMark}\)) and
+\(CDFT\) (resp. \(CDFT^+\), \(CDFT^{\plusMark}\))
 are equivalent. We now further bridge the gap between \(CDFT\)
@@
 
-This result may similarly be generalized in a game theoretic sense.
+This result may similarly be generalized in a game-theoretic sense.
 In addition, this proof will demonstrate the equivalence of
@@
   Any witness for \(\Omega M\) (resp.
-  \(\Omega M^+,\Omega M^{+mark}\))
-  may be improved such that any final sequence of the chosen
+  \(\Omega M^+,\Omega M^{\plusMark}\))
+  may be improved so that any final sequence of the chosen
   finite subcollections is an \(\omega\)-cover.
@@
     \bigcup_{i\leq n}\sigma(\<\mc U_i,\dots,\mc U_n\>)
-  \). For \(\Omega M^{+mark}\), the winning Markov strategy \(\sigma\) may
+  \). For \(\Omega M^{\plusMark}\), the winning Markov strategy \(\sigma\) may
   be improved to \(\tau\) where
@@
   If \(X\) is \(\Omega M\)
-  (resp. \(\Omega M^+\), \(\Omega M^{+mark}\)).
+  (resp. \(\Omega M^+\), \(\Omega M^{\plusMark}\)).
   then \(C_p(X)\) is \(CFT_{\vec 0}\)
-  (resp. \(CFT_{\vec 0}^+\), \(CFT_{\vec 0}^{+mark}\)).
+  (resp. \(CFT_{\vec 0}^+\), \(CFT_{\vec 0}^{\plusMark}\)).
 \end{lemma}
@@
 
-  Assuming \(X\) is \(\Omega M^{+mark}\), choose a witness
+  Assuming \(X\) is \(\Omega M^{\plusMark}\), choose a witness
   \(\sigma\) such that
@@
   If \(C_p(X)\) is \(CDFT_{\vec 0}\)
-  (resp. \(CDFT_{\vec 0}^+\), \(CDFT_{\vec 0}^{+mark}\)),
+  (resp. \(CDFT_{\vec 0}^+\), \(CDFT_{\vec 0}^{\plusMark}\)),
   then \(X\) is \(\Omega M\)
-  (resp. \(\Omega M^+\), \(\Omega M^{+mark}\)).
+  (resp. \(\Omega M^+\), \(\Omega M^{\plusMark}\)).
 \end{lemma}
@@
 
-  Assuming \(C_p(X)\) is \(CDFT_{\vec 0}^{+mark}\), choose a witness
+  Assuming \(C_p(X)\) is \(CDFT_{\vec 0}^{\plusMark}\), choose a witness
   \(\sigma\) such that
@@
       \in
-    [\mc U_n]^{<\omega}S
+    [\mc U_n]^{<\omega}
   .\]
@@
       \item \(X\) is \(\Omega M\)
-            (resp. \(\Omega M^+\), \(\Omega M^{+mark}\)).
+            (resp. \(\Omega M^+\), \(\Omega M^{\plusMark}\)).
       \item \(C_p(X)\) is \(CFT\)
-            (resp. \(CFT^+\), \(CFT^{+mark}\)).
+            (resp. \(CFT^+\), \(CFT^{\plusMark}\)).
       \item \(C_p(X)\) is \(CDFT\)
-            (resp. \(CDFT^+\), \(CDFT^{+mark}\)).
+            (resp. \(CDFT^+\), \(CDFT^{\plusMark}\)).
     \end{itemize}
@@
   Since \(\mc D_X\subseteq \Omega_{X,x}\), the second condition trivially
-  implies the first. As \(C_p(X)\) is homogeneous, the \(C(D)FT\) properties
+  implies the third. As \(C_p(X)\) is homogeneous, the \(C(D)FT\) properties
   follow from \(C(D)FT_{\vec 0}\). So the result follows from the
@@
 
-\section{A space which is \(CFT^+\) but not \(CDFT^{+mark}\)}
+\section{A space which is \(CFT^+\) but not \(CDFT^{\plusMark}\)}
 
 Our goal is to now demonstrate a space which is \(CFT^+\),
-but not even \(CDFT^{+mark}\). To do so, we will find a space \(X\)
-which is \(\Omega M^+\) but not \(\Omega M^{+mark}\), yielding \(C_p(X)\)
+but not even \(CDFT^{\plusMark}\). To do so, we will find a space \(X\)
+which is \(\Omega M^+\) but not \(\Omega M^{\plusMark}\), yielding \(C_p(X)\)
 as our example.
@@
     \item \(X\) is \(\sigma\)-compact
-    \item \(X\) is \(\Omega M^{+mark}\)
-    \item \(X\) is \(M^{+mark}\)
+    \item \(X\) is \(\Omega M^{\plusMark}\)
+    \item \(X\) is \(M^{\plusMark}\)
   \end{itemize}
@@
 \begin{proof}
-  The equivalence of \(\sigma\)-compact and \(M^{+mark}\) in regular spaces
-  was shown in \cite{clontzMengerCMUC}. As \(\Omega M^{+mark}\)
-  trivially implies \(M^{+mark}\), we need only demonstrate that
+  The equivalence of \(\sigma\)-compact and \(M^{\plusMark}\) in regular spaces
+  was shown in \cite{clontzMengerCMUC}. As \(\Omega M^{\plusMark}\)
+  trivially implies \(M^{\plusMark}\), we need only demonstrate that
   if \(X=\bigcup_{n<\omega} K_n\) for \(K_n\) compact and increasing,
-  then \(X\) is \(\Omega M^{+mark}\).
+  then \(X\) is \(\Omega M^{\plusMark}\).
 
@@
   Let \(\omega_1\) have the discrete topology. Then
-  \(\onePtLind{\omega_1}\) is \(\Omega M^+\) but not \(\Omega M^{+mark}\).
+  \(\onePtLind{\omega_1}\) is \(\Omega M^+\) but not \(\Omega M^{\plusMark}\).
 \end{theorem}
@@
   The proof that \(X=\onePtLind{\omega_1}\) is not
-  \(\sigma\)-compact (and therefore not \(\Omega M^{+mark}\))
+  \(\sigma\)-compact (and therefore not \(\Omega M^{\plusMark}\))
   follows from the fact that its countably infinite subsets
@@
 \begin{corollary}
-  \(C_p(\onePtLind{\omega_1})\) is \(CFT^+\) but not \(CDFT^{+mark}\).
+  \(C_p(\onePtLind{\omega_1})\) is \(CFT^+\) but not \(CDFT^{\plusMark}\).
 \end{corollary}
@@
   Does there exist a separable subspace of \(C_p(\onePtLind{\omega_1})\)
-  which is not \(CDFT^{+mark}\)?
+  which is not \(CDFT^{\plusMark}\)?
 \end{question}
@@
 previously demonstrated that \(SS^+\) is equivalent to
-\(SS^{+mark}\) amongst countable spaces.
+\(SS^{\plusMark}\) amongst countable spaces.
 A similar result by the author
-showed that \(M^+\) is equivalent to \(M^{+mark}\) in second-countable
+showed that \(M^+\) is equivalent to \(M^{\plusMark}\) in second-countable
 spaces. The following result generalizes both.
@@
   \(
-    \{\sigma(\<Z_{t\rest1},Z_{t\rest2},\dots,Z_t,A\>:A\in\mc A\}
+    \{\sigma(\<Z_{t\rest1},Z_{t\rest2},\dots,Z_t,A\>):A\in\mc A\}
       \subseteq
@@
   \(
-    \{\sigma(\<Z_{t\rest1},Z_{t\rest2},\dots,Z_t,A\>:A\in\mc A\}
+    \{\sigma(\<Z_{t\rest1},Z_{t\rest2},\dots,Z_t,A\>):A\in\mc A\}
       =
@@
   Define \(f\in\omega^\omega\) as follows.
-  Let \(n<\omega\) and suppose that \(f\rest n\) has been already
+  Let \(n<\omega\) and suppose that \(f\rest n\) has already
   been defined. Then choose \(f(n)<\omega\) such that
@@
   A countable space is \(SS^+\) if and only if it is
-  \(SS^{+mark}\).
+  \(SS^{\plusMark}\).
 \end{corollary}
@@
   A second-countable space is \(\Omega M^+\) if and only if
-  it is \(\Omega M^{+mark}\).
+  it is \(\Omega M^{\plusMark}\).
 \end{corollary}
@@
   A second-countable space is \(M^+\) if and only if
-  it is \(M^{+mark}\).
+  it is \(M^{\plusMark}\).
 \end{corollary}
@@
 \begin{proof}
-  An easy adapatation of the preceding proof, replacing \(\omega\)-covers
+  An easy adaptation of the preceding proof, replacing \(\omega\)-covers
   with open covers, and replacing \(F\in[X]^{<\omega}\) with \(x\in X\).
@@
 
-\section{Strong variants of selection princples and games}
+\section{Strong variants of selection principles and games}
 
@@
 set. Convention calls for denoting these as
-\term{strong} versions of the corresponding selection princples and games,
+\term{strong} versions of the corresponding selection principles and games,
 although the ``strong Menger'' property is commonly known as ``Rothberger''
@@
   \begin{itemize}
-    \item \(X\) is \(sSS\) (resp. \(sSS^+\), \(sSS^{+mark}\)).
+    \item \(X\) is \(sSS\) (resp. \(sSS^+\), \(sSS^{\plusMark}\)).
     \item \(X\) is separable and \(sCDFT\)
-          (resp. \(sCDFT^+\), \(sCDFT^{+mark}\)).
+          (resp. \(sCDFT^+\), \(sCDFT^{\plusMark}\)).
     \item \(X\) has a countable dense subset \(D\) where
-          \(sCDFT_x\) (resp. \(sCDFT_x^+\), \(sCDFT_x^{+mark}\))
+          \(sCDFT_x\) (resp. \(sCDFT_x^+\), \(sCDFT_x^{\plusMark}\))
           holds for all \(x\in D\).
@@
 
-  Let \(\sigma_i\) be a witness for \(sCDFT_{d_i}^{+mark}\)
+  Let \(\sigma_i\) be a witness for \(sCDFT_{d_i}^{\plusMark}\)
   for each \(i<\omega\).
@@
   removing all terms of index \(n\) such that \(p(n)\not=i\).
-  By \(sCDFT_{d_i}^{+mark}\), we have
+  By \(sCDFT_{d_i}^{\plusMark}\), we have
   \[
@@
       \item \(X\) is \(\Omega R\)
-            (resp. \(\Omega R^+\), \(\Omega R^{+mark}\)).
+            (resp. \(\Omega R^+\), \(\Omega R^{\plusMark}\)).
       \item \(C_p(X)\) is \(sCFT\)
-            (resp. \(sCFT^+\), \(sCFT^{+mark}\)).
+            (resp. \(sCFT^+\), \(sCFT^{\plusMark}\)).
       \item \(C_p(X)\) is \(sCDFT\)
-            (resp. \(sCDFT^+\), \(sCDFT^{+mark}\)).
+            (resp. \(sCDFT^+\), \(sCDFT^{\plusMark}\)).
     \end{itemize}
@@
   Let \(\omega_1\) have the discrete topology. Then
-  \(\onePtLind{\omega_1}\) is \(\Omega R^+\) but not \(\Omega M^{+mark}\).
+  \(\onePtLind{\omega_1}\) is \(\Omega R^+\) but not \(\Omega M^{\plusMark}\).
 \end{theorem}
@@
 \begin{corollary}
-  \(C_p(\onePtLind{\omega_1})\) is \(sCFT^+\) but not \(CDFT^{+mark}\).
+  \(C_p(\onePtLind{\omega_1})\) is \(sCFT^+\) but not \(CDFT^{\plusMark}\).
 \end{corollary}
@@
   A countable space is \(sSS^+\) if and only if it is
-  \(sSS^{+mark}\).
+  \(sSS^{\plusMark}\).
 \end{corollary}
@@
   A second-countable space is \(\Omega R^+\) if and only if
-  it is \(\Omega R^{+mark}\).
+  it is \(\Omega R^{\plusMark}\).
 \end{corollary}
@@
   A second-countable space is \(R^+\) if and only if
-  it is \(R^{+mark}\).
+  it is \(R^{\plusMark}\).
 \end{corollary}

### 2018-03-02 articles/relating-games-menger-cft-ss/article.tex
fix technical error by applying AC

@@
 \begin{lemma}\label{mengerFanLemma1}
-  Let \(X\) be a \(T_{3\frac{1}{2}}\) topological space.
   If \(X\) is \(\Omega M\)
-  (resp. \(\Omega M^+\), \(\Omega M^{\plusMark}\)).
+  (resp. \(\Omega M^+\), \(\Omega M^{\plusMark}\)),
   then \(C_p(X)\) is \(CFT_{\vec 0}\)
@@
   \(\<\mc U_0(B_0),\mc U_1(B_1),\dots\>\in \Omega_X^\omega\).
+  For \(U\in\mc U_n(B_n)\), choose \(\vec x_U\in B_n\) such that
+  \(
+    U
+      =
+    \vec x_U^{\leftarrow}\left[\left(-\frac{1}{2^n},\frac{1}{2^n}\right)\right]
+  \).
 
@@
   is an \(\omega\)-cover of \(X\) for all \(i<\omega\).
-  Now let
+  Let
   \[
@@
     \left\{
-      \vec x\in B_n
+      \vec x_U
     :
-      \vec x^{\leftarrow}\left[\left(-\frac{1}{2^n},\frac{1}{2^n}\right)\right]
+      U
         \in
@@
   \(i\leq n<\omega\) and
-  \(\vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\in\mc F_n\)
-  such that \(G\subseteq \vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\).
-  Therefore, \(G\subseteq \vec x^{\leftarrow}[(-\epsilon,\epsilon)]\).
-  It follows that \(\vec x\in F_n\cap[\vec 0,G,\epsilon]\), and thus
+  \(U\in\mc F_n\)
+  such that
+  \[
+    G
+      \subseteq
+    U
+      =
+    \vec x_U^{\leftarrow}\left[\left(-\frac{1}{2^n},\frac{1}{2^n}\right)\right]
+      \subseteq
+    \vec x_U^{\leftarrow}[(-\epsilon,\epsilon)]
+  .\]
+  It follows that \(\vec x_U\in F_n\cap[\vec 0,G,\epsilon]\), and thus
   every basic open neighborhood of \(\vec 0\) intersects
@@
   is an \(\omega\)-cover, we may choose
-  \(i\leq n<\omega\) and \(\vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]
-  \in\sigma(\<\mc U_0(B_0),\dots,\mc U_n(B_n)\>)\)
-  such that \(G\subseteq \vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\).
-  Therefore \(G\subseteq \vec x^{\leftarrow}[(-\epsilon,\epsilon)]\).
-  It follows that \(\vec x\in \tau(\<B_0,\dots,B_n\>)\cap[\vec 0,G,\epsilon]\),
+  \(i\leq n<\omega\) and
+  \(U\in\sigma(\<\mc U_0(B_0),\dots,\mc U_n(B_n)\>)\)
+  such that
+  \[
+    G
+      \subseteq
+    U
+      =
+    \vec x_U^{\leftarrow}\left[\left(-\frac{1}{2^n},\frac{1}{2^n}\right)\right]
+      \subseteq
+    \vec x_U^{\leftarrow}[(-\epsilon,\epsilon)]
+  .\]
+  It follows that
+  \(\vec x_U\in \tau(\<B_0,\dots,B_n\>)\cap[\vec 0,G,\epsilon]\),
   and thus every basic open neighborhood of \(\vec 0\) intersects
@@
   we may choose \(i\leq n<\omega\) and
-  \(\vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\in\sigma(\mc U_n(B_n),n)\)
-  such that \(G\subseteq \vec x^{\leftarrow}[(-\frac{1}{2^n},\frac{1}{2^n})]\).
-  Therefore \(G\subseteq \vec x^{\leftarrow}[(-\epsilon,\epsilon)]\).
-  It follows that \(\vec x\in \tau(B_n,n)\cap[\vec 0,G,\epsilon]\), and thus
+  \(U\in\sigma(\mc U_n(B_n),n)\)
+  such that
+  \[
+    G
+      \subseteq
+    U
+      =
+    \vec x_U^{\leftarrow}\left[\left(-\frac{1}{2^n},\frac{1}{2^n}\right)\right]
+      \subseteq
+    \vec x_U^{\leftarrow}[(-\epsilon,\epsilon)]
+  .\]
+  It follows that \(\vec x_U\in \tau(B_n,n)\cap[\vec 0,G,\epsilon]\), and thus
   every basic open neighborhood of \(\vec 0\) intersects

### 2018-03-06 articles/relating-games-menger-cft-ss/article.tex
finish incorporating reviewer's mathematical corrections

@@
 Our goal is to now demonstrate a space which is \(CFT^+\),
-but not even \(CDFT^{\plusMark}\). To do so, we will find a space \(X\)
+but not \(CFT^{\plusMark}\) or even \(CDFT^{\plusMark}\).
+To do so, we will find a space \(X\)
 which is \(\Omega M^+\) but not \(\Omega M^{\plusMark}\), yielding \(C_p(X)\)
@@
   arbitrary open cover \(\mc V\), close it under finite unions to obtain
-  an \(\omega\)-cover \(\mc U\). Then the finite subcollection \(\mc F\)
-  of \(\mc U\) is of course a finite subcover,
-  and since each member of \(\mc F\) is a finite union of open sets in
+  an \(\omega\)-cover \(\mc U\). Then for \(n=1\),
+  the finite subcollection \(\mc F\) of \(\mc U\) satisfying
+  \(\{x\}\subseteq U\) for all \(x\in X\) and some \(U\in\mc U\)
+  is of course a finite subcover.
+  Since each member of \(\mc F\) is a finite union of open sets in
   \(\mc V\), there exists a finite subcover \(\mc G\) of \(\mc V\).
@@
 \begin{question}
-  Does there exist a non-\(\sigma\)-compact \(\Omega M^+\) space
+  Does there exist a \(T_{3\frac{1}{2}}\),
+  non-\(\sigma\)-compact, and \(\Omega M^+\) space
   with a coarser separable metrizable topology?
@@
   \(|\bigcup\mc A|\leq\omega\)
-  and let \(\mc B\) be a family of sets closed under supersets. Then
+  and let \(\mc B\) be a family of sets such that
+  \(B\in\mc B\) and \(B\subseteq B'\subseteq\bigcup\mc A\)
+  implies \(B'\in\mc B\). Then
   \(\plII\win\schSelGame{\mc A}{\mc B}\) if and only if
@@
   For \(t\in\omega^{<\omega}\), suppose
-  \(Z_s\in\mc A\) has been defined for all \(s\leq t\). Note then that
+  \(Z_s\in\mc A\) has been defined for all nonempty \(s\leq t\).
+  We use the convention
   \(
+    \<Z_{\emptyset\rest1},Z_{\emptyset\rest2},\dots,Z_\emptyset,A\>
+      =
+    \<A\>
+  \).
+  Note then that
+  \[
     \{\sigma(\<Z_{t\rest1},Z_{t\rest2},\dots,Z_t,A\>):A\in\mc A\}
       \subseteq
-    [\bigcup\mc A]^{<\omega}
-  \)
+    \left[\bigcup\mc A\right]^{<\omega}
+  \]
   and therefore is countable.
   So choose \(Z_{t\concat\<n\>}\in\mc A\) for \(n<\omega\) such that
-  \(
+  \[
     \{\sigma(\<Z_{t\rest1},Z_{t\rest2},\dots,Z_t,A\>):A\in\mc A\}
@@
     \{\sigma(\<Z_{t\rest1},Z_{t\rest2},\dots,Z_t,Z_{t\concat\<n\>}\>):n<\omega\}
-  \).
+  .\]
 
@@
   For each \(\omega\)-cover \(\mc U\) and finite set \(F\in[X]^{<\omega}\),
-  choose \(U_{\mc U,F}\in\mc U\) such that \(F\subseteq U\). Then choose a
-  basic open set \(U_{\mc U,F}^*\) such that
-  \(F\subseteq U_{\mc U,F}^*\subseteq U_{\mc U,F}\). Finally, for each
-  \(\omega\)-cover \(\mc U\), let
+  choose \(U_{\mc U,F}\in\mc U\) and a basic open set \(B_{\mc U,F}\)
+  such that \(F\subseteq B_{\mc U,F}\subseteq U_{\mc U,F}\).
+  Finally, for each \(\omega\)-cover \(\mc U\), let
   \[
@@
     \{
-      U_{\mc U,F}^*
+      B_{\mc U,F}
         :
@@
     \Omega_X^*
-  .\]
-
+  \]
+  be an \(\omega\)-cover of basic open sets refining \(\mc U\).
+
+  Given \(\mc U\) and \(V\in\mc U^*\), choose
+  \(F(V)\in[X]^{<\omega}\) such that \(V=B_{\mc U,F(V)}\).
   Define the strategy \(\tau\) such that
-  \(\tau(\mc U,n)=\{U_{\mc U,F}:U_{\mc U,F}^*\in\sigma(\mc U^*,n)\}\).
+  \(\tau(\mc U,n)=\{U_{\mc U,F(V)}:V\in\sigma(\mc U^*,n)\}\).
   For any sequence of \(\omega\)-covers \(\<\mc U_0,\mc U_1,\dots\>\),
   it follows that \(\bigcup_{n<\omega}\sigma(\mc U_n^*,n)\) is an
-  \(\omega\)-cover, and therefore
-  \(\bigcup_{n<\omega}\tau(\mc U_n,n)\) is an \(\omega\)-cover also.
+  \(\omega\)-cover refining \(\bigcup_{n<\omega}\tau(\mc U_n,n)\), and therefore
+  \(\bigcup_{n<\omega}\tau(\mc U_n,n)\) is an \(\omega\)-cover also,
+  demonstrating that \(X\) is \(\Omega M^{\plusMark}\).
 \end{proof}

### 2018-03-06 articles/relating-games-menger-cft-ss/article.tex
add improvements and further results suggested by referee

@@
 
-\begin{proposition}
-  Any witness for \(\Omega M\) (resp.
-  \(\Omega M^+,\Omega M^{\plusMark}\))
-  may be improved so that any final sequence of the chosen
-  finite subcollections is an \(\omega\)-cover.
+\begin{proposition}\label{cofinalSequence}
+  Let \(\mc A\), \(\mc B\) be families of sets such that
+  \(B\in\mc B\) and \(B\subseteq B'\subseteq\bigcup\mc A\)
+  implies \(B'\in\mc B\).
+  Then any witness for \(\schSelProp{\mc A}{\mc B}\)
+  may be improved so that any final sequence of the sets chosen by \(\plII\)
+  belongs to \(\mc B\).
+
+  Furthermore, any witness for
+  \(\plII\win\schSelGame{\mc A}{\mc B}\) or
+  \(\plII\markwin\schSelGame{\mc A}{\mc B}\)
+  may be improved so that any subsequence of the sets chosen by \(\plII\)
+  belongs to \(\mc B\).
 \end{proposition}
@@
 \begin{proof}
-  Consider any sequence \(\<\mc U_0,\mc U_1,\dots\>\) of \(\omega\)-covers.
-  For each \(n<\omega\), let
-  \(\<\mc F_n^n,\mc F_{n+1}^n,\dots\>\) witness \(\Omega M\) for the final
-  sequence \(\<\mc U_n,\mc U_{n+1},\dots\>\),
-  and let \(\mc F_n=\bigcup_{i\leq n}\mc F_n^i\); it follows that
-  \(\<\mc F_0,\mc F_1,\dots\>\) satisfies the proposition.
-
-  For \(\Omega M^+\), the winning strategy \(\sigma\) may be improved to
+  Let \(A_n\in\mc A\) for \(n<\omega\), and suppose
+  \(\<B_{n,n},B_{n+1,n},\dots\>\) witnesses \(\schSelProp{\mc A}{\mc B}\)
+  for \(\<A_n,A_{n+1},\dots\>\).
+  Let \(B_n=\bigcup_{i\leq n}B_{n,i}\); it follows that
+  \(\<B_0,B_1,\dots\>\) satisfies the proposition.
+
+  Let \(s\preceq t\) indicate that \(s\) is a subsequence
+  of \(t\). Then for \(\plII\win\schSelGame{\mc A}{\mc B}\),
+  the winning strategy \(\sigma\) may be improved to
   \(\tau\) where
   \(
-    \tau(\<\mc U_0,\dots,\mc U_n\>)
-      =
-    \bigcup_{i\leq n}\sigma(\<\mc U_i,\dots,\mc U_n\>)
-  \). For \(\Omega M^{\plusMark}\), the winning Markov strategy \(\sigma\) may
+    \tau(t\concat\<A\>)
+      =
+    \bigcup_{s\preceq t}\sigma(s\concat\<A\>)
+  \).
+  For \(\plII\markwin\schSelGame{\mc A}{\mc B}\),
+  the winning Markov strategy \(\sigma\) may
   be improved to \(\tau\) where
   \(
-    \tau(\mc U,n)
-      =
-    \bigcup_{i\leq n}\sigma(\mc U,i)
+    \tau(A,n)
+      =
+    \bigcup_{i\leq n}\sigma(A,i)
   \). Both improved strategies are easily seen to satisfy the proposition.
 \end{proof}
+
+It's worth noting that Gruenhage applied a similar technique used above
+for strategies in \(\schSelGame{\mc A}{\mc B}\) to obtain strengthened
+strategies in his game played with open neighborhoods and points in
+\cite{MR0413049}.
 
@@
 \end{question}
+
+We conclude this section by covering a related result observed by the
+anonymous referee in their initial review of this manuscript.
+
+\begin{theorem}
+  A topological space is \(M^+\) if and only if it is \(\Omega M^+\).
+\end{theorem}
+
+\begin{proof}
+  Assume \(X\) is \(M^+\). In \cite[Proposition 5.1]{MR3383283} it is shown
+  that that \(X^m\) must be \(M^+\) for all powers \(m<\omega\), so we shall
+  proceed in the spirit of Proposition \ref{altCompactCharacterization}
+  and its following lemma. Given an \(\omega\)-cover \(\mc U\),
+  it follows that \((\mc U)^m=\{U^m:U\in\mc U\}\) is an open cover of
+  \(X^m\). Given a finite subset \(\mc F\in[(\mc U)^m]^{<\omega}\),
+  let \(\pi_m\mc F=\{U:U^m\in\mc F\}\in[\mc U]^{<\omega}\).
+
+  Let \(\sigma_m\) witness \(M^+\) for \(X^m\), and define
+  the following strategy for \(\plII\) in \(\schSelGame{\Omega}{\Omega}\):
+  \[
+    \tau(\<\mc U_0,\dots,\mc U_n\>)
+      =
+    \bigcup_{m\leq n}
+    \pi_m\sigma_m(\<(\mc U_m)^m,\dots,(\mc U_n)^m\>)
+  .\]
+  Since
+  \[
+    \bigcup_{m\leq n<\omega}
+    \sigma_m(\<(\mc U_m)^m,\dots,(\mc U_n)^m\>)
+  \]
+  is an open cover of \(X^m\) for \(m<\omega\), it follows that
+  \[
+    \bigcup_{n<\omega}
+    \tau(\<\mc U_0,\dots,\mc U_n\>)
+      \supseteq
+    \bigcup_{m\leq n<\omega}
+    \pi_m\sigma_m(\<(\mc U_m)^m,\dots,(\mc U_n)^m\>)
+  \]
+  covers all finite sets of size \(m<\omega\), that is,
+  \(
+    \bigcup_{n<\omega}
+    \tau(\<\mc U_0,\dots,\mc U_n\>)
+  \)
+  is an \(\omega\)-cover, making \(\tau\) a winning strategy.
+\end{proof}
 
@@
 \begin{proof}
-  In Lemmas \ref{mengerFanLemma1} and \ref{mengerFanLemma2},
-  \(|\tau(t)|=|\sigma(t)|\). Therefore they may be extended to
-  the strong cases requiring \(|\tau(t)|=|\sigma(t)|=1\),
-  which yields our result.
+  In the proof of Lemmas \ref{mengerFanLemma1} and \ref{mengerFanLemma2},
+  if the strategy \(\sigma\) produces singletons, so does the strategy
+  \(\tau\).
 \end{proof}
@@
   \(|\bigcup\mc A|\leq\omega\)
-  and let \(\mc B\) be a family of sets closed under supersets. Then
+  and let \(\mc B\) be a family of sets such that
+  \(B\in\mc B\) and \(B\subseteq B'\subseteq\bigcup\mc A\)
+  implies \(B'\in\mc B\). Then
   \(\plII\win\schStrongSelGame{\mc A}{\mc B}\) if and only if
@@
 \begin{proof}
-  In the proof of Lemma \ref{mainLemma}, \(|\tau(t)|=|\sigma(t)|\).
+  In the proof of Lemma \ref{mainLemma},
+  if the perfect information strategy \(\sigma\) always
+  produces singletons, so does the Markov strategy \(\tau\).
 \end{proof}
@@
 for their helpful comments on the topic of \(C_p(\onePtLind{\omega_1})\).
+The author also thanks the anonymous referree who pointed out
+the game strategies in Proposition \ref{cofinalSequence} could handle all
+subsequences rather than only final sequences, in addition to the
+observation given as the final result of the third section.
 

### 2018-03-27 articles/relating-games-menger-cft-ss/article.tex
add bella notes

@@
 The University of South Alabama,
-Mobile, AL 36606}
-\email{steven.clontz@gmail.com}
+Mobile, AL 36688}
+\email{sclontz@southalabama.edu}
 
@@
 
+At this point, it's worth noting the following open question asked by Angelo Bella
+in personal correspondance with the author. The following
+term is defined in \cite{MR0370506}.
+
+\begin{definition}
+  A space is \term{dense-separable} if every dense subspace is separable.
+\end{definition}
+
+In dense-separable spaces, it is safe to assume the first player
+only chooses countable dense subsets in the \(SS\) and \(CDFT\)
+principles/games.
+
+\begin{question}
+  Suppose \(X\) is a dense-separable space such that every countable dense
+  subspace \(D\subseteq X\) is \(SS^+\). Is \(X\) itself \(SS^+\)?
+\end{question}
+
+Bella noted that this is certainly true for non-strategic \(SS\),
+as verified below. Note the use of knowledge of all \(D_n\) 
+to define \(E_n\) in this proof,
+demonstrating why it cannot be trivially modified to the \(SS^+\) case.
+
+\begin{proposition}
+  Let \(X\) be a dense-separable space such that every countable dense
+  subspace \(D\subseteq X\) is \(SS\). Then \(X\) is \(SS\).
+\end{proposition}
+
+\begin{proof}
+  Take \(\{D_n:n<\omega\}\) with \(D_n\subseteq X\) countable dense,
+  so \(E_n=\bigcup\{D_m:n\leq m<\omega\}\) is countable dense in
+  the \(SS\) subspace \(D=\bigcup\{D_n:n<\omega\}\). So choose \(F_n\in[E_n]^{<\omega}\)
+  with \(cl_D(\bigcup\{F_n:n<\omega\})=D\) and therefore 
+  \(cl(\bigcup\{F_n:n<\omega\})=X\).
+
+  Define \(G_n\in[D_n]^{<\omega}\) by \(G_n=D_n\cap\bigcup\{F_m:m\leq n\}\).
+  The result follows as \(\bigcup\{G_n:n<\omega\}=\bigcup\{F_n:n<\omega\}\).
+\end{proof}
+
 \section{A space which is \(CFT^+\) but not \(CDFT^{\plusMark}\)}
@@
 \end{proof}
+
+\begin{corollary}
+  The following are equivalent for any \(T_{3\frac{1}{2}}\)
+  topological space \(X\).
+    \begin{itemize}
+      \item \(X\) is \(M^+\)
+      \item \(X\) is \(\Omega M^+\)
+      \item \(C_p(X)\) is \(CFT^+\)
+      \item \(C_p(X)\) is \(CDFT^+\)
+    \end{itemize}
+\end{corollary}
 

### 2018-03-27 postdoctoral/go-first.tex

\documentclass{article}
\usepackage{amsmath}
\usepackage{amsthm}
\begin{document}

\begin{theorem}
	Suppose \(T\) be a formula representing a gofirst-fair set of \(n+1\) dice
	extending a formula \(S\) for \(n\) dice such that for each symbol in
	\(T\) representing a face of the extra die, \(S\) restricted below that
	symbol is permutation-fair. Then \(T\) is permutation-fair.
\end{theorem}

\begin{proof}
	Since gofirst-fair implies permutation-fair in the base case of one
	(or two, or zero, whatever) dice, assume the theorem holds for formulas
	\(T\) of length \(n+1\), and let \(T'\) be length \(n+2\) extending \(S'\).
\end{proof}
\end{document}

### 2018-04-15 postdoctoral/go-first.tex
work on gofirst

@@
 \usepackage{amsthm}
+\usepackage{amssymb}
+\newtheorem{theorem}{Theorem}
+\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{proposition}[theorem]{Proposition}
+\theoremstyle{definition}
+\newtheorem{definition}[theorem]{Definition}
+\newcommand{\rest}{\upharpoonright}
+\newcommand{\term}{\textbf}
 \begin{document}
 
+By convention, \(n=\{0,1,\dots,n-1\}\) for each natural number \(n\).
+
+\begin{definition}
+    A function \(F:n\to S\) is called a \term{formula} for a 
+    set \(S\) of dice, where \(F(k)\) returns which die in the set \(S\)
+    has a face with the number \(k<n\).
+\end{definition}
+
+For example, the formula \(F:4\to\{A,B\}\) defined by \(ABBA\)
+represents an assignment of values to the faces of dice in the set \(\{A,B\}\).
+In particular \(A\) has two sides \(\{0,3\}\) while die \(B\) has sides \(\{1,2\}\).
+
+\begin{definition}
+    Given a formula \(F:n\to S\) and \(T\subseteq S\), let \(F_T:m\to T\) be the 
+    \term{subformula} obtained by removing the dice in \(S\setminus T\) from the sequence.
+\end{definition}
+
+So for \(F:7\to\{A,B,C\}\) defined by \(ABCACBA\), \(F_{\{A,C\}}\) is defined by
+\(ACACA\).
+
+\begin{definition}
+    Given a formula \(F:n\to S\) and \(m\leq n\), let \(F\rest m:m\to S\) be the 
+    \term{restriction formula} where \((F\rest m)(k)=F(k)\) for \(k<m\).
+\end{definition}
+
+So for \(F:7\to\{A,B,C\}\) defined by \(ABCACBA\), \(F\rest 4\) is defined by
+\(ABCA\).
+
+\begin{definition}
+    A \term{sample} for a formula \(F:n\to S\) is a function \(f:S\to n\) such
+    that \(F(f(A))=A\) for all \(A\in S\).
+\end{definition}
+
+\begin{definition}
+    The \term{winner} of a given sample is \(A\in S\) such that
+    \(f(A)=\max\{f(B):B\in S\}\).
+\end{definition}
+
+\begin{definition}
+    A formula \(F:n\to S\) is called \term{go-first-fair} if each \(A\in S\)
+    is the winner of an equal number of samples of \(F\).
+\end{definition}
+
+\begin{definition}etc.\end{definition}
+
+\begin{proposition}
+    Suppose \(F:n\to S\) is a permutation-fair (resp. place-fair, go-first-fair)
+    formula. Then \(F_T\) is permutation-fair (resp. place-fair, go-first-fair)
+    for all \(T\subseteq S\).
+\end{proposition}
+
 \begin{theorem}
-	Suppose \(T\) be a formula representing a gofirst-fair set of \(n+1\) dice
-	extending a formula \(S\) for \(n\) dice such that for each symbol in
-	\(T\) representing a face of the extra die, \(S\) restricted below that
-	symbol is permutation-fair. Then \(T\) is permutation-fair.
+    Suppose \(F:n\to S\cup\{X\}\) is a go-first-fair formula such that 
+    for each \(m\leq n\) where \(f(m)=X\), 
+    \((F\rest m)_S\) is permutation-fair.
+    Then \(F\) is permutation-fair.
 \end{theorem}
@@
 \begin{proof}
-	Since gofirst-fair implies permutation-fair in the base case of one
-	(or two, or zero, whatever) dice, assume the theorem holds for formulas
-	\(T\) of length \(n+1\), and let \(T'\) be length \(n+2\) extending \(S'\).
+    Since go-first-fair implies permutation-fair in the base case \(|S|=0\),
+    assume the theorem holds when \(|S|\leq k\), and let \(|S|=k+1\).
+
+    For each \(T\subsetneq S\), we note that \(F_{T\cup\{X\}}\) is a go-first-fair 
+    formula such that for each \(m\leq|F_{T\cup\{X\}}|\) where \(F_{T\cup\{X\}}(m)=X\), 
+    \(F_{T\cup\{X\}}\rest m=F\rest m'\) for some \(m\leq m'< n\) and
+    \(F(m')=X\). Thus \((F_{T\cup\{X\}}\rest m)_T=(F\rest m')_T=((F\rest m')_S)_T\)
+    is permutation-fair, and since \(|T|\leq k\), \(F_{T\cup\{X\}}\) is permutation-fair.
+
 \end{proof}

### 2018-04-15 postdoctoral/go-first.tex
more go-first progress

@@
 \newcommand{\term}{\textbf}
+
+\title{On constructing permutation-fair dice}
+\author{Steven Clontz}
 \begin{document}
+\maketitle
 
@@
 \begin{definition}
-    Given a formula \(F:n\to S\) and \(m\leq n\), let \(F\rest m:m\to S\) be the 
-    \term{restriction formula} where \((F\rest m)(k)=F(k)\) for \(k<m\).
+    Given a sequence \(F:n\to S\) and \(m\leq n\), let \(F\rest m:m\to S\) be the 
+    \term{restriction sequence} where \((F\rest m)(k)=F(k)\) for \(k<m\).
 \end{definition}
@@
 \begin{definition}
-    A \term{sample} for a formula \(F:n\to S\) is a function \(f:S\to n\) such
-    that \(F(f(A))=A\) for all \(A\in S\).
+    A \term{sample} for a formula \(F:n\to S\) is a function \(s:S\to n\) such
+    that \(F(s(A))=A\) for all \(A\in S\). Let \(\sigma (F)\) collect
+    all samples for the formula \(F\).
 \end{definition}
@@
 \begin{definition}
-    The \term{winner} of a given sample is \(A\in S\) such that
-    \(f(A)=\max\{f(B):B\in S\}\).
+    The \term{result} of a sample \(s:S\to n\) is a permutation \(r_s:|S|\to S\)
+    of \(S\) such that \(i\leq j\) if and only if \(f(r_s(i))\leq f(r_s(j))\).
+\end{definition}
+
+So for the formula \(ABCACBA\), a sample might be defined
+by \(f(A)=3,f(B)=2,f(C)=4\), yielding the result \(BAC\).
+Note that the highest-valued die in the sample \(s\) is given by \(r_s(|S|-1)\).
+
+\begin{definition}
+    A formula \(F:n\to S\) is called \term{permutation-fair} if
+    for all permutations \(p,q\) of \(S\),
+    \(|\{s\in\sigma (F):r_s=p\}|=|\{s\in\sigma (F):r_s=q\}|\). 
 \end{definition}
@@
 \begin{definition}
-    A formula \(F:n\to S\) is called \term{go-first-fair} if each \(A\in S\)
-    is the winner of an equal number of samples of \(F\).
+    A formula \(F:n\to S\) is called \term{go-first-fair} if
+    for all \(A,B\in S\),
+    \(|\{s\in\sigma (F):r_s(|S|-1)=A\}|=|\{s\in\sigma (F):r_s(|S|-1)=B\}|\). 
 \end{definition}
 
-\begin{definition}etc.\end{definition}
-
 \begin{proposition}
-    Suppose \(F:n\to S\) is a permutation-fair (resp. place-fair, go-first-fair)
-    formula. Then \(F_T\) is permutation-fair (resp. place-fair, go-first-fair)
+    Suppose \(F:n\to S\) is a permutation-fair (resp. go-first-fair)
+    formula. Then \(F_T\) is permutation-fair (resp. go-first-fair)
     for all \(T\subseteq S\).
@@
     Suppose \(F:n\to S\cup\{X\}\) is a go-first-fair formula such that 
-    for each \(m\leq n\) where \(f(m)=X\), 
+    \(F_S\) is permutation fair, and for each \(m\leq n\) where \(f(m)=X\), 
     \((F\rest m)_S\) is permutation-fair.
@@
 
+    So let \(p,q\) be permutations of \(S\cup\{X\}\); we aim to show that
+    \(|\{s\in\sigma (F):r_s=p\}|=|\{s\in\sigma (F):r_s=q\}|\).
+
+    First, suppose \(p(|S|)=q(|S|)=X\). Thus 
+    \[
+        |\{s\in\sigma (F):r_s=p\}|
+    =
+        \sum\Big\{\Big|\{s\in\sigma ((F\rest m)_S):r_s=p\rest|S|\}\Big|:f(m)=X\Big\}
+    \] 
+    and likewise for \(q\). Since \((F\rest m)_S\) is permutation-fair,
+    \[
+        |\{s\in\sigma ((F\rest m)_S):r_s=p\rest|S|\}|
+    =
+        |\{s\in\sigma ((F\rest m)_S):r_s=q\rest|S|\}|
+    \]
+    so the result follows in this case.
+
 \end{proof}

### 2018-07-06 articles/relating-games-menger-cft-ss/article-zip/article.tex
reorganize article for submission
update zipped article

--- 2018-03-06 articles/relating-games-menger-cft-ss/article.tex
@@
 
+At this point, it's worth noting the following open question asked by Angelo Bella
+in personal correspondance with the author. The following
+term is defined in \cite{MR0370506}.
+
+\begin{definition}
+  A space is \term{dense-separable} if every dense subspace is separable.
+\end{definition}
+
+As noted earlier, all \(SS\) spaces are separable as witnessed
+by choosing \(D_n=X\); in fact, they
+are dense-separable as witnessed by choosing \(D_n=D\) for
+any dense subset \(D\) of \(X\).
+As such, it is safe to assume that the first player
+only chooses countable dense subsets in the \(SS\) and \(CDFT\)
+principles/games.
+
+\begin{question}
+  Suppose \(X\) is a dense-separable space such that every countable dense
+  subspace \(D\subseteq X\) is \(SS^+\). Is \(X\) itself \(SS^+\)?
+\end{question}
+
+Bella noted that this is certainly true for non-strategic \(SS\),
+as shown below.
+Note that the knowledge of all \(D_n\) is used to define \(D\)
+in this proof, preventing a trivial modification to answer the
+above question.
+
+\begin{proposition}\label{ds-ss}
+  Let \(X\) be a dense-separable space such that every countable dense
+  subspace \(D\subseteq X\) is \(SS\). Then \(X\) is \(SS\).
+\end{proposition}
+
+\begin{proof}
+  Take \(\{D_n:n<\omega\}\) with \(D_n\subseteq X\) countable dense in
+  \(X\), and therefore countable dense in the \(SS\) subspace 
+  \(D=\bigcup\{D_n:n<\omega\}\),
+  So choose \(E_n\in[D_n]^{<\omega}\)
+  with \(cl_D(\bigcup\{E_n:n<\omega\})=D\) and therefore 
+  \(cl(\bigcup\{E_n:n<\omega\})\supseteq cl(D)=X\). Thus the \(E_n\)
+  witness that \(X\) is \(SS\). 
+\end{proof}
+
 \section{A space which is \(CFT^+\) but not \(CDFT^{\plusMark}\)}
@@
 
-\begin{theorem}
+\begin{theorem}\label{m-om}
   A topological space is \(M^+\) if and only if it is \(\Omega M^+\).
@@
 for their helpful comments on the topic of \(C_p(\onePtLind{\omega_1})\).
-The author also thanks the anonymous referree who pointed out
-the game strategies in Proposition \ref{cofinalSequence} could handle all
-subsequences rather than only final sequences, in addition to the
-observation given as the final result of the third section.
+The author also thanks the anonymous referee for their helpful suggestions
+to improve Propositions \ref{cofinalSequence} and \ref{ds-ss}, and the observation
+of Theorem \ref{m-om}.
 
 \bibliographystyle{plain}
-\bibliography{../../bibliography}
+\bibliography{bibliography}
 

### 2018-07-07 articles/dual-selection-games/article.tex
add draft of dual selection games (possible) paper

\documentclass{amsart}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}

\usepackage{tikz}
\usetikzlibrary{arrows}

\usepackage{../../clontzDefinitions}

\renewcommand{\vec}{\mathbf}

      \theoremstyle{plain}
      \newtheorem{theorem}{Theorem}
      \newtheorem{lemma}[theorem]{Lemma}
      \newtheorem{corollary}[theorem]{Corollary}
      \newtheorem{proposition}[theorem]{Proposition}
      \newtheorem{conjecture}[theorem]{Conjecture}
      \newtheorem{question}[theorem]{Question}
      \newtheorem{claim}[theorem]{Claim}

      \theoremstyle{definition}
      \newtheorem{definition}[theorem]{Definition}
      \newtheorem{notation}[theorem]{Notation}
      \newtheorem{example}[theorem]{Example}
      \newtheorem{game}[theorem]{Game}

      \theoremstyle{remark}
      \newtheorem{remark}[theorem]{Remark}

      \theoremstyle{plain}
      \newtheorem*{theorem*}{Theorem}
      \newtheorem*{lemma*}{Lemma}
      \newtheorem*{corollary*}{Corollary}
      \newtheorem*{proposition*}{Proposition}
      \newtheorem*{conjecture*}{Conjecture}
      \newtheorem*{question*}{Question}
      \newtheorem*{claim*}{Claim}

      \theoremstyle{definition}
      \newtheorem*{definition*}{Definition}
      \newtheorem*{example*}{Example}
      \newtheorem*{game*}{Game}

      \theoremstyle{remark}
      \newtheorem*{remark*}{Remark}

\begin{document}

\title{Dual selection games}

\author{Steven Clontz}
\address{Department of Mathematics and Statistics,
The University of South Alabama,
Mobile, AL 36688}
\email{sclontz@southalabama.edu}

\keywords{Selection principle, selection game,
limited information strategies}

\subjclass[2010]{54C30, 54D20, 54D45, 91A44}

\begin{abstract}
  (an investigation of dual selection games)
\end{abstract}

\maketitle

\section{Introduction}

\begin{definition}
  The \term{selection game} \(\schStrongSelGame{\mc A}{\mc B}\) 
  is an \(\omega\)-length game involving Players \(\plI\) and \(\plII\). 
  During round \(n\), \(\plI\) chooses
  \(A_n\in\mc A\), followed by \(\plII\) choosing \(B_n\in A_n\).
  Player \(\plII\) wins in the case that \(\{B_n:n<\omega\}\in\mc B\),
  and Player \(\plI\) wins otherwise.
\end{definition}

  For brevity, let 
  \[
    \schStrongSelGame{\mc A}{\neg \mc B}
      =
    \schStrongSelGame{\mc A}{\mc P\left(\bigcup \mc A\right)\setminus \mc B}
  .\]
  That is, \(\plII\) wins in the case that \(\{B_n:n<\omega\}\not\in\mc B\),
  and \(\plI\) wins otherwise.

\begin{definition}
  For a set \(X\), let \(\mathbf C(X)\) be the collection of all
  choice functions on \(X\), functions \(f:X\to\bigcup X\) 
  such that \(f(x)\in x\) for all \(x\in X\).
\end{definition}

\begin{definition}
  The set \(\mc A'\) is said to be a \term{reflection} of the set \(\mc A\)
  if \[\{\ran f:f\in\mathbf C(\mc A')\}=\mc A.\]
\end{definition}

  For example, a reflection of the collection \(\mc O_X\) of basic open covers
  of \(X\) would be \(\mc P_X=\{\mc T_{X,x}:x\in X\}\), where \(\mc T_{X,x}\) 
  is the corresponding point-base at \(x\in X\). 
  Likewise for the collection \(\Omega_{X,x}\)
  of sets with \(x\in X\) as a limit point, \(\mc T_{X,x}\) is itself
  a reflection.

\begin{theorem}
  Let \(\mc A'\) be a reflection of \(\mc A\).

  Then
  \(\plI\prewin\schStrongSelGame{\mc A}{\mc B}\) if and only if
  \(\plII\markwin\schStrongSelGame{\mc A'}{\neg\mc B}\).
\end{theorem}

\begin{proof}
  Let \(\sigma\) witness 
  \(\plI\prewin\schStrongSelGame{\mc A}{\mc B}\).
  Since \(\sigma(n)\in\mc A\), \(\sigma(n)=\ran{f_n}\)
  for some \(f_n\in\mathbf C(\mc A')\). So let
  \(\tau(A,n)=f_n(A)\) for all \(A\in \mc A'\) and \(n<\omega\).
  Suppose \(A_n\in \mc A'\) for all \(n<\omega\).
  Note that since \(\sigma\) is winning and 
  \(\tau(A_n,n)=f_n(A_n)\in\ran{f_n}=\sigma(n)\),
  \(\{\tau(A_n,n):n<\omega\}\not\in\mc B\). Thus \(\tau\) witnesses
  \(\plII\markwin\schStrongSelGame{\mc A'}{\neg\mc B}\).

  Now let \(\sigma\) witness
  \(\plII\markwin\schStrongSelGame{\mc A'}{\neg\mc B}\).
  Let \(f_n\in\mathbf C(\mc A')\) be defined by \(f_n(A)=\sigma(A,n)\).
  Since \(\mc A=\{\ran f:f\in\mathbf C(\mc A')\}\), let
  \(\tau(n)=\ran{f_n}\). Suppose that \(B_n\in\tau(n)=\ran{f_n}\) for
  all \(n<\omega\). Choose \(A_n\in\mc A'\) such that 
  \(B_n=f_n(A_n)=\sigma(A_n,n)\). Since \(\sigma\) is winning,
  \(\{B_n:n<\omega\}\not\in\mc B\). Thus \(\tau\) witnesses
  \(\plI\prewin\schStrongSelGame{\mc A}{\mc B}\).
\end{proof}

\bibliographystyle{plain}
\bibliography{../../bibliography}

\end{document}

### 2018-07-09 articles/dual-selection-games/article.tex
start adding perfect info results

@@
 \begin{definition}
-  The set \(\mc A'\) is said to be a \term{reflection} of the set \(\mc A\)
-  if \[\{\ran f:f\in\mathbf C(\mc A')\}=\mc A.\]
+  The set \(\mc R\) is said to be a \term{reflection} of the set \(\mc A\)
+  if \[\mc A= \{\ran f:f\in\mathbf C(\mc R)\}.\]
 \end{definition}
@@
 
+\begin{lemma}
+  Let \(\mc R\) be a reflection of \(\mc A\). Then \(\bigcup \mc R=\bigcup \mc A\).
+\end{lemma}
+\begin{proof}
+  If \(x\in \bigcup\mc A\), then \(x\in\ran{f}\) for some \(f\in\mathbf C(\mc R)\).
+  Thus \(x=f(R)\in R\) for some \(R\in\mc R\), showing \(x\in\bigcup\mc R\).
+
+  Likewise if \(x\in\bigcup\mc R\), so \(x\in R\) for some \(R\in \mc R\).
+  Let \(f\in\mathbf C(\mc R)\) satisfy \(f(R)=x\), so \(x\in\ran{f}\),
+  showing \(x\in\bigcup\mc A\).
+\end{proof}
+
 \begin{theorem}
-  Let \(\mc A'\) be a reflection of \(\mc A\).
+  Let \(\mc R\) be a reflection of \(\mc A\).
 
@@
   \(\plI\prewin\schStrongSelGame{\mc A}{\mc B}\) if and only if
-  \(\plII\markwin\schStrongSelGame{\mc A'}{\neg\mc B}\).
+  \(\plII\markwin\schStrongSelGame{\mc R}{\neg\mc B}\).
 \end{theorem}
@@
   \(\plI\prewin\schStrongSelGame{\mc A}{\mc B}\).
-  Since \(\sigma(n)\in\mc A\), \(\sigma(n)=\ran{f_n}\)
-  for some \(f_n\in\mathbf C(\mc A')\). So let
-  \(\tau(A,n)=f_n(A)\) for all \(A\in \mc A'\) and \(n<\omega\).
-  Suppose \(A_n\in \mc A'\) for all \(n<\omega\).
+  Since \(\sigma(n)\in\mc A=\{\ran{f}:f\in\mathbf C(\mc R)\}\), 
+  \(\sigma(n)=\ran{f_n}\)
+  for some \(f_n\in\mathbf C(\mc R)\). So let
+  \(\tau(R,n)=f_n(R)\) for all \(R\in \mc R\) and \(n<\omega\).
+  Suppose \(R_n\in \mc R\) for all \(n<\omega\).
   Note that since \(\sigma\) is winning and 
-  \(\tau(A_n,n)=f_n(A_n)\in\ran{f_n}=\sigma(n)\),
-  \(\{\tau(A_n,n):n<\omega\}\not\in\mc B\). Thus \(\tau\) witnesses
-  \(\plII\markwin\schStrongSelGame{\mc A'}{\neg\mc B}\).
+  \(\tau(R_n,n)=f_n(R_n)\in\ran{f_n}=\sigma(n)\),
+  \(\{\tau(R_n,n):n<\omega\}\not\in\mc B\). Thus \(\tau\) witnesses
+  \(\plII\markwin\schStrongSelGame{\mc R}{\neg\mc B}\).
 
   Now let \(\sigma\) witness
-  \(\plII\markwin\schStrongSelGame{\mc A'}{\neg\mc B}\).
-  Let \(f_n\in\mathbf C(\mc A')\) be defined by \(f_n(A)=\sigma(A,n)\).
-  Since \(\mc A=\{\ran f:f\in\mathbf C(\mc A')\}\), let
+  \(\plII\markwin\schStrongSelGame{\mc R}{\neg\mc B}\).
+  Let \(f_n\in\mathbf C(\mc R)\) be defined by \(f_n(R)=\sigma(R,n)\).
+  Since \(\tau(n)\in\mc A=\{\ran f:f\in\mathbf C(\mc R)\}\), let
   \(\tau(n)=\ran{f_n}\). Suppose that \(B_n\in\tau(n)=\ran{f_n}\) for
-  all \(n<\omega\). Choose \(A_n\in\mc A'\) such that 
-  \(B_n=f_n(A_n)=\sigma(A_n,n)\). Since \(\sigma\) is winning,
+  all \(n<\omega\). Choose \(R_n\in\mc R\) such that 
+  \(B_n=f_n(R_n)=\sigma(R_n,n)\). Since \(\sigma\) is winning,
   \(\{B_n:n<\omega\}\not\in\mc B\). Thus \(\tau\) witnesses
   \(\plI\prewin\schStrongSelGame{\mc A}{\mc B}\).
+\end{proof}
+
+\begin{theorem}
+  Let \(\mc R\) be a reflection of \(\mc A\).
+
+  Then
+  \(\plII\markwin\schStrongSelGame{\mc A}{\mc B}\) if and only if
+  \(\plI\prewin\schStrongSelGame{\mc R}{\neg\mc B}\).
+\end{theorem}
+
+\begin{proof}
+  Let \(\sigma\) witness 
+  \(\plII\markwin\schStrongSelGame{\mc A}{\mc B}\).
+  Let \(n<\omega\). Suppose that for each \(R\in\mc R\),
+  there was \(g(R)\in R\) such that for all \(A\in \mc A\),
+  \(\sigma(A,n)\not=g(R)\). Then \(g\in\mathbf C(\mc R)\),
+  and \(\sigma(\ran g,n)\not=g(R)\) for all \(R\in\mc R\),
+  a contradiction.
+
+  So choose \(\tau(n)\in\mc R\) such that for all \(r\in \tau(n)\)
+  there exists \(A_{r,n}\in\mc A\) such that \(\sigma(A_{r,n},n)=r\).
+  It follows that when \(r_n\in\tau(n)\) for \(n<\omega\),
+  \(\{r_n:n<\omega\}=\{\sigma(A_{r_n,n}:n<\omega\}\in B\),
+  so \(\tau\) witnesses
+  \(\plI\prewin\schStrongSelGame{\mc R}{\neg\mc B}\).
+
+  Now let \(\sigma\) witness 
+  \(\plI\prewin\schStrongSelGame{\mc R}{\neg\mc B}\).
+  Then \(\sigma(n)\in\mc R\), so for \(A\in\mc A\), let
+  \(f_A\in\mathbf C(\mc R)\) satisfy \(A=\ran{f_A}\),
+  and let \(\tau(A,n)=f_A(\sigma(n))\).
+  Then if \(A_n\in\mc A\) for \(n<\omega\), \(\tau(A_n,n)\in\sigma(n)\),
+  so \(\{\tau(A_n,n):n<\omega\}\in\mc B\).
+  Thus \(\tau\) witnesses
+  \(\plII\markwin\schStrongSelGame{\mc A}{\mc B}\).
+\end{proof}
+
+\begin{theorem}
+  Let \(\mc R\) be a reflection of \(\mc A\).
+
+  Then
+  \(\plI\win\schStrongSelGame{\mc A}{\mc B}\) if and only if
+  \(\plII\win\schStrongSelGame{\mc R}{\neg\mc B}\).
+\end{theorem}
+
+\begin{proof}
+  Let \(\sigma\) witness 
+  \(\plI\win\schStrongSelGame{\mc A}{\mc B}\).
+  Let \(c(\emptyset)=\emptyset\). Suppose 
+  \(c(s)\in(\bigcup A)^{<\omega}=(\bigcup R)^{<\omega}\)
+  is defined for \(s\in\mc R^{<\omega}\). Since \(\sigma(c(s))\in\mc A\),
+  let \(f_s\in\mathbf C(\mc R)\) satisfy \(\sigma(c(s))=\ran{f_s}\),
+  and let \(c(s\concat\<R\>)=c(s)\concat\<f_s(R)\>\).
+  Then let \(c(\alpha)=\bigcup\{c(\alpha\rest n):n<\omega\}\)
+  for \(\alpha\in\mc R^\omega\), so
+  \[
+    c(\alpha)(n)
+      =
+    f_{\alpha\rest n}(\alpha(n))
+      \in
+    \ran{f_{\alpha\rest n}}
+      =
+    \sigma(c(\alpha\rest n))
+  \]
+  demonstrating that \(c(\alpha)\) is a legal attack against \(\sigma\).
+
+  Let \(\tau(s\concat\<R\>)=f_s(R)\). Consider the attack \(\alpha\in\mc R^\omega\)
+  against \(\tau\). Then since \(\sigma\) is winning and
+  \(
+    \tau(\alpha\rest n+1)=f_{\alpha\rest n}(\alpha(n))\in
+    \ran{f_{\alpha\rest n}}=\sigma(c(\alpha\rest n))
+  \), it follows that \(\{\tau(\alpha\rest n+1):n<\omega\}\not\in\mc B\).
+  Thus \(\tau\) witnesses
+  \(\plII\win\schStrongSelGame{\mc R}{\neg\mc B}\).
+
+%  Now let \(\sigma\) witness
+%  \(\plII\markwin\schStrongSelGame{\mc R}{\neg\mc B}\).
+%  Let \(f_n\in\mathbf C(\mc R)\) be defined by \(f_n(R)=\sigma(R,n)\).
+%  Since \(\tau(n)\in\mc A=\{\ran f:f\in\mathbf C(\mc R)\}\), let
+%  \(\tau(n)=\ran{f_n}\). Suppose that \(B_n\in\tau(n)=\ran{f_n}\) for
+%  all \(n<\omega\). Choose \(R_n\in\mc R\) such that 
+%  \(B_n=f_n(R_n)=\sigma(R_n,n)\). Since \(\sigma\) is winning,
+%  \(\{B_n:n<\omega\}\not\in\mc B\). Thus \(\tau\) witnesses
+%  \(\plI\prewin\schStrongSelGame{\mc A}{\mc B}\).
 \end{proof}

### 2018-07-11 articles/dual-selection-games/article.tex
half of the perfect info result

@@
 
-%  Now let \(\sigma\) witness
-%  \(\plII\markwin\schStrongSelGame{\mc R}{\neg\mc B}\).
-%  Let \(f_n\in\mathbf C(\mc R)\) be defined by \(f_n(R)=\sigma(R,n)\).
-%  Since \(\tau(n)\in\mc A=\{\ran f:f\in\mathbf C(\mc R)\}\), let
-%  \(\tau(n)=\ran{f_n}\). Suppose that \(B_n\in\tau(n)=\ran{f_n}\) for
-%  all \(n<\omega\). Choose \(R_n\in\mc R\) such that 
-%  \(B_n=f_n(R_n)=\sigma(R_n,n)\). Since \(\sigma\) is winning,
-%  \(\{B_n:n<\omega\}\not\in\mc B\). Thus \(\tau\) witnesses
-%  \(\plI\prewin\schStrongSelGame{\mc A}{\mc B}\).
+  Now let \(\sigma\) witness
+  \(\plII\win\schStrongSelGame{\mc R}{\neg\mc B}\).
+  For \(s\in \mc R^{<\omega}\), define \(f_s\in\mathbf C(\mc R)\)
+  by \(f_s(R)=\sigma(s\concat\<R\>)\). Let \(\tau(\emptyset)=\ran{f_\emptyset}\),
+  and for \(x\in\tau(\emptyset)\), choose \(R_{\<x\>}\in\mc R\) such that
+  \(x=f_{\emptyset}(R_{\<x\>})\) (for other \(x\in\bigcup A\), choose \(R_{\<x\>}\)
+  arbitrarily as it won't be used). Now let \(s\in(\bigcup A)^{<\omega}\setminus\emptyset\),
+  and suppose \(\tau(s\rest n)\in\mc A\) and \(R_{s\rest n+1}\in\mc R\) have been
+  defined for \(n<|s|\). Then let \(\tau(s)=\ran{f_{\<R_{s\rest 0},\dots,R_s\>}}\)
+  and for \(x\in\tau(s)\) choose \(R_{s\concat\<x\>}\) such that
+  \(x=f_{\<R_{s\rest 0},\dots,R_s\>}(R_{s\concat\<x\>})\) (and again,
+  choose \(R_{s\concat\<x\>}\) arbitrarily for other \(x\in\bigcup\mc A\) as it won't be used).
+
+  Then let \(\alpha\) attack \(\tau\), so
+  \(\alpha(n)\in\tau(\alpha\rest n)\) and thus 
+  \(\alpha(n)=f_{\<R_{\alpha\rest 0},\dots,R_{\alpha\rest n}\>}(R_{\alpha\rest n+1})
+  =\sigma(\<R_{\alpha\rest 0},\dots,R_{\alpha\rest n+1}\>)\).  Since \(\sigma\) is winning,
+  \(\{\sigma(\<R_{\alpha\rest 0},\dots,R_{\alpha\rest n+1}\>):n<\omega\}
+  =\{\alpha(n):n<\omega\}\not\in\mc B\).
+  Thus \(\tau\) witnesses
+  \(\plI\win\schStrongSelGame{\mc A}{\mc B}\).
 \end{proof}

### 2018-07-12 articles/dual-selection-games/article.tex
finish perfect info results

@@
 
+\begin{theorem}
+  Let \(\mc R\) be a reflection of \(\mc A\).
+
+  Then
+  \(\plII\win\schStrongSelGame{\mc A}{\mc B}\) if and only if
+  \(\plI\win\schStrongSelGame{\mc R}{\neg\mc B}\).
+\end{theorem}
+
+\begin{proof}
+  Let \(\sigma\) witness 
+  \(\plII\win\schStrongSelGame{\mc A}{\mc B}\).
+  Let \(s\in(\bigcup R)^{<\omega}\) and assume \(a(s)\in\mc A^{|s|}\) is defined
+  (of course, \(a(\emptyset)=\emptyset\)).
+  Suppose for all \(R\in\mc R\) there existed \(f(R)\in R\) such that for all
+  \(A\in\mc A\), \(\sigma(a(s)\concat\<A\>)\not=f(R)\). Then 
+  \(\sigma(a(s)\concat\<\ran{f}\>)\not=f(R)\) for all \(R\in\mc R\), a contradiction.
+  So let \(\tau(s)\in\mc R\) satisfy for all \(x\in\tau(s)\) there exists
+  \(a(s\concat\<x\>)\in\mc A^{|s|+1}\) extending \(a(s)\) such that 
+  \(x=\sigma(a(s\concat\<x\>))\).
+
+  If \(\tau\) is attacked by \(\alpha\in(\bigcup R)^\omega\), then 
+  \(\alpha(n)\in\tau(\alpha\rest n)\). So \(\alpha(n)=\sigma(a(\alpha\rest n+1))\),
+  and since \(\sigma\) is winning, 
+  \(\{\sigma(a(\alpha\rest n+1)):n<\omega\}=\{\alpha(n):n<\omega\}\in\mc B\).
+  Therefore \(\tau\) witnesses
+  \(\plI\win\schStrongSelGame{\mc R}{\neg\mc B}\).
+
+  Now let \(\sigma\) witness
+  \(\plI\win\schStrongSelGame{\mc R}{\neg\mc B}\).
+  Let \(s\in\mc A^{<\omega}\), and suppose \(c(s)\in(\bigcup \mc R)^{|s|}\) is defined
+  (again, \(c(\emptyset)=\emptyset\)). Let \(\tau(s\concat\<\ran{f}\>)=f(\sigma(c(s)))\),
+  and let \(c(s\concat\<\ran f\>)\) extend \(c(s)\) by letting
+  \(c(s\concat\<\ran f\>)(|s|)=\tau(s\concat\<\ran f\>)\).
+
+  If \(\tau\) is attacked by \(\alpha\in\mc A^\omega\), where \(\alpha(n)=\ran{f_n}\)
+  for \(n<\omega\), then since \(\tau(\alpha\rest n+1)\in\sigma(c(\alpha\rest n))\)
+  and \(\sigma\) is winning, we conclude that 
+  \(\{\tau(\alpha\rest n+1):n<\omega\}\in\mc B\).
+  Therefore \(\tau\) witnesses
+  \(\plII\win\schStrongSelGame{\mc A}{\mc B}\).
+\end{proof}
+
 \bibliographystyle{plain}

### 2018-07-15 articles/dual-selection-games/article.tex
add abstract, define dual

@@
 \begin{abstract}
-  (an investigation of dual selection games)
+  Often, selection games have dual games for which a winning
+  strategy for a player in one game may be used to create
+  a winning strategy 
+  For example, the Rothberger selection game involving open covers
+  is dual to the point-open game. This extends to a general
+  theorem: if \(\mc A=\{\ran{f}:f\in\mathbf C(\mc R)\}\)
+  where \(\mathbf C(\mc R)=\{f\in(\bigcup\mc R)^{\mc R}:R\in\mc R\Rightarrow f(R)\in R\}\) 
+  collects the choice functions on the set \(\mc R\),
+  then \(G_1(\mc A,\mc B)\) and \(G_1(\mc R,\neg\mc B)\)
+  are dual selection games. 
 \end{abstract}
@@
 \begin{definition}
-  For a set \(X\), let \(\mathbf C(X)\) be the collection of all
-  choice functions on \(X\), functions \(f:X\to\bigcup X\) 
-  such that \(f(x)\in x\) for all \(x\in X\).
+  For a set \(X\), let \(\mathbf C(X)=\{f\in(\bigcup X)^X:x\in X\Rightarrow f(x)\in x\}\)
+  be the collection of all choice functions on \(X\).
 \end{definition}
@@
 
-  For example, a reflection of the collection \(\mc O_X\) of basic open covers
-  of \(X\) would be \(\mc P_X=\{\mc T_{X,x}:x\in X\}\), where \(\mc T_{X,x}\) 
-  is the corresponding point-base at \(x\in X\). 
-  Likewise for the collection \(\Omega_{X,x}\)
-  of sets with \(x\in X\) as a limit point, \(\mc T_{X,x}\) is itself
-  a reflection.
+As we will see, reflections of selection sets are used frequently (but implicitly) 
+throughout the literature to define dual selection games.
 
-\begin{lemma}
+%  For example, a reflection of the collection \(\mc O_X\) of basic open covers
+%  of \(X\) would be \(\mc P_X=\{\mc T_{X,x}:x\in X\}\), where \(\mc T_{X,x}\) 
+%  is the corresponding point-base at \(x\in X\). 
+%  Likewise for the collection \(\Omega_{X,x}\)
+%  of sets with \(x\in X\) as a limit point, \(\mc T_{X,x}\) is itself
+%  a reflection.
+
+\section{Main Results}
+
+\begin{proposition}
   Let \(\mc R\) be a reflection of \(\mc A\). Then \(\bigcup \mc R=\bigcup \mc A\).
-\end{lemma}
+\end{proposition}
 \begin{proof}
@@
 \end{proof}
+
+The following four theorems demonstrate that reflections characterize
+dual selection games for both perfect information strategies and
+certain limited information strategies.
+
+\begin{definition}
+  A pair of games \(G(X),H(X)\) are \term{Markov information dual} if both
+  of the following hold.
+  \begin{itemize}
+    \item \(I\prewin G(X)\) if and only if \(II\markwin H(X)\).
+    \item \(II\markwin G(X)\) if and only if \(I\prewin H(X)\).
+  \end{itemize}
+\end{definition}
 
@@
   It follows that when \(r_n\in\tau(n)\) for \(n<\omega\),
-  \(\{r_n:n<\omega\}=\{\sigma(A_{r_n,n}:n<\omega\}\in B\),
+  \(\{r_n:n<\omega\}=\{\sigma(A_{r_n,n}):n<\omega\}\in B\),
   so \(\tau\) witnesses
@@
 \end{proof}
+
+\begin{definition}
+  A pair of games \(G(X),H(X)\) are \term{perfect information dual} if both
+  of the following hold.
+  \begin{itemize}
+    \item \(I\win G(X)\) if and only if \(II\win H(X)\).
+    \item \(II\win G(X)\) if and only if \(I\win H(X)\).
+  \end{itemize}
+\end{definition}
 
@@
 
+\begin{corollary}
+  If \(\mc R\) is a reflection of \(\mc A\),
+  then \(\schStrongSelGame{\mc A}{\mc B}\) and \(\schStrongSelGame{\mc R}{\neg\mc B}\)
+  are both perfect information dual and Markov information dual.
+\end{corollary}
+
 \bibliographystyle{plain}

### 2018-07-17 articles/dual-selection-games/article.tex
start revising to use coinitial reflections

@@
   is dual to the point-open game. This extends to a general
-  theorem: if \(\mc A=\{\ran{f}:f\in\mathbf C(\mc R)\}\)
+  theorem: if \(\{\ran{f}:f\in\mathbf C(\mc R)\}\) is coinitial in \(\mc A\)
+  with respect to \(\subseteq\),
   where \(\mathbf C(\mc R)=\{f\in(\bigcup\mc R)^{\mc R}:R\in\mc R\Rightarrow f(R)\in R\}\) 
@@
 \begin{definition}
+  Write \(X\preceq Y\) if \(X\) is coinitial in \(Y\) with respect to \(\subseteq\);
+  that is, \(X\subseteq Y\), and for all \(y\in Y\), there exists \(x\in X\) such that 
+  \(x\subseteq y\).
+\end{definition}
+
+\begin{definition}
   The set \(\mc R\) is said to be a \term{reflection} of the set \(\mc A\)
-  if \[\mc A= \{\ran f:f\in\mathbf C(\mc R)\}.\]
+  if \[\{\ran f:f\in\mathbf C(\mc R)\}\preceq\mc A.\]
 \end{definition}
@@
 
-\begin{proposition}
-  Let \(\mc R\) be a reflection of \(\mc A\). Then \(\bigcup \mc R=\bigcup \mc A\).
-\end{proposition}
-\begin{proof}
-  If \(x\in \bigcup\mc A\), then \(x\in\ran{f}\) for some \(f\in\mathbf C(\mc R)\).
-  Thus \(x=f(R)\in R\) for some \(R\in\mc R\), showing \(x\in\bigcup\mc R\).
-
-  Likewise if \(x\in\bigcup\mc R\), so \(x\in R\) for some \(R\in \mc R\).
-  Let \(f\in\mathbf C(\mc R)\) satisfy \(f(R)=x\), so \(x\in\ran{f}\),
-  showing \(x\in\bigcup\mc A\).
-\end{proof}
+%\begin{proposition}
+%  Let \(\mc R\) be a reflection of \(\mc A\). Then \(\bigcup \mc R=\bigcup \mc A\).
+%\end{proposition}
+%\begin{proof}
+%  If \(x\in \bigcup\mc A\), then \(x\in\ran{f}\) for some \(f\in\mathbf C(\mc R)\).
+%  Thus \(x=f(R)\in R\) for some \(R\in\mc R\), showing \(x\in\bigcup\mc R\).
+%
+%  Likewise if \(x\in\bigcup\mc R\), so \(x\in R\) for some \(R\in \mc R\).
+%  Let \(f\in\mathbf C(\mc R)\) satisfy \(f(R)=x\), so \(x\in\ran{f}\),
+%  showing \(x\in\bigcup\mc A\).
+%\end{proof}
 
@@
   \(\plI\prewin\schStrongSelGame{\mc A}{\mc B}\).
-  Since \(\sigma(n)\in\mc A=\{\ran{f}:f\in\mathbf C(\mc R)\}\), 
-  \(\sigma(n)=\ran{f_n}\)
+  Since \(\sigma(n)\in\mc A\),
+  \(\ran{f_n}\subseteq\sigma(n)\)
   for some \(f_n\in\mathbf C(\mc R)\). So let
@@
   Note that since \(\sigma\) is winning and 
-  \(\tau(R_n,n)=f_n(R_n)\in\ran{f_n}=\sigma(n)\),
+  \(\tau(R_n,n)=f_n(R_n)\in\ran{f_n}\subseteq\sigma(n)\),
   \(\{\tau(R_n,n):n<\omega\}\not\in\mc B\). Thus \(\tau\) witnesses
@@
   \(\plII\markwin\schStrongSelGame{\mc R}{\neg\mc B}\).
-  Let \(f_n\in\mathbf C(\mc R)\) be defined by \(f_n(R)=\sigma(R,n)\).
-  Since \(\tau(n)\in\mc A=\{\ran f:f\in\mathbf C(\mc R)\}\), let
-  \(\tau(n)=\ran{f_n}\). Suppose that \(B_n\in\tau(n)=\ran{f_n}\) for
+  Let \(f_n\in\mathbf C(\mc R)\) be defined by \(f_n(R)=\sigma(R,n)\),
+  and let \(\tau(n)=\ran{f_n}\in\mc A\). 
+  Suppose that \(B_n\in\tau(n)=\ran{f_n}\) for
   all \(n<\omega\). Choose \(R_n\in\mc R\) such that 
@@
 
+\section{Acknowledgements}
+
+Thanks to Prof. Jared Holshouser for his input during the writing of these results.
+
 \bibliographystyle{plain}

### 2018-07-18 articles/dual-selection-games/article.tex
fix results to use selection basis

@@
 \begin{abstract}
-  Often, selection games have dual games for which a winning
-  strategy for a player in one game may be used to create
-  a winning strategy 
+  Often, a given selection game studied in the literature has
+  a known dual game. In dual games, a winning
+  strategy for a player in either game may be used to create
+  a winning strategy for the opponent in the dual. 
   For example, the Rothberger selection game involving open covers
@@
   \(x\subseteq y\).
+
+  In the context of selection games, we will say \(\mc A'\) is a \term{selection basis}
+  for \(\mc A\) when \(\mc A'\preceq \mc A\).
 \end{definition}
@@
   The set \(\mc R\) is said to be a \term{reflection} of the set \(\mc A\)
-  if \[\{\ran f:f\in\mathbf C(\mc R)\}\preceq\mc A.\]
+  if \[\{\ran f:f\in\mathbf C(\mc R)\}\] is a selection basis for \(\mc A\).
 \end{definition}
@@
   there was \(g(R)\in R\) such that for all \(A\in \mc A\),
-  \(\sigma(A,n)\not=g(R)\). Then \(g\in\mathbf C(\mc R)\),
-  and \(\sigma(\ran g,n)\not=g(R)\) for all \(R\in\mc R\),
+  \(\sigma(A,n)\not=g(R)\). Then \(g\in\mathbf C(\mc R)\)
+  and \(\ran g\in\mc A\),
+  thus \(\sigma(\ran g,n)\not=g(R)\) for all \(R\in\mc R\),
   a contradiction.
@@
   Then \(\sigma(n)\in\mc R\), so for \(A\in\mc A\), let
-  \(f_A\in\mathbf C(\mc R)\) satisfy \(A=\ran{f_A}\),
-  and let \(\tau(A,n)=f_A(\sigma(n))\).
+  \(f_A\in\mathbf C(\mc R)\) satisfy \(\ran{f_A}\subseteq A\),
+  and let \(\tau(A,n)=f_A(\sigma(n))\in A\cap\sigma(n)\).
   Then if \(A_n\in\mc A\) for \(n<\omega\), \(\tau(A_n,n)\in\sigma(n)\),
@@
   Let \(c(\emptyset)=\emptyset\). Suppose 
-  \(c(s)\in(\bigcup A)^{<\omega}=(\bigcup R)^{<\omega}\)
+  \(c(s)\in(\bigcup A)^{<\omega}\)
   is defined for \(s\in\mc R^{<\omega}\). Since \(\sigma(c(s))\in\mc A\),
-  let \(f_s\in\mathbf C(\mc R)\) satisfy \(\sigma(c(s))=\ran{f_s}\),
+  let \(f_s\in\mathbf C(\mc R)\) satisfy \(\ran{f_s}\subseteq\sigma(c(s))\),
   and let \(c(s\concat\<R\>)=c(s)\concat\<f_s(R)\>\).
@@
     \ran{f_{\alpha\rest n}}
-      =
+      \subseteq
     \sigma(c(\alpha\rest n))
@@
     \tau(\alpha\rest n+1)=f_{\alpha\rest n}(\alpha(n))\in
-    \ran{f_{\alpha\rest n}}=\sigma(c(\alpha\rest n))
+    \ran{f_{\alpha\rest n}}\subseteq\sigma(c(\alpha\rest n))
   \), it follows that \(\{\tau(\alpha\rest n+1):n<\omega\}\not\in\mc B\).
@@
   For \(s\in \mc R^{<\omega}\), define \(f_s\in\mathbf C(\mc R)\)
-  by \(f_s(R)=\sigma(s\concat\<R\>)\). Let \(\tau(\emptyset)=\ran{f_\emptyset}\),
+  by \(f_s(R)=\sigma(s\concat\<R\>)\). Let \(\tau(\emptyset)=\ran{f_\emptyset}\in\mc A\),
   and for \(x\in\tau(\emptyset)\), choose \(R_{\<x\>}\in\mc R\) such that
   \(x=f_{\emptyset}(R_{\<x\>})\) (for other \(x\in\bigcup A\), choose \(R_{\<x\>}\)
-  arbitrarily as it won't be used). Now let \(s\in(\bigcup A)^{<\omega}\setminus\emptyset\),
-  and suppose \(\tau(s\rest n)\in\mc A\) and \(R_{s\rest n+1}\in\mc R\) have been
-  defined for \(n<|s|\). Then let \(\tau(s)=\ran{f_{\<R_{s\rest 0},\dots,R_s\>}}\)
-  and for \(x\in\tau(s)\) choose \(R_{s\concat\<x\>}\) such that
-  \(x=f_{\<R_{s\rest 0},\dots,R_s\>}(R_{s\concat\<x\>})\) (and again,
-  choose \(R_{s\concat\<x\>}\) arbitrarily for other \(x\in\bigcup\mc A\) as it won't be used).
+  arbitrarily as it won't be used). Now let \(s\in(\bigcup A)^{<\omega}\),
+  and suppose \(R_{s\rest n\concat\<x\>}\in\mc R\) has been defined for
+  \(n\leq|s|\) and \(x\in\bigcup A\). 
+  Then let \(\tau(s\concat\<x\>)=\ran{f_{\<R_{s\rest 0},\dots,R_s,R_{s\concat\<x\>}\>}}\)
+  and for \(y\in\tau(s)\) choose \(R_{s\concat\<x,y\>}\) such that
+  \(x=f_{\<R_{s\rest 0},\dots,R_s,R_{s\concat\<x\>}\>}(R_{s\concat\<x,y\>})\) (and again,
+  choose \(R_{s\concat\<x,y\>}\) arbitrarily for other \(y\in\bigcup\mc A\) as it won't be used).
 
@@
   \(\plII\win\schStrongSelGame{\mc A}{\mc B}\).
-  Let \(s\in(\bigcup R)^{<\omega}\) and assume \(a(s)\in\mc A^{|s|}\) is defined
+  Let \(s\in(\bigcup A)^{<\omega}\) and assume \(a(s)\in\mc A^{|s|}\) is defined
   (of course, \(a(\emptyset)=\emptyset\)).
@@
   \(A\in\mc A\), \(\sigma(a(s)\concat\<A\>)\not=f(R)\). Then
+  \(f\in\mathbf C(\mc R)\) and \(\ran{f}\in\mc A\), and thus 
   \(\sigma(a(s)\concat\<\ran{f}\>)\not=f(R)\) for all \(R\in\mc R\), a contradiction.
@@
   \(\plI\win\schStrongSelGame{\mc R}{\neg\mc B}\).
-  Let \(s\in\mc A^{<\omega}\), and suppose \(c(s)\in(\bigcup \mc R)^{|s|}\) is defined
-  (again, \(c(\emptyset)=\emptyset\)). Let \(\tau(s\concat\<\ran{f}\>)=f(\sigma(c(s)))\),
-  and let \(c(s\concat\<\ran f\>)\) extend \(c(s)\) by letting
-  \(c(s\concat\<\ran f\>)(|s|)=\tau(s\concat\<\ran f\>)\).
+  Let \(s\in\mc A^{<\omega}\), and suppose \(r(s)\in(\bigcup \mc R)^{|s|}\) is defined
+  (again, \(r(\emptyset)=\emptyset\)). For \(A\in\mc A\) choose \(f_A\in\mathbf C(\mc R)\)
+  where \(\ran{f_A}\subseteq A\), and let \(\tau(s\concat\<A\>)=f_A(\sigma(r(s)))\),
+  and let \(r(s\concat\<A\>)\) extend \(r(s)\) by letting
+  \(r(s\concat\<A\>)(|s|)=\tau(s\concat\<A\>)\).
 
-  If \(\tau\) is attacked by \(\alpha\in\mc A^\omega\), where \(\alpha(n)=\ran{f_n}\)
-  for \(n<\omega\), then since \(\tau(\alpha\rest n+1)\in\sigma(c(\alpha\rest n))\)
-  and \(\sigma\) is winning, we conclude that 
+  If \(\tau\) is attacked by \(\alpha\in\mc A^\omega\), 
+  then since \(\tau(\alpha\rest n+1)=f_{\alpha(n)}(\sigma(r(\alpha\rest n))\in\alpha(n)\cap\sigma(r(\alpha\rest n))\)
+  and \(\sigma\) is winning, we conclude that \(\tau\) is a legal strategy and
   \(\{\tau(\alpha\rest n+1):n<\omega\}\in\mc B\).

### 2018-07-20 articles/dual-selection-games/article.tex
lots of reflections

@@
 \begin{definition}
+  An \term{\(\omega\)-length game} is a pair \(G=\<M,W\>\) such that
+  \(W\subseteq M^\omega\). The set \(M\) is the \term{moveset} of the game,
+  and the set \(W\) is the \term{payoff set} for the second player.
+\end{definition}
+
+In such a game \(G\), players \(\plI\) and \(\plII\) alternate making choices
+\(a_n\in M\) and \(b_n\in M\) during each round \(n<\omega\), 
+and \(\plII\) wins the game if and only if \(\<a_0,b_0,a_1,b_1,\dots\>\in W\).
+
+Often when defining games, \(\plI\) and \(\plII\) are restricted to choosing
+from different movesets \(A,B\). Of course, this can be modeled with \(\<M,W\>\)
+by simply letting \(M=A\cup B\) and adding/removing sequences from \(W\)
+whenever player \(\plI\)/\(\plII\) makes the first ``illegal'' move.
+
+A class of such games heavily studied in the literature (see \cite{MR1378387} and its
+many sequels) are selection games.
+
+\begin{definition}
   The \term{selection game} \(\schStrongSelGame{\mc A}{\mc B}\) 
@@
 
+Put another way, \(\mc R\) is a reflection of \(\mc A\) if for every \(A\in\mc A\),
+there exists \(f\in\mathbf C(\mc R)\) such that \(\ran f\in\mc A\) and \(\ran f\subseteq A\).
+
 As we will see, reflections of selection sets are used frequently (but implicitly) 
@@
 
-%  For example, a reflection of the collection \(\mc O_X\) of basic open covers
-%  of \(X\) would be \(\mc P_X=\{\mc T_{X,x}:x\in X\}\), where \(\mc T_{X,x}\) 
-%  is the corresponding point-base at \(x\in X\). 
-%  Likewise for the collection \(\Omega_{X,x}\)
-%  of sets with \(x\in X\) as a limit point, \(\mc T_{X,x}\) is itself
-%  a reflection.
-
-\section{Main Results}
-
-%\begin{proposition}
-%  Let \(\mc R\) be a reflection of \(\mc A\). Then \(\bigcup \mc R=\bigcup \mc A\).
-%\end{proposition}
-%\begin{proof}
-%  If \(x\in \bigcup\mc A\), then \(x\in\ran{f}\) for some \(f\in\mathbf C(\mc R)\).
-%  Thus \(x=f(R)\in R\) for some \(R\in\mc R\), showing \(x\in\bigcup\mc R\).
-%
-%  Likewise if \(x\in\bigcup\mc R\), so \(x\in R\) for some \(R\in \mc R\).
-%  Let \(f\in\mathbf C(\mc R)\) satisfy \(f(R)=x\), so \(x\in\ran{f}\),
-%  showing \(x\in\bigcup\mc A\).
-%\end{proof}
-
-The following four theorems demonstrate that reflections characterize
-dual selection games for both perfect information strategies and
-certain limited information strategies.
+We use the following conventions to describe strategies for playing games.
 
 \begin{definition}
-  A pair of games \(G(X),H(X)\) are \term{Markov information dual} if both
+  For \(f\in B^A\) and \(X\subseteq A\), let \(f\rest X\) be the restrction of \(f\)
+  to \(X\). In particular, for \(f\in B^\omega\) and \(n<\omega\), \(f\rest n\)
+  describes the first \(n\) terms of the sequence \(f\).
+\end{definition}
+
+\begin{definition}
+  A \term{strategy} for the first player \(\plI\) (resp. second player \(\plII\))
+  in a game \(G\) with moveset \(M\) is a function
+  \(\sigma:M^{<\omega}\to M\). This strategy is said to be \term{winning} if
+  for all possible \term{attacks} \(\alpha\in M^\omega\) by their opponent,
+  where \(\alpha(n)\) is played by the opponent during round \(n\),
+  the player wins the game by playing \(\sigma(\alpha\rest n)\)
+  (resp. \(\sigma(\alpha\rest n+1)\)) during round \(n\).
+\end{definition}
+
+That is, a strategy is a rule that determines the moves of a player based upon
+all previous moves of the opponent. (It could also rely on all previous
+moves of the player using the strategy, since these can be reconstructed from
+the previous moves of the opponent and the strategy itself.)
+
+\begin{definition}
+  A \term{predetermined strategy} for the first player \(\plI\)
+  in a game \(G\) with moveset \(M\) is a function
+  \(\sigma:\omega\to M\). This strategy is said to be winning if
+  for all possible attacks \(\alpha\in M^\omega\) by their opponent,
+  the first player wins the game by playing \(\sigma(n)\)
+  during round \(n\).
+\end{definition}
+
+So a predetermined strategy ignores all moves of the opponent during the
+game (all moves were decided before the game began).
+
+\begin{definition}
+  A \term{Markov strategy} for the second player \(\plII\)
+  in a game \(G\) with moveset \(M\) is a function
+  \(\sigma:M\times\omega\to M\). This strategy is said to be winning if
+  for all possible attacks \(\alpha\in M^\omega\) by their opponent,
+  the first player wins the game by playing \(\sigma(\alpha(n),n)\)
+  during round \(n\).
+\end{definition}
+
+So a Markov strategy may only consider the most recent move of the opponent,
+and the current round number. Note that unlike perfect-information or
+predetermined strategies, a Markov strategy cannot use knowledge of
+moves used previously by the player (since they depend on previous moves of
+the opponent that have been ``forgotten'').
+
+\begin{definition}
+  Write \(\plI\win G\) (resp. \(\plI\prewin G\)) if player \(\plI\) has a winning
+  strategy (resp. winning predetermined strategy) for the game \(G\). Similarly,
+  write \(\plII\win G\) (resp. \(\plII\markwin G\)) if player \(\plII\) has a winning
+  strategy (resp. winning Markov strategy) for the game \(G\).
+\end{definition}
+
+Of course, \(\plII\markwin G\Rightarrow \plII\win G\Rightarrow \plI\notwin G\Rightarrow \plI\notprewin G\).
+In general, none of these implications (not even the second \cite{MR0054922}) can be reversed.
+
+It's worth noting that \(\plI\notprewin \schStrongSelGame{\mc A}{\mc B}\) is equivalent
+to the selection principle often denoted \(\schStrongSelProp{\mc A}{\mc B}\) in the literature.
+
+The goal of this paper is to characerize when two games are ``dual'' in the following
+senses.
+
+\begin{definition}
+  A pair of games \(G(X),H(X)\) defined for a topological space \(X\)
+  are \term{Markov information dual} if both
   of the following hold.
@@
 \end{definition}
+
+\begin{definition}
+  A pair of games \(G(X),H(X)\) defeind for a topological space \(X\)
+  are \term{perfect information dual} if both
+  of the following hold.
+  \begin{itemize}
+    \item \(I\win G(X)\) if and only if \(II\win H(X)\).
+    \item \(II\win G(X)\) if and only if \(I\win H(X)\).
+  \end{itemize}
+\end{definition}
+
+\section{Main Results}
+
+The following four theorems demonstrate that reflections characterize
+dual selection games for both perfect information strategies and
+certain limited information strategies.
+
+The duality of the Rothberger game \(\schStrongSelGame{\mc O_X}{\mc O_X}\)
+and the point-open game on \(X\) for perfect information strategies
+was first noted by Galvin in \cite{MR0493925}, and
+for Markov-information strategies by Clontz and Holshouser in
+[TODO cite]. These proofs may be generalized as follows.
 
@@
 \end{proof}
-
-\begin{definition}
-  A pair of games \(G(X),H(X)\) are \term{perfect information dual} if both
-  of the following hold.
-  \begin{itemize}
-    \item \(I\win G(X)\) if and only if \(II\win H(X)\).
-    \item \(II\win G(X)\) if and only if \(I\win H(X)\).
-  \end{itemize}
-\end{definition}
 
@@
 
+\section{Applications of Reflections}
+
+\begin{definition}\label{selectionSets}
+  Let \(X\) be a topological space and \(\mc T_X\) be a chosen basis of nonempty sets for its topology.
+  \begin{itemize}
+    \item Let \(\mc T_{X,x} = \{U\in\mc T_X : x\in U\}\) be the local point-base at \(x\in X\).
+    \item Let \(\Omega_{X,x} = \{Y\subseteq X: \forall U\in\mc T_{X,x}(U\cap Y\not=\emptyset)\}\) be the fan at \(x\in X\).
+    \item Let \(\mc T_{X,F} = \{U\in\mc T_X : F\subseteq U\}\) be the local finite-base at \(F\in[X]^{<\aleph_0}\).
+    \item Let \(\mc O_X = \{\mc U\subseteq\mc T_X : \bigcup \mc U=X\}\) be the collection
+          of basic open covers of \(X\).
+    \item Let \(\mc P_X = \{\mc T_{X,x} : x\in X\}\) be the collection of local point-bases of \(X\).
+    \item Let \(\Omega_X = \{\mc U\subseteq\mc T_X : \forall F\in[X]^{<\aleph_0}\exists U\in\mc U(F\subseteq U)\}\)
+          be the collection of basic \(\omega\)-covers of \(X\).
+    \item Let \(\mc F_X = \{\mc T_{X,F} : F\in [X]^{<\aleph_0}\}\) be the collection of local finite-bases of \(X\).
+    \item Let \(\mc D_X = \{Y\subseteq X: \forall U\in\mc T_X(U\cap Y\not=\emptyset)\}\) be the collection of dense subsets of \(X\).
+    \item Let \(\Gamma_{X,x} = \{Y\subseteq X: \forall U\in\mc T_{X,x}(Y\setminus U\in[X]^{<\aleph_0})\}\) be the collection
+          of converging fans at \(x\in X\). (When intersected with \([X]^{\aleph_0}\), these are the non-trivial
+          sequences of \(X\) converging to \(x\).)
+  \end{itemize}
+\end{definition}
+
+While these notions were defined in terms of a particular basis, the reader may verify the the following.
+
+\begin{proposition}
+  Let \(\mc A'\) be a selection basis for \(\mc A\).
+  \begin{itemize}
+    \item \(\plI\win\schStrongSelGame{\mc A}{\mc B}\Leftrightarrow\plI\win\schStrongSelGame{\mc A'}{\mc B}\).
+    \item \(\plI\prewin\schStrongSelGame{\mc A}{\mc B}\Leftrightarrow\plI\prewin\schStrongSelGame{\mc A'}{\mc B}\).
+    \item \(\plII\win\schStrongSelGame{\mc A}{\mc B}\Leftrightarrow\plII\win\schStrongSelGame{\mc A'}{\mc B}\).
+    \item \(\plII\markwin\schStrongSelGame{\mc A}{\mc B}\Leftrightarrow\plII\markwin\schStrongSelGame{\mc A'}{\mc B}\).
+  \end{itemize}
+\end{proposition}
+
+\begin{proposition}
+  Each selection set in Definition \ref{selectionSets} is a selection basis for the set
+  defined by replacing \(\mc T_X\) with the set of all nonempty open sets in \(X\).
+\end{proposition}
+
+As such, the choice of topological basis is irrelevant when playing selection games using these sets.
+
+We may now establish (or re-establish) the following dual games.
+
+\begin{proposition}
+  \(\mc P_X\) is a reflection of \(\mc O_X\).
+\end{proposition}
+\begin{proof}
+  For every open cover \(\mc U\), the corresponding choice function \(f\in\mathbf C(\mc P_X)\) is simply
+  the witness that \(x\in f(\mc T_{X,x})\in\mc U\).
+\end{proof}
+
+\begin{corollary}
+  \(\schStrongSelGame{\mc O_X}{\mc B}\) and \(\schStrongSelGame{\mc P_X}{\neg\mc B}\) are perfect-information
+  and Markov-information dual.
+\end{corollary}
+
+In the case that \(\mc B=\mc O_X\), \(\schStrongSelGame{\mc O_X}{\mc O_X}\) is the well-known Rothberger game,
+and \(\schStrongSelGame{\mc P_X}{\neg\mc O_X}\) is isomorphic
+to the point-open game \(PO(X)\): \(\plI\) chooses points of \(X\), \(\plII\) chooses an open neighborhood
+of each chosen point, and \(\plI\) wins if \(\plII\)'s choices are a cover.
+So this was simply the classic result that the Rothberger game and
+point-open game are perfect-information dual \cite{MR0493925}, and the more recent result that
+these games are Markov-information dual [TODO cite clontzHols].
+
+\begin{proposition}
+  \(\mc F_X\) is a reflection of \(\Omega_X\).
+\end{proposition}
+\begin{proof}
+  For every \(\omega\)-cover \(\mc U\), the corresponding choice function \(f\in\mathbf C(\mc F_X)\) is simply
+  the witness that \(F\subseteq f(\mc T_{X,F})\in\mc U\).
+\end{proof}
+
+\begin{corollary}
+  \(\schStrongSelGame{\Omega_X}{\mc B}\) and \(\schStrongSelGame{\mc F_X}{\neg\mc B}\) are perfect-information
+  and Markov-information dual.
+\end{corollary}
+
+Note that in the case that \(\mc B=\Omega_X\), \(\schStrongSelGame{\Omega_X}{\Omega_X}\) is the Rothberger
+game played with \(\omega\)-covers, and \(\schStrongSelGame{\mc F_X}{\neg\Omega_X}\) is isomorphic
+to the \(\Omega\)-finite-open game \(\Omega FO(X)\): \(\plI\) chooses finite subsets of \(X\), \(\plII\) chooses an open neighborhood
+of each chosen finite set, and \(\plI\) wins if \(\plII\)'s choices are an \(\omega\)-cover.
+These games were shown to be dual in [TODO cite clontzHols].
+
+\begin{proposition}
+  \(\mc T_X\) is a reflection of \(\mc D_X\).
+\end{proposition}
+\begin{proof}
+  For every dense \(D\), the corresponding choice function \(f\in\mathbf C(\mc T_X)\) is simply
+  the witness that \(f(U)\in U\cap D\).
+\end{proof}
+
+\begin{corollary}
+  \(\schStrongSelGame{\mc D_X}{\mc B}\) and \(\schStrongSelGame{\mc T_X}{\neg\mc B}\) are perfect-information
+  and Markov-information dual.
+\end{corollary}
+
+In the case that \(\mc B=\Omega_{X,x}\) for some \(x\in X\), \(\schStrongSelGame{\mc D_X}{\Omega_{X,x}}\) is
+the strong countable dense fan-tightness game at \(x\), see e.g. \cite{MR2678950}. \(\schStrongSelGame{\mc T_X}{\neg\Omega_{X,x}}\)
+is the game \(CL(X,x)\) first studied by Tkachuk in \cite{tkachukTwoPointGame}. Tkachuk showed in that paper
+that these games are perfect-information dual; Clontz and Holshouser previously showed these were Markov-information
+dual in the case that \(X=C_p(Y)\) [TODO cite].
+
+In the case that \(\mc B=D_X\), then \(\schStrongSelGame{\mc D_X}{\mc D_X}\) is the strong selective
+separability game introduced in \cite{MR1711901}, and \(\schStrongSelGame{\mc T_X}{\neg\mc D_X}\) is the
+point-picking game of Berner and Juh\'asz defined in \cite{MR775687}. Scheepers showed that these
+were perfect-information dual in his paper.
+
+\begin{proposition}
+  \(\mc T_{X,x}\) is a reflection of \(\Omega_{X,x}\).
+\end{proposition}
+\begin{proof}
+  For every set \(Y\) with limit point \(x\), the corresponding choice function \(f\in\mathbf C(\mc T_{X,x})\) is simply
+  the witness that \(f(U)\in U\cap Y\).
+\end{proof}
+
+\begin{corollary}
+  \(\schStrongSelGame{\Omega_{X,x}}{\mc B}\) and \(\schStrongSelGame{\mc T_{X,x}}{\neg\mc B}\) are perfect-information
+  and Markov-information dual.
+\end{corollary}
+
+In the case that \(\mc B=\Gamma_{X,x}\) for some \(x\in X\), \(\schStrongSelGame{\mc T_{X,x}}{\neg\Gamma_{X,x}}\)
+is Gruenhage's \(W\) game \cite{MR0413049}. Its dual \(\schStrongSelGame{\Omega_{X,x}}{\Gamma_{X,x}}\) characterizes
+the strong Fr\'echet-Urysohn property \(\plI\notprewin\schStrongSelGame{\Omega_{X,x}}{\Gamma_{X,x}}\) at \(x\),
+which now seen to be equivalent to \(\plII\notmarkwin\schStrongSelGame{\mc T_{X,x}}{\neg\Gamma_{X,x}}\).
+This allows us to obtain the following result.
+
+\begin{corollary}
+  \(\plI\notprewin\schStrongSelGame{\Omega_{X,x}}{\Gamma_{X,x}}\)
+  if and only if
+  \(\plI\notwin\schStrongSelGame{\Omega_{X,x}}{\Gamma_{X,x}}\).
+\end{corollary} 
+\begin{proof}
+  As shown in \cite{MR510910},
+  a space is \(w\) at \(x\), that is, \(\plII\notwin\schStrongSelGame{\mc T_{X,x}}{\neg\Gamma_{X,x}}\) 
+  if and only if \(\plI\notprewin\schStrongSelGame{\Omega_{X,x}}{\Gamma_{X,x}}\) for all \(x\in X\).
+\end{proof}
+
+For \(\mc B=\Omega_{X,x}\), \(\schStrongSelGame{\mc T_{X,x}}{\neg\Omega_{X,x}}\) is the variant of
+Gruenhage's \(W\) game for clustering. This game is now seen to be dual to the strong countable fan tightness game
+\(\schStrongSelGame{\Omega_{X,x}}{\Omega_{X,x}}\) at \(x\).
+
+%Finally, consider the following result from \cite{2016arXiv161004800C}.
+%
+%\begin{proposition}
+%  
+%\end{proposition}
+
+\section{Open Questions}
+
+\begin{question}
+  Does there exist a natural reflection for \(\Gamma_{X,x}\)
+  or \(\Gamma_X=\{\mc U\subseteq\mc T_X:\forall x\in X(\mc U\setminus\mc T_{X,x}\in[T_X]^{<\aleph_0})\}\)?
+\end{question}
+
+\begin{question}
+  Can these results be extended for \(\schSelGame{\mc A}{\mc B}\)?
+\end{question}
+
 \section{Acknowledgements}

### 2018-09-27 articles/dual-selection-games/article.tex
prepare dual game paper for arxiv

@@
 for Markov-information strategies by Clontz and Holshouser in
-[TODO cite]. These proofs may be generalized as follows.
+\cite{2018arXiv180606001C}. These proofs may be generalized as follows.
 
@@
 point-open game are perfect-information dual \cite{MR0493925}, and the more recent result that
-these games are Markov-information dual [TODO cite clontzHols].
+these games are Markov-information dual \cite{2018arXiv180606001C}.
 
@@
 of each chosen finite set, and \(\plI\) wins if \(\plII\)'s choices are an \(\omega\)-cover.
-These games were shown to be dual in [TODO cite clontzHols].
+These games were shown to be dual in \cite{2018arXiv180606001C}.
 
@@
 that these games are perfect-information dual; Clontz and Holshouser previously showed these were Markov-information
-dual in the case that \(X=C_p(Y)\) [TODO cite].
+dual in the case that \(X=C_p(Y)\)  \cite{2018arXiv180606001C}.
 
@@
 \bibliographystyle{plain}
-\bibliography{../../bibliography}
+\bibliography{bibliography}
 

### 2019-02-27 articles/mahavier-products/main.tex
add varagona coauthored paper

\documentclass{article}

%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}

%% Sets page size and margins
\usepackage[letterpaper,margin=2.5in,marginparwidth=1in]{geometry}

%% Useful packages
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{tikz}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\title{Mahavier Products, Idempotent Relations, and Condition $\Gamma$}
\author{Steven Clontz and Scott Varagona}

\newcommand{\term}{\textit}
\newcommand{\vect}{\mathbf}
\newcommand{\tuple}[1]{\left\langle{#1}\right\rangle}
\newcommand{\genInvLim}[1]{\varprojlim\tuple{#1}}
\newcommand{\maProd}[1]{{\mathbf{M}}\tuple{#1}}
\newcommand{\rest}{\upharpoonright}

      \theoremstyle{plain}
      \newtheorem{theorem}{Theorem}
      \newtheorem{lemma}[theorem]{Lemma}
      \newtheorem{corollary}[theorem]{Corollary}
      \newtheorem{proposition}[theorem]{Proposition}
      \newtheorem{conjecture}[theorem]{Conjecture}
      \newtheorem{question}[theorem]{Question}
      \newtheorem{claim}[theorem]{Claim}
      \newtheorem{observation}[theorem]{Observation}

      \theoremstyle{definition}
      \newtheorem{definition}[theorem]{Definition}
      \newtheorem{example}[theorem]{Example}
      \newtheorem{game}[theorem]{Game}

      \theoremstyle{remark}
      \newtheorem{remark}[theorem]{Remark}

\begin{document}
\maketitle

\begin{abstract}
Clearly, a generalized inverse limit of metrizable spaces 
indexed by \(\mathbb N\) is metrizable,
as it is a subspace of a countable product of metrizable spaces.
The authors previously showed that all idempotent, upper semi-continuous, surjective,
continuum-valued bonding functions on \([0,1]\) (besides the identity) satisfy a certain Condition \(\Gamma\);
it follows that only in trivial cases can a generalized inverse limit of
copies of \([0,1]\) indexed by an uncountable ordinal be metrizable. 
The authors show that Condition \(\Gamma\)
is in fact guaranteed by much weaker criteria, proving a more general metrizability theorem for certain Mahavier Products.
\end{abstract}

\section{Introduction}

In the spirit of the celebrated work by Mahavier \cite{Mahavier} and Ingram \& Mahavier \cite{IngMah1}, 
who first generalized traditional inverse limits to those with set-valued bonding 
functions, researchers have sought more ways to generalize inverse limits. One 
route proposed in \cite{IngMahbook} would be to index the factor spaces of an inverse limit not 
necessarily by the natural numbers, but rather, by some other directed set. 
However, a poorly-behaved directed set can cause an inverse limit to be empty \cite{IngMahbook};
therefore, most research in this area has involved inverse limits with totally  
ordered index sets.

Various results in recent years have shown that investigating totally 
ordered index sets besides the natural numbers is fertile ground for new work. 
Ingram and Mahavier laid the foundation in \cite{IngMahbook} by proving some basic connectedness 
theorems. Notably, Patrick Vernon in \cite{vernon} studied inverse limits on $[0,1]$ with 
set-valued functions indexed by the integers, and he showed that such an inverse 
limit with a single bonding function could be homeomorphic to a 2-cell---a 
striking result, considering Van Nall had shown in \cite{vannall} that this could never 
happen for an inverse limit indexed by the natural numbers.
Later, the notion of a generalized inverse limit was further generalized to the notion of a Mahavier product, which only required the index set to be a preordered set. Thus, the recent interest in Mahavier products (e.g., Greenwood \& Kennedy \cite{GreenKen} and Charatonik \& Roe \cite{charroe}) has helped bring ``alternate'' index sets further into the mainstream.
In particular, in \cite{charroe}, Charatonik and Roe proved theorems about Mahavier products indexed by arbitrary totally ordered sets, and in the process introduced some helpful terminology in the study of generalized inverse limits. Therefore, given this context, it is natural to consider generalized inverse limits (or Mahavier products) indexed by ordinals.

In \cite{CLONTZVARAGONA} the authors studied the special case of a generalized inverse limit 
of copies of \([0,1]\) with a 
single continuum-valued upper semi-continuous idempotent bonding function. 
They proved that when \(f\) is a surjection besides the identity, 
the graph of \(f\) must contain two distinct points 
\(\tuple{x,x},\tuple{y,y}\) on the diagonal, in addition
to a third point \(\tuple{x,y}\). This Condition \(\Gamma\)
is sufficient to guarantee that whenever
the inverse limit is indexed by an ordinal \(\alpha\),
the inverse limit contains a copy of \(\alpha+1\). It 
therefore follows that such an inverse limit is a metric continuum if and only if 
\(\alpha\) is countable. The authors suspected, however, that this was merely
a special case of a more general trend. To this end, it will be shown
that to guarantee Condition \(\Gamma\), \([0,1]\) may be replaced with any
weakly countably compact space, \(f\) need not be continuum-valued,
and the surjectivity of \(f\) may be replaced with a weaker assumption
to prevent trivialities. Applying this result, we also prove metrizability theorems for certain Mahavier products indexed by ordinals.

\section{Definitions and Conventions}

Except when otherwise stated,
we assume that all topological spaces are Hausdorff. By convention, all natural numbers are ordinals, e.g. \(4=\{0,1,2,3\}\).
Let \(B^A\) denote the set of functions from \(A\) to \(B\);
in particular, \(X^2\) is the usual square of ordered pairs 
\(\{\tuple{x,y}:x,y\in X\}\) (each pair is a function from \(\{0,1\}\) to \(X\))
and \(2^X\) is the Cantor set of functions from \(X\) to \(\{0,1\}\).
Let \(F(X)\) denote the non-empty closed subsets of \(X\).

Given a relation \(R\subseteq X\times Y\), let 
\(R(x)=\{y:xRy\}=\{y:\tuple{x,y}\in R\}\); we often will use letters
\(f,g\) to define relations and treat them as set-valued functions in this way.
Given relations or set-valued functions \(f,g\) and a set \(A\), let
\(f(A)=\{f(x):x\in A\}\) and
\(
  (f\circ g)(x)=f(g(x))=\bigcup_{y\in g(x)}f(y)
=
  \{z:\exists y(z\in f(y),y\in g(x))\}
\).
If \(f:X\to F(X)\) or \(f\subseteq X^2\), let \(f^2=f\circ f\).

\begin{definition}
Suppose \(\tuple{P,\leq}\) is a directed set (\(\leq\) is transitive and reflexive, and each pair of points shares a common upper bound)
and for each \(p \in P\), \(X_p\) is a space. 
Let \(\Pi=\prod_{p\in P}X_p\); we will use boldface letters such as 
\(\vect{x}\in\Pi\) to denote sequences in \(\Pi\).
Suppose further that for each \(p \leq q \in P\), there is a set-valued 
\term{bonding function}
\(f_{p,q} : X_q \to F(X_p)\) 
such that for \(p\leq q\leq r\),
\(
  f_{p,r}=f_{p,q}\circ f_{q,r}
\) 
with \(f_{p,p}:X_p\to F(X_p)\) 
defined by \(f_{p,p}(x)=\{x\}\).
Then the \term{generalized inverse limit} 
\(\genInvLim{X_p, f_{p,q}, P}\subseteq\Pi\) is given by:

\[
  \genInvLim{X_p, f_{p,q}, P} 
= 
  \{
    \textbf{x}\in \Pi 
  : 
    p \leq q \Rightarrow \vect{x}(p) \in f_{p,q}(\vect{x}(q)) 
  \}
.\]
\end{definition}

The preceding definition is based upon the one given in \cite{IngMahbook}.
Much of the literature assumes that \(P\) is a total order,
often simply \(\omega=\mathbb{N}=\{0,1,2,\dots\}\), but
allowing for other orders such as \(\mathbb{Z}\) enables
the construction of many interesting examples unattainable with
simply \(\omega\) \cite{vernon}.

The study of generalized inverse limits typically focuses on
upper semi-continuous bonding functions \(f_{p,q}:X_q\to F(X_p)\), 
which for compact
spaces may be characterized as those that map points to non-empty sets
and whose graphs are closed in \(X_q\times X_p\). 
In fact, it will be convenient to simply consider
this graph itself as a relation. This is
exactly the approach taken with Mahavier products
in \cite{charroe}, \cite{GreenKen}.

\begin{definition}
Take the assumptions of the previous definition,
but let \(\tuple{P,\leq}\) be a preordered set (\(\leq\) is transitive and reflexive) and let \(f_{p,q}\subseteq X_q\times X_p\)
such that \(f_{p,r}\subseteq f_{p,q}\circ f_{q,r}\).
Then the \term{Mahavier product} 
\(\maProd{X_p, f_{p,q}, P}\subseteq\Pi\) is given by:

\[
  \maProd{X_p, f_{p,q}, P} 
= 
  \{
    \textbf{x}\in \Pi 
  : 
    p \leq q \Rightarrow \vect{x}(p) \in f_{p,q}(\vect{x}(q)) 
  \}
\]
\end{definition}

Note that the condition 
\(f_{p,r}\subseteq f_{p,q} \circ f_{q,r}\)
has been weakened from equality,
\(f_{p,q}\) is an arbitrary relation from
\(X_q\) to \(X_p\),
and the directed set is now only preordered,
as is done in \cite{charroe}.

\begin{definition}
A Mahavier product \(\maProd{X_p,f_{p,q},P}\) is \term{exact}
whenever \(f_{p,r}=f_{p,q}\circ f_{q,r}\) for all \(p\leq q\leq r\).
\end{definition}

\begin{definition}
A relation \(f\subseteq X\times Y\) is said to be \term{left-total}
(also called \term{full} \cite{charroe})
if  \(\forall x \in X\) \(\exists y \in Y\) such that 
\(\tuple{x,y}\in f\); that is, \(f(x)\not=\emptyset\)
for all \(x\in X\).
\end{definition}

Note that we will refrain from using the term ``full'' to describe such 
relations, as ``full'' bonding functions are defined in another sense in 
\cite{GreenKen2}.

\begin{observation}
Exact Mahavier products bonded by 
closed-valued left-total relations
indexed by a directed set
are generalized inverse limits.
\end{observation}

\begin{definition}
A left-total relation that is a closed subset of \(X \times Y\) 
is called \term{USC}.
\end{definition}

Here USC stands for upper semi-continuous, as
in the case that \(X,Y\) are compact, this property may be characterized
as follows: for every \(x\in X\) and open set \(V\supseteq f(x)\),
there exists an open neighborhood \(U\) of \(x\) such that
\(f(u)\subseteq V\) for all \(u\in U\) \cite{IngMah1}.
Put another way, the set-valued function \(f:X\to F(Y)\) is continuous
where \(F(Y)\) is given the upper Vietoris topology.

\begin{definition}
A relation \(f\subseteq X\times Y\) is \term{surjective} if, 
for all \(y\in Y\), there exists \(x \in X\) such that 
\(\tuple{x,y}\in f\).
\end{definition}

\begin{definition}
An \term{idempotent} relation on \(f\subseteq X^2\) 
is one that satisfies \(f^2=f\).
\end{definition}

Note that transitivity may be characterized by
\(f^2\subseteq f\), so all idempotent relations are transitive.
Put another way, an idempotent relation \(R\subseteq X^2\)
satisfies \(xRz\) if and only if \(xRyRz\) for some \(y\in X\);
transitivity is the backwards implication.
Assuming reflexivity, idempotence and transitivity are equivalent:
let \(y=z\), so \(xRz\Leftrightarrow xRzRz \Leftrightarrow xRyRz\).
Note also that the inverse of an idempotent relation is idempotent.

The usual strict linear order \(<\) on \(\mathbb{Z}\) is
an example of a transitive yet non-idempotent relation.
Likewise, the strict linear order on any dense subset of \(\mathbb R\)
is a non-reflexive idempotent relation.

Idempotent relations are of significant interest
when studying exact Mahavier products of many copies of the same topological space.

\begin{observation}
If \(X_p=X\) and \(f_{p,q}=f\) for all \(p<q\),
and there exist \(p,q,r\in P\) such that \(p<q<r\), 
then the bonding relation \(f\) 
in an exact Mahavier product \(\maProd{X,f,P}\) must be idempotent. 
\end{observation}

Note that \(f_{p,p}\not=f\) unless \(f\) is the identity, but for
simplicity we still simply write \(\maProd{X,f,P}\).

\begin{definition}
For convenience, we call a USC idempotent surjective relation 
\(f \subseteq X^2\) a \term{V-relation}. 
\end{definition}

\begin{figure}
\begin{center}
\begin{tikzpicture}
\begin{scope}[shift={(0,0)}]
  \draw[gray] (0,0) rectangle (2,2);
  \draw[thick,blue] (0,0) -- (2,2);
\end{scope}
\begin{scope}[shift={(3,0)}]
  \draw[gray] (0,0) rectangle (2,2);
  \draw[thick,blue] (0,2) -- (0,0) -- (2,2);
  \draw[black,fill=red] (0,0) circle (0.1);
  \draw[black,fill=red] (0,1) circle (0.1);
  \draw[black,fill=red] (1,1) circle (0.1);
\end{scope}
\begin{scope}[shift={(6,0)}]
  \draw[gray] (0,0) rectangle (2,2);
  \draw[thick,blue] (0,0) -- (0.5,0.5) -- (0.5,2) -- (2,2) -- (1.5,1.5)
    -- (1.5,2); 
  \draw[black,fill=red] (0.5,0.5) circle (0.1);
  \draw[black,fill=red] (0.5,1.5) circle (0.1);
  \draw[black,fill=red] (1.5,1.5) circle (0.1);
\end{scope}
\begin{scope}[shift={(9,0)}]
  \draw[gray] (0,0) rectangle (2,2);
  \draw[thick,blue] (0,0) -- (1,1) -- (2,1);
  \draw[thick,blue,fill] (1.5,1) -- (1.5,2) -- (2,2) -- (2,1);
  \draw[black,fill=red] (1.5,1.5) circle (0.1);
  \draw[black,fill=red] (2,1.5) circle (0.1);
  \draw[black,fill=red] (2,2) circle (0.1);
\end{scope}
\end{tikzpicture}
\end{center}
\caption{Illustrating Condition \(\Gamma\) for V-relations on \([0,1]\)}
\label{VRelation}
\end{figure}

Examples of V-relations are given in Figure \ref{VRelation}
(the designated points illustrate the definition of Condition \(\Gamma\),
given in Section \ref{conditionGamma}).
The next section will outline how to construct and identify
V-relations.

\section{Constructing V-relations}

The following propositions not only give necessary and/or sufficient conditions 
for a relation \(f\) to be a V-relation, but also give the reader a few tools for 
constructing simple V-relations from scratch. The first proposition is a
useful recharacterization of idempotence.

\begin{proposition}\label{Vrelcondition}
Let $X$ be a space and let $f \subseteq X^2$ be USC and surjective. Then $f$ is a V-relation iff whenever $A$ is the image of some $x \in X$, then $f(A)=A$.
\end{proposition}

As an obvious consequence of Proposition \ref{Vrelcondition}, if $f \subseteq X^2$ 
is a V-relation and for some $x \in X$, $f(x)=\{y\}$, then $f(y)=\{y\}$.

\begin{proposition} \label{Vrelcondition2}
Let $f \subseteq [0,1]^2$ be USC. If $f$ satisfies at least one of the following conditions, then $f$ is a V-relation.

\begin{enumerate}
\item For each $x \in [0,1]$, $f(x)=\{x, 1-x\}$ .

\item The relation $f$ is surjective, and for each $x \in [0,1]$, $f(x)=[0,x]$ 
or $f(x) \subseteq \{0, x\}$.

\item
The relation $f$ is surjective, and for each $x \in [0,1]$, $f(x)=[x,1]$ or 
$f(x) \subseteq \{x,1\}$.

\item
For some non-empty $A, B \subseteq [0,1]$ with $A \cap B = \emptyset$, we have 
$f(a)=[0,1]$ for each $a \in A$ and $f(x)=B$ for each $x \in [0,1] \setminus A$.

\item  
The relation $f$ is surjective, and there exists $b\in [0,1]$ with 
$b\in f(b)=B$ so that for all $x \in [0,1]$, 
either $f(x)=\{x\}$, $f(x)=B$, or $f(x)=\{y\}$ for some $y\in B$ 
satisfying $f(y)=\{y\}$.
\end{enumerate}
\end{proposition}

\begin{proof}
Each of the five conditions implies that $f$ is surjective, so it remains to verify that each condition implies that $f$ is idempotent.  Ingram already observed that condition 1 implies $f$ is idempotent in \cite{Ingrambook}. For condition 2, let $x \in [0,1]$. We note that $f(y)\subseteq [0,x]$ for every $y \le x$. Therefore, if $f(x)= [0,x]$, then clearly $f^2(x)= [0,x]=f(x)$. On the other hand, if $f(x) = \{0,x\}$, then $f^2(x)=f(0) \cup f(x) = \{0\} \cup \{0,x\}=f(x)$; the remaining cases are obvious. The details for condition 3 are similarly straightforward and are left to the reader.

For condition 4, we note that when $x \in A$, $f(x)=[0,1]$ (so of course $f^2(x)=[0,1]$), whereas if $x \in [0,1] \setminus A$, then $f(x)=B$, so that $f^2(x)=f(B)$. However, when $b \in B$, since $b \not\in A$, it follows that $f(b)=B$; thus, $f^2(x)=B$, and we conclude that $f$ is idempotent.

To prove that condition 5 implies $f$ is idempotent, let $x \in [0,1]$. If $f(x)=\{x\}$ then clearly $f^2(x)=f(x)$. If $f(x)=\{y\}$ for some $y \in B$ with $f(y)=\{y\}$, then $f^2(x)=f(y)=\{y\}=f(x)$. Finally, if $f(x)=B$, then $f^2(x)=f(B)$; since $f(b) \subseteq B$ for each $b \in B$, and there is some $b \in B$ that satisfies $f(b)=B$, it follows that $f(B)=B$. Thus, $f^2(x)=f(x)$ in each case.
\end{proof}

Note that Proposition \ref{Vrelcondition2} implies that each of the relations pictured in Figure \ref{VRelation}  is a V-relation. (Of course, the sufficient conditions given in Proposition \ref{Vrelcondition2} are by no means exhaustive.)

\section{
Condition \texorpdfstring{\(\Gamma\)}{Gamma}
}\label{conditionGamma}

\begin{definition}
  A relation \(f \subseteq X^2\) satisfies \term{Condition \(\Gamma\)} if there 
  exist distinct \(x, y \in X\) such that \(\tuple{x,x},\tuple{x,y},\tuple{y,y}\in f\).
\end{definition}

Note that in Figure \ref{VRelation}, every example given besides the
identity satisfies Condition \(\Gamma\).
In fact, this section will show that every V-relation besides the identity on a 
weakly countably compact space satisfies Condition \(\Gamma\).

\begin{definition}
  Let \(\iota\subseteq X^2\) be the diagonal
  \(\iota=\{\tuple{x,x}:x\in X\}\), i.e. the identity relation.
\end{definition}

\begin{definition}
  For \(f\subseteq X\times Y\) and \(A\subseteq X\), 
  let \(f\rest A=f\cap (A\times Y)\). 
\end{definition}

\begin{proposition}
  For \(f\) transitive, \(f\rest f(x)=f\cap (f(x))^2\).
\end{proposition}

\begin{definition}
  A relation is said to be \term{trivial} if for all
  \(x\in X\), \(f\rest f(x)=\iota \rest f(x)\).
\end{definition}

Any trivial relation is idempotent, and
of course \(\iota\) is trivial, but there exist trivial
idempotent relations besides the identity. For example, let
\(
  t\subseteq 3^2=\{0,1,2\}^2
\)
be defined by
\[
  t=\{\tuple{0,0},\tuple{1,1},\tuple{2,0},\tuple{2,1}\}
.\]
It follows that \(t\rest f(0)=t\rest\{0\}=\iota\rest\{0\}\),
\(t\rest f(1)=t\rest\{1\}=\iota\rest\{1\}\),
and \(t\rest f(2)=t\rest\{0,1\}=\iota\rest\{0,1\}\).
Figure \ref{trivialRelation} shows examples of trivial relations
defined on \([0,1]\); note that these do not satisfy Condition \(\Gamma\).

\begin{figure}
\begin{center}
\begin{tikzpicture}
\begin{scope}
  \draw[gray] (0,0) rectangle (2,2);
  \draw[thick,blue] (0,0) -- (1,1) -- (2,1);
\end{scope}
\begin{scope}[shift={(3,0)}]
  \draw[gray] (0,0) rectangle (2,2);
  \draw[thick,blue] (0,0) -- (1,1);
  \draw[thick,blue,fill=blue] (2,1) -- (2,0) -- (1,1) -- (2,1);
\end{scope}
\begin{scope}[shift={(6,0)}]
  \draw[gray] (0,0) rectangle (2,2);
  \draw[thick,blue] (2,2) -- (1,1) -- (0,1) -- (0,2) -- (0.5,2) -- (0.5,1);
\end{scope}
\end{tikzpicture}
\end{center}
\caption{Trivial idempotent relations on \([0,1]\) besides \(\iota\)}
\label{trivialRelation}
\end{figure}

Observing that none of the examples in Figure \ref{trivialRelation}
are surjective, the following proposition will allow us to ignore
such exceptional cases when considering V-relations besides the identity.

\begin{proposition}
  Let \(f\) be a transitive surjective relation on \(X\).
  Then the following are equivalent.
  \begin{enumerate}[a)]
  \item \(f=\iota\)
  \item \(|f(x)|=1\) for all \(x\in X\)
  \item \(f\) is trivial
  \end{enumerate}
\end{proposition}
\begin{proof}
  (a) implies (b) trivially, so assume (b). For an arbitrary \(x\in X\),
  there exists some \(y\in X\) such that \(f(x)=\{y\}\). 
  Thus \(f^2(x)=\{y\}=f(y)\) by transitivity, so it follows that 
  \(f\rest\{y\}=\{\tuple{y,y}\}=\iota\rest\{y\}\), showing (c).

  Finally, assuming (c), let \(y\in X\) and by surjectivity choose
  \(x\in X\) with \(y\in f(x)\). By triviality,
  \(f(y)=(f\rest f(x))(y)=(\iota\rest f(x))(y)=\iota(y)\),
  showing (a).
%  Now assuming (c), take \(y\in X\). As \(f\) is surjective, 
%  there exists \(x\in X\) where \(y\in f(x)\). By idempotence,
%  \(y\in f^2(x)\), and in particular, \(y\in f(y)\).
%  But since \(f\rest f(y)=\iota\rest f(y)\) by triviality,
%  we note that \(f(y)=(f\rest f(y))(y)=(\iota\rest f(y))(y)=\iota(y)=\{y\}\),
%  showing (a).
\end{proof}

\begin{corollary}
  \(\iota\) is the only trivial V-relation.
\end{corollary}

We now aim to exploit the properties of non-trivial relations
to produce Condition \(\Gamma\) in V-relations besides \(\iota\).
To do this, we require the following lemmas.

\begin{definition}
A weakly countably compact space is a space such that every infinite
subset has a limit point.
\end{definition}

Assuming spaces are \(T_2\), this property is equivalent
to countable compactness: every countable open cover has a finite subcover.
But we will need only this weaker characterization, and the remainder
of this section does not assume any separation axioms for the spaces under
consideration.

\begin{lemma}\label{lemma-usc-idempotent}
  Let \(X\) be weakly countably compact.
  Every USC idempotent relation \(f\subseteq X^2\) besides \(\iota\)
  contains two points \(\tuple{y,y},\tuple{x,y}\) for some 
  distinct \(x,y\in X\).
\end{lemma}
\begin{proof}
  Note first that if \(\iota\subseteq f\), then since
  \(\iota\not=f\) the lemma follows
  immediately. So 
  let \(x_0\in X\) be a point where \(\tuple{x_0,x_0}\not\in f\).

  Suppose \(x_i\) is defined for \(i\leq n\) such that
  \(\tuple{x_i,x_j}\in f\) if and only if \(i<j\).
  Since \(\{x_0,\dots,x_n\}\cap f(x_n)=\emptyset\),
  we may choose \(x_{n+1}\not\in\{x_0,\dots,x_n\}\)
  such that \(\tuple{x_n,x_{n+1}}\in f\).
  Note that by idempotence, \(\tuple{x_{n+1},x_i}\not\in f\)
  for \(i\leq n\) since 
  \(x_i\not\in f(x_n)=f^2(x_n)\supseteq f(x_{n+1})\).
  Similarly, \(\tuple{x_i,x_{n+1}}\in f\) for \(i<n\) since
  \(\tuple{x_i,x_n}\in f\) and \(\tuple{x_n,x_{n+1}}\in f\).
  If \(\tuple{x_{n+1},x_{n+1}}\in f\),
  then the lemma is satisfied by \(x=x_n\) and \(y=x_{n+1}\).

  If not, we have recursively constructed an infinite
  set \(\{x_n:n<\omega\}\).
  Since \(X\) is a weakly countably compact space, 
  \(\{x_n:n<\omega\}\) has a limit point \(x_\omega\).
  Since \(\{\tuple{x_n,x_{n+1}}:n<\omega\}\subseteq f\), it follows that
  \(\tuple{x_\omega,x_\omega}\) is a limit point of \(f\).
  Similarly, \(\{\tuple{x_0,x_n}:0<n<\omega\}\subseteq f\),
  so it follows that \(\tuple{x_0,x_\omega}\)
  is also a limit point of \(f\). Since \(f\) is closed,
  these limit points belong to \(f\).
  Therefore the lemma is witnessed by
  \(x=x_0\) and \(y=x_\omega\).
\end{proof}

\begin{lemma}
  Let \(f\subseteq X^2\) be idempotent and left-total, and let \(x_0\in X\).
  Then \(f\rest f(x_0)\) and its inverse are idempotent, left-total,
  surjective relations on \(f(x_0)\).
\end{lemma}
\begin{proof}
  Let \(g=f\rest f(x_0)\). For each \(x\in f(x_0)\), \(f(x)\subseteq f^2(x_0)=f(x_0)\).
  Thus \(g(x)=f(x)\not=\emptyset\) and 
  \(g^2(x)=f^2(x)=f(x)=g(x)\), showing that \(g\) is idempotent and left-total.
  It is also surjective: for \(y\in f(x_0)\), \(y\in f^2(x_0)\), so there
  exists some \(x\in f(x_0)\) such that \(g(x)=f(x)=y\).
  Since \(g\) is left-total, surjective, and idempotent, so is \(g^{-1}\).
\end{proof}

\begin{lemma}\label{lemma-nontrivial-idempotent}
  Let \(f\subseteq X^2\) be idempotent and left-total, and let \(x_0\in X\)
  witness that \(f\) is non-trivial.
  Then \(f\rest f(x_0)\) and its inverse are idempotent, left-total,
  surjective, non-trivial relations on \(f(x_0)\).
\end{lemma}
\begin{proof}
  By the previous lemma, \(g=f\rest f(x_0)\) and \(g^{-1}\) 
  are idempotent, left-total, and surjective.
  By non-triviality, \(g\not=\iota \rest f(x_0)\),
  so \(g^{-1}\not=\iota\rest f(x_0)\) too.
  But since \(\iota\rest f(x_0)\) 
  is the only surjective idempotent trivial relation on \(f(x_0)\),
  neither \(g\) nor \(g^{-1}\) are trivial.
\end{proof}

\begin{theorem}
  Let \(X\) be weakly countably compact, and let \(f\subseteq X^2\) be
  an idempotent USC relation. Then the following are equivalent.
  \begin{enumerate}[a)]
  \item \(f\) satisfies Condition \(\Gamma\)
  \item \(f\) contains points \(\tuple{x,x},\tuple{x,y}\) for some distinct
        \(x,y\in X\)
  \item \(f\) is non-trivial
  \end{enumerate}
\end{theorem}

\begin{proof}
  (a) implies (b) trivially. Assuming (b), it follows that
  \(f\rest f(x)\not=\iota\rest f(x)\) since \(\tuple{x,y}\in f\rest f(x)\),
  showing (c).

  Assuming (c), we may apply Lemma \ref{lemma-nontrivial-idempotent} 
  to choose \(x_0\)
  such that \(g=f\rest f(x_0)\) and \(g^{-1}\) are idempotent, USC,
  surjective, non-trivial relations. 
  Then Lemma \ref{lemma-usc-idempotent} allows us to conclude that
  \(g^{-1}\) contains points \(\tuple{x,x},\tuple{y,x}\) for some distinct
  \(x,y\in X\), so (b) is satisfied.

  Assume (b) such that \(\tuple{y,y}\not\in f\).
  Note then that \(\tuple{y,x}\not\in f\) as otherwise
  \(\tuple{y,x},\tuple{x,y}\in f\) would imply \(\tuple{y,y}\in f\).
  Let \(z_0=x\) and \(z_1=y\).

  Suppose \(z_i\) is defined for \(i\leq n+1\) such that
  \(\tuple{z_i,z_j}\in f\) if and only if \(i<j\) or \(i=j=0\).
  Since \(\{z_0,\dots,z_{n+1}\}\cap f(z_{n+1})=\emptyset\),
  we may choose \(z_{n+2}\) distinct from \(z_i\) for \(i\leq n+1\) 
  such that \(\tuple{z_{n+1},z_{n+2}}\in f\).
  Note that by idempotence, \(\tuple{z_{n+2},z_i}\not\in f\)
  for \(i\leq n+1\) since 
  \(z_i\not\in f(z_{n+1})=f^2(z_{n+1})\supseteq f(z_{n+2})\).
  Similarly, \(\tuple{z_i,z_{n+2}}\in f\) for \(i<n+1\) since
  \(\tuple{z_i,z_{n+1}}\in f\) and \(\tuple{z_{n+1},z_{n+2}}\in f\).
  If \(\tuple{z_{n+2},z_{n+2}}\in f\),
  then Condition \(\Gamma\) is witnessed by 
  \(\tuple{z_0,z_0},\tuple{z_0,z_{n+2}},\tuple{z_{n+2},z_{n+2}}\).

  If not, we have recursively constructed an infinite
  set \(\{z_n:n<\omega\}\).
  Since \(X\) is a weakly countably compact space, 
  \(\{z_n:n<\omega\}\) has a limit point \(z_\omega\).
  Since \(\{\tuple{z_n,z_{n+1}}:n<\omega\}\subseteq f\), it follows that
  \(\tuple{z_\omega,z_\omega}\) is a limit point of \(f\).
  Similarly, \(\{\tuple{z_0,z_n}:n<\omega\}\subseteq f\),
  so it follows that \(\tuple{z_0,z_\omega}\)
  is also a limit point of \(f\). Since \(f\) is closed,
  these limit points belong to \(f\).
  Therefore Condition \(\Gamma\) is witnessed by
  \(\tuple{z_0,z_0},\tuple{z_0,z_\omega},\tuple{z_\omega,z_\omega}\),
  showing \((a)\).
\end{proof}

\begin{corollary}Let $X$ be weakly countably compact, and let $f \ne \iota$ be a V-relation on $X$. Then $f$ satisfies Condition $\Gamma$.
\end{corollary}

It is worth noting that the strict linear order \(<\) on \(\mathbb Q\) 
with the discrete topology is an example of a non-trivial idempotent
USC relation on a space that is not weakly countably compact
that does not satisfy Condition \(\Gamma\). Likewise,
the strict lexicographic order \(<\) on the long ray
\(\omega_1\times[0,1]\) with the topology induced by this linear order 
is an example of a non-trivial idempotent
left-total non-USC relation on a Hausdorff countably compact 
space that does not satisfy Condition \(\Gamma\).

\section{Applications}

Let \(\alpha=\{\beta:\beta<\alpha\}\) be an ordinal with its usual 
linear order. As noted in \cite{CLONTZVARAGONA}, it is well-known and 
easy to see that \(\alpha+1\) as a totally ordered topological space
is metrizable if and only if \(\alpha\) is countable: if 
\(\alpha\) is uncountable, then the first uncountable ordinal
\(\omega_1\) is
a point of non-first-countability in \(\alpha+1\); if \(\alpha\)
is countable, then \(\alpha+1\) is regular and second-countable.

\begin{theorem}
  Let \(X\) be a \(T_1\) topological space, let
  \(\alpha\) be an uncountable ordinal, and let \(f\) be a relation on $X$ (with $f \subseteq f \circ f$)
  satisfying Condition \(\Gamma\). 
  Then the Mahavier product 
  \(\maProd{X,f,\alpha}\) contains a copy of \(\alpha+1\); 
  therefore, \(\maProd{X,f,\alpha}\) cannot be metrizable.
\end{theorem}

\begin{proof}
  Let \(\tuple{x,x},\tuple{x,y},\tuple{y,y}\in f\)
  for distinct \(x,y\in X\). For \(\gamma\leq \alpha\),
  define \(\vect{x}_\gamma\in\maProd{X,f,\alpha}\) by
  \(\vect{x}_\gamma(\beta)=y\) for \(\beta<\gamma\)
  and \(\vect{x}_\gamma(\beta)=x\) for \(\gamma\leq\beta<\alpha\).
  That is, \(\vect{x}_\gamma\) is defined such that \(\gamma\) is
  the least ordinal such that \(\vect{x}_\gamma(\gamma)=x\).

  We will show that the map \(\gamma\mapsto\vect{x}_\gamma\) is
  a homeomorphism from \(\alpha+1\) to
  \(A=\{\vect{x}_\gamma:\gamma\leq\alpha\}\subseteq\maProd{X,f,\alpha}\). 
  This may be accomplished by comparing subbases: for \(\beta\leq\alpha\),
  the subbasic open set \([0,\beta)\subseteq\alpha+1\) maps to
  the set \(\{\vect{x}\in A:\vect{x}(\beta)=x\}\subseteq A\),
  which equals the open set \(A\cap\prod_{\gamma<\alpha}U_\gamma\) where
  \(U_\beta=X\setminus\{y\}\) and \(U_\gamma=X\) otherwise.
  Similarly, the subbasic open set \((\beta,\alpha]\subseteq\alpha+1\) 
  maps to the set \(\{\vect{x}\in A:\vect{x}(\beta)=y\}\subseteq A\), 
  which equals the open set \(A\cap\prod_{\gamma<\alpha}U_\gamma\) where
  \(U_{\beta}=X\setminus\{x\}\) and \(U_\gamma=X\) otherwise.
  And since \(A\cap\prod_{\gamma<\alpha}U_\gamma\) describes every
  subbasic open subset of \(A\) for 
  \(U_\beta\in\{\emptyset,X\setminus\{x\},X\setminus\{y\},X\}\)
  and \(U_\gamma=X\) otherwise,
  it follows that this map is indeed a homeomorphism.
\end{proof}

Noting that in metrizable spaces, compactness is characterized by
weak countable compactness, we have the following corollary.

\begin{corollary}
  Let \(X\) be any compact metrizable space, let
  \(\alpha\) be an ordinal, and let \(f\not=\iota\) be a 
  V-relation on $X$. Then the exact Mahavier product 
  \(\maProd{X,f,\alpha}\) contains a copy of \(\alpha+1\); 
  therefore, \(\maProd{X,f,\alpha}\) is metrizable
  if and only if \(\alpha\) is countable.
\end{corollary}

As noted in \cite{CLONTZVARAGONA}, a bit more can be said.

\begin{definition}
  The \term{\(\Sigma\)-product of reals \(\Sigma\mathbb{R}^\kappa\)}
  for a cardinal \(\kappa\) is given by
  \[\{
    \vect x\in \mathbb{R}^\kappa
  :
    |\{\alpha<\kappa:\vect{x}(\alpha)\not=0\}|\leq\aleph_0
  \}\]
\end{definition}

Note \(\Sigma\mathbb{R}^\omega=\mathbb{R}^\omega\), and
since every compact metrizable space embeds in \([0,1]^\omega\),
it follows that every compact metrizable space embeds in
a \(\Sigma\)-product of reals.

Compact subspaces of \(\Sigma\mathbb{R}^\kappa\) are known
as Corson compacts: see e.g. \cite{Corson} for
an investigation into the applications of Corson compacts in functional
analysis.

\begin{corollary}
  Let \(X\) be a \(T_1\) topological space, let
  \(\alpha\) be an uncountable ordinal, and let \(f\) be a relation on $X$ (with $f \subseteq f \circ f$)
  satisfying Condition \(\Gamma\). 
  Then the Mahavier product 
  \(\maProd{X,f,\alpha}\) cannot be embedded in a \(\Sigma\)-product
  of reals.
\end{corollary}
\begin{proof}
The Mahavier product \(\maProd{X,f,\alpha}\) contains a copy of \(\alpha+1\),
  which cannot be embedded into a \(\Sigma\)-product of reals.
\end{proof}

\section{Acknowledgements}

The authors wish to thank Jonathan Meddaugh, Christopher Night,
and the participants in the Spring 2016 Carolina
Topology Seminar for their comments on various working versions
of these results.

\begin{thebibliography}{999}

\bibitem{Corson}
Argyros, S., Mercourakis, S., \& Negrepontis, S., \emph{Functional-analytic properties of Corson-compact spaces}, Studia Math. vol. 89 (1988), no. 3, 197–229.
%MR956239 46E15 (46A55 54C35 54D99)

\bibitem{charroe}
Wlodzimierz J. Charatonik, Robert P. Roe, \emph{On Mahavier Products}, Topology and its
Applications, vol. 166 (2014), 92-97.

\bibitem{CLONTZVARAGONA}
Steven Clontz, Scott Varagona, \emph{Destruction of Metrizability in Generalized Inverse Limits}, Topology Proceedings, vol. 48 (2016), pp. 289-297.

\bibitem{GreenKen}
Sina Greenwood, Judy Kennedy, \emph{Connectedness and Ingram-Mahavier products}, Topology and its Applications, vol. 166 (2014), 1-9.

\bibitem{GreenKen2}
Sina Greenwood, Judy Kennedy, Michael Lockyer, \emph{Connectedness and inverse limits with set-valued functions on intervals}, Topology and its Applications, vol. 221 (2017), 69-90.

\bibitem{Ingrambook}
W. T. Ingram, \emph{An introduction to inverse limits with set-valued functions}, Springer Briefs in
Mathematics, 2012.

\bibitem{IngMah1}
W. T. Ingram, William S. Mahavier, \emph{Inverse limits of upper semi-continuous set valued functions}, Houston Journal of Mathematics, vol. 32 (2006) no. 1, 119-130.

\bibitem{IngMahbook}
W. T. Ingram, William S. Mahavier, \emph{Inverse Limits: from Continua to Chaos}, Springer, Developments in Mathematics (vol. 25), 2012.

\bibitem{Mahavier}
William S. Mahavier, \emph{Inverse Limits with Subsets of $[0,1] \times [0,1]$}, Topology and its Applications, vol. 141 (2004), no. 1-3, 225-231.

\bibitem{vannall}
Van Nall, \emph{Inverse limits with set valued functions}, Houston Journal of Mathematics, vol. 37 (2011), no. 4, 1323-1332.

\bibitem{vernon}
Patrick Vernon, \emph{Inverse limits of set-valued functions indexed by the integers}, Topology and its Applications, vol. 171 (2014), 35-40.

\end{thebibliography}

\end{document}

### 2019-10-11 articles/dual-selection-games/article.tex
remove unused AMS classification
submission-ready dual game draft

--- 2018-07-20 articles/dual-selection-games/article.tex
@@
 
-\subjclass[2010]{54C30, 54D20, 54D45, 91A44}
+\subjclass[2010]{54D20, 54D45, 91A44}
 
@@
 
-A class of such games heavily studied in the literature (see \cite{MR1378387} and its
-many sequels) are selection games.
+A class of such games heavily studied in the literature, particularly
+topology (see \cite{MR1378387} and its
+many sequels), are selection games.
 
@@
 
-Put another way, \(\mc R\) is a reflection of \(\mc A\) if for every \(A\in\mc A\),
-there exists \(f\in\mathbf C(\mc R)\) such that \(\ran f\in\mc A\) and \(\ran f\subseteq A\).
+Put another way, \(\mc R\) is a reflection of \(\mc A\) if \(\ran f\in\mc A\) 
+for all \(f\in\mathbf C(\mc R)\), and for each \(A\in\mc A\) there exists
+\(f_A\in\mathbf C(\mc R)\) such that \(\ran{f_A}\subseteq A\).
 
@@
 So a predetermined strategy ignores all moves of the opponent during the
-game (all moves were decided before the game began).
+game (all moves were decided before the game began). Such strategies
+are also known as \(0\)-Markov strategies or \(0\)-Markov tactics.
+The following definition is similarly also known as a \(1\)-Markov strategy.
 
@@
   for all possible attacks \(\alpha\in M^\omega\) by their opponent,
-  the first player wins the game by playing \(\sigma(\alpha(n),n)\)
+  the second player wins the game by playing \(\sigma(\alpha(n),n)\)
   during round \(n\).
@@
 
+We also consider similar strategies that ignore the round number.
+
 \begin{definition}
-  Write \(\plI\win G\) (resp. \(\plI\prewin G\)) if player \(\plI\) has a winning
-  strategy (resp. winning predetermined strategy) for the game \(G\). Similarly,
-  write \(\plII\win G\) (resp. \(\plII\markwin G\)) if player \(\plII\) has a winning
-  strategy (resp. winning Markov strategy) for the game \(G\).
+  A \term{constant strategy} for the first player \(\plI\)
+  in a game \(G\) with moveset \(M\) is simply a choice \(m\in M\).
+  This strategy is said to be winning if
+  for all possible attacks \(\alpha\in M^\omega\) by their opponent,
+  the first player wins the game by playing \(m\) during every round.
 \end{definition}
 
-Of course, \(\plII\markwin G\Rightarrow \plII\win G\Rightarrow \plI\notwin G\Rightarrow \plI\notprewin G\).
-In general, none of these implications (not even the second \cite{MR0054922}) can be reversed.
+\begin{definition}
+  A \term{tactical strategy} for the second player \(\plII\)
+  in a game \(G\) with moveset \(M\) is a function
+  \(\sigma:M\to M\). This strategy is said to be winning if
+  for all possible attacks \(\alpha\in M^\omega\) by their opponent,
+  the second player wins the game by playing \(\sigma(\alpha(n))\)
+  during round \(n\).
+\end{definition}
 
-It's worth noting that \(\plI\notprewin \schStrongSelGame{\mc A}{\mc B}\) is equivalent
-to the selection principle often denoted \(\schStrongSelProp{\mc A}{\mc B}\) in the literature.
+\begin{definition}
+  Write \(\plI\win G\) (resp. \(\plI\prewin G\), \(\plI\conwin G\)) 
+  if player \(\plI\) has a winning
+  strategy (resp. winning predetermined/constant strategy) for the game \(G\). Similarly,
+  write \(\plII\win G\) (resp. \(\plII\markwin G\), \(\plII\tactwin G\)) 
+  if player \(\plII\) has a winning
+  strategy (resp. winning Markov/tactical strategy) for the game \(G\).
+\end{definition}
 
-The goal of this paper is to characerize when two games are ``dual'' in the following
+Of course: 
+\[
+  \plII\tactwin G\Rightarrow 
+  \plII\markwin G\Rightarrow 
+  \plII\win G\Rightarrow 
+  \plI\notwin G\Rightarrow 
+  \plI\notprewin G\Rightarrow 
+  \plI\notconwin G
+.\]
+In general, none of these implications (not even the middle \cite{MR0054922}) can be reversed.
+
+While predetermined and constant strategies are rarely explicitly studied in the literature,
+they are implicitly considered when studying the following well-known principles.
+
+\begin{definition}
+  The selection principle \(\schStrongSelProp{\mc A}{\mc B}\) asserts
+  that for each sequence \(\setB{A_n}{n<\omega}\in[\mc A]^\omega\),
+  there exist \(B_n\in A_n\) such that \(\setB{B_n}{n<\omega}\in\mc B\).
+\end{definition}
+
+For example, if \(\mc O_X\) denotes the open covers of a space \(X\), 
+then \(\schStrongSelProp{\mc O_X}{\mc O_X}\) is the Rothberger covering property.
+
+\begin{definition}
+  The choice principle \(\binom{\mc A}{\mc B}^\kappa\) asserts
+  that for each \(A\in \mc A\), there exists a subset
+  \(B\subseteq A\) where \(|B|=\kappa\) and \(B\in\mc B\).
+\end{definition}
+
+For example,
+\(\binom{\mc O_X}{\mc O_X}^\omega\) is the Lindel\"of covering property.
+
+\begin{proposition}
+  \(\schStrongSelProp{\mc A}{\mc B}\) is equivalent to
+  \(\plI\notprewin \schStrongSelGame{\mc A}{\mc B}\), and
+  \(\binom{\mc A}{\mc B}^\omega\) is equivalent to
+  \(\plI\notconwin \schStrongSelGame{\mc A}{\mc B}\).
+\end{proposition}
+
+\begin{proof}
+  The first equivalence is direct from their defintions.
+
+  To see the second,
+  assume \(\binom{\mc A}{\mc B}^\omega\). Then given a constant strategy
+  \(A\in\mc A\) for \(\plI\), \(\plII\) uses \(\binom{\mc A}{\mc B}^\omega\) to
+  choose \(B=\setB{b_n}{n<\omega}\subseteq A\) where \(B\in\mc B\); thus
+  playing \(b_n\) in round
+  \(n\) defeats \(\plI\)'s constant strategy.
+
+  Likewise, assuming 
+  \(\plI\notconwin \schStrongSelGame{\mc A}{\mc B}\), for each constant strategy
+  \(A\in\mc A\) for \(\plI\) there must be a counterattack playing \(b_n\in A\)
+  during each round \(n\) such that \(\setB{b_n}{n<\omega}\in\mc B\); this witnesses
+  \(\binom{\mc A}{\mc B}^\omega\).
+\end{proof}
+
+The goal of this paper is to characterize when two games are ``dual'' in the following
 senses.
+
+\begin{definition}
+  A pair of games \(G(X),H(X)\) defined for a topological space \(X\)
+  are \term{tactical information dual} if both
+  of the following hold.
+  \begin{itemize}
+    \item \(I\conwin G(X)\) if and only if \(II\tactwin H(X)\).
+    \item \(II\tactwin G(X)\) if and only if \(I\conwin H(X)\).
+  \end{itemize}
+\end{definition}
 
@@
 
+\begin{definition}
+  A pair of games \(G(X),H(X)\) defined for a topological space \(X\)
+  are \term{dual} if they are tactial, Markov, and perfect information
+  dual.
+\end{definition}
+
 \section{Main Results}
 
-The following four theorems demonstrate that reflections characterize
-dual selection games for both perfect information strategies and
+The following six theorems demonstrate that reflections characterize
+dual selection games for perfect information strategies and
 certain limited information strategies.
 
-The duality of the Rothberger game \(\schStrongSelGame{\mc O_X}{\mc O_X}\)
+For example,
+the duality of the Rothberger game \(\schStrongSelGame{\mc O_X}{\mc O_X}\)
 and the point-open game on \(X\) for perfect information strategies
@@
 for Markov-information strategies by Clontz and Holshouser in
-[TODO cite]. These proofs may be generalized as follows.
+\cite{CLONTZ2019106815}. These proofs may be generalized as follows.
+
+\begin{theorem}
+  Let \(\mc R\) be a reflection of \(\mc A\).
+
+  Then
+  \(\plI\conwin\schStrongSelGame{\mc A}{\mc B}\) if and only if
+  \(\plII\tactwin\schStrongSelGame{\mc R}{\neg\mc B}\).
+\end{theorem}
+
+\begin{proof}
+  Let \(A\) witness 
+  \(\plI\conwin\schStrongSelGame{\mc A}{\mc B}\).
+  Since \(A\in\mc A\),
+  \(\ran{\tau}\subseteq A\)
+  for some \(\tau\in\mathbf C(\mc R)\). 
+  Suppose \(R_n\in \mc R\) for all \(n<\omega\).
+  Note that since \(A\) is winning and 
+  \(\tau(R_n)\in\ran{\tau}\subseteq A\),
+  \(\{\tau(R_n):n<\omega\}\not\in\mc B\). Thus \(\tau\) witnesses
+  \(\plII\tactwin\schStrongSelGame{\mc R}{\neg\mc B}\).
+
+  Now let \(\sigma\) witness
+  \(\plII\tactwin\schStrongSelGame{\mc R}{\neg\mc B}\).
+  Then \(\sigma\in\mathbf C(\mc R)\) and we may let
+  \(A=\ran{\sigma}\in\mc A\). 
+  Suppose that \(B_n\in A=\ran{\sigma}\) for
+  all \(n<\omega\). Choose \(R_n\in\mc R\) such that 
+  \(B_n=\sigma(R_n)\). Since \(\sigma\) is winning,
+  \(\{B_n:n<\omega\}\not\in\mc B\). Thus \(A\) witnesses
+  \(\plI\conwin\schStrongSelGame{\mc A}{\mc B}\).
+\end{proof}
+
+\begin{theorem}
+  Let \(\mc R\) be a reflection of \(\mc A\).
+
+  Then
+  \(\plII\tactwin\schStrongSelGame{\mc A}{\mc B}\) if and only if
+  \(\plI\conwin\schStrongSelGame{\mc R}{\neg\mc B}\).
+\end{theorem}
+
+\begin{proof}
+  Let \(\sigma\) witness 
+  \(\plII\tactwin\schStrongSelGame{\mc A}{\mc B}\).
+  Suppose that for each \(R\in\mc R\),
+  there was \(g(R)\in R\) such that for all \(A\in \mc A\),
+  \(\sigma(A)\not=g(R)\). Then \(g\in\mathbf C(\mc R)\)
+  and \(\ran g\in\mc A\),
+  thus \(\sigma(\ran g)\not=g(R)\) for all \(R\in\mc R\),
+  a contradiction.
+
+  So choose \(R\in\mc R\) such that for all \(r\in R\)
+  there exists \(A_r\in\mc A\) such that \(\sigma(A_r)=r\).
+  It follows that when \(r_n\in R\) for \(n<\omega\),
+  \(\{r_n:n<\omega\}=\{\sigma(A_{r_n}):n<\omega\}\in B\),
+  so \(R\) witnesses
+  \(\plI\conwin\schStrongSelGame{\mc R}{\neg\mc B}\).
+
+  Now let \(R\) witness 
+  \(\plI\conwin\schStrongSelGame{\mc R}{\neg\mc B}\).
+  Then \(R\in\mc R\), so for \(A\in\mc A\), let
+  \(f_A\in\mathbf C(\mc R)\) satisfy \(\ran{f_A}\subseteq A\),
+  and let \(\tau(A)=f_A(R)\in A\cap R\).
+  Then if \(A_n\in\mc A\) for \(n<\omega\), \(\tau(A_n)\in R\),
+  so \(\{\tau(A_n):n<\omega\}\in\mc B\).
+  Thus \(\tau\) witnesses
+  \(\plII\tactwin\schStrongSelGame{\mc A}{\mc B}\).
+\end{proof}
 
@@
 
-\begin{corollary}
+\begin{corollary}\label{mainResult}
   If \(\mc R\) is a reflection of \(\mc A\),
   then \(\schStrongSelGame{\mc A}{\mc B}\) and \(\schStrongSelGame{\mc R}{\neg\mc B}\)
-  are both perfect information dual and Markov information dual.
+  are  dual.
 \end{corollary}
@@
 
-While these notions were defined in terms of a particular basis, the reader may verify the the following.
+%While these notions were defined in terms of a particular basis, the reader may verify the the following.
+%
+%\begin{proposition}
+%  Let \(\mc A'\) be a selection basis for \(\mc A\).
+%  \begin{itemize}
+%    \item \(\plI\win\schStrongSelGame{\mc A}{\mc B}\Leftrightarrow\plI\win\schStrongSelGame{\mc A'}{\mc B}\).
+%    \item \(\plI\prewin\schStrongSelGame{\mc A}{\mc B}\Leftrightarrow\plI\prewin\schStrongSelGame{\mc A'}{\mc B}\).
+%    \item \(\plII\win\schStrongSelGame{\mc A}{\mc B}\Leftrightarrow\plII\win\schStrongSelGame{\mc A'}{\mc B}\).
+%    \item \(\plII\markwin\schStrongSelGame{\mc A}{\mc B}\Leftrightarrow\plII\markwin\schStrongSelGame{\mc A'}{\mc B}\).
+%  \end{itemize}
+%\end{proposition}
+%
+%\begin{proposition}
+%  Each selection set in Definition \ref{selectionSets} is a selection basis for the set
+%  defined by replacing \(\mc T_X\) with the set of all nonempty open sets in \(X\).
+%\end{proposition}
+%
+%As such, the choice of topological basis is irrelevant when playing selection games using these sets.
 
-\begin{proposition}
-  Let \(\mc A'\) be a selection basis for \(\mc A\).
-  \begin{itemize}
-    \item \(\plI\win\schStrongSelGame{\mc A}{\mc B}\Leftrightarrow\plI\win\schStrongSelGame{\mc A'}{\mc B}\).
-    \item \(\plI\prewin\schStrongSelGame{\mc A}{\mc B}\Leftrightarrow\plI\prewin\schStrongSelGame{\mc A'}{\mc B}\).
-    \item \(\plII\win\schStrongSelGame{\mc A}{\mc B}\Leftrightarrow\plII\win\schStrongSelGame{\mc A'}{\mc B}\).
-    \item \(\plII\markwin\schStrongSelGame{\mc A}{\mc B}\Leftrightarrow\plII\markwin\schStrongSelGame{\mc A'}{\mc B}\).
-  \end{itemize}
-\end{proposition}
-
-\begin{proposition}
-  Each selection set in Definition \ref{selectionSets} is a selection basis for the set
-  defined by replacing \(\mc T_X\) with the set of all nonempty open sets in \(X\).
-\end{proposition}
-
-As such, the choice of topological basis is irrelevant when playing selection games using these sets.
-
-We may now establish (or re-establish) the following dual games.
+We may now establish the following dual games.
 
@@
 \begin{proof}
-  For every open cover \(\mc U\), the corresponding choice function \(f\in\mathbf C(\mc P_X)\) is simply
-  the witness that \(x\in f(\mc T_{X,x})\in\mc U\).
+  For every basic open cover \(\mc U\), the corresponding choice function \(f_{\mc U}\in\mathbf C(\mc P_X)\) is simply
+  the witness that for each \(\mc T_{X,x}\in\mc P_X\), there exists \(f_{\mc U}(\mc T_{X,x})\in\mc U\) such that
+  \(x\in f_{\mc U}(\mc T_{X,x})\).
 \end{proof}
 
-\begin{corollary}
-  \(\schStrongSelGame{\mc O_X}{\mc B}\) and \(\schStrongSelGame{\mc P_X}{\neg\mc B}\) are perfect-information
-  and Markov-information dual.
+\begin{corollary}\label{coverSel1}
+  \(\schStrongSelGame{\mc O_X}{\mc B}\) and \(\schStrongSelGame{\mc P_X}{\neg\mc B}\) are dual.
 \end{corollary}
@@
 of each chosen point, and \(\plI\) wins if \(\plII\)'s choices are a cover.
-So this was simply the classic result that the Rothberger game and
-point-open game are perfect-information dual \cite{MR0493925}, and the more recent result that
-these games are Markov-information dual [TODO cite clontzHols].
+So this encapsulates the classic result that the Rothberger game and
+point-open game are perfect-information dual \cite{MR0493925}, the more recent result that
+these games are Markov-information dual \cite{CLONTZ2019106815}, and the quickly verified fact that
+a Lindel\"of space \(X\) may be characterized as follows: for each neighborhood assignment (i.e.
+tactic for \(\plII\) in \(PO(X)\)) there exists a countable subset
+of \(X\) such that its neighborhoods cover the space.
 
@@
 \begin{proof}
-  For every \(\omega\)-cover \(\mc U\), the corresponding choice function \(f\in\mathbf C(\mc F_X)\) is simply
-  the witness that \(F\subseteq f(\mc T_{X,F})\in\mc U\).
+  For every basic open \(\omega\)-cover \(\mc U\), the corresponding choice function \(f_{\mc U}\in\mathbf C(\mc F_X)\) is simply
+  the witness that for each \(\mc T_{X,F}\in\mc F_X\), there exists \(f_{\mc U}(\mc T_{X,F})\in\mc U\) such that
+  \(F\subseteq f_{\mc U}(\mc T_{X,F})\).
 \end{proof}
 
-\begin{corollary}
-  \(\schStrongSelGame{\Omega_X}{\mc B}\) and \(\schStrongSelGame{\mc F_X}{\neg\mc B}\) are perfect-information
-  and Markov-information dual.
+\begin{corollary}\label{coverSel2}
+  \(\schStrongSelGame{\Omega_X}{\mc B}\) and \(\schStrongSelGame{\mc F_X}{\neg\mc B}\) are dual.
 \end{corollary}
@@
 of each chosen finite set, and \(\plI\) wins if \(\plII\)'s choices are an \(\omega\)-cover.
-These games were shown to be dual in [TODO cite clontzHols].
+These games were directly shown to be Markov and perfect-information dual in \cite{CLONTZ2019106815}.
 
@@
 \begin{proof}
-  For every dense \(D\), the corresponding choice function \(f\in\mathbf C(\mc T_X)\) is simply
-  the witness that \(f(U)\in U\cap D\).
+  For every dense \(D\), the corresponding choice function \(f_D\in\mathbf C(\mc T_X)\) is simply
+  the witness that for each \(U\in\mc T_X\), there exists \(f_D(U)\in U\cap D\).
 \end{proof}
@@
 that these games are perfect-information dual; Clontz and Holshouser previously showed these were Markov-information
-dual in the case that \(X=C_p(Y)\) [TODO cite].
+dual in the case that \(X=C_p(Y)\)  \cite{CLONTZ2019106815}.
 
 In the case that \(\mc B=D_X\), then \(\schStrongSelGame{\mc D_X}{\mc D_X}\) is the strong selective
-separability game introduced in \cite{MR1711901}, and \(\schStrongSelGame{\mc T_X}{\neg\mc D_X}\) is the
+separability game introduced by Scheepers 
+in \cite{MR1711901}, and \(\schStrongSelGame{\mc T_X}{\neg\mc D_X}\) is the
 point-picking game of Berner and Juh\'asz defined in \cite{MR775687}. Scheepers showed that these
@@
 \begin{proof}
-  For every set \(Y\) with limit point \(x\), the corresponding choice function \(f\in\mathbf C(\mc T_{X,x})\) is simply
-  the witness that \(f(U)\in U\cap Y\).
+  For every set \(Y\) with limit point \(x\), the corresponding choice function \(f_Y\in\mathbf C(\mc T_{X,x})\) is simply
+  the witness that for each \(U\in\mc T_{X,x}\), there exists \(f_Y(U)\in U\cap Y\).
 \end{proof}
@@
 \begin{corollary}
-  \(\schStrongSelGame{\Omega_{X,x}}{\mc B}\) and \(\schStrongSelGame{\mc T_{X,x}}{\neg\mc B}\) are perfect-information
-  and Markov-information dual.
+  \(\schStrongSelGame{\Omega_{X,x}}{\mc B}\) and \(\schStrongSelGame{\mc T_{X,x}}{\neg\mc B}\) are dual.
 \end{corollary}
@@
   As shown in \cite{MR510910},
-  a space is \(w\) at \(x\), that is, \(\plII\notwin\schStrongSelGame{\mc T_{X,x}}{\neg\Gamma_{X,x}}\) 
-  if and only if \(\plI\notprewin\schStrongSelGame{\Omega_{X,x}}{\Gamma_{X,x}}\) for all \(x\in X\).
+  \(\plII\notwin\schStrongSelGame{\mc T_{X,x}}{\neg\Gamma_{X,x}}\) (i.e. \(X\) is \(w\) in the
+  terminology of that paper)
+  if and only if \(\plI\notprewin\schStrongSelGame{\Omega_{X,x}}{\Gamma_{X,x}}\).
+  The result follows as 
+  \(\schStrongSelGame{\mc T_{X,x}}{\neg\Gamma_{X,x}}\) and
+  \(\schStrongSelGame{\Omega_{X,x}}{\Gamma_{X,x}}\) are dual.
 \end{proof}
@@
 
-%Finally, consider the following result from \cite{2016arXiv161004800C}.
-%
-%\begin{proposition}
-%  
-%\end{proposition}
+We conclude by noting how Corollary \ref{mainResult}
+was used by the authors of \cite{MR3991109} to
+easily strengthen Propositions \ref{coverSel1} and \ref{coverSel2}
+while this paper was still in preparation.
+
+\begin{definition}
+Let \(\mc Q\) be a collection of subsets of a topological space \(X\).
+Then \(\mc O_{X,\mc Q}\) is the collection of basic open covers \(\mc U\) such that for
+each \(Q\in\mc Q\), there is \(U\in\mc U\) with \(Q\subseteq U\).
+Likewise, \(\mc N_{X,\mc Q}=\{\mc T_{X,Q}:Q\in\mc Q\}\) where each \(\mc T_{X,Q}\) collects all
+basic open sets \(U\) such that \(Q\subseteq U\). 
+\end{definition}
+
+In particular, \(\mc O_{X,[X]^1}=\mc O_X\) and \(\mc O_{X,[X]^{<\omega}}=\Omega_X\).
+Likewise \(\mc N_{X,[X]^1}=\mc P_X\) and \(\mc N_{X,[X]^{<\omega}}=\mc F_X\).
+
+\begin{theorem}[\cite{MR3991109}]
+  The games \(\schStrongSelGame{\mc O_{X,\mc Q}}{\mc B}\) and
+  \(\schStrongSelGame{\mc N_{X,\mc Q}}{\neg\mc B}\) are dual.
+\end{theorem}
+
+\begin{proof}
+  This is immediate as \(\mc N_{X,\mc Q}\) reflects \(\mc O_{X,\mc Q}\). 
+  To see this, for each
+  \(\mc U\in\mc O_{X,\mc Q}\), choose \(f_{\mc U}\in\mathbf C(\mc N_{X,\mc Q})\)
+  satisfying that for each \(\mc T_{X,Q}\in\mc N_{X,\mc Q}\), there exists
+  \(f_{\mc U}(\mc T_{X,Q})\in\mc U\) such that \(Q\subseteq f_{\mc U}(\mc T_{X,Q})\).
+\end{proof}
 
@@
 
+Let 
+\(\Gamma_X=\{\mc U\subseteq\mc T_X:\forall x\in X(\mc U\setminus\mc T_{X,x}\in[T_X]^{<\aleph_0})\}\). 
+Such \(\gamma\)-covers are related to the convergent sequences of \(C_p(X)\) (that is,
+\(\Gamma_{C_p(X),\mathbf 0}\) as defined in Definition \ref{selectionSets}),
+see e.g. \cite{BUKOVSKY2019239}.
+
 \begin{question}
   Does there exist a natural reflection for \(\Gamma_{X,x}\)
-  or \(\Gamma_X=\{\mc U\subseteq\mc T_X:\forall x\in X(\mc U\setminus\mc T_{X,x}\in[T_X]^{<\aleph_0})\}\)?
+  or \(\Gamma_X\)?
 \end{question}
 
+The game \(\schSelGame{\mc A}{\mc B}\) is defined analogously to
+\(\schStrongSelGame{\mc A}{\mc B}\), except \(\plII\) may choose a finite subset each round
+rather than a single set.
+
 \begin{question}
-  Can these results be extended for \(\schSelGame{\mc A}{\mc B}\)?
+  Do there exist any duality results for \(\schSelGame{\mc A}{\mc B}\) similar to the technique
+  of reflections?
 \end{question}

### 2019-10-22 articles/selection-alpha-games/article.tex
characterize sequence-like alpha properties as selection principles

\documentclass{amsart}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}

\usepackage{tikz}
\usetikzlibrary{arrows}

\usepackage{../../clontzDefinitions}

\renewcommand{\vec}{\mathbf}

      \theoremstyle{plain}
      \newtheorem{theorem}{Theorem}
      \newtheorem{lemma}[theorem]{Lemma}
      \newtheorem{corollary}[theorem]{Corollary}
      \newtheorem{proposition}[theorem]{Proposition}
      \newtheorem{conjecture}[theorem]{Conjecture}
      \newtheorem{question}[theorem]{Question}
      \newtheorem{claim}[theorem]{Claim}

      \theoremstyle{definition}
      \newtheorem{definition}[theorem]{Definition}
      \newtheorem{notation}[theorem]{Notation}
      \newtheorem{example}[theorem]{Example}
      \newtheorem{game}[theorem]{Game}

      \theoremstyle{remark}
      \newtheorem{remark}[theorem]{Remark}

      \theoremstyle{plain}
      \newtheorem*{theorem*}{Theorem}
      \newtheorem*{lemma*}{Lemma}
      \newtheorem*{corollary*}{Corollary}
      \newtheorem*{proposition*}{Proposition}
      \newtheorem*{conjecture*}{Conjecture}
      \newtheorem*{question*}{Question}
      \newtheorem*{claim*}{Claim}

      \theoremstyle{definition}
      \newtheorem*{definition*}{Definition}
      \newtheorem*{example*}{Example}
      \newtheorem*{game*}{Game}

      \theoremstyle{remark}
      \newtheorem*{remark*}{Remark}

\usepackage{lineno}
\linenumbers

\begin{document}

\title{Selection games and Arhangelskii's convergence principles}

\author{Steven Clontz}
\address{Department of Mathematics and Statistics,
The University of South Alabama,
Mobile, AL 36688}
\email{sclontz@southalabama.edu}

\keywords{Selection principle, selection game,
\(\alpha_i\) property, convergence}

%\subjclass[2010]{54D20, 54D45, 91A44}

\begin{abstract}
We prove the things.
\end{abstract}

\maketitle

%
%\section{Introduction}
%
%\begin{definition}
%  The \term{selection game} \(\schStrongSelGame{\mc A}{\mc B}\) 
%  is an \(\omega\)-length game involving Players \(\plI\) and \(\plII\). 
%  During round \(n\), \(\plI\) chooses
%  \(A_n\in\mc A\), followed by \(\plII\) choosing \(B_n\in A_n\).
%  Player \(\plII\) wins in the case that \(\{B_n:n<\omega\}\in\mc B\),
%  and Player \(\plI\) wins otherwise.
%\end{definition}
%
%\begin{definition}
%  The \term{selection game} \(\schSelGame{\mc A}{\mc B}\) 
%  is an \(\omega\)-length game involving Players \(\plI\) and \(\plII\). 
%  During round \(n\), \(\plI\) chooses
%  \(A_n\in\mc A\), followed by \(\plII\) choosing \(B_n\in [A_n]^{<\aleph_0}\).
%  Player \(\plII\) wins in the case that \(\bigcup\{B_n:n<\omega\}\in\mc B\),
%  and Player \(\plI\) wins otherwise.
%\end{definition}
%
\section{Clontz results}

\begin{definition}
Say a collection \(\mc A\) is \term{sequence-like} if it satisfies the following
for each \(A\in\mc A\).
\begin{itemize}
\item \(|A|\geq\aleph_0\).
\item If \(A'\subseteq A\) and \(|A'|\geq\aleph_0\), then \(A'\in\mc A\).
\end{itemize}
\end{definition}

\begin{definition}
Let \(\Gamma_X\) be the collection of open \term{\(\gamma\)-covers} \(\mc U\) of \(X\),
that is, infinite open covers of \(X\) such that for each \(x\in X\),
\(\{U\in\mc U:x\in U\}\) is cofinite in \(\mc U\).
\end{definition}

\begin{definition}
Let \(\Gamma_{X,x}\) be the collection of non-trivial sequences \(S\subseteq X\) converging to \(x\),
that is, infinite subsets of \(X\) such that for each neighborhood \(U\) of \(x\),
\(S\cap U\) is cofinite in \(S\).
\end{definition}

It follows that \(\Gamma_X,\Gamma_{X,x}\) are both sequence-like.

\begin{theorem}
Let \(\mc B\) be sequence-like. Then \(\alpha_1(\mc A,\mc B)\) holds if and only
if \(\plI\notprewin G_{cf}(\mc A,\mc B)\).
\end{theorem}

\begin{proof}
We first assume \(\alpha_1(\mc A,\mc B)\) and let \(A_n\in\mc A\) for \(n<\omega\)
define a predetermined strategy for \(\plI\). By \(\alpha_1(\mc A,\mc B)\), we
immediately obtain \(B\in\mc B\) such that \(|A_n\setminus B|<\aleph_0\). Thus
\(B_n=A_n\cap B\) is a cofinite choice from \(A_n\), and 
\(B'=\bigcup\{B_n:n<\omega\}\) is an infinite subset of \(B\),
so \(B'\in\mc B\). Thus \(\plII\) may defeat \(\plI\) by choosing
\(B_n\subseteq A_n\) each round, witnessing \(\plI\notprewin G_{cf}(\mc A,\mc B)\).

On the other hand, let \(\plI\notprewin G_{cf}(\mc A,\mc B)\). Given \(A_n\in\mc A\)
for \(n<\omega\), we note that \(\plII\) may choose a cofinite subset \(B_n\subseteq A_n\)
such that \(B=\bigcup\{B_n:n<\omega\}\in\mc B\). Then \(B\) witnesses \(\alpha_1(\mc A,\mc B)\)
since \(|A_n\setminus B|\leq|A_n\setminus B_n|\leq\aleph_0\).
\end{proof}

\begin{theorem}
Let \(\mc A,\mc B\) be sequence-like. Then \(\alpha_2(\mc A,\mc B)\) holds if and only
if \(\plI\notprewin G_1(\mc A,\mc B)\).
\end{theorem}

\begin{proof}
We first assume \(\alpha_2(\mc A,\mc B)\) and let \(A_n\in\mc A\) for \(n<\omega\)
define a predetermined strategy for \(\pl I\).
We may apply \(\alpha_2(\mc A,\mc B)\) to choose \(B\in\mc B\) such that
\(|A_n\cap B|\geq\aleph_0\). We may then choose \(a_n\in(A_n\cap B)\setminus\{a_i:i<n\}\)
for each \(n<\omega\). It follows that \(B'=\{a_n:n<\omega\}\in\mc B\) since
\(B'\) is an infinite subset of \(B\in\mc B\); therefore \(A_n\) does not define
a winning predetermined strategy for \(\plI\).

Now suppose \(\plI\notprewin G_1(\mc A,\mc B)\). Given \(A_n\in\mc A\) for \(n<\omega\),
first choose \(A_n'=\{a_{n,j}:j<\omega\}\subseteq A_n\) such that \(j<k\) implies
\(a_{n,j}\not=a_{n,k}\),
and then let \(A_{n,m}=\{a_{n,j}:m\leq j<\omega\}\), noting \(A_{n,m}\in\mc A\) since
\(A_{n,m}\) is an infinite subset of \(A_n\in\mc A\). Finally choose
some \(\theta:\omega\to\omega\) such that \(|\theta^{\leftarrow}(n)|=\aleph_0\) for
each \(n<\omega\).

Since playing \(A_{\theta(m),m}\) during round \(m\)
does not define a winning strategy for \(\plI\) in
\(G_1(\mc A,\mc B)\), \(\plII\) may choose \(x_m\in A_{\theta(m),m}\)
such that \(B=\{x_m:m<\omega\}\in\mc B\).
Choose \(i_m<\omega\) for each \(m<\omega\) such that
\(x_m=a_{\theta(m),i_m}\), noting \(i_m\geq m\).
It follows that 
\(A_n\cap B\supseteq\{a_{\theta(m),i_m}:m\in\theta^{\leftarrow}(n)\}\).
Since for each \(m\in\theta^{\leftarrow}(n)\) there exists
\(M\in\theta^{\leftarrow}(n)\) such that \(m\leq i_m<M\leq i_{M}\),
and therefore \(a_{\theta(m),i_m}\not=a_{\theta(m),i_{M}}=a_{\theta(M),i_{M}}\),
we have shown that \(A_n\cap B\) is infinite. Thus \(B\) witnesses
\(\alpha_2(\mc A,\mc B)\).
\end{proof}

\begin{theorem}
Let \(\mc A,\mc B\) be sequence-like. Then \(\alpha_4(\mc A,\mc B)\) holds if and only
if \(\plI\notprewin G_{<2}(\mc A,\mc B)\) if and only if
\(\plI\notprewin G_{fin}(\mc A,\mc B)\).
\end{theorem}

\begin{proof}
We first assume \(\alpha_4(\mc A,\mc B)\) and let \(A_n\in\mc A\) for \(n<\omega\)
define a predetermined strategy for \(\plI\) in 
\(G_{<2}(\mc A,\mc B)\). We then choose
\(A_n'=\{a_{n,j}:j<\omega\}\subseteq A_n\) such that \(j<k\) implies
\(a_{n,j}\not=a_{n,k}\), and then let \(A_n''=A_n'\setminus\{a_{i,j}:i,j<n\}\),
noting \(A_n''\in\mc A\) since it is an infinite subset of \(A_n\).

By applying \(\alpha_4(\mc A,\mc B)\) to \(A_n''\), we obtain \(B\in\mc B\)
such that \(A_n''\cap B\not=\emptyset\) for infintely-many \(n<\omega\).
We then let \(F_n=\emptyset\) when \(A_n''\cap B=\emptyset\), and
\(F_n=\{x_n\}\) for some \(x_n\in A_n''\cap B\) otherwise. Then we will have that
\(B'=\bigcup\{F_n:n<\omega\}\subseteq B\) belongs to \(\mc B\) once we show that
\(B'\) is infinite. To see this, for \(m\leq n<\omega\) note that either \(F_m\) is
empty (and we let \(j_m=0\)) or \(F_m=\{a_{m,j_m}\}\)
for some \(j_m\geq m\); choose \(N<\omega\) such that \(j_m<N\) for all
\(m\leq n\) and \(F_N=\{x_N\}\). Thus \(F_m\not=F_N\) for all \(m\leq n\) since
\(x_{N}\not\in\{a_{i,j}:i,j< N\}\). Thus \(\plII\) may defeat the predetermined
strategy \(A_n\) by playing \(F_n\) each round.

Since \(\plI\notprewin G_{<2}(\mc A,\mc B)\) immediately implies
\(\plI\notprewin G_{fin}(\mc A,\mc B)\), we assume the latter. Given \(A_n\in\mc A\)
for \(n<\omega\), we note this defines a (non-winning) predetermined 
strategy for \(\plI\), so \(\plII\) may choose \(F_n\in[A_n]^{<\aleph_0}\) such that
\(B=\bigcup\{F_n:n<\omega\}\in\mc B\). Since \(B\) is infinite, we note
\(F_n\not=\emptyset\) for infinitely-many \(n<\omega\). Thus \(B\) witnesses
\(\alpha_4(\mc A,\mc B)\) since \(A_n\cap B\supseteq F_n\not=\emptyset\) for
infinitely-many \(n<\omega\).
\end{proof}

\bibliographystyle{plain}
\bibliography{../../bibliography}

\end{document}

### 2019-10-23 articles/selection-alpha-games/article.tex
buncha sequence-like selection game results

@@
 
-It follows that \(\Gamma_X,\Gamma_{X,x}\) are both sequence-like.
+It follows that \(\Gamma_X,\Gamma_{X,x}\) are both sequence-like. We also require
+the following.
+
+\begin{definition}
+Say a collection \(\mc A\) is \term{almost-sequence-like} if
+for each \(A\in\mc A\), there is \(A'\subseteq A\) such that:
+\begin{itemize}
+\item \(|A'|=\aleph_0\).
+\item If \(A''\) is a cofinite subset of \(A'\), then \(A''\in\mc A\).
+\end{itemize}
+\end{definition}
+
+So all sequence-like sets are almost-sequence-like.
 
@@
 \begin{theorem}
-Let \(\mc A,\mc B\) be sequence-like. Then \(\alpha_2(\mc A,\mc B)\) holds if and only
+Let \(\mc A\) be almost-sequence-like and \(\mc B\) be sequence-like. 
+Then \(\alpha_2(\mc A,\mc B)\) holds if and only
 if \(\plI\notprewin G_1(\mc A,\mc B)\).
@@
 Now suppose \(\plI\notprewin G_1(\mc A,\mc B)\). Given \(A_n\in\mc A\) for \(n<\omega\),
-first choose \(A_n'=\{a_{n,j}:j<\omega\}\subseteq A_n\) such that \(j<k\) implies
-\(a_{n,j}\not=a_{n,k}\),
-and then let \(A_{n,m}=\{a_{n,j}:m\leq j<\omega\}\), noting \(A_{n,m}\in\mc A\) since
-\(A_{n,m}\) is an infinite subset of \(A_n\in\mc A\). Finally choose
+first choose \(A_n'\in\mc A\) such that \(A_n'=\{a_{n,j}:j<\omega\}\subseteq A_n\),
+\(j<k\) implies \(a_{n,j}\not=a_{n,k}\),
+and \(A_{n,m}=\{a_{n,j}:m\leq j<\omega\}\in\mc A\).
+Finally choose
 some \(\theta:\omega\to\omega\) such that \(|\theta^{\leftarrow}(n)|=\aleph_0\) for
@@
 \begin{theorem}
-Let \(\mc A,\mc B\) be sequence-like. Then \(\alpha_4(\mc A,\mc B)\) holds if and only
+Let \(\mc A\) be almost-sequence-like and \(\mc B\) be sequence-like. 
+Then \(\alpha_4(\mc A,\mc B)\) holds if and only
 if \(\plI\notprewin G_{<2}(\mc A,\mc B)\) if and only if
@@
 define a predetermined strategy for \(\plI\) in 
-\(G_{<2}(\mc A,\mc B)\). We then choose
-\(A_n'=\{a_{n,j}:j<\omega\}\subseteq A_n\) such that \(j<k\) implies
-\(a_{n,j}\not=a_{n,k}\), and then let \(A_n''=A_n'\setminus\{a_{i,j}:i,j<n\}\),
-noting \(A_n''\in\mc A\) since it is an infinite subset of \(A_n\).
+\(G_{<2}(\mc A,\mc B)\). We then may choose \(A_n'\in\mc A\) where
+\(A_n'=\{a_{n,j}:j<\omega\}\subseteq A_n\), \(j<k\) implies
+\(a_{n,j}\not=a_{n,k}\), and \(A_n''=A_n'\setminus\{a_{i,j}:i,j<n\}\in\mc A\).
 
@@
 
+\begin{theorem}
+Let \(\mc B\) be sequence-like. Then \(\plI\prewin G_{<2}(\mc A,\mc B)\)
+if and only if \(\plI\prewin G_{fin}(\mc A,\mc B)\).
+\end{theorem}
+
+\begin{proof}
+Assume \(\bigcup\mc A\) is well-ordered.
+Given a winning predetermined strategy \(A_n\) for \(\plI\) in
+\(G_{<2}(\mc A,\mc B)\), consider \(F_n\in[A_n]^{<\aleph_0}\). We set
+\[
+  F_n^*
+=
+  \begin{cases}
+    \emptyset
+      & \text{ if }
+    F_n\setminus\bigcup\{F_m:m<n\}=\emptyset
+      \\
+    \{\min(
+      F_n\setminus\bigcup\{F_m:m<n\}
+    )\}
+      & \text{ otherwise}
+  \end{cases}
+\]
+Since \(|F_n|<2\), we have that \(\bigcup\{F_n^*:n<\omega\}\not\in\mc B\).
+In the case that \(\bigcup\{F_n^*:n<\omega\}\) is finite, we immediately
+see that \(\bigcup\{F_n:n<\omega\}\) is also finite and therefore not
+in \(\mc B\). Otherwise \(\bigcup\{F_n^*:n<\omega\}\not\in\mc B\)
+is an infinite subset of \(\bigcup\{F_n:n<\omega\}\), and thus
+\(\bigcup\{F_n:n<\omega\}\not\in\mc B\) too. Therefore
+\(A_n\) is a winning predetermined strategy for \(\plI\) in
+\(G_{fin}(\mc A,\mc B)\) as well.
+\end{proof}
+
+\begin{theorem}
+Let \(\mc B\) be sequence-like. Then \(\plI\win G_{<2}(\mc A,\mc B)\)
+if and only if \(\plI\win G_{fin}(\mc A,\mc B)\).
+\end{theorem}
+
+\begin{proof}
+Assume \(\bigcup\mc A\) is well-ordered.
+Suppose \(\plI\win G_{<2}(\mc A,\mc B)\) is witnessed by the strategy
+\(\sigma\). Let \(\tuple{}^\star=\tuple{}\), and for 
+\(s\concat\tuple{F}\in([\bigcup\mc A]^{<\aleph_0})^{<\omega}
+\setminus\{\tuple{}\}\) let 
+\[
+  (s\concat\tuple{F})^\star
+=
+  \begin{cases}
+    s^\star\concat\tuple{\emptyset}
+      & \text{ if }
+    F\setminus\bigcup\ran{s}=\emptyset
+      \\
+    s^\star\concat\tuple{
+      \{\min(F\setminus\bigcup\ran{s})\}
+    }
+      & \text{ otherwise}
+  \end{cases}
+\]
+
+We then define the strategy \(\tau\) for \(\plI\) in \(G_{fin}(\mc A,\mc B)\)
+by \(\tau(s)=\sigma(s^\star)\). Then given any counterattack
+\(\alpha\in([\bigcup\mc A]^{<\aleph_0})^\omega\) by \(\plII\) played against 
+\(\tau\), we note that \(\alpha^*=\bigcup\{(\alpha\rest n)^*:n<\omega\}\)
+is a counterattack to \(\sigma\), and thus loses.
+This means \(B=\bigcup\ran{\alpha^*}\not\in\mc B\).
+
+We consider two cases. The first is the case that \(\bigcup\ran{\alpha^*}\)
+is finite. Noting that \(\alpha^*(m)\cap\alpha^*(n)=\emptyset\) whenever
+\(m\not=n\), there exists \(N<\omega\) such that 
+\(\alpha^*(n)=\emptyset\) for all \(n>N\). As a result,
+\(\bigcup\ran{\alpha}=\bigcup\ran{\alpha\rest n}\), and thus
+\(\bigcup\ran{\alpha}\) is finite, and therefore not in \(\mc B\).
+
+In the other case, \(\bigcup\ran{\alpha^*}\not\in\mc B\) is an 
+infinite subset of \(\bigcup\ran{\alpha}\), and therefore 
+\(\bigcup\ran{\alpha}\not\in\mc B\) as well. Thus we have shown
+that \(\tau\) is a winning strategy for \(\plI\) in
+\(G_{fin}(\mc A,\mc B)\).
+\end{proof}
+
+\begin{theorem}
+Let \(\mc B\) be sequence-like. Then \(\plII\win G_{<2}(\mc A,\mc B)\)
+if and only if \(\plII\win G_{fin}(\mc A,\mc B)\).
+\end{theorem}
+
+\begin{theorem}
+Let \(\mc B\) be sequence-like. Then \(\plII\markwin G_{<2}(\mc A,\mc B)\)
+if and only if \(\plII\markwin G_{fin}(\mc A,\mc B)\).
+\end{theorem}
+
+\begin{theorem}\label{pawlikowskii}
+Let \(\mc A\) be almost-sequence-like and \(\mc B\) be sequence-like.
+Then \(\plI\win G_{fin}(\mc A,\mc B)\) if and only if
+\(\plI\prewin G_{fin}(\mc A,\mc B)\).
+\end{theorem}
+
+\begin{proof}
+We assume \(\plI\win G_{fin}(\mc A,\mc B)\).
+As \(\mc A\) is almost-sequence-like, there is a strategy \(\sigma\)
+witnessing \(\plI\win G_{fin}(\mc A,\mc B)\) where
+\(|\sigma(s)|=\aleph_0\) and \(\sigma(s)\cap\bigcup\ran{s}=\emptyset\)
+(that is, \(\sigma\) never replays the choices of \(\plII\))
+for all partial plays \(s\) by \(\plII\).
+
+For each \(s\in\omega^{<\omega}\), suppose \(F_{s\rest m}\in[\bigcup A]^{<\aleph_0}\)
+is defined for each \(0<m\leq|s|\).
+Then let \(s^\star:|s|\to[\bigcup\mc A]^{<\aleph_0}\) be defined by
+\(s^\star(m)=F_{s\rest m+1}\), and define \(\tau':\omega^{<\omega}\to\mc A\)
+by \(\tau'(s)=\sigma(s^\star)\). Finally, set 
+\([\sigma(s^\star)]^{<\aleph_0}=\{F_{s\concat\tuple{n}}:n<\omega\}\), and
+for some bijection \(b:\omega^{<\omega}\to\omega\) let \(\tau(n)=\tau'(b(n))\)
+be a predetermined strategy for \(\plI\) in \(G_{fin}(\mc A,\mc B)\).
+
+Suppose \(\alpha\) is a counterattack by \(\plII\) against \(\tau\), so 
+\[
+  \alpha(n)
+    \in
+  [\tau(n)]^{<\aleph_0}
+    =
+  [\tau'(b(n))]^{<\aleph_0}
+    =
+  [\sigma(b(n)^\star)]^{<\aleph_0}
+\]
+It follows that \(\alpha(n)=F_{b(n)\concat\tuple{m}}\) for some \(m<\omega\).
+In particular, there is some infinite subset \(W\subseteq\omega\) and \(f\in\omega^\omega\)
+such that \(\{\alpha(n):n\in W\}=\{F_{f\rest n+1}:n<\omega\}\).
+Note here that \((f\rest n+1)^\star=(f\rest n)^\star\concat\tuple{F_{f\rest n+1}}\).
+This shows that \(F_{f\rest n+1}\in[\sigma((f\rest n)^\star)]^{<\aleph_0}\) 
+is an attempt by \(\plII\) to defeat \(\sigma\), which fails. Thus 
+\(\bigcup\{F_{f\rest n+1}:n<\omega\}=\bigcup\{\alpha(n):n\in W\}\not\in\mc B\),
+and since this set is infinite (as \(\sigma\) prevents \(\plII\)
+from repeating choices) we have \(\bigcup\{\alpha(n):n<\omega\}\not\in\mc B\) too.
+Therefore \(\tau\) is winning.
+\end{proof}
+
+\begin{proposition}\label{auto-asl}
+Let \(\mc B\) be sequence-like, \(\mc A\subseteq\mc B\),
+and \(\plI\notprewin G_{fin}(\mc A,\mc B)\). Then
+\(\mc A\) is almost-sequence-like.
+\end{proposition}
+\begin{proof}
+Let \(A\in\mc A\), and for all \(n<\omega\) let \(A_n=A\).
+Then \(A_n\) is not a winning predetermined strategy for
+\(\plI\), so \(\plII\) may choose finite subsets
+\(B_n\subseteq A_n\) such that \(A_n'\bigcup\{B_n:n<\omega\}\in\mc B\subseteq\mc A\).
+
+It follows that \(|A_n'|=\aleph_0\), and for any infinite subset
+\(A_n''\subseteq A_n'\) (in particular, any cofinite subset),
+\(A_n''\in\mc B\subseteq\mc A\). Thus \(\mc A\) is almost-sequence-like.
+\end{proof}
+
+\begin{corollary}
+Let \(\mc B\) be sequence-like and \(\mc A\subseteq\mc B\).
+Then \(\plI\win G_{fin}(\mc A,\mc B)\) if and only if
+\(\plI\prewin G_{fin}(\mc A,\mc B)\).
+\end{corollary}
+\begin{proof}
+Assuming \(\plI\notprewin G_{fin}(\mc A,\mc B)\), we have
+\(\plI\notwin G_{fin}(\mc A,\mc B)\) by Proposition \ref{auto-asl}
+and Theorem \ref{pawlikowskii}.
+\end{proof}
+
 \bibliographystyle{plain}

### 2019-10-30 articles/selection-alpha-games/article.tex
several selection/arhangelskii updates

@@
 \begin{definition}
-Say a collection \(\mc A\) is \term{sequence-like} if it satisfies the following
+Say a collection \(\mc A\) is \term{\(\Gamma\)-like} if it satisfies the following
 for each \(A\in\mc A\).
@@
 
-It follows that \(\Gamma_X,\Gamma_{X,x}\) are both sequence-like. We also require
+It follows that \(\Gamma_X,\Gamma_{X,x}\) are both \(\Gamma\)-like. We also require
 the following.
@@
 \begin{definition}
-Say a collection \(\mc A\) is \term{almost-sequence-like} if
+Say a collection \(\mc A\) is \term{almost-\(\Gamma\)-like} if
 for each \(A\in\mc A\), there is \(A'\subseteq A\) such that:
@@
 
-So all sequence-like sets are almost-sequence-like.
+So all \(\Gamma\)-like sets are almost-\(\Gamma\)-like.
 
 \begin{theorem}
-Let \(\mc B\) be sequence-like. Then \(\alpha_1(\mc A,\mc B)\) holds if and only
+Let \(\mc B\) be \(\Gamma\)-like. Then \(\alpha_1(\mc A,\mc B)\) holds if and only
 if \(\plI\notprewin G_{cf}(\mc A,\mc B)\).
@@
 \begin{theorem}
-Let \(\mc A\) be almost-sequence-like and \(\mc B\) be sequence-like. 
+Let \(\mc A\) be almost-\(\Gamma\)-like and \(\mc B\) be \(\Gamma\)-like. 
 Then \(\alpha_2(\mc A,\mc B)\) holds if and only
@@
 \begin{theorem}
-Let \(\mc A\) be almost-sequence-like and \(\mc B\) be sequence-like. 
+Let \(\mc A\) be almost-\(\Gamma\)-like and \(\mc B\) be \(\Gamma\)-like. 
 Then \(\alpha_4(\mc A,\mc B)\) holds if and only
@@
 \begin{theorem}
-Let \(\mc B\) be sequence-like. Then \(\plI\prewin G_{<2}(\mc A,\mc B)\)
+Let \(\mc B\) be \(\Gamma\)-like. Then \(\plI\prewin G_{<2}(\mc A,\mc B)\)
 if and only if \(\plI\prewin G_{fin}(\mc A,\mc B)\).
@@
 \]
-Since \(|F_n|<2\), we have that \(\bigcup\{F_n^*:n<\omega\}\not\in\mc B\).
+Since \(|F_n^*|<2\), we have that \(\bigcup\{F_n^*:n<\omega\}\not\in\mc B\).
 In the case that \(\bigcup\{F_n^*:n<\omega\}\) is finite, we immediately
@@
 \begin{theorem}
-Let \(\mc B\) be sequence-like. Then \(\plI\win G_{<2}(\mc A,\mc B)\)
+Let \(\mc B\) be \(\Gamma\)-like. Then \(\plI\win G_{<2}(\mc A,\mc B)\)
 if and only if \(\plI\win G_{fin}(\mc A,\mc B)\).
@@
 
-\begin{theorem}
-Let \(\mc B\) be sequence-like. Then \(\plII\win G_{<2}(\mc A,\mc B)\)
-if and only if \(\plII\win G_{fin}(\mc A,\mc B)\).
-\end{theorem}
+We further note that the above proof technique could be
+used to establish that perfect-information and
+Markov winning strategies for \(\plII\) in
+\(G_{fin}(\mc A,\mc B)\) may be improved to
+be valid in \(G_{<2}(\mc A,\mc B)\), provided
+\(\mc B\) is \(\Gamma\)-like. As such,
+\(G_{<2}(\mc A,\mc B)\) and \(G_{fin}(\mc A,\mc B)\)
+are effectively equivalent games under this hypothesis.
+%\begin{theorem}
+%Let \(\mc B\) be \(\Gamma\)-like. Then \(\plII\win G_{<2}(\mc A,\mc B)\)
+%if and only if \(\plII\win G_{fin}(\mc A,\mc B)\).
+%\end{theorem}
 
-\begin{theorem}
-Let \(\mc B\) be sequence-like. Then \(\plII\markwin G_{<2}(\mc A,\mc B)\)
-if and only if \(\plII\markwin G_{fin}(\mc A,\mc B)\).
-\end{theorem}
+%\begin{theorem}
+%Let \(\mc B\) be \(\Gamma\)-like. Then \(\plII\markwin G_{<2}(\mc A,\mc B)\)
+%if and only if \(\plII\markwin G_{fin}(\mc A,\mc B)\).
+%\end{theorem}
 
 \begin{theorem}\label{pawlikowskii}
-Let \(\mc A\) be almost-sequence-like and \(\mc B\) be sequence-like.
+Let \(\mc A\) be almost-\(\Gamma\)-like and \(\mc B\) be \(\Gamma\)-like.
 Then \(\plI\win G_{fin}(\mc A,\mc B)\) if and only if
-\(\plI\prewin G_{fin}(\mc A,\mc B)\).
+\(\plI\prewin G_{fin}(\mc A,\mc B)\), and
+\(\plI\win G_1(\mc A,\mc B)\) if and only if
+\(\plI\prewin G_1(\mc A,\mc B)\).
 \end{theorem}
@@
 \begin{proof}
-We assume \(\plI\win G_{fin}(\mc A,\mc B)\).
-As \(\mc A\) is almost-sequence-like, there is a strategy \(\sigma\)
-witnessing \(\plI\win G_{fin}(\mc A,\mc B)\) where
+We assume \(\plI\win G_{fin}(\mc A,\mc B)\)
+and let the symbol \(\dagger\) mean \(<\aleph_0\)
+(respectively, \(\plI\win G_1(\mc A,\mc B)\)
+and \(\dagger=1\),
+and for convenience we assume \(\plII\) plays
+singleton subsets of \(\mc A\) rather than elements).
+As \(\mc A\) is almost-\(\Gamma\)-like, there is a 
+winning strategy \(\sigma\) where
 \(|\sigma(s)|=\aleph_0\) and \(\sigma(s)\cap\bigcup\ran{s}=\emptyset\)
@@
 
-For each \(s\in\omega^{<\omega}\), suppose \(F_{s\rest m}\in[\bigcup A]^{<\aleph_0}\)
+For each \(s\in\omega^{<\omega}\), suppose 
+\(F_{s\rest m}\in[\bigcup A]^{\dagger}\) 
 is defined for each \(0<m\leq|s|\).
-Then let \(s^\star:|s|\to[\bigcup\mc A]^{<\aleph_0}\) be defined by
+Then let \(s^\star:|s|\to[\bigcup\mc A]^{\dagger}\)
+be defined by
 \(s^\star(m)=F_{s\rest m+1}\), and define \(\tau':\omega^{<\omega}\to\mc A\)
 by \(\tau'(s)=\sigma(s^\star)\). Finally, set 
-\([\sigma(s^\star)]^{<\aleph_0}=\{F_{s\concat\tuple{n}}:n<\omega\}\), and
+\([\sigma(s^\star)]^{\dagger}=\{F_{s\concat\tuple{n}}:n<\omega\}\), and
 for some bijection \(b:\omega^{<\omega}\to\omega\) let \(\tau(n)=\tau'(b(n))\)
-be a predetermined strategy for \(\plI\) in \(G_{fin}(\mc A,\mc B)\).
+be a predetermined strategy for \(\plI\) in \(G_{fin}(\mc A,\mc B)\)
+(resp. \(G_1(\mc A,\mc B)\)).
 
@@
     \in
-  [\tau(n)]^{<\aleph_0}
+  [\tau(n)]^{\dagger}
     =
-  [\tau'(b(n))]^{<\aleph_0}
+  [\tau'(b(n))]^{\dagger}
     =
-  [\sigma(b(n)^\star)]^{<\aleph_0}
+  [\sigma(b(n)^\star)]^{\dagger}
 \]
@@
 Note here that \((f\rest n+1)^\star=(f\rest n)^\star\concat\tuple{F_{f\rest n+1}}\).
-This shows that \(F_{f\rest n+1}\in[\sigma((f\rest n)^\star)]^{<\aleph_0}\) 
+This shows that \(F_{f\rest n+1}\in[\sigma((f\rest n)^\star)]^{\dagger}\) 
 is an attempt by \(\plII\) to defeat \(\sigma\), which fails. Thus 
@@
 
+Note that the assumption in Theorem \ref{pawlikowskii} that \(\mc A\)
+be almost-\(\Gamma\)-like cannot be omitted. In
+[todo cite Clontz k-tactics in Gruenhage game]
+an example of a space and point where \(\plI\win G_1(\mc A,\mc B)\) but
+\(\plI\notprewin G_1(\mc A,\mc B)\) is given, where \(\mc A\) is
+the set of open neighborhoods of the given point 
+(which are all uncountable), 
+and \(\mc B\) is the set of converging sequences to that point.
+(Note that \(G_1(\mc A,\mc B)\) is called \(Gru_{O,P}(X,x)\) in that
+paper. In fact, more is shown: \(\plI\) has a winning perfect-information
+strategy, but any strategy that only uses 
+the most recent \(k\) moves of \(\plII\) and the round number
+can be defeated, where \(k\) is any natural number.)
+
 \begin{proposition}\label{auto-asl}
-Let \(\mc B\) be sequence-like, \(\mc A\subseteq\mc B\),
+Let \(\mc B\) be \(\Gamma\)-like, \(\mc B\subseteq\mc A\),
 and \(\plI\notprewin G_{fin}(\mc A,\mc B)\). Then
-\(\mc A\) is almost-sequence-like.
+\(\mc A\) is almost-\(\Gamma\)-like.
 \end{proposition}
@@
 Then \(A_n\) is not a winning predetermined strategy for
-\(\plI\), so \(\plII\) may choose finite subsets
-\(B_n\subseteq A_n\) such that \(A_n'\bigcup\{B_n:n<\omega\}\in\mc B\subseteq\mc A\).
+\(\plI\), so \(\plII\) may choose finite sets
+\(B_n\subseteq A_n=A\) such that 
+\(A'=\bigcup\{B_n:n<\omega\}\in\mc B\subseteq\mc A\).
 
-It follows that \(|A_n'|=\aleph_0\), and for any infinite subset
-\(A_n''\subseteq A_n'\) (in particular, any cofinite subset),
-\(A_n''\in\mc B\subseteq\mc A\). Thus \(\mc A\) is almost-sequence-like.
+It follows that \(A'\subseteq A\) and \(|A'|=\aleph_0\), 
+and for any infinite subset
+\(A''\subseteq A'\) (in particular, any cofinite subset),
+\(A''\in\mc B\subseteq\mc A\). Thus \(\mc A\) is almost-\(\Gamma\)-like.
 \end{proof}
@@
 \begin{corollary}
-Let \(\mc B\) be sequence-like and \(\mc A\subseteq\mc B\).
+Let \(\mc B\) be \(\Gamma\)-like and \(\mc B\subseteq\mc A\).
 Then \(\plI\win G_{fin}(\mc A,\mc B)\) if and only if
-\(\plI\prewin G_{fin}(\mc A,\mc B)\).
+\(\plI\prewin G_{fin}(\mc A,\mc B)\), and
+\(\plI\win G_{1}(\mc A,\mc B)\) if and only if
+\(\plI\prewin G_{1}(\mc A,\mc B)\).
 \end{corollary}
@@
 and Theorem \ref{pawlikowskii}.
+
+Similarly, assuming \(\plI\notprewin G_{1}(\mc A,\mc B)
+\Rightarrow\plI\notprewin G_{fin}(\mc A,\mc B)\), we have
+\(\plI\notwin G_{1}(\mc A,\mc B)\) by Proposition \ref{auto-asl}
+and Theorem \ref{pawlikowskii}.
 \end{proof}
+
+This corollary generalizes e.g. Theorems 26 and 30 of [cite Scheepers 1996 Ramsey]
+and Theorem 5 of [cite MR2119791].
 

### 2019-10-30 articles/selection-alpha-games/article.tex
add another citation
add narrative

@@
 
-\title{Selection games and Arhangelskii's convergence principles}
+\title{Arhangelskii's \(\alpha\)-principles and selection games}
 
@@
 \begin{abstract}
-We prove the things.
+Arhangelskii's convergence properties \(\alpha_2\) and \(\alpha_4\)
+may be characterized in terms of Scheeper's selection games.
+We generalize these folklore results to hold for more general collections.
 \end{abstract}
@@
 
-%
-%\section{Introduction}
-%
-%\begin{definition}
-%  The \term{selection game} \(\schStrongSelGame{\mc A}{\mc B}\) 
-%  is an \(\omega\)-length game involving Players \(\plI\) and \(\plII\). 
-%  During round \(n\), \(\plI\) chooses
-%  \(A_n\in\mc A\), followed by \(\plII\) choosing \(B_n\in A_n\).
-%  Player \(\plII\) wins in the case that \(\{B_n:n<\omega\}\in\mc B\),
-%  and Player \(\plI\) wins otherwise.
-%\end{definition}
-%
-%\begin{definition}
-%  The \term{selection game} \(\schSelGame{\mc A}{\mc B}\) 
-%  is an \(\omega\)-length game involving Players \(\plI\) and \(\plII\). 
-%  During round \(n\), \(\plI\) chooses
-%  \(A_n\in\mc A\), followed by \(\plII\) choosing \(B_n\in [A_n]^{<\aleph_0}\).
-%  Player \(\plII\) wins in the case that \(\bigcup\{B_n:n<\omega\}\in\mc B\),
-%  and Player \(\plI\) wins otherwise.
-%\end{definition}
-%
-\section{Clontz results}
+The following characterizations were given as Definition 1 by Kocinac in
+[cite Kocinac selection principles related].
+
+\begin{definition}
+\term{Arhangelskii's \(\alpha\)-principles} \(\alpha_i(\mc A,\mc B)\) are defined as follows
+for \(i\in\{1,2,3,4\}\).
+Let \(A_n\in\mc A\) for all \(n<\omega\); then there exists \(B\in\mc B\) such that:
+\begin{itemize}
+\item[\(\alpha_1\):] \(A_n\cap B\) is cofinite in \(A_n\) for all \(n<\omega\).
+\item[\(\alpha_2\):] \(A_n\cap B\) is infinite for all \(n<\omega\).
+\item[\(\alpha_3\):] \(A_n\cap B\) is infinite for infinitely-many \(n<\omega\).
+\item[\(\alpha_4\):] \(A_n\cap B\) is non-empty for infinitely-many \(n<\omega\).
+\end{itemize}
+\end{definition}
+
+When \((\mc A,\mc B)\) is omitted, it is assumed that \(\mc A=\mc B\) is the
+collection \(\Gamma_{X,x}\) of sequences converging to some point \(x\in X\),
+as introduced by Arhangelskii in [cite Arhangelskii frequency spectrum].
+Provided \(\mc A\) only contains infinite sets, it's easy to see that
+\(\alpha_n(\mc A,\mc B)\) implies \(\alpha_{n+1}(\mc A,\mc B)\).
+
+We aim to relate these to the following games.
+
+\begin{definition}
+  The \term{selection game} \(G_1(\mc A,\mc B)\) (resp. \(G_{fin}(\mc A,\mc B)\))
+  is an \(\omega\)-length game involving Players \(\plI\) and \(\plII\). 
+  During round \(n\), \(\plI\) chooses
+  \(A_n\in\mc A\), followed by \(\plII\) choosing \(a_n\in A_n\)
+  (resp. \(F_n\in[A_n]^{<\aleph_0}\)).
+  Player \(\plII\) wins in the case that \(\{a_n:n<\omega\}\in\mc B\)
+  (resp. \(\bigcup\{F_n:n<\omega\}\in\mc B\)),
+  and Player \(\plI\) wins otherwise.
+\end{definition}
+
+Such games are well-represented in the literature; see [cite Scheepers combinatorics ramsey]
+for example.
+We will also consider the similarly-defined games \(G_{<2}(\mc A,\mc B)\)
+(\(\plII\) chooses 0 or 1 points from each choice by \(\plI\)) and \(G_{cf}(\mc A,\mc B)\)
+(\(\plII\) chooses cofinitely-many points).
+
+\begin{definition}
+  Let \(P\) be a player in a game \(G\). \(P\) has a \term{winning strategy}
+  for \(G\), denoted \(P\win G\), if \(P\) has a strategy that defeats every
+  possible counterplay by their opponent. If a strategy only relies on the
+  round number and ignores the moves of the opponent, the strategy is said
+  to be \term{predetermined}; the existence of a predetermined winning strategy
+  is denoted \(P\prewin G\).
+\end{definition}
+
+We briefly note that the statement \(\plI\notprewin G_\star(\mc A,\mc B)\)
+is often denoted as the \term{selection principle} \(S_\star(\mc A,\mc B)\).
+
+The equivalence of \(\alpha_2(\Gamma_{X,x}\Gamma_{X,x})\) and 
+\(\plI\notprewin G_1(\Gamma_{X,x},\Gamma_{X,x})\) was briefly asserted by Sakai
+in the introduction of [cite Sakai sequence selection properties]; the similar
+equivalence of \(\alpha_4(\Gamma_{X,x}\Gamma_{X,x})\) and 
+\(\plI\notprewin G_{fin}(\Gamma_{X,x},\Gamma_{X,x})\) seems to be folklore.
+In fact, these relationships hold in more generality.
+
+\section{Main Results}
+
+\begin{definition}
+Let \(\Gamma_{X,x}\) be the collection of non-trivial sequences \(S\subseteq X\) converging to \(x\),
+that is, infinite subsets of \(X\setminus\{x\}\) such that for each neighborhood \(U\) of \(x\),
+\(S\cap U\) is cofinite in \(S\).
+\end{definition}
+
+\begin{definition}
+Let \(\Gamma_X\) be the collection of open \term{\(\gamma\)-covers} \(\mc U\) of \(X\),
+that is, infinite open covers of \(X\) such that \(X\not\in \mc U\) and for each \(x\in X\),
+\(\{U\in\mc U:x\in U\}\) is cofinite in \(\mc U\).
+\end{definition}
+
+The similarity in nomenclature follows from the observation that every non-trivial sequence in
+\(C_p(X)\) converging to the zero function \(\vec{0}\) naturally defines a corresponding
+\(\gamma\)-cover in \(X\), see e.g. Theorem 4 of
+[Scheepers a sequential property and covering property].
+
+Note that by these definitions, convergent sequences (resp. \(\gamma\)-covers) may be uncountable,
+but any infinite subset of either would remain a convergent sequence (resp. \(\gamma\)-cover),
+in particular, countably infinite subsets. We capture this idea as follows.
 
@@
 
-\begin{definition}
-Let \(\Gamma_X\) be the collection of open \term{\(\gamma\)-covers} \(\mc U\) of \(X\),
-that is, infinite open covers of \(X\) such that for each \(x\in X\),
-\(\{U\in\mc U:x\in U\}\) is cofinite in \(\mc U\).
-\end{definition}
-
-\begin{definition}
-Let \(\Gamma_{X,x}\) be the collection of non-trivial sequences \(S\subseteq X\) converging to \(x\),
-that is, infinite subsets of \(X\) such that for each neighborhood \(U\) of \(x\),
-\(S\cap U\) is cofinite in \(S\).
-\end{definition}
-
-It follows that \(\Gamma_X,\Gamma_{X,x}\) are both \(\Gamma\)-like. We also require
-the following.
+We also require the following.
 
@@
 
-\begin{theorem}
-Let \(\mc B\) be \(\Gamma\)-like. Then \(\alpha_1(\mc A,\mc B)\) holds if and only
-if \(\plI\notprewin G_{cf}(\mc A,\mc B)\).
-\end{theorem}
-
-\begin{proof}
-We first assume \(\alpha_1(\mc A,\mc B)\) and let \(A_n\in\mc A\) for \(n<\omega\)
-define a predetermined strategy for \(\plI\). By \(\alpha_1(\mc A,\mc B)\), we
-immediately obtain \(B\in\mc B\) such that \(|A_n\setminus B|<\aleph_0\). Thus
-\(B_n=A_n\cap B\) is a cofinite choice from \(A_n\), and 
-\(B'=\bigcup\{B_n:n<\omega\}\) is an infinite subset of \(B\),
-so \(B'\in\mc B\). Thus \(\plII\) may defeat \(\plI\) by choosing
-\(B_n\subseteq A_n\) each round, witnessing \(\plI\notprewin G_{cf}(\mc A,\mc B)\).
-
-On the other hand, let \(\plI\notprewin G_{cf}(\mc A,\mc B)\). Given \(A_n\in\mc A\)
-for \(n<\omega\), we note that \(\plII\) may choose a cofinite subset \(B_n\subseteq A_n\)
-such that \(B=\bigcup\{B_n:n<\omega\}\in\mc B\). Then \(B\) witnesses \(\alpha_1(\mc A,\mc B)\)
-since \(|A_n\setminus B|\leq|A_n\setminus B_n|\leq\aleph_0\).
-\end{proof}
+We are now able to prove a few general equivalences between \(\alpha\)-princples
+and selection games.
 
@@
 We first assume \(\alpha_2(\mc A,\mc B)\) and let \(A_n\in\mc A\) for \(n<\omega\)
-define a predetermined strategy for \(\pl I\).
+define a predetermined strategy for \(\plI\).
 We may apply \(\alpha_2(\mc A,\mc B)\) to choose \(B\in\mc B\) such that
@@
 \end{proof}
+
+This shows that \(\plII\) gains no advantage from picking more than one
+point per round. This in fact only depends on \(\mc B\) being
+\(\Gamma\)-like, which we formalize in the following results.
 
@@
 
-We further note that the above proof technique could be
+We note that the above proof technique could be
 used to establish that perfect-information and
-Markov winning strategies for \(\plII\) in
+limited-information strategies for \(\plII\) in
 \(G_{fin}(\mc A,\mc B)\) may be improved to
@@
 are effectively equivalent games under this hypothesis.
-%\begin{theorem}
-%Let \(\mc B\) be \(\Gamma\)-like. Then \(\plII\win G_{<2}(\mc A,\mc B)\)
-%if and only if \(\plII\win G_{fin}(\mc A,\mc B)\).
-%\end{theorem}
-
-%\begin{theorem}
-%Let \(\mc B\) be \(\Gamma\)-like. Then \(\plII\markwin G_{<2}(\mc A,\mc B)\)
-%if and only if \(\plII\markwin G_{fin}(\mc A,\mc B)\).
-%\end{theorem}
 
 \begin{theorem}\label{pawlikowskii}
-Let \(\mc A\) be almost-\(\Gamma\)-like and \(\mc B\) be \(\Gamma\)-like.
-Then \(\plI\win G_{fin}(\mc A,\mc B)\) if and only if
+Let \(\mc A\) be almost-\(\Gamma\)-like and \(\mc B\) be \(\Gamma\)-like. Then
+\begin{itemize}
+\item \(\plI\win G_{fin}(\mc A,\mc B)\) if and only if
 \(\plI\prewin G_{fin}(\mc A,\mc B)\), and
-\(\plI\win G_1(\mc A,\mc B)\) if and only if
+\item \(\plI\win G_1(\mc A,\mc B)\) if and only if
 \(\plI\prewin G_1(\mc A,\mc B)\).
+\end{itemize}
 \end{theorem}
@@
 [todo cite Clontz k-tactics in Gruenhage game]
-an example of a space and point where \(\plI\win G_1(\mc A,\mc B)\) but
+an example of a space \(X^*\) and point \(\infty\in X^*\) 
+where \(\plI\win G_1(\mc A,\mc B)\) but
 \(\plI\notprewin G_1(\mc A,\mc B)\) is given, where \(\mc A\) is
-the set of open neighborhoods of the given point 
+the set of open neighborhoods of \(\infty\) 
 (which are all uncountable), 
-and \(\mc B\) is the set of converging sequences to that point.
-(Note that \(G_1(\mc A,\mc B)\) is called \(Gru_{O,P}(X,x)\) in that
-paper. In fact, more is shown: \(\plI\) has a winning perfect-information
-strategy, but any strategy that only uses 
+and \(\mc B\) is the set \(\Gamma_{X^*,\infty}\) of sequences converging to that point.
+(Note that \(G_1(\mc A,\mc B)\) is called \(Gru_{O,P}(X^*,\infty)\) in that
+paper, and an equivalent game \(Gru_{K,P}(X)\) is what is directly
+studied. In fact, more is shown: \(\plI\) has a winning perfect-information
+strategy, but for any natural number \(k\), any strategy that only uses 
 the most recent \(k\) moves of \(\plII\) and the round number
-can be defeated, where \(k\) is any natural number.)
+can be defeated.)
+
+While \(\mc A\) is often not almost-\(\Gamma\)-like in general,
+it may satisfy that property in combination with the selection principles
+being considered.
 
@@
 
+Note that in the previous result, 
+\(\plI\notprewin G_{fin}(\mc A,\mc B)\) could be weakened
+to the choice principle \({\mc A}\choose{\mc B}\): for every
+member of \(\mc A\), there is some countable subset belonging to \(\mc B\).
+
 \begin{corollary}
 Let \(\mc B\) be \(\Gamma\)-like and \(\mc B\subseteq\mc A\).
-Then \(\plI\win G_{fin}(\mc A,\mc B)\) if and only if
+Then 
+\begin{itemize}
+\item \(\plI\win G_{fin}(\mc A,\mc B)\) if and only if
 \(\plI\prewin G_{fin}(\mc A,\mc B)\), and
-\(\plI\win G_{1}(\mc A,\mc B)\) if and only if
+\item \(\plI\win G_{1}(\mc A,\mc B)\) if and only if
 \(\plI\prewin G_{1}(\mc A,\mc B)\).
+\end{itemize}
 \end{corollary}
@@
 
-This corollary generalizes e.g. Theorems 26 and 30 of [cite Scheepers 1996 Ramsey]
-and Theorem 5 of [cite MR2119791].
+This corollary generalizes e.g. Theorems 26 and 30 of [cite Scheepers 1996 Ramsey],
+Theorem 5 of [cite MR2119791], and Corollary 36 of [cite Clontz dual games].
+
+In summary, using the selection principle notation \(S_\star(\mc A,\mc B)\):
+
+\begin{corollary}
+Let \(\mc B\) be \(\Gamma\)-like and \(\mc B\subseteq\mc A\).
+Then 
+\begin{itemize}
+\item \(\plI\notwin G_{fin}(\mc A,\mc B)\) if and only if
+\(S_{fin}(\mc A,\mc B)\) if and only if
+\(\alpha_2(\mc A,\mc B)\), and
+\item \(\plI\notwin G_{1}(\mc A,\mc B)\) if and only if
+\(S_{1}(\mc A,\mc B)\) if and only if
+\(\alpha_4(\mc A,\mc B)\).
+\end{itemize}
+\end{corollary}
+
+\section{Conclusion}
+
+We conclude with the following easy result, and a couple questions.
+
+\begin{proposition}
+Let \(\mc B\) be \(\Gamma\)-like. Then \(\alpha_1(\mc A,\mc B)\) holds if and only
+if \(\plI\notprewin G_{cf}(\mc A,\mc B)\).
+\end{proposition}
+
+\begin{proof}
+We first assume \(\alpha_1(\mc A,\mc B)\) and let \(A_n\in\mc A\) for \(n<\omega\)
+define a predetermined strategy for \(\plI\). By \(\alpha_1(\mc A,\mc B)\), we
+immediately obtain \(B\in\mc B\) such that \(|A_n\setminus B|<\aleph_0\). Thus
+\(B_n=A_n\cap B\) is a cofinite choice from \(A_n\), and 
+\(B'=\bigcup\{B_n:n<\omega\}\) is an infinite subset of \(B\),
+so \(B'\in\mc B\). Thus \(\plII\) may defeat \(\plI\) by choosing
+\(B_n\subseteq A_n\) each round, witnessing \(\plI\notprewin G_{cf}(\mc A,\mc B)\).
+
+On the other hand, let \(\plI\notprewin G_{cf}(\mc A,\mc B)\). Given \(A_n\in\mc A\)
+for \(n<\omega\), we note that \(\plII\) may choose a cofinite subset \(B_n\subseteq A_n\)
+such that \(B=\bigcup\{B_n:n<\omega\}\in\mc B\). Then \(B\) witnesses \(\alpha_1(\mc A,\mc B)\)
+since \(|A_n\setminus B|\leq|A_n\setminus B_n|\leq\aleph_0\).
+\end{proof}
+
+\begin{question}
+Is there a game-theoretic characterization of \(\alpha_3(\mc A,\mc B)\)?
+\end{question}
+
+Noting that \(\plI\win G_1(\Gamma_X,\Gamma_X)\) if and only if
+\(\plI\win G_{fin}(\Gamma_X,\Gamma_X)\) [cite Kocinac], but
+the same is not true of \(G_\star(\Gamma_{X,x},\Gamma_{X,x})\)
+(i.e. there are \(\alpha_4\) spaces that are not \(\alpha_2\)
+[cite Arhangelskii]),
+we also ask the following.
+
+\begin{question}
+Is there an elegant condition on \(\mc A,\mc B\) guaranteeing
+\(\plI\win G_1(\mc A,\mc B)\Rightarrow\plI\win G_{fin}(\mc A,\mc B)\)?
+\end{question}
 

### 2019-10-30 articles/selection-alpha-games/article.tex
add pawlikowskii note

@@
 \(G_{<2}(\mc A,\mc B)\) and \(G_{fin}(\mc A,\mc B)\)
-are effectively equivalent games under this hypothesis.
+are effectively equivalent games under this hypothesis,
+so we will no longer consider \(G_{<2}(\mc A,\mc B)\).
+
+We now demonstrate the following, in the spirit of Pawlikowskii's celebrated
+result that a winning strategy for the first player in the Rothberger game
+may always be improved to a winning predetermined strategy [cite pawlikowskii].
 

### 2019-11-05 articles/selection-alpha-games/article.tex
fix 1.5 to 1.1

@@
 \begin{abstract}
-Arhangelskii's convergence properties \(\alpha_2\) and \(\alpha_4\)
-may be characterized in terms of Scheeper's selection games.
-We generalize these folklore results to hold for more general collections.
+Arhangelskii's properties \(\alpha_2\) and \(\alpha_4\)
+defined for convergent sequences
+may be characterized in terms of Scheeper's selection principles.
+We generalize these results to hold for more general collections
+and consider these results in terms of selection games.
 \end{abstract}
@@
 
-The equivalence of \(\alpha_2(\Gamma_{X,x}\Gamma_{X,x})\) and 
-\(\plI\notprewin G_1(\Gamma_{X,x},\Gamma_{X,x})\) was briefly asserted by Sakai
-in the introduction of [cite Sakai sequence selection properties]; the similar
-equivalence of \(\alpha_4(\Gamma_{X,x}\Gamma_{X,x})\) and 
-\(\plI\notprewin G_{fin}(\Gamma_{X,x},\Gamma_{X,x})\) seems to be folklore.
-In fact, these relationships hold in more generality.
-
-\section{Main Results}
-
 \begin{definition}
@@
 [Scheepers a sequential property and covering property].
+
+The equivalence of \(\alpha_2(\Gamma_{X,x}\Gamma_{X,x})\) and 
+\(\plI\notprewin G_1(\Gamma_{X,x},\Gamma_{X,x})\) was briefly asserted by Sakai
+in the introduction of [cite Sakai sequence selection properties]; the similar
+equivalence of \(\alpha_4(\Gamma_{X,x}\Gamma_{X,x})\) and 
+\(\plI\notprewin G_{fin}(\Gamma_{X,x},\Gamma_{X,x})\) seems to be folklore.
+In fact, these relationships hold in more generality.
 
@@
 and selection games.
+
+\section{On \(\alpha_2(\mc A,\mc B)\) and \(G_1(\mc A,\mc B)\)}
 
@@
 \end{proof}
+
+While \(\alpha_2(\mc A,\mc B)\) involves infinite intersection and
+\(G_1(\mc A,\mc B)\) involves single selections, the previous result is made
+more intuitive given the following result, shown for \(\mc A=\mc B=\Gamma_{X,x}\)
+by Nogura in [cite product of alpha spaces].
+
+\begin{definition}
+\(\alpha_2'(\mc A,\mc B)\) is the following claim:
+if \(A_n\in\mc A\) for all \(n<\omega\), then there exists \(B\in\mc B\) such that
+\(A_n\cap B\) is nonempty for all \(n<\omega\).
+\end{definition}
+
+(Note that \(\alpha_5\) is sometimes used in the literature in place of \(\alpha_2'\).)
+
+\begin{proposition}
+If \(\mc A\) is almost-\(\Gamma\)-like, then
+\(\alpha_2(\mc A,\mc B)\) is equivalent to \(\alpha_2'(\mc A,\mc B)\).
+\end{proposition}
+
+\begin{proof}
+The forward implication is immediate, so we assume \(\alpha_2'(\mc A,\mc B)\).
+Given \(A_n\in\mc A\), we apply the almost-\(\Gamma\)-like property to obtain
+\(A_n'=\{a_{n,m}:m<\omega\}\subseteq A_n\) such that
+\(A_{n,m}=A_n\setminus\{a_{i,j}:i,j<m\}\in\mc A\) for all \(m<\omega\).
+
+By applying \(\alpha_2'(\mc A,\mc B)\) to \(A_{n,m}\), we obtain
+\(B\in\mc B\) such that \(A_{n,m}\cap B\) is nonempty for all \(n,m<\omega\).
+Since it follows that \(A_n\cap B\) is infinite for all \(n<\omega\),
+we have established \(\alpha_2(\mc A,\mc B)\).
+\end{proof}
+
+\section{On \(\alpha_4(\mc A,\mc B)\) and \(G_{fin}(\mc A,\mc B)\)}
+
+A similar correspondence exists between \(\alpha_4(\mc A,\mc B)\)
+and \(G_{fin}(\mc A,\mc B)\).
 
@@
 so we will no longer consider \(G_{<2}(\mc A,\mc B)\).
+
+\section{Perfect information and predetermined strategies}
 
@@
 
+\section{Disjoint selections}
+
+In each \(\alpha_i(\mc A,\mc B)\) principle, it is not required for the collection
+\(\{A_n:n<\omega\}\) to be pairwise disjoint. However, in many cases it may as
+well be.
+
+\begin{definition}
+For \(i\in\{1,2,3,4\}\) let \(\alpha_{i.1}(\mc A,\mc B)\) denote the claim that
+\(\alpha_i(\mc A,\mc B)\) holds provided the collection \(\{A_n:n<\omega\}\)
+is pairwise disjoint.
+\end{definition}
+
+Of course, \(\alpha_i(\mc A,\mc B)\) implies \(\alpha_{i.1}(\mc A,\mc B)\).
+It's also immediate that \(\alpha_{i.1}(\mc A,\mc B)\) implies
+\(\alpha_{i.1+1}(\mc A,\mc B)\) for the same reason that \(\alpha_i(\mc A,\mc B)\)
+implies \(\alpha_{i+1}(\mc A,\mc B)\).
+
+%Nyikos considered these half-variants
+%in [cite Nyikos 1992] for \(\mc A=\mc B=\Gamma_{X,x}\), but his arguments
+%can be generalized provided \(\mc A\) is \(\Gamma\)-like.
+
+We take advantage of the following lemma.
+
+\begin{lemma}[Lemma 1.2 of (cite Nyikos 92)]
+Given a family \(\{A_n:n<\omega\}\) of infinite sets, there exist infinite subsets
+\(A_n'\subseteq A_n\) such that \(\{A_n':n<\omega\}\) is pairwise disjoint.
+\end{lemma}
+
+\begin{proposition}
+Let \(\mc A\) be \(\Gamma\)-like.
+For \(i\in\{2,3,4\}\), \(\alpha_i(\mc A,\mc B)\) is equivalent to
+\(\alpha_{i.1}(\mc A,\mc B)\).
+\end{proposition}
+
+\begin{proof}
+Assume \(\alpha_{i.1}(\mc A,\mc B)\).
+Let \(A_n\in\mc A\). By applying the previous lemma, we have
+\(\{A_n':n<\omega\}\) pairwise disjoint with each \(A_n'\) being
+an infinite subset of \(A_n\). Since \(\mc A\) is \(\Gamma\)-like,
+\(A_n'\in\mc A\), so we have a witness \(B\in\mc B\) such that
+\(A_n'\cap B\) satisfies \(\alpha_{i.1}(\mc A,\mc B)\) for all \(n<\omega\).
+Since \(A_n'\subseteq A_n\), it follows that \(A_n\cap B\) satisfies
+\(\alpha_{i}(\mc A,\mc B)\) for all \(n<\omega\).
+\end{proof}
+
+It's also true that \(\alpha_1(\Gamma_{X,x},\Gamma_{X,x})\)
+is equivalent to \(\alpha_{1.1}(\Gamma_{X,x},\Gamma_{X,x})\),
+which is captured by the following theorem.
+
+\begin{proposition}
+Let \(\mc A\) be a \(\Gamma\)-like collection closed under finite unions.
+Then \(\alpha_1(\mc A,\mc A)\) is equivalent to
+\(\alpha_{1.1}(\mc A,\mc A)\).
+\end{proposition}
+
+\begin{proof}
+Let \(A_n\in\mc A\) and assume \(\alpha_{1.1}(\mc A,\mc A)\).
+To apply the assumption, we will define a pairwise disjoint
+collection \(\{A_n':n<\omega\}\). First let \(0'=0\) and \(A_0'=A_0\).
+Then suppose \(m'\geq m\) and \(A_m'\subseteq A_{m'}\subseteq\bigcup_{i\leq m}A_i'\) 
+are defined for all \(m\leq n\).
+
+If \(A_k\setminus\bigcup_{m\leq n}A_m'\) is finite for \(k>n'\), let
+\(B=\bigcup_{m\leq n'}A_m\in\mc A\). This \(B\) then witnesses 
+\(\alpha_1(\mc A,\mc A)\) since \(A_k\setminus B\) is finite for all \(k<\omega\).
+
+Otherwise pick the minimal \((n+1)'>n\) where 
+\(A_{n+1}'=A_{(n+1)'}\setminus\bigcup_{m\leq n}A_m'\) is infinite.
+It follows that \(A_{n+1}'\subseteq A_{(n+1)'}\subseteq \bigcup_{m\leq n+1}A_m'\).
+By construction, \(\{A_n':n<\omega\}\) is a pairwise disjoint collection of
+members of \(\mc A\), and we may
+apply \(\alpha_{1.1}(\mc A,\mc A)\) to obtain \(B\in\mc A\) where
+\(A_n'\setminus B\) is finite for all \(n<\omega\).
+
+Finally let \(k<\omega\). If \(k=n'\) for some \(n<\omega\), then 
+\(A_k\setminus B=A_{n'}\setminus B\subseteq (\bigcup_{m\leq n}A_m')\setminus B\) 
+is finite.
+Otherwise, \(n'<k<(n+1)'\) for some \(n<\omega\).
+Then 
+\((A_k\setminus\bigcup_{m\leq n}A_m')\setminus B\subseteq A_k\setminus\bigcup_{m\leq n}A_m'\)
+is finite, and 
+\((A_k\cap\bigcup_{m\leq n}A_m')\setminus B\subseteq(\bigcup_{m\leq n}A_m')\setminus B\)
+is finite, showing \(A_k\setminus B\) is finite.
+\end{proof}
+
+TODO add discussion of \(\alpha_{1.5}\) here.
+
+For this paragraph we adopt the conventional assumption that
+\(\Gamma_{X,x}\) is restricted to countable sets.
+Nyikos showed a consistent example
+where \(\alpha_2(\Gamma_{X,x},\Gamma_{X,x})\) fails to imply
+\(\alpha_{1.5}(\Gamma_{X,x},\Gamma_{X,x})\), and a consistent example where
+\(\alpha_{1.5}(\Gamma_{X,x},\Gamma_{X,x})\) fails to imply
+\(\alpha_{1}(\Gamma_{X,x},\Gamma_{X,x})\) [cite Nyikos 92].
+On the other hand, Dow showed that \(\alpha_2(\Gamma_{X,x},\Gamma_{X,x})\)
+implies \(\alpha_{1}(\Gamma_{X,x},\Gamma_{X,x})\) in the Laver model
+for the Borel conjecture [cite Dow 1990]; the author conjectures
+that this model (specifically, the fact that
+every \(\omega\)-splitting family contains an \(\omega\)-splitting
+family of size less than \(\mathfrak b\) in this model) witnesses
+an affirmative answer to the following question.
+
+\begin{definition}
+A \(\Gamma\)-like collection is \term{strongly-\(\Gamma\)-like}
+if the collection is closed under finite unions and each member
+is countable.
+\end{definition}
+
+\begin{question}
+Let \(\mc A,\mc B\) be strongly-\(\Gamma\)-like
+and \(\mc B\subseteq\mc A\).
+Is it consistent that \(\alpha_2(\mc A,\mc B)\)
+implies \(\alpha_1(\mc A,\mc B)\)?
+\end{question}
+
 \section{Conclusion}
@@
 (i.e. there are \(\alpha_4\) spaces that are not \(\alpha_2\)
-[cite Arhangelskii]),
+[cite Shakhmatov convergence algebraic structure]),
 we also ask the following.
@@
 \begin{question}
-Is there an elegant condition on \(\mc A,\mc B\) guaranteeing
+Is there a natural condition on \(\mc A,\mc B\) guaranteeing
 \(\plI\win G_1(\mc A,\mc B)\Rightarrow\plI\win G_{fin}(\mc A,\mc B)\)?
 \end{question}
+
+\section{Acknowledgements}
+
+The author would like to thank Dr. Alan Dow and Dr. Jared Holshouser
+for their discussions on the subject of the paper.
 

### 2019-11-06 articles/selection-alpha-games/article.tex
discuss alpha_1.5

@@
 
-\begin{proposition}
+\begin{proposition}\label{pointOne}
 Let \(\mc A\) be \(\Gamma\)-like.
@@
 
-\begin{proposition}
-Let \(\mc A\) be a \(\Gamma\)-like collection closed under finite unions.
-Then \(\alpha_1(\mc A,\mc A)\) is equivalent to
-\(\alpha_{1.1}(\mc A,\mc A)\).
-\end{proposition}
+\begin{theorem}
+Let \(\mc A\) be a \(\Gamma\)-like collection closed under finite unions
+and \(\mc A\subseteq\mc B\).
+Then \(\alpha_1(\mc A,\mc B)\) is equivalent to
+\(\alpha_{1.1}(\mc A,\mc B)\).
+\end{theorem}
 
 \begin{proof}
-Let \(A_n\in\mc A\) and assume \(\alpha_{1.1}(\mc A,\mc A)\).
+Let \(A_n\in\mc A\) and assume \(\alpha_{1.1}(\mc A,\mc B)\).
 To apply the assumption, we will define a pairwise disjoint
@@
 If \(A_k\setminus\bigcup_{m\leq n}A_m'\) is finite for \(k>n'\), let
-\(B=\bigcup_{m\leq n'}A_m\in\mc A\). This \(B\) then witnesses 
-\(\alpha_1(\mc A,\mc A)\) since \(A_k\setminus B\) is finite for all \(k<\omega\).
+\(B=\bigcup_{m\leq n'}A_m\in\mc A\subseteq\mc B\). This \(B\) then witnesses 
+\(\alpha_1(\mc A,\mc B)\) since \(A_k\setminus B\) is finite for all \(k<\omega\).
 
@@
 members of \(\mc A\), and we may
-apply \(\alpha_{1.1}(\mc A,\mc A)\) to obtain \(B\in\mc A\) where
+apply \(\alpha_{1.1}(\mc A,\mc B)\) to obtain \(B\in\mc B\) where
 \(A_n'\setminus B\) is finite for all \(n<\omega\).
@@
 
-TODO add discussion of \(\alpha_{1.5}\) here.
+Another fractional version of these \(\alpha\)-principles is given as
+\(\alpha_{1.5}\) in [Nyikos 92], defined in general as follows.
+
+\begin{definition}
+Let \(\alpha_{1.5}(\mc A,\mc B)\) be the assertion that when \(A_n\in\mc A\)
+and \(\{A_n:n<\omega\}\) is pairwise disjoint, then there exists \(B\in\mc B\)
+such that \(A_n\cap B\) is cofinite in \(A_n\) for infinitely-many \(n<\omega\).
+\end{definition}
+
+It's immediate from their definitions that 
+\(\alpha_{1.1}(\mc A,\mc B)\) implies \(\alpha_{1.5}(\mc A,\mc B)\), which
+implies \(\alpha_{3.1}(\mc A,\mc B)\).
+Nyikos originally showed that \(\alpha_{1.5}(\Gamma_{X,x},\Gamma_{X,x})\) implies
+\(\alpha_2(\Gamma_{X,x},\Gamma_{X,x})\); this result generalizes as follows.
+
+\begin{theorem}
+Let \(\mc A\) be a \(\Gamma\)-like collection closed under finite unions.
+Then \(\alpha_{1.5}(\mc A,\mc B)\) implies
+\(\alpha_{2}(\mc A,\mc B)\).
+\end{theorem}
+
+\begin{proof}
+We assume \(\alpha_{1.5}(\mc A,\mc B)\) and demonstrate
+\(\alpha_{2.1}(\mc A,\mc B)\), which is equivalent to
+\(\alpha_{2}(\mc A,\mc B)\) by Proposition \ref{pointOne}.
+So let \(A_n\in\mc A\) such that \(\{A_n:n<\omega\}\) is pairwise-disjoint.
+
+We may partition each \(A_n\) into \(\{A_{n,m}:m<\omega\}\) with
+\(A_{n,m}\in\mc A\) for all \(m<\omega\). 
+Let \(A_n'=\bigcup\{A_{i,j}:i+j=n\}\in\mc A\);
+since \(\{A_n':n<\omega\}\) is pairwise disjoint, we may apply
+\(\alpha_{1.5}(\mc A,\mc B)\) to obtain \(B\in\mc B\) where
+\(A_n'\cap B\) is cofinite in \(A_n'\) for infinitely-many \(n<\omega\).
+
+Then for \(n<\omega\), choose \(N\geq n\) with \(A_N'\cap B\) cofinite in \(A_N'\).
+Then \(A_{n,N-n}\subseteq A_N'\), 
+so \(A_{n,N-n}\cap B\) is cofinite in \(A_{n,N-n}\), in particular,
+\(A_{n,N-n}\cap B\) is infinite.
+Therefore \(A_n\cap B\) is infinite, and we have shown
+\(\alpha_{2.1}(\mc A,\mc B)\).
+\end{proof}
+
+\begin{corollary}
+Let \(\mc A\) be a \(\Gamma\)-like collection closed under finite unions.
+Then \(\alpha_x(\mc A,\mc B)\) implies \(\alpha_y(\mc A,\mc B)\) for
+\(1<x\leq y\). Additionally, if \(\mc A\subseteq\mc B\), then 
+\(\alpha_x(\mc A,\mc B)\) implies \(\alpha_y(\mc A,\mc B)\) for
+\(1\leq x\leq y\).
+\end{corollary}
 
@@
 \begin{question}
-Let \(\mc A,\mc B\) be strongly-\(\Gamma\)-like
-and \(\mc B\subseteq\mc A\).
-Is it consistent that \(\alpha_2(\mc A,\mc B)\)
-implies \(\alpha_1(\mc A,\mc B)\)?
+Let \(\mc A\) be strongly-\(\Gamma\)-like.
+Is it consistent that \(\alpha_2(\mc A,\mc A)\)
+implies \(\alpha_1(\mc A,\mc A)\)?
 \end{question}
@@
 
-The author would like to thank Dr. Alan Dow and Dr. Jared Holshouser
-for their discussions on the subject of the paper.
+The author would like to thank Alan Dow, Jared Holshouser,
+and Alexander Osipov for various discussions related to this paper.
 

### 2019-11-06 articles/selection-alpha-games/article.tex
fix bibliography

@@
 The following characterizations were given as Definition 1 by Kocinac in
-[cite Kocinac selection principles related].
+\cite{MR2417134}.
 
@@
 collection \(\Gamma_{X,x}\) of sequences converging to some point \(x\in X\),
-as introduced by Arhangelskii in [cite Arhangelskii frequency spectrum].
+as introduced by Arhangelskii in \cite{MR0394575}.
 Provided \(\mc A\) only contains infinite sets, it's easy to see that
@@
 
-Such games are well-represented in the literature; see [cite Scheepers combinatorics ramsey]
+Such games are well-represented in the literature; see \cite{MR1378387}
 for example.
@@
 \(\gamma\)-cover in \(X\), see e.g. Theorem 4 of
-[Scheepers a sequential property and covering property].
+\cite{MR1396994}.
 
@@
 \(\plI\notprewin G_1(\Gamma_{X,x},\Gamma_{X,x})\) was briefly asserted by Sakai
-in the introduction of [cite Sakai sequence selection properties]; the similar
+in the introduction of \cite{MR2280899}; the similar
 equivalence of \(\alpha_4(\Gamma_{X,x}\Gamma_{X,x})\) and 
@@
 more intuitive given the following result, shown for \(\mc A=\mc B=\Gamma_{X,x}\)
-by Nogura in [cite product of alpha spaces].
+by Nogura in \cite{MR812643}.
 
@@
 result that a winning strategy for the first player in the Rothberger game
-may always be improved to a winning predetermined strategy [cite pawlikowskii].
+may always be improved to a winning predetermined strategy \cite{MR1279482}.
 
@@
 be almost-\(\Gamma\)-like cannot be omitted. In
-[todo cite Clontz k-tactics in Gruenhage game]
+\cite{MR3467819}
 an example of a space \(X^*\) and point \(\infty\in X^*\) 
@@
 
-This corollary generalizes e.g. Theorems 26 and 30 of [cite Scheepers 1996 Ramsey],
-Theorem 5 of [cite MR2119791], and Corollary 36 of [cite Clontz dual games].
+This corollary generalizes e.g. Theorems 26 and 30 of \cite{MR1378387}
+Theorem 5 of \cite{MR2119791}, and Corollary 36 of \cite{clontzDualPreprint}.
 
@@
 
-%Nyikos considered these half-variants
-%in [cite Nyikos 1992] for \(\mc A=\mc B=\Gamma_{X,x}\), but his arguments
-%can be generalized provided \(\mc A\) is \(\Gamma\)-like.
-
 We take advantage of the following lemma.
 
-\begin{lemma}[Lemma 1.2 of (cite Nyikos 92)]
+\begin{lemma}[Lemma 1.2 of \cite{MR1195504}]
 Given a family \(\{A_n:n<\omega\}\) of infinite sets, there exist infinite subsets
@@
 Another fractional version of these \(\alpha\)-principles is given as
-\(\alpha_{1.5}\) in [Nyikos 92], defined in general as follows.
+\(\alpha_{1.5}\) in \cite{MR1195504}, defined in general as follows.
 
@@
 \(\alpha_{1.5}(\Gamma_{X,x},\Gamma_{X,x})\) fails to imply
-\(\alpha_{1}(\Gamma_{X,x},\Gamma_{X,x})\) [cite Nyikos 92].
+\(\alpha_{1}(\Gamma_{X,x},\Gamma_{X,x})\) \cite{MR1195504}.
 On the other hand, Dow showed that \(\alpha_2(\Gamma_{X,x},\Gamma_{X,x})\)
 implies \(\alpha_{1}(\Gamma_{X,x},\Gamma_{X,x})\) in the Laver model
-for the Borel conjecture [cite Dow 1990]; the author conjectures
+for the Borel conjecture \cite{MR975638}; the author conjectures
 that this model (specifically, the fact that
@@
 Noting that \(\plI\win G_1(\Gamma_X,\Gamma_X)\) if and only if
-\(\plI\win G_{fin}(\Gamma_X,\Gamma_X)\) [cite Kocinac], but
+\(\plI\win G_{fin}(\Gamma_X,\Gamma_X)\) \cite{MR2417134}, but
 the same is not true of \(G_\star(\Gamma_{X,x},\Gamma_{X,x})\)
 (i.e. there are \(\alpha_4\) spaces that are not \(\alpha_2\)
-[cite Shakhmatov convergence algebraic structure]),
+\cite{shakhmatov2002convergence}),
 we also ask the following.

### 2020-01-03 articles/dual-selection-games/article.tex
add line numbers
revise based on referee report

@@
       \newtheorem*{remark*}{Remark}
+
+\usepackage{lineno}
+\linenumbers
 
@@
 
-  For brevity, let 
+  Let \(\mc P(Z)=\{z:z\subseteq Z\}\) denote the power set of \(Z\),
+  so \(\{B_n:n<\omega\}\in\mc P(\bigcup\mc A)\) for any choices
+  \(B_n\in A_n\in\mc A\) made by the players.
+  Then for brevity, let 
   \[
@@
   .\]
-  That is, \(\plII\) wins in the case that \(\{B_n:n<\omega\}\not\in\mc B\),
+  That is, this is the analogous game where
+  \(\plII\) wins provided \(\{B_n:n<\omega\}\not\in\mc B\),
   and \(\plI\) wins otherwise.
 
-\begin{definition}
+\begin{notation}
   For a set \(X\), let \(\mathbf C(X)=\{f\in(\bigcup X)^X:x\in X\Rightarrow f(x)\in x\}\)
   be the collection of all choice functions on \(X\).
-\end{definition}
+\end{notation}
 
@@
 
-\begin{definition}
-  For \(f\in B^A\) and \(X\subseteq A\), let \(f\rest X\) be the restrction of \(f\)
+\begin{notation}
+  For \(f\in B^A\) and \(X\subseteq A\), let \(f\rest X\) be the restriction of \(f\)
   to \(X\). In particular, for \(f\in B^\omega\) and \(n<\omega\), \(f\rest n\)
   describes the first \(n\) terms of the sequence \(f\).
-\end{definition}
+\end{notation}
 
@@
 
-\begin{definition}
+\begin{notation}
   Write \(\plI\win G\) (resp. \(\plI\prewin G\), \(\plI\conwin G\)) 
@@
   strategy (resp. winning Markov/tactical strategy) for the game \(G\).
-\end{definition}
+\end{notation}
 
@@
 
-\begin{definition}
+\begin{definition}[\cite{MR1378387}]
   The selection principle \(\schStrongSelProp{\mc A}{\mc B}\) asserts
@@
 
-\begin{definition}
+\begin{definition}[\cite{MR2363173}]
   The choice principle \(\binom{\mc A}{\mc B}^\kappa\) asserts
@@
   \(B\subseteq A\) where \(|B|=\kappa\) and \(B\in\mc B\).
+  (When \(\kappa\) is omitted, the criterion \(|B|=\kappa\) is also omitted.)
 \end{definition}
@@
 point-picking game of Berner and Juh\'asz defined in \cite{MR775687}. Scheepers showed that these
-were perfect-information dual in his paper.
+were perfect-information dual in \cite{MR1711901}.
 
@@
 Let 
-\(\Gamma_X=\{\mc U\subseteq\mc T_X:\forall x\in X(\mc U\setminus\mc T_{X,x}\in[T_X]^{<\aleph_0})\}\). 
+\(\Gamma_X=\{\mc U\subseteq\mc T_X:\forall x\in X(\mc U\setminus\mc T_{X,x}\in[\mc T_X]^{<\aleph_0})\}\). 
 Such \(\gamma\)-covers are related to the convergent sequences of \(C_p(X)\) (that is,

### 2020-05-20 articles/selection-alpha-games/article.tex
prepare for arxiv
remove line numbers for arxiv
dedicate paper to Zenor for submission

@@
 the same is not true of \(G_\star(\Gamma_{X,x},\Gamma_{X,x})\)
-(i.e. there are \(\alpha_4\) spaces that are not \(\alpha_2\)
+(e.g. there are \(\alpha_4\) spaces that are not \(\alpha_2\)
 \cite{shakhmatov2002convergence}),
@@
 
-\section{Acknowledgements}
+\section{Acknowledgements and Dedication}
 
@@
 
+This paper is dedicated to the memory of Dr. Phil Zenor. Dr. Zenor
+was the instructor of the author's undergraduate real analysis course,
+which was taught using inquiry-based learning.
+The author was first inspired to become a mathematician because
+Dr. Zenor's class modeled the experience of being a mathematician;
+rather than listening to lectures, students in Dr. Zenor's class
+were encouraged and rewarded for engaging with the material
+themselves and presenting their findings to their peers.
+
 \bibliographystyle{plain}
-\bibliography{../../bibliography}
+\bibliography{bibliography}
 

### 2020-10-29 articles/selection-alpha-games/article.tex
add notes from Carolinas topology seminar
incorporate referee feedback

@@
 (\(\plII\) chooses 0 or 1 points from each choice by \(\plI\)) and \(G_{cf}(\mc A,\mc B)\)
-(\(\plII\) chooses cofinitely-many points).
+(\(\plII\) chooses cofinitely-many points). We use \(G_\star(\mc A,\mc B)\)
+to denote an arbitrary selection game.
 
@@
 We briefly note that the statement \(\plI\notprewin G_\star(\mc A,\mc B)\)
-is often denoted as the \term{selection principle} \(S_\star(\mc A,\mc B)\).
+is more often denoted as the \term{selection principle}
+\(S_\star(\mc A,\mc B)\). However, we will generally characterize
+results in terms of selection games rather than selection principles
+in order to emphasize the commonalities between the statements
+\(\plI\notwin G_\star(\mc A,\mc B)\) and
+\(\plI\notprewin G_\star(\mc A,\mc B)\).
 
@@
 some \(\theta:\omega\to\omega\) such that \(|\theta^{\leftarrow}(n)|=\aleph_0\) for
-each \(n<\omega\).
+each \(n<\omega\)
+(where \(\theta^{\leftarrow}\) denotes the inverse set map.
 
@@
 \begin{itemize}
+\item \(\plI\notwin G_{1}(\mc A,\mc B)\) if and only if
+\(S_{1}(\mc A,\mc B)\) if and only if
+\(\alpha_2(\mc A,\mc B)\).
 \item \(\plI\notwin G_{fin}(\mc A,\mc B)\) if and only if
 \(S_{fin}(\mc A,\mc B)\) if and only if
-\(\alpha_2(\mc A,\mc B)\), and
-\item \(\plI\notwin G_{1}(\mc A,\mc B)\) if and only if
-\(S_{1}(\mc A,\mc B)\) if and only if
-\(\alpha_4(\mc A,\mc B)\).
+\(\alpha_4(\mc A,\mc B)\), and
 \end{itemize}
@@
 
-We take advantage of the following lemma.
+We take advantage of the following lemma. The citation is given to Peter Nyikos who provides
+a nice proof. At a 2020 Fall meeting of the Carolinas Topology Seminar,
+it was suggested by Alan Dow that this lemma may be known as the
+``[Hausdorff] Disjoint Refinement Lemma'', as found in e.g. \cite[Lemma 3.4]{COMFORT1996149}.
 

### 2021-05-10 articles/bakers-game-coding/article.tex
add toy result on baker's game

--- 2020-01-03 articles/dual-selection-games/article.tex
@@
 
-\title{Dual selection games}
+\title{Coding Strategies in Baker's Game}
 
@@
 \begin{abstract}
-  Often, a given selection game studied in the literature has
-  a known dual game. In dual games, a winning
-  strategy for a player in either game may be used to create
-  a winning strategy for the opponent in the dual. 
-  For example, the Rothberger selection game involving open covers
-  is dual to the point-open game. This extends to a general
-  theorem: if \(\{\ran{f}:f\in\mathbf C(\mc R)\}\) is coinitial in \(\mc A\)
-  with respect to \(\subseteq\),
-  where \(\mathbf C(\mc R)=\{f\in(\bigcup\mc R)^{\mc R}:R\in\mc R\Rightarrow f(R)\in R\}\) 
-  collects the choice functions on the set \(\mc R\),
-  then \(G_1(\mc A,\mc B)\) and \(G_1(\mc R,\neg\mc B)\)
-  are dual selection games. 
+TODO
 \end{abstract}
@@
 
-\section{Introduction}
+\begin{abstract}
+TODO
+\end{abstract}
+
+\maketitle
+
+Let \(f^\leftarrow(y)=\setB{x\in A}{f(x)=y}\).
+
+\begin{proposition}\label{denseThreads}
+There exists a function \(f:\mathbb R\to\mathbb R^{<\omega}\) such that
+for each \(s\in\mathbb R^{<\omega}\), \(f^\leftarrow(s)\) is dense in \(\mathbb R\).
+\end{proposition}
+
+\begin{proof}
+Noting that \(|\mathbb R^{<\omega}|=|\mathbb R|=\mathfrak c\), we recall that
+\(\mathbb R\) may be partitioned into \(\mathfrak c\)-many parts, each dense in
+\(\mathbb R\) (e.g., the equivalence classes of \(x\sim y\) iff \(x-y\in\mathbb Q\)).
+We may then let \(f\) assign each equivalence class to a distinct sequence in
+\(\mathbb R^{<\omega}\).
+\end{proof}
+
+(We thank Lynne Yengulalp for
+suggesting the partition result that greatly simplified the preceding proof.)
+
+\begin{theorem}
+\(\plII\win G(W)\) if and only if \(\plII\codewin G(W)\).
+\end{theorem}
+\begin{proof}
+We need only show 
+\(\plII\notcodewin G(W)\) implies \(\plII\notwin G(W)\).
+Let \(\sigma\) be a perfect-information strategy for \(\plII\),
+and let \(f\) be given by Prop \ref{denseThreads}.
+
+First, we choose
+\[
+\tau(\tuple{a_0})\in
+\big(a_0,\sigma(\tuple{a_0})\big)\cap
+f^\leftarrow\big(\tuple{a_0}\big)
+\]
+that is, we guarantee \(a_0<\tau(\tuple{a_0})<\sigma(\tuple{a_0})\)
+and \(f\big(\tau(\tuple{a_0})\big)=\tuple{a_0}\).
+
+Given \(b_n,a_{n+1}\), define
+\(b_n'=\min\big(b_n,\sigma(f(b_n)\concat\tuple{a_{n+1}})\big)\),
+noting \(a_{n+1}<b_n'\). Now choose
+\[
+\tau(\tuple{b_n,a_{n+1}})\in
+\big(a_{n+1},b'\big)\cap
+f^\leftarrow\big(f(b_n)\concat\tuple{a_{n+1}}\big)
+\]
+that is, we guarantee
+\(a_{n+1}<\tau(\tuple{b_n,a_{n+1}})<b_n'\leq b_n\) and
+\(f\big(\tau(\tuple{b_n,a_{n+1}})\big)=f(b_n)\concat\tuple{a_{n+1}}\).
+
+Then \(\tau\) defines a coding strategy for \(\plII\); suppose it is
+defeated by \(\plI\) choosing \(a_n\) during round \(n\).
+
+Then if \(b_n\) is the move designated by \(\tau\) for player \(\plII\)
+during round \(n\), that is, \(b_0=\tau(\tuple{a_0})\) and
+\(b_{n+1}=\tau(\tuple{b_n,a_{n+1}})\),
+we have \(f(b_n)=\tuple{a_0,\dots,a_n}\).
+
+First, we see that
+\[a_0<a_1<\tau(\tuple{a_0})<\sigma(\tuple{a_0})\]
+
+And finally, we see that
+\[a_{n+1}<a_{n+2}<\tau(\tuple{b_n,a_{n+1}})<b_n'\leq
+\sigma(f(b_n)\concat\tuple{a_{n+1}})=\sigma(\tuple{a_0,\dots,a_{n+1}})\]
+
+Therefore we have shown that \(a_n\) is also a legal move against the
+perfect information strategy \(\sigma\) each round, and therefore
+\(\sigma\) is also not a winning strategy.
+\end{proof}
+
+\end{document}
+
+\section{TODO}
+
+\begin{definition}
+  An \term{\(\omega\)-length game} is a pair \(G=\<M,W\>\) such that
+  \(W\subseteq M^\omega\). The set \(M\) is the \term{moveset} of the game,
+  and the set \(W\) is the \term{payoff set} for the second player.
+\end{definition}
+
+In such a game \(G\), players \(\plI\)\end{proof}
+
+\end{document}
+
+\section{TODO}
 
@@
 In such a game \(G\), players \(\plI\) and \(\plII\) alternate making choices
+\(a_n\in M\) and \(b_n\in M\) during each round \(n<\omega\), 
+and \(\plII\) wins the game if and only if \(\<a_0,b_0,a_1,b_1,\dots\>\in W\).
+
+Often when defining games, \(\plI\) and \(\plII\) alternate making choices
 \(a_n\in M\) and \(b_n\in M\) during each round \(n<\omega\), 
